### 2021-09-01 docs/paper.Rmd
init

---
title: 'Financialisation of commodities: co-movement behind-the-scenes'
subtitle: "A tale of four factors"
date: "`r format(Sys.Date(), '%B %Y')`"
abstract: |
  The last two decades have seen major changes in the nature of the commodity markets with the influx of financial investor inflows followed by the financial crisis. We study the effects of these events on commodity futures pricing dynamics using commodity asset pricing techniques. We find that Keynesian and Working’s term structure paradigms based factors are best able to detect the effects of commodity financialisation, while the effects of the financial crisis and its aftermath are most clearly visible through the performance of the market factor. Besides, the effects of financialisation seem to go beyond mechanical effects induced by the rise of indexing.
bibliography: literature_files/references.bib
output:
  bookdown::gitbook:
    pandoc_args: html.yaml
    split_by: "chapter"
    css: style.css
    toc_depth: 3
    config:
      toc:
        collapse: subsection
        scroll_highlight: true
        before: |
          <li><a href="http://bautheac.com.s3-website.eu-west-2.amazonaws.com/research/financialization-co-movement/_book/index.html">Financialization: co-movement</a></li>
      edit: https://github.com/bautheac/financialisation-co-movement/edit/master/%s
      sharing:
        facebook: true
        twitter: true
        whatsapp: true
        all: ['whatsapp', 'twitter', 'facebook']
      download: [ ["paper.pdf", "pdf"] ]
      info: false
    includes:
      after_body: doc_suffix.html
  bookdown::pdf_book:
      pandoc_args: latex.yaml
      base_format: rticles::elsevier_article
      latex_engine: xelatex
      toc_depth: 3
      includes:
        in_header: preamble.tex
---

```{r globals, include = FALSE}
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)

folder <- "literature_files"; dir.create(folder)
path <- paste(folder, "references.bib", sep = "/")
download.file(
  "https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", 
  paste(folder, "references.bib", sep = "/")
)
path <- paste(folder, "format.r", sep = "/")
download.file(
  "https://www.dropbox.com/s/a88duv7rhqq8aar/bookdown-functions-book-building.r?dl=1",
  path
)
source(path)

tables_font_size <- 9L
tables_collapse_rows_align <- "top"
tables_cut <- TRUE
tables_hline <- "major"

latex_options <- c("repeat_header")
latex_repeat_header_text <- "\\textit{(continued)}"
latex_repeat_header_method <- "replace"

html_font <- "Cambria"

html <- knitr::is_html_output(); latex <- knitr::is_latex_output()
```

```{r, include=latex}
knitr::asis_output('\\cleardoublepage')
```

# Introduction {#introduction}
<!-- Introduction {#introduction} -->
<!-- ========================== -->

The last twenty years have seen major upheavals in the commodity markets with the onset of financialisation^[Starting around 2004, with a view of commodity markets as an emerging asset class and in an effort to hedge against inflation and seek diversification benefits [@buyuksahin_speculators_2014; @singleton_investor_2013], institutional investors sent forth an unprecedented flow of capital into commodity futures markets. This phenomenon is commonly referred to as the financialisation of commodities [@domanski_financial_2007].] as well as the period of the 2008 financial crisis and its aftermath. Financialisation appears to have affected multiple economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres. A vigorous legislative debate has led to regulatory changes accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section `r knitr::asis_output(ifelse(latex, '\\ref{co-movement-background}', '\\@ref(co-movement-background)'))` for a detailed discussion.]. In response to immediate policy concerns, the academic debate was initially framed rather narrowly. In this paper we take a fundamentally different empirical approach that is broader in scope. We consider the entire cross-section of actively traded commodities on futures markets and use a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations.  
Commodity futures markets have a history of being the classic physical commodity price risk shifting conduit for commodity specialists, and financialisation may have altered this long-standing paradigm with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants. This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of market participation. Factor model techniques are well suited to isolating common driving factors and detecting co-movement; building on theory we therefore develop a bespoke commodity-based asset pricing framework that seems well adapted to study these two issues simultaneously. It is comprised of factor models based both on fundamentals as well as liquidity considerations. One of these is based on the Keynes-Hicks [@keynes_some_1923; @keynes_treatise_1930; @hicks_value_1939; @hicks_value_1946] risk transfer approach to the term structure; the corresponding "theory of normal backwardation", complemented for the possibility of contango [@houthakker_restatement_1957; @cootner_returns_1960], postulates that futures prices for a given commodity are inversely related to the extent that commercial hedgers are short or long and using commercial hedging pressure (CHP) as a proxy for hedgers net market position we construct factor mimicking portfolios that capture the impact of hedging pressure as a systemic factor [@basu_capturing_2013]. Working's contending approach that relates futures price formation to storage costs in the theory of "the price of storage" [@working_theory_1949] forms the basis of another model that we consider where, following @szymanowska_anatomy_2014 and @fuertes_commodity_2015 who demonstrate that the term structure factor has explanatory power for the cross-section of commodity returns, we construct factor mimicking portfolios using roll-yield as a proxy for the front end shape of individual commodity term structures. We further consider a liquidity-based model following @hong_what_2012 who find that open interest growth has predictive power for individual commodity returns and again, using the latter measure as a proxy for individual commodity liquidity, we construct long-short factor mimicking portfolios.

```{r, include=html}
knitr::asis_output('<br/>')
```
```{r, include=latex}
knitr::asis_output('\\bigskip\n')
knitr::asis_output('\\setlength{\\parindent}{0pt}')
```

We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008^[Starting point based on earlier studies [@baker_financialisation_2014; @christoffersen_factor_2014].]); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).   
Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.  
The cross-sectional nature of financialisation [@cheng_financialisation_2014; @basak_model_2016] leads us to extend the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure first considered in @hong_what_2012. This paradigm implies that returns for individual commodities should be high in periods where **CHP** is low (**backwardation**) and low in periods where **CHP** is high (**contango**). Over the first period the cross-sectional average returns during phases of **backwardation** for both the US and UK commodities are positive and overall higher than during phases of **contango**, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis. Over the second period this pattern reverses, with both the US and UK commodities having higher returns during phases of **contango** as opposed to **backwardation**. This change in pattern suggests the onset of financialisation altered the traditional risk shifting nature of hedger’s behaviour, implied by the Keynesian hypothesis.   
The arrival of financial investors, on the other hand, raises the question of whether they functioned as liquidity providers or demanders. Arguments have been put forward in favour of both possibilities with @moskowitz_time_2012 arguing that financial investors provide liquidity and @kang_tale_2020 taking the opposite stance. Our analysis of returns in periods of low and high **CHP** before and during financialisation allows us to analyse this issue from a new perspective and suggests that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.  
@goldstein_speculation_2014 and @goldstein_commodity_2017 argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets. Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger’s positions (Keynesian perspective, theory of normal backwardation: @keynes_treatise_1930, @hicks_value_1939, @houthakker_speculators_1957, @telser_futures_1958), as well our term structure factor, based on backwardation as measured by roll yield (Working's perspective, theory of storage: @working_price_1933, @kaldor_speculation_1939, @working_theory_1948, @brennan_supply_1958, @cootner_returns_1960, @weymar_supply_1966, @danthine_information_1978, @turnovsky_determination_1983, @schwartz_stochastic_1997), to be best suited to measure the impact of financialisation.  
We analyse the pricing dynamics over the different periods by first studying the time series explanatory performance of the various factors on all the US traded commodities with the factors constructed using the latter set of commodities. The market-based factor outperforms the other three in the first period and, although its performance increases over the financialisation period, that of the CHP factor shows a greater improvement in a relative sense. The performance of the market factor is driven by agricultural and energy commodities in the first period while metals strongly contribute to the performance improvement observed over the second period. Similarly, the dramatic improvement of the CHP factor in the second period, is driven by the metals complex, particularly that of the long leg where they predominantly load. Average pairwise correlations amongst individual factors' best performing commodities increase across the board over the financialisation period, far beyond the average for the whole cross-section of US traded commodities. The increase is particularly strong for the long-short factors, in a relative sense, on which the metal complex loads significantly more during financialisation. This increase is due to the dramatic rise in average pairwise correlation amongst the US traded metals all of which exhibited high $R^{2}$ with respect to the CHP factor during financialisation which in turn is due to their common low level of CHP over this period. The CHP factor model thus seems able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialisation.   
We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period^[See section \@ref(co-movement-methods) for further details.] and evaluating its performance on these selected commodities as well as on all US traded commodities. The results of this exercise provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.  
The UK traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialisation. To that end, we examine the performance of the four factors on the six UK metals, when constructed from each set of factor picks. The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.  
The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes. Commodity futures returns fell dramatically into the crisis and the pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as evidence of cross-market linkages with the UK traded commodity subset. The post-crisis results, in contrast, show a substancial pullback in performance for the market factor across the board as well as evidence of decoupling between the US and UK markets. Besides, starting in the crisis the Keneysian paradigm of returns begins to revert with higher mean returns during low (**backwardation**) relative to high (**contango**) **CHP** phases and this pattern continues, more pronounced, over the post-crisis period. As pointed out in @basu_definancialisation, the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.

```{r, include=html}
knitr::asis_output('<br/>')
```
```{r, include=latex}
knitr::asis_output('\\bigskip')
```

Financialisation was an issue of such policy importance that it triggered legislative action. The debate was initially framed around adequacy of speculation, the burning issue of the day, and the ensuing academic analysis focused on the more mechanical effects of financialisation. With the benefit of hindsight, it appears this approach was perhaps too narrow, and it now seems necessary to address the phenomenon from a broader perspective. Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggered a process of "definancialisaion" in global commodity futures markets. The initial view of financialisation was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity futures prices^[@masters_testimony_2008; @masters_accidental_2008; @unctad_global_2009; @deschutter_food_2010; @gilbert_how_2010; @gilbert_speculative_2010; @herman_not_2011; @schumann_hunger_2011; @singleton_investor_2013.]. However, the fundamental question of the nature of the impact of financialisation across the entire cross-section of commodity futures markets has not yet been completely answered. We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2014, @ekeland_speculation_2016, @goldstein_commodity_2017.] and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in @tang_index_2012 and @basak_model_2016.

```{r, include=latex}
knitr::asis_output('\\cleardoublepage')
```

# Data & methods {#co-movement-data-methods}
<!-- Data & methods {#co-movement-data-methods} -->
<!-- ============ -->

## Background {#co-movement-background}

The period from 1998 to 2008 saw an influx of investment into commodity index linked products most of which made its way into the commodity futures market. Popular commodity indexes whose goal was to track the broad movement of commodity prices became accessible by means of swaps, exchange traded funds and exchange traded notes and attracted at least \$100 billion of net super-hoc investment over the 1998-2008 period. Concerns over the consequences of this financialisation phenomenon eventually led to legislative changes including the approval of Rule 76 FR 4752 issued by the US Commodity Futures Trading Commission (CFTC) on January 26^th^, 2011. This provision emanates from the Dodd-Frank Wall Street and Consumer Protection Act of 2010 (Title VII, Section 737) that mandates the CFTC to use position limits to restrict the flow of speculative capital into a number of commodity markets. The Rule was approved in a close 3-2 vote and the ensuing rule-making process was extremely contentious with several commissioners (Michael Dunn and Scott D. O’Malia in particular) expressing reservations about the lack of supporting evidence and the Rule also triggering thousands of comment letters as well as a lawsuit against the CFTC spearheaded by two Wall Street trade groups, the International Swaps & Derivatives Association (ISDA) and the Securities Industries & Financial Markets Association (SIFMA)^[ISDA & SIFMA v US CFTC; Complaint, 1:11-cv-02146; December 2^nd^, 2011.].  
A world-wide debate ensued about the role of index funds in commodity markets. The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs [@deschutter_food_2010; @gilbert_speculative_2010; @herman_not_2011; @schumann_hunger_2011; @unctad_global_2009]. Early US Senate investigations on the matter drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US agricultural and energy markets to the observed surges in both futures and cash prices [@masters_testimony_2008; @masters_accidental_2008]. This contention has since come to be known as the Masters’ hypothesis and was largely endorsed by the final US Senate report on the issue [@senate_excessive_2009]. At this stage, the question thrust on the academic sphere was whether "excessive speculation" (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices. A number of ensuing academic studies, most of which used commodity specific correlation and causality based analysis have since disproved this contention: @irwin_devil_2009, @sanders_adequacy_2010, @sanders_impact_2011, @sanders_new_2011, @irwin_commodity_2013, @brunetti_commodity_2014, @hamilton_effects_2015 and @bruno_financialisation_2017 investigated the issue in the context of the agricultural markets; meanwhile, @buyuksahin_speculators_2011, @tokic_speculation_2012, @fattouh_role_2013, @kilian_role_2014, @knittel_simple_2016 and @manera_modeling_2016 examined the energy markets while @bohl_does_2013, @kim_does_2015 and @boyd_prevalence_2016 studied both energy and agricultural markets and @irwin_index_2011, @irwin_financialisation_2012 as well as @stoll_commodity_2011 examined the commodity markets in general. Other studies have underlined various alterations in commodity pricing dynamics over the period. @gilbert_role_2014 reject the view that financialisation has not had any effects in the grains markets and demonstrate that trades originated by financial market participants, and specifically index investors, can move prices but tend to be typically volatility-reducing. @juvenal_speculation_2015 contend that the oil price increase between 2004 and 2008 was mainly driven by the strength of global demand but that the financialisation process of commodity markets also played a role. Likewise, @henderson_new_2015 show that non-information-based financial investments have important impacts on commodity prices. @cheng_financialisation_2014, on the other hand, show that in the case of index commodities, financialisation has transformed the risk sharing, and information discovery functions of commodity futures markets.

## Data {#co-movement-data}

Commodity index swaps, commodity index funds (CIFs), commodity-based exchange traded funds (ETFs) and notes (ETNs) or commodity linked notes (CLNs) were amongst the main investment vehicles that allowed institutional and retail investors to build up commodity exposure in the early 2000s [@boons_stock_2012; @henderson_new_2015; @irwin_index_2011; @unctad_global_2009; @schumann_hunger_2011]. Most of these products were primarily designed to track prominent commodity indexes among which the S&P-GSCI, the most popular. Most of its constituents at the time of writing form the basis of the broad cross-section of commodities that we consider in this study: corn-#2 yellow (XCBT), oats (XCBT), soybean meal (XCBT), soybean oil (XCBT), soybeans (XCBT), wheat-SRW (XCBT), cattle-feeder (XCME), cattle-live (XCME), lean hogs (XCME), cocoa (IFUS), coffee-C (IFUS), cotton-#2 (IFUS), lumber (XCME), orange juice (IFUS), sugar-#11 (IFUS), natural gas (XNYM), crude oil-WTI (XNYM), gasoline (XNYM), heating oil (XNYM), copper (XCEC), gold (XCEC), palladium (XNYM), platinum (XNYM) and silver (XCEC). Unleaded gasoline, the NYMEX legacy contract for gasoline, stopped trading in 2006 when it was replaced by Reformulated Gasoline Blendstock for Oxygen Blending (RBOB) with the two futures series trading alongside for most of the year. For our NYMEX gasoline data series, we consider unleaded gasoline up to September 1^st^, 2006 and RBOB gasoline thereafter, date at which liquidity for the latter overtook that for the former. We also consider the UK metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).  
The commodity futures trading commission (CFTC) operates a comprehensive system of collecting information on market participants known as the large trader reporting program (LTRP) where it records and reports to the public position data on market participants who have position levels in excess of a particular market specific threshold^[Current reporting level thresholds available at: [www.ecfr.gov](https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=&SID=970471b8455f4bab7db4110cfde50731&mc=true&r=SECTION&n=se17.1.15_103).]. The commission collects market data and position information daily from clearing members, futures commission merchants (FCMs) and foreign brokers and publishes corresponding summaries weekly in a series of market specific reports. In these reports, individual traders are categorised according to the nature of their trading activity on the basis of self-reported information^[CFTC form 40. Available at: [www.cftc.gov](https://www.cftc.gov/sites/default/files/idc/groups/public/@forms/documents/file/cftcform40.pdf).] that is subject to review by CFTC staff for reasonableness. Position information is then aggregated by category and asset type with each report providing an aggregation for a set of report specific categories and, for each category, a breakdown between futures only positions and positions in futures and options combined.  
In its legacy report, the commitment of trader report (COT) with data dating back to 1962, the CFTC distinguishes "commercial" and "non-commercial" market participants where a "commercial" participant is defined as one "[...] engaged in business activities hedged by the use of futures and option markets"^[See [CFTC regulation 1.3, 17 CFR 1.3(z)](https://www.gpo.gov/fdsys/pkg/CFR-1998-title17-vol1/xml/CFR-1998-title17-vol1-sec1-3.xml) for details.]. A third category, "non-reportable", aggregates positions for participants not meeting the reporting threshold. In response to concerns related to category accuracy^[See for example @ederington_who_2002.] the CFTC now refines its classification in the disaggregated commitment of trader report (DCOT) where participant categories include "Producer/Merchant/Processor/User", "Swap dealer", "Money manager" and "Other reportable" as well as in the supplemental commitment of trader report (SCOT) that details commodity index trader aggregate positions for thirteen agricultural commodity futures markets. Data for DCOT and SCOT date back to 2006 and 2007 respectively.  
We study the 1997/2018 period where we observe futures only position data from the COT report, the only CFTC report with data available for the whole period of interest; as well as futures term structure price and open interest data from Bloomberg.

## Methods {#co-movement-methods}

On the one hand, futures markets have a long history of serving commodity producers to alleviate their commodity price and output risks. @keynes_treatise_1930 and @hicks_value_1939 emphasise the "normal" behaviour of naturally short hedgers outsourcing their commodity risk to naturally long commodity specialist speculators. This market configuration is referred to as "backwardation" where futures are expected to trade at a discount to spot prices, providing speculators with incentives to take the long side. The opposite market paradigm is referred to as "contango". Working [@working_price_1933; @working_theory_1948; @working_hedging_1953] and Kaldor [@kaldor_speculation_1939] somehow relax this "supply-of-speculative-services" [@till_long_2007] approach by introducing processors and merchants, also commodity experts, on the hedgers side and relating the notions of backwardation and contango more directly to the term structure via the theory of storage where the shape of the front end of the term structure (basis) is directly related to the market price of storage.  
Financialisation, on the other hand, refers to the entry of financial investors into the commodity futures markets who, for the most part, are not commodity experts. Besides, these new market participants tend to exhibit herding like behaviour, often taking massive long-only positions on the whole cross-section of indexed commodities in an attempt to enhance returns while hedging against inflation and reaping further diversification benefits for portfolios with, in most cases, existing large positions across various asset classes [@brunetti_speculators_2016; @boyd_prevalence_2016; @cheng_convective_2014; @juvenal_speculation_2015; @singleton_investor_2013; @tang_index_2012]. This contrasts with the traditional approaches of Keynes and Working and in this context the issues of co-movement and aggregate market participants behaviour seem particularly relevant.  
Asset pricing techniques are well suited to study co-movement. Building on theory we therefore develop an ad-hoc commodity-based asset pricing framework that we believe is well adapted to study these two issues simultaneously and implement it over four periods of interest. The first, the pre-financialisation period, starts in 1997 and is naturally followed by financialisation, spanning the 2004/2008 period, and the financial crisis and its aftermath, spanning the 2008/2013 period. The last period spans the 2014/2018 period starting with the beginning of the tapering/end of the US Quantitative Easing program (QE).  
Using the weekly price, open interest and market position data described above we construct market portfolios of individual commodity nearby futures as well as mimicking portfolios for market, commercial hedging pressure, term structure and liquidity risk factors in returns. While our market portfolios are long only, equally weighted portfolios of particular commodity sets, our other mimicking portfolios for risk factors are constructed as combinations of two sub-portfolios (legs), one held long, one held short, which respective constituents are pooled on a weekly basis according to risk factor specific criteria. For each leg, the position weight for a particular asset for a particular week is contingent on the value of the corresponding sorting variable and its rank relative to the other assets in the pool. The sorting variable values for the asset pool are first rescaled so that the highest (lowest) value becomes 1 (0). Weights are then determined pairwise, starting from the extremes with the highest and lowest figures. A coefficient $\alpha$ is determined by dividing their difference (1 in this case) by the mean of the rescaled values. The high figure is attributed a score of $\frac{1}{n} \times \alpha$ where $n$ is the number of assets in the pool while the score for the low figure is $\frac{1/n}{\alpha}$. The operation is repeated for the pair of assets showing the second highest and second lowest values for the sorting variable and so on until all the assets in the pool are attributed a score. The individual asset weights are then determined by dividing each score by the sum of the scores. The weekly return for a particular mimicking portfolio is calculated as the difference between the weighted average return for constituents of the long portfolio and that for the constituents of the short portfolio. i.e, return on the mimicking portfolio for risk factor $i$ ($f_{i}$) for week $t$:

$$r_{t}^{f_{i}}=\sum_{j=1}^{x}w^{long}_{j,t} \times r_{j,t}-\sum_{j=n-x}^{n}w^{short}_{j,t} \times r_{j,t}$$
$n\equiv$ number of commodities in the set considered for mimicking portfolio construction.  
<!-- $x = \left \lceil n \cdot s \right \rceil$   -->
$x = n \cdot s$.  
$s\equiv$ selection threshold ($\frac{1}{3}$ here).  
$w^{*}_{j,t}\equiv$ week $t$ weight for commodity $j$ on the long or short leg.  
$r_{j,t}\equiv$ week $t$ front contract return for commodity $j$.  
$j\equiv$ commodity rank in the ordered set $Y_{t}^{f_{i}}$.   
$Y_{t}^{f_{i}}\equiv$ week $t$ ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is specific to $f_{i}$.

```{r, include=html}
knitr::asis_output('<br/>')
```
```{r, include=latex}
knitr::asis_output('\\bigskip\n')
```

For our portfolio CHP (commercial hedging pressure), we sort the set of commodities considered on past twenty-six-week average CHP from lowest to highest. The bottom third constituents (lowest $\overline{CHP}$s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg:

$$Y_{t}^{CHP}\equiv\left \{ \left \{ \overline{CHP_{1}}, \overline{CHP_{2}}, ..., \overline{CHP_{n}} \right \}, \leq \right \}$$

$\overline{CHP_{j}}=\frac{1}{26}\sum_{k=0}^{25}\frac{L_{j,t-k}}{L_{j,t-k}+S_{j,t-k}}$  
$L_{j,t}\equiv$ number of long positions held by commercial hedgers for week $t$ on the futures series of commodity $j$.  
$S_{j,t}\equiv$ number of short positions held by commercial hedgers for week $t$ on the futures series of commodity $j$.

```{r, include=html}
knitr::asis_output('<br/>')
```
```{r, include=latex}
knitr::asis_output('\\bigskip\n')
```

For our portfolio TS (term structure), we sort the set of commodities considered on past twenty-six-week average roll-yield from highest to lowest. The bottom third constituents (highest $\overline{RY}$s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg:

$$Y_{t}^{TS}\equiv\left \{ \left \{ \overline{RY_{1}}, \overline{RY_{2}}, ..., \overline{RY_{n}} \right \}, \geq \right \}$$

$\overline{RY_{j}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{F_{j,t-k}^{1}}{F_{j,t-k}^{2}} - 1)$   
$F_{j,t}^{1}\equiv$ week $t$ close price for commodity $j$ first nearby futures contract.  
$F_{j,t}^{2}\equiv$ week $t$ close price for commodity $j$ second nearby futures contract.

```{r, include=html}
knitr::asis_output('<br/>')
```
```{r, include=latex}
knitr::asis_output('\\bigskip\n')
```

For our portfolio OI (open interest), we sort the set of commodities considered on past twenty-six-week average front contract open interest growth from highest to lowest. The bottom third constituents (highest $\overline{OI^{\Delta \%}}$s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg.

$$Y_{t}^{OI}\equiv\left \{ \left \{ \overline{{OI}_{1}^{\Delta \%}}, \overline{{OI}_{2}^{\Delta \%}}, ..., \overline{{OI}_{n}^{\Delta \%}} \right \}, \geq \right \}$$

$\overline{{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{{OI}_{j,t-k}}{{OI}_{j,t-k-1}} - 1)$  
$OI_{j,t}\equiv$ open interest at close of week $t$ on the front (nearby) contract for commodity $j$.

```{r, include=html}
knitr::asis_output('<br/>')
```
```{r, include=latex}
knitr::asis_output('\\bigskip\n')
```

We use a time series regression approach where we start with regressions of the US traded individual commodity weekly front contract returns on returns to the mimicking portfolio for a particular risk factor where the portfolio is constructed using the whole cross-section of US traded commodities. The corresponding $R^{2}$s are averaged and the process is repeated for each of our four risk factors (market, hedging pressure, term structure and liquidity) and periods (1997/2003, 2004/2008, 2008/2013 and 2014/2018). For the long-short factors the results are reported independently for models where the regressor is the factor itself or one of its legs (long vs. short). The same operation is repeated for the two ($p=2$) and three ($p=3$) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectively, as well as for the four ($p=4$) factor model case where all the risk factor mimicking portfolios are included. Results are reported for the one-factor model case with the other results available on the [online results dashboard](http://18.135.131.217:3838/financialization-asset-pricing/).  
For each period we also implement the analysis described above over periods of low and high aggregate CHP (**CHP**), a notion that we believe is particularly relevant in the context of financialisation where issues of co-movement and aggregate market behaviour play a central role. We define **CHP** as the cross-sectional average of CHPs for a particular pool of assets. i.e., Week $t$ **CHP** for asset pool $x$:

$$\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}$$
$n\equiv$ number of commodities in set $x$.  
$CHP_{i,t}\equiv$ week $t$ CHP for commodity $i$ as defined above.

```{r, include=html}
knitr::asis_output('<br/>')
```
```{r, include=latex}
knitr::asis_output('\\bigskip\n')
```

We further define aggregate backwardation (**backwardation**) and contango (**contango**) **CHP** regimes as, for a given period, **CHP** levels below and above the period's median respectively and, in contrast with [@hong_what_2012] who aggregate across sub-sectors, the asset pool we consider for **CHP** construction include the whole cross-section of US traded commodities.  
In the next part of the analysis, our mimicking portfolios for risk factors, constructed from the set of all US traded commodities are used as commodity picking devices on the latter commodity set. For each risk factor and period, individual US traded commodity front returns are regressed on returns for the corresponding mimicking portfolio. Individual commodities are sorted by $R^{2}$ accordingly from highest to lowest and the top third (highest $R^{2}$s) are selected as commodity picks for the risk factor for the period. i.e, set of picks $P_{t}^{f_{i}}$ for risk factor $i$ ($f_{i}$) over period $t$:

$$P_{t}^{f_{i}}\equiv\left \{ P_{1}, P_{2}, ..., P_{x} \right \}$$
$x = n \cdot s$.    
$n\equiv$ number of commodities in the set considered for the picking exercise (twenty-four here).  
$s\equiv$ selection threshold ($\frac{1}{3}$ here).  
$P_{j}\equiv$ commodity pick $j$ for risk factor $f_{i}$ over period $t$  
$j\equiv$ rank in the ordered set $Y_{t}^{f_{i}}$  
$$Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}$$
$n\equiv$ number of commodities in the set considered for picking (twenty-four here).   
$\tilde{R_{j}^{2}}\equiv$ risk factor $f_{i}$ returns' explanatory power on commodity $j$ nearby futures returns over period $t$ as defined above.

```{r, include=html}
knitr::asis_output('<br/>')
```
```{r, include=latex}
knitr::asis_output('\\bigskip\n')
```

For each period we report the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every set of picks.  
In the last part of the analysis, for each period our mimicking portfolios for risk factors in returns are constructed using each set of commodity picks independently as the asset pool for portfolio construction. A similar time series approach to that described above is then implemented using these newly formed mimicking portfolios. In this case, a first set of dependent variables includes the sets of commodity picks themselves, a second set includes the whole cross-section of US traded commodities while a third set includes the six UK traded metals considered in the study.

```{r, include=latex}
knitr::asis_output('\\cleardoublepage')
```

# Results & discussion {#co-movement-results}
<!-- Results & discussion {#co-movement-results} -->
<!-- =================== -->

The descriptive statistics over the various time periods for our two sets of commodities (US and non-US) are shown in table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-stats-no-regimes}', '\\@ref(tab:co-movement-stats-no-regimes)'))`. The traditional Keynesian hedging pressure paradigm postulates a negative relationship between the return on an individual commodity futures and its hedging pressure. Financialisation has been seen as a cross-sectional commodity market phenomenon; this naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure. The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.

In table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-stats-regimes}', '\\@ref(tab:co-movement-stats-regimes)'))` the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period. Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another. For the remaining six commodities the higher mean return during **contango** is not statistically significant for any of them. For the six UK commodities, all metals, five of them had higher mean returns during phases of **backwardation** as compared to **contango** in the first period, with one of these differences being statistically significant at the 10% level while for the remaining asset (Zinc) the higher mean return during **contango** is not statistically significant. An equally weighted portfolio of the twenty-four US commodities had a mean return of 15.4% during **backwardation** phases, statistically significant at the 1% level, and a mean return of -1.1% during **contango**, both in the first period, with the difference between them statistically significant at the 5% level. The corresponding figures for an equally weighted portfolio of the UK metals were 4.4% and 0.3% respectively. These results provide broad support for an aggregate version of the Keynesian hedging pressure hypothesis and suggest that hedgers in the aggregate were engaged in risk transfer during this period.  
Over the second period the pattern essentially reverses. For the twenty-four US commodities over this period, fourteen have higher mean returns during phases of **contango** over **backwardation**. Four of the six UK metals achieved higher mean returns over **contango** relative to **backwardation** phases with the difference being statistically significant for one commodity. The equally weighted US portfolio had a mean return of 15.7% over **backwardation** against 16.2% during phases of **contango**, both statistically significant at the 10% level. The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 8% during **backwardation** rising to 35.6% during **contango**.  
The onset of financialisation thus seems to have engendered a change in the nature of hedger’s behaviour in the aggregate, taking it away from the traditional Keynesian view of risk shifting. This phenomenon has been noted in earlier theoretical and empirical work [@danthine_information_1978; @stout_why_1998] in different contexts from which two competing models of behaviour have emerged. The information arbitrage model [@grossman_impossibility_1980; @danthine_information_1978; @kyle_informed_1989] implies that hedgers may often be seeking out counterparties to trade with rather than being purely passive. This issue is also raised in both @cheng_financialisation_2014 and @stulz_rethink_1996 who point out that hedgers may be taking a view on prices just as speculators do. In fact, by hedging away some of their risk, hedgers are able to speculate more heavily based on their disagreement against speculators regarding futures price movement [@simsek_speculation_2013], which fits into a heterogeneous expectation theory of speculation^[@hirshleifer_speculation_1975; @hirshleifer_reply_1976; @hirshleifer_theory_1977]. As @stout_why_1998 points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves speculation as this form of trading is regarded as non-productive^[@duffie_challenges_2014 also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.]. In the second model hedgers are seen as liquidity providers as in @kang_tale_2020 with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions. Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-CHP-US}', '\\@ref(tab:co-movement-time-reg-US-CHP-US)'))` supports this view. We regress commodity futures front returns on individual commercial hedging pressure (CHP) as well as aggregate CHP (**CHP**), our market wide measure of CHP, in separate models and find that the explanatory power of CHP at the individual commodity level decreases over the financialisation period with the US cross-sectional average $R^{2}$ falling down to 20.8% from 25.8% in the previous period while that of **CHP** increases (7.1% vs 5.4%). Financialisation therefore seems to have had the effect of loosening the extent to which futures risk premiums relate to commodity specific commercial hedging motives while strengthening that to which they relate to broader dynamics such as cross-sectional liquidity provision. The pattern is strongest for the metals sector where the average $R^{2}$ drops down to 19.1% from 28.1% between the two periods at the individual level while it rises from 8.4% to 15.7% at the aggregate level. The symmetry breaks in the crisis period, with the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%), before eventually resuming post-crisis with a further rise at the individual level (27.2% vs 22.5%) and a drop at the aggregate level (7.5% vs 14.7%) suggesting a return to legacy commodity specific dynamics.

The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-US}', '\\@ref(tab:co-movement-time-reg-US-facts-US)'))`. Over the first period the market factor has the best average time series performance with the highest average $R^{2}$ with all three futures market factors performing poorly and the overall performance consistent across periods of high and low **CHP** (below period median). The two factor models average $R^{2}$s (results available on the [online results dashboard](http://18.135.131.217:3838/financialization-asset-pricing/)) are roughly the sum of the one factor $R^{2}$s indicating that the factors are almost orthogonal over this period. The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average $R^{2}$ increasing to 8.2% in the second period relative to 1.7% in the first with this improvement coming from the long leg that shows a greater improvement (4.5% to 15.1%) relative to the short (3% to 4%) bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period. The performance of the market factor also improves though not by as much in a relative sense (21.6% from 11.7%) and both the term structure factor and the open interest growth factor show a much smaller improvement in performance with smaller differences between legs. Over all periods, all of our factor models show similar performance across regimes of high and low **CHP**.

We next investigate the top eight of the US traded commodities which achieved the highest time series $R^{2}$ for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-picks}', '\\@ref(tab:co-movement-picks)'))`. For the CHP factor the commodities that achieve high $R^{2}$ in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor. The same applies to the open interest and term structure factors with CHP replaced by open interest growth and roll yield respectively; while for the market factor the picks are those that co-vary most strongly with the market factor over that period. For the CHP factor, we observe a change in the picks between the first and the second period; the picks in the first period included five agricultural commodities and three metals while in the second period they include all the five base and precious metals and only three agricultural commodities. This pattern is also visible for the term structure factor for which there are four metals (copper, silver, gold and platinum) picks in the second period against two in the first (palladium and platinum) as well as for the open interest nearby growth factor for which there are three metals (silver, gold and platinum) picks in the second period against one in the first (platinum). The market factor has three metal picks in the second period (palladium, gold and silver) while all the picks in the first period were agricultural or energy commodities. Over the third period, the average CHP factor shows the same metal picks with the agriculturals replaced by energy commodity; the open interest nearby growth factor still has three metal picks with gold swapped for copper and both the market and term structure factors have one, copper. The table also shows the proportion of time that these picks were constituents of the corresponding factor. All the picks of the long-short factors (average CHP, open interest nearby growth and term structure factors) were constituents of the corresponding factor for some proportion of time in all of the time periods. In this respect, there is a contrast between the first and second periods with the average CHP and open interest nearby growth factor picks appearing predominantly on the long side of the corresponding factor in the second period, as opposed to both legs in the first. The pattern is particularly strong for the metals and energy commodities respectively, with the exception of copper for the average CHP factor that lives in the short leg a higher proportion of the time over the financialisation period. The pattern is reversed for the term structure factor where the picks appear predominantly on the short leg in the second period, as opposed to both legs in the first with the pattern again strongest for the metals. This behaviour continues over the third period for the average CHP and open interest nearby growth factors and indicates that their picks consistently exhibited low commercial hedging pressure and high front contract open interest growth respectively while indicating that the term structure factor picks showed low roll yield in the first and second period.

In table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-correlations}', '\\@ref(tab:co-movement-correlations)'))`, we show the average pairwise returns correlation between each set of picks in each time period. This exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement. In the first period the average picks pairwise correlation for the long-short factors ranges from 7.1% (term structure factor picks) to 12.4% (open interest factor picks) while the market factor picks show the highest figure (23.7%). In the second period the figures for the long-short factors rise sharply; up to 22.9% from 8.1% for the average CHP factor picks, up to 32.4% from 12.4% for the open interest factor picks and up to 23.4% from 7.1% for the term structure factor picks. This increase is stronger than that for the market factor picks in a relative sense and is a consequence of the dramatic increase in average pairwise price correlation amongst the US traded metals which dominate the average CHP factor set of picks and which presence is stronger amongst both the open interest and term structure factor sets of picks over the financialisation period. The higher figures for the open interest factor are driven by the strong presence of the energy complex amongst the corresponding picks. The latter exhibits much higher average pairwise correlations than the other sectors in both periods although lower in the second relative to the first which reinforces to role played by the metals in the sharp increase in average pairwise correlation amongst picks for this factor. With regards to **CHP** regimes, although not very pronounced, a pattern is noticeable. For the market, open interest and term structure factor picks, average pairwise correlations are stronger over phases of **contango** in the first period and over phases of **backwardation** in the financialisation period, eventually reverting back to being stronger over **contango** phases in the crisis period with the CHP factor sets of picks showing the opposite pattern. Overall, these results suggest an increase in correlation between non-price attributes co-movement and price co-movement over the financialisation period. It is also interesting to note that US traded metals returns were negatively correlated with the rest of US traded commodities in the first period and positively in the second.

To further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their explanatory performance on these sets of picks over the four periods independently. The results are shown in table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-picks-facts-picks}', '\\@ref(tab:co-movement-time-reg-picks-facts-picks)'))`. The long-short factors for a particular attribute select the top and bottom two of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks. In the absence of price co-movement between the picks, this market factor will achieve an average $R^{2}$ of around 12.5%^[Market factor lemma: $\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv$ size of market portfolio (eight here).], while there is no non-zero $R^{2}$ lower bound for the corresponding long-short factors. A high average $R^{2}$ for the market factor is indicative of strong price co-movement. In this respect, the most remarkable change in performance in a relative sense is that of the market factor built from the CHP factor sets of picks with the average $R^{2}$ more than doubling, from 18.6% up to 38.1%. For the long-short factors on the other hand it is indicative of simultaneous attribute and price co-movement. For the factors built from the market factor picks the increase is strongest in a relative sense for the CHP factor with the $R^{2}$ more than doubling, going from 5.6% in the first period up to 12.4% in the second with the increase stronger for the long leg (17.1% vs. 27.9%) relative to the short (16.5% vs. 21.4%). In the case of the factors built from the CHP factor picks, the CHP factor built with its own picks shows a remarkable increase in a relative sense with the $R^{2}$ tripling, from 7.2% to 21.4% and the long leg showing a much greater increase relative to the short (10.4% to 31.1% vs. 8.3% to 9.8%). The performance of the term structure factor built from the CHP factor sets of picks also shows a sizable increase in a relative sense, from 3.5% to 5.3% and even more remarkable in this case is the substantial increase in performance of the short leg, from 6.3% to 15.7% relative to the long (7.5% to 9.8%). The pattern is reversed for the CHP factor built from the term structure factor picks where the average $R^{2}$ increases from 4.7% to 8% with the performance of the long leg increasing from 11.9% to 28.1% vs. 5.5% to 9.1% for the short. The performance of the term structure factor constructed from its own sets of picks also shows a substantial increase, from 5.1% to 8.4%  with, here again the increase in performance relatively stronger for the short leg, from 6% to 16.1% vs. 7.6% to 12.1% for the long. Taken together with the previous results showing that the metal complex predominantly loads on the long and short legs of the original CHP and term structure factors respectively, these results provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation.

In table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-picks}', '\\@ref(tab:co-movement-time-reg-US-facts-picks)'))` we assess the performance of the same factors on all the commodities instead of just the picks. While the average $R^{2}$s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-picks-facts-picks}', '\\@ref(tab:co-movement-time-reg-picks-facts-picks)'))`. In contrast, the average CHP factor built with average CHP factor picks shows a smaller absolute increase in average $R^{2}$ indicating that the link between CHP co-movement and price co-movement is stronger amongst the picks which are predominantly metals. Taken together, the results in tables `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-picks-facts-picks}', '\\@ref(tab:co-movement-time-reg-picks-facts-picks)'))` and `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-picks}', '\\@ref(tab:co-movement-time-reg-US-facts-picks)'))` suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.  
To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-UK-facts-picks}', '\\@ref(tab:co-movement-time-reg-UK-facts-picks)'))`. In the first period, although all sets of picks, except that of the market factor, included at least one metal, the average $R^{2}$s are very low; close to zero in most cases. These figures drastically increase across the board in the financialisation period and show a pattern similar to that observed in the US complex. The market factor built from the CHP and term structure factor sets of picks shows the sharpest increase in performance, relative to using the other sets of factor picks; rising to 20.1% from 1.5% and to 15% from 0.8% respectively. The increase in $R^{2}$ for the market factor built with market factor picks is more modest, providing further evidence of concentration of co-movement in the metals sector during financialisation. Here again the change in performance for the CHP and term structure factor legs stands out where the factors are built with their own as well as each other's sets of picks. The average $R^{2}$ for the long leg of the CHP factor built with its own sets of picks increases from 1% to 11% while the short leg shows no significant change. The opposite holds for the term structure factor built from its own set of picks with the short leg performance increasing from 0.1% to 14% while that of the long leg remains below 1%. Building these factors from each other's sets of picks produces a similar pattern with the performance of the long leg of the CHP factor built from the term structure factor picks increasing from 0.7% to 11.4%; a much greater increase relative to the short leg although in this case the latter also shows a sizable increase in performance (0.3% to 6%). The performance of the short leg of the term structure factor built from the CHP factor sets of picks on the other hand increases from 0.3% to 19.2% while the performance for the long leg in the second period remains below 1.5%. Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working's term structure paradigms. There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of @kang_tale_2020 who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).

The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results. Returns fall sharply relative to the financialisation period (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-stats-no-regimes}', '\\@ref(tab:co-movement-stats-no-regimes)'))`. with eighteen US commodities along with all six UK traded metals showing lower mean returns. Returns for equally weighted portfolios of both sets of assets fall down to 9.4% and 5.3% from 15.9% and 21.8% respectively. Returns are mostly higher during phases of **backwardation** relative to **contango** (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-stats-regimes}', '\\@ref(tab:co-movement-stats-regimes)'))`) with fifteen US assets and five of the UK traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets. Volatility is moderately higher for both sets with fifteen US commodities and three UK metals showing higher figures and interestingly eminently higher over phases of **contango**; out of the US complex only Sugar-#11 (IFUS) and none of the UK traded metals show higher volatility figures over **backwardation** phases. The performance of the market factor dominates the US commodity complex over the period with a 50% increase in mean average $R^{2}$ to over 30% (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-US}', '\\@ref(tab:co-movement-time-reg-US-facts-US'))`) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors. The average pairwise correlation amongst the market factor picks increases beyond 50% while there is a leveling in that amongst the picks of the long-short factors as shown in table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-correlations}', '\\@ref(tab:co-movement-correlations)'))`. Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-picks}', '\\@ref(tab:co-movement-time-reg-US-facts-picks))'))`). Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities. Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-UK-facts-picks}', '\\@ref(tab:co-movement-time-reg-UK-facts-picks))'))` provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average $R^{2}$ increasing to 31.7% from 10.2% in the previous period.  
The returns pullback continues into the post-crisis period with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively. Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period. The figures for the equally weighted portfolios of US and UK assets drop to 9.9% and 16.2% respectively, very close to pre-financialisation levels. The pattern of reversion toward the pre-financialisation Keynesian paradigm intiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of **backwardation** relative to **contango** (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-stats-regimes}', '\\@ref(tab:co-movement-stats-regimes))'))`), more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases. The difference is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**. The pattern is more pronounced for the UK traded subset with all six assets showing higher mean returns in **backwardation** with the difference significant at the 1% level for Nickel-primary (XLME), 5% level for Aluminium (XLME) and 10% level for Zinc (XLME). It also extends to equally weighted portfolios of US and UK traded assets that both show higher mean returns during **backwardation** with the difference significant at the 5% level for the UK portfolio and the figure close to the 10% level significance threshold for the portfolio of US assets. Volatilities are overall higher in **contango** although less so than over the previous period with seventeen US commodities showing higher figures over **contango** against twenty-three in the crisis period. The pattern extends to three of the six UK traded metals with the difference significant at the 1% level for Copper (XLME) and Tin (XLME) and at the 5% level for Zinc (XLME) while differences are not significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit higher volatility over **backwardation** phases. Equally weighted portfolios of US and UK traded assets on the other hand both show higher volatility in **contango** with the difference significant at the 1% level for both. Over the financialisation period in contrast volatilities were predominantly higher in **backwardation** for US traded assets with fourteen commodities showing higher volatility figures in these phases; the post-crisis pattern of results for volatilities thus likewise shows signs of reversion to pre-financialisation standards. Average pairwise correlations amongst factor picks (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-correlations}', '\\@ref(tab:co-movement-correlations))'))`) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1% to 26.1%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks. The performance of the market factor on the US complex declines below financialisation levels (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-US}', '\\@ref(tab:co-movement-time-reg-US-facts-US))'))`) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-picks}', '\\@ref(tab:co-movement-time-reg-US-facts-picks))'))`) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors. Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-UK-facts-picks}', '\\@ref(tab:co-movement-time-reg-UK-facts-picks))'))` provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks. 
Taken together the patterns of results over the crisis and post-crisis periods echo those in @basu_definancialisation in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex, in other words, a process of "definancialisation".

```{r, include=latex}
knitr::asis_output('\\cleardoublepage')
```

# Conclusion {#conclusion}
<!-- Conclusion {#conclusion} -->
<!-- ============ -->

In the early 2000s, against a backdrop of a low yield environment and poor stock market performance, a combination of financial innovations^[Commodity price indexes and the ad-hoc financial instruments enabling investment in them were the main financial innovations which allowed large global banks to offer commodity investment products to institutional and retail investors. In 1991 Goldman Sachs created the S&P-GSCI which provides investors with buy-side exposure to commodities via the OTC swap market and thus without having to participate in the formal futures markets with their position limit restrictions. At this stage, these restrictions still applied to the issuing institutions though, as they hedged the corresponding commodity swap exposure in the futures markets. The first commodity-based ETFs were created through buying physical precious metals with gold and silver ETFs offered as early as 2002/2003. The regulatory hurdle here related to the licensing of commodity trading professionals. Typically, investors had to sign a statement with their broker stating that they understood the risks of commodity investments; a rather inconvenient paperwork for a product designed to trade like a stock, as set forth by a number of industry players at the time.] and regulatory changes^[In 2000, the Commodity Futures Modernization Act (CFMA) granted non-agricultural commodity futures statutory exemption from regulation ("Enron loophole"). It still required agricultural commodity derivatives be traded on a CFTC-regulated exchange however. Eventually, the CFTC classified swap dealers as "bona fide" hedgers, granting them position limits exemption ("swap dealer loophole"). In 2005, the CFTC waived the rule that required commodity investors to sign a statement saying they understood the risks, letting the funds replace it with their prospectus. The regulatory bottleneck that prevented the large-scale expansion of commodity index investment was no more.] led to large inflows of institutional capital into the commodity futures markets. This process known as "financialisation" spurred a heated public policy debate about whether the ensuing increase in open interest and trading volume in commodity futures exerted upward pressure on prices. The debate spread to the legislative sphere, with the US senate launching formal investigations, and was thrust onto the academic community as a matter of urgency. Perhaps in response to this, most of the early studies focused on the more mechanical effects of financialisation, relying on commodity specific causality and correlation-based analysis. The contention eventually triggered legislative action and new position limits were introduced in a number of grains and energy futures markets with substantial potential effects on their functioning and consequently, to a larger extent, on that of the economic system as a whole. With the benefit of hindsight, the focus of the debate appears to have been too narrow, and the ensuing regulatory changes might thus have been unwarranted; it therefore seems important to analyse the effects of financialisation from a broader perspective which we do in this study. Factor model techniques are well suited to isolating common driving factors and detecting co-movement, a central issue in financialisation which we believe the existing literature has not fully analysed; we thus consider the entire cross-section of actively traded commodities on futures markets and use a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations. Our analysis suggests that, beyond energy and agriculturals, financialisation appears to have had a substantial impact on the metals sector at the global level. The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in commodity pricing dynamics. In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have set off a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of "definancialisation" in global commodity futures markets.

```{r, include=latex}
knitr::asis_output('\\cleardoublepage')
knitr::asis_output('\\newgeometry{left=2.50cm, right=2.50cm, top=2.50cm, bottom=3cm}')
```

# Tables {#tables .unnumbered}
<!-- Tables {#tables .unnumbered} -->
<!-- ============ -->

```{r}
tables <- readr::read_rds(here::here("explore", "tables", "tables.rds"))
```

```{r co-movement-stats-no-regimes}
table <- dplyr::filter(tables, analysis == "descriptive statistics (no regimes)") %>%
  dplyr::select(results) %>% tidyr::unnest(results)

caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively. The results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("asset", "estimate", "past", "financialisation", "crisis", "post-crisis")
align <- c("llrrrr")

table <- kbl(
    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(columns = 1L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
  pack_rows("individual commodities", 1, 60) %>%
  pack_rows("equally weighted portfolios", 61, 64)

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

```{r, include=html}
knitr::asis_output('<br/><br/>')
```
```{r, include=latex}
knitr::asis_output('\\newpage')
```

```{r co-movement-stats-regimes}
table <- dplyr::filter(tables, analysis == "descriptive statistics (regimes)") %>%
  dplyr::select(results) %>% tidyr::unnest(results)

caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively. Aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("asset", "regime", "estimate", "past", "financialisation", "crisis", "post-crisis")
align <- c("lllrrrr")

table <- kbl(
    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
  pack_rows("individual commodities", 1, 120) %>%
  pack_rows("equally weighted portfolios", 121, 128)

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

```{r, include=html}
knitr::asis_output('<br/><br/>')
```
```{r, include=latex}
knitr::asis_output('\\newpage')
```

```{r co-movement-time-reg-US-CHP-US}
table <- dplyr::filter(
  tables,
  analysis == "regressions - time series - US commodity returns ~ US commodity CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(regressor, dplyr::everything())

caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against relative changes in commercial hedging pressure (CHP) both at the individual (commodity CHP) and aggregate (aggregate CHP) levels independently. The results are reported for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("regressor", "sector", "subsector", "past", "financialisation", "crisis", "post-crisis")
align <- c("lllrrrr")

table <- kbl(
    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

```{r, include=html}
knitr::asis_output('<br/><br/>')
```
```{r, include=latex}
knitr::asis_output('\\newpage')
```

```{r co-movement-time-reg-US-facts-US}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - US commodities ~ factors from US commodities"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    factor = as.character(factor),
    factor = ifelse(factor == "OI nearby", "open interest", factor)
  )

caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities. The asset pool for the factor mimicking portfolio construction includes the twenty four US commodities. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption

colnames <- c("factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("lllrrrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, col.names = colnames, align = align
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

```{r, include=html}
knitr::asis_output('<br/><br/>')
```
```{r, include=latex}
knitr::asis_output('\\newpage')
```

```{r co-movement-picks}
table <- dplyr::filter(
  tables, analysis == "proportions"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(period = stringr::str_replace_all(period, "present", "post-crisis")) %>%
  dplyr::mutate(
    factor = as.character(factor),
    factor = ifelse(factor == "OI nearby", "open interest", factor)
  )

caption <- "This table shows the factor 'picks' for the market as well as the long-short factors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). For each factor and period the twenty four US commodities are regressed against the corresponding factor mimicking portfolio and ranked by $R^{2}$. The top eight commodities are selected as 'picks' for the corresponding factor and period. The table also shows the proportion of time, for each period, each individual pick lives on both legs (long vs. short) of its picking factor. The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor. Factors construction details are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "period", "pick", "long", "short")
align <- c("lllrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    )

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

```{r, include=html}
knitr::asis_output('<br/><br/>')
```
```{r, include=latex}
knitr::asis_output('\\newpage')
```

```{r co-movement-correlations}
table <- dplyr::filter(
  tables, analysis == "average correlations (amongst factor picks)"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    factor = as.character(factor),
    factor = ifelse(factor == "OI nearby", "open interest", factor)
  )

caption <- "This table shows the average pairwise correlation amongst factor picks for each factor and period independently. The figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor. Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llrrrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    )

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

```{r, include=html}
knitr::asis_output('<br/><br/>')
```
```{r, include=latex}
knitr::asis_output('\\newpage')
```

```{r co-movement-time-reg-picks-facts-picks}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - factor picks ~ factors from picks"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
    dplyr::across(
      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
    )
  )

caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the various sets of factor picks are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the picks. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llllrrrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    )

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

```{r, include=html}
knitr::asis_output('<br/><br/>')
```
```{r, include=latex}
knitr::asis_output('\\newpage')
```

```{r co-movement-time-reg-US-facts-picks}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - US commodities ~ factors from picks"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
    dplyr::across(
      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
    )
  )

caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llllrrrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    )

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size,
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

```{r, include=html}
knitr::asis_output('<br/><br/>')
```
```{r, include=latex}
knitr::asis_output('\\newpage')
```

```{r co-movement-time-reg-UK-facts-picks}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - UK metals ~ factors from picks"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
    dplyr::across(
      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
    )
  )

caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the six UK metals are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the six UK metals. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llllrrrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(
    columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
  )

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

```{r, include=latex}
knitr::asis_output('\\cleardoublepage')
knitr::asis_output('\\restoregeometry')
```

# References {#references .unnumbered}
<!-- References {#references .unnumbered} -->
<!-- ========== -->

### 2021-09-01 docs/paper.tex
init

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

  \journal{no journal yet} % Sets Journal name

\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Financialisation of commodities: co-movement behind-the-scenes},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

% Pandoc citation processing

% Pandoc header
\usepackage[width=1\textwidth]{caption}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}
\begin{frontmatter}

  \title{Financialisation of commodities: co-movement behind-the-scenes}
    \author[strath]{Devraj Basu\corref{1}}
   \ead{devraj.basu@strath.ac.uk} 
    \author[strath]{Olivier Bauthéac}

      \address[strath]{University of Strathclyde Business school}
      \cortext[1]{Corresponding Author}

  \begin{abstract}
  The last two decades have seen major changes in the nature of the commodity markets with the influx of financial investor inflows followed by the financial crisis. We study the effects of these events on commodity futures pricing dynamics using commodity asset pricing techniques. We find that Keynesian and Working's term structure paradigms based factors are best able to detect the effects of commodity financialisation, while the effects of the financial crisis and its aftermath are most clearly visible through the performance of the market factor. Besides, the effects of financialisation seem to go beyond mechanical effects induced by the rise of indexing.
  \end{abstract}

 \end{frontmatter}

\cleardoublepage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The last twenty years have seen major upheavals in the commodity markets with the onset of financialisation\footnote{Starting around 2004, with a view of commodity markets as an emerging asset class and in an effort to hedge against inflation and seek diversification benefits (Büyükşahin and Robe, 2014; Singleton, 2013), institutional investors sent forth an unprecedented flow of capital into commodity futures markets. This phenomenon is commonly referred to as the financialisation of commodities (Domanski and Heath, 2007).} as well as the period of the 2008 financial crisis and its aftermath. Financialisation appears to have affected multiple economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres. A vigorous legislative debate has led to regulatory changes accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors\footnote{See section \ref{co-movement-background} for a detailed discussion.}. In response to immediate policy concerns, the academic debate was initially framed rather narrowly. In this paper we take a fundamentally different empirical approach that is broader in scope. We consider the entire cross-section of actively traded commodities on futures markets and use a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations.\\
Commodity futures markets have a history of being the classic physical commodity price risk shifting conduit for commodity specialists, and financialisation may have altered this long-standing paradigm with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants. This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of market participation. Factor model techniques are well suited to isolating common driving factors and detecting co-movement; building on theory we therefore develop a bespoke commodity-based asset pricing framework that seems well adapted to study these two issues simultaneously. It is comprised of factor models based both on fundamentals as well as liquidity considerations. One of these is based on the Keynes-Hicks (Hicks, 1946, 1939; Keynes, 1930, 1923) risk transfer approach to the term structure; the corresponding ``theory of normal backwardation'', complemented for the possibility of contango (Cootner, 1960; H. Houthakker, 1957), postulates that futures prices for a given commodity are inversely related to the extent that commercial hedgers are short or long and using commercial hedging pressure (CHP) as a proxy for hedgers net market position we construct factor mimicking portfolios that capture the impact of hedging pressure as a systemic factor (Basu and Miffre, 2013). Working's contending approach that relates futures price formation to storage costs in the theory of ``the price of storage'' (Working, 1949) forms the basis of another model that we consider where, following Szymanowska et al. (2014) and Fuertes et al. (2015) who demonstrate that the term structure factor has explanatory power for the cross-section of commodity returns, we construct factor mimicking portfolios using roll-yield as a proxy for the front end shape of individual commodity term structures. We further consider a liquidity-based model following Hong and Yogo (2012) who find that open interest growth has predictive power for individual commodity returns and again, using the latter measure as a proxy for individual commodity liquidity, we construct long-short factor mimicking portfolios.

\bigskip
\setlength{\parindent}{0pt}

We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008\footnote{Starting point based on earlier studies (Baker, 2014; Christoffersen et al., 2014).}); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).\\
Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.\\
The cross-sectional nature of financialisation (Basak and Pavlova, 2016; Cheng and Xiong, 2014) leads us to extend the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in Hong and Yogo (2012). This paradigm implies that returns for individual commodities should be high in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in periods where \textbf{CHP} is high (\textbf{contango}). Over the first period the cross-sectional average returns during phases of \textbf{backwardation} for both the US and UK commodities are positive and overall higher than during phases of \textbf{contango}, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis. Over the second period this pattern reverses, with both the US and UK commodities having higher returns during phases of \textbf{contango} as opposed to \textbf{backwardation}. This change in pattern suggests the onset of financialisation altered the traditional risk shifting nature of hedger's behaviour, implied by the Keynesian hypothesis.\\
The arrival of financial investors, on the other hand, raises the question of whether they functioned as liquidity providers or demanders. Arguments have been put forward in favour of both possibilities with Moskowitz et al. (2012) arguing that financial investors provide liquidity and Kang et al. (2020) taking the opposite stance. Our analysis of returns in periods of low and high \textbf{CHP} before and during financialisation allows us to analyse this issue from a new perspective and suggests that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.\\
Goldstein et al. (2014) and Goldstein and Yang (2017) argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets. Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger's positions (Keynesian perspective, theory of normal backwardation: Keynes (1930), Hicks (1939), H. S. Houthakker (1957), Telser (1958)), as well our term structure factor, based on backwardation as measured by roll yield (Working's perspective, theory of storage: Working (1933), Kaldor (1939), Working (1948), Brennan (1958), Cootner (1960), Weymar (1966), Danthine (1978), Turnovsky (1983), Schwartz (1997)), to be best suited to measure the impact of financialisation.\\
We analyse the pricing dynamics over the different periods by first studying the time series explanatory performance of the various factors on all the US traded commodities with the factors constructed using the latter set of commodities. The market-based factor outperforms the other three in the first period and, although its performance increases over the financialisation period, that of the CHP factor shows a greater improvement in a relative sense. The performance of the market factor is driven by agricultural and energy commodities in the first period while metals strongly contribute to the performance improvement observed over the second period. Similarly, the dramatic improvement of the CHP factor in the second period, is driven by the metals complex, particularly that of the long leg where they predominantly load. Average pairwise correlations amongst individual factors' best performing commodities increase across the board over the financialisation period, far beyond the average for the whole cross-section of US traded commodities. The increase is particularly strong for the long-short factors, in a relative sense, on which the metal complex loads significantly more during financialisation. This increase is due to the dramatic rise in average pairwise correlation amongst the US traded metals all of which exhibited high \(R^{2}\) with respect to the CHP factor during financialisation which in turn is due to their common low level of CHP over this period. The CHP factor model thus seems able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialisation.\\
We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period\footnote{See section \ref{co-movement-methods} for further details.} and evaluating its performance on these selected commodities as well as on all US traded commodities. The results of this exercise provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.\\
The UK traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialisation. To that end, we examine the performance of the four factors on the six UK metals, when constructed from each set of factor picks. The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.\\
The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes. Commodity futures returns fell dramatically into the crisis and the pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as evidence of cross-market linkages with the UK traded commodity subset. The post-crisis results, in contrast, show a substancial pullback in performance for the market factor across the board as well as evidence of decoupling between the US and UK markets. Besides, starting in the crisis the Keneysian paradigm of returns begins to revert with higher mean returns during low (\textbf{backwardation}) relative to high (\textbf{contango}) \textbf{CHP} phases and this pattern continues, more pronounced, over the post-crisis period. As pointed out in Basu and Bauthéac (2021), the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.

\bigskip

Financialisation was an issue of such policy importance that it triggered legislative action. The debate was initially framed around adequacy of speculation, the burning issue of the day, and the ensuing academic analysis focused on the more mechanical effects of financialisation. With the benefit of hindsight, it appears this approach was perhaps too narrow, and it now seems necessary to address the phenomenon from a broader perspective. Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggered a process of ``definancialisaion'' in global commodity futures markets. The initial view of financialisation was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity futures prices\footnote{Masters (2008); Masters and White (2008); UNCTAD and Cooperation (2009); De Schutter (2010); Gilbert (2010a); Gilbert (2010b); Herman et al. (2011); Schumann (2011); Singleton (2013).}. However, the fundamental question of the nature of the impact of financialisation across the entire cross-section of commodity futures markets has not yet been completely answered. We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets\footnote{Etula (2013), Acharya et al. (2013), Cheng et al. (2014), Leclercq and Praz (2014), Sockin and Xiong (2015), Goldstein et al. (2014), Ekeland et al. (2016), Goldstein and Yang (2017).} and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in Tang and Xiong (2012) and Basak and Pavlova (2016).

\cleardoublepage

\hypertarget{co-movement-data-methods}{%
\section{Data \& methods}\label{co-movement-data-methods}}

\hypertarget{co-movement-background}{%
\subsection{Background}\label{co-movement-background}}

The period from 1998 to 2008 saw an influx of investment into commodity index linked products most of which made its way into the commodity futures market. Popular commodity indexes whose goal was to track the broad movement of commodity prices became accessible by means of swaps, exchange traded funds and exchange traded notes and attracted at least \$100 billion of net super-hoc investment over the 1998-2008 period. Concerns over the consequences of this financialisation phenomenon eventually led to legislative changes including the approval of Rule 76 FR 4752 issued by the US Commodity Futures Trading Commission (CFTC) on January 26\textsuperscript{th}, 2011. This provision emanates from the Dodd-Frank Wall Street and Consumer Protection Act of 2010 (Title VII, Section 737) that mandates the CFTC to use position limits to restrict the flow of speculative capital into a number of commodity markets. The Rule was approved in a close 3-2 vote and the ensuing rule-making process was extremely contentious with several commissioners (Michael Dunn and Scott D. O'Malia in particular) expressing reservations about the lack of supporting evidence and the Rule also triggering thousands of comment letters as well as a lawsuit against the CFTC spearheaded by two Wall Street trade groups, the International Swaps \& Derivatives Association (ISDA) and the Securities Industries \& Financial Markets Association (SIFMA)\footnote{ISDA \& SIFMA v US CFTC; Complaint, 1:11-cv-02146; December 2\textsuperscript{nd}, 2011.}.\\
A world-wide debate ensued about the role of index funds in commodity markets. The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs (De Schutter, 2010; Gilbert, 2010b; Herman et al., 2011; Schumann, 2011; UNCTAD and Cooperation, 2009). Early US Senate investigations on the matter drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US agricultural and energy markets to the observed surges in both futures and cash prices (Masters, 2008; Masters and White, 2008). This contention has since come to be known as the Masters' hypothesis and was largely endorsed by the final US Senate report on the issue (Senate, 2009). At this stage, the question thrust on the academic sphere was whether ``excessive speculation'' (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices. A number of ensuing academic studies, most of which used commodity specific correlation and causality based analysis have since disproved this contention: Irwin et al. (2009), Sanders et al. (2010), Sanders and Irwin (2011a), Sanders and Irwin (2011b), Irwin (2013), Brunetti and Reiffen (2014), Hamilton and Wu (2015) and Bruno et al. (2017) investigated the issue in the context of the agricultural markets; meanwhile, Büyükşahin and Harris (2011), Tokic (2012), Fattouh et al. (2013), Kilian and Murphy (2014), Knittel and Pindyck (2016) and Manera et al. (2016) examined the energy markets while Bohl and Stephan (2013), Kim (2015) and Boyd et al. (2016) studied both energy and agricultural markets and Irwin and Sanders (2011), Irwin and Sanders (2012) as well as Stoll and Whaley (2011) examined the commodity markets in general. Other studies have underlined various alterations in commodity pricing dynamics over the period. Gilbert and Pfuderer (2014) reject the view that financialisation has not had any effects in the grains markets and demonstrate that trades originated by financial market participants, and specifically index investors, can move prices but tend to be typically volatility-reducing. Juvenal and Petrella (2015) contend that the oil price increase between 2004 and 2008 was mainly driven by the strength of global demand but that the financialisation process of commodity markets also played a role. Likewise, Henderson et al. (2015) show that non-information-based financial investments have important impacts on commodity prices. Cheng and Xiong (2014), on the other hand, show that in the case of index commodities, financialisation has transformed the risk sharing, and information discovery functions of commodity futures markets.

\hypertarget{co-movement-data}{%
\subsection{Data}\label{co-movement-data}}

Commodity index swaps, commodity index funds (CIFs), commodity-based exchange traded funds (ETFs) and notes (ETNs) or commodity linked notes (CLNs) were amongst the main investment vehicles that allowed institutional and retail investors to build up commodity exposure in the early 2000s (Boons et al., 2012; Henderson et al., 2015; Irwin and Sanders, 2011; Schumann, 2011; UNCTAD and Cooperation, 2009). Most of these products were primarily designed to track prominent commodity indexes among which the S\&P-GSCI, the most popular. Most of its constituents at the time of writing form the basis of the broad cross-section of commodities that we consider in this study: corn-\#2 yellow (XCBT), oats (XCBT), soybean meal (XCBT), soybean oil (XCBT), soybeans (XCBT), wheat-SRW (XCBT), cattle-feeder (XCME), cattle-live (XCME), lean hogs (XCME), cocoa (IFUS), coffee-C (IFUS), cotton-\#2 (IFUS), lumber (XCME), orange juice (IFUS), sugar-\#11 (IFUS), natural gas (XNYM), crude oil-WTI (XNYM), gasoline (XNYM), heating oil (XNYM), copper (XCEC), gold (XCEC), palladium (XNYM), platinum (XNYM) and silver (XCEC). Unleaded gasoline, the NYMEX legacy contract for gasoline, stopped trading in 2006 when it was replaced by Reformulated Gasoline Blendstock for Oxygen Blending (RBOB) with the two futures series trading alongside for most of the year. For our NYMEX gasoline data series, we consider unleaded gasoline up to September 1\textsuperscript{st}, 2006 and RBOB gasoline thereafter, date at which liquidity for the latter overtook that for the former. We also consider the UK metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).\\
The commodity futures trading commission (CFTC) operates a comprehensive system of collecting information on market participants known as the large trader reporting program (LTRP) where it records and reports to the public position data on market participants who have position levels in excess of a particular market specific threshold\footnote{Current reporting level thresholds available at: \href{https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=\&SID=970471b8455f4bab7db4110cfde50731\&mc=true\&r=SECTION\&n=se17.1.15_103}{www.ecfr.gov}.}. The commission collects market data and position information daily from clearing members, futures commission merchants (FCMs) and foreign brokers and publishes corresponding summaries weekly in a series of market specific reports. In these reports, individual traders are categorised according to the nature of their trading activity on the basis of self-reported information\footnote{CFTC form 40. Available at: \href{https://www.cftc.gov/sites/default/files/idc/groups/public/@forms/documents/file/cftcform40.pdf}{www.cftc.gov}.} that is subject to review by CFTC staff for reasonableness. Position information is then aggregated by category and asset type with each report providing an aggregation for a set of report specific categories and, for each category, a breakdown between futures only positions and positions in futures and options combined.\\
In its legacy report, the commitment of trader report (COT) with data dating back to 1962, the CFTC distinguishes ``commercial'' and ``non-commercial'' market participants where a ``commercial'' participant is defined as one ``{[}\ldots{]} engaged in business activities hedged by the use of futures and option markets''\footnote{See \href{https://www.gpo.gov/fdsys/pkg/CFR-1998-title17-vol1/xml/CFR-1998-title17-vol1-sec1-3.xml}{CFTC regulation 1.3, 17 CFR 1.3(z)} for details.}. A third category, ``non-reportable'', aggregates positions for participants not meeting the reporting threshold. In response to concerns related to category accuracy\footnote{See for example Ederington and Lee (2002).} the CFTC now refines its classification in the disaggregated commitment of trader report (DCOT) where participant categories include ``Producer/Merchant/Processor/User'', ``Swap dealer'', ``Money manager'' and ``Other reportable'' as well as in the supplemental commitment of trader report (SCOT) that details commodity index trader aggregate positions for thirteen agricultural commodity futures markets. Data for DCOT and SCOT date back to 2006 and 2007 respectively.\\
We study the 1997/2018 period where we observe futures only position data from the COT report, the only CFTC report with data available for the whole period of interest; as well as futures term structure price and open interest data from Bloomberg.

\hypertarget{co-movement-methods}{%
\subsection{Methods}\label{co-movement-methods}}

On the one hand, futures markets have a long history of serving commodity producers to alleviate their commodity price and output risks. Keynes (1930) and Hicks (1939) emphasise the ``normal'' behaviour of naturally short hedgers outsourcing their commodity risk to naturally long commodity specialist speculators. This market configuration is referred to as ``backwardation'' where futures are expected to trade at a discount to spot prices, providing speculators with incentives to take the long side. The opposite market paradigm is referred to as ``contango''. Working (Working, 1953, 1948, 1933) and Kaldor (Kaldor, 1939) somehow relax this ``supply-of-speculative-services'' (Till, 2007) approach by introducing processors and merchants, also commodity experts, on the hedgers side and relating the notions of backwardation and contango more directly to the term structure via the theory of storage where the shape of the front end of the term structure (basis) is directly related to the market price of storage.\\
Financialisation, on the other hand, refers to the entry of financial investors into the commodity futures markets who, for the most part, are not commodity experts. Besides, these new market participants tend to exhibit herding like behaviour, often taking massive long-only positions on the whole cross-section of indexed commodities in an attempt to enhance returns while hedging against inflation and reaping further diversification benefits for portfolios with, in most cases, existing large positions across various asset classes (Boyd et al., 2016; Brunetti et al., 2016; Cheng et al., 2014; Juvenal and Petrella, 2015; Singleton, 2013; Tang and Xiong, 2012). This contrasts with the traditional approaches of Keynes and Working and in this context the issues of co-movement and aggregate market participants behaviour seem particularly relevant.\\
Asset pricing techniques are well suited to study co-movement. Building on theory we therefore develop an ad-hoc commodity-based asset pricing framework that we believe is well adapted to study these two issues simultaneously and implement it over four periods of interest. The first, the pre-financialisation period, starts in 1997 and is naturally followed by financialisation, spanning the 2004/2008 period, and the financial crisis and its aftermath, spanning the 2008/2013 period. The last period spans the 2014/2018 period starting with the beginning of the tapering/end of the US Quantitative Easing program (QE).\\
Using the weekly price, open interest and market position data described above we construct market portfolios of individual commodity nearby futures as well as mimicking portfolios for market, commercial hedging pressure, term structure and liquidity risk factors in returns. While our market portfolios are long only, equally weighted portfolios of particular commodity sets, our other mimicking portfolios for risk factors are constructed as combinations of two sub-portfolios (legs), one held long, one held short, which respective constituents are pooled on a weekly basis according to risk factor specific criteria. For each leg, the position weight for a particular asset for a particular week is contingent on the value of the corresponding sorting variable and its rank relative to the other assets in the pool. The sorting variable values for the asset pool are first rescaled so that the highest (lowest) value becomes 1 (0). Weights are then determined pairwise, starting from the extremes with the highest and lowest figures. A coefficient \(\alpha\) is determined by dividing their difference (1 in this case) by the mean of the rescaled values. The high figure is attributed a score of \(\frac{1}{n} \times \alpha\) where \(n\) is the number of assets in the pool while the score for the low figure is \(\frac{1/n}{\alpha}\). The operation is repeated for the pair of assets showing the second highest and second lowest values for the sorting variable and so on until all the assets in the pool are attributed a score. The individual asset weights are then determined by dividing each score by the sum of the scores. The weekly return for a particular mimicking portfolio is calculated as the difference between the weighted average return for constituents of the long portfolio and that for the constituents of the short portfolio. i.e, return on the mimicking portfolio for risk factor \(i\) (\(f_{i}\)) for week \(t\):

\[r_{t}^{f_{i}}=\sum_{j=1}^{x}w^{long}_{j,t} \times r_{j,t}-\sum_{j=n-x}^{n}w^{short}_{j,t} \times r_{j,t}\]
\(n\equiv\) number of commodities in the set considered for mimicking portfolio construction.\\
\(x = n \cdot s\).\\
\(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
\(w^{*}_{j,t}\equiv\) week \(t\) weight for commodity \(j\) on the long or short leg.\\
\(r_{j,t}\equiv\) week \(t\) front contract return for commodity \(j\).\\
\(j\equiv\) commodity rank in the ordered set \(Y_{t}^{f_{i}}\).\\
\(Y_{t}^{f_{i}}\equiv\) week \(t\) ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is specific to \(f_{i}\).

\bigskip

For our portfolio CHP (commercial hedging pressure), we sort the set of commodities considered on past twenty-six-week average CHP from lowest to highest. The bottom third constituents (lowest \(\overline{CHP}\)s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg:

\[Y_{t}^{CHP}\equiv\left \{ \left \{ \overline{CHP_{1}}, \overline{CHP_{2}}, ..., \overline{CHP_{n}} \right \}, \leq \right \}\]

\(\overline{CHP_{j}}=\frac{1}{26}\sum_{k=0}^{25}\frac{L_{j,t-k}}{L_{j,t-k}+S_{j,t-k}}\)\\
\(L_{j,t}\equiv\) number of long positions held by commercial hedgers for week \(t\) on the futures series of commodity \(j\).\\
\(S_{j,t}\equiv\) number of short positions held by commercial hedgers for week \(t\) on the futures series of commodity \(j\).

\bigskip

For our portfolio TS (term structure), we sort the set of commodities considered on past twenty-six-week average roll-yield from highest to lowest. The bottom third constituents (highest \(\overline{RY}\)s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg:

\[Y_{t}^{TS}\equiv\left \{ \left \{ \overline{RY_{1}}, \overline{RY_{2}}, ..., \overline{RY_{n}} \right \}, \geq \right \}\]

\(\overline{RY_{j}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{F_{j,t-k}^{1}}{F_{j,t-k}^{2}} - 1)\)\\
\(F_{j,t}^{1}\equiv\) week \(t\) close price for commodity \(j\) first nearby futures contract.\\
\(F_{j,t}^{2}\equiv\) week \(t\) close price for commodity \(j\) second nearby futures contract.

\bigskip

For our portfolio OI (open interest), we sort the set of commodities considered on past twenty-six-week average front contract open interest growth from highest to lowest. The bottom third constituents (highest \(\overline{OI^{\Delta \%}}\)s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg.

\[Y_{t}^{OI}\equiv\left \{ \left \{ \overline{{OI}_{1}^{\Delta \%}}, \overline{{OI}_{2}^{\Delta \%}}, ..., \overline{{OI}_{n}^{\Delta \%}} \right \}, \geq \right \}\]

\(\overline{{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{{OI}_{j,t-k}}{{OI}_{j,t-k-1}} - 1)\)\\
\(OI_{j,t}\equiv\) open interest at close of week \(t\) on the front (nearby) contract for commodity \(j\).

\bigskip

We use a time series regression approach where we start with regressions of the US traded individual commodity weekly front contract returns on returns to the mimicking portfolio for a particular risk factor where the portfolio is constructed using the whole cross-section of US traded commodities. The corresponding \(R^{2}\)s are averaged and the process is repeated for each of our four risk factors (market, hedging pressure, term structure and liquidity) and periods (1997/2003, 2004/2008, 2008/2013 and 2014/2018). For the long-short factors the results are reported independently for models where the regressor is the factor itself or one of its legs (long vs.~short). The same operation is repeated for the two (\(p=2\)) and three (\(p=3\)) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectively, as well as for the four (\(p=4\)) factor model case where all the risk factor mimicking portfolios are included. Results are reported for the one-factor model case with the other results available on the \href{http://18.135.131.217:3838/financialization-asset-pricing/}{online results dashboard}.\\
For each period we also implement the analysis described above over periods of low and high aggregate CHP (\textbf{CHP}), a notion that we believe is particularly relevant in the context of financialisation where issues of co-movement and aggregate market behaviour play a central role. We define \textbf{CHP} as the cross-sectional average of CHPs for a particular pool of assets. i.e., Week \(t\) \textbf{CHP} for asset pool \(x\):

\[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}\]
\(n\equiv\) number of commodities in set \(x\).\\
\(CHP_{i,t}\equiv\) week \(t\) CHP for commodity \(i\) as defined above.

\bigskip

We further define aggregate backwardation (\textbf{backwardation}) and contango (\textbf{contango}) \textbf{CHP} regimes as, for a given period, \textbf{CHP} levels below and above the period's median respectively and, in contrast with (Hong and Yogo, 2012) who aggregate across sub-sectors, the asset pool we consider for \textbf{CHP} construction include the whole cross-section of US traded commodities.\\
In the next part of the analysis, our mimicking portfolios for risk factors, constructed from the set of all US traded commodities are used as commodity picking devices on the latter commodity set. For each risk factor and period, individual US traded commodity front returns are regressed on returns for the corresponding mimicking portfolio. Individual commodities are sorted by \(R^{2}\) accordingly from highest to lowest and the top third (highest \(R^{2}\)s) are selected as commodity picks for the risk factor for the period. i.e, set of picks \(P_{t}^{f_{i}}\) for risk factor \(i\) (\(f_{i}\)) over period \(t\):

\[P_{t}^{f_{i}}\equiv\left \{ P_{1}, P_{2}, ..., P_{x} \right \}\]
\(x = n \cdot s\).\\
\(n\equiv\) number of commodities in the set considered for the picking exercise (twenty-four here).\\
\(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
\(P_{j}\equiv\) commodity pick \(j\) for risk factor \(f_{i}\) over period \(t\)\\
\(j\equiv\) rank in the ordered set \(Y_{t}^{f_{i}}\)\\
\[Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}\]
\(n\equiv\) number of commodities in the set considered for picking (twenty-four here).\\
\(\tilde{R_{j}^{2}}\equiv\) risk factor \(f_{i}\) returns' explanatory power on commodity \(j\) nearby futures returns over period \(t\) as defined above.

\bigskip

For each period we report the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every set of picks.\\
In the last part of the analysis, for each period our mimicking portfolios for risk factors in returns are constructed using each set of commodity picks independently as the asset pool for portfolio construction. A similar time series approach to that described above is then implemented using these newly formed mimicking portfolios. In this case, a first set of dependent variables includes the sets of commodity picks themselves, a second set includes the whole cross-section of US traded commodities while a third set includes the six UK traded metals considered in the study.

\cleardoublepage

\hypertarget{co-movement-results}{%
\section{Results \& discussion}\label{co-movement-results}}

The descriptive statistics over the various time periods for our two sets of commodities (US and non-US) are shown in table \ref{tab:co-movement-stats-no-regimes}. The traditional Keynesian hedging pressure paradigm postulates a negative relationship between the return on an individual commodity futures and its hedging pressure. Financialisation has been seen as a cross-sectional commodity market phenomenon; this naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure. The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where \textbf{CHP} is low and vice et versa.

In table \ref{tab:co-movement-stats-regimes} the mean returns are shown over high (\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP} regimes for each time period. Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of \textbf{backwardation} as compared to \textbf{contango}, with the difference being statistically significant at the 10\% level for two commodities, at the 5\% level for one and at the 1\% level for another. For the remaining six commodities the higher mean return during \textbf{contango} is not statistically significant for any of them. For the six UK commodities, all metals, five of them had higher mean returns during phases of \textbf{backwardation} as compared to \textbf{contango} in the first period, with one of these differences being statistically significant at the 10\% level while for the remaining asset (Zinc) the higher mean return during \textbf{contango} is not statistically significant. An equally weighted portfolio of the twenty-four US commodities had a mean return of 15.4\% during \textbf{backwardation} phases, statistically significant at the 1\% level, and a mean return of -1.1\% during \textbf{contango}, both in the first period, with the difference between them statistically significant at the 5\% level. The corresponding figures for an equally weighted portfolio of the UK metals were 4.4\% and 0.3\% respectively. These results provide broad support for an aggregate version of the Keynesian hedging pressure hypothesis and suggest that hedgers in the aggregate were engaged in risk transfer during this period.\\
Over the second period the pattern essentially reverses. For the twenty-four US commodities over this period, fourteen have higher mean returns during phases of \textbf{contango} over \textbf{backwardation}. Four of the six UK metals achieved higher mean returns over \textbf{contango} relative to \textbf{backwardation} phases with the difference being statistically significant for one commodity. The equally weighted US portfolio had a mean return of 15.7\% over \textbf{backwardation} against 16.2\% during phases of \textbf{contango}, both statistically significant at the 10\% level. The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 8\% during \textbf{backwardation} rising to 35.6\% during \textbf{contango}.\\
The onset of financialisation thus seems to have engendered a change in the nature of hedger's behaviour in the aggregate, taking it away from the traditional Keynesian view of risk shifting. This phenomenon has been noted in earlier theoretical and empirical work (Danthine, 1978; Stout, 1998) in different contexts from which two competing models of behaviour have emerged. The information arbitrage model (Danthine, 1978; Grossman and Stiglitz, 1980; Kyle, 1989) implies that hedgers may often be seeking out counterparties to trade with rather than being purely passive. This issue is also raised in both Cheng and Xiong (2014) and Stulz (1996) who point out that hedgers may be taking a view on prices just as speculators do. In fact, by hedging away some of their risk, hedgers are able to speculate more heavily based on their disagreement against speculators regarding futures price movement (Simsek, 2013), which fits into a heterogeneous expectation theory of speculation\footnote{Hirshleifer (1975); Hirshleifer (1976); Hirshleifer (1977)}. As Stout (1998) points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves speculation as this form of trading is regarded as non-productive\footnote{Duffie (2014) also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.}. In the second model hedgers are seen as liquidity providers as in Kang et al. (2020) with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions. Table \ref{tab:co-movement-time-reg-US-CHP-US} supports this view. We regress commodity futures front returns on individual commercial hedging pressure (CHP) as well as aggregate CHP (\textbf{CHP}), our market wide measure of CHP, in separate models and find that the explanatory power of CHP at the individual commodity level decreases over the financialisation period with the US cross-sectional average \(R^{2}\) falling down to 20.8\% from 25.8\% in the previous period while that of \textbf{CHP} increases (7.1\% vs 5.4\%). Financialisation therefore seems to have had the effect of loosening the extent to which futures risk premiums relate to commodity specific commercial hedging motives while strengthening that to which they relate to broader dynamics such as cross-sectional liquidity provision. The pattern is strongest for the metals sector where the average \(R^{2}\) drops down to 19.1\% from 28.1\% between the two periods at the individual level while it rises from 8.4\% to 15.7\% at the aggregate level. The symmetry breaks in the crisis period, with the US cross-sectional average \(R^{2}\) at the individual level bouncing back up (22.5\% vs 20.8\%) while that at the aggregate level rises further (14.7\% vs 7.1\%), before eventually resuming post-crisis with a further rise at the individual level (27.2\% vs 22.5\%) and a drop at the aggregate level (7.5\% vs 14.7\%) suggesting a return to legacy commodity specific dynamics.

The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \ref{tab:co-movement-time-reg-US-facts-US}. Over the first period the market factor has the best average time series performance with the highest average \(R^{2}\) with all three futures market factors performing poorly and the overall performance consistent across periods of high and low \textbf{CHP} (below period median). The two factor models average \(R^{2}\)s (results available on the \href{http://18.135.131.217:3838/financialization-asset-pricing/}{online results dashboard}) are roughly the sum of the one factor \(R^{2}\)s indicating that the factors are almost orthogonal over this period. The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average \(R^{2}\) increasing to 8.2\% in the second period relative to 1.7\% in the first with this improvement coming from the long leg that shows a greater improvement (4.5\% to 15.1\%) relative to the short (3\% to 4\%) bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period. The performance of the market factor also improves though not by as much in a relative sense (21.6\% from 11.7\%) and both the term structure factor and the open interest growth factor show a much smaller improvement in performance with smaller differences between legs. Over all periods, all of our factor models show similar performance across regimes of high and low \textbf{CHP}.

We next investigate the top eight of the US traded commodities which achieved the highest time series \(R^{2}\) for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \ref{tab:co-movement-picks}. For the CHP factor the commodities that achieve high \(R^{2}\) in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor. The same applies to the open interest and term structure factors with CHP replaced by open interest growth and roll yield respectively; while for the market factor the picks are those that co-vary most strongly with the market factor over that period. For the CHP factor, we observe a change in the picks between the first and the second period; the picks in the first period included five agricultural commodities and three metals while in the second period they include all the five base and precious metals and only three agricultural commodities. This pattern is also visible for the term structure factor for which there are four metals (copper, silver, gold and platinum) picks in the second period against two in the first (palladium and platinum) as well as for the open interest nearby growth factor for which there are three metals (silver, gold and platinum) picks in the second period against one in the first (platinum). The market factor has three metal picks in the second period (palladium, gold and silver) while all the picks in the first period were agricultural or energy commodities. Over the third period, the average CHP factor shows the same metal picks with the agriculturals replaced by energy commodity; the open interest nearby growth factor still has three metal picks with gold swapped for copper and both the market and term structure factors have one, copper. The table also shows the proportion of time that these picks were constituents of the corresponding factor. All the picks of the long-short factors (average CHP, open interest nearby growth and term structure factors) were constituents of the corresponding factor for some proportion of time in all of the time periods. In this respect, there is a contrast between the first and second periods with the average CHP and open interest nearby growth factor picks appearing predominantly on the long side of the corresponding factor in the second period, as opposed to both legs in the first. The pattern is particularly strong for the metals and energy commodities respectively, with the exception of copper for the average CHP factor that lives in the short leg a higher proportion of the time over the financialisation period. The pattern is reversed for the term structure factor where the picks appear predominantly on the short leg in the second period, as opposed to both legs in the first with the pattern again strongest for the metals. This behaviour continues over the third period for the average CHP and open interest nearby growth factors and indicates that their picks consistently exhibited low commercial hedging pressure and high front contract open interest growth respectively while indicating that the term structure factor picks showed low roll yield in the first and second period.

In table \ref{tab:co-movement-correlations}, we show the average pairwise returns correlation between each set of picks in each time period. This exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement. In the first period the average picks pairwise correlation for the long-short factors ranges from 7.1\% (term structure factor picks) to 12.4\% (open interest factor picks) while the market factor picks show the highest figure (23.7\%). In the second period the figures for the long-short factors rise sharply; up to 22.9\% from 8.1\% for the average CHP factor picks, up to 32.4\% from 12.4\% for the open interest factor picks and up to 23.4\% from 7.1\% for the term structure factor picks. This increase is stronger than that for the market factor picks in a relative sense and is a consequence of the dramatic increase in average pairwise price correlation amongst the US traded metals which dominate the average CHP factor set of picks and which presence is stronger amongst both the open interest and term structure factor sets of picks over the financialisation period. The higher figures for the open interest factor are driven by the strong presence of the energy complex amongst the corresponding picks. The latter exhibits much higher average pairwise correlations than the other sectors in both periods although lower in the second relative to the first which reinforces to role played by the metals in the sharp increase in average pairwise correlation amongst picks for this factor. With regards to \textbf{CHP} regimes, although not very pronounced, a pattern is noticeable. For the market, open interest and term structure factor picks, average pairwise correlations are stronger over phases of \textbf{contango} in the first period and over phases of \textbf{backwardation} in the financialisation period, eventually reverting back to being stronger over \textbf{contango} phases in the crisis period with the CHP factor sets of picks showing the opposite pattern. Overall, these results suggest an increase in correlation between non-price attributes co-movement and price co-movement over the financialisation period. It is also interesting to note that US traded metals returns were negatively correlated with the rest of US traded commodities in the first period and positively in the second.

To further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their explanatory performance on these sets of picks over the four periods independently. The results are shown in table \ref{tab:co-movement-time-reg-picks-facts-picks}. The long-short factors for a particular attribute select the top and bottom two of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks. In the absence of price co-movement between the picks, this market factor will achieve an average \(R^{2}\) of around 12.5\%\footnote{Market factor lemma: \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\) size of market portfolio (eight here).}, while there is no non-zero \(R^{2}\) lower bound for the corresponding long-short factors. A high average \(R^{2}\) for the market factor is indicative of strong price co-movement. In this respect, the most remarkable change in performance in a relative sense is that of the market factor built from the CHP factor sets of picks with the average \(R^{2}\) more than doubling, from 18.6\% up to 38.1\%. For the long-short factors on the other hand it is indicative of simultaneous attribute and price co-movement. For the factors built from the market factor picks the increase is strongest in a relative sense for the CHP factor with the \(R^{2}\) more than doubling, going from 5.6\% in the first period up to 12.4\% in the second with the increase stronger for the long leg (17.1\% vs.~27.9\%) relative to the short (16.5\% vs.~21.4\%). In the case of the factors built from the CHP factor picks, the CHP factor built with its own picks shows a remarkable increase in a relative sense with the \(R^{2}\) tripling, from 7.2\% to 21.4\% and the long leg showing a much greater increase relative to the short (10.4\% to 31.1\% vs.~8.3\% to 9.8\%). The performance of the term structure factor built from the CHP factor sets of picks also shows a sizable increase in a relative sense, from 3.5\% to 5.3\% and even more remarkable in this case is the substantial increase in performance of the short leg, from 6.3\% to 15.7\% relative to the long (7.5\% to 9.8\%). The pattern is reversed for the CHP factor built from the term structure factor picks where the average \(R^{2}\) increases from 4.7\% to 8\% with the performance of the long leg increasing from 11.9\% to 28.1\% vs.~5.5\% to 9.1\% for the short. The performance of the term structure factor constructed from its own sets of picks also shows a substantial increase, from 5.1\% to 8.4\% with, here again the increase in performance relatively stronger for the short leg, from 6\% to 16.1\% vs.~7.6\% to 12.1\% for the long. Taken together with the previous results showing that the metal complex predominantly loads on the long and short legs of the original CHP and term structure factors respectively, these results provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation.

In table \ref{tab:co-movement-time-reg-US-facts-picks} we assess the performance of the same factors on all the commodities instead of just the picks. While the average \(R^{2}\)s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table \ref{tab:co-movement-time-reg-picks-facts-picks}. In contrast, the average CHP factor built with average CHP factor picks shows a smaller absolute increase in average \(R^{2}\) indicating that the link between CHP co-movement and price co-movement is stronger amongst the picks which are predominantly metals. Taken together, the results in tables \ref{tab:co-movement-time-reg-picks-facts-picks} and \ref{tab:co-movement-time-reg-US-facts-picks} suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.\\
To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in Table \ref{tab:co-movement-time-reg-UK-facts-picks}. In the first period, although all sets of picks, except that of the market factor, included at least one metal, the average \(R^{2}\)s are very low; close to zero in most cases. These figures drastically increase across the board in the financialisation period and show a pattern similar to that observed in the US complex. The market factor built from the CHP and term structure factor sets of picks shows the sharpest increase in performance, relative to using the other sets of factor picks; rising to 20.1\% from 1.5\% and to 15\% from 0.8\% respectively. The increase in \(R^{2}\) for the market factor built with market factor picks is more modest, providing further evidence of concentration of co-movement in the metals sector during financialisation. Here again the change in performance for the CHP and term structure factor legs stands out where the factors are built with their own as well as each other's sets of picks. The average \(R^{2}\) for the long leg of the CHP factor built with its own sets of picks increases from 1\% to 11\% while the short leg shows no significant change. The opposite holds for the term structure factor built from its own set of picks with the short leg performance increasing from 0.1\% to 14\% while that of the long leg remains below 1\%. Building these factors from each other's sets of picks produces a similar pattern with the performance of the long leg of the CHP factor built from the term structure factor picks increasing from 0.7\% to 11.4\%; a much greater increase relative to the short leg although in this case the latter also shows a sizable increase in performance (0.3\% to 6\%). The performance of the short leg of the term structure factor built from the CHP factor sets of picks on the other hand increases from 0.3\% to 19.2\% while the performance for the long leg in the second period remains below 1.5\%. Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working's term structure paradigms. There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of Kang et al. (2020) who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).

The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results. Returns fall sharply relative to the financialisation period (table \ref{tab:co-movement-stats-no-regimes}. with eighteen US commodities along with all six UK traded metals showing lower mean returns. Returns for equally weighted portfolios of both sets of assets fall down to 9.4\% and 5.3\% from 15.9\% and 21.8\% respectively. Returns are mostly higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:co-movement-stats-regimes}) with fifteen US assets and five of the UK traded metals showing higher mean returns in \textbf{backwardation} and the pattern extending to equally weighted portfolios of the two sets of assets. Volatility is moderately higher for both sets with fifteen US commodities and three UK metals showing higher figures and interestingly eminently higher over phases of \textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none of the UK traded metals show higher volatility figures over \textbf{backwardation} phases. The performance of the market factor dominates the US commodity complex over the period with a 50\% increase in mean average \(R^{2}\) to over 30\% (table \ref{tab:co-movement-time-reg-US-facts-US}) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors. The average pairwise correlation amongst the market factor picks increases beyond 50\% while there is a leveling in that amongst the picks of the long-short factors as shown in table \ref{tab:co-movement-correlations}. Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table \ref{tab:co-movement-time-reg-US-facts-picks}). Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities. Table \ref{tab:co-movement-time-reg-UK-facts-picks} provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average \(R^{2}\) increasing to 31.7\% from 10.2\% in the previous period.\\
The returns pullback continues into the post-crisis period with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2\% and 2.7\% respectively. Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period. The figures for the equally weighted portfolios of US and UK assets drop to 9.9\% and 16.2\% respectively, very close to pre-financialisation levels. The pattern of reversion toward the pre-financialisation Keynesian paradigm intiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:co-movement-stats-regimes}), more so than over the crisis period with seventeen US commodities showing higher mean returns over \textbf{backwardation} phases. The difference is significant at the 5\% level for Lumber (XCME) and at the 10\% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of \textbf{contango}. The pattern is more pronounced for the UK traded subset with all six assets showing higher mean returns in \textbf{backwardation} with the difference significant at the 1\% level for Nickel-primary (XLME), 5\% level for Aluminium (XLME) and 10\% level for Zinc (XLME). It also extends to equally weighted portfolios of US and UK traded assets that both show higher mean returns during \textbf{backwardation} with the difference significant at the 5\% level for the UK portfolio and the figure close to the 10\% level significance threshold for the portfolio of US assets. Volatilities are overall higher in \textbf{contango} although less so than over the previous period with seventeen US commodities showing higher figures over \textbf{contango} against twenty-three in the crisis period. The pattern extends to three of the six UK traded metals with the difference significant at the 1\% level for Copper (XLME) and Tin (XLME) and at the 5\% level for Zinc (XLME) while differences are not significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit higher volatility over \textbf{backwardation} phases. Equally weighted portfolios of US and UK traded assets on the other hand both show higher volatility in \textbf{contango} with the difference significant at the 1\% level for both. Over the financialisation period in contrast volatilities were predominantly higher in \textbf{backwardation} for US traded assets with fourteen commodities showing higher volatility figures in these phases; the post-crisis pattern of results for volatilities thus likewise shows signs of reversion to pre-financialisation standards. Average pairwise correlations amongst factor picks (table \ref{tab:co-movement-correlations}) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1\% to 26.1\%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks. The performance of the market factor on the US complex declines below financialisation levels (table \ref{tab:co-movement-time-reg-US-facts-US}) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table \ref{tab:co-movement-time-reg-US-facts-picks}) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors. Table \ref{tab:co-movement-time-reg-UK-facts-picks} provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
Taken together the patterns of results over the crisis and post-crisis periods echo those in Basu and Bauthéac (2021) in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex, in other words, a process of ``definancialisation''.

\cleardoublepage

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

In the early 2000s, against a backdrop of a low yield environment and poor stock market performance, a combination of financial innovations\footnote{Commodity price indexes and the ad-hoc financial instruments enabling investment in them were the main financial innovations which allowed large global banks to offer commodity investment products to institutional and retail investors. In 1991 Goldman Sachs created the S\&P-GSCI which provides investors with buy-side exposure to commodities via the OTC swap market and thus without having to participate in the formal futures markets with their position limit restrictions. At this stage, these restrictions still applied to the issuing institutions though, as they hedged the corresponding commodity swap exposure in the futures markets. The first commodity-based ETFs were created through buying physical precious metals with gold and silver ETFs offered as early as 2002/2003. The regulatory hurdle here related to the licensing of commodity trading professionals. Typically, investors had to sign a statement with their broker stating that they understood the risks of commodity investments; a rather inconvenient paperwork for a product designed to trade like a stock, as set forth by a number of industry players at the time.} and regulatory changes\footnote{In 2000, the Commodity Futures Modernization Act (CFMA) granted non-agricultural commodity futures statutory exemption from regulation (``Enron loophole''). It still required agricultural commodity derivatives be traded on a CFTC-regulated exchange however. Eventually, the CFTC classified swap dealers as ``bona fide'' hedgers, granting them position limits exemption (``swap dealer loophole''). In 2005, the CFTC waived the rule that required commodity investors to sign a statement saying they understood the risks, letting the funds replace it with their prospectus. The regulatory bottleneck that prevented the large-scale expansion of commodity index investment was no more.} led to large inflows of institutional capital into the commodity futures markets. This process known as ``financialisation'' spurred a heated public policy debate about whether the ensuing increase in open interest and trading volume in commodity futures exerted upward pressure on prices. The debate spread to the legislative sphere, with the US senate launching formal investigations, and was thrust onto the academic community as a matter of urgency. Perhaps in response to this, most of the early studies focused on the more mechanical effects of financialisation, relying on commodity specific causality and correlation-based analysis. The contention eventually triggered legislative action and new position limits were introduced in a number of grains and energy futures markets with substantial potential effects on their functioning and consequently, to a larger extent, on that of the economic system as a whole. With the benefit of hindsight, the focus of the debate appears to have been too narrow, and the ensuing regulatory changes might thus have been unwarranted; it therefore seems important to analyse the effects of financialisation from a broader perspective which we do in this study. Factor model techniques are well suited to isolating common driving factors and detecting co-movement, a central issue in financialisation which we believe the existing literature has not fully analysed; we thus consider the entire cross-section of actively traded commodities on futures markets and use a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations. Our analysis suggests that, beyond energy and agriculturals, financialisation appears to have had a substantial impact on the metals sector at the global level. The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in commodity pricing dynamics. In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have set off a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of ``definancialisation'' in global commodity futures markets.

\cleardoublepage\newgeometry{left=2.50cm, right=2.50cm, top=2.50cm, bottom=3cm}

\hypertarget{tables}{%
\section*{Tables}\label{tables}}
\addcontentsline{toc}{section}{Tables}

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{>{}llrrrr}
\caption{\label{tab:co-movement-stats-no-regimes}This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1\%, 5\% and 10\% level are marked with ***, ** and * respectively. The results are discussed in section \ref{co-movement-results}.}\\
\toprule
asset & estimate & past & financialisation & crisis & post-crisis\\
\midrule
\endfirsthead
\caption[]{\textit{(continued)}}\\
\toprule
asset & estimate & past & financialisation & crisis & post-crisis\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{individual commodities}}\\
\hspace{1em} & mean & 3.48\% & 21.37\% & 6.89\% & -4.51\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Corn-\#2 yellow (XCBT)}} & sd & 23\% & 29.54\% & 36.15\% & 21.8\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 5.49\% & 21.62\% & 8.89\% & -0.87\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Oats (XCBT)}} & sd & 32.22\% & 31.04\% & 34.67\% & 29.5\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 7.29\% & 12.06\% & 8.12\% & -0.33\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Soybean meal (XCBT)}} & sd & 26.34\% & 32.55\% & 31.78\% & 25.11\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 6.21\% & 15.57\% & 4.04\% & -7.39\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Soybean oil (XCBT)}} & sd & 21.43\% & 28.35\% & 25.75\% & 18.95\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 6.89\% & 13.36\% & 6.19\% & -3.82\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Soybeans (XCBT)}} & sd & 21.47\% & 30.04\% & 28\% & 21.22\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 5.07\% & 17.63\% & 6.68\% & -1.58\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Wheat-SRW (XCBT)}} & sd & 24.93\% & 33.03\% & 37.62\% & 26.58\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 0.39\% & 7.43\% & 7.13\% & 1.87\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cattle-feeder (XCME)}} & sd & 13.23\% & 15.16\% & 15.24\% & 18.69\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 3.45\% & 8.77\% & 4.13\% & 1.92\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cattle-live (XCME)}} & sd & 17.1\% & 17.43\% & 16.32\% & 18.3\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 0.73\% & 8.4\% & 12.69\% & -1.09\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Lean hogs (XCME)}} & sd & 38.33\% & 31.89\% & 30.37\% & 36.94\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 3.66\% & 16.35\% & 1.39\% & 3.65\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cocoa (IFUS)}} & sd & 32.66\% & 29.99\% & 31.03\% & 24.69\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & -5.91\% & 20.38\% & 2.2\% & 1.99\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Coffee-C (IFUS)}} & sd & 43.84\% & 32.3\% & 30.17\% & 31.86\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 3.24\% & 0.95\% & 12.53\% & 0.5\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cotton-\#2 (IFUS)}} & sd & 26.38\% & 29.01\% & 33.26\% & 20.61\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 1.9\% & -3.58\% & 11.74\% & 5.06\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Lumber (XCME)}} & sd & 30.58\% & 29.39\% & 36.31\% & 25.1\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 1.67\% & 13.87\% & 14.4\% & 3.8\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Orange juice (IFUS)}} & sd & 29.5\% & 33.01\% & 34.43\% & 29.37\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & -4.56\% & 24.87\% & 11.82\% & -1.16\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Sugar-\#11 (IFUS)}} & sd & 34.88\% & 33.25\% & 37.9\% & 28.72\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 35.38\% & 16.25\% & 0.93\% & 8.33\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Natural gas (XNYM)}} & sd & 61.55\% & 54.6\% & 53.58\% & 44.58\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 15.43\% & *28.74\% & 9.67\% & -5.64\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Crude oil-WTI (XNYM)}} & sd & 39.87\% & 32.56\% & 42.84\% & 34.69\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 16.65\% & 30.95\% & 10.59\% & -5.37\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Gasoline (XNYM)}} & sd & 42.77\% & 41.76\% & 40.07\% & 37.09\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 16.31\% & *29.88\% & 6.83\% & -3.44\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Heating oil (XNYM)}} & sd & 40.75\% & 35.09\% & 33.17\% & 30.56\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 1.45\% & *28.15\% & 6.19\% & -0.1\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Copper (XCEC)}} & sd & 21.23\% & 31.89\% & 34.91\% & 19.56\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 4.5\% & 14.35\% & 14.01\% & 0.53\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Gold (XCEC)}} & sd & 15.14\% & 18.89\% & 21.46\% & 14.41\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 9.12\% & 9.03\% & *29.12\% & 13.75\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Palladium (XNYM)}} & sd & 38.27\% & 32.71\% & 36.14\% & 25.38\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 12.93\% & 10.56\% & 7.29\% & -7.92\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Platinum (XNYM)}} & sd & 22.62\% & 22.66\% & 25.53\% & 19.48\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 6.19\% & 17.54\% & 21.96\% & -2.43\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Silver (XCEC)}} & sd & 22\% & 33.92\% & 39.87\% & 24.35\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 1.13\% & 13.78\% & -3.58\% & 3.15\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Aluminium (XLME)}} & sd & 17.6\% & 26.41\% & 26.48\% & 18.56\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 0.45\% & **28.59\% & 5.74\% & 0.03\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Copper (XLME)}} & sd & 19.25\% & 31.09\% & 34.27\% & 18.92\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 3.83\% & 28.99\% & 10.74\% & 2.07\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Lead (XLME)}} & sd & 19.64\% & 41.74\% & 41.05\% & 23.26\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 19.31\% & 12.5\% & 3.52\% & 0.31\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Nickel-primary (XLME)}} & sd & 32.26\% & 44.27\% & 41.45\% & 28.98\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 4.07\% & *29.1\% & 7.46\% & 1.68\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Tin-refined (XLME)}} & sd & 15.38\% & 31.71\% & 35.61\% & 18.79\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & -4.52\% & 20.13\% & 7.62\% & 9.07\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Zinc (XLME)}} & sd & 21.73\% & 38.77\% & 36.17\% & 23.25\%\\
\cmidrule{1-6}\pagebreak[0]
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{equally weighted portfolios}}\\
\hspace{1em} & mean & *6.89\% & **15.89\% & 9.39\% & -0.18\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{US commodities}} & sd & 10\% & 13.62\% & 17.58\% & 9.86\%\\
\cmidrule{1-6}\pagebreak[0]
\hspace{1em} & mean & 2.47\% & *21.77\% & 5.25\% & 2.72\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{GB commodities}} & sd & 15.66\% & 26.91\% & 30.24\% & 16.19\%\\*
\end{longtable}
\endgroup{}

\newpage

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{>{}lllrrrr}
\caption{\label{tab:co-movement-stats-regimes}This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median). Mean values significant at the 1\%, 5\% and 10\% level are marked with ***, ** and * respectively. Aggregate CHP construction and corresponding regime definitions are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
\toprule
asset & regime & estimate & past & financialisation & crisis & post-crisis\\
\midrule
\endfirsthead
\caption[]{\textit{(continued)}}\\
\toprule
asset & regime & estimate & past & financialisation & crisis & post-crisis\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{individual commodities}}\\
\hspace{1em} &  & mean & -4.86\% & 19.26\% & 20.48\% & -8.74\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 23.07\% & 29.14\% & 31.59\% & 21\%\\
\nopagebreak
\hspace{1em} &  & mean & 11.3\% & 23.54\% & -4.43\% & 0.78\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Corn-\#2 yellow (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 23\% & 30.01\% & 40.14\% & 22.68\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & -5.39\% & 7.82\% & 7.85\% & 2.56\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 29.02\% & 33.82\% & 31.43\% & 31.55\%\\
\nopagebreak
\hspace{1em} &  & mean & 16.95\% & *35.38\% & 11.68\% & -3.17\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Oats (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 35.22\% & 28.1\% & 37.7\% & 27.5\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 13.15\% & 8.22\% & 16.04\% & -3.52\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 27.77\% & 33.06\% & 25.7\% & 25.1\%\\
\nopagebreak
\hspace{1em} &  & mean & 1.52\% & 15.91\% & 2.32\% & 2.22\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Soybean meal (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 24.94\% & 32.13\% & 36.85\% & 25.32\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 14.79\% & 14.62\% & 20.34\% & -9.44\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.35\% & 28.94\% & 22.33\% & 18.19\%\\
\nopagebreak
\hspace{1em} &  & mean & -2.68\% & 16.62\% & -10.01\% & -4.12\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Soybean oil (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 21.55\% & 27.91\% & 28.65\% & 19.79\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 13.69\% & 0.93\% & 13.42\% & -11.45\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.93\% & 34.58\% & 24.39\% & 22.04\%\\
\nopagebreak
\hspace{1em} &  & mean & -0.16\% & 25.71\% & 0.96\% & 3.75\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Soybeans (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 21.09\% & 24.74\% & 31.11\% & 20.56\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & -2.7\% & 19.02\% & 0.98\% & 0.44\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 25.79\% & 36\% & 37.53\% & 26.57\%\\
\nopagebreak
\hspace{1em} &  & mean & 11.78\% & 16.29\% & 14.57\% & -2.77\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Wheat-SRW (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 24.04\% & 29.84\% & 37.73\% & 26.72\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 2.31\% & **20.52\% & 7.51\% & 6.58\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 12.79\% & 14.93\% & 13.39\% & 20.14\%\\
\nopagebreak
\hspace{1em} &  & mean & -0.81\% & -5.49\% & 7.28\% & -3.12\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cattle-feeder (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 13.67\% & 15.35\% & 16.91\% & 17.23\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 8.39\% & 14.2\% & 5.87\% & -2.07\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 16.65\% & 17.91\% & 14.97\% & 19.9\%\\
\nopagebreak
\hspace{1em} &  & mean & -0.34\% & 3.43\% & 2.7\% & 5.82\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cattle-live (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 17.49\% & 16.99\% & 17.57\% & 16.66\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 12.34\% & 16.3\% & 18.23\% & 19.24\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 37.6\% & 35.73\% & 27.83\% & 35.61\%\\
\nopagebreak
\hspace{1em} &  & mean & -10.5\% & 0.6\% & 7.5\% & -20.66\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Lean hogs (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 39.22\% & 27.67\% & 32.78\% & 38.28\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 4.12\% & 9.25\% & -9.56\% & -2.98\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 33.57\% & 31.05\% & 26.93\% & 25.86\%\\
\nopagebreak
\hspace{1em} &  & mean & 3.67\% & 23.43\% & 12.92\% & 10.29\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cocoa (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 31.81\% & 28.91\% & 34.66\% & 23.57\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 4.51\% & 26.49\% & 2.66\% & 14.36\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 48.82\% & 32.6\% & 29.92\% & 31.52\%\\
\nopagebreak
\hspace{1em} &  & mean & -16.87\% & 14.38\% & 3.4\% & -10.24\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Coffee-C (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 38.35\% & 32.06\% & 30.22\% & 32.24\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 22.64\% & 7.85\% & 35.53\% & 10.84\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 26.02\% & 29.71\% & 33.94\% & 21.33\%\\
\nopagebreak
\hspace{1em} &  & mean & -16.46\% & -5.92\% & -9.36\% & -8.91\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cotton-\#2 (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 26.77\% & 28.35\% & 32.59\% & 19.95\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & -8.48\% & -2.37\% & 29.11\% & **26.99\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 30.43\% & 30.72\% & 35.45\% & 21.26\%\\
\nopagebreak
\hspace{1em} &  & mean & 11.68\% & -4.77\% & -5.04\% & -17.14\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Lumber (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 30.56\% & 28.2\% & 37.23\% & 28.45\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & -2.38\% & -2.22\% & 18.24\% & 18.64\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 28.01\% & 33.01\% & 30.09\% & 28.64\%\\
\nopagebreak
\hspace{1em} &  & mean & 5.83\% & 29.93\% & 12.29\% & -8.64\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Orange juice (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 31.05\% & 33.1\% & 38.06\% & 30.11\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 11.98\% & 29.51\% & 2.7\% & -8.07\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 33.23\% & 33.6\% & 41.29\% & 27.69\%\\
\nopagebreak
\hspace{1em} &  & mean & -20.49\% & 20.35\% & 21.47\% & 4.7\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Sugar-\#11 (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 36.48\% & 32.98\% & 34.09\% & 29.83\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & **85.84\% & 4.76\% & -2.32\% & 18.33\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 63.46\% & 47.3\% & 48.85\% & 42.59\%\\
\nopagebreak
\hspace{1em} &  & mean & -11.98\% & 27.84\% & 4.77\% & 3.25\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Natural gas (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 59.76\% & 61.3\% & 58.18\% & 46.41\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 29.17\% & *35.61\% & 11.47\% & 14.24\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 36.74\% & 32.09\% & 28.19\% & 26.94\%\\
\nopagebreak
\hspace{1em} &  & mean & 2.21\% & 22.04\% & 9.95\% & -24.85\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Crude oil-WTI (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 42.74\% & 33.1\% & 53.7\% & 41.08\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 39\% & 19.82\% & 23.98\% & 9.69\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 42.47\% & 39.38\% & 31.41\% & 32.1\%\\
\nopagebreak
\hspace{1em} &  & mean & -5.22\% & 42.13\% & -0.09\% & -19.47\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Gasoline (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 43.14\% & 44.13\% & 47.11\% & 41.71\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 36.32\% & 29.41\% & 25.56\% & 15.16\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 41.37\% & 33.33\% & 25.95\% & 24.62\%\\
\nopagebreak
\hspace{1em} &  & mean & -2.74\% & 30.5\% & -10.77\% & -21.62\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Heating oil (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 40.19\% & 36.98\% & 39.16\% & 35.69\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 3.14\% & 22.17\% & 16.53\% & 12.1\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 20.71\% & 30.05\% & 25.73\% & 18.16\%\\
\nopagebreak
\hspace{1em} &  & mean & -0.28\% & 34.17\% & -3.46\% & -12.15\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Copper (XCEC)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 21.78\% & 33.69\% & 42.28\% & 20.87\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 9.19\% & 13.37\% & 9.37\% & 4.21\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 16.89\% & 19.2\% & 17.03\% & 12.36\%\\
\nopagebreak
\hspace{1em} &  & mean & -0.01\% & 15.37\% & 19.1\% & -3.1\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Gold (XCEC)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 13.24\% & 18.58\% & 25.21\% & 16.23\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & **49.79\% & 24.47\% & 30.01\% & **31.93\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 34.98\% & 34.23\% & 33.49\% & 23.82\%\\
\nopagebreak
\hspace{1em} &  & mean & -30.19\% & -6.3\% & 30.58\% & -4.88\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Palladium (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 41.22\% & 31.2\% & 38.71\% & 26.8\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & **29.46\% & *25.07\% & 10.46\% & 1.17\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 22.1\% & 22.51\% & 21.24\% & 18.04\%\\
\nopagebreak
\hspace{1em} &  & mean & -3.22\% & -3.81\% & 8.04\% & -17.28\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Platinum (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 23.12\% & 22.81\% & 28.75\% & 20.8\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 5.98\% & 14.29\% & 19.66\% & 3.44\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.07\% & 32.5\% & 37.17\% & 20.3\%\\
\nopagebreak
\hspace{1em} &  & mean & 6.57\% & 20.83\% & 26.77\% & -8.09\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Silver (XCEC)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 22.93\% & 35.34\% & 42.44\% & 27.77\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 2.56\% & 14.78\% & 16.25\% & **23.68\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 14.82\% & 25.57\% & 24.94\% & 18.94\%\\
\nopagebreak
\hspace{1em} &  & mean & -0.38\% & 12.86\% & -23.04\% & -16.74\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Aluminium (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 20.13\% & 27.29\% & 28.01\% & 18.23\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 1.54\% & 25.22\% & 18.66\% & 11.99\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 17.98\% & 29.01\% & 25.53\% & 17.92\%\\
\nopagebreak
\hspace{1em} &  & mean & -0.95\% & 32\% & -6.78\% & -11.89\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Copper (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 20.41\% & 32.98\% & 41.31\% & 19.86\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 7.59\% & 11.21\% & 9.87\% & 17.05\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 19.16\% & 39.91\% & 35.35\% & 23.37\%\\
\nopagebreak
\hspace{1em} &  & mean & -0.09\% & *46.48\% & 12.65\% & -13.41\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Lead (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 20.12\% & 43.16\% & 46.22\% & 23.09\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 23.25\% & -39.24\% & 16.3\% & **35.09\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 30.23\% & 41.62\% & 34.48\% & 29.13\%\\
\nopagebreak
\hspace{1em} &  & mean & 15.46\% & **63.47\% & -7.67\% & **-34.64\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Nickel-primary (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 34.28\% & 46.72\% & 47.44\% & 28.6\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & *15.83\% & 34.62\% & 23.7\% & 4.48\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 14.99\% & 31.4\% & 29.09\% & 15.27\%\\
\nopagebreak
\hspace{1em} &  & mean & -7.78\% & 23.88\% & -6.82\% & -1.69\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Tin-refined (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 15.77\% & 32.08\% & 41.13\% & 21.68\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & -9.06\% & 2.95\% & 10.05\% & **29.42\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.15\% & 36.86\% & 33.28\% & 22.12\%\\
\nopagebreak
\hspace{1em} &  & mean & -0.13\% & 37.11\% & 5.43\% & -11.31\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Zinc (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 22.38\% & 40.51\% & 39.03\% & 24.32\%\\
\cmidrule{1-7}\pagebreak[0]
\addlinespace[0.3em]
\multicolumn{7}{l}{\textbf{equally weighted portfolios}}\\
\hspace{1em} &  & mean & ***15.44\% & *15.66\% & 13.4\% & 6.82\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 9.88\% & 14.21\% & 14.83\% & 8.59\%\\
\nopagebreak
\hspace{1em} &  & mean & -1.09\% & *16.16\% & 4.9\% & -6.33\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{US commodities}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 10.09\% & 13.05\% & 19.98\% & 10.95\%\\
\cmidrule{1-7}\pagebreak[0]
\hspace{1em} &  & mean & 4.41\% & 8.01\% & 15.06\% & **19.95\%\\
\nopagebreak
\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 14.39\% & 25.92\% & 25.94\% & 15.13\%\\
\nopagebreak
\hspace{1em} &  & mean & 0.34\% & *35.56\% & -5.24\% & -14.05\%\\
\nopagebreak
\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{GB commodities}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 16.87\% & 27.88\% & 34.06\% & 17.1\%\\*
\end{longtable}
\endgroup{}

\newpage

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{>{}lllrrrr}
\caption{\label{tab:co-movement-time-reg-US-CHP-US}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against relative changes in commercial hedging pressure (CHP) both at the individual (commodity CHP) and aggregate (aggregate CHP) levels independently. The results are reported for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).}\\
\toprule
regressor & sector & subsector & past & financialisation & crisis & post-crisis\\
\midrule
\endfirsthead
\caption[]{\textit{(continued)}}\\
\toprule
regressor & sector & subsector & past & financialisation & crisis & post-crisis\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
 & all & all & 25.79\% & 20.72\% & 22.46\% & 27.17\%\\
\nopagebreak
 &  & all & 25.19\% & 21.6\% & 23.91\% & 28.12\%\\
\nopagebreak
 &  & grains & 33.18\% & 27.86\% & 29.15\% & 36.24\%\\
\nopagebreak
 &  & livestock & 6.23\% & 10.53\% & 6.89\% & 4.34\%\\
\nopagebreak
 & \multirow[t]{-4}{*}{\raggedright\arraybackslash agriculturals} & softs & 26.68\% & 20.89\% & 27.19\% & 31.88\%\\
\nopagebreak
 &  & all & 25.12\% & 19.45\% & 16\% & 10.96\%\\
\nopagebreak
 &  & gas & 19.69\% & 15.65\% & 7.36\% & 5.29\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash energy} & petroleum & 26.93\% & 20.71\% & 18.87\% & 12.85\%\\
\nopagebreak
 &  & all & 28.12\% & 19.1\% & 23.27\% & 37.32\%\\
\nopagebreak
 &  & base & 47.38\% & 25.86\% & 18.07\% & 34.9\%\\
\nopagebreak
\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{Δ\% commodity CHP}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash metals} & precious & 23.3\% & 17.41\% & 24.57\% & 37.93\%\\
\cmidrule{1-7}\pagebreak[0]
 & all & all & 5.37\% & 7.12\% & 14.72\% & 7.49\%\\
\nopagebreak
 &  & all & 4.91\% & 4.5\% & 12.14\% & 6.23\%\\
\nopagebreak
 &  & grains & 7.25\% & 5.4\% & 19.75\% & 8.45\%\\
\nopagebreak
 &  & livestock & 1.35\% & 0.41\% & 0.52\% & 0.26\%\\
\nopagebreak
 & \multirow[t]{-4}{*}{\raggedright\arraybackslash agriculturals} & softs & 4.34\% & 5.64\% & 10.35\% & 6.98\%\\
\nopagebreak
 &  & all & 3.35\% & 6.27\% & 14.83\% & 2.45\%\\
\nopagebreak
 &  & gas & 2.65\% & 2.58\% & 2.6\% & 0.27\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash energy} & petroleum & 3.59\% & 7.49\% & 18.9\% & 3.17\%\\
\nopagebreak
 &  & all & 8.36\% & 15.67\% & 22.37\% & 15.33\%\\
\nopagebreak
 &  & base & 10.12\% & 12.74\% & 23.94\% & 7.67\%\\
\nopagebreak
\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{Δ\% aggregate CHP}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash metals} & precious & 7.92\% & 16.4\% & 21.98\% & 17.25\%\\*
\end{longtable}
\endgroup{}

\newpage

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{>{}lllrrrr}
\caption{\label{tab:co-movement-time-reg-US-facts-US}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities. The asset pool for the factor mimicking portfolio construction includes the twenty four US commodities. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
\toprule
factor & leg & regime & past & financialisation & crisis & post-crisis\\
\midrule
\endfirsthead
\caption[]{\textit{(continued)}}\\
\toprule
factor & leg & regime & past & financialisation & crisis & post-crisis\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
 &  & all & 11.68\% & 21.6\% & 30.72\% & 15.57\%\\
\nopagebreak
 &  & backwardation & 11.28\% & 23.51\% & 28.95\% & 13.12\%\\
\nopagebreak
\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{market}} &  & contango & 12.23\% & 19.96\% & 32.47\% & 17.66\%\\
\nopagebreak
 &  & all & 1.67\% & 8.24\% & 5.67\% & 4.07\%\\
\nopagebreak
 &  & backwardation & 1.84\% & 8.81\% & 5.01\% & 5.74\%\\
\nopagebreak
 & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 2.05\% & 8.25\% & 6.81\% & 3.58\%\\
\nopagebreak
 &  & all & 4.53\% & 15.14\% & 21.88\% & 9.31\%\\
\nopagebreak
 &  & backwardation & 4.77\% & 17.25\% & 21.46\% & 8.07\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.85\% & 13.8\% & 22.56\% & 10.53\%\\
\nopagebreak
 &  & all & 3.02\% & 4\% & 9.1\% & 4.36\%\\
\nopagebreak
 &  & backwardation & 2.51\% & 4.03\% & 7.14\% & 6.24\%\\
\nopagebreak
\multirow[t]{-9}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 4\% & 4.81\% & 12.42\% & 3.88\%\\
\cmidrule{1-7}\pagebreak[0]
 &  & all & 2.91\% & 3.84\% & 6.21\% & 5.12\%\\
\nopagebreak
 &  & backwardation & 3.61\% & 2.93\% & 4.99\% & 5.04\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.5\% & 5.21\% & 7.39\% & 5.41\%\\
\nopagebreak
 &  & all & 5.94\% & 13.15\% & 21.23\% & 8.72\%\\
\nopagebreak
 &  & backwardation & 6.78\% & 14.01\% & 18.83\% & 8.01\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 5.47\% & 12.78\% & 23.07\% & 9.34\%\\
\nopagebreak
 &  & all & 3.55\% & 7.41\% & 12.39\% & 4.25\%\\
\nopagebreak
 &  & backwardation & 3.32\% & 9.77\% & 10.61\% & 3.97\%\\
\nopagebreak
\multirow[t]{-9}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.98\% & 5.16\% & 13.83\% & 4.86\%\\
\cmidrule{1-7}\pagebreak[0]
 &  & all & 1.12\% & 1.46\% & 2.93\% & 0.94\%\\
\nopagebreak
 &  & backwardation & 1.16\% & 2.17\% & 2.53\% & 1.28\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1.55\% & 2.02\% & 3.6\% & 1.22\%\\
\nopagebreak
 &  & all & 4.15\% & 6.36\% & 8.39\% & 5.07\%\\
\nopagebreak
 &  & backwardation & 4.38\% & 8.41\% & 9.91\% & 4.98\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.28\% & 5.73\% & 7.99\% & 5.5\%\\
\nopagebreak
 &  & all & 2.59\% & 8.79\% & 14.46\% & 4\%\\
\nopagebreak
 &  & backwardation & 2.78\% & 10.16\% & 10.18\% & 2.69\%\\
\nopagebreak
\multirow[t]{-9}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.9\% & 7.9\% & 18.16\% & 6.25\%\\*
\end{longtable}
\endgroup{}

\newpage

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{>{}lllrr}
\caption{\label{tab:co-movement-picks}This table shows the factor 'picks' for the market as well as the long-short factors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). For each factor and period the twenty four US commodities are regressed against the corresponding factor mimicking portfolio and ranked by $R^{2}$. The top eight commodities are selected as 'picks' for the corresponding factor and period. The table also shows the proportion of time, for each period, each individual pick lives on both legs (long vs. short) of its picking factor. The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor. Factors construction details are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
\toprule
picking factor & period & pick & long & short\\
\midrule
\endfirsthead
\caption[]{\textit{(continued)}}\\
\toprule
picking factor & period & pick & long & short\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
 &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Soybean meal (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Soybeans (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Wheat-SRW (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Natural gas (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Gasoline (XNYM) & 100\% & 0\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Heating oil (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Soybean oil (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Soybeans (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Heating oil (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Gold (XCEC) & 100\% & 0\%\\
\nopagebreak
 &  & Palladium (XNYM) & 100\% & 0\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 100\% & 0\%\\
\nopagebreak
 &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Soybean oil (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Soybeans (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Wheat-SRW (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Gasoline (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Heating oil (XNYM) & 100\% & 0\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Copper (XCEC) & 100\% & 0\%\\
\nopagebreak
 &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Soybean oil (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Soybeans (XCBT) & 100\% & 0\%\\
\nopagebreak
 &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Gasoline (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Heating oil (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Copper (XCEC) & 100\% & 0\%\\
\nopagebreak
\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Silver (XCEC) & 100\% & 0\%\\
\cmidrule{1-5}\pagebreak[0]
 &  & Cattle-feeder (XCME) & 12.28\% & 67.96\%\\
\nopagebreak
 &  & Cattle-live (XCME) & 16.47\% & 50.3\%\\
\nopagebreak
 &  & Lean hogs (XCME) & 13.77\% & 58.98\%\\
\nopagebreak
 &  & Cotton-\#2 (IFUS) & 18.56\% & 46.11\%\\
\nopagebreak
 &  & Orange juice (IFUS) & 55.39\% & 18.56\%\\
\nopagebreak
 &  & Gold (XCEC) & 36.83\% & 61.68\%\\
\nopagebreak
 &  & Platinum (XNYM) & 91.92\% & 2.1\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Silver (XCEC) & 100\% & 0\%\\
\nopagebreak
 &  & Oats (XCBT) & 97.91\% & 0\%\\
\nopagebreak
 &  & Cattle-feeder (XCME) & 0\% & 97.49\%\\
\nopagebreak
 &  & Lean hogs (XCME) & 0\% & 72.38\%\\
\nopagebreak
 &  & Copper (XCEC) & 28.45\% & 46.44\%\\
\nopagebreak
 &  & Gold (XCEC) & 100\% & 0\%\\
\nopagebreak
 &  & Palladium (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Platinum (XNYM) & 100\% & 0\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 100\% & 0\%\\
\nopagebreak
 &  & Natural gas (XNYM) & 0\% & 100\%\\
\nopagebreak
 &  & Crude oil-WTI (XNYM) & 5.76\% & 46.09\%\\
\nopagebreak
 &  & Gasoline (XNYM) & 52.67\% & 0\%\\
\nopagebreak
 &  & Copper (XCEC) & 0\% & 81.48\%\\
\nopagebreak
 &  & Gold (XCEC) & 100\% & 0\%\\
\nopagebreak
 &  & Palladium (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Platinum (XNYM) & 100\% & 0\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Silver (XCEC) & 99.59\% & 0\%\\
\nopagebreak
 &  & Corn-\#2 yellow (XCBT) & 0\% & 62.77\%\\
\nopagebreak
 &  & Soybean meal (XCBT) & 34.04\% & 0\%\\
\nopagebreak
 &  & Wheat-SRW (XCBT) & 0\% & 97.52\%\\
\nopagebreak
 &  & Natural gas (XNYM) & 0\% & 100\%\\
\nopagebreak
 &  & Gold (XCEC) & 80.14\% & 0\%\\
\nopagebreak
 &  & Palladium (XNYM) & 100\% & 0\%\\
\nopagebreak
 &  & Platinum (XNYM) & 96.81\% & 0\%\\
\nopagebreak
\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Silver (XCEC) & 57.45\% & 0\%\\
\cmidrule{1-5}\pagebreak[0]
 &  & Oats (XCBT) & 17.1\% & 50.3\%\\
\nopagebreak
 &  & Soybean meal (XCBT) & 19.71\% & 49.1\%\\
\nopagebreak
 &  & Cattle-live (XCME) & 12.46\% & 58.68\%\\
\nopagebreak
 &  & Natural gas (XNYM) & 82.61\% & 1.2\%\\
\nopagebreak
 &  & Crude oil-WTI (XNYM) & 99.71\% & 0\%\\
\nopagebreak
 &  & Gasoline (XNYM) & 99.71\% & 0\%\\
\nopagebreak
 &  & Heating oil (XNYM) & 99.71\% & 0\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Palladium (XNYM) & 10.14\% & 52.69\%\\
\nopagebreak
 &  & Soybean meal (XCBT) & 0.75\% & 80.09\%\\
\nopagebreak
 &  & Natural gas (XNYM) & 87.97\% & 0\%\\
\nopagebreak
 &  & Crude oil-WTI (XNYM) & 92.48\% & 0\%\\
\nopagebreak
 &  & Gasoline (XNYM) & 92.11\% & 0\%\\
\nopagebreak
 &  & Heating oil (XNYM) & 92.11\% & 0\%\\
\nopagebreak
 &  & Gold (XCEC) & 16.54\% & 37.04\%\\
\nopagebreak
 &  & Platinum (XNYM) & 19.55\% & 31.02\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 49.25\% & 17.13\%\\
\nopagebreak
 &  & Soybean oil (XCBT) & 10.61\% & 58.38\%\\
\nopagebreak
 &  & Natural gas (XNYM) & 95.45\% & 0\%\\
\nopagebreak
 &  & Crude oil-WTI (XNYM) & 95.45\% & 0\%\\
\nopagebreak
 &  & Gasoline (XNYM) & 92.05\% & 0\%\\
\nopagebreak
 &  & Heating oil (XNYM) & 94.7\% & 0\%\\
\nopagebreak
 &  & Copper (XCEC) & 23.11\% & 35.14\%\\
\nopagebreak
 &  & Platinum (XNYM) & 51.14\% & 17.84\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Silver (XCEC) & 25.76\% & 34.05\%\\
\nopagebreak
 &  & Corn-\#2 yellow (XCBT) & 14.97\% & 48.33\%\\
\nopagebreak
 &  & Oats (XCBT) & 19.73\% & 53.53\%\\
\nopagebreak
 &  & Wheat-SRW (XCBT) & 10.54\% & 43.49\%\\
\nopagebreak
 &  & Cattle-feeder (XCME) & 26.53\% & 54.65\%\\
\nopagebreak
 &  & Natural gas (XNYM) & 98.64\% & 0\%\\
\nopagebreak
 &  & Crude oil-WTI (XNYM) & 98.64\% & 0\%\\
\nopagebreak
 &  & Gasoline (XNYM) & 97.28\% & 0\%\\
\nopagebreak
\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Heating oil (XNYM) & 97.28\% & 0\%\\
\cmidrule{1-5}\pagebreak[0]
 &  & Corn-\#2 yellow (XCBT) & 94.52\% & 1.15\%\\
\nopagebreak
 &  & Lean hogs (XCME) & 43.8\% & 36.68\%\\
\nopagebreak
 &  & Cotton-\#2 (IFUS) & 77.81\% & 13.18\%\\
\nopagebreak
 &  & Sugar-\#11 (IFUS) & 25.07\% & 55.87\%\\
\nopagebreak
 &  & Gasoline (XNYM) & 16.43\% & 60.17\%\\
\nopagebreak
 &  & Heating oil (XNYM) & 15.56\% & 33.24\%\\
\nopagebreak
 &  & Palladium (XNYM) & 0\% & 59.03\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Platinum (XNYM) & 0\% & 89.68\%\\
\nopagebreak
 &  & Soybean meal (XCBT) & 17.27\% & 48.18\%\\
\nopagebreak
 &  & Soybeans (XCBT) & 20.45\% & 31.98\%\\
\nopagebreak
 &  & Cattle-live (XCME) & 19.09\% & 48.18\%\\
\nopagebreak
 &  & Natural gas (XNYM) & 78.18\% & 0\%\\
\nopagebreak
 &  & Copper (XCEC) & 0\% & 89.88\%\\
\nopagebreak
 &  & Gold (XCEC) & 0\% & 17\%\\
\nopagebreak
 &  & Platinum (XNYM) & 0\% & 92.71\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 0\% & 30.77\%\\
\nopagebreak
 &  & Soybean meal (XCBT) & 0\% & 82.54\%\\
\nopagebreak
 &  & Soybeans (XCBT) & 0\% & 58.33\%\\
\nopagebreak
 &  & Lean hogs (XCME) & 69.84\% & 21.83\%\\
\nopagebreak
 &  & Cotton-\#2 (IFUS) & 38.1\% & 48.02\%\\
\nopagebreak
 &  & Sugar-\#11 (IFUS) & 34.52\% & 50.79\%\\
\nopagebreak
 &  & Natural gas (XNYM) & 76.59\% & 0\%\\
\nopagebreak
 &  & Gasoline (XNYM) & 8.33\% & 60.32\%\\
\nopagebreak
 & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Copper (XCEC) & 0\% & 40.87\%\\
\nopagebreak
 &  & Corn-\#2 yellow (XCBT) & 89.69\% & 6.77\%\\
\nopagebreak
 &  & Wheat-SRW (XCBT) & 96.91\% & 0\%\\
\nopagebreak
 &  & Cattle-feeder (XCME) & 17.87\% & 69.55\%\\
\nopagebreak
 &  & Cattle-live (XCME) & 27.84\% & 60.9\%\\
\nopagebreak
 &  & Coffee-C (IFUS) & 100\% & 0\%\\
\nopagebreak
 &  & Lumber (XCME) & 40.89\% & 39.85\%\\
\nopagebreak
 &  & Sugar-\#11 (IFUS) & 69.07\% & 20.68\%\\
\nopagebreak
\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Natural gas (XNYM) & 71.48\% & 17.29\%\\*
\end{longtable}
\endgroup{}

\newpage

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{>{}llrrrr}
\caption{\label{tab:co-movement-correlations}This table shows the average pairwise correlation amongst factor picks for each factor and period independently. The figures are shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor. Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
\toprule
picking factor & regime & past & financialisation & crisis & post-crisis\\
\midrule
\endfirsthead
\caption[]{\textit{(continued)}}\\
\toprule
picking factor & regime & past & financialisation & crisis & post-crisis\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
 & all & 23.68\% & 34.2\% & 50.07\% & 26.13\%\\
\nopagebreak
 & backwardation & 22.21\% & 36.28\% & 45.4\% & 22.53\%\\
\nopagebreak
\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{market}} & contango & 25.31\% & 32.6\% & 52.73\% & 29.07\%\\
\cmidrule{1-6}\pagebreak[0]
 & all & 8.05\% & 22.94\% & 40.1\% & 19.84\%\\
\nopagebreak
 & backwardation & 8.4\% & 22.48\% & 43.5\% & 16.63\%\\
\nopagebreak
\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{CHP}} & contango & 7.64\% & 23.6\% & 38.72\% & 22.32\%\\
\cmidrule{1-6}\pagebreak[0]
 & all & 12.42\% & 32.35\% & 41.96\% & 16.13\%\\
\nopagebreak
 & backwardation & 11.62\% & 35.44\% & 41.9\% & 14.44\%\\
\nopagebreak
\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{open interest}} & contango & 12.99\% & 29.69\% & 42.18\% & 17.75\%\\
\cmidrule{1-6}\pagebreak[0]
 & all & 7.07\% & 23.41\% & 23.15\% & 8.86\%\\
\nopagebreak
 & backwardation & 5.63\% & 24.56\% & 18.99\% & 8.37\%\\
\nopagebreak
\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{term structure}} & contango & 8.3\% & 22.66\% & 26.34\% & 9.15\%\\*
\end{longtable}
\endgroup{}

\newpage

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{>{}llllrrrr}
\caption{\label{tab:co-movement-time-reg-picks-facts-picks}This table shows the average time series $R^{2}$ for models where the returns series for the various sets of factor picks are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the picks. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
\toprule
picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
\midrule
\endfirsthead
\caption[]{\textit{(continued)}}\\
\toprule
picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
 &  &  & all & 32.72\% & 42.33\% & 56.22\% & 36.48\%\\
\nopagebreak
 &  &  & backwardation & 31.67\% & 43.85\% & 52.22\% & 34.13\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 33.87\% & 41.14\% & 58.62\% & 38.39\%\\
\nopagebreak
 &  &  & all & 5.61\% & 12.44\% & 6.89\% & 6.83\%\\
\nopagebreak
 &  &  & backwardation & 5.02\% & 11.4\% & 7.33\% & 5.58\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 7.73\% & 15.34\% & 8.2\% & 9.49\%\\
\nopagebreak
 &  &  & all & 17.09\% & 27.87\% & 40.38\% & 17.61\%\\
\nopagebreak
 &  &  & backwardation & 17.36\% & 26.97\% & 33.21\% & 13.37\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 17.39\% & 29.12\% & 44.06\% & 21.69\%\\
\nopagebreak
 &  &  & all & 16.49\% & 21.39\% & 35.95\% & 16.37\%\\
\nopagebreak
 &  &  & backwardation & 13.19\% & 25.78\% & 32.18\% & 12.42\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 20.53\% & 18.68\% & 39.1\% & 20.49\%\\
\nopagebreak
 &  &  & all & 23.2\% & 7.78\% & 11.68\% & 19.69\%\\
\nopagebreak
 &  &  & backwardation & 24.03\% & 8.65\% & 8.56\% & 19.29\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 22.67\% & 7.38\% & 14.32\% & 20.15\%\\
\nopagebreak
 &  &  & all & 25.03\% & 26.41\% & 39.29\% & 27.68\%\\
\nopagebreak
 &  &  & backwardation & 26.05\% & 28.34\% & 34.39\% & 27.3\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 24.42\% & 24.86\% & 41.79\% & 28.25\%\\
\nopagebreak
 &  &  & all & 23.67\% & 22.99\% & 34.48\% & 17.13\%\\
\nopagebreak
 &  &  & backwardation & 21.81\% & 26.13\% & 33.14\% & 14.96\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 26.47\% & 20.67\% & 35.71\% & 19.57\%\\
\nopagebreak
 &  &  & all & 5.92\% & 7.26\% & 4.29\% & 1.98\%\\
\nopagebreak
 &  &  & backwardation & 6.44\% & 7.24\% & 9.11\% & 1.51\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 5.52\% & 9.23\% & 3.01\% & 2.81\%\\
\nopagebreak
 &  &  & all & 11.61\% & 24.74\% & 35.76\% & 17.54\%\\
\nopagebreak
 &  &  & backwardation & 10.72\% & 27.25\% & 33.61\% & 18.51\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 12.92\% & 23.08\% & 37.43\% & 17.53\%\\
\nopagebreak
 &  &  & all & 16.22\% & 24.13\% & 35.98\% & 20.6\%\\
\nopagebreak
 &  &  & backwardation & 17.07\% & 25.62\% & 30.3\% & 16.38\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 16.15\% & 24.36\% & 39.28\% & 23.56\%\\
\cmidrule{1-8}\pagebreak[0]
 &  &  & all & 18.62\% & 38.1\% & 47.61\% & 28.42\%\\
\nopagebreak
 &  &  & backwardation & 19.04\% & 36.9\% & 50.48\% & 25.17\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 18.39\% & 39.54\% & 46.48\% & 30.9\%\\
\nopagebreak
 &  &  & all & 7.19\% & 21.38\% & 13\% & 14.34\%\\
\nopagebreak
 &  &  & backwardation & 6.78\% & 19.58\% & 12.57\% & 18.44\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 8.32\% & 23.66\% & 13.51\% & 14.5\%\\
\nopagebreak
 &  &  & all & 10.45\% & 31.09\% & 38.06\% & 24.09\%\\
\nopagebreak
 &  &  & backwardation & 11.18\% & 30.55\% & 41.19\% & 22.78\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 10.21\% & 31.88\% & 36.81\% & 25.3\%\\
\nopagebreak
 &  &  & all & 8.27\% & 9.84\% & 15.7\% & 10.44\%\\
\nopagebreak
 &  &  & backwardation & 8.12\% & 9.87\% & 16.25\% & 15.17\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 9.33\% & 9.98\% & 15.57\% & 11.21\%\\
\nopagebreak
 &  &  & all & 1.47\% & 4.76\% & 9.16\% & 11.59\%\\
\nopagebreak
 &  &  & backwardation & 2.34\% & 4.23\% & 7.98\% & 11.57\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1\% & 5.64\% & 10.58\% & 11.9\%\\
\nopagebreak
 &  &  & all & 6.27\% & 24.94\% & 25.22\% & 12.58\%\\
\nopagebreak
 &  &  & backwardation & 6.82\% & 26.16\% & 19.14\% & 12.47\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 6.42\% & 24.13\% & 28.34\% & 12.75\%\\
\nopagebreak
 &  &  & all & 5.59\% & 13.44\% & 35.65\% & 14.08\%\\
\nopagebreak
 &  &  & backwardation & 6.49\% & 16.16\% & 39.06\% & 12.01\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 5.2\% & 11.43\% & 34.37\% & 16.51\%\\
\nopagebreak
 &  &  & all & 3.5\% & 5.28\% & 8.11\% & 5.96\%\\
\nopagebreak
 &  &  & backwardation & 3.79\% & 8.13\% & 9.48\% & 6.88\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 4.9\% & 4.01\% & 7.64\% & 5.86\%\\
\nopagebreak
 &  &  & all & 7.45\% & 9.78\% & 15.63\% & 12.48\%\\
\nopagebreak
 &  &  & backwardation & 7.12\% & 9.85\% & 15.97\% & 11.94\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.85\% & 10.75\% & 15.59\% & 13.31\%\\
\nopagebreak
 &  &  & all & 6.26\% & 15.74\% & 28.56\% & 13.03\%\\
\nopagebreak
 &  &  & backwardation & 6.51\% & 19.46\% & 28.59\% & 10.21\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 6.58\% & 13.22\% & 28.76\% & 17.2\%\\
\cmidrule{1-8}\pagebreak[0]
 &  &  & all & 28.43\% & 41.66\% & 49.79\% & 29.2\%\\
\nopagebreak
 &  &  & backwardation & 28\% & 44.29\% & 49.09\% & 27.73\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 28.84\% & 39.55\% & 50.49\% & 30.43\%\\
\nopagebreak
 &  &  & all & 9.58\% & 14.48\% & 11.28\% & 9.83\%\\
\nopagebreak
 &  &  & backwardation & 9.81\% & 13.64\% & 11.15\% & 10.3\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 9.47\% & 16.17\% & 11.62\% & 11.76\%\\
\nopagebreak
 &  &  & all & 12.63\% & 27.21\% & 32.29\% & 18.56\%\\
\nopagebreak
 &  &  & backwardation & 12.41\% & 28.26\% & 35.25\% & 15.67\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 13.06\% & 26.85\% & 31.22\% & 20.78\%\\
\nopagebreak
 &  &  & all & 10.71\% & 23.23\% & 16.94\% & 8.09\%\\
\nopagebreak
 &  &  & backwardation & 9.72\% & 24.06\% & 16.56\% & 13.98\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 11.79\% & 23.43\% & 17.35\% & 9.21\%\\
\nopagebreak
 &  &  & all & 18.25\% & 15.83\% & 9.45\% & 11.79\%\\
\nopagebreak
 &  &  & backwardation & 19.96\% & 14.24\% & 6.39\% & 12.24\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 16.97\% & 17.33\% & 11.49\% & 11.87\%\\
\nopagebreak
 &  &  & all & 24.83\% & 30.24\% & 33.8\% & 13.61\%\\
\nopagebreak
 &  &  & backwardation & 25.07\% & 31.83\% & 26.7\% & 13.11\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 24.77\% & 29.24\% & 37.38\% & 14.3\%\\
\nopagebreak
 &  &  & all & 8.32\% & 17.57\% & 31.68\% & 11.76\%\\
\nopagebreak
 &  &  & backwardation & 7.65\% & 17.99\% & 32.14\% & 11.62\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 9.17\% & 17.62\% & 31.72\% & 12.44\%\\
\nopagebreak
 &  &  & all & 2.3\% & 6.95\% & 7.93\% & 3.63\%\\
\nopagebreak
 &  &  & backwardation & 3.56\% & 5.35\% & 10.01\% & 5.48\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.61\% & 8.26\% & 7.22\% & 3.24\%\\
\nopagebreak
 &  &  & all & 7.54\% & 20.81\% & 17.64\% & 12.3\%\\
\nopagebreak
 &  &  & backwardation & 7.45\% & 22.37\% & 16.44\% & 14.08\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 7.84\% & 19.88\% & 18.58\% & 11.56\%\\
\nopagebreak
 &  &  & all & 8.85\% & 19.61\% & 32.42\% & 11.02\%\\
\nopagebreak
 &  &  & backwardation & 12.38\% & 24.66\% & 32.66\% & 7.46\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 7.69\% & 16.26\% & 32.72\% & 14.76\%\\
\cmidrule{1-8}\pagebreak[0]
 &  &  & all & 20\% & 33.71\% & 33.64\% & 19.37\%\\
\nopagebreak
 &  &  & backwardation & 18.65\% & 35.1\% & 29.47\% & 19.58\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 21.25\% & 32.72\% & 36.91\% & 19.29\%\\
\nopagebreak
 &  &  & all & 4.68\% & 7.97\% & 8.75\% & 3.74\%\\
\nopagebreak
 &  &  & backwardation & 4.7\% & 7.11\% & 10.38\% & 8.99\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 5.19\% & 9.3\% & 8.01\% & 3.69\%\\
\nopagebreak
 &  &  & all & 11.93\% & 28.13\% & 22.6\% & 7.81\%\\
\nopagebreak
 &  &  & backwardation & 14.34\% & 27.9\% & 21.19\% & 8.65\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 10.77\% & 28.61\% & 24.63\% & 8.45\%\\
\nopagebreak
 &  &  & all & 5.54\% & 9.15\% & 13.2\% & 5.52\%\\
\nopagebreak
 &  &  & backwardation & 4.6\% & 8.86\% & 12.38\% & 11.89\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 7.11\% & 10.4\% & 14.58\% & 5.3\%\\
\nopagebreak
 &  &  & all & 8.62\% & 8.02\% & 5.96\% & 10.47\%\\
\nopagebreak
 &  &  & backwardation & 9.54\% & 7.27\% & 6.5\% & 10.93\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 7.77\% & 8.87\% & 6.99\% & 10.46\%\\
\nopagebreak
 &  &  & all & 13.53\% & 15.51\% & 16.65\% & 12.44\%\\
\nopagebreak
 &  &  & backwardation & 13.3\% & 16.33\% & 12.47\% & 12.45\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 13.92\% & 15.23\% & 20.05\% & 12.48\%\\
\nopagebreak
 &  &  & all & 5.94\% & 14.55\% & 14.78\% & 7.79\%\\
\nopagebreak
 &  &  & backwardation & 5.61\% & 16.34\% & 13.08\% & 8.88\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 6.29\% & 13.09\% & 17.1\% & 7.81\%\\
\nopagebreak
 &  &  & all & 5.1\% & 8.38\% & 8.8\% & 6.83\%\\
\nopagebreak
 &  &  & backwardation & 7.27\% & 6.31\% & 8.91\% & 9.15\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 5.15\% & 10.07\% & 9.39\% & 5.96\%\\
\nopagebreak
 &  &  & all & 7.6\% & 12.13\% & 11.03\% & 7.86\%\\
\nopagebreak
 &  &  & backwardation & 7.13\% & 12.38\% & 10.13\% & 9.57\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.38\% & 12.17\% & 12.68\% & 7.96\%\\
\nopagebreak
 &  &  & all & 6.03\% & 16.11\% & 20.26\% & 9.96\%\\
\nopagebreak
 &  &  & backwardation & 9.07\% & 15.15\% & 15.34\% & 10.19\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 6.06\% & 17.5\% & 24.31\% & 10.3\%\\*
\end{longtable}
\endgroup{}

\newpage

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{>{}llllrrrr}
\caption{\label{tab:co-movement-time-reg-US-facts-picks}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
\toprule
picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
\midrule
\endfirsthead
\caption[]{\textit{(continued)}}\\
\toprule
picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
 &  &  & all & 11.67\% & 21.24\% & 28.16\% & 14.85\%\\
\nopagebreak
 &  &  & backwardation & 11.34\% & 22.98\% & 26.68\% & 13.36\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 12.09\% & 19.79\% & 29.81\% & 16.31\%\\
\nopagebreak
 &  &  & all & 1.96\% & 5.44\% & 2.52\% & 3.24\%\\
\nopagebreak
 &  &  & backwardation & 1.83\% & 4.93\% & 3.16\% & 4.06\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 2.85\% & 6.82\% & 2.83\% & 3.73\%\\
\nopagebreak
 &  &  & all & 6.64\% & 13.42\% & 18.81\% & 7.99\%\\
\nopagebreak
 &  &  & backwardation & 6.99\% & 13.31\% & 16.43\% & 7.93\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 6.6\% & 13.78\% & 20.61\% & 9.08\%\\
\nopagebreak
 &  &  & all & 6.12\% & 10.75\% & 18.35\% & 7.61\%\\
\nopagebreak
 &  &  & backwardation & 4.75\% & 13.22\% & 16.28\% & 5.87\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 7.85\% & 9.05\% & 20.59\% & 9.7\%\\
\nopagebreak
 &  &  & all & 8.25\% & 3.72\% & 4.49\% & 6.9\%\\
\nopagebreak
 &  &  & backwardation & 8.64\% & 4.35\% & 3.3\% & 6.81\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 8.08\% & 3.44\% & 5.7\% & 7.11\%\\
\nopagebreak
 &  &  & all & 8.51\% & 12.69\% & 18.26\% & 9.71\%\\
\nopagebreak
 &  &  & backwardation & 8.85\% & 13.94\% & 17.03\% & 9.45\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.4\% & 11.82\% & 19.42\% & 10.13\%\\
\nopagebreak
 &  &  & all & 9.47\% & 11.69\% & 17.99\% & 8.18\%\\
\nopagebreak
 &  &  & backwardation & 8.98\% & 14.42\% & 17.72\% & 6.81\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 10.39\% & 9.76\% & 18.66\% & 9.79\%\\
\nopagebreak
 &  &  & all & 2.1\% & 3.26\% & 1.76\% & 0.79\%\\
\nopagebreak
 &  &  & backwardation & 2.31\% & 3.4\% & 4.15\% & 0.77\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.06\% & 4.12\% & 1.21\% & 1.05\%\\
\nopagebreak
 &  &  & all & 4.51\% & 13.46\% & 17.75\% & 7.25\%\\
\nopagebreak
 &  &  & backwardation & 4.26\% & 15.48\% & 17.21\% & 7.69\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 5.01\% & 12.06\% & 18.8\% & 7.44\%\\
\nopagebreak
 &  &  & all & 5.69\% & 11.42\% & 17.51\% & 7.68\%\\
\nopagebreak
 &  &  & backwardation & 5.91\% & 12.62\% & 15.24\% & 6.11\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 5.87\% & 11.09\% & 19.48\% & 8.94\%\\
\cmidrule{1-8}\pagebreak[0]
 &  &  & all & 6.77\% & 16.67\% & 25.41\% & 12.77\%\\
\nopagebreak
 &  &  & backwardation & 6.85\% & 17.81\% & 24.61\% & 10.81\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 6.84\% & 15.98\% & 26.51\% & 14.52\%\\
\nopagebreak
 &  &  & all & 2.54\% & 8.73\% & 4.39\% & 5.06\%\\
\nopagebreak
 &  &  & backwardation & 2.46\% & 8.28\% & 4.36\% & 6.61\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 3.04\% & 9.5\% & 4.67\% & 5.16\%\\
\nopagebreak
 &  &  & all & 3.9\% & 12.72\% & 17.36\% & 9.4\%\\
\nopagebreak
 &  &  & backwardation & 4.13\% & 13.64\% & 19.11\% & 8.14\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4\% & 12.3\% & 16.6\% & 10.8\%\\
\nopagebreak
 &  &  & all & 2.83\% & 3.82\% & 7.51\% & 4.17\%\\
\nopagebreak
 &  &  & backwardation & 2.82\% & 3.72\% & 7.27\% & 6.11\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.31\% & 4.19\% & 7.95\% & 4.3\%\\
\nopagebreak
 &  &  & all & 0.54\% & 1.68\% & 4.1\% & 4.1\%\\
\nopagebreak
 &  &  & backwardation & 0.9\% & 1.54\% & 2.96\% & 4.14\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.38\% & 2.27\% & 5.48\% & 4.26\%\\
\nopagebreak
 &  &  & all & 2.36\% & 10.1\% & 15.23\% & 4.56\%\\
\nopagebreak
 &  &  & backwardation & 2.57\% & 10.72\% & 10.19\% & 4.46\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 2.45\% & 9.77\% & 18.64\% & 4.71\%\\
\nopagebreak
 &  &  & all & 1.94\% & 6.35\% & 17.65\% & 6.96\%\\
\nopagebreak
 &  &  & backwardation & 2.25\% & 8.71\% & 17.99\% & 5.62\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 1.88\% & 4.71\% & 17.98\% & 8.46\%\\
\nopagebreak
 &  &  & all & 1.31\% & 1.97\% & 2.83\% & 2.2\%\\
\nopagebreak
 &  &  & backwardation & 1.59\% & 2.9\% & 3.32\% & 2.55\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1.85\% & 1.65\% & 2.74\% & 2.37\%\\
\nopagebreak
 &  &  & all & 2.62\% & 4.52\% & 8.05\% & 5.5\%\\
\nopagebreak
 &  &  & backwardation & 2.65\% & 5.03\% & 7.26\% & 5.11\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 3.08\% & 4.51\% & 8.86\% & 6.15\%\\
\nopagebreak
 &  &  & all & 2.43\% & 7\% & 15.51\% & 6.71\%\\
\nopagebreak
 &  &  & backwardation & 2.49\% & 9.01\% & 13.83\% & 4.78\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.94\% & 5.61\% & 16.98\% & 9.57\%\\
\cmidrule{1-8}\pagebreak[0]
 &  &  & all & 10.6\% & 18.43\% & 26.36\% & 12.03\%\\
\nopagebreak
 &  &  & backwardation & 10.25\% & 20.18\% & 25.13\% & 10.91\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 11.05\% & 17.11\% & 27.83\% & 13.17\%\\
\nopagebreak
 &  &  & all & 4\% & 5.34\% & 4.54\% & 3.71\%\\
\nopagebreak
 &  &  & backwardation & 4.1\% & 4.98\% & 4.37\% & 3.61\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 4.02\% & 6.14\% & 4.86\% & 4.74\%\\
\nopagebreak
 &  &  & all & 6.78\% & 13.48\% & 18.66\% & 7.42\%\\
\nopagebreak
 &  &  & backwardation & 6.63\% & 14.34\% & 20.18\% & 5.9\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 7.12\% & 13.11\% & 18.16\% & 8.77\%\\
\nopagebreak
 &  &  & all & 3.94\% & 9.11\% & 7.49\% & 3.11\%\\
\nopagebreak
 &  &  & backwardation & 3.56\% & 9.31\% & 7.08\% & 5.61\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 4.45\% & 9.44\% & 8.05\% & 3.32\%\\
\nopagebreak
 &  &  & all & 6.4\% & 5.64\% & 3.37\% & 4.11\%\\
\nopagebreak
 &  &  & backwardation & 6.93\% & 5.3\% & 2.53\% & 4.35\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 6.07\% & 6.09\% & 4.25\% & 4.1\%\\
\nopagebreak
 &  &  & all & 8.48\% & 12.35\% & 15.81\% & 4.76\%\\
\nopagebreak
 &  &  & backwardation & 8.5\% & 13.24\% & 11.7\% & 4.54\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.63\% & 11.82\% & 18.57\% & 5.08\%\\
\nopagebreak
 &  &  & all & 4.07\% & 12.5\% & 19.46\% & 4.99\%\\
\nopagebreak
 &  &  & backwardation & 3.64\% & 13.52\% & 18.93\% & 4.95\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 4.64\% & 11.82\% & 20.29\% & 5.39\%\\
\nopagebreak
 &  &  & all & 0.83\% & 2.54\% & 3.13\% & 1.45\%\\
\nopagebreak
 &  &  & backwardation & 1.3\% & 2.22\% & 3.71\% & 2.52\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1.13\% & 2.95\% & 3.02\% & 1.16\%\\
\nopagebreak
 &  &  & all & 3.09\% & 7.65\% & 8.04\% & 5.26\%\\
\nopagebreak
 &  &  & backwardation & 2.8\% & 8.53\% & 7.11\% & 5.96\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 3.73\% & 7.22\% & 9\% & 5.21\%\\
\nopagebreak
 &  &  & all & 3.55\% & 9.48\% & 16.63\% & 4.56\%\\
\nopagebreak
 &  &  & backwardation & 4.8\% & 12.03\% & 15.62\% & 3.13\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.21\% & 7.83\% & 17.77\% & 6.32\%\\
\cmidrule{1-8}\pagebreak[0]
 &  &  & all & 9.13\% & 18.37\% & 25.17\% & 8.95\%\\
\nopagebreak
 &  &  & backwardation & 8.79\% & 20.14\% & 22.77\% & 8.19\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 9.55\% & 16.99\% & 27.12\% & 10.02\%\\
\nopagebreak
 &  &  & all & 1.98\% & 3.42\% & 3.3\% & 1.38\%\\
\nopagebreak
 &  &  & backwardation & 1.89\% & 3.08\% & 3.79\% & 3.4\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 2.33\% & 4.07\% & 3.17\% & 1.32\%\\
\nopagebreak
 &  &  & all & 4.8\% & 13.48\% & 15.65\% & 3.14\%\\
\nopagebreak
 &  &  & backwardation & 5.63\% & 14.34\% & 13.9\% & 3.23\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.55\% & 13.11\% & 17.32\% & 3.58\%\\
\nopagebreak
 &  &  & all & 2.58\% & 5.81\% & 7.05\% & 2.51\%\\
\nopagebreak
 &  &  & backwardation & 1.91\% & 5.91\% & 5.92\% & 5.04\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.55\% & 6.2\% & 8.3\% & 2.29\%\\
\nopagebreak
 &  &  & all & 3.93\% & 3.97\% & 2.83\% & 3.6\%\\
\nopagebreak
 &  &  & backwardation & 4.31\% & 3.56\% & 2.88\% & 3.87\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 3.67\% & 4.63\% & 3.53\% & 3.57\%\\
\nopagebreak
 &  &  & all & 6.42\% & 8.62\% & 12.51\% & 4.45\%\\
\nopagebreak
 &  &  & backwardation & 6.24\% & 9.01\% & 9.32\% & 4.44\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 6.73\% & 8.59\% & 14.98\% & 4.53\%\\
\nopagebreak
 &  &  & all & 2.49\% & 8.49\% & 10.4\% & 3.46\%\\
\nopagebreak
 &  &  & backwardation & 2.6\% & 10.34\% & 8.32\% & 3.83\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.58\% & 6.84\% & 12.73\% & 3.64\%\\
\nopagebreak
 &  &  & all & 2.17\% & 3.38\% & 3.69\% & 2.53\%\\
\nopagebreak
 &  &  & backwardation & 3.39\% & 2.69\% & 3.48\% & 3.52\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.06\% & 4.03\% & 4.16\% & 2.16\%\\
\nopagebreak
 &  &  & all & 3.91\% & 5.88\% & 5.59\% & 3.55\%\\
\nopagebreak
 &  &  & backwardation & 3.65\% & 6.37\% & 4.61\% & 3.98\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.38\% & 5.7\% & 6.74\% & 3.94\%\\
\nopagebreak
 &  &  & all & 2.44\% & 7.8\% & 12.81\% & 3.63\%\\
\nopagebreak
 &  &  & backwardation & 4.14\% & 8.02\% & 9.12\% & 3.54\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.27\% & 8.05\% & 15.82\% & 4.21\%\\*
\end{longtable}
\endgroup{}

\newpage

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{>{}llllrrrr}
\caption{\label{tab:co-movement-time-reg-UK-facts-picks}This table shows the average time series $R^{2}$ for models where the returns series for the six UK metals are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the six UK metals. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
\toprule
picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
\midrule
\endfirsthead
\caption[]{\textit{(continued)}}\\
\toprule
picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
 &  &  & all & 0.25\% & 10.17\% & 31.69\% & 11.52\%\\
\nopagebreak
 &  &  & backwardation & 0.32\% & 11.66\% & 31.95\% & 8.64\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 0.3\% & 9.16\% & 31.72\% & 14.26\%\\
\nopagebreak
 &  &  & all & 0.06\% & 3.39\% & 0.42\% & 0.38\%\\
\nopagebreak
 &  &  & backwardation & 0.36\% & 1.84\% & 0.26\% & 0.25\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.05\% & 5.36\% & 0.66\% & 0.82\%\\
\nopagebreak
 &  &  & all & 0.15\% & 13.12\% & 18.65\% & 5.45\%\\
\nopagebreak
 &  &  & backwardation & 0.58\% & 12.24\% & 18.24\% & 5.07\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.1\% & 14.17\% & 19.06\% & 5.98\%\\
\nopagebreak
 &  &  & all & 0.05\% & 3\% & 24.38\% & 16.07\%\\
\nopagebreak
 &  &  & backwardation & 0.11\% & 4.23\% & 14.79\% & 6.56\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.06\% & 2.24\% & 32.21\% & 26.59\%\\
\nopagebreak
 &  &  & all & 0.04\% & 0.83\% & 1.45\% & 0.07\%\\
\nopagebreak
 &  &  & backwardation & 0.05\% & 1.4\% & 0.07\% & 0.03\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.2\% & 0.55\% & 3.21\% & 0.15\%\\
\nopagebreak
 &  &  & all & 0.11\% & 6.59\% & 17.68\% & 2.57\%\\
\nopagebreak
 &  &  & backwardation & 0.17\% & 7.76\% & 17.27\% & 1.58\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.17\% & 5.85\% & 18.2\% & 3.57\%\\
\nopagebreak
 &  &  & all & 0.05\% & 3.99\% & 17.16\% & 6.86\%\\
\nopagebreak
 &  &  & backwardation & 0.39\% & 4.23\% & 19.91\% & 3.79\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.09\% & 3.85\% & 15.74\% & 10.3\%\\
\nopagebreak
 &  &  & all & 0.1\% & 1.82\% & 0.98\% & 0.17\%\\
\nopagebreak
 &  &  & backwardation & 0.42\% & 1.22\% & 0.04\% & 0.35\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.06\% & 2.64\% & 2.2\% & 0.11\%\\
\nopagebreak
 &  &  & all & 0.26\% & 1.85\% & 11.63\% & 2.82\%\\
\nopagebreak
 &  &  & backwardation & 1.06\% & 2.98\% & 11.17\% & 1.53\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.03\% & 1.24\% & 12.09\% & 4.32\%\\
\nopagebreak
 &  &  & all & 0.03\% & 5.78\% & 20.53\% & 3.27\%\\
\nopagebreak
 &  &  & backwardation & 0.1\% & 5.75\% & 18.66\% & 2.59\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.12\% & 6.04\% & 21.67\% & 4.01\%\\
\cmidrule{1-8}\pagebreak[0]
 &  &  & all & 1.55\% & 20.13\% & 34.54\% & 7.43\%\\
\nopagebreak
 &  &  & backwardation & 1.53\% & 20.93\% & 35.18\% & 5.21\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 1.75\% & 19.83\% & 34.3\% & 9.41\%\\
\nopagebreak
 &  &  & all & 0.07\% & 5.5\% & 0.47\% & 2.12\%\\
\nopagebreak
 &  &  & backwardation & 0.12\% & 4.05\% & 1.15\% & 1.4\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.09\% & 7.36\% & 0.25\% & 2.78\%\\
\nopagebreak
 &  &  & all & 1.02\% & 10.98\% & 21.81\% & 8.99\%\\
\nopagebreak
 &  &  & backwardation & 0.77\% & 10.77\% & 25.33\% & 5.57\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 1.36\% & 11.39\% & 19.89\% & 12.11\%\\
\nopagebreak
 &  &  & all & 0.41\% & 0.25\% & 6.19\% & 0.19\%\\
\nopagebreak
 &  &  & backwardation & 0.21\% & 0.47\% & 5.55\% & 0.24\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.61\% & 0.22\% & 6.67\% & 0.2\%\\
\nopagebreak
 &  &  & all & 0.03\% & 0.64\% & 0.06\% & 0.27\%\\
\nopagebreak
 &  &  & backwardation & 0.21\% & 0.06\% & 1.07\% & 0.12\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.08\% & 1.68\% & 0.18\% & 1.33\%\\
\nopagebreak
 &  &  & all & 0.28\% & 10.41\% & 15.26\% & 0.52\%\\
\nopagebreak
 &  &  & backwardation & 0.39\% & 10.56\% & 10.18\% & 0.82\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.34\% & 10.47\% & 18.21\% & 0.38\%\\
\nopagebreak
 &  &  & all & 0.31\% & 8.77\% & 29.79\% & 4.53\%\\
\nopagebreak
 &  &  & backwardation & 0.25\% & 12.85\% & 30.49\% & 1.57\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.49\% & 5.85\% & 29.59\% & 8.33\%\\
\nopagebreak
 &  &  & all & 0.05\% & 4.73\% & 0.83\% & 0.6\%\\
\nopagebreak
 &  &  & backwardation & 0.1\% & 4.5\% & 0.6\% & 1.11\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.27\% & 5.11\% & 0.95\% & 0.31\%\\
\nopagebreak
 &  &  & all & 0.32\% & 1.38\% & 5.13\% & 0.65\%\\
\nopagebreak
 &  &  & backwardation & 0.2\% & 1.98\% & 4.85\% & 0.44\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.58\% & 1.03\% & 5.35\% & 0.86\%\\
\nopagebreak
 &  &  & all & 0.26\% & 19.23\% & 18.98\% & 3.91\%\\
\nopagebreak
 &  &  & backwardation & 0.48\% & 21.81\% & 17.8\% & 4.62\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.22\% & 17.21\% & 19.65\% & 3.4\%\\
\cmidrule{1-8}\pagebreak[0]
 &  &  & all & 0.31\% & 8.13\% & 34.43\% & 3.37\%\\
\nopagebreak
 &  &  & backwardation & 0.35\% & 9.97\% & 35.43\% & 1.72\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 0.39\% & 6.8\% & 34.06\% & 5.08\%\\
\nopagebreak
 &  &  & all & 0.02\% & 1.39\% & 0.15\% & 1.38\%\\
\nopagebreak
 &  &  & backwardation & 0.06\% & 0.83\% & 0.45\% & 0.45\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.07\% & 2.07\% & 0.11\% & 2.46\%\\
\nopagebreak
 &  &  & all & 0.11\% & 11.35\% & 19.64\% & 2.84\%\\
\nopagebreak
 &  &  & backwardation & 0.29\% & 11.19\% & 23.58\% & 1.06\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.07\% & 11.68\% & 17.62\% & 4.84\%\\
\nopagebreak
 &  &  & all & 0.15\% & 1.41\% & 5.91\% & 0.21\%\\
\nopagebreak
 &  &  & backwardation & 0.17\% & 1.89\% & 5.05\% & 0.25\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.24\% & 1.11\% & 6.54\% & 0.2\%\\
\nopagebreak
 &  &  & all & 0.04\% & 0.37\% & 0.03\% & 0.16\%\\
\nopagebreak
 &  &  & backwardation & 0.05\% & 0.3\% & 0.33\% & 0.46\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.15\% & 0.46\% & 0.13\% & 0.09\%\\
\nopagebreak
 &  &  & all & 0.2\% & 5.54\% & 15.97\% & 0.62\%\\
\nopagebreak
 &  &  & backwardation & 0.14\% & 6.38\% & 12.59\% & 0.89\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.38\% & 5.01\% & 17.83\% & 0.53\%\\
\nopagebreak
 &  &  & all & 0.14\% & 7.03\% & 30.65\% & 0.26\%\\
\nopagebreak
 &  &  & backwardation & 0.35\% & 7.6\% & 30.31\% & 0.07\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.08\% & 6.65\% & 30.96\% & 0.9\%\\
\nopagebreak
 &  &  & all & 0.06\% & 0.1\% & 1.96\% & 0.05\%\\
\nopagebreak
 &  &  & backwardation & 0.31\% & 0.2\% & 1.75\% & 0.12\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.07\% & 0.15\% & 2.05\% & 0.06\%\\
\nopagebreak
 &  &  & all & 0.19\% & 1.2\% & 4.58\% & 1.01\%\\
\nopagebreak
 &  &  & backwardation & 0.7\% & 2.21\% & 4.31\% & 0.29\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.06\% & 0.69\% & 4.78\% & 2.14\%\\
\nopagebreak
 &  &  & all & 0.07\% & 3.46\% & 22.01\% & 0.93\%\\
\nopagebreak
 &  &  & backwardation & 0.14\% & 4.11\% & 21.24\% & 0.08\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.08\% & 3.05\% & 22.44\% & 2.18\%\\
\cmidrule{1-8}\pagebreak[0]
 &  &  & all & 0.75\% & 15.9\% & 28.49\% & 1.27\%\\
\nopagebreak
 &  &  & backwardation & 0.59\% & 17.08\% & 27.92\% & 0.43\%\\
\nopagebreak
 & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 0.94\% & 15.1\% & 28.9\% & 2.52\%\\
\nopagebreak
 &  &  & all & 0.04\% & 0.34\% & 0.03\% & 0.03\%\\
\nopagebreak
 &  &  & backwardation & 0.09\% & 0.33\% & 0.06\% & 0.11\%\\
\nopagebreak
 &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.03\% & 0.46\% & 0.05\% & 0.11\%\\
\nopagebreak
 &  &  & all & 0.68\% & 11.35\% & 10.54\% & 0.44\%\\
\nopagebreak
 &  &  & backwardation & 0.4\% & 11.19\% & 8.88\% & 0.57\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 1\% & 11.68\% & 11.43\% & 0.34\%\\
\nopagebreak
 &  &  & all & 0.34\% & 6.03\% & 5.82\% & 0.25\%\\
\nopagebreak
 &  &  & backwardation & 0.18\% & 6.06\% & 3.33\% & 0.13\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.53\% & 6.1\% & 7.87\% & 0.4\%\\
\nopagebreak
 &  &  & all & 0.05\% & 0.08\% & 0.27\% & 0.07\%\\
\nopagebreak
 &  &  & backwardation & 0.03\% & 0.13\% & 0.05\% & 0.51\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.26\% & 0.33\% & 0.67\% & 0.25\%\\
\nopagebreak
 &  &  & all & 0.38\% & 3.41\% & 11.21\% & 0.29\%\\
\nopagebreak
 &  &  & backwardation & 0.16\% & 3.72\% & 7.67\% & 0.6\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.75\% & 3.24\% & 13.44\% & 0.18\%\\
\nopagebreak
 &  &  & all & 0.19\% & 7.89\% & 11.78\% & 0.3\%\\
\nopagebreak
 &  &  & backwardation & 0.34\% & 10.15\% & 8.1\% & 0.07\%\\
\nopagebreak
 & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.13\% & 6.06\% & 15.31\% & 1.33\%\\
\nopagebreak
 &  &  & all & 0.05\% & 2.34\% & 1.67\% & 0.3\%\\
\nopagebreak
 &  &  & backwardation & 0.09\% & 1.07\% & 0.86\% & 0.35\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.04\% & 3.61\% & 2.43\% & 0.31\%\\
\nopagebreak
 &  &  & all & 0.29\% & 0.88\% & 2.66\% & 0.92\%\\
\nopagebreak
 &  &  & backwardation & 0.44\% & 1.81\% & 1.5\% & 0.44\%\\
\nopagebreak
 &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.22\% & 0.44\% & 3.64\% & 1.65\%\\
\nopagebreak
 &  &  & all & 0.09\% & 13.93\% & 11.04\% & 0.17\%\\
\nopagebreak
 &  &  & backwardation & 0.08\% & 10.91\% & 6.36\% & 0.06\%\\
\nopagebreak
\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.11\% & 16.59\% & 14.67\% & 0.6\%\\*
\end{longtable}
\endgroup{}

\cleardoublepage\restoregeometry

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-acharya_limits_2013}{}%
Acharya, V.V., Lochstoer, L.A., Ramadorai, T., 2013. Limits to arbitrage and hedging: Evidence from commodity markets. Journal of Financial Economics 109, 441--465. doi:\href{https://doi.org/10.1016/j.jfineco.2013.03.003}{10.1016/j.jfineco.2013.03.003}

\leavevmode\hypertarget{ref-baker_financialisation_2014}{}%
Baker, S.D., 2014. The financialization of storable commodities (SSRN Scholarly Paper No. ID 2348333). Social Science Research Network, Rochester, NY. doi:\href{https://doi.org/10.2139/ssrn.2348333}{10.2139/ssrn.2348333}

\leavevmode\hypertarget{ref-basak_model_2016}{}%
Basak, S., Pavlova, A., 2016. A model of financialization of commodities. The Journal of Finance 71, 1511--1556. doi:\href{https://doi.org/10.1111/jofi.12408}{10.1111/jofi.12408}

\leavevmode\hypertarget{ref-basu_definancialisation}{}%
Basu, D., Bauthéac, O., 2021. Commodity definancialisation. Working paper.

\leavevmode\hypertarget{ref-basu_capturing_2013}{}%
Basu, D., Miffre, J., 2013. Capturing the risk premium of commodity futures: The role of hedging pressure. Journal of Banking \& Finance 37, 2652--2664. doi:\href{https://doi.org/10.1016/j.jbankfin.2013.02.031}{10.1016/j.jbankfin.2013.02.031}

\leavevmode\hypertarget{ref-bohl_does_2013}{}%
Bohl, M.T., Stephan, P.M., 2013. Does futures speculation destabilize spot prices? New evidence for commodity markets. Journal of Agricultural and Applied Economics 45, 595--616. doi:\href{https://doi.org/10.1017/S1074070800005150}{10.1017/S1074070800005150}

\leavevmode\hypertarget{ref-boons_stock_2012}{}%
Boons, M., De Roon, F., Szymanowska, M., 2012. The stock market price of commodity risk, in: AFA 2012 Chicago Meetings Paper.

\leavevmode\hypertarget{ref-boyd_prevalence_2016}{}%
Boyd, N.E., Büyükşahin, B., Haigh, M.S., Harris, J.H., 2016. The prevalence, sources, and effects of herding. Journal of Futures Markets 36, 671--694. doi:\href{https://doi.org/10.1002/fut.21756}{10.1002/fut.21756}

\leavevmode\hypertarget{ref-brennan_supply_1958}{}%
Brennan, M.J., 1958. The supply of storage. The American Economic Review 48, 50--72.

\leavevmode\hypertarget{ref-brunetti_speculators_2016}{}%
Brunetti, C., Büyükşahin, B., Harris, J.H., 2016. Speculators, prices, and market volatility. Journal of Financial and Quantitative Analysis 51, 1545--1574. doi:\href{https://doi.org/10.1017/S0022109016000569}{10.1017/S0022109016000569}

\leavevmode\hypertarget{ref-brunetti_commodity_2014}{}%
Brunetti, C., Reiffen, D., 2014. Commodity index trading and hedging costs. Journal of Financial Markets 21, 153--180. doi:\href{https://doi.org/10.1016/j.finmar.2014.08.001}{10.1016/j.finmar.2014.08.001}

\leavevmode\hypertarget{ref-bruno_financialisation_2017}{}%
Bruno, V.G., Büyükşahin, B., Robe, M.A., 2017. The financialization of food? American Journal of Agricultural Economics 99, 243--264. doi:\href{https://doi.org/10.1093/ajae/aaw059}{10.1093/ajae/aaw059}

\leavevmode\hypertarget{ref-buyuksahin_speculators_2011}{}%
Büyükşahin, B., Harris, J.H., 2011. Do speculators drive crude oil futures prices? The Energy Journal 167--202.

\leavevmode\hypertarget{ref-buyuksahin_speculators_2014}{}%
Büyükşahin, B., Robe, M.A., 2014. Speculators, commodities and cross-market linkages. Journal of International Money and Finance, Understanding international commodity price fluctuations 42, 38--70. doi:\href{https://doi.org/10.1016/j.jimonfin.2013.08.004}{10.1016/j.jimonfin.2013.08.004}

\leavevmode\hypertarget{ref-cheng_convective_2014}{}%
Cheng, I.-H., Kirilenko, A., Xiong, W., 2014. Convective risk flows in commodity futures markets. Review of Finance 19, 1733--1781. doi:\href{https://doi.org/10.1093/rof/rfu043}{10.1093/rof/rfu043}

\leavevmode\hypertarget{ref-cheng_financialisation_2014}{}%
Cheng, I.-H., Xiong, W., 2014. Financialization of commodity markets. Annual Review of Financial Economics 6, 419--441. doi:\href{https://doi.org/10.1146/annurev-financial-110613-034432}{10.1146/annurev-financial-110613-034432}

\leavevmode\hypertarget{ref-christoffersen_factor_2014}{}%
Christoffersen, P., Lunde, A., Olesen, K.V., 2014. Factor structure in commodity futures return and volatility. Journal of Financial and Quantitative Analysis 1--74. doi:\href{https://doi.org/10.1017/S0022109018000765}{10.1017/S0022109018000765}

\leavevmode\hypertarget{ref-cootner_returns_1960}{}%
Cootner, P.H., 1960. Returns to speculators: Telser versus keynes. Journal of political Economy 68, 396--404. doi:\href{https://doi.org/10.1086/258347}{10.1086/258347}

\leavevmode\hypertarget{ref-danthine_information_1978}{}%
Danthine, J.-P., 1978. Information, futures prices, and stabilizing speculation. Journal of Economic Theory 17, 79--98. doi:\href{https://doi.org/10.1016/0022-0531(78)90124-2}{10.1016/0022-0531(78)90124-2}

\leavevmode\hypertarget{ref-deschutter_food_2010}{}%
De Schutter, O., 2010. Food commodities speculation and food price crises: Regulation to reduce the risks of price volatility. United Nations Special Rapporteur on the Right to Food Briefing Note 2, 1--14.

\leavevmode\hypertarget{ref-domanski_financial_2007}{}%
Domanski, D., Heath, A., 2007. Financial investors and commodity markets. Working Paper.

\leavevmode\hypertarget{ref-duffie_challenges_2014}{}%
Duffie, D., 2014. Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs. The Journal of Legal Studies 43, S173--S182. doi:\href{https://doi.org/10.1086/677836}{10.1086/677836}

\leavevmode\hypertarget{ref-ederington_who_2002}{}%
Ederington, L., Lee, J.H., 2002. Who trades futures and how: Evidence from the heating oil futures market. The Journal of Business 75, 353--373. doi:\href{https://doi.org/10.1086/338706}{10.1086/338706}

\leavevmode\hypertarget{ref-ekeland_speculation_2016}{}%
Ekeland, I., Lautier, D., Villeneuve, B., 2016. Speculation in commodity futures markets: A simple equilibrium model.

\leavevmode\hypertarget{ref-etula_broker-dealer_2013}{}%
Etula, E., 2013. Broker-dealer risk appetite and commodity returns. Journal of Financial Econometrics 11, 486--521. doi:\href{https://doi.org/10.1093/jjfinec/nbs024}{10.1093/jjfinec/nbs024}

\leavevmode\hypertarget{ref-fattouh_role_2013}{}%
Fattouh, B., Kilian, L., Mahadeva, L., 2013. The role of speculation in oil markets: What have we learnt so far? The Energy Journal 34, 7--33.

\leavevmode\hypertarget{ref-fuertes_commodity_2015}{}%
Fuertes, A.-M., Miffre, J., Fernandez-Perez, A., 2015. Commodity strategies based on momentum, term structure, and idiosyncratic volatility. Journal of Futures Markets 35, 274--297. doi:\href{https://doi.org/10.1002/fut.21656}{10.1002/fut.21656}

\leavevmode\hypertarget{ref-gilbert_how_2010}{}%
Gilbert, C.L., 2010a. How to understand high food prices. Journal of Agricultural Economics 61, 398--425. doi:\href{https://doi.org/10.1111/j.1477-9552.2010.00248.x}{10.1111/j.1477-9552.2010.00248.x}

\leavevmode\hypertarget{ref-gilbert_speculative_2010}{}%
Gilbert, C.L., 2010b. Speculative influences on commodity futures prices 2006-2008. UNCTAD, Geneva.

\leavevmode\hypertarget{ref-gilbert_role_2014}{}%
Gilbert, C.L., Pfuderer, S., 2014. The role of index trading in price formation in the grains and oilseeds markets. Journal of Agricultural Economics 65, 303--322. doi:\href{https://doi.org/10.1111/1477-9552.12068}{10.1111/1477-9552.12068}

\leavevmode\hypertarget{ref-goldstein_speculation_2014}{}%
Goldstein, I., Li, Y., Yang, L., 2014. Speculation and hedging in segmented markets. The Review of Financial Studies 27, 881--922. doi:\href{https://doi.org/10.1093/rfs/hht059}{10.1093/rfs/hht059}

\leavevmode\hypertarget{ref-goldstein_commodity_2017}{}%
Goldstein, I., Yang, L., 2017. Commodity financialization and information transmission (SSRN Scholarly Paper No. ID 2555996). Social Science Research Network, Rochester, NY. doi:\href{https://doi.org/10.2139/ssrn.2555996}{10.2139/ssrn.2555996}

\leavevmode\hypertarget{ref-grossman_impossibility_1980}{}%
Grossman, S.J., Stiglitz, J.E., 1980. On the impossibility of informationally efficient markets. The American economic review 70, 393--408.

\leavevmode\hypertarget{ref-hamilton_effects_2015}{}%
Hamilton, J.D., Wu, J.C., 2015. Effects of index-fund investing on commodity futures prices. International Economic Review 56, 187--205. doi:\href{https://doi.org/10.1111/iere.12099}{10.1111/iere.12099}

\leavevmode\hypertarget{ref-henderson_new_2015}{}%
Henderson, B.J., Pearson, N.D., Wang, L., 2015. New evidence on the financialization of commodity markets. The Review of Financial Studies 28, 1285--1311. doi:\href{https://doi.org/10.1093/rfs/hhu091}{10.1093/rfs/hhu091}

\leavevmode\hypertarget{ref-herman_not_2011}{}%
Herman, M.-O., Kelly, R., Nash, R., 2011. Not a game, speculation v. Food security: Regulating financial markets to grow a better future. Oxfam policy and practice: agriculture, food and land 11, 127--138.

\leavevmode\hypertarget{ref-hicks_value_1939}{}%
Hicks, J.R., 1939. Value and capital, 1st ed. Oxford University Press, Cambridge.

\leavevmode\hypertarget{ref-hicks_value_1946}{}%
Hicks, J.R., 1946. Value and capital, 2nd ed. Oxford University Press, Cambridge.

\leavevmode\hypertarget{ref-hirshleifer_speculation_1975}{}%
Hirshleifer, J., 1975. Speculation and equilibrium: Information, risk, and markets. The Quarterly Journal of Economics 89, 519--542.

\leavevmode\hypertarget{ref-hirshleifer_reply_1976}{}%
Hirshleifer, J., 1976. Reply to comments on" speculation and equilibrium: Information, risk, and markets". The Quarterly Journal of Economics 689--696.

\leavevmode\hypertarget{ref-hirshleifer_theory_1977}{}%
Hirshleifer, J., 1977. The theory of speculation under alternative regimes of markets. The Journal of Finance 32, 975--999.

\leavevmode\hypertarget{ref-hong_what_2012}{}%
Hong, H., Yogo, M., 2012. What does futures market interest tell us about the macroeconomy and asset prices? Journal of Financial Economics 105, 473--490. doi:\href{https://doi.org/10.1016/j.jfineco.2012.04.005}{10.1016/j.jfineco.2012.04.005}

\leavevmode\hypertarget{ref-houthakker_restatement_1957}{}%
Houthakker, H., 1957. Restatement of the theory of normal backwardation (Cowles Foundation Discussion Papers No. 44). Cowles Foundation for Research in Economics, Yale University.

\leavevmode\hypertarget{ref-houthakker_speculators_1957}{}%
Houthakker, H.S., 1957. Can speculators forecast prices? The Review of Economics and Statistics 39, 143--151.

\leavevmode\hypertarget{ref-irwin_commodity_2013}{}%
Irwin, S.H., 2013. Commodity index investment and food prices: Does the ``masters hypothesis'' explain recent price spikes? Agricultural Economics 44, 29--41. doi:\href{https://doi.org/10.1111/agec.12048}{10.1111/agec.12048}

\leavevmode\hypertarget{ref-irwin_index_2011}{}%
Irwin, S.H., Sanders, D.R., 2011. Index funds, financialization, and commodity futures markets. Applied Economic Perspectives and Policy 33, 1--31. doi:\href{https://doi.org/10.1093/aepp/ppq032}{10.1093/aepp/ppq032}

\leavevmode\hypertarget{ref-irwin_financialisation_2012}{}%
Irwin, S.H., Sanders, D.R., 2012. Financialization and structural change in commodity futures markets. Journal of Agricultural and Applied Economics 44, 371--396. doi:\href{https://doi.org/10.1017/S1074070800000481}{10.1017/S1074070800000481}

\leavevmode\hypertarget{ref-irwin_devil_2009}{}%
Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009. Devil or angel? The role of speculation in the recent commodity price boom (and bust). Journal of Agricultural and Applied Economics 41, 377--391. doi:\href{https://doi.org/10.1017/S1074070800002856}{10.1017/S1074070800002856}

\leavevmode\hypertarget{ref-juvenal_speculation_2015}{}%
Juvenal, L., Petrella, I., 2015. Speculation in the oil market. Journal of Applied Econometrics 30, 621--649. doi:\href{https://doi.org/10.1002/jae.2388}{10.1002/jae.2388}

\leavevmode\hypertarget{ref-kaldor_speculation_1939}{}%
Kaldor, N., 1939. Speculation and economic stability. The Review of Economic Studies 7, 1--27. doi:\href{https://doi.org/10.2307/2967593}{10.2307/2967593}

\leavevmode\hypertarget{ref-kang_tale_2020}{}%
Kang, W., Rouwenhorst, K.G., Tang, K., 2020. A tale of two premiums: The role of hedgers and speculators in commodity futures markets. The Journal of Finance 75, 377--417.

\leavevmode\hypertarget{ref-keynes_some_1923}{}%
Keynes, J.M., 1923. Some aspects of commodity markets. Manchester Guardian Commercial: European Reconstruction Series 13, 784--786.

\leavevmode\hypertarget{ref-keynes_treatise_1930}{}%
Keynes, J.M., 1930. Treatise on money. Macmillan, London.

\leavevmode\hypertarget{ref-kilian_role_2014}{}%
Kilian, L., Murphy, D.P., 2014. The role of inventories and speculative trading in the global market for crude oil. Journal of Applied Econometrics 29, 454--478. doi:\href{https://doi.org/10.1002/jae.2322}{10.1002/jae.2322}

\leavevmode\hypertarget{ref-kim_does_2015}{}%
Kim, A., 2015. Does futures speculation destabilize commodity markets? Journal of Futures Markets 35, 696--714. doi:\href{https://doi.org/10.1002/fut.21716}{10.1002/fut.21716}

\leavevmode\hypertarget{ref-knittel_simple_2016}{}%
Knittel, C.R., Pindyck, R.S., 2016. The simple economics of commodity price speculation. American Economic Journal: Macroeconomics 8, 85--110. doi:\href{https://doi.org/10.1257/mac.20140033}{10.1257/mac.20140033}

\leavevmode\hypertarget{ref-kyle_informed_1989}{}%
Kyle, A.S., 1989. Informed speculation with imperfect competition. The Review of Economic Studies 56, 317--355.

\leavevmode\hypertarget{ref-leclercq_equilibrium_2014}{}%
Leclercq, E., Praz, R., 2014. Equilibrium commodity trading (SSRN Scholarly Paper No. ID 2464400). Social Science Research Network, Rochester, NY. doi:\href{https://doi.org/10.2139/ssrn.2464400}{10.2139/ssrn.2464400}

\leavevmode\hypertarget{ref-manera_modeling_2016}{}%
Manera, M., Nicolini, M., Vignati, I., 2016. Modeling futures price volatility in energy markets: Is there a role for financial speculation? Energy Economics, Energy markets 53, 220--229. doi:\href{https://doi.org/10.1016/j.eneco.2014.07.001}{10.1016/j.eneco.2014.07.001}

\leavevmode\hypertarget{ref-masters_testimony_2008}{}%
Masters, M.W., 2008. Testimony before the committee on homeland security and governmental affairs. U.S. Senate 20.

\leavevmode\hypertarget{ref-masters_accidental_2008}{}%
Masters, M., White, A., 2008. The accidental hunt brothers: How institutional investors are driving up food and energy prices. Working paper.

\leavevmode\hypertarget{ref-moskowitz_time_2012}{}%
Moskowitz, T.J., Ooi, Y.H., Pedersen, L.H., 2012. Time series momentum. Journal of Financial Economics, Special issue on investor sentiment 104, 228--250. doi:\href{https://doi.org/10.1016/j.jfineco.2011.11.003}{10.1016/j.jfineco.2011.11.003}

\leavevmode\hypertarget{ref-sanders_impact_2011}{}%
Sanders, D.R., Irwin, S.H., 2011a. The impact of index funds in commodity futures markets: A systems approach. The Journal of Alternative Investments 14, 40--49.

\leavevmode\hypertarget{ref-sanders_new_2011}{}%
Sanders, D.R., Irwin, S.H., 2011b. New evidence on the impact of index funds in u.s. Grain futures markets. Canadian Journal of Agricultural Economics/Revue canadienne d'agroeconomie 59, 519--532. doi:\href{https://doi.org/10.1111/j.1744-7976.2011.01226.x}{10.1111/j.1744-7976.2011.01226.x}

\leavevmode\hypertarget{ref-sanders_adequacy_2010}{}%
Sanders, D.R., Irwin, S.H., Merrin, R.P., 2010. The adequacy of speculation in agricultural futures markets: Too much of a good thing? Applied Economic Perspectives and Policy 32, 77--94. doi:\href{https://doi.org/10.1093/aepp/ppp006}{10.1093/aepp/ppp006}

\leavevmode\hypertarget{ref-schumann_hunger_2011}{}%
Schumann, H., 2011. The hunger-makers: How deutsche bank, goldman sachs and other financial institutions are speculating with food at the expense of the poorest. Foodwatch, Berlin.

\leavevmode\hypertarget{ref-schwartz_stochastic_1997}{}%
Schwartz, E.S., 1997. The stochastic behavior of commodity prices: Implications for valuation and hedging. The Journal of Finance 52, 923--973.

\leavevmode\hypertarget{ref-senate_excessive_2009}{}%
Senate, U.S., 2009. Excessive speculation in the wheat market. Majority and Minority Staff Report. Permanent Subcommittee on Investigations 24, 107--108.

\leavevmode\hypertarget{ref-simsek_speculation_2013}{}%
Simsek, A., 2013. Speculation and risk sharing with new financial assets. The Quarterly Journal of Economics 128, 1365--1396. doi:\href{https://doi.org/10.1093/qje/qjt007}{10.1093/qje/qjt007}

\leavevmode\hypertarget{ref-singleton_investor_2013}{}%
Singleton, K.J., 2013. Investor flows and the 2008 boom/bust in oil prices. Management Science 60, 300--318. doi:\href{https://doi.org/10.1287/mnsc.2013.1756}{10.1287/mnsc.2013.1756}

\leavevmode\hypertarget{ref-sockin_informational_2015}{}%
Sockin, M., Xiong, W., 2015. Informational frictions and commodity markets. The Journal of Finance 70, 2063--2098. doi:\href{https://doi.org/10.1111/jofi.12261}{10.1111/jofi.12261}

\leavevmode\hypertarget{ref-stoll_commodity_2011}{}%
Stoll, H.R., Whaley, R.E., 2011. Commodity index investing: Speculation or diversification? The Journal of Alternative Investments 14, 50--60. doi:\href{https://doi.org/10.2139/ssrn.1633908}{10.2139/ssrn.1633908}

\leavevmode\hypertarget{ref-stout_why_1998}{}%
Stout, L.A., 1998. Why the law hates speculators: Regulation and private ordering in the market for otc derivatives. Duke Law Journal 48, 701--786.

\leavevmode\hypertarget{ref-stulz_rethink_1996}{}%
Stulz, R.M., 1996. Rethinking risk management. Journal of Applied Corporate Finance 9, 8--25. doi:\href{https://doi.org/10.1111/j.1745-6622.1996.tb00295.x}{10.1111/j.1745-6622.1996.tb00295.x}

\leavevmode\hypertarget{ref-szymanowska_anatomy_2014}{}%
Szymanowska, M., De Roon, F., Nijman, T., Van Den Goorbergh, R., 2014. An anatomy of commodity futures risk premia. The Journal of Finance 69, 453--482. doi:\href{https://doi.org/10.1111/jofi.12096}{10.1111/jofi.12096}

\leavevmode\hypertarget{ref-tang_index_2012}{}%
Tang, K., Xiong, W., 2012. Index investment and the financialization of commodities. Financial Analysts Journal 68, 54--74. doi:\href{https://doi.org/10.2469/faj.v68.n6.5}{10.2469/faj.v68.n6.5}

\leavevmode\hypertarget{ref-telser_futures_1958}{}%
Telser, L.G., 1958. Futures trading and the storage of cotton and wheat. Journal of Political Economy 66, 233--255. doi:\href{https://doi.org/10.1086/258036}{10.1086/258036}

\leavevmode\hypertarget{ref-till_long_2007}{}%
Till, H., 2007. A long-term perspective on commodity futures returns, in: Intelligent Commodity Investing. Risk books, London.

\leavevmode\hypertarget{ref-tokic_speculation_2012}{}%
Tokic, D., 2012. Speculation and the 2008 oil bubble: The d.c.o.t. Report analysis. Energy Policy 45, 541--550. doi:\href{https://doi.org/10.1016/j.enpol.2012.02.069}{10.1016/j.enpol.2012.02.069}

\leavevmode\hypertarget{ref-turnovsky_determination_1983}{}%
Turnovsky, S.J., 1983. The determination of spot and futures prices with storable commodities. Econometrica 51, 1363--1387.

\leavevmode\hypertarget{ref-unctad_global_2009}{}%
UNCTAD, S.T.F. on S.I., Cooperation, E., 2009. The global economic crisis: Systemic failures and multilateral remedies. UNCTAD, Geneva.

\leavevmode\hypertarget{ref-weymar_supply_1966}{}%
Weymar, F.H., 1966. The supply of storage revisited. The American Economic Review 56, 1226--1234.

\leavevmode\hypertarget{ref-working_price_1933}{}%
Working, H., 1933. Price relations between july and september wheat futures at chicago since 1885. Wheat Studies 9, 187.

\leavevmode\hypertarget{ref-working_theory_1948}{}%
Working, H., 1948. Theory of the inverse carrying charge in futures markets. Journal of Farm Economics 30, 1--28. doi:\href{https://doi.org/10.2307/1232678}{10.2307/1232678}

\leavevmode\hypertarget{ref-working_theory_1949}{}%
Working, H., 1949. The theory of price of storage. The American Economic Review 1254--1262.

\leavevmode\hypertarget{ref-working_hedging_1953}{}%
Working, H., 1953. Hedging reconsidered. Journal of Farm Economics 35, 544--561. doi:\href{https://doi.org/10.2307/1233368}{10.2307/1233368}

\end{document}

### 2021-09-01 paper/paper.Rmd
add complementary files

--- 2021-09-01 docs/paper.Rmd
@@
   bookdown::gitbook:
+    output_dir: "docs"
     pandoc_args: html.yaml

### 2021-09-01 explore/scripts/correlations.r

@@ -1,0 +1,2685 @@
+library(finRes); library(magrittr); library(doParallel)
+# source("explore/scripts/functions - shared.r")
+
+# start cluster ####
+cluster <- makeCluster(detectCores() - 1L, outfile = "")
+registerDoParallel(cluster, cores = detectCores() - 1L)
+
+# globals ####
+data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
+data("exchanges", package = "fewISOs")
+
+storethat <- paste0(here::here(), "/data/storethat.sqlite")
+
+periods <- tibble::tibble(
+  period = c(
+    rep("past", 2L), rep("financialization", 2L), 
+    rep("crisis", 2L), rep("present", 2L)
+  ),
+  bound = rep(c("start", "end"), 4L),
+  date = c(
+    "1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", 
+    "2008-09-15", "2013-06-19", "2013-06-20", "2018-12-31"
+  )
+)
+
+# load data ####
+start <- "1996-01-01"; end <- "2018-12-31"
+# could add COA Comdty (Crude oil-brent - IFEU) ENA Comdty (Crude oil-WTI - IFEU), PGA Comdty (Gasoline-RBOB - IFEU), NVA Comdty (Heating oil - IFEU), 
+# FNA Comdty (Natural gas - IFEU), QSA Comdty (Gasoil-low sulfur - IFEU)
+`commodity futures tickers` <- c(
+  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
+  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
+  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
+  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
+  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
+  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty",
+  "LAA Comdty", "LPA Comdty", "LLA Comdty", "LNA Comdty", "LTA Comdty",
+  "LXA Comdty"
+)
+
+`commodity futures data` <- pullit::pull_futures_market(
+  source = "storethat", type = "term structure", 
[…]

### 2021-09-01 explore/scripts/regressions-time-series.r

@@ -1,0 +1,2815 @@
+library(finRes); library(magrittr); library(doParallel); library(lubridate)
+
+
+# start cluster ####
+cluster <- makeCluster(detectCores() - 1L, outfile = "")
+registerDoParallel(cluster, cores = detectCores() - 1L)
+
+
+# globals ####
+data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
+data("exchanges", package = "fewISOs")
+rf <- readr::read_rds(here::here("data", "risk-free-rate.rds"))
+
+storethat <- here::here("data", "storethat.sqlite")
+
+
+periods <- tibble::tibble(
+  period = c(
+    rep("past", 2L), rep("financialization", 2L), 
+    rep("crisis", 2L), rep("present", 2L)
+  ), 
+  bound = rep(c("start", "end"), 4L),
+  date = c(
+    "1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", "2008-09-15", 
+    "2013-06-19", "2013-06-20", "2018-12-31"
+  )
+)
+# load data ####
+start <- "1996-01-01"; end <- "2018-12-31"
+# could add COA Comdty (Crude oil-brent - IFEU) ENA Comdty (Crude oil-WTI - IFEU), 
+# PGA Comdty (Gasoline-RBOB - IFEU), NVA Comdty (Heating oil - IFEU), 
+# FNA Comdty (Natural gas - IFEU), QSA Comdty (Gasoil-low sulfur - IFEU)
+`commodity futures tickers` <- c(
+  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
+  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
+  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
+  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
+  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
+  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty"
+)
+
+`US commodity futures tickers` <- dplyr::left_join(
+  dplyr::select(tickers_futures, ticker, MIC), 
+  dplyr::select(exchanges, MIC, country), 
+  by = "MIC"
+) %>% 
[…]

### 2021-09-01 explore/scripts/results-cleaning.r

@@ -1,0 +1,617 @@
+library(magrittr)
+data(tickers_futures, package = "BBGsymbols")
+data(exchanges, package = "fewISOs")
+
+commodity_names <- dplyr::right_join(
+  dplyr::select(exchanges, MIC, country),
+  dplyr::select(
+    tickers_futures, ticker, commodity_name = name, MIC, sector, subsector
+  ),
+  by = "MIC"
+) %>% dplyr::select(ticker, commodity_name, MIC, country, sector, subsector) %>%
+  dplyr::mutate(
+    commodity_name = ifelse(
+      nchar(commodity_name) > 15L,
+      stringr::str_extract(commodity_name, "^.+?(?=-)"),
+      commodity_name
+    ),
+    commodity_name = stringr::str_replace_all(paste0(commodity_name, " (", MIC, ")"), "  ", " ")
+  ) %>% dplyr::select(-MIC)
+
+fields <- tibble::tibble(
+  symbol = c(
+    "carry", "FUT_AGGTE_OPEN_INT", "FUT_AGGTE_VOL", "OPEN_INT", "PX_ASK", "PX_BID", 
+    "PX_HIGH", "PX_LAST", "PX_LOW", "PX_MID", "PX_OPEN", "PX_VOLUME"
+  ),
+  field_name = c(
+    "carry", "aggregate open interest", "aggregate volume", "open interest", 
+    "ask price", "bid price", "high price", "close price", "low price", "mid price", 
+    "open price", "volume"
+  )
+)
+
+
+
+
+
+# Descriptive statistics ####
+statistics <- readr::read_rds(
+  here::here("explore", "results", "descriptive-statistics.rds")
+)
+
+## Extract mean and p.value from raw model ####
+commodity_futures <- dplyr::mutate(
+  statistics$results[[1L]],
+  results = purrr::map(results, function(y){
+    dplyr::mutate(
+      y, 
+      results = purrr::map(results, function(x){
+        
+        # browser()
+        dplyr::mutate(
+          x, 
+          p.value = purrr::map(mean, function(a){
+            tryCatch(
+              { a$p.value }, 
+              error=function(cond) {NA_real_}
+            )
+          }),
+          mean = purrr::map(mean, function(a){
+            tryCatch(
+              { a$estimate }, 
+              error=function(cond) {NA_real_}
+            )
+          })
+        ) %>%
+          dplyr::relocate(sd, .after = last_col())
+      })
[…]

### 2021-09-01 explore/scripts/tables.r

@@ -1,0 +1,603 @@
+library(magrittr)
+
+significance <- function(p.value, estimate){
+  if(p.value <= 0.01) paste0("***", estimate)
+  else if (p.value > 0.01 && p.value <= 0.05) paste0("**", estimate)
+  else if (p.value > 0.05 && p.value <= 0.10) paste0("*", estimate)
+  else estimate
+}
+
+percentize <- function(value) paste0(round(value, digits = 4L) * 100, "%")
+
+factors <- c("market", "CHP", "OI nearby", "OI aggregate", "term structure")
+sector_levels <- c("all", "agriculturals", "energy", "metals")
+subsector_levels <- c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")
+
+# descriptive stats ####
+stats <- readr::read_rds(
+  here::here("explore", "results", "descriptive-statistics-clean.rds")
+)
+
+commodities_market_individuals <- dplyr::filter(stats, analysis == "commodity futures") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(analysis == "market variables") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(assets == "individual commodities") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(
+    type == "returns", period != "year", frequency == "daily", 
+    field == "close price"
+  ) %>% dplyr::select(-c(ticker, type, frequency, field, year)) %>%
+  dplyr::mutate_if(.predicate = is.list, .funs = unlist)
+
+commodities_market_countries <- dplyr::filter(stats, analysis == "commodity futures") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(analysis == "market variables") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(assets == "countries - sectors - subsectors") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(
+    sector == "all", subsector == "all", field == "close price",
+    type == "returns", period != "year", frequency == "daily"
+  ) %>% dplyr::select(-c(type, frequency, field, year)) %>%
+  dplyr::mutate_if(.predicate = is.list, .funs = unlist)
+
[…]

### 2021-09-01 explore/scripts/test-differences.r

@@ -1,0 +1,3567 @@
+library(magrittr); library(doParallel); library(storethat); library(pullit)
+library(factorem)
+
+# start cluster ####
+cluster <- makeCluster(detectCores() - 1L, outfile = ""); registerDoParallel(cluster)
+
+# globals ####
+data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
+data("exchanges", package = "fewISOs")
+
+storethat <- paste0(here::here(), "/data/storethat.sqlite")
+
+
+periods <- tibble::tibble(
+  period = c(
+    rep("past", 2L), 
+    rep("financialization", 2L), 
+    rep("crisis", 2L), 
+    rep("present", 2L)
+  ),
+  bound = rep(c("start", "end"), 4L),
+  date = c(
+    "1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", "2008-09-15", 
+    "2013-06-19", "2013-06-20", "2018-12-31"
+  )
+) %>% dplyr::mutate(period = forcats::as_factor(period))
+
+
+# load data ####
+start <- "1996-01-01"; end <- "2018-12-31"
+# could add COA Comdty (Crude oil-brent - IFEU) ENA Comdty (Crude oil-WTI - IFEU), 
+# PGA Comdty (Gasoline-RBOB - IFEU), NVA Comdty (Heating oil - IFEU), 
+# FNA Comdty (Natural gas - IFEU), QSA Comdty (Gasoil-low sulfur - IFEU)
+`commodity futures tickers` <- c(
+  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
+  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
+  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
+  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
+  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
+  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty",
+  "LAA Comdty", "LPA Comdty", "LLA Comdty", "LNA Comdty", "LTA Comdty",
+  "LXA Comdty"
+)
+
+`commodity futures data` <- pullit::pull_futures_market(
[…]

### 2021-09-01 paper/literature_files/format.r

@@ -1,0 +1,7 @@
+caption_latex <- function(x){
+  x <- gsub("(\\d)\\%", "\\1\\\\%", x, ignore.case = TRUE, perl = TRUE)
+  x <- gsub("&", "\\\\&", x, ignore.case = TRUE, perl = TRUE)
+  x <- gsub("\\\\\\*", "*", x, ignore.case = TRUE, perl = TRUE)
+  x <- gsub("\\\\@ref\\((.+?)\\)", "\\\\ref{\\1}", x, ignore.case = TRUE, perl = TRUE)
+  x
+}

### 2021-09-01 paper/script.js

@@ -1,0 +1,21 @@
+let header = document.getElementById("header");
+let title = document.querySelector(".title");
+let authors = document.querySelectorAll(".author");
+let date = document.querySelector(".date");
+let abstract = document.querySelector(".abstract");
+
+let container = document.createElement("div");
+container.classList.add("authors");
+authors.forEach(author => {
+    console.log(author);
+    container.appendChild(author);
+});
+console.log(container)
+
+
+header.innerHTML = "";
+header.appendChild(title);
+header.appendChild(container);
+header.appendChild(date);
+header.appendChild(abstract);
+console.log(header)

### 2021-09-01 explore/shiny/financialization-asset-pricing/datasets.r
untrack some references

@@ -1,1233 +1,0 @@
-library(magrittr)
-
-# data(tickers_futures, package = "BBGsymbols")
-
-factor_parameters <- tibble::tibble(
-  `update frequency` = "week",
-  `return frequency` = "day",
-  `ranking period` = 26L,
-  `long threshold` = 0.67,
-  `short threshold` = 0.33,
-  weighted = TRUE
-)
-
-periods <- tibble::tibble(
-  period = c(
-    rep("past", 2L), rep("financialization", 2L), 
-    rep("crisis", 2L), rep("present", 2L)
-  ), 
-  bound = rep(c("start", "end"), 4L),
-  date = c(
-    "1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", "2008-09-15", 
-    "2013-06-19", "2013-06-20", "2018-12-31"
-  )
-)
-
-# Descriptive statistics ####
-statistics <- readr::read_rds("results/descriptive-statistics-clean.rds")
-
-## Commodity futures 
-
-### market variables 
-
-#### individuals
-
-##### by year 
-
-###### levels 
-# Commodity futures - market variables - individuals - by year - levels
-statistics_commodity_futures_market_individuals_years_levels <-
-  dplyr::filter(statistics, analysis == "commodity futures") %>%
-  dplyr::select(-analysis) %>%
-  tidyr::unnest(results) %>%
-  dplyr::filter(analysis == "market variables") %>%
-  dplyr::select(-analysis) %>%
-  tidyr::unnest(results) %>%
-  dplyr::filter(assets == "individual commodities") %>%
-  dplyr::select(-assets) %>%
-  tidyr::unnest(results) %>% 
-  dplyr::filter(type == "levels", period == "year") %>%
-  dplyr::select(-c(ticker, type, frequency, period)) %>%
-  dplyr::select(
-    country, sector, subsector, commodity, field, dplyr::everything()
-  ) %>%
-  dplyr::mutate(year = as.integer(year)) %>%
-  dplyr::mutate_at(.vars = c("mean", "p.value"), .funs = unlist) %>%
-  dplyr::arrange(dplyr::desc(country), sector, subsector, commodity)
-
-###### returns 
-# Commodity futures - market variables - individuals - by year - returns
-statistics_commodity_futures_market_individuals_years_returns <-
-  dplyr::filter(statistics, analysis == "commodity futures") %>%
-  dplyr::select(-analysis) %>%
[…]

### 2021-09-01 paper/literature_files/format.r

@@ -1,7 +1,0 @@
-caption_latex <- function(x){
-  x <- gsub("(\\d)\\%", "\\1\\\\%", x, ignore.case = TRUE, perl = TRUE)
-  x <- gsub("&", "\\\\&", x, ignore.case = TRUE, perl = TRUE)
-  x <- gsub("\\\\\\*", "*", x, ignore.case = TRUE, perl = TRUE)
-  x <- gsub("\\\\@ref\\((.+?)\\)", "\\\\ref{\\1}", x, ignore.case = TRUE, perl = TRUE)
-  x
-}

### 2021-09-01 paper/script.js

@@ -1,21 +1,0 @@
-let header = document.getElementById("header");
-let title = document.querySelector(".title");
-let authors = document.querySelectorAll(".author");
-let date = document.querySelector(".date");
-let abstract = document.querySelector(".abstract");
-
-let container = document.createElement("div");
-container.classList.add("authors");
-authors.forEach(author => {
-    console.log(author);
-    container.appendChild(author);
-});
-console.log(container)
-
-
-header.innerHTML = "";
-header.appendChild(title);
-header.appendChild(container);
-header.appendChild(date);
-header.appendChild(abstract);
-console.log(header)

### 2021-09-01 docs/paper.Rmd
github pages

@@
         before: |
-          <li><a href="http://bautheac.com.s3-website.eu-west-2.amazonaws.com/research/financialization-co-movement/_book/index.html">Financialization: co-movement</a></li>
+          <li><a href="index.html">Financialization: co-movement</a></li>
       edit: https://github.com/bautheac/financialisation-co-movement/edit/master/%s
@@
 
-# Introduction {#introduction}
+# Introduction {#index}
 <!-- Introduction {#introduction} -->

### 2021-09-01 docs/paper.Rmd
fix html edit link

@@
           <li><a href="index.html">Financialization: co-movement</a></li>
-      edit: https://github.com/bautheac/financialisation-co-movement/edit/master/%s
+      edit: https://github.com/bautheac/financialisation-co-movement/edit/master/docs/%s
       sharing:

### 2021-09-01 docs/paper.Rmd
github pages

--- 2021-09-01 docs/paper.Rmd
@@
 bibliography: literature_files/references.bib
+github-repo: bautheac/financialisation-co-movement
 output:
@@
           <li><a href="index.html">Financialization: co-movement</a></li>
-      edit: https://github.com/bautheac/financialisation-co-movement/edit/master/%s
+        after: |
+          <li id="github"><a href="https://github.com/bautheac/financialisation-co-movement"><img src="github.png" alt="github" width="50" height="50"></a></li>
       sharing:

### 2021-09-01 docs/paper.Rmd
fix github icon

--- 2021-09-01 docs/paper.Rmd
@@
           <li><a href="index.html">Financialization: co-movement</a></li>
-      edit: https://github.com/bautheac/financialisation-co-movement/edit/master/%s
+        after: |
+          <li><a href="https://github.com/bautheac/financialisation-co-movement"><img src="github.png" alt="github" width="50" height="50"></a></li>
       sharing:

### 2021-09-02 docs/paper.Rmd
github pages

--- 2021-09-01 docs/paper.Rmd
@@
 title: 'Financialisation of commodities: co-movement behind-the-scenes'
-subtitle: "A tale of four factors"
+subtitle: A tale of four factors
 date: "`r format(Sys.Date(), '%B %Y')`"
+bibliography: literature_files/references.bib
+github-repo: bautheac/financialisation-co-movement
 abstract: |
@@
 Besides, the effects of financialisation seem to go beyond mechanical effects induced by the rise of indexing.
-bibliography: literature_files/references.bib
 output:
+  bookdown::pdf_book:
+      pandoc_args: latex.yaml
+      base_format: rticles::elsevier_article
+      latex_engine: xelatex
+      toc_depth: 3
+      includes:
+        in_header: preamble.tex
   bookdown::gitbook:
@@
           <li><a href="index.html">Financialization: co-movement</a></li>
-      edit: https://github.com/bautheac/financialisation-co-movement/edit/master/docs/%s
+        after: |
+          <li id="github"><a href="https://github.com/bautheac/financialisation-co-movement"><img src="github.png" alt="github" width="50" height="50"></a></li>
       sharing:
@@
       after_body: doc_suffix.html
-  bookdown::pdf_book:
-      pandoc_args: latex.yaml
-      base_format: rticles::elsevier_article
-      latex_engine: xelatex
-      toc_depth: 3
-      includes:
-        in_header: preamble.tex
 ---

### 2021-09-02 docs/paper.tex
github pages

@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\hypertarget{index}{%
+\section{Introduction}\label{index}}
 
@@
 \leavevmode\hypertarget{ref-acharya_limits_2013}{}%
-Acharya, V.V., Lochstoer, L.A., Ramadorai, T., 2013.
-Limits to arbitrage and hedging: Evidence from commodity markets.
-Journal of Financial Economics 109, 441--465.
-doi:\href{https://doi.org/10.1016/j.jfineco.2013.03.003}{10.1016/j.jfineco.2013.03.003}
+Acharya, V.V., Lochstoer, L.A., Ramadorai, T., 2013. Limits to arbitrage and hedging: Evidence from commodity markets. Journal of Financial Economics 109, 441--465.
 
 \leavevmode\hypertarget{ref-baker_financialisation_2014}{}%
-Baker, S.D., 2014.
-The financialization of storable commodities (SSRN Scholarly Paper No.
-ID 2348333).
-Social Science Research Network, Rochester, NY.
-doi:\href{https://doi.org/10.2139/ssrn.2348333}{10.2139/ssrn.2348333}
+Baker, S.D., 2014. The financialization of storable commodities (SSRN Scholarly Paper No. ID 2348333). Social Science Research Network, Rochester, NY.
 
 \leavevmode\hypertarget{ref-basak_model_2016}{}%
-Basak, S., Pavlova, A., 2016. A model of financialization of commodities. The Journal of Finance 71, 1511--1556. doi:\href{https://doi.org/10.1111/jofi.12408}{10.1111/jofi.12408}
+Basak, S., Pavlova, A., 2016. A model of financialization of commodities. The Journal of Finance 71, 1511--1556.
 
@@
 \leavevmode\hypertarget{ref-basu_capturing_2013}{}%
-Basu, D., Miffre, J., 2013.
-Capturing the risk premium of commodity futures: The role of hedging pressure.
-Journal of Banking \& Finance 37, 2652--2664.
-doi:\href{https://doi.org/10.1016/j.jbankfin.2013.02.031}{10.1016/j.jbankfin.2013.02.031}
+Basu, D., Miffre, J., 2013. Capturing the risk premium of commodity futures: The role of hedging pressure. Journal of Banking \& Finance 37, 2652--2664.
 
 \leavevmode\hypertarget{ref-bohl_does_2013}{}%
-Bohl, M.T., Stephan, P.M., 2013.
-Does futures speculation destabilize spot prices?
-New evidence for commodity markets.
-Journal of Agricultural and Applied Economics 45, 595--616.
-doi:\href{https://doi.org/10.1017/S1074070800005150}{10.1017/S1074070800005150}
+Bohl, M.T., Stephan, P.M., 2013. Does futures speculation destabilize spot prices? New evidence for commodity markets. Journal of Agricultural and Applied Economics 45, 595--616.
 
@@
 \leavevmode\hypertarget{ref-boyd_prevalence_2016}{}%
-Boyd, N.E., Büyükşahin, B., Haigh, M.S., Harris, J.H., 2016.
-The prevalence, sources, and effects of herding.
-Journal of Futures Markets 36, 671--694.
-doi:\href{https://doi.org/10.1002/fut.21756}{10.1002/fut.21756}
+Boyd, N.E., Büyükşahin, B., Haigh, M.S., Harris, J.H., 2016. The prevalence, sources, and effects of herding. Journal of Futures Markets 36, 671--694.
 
@@
 \leavevmode\hypertarget{ref-brunetti_speculators_2016}{}%
-Brunetti, C., Büyükşahin, B., Harris, J.H., 2016.
-Speculators, prices, and market volatility.
-Journal of Financial and Quantitative Analysis 51, 1545--1574.
-doi:\href{https://doi.org/10.1017/S0022109016000569}{10.1017/S0022109016000569}
+Brunetti, C., Büyükşahin, B., Harris, J.H., 2016. Speculators, prices, and market volatility. Journal of Financial and Quantitative Analysis 51, 1545--1574.
 
 \leavevmode\hypertarget{ref-brunetti_commodity_2014}{}%
-Brunetti, C., Reiffen, D., 2014.
-Commodity index trading and hedging costs.
-Journal of Financial Markets 21, 153--180.
-doi:\href{https://doi.org/10.1016/j.finmar.2014.08.001}{10.1016/j.finmar.2014.08.001}
+Brunetti, C., Reiffen, D., 2014. Commodity index trading and hedging costs. Journal of Financial Markets 21, 153--180.
 
 \leavevmode\hypertarget{ref-bruno_financialisation_2017}{}%
-Bruno, V.G., Büyükşahin, B., Robe, M.A., 2017.
-The financialization of food?
-American Journal of Agricultural Economics 99, 243--264.
-doi:\href{https://doi.org/10.1093/ajae/aaw059}{10.1093/ajae/aaw059}
+Bruno, V.G., Büyükşahin, B., Robe, M.A., 2017. The financialization of food? American Journal of Agricultural Economics 99, 243--264.
 
@@
 \leavevmode\hypertarget{ref-buyuksahin_speculators_2014}{}%
-Büyükşahin, B., Robe, M.A., 2014.
-Speculators, commodities and cross-market linkages.
-Journal of International Money and Finance, Understanding international commodity price fluctuations 42, 38--70.
-doi:\href{https://doi.org/10.1016/j.jimonfin.2013.08.004}{10.1016/j.jimonfin.2013.08.004}
+Büyükşahin, B., Robe, M.A., 2014. Speculators, commodities and cross-market linkages. Journal of International Money and Finance, Understanding international commodity price fluctuations 42, 38--70.
 
 \leavevmode\hypertarget{ref-cheng_convective_2014}{}%
-Cheng, I.-H., Kirilenko, A., Xiong, W., 2014. Convective risk flows in commodity futures markets. Review of Finance 19, 1733--1781. doi:\href{https://doi.org/10.1093/rof/rfu043}{10.1093/rof/rfu043}
+Cheng, I.-H., Kirilenko, A., Xiong, W., 2014. Convective risk flows in commodity futures markets. Review of Finance 19, 1733--1781.
 
 \leavevmode\hypertarget{ref-cheng_financialisation_2014}{}%
-Cheng, I.-H., Xiong, W., 2014.
-Financialization of commodity markets.
-Annual Review of Financial Economics 6, 419--441.
-doi:\href{https://doi.org/10.1146/annurev-financial-110613-034432}{10.1146/annurev-financial-110613-034432}
+Cheng, I.-H., Xiong, W., 2014. Financialization of commodity markets. Annual Review of Financial Economics 6, 419--441.
 
 \leavevmode\hypertarget{ref-christoffersen_factor_2014}{}%
-Christoffersen, P., Lunde, A., Olesen, K.V., 2014.
-Factor structure in commodity futures return and volatility.
-Journal of Financial and Quantitative Analysis 1--74.
-doi:\href{https://doi.org/10.1017/S0022109018000765}{10.1017/S0022109018000765}
+Christoffersen, P., Lunde, A., Olesen, K.V., 2014. Factor structure in commodity futures return and volatility. Journal of Financial and Quantitative Analysis 1--74.
 
 \leavevmode\hypertarget{ref-cootner_returns_1960}{}%
-Cootner, P.H., 1960. Returns to speculators: Telser versus keynes. Journal of political Economy 68, 396--404. doi:\href{https://doi.org/10.1086/258347}{10.1086/258347}
+Cootner, P.H., 1960. Returns to speculators: Telser versus keynes. Journal of political Economy 68, 396--404.
 
 \leavevmode\hypertarget{ref-danthine_information_1978}{}%
-Danthine, J.-P., 1978.
-Information, futures prices, and stabilizing speculation.
-Journal of Economic Theory 17, 79--98.
-doi:\href{https://doi.org/10.1016/0022-0531(78)90124-2}{10.1016/0022-0531(78)90124-2}
+Danthine, J.-P., 1978. Information, futures prices, and stabilizing speculation. Journal of Economic Theory 17, 79--98.
 
@@
 \leavevmode\hypertarget{ref-duffie_challenges_2014}{}%
-Duffie, D., 2014.
-Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs.
-The Journal of Legal Studies 43, S173--S182.
-doi:\href{https://doi.org/10.1086/677836}{10.1086/677836}
+Duffie, D., 2014. Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs. The Journal of Legal Studies 43, S173--S182.
 
 \leavevmode\hypertarget{ref-ederington_who_2002}{}%
-Ederington, L., Lee, J.H., 2002.
-Who trades futures and how: Evidence from the heating oil futures market.
-The Journal of Business 75, 353--373.
-doi:\href{https://doi.org/10.1086/338706}{10.1086/338706}
+Ederington, L., Lee, J.H., 2002. Who trades futures and how: Evidence from the heating oil futures market. The Journal of Business 75, 353--373.
 
@@
 \leavevmode\hypertarget{ref-etula_broker-dealer_2013}{}%
-Etula, E., 2013. Broker-dealer risk appetite and commodity returns. Journal of Financial Econometrics 11, 486--521. doi:\href{https://doi.org/10.1093/jjfinec/nbs024}{10.1093/jjfinec/nbs024}
+Etula, E., 2013. Broker-dealer risk appetite and commodity returns. Journal of Financial Econometrics 11, 486--521.
 
@@
 \leavevmode\hypertarget{ref-fuertes_commodity_2015}{}%
-Fuertes, A.-M., Miffre, J., Fernandez-Perez, A., 2015.
-Commodity strategies based on momentum, term structure, and idiosyncratic volatility.
-Journal of Futures Markets 35, 274--297.
-doi:\href{https://doi.org/10.1002/fut.21656}{10.1002/fut.21656}
+Fuertes, A.-M., Miffre, J., Fernandez-Perez, A., 2015. Commodity strategies based on momentum, term structure, and idiosyncratic volatility. Journal of Futures Markets 35, 274--297.
 
 \leavevmode\hypertarget{ref-gilbert_how_2010}{}%
-Gilbert, C.L., 2010a. How to understand high food prices. Journal of Agricultural Economics 61, 398--425. doi:\href{https://doi.org/10.1111/j.1477-9552.2010.00248.x}{10.1111/j.1477-9552.2010.00248.x}
+Gilbert, C.L., 2010a. How to understand high food prices. Journal of Agricultural Economics 61, 398--425.
 
@@
 \leavevmode\hypertarget{ref-gilbert_role_2014}{}%
-Gilbert, C.L., Pfuderer, S., 2014.
-The role of index trading in price formation in the grains and oilseeds markets.
-Journal of Agricultural Economics 65, 303--322.
-doi:\href{https://doi.org/10.1111/1477-9552.12068}{10.1111/1477-9552.12068}
+Gilbert, C.L., Pfuderer, S., 2014. The role of index trading in price formation in the grains and oilseeds markets. Journal of Agricultural Economics 65, 303--322.
 
 \leavevmode\hypertarget{ref-goldstein_speculation_2014}{}%
-Goldstein, I., Li, Y., Yang, L., 2014. Speculation and hedging in segmented markets. The Review of Financial Studies 27, 881--922. doi:\href{https://doi.org/10.1093/rfs/hht059}{10.1093/rfs/hht059}
+Goldstein, I., Li, Y., Yang, L., 2014. Speculation and hedging in segmented markets. The Review of Financial Studies 27, 881--922.
 
 \leavevmode\hypertarget{ref-goldstein_commodity_2017}{}%
-Goldstein, I., Yang, L., 2017.
-Commodity financialization and information transmission (SSRN Scholarly Paper No.
-ID 2555996).
-Social Science Research Network, Rochester, NY.
-doi:\href{https://doi.org/10.2139/ssrn.2555996}{10.2139/ssrn.2555996}
+Goldstein, I., Yang, L., 2017. Commodity financialization and information transmission (SSRN Scholarly Paper No. ID 2555996). Social Science Research Network, Rochester, NY.
 
@@
 \leavevmode\hypertarget{ref-hamilton_effects_2015}{}%
-Hamilton, J.D., Wu, J.C., 2015.
-Effects of index-fund investing on commodity futures prices.
-International Economic Review 56, 187--205.
-doi:\href{https://doi.org/10.1111/iere.12099}{10.1111/iere.12099}
+Hamilton, J.D., Wu, J.C., 2015. Effects of index-fund investing on commodity futures prices. International Economic Review 56, 187--205.
 
 \leavevmode\hypertarget{ref-henderson_new_2015}{}%
-Henderson, B.J., Pearson, N.D., Wang, L., 2015.
-New evidence on the financialization of commodity markets.
-The Review of Financial Studies 28, 1285--1311.
-doi:\href{https://doi.org/10.1093/rfs/hhu091}{10.1093/rfs/hhu091}
+Henderson, B.J., Pearson, N.D., Wang, L., 2015. New evidence on the financialization of commodity markets. The Review of Financial Studies 28, 1285--1311.
 
@@
 \leavevmode\hypertarget{ref-hong_what_2012}{}%
-Hong, H., Yogo, M., 2012.
-What does futures market interest tell us about the macroeconomy and asset prices?
-Journal of Financial Economics 105, 473--490.
-doi:\href{https://doi.org/10.1016/j.jfineco.2012.04.005}{10.1016/j.jfineco.2012.04.005}
+Hong, H., Yogo, M., 2012. What does futures market interest tell us about the macroeconomy and asset prices? Journal of Financial Economics 105, 473--490.
 
@@
 \leavevmode\hypertarget{ref-irwin_commodity_2013}{}%
-Irwin, S.H., 2013.
-Commodity index investment and food prices: Does the ``masters hypothesis'' explain recent price spikes?
-Agricultural Economics 44, 29--41.
-doi:\href{https://doi.org/10.1111/agec.12048}{10.1111/agec.12048}
+Irwin, S.H., 2013. Commodity index investment and food prices: Does the ``masters hypothesis'' explain recent price spikes? Agricultural Economics 44, 29--41.
 
 \leavevmode\hypertarget{ref-irwin_index_2011}{}%
-Irwin, S.H., Sanders, D.R., 2011.
-Index funds, financialization, and commodity futures markets.
-Applied Economic Perspectives and Policy 33, 1--31.
-doi:\href{https://doi.org/10.1093/aepp/ppq032}{10.1093/aepp/ppq032}
+Irwin, S.H., Sanders, D.R., 2011. Index funds, financialization, and commodity futures markets. Applied Economic Perspectives and Policy 33, 1--31.
 
 \leavevmode\hypertarget{ref-irwin_financialisation_2012}{}%
-Irwin, S.H., Sanders, D.R., 2012.
-Financialization and structural change in commodity futures markets.
-Journal of Agricultural and Applied Economics 44, 371--396.
-doi:\href{https://doi.org/10.1017/S1074070800000481}{10.1017/S1074070800000481}
+Irwin, S.H., Sanders, D.R., 2012. Financialization and structural change in commodity futures markets. Journal of Agricultural and Applied Economics 44, 371--396.
 
 \leavevmode\hypertarget{ref-irwin_devil_2009}{}%
-Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009.
-Devil or angel?
-The role of speculation in the recent commodity price boom (and bust).
-Journal of Agricultural and Applied Economics 41, 377--391.
-doi:\href{https://doi.org/10.1017/S1074070800002856}{10.1017/S1074070800002856}
+Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009. Devil or angel? The role of speculation in the recent commodity price boom (and bust). Journal of Agricultural and Applied Economics 41, 377--391.
 
 \leavevmode\hypertarget{ref-juvenal_speculation_2015}{}%
-Juvenal, L., Petrella, I., 2015. Speculation in the oil market. Journal of Applied Econometrics 30, 621--649. doi:\href{https://doi.org/10.1002/jae.2388}{10.1002/jae.2388}
+Juvenal, L., Petrella, I., 2015. Speculation in the oil market. Journal of Applied Econometrics 30, 621--649.
 
 \leavevmode\hypertarget{ref-kaldor_speculation_1939}{}%
-Kaldor, N., 1939. Speculation and economic stability. The Review of Economic Studies 7, 1--27. doi:\href{https://doi.org/10.2307/2967593}{10.2307/2967593}
+Kaldor, N., 1939. Speculation and economic stability. The Review of Economic Studies 7, 1--27.
 
@@
 \leavevmode\hypertarget{ref-kilian_role_2014}{}%
-Kilian, L., Murphy, D.P., 2014.
-The role of inventories and speculative trading in the global market for crude oil.
-Journal of Applied Econometrics 29, 454--478.
-doi:\href{https://doi.org/10.1002/jae.2322}{10.1002/jae.2322}
+Kilian, L., Murphy, D.P., 2014. The role of inventories and speculative trading in the global market for crude oil. Journal of Applied Econometrics 29, 454--478.
 
 \leavevmode\hypertarget{ref-kim_does_2015}{}%
-Kim, A., 2015. Does futures speculation destabilize commodity markets? Journal of Futures Markets 35, 696--714. doi:\href{https://doi.org/10.1002/fut.21716}{10.1002/fut.21716}
+Kim, A., 2015. Does futures speculation destabilize commodity markets? Journal of Futures Markets 35, 696--714.
 
 \leavevmode\hypertarget{ref-knittel_simple_2016}{}%
-Knittel, C.R., Pindyck, R.S., 2016.
-The simple economics of commodity price speculation.
-American Economic Journal: Macroeconomics 8, 85--110.
-doi:\href{https://doi.org/10.1257/mac.20140033}{10.1257/mac.20140033}
+Knittel, C.R., Pindyck, R.S., 2016. The simple economics of commodity price speculation. American Economic Journal: Macroeconomics 8, 85--110.
 
@@
 \leavevmode\hypertarget{ref-leclercq_equilibrium_2014}{}%
-Leclercq, E., Praz, R., 2014.
-Equilibrium commodity trading (SSRN Scholarly Paper No.
-ID 2464400).
-Social Science Research Network, Rochester, NY.
-doi:\href{https://doi.org/10.2139/ssrn.2464400}{10.2139/ssrn.2464400}
+Leclercq, E., Praz, R., 2014. Equilibrium commodity trading (SSRN Scholarly Paper No. ID 2464400). Social Science Research Network, Rochester, NY.
 
 \leavevmode\hypertarget{ref-manera_modeling_2016}{}%
-Manera, M., Nicolini, M., Vignati, I., 2016.
-Modeling futures price volatility in energy markets: Is there a role for financial speculation?
-Energy Economics, Energy markets 53, 220--229.
-doi:\href{https://doi.org/10.1016/j.eneco.2014.07.001}{10.1016/j.eneco.2014.07.001}
+Manera, M., Nicolini, M., Vignati, I., 2016. Modeling futures price volatility in energy markets: Is there a role for financial speculation? Energy Economics, Energy markets 53, 220--229.
 
@@
 \leavevmode\hypertarget{ref-moskowitz_time_2012}{}%
-Moskowitz, T.J., Ooi, Y.H., Pedersen, L.H., 2012.
-Time series momentum.
-Journal of Financial Economics, Special issue on investor sentiment 104, 228--250.
-doi:\href{https://doi.org/10.1016/j.jfineco.2011.11.003}{10.1016/j.jfineco.2011.11.003}
+Moskowitz, T.J., Ooi, Y.H., Pedersen, L.H., 2012. Time series momentum. Journal of Financial Economics, Special issue on investor sentiment 104, 228--250.
 
@@
 \leavevmode\hypertarget{ref-sanders_new_2011}{}%
-Sanders, D.R., Irwin, S.H., 2011b.
-New evidence on the impact of index funds in u.s.
-Grain futures markets.
-Canadian Journal of Agricultural Economics/Revue canadienne d'agroeconomie 59, 519--532.
-doi:\href{https://doi.org/10.1111/j.1744-7976.2011.01226.x}{10.1111/j.1744-7976.2011.01226.x}
+Sanders, D.R., Irwin, S.H., 2011b. New evidence on the impact of index funds in u.s. Grain futures markets. Canadian Journal of Agricultural Economics/Revue canadienne d'agroeconomie 59, 519--532.
 
 \leavevmode\hypertarget{ref-sanders_adequacy_2010}{}%
-Sanders, D.R., Irwin, S.H., Merrin, R.P., 2010.
-The adequacy of speculation in agricultural futures markets: Too much of a good thing?
-Applied Economic Perspectives and Policy 32, 77--94.
-doi:\href{https://doi.org/10.1093/aepp/ppp006}{10.1093/aepp/ppp006}
+Sanders, D.R., Irwin, S.H., Merrin, R.P., 2010. The adequacy of speculation in agricultural futures markets: Too much of a good thing? Applied Economic Perspectives and Policy 32, 77--94.
 
@@
 \leavevmode\hypertarget{ref-simsek_speculation_2013}{}%
-Simsek, A., 2013. Speculation and risk sharing with new financial assets. The Quarterly Journal of Economics 128, 1365--1396. doi:\href{https://doi.org/10.1093/qje/qjt007}{10.1093/qje/qjt007}
+Simsek, A., 2013. Speculation and risk sharing with new financial assets. The Quarterly Journal of Economics 128, 1365--1396.
 
 \leavevmode\hypertarget{ref-singleton_investor_2013}{}%
-Singleton, K.J., 2013. Investor flows and the 2008 boom/bust in oil prices. Management Science 60, 300--318. doi:\href{https://doi.org/10.1287/mnsc.2013.1756}{10.1287/mnsc.2013.1756}
+Singleton, K.J., 2013. Investor flows and the 2008 boom/bust in oil prices. Management Science 60, 300--318.
 
 \leavevmode\hypertarget{ref-sockin_informational_2015}{}%
-Sockin, M., Xiong, W., 2015. Informational frictions and commodity markets. The Journal of Finance 70, 2063--2098. doi:\href{https://doi.org/10.1111/jofi.12261}{10.1111/jofi.12261}
+Sockin, M., Xiong, W., 2015. Informational frictions and commodity markets. The Journal of Finance 70, 2063--2098.
 
 \leavevmode\hypertarget{ref-stoll_commodity_2011}{}%
-Stoll, H.R., Whaley, R.E., 2011.
-Commodity index investing: Speculation or diversification?
-The Journal of Alternative Investments 14, 50--60.
-doi:\href{https://doi.org/10.2139/ssrn.1633908}{10.2139/ssrn.1633908}
+Stoll, H.R., Whaley, R.E., 2011. Commodity index investing: Speculation or diversification? The Journal of Alternative Investments 14, 50--60.
 
@@
 \leavevmode\hypertarget{ref-stulz_rethink_1996}{}%
-Stulz, R.M., 1996. Rethinking risk management. Journal of Applied Corporate Finance 9, 8--25. doi:\href{https://doi.org/10.1111/j.1745-6622.1996.tb00295.x}{10.1111/j.1745-6622.1996.tb00295.x}
+Stulz, R.M., 1996. Rethinking risk management. Journal of Applied Corporate Finance 9, 8--25.
 
 \leavevmode\hypertarget{ref-szymanowska_anatomy_2014}{}%
-Szymanowska, M., De Roon, F., Nijman, T., Van Den Goorbergh, R., 2014.
-An anatomy of commodity futures risk premia.
-The Journal of Finance 69, 453--482.
-doi:\href{https://doi.org/10.1111/jofi.12096}{10.1111/jofi.12096}
+Szymanowska, M., De Roon, F., Nijman, T., Van Den Goorbergh, R., 2014. An anatomy of commodity futures risk premia. The Journal of Finance 69, 453--482.
 
 \leavevmode\hypertarget{ref-tang_index_2012}{}%
-Tang, K., Xiong, W., 2012. Index investment and the financialization of commodities. Financial Analysts Journal 68, 54--74. doi:\href{https://doi.org/10.2469/faj.v68.n6.5}{10.2469/faj.v68.n6.5}
+Tang, K., Xiong, W., 2012. Index investment and the financialization of commodities. Financial Analysts Journal 68, 54--74.
 
 \leavevmode\hypertarget{ref-telser_futures_1958}{}%
-Telser, L.G., 1958. Futures trading and the storage of cotton and wheat. Journal of Political Economy 66, 233--255. doi:\href{https://doi.org/10.1086/258036}{10.1086/258036}
+Telser, L.G., 1958. Futures trading and the storage of cotton and wheat. Journal of Political Economy 66, 233--255.
 
@@
 \leavevmode\hypertarget{ref-tokic_speculation_2012}{}%
-Tokic, D., 2012. Speculation and the 2008 oil bubble: The d.c.o.t. Report analysis. Energy Policy 45, 541--550. doi:\href{https://doi.org/10.1016/j.enpol.2012.02.069}{10.1016/j.enpol.2012.02.069}
+Tokic, D., 2012. Speculation and the 2008 oil bubble: The d.c.o.t. Report analysis. Energy Policy 45, 541--550.
 
@@
 \leavevmode\hypertarget{ref-working_theory_1948}{}%
-Working, H., 1948. Theory of the inverse carrying charge in futures markets. Journal of Farm Economics 30, 1--28. doi:\href{https://doi.org/10.2307/1232678}{10.2307/1232678}
+Working, H., 1948. Theory of the inverse carrying charge in futures markets. Journal of Farm Economics 30, 1--28.
 
@@
 \leavevmode\hypertarget{ref-working_hedging_1953}{}%
-Working, H., 1953. Hedging reconsidered. Journal of Farm Economics 35, 544--561. doi:\href{https://doi.org/10.2307/1233368}{10.2307/1233368}
+Working, H., 1953. Hedging reconsidered. Journal of Farm Economics 35, 544--561.
 

### 2021-09-03 docs/paper.Rmd
update abstract

--- 2021-09-01 docs/paper.Rmd
@@
 title: 'Financialisation of commodities: co-movement behind-the-scenes'
-subtitle: "A tale of four factors"
+subtitle: A tale of four factors
 date: "`r format(Sys.Date(), '%B %Y')`"
-abstract: |
-  The last two decades have seen major changes in the nature of the commodity markets with the influx of financial investor inflows followed by the financial crisis.
-We study the effects of these events on commodity futures pricing dynamics using commodity asset pricing techniques.
-We find that Keynesian and Working’s term structure paradigms based factors are best able to detect the effects of commodity financialisation, while the effects of the financial crisis and its aftermath are most clearly visible through the performance of the market factor.
-Besides, the effects of financialisation seem to go beyond mechanical effects induced by the rise of indexing.
 bibliography: literature_files/references.bib
 github-repo: bautheac/financialisation-co-movement
+abstract: |
+  In the early 2000s institutional investors entered the commodity futures markets en masse with passive, long only, index type positions in sharp contrast with those typically assumed by traditional expert participants.
+A heated public debate soon erupted over the perceived consequences of the phenomenon--commonly referred to as "financialisation"—and, in response to immediate policy concerns, the matter was thrust onto the academic sphere as a burning issue.
+With the benefit of hindsight it now seems that the academic debate was framed rather narrowly, used contentious research methods, and eventually led to regulatory changes that were therefore perhaps unwarranted.
+In contrast, we take a broader approach where we consider a large cross-section of liquid commodities as suggested by the nature of financilisation that comprehends commodity futures as an asset class.
+Using a bespoke asset pricing factors based framework we study the issue through the lens of co-movement and find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
+The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of "definancialisation" in global commodity futures markets.
 output:
@@
         after: |
-          <li><a href="https://github.com/bautheac/financialisation-co-movement"><img src="github.png" alt="github" width="50" height="50"></a></li>
+          <li id="github"><a href="https://github.com/bautheac/financialisation-co-movement"><img src="github.png" alt="github" width="50" height="50"></a></li>
       sharing:

### 2021-09-03 docs/paper.tex
update abstract

@@
   \begin{abstract}
-  The last two decades have seen major changes in the nature of the commodity markets with the influx of financial investor inflows followed by the financial crisis.
-We study the effects of these events on commodity futures pricing dynamics using commodity asset pricing techniques.
-We find that Keynesian and Working's term structure paradigms based factors are best able to detect the effects of commodity financialisation, while the effects of the financial crisis and its aftermath are most clearly visible through the performance of the market factor.
-Besides, the effects of financialisation seem to go beyond mechanical effects induced by the rise of indexing.
+  In the early 2000s institutional investors entered the commodity futures markets en masse with passive, long only, index type positions in sharp contrast with those typically assumed by traditional expert participants.
+A heated public debate soon erupted over the perceived consequences of the phenomenon--commonly referred to as ``financialisation''---and, in response to immediate policy concerns, the matter was thrust onto the academic sphere as a burning issue.
+With the benefit of hindsight it now seems that the academic debate was framed rather narrowly, used contentious research methods, and eventually led to regulatory changes that were therefore perhaps unwarranted.
+In contrast, we take a broader approach where we consider a large cross-section of liquid commodities as suggested by the nature of financilisation that comprehends commodity futures as an asset class.
+Using a bespoke asset pricing factors based framework we study the issue through the lens of co-movement and find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
+The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of ``definancialisation'' in global commodity futures markets.
   \end{abstract}

### 2022-04-27 docs/paper-remote.Rmd
update paper

--- 2021-09-03 docs/paper.Rmd
@@
 knitr::opts_chunk$set(echo = FALSE)
-
 folder <- "literature_files"; dir.create(folder)
@@
 source(path)
-
 tables_font_size <- 9L
@@
 tables_hline <- "major"
-
 latex_options <- c("repeat_header")
@@
 latex_repeat_header_method <- "replace"
-
 html_font <- "Cambria"
-
 html <- knitr::is_html_output(); latex <- knitr::is_latex_output()
@@
   dplyr::select(results) %>% tidyr::unnest(results)
-
 caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
@@
 align <- c("llrrrr")
-
 table <- kbl(
@@
   pack_rows("equally weighted portfolios", 61, 64) 
-
 if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
@@
 align <- c("lllrrrr")
-
 table <- kbl(
@@
   pack_rows("equally weighted portfolios", 121, 128)
-
 if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
@@
   dplyr::select(regressor, dplyr::everything())
-
 caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against relative changes in commercial hedging pressure (CHP) both at the individual (commodity CHP) and aggregate (aggregate CHP) levels independently.
@@
   collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)
-
 if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
@@
   )
-
 caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities.
@@
 caption <- if (latex) caption_latex(x = caption) else if (html) caption
-
 colnames <- c("factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
 align <- c("lllrrrr")
-
 table <- kbl(
@@
     collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) 
-
 if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
@@
   )
-
 caption <- "This table shows the factor 'picks' for the market as well as the long-short factors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
@@
 align <- c("lllrr")
-
 table <- kbl(
@@
     ) 
-
 if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
@@
   )
-
 caption <- "This table shows the average pairwise correlation amongst factor picks for each factor and period independently.
@@
     )
-
 if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
@@
   )
-
 caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the various sets of factor picks are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the picks.
@@
 align <- c("llllrrrr")
-
 table <- kbl(
@@
   )
-
 caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities.
@@
   )
-
 caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the six UK metals are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the six UK metals.
@@
   ) 
-
 if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {

### 2022-04-27 docs/paper.Rmd
update paper

@@
 library(kableExtra)
-knitr::opts_chunk$set(echo = FALSE)
 
-folder <- "literature_files"; dir.create(folder)
-path <- paste(folder, "references.bib", sep = "/")
-download.file(
-  "https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", 
-  paste(folder, "references.bib", sep = "/")
-)
-path <- paste(folder, "format.r", sep = "/")
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+
+folder <- "literature_files"; dir.create(folder); path <- paste(folder, "references.bib", sep = "/")
+download.file("https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", path)
+
+path <- "./format.r"
 download.file(
@@
 )
-source(path)
+source(path); file.remove(path)
 
@@
 html <- knitr::is_html_output(); latex <- knitr::is_latex_output()
+output_type <- ""
+if (html){ output_type <- "html" }
+if (latex){ output_type <- "latex" }
+
 ```
@@
 Financialisation appears to have affected multiple economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres.
-A vigorous legislative debate has led to regulatory changes accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section `r knitr::asis_output(ifelse(latex, '\\ref{co-movement-background}', '\\@ref(co-movement-background)'))` for a detailed discussion.].
-In response to immediate policy concerns, the academic debate was initially framed rather narrowly.
-In this paper we take a fundamentally different empirical approach that is broader in scope.
+A vigorous legislative debate accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section \@ref(co-movement-background) for a detailed discussion.] eventually led to regulatory changes in several individual markets.
+In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation--the burning issue of the day--at the individual commodity market level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
+With the benefit of hindsight, this approach seems to lack a fundamental understanding of the phenomenon it endeavoured to study and which consequences it attempted to address.
+Financialisation was a phenomenon global in nature; through the channel of index investment it swayed the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
+Focusing on individual markets in this context thus seems incomprehensive.
+The mechanical approach similarly seems amiss both in form and substance.
+Most of the studies underpinning the regulatory response to financialisation took the form of pairwise correlation, causation and to some extent co-integration analysis, all of which are idiosyncratic in nature for they study single pairs of individual commodity assets.
+Besides, some of these techniques since proved controversial and seem to produce results the quality of which may fall short of the standards that may reasonably be expected to lay the ground for legislative action.
+In substance, leaving the idiosyncrasy issue aside, a case could be made for the mechanical approach under the assumption that financialised commodity markets can be described, ceteris paribus, as their prior or legacy state with increased uninformed financial participation.
+The aforementioned technique(s) could thence be used to observe potential changes in pricing dynamics, for example, which origin could be naturally attributed to the market behaviour of the new comers.
+Although appealing, for it comes with the promise of prompt "significant" results, this assumption depicts an incomplete picture for it misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure [@keynes_treatise_1930; @hicks_value_1939].
+While essential to the understanding of the phenomenon, the global nature of financialisation and its impact on market fundamentals therefore appear to have been originally overlooked and another approach, perhaps more refined, seems warranted.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
+We strive to provide one in this study by taking a fundamentally different empirical perspective that is broader in scope.
 We consider the entire cross-section of actively traded commodities on futures markets and use a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations.
-Commodity futures markets have a history of being the classic physical commodity price risk shifting conduit for commodity specialists, and financialisation may have altered this long-standing paradigm with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants.
+The global nature of financialisation makes cross-sectional co-movement a cornerstone issue that the direct impact of increased market participation alone might not be able to fully explain for it potentially had deeper effects, for example on market fundamentals as our results suggest.
+Commodity futures markets have a history of being the classic physical commodity price risk shifting conduit for commodity specialists.
+Over the financialisation period we observe a decrease in effectiveness of commercial hedging pressure (CHP) at explaining commodity futures returns at the individual level accompanied by a more pronounced increase at the aggregate level.
+We further note an overall shift in the nature of hedger’s behaviour away from the traditional Keynesian view of risk transfer with higher individual risk premiums over phases of cross-sectional contango as opposed to backwardation.
+Both patterns suggest that the phenomenon may have altered this long-standing paradigm of commercial risk transfer with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants.
 This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of market participation.
-Factor model techniques are well suited to isolating common driving factors and detecting co-movement; building on theory we therefore develop a bespoke commodity-based asset pricing framework that seems well adapted to study these two issues simultaneously.
-It is comprised of factor models based both on fundamentals as well as liquidity considerations.
+Factor model techniques are well suited to isolating common driving factors and detecting co-movement [@fama_common_1993; @carhart_persistence_1997; @asness_devil_2013; @fama_five_factor_2015; @hou_digesting_2015; @asness_fact_2015; @frazzini_betting_2014; @asness_quality_2019] at a broader level, beyond individual pairs of assets, and are commonly used to study commodity market fundamentals [@schwartz_short_2000; @miffre_momentum_2007; @gorton_fundamentals_2012; @cortazar_commodity_2013; @yang_investment_2013; @daskalaki_factors_2014; @szymanowska_anatomy_2014; @fernandez_skewness_2018; @bakshi_understanding_2019; @boons_basis_2019; @sakkas_factor_2020]; they consequently seem well adapted to study these two issues simultaneously.
+Building on theory we therefore develop a bespoke commodity-based asset pricing framework comprised of factor models based both on fundamentals as well as liquidity considerations.
 One of these is based on the Keynes-Hicks [@keynes_some_1923; @keynes_treatise_1930; @hicks_value_1939; @hicks_value_1946] risk transfer approach to the term structure; the corresponding "theory of normal backwardation", complemented for the possibility of contango [@houthakker_restatement_1957; @cootner_returns_1960], postulates that futures prices for a given commodity are inversely related to the extent that commercial hedgers are short or long and using commercial hedging pressure (CHP) as a proxy for hedgers net market position we construct factor mimicking portfolios that capture the impact of hedging pressure as a systemic factor [@basu_capturing_2013].
@@
 ```{r, include=latex}
-knitr::asis_output('\\bigskip\n')
+knitr::asis_output('\\bigskip')
+knitr::asis_output('\\bigskip')
 knitr::asis_output('\\setlength{\\parindent}{0pt}')
@@
 Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 The cross-sectional nature of financialisation [@cheng_financialisation_2014; @basak_model_2016] leads us to extend the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure first considered in @hong_what_2012.
@@
 This change in pattern suggests the onset of financialisation altered the traditional risk shifting nature of hedger’s behaviour, implied by the Keynesian hypothesis.
-The arrival of financial investors, on the other hand, raises the question of whether they functioned as liquidity providers or demanders.
+This change of paradigm due to the arrival of financial investors, on the other hand, raises the question of whether they functioned as liquidity providers or demanders.
 Arguments have been put forward in favour of both possibilities with @moskowitz_time_2012 arguing that financial investors provide liquidity and @kang_tale_2020 taking the opposite stance.
-Our analysis of returns in periods of low and high **CHP** before and during financialisation allows us to analyse this issue from a new perspective and suggests that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
+Our analysis of individual commodity returns' relation with both CHP and **CHP** before and during financialisation sheds new lights on this issue with our results suggesting that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 @goldstein_speculation_2014 and @goldstein_commodity_2017 argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
@@
 The results of this exercise provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 The UK traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialisation.
@@
 The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes.
@@
 knitr::asis_output('\\bigskip')
+knitr::asis_output('\\bigskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
 ```
@@
 ```{r, include=latex}
-knitr::asis_output('\\cleardoublepage')
+knitr::asis_output('\\newpage')
+```
+```{r, include=html}
+knitr::asis_output('<br/><br/>')
 ```
@@
 Popular commodity indexes whose goal was to track the broad movement of commodity prices became accessible by means of swaps, exchange traded funds and exchange traded notes and attracted at least \$100 billion of net super-hoc investment over the 1998-2008 period.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 Concerns over the consequences of this financialisation phenomenon eventually led to legislative changes including the approval of Rule 76 FR 4752 issued by the US Commodity Futures Trading Commission (CFTC) on January 26^th^, 2011.
@@
 O’Malia in particular) expressing reservations about the lack of supporting evidence and the Rule also triggering thousands of comment letters as well as a lawsuit against the CFTC spearheaded by two Wall Street trade groups, the International Swaps & Derivatives Association (ISDA) and the Securities Industries & Financial Markets Association (SIFMA)^[ISDA & SIFMA v US CFTC; Complaint, 1:11-cv-02146; December 2^nd^, 2011.].
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 A world-wide debate ensued about the role of index funds in commodity markets.
@@
 
+```{r, include=html}
+knitr::asis_output('<br/>')
+```
+
 ## Data {#co-movement-data}
-
 Commodity index swaps, commodity index funds (CIFs), commodity-based exchange traded funds (ETFs) and notes (ETNs) or commodity linked notes (CLNs) were amongst the main investment vehicles that allowed institutional and retail investors to build up commodity exposure in the early 2000s [@boons_stock_2012; @henderson_new_2015; @irwin_index_2011; @unctad_global_2009; @schumann_hunger_2011].
@@
 We also consider the UK metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 The commodity futures trading commission (CFTC) operates a comprehensive system of collecting information on market participants known as the large trader reporting program (LTRP) where it records and reports to the public position data on market participants who have position levels in excess of a particular market specific threshold^[Current reporting level thresholds available at: [www.ecfr.gov](https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=&SID=970471b8455f4bab7db4110cfde50731&mc=true&r=SECTION&n=se17.1.15_103).].
@@
 
+```{r, include=html}
+knitr::asis_output('<br/>')
+```
+
 ## Methods {#co-movement-methods}
-
 On the one hand, futures markets have a long history of serving commodity producers to alleviate their commodity price and output risks.
@@
 This contrasts with the traditional approaches of Keynes and Working and in this context the issues of co-movement and aggregate market participants behaviour seem particularly relevant.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 Asset pricing techniques are well suited to study co-movement.
@@
 While our market portfolios are long only, equally weighted portfolios of particular commodity sets, our other mimicking portfolios for risk factors are constructed as combinations of two sub-portfolios (legs), one held long, one held short, which respective constituents are pooled on a weekly basis according to risk factor specific criteria.
-For each leg, the position weight for a particular asset for a particular week is contingent on the value of the corresponding sorting variable and its rank relative to the other assets in the pool.
+For each leg, the position weight for a particular asset for a particular period is contingent on the value of the corresponding sorting variable and its rank relative to the other assets in the pool.
 The sorting variable values for the asset pool are first rescaled so that the highest (lowest) value becomes 1 (0).
@@
 The individual asset weights are then determined by dividing each score by the sum of the scores.
-The weekly return for a particular mimicking portfolio is calculated as the difference between the weighted average return for constituents of the long portfolio and that for the constituents of the short portfolio.
-i.e, return on the mimicking portfolio for risk factor $i$ ($f_{i}$) for week $t$:
+The period return for a particular mimicking portfolio is calculated as the difference between the weighted average return for constituents of the long portfolio and that for the constituents of the short portfolio.
+i.e, return on the mimicking portfolio for risk factor $i$ ($f_{i}$) for period $t$:
 
@@
 $s\equiv$ selection threshold ($\frac{1}{3}$ here).  
-$w^{*}_{j,t}\equiv$ week $t$ weight for commodity $j$ on the long or short leg.  
-$r_{j,t}\equiv$ week $t$ front contract return for commodity $j$.  
+$w^{*}_{j,t}\equiv$ period $t$ weight for commodity $j$ on the long or short leg.  
+$r_{j,t}\equiv$ period $t$ front contract return for commodity $j$.  
 $j\equiv$ commodity rank in the ordered set $Y_{t}^{f_{i}}$.   
-$Y_{t}^{f_{i}}\equiv$ week $t$ ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is specific to $f_{i}$.
+$Y_{t}^{f_{i}}\equiv$ period $t$ ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is specific to $f_{i}$.
 
-```{r, include=html}
-knitr::asis_output('<br/>')
-```
 ```{r, include=latex}
-knitr::asis_output('\\bigskip\n')
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
 ```
@@
 $\overline{CHP_{j}}=\frac{1}{26}\sum_{k=0}^{25}\frac{L_{j,t-k}}{L_{j,t-k}+S_{j,t-k}}$  
-$L_{j,t}\equiv$ number of long positions held by commercial hedgers for week $t$ on the futures series of commodity $j$.  
-$S_{j,t}\equiv$ number of short positions held by commercial hedgers for week $t$ on the futures series of commodity $j$.
+$L_{j,t}\equiv$ number of long positions held by commercial hedgers for period $t$ on the futures series of commodity $j$.  
+$S_{j,t}\equiv$ number of short positions held by commercial hedgers for period $t$ on the futures series of commodity $j$.
 
-```{r, include=html}
-knitr::asis_output('<br/>')
-```
 ```{r, include=latex}
-knitr::asis_output('\\bigskip\n')
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
 ```
@@
 $\overline{RY_{j}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{F_{j,t-k}^{1}}{F_{j,t-k}^{2}} - 1)$   
-$F_{j,t}^{1}\equiv$ week $t$ close price for commodity $j$ first nearby futures contract.  
-$F_{j,t}^{2}\equiv$ week $t$ close price for commodity $j$ second nearby futures contract.
+$F_{j,t}^{1}\equiv$ period $t$ close price for commodity $j$ first nearby futures contract.  
+$F_{j,t}^{2}\equiv$ period $t$ close price for commodity $j$ second nearby futures contract.
 
-```{r, include=html}
-knitr::asis_output('<br/>')
-```
 ```{r, include=latex}
-knitr::asis_output('\\bigskip\n')
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
 ```
@@
 $\overline{{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{{OI}_{j,t-k}}{{OI}_{j,t-k-1}} - 1)$  
-$OI_{j,t}\equiv$ open interest at close of week $t$ on the front (nearby) contract for commodity $j$.
+$OI_{j,t}\equiv$ open interest at close of period $t$ on the front (nearby) contract for commodity $j$.
 
-```{r, include=html}
-knitr::asis_output('<br/>')
-```
 ```{r, include=latex}
-knitr::asis_output('\\bigskip\n')
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
 ```
@@
 Results are reported for the one-factor model case with the other results available on the [online results dashboard](http://18.135.131.217:3838/financialization-asset-pricing/).
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 For each period we also implement the analysis described above over periods of low and high aggregate CHP (**CHP**), a notion that we believe is particularly relevant in the context of financialisation where issues of co-movement and aggregate market behaviour play a central role.
 We define **CHP** as the cross-sectional average of CHPs for a particular pool of assets.
-i.e., Week $t$ **CHP** for asset pool $x$:
+i.e., period $t$ **CHP** for asset pool $x$:
 
@@
 $n\equiv$ number of commodities in set $x$.  
-$CHP_{i,t}\equiv$ week $t$ CHP for commodity $i$ as defined above.
+$CHP_{i,t}\equiv$ period $t$ CHP for commodity $i$ as defined above.
 
-```{r, include=html}
-knitr::asis_output('<br/>')
-```
 ```{r, include=latex}
-knitr::asis_output('\\bigskip\n')
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
 ```
@@
 We further define aggregate backwardation (**backwardation**) and contango (**contango**) **CHP** regimes as, for a given period, **CHP** levels below and above the period's median respectively and, in contrast with [@hong_what_2012] who aggregate across sub-sectors, the asset pool we consider for **CHP** construction include the whole cross-section of US traded commodities.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 In the next part of the analysis, our mimicking portfolios for risk factors, constructed from the set of all US traded commodities are used as commodity picking devices on the latter commodity set.
@@
 
-```{r, include=html}
-knitr::asis_output('<br/>')
-```
 ```{r, include=latex}
-knitr::asis_output('\\bigskip\n')
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
 ```
@@
 For each period we report the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every set of picks.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 In the last part of the analysis, for each period our mimicking portfolios for risk factors in returns are constructed using each set of commodity picks independently as the asset pool for portfolio construction.
@@
 
-The descriptive statistics over the various time periods for our two sets of commodities (US and non-US) are shown in table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-stats-no-regimes}', '\\@ref(tab:co-movement-stats-no-regimes)'))`.
+The descriptive statistics for the commodity series considered in the study displayed in table \@ref(tab:co-movement-stats-no-regimes) show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
+6.9% with a 10% significance in the pre-financialisation period.
+The increase is even more pronounced for an equally weighted portfolio of UK traded assets (metals), 2.47% (not significant) to 21.8% (significant at the 10% level), which sets out the global nature of the phenomenon.
+Most commodities show a higher mean return while five--Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)--show a lower figure with five significant figures--Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)--against none pre-financialisation.
+Sugar-#11 wins the race with a mean return increasing from -4.6% to 24.9% followed by copper with sizeable increases for both markets: 1.5% to 28.2% (XCEC) and 0.5% to 28.6% (XLME).
+The pattern of results for volatilities is similar although the increase is less pronounced.
+Both equally weighted portfolios shows an increase, more pronounced for the UK assets, 10% to 13.6% (US) vs.
+15.7% to 26.9% (UK), while out of the thirty assets, eleven show a drop in volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C (IFUS), Lumber (XCME), Sugar-#11 (IFUS), Natural gas (XNYM), Crude oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
+Financialisation seems however to have impacted the commodity complex beyond these mechanical effects of increased long participation ensuing from the entry on index type investments as our results suggest next.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
+The cross-sectional nature of financialisation naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure.
 The traditional Keynesian hedging pressure paradigm postulates a negative relationship between the return on an individual commodity futures and its hedging pressure.
-Financialisation has been seen as a cross-sectional commodity market phenomenon; this naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure.
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
-
-In table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-stats-regimes}', '\\@ref(tab:co-movement-stats-regimes)'))` the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
+In table \@ref(tab:co-movement-stats-regimes) the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
 Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another.
@@
 The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 8% during **backwardation** rising to 35.6% during **contango**.
-The onset of financialisation thus seems to have engendered a change in the nature of hedger’s behaviour in the aggregate, taking it away from the traditional Keynesian view of risk shifting.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
+The onset of financialisation thus seems to have engendered a change in the nature of hedger’s behaviour, at the aggregate level in particular, taking it away from the traditional Keynesian view of risk shifting.
 This phenomenon has been noted in earlier theoretical and empirical work [@danthine_information_1978; @stout_why_1998] in different contexts from which two competing models of behaviour have emerged.
@@
 In the second model hedgers are seen as liquidity providers as in @kang_tale_2020 with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
-Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-CHP-US}', '\\@ref(tab:co-movement-time-reg-US-CHP-US)'))` supports this view.
+Table \@ref(tab:co-movement-time-reg-US-CHP) supports this view.
 We regress commodity futures front returns on individual commercial hedging pressure (CHP) as well as aggregate CHP (**CHP**), our market wide measure of CHP, in separate models and find that the explanatory power of CHP at the individual commodity level decreases over the financialisation period with the US cross-sectional average $R^{2}$ falling down to 20.8% from 25.8% in the previous period while that of **CHP** increases (7.1% vs 5.4%).
@@
 
-The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-US}', '\\@ref(tab:co-movement-time-reg-US-facts-US)'))`.
+```{r, include=html}
+knitr::asis_output('<br/>')
+```
+```{r, include=latex}
+knitr::asis_output('\\bigskip')
+knitr::asis_output('\\bigskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
+Using our bespoke commodity-based asset pricing framework we strive to shed new lights on the phenomenon by first regressing returns series for the twenty four individual US commodities against our factor mimicking portfolios independently.
+The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \@ref(tab:co-movement-time-reg-US-facts-US).
 Over the first period the market factor has the best average time series performance with the highest average $R^{2}$ with all three futures market factors performing poorly and the overall performance consistent across periods of high and low **CHP** (below period median).
@@
 
-We next investigate the top eight of the US traded commodities which achieved the highest time series $R^{2}$ for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-picks}', '\\@ref(tab:co-movement-picks)'))`.
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
+We next investigate the top eight of the US traded commodities which achieved the highest time series $R^{2}$ for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \@ref(tab:co-movement-picks).
 For the CHP factor the commodities that achieve high $R^{2}$ in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor.
@@
 
-In table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-correlations}', '\\@ref(tab:co-movement-correlations)'))`, we show the average pairwise returns correlation between each set of picks in each time period.
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
+In table \@ref(tab:co-movement-correlations), we show the average pairwise returns correlation between each set of picks in each time period.
 This exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.
@@
 The higher figures for the open interest factor are driven by the strong presence of the energy complex amongst the corresponding picks.
-The latter exhibits much higher average pairwise correlations than the other sectors in both periods although lower in the second relative to the first which reinforces to role played by the metals in the sharp increase in average pairwise correlation amongst picks for this factor.
+The latter exhibits much higher average pairwise correlations than the other sectors in both periods although lower in the second relative to the first which reinforces the role played by the metals in the sharp increase in average pairwise correlation amongst picks for this factor.
 With regards to **CHP** regimes, although not very pronounced, a pattern is noticeable.
@@
 
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 To further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their explanatory performance on these sets of picks over the four periods independently.
-The results are shown in table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-picks-facts-picks}', '\\@ref(tab:co-movement-time-reg-picks-facts-picks)'))`.
+The results are shown in table \@ref(tab:co-movement-time-reg-picks-facts-picks).
 The long-short factors for a particular attribute select the top and bottom two of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks.
-In the absence of price co-movement between the picks, this market factor will achieve an average $R^{2}$ of around 12.5%^[Market factor lemma: $\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv$ size of market portfolio (eight here).], while there is no non-zero $R^{2}$ lower bound for the corresponding long-short factors.
+In the absence of price co-movement between the picks, the market factor will achieve an average $R^{2}$ of around 12.5%^[Market factor lemma: $\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv$ size of market portfolio (eight here).], while there is no non-zero $R^{2}$ lower bound for the corresponding long-short factors.
 A high average $R^{2}$ for the market factor is indicative of strong price co-movement.
@@
 7.6% to 12.1% for the long.
-Taken together with the previous results showing that the metal complex predominantly loads on the long and short legs of the original CHP and term structure factors respectively, these results provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation.
+Taken together with the previous results showing that the metal complex predominantly loads on the long and short legs of the original CHP and term structure factors respectively, these results provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation perhaps as a result of spillover effects between the corresponding futures and spot markets as suggested in @basak_model_2016.
 
-In table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-picks}', '\\@ref(tab:co-movement-time-reg-US-facts-picks)'))` we assess the performance of the same factors on all the commodities instead of just the picks.
-While the average $R^{2}$s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-picks-facts-picks}', '\\@ref(tab:co-movement-time-reg-picks-facts-picks)'))`.
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
+In table \@ref(tab:co-movement-time-reg-US-facts-picks) we assess the performance of the same factors on all the commodities instead of just the picks.
+While the average $R^{2}$s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table \@ref(tab:co-movement-time-reg-picks-facts-picks).
 In contrast, the average CHP factor built with average CHP factor picks shows a smaller absolute increase in average $R^{2}$ indicating that the link between CHP co-movement and price co-movement is stronger amongst the picks which are predominantly metals.
-Taken together, the results in tables `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-picks-facts-picks}', '\\@ref(tab:co-movement-time-reg-picks-facts-picks)'))` and `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-picks}', '\\@ref(tab:co-movement-time-reg-US-facts-picks)'))` suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.
-To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-UK-facts-picks}', '\\@ref(tab:co-movement-time-reg-UK-facts-picks)'))`.
+Taken together, the results in tables \@ref(tab:co-movement-time-reg-picks-facts-picks) and \@ref(tab:co-movement-time-reg-US-facts-picks) suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.
+To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in Table \@ref(tab:co-movement-time-reg-UK-facts-picks).
 In the first period, although all sets of picks, except that of the market factor, included at least one metal, the average $R^{2}$s are very low; close to zero in most cases.
@@
 
+```{r, include=html}
+knitr::asis_output('<br/>')
+```
+```{r, include=latex}
+knitr::asis_output('\\bigskip')
+knitr::asis_output('\\bigskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results.
-Returns fall sharply relative to the financialisation period (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-stats-no-regimes}', '\\@ref(tab:co-movement-stats-no-regimes)'))`.
-with eighteen US commodities along with all six UK traded metals showing lower mean returns.
+Returns fall sharply relative to the financialisation period (table \@ref(tab:co-movement-stats-no-regimes)) with eighteen US commodities along with all six UK traded metals showing lower mean returns.
 Returns for equally weighted portfolios of both sets of assets fall down to 9.4% and 5.3% from 15.9% and 21.8% respectively.
-Returns are mostly higher during phases of **backwardation** relative to **contango** (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-stats-regimes}', '\\@ref(tab:co-movement-stats-regimes)'))`) with fifteen US assets and five of the UK traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets.
+Returns are mostly higher during phases of **backwardation** relative to **contango** (table \@ref(tab:co-movement-stats-regimes)) with fifteen US assets and five of the UK traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets.
 Volatility is moderately higher for both sets with fifteen US commodities and three UK metals showing higher figures and interestingly eminently higher over phases of **contango**; out of the US complex only Sugar-#11 (IFUS) and none of the UK traded metals show higher volatility figures over **backwardation** phases.
-The performance of the market factor dominates the US commodity complex over the period with a 50% increase in mean average $R^{2}$ to over 30% (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-US}', '\\@ref(tab:co-movement-time-reg-US-facts-US'))`) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
-The average pairwise correlation amongst the market factor picks increases beyond 50% while there is a leveling in that amongst the picks of the long-short factors as shown in table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-correlations}', '\\@ref(tab:co-movement-correlations)'))`.
-Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-picks}', '\\@ref(tab:co-movement-time-reg-US-facts-picks))'))`).
+The symmetry between the dynamics of CHP and **CHP**'s explanatory power on individual commodity returns breaks in the crisis period with both now seemingly converging; the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%).
+The performance of the market factor dominates the US commodity complex over the period with a 50% increase in mean average $R^{2}$ to over 30% (table \@ref(tab:co-movement-time-reg-US-facts-US)) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
+The average pairwise correlation amongst the market factor picks increases beyond 50% while there is a leveling in that amongst the picks of the long-short factors as shown in table \@ref(tab:co-movement-correlations).
+Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table \@ref(tab:co-movement-time-reg-US-facts-picks)).
 Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
-Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-UK-facts-picks}', '\\@ref(tab:co-movement-time-reg-UK-facts-picks))'))` provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average $R^{2}$ increasing to 31.7% from 10.2% in the previous period.
-The returns pullback continues into the post-crisis period with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively.
+Table \@ref(tab:co-movement-time-reg-UK-facts-picks) provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average $R^{2}$ increasing to 31.7% from 10.2% in the previous period.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
+The returns pullback continues into the post-crisis period (table \@ref(tab:co-movement-stats-no-regimes)) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively.
 Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
 The figures for the equally weighted portfolios of US and UK assets drop to 9.9% and 16.2% respectively, very close to pre-financialisation levels.
-The pattern of reversion toward the pre-financialisation Keynesian paradigm intiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of **backwardation** relative to **contango** (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-stats-regimes}', '\\@ref(tab:co-movement-stats-regimes))'))`), more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
+The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (table \@ref(tab:co-movement-stats-regimes)) with mean returns higher during phases of **backwardation** relative to **contango** (table \@ref(tab:co-movement-stats-regimes)), more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
 The difference is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
@@
 Over the financialisation period in contrast volatilities were predominantly higher in **backwardation** for US traded assets with fourteen commodities showing higher volatility figures in these phases; the post-crisis pattern of results for volatilities thus likewise shows signs of reversion to pre-financialisation standards.
-Average pairwise correlations amongst factor picks (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-correlations}', '\\@ref(tab:co-movement-correlations))'))`) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1% to 26.1%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
-The performance of the market factor on the US complex declines below financialisation levels (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-US}', '\\@ref(tab:co-movement-time-reg-US-facts-US))'))`) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-US-facts-picks}', '\\@ref(tab:co-movement-time-reg-US-facts-picks))'))`) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors.
-Table `r knitr::asis_output(ifelse(latex, '\\ref{tab:co-movement-time-reg-UK-facts-picks}', '\\@ref(tab:co-movement-time-reg-UK-facts-picks))'))` provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
+After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and **CHP** part ways (table \@ref(tab:co-movement-time-reg-US-CHP)), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
+The recovery initiated in the crisis period for that of CHP is confirmed with a stronger increase in the post-crisis period, 27.2% vs.
+22.5%, strongest for the metals sector, 37.3% vs.
+23.7%, while the energy sector shows the opposite pattern: 11% vs.
+16%.
+In contrast, after increasing stronger in the crisis, that for **CHP** falls overall in the post-crisis period, 7.5% vs 14.7%, with the decrease strongest for the energy sector in a relative sense: 2.5% vs.
+14.8%.
+Average pairwise correlations amongst factor picks (table \@ref(tab:co-movement-correlations)) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1% to 26.1%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
+The performance of the market factor on the US complex declines below financialisation levels (table \@ref(tab:co-movement-time-reg-US-facts-US)) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table \@ref(tab:co-movement-time-reg-US-facts-picks)) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors.
+Table \@ref(tab:co-movement-time-reg-UK-facts-picks) provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
+
+```{r, include=latex}
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
 Taken together the patterns of results over the crisis and post-crisis periods echo those in @basu_definancialisation in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex, in other words, a process of "definancialisation".
@@
 <!-- ============ -->
-
 In the early 2000s, against a backdrop of a low yield environment and poor stock market performance, a combination of financial innovations^[Commodity price indexes and the ad-hoc financial instruments enabling investment in them were the main financial innovations which allowed large global banks to offer commodity investment products to institutional and retail investors.
@@
 The debate spread to the legislative sphere, with the US senate launching formal investigations, and was thrust onto the academic community as a matter of urgency.
-Perhaps in response to this, most of the early studies focused on the more mechanical effects of financialisation, relying on commodity specific causality and correlation-based analysis.
-The contention eventually triggered legislative action and new position limits were introduced in a number of grains and energy futures markets with substantial potential effects on their functioning and consequently, to a larger extent, on that of the economic system as a whole.
-With the benefit of hindsight, the focus of the debate appears to have been too narrow, and the ensuing regulatory changes might thus have been unwarranted; it therefore seems important to analyse the effects of financialisation from a broader perspective which we do in this study.
-Factor model techniques are well suited to isolating common driving factors and detecting co-movement, a central issue in financialisation which we believe the existing literature has not fully analysed; we thus consider the entire cross-section of actively traded commodities on futures markets and use a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations.
-Our analysis suggests that, beyond energy and agriculturals, financialisation appears to have had a substantial impact on the metals sector at the global level.
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in commodity pricing dynamics.
-In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have set off a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of "definancialisation" in global commodity futures markets.
+Perhaps in response to this, most of the early studies focused on the more mechanical effects of financialisation in individual markets, relying on commodity specific causality and correlation-based analysis.
+The contention eventually triggered legislative action and new position limits were introduced in a number of grains and energy futures markets.
 
 ```{r, include=latex}
-knitr::asis_output('\\cleardoublepage')
-knitr::asis_output('\\newgeometry{left=2.50cm, right=2.50cm, top=2.50cm, bottom=3cm}')
+knitr::asis_output('\\medskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
 ```
 
-# Tables {#tables .unnumbered}
+With the benefit of hindsight, this focus appears to have been too narrow.
+As our results suggests, financialisation was a phenomenon global in nature, with cross-sectional effects on market fundamentals and studying the direct effects of increased market participation in single markets thus seems amiss in this context.
+The results of our analysis further suggest that financialisation set off an ontological drift in the commodity complex beyond energy and agricultural commodities and in fact strongest for the metals sector at the global level; an aspect largely overlooked in the original approach that we believe the existing literature has not fully analysed.
+The regulatory changes underpinned by these studies may thus have been unwarranted with potential substantial undesired effects on the functioning of the markets in which they were enforced and thence, to a larger extent on that of the economic system as a whole.
+The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in commodity pricing dynamics.
+In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have triggered a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of "definancialisation" in global commodity futures markets.
+
+```{r, include=latex}
+knitr::asis_output('\\newpage')
+```
+```{r, include=html}
+knitr::asis_output('<br/><br/>')
+```
+
+# Tables {#tables}
 <!-- Tables {#tables .unnumbered} -->
@@
 ```{r co-movement-stats-no-regimes}
-table <- dplyr::filter(tables, analysis == "descriptive statistics (no regimes)") %>%
-  dplyr::select(results) %>% tidyr::unnest(results)
-
 caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
@@
 
-table <- kbl(
-    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
-  ) %>%
+table <- get_table(tables, "descriptive statistics (no regimes)") %>% 
+  kbl(booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 
-if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
-   kable_classic(
-     table, font_size = tables_font_size, 
-     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
-   )
-}
+show_table(output_type, table)
 ```
@@
 ```{r co-movement-stats-regimes}
-table <- dplyr::filter(tables, analysis == "descriptive statistics (regimes)") %>%
-  dplyr::select(results) %>% tidyr::unnest(results)
-
 caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
@@
 
-table <- kbl(
-    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
-  ) %>%
+table <- get_table(tables, "descriptive statistics (regimes)") %>% 
+  kbl(booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 
-```{r co-movement-time-reg-US-CHP-US}
-table <- dplyr::filter(
-  tables,
-  analysis == "regressions - time series - US commodity returns ~ US commodity CHP"
-) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::select(regressor, dplyr::everything())
-
-caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against relative changes in commercial hedging pressure (CHP) both at the individual (commodity CHP) and aggregate (aggregate CHP) levels independently.
-The results are reported for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018)."
+```{r co-movement-time-reg-US-CHP}
+caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \\@ref(co-movement-methods).
+Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+The results are discussed in section \\@ref(co-movement-results)."
 caption <- if (latex) caption_latex(x = caption) else if (html) caption
@@
 
-table <- kbl(
-    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
-  ) %>%
+table <- get_table(tables, "regressions - time series - US commodities ~ CHP") %>% 
+  kbl(booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
   column_spec(1L, bold = TRUE) %>%
-  collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)
+  collapse_rows(columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)
 
-if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
-   kable_classic(
-     table, font_size = tables_font_size, 
-     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
-   )
-}
+show_table(output_type, table)
 ```
@@
 ```{r co-movement-time-reg-US-facts-US}
-table <- dplyr::filter(
-  tables, 
-  analysis == "regressions - time series - US commodities ~ factors from US commodities"
-) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::mutate(
-    factor = as.character(factor),
-    factor = ifelse(factor == "OI nearby", "open interest", factor)
-  )
-
 caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities.
@@
 
-table <- kbl(
-    table, longtable = T, booktabs = T, caption = caption, col.names = colnames, align = align
+table <- get_table(tables, "regressions - time series - US commodities ~ factors from US commodities") %>%
+  dplyr::mutate(
+    factor = as.character(factor),
+    factor = ifelse(factor == "OI nearby", "open interest", factor)
   ) %>% 
+  kbl(longtable = T, booktabs = T, caption = caption, col.names = colnames, align = align) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 ```{r co-movement-picks}
-table <- dplyr::filter(
-  tables, analysis == "proportions"
-) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::mutate(period = stringr::str_replace_all(period, "present", "post-crisis")) %>%
-  dplyr::mutate(
-    factor = as.character(factor),
-    factor = ifelse(factor == "OI nearby", "open interest", factor)
-  )
-
 caption <- "This table shows the factor 'picks' for the market as well as the long-short factors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
@@
 
-table <- kbl(
-    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
+table <- get_table(tables, "proportions") %>%
+  dplyr::mutate(period = stringr::str_replace_all(period, "present", "post-crisis")) %>%
+  dplyr::mutate(
+    factor = as.character(factor),
+    factor = ifelse(factor == "OI nearby", "open interest", factor)
   ) %>% 
+  kbl(longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 ```{r co-movement-correlations}
-table <- dplyr::filter(
-  tables, analysis == "average correlations (amongst factor picks)"
-) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::mutate(
-    factor = as.character(factor),
-    factor = ifelse(factor == "OI nearby", "open interest", factor)
-  )
-
 caption <- "This table shows the average pairwise correlation amongst factor picks for each factor and period independently.
@@
 
-table <- kbl(
-    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
-  ) %>%
+table <- get_table(tables, "average correlations (amongst factor picks)") %>%
+  dplyr::mutate( factor = as.character(factor), factor = ifelse(factor == "OI nearby", "open interest", factor)) %>% 
+  kbl(longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 ```{r co-movement-time-reg-picks-facts-picks}
-table <- dplyr::filter(
-  tables, 
-  analysis == "regressions - time series - factor picks ~ factors from picks"
-) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::mutate(
-    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
-    dplyr::across(
-      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
-    )
-  )
-
 caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the various sets of factor picks are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the picks.
@@
 
-table <- kbl(
-    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
-  ) %>%
+table <- get_table(tables, "regressions - time series - factor picks ~ factors from picks") %>% 
+  kbl(longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 ```{r co-movement-time-reg-US-facts-picks}
-table <- dplyr::filter(
-  tables, 
-  analysis == "regressions - time series - US commodities ~ factors from picks"
-) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::mutate(
-    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
-    dplyr::across(
-      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
-    )
-  )
-
 caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities.
@@
 
-table <- kbl(
-    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
-  ) %>%
+table <- get_table(tables, "regressions - time series - US commodities ~ factors from picks") %>% 
+  kbl(longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 
-if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
-   kable_classic(
-     table, font_size = tables_font_size,
-     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
-   )
-}
+show_table(output_type, table)
 ```
@@
 ```{r co-movement-time-reg-UK-facts-picks}
-table <- dplyr::filter(
-  tables, 
-  analysis == "regressions - time series - UK metals ~ factors from picks"
-) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::mutate(
-    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
-    dplyr::across(
-      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
-    )
-  )
-
 caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the six UK metals are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the six UK metals.
@@
 
-table <- kbl(
-    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
-  ) %>%
+table <- get_table(tables, "regressions - time series - UK metals ~ factors from picks") %>% 
+  kbl(longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
   column_spec(1L, bold = TRUE) %>%

### 2022-04-27 docs/paper.tex
update paper

@@
 \usepackage{lineno} % add
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
 \usepackage{graphicx}
-\usepackage{booktabs} % book-quality tables
 %%%%%%%%%%%%%%%% end my additions to header
@@
 \bibliographystyle{elsarticle-harv}
-\usepackage{longtable}
 \ifxetex
@@
 
-% Pandoc citation processing
-
-% Pandoc header
-\usepackage[width=1\textwidth]{caption}
+% tightlist command for lists without linebreak
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% From pandoc table feature
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+
+% \usepackage[width=1\textwidth]{caption}
+\usepackage[margin=0pt]{caption}
 \usepackage{geometry}
@@
 \begin{document}
+
 \begin{frontmatter}
@@
 Financialisation appears to have affected multiple economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres.
-A vigorous legislative debate has led to regulatory changes accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors\footnote{See section \ref{co-movement-background} for a detailed discussion.}.
-In response to immediate policy concerns, the academic debate was initially framed rather narrowly.
-In this paper we take a fundamentally different empirical approach that is broader in scope.
+A vigorous legislative debate accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors\footnote{See section \ref{co-movement-background} for a detailed discussion.} eventually led to regulatory changes in several individual markets.\\
+In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation--the burning issue of the day--at the individual commodity market level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
+With the benefit of hindsight, this approach seems to lack a fundamental understanding of the phenomenon it endeavoured to study and which consequences it attempted to address.\\
+Financialisation was a phenomenon global in nature; through the channel of index investment it swayed the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
+Focusing on individual markets in this context thus seems incomprehensive.
+The mechanical approach similarly seems amiss both in form and substance.
+Most of the studies underpinning the regulatory response to financialisation took the form of pairwise correlation, causation and to some extent co-integration analysis, all of which are idiosyncratic in nature for they study single pairs of individual commodity assets.
+Besides, some of these techniques since proved controversial and seem to produce results the quality of which may fall short of the standards that may reasonably be expected to lay the ground for legislative action.
+In substance, leaving the idiosyncrasy issue aside, a case could be made for the mechanical approach under the assumption that financialised commodity markets can be described, ceteris paribus, as their prior or legacy state with increased uninformed financial participation.
+The aforementioned technique(s) could thence be used to observe potential changes in pricing dynamics, for example, which origin could be naturally attributed to the market behaviour of the new comers.
+Although appealing, for it comes with the promise of prompt ``significant'' results, this assumption depicts an incomplete picture for it misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure (Hicks, 1939; Keynes, 1930).\\
+While essential to the understanding of the phenomenon, the global nature of financialisation and its impact on market fundamentals therefore appear to have been originally overlooked and another approach, perhaps more refined, seems warranted.
+
+\medskip\setlength{\parindent}{0pt}
+
+We strive to provide one in this study by taking a fundamentally different empirical perspective that is broader in scope.
 We consider the entire cross-section of actively traded commodities on futures markets and use a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations.\\
-Commodity futures markets have a history of being the classic physical commodity price risk shifting conduit for commodity specialists, and financialisation may have altered this long-standing paradigm with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants.
-This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of market participation.
-Factor model techniques are well suited to isolating common driving factors and detecting co-movement; building on theory we therefore develop a bespoke commodity-based asset pricing framework that seems well adapted to study these two issues simultaneously.
-It is comprised of factor models based both on fundamentals as well as liquidity considerations.
+The global nature of financialisation makes cross-sectional co-movement a cornerstone issue that the direct impact of increased market participation alone might not be able to fully explain for it potentially had deeper effects, for example on market fundamentals as our results suggest.
+Commodity futures markets have a history of being the classic physical commodity price risk shifting conduit for commodity specialists.
+Over the financialisation period we observe a decrease in effectiveness of commercial hedging pressure (CHP) at explaining commodity futures returns at the individual level accompanied by a more pronounced increase at the aggregate level.
+We further note an overall shift in the nature of hedger's behaviour away from the traditional Keynesian view of risk transfer with higher individual risk premiums over phases of cross-sectional contango as opposed to backwardation.
+Both patterns suggest that the phenomenon may have altered this long-standing paradigm of commercial risk transfer with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants.
+This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of market participation.\\
+Factor model techniques are well suited to isolating common driving factors and detecting co-movement (Asness and Frazzini, 2013; Asness et al., 2015, 2019; Carhart, 1997; Fama and French, 2015, 1993; Frazzini and Pedersen, 2014; Hou et al., 2015) at a broader level, beyond individual pairs of assets, and are commonly used to study commodity market fundamentals (Bakshi et al., 2019; Boons and Prado, 2019; Cortazar et al., 2013; Daskalaki et al., 2014; Fernandez-Perez et al., 2018; Gorton et al., 2012; Miffre and Rallis, 2007; Sakkas and Tessaromatis, 2020; Schwartz and Smith, 2000; Szymanowska et al., 2014; Yang, 2013); they consequently seem well adapted to study these two issues simultaneously.
+Building on theory we therefore develop a bespoke commodity-based asset pricing framework comprised of factor models based both on fundamentals as well as liquidity considerations.\\
 One of these is based on the Keynes-Hicks (Hicks, 1946, 1939; Keynes, 1930, 1923) risk transfer approach to the term structure; the corresponding ``theory of normal backwardation'', complemented for the possibility of contango (Cootner, 1960; H.
@@
 
-\bigskip
-\setlength{\parindent}{0pt}
+\bigskip\bigskip\setlength{\parindent}{0pt}
 
 We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008\footnote{Starting point based on earlier studies (Baker, 2014; Christoffersen et al., 2014).}); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).\\
-Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.\\
+Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.
+
+\medskip\setlength{\parindent}{0pt}
+
 The cross-sectional nature of financialisation (Basak and Pavlova, 2016; Cheng and Xiong, 2014) leads us to extend the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in Hong and Yogo (2012).
@@
 This change in pattern suggests the onset of financialisation altered the traditional risk shifting nature of hedger's behaviour, implied by the Keynesian hypothesis.\\
-The arrival of financial investors, on the other hand, raises the question of whether they functioned as liquidity providers or demanders.
+This change of paradigm due to the arrival of financial investors, on the other hand, raises the question of whether they functioned as liquidity providers or demanders.
 Arguments have been put forward in favour of both possibilities with Moskowitz et al.
@@
 (2020) taking the opposite stance.
-Our analysis of returns in periods of low and high \textbf{CHP} before and during financialisation allows us to analyse this issue from a new perspective and suggests that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.\\
+Our analysis of individual commodity returns' relation with both CHP and \textbf{CHP} before and during financialisation sheds new lights on this issue with our results suggesting that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
+
+\medskip\setlength{\parindent}{0pt}
+
 Goldstein et al.
@@
 We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period\footnote{See section \ref{co-movement-methods} for further details.} and evaluating its performance on these selected commodities as well as on all US traded commodities.
-The results of this exercise provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.\\
+The results of this exercise provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
+
+\medskip\setlength{\parindent}{0pt}
+
 The UK traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialisation.
 To that end, we examine the performance of the four factors on the six UK metals, when constructed from each set of factor picks.
-The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.\\
+The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.
+
+\medskip\setlength{\parindent}{0pt}
+
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes.
@@
 
-\bigskip
+\bigskip\bigskip\setlength{\parindent}{0pt}
 
 Financialisation was an issue of such policy importance that it triggered legislative action.
-The debate was initially framed around adequacy of speculation, the burning issue of the day, and the ensuing academic analysis focused on the more mechanical effects of financialisation.
+The debate was initially framed around adequacy of speculation, the burning issue of the day, and the ensuing academic analysis focused on the more mechanical effects of financialisation.\\
 With the benefit of hindsight, it appears this approach was perhaps too narrow, and it now seems necessary to address the phenomenon from a broader perspective.
-Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggered a process of ``definancialisaion'' in global commodity futures markets.
+Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggered a process of ``definancialisaion'' in global commodity futures markets.\\
 The initial view of financialisation was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity futures prices\footnote{Masters (2008); Masters and White (2008); UNCTAD and Cooperation (2009); De Schutter (2010); Gilbert (2010a); Gilbert (2010b); Herman et al.
@@
 
-\cleardoublepage
+\newpage
 
@@
 Popular commodity indexes whose goal was to track the broad movement of commodity prices became accessible by means of swaps, exchange traded funds and exchange traded notes and attracted at least \$100 billion of net super-hoc investment over the 1998-2008 period.
+
+\medskip\setlength{\parindent}{0pt}
+
 Concerns over the consequences of this financialisation phenomenon eventually led to legislative changes including the approval of Rule 76 FR 4752 issued by the US Commodity Futures Trading Commission (CFTC) on January 26\textsuperscript{th}, 2011.
@@
 The Rule was approved in a close 3-2 vote and the ensuing rule-making process was extremely contentious with several commissioners (Michael Dunn and Scott D.
-O'Malia in particular) expressing reservations about the lack of supporting evidence and the Rule also triggering thousands of comment letters as well as a lawsuit against the CFTC spearheaded by two Wall Street trade groups, the International Swaps \& Derivatives Association (ISDA) and the Securities Industries \& Financial Markets Association (SIFMA)\footnote{ISDA \& SIFMA v US CFTC; Complaint, 1:11-cv-02146; December 2\textsuperscript{nd}, 2011.}.\\
+O'Malia in particular) expressing reservations about the lack of supporting evidence and the Rule also triggering thousands of comment letters as well as a lawsuit against the CFTC spearheaded by two Wall Street trade groups, the International Swaps \& Derivatives Association (ISDA) and the Securities Industries \& Financial Markets Association (SIFMA)\footnote{ISDA \& SIFMA v US CFTC; Complaint, 1:11-cv-02146; December 2\textsuperscript{nd}, 2011.}.
+
+\medskip\setlength{\parindent}{0pt}
+
 A world-wide debate ensued about the role of index funds in commodity markets.
-The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs (De Schutter, 2010; Gilbert, 2010b; Herman et al., 2011; Schumann, 2011; UNCTAD and Cooperation, 2009).
+The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs (De Schutter, 2010; Gilbert, 2010b; Herman et al., 2011; Schumann, 2011; UNCTAD and Cooperation, 2009).\\
 Early US Senate investigations on the matter drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US agricultural and energy markets to the observed surges in both futures and cash prices (Masters, 2008; Masters and White, 2008).
-This contention has since come to be known as the Masters' hypothesis and was largely endorsed by the final US Senate report on the issue (Senate, 2009).
+This contention has since come to be known as the Masters' hypothesis and was largely endorsed by the final US Senate report on the issue (Senate, 2009).\\
 At this stage, the question thrust on the academic sphere was whether ``excessive speculation'' (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices.
@@
 Commodity index swaps, commodity index funds (CIFs), commodity-based exchange traded funds (ETFs) and notes (ETNs) or commodity linked notes (CLNs) were amongst the main investment vehicles that allowed institutional and retail investors to build up commodity exposure in the early 2000s (Boons et al., 2012; Henderson et al., 2015; Irwin and Sanders, 2011; Schumann, 2011; UNCTAD and Cooperation, 2009).
-Most of these products were primarily designed to track prominent commodity indexes among which the S\&P-GSCI, the most popular.
+Most of these products were primarily designed to track prominent commodity indexes among which the S\&P-GSCI, the most popular.\\
 Most of its constituents at the time of writing form the basis of the broad cross-section of commodities that we consider in this study: corn-\#2 yellow (XCBT), oats (XCBT), soybean meal (XCBT), soybean oil (XCBT), soybeans (XCBT), wheat-SRW (XCBT), cattle-feeder (XCME), cattle-live (XCME), lean hogs (XCME), cocoa (IFUS), coffee-C (IFUS), cotton-\#2 (IFUS), lumber (XCME), orange juice (IFUS), sugar-\#11 (IFUS), natural gas (XNYM), crude oil-WTI (XNYM), gasoline (XNYM), heating oil (XNYM), copper (XCEC), gold (XCEC), palladium (XNYM), platinum (XNYM) and silver (XCEC).
 Unleaded gasoline, the NYMEX legacy contract for gasoline, stopped trading in 2006 when it was replaced by Reformulated Gasoline Blendstock for Oxygen Blending (RBOB) with the two futures series trading alongside for most of the year.
-For our NYMEX gasoline data series, we consider unleaded gasoline up to September 1\textsuperscript{st}, 2006 and RBOB gasoline thereafter, date at which liquidity for the latter overtook that for the former.
-We also consider the UK metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).\\
+For our NYMEX gasoline data series, we consider unleaded gasoline up to September 1\textsuperscript{st}, 2006 and RBOB gasoline thereafter, date at which liquidity for the latter overtook that for the former.\\
+We also consider the UK metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).
+
+\medskip\setlength{\parindent}{0pt}
+
 The commodity futures trading commission (CFTC) operates a comprehensive system of collecting information on market participants known as the large trader reporting program (LTRP) where it records and reports to the public position data on market participants who have position levels in excess of a particular market specific threshold\footnote{Current reporting level thresholds available at: \href{https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=\&SID=970471b8455f4bab7db4110cfde50731\&mc=true\&r=SECTION\&n=se17.1.15_103}{www.ecfr.gov}.}.
@@
 Besides, these new market participants tend to exhibit herding like behaviour, often taking massive long-only positions on the whole cross-section of indexed commodities in an attempt to enhance returns while hedging against inflation and reaping further diversification benefits for portfolios with, in most cases, existing large positions across various asset classes (Boyd et al., 2016; Brunetti et al., 2016; Cheng et al., 2014; Juvenal and Petrella, 2015; Singleton, 2013; Tang and Xiong, 2012).
-This contrasts with the traditional approaches of Keynes and Working and in this context the issues of co-movement and aggregate market participants behaviour seem particularly relevant.\\
+This contrasts with the traditional approaches of Keynes and Working and in this context the issues of co-movement and aggregate market participants behaviour seem particularly relevant.
+
+\medskip\setlength{\parindent}{0pt}
+
 Asset pricing techniques are well suited to study co-movement.
@@
 Using the weekly price, open interest and market position data described above we construct market portfolios of individual commodity nearby futures as well as mimicking portfolios for market, commercial hedging pressure, term structure and liquidity risk factors in returns.
-While our market portfolios are long only, equally weighted portfolios of particular commodity sets, our other mimicking portfolios for risk factors are constructed as combinations of two sub-portfolios (legs), one held long, one held short, which respective constituents are pooled on a weekly basis according to risk factor specific criteria.
-For each leg, the position weight for a particular asset for a particular week is contingent on the value of the corresponding sorting variable and its rank relative to the other assets in the pool.
+While our market portfolios are long only, equally weighted portfolios of particular commodity sets, our other mimicking portfolios for risk factors are constructed as combinations of two sub-portfolios (legs), one held long, one held short, which respective constituents are pooled on a weekly basis according to risk factor specific criteria.\\
+For each leg, the position weight for a particular asset for a particular period is contingent on the value of the corresponding sorting variable and its rank relative to the other assets in the pool.
 The sorting variable values for the asset pool are first rescaled so that the highest (lowest) value becomes 1 (0).
@@
 The operation is repeated for the pair of assets showing the second highest and second lowest values for the sorting variable and so on until all the assets in the pool are attributed a score.
-The individual asset weights are then determined by dividing each score by the sum of the scores.
-The weekly return for a particular mimicking portfolio is calculated as the difference between the weighted average return for constituents of the long portfolio and that for the constituents of the short portfolio.
-i.e, return on the mimicking portfolio for risk factor \(i\) (\(f_{i}\)) for week \(t\):
+The individual asset weights are then determined by dividing each score by the sum of the scores.\\
+The period return for a particular mimicking portfolio is calculated as the difference between the weighted average return for constituents of the long portfolio and that for the constituents of the short portfolio.
+i.e, return on the mimicking portfolio for risk factor \(i\) (\(f_{i}\)) for period \(t\):
 
@@
 \(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
-\(w^{*}_{j,t}\equiv\) week \(t\) weight for commodity \(j\) on the long or short leg.\\
-\(r_{j,t}\equiv\) week \(t\) front contract return for commodity \(j\).\\
+\(w^{*}_{j,t}\equiv\) period \(t\) weight for commodity \(j\) on the long or short leg.\\
+\(r_{j,t}\equiv\) period \(t\) front contract return for commodity \(j\).\\
 \(j\equiv\) commodity rank in the ordered set \(Y_{t}^{f_{i}}\).\\
-\(Y_{t}^{f_{i}}\equiv\) week \(t\) ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is specific to \(f_{i}\).
-
-\bigskip
+\(Y_{t}^{f_{i}}\equiv\) period \(t\) ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is specific to \(f_{i}\).
+
+\medskip\setlength{\parindent}{0pt}
 
@@
 \(\overline{CHP_{j}}=\frac{1}{26}\sum_{k=0}^{25}\frac{L_{j,t-k}}{L_{j,t-k}+S_{j,t-k}}\)\\
-\(L_{j,t}\equiv\) number of long positions held by commercial hedgers for week \(t\) on the futures series of commodity \(j\).\\
-\(S_{j,t}\equiv\) number of short positions held by commercial hedgers for week \(t\) on the futures series of commodity \(j\).
-
-\bigskip
+\(L_{j,t}\equiv\) number of long positions held by commercial hedgers for period \(t\) on the futures series of commodity \(j\).\\
+\(S_{j,t}\equiv\) number of short positions held by commercial hedgers for period \(t\) on the futures series of commodity \(j\).
+
+\medskip\setlength{\parindent}{0pt}
 
@@
 \(\overline{RY_{j}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{F_{j,t-k}^{1}}{F_{j,t-k}^{2}} - 1)\)\\
-\(F_{j,t}^{1}\equiv\) week \(t\) close price for commodity \(j\) first nearby futures contract.\\
-\(F_{j,t}^{2}\equiv\) week \(t\) close price for commodity \(j\) second nearby futures contract.
-
-\bigskip
+\(F_{j,t}^{1}\equiv\) period \(t\) close price for commodity \(j\) first nearby futures contract.\\
+\(F_{j,t}^{2}\equiv\) period \(t\) close price for commodity \(j\) second nearby futures contract.
+
+\medskip\setlength{\parindent}{0pt}
 
@@
 \(\overline{{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{{OI}_{j,t-k}}{{OI}_{j,t-k-1}} - 1)\)\\
-\(OI_{j,t}\equiv\) open interest at close of week \(t\) on the front (nearby) contract for commodity \(j\).
-
-\bigskip
+\(OI_{j,t}\equiv\) open interest at close of period \(t\) on the front (nearby) contract for commodity \(j\).
+
+\medskip\setlength{\parindent}{0pt}
 
@@
 The same operation is repeated for the two (\(p=2\)) and three (\(p=3\)) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectively, as well as for the four (\(p=4\)) factor model case where all the risk factor mimicking portfolios are included.
-Results are reported for the one-factor model case with the other results available on the \href{http://18.135.131.217:3838/financialization-asset-pricing/}{online results dashboard}.\\
+Results are reported for the one-factor model case with the other results available on the \href{http://18.135.131.217:3838/financialization-asset-pricing/}{online results dashboard}.
+
+\medskip\setlength{\parindent}{0pt}
+
 For each period we also implement the analysis described above over periods of low and high aggregate CHP (\textbf{CHP}), a notion that we believe is particularly relevant in the context of financialisation where issues of co-movement and aggregate market behaviour play a central role.
 We define \textbf{CHP} as the cross-sectional average of CHPs for a particular pool of assets.
-i.e., Week \(t\) \textbf{CHP} for asset pool \(x\):
+i.e., period \(t\) \textbf{CHP} for asset pool \(x\):
 
@@
 \(n\equiv\) number of commodities in set \(x\).\\
-\(CHP_{i,t}\equiv\) week \(t\) CHP for commodity \(i\) as defined above.
-
-\bigskip
-
-We further define aggregate backwardation (\textbf{backwardation}) and contango (\textbf{contango}) \textbf{CHP} regimes as, for a given period, \textbf{CHP} levels below and above the period's median respectively and, in contrast with (Hong and Yogo, 2012) who aggregate across sub-sectors, the asset pool we consider for \textbf{CHP} construction include the whole cross-section of US traded commodities.\\
+\(CHP_{i,t}\equiv\) period \(t\) CHP for commodity \(i\) as defined above.
+
+\medskip\setlength{\parindent}{0pt}
+
+We further define aggregate backwardation (\textbf{backwardation}) and contango (\textbf{contango}) \textbf{CHP} regimes as, for a given period, \textbf{CHP} levels below and above the period's median respectively and, in contrast with (Hong and Yogo, 2012) who aggregate across sub-sectors, the asset pool we consider for \textbf{CHP} construction include the whole cross-section of US traded commodities.
+
+\medskip\setlength{\parindent}{0pt}
+
 In the next part of the analysis, our mimicking portfolios for risk factors, constructed from the set of all US traded commodities are used as commodity picking devices on the latter commodity set.
@@
 
-\bigskip
-
-For each period we report the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every set of picks.\\
+\medskip\setlength{\parindent}{0pt}
+
+For each period we report the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every set of picks.
+
+\medskip\setlength{\parindent}{0pt}
+
 In the last part of the analysis, for each period our mimicking portfolios for risk factors in returns are constructed using each set of commodity picks independently as the asset pool for portfolio construction.
@@
 
-The descriptive statistics over the various time periods for our two sets of commodities (US and non-US) are shown in table \ref{tab:co-movement-stats-no-regimes}.
+The descriptive statistics for the commodity series considered in the study displayed in table \ref{tab:co-movement-stats-no-regimes} show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9\% significant at the 5\% level vs.~6.9\% with a 10\% significance in the pre-financialisation period.
+The increase is even more pronounced for an equally weighted portfolio of UK traded assets (metals), 2.47\% (not significant) to 21.8\% (significant at the 10\% level), which sets out the global nature of the phenomenon.
+Most commodities show a higher mean return while five--Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)--show a lower figure with five significant figures--Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)--against none pre-financialisation.
+Sugar-\#11 wins the race with a mean return increasing from -4.6\% to 24.9\% followed by copper with sizeable increases for both markets: 1.5\% to 28.2\% (XCEC) and 0.5\% to 28.6\% (XLME).\\
+The pattern of results for volatilities is similar although the increase is less pronounced.
+Both equally weighted portfolios shows an increase, more pronounced for the UK assets, 10\% to 13.6\% (US) vs.~15.7\% to 26.9\% (UK), while out of the thirty assets, eleven show a drop in volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C (IFUS), Lumber (XCME), Sugar-\#11 (IFUS), Natural gas (XNYM), Crude oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
+Financialisation seems however to have impacted the commodity complex beyond these mechanical effects of increased long participation ensuing from the entry on index type investments as our results suggest next.
+
+\medskip\setlength{\parindent}{0pt}
+
+The cross-sectional nature of financialisation naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure.
 The traditional Keynesian hedging pressure paradigm postulates a negative relationship between the return on an individual commodity futures and its hedging pressure.
-Financialisation has been seen as a cross-sectional commodity market phenomenon; this naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure.
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where \textbf{CHP} is low and vice et versa.
-
-In table \ref{tab:co-movement-stats-regimes} the mean returns are shown over high (\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP} regimes for each time period.
+In table \ref{tab:co-movement-stats-regimes} the mean returns are shown over high (\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP} regimes for each time period.\\
 Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of \textbf{backwardation} as compared to \textbf{contango}, with the difference being statistically significant at the 10\% level for two commodities, at the 5\% level for one and at the 1\% level for another.
@@
 The equally weighted US portfolio had a mean return of 15.7\% over \textbf{backwardation} against 16.2\% during phases of \textbf{contango}, both statistically significant at the 10\% level.
-The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 8\% during \textbf{backwardation} rising to 35.6\% during \textbf{contango}.\\
-The onset of financialisation thus seems to have engendered a change in the nature of hedger's behaviour in the aggregate, taking it away from the traditional Keynesian view of risk shifting.
-This phenomenon has been noted in earlier theoretical and empirical work (Danthine, 1978; Stout, 1998) in different contexts from which two competing models of behaviour have emerged.
+The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 8\% during \textbf{backwardation} rising to 35.6\% during \textbf{contango}.
+
+\medskip\setlength{\parindent}{0pt}
+
+The onset of financialisation thus seems to have engendered a change in the nature of hedger's behaviour, at the aggregate level in particular, taking it away from the traditional Keynesian view of risk shifting.
+This phenomenon has been noted in earlier theoretical and empirical work (Danthine, 1978; Stout, 1998) in different contexts from which two competing models of behaviour have emerged.\\
 The information arbitrage model (Danthine, 1978; Grossman and Stiglitz, 1980; Kyle, 1989) implies that hedgers may often be seeking out counterparties to trade with rather than being purely passive.
@@
 In fact, by hedging away some of their risk, hedgers are able to speculate more heavily based on their disagreement against speculators regarding futures price movement (Simsek, 2013), which fits into a heterogeneous expectation theory of speculation\footnote{Hirshleifer (1975); Hirshleifer (1976); Hirshleifer (1977)}.
-As Stout (1998) points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves speculation as this form of trading is regarded as non-productive\footnote{Duffie (2014) also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.}.
+As Stout (1998) points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves speculation as this form of trading is regarded as non-productive\footnote{Duffie (2014) also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.}.\\
 In the second model hedgers are seen as liquidity providers as in Kang et al.
 (2020) with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
-Table \ref{tab:co-movement-time-reg-US-CHP-US} supports this view.
+Table \ref{tab:co-movement-time-reg-US-CHP} supports this view.
 We regress commodity futures front returns on individual commercial hedging pressure (CHP) as well as aggregate CHP (\textbf{CHP}), our market wide measure of CHP, in separate models and find that the explanatory power of CHP at the individual commodity level decreases over the financialisation period with the US cross-sectional average \(R^{2}\) falling down to 20.8\% from 25.8\% in the previous period while that of \textbf{CHP} increases (7.1\% vs 5.4\%).
@@
 
-The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \ref{tab:co-movement-time-reg-US-facts-US}.
+\bigskip\bigskip\setlength{\parindent}{0pt}
+
+Using our bespoke commodity-based asset pricing framework we strive to shed new lights on the phenomenon by first regressing returns series for the twenty four individual US commodities against our factor mimicking portfolios independently.
+The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \ref{tab:co-movement-time-reg-US-facts-US}.\\
 Over the first period the market factor has the best average time series performance with the highest average \(R^{2}\) with all three futures market factors performing poorly and the overall performance consistent across periods of high and low \textbf{CHP} (below period median).
-The two factor models average \(R^{2}\)s (results available on the \href{http://18.135.131.217:3838/financialization-asset-pricing/}{online results dashboard}) are roughly the sum of the one factor \(R^{2}\)s indicating that the factors are almost orthogonal over this period.
+The two factor models average \(R^{2}\)s (results available on the \href{http://18.135.131.217:3838/financialization-asset-pricing/}{online results dashboard}) are roughly the sum of the one factor \(R^{2}\)s indicating that the factors are almost orthogonal over this period.\\
 The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average \(R^{2}\) increasing to 8.2\% in the second period relative to 1.7\% in the first with this improvement coming from the long leg that shows a greater improvement (4.5\% to 15.1\%) relative to the short (3\% to 4\%) bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period.
@@
 
-We next investigate the top eight of the US traded commodities which achieved the highest time series \(R^{2}\) for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \ref{tab:co-movement-picks}.
+\medskip\setlength{\parindent}{0pt}
+
+We next investigate the top eight of the US traded commodities which achieved the highest time series \(R^{2}\) for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \ref{tab:co-movement-picks}.\\
 For the CHP factor the commodities that achieve high \(R^{2}\) in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor.
-The same applies to the open interest and term structure factors with CHP replaced by open interest growth and roll yield respectively; while for the market factor the picks are those that co-vary most strongly with the market factor over that period.
+The same applies to the open interest and term structure factors with CHP replaced by open interest growth and roll yield respectively; while for the market factor the picks are those that co-vary most strongly with the market factor over that period.\\
 For the CHP factor, we observe a change in the picks between the first and the second period; the picks in the first period included five agricultural commodities and three metals while in the second period they include all the five base and precious metals and only three agricultural commodities.
 This pattern is also visible for the term structure factor for which there are four metals (copper, silver, gold and platinum) picks in the second period against two in the first (palladium and platinum) as well as for the open interest nearby growth factor for which there are three metals (silver, gold and platinum) picks in the second period against one in the first (platinum).
-The market factor has three metal picks in the second period (palladium, gold and silver) while all the picks in the first period were agricultural or energy commodities.
-Over the third period, the average CHP factor shows the same metal picks with the agriculturals replaced by energy commodity; the open interest nearby growth factor still has three metal picks with gold swapped for copper and both the market and term structure factors have one, copper.
+The market factor has three metal picks in the second period (palladium, gold and silver) while all the picks in the first period were agricultural or energy commodities.\\
+Over the third period, the average CHP factor shows the same metal picks with the agriculturals replaced by energy commodity; the open interest nearby growth factor still has three metal picks with gold swapped for copper and both the market and term structure factors have one, copper.\\
 The table also shows the proportion of time that these picks were constituents of the corresponding factor.
@@
 
+\medskip\setlength{\parindent}{0pt}
+
 In table \ref{tab:co-movement-correlations}, we show the average pairwise returns correlation between each set of picks in each time period.
-This exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.
+This exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.\\
 In the first period the average picks pairwise correlation for the long-short factors ranges from 7.1\% (term structure factor picks) to 12.4\% (open interest factor picks) while the market factor picks show the highest figure (23.7\%).
@@
 The higher figures for the open interest factor are driven by the strong presence of the energy complex amongst the corresponding picks.
-The latter exhibits much higher average pairwise correlations than the other sectors in both periods although lower in the second relative to the first which reinforces to role played by the metals in the sharp increase in average pairwise correlation amongst picks for this factor.
+The latter exhibits much higher average pairwise correlations than the other sectors in both periods although lower in the second relative to the first which reinforces the role played by the metals in the sharp increase in average pairwise correlation amongst picks for this factor.\\
 With regards to \textbf{CHP} regimes, although not very pronounced, a pattern is noticeable.
@@
 
+\medskip\setlength{\parindent}{0pt}
+
 To further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their explanatory performance on these sets of picks over the four periods independently.
@@
 The long-short factors for a particular attribute select the top and bottom two of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks.
-In the absence of price co-movement between the picks, this market factor will achieve an average \(R^{2}\) of around 12.5\%\footnote{Market factor lemma: \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\) size of market portfolio (eight here).}, while there is no non-zero \(R^{2}\) lower bound for the corresponding long-short factors.
+In the absence of price co-movement between the picks, the market factor will achieve an average \(R^{2}\) of around 12.5\%\footnote{Market factor lemma: \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\) size of market portfolio (eight here).}, while there is no non-zero \(R^{2}\) lower bound for the corresponding long-short factors.\\
 A high average \(R^{2}\) for the market factor is indicative of strong price co-movement.
@@
 The pattern is reversed for the CHP factor built from the term structure factor picks where the average \(R^{2}\) increases from 4.7\% to 8\% with the performance of the long leg increasing from 11.9\% to 28.1\% vs.~5.5\% to 9.1\% for the short.
-The performance of the term structure factor constructed from its own sets of picks also shows a substantial increase, from 5.1\% to 8.4\% with, here again the increase in performance relatively stronger for the short leg, from 6\% to 16.1\% vs.~7.6\% to 12.1\% for the long.
-Taken together with the previous results showing that the metal complex predominantly loads on the long and short legs of the original CHP and term structure factors respectively, these results provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation.
+The performance of the term structure factor constructed from its own sets of picks also shows a substantial increase, from 5.1\% to 8.4\% with, here again the increase in performance relatively stronger for the short leg, from 6\% to 16.1\% vs.~7.6\% to 12.1\% for the long.\\
+Taken together with the previous results showing that the metal complex predominantly loads on the long and short legs of the original CHP and term structure factors respectively, these results provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation perhaps as a result of spillover effects between the corresponding futures and spot markets as suggested in Basak and Pavlova (2016).
+
+\medskip\setlength{\parindent}{0pt}
 
@@
 The market factor built from the CHP and term structure factor sets of picks shows the sharpest increase in performance, relative to using the other sets of factor picks; rising to 20.1\% from 1.5\% and to 15\% from 0.8\% respectively.
-The increase in \(R^{2}\) for the market factor built with market factor picks is more modest, providing further evidence of concentration of co-movement in the metals sector during financialisation.
+The increase in \(R^{2}\) for the market factor built with market factor picks is more modest, providing further evidence of concentration of co-movement in the metals sector during financialisation.\\
 Here again the change in performance for the CHP and term structure factor legs stands out where the factors are built with their own as well as each other's sets of picks.
@@
 Building these factors from each other's sets of picks produces a similar pattern with the performance of the long leg of the CHP factor built from the term structure factor picks increasing from 0.7\% to 11.4\%; a much greater increase relative to the short leg although in this case the latter also shows a sizable increase in performance (0.3\% to 6\%).
-The performance of the short leg of the term structure factor built from the CHP factor sets of picks on the other hand increases from 0.3\% to 19.2\% while the performance for the long leg in the second period remains below 1.5\%.
+The performance of the short leg of the term structure factor built from the CHP factor sets of picks on the other hand increases from 0.3\% to 19.2\% while the performance for the long leg in the second period remains below 1.5\%.\\
 Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working's term structure paradigms.
@@
 
+\bigskip\bigskip\setlength{\parindent}{0pt}
+
 The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results.
-Returns fall sharply relative to the financialisation period (table \ref{tab:co-movement-stats-no-regimes}.
-with eighteen US commodities along with all six UK traded metals showing lower mean returns.
+Returns fall sharply relative to the financialisation period (table \ref{tab:co-movement-stats-no-regimes}) with eighteen US commodities along with all six UK traded metals showing lower mean returns.
 Returns for equally weighted portfolios of both sets of assets fall down to 9.4\% and 5.3\% from 15.9\% and 21.8\% respectively.
@@
 Volatility is moderately higher for both sets with fifteen US commodities and three UK metals showing higher figures and interestingly eminently higher over phases of \textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none of the UK traded metals show higher volatility figures over \textbf{backwardation} phases.
+The symmetry between the dynamics of CHP and \textbf{CHP}'s explanatory power on individual commodity returns breaks in the crisis period with both now seemingly converging; the US cross-sectional average \(R^{2}\) at the individual level bouncing back up (22.5\% vs 20.8\%) while that at the aggregate level rises further (14.7\% vs 7.1\%).\\
 The performance of the market factor dominates the US commodity complex over the period with a 50\% increase in mean average \(R^{2}\) to over 30\% (table \ref{tab:co-movement-time-reg-US-facts-US}) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
 The average pairwise correlation amongst the market factor picks increases beyond 50\% while there is a leveling in that amongst the picks of the long-short factors as shown in table \ref{tab:co-movement-correlations}.
-Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table \ref{tab:co-movement-time-reg-US-facts-picks}).
+Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table \ref{tab:co-movement-time-reg-US-facts-picks}).\\
 Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
-Table \ref{tab:co-movement-time-reg-UK-facts-picks} provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average \(R^{2}\) increasing to 31.7\% from 10.2\% in the previous period.\\
-The returns pullback continues into the post-crisis period with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2\% and 2.7\% respectively.
+Table \ref{tab:co-movement-time-reg-UK-facts-picks} provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average \(R^{2}\) increasing to 31.7\% from 10.2\% in the previous period.
+
+\medskip\setlength{\parindent}{0pt}
+
+The returns pullback continues into the post-crisis period (table \ref{tab:co-movement-stats-no-regimes}) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2\% and 2.7\% respectively.
 Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
-The figures for the equally weighted portfolios of US and UK assets drop to 9.9\% and 16.2\% respectively, very close to pre-financialisation levels.
-The pattern of reversion toward the pre-financialisation Keynesian paradigm intiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:co-movement-stats-regimes}), more so than over the crisis period with seventeen US commodities showing higher mean returns over \textbf{backwardation} phases.
+The figures for the equally weighted portfolios of US and UK assets drop to 9.9\% and 16.2\% respectively, very close to pre-financialisation levels.\\
+The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (table \ref{tab:co-movement-stats-regimes}) with mean returns higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:co-movement-stats-regimes}), more so than over the crisis period with seventeen US commodities showing higher mean returns over \textbf{backwardation} phases.
 The difference is significant at the 5\% level for Lumber (XCME) and at the 10\% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of \textbf{contango}.
@@
 Over the financialisation period in contrast volatilities were predominantly higher in \textbf{backwardation} for US traded assets with fourteen commodities showing higher volatility figures in these phases; the post-crisis pattern of results for volatilities thus likewise shows signs of reversion to pre-financialisation standards.
+After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and \textbf{CHP} part ways (table \ref{tab:co-movement-time-reg-US-CHP}), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
+The recovery initiated in the crisis period for that of CHP is confirmed with a stronger increase in the post-crisis period, 27.2\% vs.~22.5\%, strongest for the metals sector, 37.3\% vs.~23.7\%, while the energy sector shows the opposite pattern: 11\% vs.~16\%.
+In contrast, after increasing stronger in the crisis, that for \textbf{CHP} falls overall in the post-crisis period, 7.5\% vs 14.7\%, with the decrease strongest for the energy sector in a relative sense: 2.5\% vs.~14.8\%.\\
 Average pairwise correlations amongst factor picks (table \ref{tab:co-movement-correlations}) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1\% to 26.1\%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
@@
 Table \ref{tab:co-movement-time-reg-UK-facts-picks} provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
+
+\medskip\setlength{\parindent}{0pt}
+
 Taken together the patterns of results over the crisis and post-crisis periods echo those in Basu and Bauthéac (2021) in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex, in other words, a process of ``definancialisation''.
 
-\cleardoublepage
+\newpage
 
@@
 The regulatory bottleneck that prevented the large-scale expansion of commodity index investment was no more.} led to large inflows of institutional capital into the commodity futures markets.
-This process known as ``financialisation'' spurred a heated public policy debate about whether the ensuing increase in open interest and trading volume in commodity futures exerted upward pressure on prices.
+This process known as ``financialisation'' spurred a heated public policy debate about whether the ensuing increase in open interest and trading volume in commodity futures exerted upward pressure on prices.\\
 The debate spread to the legislative sphere, with the US senate launching formal investigations, and was thrust onto the academic community as a matter of urgency.
-Perhaps in response to this, most of the early studies focused on the more mechanical effects of financialisation, relying on commodity specific causality and correlation-based analysis.
-The contention eventually triggered legislative action and new position limits were introduced in a number of grains and energy futures markets with substantial potential effects on their functioning and consequently, to a larger extent, on that of the economic system as a whole.
-With the benefit of hindsight, the focus of the debate appears to have been too narrow, and the ensuing regulatory changes might thus have been unwarranted; it therefore seems important to analyse the effects of financialisation from a broader perspective which we do in this study.
-Factor model techniques are well suited to isolating common driving factors and detecting co-movement, a central issue in financialisation which we believe the existing literature has not fully analysed; we thus consider the entire cross-section of actively traded commodities on futures markets and use a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations.
-Our analysis suggests that, beyond energy and agriculturals, financialisation appears to have had a substantial impact on the metals sector at the global level.
+Perhaps in response to this, most of the early studies focused on the more mechanical effects of financialisation in individual markets, relying on commodity specific causality and correlation-based analysis.
+The contention eventually triggered legislative action and new position limits were introduced in a number of grains and energy futures markets.
+
+\medskip\setlength{\parindent}{0pt}
+
+With the benefit of hindsight, this focus appears to have been too narrow.
+As our results suggests, financialisation was a phenomenon global in nature, with cross-sectional effects on market fundamentals and studying the direct effects of increased market participation in single markets thus seems amiss in this context.\\
+The results of our analysis further suggest that financialisation set off an ontological drift in the commodity complex beyond energy and agricultural commodities and in fact strongest for the metals sector at the global level; an aspect largely overlooked in the original approach that we believe the existing literature has not fully analysed.
+The regulatory changes underpinned by these studies may thus have been unwarranted with potential substantial undesired effects on the functioning of the markets in which they were enforced and thence, to a larger extent on that of the economic system as a whole.\\
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in commodity pricing dynamics.
-In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have set off a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of ``definancialisation'' in global commodity futures markets.
-
-\cleardoublepage\newgeometry{left=2.50cm, right=2.50cm, top=2.50cm, bottom=3cm}
+In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have triggered a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of ``definancialisation'' in global commodity futures markets.
+
+\newpage
 
 \hypertarget{tables}{%
-\section*{Tables}\label{tables}}
-\addcontentsline{toc}{section}{Tables}
+\section{Tables}\label{tables}}
 
@@
 \begin{longtable}[t]{>{}lllrrrr}
-\caption{\label{tab:co-movement-time-reg-US-CHP-US}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against relative changes in commercial hedging pressure (CHP) both at the individual (commodity CHP) and aggregate (aggregate CHP) levels independently.
-The results are reported for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).}\\
+\caption{\label{tab:co-movement-time-reg-US-CHP}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \ref{co-movement-methods}.
+Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+The results are discussed in section \ref{co-movement-results}.}\\
 \toprule
@@
 \endlastfoot
- & all & all & 25.79\% & 20.72\% & 22.46\% & 27.17\%\\
-\nopagebreak
- &  & all & 25.19\% & 21.6\% & 23.91\% & 28.12\%\\
+ & all &  & 25.79\% & 20.72\% & 22.46\% & 27.17\%\\
+\nopagebreak
+ & agriculturals &  & 25.19\% & 21.6\% & 23.91\% & 28.12\%\\
+\nopagebreak
+ & energy &  & 25.12\% & 19.45\% & 16\% & 10.96\%\\
+\nopagebreak
+ & metals & \multirow[t]{-4}{*}{\raggedright\arraybackslash all} & 28.12\% & 19.1\% & 23.27\% & 37.32\%\\
 \nopagebreak
@@
 \nopagebreak
- & \multirow[t]{-4}{*}{\raggedright\arraybackslash agriculturals} & softs & 26.68\% & 20.89\% & 27.19\% & 31.88\%\\
-\nopagebreak
- &  & all & 25.12\% & 19.45\% & 16\% & 10.96\%\\
+ & \multirow[t]{-3}{*}{\raggedright\arraybackslash agriculturals} & softs & 26.68\% & 20.89\% & 27.19\% & 31.88\%\\
 \nopagebreak
@@
 \nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash energy} & petroleum & 26.93\% & 20.71\% & 18.87\% & 12.85\%\\
-\nopagebreak
- &  & all & 28.12\% & 19.1\% & 23.27\% & 37.32\%\\
+ & \multirow[t]{-2}{*}{\raggedright\arraybackslash energy} & petroleum & 26.93\% & 20.71\% & 18.87\% & 12.85\%\\
 \nopagebreak
@@
 \nopagebreak
-\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{Δ\% commodity CHP}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash metals} & precious & 23.3\% & 17.41\% & 24.57\% & 37.93\%\\
-\cmidrule{1-7}\pagebreak[0]
- & all & all & 5.37\% & 7.12\% & 14.72\% & 7.49\%\\
-\nopagebreak
- &  & all & 4.91\% & 4.5\% & 12.14\% & 6.23\%\\
+\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{individual CHP}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash metals} & precious & 23.3\% & 17.41\% & 24.57\% & 37.93\%\\
+\cmidrule{1-7}\pagebreak[0]
+ & all &  & 5.37\% & 7.12\% & 14.72\% & 7.49\%\\
+\nopagebreak
+ & agriculturals &  & 4.91\% & 4.5\% & 12.14\% & 6.23\%\\
+\nopagebreak
+ & energy &  & 3.35\% & 6.27\% & 14.83\% & 2.45\%\\
+\nopagebreak
+ & metals & \multirow[t]{-4}{*}{\raggedright\arraybackslash all} & 8.36\% & 15.67\% & 22.37\% & 15.33\%\\
 \nopagebreak
@@
 \nopagebreak
- & \multirow[t]{-4}{*}{\raggedright\arraybackslash agriculturals} & softs & 4.34\% & 5.64\% & 10.35\% & 6.98\%\\
-\nopagebreak
- &  & all & 3.35\% & 6.27\% & 14.83\% & 2.45\%\\
+ & \multirow[t]{-3}{*}{\raggedright\arraybackslash agriculturals} & softs & 4.34\% & 5.64\% & 10.35\% & 6.98\%\\
 \nopagebreak
@@
 \nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash energy} & petroleum & 3.59\% & 7.49\% & 18.9\% & 3.17\%\\
-\nopagebreak
- &  & all & 8.36\% & 15.67\% & 22.37\% & 15.33\%\\
+ & \multirow[t]{-2}{*}{\raggedright\arraybackslash energy} & petroleum & 3.59\% & 7.49\% & 18.9\% & 3.17\%\\
 \nopagebreak
@@
 \nopagebreak
-\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{Δ\% aggregate CHP}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash metals} & precious & 7.92\% & 16.4\% & 21.98\% & 17.25\%\\*
+\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{aggregate CHP}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash metals} & precious & 7.92\% & 16.4\% & 21.98\% & 17.25\%\\*
 \end{longtable}
@@
 
+\leavevmode\hypertarget{ref-asness_devil_2013}{}%
+Asness, C., Frazzini, A., 2013. The devil in hml's details. The Journal of Portfolio Management 39, 49--68.
+
+\leavevmode\hypertarget{ref-asness_fact_2015}{}%
+Asness, C., Frazzini, A., Israel, R., Moskowitz, T., 2015. Fact, fiction, and value investing. The Journal of Portfolio Management 42, 34--52.
+
+\leavevmode\hypertarget{ref-asness_quality_2019}{}%
+Asness, C.S., Frazzini, A., Pedersen, L.H., 2019. Quality minus junk. Review of Accounting Studies 24, 34--112.
+
 \leavevmode\hypertarget{ref-baker_financialisation_2014}{}%
@@
 
+\leavevmode\hypertarget{ref-bakshi_understanding_2019}{}%
+Bakshi, G., Gao, X., Rossi, A.G., 2019. Understanding the sources of risk underlying the cross section of commodity returns. Management Science 65, 619--641.
+
 \leavevmode\hypertarget{ref-basak_model_2016}{}%
@@
 
+\leavevmode\hypertarget{ref-boons_basis_2019}{}%
+Boons, M., Prado, M.P., 2019. Basis-momentum. The Journal of Finance 74, 239--279.
+
 \leavevmode\hypertarget{ref-boyd_prevalence_2016}{}%
@@
 
+\leavevmode\hypertarget{ref-carhart_persistence_1997}{}%
+Carhart, M.M., 1997. On persistence in mutual fund performance. The Journal of finance 52, 57--82.
+
 \leavevmode\hypertarget{ref-cheng_convective_2014}{}%
@@
 
+\leavevmode\hypertarget{ref-cortazar_commodity_2013}{}%
+Cortazar, G., Kovacevic, I., Schwartz, E.S., 2013. Commodity and asset pricing models: An integration (NBER Working Papers No. 19167). National Bureau of Economic Research, Inc.
+
 \leavevmode\hypertarget{ref-danthine_information_1978}{}%
 Danthine, J.-P., 1978. Information, futures prices, and stabilizing speculation. Journal of Economic Theory 17, 79--98.
+
+\leavevmode\hypertarget{ref-daskalaki_factors_2014}{}%
+Daskalaki, C., Kostakis, A., Skiadopoulos, G., 2014. Are there common factors in individual commodity futures returns? Journal of Banking \& Finance 40, 346--363.
 
@@
 
+\leavevmode\hypertarget{ref-fama_common_1993}{}%
+Fama, E.F., French, K.R., 1993. Common risk factors in the returns on stocks and bonds. Journal of Financial Economics 33, 3--56.
+
+\leavevmode\hypertarget{ref-fama_five_factor_2015}{}%
+Fama, E.F., French, K.R., 2015. A five-factor asset pricing model. Journal of Financial Economics 116, 1--22.
+
 \leavevmode\hypertarget{ref-fattouh_role_2013}{}%
@@
 
+\leavevmode\hypertarget{ref-fernandez_skewness_2018}{}%
+Fernandez-Perez, A., Frijns, B., Fuertes, A.-M., Miffre, J., 2018. The skewness of commodity futures returns. Journal of Banking \& Finance 86, 143--158.
+
+\leavevmode\hypertarget{ref-frazzini_betting_2014}{}%
+Frazzini, A., Pedersen, L.H., 2014. Betting against beta. Journal of Financial Economics 111, 1--25.
+
 \leavevmode\hypertarget{ref-fuertes_commodity_2015}{}%
@@
 Goldstein, I., Yang, L., 2017. Commodity financialization and information transmission (SSRN Scholarly Paper No. ID 2555996). Social Science Research Network, Rochester, NY.
+
+\leavevmode\hypertarget{ref-gorton_fundamentals_2012}{}%
+Gorton, G.B., Hayashi, F., Rouwenhorst, K.G., 2012. The fundamentals of commodity futures returns. Review of Finance 17, 35--105.
 
@@
 
+\leavevmode\hypertarget{ref-hou_digesting_2015}{}%
+Hou, K., Xue, C., Zhang, L., 2015. Digesting anomalies: An investment approach. The Review of Financial Studies 28, 650--705.
+
 \leavevmode\hypertarget{ref-houthakker_restatement_1957}{}%
@@
 \leavevmode\hypertarget{ref-irwin_commodity_2013}{}%
-Irwin, S.H., 2013. Commodity index investment and food prices: Does the ``masters hypothesis'' explain recent price spikes? Agricultural Economics 44, 29--41.
+Irwin, S.H., 2013. Commodity index investment and food prices: Does the "masters hypothesis" explain recent price spikes? Agricultural Economics 44, 29--41.
 
@@
 
+\leavevmode\hypertarget{ref-miffre_momentum_2007}{}%
+Miffre, J., Rallis, G., 2007. Momentum strategies in commodity futures markets. Journal of Banking \& Finance 31, 1863--1886.
+
 \leavevmode\hypertarget{ref-moskowitz_time_2012}{}%
@@
 
+\leavevmode\hypertarget{ref-sakkas_factor_2020}{}%
+Sakkas, A., Tessaromatis, N., 2020. Factor based commodity investing. Journal of Banking \& Finance 115, 105807.
+
 \leavevmode\hypertarget{ref-sanders_impact_2011}{}%
@@
 
+\leavevmode\hypertarget{ref-schwartz_short_2000}{}%
+Schwartz, E., Smith, J.E., 2000. Short-term variations and long-term dynamics in commodity prices. Management Science 46, 893--911.
+
 \leavevmode\hypertarget{ref-senate_excessive_2009}{}%
@@
 \leavevmode\hypertarget{ref-tokic_speculation_2012}{}%
-Tokic, D., 2012. Speculation and the 2008 oil bubble: The d.c.o.t. Report analysis. Energy Policy 45, 541--550.
+Tokic, D., 2012. Speculation and the 2008 oil bubble: The dcot report analysis. Energy Policy 45, 541--550.
 
@@
 
+\leavevmode\hypertarget{ref-yang_investment_2013}{}%
+Yang, F., 2013. Investment shocks and the commodity basis spread. Journal of Financial Economics 110, 164--184.
+
 \end{document}

### 2022-04-27 docs/literature_files/format.r

@@ -5,3 +5,34 @@ caption_latex <- function(x){
   x <- gsub("\\\\@ref\\((.+?)\\)", "\\\\ref{\\1}", x, ignore.case = TRUE, perl = TRUE)
   x
 }
+
+show_table <- function(type, table){
+  if (type == 'html') { 
+    table <- kable_classic(table, full_width = TRUE, html_font = html_font) 
+  } 
+  else if (type == 'latex') {
+    table <- kable_classic(
+      table, font_size = tables_font_size, 
+      latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
+    )
+  }
+
+  table
+}
+
+#' Extract result table from result tables data frame provided
+#'
+#' @param tables A data frame with result tables. Columns are:
+#'  - analysis: name of the analysis.
+#'  - result: nested result table.
+#' @param analysis A string with the analysis name
+#' @return A data frame with the result table
+get_table <- function(tables, analysis){
+  results <- tables[tables$analysis  == analysis, "results"]
+  if (NCOL(results) > 1L) { 
+    message <- paste0("Multiple tables found for analysis: ", analysis)
+    message(message) 
+  } else {
+    results[[1]]
+  }
+}

### 2022-04-27 explore/scripts/tables.r

@@ -594,7 +594,7 @@ readr::write_rds(tables, here::here("explore", "tables", "tables.rds"))
 
 
 tables <- readr::read_rds(here::here("explore", "tables", "tables.rds"))
-
+tidyr::unnest(tables[1, 2])
 
 
 

### 2022-04-27 renv_init.r

@@ -1,0 +1,16 @@
+
+
+config <- list(
+  renv.config.cache.enabled = FALSE,
+  renv.config.install.transactional = FALSE
+)
+
+options(config)
+
+settings <- list(
+  r.version = 3.6, use.cache = FALSE, vcs.ignore.cellar = TRUE,
+  vcs.ignore.library = TRUE, vcs.ignore.local = TRUE
+)
+
+renv::init(settings = settings)
+

### 2022-04-28 docs/paper.Rmd
update table geometry + use slituR package

@@
 output:
+  bookdown::pdf_book:
+      pandoc_args: latex.yaml
+      base_format: rticles::elsevier_article
+      latex_engine: xelatex
+      toc_depth: 3
+      includes:
+        in_header: preamble.tex
   bookdown::gitbook:
@@
     toc_depth: 3
+    fig_caption: true
+    number_sections: true
+    global_numbering: true
     config:
@@
 ```{r globals, include = FALSE}
-library(kableExtra)
+library(kableExtra); library(slituR)
 
@@
 
-path <- "./format.r"
-download.file(
-  "https://www.dropbox.com/s/a88duv7rhqq8aar/bookdown-functions-book-building.r?dl=1",
-  path
-)
-source(path); file.remove(path)
-
-tables_font_size <- 9L
 tables_collapse_rows_align <- "top"
@@
 tables_hline <- "major"
-
-latex_options <- c("repeat_header")
-latex_repeat_header_text <- "\\textit{(continued)}"
-latex_repeat_header_method <- "replace"
-
-html_font <- "Cambria"
 
@@
 
+```
+
+```{r, include=latex}
+knitr::asis_output('\\newgeometry{a4paper,left=1in,right=1in,top=1in,bottom=1in,nohead}')
+knitr::asis_output('\\savegeometry{tables}')
+knitr::asis_output('\\restoregeometry')
 ```
@@
 The mechanical approach similarly seems amiss both in form and substance.
-Most of the studies underpinning the regulatory response to financialisation took the form of pairwise correlation, causation and to some extent co-integration analysis, all of which are idiosyncratic in nature for they study single pairs of individual commodity assets.
+Most of the studies underpinning the regulatory response to financialisation took the form of pairwise correlation, causation and to some extent co-integration analysis, all of which are idiosyncratic in nature for they study single pairs of individual assets.
 Besides, some of these techniques since proved controversial and seem to produce results the quality of which may fall short of the standards that may reasonably be expected to lay the ground for legislative action.
@@
 The aforementioned technique(s) could thence be used to observe potential changes in pricing dynamics, for example, which origin could be naturally attributed to the market behaviour of the new comers.
-Although appealing, for it comes with the promise of prompt "significant" results, this assumption depicts an incomplete picture for it misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure [@keynes_treatise_1930; @hicks_value_1939].
+Although appealing, for it comes with the promise of prompt "significant" results, this approach misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure [@keynes_treatise_1930; @hicks_value_1939].
 While essential to the understanding of the phenomenon, the global nature of financialisation and its impact on market fundamentals therefore appear to have been originally overlooked and another approach, perhaps more refined, seems warranted.
@@
 Taken together, the results in tables \@ref(tab:co-movement-time-reg-picks-facts-picks) and \@ref(tab:co-movement-time-reg-US-facts-picks) suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.
-To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in Table \@ref(tab:co-movement-time-reg-UK-facts-picks).
+To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in table \@ref(tab:co-movement-time-reg-UK-facts-picks).
 In the first period, although all sets of picks, except that of the market factor, included at least one metal, the average $R^{2}$s are very low; close to zero in most cases.
@@
 
-```{r, include=latex}
-knitr::asis_output('\\newpage')
-```
 ```{r, include=html}
@@
 ```
+```{r, include=latex}
+knitr::asis_output('\\newpage')
+knitr::asis_output('\\loadgeometry{tables}')
+```
 
 # Tables {#tables}
-<!-- Tables {#tables .unnumbered} -->
+<!-- # Tables {#tables .unnumbered} -->
 <!-- ============ -->
@@
 
-table <- get_table(tables, "descriptive statistics (no regimes)") %>% 
-  kbl(booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
+table <- get_results(tables, "descriptive statistics (no regimes)") %>%
+  kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 
-show_table(output_type, table)
+style_table(output_type, table)
 ```
@@
 
-table <- get_table(tables, "descriptive statistics (regimes)") %>% 
-  kbl(booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
+table <- get_results(tables, "descriptive statistics (regimes)") %>% 
+  kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 
-table <- get_table(tables, "regressions - time series - US commodities ~ CHP") %>% 
-  kbl(booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
+table <- get_results(tables, "regressions - time series - US commodities ~ CHP") %>% 
+  kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 
-table <- get_table(tables, "regressions - time series - US commodities ~ factors from US commodities") %>%
+table <- get_results(tables, "regressions - time series - US commodities ~ factors from US commodities") %>%
   dplyr::mutate(
@@
   ) %>% 
-  kbl(longtable = T, booktabs = T, caption = caption, col.names = colnames, align = align) %>%
+  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, col.names = colnames, align = align) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 
-table <- get_table(tables, "proportions") %>%
+table <- get_results(tables, "proportions") %>%
   dplyr::mutate(period = stringr::str_replace_all(period, "present", "post-crisis")) %>%
@@
   ) %>% 
-  kbl(longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
+  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 
-table <- get_table(tables, "average correlations (amongst factor picks)") %>%
+table <- get_results(tables, "average correlations (amongst factor picks)") %>%
   dplyr::mutate( factor = as.character(factor), factor = ifelse(factor == "OI nearby", "open interest", factor)) %>% 
-  kbl(longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
+  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 ```
-```{r, include=latex}
-knitr::asis_output('\\newpage')
-```
 
-```{r co-movement-time-reg-picks-facts-picks}
+```{r co-movement-time-reg-picks-facts-picks, fig.pos = 'htbp'}
 caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the various sets of factor picks are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the picks.
@@
 
-table <- get_table(tables, "regressions - time series - factor picks ~ factors from picks") %>% 
-  kbl(longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
+table <- get_results(tables, "regressions - time series - factor picks ~ factors from picks") %>% 
+  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 
-table <- get_table(tables, "regressions - time series - US commodities ~ factors from picks") %>% 
-  kbl(longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
+table <- get_results(tables, "regressions - time series - US commodities ~ factors from picks") %>% 
+  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 
-table <- get_table(tables, "regressions - time series - UK metals ~ factors from picks") %>% 
-  kbl(longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
+table <- get_results(tables, "regressions - time series - UK metals ~ factors from picks") %>% 
+  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
   column_spec(1L, bold = TRUE) %>%
@@
 ```{r, include=latex}
-knitr::asis_output('\\cleardoublepage')
 knitr::asis_output('\\restoregeometry')
+knitr::asis_output('\\newpage')
 ```

### 2022-04-28 docs/paper.tex
update table geometry + use slituR package

@@
 
-% \usepackage[width=1\textwidth]{caption}
-\usepackage[margin=0pt]{caption}
 \usepackage{geometry}
 \usepackage{hyperref}
+\usepackage{lscape}
+\usepackage[margin=0pt]{caption}
 \usepackage{booktabs}
@@
 
+\newgeometry{a4paper,left=1in,right=1in,top=1in,bottom=1in,nohead}\savegeometry{tables}\restoregeometry
+
 \cleardoublepage
@@
 The aforementioned technique(s) could thence be used to observe potential changes in pricing dynamics, for example, which origin could be naturally attributed to the market behaviour of the new comers.
-Although appealing, for it comes with the promise of prompt ``significant'' results, this assumption depicts an incomplete picture for it misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure (Hicks, 1939; Keynes, 1930).\\
+Although appealing, for it comes with the promise of prompt ``significant'' results, this approach misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure (Hicks, 1939; Keynes, 1930).\\
 While essential to the understanding of the phenomenon, the global nature of financialisation and its impact on market fundamentals therefore appear to have been originally overlooked and another approach, perhaps more refined, seems warranted.
@@
 Taken together, the results in tables \ref{tab:co-movement-time-reg-picks-facts-picks} and \ref{tab:co-movement-time-reg-US-facts-picks} suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.\\
-To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in Table \ref{tab:co-movement-time-reg-UK-facts-picks}.
+To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in table \ref{tab:co-movement-time-reg-UK-facts-picks}.
 In the first period, although all sets of picks, except that of the market factor, included at least one metal, the average \(R^{2}\)s are very low; close to zero in most cases.
@@
 
-\newpage
+\newpage\loadgeometry{tables}
 
@@
 
-\newpage
-
 \begingroup\fontsize{9}{11}\selectfont
@@
 
-\cleardoublepage\restoregeometry
+\restoregeometry\newpage
 

### 2022-05-26 explore/scripts/tables.r
fix dependency typo

@@ -63,7 +63,7 @@ commodities <- dplyr::filter(commodities_market_individuals, regime == "all") %>
   tidyr::pivot_longer(
     cols = c("mean", "sd"), names_to = "estimate", values_to = "value"
   ) %>% tidyr::pivot_wider(names_from = "period", values_from = "value") %>%
-  dplyr::arrange(dplys::desc(country), sector, subsector, commodity) %>%
+  dplyr::arrange(dplyr::desc(country), sector, subsector, commodity) %>%
   dplyr::select(-c(country, sector, subsector)) %>%
   dplyr::rename(asset = commodity)
 
@@ -109,7 +109,7 @@ commodities <- dplyr::filter(commodities_market_individuals, regime != "all") %>
   tidyr::pivot_longer(
     cols = c("mean", "sd"), names_to = "estimate", values_to = "value"
   ) %>% tidyr::pivot_wider(names_from = "period", values_from = "value") %>%
-  dplyr::arrange(dplys::desc(country), sector, subsector, commodity) %>%
+  dplyr::arrange(dplyr::desc(country), sector, subsector, commodity) %>%
   dplyr::select(-c(country, sector, subsector)) %>%
   dplyr::rename(asset = commodity)
 

### 2022-05-26 docs/paper.Rmd
revision first pass

@@
 Using a bespoke asset pricing factors based framework we study the issue through the lens of co-movement and find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of "definancialisation" in global commodity futures markets.
+The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals.
 output:
@@
 With the benefit of hindsight, this approach seems to lack a fundamental understanding of the phenomenon it endeavoured to study and which consequences it attempted to address.
-Financialisation was a phenomenon global in nature; through the channel of index investment it swayed the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
-Focusing on individual markets in this context thus seems incomprehensive.
-The mechanical approach similarly seems amiss both in form and substance.
+Financialisation was a phenomenon global in nature; through the channel of index investment it affected the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
+Focusing on individual markets in this context thus seems limited.
 Most of the studies underpinning the regulatory response to financialisation took the form of pairwise correlation, causation and to some extent co-integration analysis, all of which are idiosyncratic in nature for they study single pairs of individual assets.
 Besides, some of these techniques since proved controversial and seem to produce results the quality of which may fall short of the standards that may reasonably be expected to lay the ground for legislative action.
-In substance, leaving the idiosyncrasy issue aside, a case could be made for the mechanical approach under the assumption that financialised commodity markets can be described, ceteris paribus, as their prior or legacy state with increased uninformed financial participation.
-The aforementioned technique(s) could thence be used to observe potential changes in pricing dynamics, for example, which origin could be naturally attributed to the market behaviour of the new comers.
 Although appealing, for it comes with the promise of prompt "significant" results, this approach misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure [@keynes_treatise_1930; @hicks_value_1939].
@@
 With the benefit of hindsight, it appears this approach was perhaps too narrow, and it now seems necessary to address the phenomenon from a broader perspective.
-Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggered a process of "definancialisaion" in global commodity futures markets.
+Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggering a reversion to pre-financialisation dynamics.
+
 The initial view of financialisation was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity futures prices^[@masters_testimony_2008; @masters_accidental_2008; @unctad_global_2009; @deschutter_food_2010; @gilbert_how_2010; @gilbert_speculative_2010; @herman_not_2011; @schumann_hunger_2011; @singleton_investor_2013.].
@@
 
-Using our bespoke commodity-based asset pricing framework we strive to shed new lights on the phenomenon by first regressing returns series for the twenty four individual US commodities against our factor mimicking portfolios independently.
+Using our bespoke commodity-based asset pricing framework we strive to shed new light on the phenomenon by first regressing returns series for the twenty four individual US commodities against our factor mimicking portfolios independently.
+The resulting individual explanatory powers ($R^2$s), once averaged by factor and period, offer a refined perspective on the relation between return and factor attribute co-movement.
+A low figure indicates low cross-sectional return co-movement for, in this context, return on the corresponding factor mimicking portfolio only has explanatory power on return for commodities that are constituents of one of its legs over the corresponding period.
+The explanatory power for the other commodities is typically low or even 0 for the case where commodities are perfectly uncorrelated with one-another.
+A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities, which suggests that pairwise correlation relate to factor attribute.
 The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \@ref(tab:co-movement-time-reg-US-facts-US).
-Over the first period the market factor has the best average time series performance with the highest average $R^{2}$ with all three futures market factors performing poorly and the overall performance consistent across periods of high and low **CHP** (below period median).
+Over the first period the market factor has the best average time series performance with the highest average $R^{2}$ with all three futures market factors performing poorly, indicating that the commodities with extreme factor attributes (high or low CHP for example) are uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of high and low **CHP** (below period median).
 The two factor models average $R^{2}$s (results available on the [online results dashboard](http://18.135.131.217:3838/financialization-asset-pricing/)) are roughly the sum of the one factor $R^{2}$s indicating that the factors are almost orthogonal over this period.
-The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average $R^{2}$ increasing to 8.2% in the second period relative to 1.7% in the first with this improvement coming from the long leg that shows a greater improvement (4.5% to 15.1%) relative to the short (3% to 4%) bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period.
+The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average $R^{2}$ increasing to 8.2% in the second period relative to 1.7% in the first with this improvement coming from the long leg that shows a greater improvement (4.5% to 15.1%) relative to the short (3% to 4%), suggesting that "normally" backwardated commodities (Keynesian perspective) have higher correlation with the rest of the commodity cross-section, and thereby bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period.
 The performance of the market factor also improves though not by as much in a relative sense (21.6% from 11.7%) and both the term structure factor and the open interest growth factor show a much smaller improvement in performance with smaller differences between legs.
@@
 In table \@ref(tab:co-movement-correlations), we show the average pairwise returns correlation between each set of picks in each time period.
-This exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.
+Following on form the earlier observations, this exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.
 In the first period the average picks pairwise correlation for the long-short factors ranges from 7.1% (term structure factor picks) to 12.4% (open interest factor picks) while the market factor picks show the highest figure (23.7%).
@@
 
-Taken together the patterns of results over the crisis and post-crisis periods echo those in @basu_definancialisation in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex, in other words, a process of "definancialisation".
+Taken together the patterns of results over the crisis and post-crisis periods echo those in @basu_definancialisation in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex.
 
@@
 With the benefit of hindsight, this focus appears to have been too narrow.
-As our results suggests, financialisation was a phenomenon global in nature, with cross-sectional effects on market fundamentals and studying the direct effects of increased market participation in single markets thus seems amiss in this context.
-The results of our analysis further suggest that financialisation set off an ontological drift in the commodity complex beyond energy and agricultural commodities and in fact strongest for the metals sector at the global level; an aspect largely overlooked in the original approach that we believe the existing literature has not fully analysed.
-The regulatory changes underpinned by these studies may thus have been unwarranted with potential substantial undesired effects on the functioning of the markets in which they were enforced and thence, to a larger extent on that of the economic system as a whole.
+As our results suggests, financialisation was a phenomenon global in nature and studying the direct effects of increased market participation in single markets thus seems amiss in this context.
+The results of our analysis further suggest that financialisation had cross-sectional effects on market fundamentals across the commodity complex beyond energy and agricultural commodities and in fact strongest for the metals sector at the global level; an aspect largely overlooked in the original approach that we believe the existing literature has not fully analysed.
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in commodity pricing dynamics.
-In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have triggered a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of "definancialisation" in global commodity futures markets.
+In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have triggered a motion of reversion to legacy pre-financialisation fundamentals.
 

### 2022-05-26 docs/paper.tex
revision first pass

@@
 Using a bespoke asset pricing factors based framework we study the issue through the lens of co-movement and find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of ``definancialisation'' in global commodity futures markets.
+The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals.
   \end{abstract}
@@
 With the benefit of hindsight, this approach seems to lack a fundamental understanding of the phenomenon it endeavoured to study and which consequences it attempted to address.\\
-Financialisation was a phenomenon global in nature; through the channel of index investment it swayed the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
-Focusing on individual markets in this context thus seems incomprehensive.
-The mechanical approach similarly seems amiss both in form and substance.
+Financialisation was a phenomenon global in nature; through the channel of index investment it affected the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
+Focusing on individual markets in this context thus seems limited.
 Most of the studies underpinning the regulatory response to financialisation took the form of pairwise correlation, causation and to some extent co-integration analysis, all of which are idiosyncratic in nature for they study single pairs of individual assets.
 Besides, some of these techniques since proved controversial and seem to produce results the quality of which may fall short of the standards that may reasonably be expected to lay the ground for legislative action.
-In substance, leaving the idiosyncrasy issue aside, a case could be made for the mechanical approach under the assumption that financialised commodity markets can be described, ceteris paribus, as their prior or legacy state with increased uninformed financial participation.
-The aforementioned technique(s) could thence be used to observe potential changes in pricing dynamics, for example, which origin could be naturally attributed to the market behaviour of the new comers.
 Although appealing, for it comes with the promise of prompt ``significant'' results, this approach misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure (Hicks, 1939; Keynes, 1930).\\
@@
 With the benefit of hindsight, it appears this approach was perhaps too narrow, and it now seems necessary to address the phenomenon from a broader perspective.
-Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggered a process of ``definancialisaion'' in global commodity futures markets.\\
+Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggering a reversion to pre-financialisation dynamics.
+
 The initial view of financialisation was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity futures prices\footnote{Masters (2008); Masters and White (2008); UNCTAD and Cooperation (2009); De Schutter (2010); Gilbert (2010a); Gilbert (2010b); Herman et al.
@@
 
-Using our bespoke commodity-based asset pricing framework we strive to shed new lights on the phenomenon by first regressing returns series for the twenty four individual US commodities against our factor mimicking portfolios independently.
-The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \ref{tab:co-movement-time-reg-US-facts-US}.\\
-Over the first period the market factor has the best average time series performance with the highest average \(R^{2}\) with all three futures market factors performing poorly and the overall performance consistent across periods of high and low \textbf{CHP} (below period median).
+Using our bespoke commodity-based asset pricing framework we strive to shed new light on the phenomenon by first regressing returns series for the twenty four individual US commodities against our factor mimicking portfolios independently.
+The resulting individual explanatory powers (\(R^2\)s), once averaged by factor and period, offer a refined perspective on the relation between return and factor attribute co-movement.
+A low figure indicates low cross-sectional return co-movement for, in this context, return on the corresponding factor mimicking portfolio only has explanatory power on return for commodities that are constituents of one of its legs over the corresponding period.
+The explanatory power for the other commodities is typically low or even 0 for the case where commodities are perfectly uncorrelated with one-another.
+A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities, which suggests that pairwise correlation relate to factor attribute.\\
+The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \ref{tab:co-movement-time-reg-US-facts-US}.
+Over the first period the market factor has the best average time series performance with the highest average \(R^{2}\) with all three futures market factors performing poorly, indicating that the commodities with extreme factor attributes (high or low CHP for example) are uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of high and low \textbf{CHP} (below period median).
 The two factor models average \(R^{2}\)s (results available on the \href{http://18.135.131.217:3838/financialization-asset-pricing/}{online results dashboard}) are roughly the sum of the one factor \(R^{2}\)s indicating that the factors are almost orthogonal over this period.\\
-The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average \(R^{2}\) increasing to 8.2\% in the second period relative to 1.7\% in the first with this improvement coming from the long leg that shows a greater improvement (4.5\% to 15.1\%) relative to the short (3\% to 4\%) bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period.
+The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average \(R^{2}\) increasing to 8.2\% in the second period relative to 1.7\% in the first with this improvement coming from the long leg that shows a greater improvement (4.5\% to 15.1\%) relative to the short (3\% to 4\%), suggesting that ``normally'' backwardated commodities (Keynesian perspective) have higher correlation with the rest of the commodity cross-section, and thereby bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period.
 The performance of the market factor also improves though not by as much in a relative sense (21.6\% from 11.7\%) and both the term structure factor and the open interest growth factor show a much smaller improvement in performance with smaller differences between legs.
@@
 In table \ref{tab:co-movement-correlations}, we show the average pairwise returns correlation between each set of picks in each time period.
-This exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.\\
+Following on form the earlier observations, this exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.\\
 In the first period the average picks pairwise correlation for the long-short factors ranges from 7.1\% (term structure factor picks) to 12.4\% (open interest factor picks) while the market factor picks show the highest figure (23.7\%).
@@
 
-Taken together the patterns of results over the crisis and post-crisis periods echo those in Basu and Bauthéac (2021) in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex, in other words, a process of ``definancialisation''.
+Taken together the patterns of results over the crisis and post-crisis periods echo those in Basu and Bauthéac (2021) in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex.
 
@@
 With the benefit of hindsight, this focus appears to have been too narrow.
-As our results suggests, financialisation was a phenomenon global in nature, with cross-sectional effects on market fundamentals and studying the direct effects of increased market participation in single markets thus seems amiss in this context.\\
-The results of our analysis further suggest that financialisation set off an ontological drift in the commodity complex beyond energy and agricultural commodities and in fact strongest for the metals sector at the global level; an aspect largely overlooked in the original approach that we believe the existing literature has not fully analysed.
-The regulatory changes underpinned by these studies may thus have been unwarranted with potential substantial undesired effects on the functioning of the markets in which they were enforced and thence, to a larger extent on that of the economic system as a whole.\\
+As our results suggests, financialisation was a phenomenon global in nature and studying the direct effects of increased market participation in single markets thus seems amiss in this context.\\
+The results of our analysis further suggest that financialisation had cross-sectional effects on market fundamentals across the commodity complex beyond energy and agricultural commodities and in fact strongest for the metals sector at the global level; an aspect largely overlooked in the original approach that we believe the existing literature has not fully analysed.\\
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in commodity pricing dynamics.
-In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have triggered a motion of reversion to legacy pre-financialisation fundamentals, in other words, a process of ``definancialisation'' in global commodity futures markets.
+In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have triggered a motion of reversion to legacy pre-financialisation fundamentals.
 

### 2022-06-29 docs/paper.Rmd

@@
       base_format: rticles::elsevier_article
-      latex_engine: xelatex
+      latex_engine: pdflatex
       toc_depth: 3
@@
 One of these is based on the Keynes-Hicks [@keynes_some_1923; @keynes_treatise_1930; @hicks_value_1939; @hicks_value_1946] risk transfer approach to the term structure; the corresponding "theory of normal backwardation", complemented for the possibility of contango [@houthakker_restatement_1957; @cootner_returns_1960], postulates that futures prices for a given commodity are inversely related to the extent that commercial hedgers are short or long and using commercial hedging pressure (CHP) as a proxy for hedgers net market position we construct factor mimicking portfolios that capture the impact of hedging pressure as a systemic factor [@basu_capturing_2013].
+The cross-sectional nature of financialisation [@cheng_financialisation_2014; @basak_model_2016] further leads us to extend this paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure first considered in @hong_what_2012.
+In this context, returns for individual commodities should be high in periods where **CHP** is low (**backwardation**) and low in periods where **CHP** is high (**contango**).
 Working's contending approach that relates futures price formation to storage costs in the theory of "the price of storage" [@working_theory_1949] forms the basis of another model that we consider where, following @szymanowska_anatomy_2014 and @fuertes_commodity_2015 who demonstrate that the term structure factor has explanatory power for the cross-section of commodity returns, we construct factor mimicking portfolios using roll-yield as a proxy for the front end shape of individual commodity term structures.
@@
 
-The cross-sectional nature of financialisation [@cheng_financialisation_2014; @basak_model_2016] leads us to extend the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure first considered in @hong_what_2012.
-This paradigm implies that returns for individual commodities should be high in periods where **CHP** is low (**backwardation**) and low in periods where **CHP** is high (**contango**).
 Over the first period the cross-sectional average returns during phases of **backwardation** for both the US and UK commodities are positive and overall higher than during phases of **contango**, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
@@
 The explanatory power for the other commodities is typically low or even 0 for the case where commodities are perfectly uncorrelated with one-another.
-A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities, which suggests that pairwise correlation relate to factor attribute.
+A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities.
+and therefore provides evidence that pairwise return correlation relates to factor attribute.
 The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \@ref(tab:co-movement-time-reg-US-facts-US).

### 2022-06-29 docs/paper.tex

@@
 
+% Pandoc citation processing
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+% for Pandoc 2.8 to 2.10.1
+\newenvironment{cslreferences}%
+  {}%
+  {\par}
+% For Pandoc 2.11+
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
 \usepackage{geometry}
@@
 
-The last twenty years have seen major upheavals in the commodity markets with the onset of financialisation\footnote{Starting around 2004, with a view of commodity markets as an emerging asset class and in an effort to hedge against inflation and seek diversification benefits (Büyükşahin and Robe, 2014; Singleton, 2013), institutional investors sent forth an unprecedented flow of capital into commodity futures markets.
-This phenomenon is commonly referred to as the financialisation of commodities (Domanski and Heath, 2007).} as well as the period of the 2008 financial crisis and its aftermath.
+The last twenty years have seen major upheavals in the commodity markets with the onset of financialisation\footnote{Starting around 2004, with a view of commodity markets as an emerging asset class and in an effort to hedge against inflation and seek diversification benefits {[}1,2{]}, institutional investors sent forth an unprecedented flow of capital into commodity futures markets.
+This phenomenon is commonly referred to as the financialisation of commodities {[}3{]}.} as well as the period of the 2008 financial crisis and its aftermath.
 Financialisation appears to have affected multiple economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres.
@@
 Besides, some of these techniques since proved controversial and seem to produce results the quality of which may fall short of the standards that may reasonably be expected to lay the ground for legislative action.
-Although appealing, for it comes with the promise of prompt ``significant'' results, this approach misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure (Hicks, 1939; Keynes, 1930).\\
+Although appealing, for it comes with the promise of prompt ``significant'' results, this approach misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure {[}4,5{]}.\\
 While essential to the understanding of the phenomenon, the global nature of financialisation and its impact on market fundamentals therefore appear to have been originally overlooked and another approach, perhaps more refined, seems warranted.
@@
 This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of market participation.\\
-Factor model techniques are well suited to isolating common driving factors and detecting co-movement (Asness and Frazzini, 2013; Asness et al., 2015, 2019; Carhart, 1997; Fama and French, 2015, 1993; Frazzini and Pedersen, 2014; Hou et al., 2015) at a broader level, beyond individual pairs of assets, and are commonly used to study commodity market fundamentals (Bakshi et al., 2019; Boons and Prado, 2019; Cortazar et al., 2013; Daskalaki et al., 2014; Fernandez-Perez et al., 2018; Gorton et al., 2012; Miffre and Rallis, 2007; Sakkas and Tessaromatis, 2020; Schwartz and Smith, 2000; Szymanowska et al., 2014; Yang, 2013); they consequently seem well adapted to study these two issues simultaneously.
+Factor model techniques are well suited to isolating common driving factors and detecting co-movement {[}6--13{]} at a broader level, beyond individual pairs of assets, and are commonly used to study commodity market fundamentals {[}14--24{]}; they consequently seem well adapted to study these two issues simultaneously.
 Building on theory we therefore develop a bespoke commodity-based asset pricing framework comprised of factor models based both on fundamentals as well as liquidity considerations.\\
-One of these is based on the Keynes-Hicks (Hicks, 1946, 1939; Keynes, 1930, 1923) risk transfer approach to the term structure; the corresponding ``theory of normal backwardation'', complemented for the possibility of contango (Cootner, 1960; H.
-Houthakker, 1957), postulates that futures prices for a given commodity are inversely related to the extent that commercial hedgers are short or long and using commercial hedging pressure (CHP) as a proxy for hedgers net market position we construct factor mimicking portfolios that capture the impact of hedging pressure as a systemic factor (Basu and Miffre, 2013).
-Working's contending approach that relates futures price formation to storage costs in the theory of ``the price of storage'' (Working, 1949) forms the basis of another model that we consider where, following Szymanowska et al.
-(2014) and Fuertes et al.
-(2015) who demonstrate that the term structure factor has explanatory power for the cross-section of commodity returns, we construct factor mimicking portfolios using roll-yield as a proxy for the front end shape of individual commodity term structures.
-We further consider a liquidity-based model following Hong and Yogo (2012) who find that open interest growth has predictive power for individual commodity returns and again, using the latter measure as a proxy for individual commodity liquidity, we construct long-short factor mimicking portfolios.
+One of these is based on the Keynes-Hicks {[}4,5,25,26{]} risk transfer approach to the term structure; the corresponding ``theory of normal backwardation'', complemented for the possibility of contango {[}27,28{]}, postulates that futures prices for a given commodity are inversely related to the extent that commercial hedgers are short or long and using commercial hedging pressure (CHP) as a proxy for hedgers net market position we construct factor mimicking portfolios that capture the impact of hedging pressure as a systemic factor {[}29{]}.
+The cross-sectional nature of financialisation {[}30,31{]} further leads us to extend this paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in {[}32{]}.
+In this context, returns for individual commodities should be high in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in periods where \textbf{CHP} is high (\textbf{contango}).
+Working's contending approach that relates futures price formation to storage costs in the theory of ``the price of storage'' {[}33{]} forms the basis of another model that we consider where, following {[}20{]} and {[}34{]} who demonstrate that the term structure factor has explanatory power for the cross-section of commodity returns, we construct factor mimicking portfolios using roll-yield as a proxy for the front end shape of individual commodity term structures.
+We further consider a liquidity-based model following {[}32{]} who find that open interest growth has predictive power for individual commodity returns and again, using the latter measure as a proxy for individual commodity liquidity, we construct long-short factor mimicking portfolios.
 
@@
 
-We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008\footnote{Starting point based on earlier studies (Baker, 2014; Christoffersen et al., 2014).}); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).\\
+We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008\footnote{Starting point based on earlier studies {[}35,36{]}.}); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).\\
 Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.
@@
 
-The cross-sectional nature of financialisation (Basak and Pavlova, 2016; Cheng and Xiong, 2014) leads us to extend the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in Hong and Yogo (2012).
-This paradigm implies that returns for individual commodities should be high in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in periods where \textbf{CHP} is high (\textbf{contango}).
 Over the first period the cross-sectional average returns during phases of \textbf{backwardation} for both the US and UK commodities are positive and overall higher than during phases of \textbf{contango}, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
@@
 This change of paradigm due to the arrival of financial investors, on the other hand, raises the question of whether they functioned as liquidity providers or demanders.
-Arguments have been put forward in favour of both possibilities with Moskowitz et al.
-(2012) arguing that financial investors provide liquidity and Kang et al.
-(2020) taking the opposite stance.
+Arguments have been put forward in favour of both possibilities with {[}37{]} arguing that financial investors provide liquidity and {[}38{]} taking the opposite stance.
 Our analysis of individual commodity returns' relation with both CHP and \textbf{CHP} before and during financialisation sheds new lights on this issue with our results suggesting that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
@@
 
-Goldstein et al.
-(2014) and Goldstein and Yang (2017) argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
-Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger's positions (Keynesian perspective, theory of normal backwardation: Keynes (1930), Hicks (1939), H.
-S.
-Houthakker (1957), Telser (1958)), as well our term structure factor, based on backwardation as measured by roll yield (Working's perspective, theory of storage: Working (1933), Kaldor (1939), Working (1948), Brennan (1958), Cootner (1960), Weymar (1966), Danthine (1978), Turnovsky (1983), Schwartz (1997)), to be best suited to measure the impact of financialisation.\\
+{[}39{]} and {[}40{]} argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
+Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger's positions (Keynesian perspective, theory of normal backwardation: {[}4{]}, {[}5{]}, {[}41{]}, {[}42{]}), as well our term structure factor, based on backwardation as measured by roll yield (Working's perspective, theory of storage: {[}43{]}, {[}44{]}, {[}45{]}, {[}46{]}, {[}28{]}, {[}47{]}, {[}48{]}, {[}49{]}, {[}50{]}), to be best suited to measure the impact of financialisation.\\
 We analyse the pricing dynamics over the different periods by first studying the time series explanatory performance of the various factors on all the US traded commodities with the factors constructed using the latter set of commodities.
@@
 Besides, starting in the crisis the Keneysian paradigm of returns begins to revert with higher mean returns during low (\textbf{backwardation}) relative to high (\textbf{contango}) \textbf{CHP} phases and this pattern continues, more pronounced, over the post-crisis period.
-As pointed out in Basu and Bauthéac (2021), the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
+As pointed out in {[}51{]}, the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
 
@@
 
-The initial view of financialisation was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity futures prices\footnote{Masters (2008); Masters and White (2008); UNCTAD and Cooperation (2009); De Schutter (2010); Gilbert (2010a); Gilbert (2010b); Herman et al.
-(2011); Schumann (2011); Singleton (2013).}.
+The initial view of financialisation was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity futures prices\footnote{{[}52{]}; {[}53{]}; {[}54{]}; {[}55{]}; {[}56{]}; {[}57{]}; {[}58{]}; {[}59{]}; {[}2{]}.}.
 However, the fundamental question of the nature of the impact of financialisation across the entire cross-section of commodity futures markets has not yet been completely answered.
-We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets\footnote{Etula (2013), Acharya et al.
-(2013), Cheng et al.
-(2014), Leclercq and Praz (2014), Sockin and Xiong (2015), Goldstein et al.
-(2014), Ekeland et al.
-(2016), Goldstein and Yang (2017).} and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in Tang and Xiong (2012) and Basak and Pavlova (2016).
+We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets\footnote{{[}60{]}, {[}61{]}, {[}62{]}, {[}63{]}, {[}64{]}, {[}39{]}, {[}65{]}, {[}40{]}.} and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in {[}66{]} and {[}31{]}.
 
@@
 A world-wide debate ensued about the role of index funds in commodity markets.
-The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs (De Schutter, 2010; Gilbert, 2010b; Herman et al., 2011; Schumann, 2011; UNCTAD and Cooperation, 2009).\\
-Early US Senate investigations on the matter drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US agricultural and energy markets to the observed surges in both futures and cash prices (Masters, 2008; Masters and White, 2008).
-This contention has since come to be known as the Masters' hypothesis and was largely endorsed by the final US Senate report on the issue (Senate, 2009).\\
+The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs {[}54,55,57--59{]}.\\
+Early US Senate investigations on the matter drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US agricultural and energy markets to the observed surges in both futures and cash prices {[}52,53{]}.
+This contention has since come to be known as the Masters' hypothesis and was largely endorsed by the final US Senate report on the issue {[}67{]}.\\
 At this stage, the question thrust on the academic sphere was whether ``excessive speculation'' (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices.
-A number of ensuing academic studies, most of which used commodity specific correlation and causality based analysis have since disproved this contention: Irwin et al.
-(2009), Sanders et al.
-(2010), Sanders and Irwin (2011a), Sanders and Irwin (2011b), Irwin (2013), Brunetti and Reiffen (2014), Hamilton and Wu (2015) and Bruno et al.
-(2017) investigated the issue in the context of the agricultural markets; meanwhile, Büyükşahin and Harris (2011), Tokic (2012), Fattouh et al.
-(2013), Kilian and Murphy (2014), Knittel and Pindyck (2016) and Manera et al.
-(2016) examined the energy markets while Bohl and Stephan (2013), Kim (2015) and Boyd et al.
-(2016) studied both energy and agricultural markets and Irwin and Sanders (2011), Irwin and Sanders (2012) as well as Stoll and Whaley (2011) examined the commodity markets in general.
+A number of ensuing academic studies, most of which used commodity specific correlation and causality based analysis have since disproved this contention: {[}68{]}, {[}69{]}, {[}70{]}, {[}71{]}, {[}72{]}, {[}73{]}, {[}74{]} and {[}75{]} investigated the issue in the context of the agricultural markets; meanwhile, {[}76{]}, {[}77{]}, {[}78{]}, {[}79{]}, {[}80{]} and {[}81{]} examined the energy markets while {[}82{]}, {[}83{]} and {[}84{]} studied both energy and agricultural markets and {[}85{]}, {[}86{]} as well as {[}87{]} examined the commodity markets in general.
 Other studies have underlined various alterations in commodity pricing dynamics over the period.
-Gilbert and Pfuderer (2014) reject the view that financialisation has not had any effects in the grains markets and demonstrate that trades originated by financial market participants, and specifically index investors, can move prices but tend to be typically volatility-reducing.
-Juvenal and Petrella (2015) contend that the oil price increase between 2004 and 2008 was mainly driven by the strength of global demand but that the financialisation process of commodity markets also played a role.
-Likewise, Henderson et al.
-(2015) show that non-information-based financial investments have important impacts on commodity prices.
-Cheng and Xiong (2014), on the other hand, show that in the case of index commodities, financialisation has transformed the risk sharing, and information discovery functions of commodity futures markets.
+{[}88{]} reject the view that financialisation has not had any effects in the grains markets and demonstrate that trades originated by financial market participants, and specifically index investors, can move prices but tend to be typically volatility-reducing.
+{[}89{]} contend that the oil price increase between 2004 and 2008 was mainly driven by the strength of global demand but that the financialisation process of commodity markets also played a role.
+Likewise, {[}90{]} show that non-information-based financial investments have important impacts on commodity prices.
+{[}30{]}, on the other hand, show that in the case of index commodities, financialisation has transformed the risk sharing, and information discovery functions of commodity futures markets.
 
@@
 
-Commodity index swaps, commodity index funds (CIFs), commodity-based exchange traded funds (ETFs) and notes (ETNs) or commodity linked notes (CLNs) were amongst the main investment vehicles that allowed institutional and retail investors to build up commodity exposure in the early 2000s (Boons et al., 2012; Henderson et al., 2015; Irwin and Sanders, 2011; Schumann, 2011; UNCTAD and Cooperation, 2009).
+Commodity index swaps, commodity index funds (CIFs), commodity-based exchange traded funds (ETFs) and notes (ETNs) or commodity linked notes (CLNs) were amongst the main investment vehicles that allowed institutional and retail investors to build up commodity exposure in the early 2000s {[}54,59,85,90,91{]}.
 Most of these products were primarily designed to track prominent commodity indexes among which the S\&P-GSCI, the most popular.\\
@@
 A third category, ``non-reportable'', aggregates positions for participants not meeting the reporting threshold.
-In response to concerns related to category accuracy\footnote{See for example Ederington and Lee (2002).} the CFTC now refines its classification in the disaggregated commitment of trader report (DCOT) where participant categories include ``Producer/Merchant/Processor/User'', ``Swap dealer'', ``Money manager'' and ``Other reportable'' as well as in the supplemental commitment of trader report (SCOT) that details commodity index trader aggregate positions for thirteen agricultural commodity futures markets.
+In response to concerns related to category accuracy\footnote{See for example {[}92{]}.} the CFTC now refines its classification in the disaggregated commitment of trader report (DCOT) where participant categories include ``Producer/Merchant/Processor/User'', ``Swap dealer'', ``Money manager'' and ``Other reportable'' as well as in the supplemental commitment of trader report (SCOT) that details commodity index trader aggregate positions for thirteen agricultural commodity futures markets.
 Data for DCOT and SCOT date back to 2006 and 2007 respectively.\\
@@
 On the one hand, futures markets have a long history of serving commodity producers to alleviate their commodity price and output risks.
-Keynes (1930) and Hicks (1939) emphasise the ``normal'' behaviour of naturally short hedgers outsourcing their commodity risk to naturally long commodity specialist speculators.
+{[}4{]} and {[}5{]} emphasise the ``normal'' behaviour of naturally short hedgers outsourcing their commodity risk to naturally long commodity specialist speculators.
 This market configuration is referred to as ``backwardation'' where futures are expected to trade at a discount to spot prices, providing speculators with incentives to take the long side.
 The opposite market paradigm is referred to as ``contango''.
-Working (Working, 1953, 1948, 1933) and Kaldor (Kaldor, 1939) somehow relax this ``supply-of-speculative-services'' (Till, 2007) approach by introducing processors and merchants, also commodity experts, on the hedgers side and relating the notions of backwardation and contango more directly to the term structure via the theory of storage where the shape of the front end of the term structure (basis) is directly related to the market price of storage.\\
+Working {[}43,45,93{]} and Kaldor {[}44{]} somehow relax this ``supply-of-speculative-services'' {[}94{]} approach by introducing processors and merchants, also commodity experts, on the hedgers side and relating the notions of backwardation and contango more directly to the term structure via the theory of storage where the shape of the front end of the term structure (basis) is directly related to the market price of storage.\\
 Financialisation, on the other hand, refers to the entry of financial investors into the commodity futures markets who, for the most part, are not commodity experts.
-Besides, these new market participants tend to exhibit herding like behaviour, often taking massive long-only positions on the whole cross-section of indexed commodities in an attempt to enhance returns while hedging against inflation and reaping further diversification benefits for portfolios with, in most cases, existing large positions across various asset classes (Boyd et al., 2016; Brunetti et al., 2016; Cheng et al., 2014; Juvenal and Petrella, 2015; Singleton, 2013; Tang and Xiong, 2012).
+Besides, these new market participants tend to exhibit herding like behaviour, often taking massive long-only positions on the whole cross-section of indexed commodities in an attempt to enhance returns while hedging against inflation and reaping further diversification benefits for portfolios with, in most cases, existing large positions across various asset classes {[}2,62,66,84,89,95{]}.
 This contrasts with the traditional approaches of Keynes and Working and in this context the issues of co-movement and aggregate market participants behaviour seem particularly relevant.
@@
 
-We further define aggregate backwardation (\textbf{backwardation}) and contango (\textbf{contango}) \textbf{CHP} regimes as, for a given period, \textbf{CHP} levels below and above the period's median respectively and, in contrast with (Hong and Yogo, 2012) who aggregate across sub-sectors, the asset pool we consider for \textbf{CHP} construction include the whole cross-section of US traded commodities.
+We further define aggregate backwardation (\textbf{backwardation}) and contango (\textbf{contango}) \textbf{CHP} regimes as, for a given period, \textbf{CHP} levels below and above the period's median respectively and, in contrast with {[}32{]} who aggregate across sub-sectors, the asset pool we consider for \textbf{CHP} construction include the whole cross-section of US traded commodities.
 
@@
 The onset of financialisation thus seems to have engendered a change in the nature of hedger's behaviour, at the aggregate level in particular, taking it away from the traditional Keynesian view of risk shifting.
-This phenomenon has been noted in earlier theoretical and empirical work (Danthine, 1978; Stout, 1998) in different contexts from which two competing models of behaviour have emerged.\\
-The information arbitrage model (Danthine, 1978; Grossman and Stiglitz, 1980; Kyle, 1989) implies that hedgers may often be seeking out counterparties to trade with rather than being purely passive.
-This issue is also raised in both Cheng and Xiong (2014) and Stulz (1996) who point out that hedgers may be taking a view on prices just as speculators do.
-In fact, by hedging away some of their risk, hedgers are able to speculate more heavily based on their disagreement against speculators regarding futures price movement (Simsek, 2013), which fits into a heterogeneous expectation theory of speculation\footnote{Hirshleifer (1975); Hirshleifer (1976); Hirshleifer (1977)}.
-As Stout (1998) points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves speculation as this form of trading is regarded as non-productive\footnote{Duffie (2014) also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.}.\\
-In the second model hedgers are seen as liquidity providers as in Kang et al.
-(2020) with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
+This phenomenon has been noted in earlier theoretical and empirical work {[}48,96{]} in different contexts from which two competing models of behaviour have emerged.\\
+The information arbitrage model {[}48,97,98{]} implies that hedgers may often be seeking out counterparties to trade with rather than being purely passive.
+This issue is also raised in both {[}30{]} and {[}99{]} who point out that hedgers may be taking a view on prices just as speculators do.
+In fact, by hedging away some of their risk, hedgers are able to speculate more heavily based on their disagreement against speculators regarding futures price movement {[}100{]}, which fits into a heterogeneous expectation theory of speculation\footnote{{[}101{]}; {[}102{]}; {[}103{]}}.
+As {[}96{]} points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves speculation as this form of trading is regarded as non-productive\footnote{{[}104{]} also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.}.\\
+In the second model hedgers are seen as liquidity providers as in {[}38{]} with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
 Table \ref{tab:co-movement-time-reg-US-CHP} supports this view.
@@
 The explanatory power for the other commodities is typically low or even 0 for the case where commodities are perfectly uncorrelated with one-another.
-A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities, which suggests that pairwise correlation relate to factor attribute.\\
+A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities.
+and therefore provides evidence that pairwise return correlation relates to factor attribute.\\
 The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \ref{tab:co-movement-time-reg-US-facts-US}.
@@
 The performance of the term structure factor constructed from its own sets of picks also shows a substantial increase, from 5.1\% to 8.4\% with, here again the increase in performance relatively stronger for the short leg, from 6\% to 16.1\% vs.~7.6\% to 12.1\% for the long.\\
-Taken together with the previous results showing that the metal complex predominantly loads on the long and short legs of the original CHP and term structure factors respectively, these results provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation perhaps as a result of spillover effects between the corresponding futures and spot markets as suggested in Basak and Pavlova (2016).
+Taken together with the previous results showing that the metal complex predominantly loads on the long and short legs of the original CHP and term structure factors respectively, these results provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation perhaps as a result of spillover effects between the corresponding futures and spot markets as suggested in {[}31{]}.
 
@@
 Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working's term structure paradigms.
-There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of Kang et al.
-(2020) who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
+There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of {[}38{]} who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
 
@@
 
-Taken together the patterns of results over the crisis and post-crisis periods echo those in Basu and Bauthéac (2021) in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex.
+Taken together the patterns of results over the crisis and post-crisis periods echo those in {[}51{]} in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex.
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-acharya_limits_2013}{}%
-Acharya, V.V., Lochstoer, L.A., Ramadorai, T., 2013. Limits to arbitrage and hedging: Evidence from commodity markets. Journal of Financial Economics 109, 441--465.
-
-\leavevmode\hypertarget{ref-asness_devil_2013}{}%
-Asness, C., Frazzini, A., 2013. The devil in hml's details. The Journal of Portfolio Management 39, 49--68.
-
-\leavevmode\hypertarget{ref-asness_fact_2015}{}%
-Asness, C., Frazzini, A., Israel, R., Moskowitz, T., 2015. Fact, fiction, and value investing. The Journal of Portfolio Management 42, 34--52.
-
-\leavevmode\hypertarget{ref-asness_quality_2019}{}%
-Asness, C.S., Frazzini, A., Pedersen, L.H., 2019. Quality minus junk. Review of Accounting Studies 24, 34--112.
-
-\leavevmode\hypertarget{ref-baker_financialisation_2014}{}%
-Baker, S.D., 2014. The financialization of storable commodities (SSRN Scholarly Paper No. ID 2348333). Social Science Research Network, Rochester, NY.
-
-\leavevmode\hypertarget{ref-bakshi_understanding_2019}{}%
-Bakshi, G., Gao, X., Rossi, A.G., 2019. Understanding the sources of risk underlying the cross section of commodity returns. Management Science 65, 619--641.
-
-\leavevmode\hypertarget{ref-basak_model_2016}{}%
-Basak, S., Pavlova, A., 2016. A model of financialization of commodities. The Journal of Finance 71, 1511--1556.
-
-\leavevmode\hypertarget{ref-basu_definancialisation}{}%
-Basu, D., Bauthéac, O., 2021. Commodity definancialisation. Working paper.
-
-\leavevmode\hypertarget{ref-basu_capturing_2013}{}%
-Basu, D., Miffre, J., 2013. Capturing the risk premium of commodity futures: The role of hedging pressure. Journal of Banking \& Finance 37, 2652--2664.
-
-\leavevmode\hypertarget{ref-bohl_does_2013}{}%
-Bohl, M.T., Stephan, P.M., 2013. Does futures speculation destabilize spot prices? New evidence for commodity markets. Journal of Agricultural and Applied Economics 45, 595--616.
-
-\leavevmode\hypertarget{ref-boons_stock_2012}{}%
-Boons, M., De Roon, F., Szymanowska, M., 2012. The stock market price of commodity risk, in: AFA 2012 Chicago Meetings Paper.
-
-\leavevmode\hypertarget{ref-boons_basis_2019}{}%
-Boons, M., Prado, M.P., 2019. Basis-momentum. The Journal of Finance 74, 239--279.
-
-\leavevmode\hypertarget{ref-boyd_prevalence_2016}{}%
-Boyd, N.E., Büyükşahin, B., Haigh, M.S., Harris, J.H., 2016. The prevalence, sources, and effects of herding. Journal of Futures Markets 36, 671--694.
-
-\leavevmode\hypertarget{ref-brennan_supply_1958}{}%
-Brennan, M.J., 1958. The supply of storage. The American Economic Review 48, 50--72.
-
-\leavevmode\hypertarget{ref-brunetti_speculators_2016}{}%
-Brunetti, C., Büyükşahin, B., Harris, J.H., 2016. Speculators, prices, and market volatility. Journal of Financial and Quantitative Analysis 51, 1545--1574.
-
-\leavevmode\hypertarget{ref-brunetti_commodity_2014}{}%
-Brunetti, C., Reiffen, D., 2014. Commodity index trading and hedging costs. Journal of Financial Markets 21, 153--180.
-
-\leavevmode\hypertarget{ref-bruno_financialisation_2017}{}%
-Bruno, V.G., Büyükşahin, B., Robe, M.A., 2017. The financialization of food? American Journal of Agricultural Economics 99, 243--264.
-
-\leavevmode\hypertarget{ref-buyuksahin_speculators_2011}{}%
-Büyükşahin, B., Harris, J.H., 2011. Do speculators drive crude oil futures prices? The Energy Journal 167--202.
-
-\leavevmode\hypertarget{ref-buyuksahin_speculators_2014}{}%
-Büyükşahin, B., Robe, M.A., 2014. Speculators, commodities and cross-market linkages. Journal of International Money and Finance, Understanding international commodity price fluctuations 42, 38--70.
-
-\leavevmode\hypertarget{ref-carhart_persistence_1997}{}%
-Carhart, M.M., 1997. On persistence in mutual fund performance. The Journal of finance 52, 57--82.
-
-\leavevmode\hypertarget{ref-cheng_convective_2014}{}%
-Cheng, I.-H., Kirilenko, A., Xiong, W., 2014. Convective risk flows in commodity futures markets. Review of Finance 19, 1733--1781.
-
-\leavevmode\hypertarget{ref-cheng_financialisation_2014}{}%
-Cheng, I.-H., Xiong, W., 2014. Financialization of commodity markets. Annual Review of Financial Economics 6, 419--441.
-
-\leavevmode\hypertarget{ref-christoffersen_factor_2014}{}%
-Christoffersen, P., Lunde, A., Olesen, K.V., 2014. Factor structure in commodity futures return and volatility. Journal of Financial and Quantitative Analysis 1--74.
-
-\leavevmode\hypertarget{ref-cootner_returns_1960}{}%
-Cootner, P.H., 1960. Returns to speculators: Telser versus keynes. Journal of political Economy 68, 396--404.
-
-\leavevmode\hypertarget{ref-cortazar_commodity_2013}{}%
-Cortazar, G., Kovacevic, I., Schwartz, E.S., 2013. Commodity and asset pricing models: An integration (NBER Working Papers No. 19167). National Bureau of Economic Research, Inc.
-
-\leavevmode\hypertarget{ref-danthine_information_1978}{}%
-Danthine, J.-P., 1978. Information, futures prices, and stabilizing speculation. Journal of Economic Theory 17, 79--98.
-
-\leavevmode\hypertarget{ref-daskalaki_factors_2014}{}%
-Daskalaki, C., Kostakis, A., Skiadopoulos, G., 2014. Are there common factors in individual commodity futures returns? Journal of Banking \& Finance 40, 346--363.
-
-\leavevmode\hypertarget{ref-deschutter_food_2010}{}%
-De Schutter, O., 2010.
-Food commodities speculation and food price crises: Regulation to reduce the risks of price volatility.
-United Nations Special Rapporteur on the Right to Food Briefing Note 2, 1--14.
-
-\leavevmode\hypertarget{ref-domanski_financial_2007}{}%
-Domanski, D., Heath, A., 2007. Financial investors and commodity markets. Working Paper.
-
-\leavevmode\hypertarget{ref-duffie_challenges_2014}{}%
-Duffie, D., 2014. Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs. The Journal of Legal Studies 43, S173--S182.
-
-\leavevmode\hypertarget{ref-ederington_who_2002}{}%
-Ederington, L., Lee, J.H., 2002. Who trades futures and how: Evidence from the heating oil futures market. The Journal of Business 75, 353--373.
-
-\leavevmode\hypertarget{ref-ekeland_speculation_2016}{}%
-Ekeland, I., Lautier, D., Villeneuve, B., 2016. Speculation in commodity futures markets: A simple equilibrium model.
-
-\leavevmode\hypertarget{ref-etula_broker-dealer_2013}{}%
-Etula, E., 2013. Broker-dealer risk appetite and commodity returns. Journal of Financial Econometrics 11, 486--521.
-
-\leavevmode\hypertarget{ref-fama_common_1993}{}%
-Fama, E.F., French, K.R., 1993. Common risk factors in the returns on stocks and bonds. Journal of Financial Economics 33, 3--56.
-
-\leavevmode\hypertarget{ref-fama_five_factor_2015}{}%
-Fama, E.F., French, K.R., 2015. A five-factor asset pricing model. Journal of Financial Economics 116, 1--22.
-
-\leavevmode\hypertarget{ref-fattouh_role_2013}{}%
-Fattouh, B., Kilian, L., Mahadeva, L., 2013. The role of speculation in oil markets: What have we learnt so far? The Energy Journal 34, 7--33.
-
-\leavevmode\hypertarget{ref-fernandez_skewness_2018}{}%
-Fernandez-Perez, A., Frijns, B., Fuertes, A.-M., Miffre, J., 2018. The skewness of commodity futures returns. Journal of Banking \& Finance 86, 143--158.
-
-\leavevmode\hypertarget{ref-frazzini_betting_2014}{}%
-Frazzini, A., Pedersen, L.H., 2014. Betting against beta. Journal of Financial Economics 111, 1--25.
-
-\leavevmode\hypertarget{ref-fuertes_commodity_2015}{}%
-Fuertes, A.-M., Miffre, J., Fernandez-Perez, A., 2015. Commodity strategies based on momentum, term structure, and idiosyncratic volatility. Journal of Futures Markets 35, 274--297.
-
-\leavevmode\hypertarget{ref-gilbert_how_2010}{}%
-Gilbert, C.L., 2010a. How to understand high food prices. Journal of Agricultural Economics 61, 398--425.
-
-\leavevmode\hypertarget{ref-gilbert_speculative_2010}{}%
-Gilbert, C.L., 2010b. Speculative influences on commodity futures prices 2006-2008. UNCTAD, Geneva.
-
-\leavevmode\hypertarget{ref-gilbert_role_2014}{}%
-Gilbert, C.L., Pfuderer, S., 2014. The role of index trading in price formation in the grains and oilseeds markets. Journal of Agricultural Economics 65, 303--322.
-
-\leavevmode\hypertarget{ref-goldstein_speculation_2014}{}%
-Goldstein, I., Li, Y., Yang, L., 2014. Speculation and hedging in segmented markets. The Review of Financial Studies 27, 881--922.
-
-\leavevmode\hypertarget{ref-goldstein_commodity_2017}{}%
-Goldstein, I., Yang, L., 2017. Commodity financialization and information transmission (SSRN Scholarly Paper No. ID 2555996). Social Science Research Network, Rochester, NY.
-
-\leavevmode\hypertarget{ref-gorton_fundamentals_2012}{}%
-Gorton, G.B., Hayashi, F., Rouwenhorst, K.G., 2012. The fundamentals of commodity futures returns. Review of Finance 17, 35--105.
-
-\leavevmode\hypertarget{ref-grossman_impossibility_1980}{}%
-Grossman, S.J., Stiglitz, J.E., 1980. On the impossibility of informationally efficient markets. The American economic review 70, 393--408.
-
-\leavevmode\hypertarget{ref-hamilton_effects_2015}{}%
-Hamilton, J.D., Wu, J.C., 2015. Effects of index-fund investing on commodity futures prices. International Economic Review 56, 187--205.
-
-\leavevmode\hypertarget{ref-henderson_new_2015}{}%
-Henderson, B.J., Pearson, N.D., Wang, L., 2015. New evidence on the financialization of commodity markets. The Review of Financial Studies 28, 1285--1311.
-
-\leavevmode\hypertarget{ref-herman_not_2011}{}%
-Herman, M.-O., Kelly, R., Nash, R., 2011.
-Not a game, speculation v.
-Food security: Regulating financial markets to grow a better future.
-Oxfam policy and practice: agriculture, food and land 11, 127--138.
-
-\leavevmode\hypertarget{ref-hicks_value_1939}{}%
-Hicks, J.R., 1939. Value and capital, 1st ed. Oxford University Press, Cambridge.
-
-\leavevmode\hypertarget{ref-hicks_value_1946}{}%
-Hicks, J.R., 1946. Value and capital, 2nd ed. Oxford University Press, Cambridge.
-
-\leavevmode\hypertarget{ref-hirshleifer_speculation_1975}{}%
-Hirshleifer, J., 1975. Speculation and equilibrium: Information, risk, and markets. The Quarterly Journal of Economics 89, 519--542.
-
-\leavevmode\hypertarget{ref-hirshleifer_reply_1976}{}%
-Hirshleifer, J., 1976. Reply to comments on" speculation and equilibrium: Information, risk, and markets". The Quarterly Journal of Economics 689--696.
-
-\leavevmode\hypertarget{ref-hirshleifer_theory_1977}{}%
-Hirshleifer, J., 1977. The theory of speculation under alternative regimes of markets. The Journal of Finance 32, 975--999.
-
-\leavevmode\hypertarget{ref-hong_what_2012}{}%
-Hong, H., Yogo, M., 2012. What does futures market interest tell us about the macroeconomy and asset prices? Journal of Financial Economics 105, 473--490.
-
-\leavevmode\hypertarget{ref-hou_digesting_2015}{}%
-Hou, K., Xue, C., Zhang, L., 2015. Digesting anomalies: An investment approach. The Review of Financial Studies 28, 650--705.
-
-\leavevmode\hypertarget{ref-houthakker_restatement_1957}{}%
-Houthakker, H., 1957. Restatement of the theory of normal backwardation (Cowles Foundation Discussion Papers No. 44). Cowles Foundation for Research in Economics, Yale University.
-
-\leavevmode\hypertarget{ref-houthakker_speculators_1957}{}%
-Houthakker, H.S., 1957. Can speculators forecast prices? The Review of Economics and Statistics 39, 143--151.
-
-\leavevmode\hypertarget{ref-irwin_commodity_2013}{}%
-Irwin, S.H., 2013. Commodity index investment and food prices: Does the "masters hypothesis" explain recent price spikes? Agricultural Economics 44, 29--41.
-
-\leavevmode\hypertarget{ref-irwin_index_2011}{}%
-Irwin, S.H., Sanders, D.R., 2011. Index funds, financialization, and commodity futures markets. Applied Economic Perspectives and Policy 33, 1--31.
-
-\leavevmode\hypertarget{ref-irwin_financialisation_2012}{}%
-Irwin, S.H., Sanders, D.R., 2012. Financialization and structural change in commodity futures markets. Journal of Agricultural and Applied Economics 44, 371--396.
-
-\leavevmode\hypertarget{ref-irwin_devil_2009}{}%
-Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009. Devil or angel? The role of speculation in the recent commodity price boom (and bust). Journal of Agricultural and Applied Economics 41, 377--391.
-
-\leavevmode\hypertarget{ref-juvenal_speculation_2015}{}%
-Juvenal, L., Petrella, I., 2015. Speculation in the oil market. Journal of Applied Econometrics 30, 621--649.
-
-\leavevmode\hypertarget{ref-kaldor_speculation_1939}{}%
-Kaldor, N., 1939. Speculation and economic stability. The Review of Economic Studies 7, 1--27.
-
-\leavevmode\hypertarget{ref-kang_tale_2020}{}%
-Kang, W., Rouwenhorst, K.G., Tang, K., 2020. A tale of two premiums: The role of hedgers and speculators in commodity futures markets. The Journal of Finance 75, 377--417.
-
-\leavevmode\hypertarget{ref-keynes_some_1923}{}%
-Keynes, J.M., 1923. Some aspects of commodity markets. Manchester Guardian Commercial: European Reconstruction Series 13, 784--786.
-
-\leavevmode\hypertarget{ref-keynes_treatise_1930}{}%
-Keynes, J.M., 1930. Treatise on money. Macmillan, London.
-
-\leavevmode\hypertarget{ref-kilian_role_2014}{}%
-Kilian, L., Murphy, D.P., 2014. The role of inventories and speculative trading in the global market for crude oil. Journal of Applied Econometrics 29, 454--478.
-
-\leavevmode\hypertarget{ref-kim_does_2015}{}%
-Kim, A., 2015. Does futures speculation destabilize commodity markets? Journal of Futures Markets 35, 696--714.
-
-\leavevmode\hypertarget{ref-knittel_simple_2016}{}%
-Knittel, C.R., Pindyck, R.S., 2016. The simple economics of commodity price speculation. American Economic Journal: Macroeconomics 8, 85--110.
-
-\leavevmode\hypertarget{ref-kyle_informed_1989}{}%
-Kyle, A.S., 1989. Informed speculation with imperfect competition. The Review of Economic Studies 56, 317--355.
-
-\leavevmode\hypertarget{ref-leclercq_equilibrium_2014}{}%
-Leclercq, E., Praz, R., 2014. Equilibrium commodity trading (SSRN Scholarly Paper No. ID 2464400). Social Science Research Network, Rochester, NY.
-
-\leavevmode\hypertarget{ref-manera_modeling_2016}{}%
-Manera, M., Nicolini, M., Vignati, I., 2016. Modeling futures price volatility in energy markets: Is there a role for financial speculation? Energy Economics, Energy markets 53, 220--229.
-
-\leavevmode\hypertarget{ref-masters_testimony_2008}{}%
-Masters, M.W., 2008. Testimony before the committee on homeland security and governmental affairs. U.S. Senate 20.
-
-\leavevmode\hypertarget{ref-masters_accidental_2008}{}%
-Masters, M., White, A., 2008. The accidental hunt brothers: How institutional investors are driving up food and energy prices. Working paper.
-
-\leavevmode\hypertarget{ref-miffre_momentum_2007}{}%
-Miffre, J., Rallis, G., 2007. Momentum strategies in commodity futures markets. Journal of Banking \& Finance 31, 1863--1886.
-
-\leavevmode\hypertarget{ref-moskowitz_time_2012}{}%
-Moskowitz, T.J., Ooi, Y.H., Pedersen, L.H., 2012. Time series momentum. Journal of Financial Economics, Special issue on investor sentiment 104, 228--250.
-
-\leavevmode\hypertarget{ref-sakkas_factor_2020}{}%
-Sakkas, A., Tessaromatis, N., 2020. Factor based commodity investing. Journal of Banking \& Finance 115, 105807.
-
-\leavevmode\hypertarget{ref-sanders_impact_2011}{}%
-Sanders, D.R., Irwin, S.H., 2011a. The impact of index funds in commodity futures markets: A systems approach. The Journal of Alternative Investments 14, 40--49.
-
-\leavevmode\hypertarget{ref-sanders_new_2011}{}%
-Sanders, D.R., Irwin, S.H., 2011b. New evidence on the impact of index funds in u.s. Grain futures markets. Canadian Journal of Agricultural Economics/Revue canadienne d'agroeconomie 59, 519--532.
-
-\leavevmode\hypertarget{ref-sanders_adequacy_2010}{}%
-Sanders, D.R., Irwin, S.H., Merrin, R.P., 2010. The adequacy of speculation in agricultural futures markets: Too much of a good thing? Applied Economic Perspectives and Policy 32, 77--94.
-
-\leavevmode\hypertarget{ref-schumann_hunger_2011}{}%
-Schumann, H., 2011. The hunger-makers: How deutsche bank, goldman sachs and other financial institutions are speculating with food at the expense of the poorest. Foodwatch, Berlin.
-
-\leavevmode\hypertarget{ref-schwartz_stochastic_1997}{}%
-Schwartz, E.S., 1997. The stochastic behavior of commodity prices: Implications for valuation and hedging. The Journal of Finance 52, 923--973.
-
-\leavevmode\hypertarget{ref-schwartz_short_2000}{}%
-Schwartz, E., Smith, J.E., 2000. Short-term variations and long-term dynamics in commodity prices. Management Science 46, 893--911.
-
-\leavevmode\hypertarget{ref-senate_excessive_2009}{}%
-Senate, U.S., 2009. Excessive speculation in the wheat market. Majority and Minority Staff Report. Permanent Subcommittee on Investigations 24, 107--108.
-
-\leavevmode\hypertarget{ref-simsek_speculation_2013}{}%
-Simsek, A., 2013. Speculation and risk sharing with new financial assets. The Quarterly Journal of Economics 128, 1365--1396.
-
-\leavevmode\hypertarget{ref-singleton_investor_2013}{}%
-Singleton, K.J., 2013. Investor flows and the 2008 boom/bust in oil prices. Management Science 60, 300--318.
-
-\leavevmode\hypertarget{ref-sockin_informational_2015}{}%
-Sockin, M., Xiong, W., 2015. Informational frictions and commodity markets. The Journal of Finance 70, 2063--2098.
-
-\leavevmode\hypertarget{ref-stoll_commodity_2011}{}%
-Stoll, H.R., Whaley, R.E., 2011. Commodity index investing: Speculation or diversification? The Journal of Alternative Investments 14, 50--60.
-
-\leavevmode\hypertarget{ref-stout_why_1998}{}%
-Stout, L.A., 1998. Why the law hates speculators: Regulation and private ordering in the market for otc derivatives. Duke Law Journal 48, 701--786.
-
-\leavevmode\hypertarget{ref-stulz_rethink_1996}{}%
-Stulz, R.M., 1996. Rethinking risk management. Journal of Applied Corporate Finance 9, 8--25.
-
-\leavevmode\hypertarget{ref-szymanowska_anatomy_2014}{}%
-Szymanowska, M., De Roon, F., Nijman, T., Van Den Goorbergh, R., 2014. An anatomy of commodity futures risk premia. The Journal of Finance 69, 453--482.
-
-\leavevmode\hypertarget{ref-tang_index_2012}{}%
-Tang, K., Xiong, W., 2012. Index investment and the financialization of commodities. Financial Analysts Journal 68, 54--74.
-
-\leavevmode\hypertarget{ref-telser_futures_1958}{}%
-Telser, L.G., 1958. Futures trading and the storage of cotton and wheat. Journal of Political Economy 66, 233--255.
-
-\leavevmode\hypertarget{ref-till_long_2007}{}%
-Till, H., 2007. A long-term perspective on commodity futures returns, in: Intelligent Commodity Investing. Risk books, London.
-
-\leavevmode\hypertarget{ref-tokic_speculation_2012}{}%
-Tokic, D., 2012. Speculation and the 2008 oil bubble: The dcot report analysis. Energy Policy 45, 541--550.
-
-\leavevmode\hypertarget{ref-turnovsky_determination_1983}{}%
-Turnovsky, S.J., 1983. The determination of spot and futures prices with storable commodities. Econometrica 51, 1363--1387.
-
-\leavevmode\hypertarget{ref-unctad_global_2009}{}%
-UNCTAD, S.T.F. on S.I., Cooperation, E., 2009. The global economic crisis: Systemic failures and multilateral remedies. UNCTAD, Geneva.
-
-\leavevmode\hypertarget{ref-weymar_supply_1966}{}%
-Weymar, F.H., 1966. The supply of storage revisited. The American Economic Review 56, 1226--1234.
-
-\leavevmode\hypertarget{ref-working_price_1933}{}%
-Working, H., 1933. Price relations between july and september wheat futures at chicago since 1885. Wheat Studies 9, 187.
-
-\leavevmode\hypertarget{ref-working_theory_1948}{}%
-Working, H., 1948. Theory of the inverse carrying charge in futures markets. Journal of Farm Economics 30, 1--28.
-
-\leavevmode\hypertarget{ref-working_theory_1949}{}%
-Working, H., 1949. The theory of price of storage. The American Economic Review 1254--1262.
-
-\leavevmode\hypertarget{ref-working_hedging_1953}{}%
-Working, H., 1953. Hedging reconsidered. Journal of Farm Economics 35, 544--561.
-
-\leavevmode\hypertarget{ref-yang_investment_2013}{}%
-Yang, F., 2013. Investment shocks and the commodity basis spread. Journal of Financial Economics 110, 164--184.
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-buyuksahin_speculators_2014}{}}%
+\CSLLeftMargin{{[}1{]} }
+\CSLRightInline{Büyükşahin B, Robe MA.
+Speculators, commodities and cross-market linkages.
+Journal of International Money and Finance 2014;42:38--70.
+doi:\href{https://doi.org/10.1016/j.jimonfin.2013.08.004}{10.1016/j.jimonfin.2013.08.004}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-singleton_investor_2013}{}}%
+\CSLLeftMargin{{[}2{]} }
+\CSLRightInline{Singleton KJ. Investor flows and the 2008 boom/bust in oil prices. Management Science 2013;60:300--18. doi:\href{https://doi.org/10.1287/mnsc.2013.1756}{10.1287/mnsc.2013.1756}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-domanski_financial_2007}{}}%
+\CSLLeftMargin{{[}3{]} }
+\CSLRightInline{Domanski D, Heath A. \href{https://www.bis.org/publ/qtrpdf/r_qt0703g.pdf}{Financial investors and commodity markets}. Working Paper 2007.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-keynes_treatise_1930}{}}%
+\CSLLeftMargin{{[}4{]} }
+\CSLRightInline{Keynes JM. Treatise on money. Macmillan, London; 1930.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hicks_value_1939}{}}%
+\CSLLeftMargin{{[}5{]} }
+\CSLRightInline{Hicks JR. Value and capital. 1st ed. Oxford University Press, Cambridge; 1939.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fama_common_1993}{}}%
+\CSLLeftMargin{{[}6{]} }
+\CSLRightInline{Fama EF, French KR.
+Common risk factors in the returns on stocks and bonds.
+Journal of Financial Economics 1993;33:3--56.
+doi:\href{https://doi.org/10.1016/0304-405X(93)90023-5}{10.1016/0304-405X(93)90023-5}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carhart_persistence_1997}{}}%
+\CSLLeftMargin{{[}7{]} }
+\CSLRightInline{Carhart MM. On persistence in mutual fund performance. The Journal of Finance 1997;52:57--82. doi:\href{https://doi.org/10.2307/2329556}{10.2307/2329556}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-asness_devil_2013}{}}%
+\CSLLeftMargin{{[}8{]} }
+\CSLRightInline{Asness C, Frazzini A.
+The devil in HML{'}s details.
+The Journal of Portfolio Management 2013;39:49--68.
+doi:\href{https://doi.org/10.3905/jpm.2013.39.4.049}{10.3905/jpm.2013.39.4.049}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fama_five_factor_2015}{}}%
+\CSLLeftMargin{{[}9{]} }
+\CSLRightInline{Fama EF, French KR.
+A five-factor asset pricing model.
+Journal of Financial Economics 2015;116:1--22.
+doi:\href{https://doi.org/10.1016/j.jfineco.2014.10.010}{10.1016/j.jfineco.2014.10.010}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hou_digesting_2015}{}}%
+\CSLLeftMargin{{[}10{]} }
+\CSLRightInline{Hou K, Xue C, Zhang L.
+Digesting anomalies: An investment approach.
+The Review of Financial Studies 2015;28:650--705.
+doi:\href{https://doi.org/10.1093/rfs/hhu068}{10.1093/rfs/hhu068}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-asness_fact_2015}{}}%
+\CSLLeftMargin{{[}11{]} }
+\CSLRightInline{Asness C, Frazzini A, Israel R, Moskowitz T.
+Fact, fiction, and value investing.
+The Journal of Portfolio Management 2015;42:34--52.
+doi:\href{https://doi.org/10.3905/jpm.2015.42.1.034}{10.3905/jpm.2015.42.1.034}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-frazzini_betting_2014}{}}%
+\CSLLeftMargin{{[}12{]} }
+\CSLRightInline{Frazzini A, Pedersen LH. Betting against beta. Journal of Financial Economics 2014;111:1--25. doi:\href{https://doi.org/10.1016/j.jfineco.2013.10.005}{10.1016/j.jfineco.2013.10.005}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-asness_quality_2019}{}}%
+\CSLLeftMargin{{[}13{]} }
+\CSLRightInline{Asness CS, Frazzini A, Pedersen LH. Quality minus junk. Review of Accounting Studies 2019;24:34--112. doi:\href{https://doi.org/10.1007/s11142-018-9470-2}{10.1007/s11142-018-9470-2}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schwartz_short_2000}{}}%
+\CSLLeftMargin{{[}14{]} }
+\CSLRightInline{Schwartz E, Smith JE. \href{https://www.jstor.org/stable/2661607}{Short-term variations and long-term dynamics in commodity prices}. Management Science 2000;46:893--911.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-miffre_momentum_2007}{}}%
+\CSLLeftMargin{{[}15{]} }
+\CSLRightInline{Miffre J, Rallis G.
+Momentum strategies in commodity futures markets.
+Journal of Banking \& Finance 2007;31:1863--86.
+doi:\href{https://doi.org/10.1016/j.jbankfin.2006.12.005}{10.1016/j.jbankfin.2006.12.005}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gorton_fundamentals_2012}{}}%
+\CSLLeftMargin{{[}16{]} }
+\CSLRightInline{Gorton GB, Hayashi F, Rouwenhorst KG.
+The fundamentals of commodity futures returns.
+Review of Finance 2012;17:35--105.
+doi:\href{https://doi.org/10.1093/rof/rfs019}{10.1093/rof/rfs019}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cortazar_commodity_2013}{}}%
+\CSLLeftMargin{{[}17{]} }
+\CSLRightInline{Cortazar G, Kovacevic I, Schwartz ES. \href{https://ssrn.com/abstract=2287027}{Commodity and asset pricing models: An integration}. National Bureau of Economic Research, Inc; 2013.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-yang_investment_2013}{}}%
+\CSLLeftMargin{{[}18{]} }
+\CSLRightInline{Yang F.
+Investment shocks and the commodity basis spread.
+Journal of Financial Economics 2013;110:164--84.
+doi:\href{https://doi.org/10.1016/j.jfineco.2013.04.012}{10.1016/j.jfineco.2013.04.012}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-daskalaki_factors_2014}{}}%
+\CSLLeftMargin{{[}19{]} }
+\CSLRightInline{Daskalaki C, Kostakis A, Skiadopoulos G.
+Are there common factors in individual commodity futures returns?
+Journal of Banking {\&} Finance 2014;40:346--63.
+doi:\href{https://doi.org/10.1016/j.jbankfin.2013.11.034}{10.1016/j.jbankfin.2013.11.034}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-szymanowska_anatomy_2014}{}}%
+\CSLLeftMargin{{[}20{]} }
+\CSLRightInline{Szymanowska M, De Roon F, Nijman T, Van Den Goorbergh R.
+An anatomy of commodity futures risk premia.
+The Journal of Finance 2014;69:453--82.
+doi:\href{https://doi.org/10.1111/jofi.12096}{10.1111/jofi.12096}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fernandez_skewness_2018}{}}%
+\CSLLeftMargin{{[}21{]} }
+\CSLRightInline{Fernandez-Perez A, Frijns B, Fuertes A-M, Miffre J.
+The skewness of commodity futures returns.
+Journal of Banking \& Finance 2018;86:143--58.
+doi:\href{https://doi.org/10.1016/j.jbankfin.2017.06.015}{10.1016/j.jbankfin.2017.06.015}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bakshi_understanding_2019}{}}%
+\CSLLeftMargin{{[}22{]} }
+\CSLRightInline{Bakshi G, Gao X, Rossi AG.
+Understanding the sources of risk underlying the cross section of commodity returns.
+Management Science 2019;65:619--41.
+doi:\href{https://doi.org/10.1287/mnsc.2017.2840}{10.1287/mnsc.2017.2840}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-boons_basis_2019}{}}%
+\CSLLeftMargin{{[}23{]} }
+\CSLRightInline{Boons M, Prado MP. Basis-momentum. The Journal of Finance 2019;74:239--79. doi:\href{https://doi.org/10.1111/jofi.12738}{10.1111/jofi.12738}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sakkas_factor_2020}{}}%
+\CSLLeftMargin{{[}24{]} }
+\CSLRightInline{Sakkas A, Tessaromatis N.
+Factor based commodity investing.
+Journal of Banking \& Finance 2020;115:105807.
+doi:\href{https://doi.org/10.1016/j.jbankfin.2020.105807}{10.1016/j.jbankfin.2020.105807}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-keynes_some_1923}{}}%
+\CSLLeftMargin{{[}25{]} }
+\CSLRightInline{Keynes JM. Some aspects of commodity markets. Manchester Guardian Commercial: European Reconstruction Series 1923;13:784--6.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hicks_value_1946}{}}%
+\CSLLeftMargin{{[}26{]} }
+\CSLRightInline{Hicks JR. Value and capital. 2nd ed. Oxford University Press, Cambridge; 1946.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-houthakker_restatement_1957}{}}%
+\CSLLeftMargin{{[}27{]} }
+\CSLRightInline{Houthakker H.
+\href{https://EconPapers.repec.org/RePEc:cwl:cwldpp:44}{Restatement of the theory of normal backwardation}.
+Cowles Foundation for Research in Economics, Yale University; 1957.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cootner_returns_1960}{}}%
+\CSLLeftMargin{{[}28{]} }
+\CSLRightInline{Cootner PH. Returns to speculators: Telser versus keynes. Journal of Political Economy 1960;68:396--404. doi:\href{https://doi.org/10.1086/258347}{10.1086/258347}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-basu_capturing_2013}{}}%
+\CSLLeftMargin{{[}29{]} }
+\CSLRightInline{Basu D, Miffre J.
+Capturing the risk premium of commodity futures: The role of hedging pressure.
+Journal of Banking \& Finance 2013;37:2652--64.
+doi:\href{https://doi.org/10.1016/j.jbankfin.2013.02.031}{10.1016/j.jbankfin.2013.02.031}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cheng_financialisation_2014}{}}%
+\CSLLeftMargin{{[}30{]} }
+\CSLRightInline{Cheng I-H, Xiong W.
+Financialization of commodity markets.
+Annual Review of Financial Economics 2014;6:419--41.
+doi:\href{https://doi.org/10.1146/annurev-financial-110613-034432}{10.1146/annurev-financial-110613-034432}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-basak_model_2016}{}}%
+\CSLLeftMargin{{[}31{]} }
+\CSLRightInline{Basak S, Pavlova A. A model of financialization of commodities. The Journal of Finance 2016;71:1511--56. doi:\href{https://doi.org/10.1111/jofi.12408}{10.1111/jofi.12408}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hong_what_2012}{}}%
+\CSLLeftMargin{{[}32{]} }
+\CSLRightInline{Hong H, Yogo M.
+What does futures market interest tell us about the macroeconomy and asset prices?
+Journal of Financial Economics 2012;105:473--90.
+doi:\href{https://doi.org/10.1016/j.jfineco.2012.04.005}{10.1016/j.jfineco.2012.04.005}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-working_theory_1949}{}}%
+\CSLLeftMargin{{[}33{]} }
+\CSLRightInline{Working H. \href{https://www.jstor.org/stable/1816601}{The theory of price of storage}. The American Economic Review 1949:1254--62.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fuertes_commodity_2015}{}}%
+\CSLLeftMargin{{[}34{]} }
+\CSLRightInline{Fuertes A-M, Miffre J, Fernandez-Perez A.
+Commodity strategies based on momentum, term structure, and idiosyncratic volatility.
+Journal of Futures Markets 2015;35:274--97.
+doi:\href{https://doi.org/10.1002/fut.21656}{10.1002/fut.21656}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-baker_financialisation_2014}{}}%
+\CSLLeftMargin{{[}35{]} }
+\CSLRightInline{Baker SD. The financialization of storable commodities. Rochester, NY: Social Science Research Network; 2014. doi:\href{https://doi.org/10.2139/ssrn.2348333}{10.2139/ssrn.2348333}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-christoffersen_factor_2014}{}}%
+\CSLLeftMargin{{[}36{]} }
+\CSLRightInline{Christoffersen P, Lunde A, Olesen KV.
+Factor structure in commodity futures return and volatility.
+Journal of Financial and Quantitative Analysis 2014:1--74.
+doi:\href{https://doi.org/10.1017/S0022109018000765}{10.1017/S0022109018000765}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-moskowitz_time_2012}{}}%
+\CSLLeftMargin{{[}37{]} }
+\CSLRightInline{Moskowitz TJ, Ooi YH, Pedersen LH.
+Time series momentum.
+Journal of Financial Economics 2012;104:228--50.
+doi:\href{https://doi.org/10.1016/j.jfineco.2011.11.003}{10.1016/j.jfineco.2011.11.003}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kang_tale_2020}{}}%
+\CSLLeftMargin{{[}38{]} }
+\CSLRightInline{Kang W, Rouwenhorst KG, Tang K.
+A tale of two premiums: The role of hedgers and speculators in commodity futures markets.
+The Journal of Finance 2020;75:377--417.
+doi:\href{https://doi.org/10.1111/jofi.12845}{10.1111/jofi.12845}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-goldstein_speculation_2014}{}}%
+\CSLLeftMargin{{[}39{]} }
+\CSLRightInline{Goldstein I, Li Y, Yang L.
+Speculation and hedging in segmented markets.
+The Review of Financial Studies 2014;27:881--922.
+doi:\href{https://doi.org/10.1093/rfs/hht059}{10.1093/rfs/hht059}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-goldstein_commodity_2017}{}}%
+\CSLLeftMargin{{[}40{]} }
+\CSLRightInline{Goldstein I, Yang L.
+Commodity financialization and information transmission.
+Rochester, NY: Social Science Research Network; 2017.
+doi:\href{https://doi.org/10.2139/ssrn.2555996}{10.2139/ssrn.2555996}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-houthakker_speculators_1957}{}}%
+\CSLLeftMargin{{[}41{]} }
+\CSLRightInline{Houthakker HS. Can speculators forecast prices? The Review of Economics and Statistics 1957;39:143--51. doi:\href{https://doi.org/10.2307/1928531}{10.2307/1928531}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-telser_futures_1958}{}}%
+\CSLLeftMargin{{[}42{]} }
+\CSLRightInline{Telser LG. Futures trading and the storage of cotton and wheat. Journal of Political Economy 1958;66:233--55. doi:\href{https://doi.org/10.1086/258036}{10.1086/258036}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-working_price_1933}{}}%
+\CSLLeftMargin{{[}43{]} }
+\CSLRightInline{Working H.
+Price relations between july and september wheat futures at chicago since 1885.
+Wheat Studies 1933;9:187.
+doi:\href{https://doi.org/10.22004/ag.econ.142876}{10.22004/ag.econ.142876}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kaldor_speculation_1939}{}}%
+\CSLLeftMargin{{[}44{]} }
+\CSLRightInline{Kaldor N. {Speculation and economic stability}. The Review of Economic Studies 1939;7:1--27. doi:\href{https://doi.org/10.2307/2967593}{10.2307/2967593}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-working_theory_1948}{}}%
+\CSLLeftMargin{{[}45{]} }
+\CSLRightInline{Working H. Theory of the inverse carrying charge in futures markets. Journal of Farm Economics 1948;30:1--28. doi:\href{https://doi.org/10.2307/1232678}{10.2307/1232678}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-brennan_supply_1958}{}}%
+\CSLLeftMargin{{[}46{]} }
+\CSLRightInline{Brennan MJ. \href{https://www.jstor.org/stable/1812340}{The supply of storage}. The American Economic Review 1958;48:50--72.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-weymar_supply_1966}{}}%
+\CSLLeftMargin{{[}47{]} }
+\CSLRightInline{Weymar FH. \href{http://www.jstor.org/stable/1815306}{The supply of storage revisited}. The American Economic Review 1966;56:1226--34.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-danthine_information_1978}{}}%
+\CSLLeftMargin{{[}48{]} }
+\CSLRightInline{Danthine J-P.
+Information, futures prices, and stabilizing speculation.
+Journal of Economic Theory 1978;17:79--98.
+doi:\href{https://doi.org/10.1016/0022-0531(78)90124-2}{10.1016/0022-0531(78)90124-2}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-turnovsky_determination_1983}{}}%
+\CSLLeftMargin{{[}49{]} }
+\CSLRightInline{Turnovsky SJ. The determination of spot and futures prices with storable commodities. Econometrica 1983;51:1363--87. doi:\href{https://doi.org/10.2307/1912279}{10.2307/1912279}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schwartz_stochastic_1997}{}}%
+\CSLLeftMargin{{[}50{]} }
+\CSLRightInline{Schwartz ES.
+The stochastic behavior of commodity prices: Implications for valuation and hedging.
+The Journal of Finance 1997;52:923--73.
+doi:\href{https://doi.org/10.1111/j.1540-6261.1997.tb02721.x}{10.1111/j.1540-6261.1997.tb02721.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-basu_definancialisation}{}}%
+\CSLLeftMargin{{[}51{]} }
+\CSLRightInline{Basu D, Bauthéac O. Commodity definancialisation. Working Paper 2021.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-masters_testimony_2008}{}}%
+\CSLLeftMargin{{[}52{]} }
+\CSLRightInline{Masters MW. Testimony before the committee on homeland security and governmental affairs. US Senate 2008;20.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-masters_accidental_2008}{}}%
+\CSLLeftMargin{{[}53{]} }
+\CSLRightInline{Masters M, White A. The accidental hunt brothers: How institutional investors are driving up food and energy prices. Working Paper 2008.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-unctad_global_2009}{}}%
+\CSLLeftMargin{{[}54{]} }
+\CSLRightInline{UNCTAD STF on SI, Cooperation E.
+\href{https://unctad.org/system/files/official-document/gds20091_en.pdf}{The global economic crisis: Systemic failures and multilateral remedies}.
+UNCTAD, Geneva 2009.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-deschutter_food_2010}{}}%
+\CSLLeftMargin{{[}55{]} }
+\CSLRightInline{De Schutter O.
+\href{https://www2.ohchr.org/english/issues/food/docs/briefing_note_02_september_2010_en.pdf}{Food commodities speculation and food price crises: Regulation to reduce the risks of price volatility}.
+United Nations Special Rapporteur on the Right to Food Briefing Note 2010;2:1--4.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gilbert_how_2010}{}}%
+\CSLLeftMargin{{[}56{]} }
+\CSLRightInline{Gilbert CL.
+How to understand high food prices.
+Journal of Agricultural Economics 2010;61:398--425.
+doi:\href{https://doi.org/10.1111/j.1477-9552.2010.00248.x}{10.1111/j.1477-9552.2010.00248.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gilbert_speculative_2010}{}}%
+\CSLLeftMargin{{[}57{]} }
+\CSLRightInline{Gilbert CL.
+\href{https://www.cftc.gov/sites/default/files/idc/groups/public/@swaps/documents/file/plstudy_14_cifrem.pdf}{Speculative influences on commodity futures prices 2006-2008}.
+UNCTAD, Geneva 2010.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-herman_not_2011}{}}%
+\CSLLeftMargin{{[}58{]} }
+\CSLRightInline{Herman M-O, Kelly R, Nash R.
+\href{https://www.ingentaconnect.com/content/oxpp/oppafl/2011/00000011/00000007/art00005}{Not a game, speculation v.
+Food security: Regulating financial markets to grow a better future}.
+Oxfam Policy and Practice: Agriculture, Food and Land 2011;11:127--38.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schumann_hunger_2011}{}}%
+\CSLLeftMargin{{[}59{]} }
+\CSLRightInline{Schumann H.
+\href{https://www.foodwatch.org/uploads/media/foodwatchreport_TheHungerMakers_observationsandcallsforaction_ger_03.pdf}{The hunger-makers: How deutsche bank, goldman sachs and other financial institutions are speculating with food at the expense of the poorest}.
+Foodwatch, Berlin 2011.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-etula_broker-dealer_2013}{}}%
+\CSLLeftMargin{{[}60{]} }
+\CSLRightInline{Etula E.
+Broker-dealer risk appetite and commodity returns.
+Journal of Financial Econometrics 2013;11:486--521.
+doi:\href{https://doi.org/10.1093/jjfinec/nbs024}{10.1093/jjfinec/nbs024}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-acharya_limits_2013}{}}%
+\CSLLeftMargin{{[}61{]} }
+\CSLRightInline{Acharya VV, Lochstoer LA, Ramadorai T.
+Limits to arbitrage and hedging: Evidence from commodity markets.
+Journal of Financial Economics 2013;109:441--65.
+doi:\href{https://doi.org/10.1016/j.jfineco.2013.03.003}{10.1016/j.jfineco.2013.03.003}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cheng_convective_2014}{}}%
+\CSLLeftMargin{{[}62{]} }
+\CSLRightInline{Cheng I-H, Kirilenko A, Xiong W.
+Convective risk flows in commodity futures markets.
+Review of Finance 2014;19:1733--81.
+doi:\href{https://doi.org/10.1093/rof/rfu043}{10.1093/rof/rfu043}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-leclercq_equilibrium_2014}{}}%
+\CSLLeftMargin{{[}63{]} }
+\CSLRightInline{Leclercq E, Praz R. Equilibrium commodity trading. Rochester, NY: Social Science Research Network; 2014. doi:\href{https://doi.org/10.2139/ssrn.2464400}{10.2139/ssrn.2464400}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sockin_informational_2015}{}}%
+\CSLLeftMargin{{[}64{]} }
+\CSLRightInline{Sockin M, Xiong W. Informational frictions and commodity markets. The Journal of Finance 2015;70:2063--98. doi:\href{https://doi.org/10.1111/jofi.12261}{10.1111/jofi.12261}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ekeland_speculation_2016}{}}%
+\CSLLeftMargin{{[}65{]} }
+\CSLRightInline{Ekeland I, Lautier D, Villeneuve B. \href{https://hal.archives-ouvertes.fr/hal-01655848}{Speculation in commodity futures markets: A simple equilibrium model} 2016.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tang_index_2012}{}}%
+\CSLLeftMargin{{[}66{]} }
+\CSLRightInline{Tang K, Xiong W.
+Index investment and the financialization of commodities.
+Financial Analysts Journal 2012;68:54--74.
+doi:\href{https://doi.org/10.2469/faj.v68.n6.5}{10.2469/faj.v68.n6.5}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-senate_excessive_2009}{}}%
+\CSLLeftMargin{{[}67{]} }
+\CSLRightInline{Senate US.
+\href{https://www.hsgac.senate.gov/imo/media/doc/REPORTExcessiveSpecullationintheWheatMarketwoexhibitschartsJune2409.pdf?attempt=2}{Excessive speculation in the wheat market}.
+Majority and Minority Staff Report Permanent Subcommittee on Investigations 2009;24:107--8.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-irwin_devil_2009}{}}%
+\CSLLeftMargin{{[}68{]} }
+\CSLRightInline{Irwin SH, Sanders DR, Merrin RP.
+Devil or angel?
+The role of speculation in the recent commodity price boom (and bust).
+Journal of Agricultural and Applied Economics 2009;41:377--91.
+doi:\href{https://doi.org/10.1017/S1074070800002856}{10.1017/S1074070800002856}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sanders_adequacy_2010}{}}%
+\CSLLeftMargin{{[}69{]} }
+\CSLRightInline{Sanders DR, Irwin SH, Merrin RP.
+The adequacy of speculation in agricultural futures markets: Too much of a good thing?
+Applied Economic Perspectives and Policy 2010;32:77--94.
+doi:\href{https://doi.org/10.1093/aepp/ppp006}{10.1093/aepp/ppp006}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sanders_impact_2011}{}}%
+\CSLLeftMargin{{[}70{]} }
+\CSLRightInline{Sanders DR, Irwin SH.
+The impact of index funds in commodity futures markets: A systems approach.
+The Journal of Alternative Investments 2011;14:40--9.
+doi:\href{https://doi.org/10.3905/jai.2011.14.1.040}{10.3905/jai.2011.14.1.040}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sanders_new_2011}{}}%
+\CSLLeftMargin{{[}71{]} }
+\CSLRightInline{Sanders DR, Irwin SH.
+New evidence on the impact of index funds in u.s.
+Grain futures markets.
+Canadian Journal of Agricultural Economics/Revue Canadienne d'agroeconomie 2011;59:519--32.
+doi:\href{https://doi.org/10.1111/j.1744-7976.2011.01226.x}{10.1111/j.1744-7976.2011.01226.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-irwin_commodity_2013}{}}%
+\CSLLeftMargin{{[}72{]} }
+\CSLRightInline{Irwin SH.
+Commodity index investment and food prices: Does the "masters hypothesis" explain recent price spikes?
+Agricultural Economics 2013;44:29--41.
+doi:\href{https://doi.org/10.1111/agec.12048}{10.1111/agec.12048}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-brunetti_commodity_2014}{}}%
+\CSLLeftMargin{{[}73{]} }
+\CSLRightInline{Brunetti C, Reiffen D.
+Commodity index trading and hedging costs.
+Journal of Financial Markets 2014;21:153--80.
+doi:\href{https://doi.org/10.1016/j.finmar.2014.08.001}{10.1016/j.finmar.2014.08.001}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hamilton_effects_2015}{}}%
+\CSLLeftMargin{{[}74{]} }
+\CSLRightInline{Hamilton JD, Wu JC.
+Effects of index-fund investing on commodity futures prices.
+International Economic Review 2015;56:187--205.
+doi:\href{https://doi.org/10.1111/iere.12099}{10.1111/iere.12099}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bruno_financialisation_2017}{}}%
+\CSLLeftMargin{{[}75{]} }
+\CSLRightInline{Bruno VG, Büyükşahin B, Robe MA.
+The financialization of food?
+American Journal of Agricultural Economics 2017;99:243--64.
+doi:\href{https://doi.org/10.1093/ajae/aaw059}{10.1093/ajae/aaw059}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-buyuksahin_speculators_2011}{}}%
+\CSLLeftMargin{{[}76{]} }
+\CSLRightInline{Büyükşahin B, Harris JH. \href{https://www.jstor.org/stable/41323326}{Do speculators drive crude oil futures prices?} The Energy Journal 2011:167--202.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tokic_speculation_2012}{}}%
+\CSLLeftMargin{{[}77{]} }
+\CSLRightInline{Tokic D.
+Speculation and the 2008 oil bubble: The DCOT report analysis.
+Energy Policy 2012;45:541--50.
+doi:\href{https://doi.org/10.1016/j.enpol.2012.02.069}{10.1016/j.enpol.2012.02.069}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fattouh_role_2013}{}}%
+\CSLLeftMargin{{[}78{]} }
+\CSLRightInline{Fattouh B, Kilian L, Mahadeva L. \href{https://www.jstor.org/stable/41970495}{The role of speculation in oil markets: What have we learnt so far?} The Energy Journal 2013;34:7--33.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kilian_role_2014}{}}%
+\CSLLeftMargin{{[}79{]} }
+\CSLRightInline{Kilian L, Murphy DP.
+The role of inventories and speculative trading in the global market for crude oil.
+Journal of Applied Econometrics 2014;29:454--78.
+doi:\href{https://doi.org/10.1002/jae.2322}{10.1002/jae.2322}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-knittel_simple_2016}{}}%
+\CSLLeftMargin{{[}80{]} }
+\CSLRightInline{Knittel CR, Pindyck RS.
+The simple economics of commodity price speculation.
+American Economic Journal: Macroeconomics 2016;8:85--110.
+doi:\href{https://doi.org/10.1257/mac.20140033}{10.1257/mac.20140033}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-manera_modeling_2016}{}}%
+\CSLLeftMargin{{[}81{]} }
+\CSLRightInline{Manera M, Nicolini M, Vignati I.
+Modeling futures price volatility in energy markets: Is there a role for financial speculation?
+Energy Economics 2016;53:220--9.
+doi:\href{https://doi.org/10.1016/j.eneco.2014.07.001}{10.1016/j.eneco.2014.07.001}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bohl_does_2013}{}}%
+\CSLLeftMargin{{[}82{]} }
+\CSLRightInline{Bohl MT, Stephan PM.
+Does futures speculation destabilize spot prices?
+New evidence for commodity markets.
+Journal of Agricultural and Applied Economics 2013;45:595--616.
+doi:\href{https://doi.org/10.1017/S1074070800005150}{10.1017/S1074070800005150}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kim_does_2015}{}}%
+\CSLLeftMargin{{[}83{]} }
+\CSLRightInline{Kim A. Does futures speculation destabilize commodity markets? Journal of Futures Markets 2015;35:696--714. doi:\href{https://doi.org/10.1002/fut.21716}{10.1002/fut.21716}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-boyd_prevalence_2016}{}}%
+\CSLLeftMargin{{[}84{]} }
+\CSLRightInline{Boyd NE, Büyükşahin B, Haigh MS, Harris JH.
+The prevalence, sources, and effects of herding.
+Journal of Futures Markets 2016;36:671--94.
+doi:\href{https://doi.org/10.1002/fut.21756}{10.1002/fut.21756}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-irwin_index_2011}{}}%
+\CSLLeftMargin{{[}85{]} }
+\CSLRightInline{Irwin SH, Sanders DR.
+Index funds, financialization, and commodity futures markets.
+Applied Economic Perspectives and Policy 2011;33:1--31.
+doi:\href{https://doi.org/10.1093/aepp/ppq032}{10.1093/aepp/ppq032}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-irwin_financialisation_2012}{}}%
+\CSLLeftMargin{{[}86{]} }
+\CSLRightInline{Irwin SH, Sanders DR.
+Financialization and structural change in commodity futures markets.
+Journal of Agricultural and Applied Economics 2012;44:371--96.
+doi:\href{https://doi.org/10.1017/S1074070800000481}{10.1017/S1074070800000481}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stoll_commodity_2011}{}}%
+\CSLLeftMargin{{[}87{]} }
+\CSLRightInline{Stoll HR, Whaley RE.
+Commodity index investing: Speculation or diversification?
+The Journal of Alternative Investments 2011;14:50--60.
+doi:\href{https://doi.org/10.2139/ssrn.1633908}{10.2139/ssrn.1633908}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gilbert_role_2014}{}}%
+\CSLLeftMargin{{[}88{]} }
+\CSLRightInline{Gilbert CL, Pfuderer S.
+The role of index trading in price formation in the grains and oilseeds markets.
+Journal of Agricultural Economics 2014;65:303--22.
+doi:\href{https://doi.org/10.1111/1477-9552.12068}{10.1111/1477-9552.12068}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-juvenal_speculation_2015}{}}%
+\CSLLeftMargin{{[}89{]} }
+\CSLRightInline{Juvenal L, Petrella I. Speculation in the oil market. Journal of Applied Econometrics 2015;30:621--49. doi:\href{https://doi.org/10.1002/jae.2388}{10.1002/jae.2388}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-henderson_new_2015}{}}%
+\CSLLeftMargin{{[}90{]} }
+\CSLRightInline{Henderson BJ, Pearson ND, Wang L.
+New evidence on the financialization of commodity markets.
+The Review of Financial Studies 2015;28:1285--311.
+doi:\href{https://doi.org/10.1093/rfs/hhu091}{10.1093/rfs/hhu091}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-boons_stock_2012}{}}%
+\CSLLeftMargin{{[}91{]} }
+\CSLRightInline{Boons M, De Roon F, Szymanowska M.
+The stock market price of commodity risk.
+AFA 2012 chicago meetings paper, 2012.
+doi:\href{https://doi.org/10.2139/ssrn.1785728}{10.2139/ssrn.1785728}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ederington_who_2002}{}}%
+\CSLLeftMargin{{[}92{]} }
+\CSLRightInline{Ederington L, Lee JH.
+Who trades futures and how: Evidence from the heating oil futures market.
+The Journal of Business 2002;75:353--73.
+doi:\href{https://doi.org/10.1086/338706}{10.1086/338706}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-working_hedging_1953}{}}%
+\CSLLeftMargin{{[}93{]} }
+\CSLRightInline{Working H. Hedging reconsidered. Journal of Farm Economics 1953;35:544--61. doi:\href{https://doi.org/10.2307/1233368}{10.2307/1233368}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-till_long_2007}{}}%
+\CSLLeftMargin{{[}94{]} }
+\CSLRightInline{Till H. A long-term perspective on commodity futures returns. Intelligent commodity investing, London: Risk books; 2007.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-brunetti_speculators_2016}{}}%
+\CSLLeftMargin{{[}95{]} }
+\CSLRightInline{Brunetti C, Büyükşahin B, Harris JH.
+Speculators, prices, and market volatility.
+Journal of Financial and Quantitative Analysis 2016;51:1545--74.
+doi:\href{https://doi.org/10.1017/S0022109016000569}{10.1017/S0022109016000569}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stout_why_1998}{}}%
+\CSLLeftMargin{{[}96{]} }
+\CSLRightInline{Stout LA.
+Why the law hates speculators: Regulation and private ordering in the market for OTC derivatives.
+Duke Law Journal 1998;48:701--86.
+doi:\href{https://doi.org/10.2307/1373070}{10.2307/1373070}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-grossman_impossibility_1980}{}}%
+\CSLLeftMargin{{[}97{]} }
+\CSLRightInline{Grossman SJ, Stiglitz JE.
+On the impossibility of informationally efficient markets.
+The American Economic Review 1980;70:393--408.
+doi:\href{https://doi.org/10.7916/D8765R99}{10.7916/D8765R99}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kyle_informed_1989}{}}%
+\CSLLeftMargin{{[}98{]} }
+\CSLRightInline{Kyle AS. Informed speculation with imperfect competition. The Review of Economic Studies 1989;56:317--55. doi:\href{https://doi.org/10.2307/2297551}{10.2307/2297551}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stulz_rethink_1996}{}}%
+\CSLLeftMargin{{[}99{]} }
+\CSLRightInline{Stulz RM.
+Rethinking risk management.
+Journal of Applied Corporate Finance 1996;9:8--25.
+doi:\href{https://doi.org/10.1111/j.1745-6622.1996.tb00295.x}{10.1111/j.1745-6622.1996.tb00295.x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-simsek_speculation_2013}{}}%
+\CSLLeftMargin{{[}100{]} }
+\CSLRightInline{Simsek A.
+Speculation and risk sharing with new financial assets.
+The Quarterly Journal of Economics 2013;128:1365--96.
+doi:\href{https://doi.org/10.1093/qje/qjt007}{10.1093/qje/qjt007}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hirshleifer_speculation_1975}{}}%
+\CSLLeftMargin{{[}101{]} }
+\CSLRightInline{Hirshleifer J.
+Speculation and equilibrium: Information, risk, and markets.
+The Quarterly Journal of Economics 1975;89:519--42.
+doi:\href{https://doi.org/10.2307/1884690}{10.2307/1884690}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hirshleifer_reply_1976}{}}%
+\CSLLeftMargin{{[}102{]} }
+\CSLRightInline{Hirshleifer J.
+Reply to comments on" speculation and equilibrium: Information, risk, and markets".
+The Quarterly Journal of Economics 1976:689--96.
+doi:\href{https://doi.org/10.2307/1885330}{10.2307/1885330}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hirshleifer_theory_1977}{}}%
+\CSLLeftMargin{{[}103{]} }
+\CSLRightInline{Hirshleifer J. The theory of speculation under alternative regimes of markets. The Journal of Finance 1977;32:975--99. doi:\href{https://doi.org/10.2307/2326507}{10.2307/2326507}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-duffie_challenges_2014}{}}%
+\CSLLeftMargin{{[}104{]} }
+\CSLRightInline{Duffie D.
+Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs.
+The Journal of Legal Studies 2014;43:S173--82.
+doi:\href{https://doi.org/10.1086/677836}{10.1086/677836}.}
+
+\end{CSLReferences}
 

### 2022-06-29 docs/paper.Rmd
#8 update html version of paper

@@
 output:
-  bookdown::pdf_book:
-      pandoc_args: latex.yaml
-      base_format: rticles::elsevier_article
-      latex_engine: pdflatex
-      toc_depth: 3
-      includes:
-        in_header: preamble.tex
   bookdown::gitbook:
@@
       after_body: doc_suffix.html
+  bookdown::pdf_book:
+      pandoc_args: latex.yaml
+      base_format: rticles::elsevier_article
+      latex_engine: pdflatex
+      toc_depth: 3
+      includes:
+        in_header: preamble.tex
 ---

### 2022-06-30 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@ca3db49583e2692f90ba7c758c584e3c461560fb 🚀

--- 2022-05-26 docs/paper.tex
@@
 
-\newgeometry{a4paper,left=1in,right=1in,top=1in,bottom=1in,nohead}\savegeometry{tables}\restoregeometry
+\newgeometry{left=1in,right=1in,top=1in,bottom=1in,nohead}\savegeometry{tables}\restoregeometry
 
@@
 This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of market participation.\\
-Factor model techniques are well suited to isolating common driving factors and detecting co-movement (Asness and Frazzini, 2013; Asness et al., 2015, 2019; Carhart, 1997; Fama and French, 2015, 1993; Frazzini and Pedersen, 2014; Hou et al., 2015) at a broader level, beyond individual pairs of assets, and are commonly used to study commodity market fundamentals (Bakshi et al., 2019; Boons and Prado, 2019; Cortazar et al., 2013; Daskalaki et al., 2014; Fernandez-Perez et al., 2018; Gorton et al., 2012; Miffre and Rallis, 2007; Sakkas and Tessaromatis, 2020; Schwartz and Smith, 2000; Szymanowska et al., 2014; Yang, 2013); they consequently seem well adapted to study these two issues simultaneously.
+Factor model techniques are well suited to isolating common driving factors and detecting co-movement (Asness et al., 2015; Asness and Frazzini, 2013; Asness et al., 2019; Carhart, 1997; Fama and French, 2015, 1993; Frazzini and Pedersen, 2014; Hou et al., 2015) at a broader level, beyond individual pairs of assets, and are commonly used to study commodity market fundamentals (Bakshi et al., 2019; Boons and Prado, 2019; Cortazar et al., 2013; Daskalaki et al., 2014; Fernandez-Perez et al., 2018; Gorton et al., 2012; Miffre and Rallis, 2007; Sakkas and Tessaromatis, 2020; Schwartz and Smith, 2000; Szymanowska et al., 2014; Yang, 2013); they consequently seem well adapted to study these two issues simultaneously.
 Building on theory we therefore develop a bespoke commodity-based asset pricing framework comprised of factor models based both on fundamentals as well as liquidity considerations.\\
@@
 Houthakker, 1957), postulates that futures prices for a given commodity are inversely related to the extent that commercial hedgers are short or long and using commercial hedging pressure (CHP) as a proxy for hedgers net market position we construct factor mimicking portfolios that capture the impact of hedging pressure as a systemic factor (Basu and Miffre, 2013).
+The cross-sectional nature of financialisation (Basak and Pavlova, 2016; Cheng and Xiong, 2014) further leads us to extend this paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in Hong and Yogo (2012).
+In this context, returns for individual commodities should be high in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in periods where \textbf{CHP} is high (\textbf{contango}).
 Working's contending approach that relates futures price formation to storage costs in the theory of ``the price of storage'' (Working, 1949) forms the basis of another model that we consider where, following Szymanowska et al.
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-acharya_limits_2013}{}%
-Acharya, V.V., Lochstoer, L.A., Ramadorai, T., 2013. Limits to arbitrage and hedging: Evidence from commodity markets. Journal of Financial Economics 109, 441--465.
-
-\leavevmode\hypertarget{ref-asness_devil_2013}{}%
-Asness, C., Frazzini, A., 2013. The devil in hml's details. The Journal of Portfolio Management 39, 49--68.
-
-\leavevmode\hypertarget{ref-asness_fact_2015}{}%
-Asness, C., Frazzini, A., Israel, R., Moskowitz, T., 2015. Fact, fiction, and value investing. The Journal of Portfolio Management 42, 34--52.
-
-\leavevmode\hypertarget{ref-asness_quality_2019}{}%
-Asness, C.S., Frazzini, A., Pedersen, L.H., 2019. Quality minus junk. Review of Accounting Studies 24, 34--112.
-
-\leavevmode\hypertarget{ref-baker_financialisation_2014}{}%
-Baker, S.D., 2014. The financialization of storable commodities (SSRN Scholarly Paper No. ID 2348333). Social Science Research Network, Rochester, NY.
-
-\leavevmode\hypertarget{ref-bakshi_understanding_2019}{}%
-Bakshi, G., Gao, X., Rossi, A.G., 2019. Understanding the sources of risk underlying the cross section of commodity returns. Management Science 65, 619--641.
-
-\leavevmode\hypertarget{ref-basak_model_2016}{}%
-Basak, S., Pavlova, A., 2016. A model of financialization of commodities. The Journal of Finance 71, 1511--1556.
-
-\leavevmode\hypertarget{ref-basu_definancialisation}{}%
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-acharya_limits_2013}{}}%
+Acharya, V.V., Lochstoer, L.A., Ramadorai, T., 2013.
+\href{https://doi.org/10.1016/j.jfineco.2013.03.003}{Limits to arbitrage and hedging: Evidence from commodity markets}.
+Journal of Financial Economics 109, 441--465.
+
+\leavevmode\vadjust pre{\hypertarget{ref-asness_devil_2013}{}}%
+Asness, C., Frazzini, A., 2013. \href{https://doi.org/10.3905/jpm.2013.39.4.049}{The devil in HML{'}s details}. The Journal of Portfolio Management 39, 49--68.
+
+\leavevmode\vadjust pre{\hypertarget{ref-asness_fact_2015}{}}%
+Asness, C., Frazzini, A., Israel, R., Moskowitz, T., 2015. \href{https://doi.org/10.3905/jpm.2015.42.1.034}{Fact, fiction, and value investing}. The Journal of Portfolio Management 42, 34--52.
+
+\leavevmode\vadjust pre{\hypertarget{ref-asness_quality_2019}{}}%
+Asness, C.S., Frazzini, A., Pedersen, L.H., 2019. \href{https://doi.org/10.1007/s11142-018-9470-2}{Quality minus junk}. Review of Accounting Studies 24, 34--112.
+
+\leavevmode\vadjust pre{\hypertarget{ref-baker_financialisation_2014}{}}%
+Baker, S.D., 2014. \href{https://doi.org/10.2139/ssrn.2348333}{The financialization of storable commodities} (SSRN Scholarly Paper No. ID 2348333). Social Science Research Network, Rochester, NY.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bakshi_understanding_2019}{}}%
+Bakshi, G., Gao, X., Rossi, A.G., 2019.
+\href{https://doi.org/10.1287/mnsc.2017.2840}{Understanding the sources of risk underlying the cross section of commodity returns}.
+Management Science 65, 619--641.
+
+\leavevmode\vadjust pre{\hypertarget{ref-basak_model_2016}{}}%
+Basak, S., Pavlova, A., 2016. \href{https://doi.org/10.1111/jofi.12408}{A model of financialization of commodities}. The Journal of Finance 71, 1511--1556.
+
+\leavevmode\vadjust pre{\hypertarget{ref-basu_definancialisation}{}}%
 Basu, D., Bauthéac, O., 2021. Commodity definancialisation. Working paper.
 
-\leavevmode\hypertarget{ref-basu_capturing_2013}{}%
-Basu, D., Miffre, J., 2013. Capturing the risk premium of commodity futures: The role of hedging pressure. Journal of Banking \& Finance 37, 2652--2664.
-
-\leavevmode\hypertarget{ref-bohl_does_2013}{}%
-Bohl, M.T., Stephan, P.M., 2013. Does futures speculation destabilize spot prices? New evidence for commodity markets. Journal of Agricultural and Applied Economics 45, 595--616.
-
-\leavevmode\hypertarget{ref-boons_stock_2012}{}%
-Boons, M., De Roon, F., Szymanowska, M., 2012. The stock market price of commodity risk, in: AFA 2012 Chicago Meetings Paper.
-
-\leavevmode\hypertarget{ref-boons_basis_2019}{}%
-Boons, M., Prado, M.P., 2019. Basis-momentum. The Journal of Finance 74, 239--279.
-
-\leavevmode\hypertarget{ref-boyd_prevalence_2016}{}%
-Boyd, N.E., Büyükşahin, B., Haigh, M.S., Harris, J.H., 2016. The prevalence, sources, and effects of herding. Journal of Futures Markets 36, 671--694.
-
-\leavevmode\hypertarget{ref-brennan_supply_1958}{}%
-Brennan, M.J., 1958. The supply of storage. The American Economic Review 48, 50--72.
-
-\leavevmode\hypertarget{ref-brunetti_speculators_2016}{}%
-Brunetti, C., Büyükşahin, B., Harris, J.H., 2016. Speculators, prices, and market volatility. Journal of Financial and Quantitative Analysis 51, 1545--1574.
-
-\leavevmode\hypertarget{ref-brunetti_commodity_2014}{}%
-Brunetti, C., Reiffen, D., 2014. Commodity index trading and hedging costs. Journal of Financial Markets 21, 153--180.
-
-\leavevmode\hypertarget{ref-bruno_financialisation_2017}{}%
-Bruno, V.G., Büyükşahin, B., Robe, M.A., 2017. The financialization of food? American Journal of Agricultural Economics 99, 243--264.
-
-\leavevmode\hypertarget{ref-buyuksahin_speculators_2011}{}%
-Büyükşahin, B., Harris, J.H., 2011. Do speculators drive crude oil futures prices? The Energy Journal 167--202.
-
-\leavevmode\hypertarget{ref-buyuksahin_speculators_2014}{}%
-Büyükşahin, B., Robe, M.A., 2014. Speculators, commodities and cross-market linkages. Journal of International Money and Finance, Understanding international commodity price fluctuations 42, 38--70.
-
-\leavevmode\hypertarget{ref-carhart_persistence_1997}{}%
-Carhart, M.M., 1997. On persistence in mutual fund performance. The Journal of finance 52, 57--82.
-
-\leavevmode\hypertarget{ref-cheng_convective_2014}{}%
-Cheng, I.-H., Kirilenko, A., Xiong, W., 2014. Convective risk flows in commodity futures markets. Review of Finance 19, 1733--1781.
-
-\leavevmode\hypertarget{ref-cheng_financialisation_2014}{}%
-Cheng, I.-H., Xiong, W., 2014. Financialization of commodity markets. Annual Review of Financial Economics 6, 419--441.
-
-\leavevmode\hypertarget{ref-christoffersen_factor_2014}{}%
-Christoffersen, P., Lunde, A., Olesen, K.V., 2014. Factor structure in commodity futures return and volatility. Journal of Financial and Quantitative Analysis 1--74.
-
-\leavevmode\hypertarget{ref-cootner_returns_1960}{}%
-Cootner, P.H., 1960. Returns to speculators: Telser versus keynes. Journal of political Economy 68, 396--404.
-
-\leavevmode\hypertarget{ref-cortazar_commodity_2013}{}%
-Cortazar, G., Kovacevic, I., Schwartz, E.S., 2013. Commodity and asset pricing models: An integration (NBER Working Papers No. 19167). National Bureau of Economic Research, Inc.
-
-\leavevmode\hypertarget{ref-danthine_information_1978}{}%
-Danthine, J.-P., 1978. Information, futures prices, and stabilizing speculation. Journal of Economic Theory 17, 79--98.
-
-\leavevmode\hypertarget{ref-daskalaki_factors_2014}{}%
-Daskalaki, C., Kostakis, A., Skiadopoulos, G., 2014. Are there common factors in individual commodity futures returns? Journal of Banking \& Finance 40, 346--363.
-
-\leavevmode\hypertarget{ref-deschutter_food_2010}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-basu_capturing_2013}{}}%
+Basu, D., Miffre, J., 2013.
+\href{https://doi.org/10.1016/j.jbankfin.2013.02.031}{Capturing the risk premium of commodity futures: The role of hedging pressure}.
+Journal of Banking \& Finance 37, 2652--2664.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bohl_does_2013}{}}%
+Bohl, M.T., Stephan, P.M., 2013.
+\href{https://doi.org/10.1017/S1074070800005150}{Does futures speculation destabilize spot prices?
+New evidence for commodity markets}.
+Journal of Agricultural and Applied Economics 45, 595--616.
+
+\leavevmode\vadjust pre{\hypertarget{ref-boons_stock_2012}{}}%
+Boons, M., De Roon, F., Szymanowska, M., 2012. \href{https://doi.org/10.2139/ssrn.1785728}{The stock market price of commodity risk}, in: AFA 2012 Chicago Meetings Paper.
+
+\leavevmode\vadjust pre{\hypertarget{ref-boons_basis_2019}{}}%
+Boons, M., Prado, M.P., 2019. \href{https://doi.org/10.1111/jofi.12738}{Basis-momentum}. The Journal of Finance 74, 239--279.
+
+\leavevmode\vadjust pre{\hypertarget{ref-boyd_prevalence_2016}{}}%
+Boyd, N.E., Büyükşahin, B., Haigh, M.S., Harris, J.H., 2016. \href{https://doi.org/10.1002/fut.21756}{The prevalence, sources, and effects of herding}. Journal of Futures Markets 36, 671--694.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brennan_supply_1958}{}}%
+Brennan, M.J., 1958. \href{https://www.jstor.org/stable/1812340}{The supply of storage}. The American Economic Review 48, 50--72.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brunetti_speculators_2016}{}}%
+Brunetti, C., Büyükşahin, B., Harris, J.H., 2016.
+\href{https://doi.org/10.1017/S0022109016000569}{Speculators, prices, and market volatility}.
+Journal of Financial and Quantitative Analysis 51, 1545--1574.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brunetti_commodity_2014}{}}%
+Brunetti, C., Reiffen, D., 2014. \href{https://doi.org/10.1016/j.finmar.2014.08.001}{Commodity index trading and hedging costs}. Journal of Financial Markets 21, 153--180.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bruno_financialisation_2017}{}}%
+Bruno, V.G., Büyükşahin, B., Robe, M.A., 2017. \href{https://doi.org/10.1093/ajae/aaw059}{The financialization of food?} American Journal of Agricultural Economics 99, 243--264.
+
+\leavevmode\vadjust pre{\hypertarget{ref-buyuksahin_speculators_2011}{}}%
+Büyükşahin, B., Harris, J.H., 2011. \href{https://www.jstor.org/stable/41323326}{Do speculators drive crude oil futures prices?} The Energy Journal 167--202.
+
+\leavevmode\vadjust pre{\hypertarget{ref-buyuksahin_speculators_2014}{}}%
+Büyükşahin, B., Robe, M.A., 2014.
+\href{https://doi.org/10.1016/j.jimonfin.2013.08.004}{Speculators, commodities and cross-market linkages}.
+Journal of International Money and Finance, Understanding international commodity price fluctuations 42, 38--70.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carhart_persistence_1997}{}}%
+Carhart, M.M., 1997. \href{https://doi.org/10.2307/2329556}{On persistence in mutual fund performance}. The Journal of finance 52, 57--82.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cheng_convective_2014}{}}%
+Cheng, I.-H., Kirilenko, A., Xiong, W., 2014. \href{https://doi.org/10.1093/rof/rfu043}{Convective risk flows in commodity futures markets}. Review of Finance 19, 1733--1781.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cheng_financialisation_2014}{}}%
+Cheng, I.-H., Xiong, W., 2014. \href{https://doi.org/10.1146/annurev-financial-110613-034432}{Financialization of commodity markets}. Annual Review of Financial Economics 6, 419--441.
+
+\leavevmode\vadjust pre{\hypertarget{ref-christoffersen_factor_2014}{}}%
+Christoffersen, P., Lunde, A., Olesen, K.V., 2014.
+\href{https://doi.org/10.1017/S0022109018000765}{Factor structure in commodity futures return and volatility}.
+Journal of Financial and Quantitative Analysis 1--74.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cootner_returns_1960}{}}%
+Cootner, P.H., 1960. \href{https://doi.org/10.1086/258347}{Returns to speculators: Telser versus keynes}. Journal of political Economy 68, 396--404.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cortazar_commodity_2013}{}}%
+Cortazar, G., Kovacevic, I., Schwartz, E.S., 2013.
+\href{https://ssrn.com/abstract=2287027}{Commodity and asset pricing models: An integration} (NBER Working Papers No.
+19167).
+National Bureau of Economic Research, Inc.
+
+\leavevmode\vadjust pre{\hypertarget{ref-danthine_information_1978}{}}%
+Danthine, J.-P., 1978. \href{https://doi.org/10.1016/0022-0531(78)90124-2}{Information, futures prices, and stabilizing speculation}. Journal of Economic Theory 17, 79--98.
+
+\leavevmode\vadjust pre{\hypertarget{ref-daskalaki_factors_2014}{}}%
+Daskalaki, C., Kostakis, A., Skiadopoulos, G., 2014.
+\href{https://doi.org/10.1016/j.jbankfin.2013.11.034}{Are there common factors in individual commodity futures returns?} Journal of Banking {\&} Finance 40, 346--363.
+
+\leavevmode\vadjust pre{\hypertarget{ref-deschutter_food_2010}{}}%
 De Schutter, O., 2010.
-Food commodities speculation and food price crises: Regulation to reduce the risks of price volatility.
+\href{https://www2.ohchr.org/english/issues/food/docs/briefing_note_02_september_2010_en.pdf}{Food commodities speculation and food price crises: Regulation to reduce the risks of price volatility}.
 United Nations Special Rapporteur on the Right to Food Briefing Note 2, 1--14.
 
-\leavevmode\hypertarget{ref-domanski_financial_2007}{}%
-Domanski, D., Heath, A., 2007. Financial investors and commodity markets. Working Paper.
-
-\leavevmode\hypertarget{ref-duffie_challenges_2014}{}%
-Duffie, D., 2014. Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs. The Journal of Legal Studies 43, S173--S182.
-
-\leavevmode\hypertarget{ref-ederington_who_2002}{}%
-Ederington, L., Lee, J.H., 2002. Who trades futures and how: Evidence from the heating oil futures market. The Journal of Business 75, 353--373.
-
-\leavevmode\hypertarget{ref-ekeland_speculation_2016}{}%
-Ekeland, I., Lautier, D., Villeneuve, B., 2016. Speculation in commodity futures markets: A simple equilibrium model.
-
-\leavevmode\hypertarget{ref-etula_broker-dealer_2013}{}%
-Etula, E., 2013. Broker-dealer risk appetite and commodity returns. Journal of Financial Econometrics 11, 486--521.
-
-\leavevmode\hypertarget{ref-fama_common_1993}{}%
-Fama, E.F., French, K.R., 1993. Common risk factors in the returns on stocks and bonds. Journal of Financial Economics 33, 3--56.
-
-\leavevmode\hypertarget{ref-fama_five_factor_2015}{}%
-Fama, E.F., French, K.R., 2015. A five-factor asset pricing model. Journal of Financial Economics 116, 1--22.
-
-\leavevmode\hypertarget{ref-fattouh_role_2013}{}%
-Fattouh, B., Kilian, L., Mahadeva, L., 2013. The role of speculation in oil markets: What have we learnt so far? The Energy Journal 34, 7--33.
-
-\leavevmode\hypertarget{ref-fernandez_skewness_2018}{}%
-Fernandez-Perez, A., Frijns, B., Fuertes, A.-M., Miffre, J., 2018. The skewness of commodity futures returns. Journal of Banking \& Finance 86, 143--158.
-
-\leavevmode\hypertarget{ref-frazzini_betting_2014}{}%
-Frazzini, A., Pedersen, L.H., 2014. Betting against beta. Journal of Financial Economics 111, 1--25.
-
-\leavevmode\hypertarget{ref-fuertes_commodity_2015}{}%
-Fuertes, A.-M., Miffre, J., Fernandez-Perez, A., 2015. Commodity strategies based on momentum, term structure, and idiosyncratic volatility. Journal of Futures Markets 35, 274--297.
-
-\leavevmode\hypertarget{ref-gilbert_how_2010}{}%
-Gilbert, C.L., 2010a. How to understand high food prices. Journal of Agricultural Economics 61, 398--425.
-
-\leavevmode\hypertarget{ref-gilbert_speculative_2010}{}%
-Gilbert, C.L., 2010b. Speculative influences on commodity futures prices 2006-2008. UNCTAD, Geneva.
-
-\leavevmode\hypertarget{ref-gilbert_role_2014}{}%
-Gilbert, C.L., Pfuderer, S., 2014. The role of index trading in price formation in the grains and oilseeds markets. Journal of Agricultural Economics 65, 303--322.
-
-\leavevmode\hypertarget{ref-goldstein_speculation_2014}{}%
-Goldstein, I., Li, Y., Yang, L., 2014. Speculation and hedging in segmented markets. The Review of Financial Studies 27, 881--922.
-
-\leavevmode\hypertarget{ref-goldstein_commodity_2017}{}%
-Goldstein, I., Yang, L., 2017. Commodity financialization and information transmission (SSRN Scholarly Paper No. ID 2555996). Social Science Research Network, Rochester, NY.
-
-\leavevmode\hypertarget{ref-gorton_fundamentals_2012}{}%
-Gorton, G.B., Hayashi, F., Rouwenhorst, K.G., 2012. The fundamentals of commodity futures returns. Review of Finance 17, 35--105.
-
-\leavevmode\hypertarget{ref-grossman_impossibility_1980}{}%
-Grossman, S.J., Stiglitz, J.E., 1980. On the impossibility of informationally efficient markets. The American economic review 70, 393--408.
-
-\leavevmode\hypertarget{ref-hamilton_effects_2015}{}%
-Hamilton, J.D., Wu, J.C., 2015. Effects of index-fund investing on commodity futures prices. International Economic Review 56, 187--205.
-
-\leavevmode\hypertarget{ref-henderson_new_2015}{}%
-Henderson, B.J., Pearson, N.D., Wang, L., 2015. New evidence on the financialization of commodity markets. The Review of Financial Studies 28, 1285--1311.
-
-\leavevmode\hypertarget{ref-herman_not_2011}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-domanski_financial_2007}{}}%
+Domanski, D., Heath, A., 2007. \href{https://www.bis.org/publ/qtrpdf/r_qt0703g.pdf}{Financial investors and commodity markets}. Working Paper.
+
+\leavevmode\vadjust pre{\hypertarget{ref-duffie_challenges_2014}{}}%
+Duffie, D., 2014. \href{https://doi.org/10.1086/677836}{Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs}. The Journal of Legal Studies 43, S173--S182.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ederington_who_2002}{}}%
+Ederington, L., Lee, J.H., 2002. \href{https://doi.org/10.1086/338706}{Who trades futures and how: Evidence from the heating oil futures market}. The Journal of Business 75, 353--373.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ekeland_speculation_2016}{}}%
+Ekeland, I., Lautier, D., Villeneuve, B., 2016. \href{https://hal.archives-ouvertes.fr/hal-01655848}{Speculation in commodity futures markets: A simple equilibrium model}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-etula_broker-dealer_2013}{}}%
+Etula, E., 2013. \href{https://doi.org/10.1093/jjfinec/nbs024}{Broker-dealer risk appetite and commodity returns}. Journal of Financial Econometrics 11, 486--521.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fama_common_1993}{}}%
+Fama, E.F., French, K.R., 1993. \href{https://doi.org/10.1016/0304-405X(93)90023-5}{Common risk factors in the returns on stocks and bonds}. Journal of Financial Economics 33, 3--56.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fama_five_factor_2015}{}}%
+Fama, E.F., French, K.R., 2015. \href{https://doi.org/10.1016/j.jfineco.2014.10.010}{A five-factor asset pricing model}. Journal of Financial Economics 116, 1--22.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fattouh_role_2013}{}}%
+Fattouh, B., Kilian, L., Mahadeva, L., 2013. \href{https://www.jstor.org/stable/41970495}{The role of speculation in oil markets: What have we learnt so far?} The Energy Journal 34, 7--33.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fernandez_skewness_2018}{}}%
+Fernandez-Perez, A., Frijns, B., Fuertes, A.-M., Miffre, J., 2018.
+\href{https://doi.org/10.1016/j.jbankfin.2017.06.015}{The skewness of commodity futures returns}.
+Journal of Banking \& Finance 86, 143--158.
+
+\leavevmode\vadjust pre{\hypertarget{ref-frazzini_betting_2014}{}}%
+Frazzini, A., Pedersen, L.H., 2014. \href{https://doi.org/10.1016/j.jfineco.2013.10.005}{Betting against beta}. Journal of Financial Economics 111, 1--25.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fuertes_commodity_2015}{}}%
+Fuertes, A.-M., Miffre, J., Fernandez-Perez, A., 2015.
+\href{https://doi.org/10.1002/fut.21656}{Commodity strategies based on momentum, term structure, and idiosyncratic volatility}.
+Journal of Futures Markets 35, 274--297.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gilbert_how_2010}{}}%
+Gilbert, C.L., 2010a. \href{https://doi.org/10.1111/j.1477-9552.2010.00248.x}{How to understand high food prices}. Journal of Agricultural Economics 61, 398--425.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gilbert_speculative_2010}{}}%
+Gilbert, C.L., 2010b.
+\href{https://www.cftc.gov/sites/default/files/idc/groups/public/@swaps/documents/file/plstudy_14_cifrem.pdf}{Speculative influences on commodity futures prices 2006-2008}.
+UNCTAD, Geneva.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gilbert_role_2014}{}}%
+Gilbert, C.L., Pfuderer, S., 2014.
+\href{https://doi.org/10.1111/1477-9552.12068}{The role of index trading in price formation in the grains and oilseeds markets}.
+Journal of Agricultural Economics 65, 303--322.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goldstein_speculation_2014}{}}%
+Goldstein, I., Li, Y., Yang, L., 2014. \href{https://doi.org/10.1093/rfs/hht059}{Speculation and hedging in segmented markets}. The Review of Financial Studies 27, 881--922.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goldstein_commodity_2017}{}}%
+Goldstein, I., Yang, L., 2017.
+\href{https://doi.org/10.2139/ssrn.2555996}{Commodity financialization and information transmission} (SSRN Scholarly Paper No.
+ID 2555996).
+Social Science Research Network, Rochester, NY.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gorton_fundamentals_2012}{}}%
+Gorton, G.B., Hayashi, F., Rouwenhorst, K.G., 2012. \href{https://doi.org/10.1093/rof/rfs019}{The fundamentals of commodity futures returns}. Review of Finance 17, 35--105.
+
+\leavevmode\vadjust pre{\hypertarget{ref-grossman_impossibility_1980}{}}%
+Grossman, S.J., Stiglitz, J.E., 1980. \href{https://doi.org/10.7916/D8765R99}{On the impossibility of informationally efficient markets}. The American economic review 70, 393--408.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hamilton_effects_2015}{}}%
+Hamilton, J.D., Wu, J.C., 2015. \href{https://doi.org/10.1111/iere.12099}{Effects of index-fund investing on commodity futures prices}. International Economic Review 56, 187--205.
+
+\leavevmode\vadjust pre{\hypertarget{ref-henderson_new_2015}{}}%
+Henderson, B.J., Pearson, N.D., Wang, L., 2015. \href{https://doi.org/10.1093/rfs/hhu091}{New evidence on the financialization of commodity markets}. The Review of Financial Studies 28, 1285--1311.
+
+\leavevmode\vadjust pre{\hypertarget{ref-herman_not_2011}{}}%
 Herman, M.-O., Kelly, R., Nash, R., 2011.
-Not a game, speculation v.
-Food security: Regulating financial markets to grow a better future.
+\href{https://www.ingentaconnect.com/content/oxpp/oppafl/2011/00000011/00000007/art00005}{Not a game, speculation v.
+Food security: Regulating financial markets to grow a better future}.
 Oxfam policy and practice: agriculture, food and land 11, 127--138.
 
-\leavevmode\hypertarget{ref-hicks_value_1939}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hicks_value_1939}{}}%
 Hicks, J.R., 1939. Value and capital, 1st ed. Oxford University Press, Cambridge.
 
-\leavevmode\hypertarget{ref-hicks_value_1946}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hicks_value_1946}{}}%
 Hicks, J.R., 1946. Value and capital, 2nd ed. Oxford University Press, Cambridge.
 
-\leavevmode\hypertarget{ref-hirshleifer_speculation_1975}{}%
-Hirshleifer, J., 1975. Speculation and equilibrium: Information, risk, and markets. The Quarterly Journal of Economics 89, 519--542.
-
-\leavevmode\hypertarget{ref-hirshleifer_reply_1976}{}%
-Hirshleifer, J., 1976. Reply to comments on" speculation and equilibrium: Information, risk, and markets". The Quarterly Journal of Economics 689--696.
-
-\leavevmode\hypertarget{ref-hirshleifer_theory_1977}{}%
-Hirshleifer, J., 1977. The theory of speculation under alternative regimes of markets. The Journal of Finance 32, 975--999.
-
-\leavevmode\hypertarget{ref-hong_what_2012}{}%
-Hong, H., Yogo, M., 2012. What does futures market interest tell us about the macroeconomy and asset prices? Journal of Financial Economics 105, 473--490.
-
-\leavevmode\hypertarget{ref-hou_digesting_2015}{}%
-Hou, K., Xue, C., Zhang, L., 2015. Digesting anomalies: An investment approach. The Review of Financial Studies 28, 650--705.
-
-\leavevmode\hypertarget{ref-houthakker_restatement_1957}{}%
-Houthakker, H., 1957. Restatement of the theory of normal backwardation (Cowles Foundation Discussion Papers No. 44). Cowles Foundation for Research in Economics, Yale University.
-
-\leavevmode\hypertarget{ref-houthakker_speculators_1957}{}%
-Houthakker, H.S., 1957. Can speculators forecast prices? The Review of Economics and Statistics 39, 143--151.
-
-\leavevmode\hypertarget{ref-irwin_commodity_2013}{}%
-Irwin, S.H., 2013. Commodity index investment and food prices: Does the "masters hypothesis" explain recent price spikes? Agricultural Economics 44, 29--41.
-
-\leavevmode\hypertarget{ref-irwin_index_2011}{}%
-Irwin, S.H., Sanders, D.R., 2011. Index funds, financialization, and commodity futures markets. Applied Economic Perspectives and Policy 33, 1--31.
-
-\leavevmode\hypertarget{ref-irwin_financialisation_2012}{}%
-Irwin, S.H., Sanders, D.R., 2012. Financialization and structural change in commodity futures markets. Journal of Agricultural and Applied Economics 44, 371--396.
-
-\leavevmode\hypertarget{ref-irwin_devil_2009}{}%
-Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009. Devil or angel? The role of speculation in the recent commodity price boom (and bust). Journal of Agricultural and Applied Economics 41, 377--391.
-
-\leavevmode\hypertarget{ref-juvenal_speculation_2015}{}%
-Juvenal, L., Petrella, I., 2015. Speculation in the oil market. Journal of Applied Econometrics 30, 621--649.
-
-\leavevmode\hypertarget{ref-kaldor_speculation_1939}{}%
-Kaldor, N., 1939. Speculation and economic stability. The Review of Economic Studies 7, 1--27.
-
-\leavevmode\hypertarget{ref-kang_tale_2020}{}%
-Kang, W., Rouwenhorst, K.G., Tang, K., 2020. A tale of two premiums: The role of hedgers and speculators in commodity futures markets. The Journal of Finance 75, 377--417.
-
-\leavevmode\hypertarget{ref-keynes_some_1923}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hirshleifer_speculation_1975}{}}%
+Hirshleifer, J., 1975. \href{https://doi.org/10.2307/1884690}{Speculation and equilibrium: Information, risk, and markets}. The Quarterly Journal of Economics 89, 519--542.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hirshleifer_reply_1976}{}}%
+Hirshleifer, J., 1976. \href{https://doi.org/10.2307/1885330}{Reply to comments on" speculation and equilibrium: Information, risk, and markets"}. The Quarterly Journal of Economics 689--696.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hirshleifer_theory_1977}{}}%
+Hirshleifer, J., 1977. \href{https://doi.org/10.2307/2326507}{The theory of speculation under alternative regimes of markets}. The Journal of Finance 32, 975--999.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hong_what_2012}{}}%
+Hong, H., Yogo, M., 2012.
+\href{https://doi.org/10.1016/j.jfineco.2012.04.005}{What does futures market interest tell us about the macroeconomy and asset prices?} Journal of Financial Economics 105, 473--490.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hou_digesting_2015}{}}%
+Hou, K., Xue, C., Zhang, L., 2015. \href{https://doi.org/10.1093/rfs/hhu068}{Digesting anomalies: An investment approach}. The Review of Financial Studies 28, 650--705.
+
+\leavevmode\vadjust pre{\hypertarget{ref-houthakker_restatement_1957}{}}%
+Houthakker, H., 1957.
+\href{https://EconPapers.repec.org/RePEc:cwl:cwldpp:44}{Restatement of the theory of normal backwardation} (Cowles Foundation Discussion Papers No.
+44).
+Cowles Foundation for Research in Economics, Yale University.
+
+\leavevmode\vadjust pre{\hypertarget{ref-houthakker_speculators_1957}{}}%
+Houthakker, H.S., 1957. \href{https://doi.org/10.2307/1928531}{Can speculators forecast prices?} The Review of Economics and Statistics 39, 143--151.
+
+\leavevmode\vadjust pre{\hypertarget{ref-irwin_commodity_2013}{}}%
+Irwin, S.H., 2013. \href{https://doi.org/10.1111/agec.12048}{Commodity index investment and food prices: Does the "masters hypothesis" explain recent price spikes?} Agricultural Economics 44, 29--41.
+
+\leavevmode\vadjust pre{\hypertarget{ref-irwin_index_2011}{}}%
+Irwin, S.H., Sanders, D.R., 2011. \href{https://doi.org/10.1093/aepp/ppq032}{Index funds, financialization, and commodity futures markets}. Applied Economic Perspectives and Policy 33, 1--31.
+
+\leavevmode\vadjust pre{\hypertarget{ref-irwin_financialisation_2012}{}}%
+Irwin, S.H., Sanders, D.R., 2012.
+\href{https://doi.org/10.1017/S1074070800000481}{Financialization and structural change in commodity futures markets}.
+Journal of Agricultural and Applied Economics 44, 371--396.
+
+\leavevmode\vadjust pre{\hypertarget{ref-irwin_devil_2009}{}}%
+Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009.
+\href{https://doi.org/10.1017/S1074070800002856}{Devil or angel?
+The role of speculation in the recent commodity price boom (and bust)}.
+Journal of Agricultural and Applied Economics 41, 377--391.
+
+\leavevmode\vadjust pre{\hypertarget{ref-juvenal_speculation_2015}{}}%
+Juvenal, L., Petrella, I., 2015. \href{https://doi.org/10.1002/jae.2388}{Speculation in the oil market}. Journal of Applied Econometrics 30, 621--649.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kaldor_speculation_1939}{}}%
+Kaldor, N., 1939. \href{https://doi.org/10.2307/2967593}{{Speculation and economic stability}}. The Review of Economic Studies 7, 1--27.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kang_tale_2020}{}}%
+Kang, W., Rouwenhorst, K.G., Tang, K., 2020.
+\href{https://doi.org/10.1111/jofi.12845}{A tale of two premiums: The role of hedgers and speculators in commodity futures markets}.
+The Journal of Finance 75, 377--417.
+
+\leavevmode\vadjust pre{\hypertarget{ref-keynes_some_1923}{}}%
 Keynes, J.M., 1923. Some aspects of commodity markets. Manchester Guardian Commercial: European Reconstruction Series 13, 784--786.
 
-\leavevmode\hypertarget{ref-keynes_treatise_1930}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-keynes_treatise_1930}{}}%
 Keynes, J.M., 1930. Treatise on money. Macmillan, London.
 
-\leavevmode\hypertarget{ref-kilian_role_2014}{}%
-Kilian, L., Murphy, D.P., 2014. The role of inventories and speculative trading in the global market for crude oil. Journal of Applied Econometrics 29, 454--478.
-
-\leavevmode\hypertarget{ref-kim_does_2015}{}%
-Kim, A., 2015. Does futures speculation destabilize commodity markets? Journal of Futures Markets 35, 696--714.
-
-\leavevmode\hypertarget{ref-knittel_simple_2016}{}%
-Knittel, C.R., Pindyck, R.S., 2016. The simple economics of commodity price speculation. American Economic Journal: Macroeconomics 8, 85--110.
-
-\leavevmode\hypertarget{ref-kyle_informed_1989}{}%
-Kyle, A.S., 1989. Informed speculation with imperfect competition. The Review of Economic Studies 56, 317--355.
-
-\leavevmode\hypertarget{ref-leclercq_equilibrium_2014}{}%
-Leclercq, E., Praz, R., 2014. Equilibrium commodity trading (SSRN Scholarly Paper No. ID 2464400). Social Science Research Network, Rochester, NY.
-
-\leavevmode\hypertarget{ref-manera_modeling_2016}{}%
-Manera, M., Nicolini, M., Vignati, I., 2016. Modeling futures price volatility in energy markets: Is there a role for financial speculation? Energy Economics, Energy markets 53, 220--229.
-
-\leavevmode\hypertarget{ref-masters_testimony_2008}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kilian_role_2014}{}}%
+Kilian, L., Murphy, D.P., 2014.
+\href{https://doi.org/10.1002/jae.2322}{The role of inventories and speculative trading in the global market for crude oil}.
+Journal of Applied Econometrics 29, 454--478.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kim_does_2015}{}}%
+Kim, A., 2015. \href{https://doi.org/10.1002/fut.21716}{Does futures speculation destabilize commodity markets?} Journal of Futures Markets 35, 696--714.
+
+\leavevmode\vadjust pre{\hypertarget{ref-knittel_simple_2016}{}}%
+Knittel, C.R., Pindyck, R.S., 2016. \href{https://doi.org/10.1257/mac.20140033}{The simple economics of commodity price speculation}. American Economic Journal: Macroeconomics 8, 85--110.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kyle_informed_1989}{}}%
+Kyle, A.S., 1989. \href{https://doi.org/10.2307/2297551}{Informed speculation with imperfect competition}. The Review of Economic Studies 56, 317--355.
+
+\leavevmode\vadjust pre{\hypertarget{ref-leclercq_equilibrium_2014}{}}%
+Leclercq, E., Praz, R., 2014. \href{https://doi.org/10.2139/ssrn.2464400}{Equilibrium commodity trading} (SSRN Scholarly Paper No. ID 2464400). Social Science Research Network, Rochester, NY.
+
+\leavevmode\vadjust pre{\hypertarget{ref-manera_modeling_2016}{}}%
+Manera, M., Nicolini, M., Vignati, I., 2016.
+\href{https://doi.org/10.1016/j.eneco.2014.07.001}{Modeling futures price volatility in energy markets: Is there a role for financial speculation?} Energy Economics, Energy markets 53, 220--229.
+
+\leavevmode\vadjust pre{\hypertarget{ref-masters_testimony_2008}{}}%
 Masters, M.W., 2008. Testimony before the committee on homeland security and governmental affairs. U.S. Senate 20.
 
-\leavevmode\hypertarget{ref-masters_accidental_2008}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-masters_accidental_2008}{}}%
 Masters, M., White, A., 2008. The accidental hunt brothers: How institutional investors are driving up food and energy prices. Working paper.
 
-\leavevmode\hypertarget{ref-miffre_momentum_2007}{}%
-Miffre, J., Rallis, G., 2007. Momentum strategies in commodity futures markets. Journal of Banking \& Finance 31, 1863--1886.
-
-\leavevmode\hypertarget{ref-moskowitz_time_2012}{}%
-Moskowitz, T.J., Ooi, Y.H., Pedersen, L.H., 2012. Time series momentum. Journal of Financial Economics, Special issue on investor sentiment 104, 228--250.
-
-\leavevmode\hypertarget{ref-sakkas_factor_2020}{}%
-Sakkas, A., Tessaromatis, N., 2020. Factor based commodity investing. Journal of Banking \& Finance 115, 105807.
-
-\leavevmode\hypertarget{ref-sanders_impact_2011}{}%
-Sanders, D.R., Irwin, S.H., 2011a. The impact of index funds in commodity futures markets: A systems approach. The Journal of Alternative Investments 14, 40--49.
-
-\leavevmode\hypertarget{ref-sanders_new_2011}{}%
-Sanders, D.R., Irwin, S.H., 2011b. New evidence on the impact of index funds in u.s. Grain futures markets. Canadian Journal of Agricultural Economics/Revue canadienne d'agroeconomie 59, 519--532.
-
-\leavevmode\hypertarget{ref-sanders_adequacy_2010}{}%
-Sanders, D.R., Irwin, S.H., Merrin, R.P., 2010. The adequacy of speculation in agricultural futures markets: Too much of a good thing? Applied Economic Perspectives and Policy 32, 77--94.
-
-\leavevmode\hypertarget{ref-schumann_hunger_2011}{}%
-Schumann, H., 2011. The hunger-makers: How deutsche bank, goldman sachs and other financial institutions are speculating with food at the expense of the poorest. Foodwatch, Berlin.
-
-\leavevmode\hypertarget{ref-schwartz_stochastic_1997}{}%
-Schwartz, E.S., 1997. The stochastic behavior of commodity prices: Implications for valuation and hedging. The Journal of Finance 52, 923--973.
-
-\leavevmode\hypertarget{ref-schwartz_short_2000}{}%
-Schwartz, E., Smith, J.E., 2000. Short-term variations and long-term dynamics in commodity prices. Management Science 46, 893--911.
-
-\leavevmode\hypertarget{ref-senate_excessive_2009}{}%
-Senate, U.S., 2009. Excessive speculation in the wheat market. Majority and Minority Staff Report. Permanent Subcommittee on Investigations 24, 107--108.
-
-\leavevmode\hypertarget{ref-simsek_speculation_2013}{}%
-Simsek, A., 2013. Speculation and risk sharing with new financial assets. The Quarterly Journal of Economics 128, 1365--1396.
-
-\leavevmode\hypertarget{ref-singleton_investor_2013}{}%
-Singleton, K.J., 2013. Investor flows and the 2008 boom/bust in oil prices. Management Science 60, 300--318.
-
-\leavevmode\hypertarget{ref-sockin_informational_2015}{}%
-Sockin, M., Xiong, W., 2015. Informational frictions and commodity markets. The Journal of Finance 70, 2063--2098.
-
-\leavevmode\hypertarget{ref-stoll_commodity_2011}{}%
-Stoll, H.R., Whaley, R.E., 2011. Commodity index investing: Speculation or diversification? The Journal of Alternative Investments 14, 50--60.
-
-\leavevmode\hypertarget{ref-stout_why_1998}{}%
-Stout, L.A., 1998. Why the law hates speculators: Regulation and private ordering in the market for otc derivatives. Duke Law Journal 48, 701--786.
-
-\leavevmode\hypertarget{ref-stulz_rethink_1996}{}%
-Stulz, R.M., 1996. Rethinking risk management. Journal of Applied Corporate Finance 9, 8--25.
-
-\leavevmode\hypertarget{ref-szymanowska_anatomy_2014}{}%
-Szymanowska, M., De Roon, F., Nijman, T., Van Den Goorbergh, R., 2014. An anatomy of commodity futures risk premia. The Journal of Finance 69, 453--482.
-
-\leavevmode\hypertarget{ref-tang_index_2012}{}%
-Tang, K., Xiong, W., 2012. Index investment and the financialization of commodities. Financial Analysts Journal 68, 54--74.
-
-\leavevmode\hypertarget{ref-telser_futures_1958}{}%
-Telser, L.G., 1958. Futures trading and the storage of cotton and wheat. Journal of Political Economy 66, 233--255.
-
-\leavevmode\hypertarget{ref-till_long_2007}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-miffre_momentum_2007}{}}%
+Miffre, J., Rallis, G., 2007. \href{https://doi.org/10.1016/j.jbankfin.2006.12.005}{Momentum strategies in commodity futures markets}. Journal of Banking \& Finance 31, 1863--1886.
+
+\leavevmode\vadjust pre{\hypertarget{ref-moskowitz_time_2012}{}}%
+Moskowitz, T.J., Ooi, Y.H., Pedersen, L.H., 2012.
+\href{https://doi.org/10.1016/j.jfineco.2011.11.003}{Time series momentum}.
+Journal of Financial Economics, Special issue on investor sentiment 104, 228--250.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sakkas_factor_2020}{}}%
+Sakkas, A., Tessaromatis, N., 2020. \href{https://doi.org/10.1016/j.jbankfin.2020.105807}{Factor based commodity investing}. Journal of Banking \& Finance 115, 105807.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sanders_impact_2011}{}}%
+Sanders, D.R., Irwin, S.H., 2011a.
+\href{https://doi.org/10.3905/jai.2011.14.1.040}{The impact of index funds in commodity futures markets: A systems approach}.
+The Journal of Alternative Investments 14, 40--49.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sanders_new_2011}{}}%
+Sanders, D.R., Irwin, S.H., 2011b.
+\href{https://doi.org/10.1111/j.1744-7976.2011.01226.x}{New evidence on the impact of index funds in u.s.
+Grain futures markets}.
+Canadian Journal of Agricultural Economics/Revue canadienne d'agroeconomie 59, 519--532.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sanders_adequacy_2010}{}}%
+Sanders, D.R., Irwin, S.H., Merrin, R.P., 2010.
+\href{https://doi.org/10.1093/aepp/ppp006}{The adequacy of speculation in agricultural futures markets: Too much of a good thing?} Applied Economic Perspectives and Policy 32, 77--94.
+
+\leavevmode\vadjust pre{\hypertarget{ref-schumann_hunger_2011}{}}%
+Schumann, H., 2011.
+\href{https://www.foodwatch.org/uploads/media/foodwatchreport_TheHungerMakers_observationsandcallsforaction_ger_03.pdf}{The hunger-makers: How deutsche bank, goldman sachs and other financial institutions are speculating with food at the expense of the poorest}.
+Foodwatch, Berlin.
+
+\leavevmode\vadjust pre{\hypertarget{ref-schwartz_stochastic_1997}{}}%
+Schwartz, E.S., 1997.
+\href{https://doi.org/10.1111/j.1540-6261.1997.tb02721.x}{The stochastic behavior of commodity prices: Implications for valuation and hedging}.
+The Journal of Finance 52, 923--973.
+
+\leavevmode\vadjust pre{\hypertarget{ref-schwartz_short_2000}{}}%
+Schwartz, E., Smith, J.E., 2000. \href{https://www.jstor.org/stable/2661607}{Short-term variations and long-term dynamics in commodity prices}. Management Science 46, 893--911.
+
+\leavevmode\vadjust pre{\hypertarget{ref-senate_excessive_2009}{}}%
+Senate, U.S., 2009.
+\href{https://www.hsgac.senate.gov/imo/media/doc/REPORTExcessiveSpecullationintheWheatMarketwoexhibitschartsJune2409.pdf?attempt=2}{Excessive speculation in the wheat market}.
+Majority and Minority Staff Report.
+Permanent Subcommittee on Investigations 24, 107--108.
+
+\leavevmode\vadjust pre{\hypertarget{ref-simsek_speculation_2013}{}}%
+Simsek, A., 2013. \href{https://doi.org/10.1093/qje/qjt007}{Speculation and risk sharing with new financial assets}. The Quarterly Journal of Economics 128, 1365--1396.
+
+\leavevmode\vadjust pre{\hypertarget{ref-singleton_investor_2013}{}}%
+Singleton, K.J., 2013. \href{https://doi.org/10.1287/mnsc.2013.1756}{Investor flows and the 2008 boom/bust in oil prices}. Management Science 60, 300--318.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sockin_informational_2015}{}}%
+Sockin, M., Xiong, W., 2015. \href{https://doi.org/10.1111/jofi.12261}{Informational frictions and commodity markets}. The Journal of Finance 70, 2063--2098.
+
+\leavevmode\vadjust pre{\hypertarget{ref-stoll_commodity_2011}{}}%
+Stoll, H.R., Whaley, R.E., 2011. \href{https://doi.org/10.2139/ssrn.1633908}{Commodity index investing: Speculation or diversification?} The Journal of Alternative Investments 14, 50--60.
+
+\leavevmode\vadjust pre{\hypertarget{ref-stout_why_1998}{}}%
+Stout, L.A., 1998. \href{https://doi.org/10.2307/1373070}{Why the law hates speculators: Regulation and private ordering in the market for OTC derivatives}. Duke Law Journal 48, 701--786.
+
+\leavevmode\vadjust pre{\hypertarget{ref-stulz_rethink_1996}{}}%
+Stulz, R.M., 1996. \href{https://doi.org/10.1111/j.1745-6622.1996.tb00295.x}{Rethinking risk management}. Journal of Applied Corporate Finance 9, 8--25.
+
+\leavevmode\vadjust pre{\hypertarget{ref-szymanowska_anatomy_2014}{}}%
+Szymanowska, M., De Roon, F., Nijman, T., Van Den Goorbergh, R., 2014. \href{https://doi.org/10.1111/jofi.12096}{An anatomy of commodity futures risk premia}. The Journal of Finance 69, 453--482.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tang_index_2012}{}}%
+Tang, K., Xiong, W., 2012. \href{https://doi.org/10.2469/faj.v68.n6.5}{Index investment and the financialization of commodities}. Financial Analysts Journal 68, 54--74.
+
+\leavevmode\vadjust pre{\hypertarget{ref-telser_futures_1958}{}}%
+Telser, L.G., 1958. \href{https://doi.org/10.1086/258036}{Futures trading and the storage of cotton and wheat}. Journal of Political Economy 66, 233--255.
+
+\leavevmode\vadjust pre{\hypertarget{ref-till_long_2007}{}}%
 Till, H., 2007. A long-term perspective on commodity futures returns, in: Intelligent Commodity Investing. Risk books, London.
 
-\leavevmode\hypertarget{ref-tokic_speculation_2012}{}%
-Tokic, D., 2012. Speculation and the 2008 oil bubble: The dcot report analysis. Energy Policy 45, 541--550.
-
-\leavevmode\hypertarget{ref-turnovsky_determination_1983}{}%
-Turnovsky, S.J., 1983. The determination of spot and futures prices with storable commodities. Econometrica 51, 1363--1387.
-
-\leavevmode\hypertarget{ref-unctad_global_2009}{}%
-UNCTAD, S.T.F. on S.I., Cooperation, E., 2009. The global economic crisis: Systemic failures and multilateral remedies. UNCTAD, Geneva.
-
-\leavevmode\hypertarget{ref-weymar_supply_1966}{}%
-Weymar, F.H., 1966. The supply of storage revisited. The American Economic Review 56, 1226--1234.
-
-\leavevmode\hypertarget{ref-working_price_1933}{}%
-Working, H., 1933. Price relations between july and september wheat futures at chicago since 1885. Wheat Studies 9, 187.
-
-\leavevmode\hypertarget{ref-working_theory_1948}{}%
-Working, H., 1948. Theory of the inverse carrying charge in futures markets. Journal of Farm Economics 30, 1--28.
-
-\leavevmode\hypertarget{ref-working_theory_1949}{}%
-Working, H., 1949. The theory of price of storage. The American Economic Review 1254--1262.
-
-\leavevmode\hypertarget{ref-working_hedging_1953}{}%
-Working, H., 1953. Hedging reconsidered. Journal of Farm Economics 35, 544--561.
-
-\leavevmode\hypertarget{ref-yang_investment_2013}{}%
-Yang, F., 2013. Investment shocks and the commodity basis spread. Journal of Financial Economics 110, 164--184.
+\leavevmode\vadjust pre{\hypertarget{ref-tokic_speculation_2012}{}}%
+Tokic, D., 2012. \href{https://doi.org/10.1016/j.enpol.2012.02.069}{Speculation and the 2008 oil bubble: The DCOT report analysis}. Energy Policy 45, 541--550.
+
+\leavevmode\vadjust pre{\hypertarget{ref-turnovsky_determination_1983}{}}%
+Turnovsky, S.J., 1983. \href{https://doi.org/10.2307/1912279}{The determination of spot and futures prices with storable commodities}. Econometrica 51, 1363--1387.
+
+\leavevmode\vadjust pre{\hypertarget{ref-unctad_global_2009}{}}%
+UNCTAD, S.T.F.
+on S.I., Cooperation, E., 2009.
+\href{https://unctad.org/system/files/official-document/gds20091_en.pdf}{The global economic crisis: Systemic failures and multilateral remedies}.
+UNCTAD, Geneva.
+
+\leavevmode\vadjust pre{\hypertarget{ref-weymar_supply_1966}{}}%
+Weymar, F.H., 1966. \href{http://www.jstor.org/stable/1815306}{The supply of storage revisited}. The American Economic Review 56, 1226--1234.
+
+\leavevmode\vadjust pre{\hypertarget{ref-working_price_1933}{}}%
+Working, H., 1933. \href{https://doi.org/10.22004/ag.econ.142876}{Price relations between july and september wheat futures at chicago since 1885}. Wheat Studies 9, 187.
+
+\leavevmode\vadjust pre{\hypertarget{ref-working_theory_1948}{}}%
+Working, H., 1948. \href{https://doi.org/10.2307/1232678}{Theory of the inverse carrying charge in futures markets}. Journal of Farm Economics 30, 1--28.
+
+\leavevmode\vadjust pre{\hypertarget{ref-working_theory_1949}{}}%
+Working, H., 1949. \href{https://www.jstor.org/stable/1816601}{The theory of price of storage}. The American Economic Review 1254--1262.
+
+\leavevmode\vadjust pre{\hypertarget{ref-working_hedging_1953}{}}%
+Working, H., 1953. \href{https://doi.org/10.2307/1233368}{Hedging reconsidered}. Journal of Farm Economics 35, 544--561.
+
+\leavevmode\vadjust pre{\hypertarget{ref-yang_investment_2013}{}}%
+Yang, F., 2013. \href{https://doi.org/10.1016/j.jfineco.2013.04.012}{Investment shocks and the commodity basis spread}. Journal of Financial Economics 110, 164--184.
+
+\end{CSLReferences}
 

### 2022-06-30 literature_files/format.r

@@ -1,0 +1,38 @@
+caption_latex <- function(x){
+  x <- gsub("(\\d)\\%", "\\1\\\\%", x, ignore.case = TRUE, perl = TRUE)
+  x <- gsub("&", "\\\\&", x, ignore.case = TRUE, perl = TRUE)
+  x <- gsub("\\\\\\*", "*", x, ignore.case = TRUE, perl = TRUE)
+  x <- gsub("\\\\@ref\\((.+?)\\)", "\\\\ref{\\1}", x, ignore.case = TRUE, perl = TRUE)
+  x
+}
+
+show_table <- function(type, table){
+  if (type == 'html') { 
+    table <- kable_classic(table, full_width = TRUE, html_font = html_font) 
+  } 
+  else if (type == 'latex') {
+    table <- kable_classic(
+      table, font_size = tables_font_size, 
+      latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
+    )
+  }
+
+  table
+}
+
+#' Extract result table from result tables data frame provided
+#'
+#' @param tables A data frame with result tables. Columns are:
+#'  - analysis: name of the analysis.
+#'  - result: nested result table.
+#' @param analysis A string with the analysis name
+#' @return A data frame with the result table
+get_table <- function(tables, analysis){
+  results <- tables[tables$analysis  == analysis, "results"]
+  if (NCOL(results) > 1L) { 
+    message <- paste0("Multiple tables found for analysis: ", analysis)
+    message(message) 
+  } else {
+    results[[1]]
+  }
+}

### 2022-06-30 script.js

@@ -1,0 +1,17 @@
+let header = document.getElementById("header");
+let title = document.querySelector(".title");
+let authors = document.querySelectorAll(".author");
+let date = document.querySelector(".date");
+let abstract = document.querySelector(".abstract");
+
+let container = document.createElement("div");
+container.classList.add("authors");
+authors.forEach(author => container.appendChild(author));
+
+
+
+header.innerHTML = "";
+header.appendChild(title);
+header.appendChild(container);
+header.appendChild(date);
+header.appendChild(abstract);

### 2022-06-30 docs/paper.Rmd

--- 2022-05-26 docs/paper.Rmd
@@
 ```{r, include=latex}
-knitr::asis_output('\\newgeometry{a4paper,left=1in,right=1in,top=1in,bottom=1in,nohead}')
+knitr::asis_output('\\newgeometry{left=1in,right=1in,top=1in,bottom=1in,nohead}')
 knitr::asis_output('\\savegeometry{tables}')

### 2022-07-04 paper.Rmd
Deploying to gh-pages from @ bautheac/financialisation-co-movement@b0712c092d6c5d374462f2541e13050b4a517966 🚀

--- 2022-06-30 docs/paper.Rmd
@@
 ## Methods {#co-movement-methods}
+
 On the one hand, futures markets have a long history of serving commodity producers to alleviate their commodity price and output risks.
@@
 
-Asset pricing techniques are well suited to study co-movement.
-Building on theory we therefore develop an ad-hoc commodity-based asset pricing framework that we believe is well adapted to study these two issues simultaneously and implement it over four periods of interest.
+By grouping together assets by shared attribute dynamics in common portfolios asset pricing techniques and factor models in particular are well suited to study co-movement [@fama_common_1993; @carhart_persistence_1997; @asness_devil_2013; @fama_five_factor_2015; @hou_digesting_2015; @asness_fact_2015; @frazzini_betting_2014; @asness_quality_2019].
+Careful, theory-based, attribute selection further enables a refined analysis of market fundamentals [@schwartz_short_2000; @miffre_momentum_2007; @gorton_fundamentals_2012; @cortazar_commodity_2013; @yang_investment_2013; @daskalaki_factors_2014; @szymanowska_anatomy_2014; @fernandez_skewness_2018; @bakshi_understanding_2019; @boons_basis_2019; @sakkas_factor_2020].
+We therefore develop a futures-based asset pricing framework that includes factors constructed using both theoretical and liquidity considerations and use this framework to carry out our analysis over four periods of interest.
 The first, the pre-financialisation period, starts in 1997 and is naturally followed by financialisation, spanning the 2004/2008 period, and the financial crisis and its aftermath, spanning the 2008/2013 period.
@@
 The same operation is repeated for the two ($p=2$) and three ($p=3$) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectively, as well as for the four ($p=4$) factor model case where all the risk factor mimicking portfolios are included.
-Results are reported for the one-factor model case with the other results available on the [online results dashboard](http://18.135.131.217:3838/financialization-asset-pricing/).
+Results are reported for the one-factor model case with the other results available upon request.
 
@@
 For each period we also implement the analysis described above over periods of low and high aggregate CHP (**CHP**), a notion that we believe is particularly relevant in the context of financialisation where issues of co-movement and aggregate market behaviour play a central role.
-We define **CHP** as the cross-sectional average of CHPs for a particular pool of assets.
+We define **CHP** as the cross-sectional average of individual CHPs for a particular pool of assets.
 i.e., period $t$ **CHP** for asset pool $x$:
@@
 In this case, a first set of dependent variables includes the sets of commodity picks themselves, a second set includes the whole cross-section of US traded commodities while a third set includes the six UK traded metals considered in the study.
+
+```{r, include=html}
+knitr::asis_output('<br/>')
+```
+```{r, include=latex}
+knitr::asis_output('\\bigskip')
+knitr::asis_output('\\bigskip')
+knitr::asis_output('\\setlength{\\parindent}{0pt}')
+```
+
+By relating returns on attribute based risk factor mimicking portfolios to returns on individual as well as group of assets, our time series approach therefore draws the link between attribute and pricing dynamics over different, theory-based market regimes, and thereby enables us to study market fundamentals and co-movement simultaneously, two key issues in the financialisation phenomenon.
 
@@
 Over the first period the market factor has the best average time series performance with the highest average $R^{2}$ with all three futures market factors performing poorly, indicating that the commodities with extreme factor attributes (high or low CHP for example) are uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of high and low **CHP** (below period median).
-The two factor models average $R^{2}$s (results available on the [online results dashboard](http://18.135.131.217:3838/financialization-asset-pricing/)) are roughly the sum of the one factor $R^{2}$s indicating that the factors are almost orthogonal over this period.
+The two factor models average $R^{2}$s (available upon request) are roughly the sum of the one factor $R^{2}$s indicating that the factors are almost orthogonal over this period.
 The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average $R^{2}$ increasing to 8.2% in the second period relative to 1.7% in the first with this improvement coming from the long leg that shows a greater improvement (4.5% to 15.1%) relative to the short (3% to 4%), suggesting that "normally" backwardated commodities (Keynesian perspective) have higher correlation with the rest of the commodity cross-section, and thereby bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period.

### 2022-07-04 docs/paper.tex

--- 2022-05-26 docs/paper.tex
@@
 
-Asset pricing techniques are well suited to study co-movement.
-Building on theory we therefore develop an ad-hoc commodity-based asset pricing framework that we believe is well adapted to study these two issues simultaneously and implement it over four periods of interest.
+By grouping together assets by shared attribute dynamics in common portfolios asset pricing techniques and factor models in particular are well suited to study co-movement (Asness et al., 2015; Asness and Frazzini, 2013; Asness et al., 2019; Carhart, 1997; Fama and French, 2015, 1993; Frazzini and Pedersen, 2014; Hou et al., 2015).
+Careful, theory-based, attribute selection further enables a refined analysis of market fundamentals (Bakshi et al., 2019; Boons and Prado, 2019; Cortazar et al., 2013; Daskalaki et al., 2014; Fernandez-Perez et al., 2018; Gorton et al., 2012; Miffre and Rallis, 2007; Sakkas and Tessaromatis, 2020; Schwartz and Smith, 2000; Szymanowska et al., 2014; Yang, 2013).
+We therefore develop a futures-based asset pricing framework that includes factors constructed using both theoretical and liquidity considerations and use this framework to carry out our analysis over four periods of interest.
 The first, the pre-financialisation period, starts in 1997 and is naturally followed by financialisation, spanning the 2004/2008 period, and the financial crisis and its aftermath, spanning the 2008/2013 period.
@@
 The same operation is repeated for the two (\(p=2\)) and three (\(p=3\)) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectively, as well as for the four (\(p=4\)) factor model case where all the risk factor mimicking portfolios are included.
-Results are reported for the one-factor model case with the other results available on the \href{http://18.135.131.217:3838/financialization-asset-pricing/}{online results dashboard}.
+Results are reported for the one-factor model case with the other results available upon request.
 
@@
 For each period we also implement the analysis described above over periods of low and high aggregate CHP (\textbf{CHP}), a notion that we believe is particularly relevant in the context of financialisation where issues of co-movement and aggregate market behaviour play a central role.
-We define \textbf{CHP} as the cross-sectional average of CHPs for a particular pool of assets.
+We define \textbf{CHP} as the cross-sectional average of individual CHPs for a particular pool of assets.
 i.e., period \(t\) \textbf{CHP} for asset pool \(x\):
@@
 In this case, a first set of dependent variables includes the sets of commodity picks themselves, a second set includes the whole cross-section of US traded commodities while a third set includes the six UK traded metals considered in the study.
+
+\bigskip\bigskip\setlength{\parindent}{0pt}
+
+By relating returns on attribute based risk factor mimicking portfolios to returns on individual as well as group of assets, our time series approach therefore draws the link between attribute and pricing dynamics over different, theory-based market regimes, and thereby enables us to study market fundamentals and co-movement simultaneously, two key issues in the financialisation phenomenon.
 
@@
 The explanatory power for the other commodities is typically low or even 0 for the case where commodities are perfectly uncorrelated with one-another.
-A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities, which suggests that pairwise correlation relate to factor attribute.\\
+A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities.
+and therefore provides evidence that pairwise return correlation relates to factor attribute.\\
 The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \ref{tab:co-movement-time-reg-US-facts-US}.
 Over the first period the market factor has the best average time series performance with the highest average \(R^{2}\) with all three futures market factors performing poorly, indicating that the commodities with extreme factor attributes (high or low CHP for example) are uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of high and low \textbf{CHP} (below period median).
-The two factor models average \(R^{2}\)s (results available on the \href{http://18.135.131.217:3838/financialization-asset-pricing/}{online results dashboard}) are roughly the sum of the one factor \(R^{2}\)s indicating that the factors are almost orthogonal over this period.\\
+The two factor models average \(R^{2}\)s (available upon request) are roughly the sum of the one factor \(R^{2}\)s indicating that the factors are almost orthogonal over this period.\\
 The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average \(R^{2}\) increasing to 8.2\% in the second period relative to 1.7\% in the first with this improvement coming from the long leg that shows a greater improvement (4.5\% to 15.1\%) relative to the short (3\% to 4\%), suggesting that ``normally'' backwardated commodities (Keynesian perspective) have higher correlation with the rest of the commodity cross-section, and thereby bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period.

### 2022-07-04 paper.Rmd
Deploying to gh-pages from @ bautheac/financialisation-co-movement@6e886bbccb60b17ed59cf06c49c39a4fbdf93144 🚀

@@
 output:
-  bookdown::pdf_book:
-      pandoc_args: latex.yaml
-      base_format: rticles::elsevier_article
-      latex_engine: xelatex
-      toc_depth: 3
-      includes:
-        in_header: preamble.tex
   bookdown::gitbook:
@@
       after_body: doc_suffix.html
+  bookdown::pdf_book:
+      pandoc_args: latex.yaml
+      base_format: rticles::elsevier_article
+      latex_engine: xelatex
+      toc_depth: 3
+      includes:
+        in_header: preamble.tex
 ---

### 2022-07-28 others/journal submissions/journal of futures markets/cover letter.qmd
#16 gather references from previous issues

---
title: "cover letter"
format: docx
editor: visual
---

## References

### Co-movement

-   [prokopczuk](https://doi.org/10.1002/fut.22222 "The dynamics of commodity return comovements")[\_dynamics_2021](https://doi.org/10.1002/fut.22222)

### Financialisation

-   [conghui](https://doi.org/10.1002/fut.22127 "Liquidity shocks, commodity financialization, and market comovements")[\_liquidity_2020](https://doi.org/10.1002/fut.22127)
-   [kupabado](https://doi.org/10.1002/fut.22269 "Financialization, common stochastic trends, and commodity prices")[\_financialisation_2021](https://doi.org/10.1002/fut.22269)
-   [yin](https://doi.org/10.1002/fut.22099 "Intermediary asset pricing in commodity futures returns")[\_intermediary_2020](https://doi.org/10.1002/fut.22099)

### Fundamentals

-   [liu_market_2020](https://doi.org/10.1002/fut.22115 "The market quality of commodity futures markets")

#### Risk hedging

-   [isleimeyyeh_role_2020](https://doi.org/10.1002/fut.22122 "The role of financial investors in determining the commodity futures risk premium")

-   [ahmadi](https://doi.org/10.1002/fut.22113 "The theory of storage in the crude oil futures market, the role of financial conditions")[\_theory_2020](https://doi.org/10.1002/fut.22113)

-   [fan_speculative_2020](https://doi.org/10.1002/fut.22085 "Speculative pressure")

#### Price formation

-   [adammer_price_2018](https://doi.org/10.1002/fut.21891 "Price discovery dynamics in European agricultural markets")

-   [bohmann_price_2019](https://doi.org/10.1002/fut.22021 "Price discovery in commodity derivatives: Speculation or hedging?")

-   [llorente_trading_2020](https://doi.org/10.1002/fut.22079 "Trading and information in futures markets")

    ###

### 2022-07-29 others/journal submissions/journal of futures markets/cover letter.qmd
#16 added reading notes on references

@@
 
+-   Market integration.
+
+    -   Within commodity complex.
+
+    -   Across asset classes (equities in particular).
+
+-   Effect of financilisation on commodity prices
+
+-   Asset pricing/factor models to study financilisation.
+
 ## References
@@
 
--   [prokopczuk](https://doi.org/10.1002/fut.22222 "The dynamics of commodity return comovements")[\_dynamics_2021](https://doi.org/10.1002/fut.22222)
+#### [prokopczuk](https://doi.org/10.1002/fut.22222 "The dynamics of commodity return comovements")[\_dynamics_2021](https://doi.org/10.1002/fut.22222)
 
-### Financialisation
+-   A simple one-factor model based on the first principal component extracted from a panel of commodity returns outperforms a macroeconomic model, and explains most of the realized comovements.
 
--   [conghui](https://doi.org/10.1002/fut.22127 "Liquidity shocks, commodity financialization, and market comovements")[\_liquidity_2020](https://doi.org/10.1002/fut.22127)
--   [kupabado](https://doi.org/10.1002/fut.22269 "Financialization, common stochastic trends, and commodity prices")[\_financialisation_2021](https://doi.org/10.1002/fut.22269)
--   [yin](https://doi.org/10.1002/fut.22099 "Intermediary asset pricing in commodity futures returns")[\_intermediary_2020](https://doi.org/10.1002/fut.22099)
+-   Intersectoral correlations display more time variations than intrasectoral correlations.
+
+-   Comovements are driven by the variation of the factor as opposed to exposure to it.
+
+-   Results cast doubt on the persistence of the effects of financialization and emphasize the importance of the dynamics of the factor variance.
+
+#### [conghui](https://doi.org/10.1002/fut.22127 "Liquidity shocks, commodity financialization, and market comovements")[\_liquidity_2020](https://doi.org/10.1002/fut.22127)
+
+-   Liquidity shocks, including both funding liquidity and market liquidity, are positively associated with comovements between commodity and stock markets after 2000.
+
+-   The effect of liquidity on cross‐market correlations is state‐dependent and intensifies when liquidity conditions deteriorate and asset returns sustain substantial declines.
+
+-   The structural change indicates that financialization creates a role for adverse liquidity shocks to increase cross‐market correlations.
+
+-    A growing body of literature explores the risk transfers between commodity markets and stock markets (e.g., @buyuksahin_speculators_2014; @cheng_convective_2015; @ordu_food_2018).
+While these studies have different research issues, they all imply that liquidity (broadly defined) matters for risk transfers across markets with the financialization of commodity markets.
+
+-   We provide direct evidence that financialization is aprecondition for liquidity shocks to be passed through to commodity markets and that the risk transfer between commodity and stock markets intensifies when liquidity tightens and asset returns are poor.
+
+```{=html}
+<!-- -->
+```
+-
+
+-   We add to the debate on the driving forces behind the dynamics of correlations between commodity and stock markets.
+
+    -   First, business cycles do not explain the structural change of liquidity's role in accounting for cross‐market correlations that happened in the early 2000s.
+
+    -   Second, we show thataside from funding liquidity, stock market liquidity also matters in predicting cross‐market correlations.
+
+    -   Third,the significant association between corporate spreads and cross‐market correlations might not be driven by business cycles.
+
+#### [isleimeyyeh_role_2020](https://doi.org/10.1002/fut.22122 "The role of financial investors in determining the commodity futures risk premium")
+
+-   The effect of the stock market on the energy market became significantly greater for the futures risk premium in the period following the 2008 crisis.
+
+-   This study extends studies that broadly address the financialization of commodities and specifically the risk premium in commodity markets.
+
+####
+
+#### [yin](https://doi.org/10.1002/fut.22099 "Intermediary asset pricing in commodity futures returns")[\_intermediary_2020](https://doi.org/10.1002/fut.22099)
+
+-   The intermediary capital (IC) effect is substantially positive and continues to grow as the financialization of commodities deepens.
+
+-   The effect of the positive IC risk factor varies significantly.
+
+-   Portfolios with low basis, low open interest, low momentum, and low liquidity earn significantly higher returns than counterparty portfolios.
 
@@
 
--   [liu_market_2020](https://doi.org/10.1002/fut.22115 "The market quality of commodity futures markets")
-
 #### Risk hedging
 
--   [isleimeyyeh_role_2020](https://doi.org/10.1002/fut.22122 "The role of financial investors in determining the commodity futures risk premium")
+#### [ahmadi](https://doi.org/10.1002/fut.22113 "The theory of storage in the crude oil futures market, the role of financial conditions")[\_theory_2020](https://doi.org/10.1002/fut.22113)
 
--   [ahmadi](https://doi.org/10.1002/fut.22113 "The theory of storage in the crude oil futures market, the role of financial conditions")[\_theory_2020](https://doi.org/10.1002/fut.22113)
+-   Validates theory of storage in the crude oil market.
 
--   [fan_speculative_2020](https://doi.org/10.1002/fut.22085 "Speculative pressure")
+#### [fan_speculative_2020](https://doi.org/10.1002/fut.22085 "Speculative pressure")
+
+-   Long-short portfolios of futures contracts sorted by speculative pressure capture a significant premium in commodity, currency, and equity markets but not in fixed income markets.
+
+-   Exposure to commodity, currency, and equity index futures' speculative pressure is priced in the broad cross-section after controlling for momentum, carry, global liquidity, and volatility risks.
+
+-   There is an efficient hedgers-speculators risk transfer in commodity, currency, and equity index futures markets.
+
+-   Contribution to literature.
+
+    -   Provides the first empirical investigation of the ability of tradeable long-short portfolios based on speculative pressure to capture premia in futures markets on instruments beyond commodities.
+
+    -   We contribute to an "everywhere" pricing literature that has so far focused on the momentum, value and carry factors.
+
+    -   Adds to the literature that investigates the potentially harmful impact of speculators on futures prices [@fattouh_role_2013; @irwin_devil_2009; @stoll_commodity_2010].
+Finding that equity index, currency and commodity futures markets facilitate risk transfer and reward suggests that calls to regulate excessive speculation are unwarranted; speculators do not destabilize these futures markets, rather they are important providers of liquidity and risk-bearing facility to hedgers.
 
@@
 
--   [adammer_price_2018](https://doi.org/10.1002/fut.21891 "Price discovery dynamics in European agricultural markets")
+#### [adammer_price_2018](https://doi.org/10.1002/fut.21891 "Price discovery dynamics in European agricultural markets")
 
--   [bohmann_price_2019](https://doi.org/10.1002/fut.22021 "Price discovery in commodity derivatives: Speculation or hedging?")
+-   The impact of the futures markets was high during the first period of price spikes (2007 to 2009) but lower during the second one (2010 to 2013).
 
--   [llorente_trading_2020](https://doi.org/10.1002/fut.22079 "Trading and information in futures markets")
+-   More trading activity in futures markets did not lead to a higher influence on spot prices.
 
-    ###
+#### [bohmann_price_2019](https://doi.org/10.1002/fut.22021 "Price discovery in commodity derivatives: Speculation or hedging?")
+
+-   Both commodity futures and option markets make a meaningful contribution to price discovery in recent times in the six most actively traded commodity markets.
+
+-   On average, options lead futures in reflecting new information for a majority of these commodities.
+
+-   Increased speculation, rather than hedging activity, in commodity derivatives is a key determinant of price discovery in the options markets.
+
+#### [kupabado](https://doi.org/10.1002/fut.22269 "Financialization, common stochastic trends, and commodity prices")[\_financialisation_2021](https://doi.org/10.1002/fut.22269)
+
+-   Financialization has contributed to the price movements of these commodities.
+
+#### [llorente_trading_2020](https://doi.org/10.1002/fut.22079 "Trading and information in futures markets")
+
+-   Nonmembers (CTI4) consume most of the intraday liquidity while local traders (CTI1) as market makers are its main provider. Both groups combine most of the intraday trading volume.
+
+-   Changes in the overnight positions of the general public (CTI4) and clearing members (CTI2) contribute mostly to daily price discovery, while the positions of CTI3 group reflect possible information advantage about future price movements.

### 2024-05-01 docs/paper.Rmd

@@
 ---
-title: 'Financialisation of commodities: co-movement behind-the-scenes'
-subtitle: A tale of four factors
+title: 'Financialisation of Commodities: Co-movement Behind-the-scenes'
 date: "`r format(Sys.Date(), '%B %Y')`"
@@
   bookdown::pdf_book:
-      pandoc_args: latex.yaml
+      pandoc_args: latex-blind.yaml
       base_format: rticles::elsevier_article
@@
 
-folder <- "literature_files"; dir.create(folder); path <- paste(folder, "references.bib", sep = "/")
-download.file("https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", path)
+# folder <- "literature_files"; dir.create(folder); path <- paste(folder, "references.bib", sep = "/")
+# download.file("https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", path)
 
@@
 Arguments have been put forward in favour of both possibilities with @moskowitz_time_2012 arguing that financial investors provide liquidity and @kang_tale_2020 taking the opposite stance.
-Our analysis of individual commodity returns' relation with both CHP and **CHP** before and during financialisation sheds new lights on this issue with our results suggesting that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
+Our analysis of individual commodity returns' relation with both CHP and **CHP** before and during financialisation sheds a new light on this issue with our results suggesting that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
 
@@
 However, the fundamental question of the nature of the impact of financialisation across the entire cross-section of commodity futures markets has not yet been completely answered.
-We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2014, @ekeland_speculation_2016, @goldstein_commodity_2017.] and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in @tang_index_2012 and @basak_model_2016.
+We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2014, @ekeland_speculation_2016, @goldstein_commodity_2017, @ekeland_hedging_2019, @isleimeyyeh_role_2020.] and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in @tang_index_2012 and @basak_model_2016.
 

### 2024-06-11 others/journal submissions/journal of futures markets/cover letter - notes.qmd
Track 'others' folder

---
title: "cover letter"
format: docx
editor: visual
bibliography: literature_files/references.bib
---

```{r globals, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

folder <- "literature_files"; dir.create(folder); path <- paste(folder, "references.bib", sep = "/")
download.file("https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", path)

```

## How does your paper advance the ongoing debates in the Journal of Futures Markets? (Clearly state the connection with previous research in the journal)

### Notes

Our paper studies the finanialisation phenomnon from a broad perspective. Our results suggest that the phenomenon had deep impact, in multiple aspects across the commodity complex as a whole. Particularly we shows that the phenomnon had strong effects on commodity co-movement within and between commodity sectors, sub-sectors and amongst individual markets. These findings complement those of @liu_analyzing_2021, @sehgal_who_2021, @yang_volatility_2021, @gong_time_2022. This phenomnon fueled by financialisation extended beyong the commodity complex by fueling market integration with legacy asset classes, including equity markets with those findings complementing those of @conghui_liquidity_2020, @isleimeyyeh_role_2020, @daskalaki_new_2021, @han_trend_2022, @saishree_exploring_2022. We futher show that financialisation had onthonlogical consequences for the commodity complex, effectivelely aletering the fundamentals of these markets in various aspect, as demonstrated in @isleimeyyeh_role_2020, @marechal_tale_2020, @yin_intermediary_2021. In particular, the risk transfer and price formation functions were particularly affected as discussed in @ahmadi_theory_2020 and @adammer_price_2018, @merkoulova_predictive_2020, @kupabado_financialisation_2021, @sehgal_who_2021 respectively. we outlined that the phenomenon therefore affected the properties of the complex as an investment device, as pointed out in @daskalaki_new_2021. As we point out, financialisation was mostly about index investments, our study therefore complement the body of work on idex investment in the comtext of commodity markets including @glover_financially_2022. We carry out our analysis using asset pricing techniques effectively complementing the body of work using asset pricing technique to study the financialisation phenomenon, including @fan_untold_2020, @marechal_tale_2020, @yin_intermediary_2020 and @han_trend_2022. In this context our analysis complement the literature studying commodity market fundamentals (@brooks_samuelson_2020, @llorente_trading_2020, @marechal_do_2021, @li_hedging_2022) including risk transfer (@fan_speculative_2020, @oglend_futures_2020, @huang_good_2023) and price formation (@bohmann_price_2019, @janardanan_commodity_2019, @arroyo_old_2020, @bohl_return_2020, @frino_sensitivity_2020, @siklos_metal_2020, @andersen_efficiency_2021, @figuerola_oil_2021, @geyer_determinants_2021, @gilbert_regional_2021, @yang_price_2021, @fuertes_risk_2022, @li_robust_2022, @bandyopadhyay_impact_2023, @chen_temperature_2023, @fan_wisdom_2023, @filippidis_evaluating_2023) as well as a that studying co-movement and market integration both within the commodity complex ( @xiao_estimating_2020, @yang_return_2020, @luo_how_2021, @prokopczuk_dynamics_2021, @deBoer_intraday_2022, @dhaene_volatility_2022, @zhang_impact_2022) as well as across asset classes (@alquist_effect_2020, @kang_commodity_2020, @wong_impact_2020, @dark_lead_2021, @li_forecasting_2021, @liu_does_2022, @ming_contagion_2022, @zhang_do_2022, @zhang_influence_2023). We further extend the body of recent empirical studies using asset pricing/factor models in the context of commodity markets, including @kang_commodity_2020 and @yuan_pobability_2023. We stress the importance of consequences the phenomenon in terms of regulatory oversight, effectively adding to the body of literature on institutional oversight including @janardanan_commodity_2019, @fan_untold_2020, @hu_impact_2020, @mixon_us_2022, @szabo_margin_2022.

-   Advances the debate on the effects of financialisation on various aspects of the commodity spectrum. our result suggest that financialisation fueled market integration both within and between commodity sectors, sub-sectors and amongst individual markets effectively complementing @yang_volatility_2021 and @gong_time_2022.
-   Our results further suggest had ontological consequences for the commodity complex with an impact on fundamentals in general, confirming the findings in @marechal_tale_2020

and favored market integration both within the commodity complex as well as with legacy asset classes - Financialisation had ontological consequences for the commodity complex. Confirms the findings of @marechal_tale_2020 who find that financialisation had a stronger impact on risk transfer capabilities of the commodity complex than of commodity futures prices at the individual or aggregate level.

-   We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets including @isleimeyyeh_role_2020.

### Links to literature from the Journal of Futures markets

-   Financialisation
    -   Effect on
        -   Co-movement and market integration.
            -   Within commodity complex: @liu_analyzing_2021, @sehgal_who_2021, @yang_volatility_2021, @gong_time_2022.
            -   Across asset classes (equities in particular): @conghui_liquidity_2020, @isleimeyyeh_role_2020, @daskalaki_new_2021, @han_trend_2022, @saishree_exploring_2022.
        -   Commodity fundamentals: @isleimeyyeh_role_2020, @marechal_tale_2020, @yin_intermediary_2021.
            -   Risk transfer: @ahmadi_theory_2020.\
            -   Price formation: @adammer_price_2018, @merkoulova_predictive_2020, @kupabado_financialisation_2021, @sehgal_who_2021.\
        -   Commodity investment: @daskalaki_new_2021, @han_trend_2022.\
    -   Asset pricing studies of the phenomenon: @fan_untold_2020, @marechal_tale_2020, @yin_intermediary_2020, @han_trend_2022.\
-   Commodity markets fundamentals: @brooks_samuelson_2020, @llorente_trading_2020, @marechal_do_2021, @li_hedging_2022.
    -   Risk transfer: @fan_speculative_2020, @oglend_futures_2020, @huang_good_2023.
    -   Price formation: @bohmann_price_2019, @janardanan_commodity_2019, @arroyo_old_2020, @bohl_return_2020, @frino_sensitivity_2020, @siklos_metal_2020, @andersen_efficiency_2021, @figuerola_oil_2021, @geyer_determinants_2021, @gilbert_regional_2021, @yang_price_2021, @fuertes_risk_2022, @li_robust_2022, @bandyopadhyay_impact_2023, @chen_temperature_2023, @fan_wisdom_2023, @filippidis_evaluating_2023.\
-   Co-movement and market integration.
    -   Within commodity complex: @xiao_estimating_2020, @yang_return_2020, @luo_how_2021, @prokopczuk_dynamics_2021, @deBoer_intraday_2022, @dhaene_volatility_2022, @zhang_impact_2022.
    -   Across asset classes (equities in particular): @alquist_effect_2020, @kang_commodity_2020, @wong_impact_2020, @dark_lead_2021, @li_forecasting_2021, @liu_does_2022, @ming_contagion_2022, @zhang_do_2022, @zhang_influence_2023.
-   Asset pricing/factor models in the context of commodity markets: @kang_commodity_2020, @yuan_pobability_2023.\
-   Futures markets oversight: @janardanan_commodity_2019, @fan_untold_2020, @hu_impact_2020, @mixon_us_2022, @szabo_margin_2022.
-   Index investment in the context of futures markets: @glover_financially_2022.\
-   Unclassified: @alturki_market_2022, @cao_market_2022, @zhang_can_2022, @zhang_hedging_2022, @ONeill_effects_2023.

### Talking points

-   Drawing upon the issues and methodologies discussed in these studies, our research extends the dialogue by ...

-   Building upon these seminal works, our research provides further empirical evidence and offers a novel perspective on the co-movement between commodity futures markets and traditional financial assets in the context of increasing financialisation.

-   Building upon seminal works such as ... our research provides further empirical evidence on ...\

-   Moreover, our paper aligns with asset pricing studies on the financialisation phenomenon, such as ...\

-   Our research provides a comprehensive analysis of ... which serves as a unique contribution to the literature.

-   Our paper contributes to the ongoing debates in the Journal of Futures Markets by providing a broader perspective on the phenomenon of financialisation.\

-   We build upon previous research in the journal by examining the impact of financialisation on a large cross-section of liquid commodities, rather than focusing on individual markets. This approach allows us to capture the global nature of financialisation and its effects on market fundamentals, which we believe have been overlooked in previous studies.

### Draft

Our paper advances the ongoing debates in the Journal of Futures Markets by providing an alternative examination of the financialisation phenomenon which serves as a unique contribution to the literature. Specifically, our research extends the dialogue on its impact on various aspects of the commodity complex including on co-movement and market integration both within the commodity space [@liu_analyzing_2021, @sehgal_who_2021, @yang_volatility_2021, @gong_time_2022] and with legacy asset classes [@conghui_liquidity_2020, @isleimeyyeh_role_2020, @daskalaki_new_2021, @han_trend_2022, @saishree_exploring_2022]; on market fundamentals [@isleimeyyeh_role_2020, @marechal_tale_2020, @yin_intermediary_2021], particularly risk transfer [@ahmadi_theory_2020] and price formation [@adammer_price_2018, @merkoulova_predictive_2020, @kupabado_financialisation_2021, @sehgal_who_2021]; as well as on investment in the sector [@daskalaki_new_2021, @han_trend_2022]. The paper also addresses the consequences of the phenomenon from a regulatory perspective, effectively contributing to the debate on futures markets oversight: @janardanan_commodity_2019, @fan_untold_2020, @hu_impact_2020, @mixon_us_2022, @szabo_margin_2022. Additionally, the study further extends the collection of recent seminal works that study financialisation using asset pricing techniques [@fan_untold_2020, @marechal_tale_2020, @yin_intermediary_2020, @han_trend_2022]. More generally, the paper provides an empirical complement to the growing body of research on co-movement and market integration within the commodity complex [@xiao_estimating_2020, @yang_return_2020, @luo_how_2021, @prokopczuk_dynamics_2021, @deBoer_intraday_2022, @dhaene_volatility_2022, @zhang_impact_2022] and beyond [@alquist_effect_2020, @kang_commodity_2020, @wong_impact_2020, @dark_lead_2021, @li_forecasting_2021, @liu_does_2022, @ming_contagion_2022, @zhang_do_2022, @zhang_influence_2023]; on commodity market fundamentals [@brooks_samuelson_2020, @llorente_trading_2020, @marechal_do_2021, @li_hedging_2022] including risk transfer [@fan_speculative_2020, @oglend_futures_2020, @huang_good_2023] and price formation [@bohmann_price_2019, @janardanan_commodity_2019, @arroyo_old_2020, @bohl_return_2020, @frino_sensitivity_2020, @siklos_metal_2020, @andersen_efficiency_2021, @figuerola_oil_2021, @geyer_determinants_2021, @gilbert_regional_2021, @yang_price_2021, @fuertes_risk_2022, @li_robust_2022, @bandyopadhyay_impact_2023, @chen_temperature_2023, @fan_wisdom_2023, @filippidis_evaluating_2023]; and on asset pricing in the context of commodity markets [@kang_commodity_2020, @yuan_pobability_2023].

## What is the novelty that the reader will learn from this paper and why is this knowledge important?

### Notes

-   Impact of financialisation went beyond mechanical effects that the main body of literature on financialisation focused on.
    -   The onset of financialisation altered the traditional risk shifting nature of hedger's behaviour, implied by the Keynesian hypothesis.\
-   Our results suggesting that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
-   The CHP factor model thus seems able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialisation.\
-   The results of this exercise provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.\
-   The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.\
-   Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggering a reversion to pre-financialisation dynamics.
-   Demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in Tang and Xiong (2012) and Basak and Pavlova (2016).

### Talking points

-   ... which have not been extensively studied in this context before.

-   Our paper equips readers with new, practical insights that combine these two frontier areas of financial research.\

-   The knowledge gained from this research can influence trading strategies, improve risk management practices, and spur further exploration of ...

-   The uniqueness of our paper lies in our comprehensive analysis of the co-movement dynamics across multiple commodity markets.\

-   Our study provides a nuanced understanding of how financialisation influences these relationships, thereby addressing a crucial gap in the literature.\

-   This understanding is crucial for investors, regulators, and policymakers in shaping risk management practices and investment strategies in the age of heightened financialisation.

-   We delve into the implications of increased financialisation.\

-   The importance of this research lies in the insights it provides for investors, regulators, and policymakers, helping them to shape risk management practices and investment strategies.

-   The novelty of our paper lies in our use of a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations. We argue that the global nature of financialisation makes cross-sectional co-movement a cornerstone issue, and we provide new insights into this issue through our analysis. We believe that this knowledge is important because it helps to deepen our understanding of the effects of financialisation on commodity markets and provides a more nuanced perspective on the debate about the impact of increased market participation.

### Draft

Drawing upon the issues and methods discussed in these studies, our research provides a broader perspective on the phenomenon of financialisation by examining its effects on a large cross-section of liquid commodities, rather than focusing on individual markets. This approach allows us to capture the global nature of financialisation and its influence on market fundamentals, an area of research that we believed has not yet been fully explored. We argue that the global nature of the phenomenon makes cross-sectional co-movement a cornerstone issue and we provide new insights into this issue through our novel approach, using a bespoke futures-based asset pricing framework. We deem this knowledge important because it helps to deepen our understanding of the consequences of financialisation for commodity markets and provides a more nuanced perspective on the debates about the phenomenon. We further believe this understanding is beneficial for regulator, policymakers and investors in shaping risk management practices and investment strategies in the age of heightened market participation.

## If published, what will this paper be cited for?

### Talking points

-   Additionally, our results provide compelling evidence on ..., offering a strong reference point for related debates in futures market research.

-   If published, our paper is likely to be cited for its meticulous analysis of the impact of financialisation on the co-movement between commodity futures.\

-   ... our findings that highlight ..., provide a solid reference for future studies on financialisation and commodity markets.

-   Upon publication, our paper is likely to be cited for its meticulous analysis of the impact of financialisation.

-   Specifically, our econometric approach and findings, which reveal ... provide a key reference for future research on financialisation and commodity markets.\

-   Furthermore, our study contributes to the discourse on futures markets oversight and index investment in futures markets, areas explored by ...

-   If published, we believe that this paper will be cited for its innovative approach to studying the phenomenon of financialisation. Our paper challenges the conventional focus on individual markets and instead emphasizes the importance of considering the global and cross-sectional effects of financialisation. We also introduce a new futures-based asset pricing framework that we believe will be of interest to other researchers in this field.

### Draft

If published, we believe that this paper will be cited for its innovative approach to studying the phenomenon of commodity markets financialisation. The paper challenges the conventional focus on individual markets and instead emphasises the importance of considering the global and cross-sectional impact of financialisation. Our results provide compelling evidence that the phenomenon had ontological consequences for the commodity complex, offering a key reference for future studies on financialisation and commodity markets. By further emphasising the regulatory implications of financialisation, our study also contributes to the discourse on futures markets oversight, offering an additional strong reference point.

## References

### 2024-06-11 others/journal submissions/journal of futures markets/literature review.qmd
Track 'others' folder

---
title: "Literature review"
format: docx
editor: visual
bibliography: literature_files/references.bib
---

```{r globals, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

folder <- "literature_files"; dir.create(folder); path <- paste(folder, "references.bib", sep = "/")
download.file("https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", path)
```

### [Price discovery dynamics in European agricultural markets](https://doi.org/10.1002/fut.21891 "@adammer_price_2018")

- The impact of the futures markets was high during the first period of price spikes (2007 to 2009) but lower during the second one (2010 to 2013).  
- More trading activity in futures markets did not lead to a higher influence on spot prices.

### [The theory of storage in the crude oil futures market, the role of financial conditions](https://doi.org/10.1002/fut.22113 "@ahmadi_theory_2020")

- Validates theory of storage in the crude oil market.

### [The effect of oil price shocks on asset markets: Evidence from oil inventory news](https://doi.org/10.1002/fut.22096 "@alquist_effect_2020")

- Equity prices decrease in response to higher oil prices before the 2007/2008 crisis but increase after it.  
- Positive oil price shocks cause a depreciation of the U.S. dollar against a broad range of currencies.  
- Positive oil price shocks have only a modest effect on bond futures returns.  
- Changes in risk premia help to explain the time‐varying effect of oil price shocks on U.S. equity returns.

### [Market inefficiencies surrounding energy announcements](https://doi.org/10.1002/fut.22264 "@alturki_market_2022")

- Evidence of inefficiency in crude oil futures and stock markets.

### [Efficiency in the Atlantic salmon futures market](https://doi.org/10.1002/fut.22204 "@andersen_efficiency_2021")

- Futures prices are efficient and unbiased in the long‐run, while being biased and inefficient in the short‐run.  
- Futures prices provide an adequate price discovery function for most contracts, while suffering from magnified risk premiums due to few noncommercial traders.

### [Old crop versus new crop prices: Explaining the correlation](https://doi.org/10.1002/fut.22106 "@arroyo_old_2020")

- Data shows high correlation between future prices with delivery dates before and after the harvest.  
- Correcting standard models by assuming that harvests appear continuously rather than at a single moment allows to to link preharvest and postharvest markets to the same source of supply, and hence obtain the empirically observed high correlation.

### [The impact of Sino–US trade war on price discovery of soybean: A double-edged sword?](https://doi.org/10.1002/fut.22415 "@bandyopadhyay_impact_2023")

- Negative impact of trade war on the leading role of US soybean futures in price discovery.  
- The trade war may have given some temporary economic and strategic benefit to the United States although it nearly killed the soybean market of the United States.

### [Return dynamics during periods of high speculation in a thinly traded commodity market](https://doi.org/10.1002/fut.22063 "@bohl_return_2020")

- Chicago Mercantile Exchange feeder cattle futures returns are predominantly explained by fundamentals.
- Volatility in this market is significantly driven by the speculation ratio.

### [Price discovery in commodity derivatives: Speculation or hedging?](https://doi.org/10.1002/fut.22021 "@bohmann_price_2019")

- Both commodity futures and option markets make a meaningful contribution to price discovery in recent times in the six most actively traded commodity markets.  
- On average, options lead futures in reflecting new information for a majority of these commodities.  
- Increased speculation, rather than hedging activity, in commodity derivatives is a key determinant of price discovery in the options markets.

### [Samuelson hypothesis, arbitrage activity, and futures term premiums](https://doi.org/10.1002/fut.22128 "@brooks_samuelson_2020")

- Samuelson hypothesis (or maturity effect): futures volatility increases as maturity decreases.\
- In most markets the slope factor is strongly negative in certain periods and at best only weakly negative in other periods.
- High inventory levels are found to correspond to flatter volatility term structures in seven futures, consistent with with the linkage between carry arbitrage and the Samuelson hypothesis.\
- Flatter volatility term structure corresponds to lower absolute futures term premiums.

### [Market uncertainty and sentiment around USDA announcements](https://doi.org/10.1002/fut.22283 "@cao_market_2022")

- Corn and soybean IVols are significantly lower for several trading days after a report.\
- The IVol response to a release depends on agricultural market experts' disagreement and sentiment before the USDA report, and on the extent to which the USDA information surprises the market.\
- IVols are generally positively related to the to financial‐market sentiment and macroeconomic uncertainty (VIX). This comovement breaks down on report days.

### [Temperature, storage, and natural gas futures prices](https://doi.org/10.1002/fut.22402 "@chen_temperature_2023")

- The authors' proposed measures of HDD (heating degree day) and CDD (cooling degree day) and temperature changes are important for explaining weekly changes in NG in storage and daily changes in NG futures prices and their variance.

### [Liquidity shocks, commodity financialization, and market comovements](https://doi.org/10.1002/fut.22127 "@conghui_liquidity_2020")

- Liquidity shocks, including both funding liquidity and market liquidity, are positively associated with comovements between commodity and stock markets after 2000.  
- The effect of liquidity on cross‐market correlations is state‐dependent and intensifies when liquidity conditions deteriorate and asset returns sustain substantial declines.  
- The structural change indicates that financialization creates a role for adverse liquidity shocks to increase cross‐market correlations.  
- A growing body of literature explores the risk transfers between commodity markets and stock markets (e.g., @buyuksahin_speculators_2014; @cheng_convective_2015; @ordu_food_2018). While these studies have different research issues, they all imply that liquidity (broadly defined) matters for risk transfers across markets with the financialization of commodity markets.  
- We provide direct evidence that financialization is a precondition for liquidity shocks to be passed through to commodity markets and that the risk transfer between commodity and stock markets intensifies when liquidity tightens and asset returns are poor.\
- We add to the debate on the driving forces behind the dynamics of correlations between commodity and stock markets.
    - First, business cycles do not explain the structural change of liquidity's role in accounting for cross‐market correlations that happened in the early 2000s.\
    - Second, we show that aside from funding liquidity, stock market liquidity also matters in predicting cross‐market correlations.\
    - Third, the significant association between corporate spreads and cross‐market correlations might not be driven by business cycles.

### [The lead of oil price rises on US equity market beliefs and preferences](https://doi.org/10.1002/fut.22247 "@dark_lead_2021")

- Oil price rises from a strengthening global economy have a state‐dependent lead on US equity market beliefs and preferences.

### [New evidence on commodity stocks](https://doi.org/10.1002/fut.22197 "@daskalaki_new_2021")

- Commodity futures provided superior diversification benefits pre-financialisation.
- Commodity stock investing is more profitable post-financialisation.
- Price‐based signals from futures markets can be used to achieve high commodity stock returns.

### [Intraday liquidity in soybean complex futures markets](https://doi.org/10.1002/fut.22325 "@deBoer_intraday_2022")

- Traders' order placement influenced by the liquidity of related markets.\
- Liquidity persistence and positive liquidity spillovers mainly occur within 30s. Spillovers for longer horizons are mostly negative.

### [Volatility spillovers: A sparse multivariate GARCH approach with an application to commodity markets](https://doi.org/10.1002/fut.22312 "@dhaene_volatility_2022")

- Correlation spillovers from metals and energy to agricultural commodities even though the latter tend to settle somewhat later

### [The untold story of commodity futures in China](https://doi.org/10.1002/fut.22087 "@fan_untold_2020")

- In the presence of retail‐dominance and barriers‐to‐entry, the term structure and momentum premia remain persistent, whereas hedging pressure, skewness, volatility, and liquidity premia are distorted by time‐varying margins and strict position limits.  
- Open interest, currency, and inflation premia are sensitive to institutional settings.  
- The observed premia cannot be attributed to common risks, sentiment, transactions costs, or data‐snooping, but are related to liquidity, anchoring, and regulation‐induced limits‐to‐arbitrage.

### [Speculative pressure](https://doi.org/10.1002/fut.22085 "@fan_speculative_2020")

- Long-short portfolios of futures contracts sorted by speculative pressure capture a significant premium in commodity, currency, and equity markets but not in fixed income markets.\
- Exposure to commodity, currency, and equity index futures' speculative pressure is priced in the broad cross-section after controlling for momentum, carry, global liquidity, and volatility risks.\
- There is an efficient hedgers-speculators risk transfer in commodity, currency, and equity index futures markets.\
- Contribution to literature.
    - Provides the first empirical investigation of the ability of tradeable long-short portfolios based on speculative pressure to capture premia in futures markets on instruments beyond commodities.\
    - We contribute to an "everywhere" pricing literature that has so far focused on the momentum, value and carry factors.\
    - Adds to the literature that investigates the potentially harmful impact of speculators on futures prices [@fattouh_role_2013; @irwin_devil_2009; @stoll_commodity_2010]. Finding that equity index, currency and commodity futures markets facilitate risk transfer and reward suggests that calls to regulate excessive speculation are unwarranted; speculators do not destabilize these futures markets, rather they are important providers of liquidity and risk-bearing facility to hedgers.

### [Wisdom of crowds and commodity pricing](https://doi.org/10.1002/fut.22393 "@fan_wisdom_2023")

- Commodities with lower (higher) sentiment shifts tend to be overvalued (undervalued) when the aggregate market is in backwardation (contango).  
- The sentiment premium is more pronounced during periods of macro contraction and deteriorating funding liquidity.  
- While the premium concentrates in commodities with higher tweet intensity, sentiment extracted from influential tweets (i.e., high number of retweets/ likes) does not exhibit stronger predictive ability than low‐attention tweets.  
- Consistent with the overreaction hypothesis, the sentiment premium fully reverses 3 years postformation.

### [Oil price analysts' forecasts](https://doi.org/10.1002/fut.22225 "@figuerola_oil_2021")

- Futures prices supersede analyst forecasts and elaborate a performance‐ based ranking of analyst firms.

### [Oil price analysts' forecasts](https://doi.org/10.1002/fut.22225 "@filippidis_evaluating_2023")

- The convenience yield, the global economic activity index, and the government bond yields act as the main factors that exercise a persistent and significant impact, for the largest part of the study period, although at different magnitude.\
- At different time periods there are additional factors that exercise a significant impact on the oil price differential, such as refining constraints, stock market volatility, trading volume, and geopolitical risk.\
- Unless a dynamic modeling framework is employed, the full spectrum of the related effects cannot be revealed.

### [The sensitivity of trading to the cost of information](https://doi.org/10.1002/fut.22152 "@frino_sensitivity_2020")

- Decrease in price discovery following two events that increase data access costs.

### [Risk-neutral skewness and commodity futures pricing](https://doi.org/10.1002/fut.22308 "@fuertes_risk_2022")

- The risk-neutral skewness (RNSK) signal exhibits a more stable and prolonged predictive ability.

### [Determinants of the WTI-Brent price spread revisited](https://doi.org/10.1002/fut.22184 "@geyer_determinants_2021")

- Important spread determinants are the convenience yield, as a proxy for crude oil inventories, the trading activity in crude oil paper markets, shipping costs, as well as the stock market development in the United States and Europe.  
- After the break in 2010, the paper market activity, open interest, and shipping costs have become more important spread drivers.

### [Regional premiums in nonferrous metals markets](https://doi.org/10.1002/fut.22245 "@gilbert_regional_2021")

- Transaction prices also include a regional premium that can account for a substantial component of the full price.
- In well-supplied markets, premiums measure the cost of intermediating exchange warehouses and consumers. In periods of tight demand they reflect the urgency of consumer requirements.

### [Financially constrained index futures arbitrage](https://doi.org/10.1002/fut.22293 "@glover_financially_2022")

- The price of an index futures contract and the value of its underlying index should deviate further from their theoretical cost-of-carry relationship when (a) the contract has a long time to go before expiry, and (b) volatility is high.  
- These predictions enjoy considerable empirical support which highlights the importance of financing constraints for explaining index futures mispricing.

### [Time-varying pure contagion effect between energy and nonenergy commodity markets](https://doi.org/10.1002/fut.22366 "@gong_time_2022")

- Significant pure contagion effects between energy and industrial metals markets in most periods.
- Pure contagion effects between energy and precious metals and agricultural markets occur only in a few specific periods.
- Energy is the main price transmitter.
- Financialisation gradually increases the frequency and harm of pure contagion effects.
- The COVID-19 pandemic exacerbates the pure contagion effects between energy and precious metals and agricultural markets.

### [A trend factor in commodity futures markets: Any economic gains from using information over investment horizons?](https://doi.org/10.1002/fut.22291 "@han_trend_2022")

- The trend factor generates statistically and economically large returns during the post-financialization period 2004--2020.  
- The trend factor cannot be explained by the existing factor models and is priced cross-sectionally.
- The trend factor is correlated with funding liquidity measured by the TED spread.  
- There are significant economic gains from using the information on historical prices in commodity futures markets.

### [The impact of trading restrictions and margin requirements on stock index futures](https://doi.org/10.1002/fut.22111 "@hu_impact_2020")

- The divergence of stock index futures prices from their theoretical values may be due to various trading and regulatory constraints, such as position limits and margin requirements, which play significant roles in Chinese market.

### [A good hedge or safe haven? The hedging ability of China's commodity futures market under extreme market conditions](https://doi.org/10.1002/fut.22423 "@huang_good_2023")

- Most futures products are good hedges and safe havens for the corresponding spot prices.
- The hedge ratios of most commodities should increase moderately in both bearish and bullish markets.
- Participating in the futures market can effectively manage risk. [...] investors pay attention to market dynamics and adjust their portfolios promptly.

### [The role of financial investors in determining the commodity futures risk premium](https://doi.org/10.1002/fut.22122 "@isleimeyyeh_role_2020")

- The effect of the stock market on the energy market became significantly greater for the futures risk premium in the period following the 2008 crisis.  
- This study extends studies that broadly address the financialization of commodities and specifically the risk premium in commodity markets.

### [On commodity price limits](https://doi.org/10.1002/fut.21999, "@janardanan_commodity_2019")

- Limits events are associated with shocks to fundamentals that lead to persistent price changes.  
- When futures trading halts price discovery migrates to options markets, but option prices provide a biased estimate of subsequent future prices when trading resumes.

### [Can commodity futures risk factors predict economic growth?](https://doi.org/10.1002/fut.22155 "@kang_commodity_2020")

- Three factors capturing term premia on the basis-momentum, basis, and change in slope are robust predictors for future economic growth, especially for long horizons.  
- Findings highlight the importance of the term premia, rather than the spot premia on which the literature has mainly focused.

### [Financialization, common stochastic trends, and commodity prices](https://doi.org/10.1002/fut.22269 "@kupabado_financialisation_2021")

- Financialization has contributed to the price movements of these commodities.

### [Forecasting equity returns: The role of commodity futures along the supply chain](https://doi.org/10.1002/fut.22167 "@li_forecasting_2021")

- A considerable number of commodities exhibit significant in-sample forecasting ability at the daily horizon, especially for supplier-side equity returns.  
- The macroeconomic risk premium effect, captured by the aggregate commodity prices, is an important source for this predictability.
- Results remain significant out-of-sample with forecasting performance improving substantially during recessions or with economic constraints.

### [The hedging pressure hypothesis and the risk premium in the soybean reverse crush spread](https://doi.org/10.1002/fut.22285 "@li_hedging_2022")

- Strong evidence of a positive return to speculators who provide futures liquidity for the soybean crush.

### [Robust information share measures with an application on the international crude oil markets](https://doi.org/10.1002/fut.22292 "@li_robust_2022")

- Authors develop an information share measure that is robust to large price movements.

### [Analyzing the frequency dynamics of volatility spillovers across precious and industrial metal markets](https://doi.org/10.1002/fut.22217 "@liu_analyzing_2021")

- While volatility spillovers across industrial metals are higher than across precious metals, the opposite occurs during crisis periods where precious metals cause net volatility spillovers to industrial metals.  
- Volatility spillovers of the two metal groups show different dynamics in the short-, medium- and long-term components, especially in the short- and medium-term components.

### [Does clean energy matter? Revisiting the spillovers between energy and foreign exchange markets](https://doi.org/10.1002/fut.22340 "@liu_does_2022")

- During the collapse of oil prices from 2014 to 2016, crude oil futures were at the center of the risk contagion.  
- Since the COVID-19 pandemic broke out, the spillovers of clean energy metal futures have become one of the main sources of the risk contagion.  
- Crude oil and the US dollar are the most important contributors to the spillovers, but further spillovers are emerging between the Chinese yuan, euro, and Japanese yen with clean energy metals.

### [Trading and information in futures markets](https://doi.org/10.1002/fut.22079 "@llorente_trading_2020")

- Nonmembers (CTI4) consume most of the intraday liquidity while local traders (CTI1) as market makers are its main provider. Both groups combine most of the intraday trading volume.  
- Changes in the overnight positions of the general public (CTI4) and clearing members (CTI2) contribute mostly to daily price discovery, while the positions of CTI3 group reflect possible information advantage about future price movements.

### [How trading in commodity futures option markets impacts commodity futures prices](https://doi.org/10.1002/fut.22221 "@luo_how_2021")

- For both commercial traders and noncommercial traders, options position changes impact the futures price in the same direction as futures position changes.\
- The nonmomentum of position changes of options market contributes overwhelmingly relative to the idiosyncratic risk and hedging pressure in the case of noncommercial trading.

### [A tale of two premiums revisited](https://doi.org/10.1002/fut.22396 "@marechal_tale_2020")

- An optimal asset‐pricing model for commodity futures consist of 4 factors: (i) the basis, (ii) basis‐momentum, (iii) momentum, and (iv) the "crowding".
- Financialization has not influenced prices but plays a role in the reorganization of futures markets as an insurance market in which the index traders supply insurance to
producers, thereby decreasing the insurance premium. Conversely, this market reorganization does not affect the premium captured by producers in providing liquidity to speculators. Given these results, the financialization would benefit the producers both ways.

### [Do economic variables forecast commodity futures volatility?](https://doi.org/10.1002/fut.22250 "@marechal_do_2021")

- Support found for the "uncertainty resolution" and the "theory of storage" hypotheses.   
- The "time to maturity" hypothesis is rejected.

### [Predictive abilities of speculators in energy markets](https://doi.org/10.1002/fut.22058 "@merkoulova_predictive_2020")

- Speculators are successful in taking profitable positions in energy futures markets.  
    The magnitude of this effect is lower than that for agricultural markets.
- Energy speculators’ returns are due to the existence of the risk premiums rather than to speculators’ forecasting abilities.  
- Futures risk premium is highly time-variant.
    Energy investors’ profits have been very limited in the GFC and post-GFC period, which coincided with the financialization of commodity markets.

### [Contagion or flight-to-quality? The linkage between oil price and the US dollar based on the local Gaussian approach](https://doi.org/10.1002/fut.22307 "@ming_contagion_2022")

- Evidence found of a contagion effect the prices of West Texas Intermediate futures and the US dollar in the 1990 Gulf War.  
- Evidence found that flight-to-quality phenomena from oil to the US dollar is a common feature for the 2008 and 2014 oil crashes.  
    Implicitly emphasizes the safe-haven role of the US dollar during oil market turmoil.

### [US experience with futures transaction taxes](https://doi.org/10.1002/fut.22276 "@mixon_us_2022")

- The transaction tax on futures reduced trading volume during the 1920s and 1930s but had no apparent effect on volatility or open interest.
- The relative magnitude of the tax was highest for intermediaries and appears to have substantially reduced intra-day trading, but it did not dramatically affect hedging activity or the level of cash or futures prices.

### [Futures market hedging efficiency in a new futures exchange: Effects of trade partner diversification](https://doi.org/10.1002/fut.22088 "@oglend_futures_2020")

- Larger firms with greater trade partner diversification have lower basis risk.   
    Such firms align their internal transaction price closer to the common spot price in the market, which encourages greater futures market participation.

### [Effects of nondiscretionary trading on futures prices](https://doi.org/10.1002/fut.22377 "@ONeill_effects_2023")

- The ETPs' informationless, mechanical rebalancing of futures positions to maintain the constant maturity of the index and the promised leverage ratios of the VIX ETPs have significantly positive predictive power for end-of-day futures returns.  
- The impact on price has diminished through time from increased liquidity provided by hedge funds, and the “natural” hedging of the issuers' inverse products.

### [The dynamics of commodity return comovements](https://doi.org/10.1002/fut.22222 "@prokopczuk_dynamics_2021")

- A simple one-factor model based on the first principal component extracted from a panel of commodity returns outperforms a macroeconomic model, and explains most of the realized comovements.  
- Intersectoral correlations display more time variations than intrasectoral correlations.  
- Comovements are driven by the variation of the factor as opposed to exposure to it.  
- Results cast doubt on the persistence of the effects of financialization and emphasize the importance of the dynamics of the factor variance.

### [Exploring the dynamics of the equity–commodity nexus: A study of base metal futures](https://doi.org/10.1002/fut.22358 "@saishree_exploring_2022")

- 36\% of the return forecast error variance originates from spillovers, to which the contribution of equity indices is minimal.
    Indicates segmentation between the two markets which offer the scope for potential diversification.
- Base metal futures are the net transmitters and equity indices are the net recipients of spillovers.

### [Who leads in intraday gold price discovery and volatility connectedness: Spot, futures, or exchange-traded fund?](https://doi.org/10.1002/fut.22208 "@sehgal_who_2021")

- Gold futures are a global leader in price discovery and volatility spillover.  
- Intraday variation in price discovery leadership is due to liquidity, hedging effectiveness, price jumps, investor attention, and macroeconomic states.

### [Metal prices made in China? A network analysis of industrial metal futures](https://doi.org/10.1002/fut.22125 "@siklos_metal_2020")

- China, despite its role as key actor in both real and financial industrial metal markets, is a price taker.

### [Margin requirements based on a stochastic correlation model](https://doi.org/10.1002/fut.22360 "@szabo_margin_2022")

- An unnecessarily large overmargin requirement is set by regulators when the applied risk measure is not calculated via a portfoliowise treatment.
- Accounting for the correlation structure of the assets during the margining process would not lead to an overly prudent method, nor would it cause greater procyclicality.

### [Impact of international energy prices on China's industries](https://doi.org/10.1002/fut.22090 "@wong_impact_2020")

- Evidence found that crude oil futures have the most significant influence.  
- Stock returns of oil-related companies are more closely align to Brent and WTI's futures returns following China's key oil pricing reform on March 27, 2013.  
  Overall, Chinese industries are also more exposed to global crude oil futures volatility after this event.

### [Estimating the connectedness of commodity futures using a network approach](https://doi.org/10.1002/fut.22086 "@xiao_estimating_2020")

- Metal futures are net transmitters of shocks to other futures, and agricultural futures are vulnerable to shocks from the others.  
- Almost two-thirds of the volatility uncertainty for commodity futures are due to the connectedness of shocks across the futures market.  
- Connectedness always increases in times of turmoil.  
- Investors could be forewarned that the connectedness of various classes of futures could threaten their portfolios.

### [Return and volatility transmission between China's and international crude oil futures markets: A first look](https://doi.org/10.1002/fut.22103 "@yang_return_2020")

- Evidence found of cointegration relationships among crude oil futures in China and international major crude oil futures markets.  
  Both China's and Oman's oil futures markets react to deviations from their long-run equilibrium with West Texas Intermediate and Brent oil futures.   
- Evidence found of asymmetric volatilities and correlations across these oil futures markets.   
- The Chinese oil futures have stronger linkages with the international major futures markets than Oman futures.

### [Price discovery in chinese agricultural futures markets: A comprehensive look](https://doi.org/10.1002/fut.22179 "@yang_price_2021")

- China's agricultural futures markets generally play a more dominant role in the price discovery process as the markets become mature.

### [Volatility spillovers in commodity futures markets: A network approach](https://doi.org/10.1002/fut.22270 "@yang_volatility_2021")

- The total volatility connectedness across commodities is substantial and fluctuates within the range of 30\%–60\%, which is largely driven by low-frequency volatility connectedness.  
- Energy futures as a group and crude oil and soybeans as individual commodities play dominant roles as net senders of volatility shocks in the system of 25 commodities.  
- Commodity volatility spillovers at medium and particularly low frequency account for over 40\% of the total volatility connectedness, which can be significantly explained by economic factors related to broad economic conditions.  
  Implies that the effect of the financialization of commodities might be more limited than previously assumed.

### [Probability weighting in commodity futures markets](https://doi.org/10.1002/fut.22400 "@yuan_pobability_2023")

- Commodities with a high probability-weighting value significantly underperform their low-value pairs by 11\% per annum.
  Neither conventional commodity risk factors nor existing characteristics explain this predictability.   
  The predictability is more pronounced when arbitrage constraints are more binding.  
- Commodities with a high probability-weighting value also attract excess demand from non-commercial traders.  
- Collectively, these findings support a prospect theory-based explanation for the cross-section of commodity returns.

### [Intermediary asset pricing in commodity futures returns](https://doi.org/10.1002/fut.22099 "@yin_intermediary_2020")

- The intermediary capital (IC) effect is substantially positive and continues to grow as the financialization of commodities deepens.  
- The effect of the positive IC risk factor varies significantly.  
- Portfolios with low basis, low open interest, low momentum, and low liquidity earn significantly higher returns than counterparty portfolios.

### [Intermediary capital risk and commodity futures volatility](https://doi.org/10.1002/fut.22185 "@yin_intermediary_2021")

- The overall effect of intermediary capital risk (ICR) is negative and more significant for the post-2008 period, although positive and negative ICR play asymmetric roles.  
- Evidence of heterogeneous structure of dependence across the volatility distribution:  
  - ICR strengthens toward upper volatility percentiles.
  - Financialization in commodities flattens this dynamic trace.
- The ability of ICR to convey economic news is the most economically important source of the dependence.

### [Can a rational expectation storage model explain the USDA ending grain stocks forecast errors?](https://doi.org/10.1002/fut.22282 "@zhang_can_2022")

- There is a predictable component of forecast errors from 1980/81 to 2018/19 that can partially be explained by the temporal basis and monthly stocks, two important factors from a rational expectation storage model that codetermines carry.  
- The USDA ending stocks forecasts can be improved by 7.1\%, 7.2\%, and 4.5\% for corn, soybean, and wheat, respectively.  
  The improvement is most significant when the last year's carry is small.

### [Do oil shocks impact stock liquidity?](https://doi.org/10.1002/fut.22289 "@zhang_do_2022")

- Evidence that differentiated oil shocks have distinctive influence on stock liquidity.  
  Oil shocks driven by demand lower stock liquidity, whereas oil supply shocks have the opposite effect.  
- Generally large corporations are more affected by oil demand and supply shocks.  
- That oil, oil-related, oil-user and the broad market categories are most affected by oil shocks, but the effects on oil-substitutes are minimum.

### [Hedging pressure and liquidity provision in commodity options markets](https://doi.org/10.1002/fut.22327 "@zhang_hedging_2022")

- There are significant hedging pressure effects in commodity options markets.  
- The empirical results indicate that commercials (swap dealers) provide liquidity to non-commercials (money managers) in commodity options markets in the short run.

### [The impact of COVID-19 on the interdependence between US and Chinese oil futures markets](https://doi.org/10.1002/fut.22326 "@zhang_impact_2022")

- The COVID-19 pandemic enhanced the long-run correlation between the two oil markets.  
  In contrast, daily changes in pandemic severity had a negative effect on the short-term transient correlation.  
- COVID-19 changed the one-direction causality from the US oil market to the Chinese market in the pre-COVID period to a bidirectional causal relation between the two markets during the COVID period.  
  It strengthened the volatility spillover effect from the Chinese to US markets.

### [The influence of oil price uncertainty on stock liquidity](https://doi.org/10.1002/fut.22383 "@zhang_influence_2023")

- Elevated oil price uncertainty has a significant and negative influence on stock liquidity.  
  Large oil-related corporations are most affected, followed by small-listed firms more generally.  
- Liquidity providers widen the bid-ask spreads to protect themselves during periods of high oil price uncertainty for large-listed firms, particularly those in the oil industry.

## References

### 2024-06-11 others/paper/custom/LaTeX/main.tex
Track 'others' folder

\documentclass[11pt, letterpaper, doublespacing]{article}

\usepackage{setspace}

\makeatletter

\renewcommand{\@seccntformat}[1]{\@nameuse{the#1}.~{}}

\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\Alph{subsection}}
\renewcommand{\thesubsubsection}{\arabic{subsubsection}}

\renewcommand{\section}{\@startsection {section}{1}{\z@}%
  {-3.5ex \@plus -1ex \@minus -.2ex}%
  {2.3ex \@plus.2ex}%
  {\centering\normalfont\large\bfseries}}

\renewcommand{\subsection}{\@startsection{subsection}{2}{\z@}%
  {-3.25ex\@plus -1ex \@minus -.2ex}%
  {1.5ex \@plus .2ex}%
  {\normalfont\large\slshape}}

\renewcommand{\subsubsection}{\@startsection{subsubsection}{3}{\z@}%
  {-3.25ex\@plus -1ex \@minus -.2ex}%
  {1.5ex \@plus .2ex}%
  {\centering\normalfont\slshape}}

\makeatother

% \newtheoremstyle{plain}{9pt}{9pt}{\itshape}{0pt}{\scshape}{:}{3pt}{}

% \theoremstyle{plain}

% \newtheorem{assumption}{Assumption}
% \newtheorem{corollary}{Corollary}
% \newtheorem{definition}{Definition}
% \newtheorem{lemma}{Lemma}  
% \newtheorem{proposition}{Proposition}
% \newtheorem{remark}{Remark}
% \newtheorem{theorem}{Theorem}

% \usepackage[bf,small,nooneline,normal]{caption}
% \renewcommand*{\captionlabeldelim}{\nobreak}
% \renewcommand*\captionlabeldelim{.}
% \renewcommand{\captionfont}{\bfseries}

\renewcommand{\thetable}{\Roman{table}}

\usepackage{indentfirst}

\renewcommand{\abstractname}{\bf \small ABSTRACT}

\renewcommand{\refname}{\bf \small REFERENCES}

\usepackage{endnotes}
\renewcommand{\footnote}{\endnote}
\renewcommand{\notesname}{\bf Footnotes}

\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Financialization of commodities: an asset pricing perspective},
            pdfauthor={Devraj Basu, Olivier Bautheac},
            pdfkeywords={Financialization of commodities, futures contracts in agricultural
commodities, speculative bubbles, volume, open interest, convenience
yield.},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{jf}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Financialization of commodities: an asset pricing perspective}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Devraj Basu, Olivier Bautheac}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \date{}
  \predate{}\postdate{}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

\usepackage{caption}
\usepackage{setspace}
\doublespacing

\begin{document}
\maketitle
\begin{abstract}
The last two decades have seen major changes in the nature of the
commodity markets with the influx of financial investor inflows followed
by the financial crisis. We study the effect of these events on
commodity futures pricing dynamics using commodity asset pricing
techniques. We consider both futures market based factors and the
traditional market factor and find that a hedging pressure based factor
is able to best detect the effects of commodity financialization while
the effects of the financial crisis and after are most clearly visible
through the performance of the market factor. The futures market seems
to have been the main channel for the effects of commodity
financialization, which seems to have delivered an exogenous schock to
the cross-section of global commodities.
\end{abstract}

\newpage

\section{Introduction}\label{introduction}

The last twenty years have seen major upheavals in the commodity markets
with the onset of financialization\footnote{Starting around 2004, with a
  view of commodity markets as an emerging asset class and in an effort
  to hedge against inflation and seek diversification benefits
  \citep{buyuksahin_speculators_2014, singleton_investor_2013},
  institutional investors sent forth an unprecedented flow of capital
  into commodity futures markets. This phenomenon is commonly referred
  to as the financialization of commodities
  \citep{domanski_financial_2007}.} as well as the period of the 2008
financial crisis and its aftermath. Financialization appears to have
affected a number of economic sectors, including agriculture and energy,
and its impact has been hotly debated in the policy, legislative,
regulatory, and academic spheres. A vigorous legislative debate has led
to regulatory changes\footnote{Concerns over the consequences of
  financialization were behind Rule 76 FR 4752 issued by the U.S.
  Commodity Futures Trading Commission (CFTC) on January 26, 2011. This
  provision emanates from the Dodd-Frank Wall Street and Consumer
  Protection Act of 2010 (Title VII, Section 737) that mandates the CFTC
  to use position limits to restrict the flow of speculative capital
  into a number of commodity markets. The Rule was approved in a close
  3-2 vote and the ensuing rulemaking process was extremely contentious
  with several commissioners (Michael Dunn and Scott D. O'Malia in
  particular) expressing reservations about the lack of supporting
  evidence and the Rule also triggering thousands of comment letters as
  well as a lawsuit against the CFTC spearheaded by two Wall Street
  trade groups, namely the International Swaps \& Derivatives
  Association (ISDA) and the Securities Industries \& Financial Markets
  Association (SIFMA) (ISDA \& SIFMA v U.S. CFTC; Complaint,
  1:11-cv-02146; December 2, 2011).} accompanied by an equally intense
policy and academic debate across a number of disciplines about the
perceived effects on commodity prices of the unprecedented inflow of
institutional funds brought into commodity futures markets by new index
type investors\footnote{The first responses to the 2007/2008 crisis of
  escalating food and energy prices took the form of policy reports,
  many of which reasoned that the growth of commodity index funds came
  along with an influx of largely speculative capital that was
  responsible for driving commodity prices beyond their historic highs
  \citep{de_schutter_food_2010_1, gilbert_speculative_2010, herman_not_2011_1, schumann_hunger-makers_2011, unctad_global_2009}.}.
In response to immediate policy concerns, the academic debate was
initially framed rather narrowly\footnote{Early U.S. Senate
  investigations drew on pricing and trading data supplied by the CFTC
  as well as interviews with numerous experts including hedge fund
  manager Michael Masters who linked the growing presence of index
  investors in U.S. wheat markets to the observed surges in both futures
  and cash prices
  \citep{masters_testimony_2008, masters_accidental_2008}. This
  contention has since come to be known as the Masters' hypothesis and
  was largely endorsed by the final U.S. Senate report on the issue
  \citep{USSenate_Excessive_speculation_wheat_2009}. At this stage, the
  question thrust on the academic sphere was whether ``excessive
  speculation'' (understood as the peculiar market activity of index
  type investors) was linked to escalating energy and agricultural
  commodity prices.} and used a fairly restricted set of statistical
techniques\footnote{Most of the studies focused on statistical analyses
  of the Granger type causal connections between ``excessive
  speculation'' and commodity prices.}.

In this paper we take a fundamentally different empirical approach that
is broader in scope. We consider the entire cross-section of actively
traded commodities on futures markets and use a futures based asset
pricing framework that includes factors constructed using both price and
non-price attributes. Factor model techniques are well suited to
isolating common driving factors and detecting co-movement, a central
issue in financialization which we believe the existing literature has
not fully analyzed.\\
The first factor model we consider (CHP) is based on the well-known
hedging pressure based theory
\citep{anderson_hedger_1983, chang_returns_1985, cootner_returns_1960, dusak_futures_1973, hicks_value_1939, hirshleifer_risk_1988, hirshleifer_determinants_1989, hirshleifer_hedging_1990, kolb_is_1992, keynes_treatise_1930}
which postulates that futures prices for a given commodity are inversely
related to the extent that commercial hedgers are short or long and we
use a factor mimicking portfolio that captures the impact of hedging
pressure as a systemic factor \citep{basu_capturing_2013}. Our second
factor model is based on open interest growth following
\citet{hong_what_2012} who find that open interest growth has predictive
power for individual commodity returns and again we construct a
long-short factor mimicking portfolio. Our third model is based on term
structure following \citet{szymanowska_anatomy_2014} and
\citet{fuertes_commodity_2015} who demonstrate that the term structure
factor has explanatory power for the cross-section of commodity returns.
We finally consider an equally weighted portfolio of commodities as a
proxy for the market factor. Our two price based and two non-price based
factors allow us to compare and contrast different channels that could
have led to changes in commodity price dynamics over the last twenty
years.

We study the performance of these models on a set of twenty-four U.S.
traded commodities and six non-U.S. traded (LME traded) industrial
metals over the 1997/2017 period that we divide into four distinct
sub-periods. The first, the pre-financialization phase, spans the
1997/2003 period; the second, the financialization phase, spans the
2004/2007 period\footnote{Starting point based on earlier studies
  \citep{baker_financialization_2014, christoffersen_factor_2014}.}; the
third, 2008/2013, encompasses both the financial crisis and the loose
monetary policy regimes that followed; and the fourth spans the period
starting in 2014 to present.\\
Consistent with earlier studies, we observe that mean returns for the
U.S. traded commodities are sharply higher over the financialization
period compared to pre-financialization and this pattern extends to LME
traded metals.

The cross-sectional nature of financialization
\citep{basak_model_2016, cheng_financialization_2014} leads us to
extends the Keynesian indivudal hedging pressure paradigm by
incorporating aggregate CHP (\(\mathbf{CHP}\)), a market wide measure of
hedging pressure. This paradigm implies that returns for individual
commodities should be high in periods where \(\mathbf{CHP}\) is low
(\(\mathbf{backwardation}\)) and low in periods where \(\mathbf{CHP}\)
is high (\(\mathbf{contango}\)) vice et versa. Over the first period the
cross sectional average returns during \(\mathbf{backwardation}\) for
both the US and UK commodities are positive with those for the US
statistically significant, and significantly higher than during
\(\mathbf{contango}\), providing broad support for an aggregate version
of the Keynesian hedging pressure hypothesis. Over the second period
this pattern reverses, with both the US and UK commodities having
significant positive returns during \(\mathbf{contango}\) with these
returns being significantly higher than during
\(\mathbf{backwardation}\). This change in pattern suggests that the
onset of financialization altered the traditional risk shifting nature
of hedger's behaviour, which is implied by the Keynesian hypothesis.

We analyze the pricing dynamics over the different periods by first
studying the time series pricing performance of the various factors on
all the U.S. traded commodities with the factors constructed using the
latter set of commodities. The market based factor outperforms the other
three in the first period and it has a similar level of performance in
the second period, while the CHP factor shows the greatest improvement
in performance in the second period. The performance of the market
factor is driven by agricultural commodities and metals in both the
first and second period and the dramatic improvement of the CHP factor
in the second period is driven by precious and precious industrial
metals. The best performing commodities for the market factor exhibited
approximately the same level of price co-movement both before and during
financialization. In contrast, the best performing commodities for the
CHP factor exhibited very low pair-wise correlation in the first period,
around the average for U.S. traded commodities, while during
financialization the average pairwise correlation between the top
performing CHP factor commodities is higher than that for the market
factor and double of the average for all the U.S. traded commodities.
This increase is due to the dramatic rise in average pairwise
correlation amongst the U.S. traded metals all of which exhibited high
R\textsuperscript{2} with respect to the CHP factor during
financialization which in turn is due to their common low level of CHP
over this period. Thus the CHP factor model is able to establish the
strengthening link between a non-price attribute and price dynamics in
the U.S. metal sub-sector during financialization.\\
We explore this issue further by constructing the four factors with the
top eight commodities for a given factor (factor picks) in each
period\footnote{See section 2.2 for further details.} and evaluating its
performance on these selected commodities as well as on all U.S. traded
commodities. The logic of this exercise is to determine the extent to
which the pricing performance of these factors in each period is
concentrated in a subset of commodities. The CHP and the market factors
built from CHP factor picks exhibit the most dramatic increase in
pricing performance on the corresponding factor picks in the second
period. In contrast, the increase in pricing performance on all the U.S.
traded commodities is roughly uniform across all sets of factor models
and lower in magnitude. This strongly suggests that the hedging pressure
co-movement and price co-movement link was concentrated in the metals
sub-sector. There is also a dramatic improvement in pricing performance
of the CHP factor built with term structure picks indicating convergence
between Keynesian and Working's theories of the futures term structure
in a U.S. context.

The LME traded industrial metals provide a useful set of assets to test
how widespread were the changes in pricing dynamics brought about by the
onset of financialization. To that end, we examine the performance of
the four factors on the six LME metals, when constructed from each set
of factor picks. The performance of the market factor built with the CHP
and term structure factor picks improves dramatically in the second
period relative to the first while the performance of all factors built
with the other sets of picks does not increase quite as much. The
pricing performance of the market factor built with CHP factor picks as
well as that of the CHP factor built with both CHP and term structure
factor picks show a dramatic increase over the financialization period.
The performance of the market factor built with the CHP factor picks
suggests that there was co-movement in global metals returns in the
second period and that this co-movement could be detected by our hedging
pressure based model while the performance of the CHP factor built with
term structure factor picks indicates the aforementioned convergence
between Keynesian and Working's views of commodity futures term
structure extends to a global context.

Our analysis suggests that financialization appears to have had the
deepest impact on global metals markets and our commodity asset pricing
based approach allows us to better understand the channels through which
it was transmitted. The initial view of financialization was that it
consisted of speculative flows which had the effect to driving up and
creating bubble like conditions in commodity future prices\footnote{\citet{de_schutter_food_2010_1};
  \citet{gilbert_how_2010}; \citet{gilbert_speculative_2010};
  \citet{masters_testimony_2008}; \citet{masters_accidental_2008};
  \citet{herman_not_2011_1}; \citet{schumann_hunger-makers_2011};
  \citet{singleton_investor_2013}; \citet{unctad_global_2009}}. A number
of academic studies, most of which used commodity specific causality and
correlation based analysis, have disproved this contention, particularly
in the case of agricultural and energy commodities\footnote{\citet{irwin_devil_2009},
  \citet{sanders_adequacy_2010}, \citet{sanders_impact_2011},
  \citet{sanders_new_2011}, \citet{irwin_commodity_2013},
  \citet{brunetti_commodity_2014}, \citet{hamilton_effects_2015} and
  \citet{bruno_financialization_2017} study the agricultural markets.
  \citet{buyuksahin_speculators_2011}, \citet{tokic_speculation_2012},
  \citet{fattouh_role_2013}, \citet{kilian_role_2014},
  \citet{knittel_simple_2016} and \citet{manera_modelling_2016} study
  the energy markets. \citet{bohl_does_2013_2}, \citet{kim_does_2015}
  and \citet{boyd_prevalence_2016} study both energy and agricultural
  markets while \citet{irwin_index_2011},
  \citet{irwin_financialization_2012} and \citet{stoll_commodity_2011}
  study the commodity markets in general.}, while other studies have
underlined various alterations in commodity pricing dynamics over the
period\footnote{\citet{gilbert_role_2014} reject the view that
  financialization has not had any effects in the grains markets and
  demonstrate that trades originated by financial actors, and
  specifically index investors, can move prices but tend typically to be
  volatility-reducing. \citet{cheng_financialization_2014} show that in
  the case of index commodities, financialization has transformed the
  risk sharing, and information discovery functions of commodity futures
  markets. \citet{juvenal_speculation_2015} contend that the oil price
  increase between 2004 and 2008 was mainly driven by the strength of
  global demand but that the financialization process of commodity
  markets also played a role. \citet{henderson_new_2015} show that
  non-information-based financial investments have important impacts on
  commodity prices.}. However, the fundamental question of the nature of
the impact of financialization on commodity futures markets has not yet
been completely answered. Our analysis takes a broader perspective and
shifts the focus away from the energy and agricultural sectors. We
provide an empirical complement to a new stream of theoretical studies
that try to model the impact of financialization on various aspects of
commodity futures markets\footnote{\citet{etula_broker-dealer_2013},
  \citet{acharya_limits_2013}, \citet{cheng_convective_2014},
  \citet{leclercq_equilibrium_2014}, \citet{sockin_informational_2015},
  \citet{goldstein_speculation_2013},
  \citet{EkelandSpeculationcommodityfutures2016},
  \citet{goldstein_commodity_2017}.}, as well as extend the empirical
findings of \citet{basak_model_2016} and \citet{tang_index_2012}. In
contrast to the earlier purely statistical studies that were designed to
study speculative behavior alone, our empirical approach allows us to
isolate the more subtle effects of financialization identified in the
theoretical studies above.

The onset of the financial crisis and the monetary policy regimes that
followed appear to have also induced significant changes in pricing
dynamics. Returns on both U.S. and LME traded commodities fell
dramatically over both the third and fourth periods with the pattern of
return for the U.S. traded commodities across \(\mathbf{CHP}\) regimes
reverting to Keynesian paradigm. The pricing results indicate the
presence of a systematic factor across the entire cross-section of the
U.S. commodities as the performance of the market factor built with
every set of picks on the entire set of U.S. traded commodities shows a
dramatic rise across the board in pricing performance. There is also
strong evidence of cross-market linkages as the market factor built with
its own picks (U.S. traded commodities) shows a six fold increase in
average R\textsuperscript{2} on the LME metals compared with the
financialization period. The market factor when built with equity index
(S\&P 500) picks does even better, providing strong evidence of
systematic spill-overs from the equity to the commodity markets.

Financialization was an issue of such policy importance that it
triggered legislative action. The debate was initially framed around
adequacy of speculation, the burning issue of the day, and the
consequent analysis focused on the more mechanical effects of
financialization. With the benefit of hindsight, it appears this
approach was perhaps too narrow and it now seems necessary to address
financialization from a broader perspective. Commodity price dynamics
appear to have altered substantially in quite different ways over the
financialization and the financial crisis periods and our commodity
futures based asset pricing approach seems to be able to provide new
insights into the nature of these changes: financialization was a
phenomenon endogenous to the commodity markets transmitted via the
commodity futures markets and mainly concentrated in a specific sector
(metals) while the crisis and its aftermath seems to have delivered an
exogenous shock across the entire cross-section of global commodities.

\section{Data \& methods}\label{data-methods}

\subsection{Data}\label{data}

Commodity index funds (CIFs), commodity based exchange traded funds
(ETFs) and notes (ETNs) as well as commodity linked notes (CLNs) were
amongst the main investment vehicules that allowed institutional and
retail investors to build up commodity exposure in the early 2000s
\citep{boons_stock_2012, henderson_new_2015, irwin_index_2011, unctad_global_2009, schumann_hunger-makers_2011}.
Most of these products were primarily designed to track prominent
commodity indexes amongst which the S\&P-GSCI, the most popular. Its
constituents at the time of writting, all U.S. traded, form the basis of
the commodity pool we consider in this study where we also include the
cross-section of the most liquid LME traded metals\footnote{See appendix
  1 for details on the commodity pool considered.}. Unleaded gasoline,
the NYMEX legacy contract for gasoline stopped trading in 2006 when it
was replaced by Reformulated Gasoline Blendstock for Oxygen Blending
(RBOB) with the two futures series trading alongside for most of the
year. For our NYMEX gasoline data series, we consider unleaded gasoline
up to Septembre 1\textsuperscript{st}, 2006 and RBOB gasoline
thereafter, date at which liquidity for the latter overtook that for the
former.

The commodity futures trading commission (CFTC) operates a comprehensive
system of collecting information on market participants know as the
large trader reporting program (LTRP) where it records and reports to
the public market position data on market particpants who have position
levels in excess of a particular futures market specific
threshold\footnote{Current reporting level thresholds available at:
  \href{https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=\&SID=970471b8455f4bab7db4110cfde50731\&mc=true\&r=SECTION\&n=se17.1.15_103}{www.ecfr.gov}.}.
The commission collects market data and position information daily from
clearing members, futures commission merchants (FCMs) and foreign
brokers and publishes corresponding summaries weekly in a series of
market specific reports. In these reports, individual traders are
categorised according to the nature of their trading activity on the
basis of self-reported information\footnote{CFTC form 40. Available at:
  \href{https://www.cftc.gov/sites/default/files/idc/groups/public/@forms/documents/file/cftcform40.pdf}{www.cftc.gov}.}
that is subject to review by CFTC staff for reasonableness. Position
information is then aggregated by category and asset type with each
report providing an aggregatetion for a set of report specific
categories and for each category, a breakdown between futures only
positions and positions in futures and options combined.\\
In its legacy report, the commitment of trader report (COT) with data
dating back to 1962, the CFTC distinguishes ``commercial'' and
``non-commercial'' market participants where a ``commercial''
participant is defined as one ``{[}\ldots{}{]} engaged in business
activities hedged by the use of futures and option markets''\footnote{See
  \href{https://www.gpo.gov/fdsys/pkg/CFR-1998-title17-vol1/xml/CFR-1998-title17-vol1-sec1-3.xml}{CFTC
  regulation 1.3, 17 CFR 1.3(z)} for details.}. A third category,
``non-reportable'', aggregates positions for participants not meeting
the reporting threshold. In response to concerns related to category
accuracy\footnote{See for example \citet{ederington_who_2002}.} the CFTC
now refines its classification in the disaggregated commitment of trader
report (DCOT) where participant categories include
``Producer/Merhcant/Processor/User'', ``Swap dealer'', ``Money manager''
and ``Other reportable'' as well as in the supplemental commitment of
trader report (SCOT) that details commodity index trader aggregate
positions for thirteen agricultural commodity futures markets.\\
In this study we consider futures only data over the 1997/2017 period.
Because DCOT and SCOT data series only date back to 2006 and 2007
respectively, we rely exclusively on the legacy COT report for market
position data. Futures market price and open interest data are from
Bloomberg.

\subsection{Methods}\label{methods}

On the one hand, futures markets have a long history of serving
commodity producers to allievate their commodity price and output risks.
\citet{keynes_treatise_1930} and \citet{hicks_value_1939} emphasise the
``normal'' behaviour of naturally short hedgers outsourcing their
commodity risk to naturally long commodity specialist speculators. This
market configuration is referred to as ``backwardation'' where futures
is expected to trade at a discount to spot, providing speculators with
incentives to take the long side. The opposite market paradigm is
referred to as ``contango''. Working
\citep{working_theory_1948, working_hedging_1953} and Cootner
\citep{cootner_returns_1960, CootnerSpeculationhedging1967} somehow
relax this ``supply-of-speculative-services''
\citep{Tilllongtermperspectivecommodity2007} approach by introducing
processors and merchants, also commodity experts, on the hedgers side
and relating the notions of backwardation and contango more directly to
the term structure via the theory of storage where the shape of the
front end of the term structure (basis) is directly related to the
market price of storage.\\
Financialization, on the other hand, refers to the entry of financial
investors into the commodity futures markets who, for the most part, are
not commodity experts. Besides, these new market participants tend to
exhibit herding like behaviour, often taking massive long-only positions
on the whole cross-section of indexed commodities in an attempt hedge
against inflation and/or seek further diversification benefits for
portfolios with, in most cases, existing large positions across various
asset classes
\citep{brunetti_speculators_2016, boyd_prevalence_2016, cheng_convective_2014, juvenal_speculation_2015, singleton_investor_2013, tang_index_2012}.
This contrasts with the traditional approaches of Keynes and Working and
in this context the issues of co-movement and aggregate market
participants behaviour seem particularly relevant.\\
Asset pricing techniques are well suited to study co-movement. Building
on theory we thus develop an ad-hoc commodity based asset pricing
framework that we believe is well adapted to study these two issues
simultaneously and implement it over four periods of interest. The
first, the pre-financialization period, starts in 1997, the earliest
year for which LME metals' price data are available on Bloomberg, and is
naturally followed by financialization, the second, that spans the
2004/2007 period with the starting year based on earlier studies
\citep{baker_financialization_2014, christoffersen_factor_2014}. The
third spans the 2008/2013 period, encompassing both the financial crisis
and the loose monetary policy that followed, while the fourth spans the
period starting for the end of this unorthodox monetary policy regime in
2014 to present.\\
Using the weekly price, open interest and market position data described
above we construct market portfolios of commodity nearby futures as well
as mimicking portfolios for commercial hedging pressure, term structure
and liquidity risk factors in returns. While our market portfolios are
long only, equally weighted portfolios of particular commodity sets, our
other mimicking portfolios for risk factors are constructed as
combinations of two sub-portfolios (legs), one held long, one held
short, which respective constituents are pooled on a weekly basis
according to risk factor specific criterias. The weekly return for a
particular mimicking portfolio is calculated as the difference between
the average return for constituents of the long portfolio and that for
the constituents of the short portfolio. i.e, return on the mimicking
portfolio for risk factor \(i\) (\(f_{i}\)) for week \(t\):

\[r_{t}^{f_{i}}=\frac{1}{x}\sum_{j=1}^{x}r_{j,t}-\frac{1}{x}\sum_{j=n-x}^{n}r_{j,t}\]
\(n\equiv\) number of commodities in the set considered for mimicking
portfolio construction.\\
\(x = \left \lceil n \cdot s \right \rceil\)\\
\(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
\(r_{j,t}=\frac{C_{j,t}}{C_{j,t-1}}-1\)\\
\(C_{j,t}\equiv\) week \(t\) close price for commodity \(j\).\\
\(j\equiv\) commodity rank in the ordered set \(Y_{t}^{f_{i}}\).\\
\(Y_{t}^{f_{i}}\equiv\) week \(t\) ordered set of the commodities
considered for mimicking portfolio construction where the ordering rule
is specific to \(f_{i}\).

For our portfolio CHP (commercial hedging pressure), we sort the set of
commodities considered on past twenty six-week average CHP from lowest
to highest. The bottom third constituents (lowest \(\overline{CHP}\)s)
of the corresponding ordered set form the long leg of the portfolio
while the top third form the short leg:

\[Y_{t}^{CHP}\equiv\left \{ \left \{ \overline{CHP_{1}}, \overline{CHP_{2}}, ..., \overline{CHP_{n}} \right \}, \leq \right \}\]

\(\overline{CHP_{j}}=\frac{1}{26}\sum_{k=0}^{25}\frac{L_{j,t-k}}{L_{j,t-k}+S_{j,t-k}}\)\\
\(L_{j,t}\equiv\) number of long positions held by commercial hedgers
for week \(t\) on the futures series of commodity \(j\).\\
\(S_{j,t}\equiv\) number of short positions held by commercial hedgers
for week \(t\) on the futures series of commodity \(j\).

For our portfolio TS (term structure), we sort the set of commodities
considered on past twenty six-week average roll-yield from highest to
lowest. The bottom third constituents (highest \(\overline{RY}\)s) of
the corresponding ordered set form the long leg of the portfolio while
the top third form tje short leg:

\[Y_{t}^{TS}\equiv\left \{ \left \{ \overline{RY_{1}}, \overline{RY_{2}}, ..., \overline{RY_{n}} \right \}, \geq \right \}\]

\(\overline{RY_{j}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{F_{j,t-k}^{1}}{F_{j,t-k}^{2}} - 1)\)\\
\(F_{j,t}^{1}\equiv\) week \(t\) close price for commodity \(j\) first
nearby futures contract.\\
\(F_{j,t}^{2}\equiv\) week \(t\) close price for commodity \(j\) second
nearby futures contract.

For our portfolio OI (open interest), we sort the set of commodities
considered on past twenty six-week average aggregate open interest
growth from highest to lowest. The bottom third constituents (highest
\(\overline{\mathbf{OI}^{\Delta \%}}\)s) of the corresponding ordered
set form the long leg of the portfolio while the top third form the
short leg.

\[Y_{t}^{OI}\equiv\left \{ \left \{ \overline{\mathbf{OI}_{1}^{\Delta \%}}, \overline{\mathbf{OI}_{2}^{\Delta \%}}, ..., \overline{\mathbf{OI}_{n}^{\Delta \%}} \right \}, \geq \right \}\]

\(\overline{\mathbf{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{\mathbf{OI}_{j,t-k}}{\mathbf{OI}_{j,t-k-1}} - 1)\)\\
\(\mathbf{OI}_{j,t}=\sum_{k=1}^{l_{j,t}}OI_{j,t,k}\)\\
\(OI_{j,t,k}\equiv\) open interest at close of week \(t\) for the
\(k^{th}\) nearby contract on the futures term structure for commodity
\(j\).\\
\(l_{j,t}\equiv\) length of commodity \(j\)'s futures term structure on
week \(t\) close.

We use a time series regression approach where we start with regressions
of the U.S. traded individual commodity weekly front returns on returns
to the mimicking portfolio for a particular risk factor where the
portfolio is constructed using the whole cross-section of U.S. traded
commodities. The corresponding adjusted \(R^{2}\)s are averaged and the
process is repeated for each of our four risk factors (market, hedging
pressure, term structure and liquidity) and periods (1997/2003,
2004/2007, 2008/2013 and 2014/2017). i.e, average adjusted \(R^{2}\) for
risk factor \(i\) (\(f_{i}\)) over period \(t\):

\[\overline{\tilde{R}_{f_{i},t}^{2}}=\frac{1}{24}\sum_{j=1}^{24}\tilde{R}_{j,t}^{2}\]
\(\tilde{R_{j}^{2}}=1-(1-R_{j}^{2})\frac{T-1}{T-p-1}\)\footnote{The
  Wherry formula-1.}\\
\(T\equiv\) length of period \(t\) (number of weeks here).\\
\(p\equiv\) number of regressors (1 here).\\
\(R_{j,t}^{2}=1-\frac{\sum_{k=1}^{T}(y_{j,k}-\hat{y_{j,k}})^{2}}{\sum_{k=1}^{T}(y_{j,k}-\overline{y_{j}})^{2}}\)\\
\(y_{j,t}\equiv\) week \(t\) nearby return for commodity \(j\).\\
\(\hat{y_{j,t}}=\beta_{0}+\beta_{1}f_{i,t}+\epsilon\)\\
\(\beta s \equiv\) classic OLS coefficient estimates.\\
\(f_{i,t}\equiv\) week \(t\) return on mimicking portfolio for risk
factor \(f_{i}\)

The same operation is repeated for the two (\(p=2\)) and three (\(p=3\))
factor model cases, where regressors include in turn all combinations of
any two and three risk factors respectivly, as well as for the four
(\(p=4\)) factor model case where all the risk factor mimicking
portfolios are included. Results are reported for the one-factor model
case with the other results available from the authors upon request.\\
For each period we also implement the analysis described above over
periods of low and high aggregate CHP (\(\mathbf{CHP}\)), a notion that
we introduce in this study and that we believe is particularly relevant
in the context of financialization where issues of co-movement and
aggregate market participants' behaviour play a central role. We define
\(\mathbf{CHP}\) as the cross-sectional average of CHPs for a particular
pool of asset. i.e, Week \(t\) \(\mathbf{CHP}\) for asset pool \(x\):

\[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{i=1}^{n}CHP_{i,t}\] \(n\equiv\)
number of commodities in set \(x\).\\
\(CHP_{i,t}\equiv\) week \(t\) CHP for commodity \(i\) as defined above.

We further define aggregate backwardation (\(\mathbf{backwardation}\))
and contango (\(\mathbf{contango}\)) \(\mathbf{CHP}\) regimes as, for a
given period, \(\mathbf{CHP}\) levels below and above the period's
median respectively.\\
For the rest of the study, the asset pool used for \(\mathbf{CHP}\)
construction include the whole cross-section of U.S. traded commodities.

In the next part of the analysis, our mimicking portfolios for risk
factors, constructed from the set of all U.S. traded commodities are
used as commodity picking devices on the latter commodity set. For each
risk factor and period, individual U.S. traded commodity front returns
are regressed on returns for the corresponding mimicking portfolio.
Individual commodities are sorted by adjusted \(R^{2}\)
(\(\tilde{R^{2}}\)) accordingly from highest to lowest and the bottom
third (highest \(\tilde{R^{2}}\)s) are selected as commodity picks for
the risk factor for the period. i.e, set of picks \(P_{t}^{f_{i}}\) for
risk factor \(i\) (\(f_{i}\)) over period \(t\):

\[P_{t}^{f_{i}}\equiv\left \{ P_{1}, P_{2}, ..., P_{x} \right \}\]
\(x = \left \lceil n \cdot s \right \rceil\)\\
\(n\equiv\) number of commodities in the set considered for the picking
excersise (24 here).\\
\(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
\(P_{j}\equiv\) commodity pick \(j\) for risk factor \(f_{i}\) over
period \(t\)\\
\(j\equiv\) rank in the ordered set \(Y_{t}^{f_{i}}\)\\
\[Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}\]
\(n\equiv\) number of commodities in the set considered for picking (24
here).\\
\(\tilde{R_{j}^{2}}\equiv\) risk factor \(f_{i}\) returns' explanatory
power on commodity \(j\) nearby returns over period \(t\) as defined
above.

For each period and \(\mathbf{CHP}\) regime we record the proportion of
time each pick is held in the long and (/or) short leg of the
corresponding risk factor mimicking portfolio as well as the average
pairwise correlation amongst every sets of picks.

In the last part of the analysis, for each period our mimicking
portfolios for risk factors in returns are constructed using each set of
commodity picks independently as the asset pool for portfolio
construction. A similar time series approach to that described above is
then implemented using these newly formed mimicking portfolios. In this
case, a first set of dependent variables includes the sets of commodity
picks themselves, a second set includes the whole cross-section of U.S.
traded commodities while a third set includes the six LME traded metals
considered. The latter are also used as dependent variables in the last
series of regressions where the long and short legs of the newly formed
risk factor mimicking portfolios described above are considered
separately as regressor.

\section{Results \& discussion}\label{results-discussion}

The descriptive statistics over the various time periods for our two
sets of commodities (U.S. and non U.S.) as well as the four factors
considered are shown in Table 1. The traditional Keynesian hedging
pressure paradigm postulates a negative relationship between the return
on an individual commodity and its hedging pressure. Financialization
has been seen as an exogenous cross-sectional commodity market
phenomenon. This naturally leads us to extend the individual hedging
pressure paradigm by incorporating aggregate CHP (\(\mathbf{CHP}\)), a
market wide measure of hedging pressure. The extended Keynesian hedging
pressure paradigm should also imply that returns for individual
commodities should be high in periods where \(\mathbf{CHP}\) is low and
vice et versa.\\
In table 2 the mean returns are shown over high (\(\mathbf{contango}\))
and low (\(\mathbf{backwardation}\)) \(\mathbf{CHP}\) regimes for each
time period. Over the first period 18 of the 24 US commodities have
higher mean returns during periods of \(\mathbf{backwardation}\) as
compared to \(\mathbf{contango}\), with the difference being
statistically significant at the 5\% level for one commodity and for the
remaining 6 commodities the higher mean return during
\(\mathbf{contango}\) is not statistically significant for any of them.
For the 6 UK commodities, all metals, 4 of them had higher mean returns
during phases of \(\mathbf{backwardation}\) as compared to
\(\mathbf{contango}\) in the first period, with one of these differences
being statistically significant at the 5\% level while for the remaining
two the higher mean return during \(\mathbf{contango}\) is not
statistically significant for either. An equally weighted portfolio of
the 24 US commodities had a mean return of 10.98\% during
\(\mathbf{backwardation}\) phases, statistically significant at the 1\%
level, and a mean return of 0.93\% during \(\mathbf{contango}\), both in
the first period, with the difference between them statistically
significant at the 5\% level. The corresponding figures for an equally
weighted portfolio of the UK metals were 8.35\% and -1.71\%, the
difference again statistically significant at the 5\% level. These
results provide broad support for an aggregate version of the Keynesian
hedging pressure hypothesis and suggests that hedgers in the aggregate
were engaged in risk transfer.\\
Over the second period the pattern essentially reverses. For the 24 US
commodities over this period, 18 have higher mean returns during phases
of \(\mathbf{backwardation}\) over \(\mathbf{contango}\), with the
difference statistically significant for 4 commodities and of the
remaining 7 the higher mean return during \(\mathbf{backwardation}\) is
statistically significant for one commodity. All of the 6 UK metals
achieved higher mean returns over \(\mathbf{backwardation}\) than
contango with the difference being statistically significant for one
commodity. The equally weighted US portfolio had a mean return of
11.16\% over \(\mathbf{backwardation}\) while it was 26.68\% during
\(\mathbf{contango}\), the first statistically significant at the 5\%
level and the second at the 1\% level, with the difference statistically
significant at the 1\% level. The difference was considerably more
pronounced for the equally weighted UK metals portfolio with a mean
return of 6.43\% during \(\mathbf{backwardation}\) rising to 41.22\%
during \(\mathbf{contango}\), with the difference also significant at
the 1\% level.\\
Thus the onset of financialization seems to have engendered a change in
the nature of hedger's behaviour in the aggregate, taking it away from
risk shifting, the traditional Keynesian view. This phenomenon has been
noted in earlier theoretical and empirical work
\citep[\citet{stout_why_1998}]{DanthineInformationfuturesprices1978} in
different context from which two competing models of behaviour have
emerged. The information arbitrage model implies that hedgers may often
be seeking out counterparties to trade with rather than being purely
passive. This issue is also raised in both
\citet{cheng_financialization_2014} and
\citet{StulzRethinkingriskmanagement1996} who point out that hedgers may
be taking a view on prices just as speculators do. In fact, by hedging
away some of their risk, hedgers are able to speculate more heavily
based on their disagreement against speculators regarding futures price
movement \citep{SimsekSpeculationrisksharing2013}, which fits into a
heterogenous expectation theory of speculation. As
\citet{stout_why_1998} points out, this disagreement-based theory of
trading is one of the main reason the public and the law disapproves the
speculators as this form of trading is regarded as
non-productive\footnote{\citet{DuffieChallengespolicytreatment2014} also
  discusses some of the challenges faced by a policy treatment of
  speculative trading motivated by differences in beliefs.}. In the
second model hedgers are seen as liquidity providers as in
\citet{Kangtaletwopremiums2017}. This explanation is also consistent
with the nature of financialization which led to the arrival of long
term, long only investors who require substantial liquidity to roll-over
their positions.

The average time series pricing performance of the various one factor
models on the U.S. traded assets over the four periods is shown in Table
3. Over the first period the market factor has the best average time
series performance with the highest average adjusted
R\textsuperscript{2} with all three futures market factors performing
poorly and the overall pricing performance consistent across periods of
high and low \(\mathbf{CHP}\) (below period median). The two factor
models average R\textsuperscript{2}s (results available upon request)
are roughly the sum of the one factor R\textsuperscript{2}s indicating
that the factors are almost orthogonal over this period. The onset of
financialization leads to a substantial improvement in the performance
of the CHP factor with its average R\textsuperscript{2} increasing to
5.4\% in the second period relative to 1.4\% in the first. The
performance of the market factor also improves though not by as much in
a relative sense (18.6\% from 12.2\%). Both the term structure factor
and the open interest growth factor show a much smaller improvement in
pricing performance. Over all periods, all of our factor models show
similar pricing performance across regimes of high and low
\(\mathbf{CHP}\).

We next investigate the top eight of the U.S. traded commodities which
achieved the highest time series R\textsuperscript{2} for the CHP,
market, open interest and term structure factors, in each of the four
time periods with the commodity picks shown in Table 4. For the CHP
factor the commodities that achieve high R\textsuperscript{2} in a given
period are likely to be those with relatively high or low CHP over that
period, or those commodities that co-vary with the short or the long
side of the factor. The same applies to the open interest and term
structure factors with CHP replaced by open interest growth and roll
yield respectively; while for the market factor the picks are those that
co-vary most strongly with the market factor over that period. For the
CHP factor, we observe a change in the picks between the first and the
second period; the picks in the first period included five agricultural
commodities and three metals while in the second period include all of
the five industrial and precious metals and only three agricultural
commodities. This pattern is also visible for the term structure factor
for which there are four metals (gold, copper, palladium and platinum)
picks in the second period against three in the first (gold, palladium
and platinum). The market factor has two metal picks in the second
period (palladium and silver) while all of the picks in the first period
were agricultural or energy commodities. Over the third period, the
average CHP factor has four metal picks while both the term structure
factor and market factor have three. Table 4 also shows the proportion
of time that these picks were constituents of the corresponding factor.
All of the picks of the long-short factors (average CHP, open interest
growth and term structure factors) were constituents of the
corresponding factor for some proportion of time in all of the time
periods. In this respect, there is a contrast between the first and
second periods for the average CHP with the picks appearing
predominantly on the long side in the second period, as opposed to both
legs in the first. This indicates that the picks in the second period
consistently exhibited low CHP. This behaviour continued over the third
period.

In table 5, we show the average pair wise correlation between each set
of picks in each time period. This exercise gives an indication of the
extent to which attribute co-movement reveals price co-movement, which
is particularly relevant for the long-short factors for which the
corresponding attribute is not directly related to price co-movement. In
the first period, the average CHP picks pairwise correlation is similar
to the average across the U.S. traded 24 commodities. In the second
period however it is the highest, comparable with the market and double
of the U.S. traded commodities average. This increase is a consequence
of the dramatic increase in average pairwise price correlation amongst
the U.S. traded metals, all of which are CHP factor picks. Taken
together with the fact that four of these metals had consistently low
CHP, we see that CHP co-movement in the second period is strongly
correlated with price co-movement. It is also interesting to note that
U.S. traded metals returns were negatively correlated with the rest of
U.S. traded commodities in the first period and positively in the second
(Results available upon request).

In order further understand the link between attribute and price
co-movement we build all of the factors from every set of factor picks
and assess their pricing performance on these sets of picks. The results
are shown in table 6. The long-short factors for a particular attribute
select the top and bottom three of the corresponding picks based on that
attribute while the market factor takes an equally weighted combination
of the eight corresponding picks. In the absence of price co-movement
between the picks, this market factor will achieve an average
R\textsuperscript{2} of around 12.5\%\footnote{Market factor lemma:
  \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\)
  size of market portfolio (8 here). See appendix 2 for a formal proof.},
while there is no non-zero R\textsuperscript{2} lower bound for the
corresponding long-short factors. A high average R\textsuperscript{2}
for the market factor is indicative of strong price co-movement while
for the long-short factors it is indicative of a simultaneous attribute
and price co-movement. The most dramatic change in pricing performance
occurs for the average CHP factor picks where the market factor built
from these picks has an average R\textsuperscript{2} of 21.3 \% in the
first period (close to the 0 correlation situation) and jumps to 37.4 \%
in the second period. The average CHP factor built with average CHP
factor picks also shows a sharp increase in pricing performance over the
second period. The most striking result is the dramatic improvement in
pricing performance of the CHP factor built with term structure picks
(3.4\% vs.~21.2\%)\footnote{In contrast to the market factor, there is
  no pricing performance lower bound for the CHP factor built with a set
  of picks.}, providing evidence of convergence of Keynesian and
Working's theories of the term structure in detecting price co-movement
during financialization. In table 7 we assess the performance of the
same factors on all the commodities instead of just the picks. While the
average R\textsuperscript{2}s are expectedly lower, the relative
performance of the market factors built with different sets of picks is
similar to table 6. In contrast, the increase in R\textsuperscript{2}
for the average CHP factor built with average CHP factor picks is lower
indicating that the link between CHP co-movement and price co-movement
is strongest amongst the picks which are predominantly metals.\\
The conclusion from Tables 6 and 7 is that the onset of financialization
seems to have had a major impact on the dynamics of U.S. traded precious
and precious industrial metals and we now seek to analyse whether this
phenomenon is true for the non US metal futures. To that end we examine
the pricing performance of the factors constructed used in Table 6 on
the six LME metals futures. The results are reported in Table 8. In the
first period, the average R\textsuperscript{2} s across the board are
always less than 4.5\%. In the second period we see a dramatic increase
in R\textsuperscript{2} for the market factor built with average CHP
factor picks and average term structure factor picks (4.48\% to 25.1\%
and 1.3\% to 20.6\% respectively) showing dramatically higher
co-movement between LME traded metals and the corresponding picks all of
which are U.S. traded commodities. The increase in R\textsuperscript{2}
for the market factor built with market factor picks is much more
modest, providing further evidence of concentration of co-movement in
the metal sector during financialization.

In order to understand this better, in table 9, we examine the pricing
performance of both long and short legs of the corresponding factors
separately on the same set of LME traded metals. The most striking
result here is the dramatic increase in R\textsuperscript{2} for the
long leg of the term structure factor built with CHP factor picks which
achieves the highest overall R\textsuperscript{2} in the second period
(1.91\% vs.~27.37\%). This provides further evidence that global metals
co-movement could be detected by US based factor models that combined
the Keynesian and Working's notions of backwardation.

We then turn our analysis to the crisis and post-crisis period
(2008-2013). In table 1 we see that the returns on both U.S. and
non-U.S. commodities fall dramatically over this period, going down to
-4.3\% for the LME metals and 8\% for the US traded commodities although
volatility for both sets of assets is similar to that during the second
period. Two of the LME metals have negative mean returns over the third
period compared to one over the first and none over the second. This
trend continues in from 2014 to 2017 with the US traded commodities
recording an average mean return of -0.6\% and the LME metals an average
of 4.9\% over this period, with fourteen US traded commodities and one
LME metals having negative mean returns. The volatility of both sets of
assets is lower than over the 2004-2007 period, particularly for the UK
metals, suggesting the impact of the investment outflows from the
commodity futures markets has had a much lower impact on volatility than
the corresponding inflows witnessed over the financialization period.
The market factor dominates pricing performance over this period with an
increase of mean average R\textsuperscript{2} of over 50\% while that
for the other factors increases slightly at best (table 3). From table 5
we see that there is an across the board increase in pairwise
correlations with a doubling in the average pairwise correlation of all
U.S. traded commodities and a levelling in the pairwise correlation of
the picks of the three long-short factors. Taken together, these results
indicate the presence of a systematic factor across the entire
cross-section of the U.S. commodities. This is clearly evident in the
performance of the market factor built with any set of picks on the
entire set of U.S. traded commodities (table 7) as we see a dramatic
rise across the board in pricing performance. Table 8 provides further
evidence of systematic linkages, in this case between U.S. and
non-U.S.traded commodities as the market factor built with its own picks
(U.S. traded commodities) achieves an average R\textsuperscript{2} of
33.7\% on the LME metals compared to 9.9\% in the previous period.

\section{Conclusion}\label{conclusion}

In the early 2000s, against a backdrop of a low yield environment and
poor stock market performance, a combination of financial
innovation\footnote{Tradable commodity price indexes (commonly referred
  to as commodity index funds or CIFs), and commodity-based exchange
  traded funds (ETFs) were the main financial innovations which allowed
  the large global banks to offer commodity investment products to
  institutional and retail investors. In 1991 Goldman Sachs created the
  S\&P-GSCI which provides investors with buy-side exposure to
  commodities via the OTC swap market and thus without having to
  participate in the formal futures markets with their position limit
  restrictions. At this stage these restrictions still applied to the
  bank though, as it hedged its commodity swap exposure in the futures
  markets. The first commodity-based ETFs were created through buying
  physical precious metals with gold and silver ETFs offered as early as
  2002/2003. The regulatory hurdle here related to the licensing of
  commodity trading professionals. Typically, investors had to sign a
  statement with their broker stating that they understood the risks of
  commodity investments; a rather inconvenient paperwork for a product
  designed to trade like a stock, as set forth by a number of industry
  players at the time.} and deregulation\footnote{In 2000, the Commodity
  Futures Modernization Act (CFMA) granted non-agricultural commodity
  futures statutory exemption from regulation (``Enron loophole'') while
  it required that agricultural commodity derivatives be traded on a
  CFTC-regulated exchange. Notwithstanding, the CFTC classified swap
  dealers as ``bona fide'' hedgers, granting them position limits
  exemption (``swap dealer loophole'').\\
  In 2005, the CFTC waived the rule that required commodity investors to
  sign a statement saying they understood the risks, letting the funds
  replace it with their prospectus and thus unleashed commodity-based
  ETFs investments.} led to a large inflow of institutional and
financial capital into the commodity futures markets. This process known
as financialization lead to a heated public policy debate about whether
the increase in open interest and trading volume in commodities exerted
upward pressure on prices. Perhaps in response to this, most of the
early studies focused on the more mechanical effects of
financialization, relying on commodity specific causality and
correlation based analysis. With the benefit of hindsight this focus
appears to have been too narrow and it seems important to analyze the
effects of financialization from a broader perspective which we do in
this study. We consider the entire cross-section of actively traded
commodities on futures markets and use a futures based asset pricing
framework that includes factors constructed using both price and
non-price attributes. Factor model techniques are well suited to
isolating common driving factors and detecting co-movement, a central
issue in financialization which we believe the existing literature has
not fully analyzed. Our analysis suggests that financialization was a
phenomenon endogenous to the commodity markets transmitted via the
futures markets and appears to have had the deepest impact on global
metal futures markets. The onset of the financial crisis and the
monetary policy regimes that followed appear to have also induced
significant changes in commodity pricing dynamics and our analysis
suggest that in contrast with financialization, the crisis and its
aftermath have delivered an exogenous shock across the entire
cross-section of global commodities.

\newpage
\begingroup\fontsize{8}{10}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\caption{\label{tab:mean_returns_no_CHP}This table shows descriptive statistics for nearby returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the U.S. traded commodities considered in the study. Figures labelled $***$ ($**$, $*$) are significant at the 1\% (5\%, 10\%) level. See section 2 for more details.}\\
\toprule
Asset pool & Variable & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
US-Agriculturals-Grains & Mean return & 3.75\% & ***18.99\% & 5.34\% & -4.14\%\\
US-Agriculturals-Grains & Volatility & 27.14\% & 29.17\% & 33.52\% & 25.18\%\\
US-Agriculturals-Livestock & Mean return & 3.81\% & 5.84\% & *9.53\% & 0.16\%\\
US-Agriculturals-Livestock & Volatility & 26.53\% & 21.59\% & 23.94\% & 26.55\%\\
US-Agriculturals-Softs & Mean return & 1.57\% & **14.26\% & 9.53\% & 2.97\%\\
\addlinespace
US-Agriculturals-Softs & Volatility & 33.47\% & 30.19\% & 35.53\% & 28.08\%\\
US-Metals-Industrial & Mean return & 2.42\% & **33.08\% & 6.74\% & 1.35\%\\
US-Metals-Industrial & Volatility & 20.2\% & 30.44\% & 31.66\% & 19.95\%\\
US-Metals-Precious & Mean return & *9.39\% & ***22.7\% & 9.99\% & 2.13\%\\
US-Metals-Precious & Volatility & 26.2\% & 25.61\% & 31.76\% & 21.57\%\\
\addlinespace
US-Agriculturals & Mean return & 2.89\% & ***14.45\% & **7.86\% & -0.44\%\\
US-Agriculturals & Volatility & 29.72\% & 28.24\% & 32.69\% & 26.64\%\\
US-Energy & Mean return & 13.56\% & ***28.33\% & 6.94\% & -4.13\%\\
US-Energy & Volatility & 44.03\% & 42.77\% & 39.5\% & 36.52\%\\
US-Metals & Mean return & *7.99\% & ***24.77\% & 9.34\% & 1.98\%\\
\addlinespace
US-Metals & Volatility & 25.12\% & 26.64\% & 31.73\% & 21.24\%\\
US-Commodity & Mean return & **5.73\% & ***18.9\% & ***8.01\% & -0.55\%\\
US-Commodity & Volatility & 31.73\% & 30.84\% & 33.72\% & 27.56\%\\
UK-Commodity & Mean return & 2.95\% & ***23.91\% & 4.25\% & 4.87\%\\
UK-Commodity & Volatility & 20.33\% & 33.43\% & 35.99\% & 22.33\%\\
\bottomrule
\end{longtabu}\endgroup{}

\newpage
\begingroup\fontsize{8}{10}\selectfont

\begin{landscape}
\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\caption{\label{tab:mean_returns_aggregate_CHP}This table shows descriptive statistics for nearby returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the U.S. traded commodities considered in the study. For each period the results are shown for periods of high (contango) and low (backwardation) aggregate CHP regimes. Figures labelled $***$ ($**$, $*$) are significant at the 1\% (5\%, 10\%) level. See section 2 for more details.}\\
\toprule
Assets & CHP regime & Variable & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
\endfirsthead
\caption[]{continued}\\
\toprule
Assets & CHP regime & Variable & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
US-Agriculturals-Grains & High & Mean return & 4.25\% & ***29.78\% & -2.92\% & -0.55\%\\
US-Agriculturals-Grains & High & Volatility & 27.61\% & 30.17\% & 36.06\% & 24.93\%\\
US-Agriculturals-Grains & Low & Mean return & 3.24\% & 8.26\% & *13.66\% & -7.76\%\\
US-Agriculturals-Grains & Low & Volatility & 26.67\% & 28.09\% & 30.73\% & 25.43\%\\
US-Agriculturals-Livestock & High & Mean return & -2.15\% & -1.68\% & 4.05\% & -15.8\%\\
\addlinespace
US-Agriculturals-Livestock & High & Volatility & 29.3\% & 20.65\% & 23.59\% & 25.46\%\\
US-Agriculturals-Livestock & Low & Mean return & 9.84\% & 13.43\% & *15.04\% & 16.28\%\\
US-Agriculturals-Livestock & Low & Volatility & 23.38\% & 22.47\% & 24.29\% & 27.48\%\\
US-Agriculturals-Softs & High & Mean return & -1.31\% & ***24.85\% & 11.43\% & -3.34\%\\
US-Agriculturals-Softs & High & Volatility & 32.54\% & 30.48\% & 36.06\% & 28.72\%\\
\addlinespace
US-Agriculturals-Softs & Low & Mean return & 4.47\% & 3.67\% & 7.62\% & 9.33\%\\
US-Agriculturals-Softs & Low & Volatility & 34.4\% & 29.84\% & 35\% & 27.42\%\\
US-Metals-Industrial & High & Mean return & -0.45\% & **51.48\% & 1.3\% & -13.36\%\\
US-Metals-Industrial & High & Volatility & 20.55\% & 31.58\% & 36.97\% & 18.91\%\\
US-Metals-Industrial & Low & Mean return & 5.3\% & 14.86\% & 12.22\% & 16.2\%\\
\addlinespace
US-Metals-Industrial & Low & Volatility & 19.89\% & 29.2\% & 25.31\% & 20.85\%\\
US-Metals-Precious & High & Mean return & -3.38\% & ***37.17\% & -2.16\% & -3.58\%\\
US-Metals-Precious & High & Volatility & 28.72\% & 23.7\% & 32.66\% & 22.64\%\\
US-Metals-Precious & Low & Mean return & ***22.26\% & 8.36\% & **22.23\% & 7.9\%\\
US-Metals-Precious & Low & Volatility & 23.28\% & 27.26\% & 30.77\% & 20.42\%\\
\addlinespace
US-Agriculturals & High & Mean return & 0.74\% & ***21.45\% & 4.21\% & -4.72\%\\
US-Agriculturals & High & Volatility & 30\% & 28.67\% & 33.93\% & 26.61\%\\
US-Agriculturals & Low & Mean return & 5.06\% & 7.46\% & **11.52\% & 3.88\%\\
US-Agriculturals & Low & Volatility & 29.44\% & 27.79\% & 31.39\% & 26.67\%\\
US-Energy & High & Mean return & 3.9\% & *29.75\% & -3.1\% & -23.15\%\\
\addlinespace
US-Energy & High & Volatility & 43.76\% & 45.83\% & 45.46\% & 40.32\%\\
US-Energy & Low & Mean return & *23.3\% & *26.93\% & *17.04\% & 15.07\%\\
US-Energy & Low & Volatility & 44.3\% & 39.55\% & 32.39\% & 32.06\%\\
US-Metals & High & Mean return & -2.79\% & ***40.04\% & -1.47\% & -5.54\%\\
US-Metals & High & Volatility & 27.27\% & 25.45\% & 33.54\% & 21.93\%\\
\addlinespace
US-Metals & Low & Mean return & ***18.86\% & 9.66\% & ***20.22\% & 9.56\%\\
US-Metals & Low & Volatility & 22.65\% & 27.63\% & 29.75\% & 20.49\%\\
US-Commodity & High & Mean return & 0.53\% & ***26.68\% & 1.81\% & *-7.96\%\\
US-Commodity & High & Volatility & 32.19\% & 31.59\% & 36.02\% & 28.52\%\\
US-Commodity & Low & Mean return & ***10.98\% & **11.16\% & ***14.25\% & *6.93\%\\
\addlinespace
US-Commodity & Low & Volatility & 31.25\% & 30.04\% & 31.22\% & 26.52\%\\
UK-Commodity & High & Mean return & -1.71\% & ***41.22\% & -1.32\% & **-13.66\%\\
UK-Commodity & High & Volatility & 21.05\% & 33.54\% & 38.82\% & 21.69\%\\
UK-Commodity & Low & Mean return & *8.35\% & 6.43\% & 10.04\% & ***23.4\%\\
UK-Commodity & Low & Volatility & 19.45\% & 33.17\% & 32.8\% & 22.69\%\\
\addlinespace
CHP factor & High & Mean return & 1.45\% & 7.88\% & 0.89\% & -3.48\%\\
CHP factor & High & Volatility & 8.08\% & 8.28\% & 9.81\% & 7.11\%\\
CHP factor & Low & Mean return & -0.98\% & -5.63\% & -1.2\% & -0.47\%\\
CHP factor & Low & Volatility & 7.43\% & 7.75\% & 7.97\% & 7.81\%\\
Market factor & High & Mean return & 0.67\% & ***26.46\% & 1.81\% & -7.96\%\\
\addlinespace
Market factor & High & Volatility & 10.27\% & 11.96\% & 18.97\% & 11.24\%\\
Market factor & Low & Mean return & **11.43\% & 11.16\% & 14.25\% & 6.93\%\\
Market factor & Low & Volatility & 10.1\% & 12.78\% & 15.37\% & 9.19\%\\
OI factor & High & Mean return & -0.76\% & 4.89\% & -6.9\% & 3.84\%\\
OI factor & High & Volatility & 7.92\% & 8.79\% & 8.64\% & 6.7\%\\
\addlinespace
OI factor & Low & Mean return & 0.46\% & 0.72\% & -1.65\% & 0.7\%\\
OI factor & Low & Volatility & 8.66\% & 7.52\% & 7.53\% & 6.7\%\\
TS factor & High & Mean return & **-13.59\% & -7.38\% & -8.14\% & *-11.23\%\\
TS factor & High & Volatility & 10.38\% & 8.71\% & 10.76\% & 8.39\%\\
TS factor & Low & Mean return & -4.6\% & -6.92\% & -3.37\% & -6.79\%\\
TS factor & Low & Volatility & 10.08\% & 7.94\% & 9\% & 8.69\%\\*
\end{longtabu}
\end{landscape}\endgroup{}

\newpage
\begingroup\fontsize{8}{10}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\caption{\label{tab:fact_regs}This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models. The dependent variables are individual nearby returns on the commodities forming the entire cross-section of U.S. traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using whole set of U.S. traded commodities considered. For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged. For each period, the models are implemented over the whole period, as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes independently. See section 2 for more details.}\\
\toprule
Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
US commodities & \textasciitilde{} CHP factor & High & 1.54\% & 5.5\% & 5.89\% & 3.73\%\\
US commodities & \textasciitilde{} CHP factor & Low & 1.39\% & 5.64\% & 7.33\% & 5.43\%\\
US commodities & \textasciitilde{} CHP factor & None & 1.37\% & 5.43\% & 5.99\% & 4.47\%\\
US commodities & \textasciitilde{} Market factor & High & 13.04\% & 16.96\% & 30.45\% & 17.62\%\\
US commodities & \textasciitilde{} Market factor & Low & 11.61\% & 19.83\% & 28.92\% & 13.53\%\\
\addlinespace
US commodities & \textasciitilde{} Market factor & None & 12.2\% & 18.55\% & 29.45\% & 15.57\%\\
US commodities & \textasciitilde{} OI factor & High & 0.82\% & 1.32\% & 1.19\% & 0.31\%\\
US commodities & \textasciitilde{} OI factor & Low & 1.42\% & -0.39\% & 0.54\% & 0.56\%\\
US commodities & \textasciitilde{} OI factor & None & 0.66\% & 0.36\% & 0.31\% & 0.31\%\\
US commodities & \textasciitilde{} TS factor & High & 2.12\% & 3.36\% & 4.68\% & 2.69\%\\
\addlinespace
US commodities & \textasciitilde{} TS factor & Low & 2.88\% & 2.72\% & 5.57\% & 3.09\%\\
US commodities & \textasciitilde{} TS factor & None & 2.4\% & 2.7\% & 4.69\% & 2.52\%\\
\bottomrule
\end{longtabu}\endgroup{}

\newpage
\begingroup\fontsize{8}{10}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
\caption{\label{tab:factor_picks}For each risk factor and period, this table displays the list of corresponding commodity factor picks along with the proportion of time they are individually held on the long and short legs of the corresponding risk factor mimicking portfolio. The factor portfolios are constructed from the whole set of the twenty four U.S. traded commodities considered which is also used as asset pool for the commodity picking exercise. See section 2 for more details.}\\
\toprule
Factor & Period & Asset & Long & Short\\
\midrule
\endfirsthead
\caption[]{continued}\\
\toprule
Factor & Period & Asset & Long & Short\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
CHP & 1997/2003 & XCBT - Oats & 97\% & 0\%\\
CHP & 1997/2003 & XCBT - Soybean oil & 42\% & 32\%\\
CHP & 1997/2003 & XCBT - Wheat-SR & 29\% & 9\%\\
CHP & 1997/2003 & XNYM - Copper & 43\% & 18\%\\
CHP & 1997/2003 & XNYM - Platinum & 91\% & 4\%\\
\addlinespace
CHP & 1997/2003 & XNYM - Silver & 100\% & 0\%\\
CHP & 1997/2003 & IFUS - Coffee & 22\% & 17\%\\
CHP & 1997/2003 & IFUS - Orange juice & 67\% & 18\%\\
Market & 1997/2003 & XCBT - Corn & 100\% & 0\%\\
Market & 1997/2003 & XCBT - Oats & 100\% & 0\%\\
\addlinespace
Market & 1997/2003 & XCBT - Soybean meal & 100\% & 0\%\\
Market & 1997/2003 & XCBT - Wheat-SR & 100\% & 0\%\\
Market & 1997/2003 & XNYM - Crude oil & 100\% & 0\%\\
Market & 1997/2003 & XNYM - Gasoline & 100\% & 0\%\\
Market & 1997/2003 & XNYM - Heating oil & 100\% & 0\%\\
\addlinespace
Market & 1997/2003 & XNYM - Natural gas & 99\% & 0\%\\
OI & 1997/2003 & XCME - Feeder cattle & 27\% & 39\%\\
OI & 1997/2003 & XCME - Lean hogs & 36\% & 30\%\\
OI & 1997/2003 & XNYM - Crude oil & 24\% & 28\%\\
OI & 1997/2003 & XNYM - Natural gas & 46\% & 24\%\\
\addlinespace
OI & 1997/2003 & XNYM - Gold & 39\% & 28\%\\
OI & 1997/2003 & XNYM - Palladium & 46\% & 33\%\\
OI & 1997/2003 & IFUS - Coffee & 39\% & 23\%\\
OI & 1997/2003 & XCME - Lumber & 42\% & 33\%\\
TS & 1997/2003 & XCBT - Soybean meal & 71\% & 0\%\\
\addlinespace
TS & 1997/2003 & XNYM - Crude oil & 53\% & 9\%\\
TS & 1997/2003 & XNYM - Gasoline & 61\% & 17\%\\
TS & 1997/2003 & XNYM - Heating oil & 35\% & 24\%\\
TS & 1997/2003 & XNYM - Gold & 10\% & 1\%\\
TS & 1997/2003 & XNYM - Palladium & 61\% & 0\%\\
\addlinespace
TS & 1997/2003 & XNYM - Platinum & 96\% & 0\%\\
TS & 1997/2003 & IFUS - Sugar & 60\% & 26\%\\
CHP & 2004/2007 & XCBT - Oats & 100\% & 0\%\\
CHP & 2004/2007 & XNYM - Copper & 44\% & 37\%\\
CHP & 2004/2007 & XNYM - Gold & 100\% & 0\%\\
\addlinespace
CHP & 2004/2007 & XNYM - Palladium & 100\% & 0\%\\
CHP & 2004/2007 & XNYM - Platinum & 100\% & 0\%\\
CHP & 2004/2007 & XNYM - Silver & 100\% & 0\%\\
CHP & 2004/2007 & IFUS - Coffee & 15\% & 5\%\\
CHP & 2004/2007 & IFUS - Orange juice & 66\% & 15\%\\
\addlinespace
Market & 2004/2007 & XCBT - Corn & 100\% & 0\%\\
Market & 2004/2007 & XCBT - Soybeans & 100\% & 0\%\\
Market & 2004/2007 & XNYM - Crude oil & 100\% & 0\%\\
Market & 2004/2007 & XNYM - Gasoline & 100\% & 0\%\\
Market & 2004/2007 & XNYM - Heating oil & 100\% & 0\%\\
\addlinespace
Market & 2004/2007 & XNYM - Natural gas & 100\% & 0\%\\
Market & 2004/2007 & XNYM - Palladium & 100\% & 0\%\\
Market & 2004/2007 & XNYM - Silver & 100\% & 0\%\\
OI & 2004/2007 & XCME - Lean hogs & 38\% & 22\%\\
OI & 2004/2007 & XCME - Live cattle & 32\% & 35\%\\
\addlinespace
OI & 2004/2007 & XNYM - Natural gas & 32\% & 35\%\\
OI & 2004/2007 & XNYM - Palladium & 43\% & 28\%\\
OI & 2004/2007 & IFUS - Cocoa & 18\% & 36\%\\
OI & 2004/2007 & IFUS - Coffee & 34\% & 28\%\\
OI & 2004/2007 & IFUS - Cotton & 33\% & 17\%\\
\addlinespace
OI & 2004/2007 & IFUS - Sugar & 48\% & 16\%\\
TS & 2004/2007 & XNYM - Copper & 86\% & 0\%\\
TS & 2004/2007 & XCME - Feeder cattle & 86\% & 0\%\\
TS & 2004/2007 & XCME - Lean hogs & 44\% & 46\%\\
TS & 2004/2007 & XCME - Live cattle & 56\% & 23\%\\
\addlinespace
TS & 2004/2007 & XNYM - Gold & 28\% & 0\%\\
TS & 2004/2007 & XNYM - Palladium & 0\% & 6\%\\
TS & 2004/2007 & XNYM - Platinum & 95\% & 0\%\\
TS & 2004/2007 & IFUS - Cocoa & 15\% & 12\%\\
CHP & 2008/2013 & XCBT - Soybean meal & 79\% & 4\%\\
\addlinespace
CHP & 2008/2013 & XNYM - Gasoline & 46\% & 0\%\\
CHP & 2008/2013 & XNYM - Heating oil & 1\% & 18\%\\
CHP & 2008/2013 & XNYM - Gold & 96\% & 0\%\\
CHP & 2008/2013 & XNYM - Palladium & 100\% & 0\%\\
CHP & 2008/2013 & XNYM - Platinum & 100\% & 0\%\\
\addlinespace
CHP & 2008/2013 & XNYM - Silver & 90\% & 0\%\\
CHP & 2008/2013 & IFUS - Orange juice & 96\% & 0\%\\
Market & 2008/2013 & XCBT - Corn & 100\% & 0\%\\
Market & 2008/2013 & XCBT - Oats & 100\% & 0\%\\
Market & 2008/2013 & XNYM - Copper & 100\% & 0\%\\
\addlinespace
Market & 2008/2013 & XNYM - Crude oil & 100\% & 0\%\\
Market & 2008/2013 & XNYM - Gasoline & 100\% & 0\%\\
Market & 2008/2013 & XNYM - Heating oil & 100\% & 0\%\\
Market & 2008/2013 & XNYM - Palladium & 100\% & 0\%\\
Market & 2008/2013 & XNYM - Silver & 100\% & 0\%\\
\addlinespace
OI & 2008/2013 & XCBT - Corn & 21\% & 37\%\\
OI & 2008/2013 & XCBT - Soybean meal & 37\% & 34\%\\
OI & 2008/2013 & XNYM - Crude oil & 23\% & 31\%\\
OI & 2008/2013 & XNYM - Gasoline & 33\% & 27\%\\
OI & 2008/2013 & XNYM - Heating oil & 27\% & 34\%\\
\addlinespace
OI & 2008/2013 & IFUS - Orange juice & 32\% & 43\%\\
OI & 2008/2013 & IFUS - Sugar & 36\% & 31\%\\
OI & 2008/2013 & XCME - Lumber & 35\% & 38\%\\
TS & 2008/2013 & XCBT - Soybean meal & 69\% & 1\%\\
TS & 2008/2013 & XCBT - Soybeans & 59\% & 0\%\\
\addlinespace
TS & 2008/2013 & XNYM - Crude oil & 25\% & 30\%\\
TS & 2008/2013 & XNYM - Gasoline & 61\% & 6\%\\
TS & 2008/2013 & XNYM - Heating oil & 33\% & 6\%\\
TS & 2008/2013 & XNYM - Palladium & 38\% & 0\%\\
TS & 2008/2013 & XNYM - Platinum & 47\% & 1\%\\
\addlinespace
TS & 2008/2013 & XNYM - Silver & 64\% & 0\%\\
CHP & 2014/2017 & XNYM - Copper & 0\% & 79\%\\
CHP & 2014/2017 & XNYM - Gasoline & 13\% & 0\%\\
CHP & 2014/2017 & XNYM - Gold & 78\% & 0\%\\
CHP & 2014/2017 & XNYM - Palladium & 100\% & 0\%\\
\addlinespace
CHP & 2014/2017 & XNYM - Platinum & 100\% & 0\%\\
CHP & 2014/2017 & XNYM - Silver & 69\% & 0\%\\
CHP & 2014/2017 & IFUS - Orange juice & 62\% & 2\%\\
CHP & 2014/2017 & XCME - Lumber & 38\% & 53\%\\
Market & 2014/2017 & XCBT - Soybean meal & 100\% & 0\%\\
\addlinespace
Market & 2014/2017 & XNYM - Crude oil & 100\% & 0\%\\
Market & 2014/2017 & XNYM - Gasoline & 100\% & 0\%\\
Market & 2014/2017 & XNYM - Heating oil & 100\% & 0\%\\
Market & 2014/2017 & XNYM - Natural gas & 100\% & 0\%\\
Market & 2014/2017 & XNYM - Palladium & 100\% & 0\%\\
\addlinespace
Market & 2014/2017 & IFUS - Coffee & 100\% & 0\%\\
Market & 2014/2017 & IFUS - Sugar & 100\% & 0\%\\
OI & 2014/2017 & XCBT - Oats & 32\% & 45\%\\
OI & 2014/2017 & XCBT - Soybean meal & 39\% & 27\%\\
OI & 2014/2017 & XNYM - Copper & 48\% & 15\%\\
\addlinespace
OI & 2014/2017 & XNYM - Gold & 39\% & 23\%\\
OI & 2014/2017 & XNYM - Silver & 44\% & 28\%\\
OI & 2014/2017 & IFUS - Cocoa & 33\% & 34\%\\
OI & 2014/2017 & IFUS - Cotton & 42\% & 31\%\\
OI & 2014/2017 & XCME - Lumber & 50\% & 30\%\\
\addlinespace
TS & 2014/2017 & XCBT - Soybean meal & 68\% & 10\%\\
TS & 2014/2017 & XCBT - Soybeans & 56\% & 10\%\\
TS & 2014/2017 & XCME - Feeder cattle & 75\% & 10\%\\
TS & 2014/2017 & XCME - Live cattle & 65\% & 24\%\\
TS & 2014/2017 & IFUS - Cocoa & 54\% & 1\%\\
\addlinespace
TS & 2014/2017 & IFUS - Cotton & 40\% & 2\%\\
TS & 2014/2017 & IFUS - Orange juice & 41\% & 23\%\\
TS & 2014/2017 & XCME - Lumber & 41\% & 39\%\\*
\end{longtabu}\endgroup{}

\newpage
\begingroup\fontsize{8}{10}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\caption{\label{tab:correlations}This table displays the average pairwise correlations for various sets of commodities including the multiple sets of risk factor commodity picks, the whole cross-section of U.S. traded commodities considered in the study, the latter with metals omitted, and the cross-section of U.S. traded metals. For each period and commodity set the correlations are calculated independently over the whole period as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes. See section 2 for more details.}\\
\toprule
Asset pool & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
CHP factor picks & High & 0.09 & 0.24 & 0.32 & 0.22\\
CHP factor picks & Low & 0.10 & 0.28 & 0.37 & 0.19\\
CHP factor picks & None & 0.10 & 0.27 & 0.34 & 0.21\\
Market factor picks & High & 0.23 & 0.24 & 0.40 & 0.22\\
Market factor picks & Low & 0.20 & 0.28 & 0.42 & 0.19\\
\addlinespace
Market factor picks & None & 0.21 & 0.26 & 0.41 & 0.21\\
OI factor picks & High & 0.03 & 0.04 & 0.28 & 0.15\\
OI factor picks & Low & 0.03 & 0.09 & 0.22 & 0.07\\
OI factor picks & None & 0.03 & 0.07 & 0.25 & 0.11\\
TS factor picks & High & 0.16 & 0.15 & 0.41 & 0.11\\
\addlinespace
TS factor picks & Low & 0.11 & 0.17 & 0.48 & 0.09\\
TS factor picks & None & 0.13 & 0.16 & 0.44 & 0.10\\
US - Commodity & High & 0.08 & 0.11 & 0.25 & 0.13\\
US - Commodity & Low & 0.07 & 0.15 & 0.22 & 0.09\\
US - Commodity & None & 0.08 & 0.13 & 0.24 & 0.11\\
\addlinespace
US - Commodity - No metals & High & 0.09 & 0.10 & 0.26 & 0.12\\
US - Commodity - No metals & Low & 0.08 & 0.13 & 0.17 & 0.10\\
US - Commodity - No metals & None & 0.09 & 0.12 & 0.22 & 0.11\\
US - Metals & High & 0.23 & 0.55 & 0.52 & 0.44\\
US - Metals & Low & 0.19 & 0.52 & 0.61 & 0.42\\
US - Metals & None & 0.21 & 0.53 & 0.55 & 0.43\\
\bottomrule
\end{longtabu}\endgroup{}

\newpage
\begingroup\fontsize{8}{10}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\caption{\label{tab:fact_pick_regs_picks_picks}This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models. The dependent variables are individual nearby returns on risk factors commodity picks while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in Table 4. For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged. For each period, the models are implemented over the whole period, as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes independently. See section 2 for more details.}\\
\toprule
Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
\endfirsthead
\caption[]{continued}\\
\toprule
Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
TS factor picks & \textasciitilde{} CHP factor & High & 1.45\% & 20.37\% & 16.95\% & 8.81\%\\
TS factor picks & \textasciitilde{} CHP factor & Low & 7.6\% & 21.82\% & 10.29\% & 4.84\%\\
TS factor picks & \textasciitilde{} CHP factor & None & 3.42\% & 21.2\% & 14.09\% & 5.06\%\\
TS factor picks & \textasciitilde{} Market factor & High & 28.64\% & 27.15\% & 48.8\% & 21.54\%\\
TS factor picks & \textasciitilde{} Market factor & Low & 25.53\% & 28.87\% & 54.4\% & 21.22\%\\
\addlinespace
TS factor picks & \textasciitilde{} Market factor & None & 27.23\% & 28.26\% & 50.95\% & 21.63\%\\
TS factor picks & \textasciitilde{} OI factor & High & 0.07\% & 6.42\% & 4.08\% & 2.13\%\\
TS factor picks & \textasciitilde{} OI factor & Low & 2.48\% & 0.81\% & 2.68\% & 0.61\%\\
TS factor picks & \textasciitilde{} OI factor & None & 0.68\% & 2.26\% & 1.81\% & 0.56\%\\
TS factor picks & \textasciitilde{} TS factor & High & 2.04\% & 7.65\% & 5.2\% & 2.98\%\\
\addlinespace
TS factor picks & \textasciitilde{} TS factor & Low & 2.22\% & 6.03\% & 2\% & 1.85\%\\
TS factor picks & \textasciitilde{} TS factor & None & 0.53\% & 6.91\% & 4.16\% & 2.02\%\\
OI factor picks & \textasciitilde{} CHP factor & High & 3.02\% & 5.9\% & 4.56\% & 10.95\%\\
OI factor picks & \textasciitilde{} CHP factor & Low & 1.32\% & 9.37\% & 7.5\% & 5.5\%\\
OI factor picks & \textasciitilde{} CHP factor & None & 1.96\% & 6.96\% & 3.95\% & 6.36\%\\
\addlinespace
OI factor picks & \textasciitilde{} Market factor & High & 14.4\% & 15.55\% & 39.51\% & 24.98\%\\
OI factor picks & \textasciitilde{} Market factor & Low & 14.99\% & 20.4\% & 32.69\% & 17.31\%\\
OI factor picks & \textasciitilde{} Market factor & None & 14.86\% & 18\% & 36.91\% & 21.08\%\\
OI factor picks & \textasciitilde{} OI factor & High & 1.67\% & 1.82\% & 0.87\% & 0.64\%\\
OI factor picks & \textasciitilde{} OI factor & Low & 0.67\% & -0.38\% & 0.95\% & 3.52\%\\
\addlinespace
OI factor picks & \textasciitilde{} OI factor & None & 0.29\% & 0.77\% & 0.09\% & 0.74\%\\
OI factor picks & \textasciitilde{} TS factor & High & 3.24\% & 7.15\% & 13.59\% & 3.69\%\\
OI factor picks & \textasciitilde{} TS factor & Low & 2.92\% & 2.7\% & 4.11\% & 3\%\\
OI factor picks & \textasciitilde{} TS factor & None & 3.07\% & 5.36\% & 9.97\% & 3.08\%\\
CHP factor picks & \textasciitilde{} CHP factor & High & 5.74\% & 15.05\% & 12.05\% & 12.46\%\\
\addlinespace
CHP factor picks & \textasciitilde{} CHP factor & Low & 7.05\% & 10.85\% & 8.7\% & 14.6\%\\
CHP factor picks & \textasciitilde{} CHP factor & None & 5.83\% & 13.23\% & 10.46\% & 12.91\%\\
CHP factor picks & \textasciitilde{} Market factor & High & 21.09\% & 35.23\% & 41.13\% & 32.66\%\\
CHP factor picks & \textasciitilde{} Market factor & Low & 21.6\% & 38.7\% & 46.97\% & 29.72\%\\
CHP factor picks & \textasciitilde{} Market factor & None & 21.27\% & 37.36\% & 43.49\% & 31.36\%\\
\addlinespace
CHP factor picks & \textasciitilde{} OI factor & High & 1.69\% & 3.9\% & 4.04\% & 0.74\%\\
CHP factor picks & \textasciitilde{} OI factor & Low & 3.51\% & 1.61\% & 1.03\% & 2.96\%\\
CHP factor picks & \textasciitilde{} OI factor & None & 1.57\% & 1.64\% & 2.07\% & 0.23\%\\
CHP factor picks & \textasciitilde{} TS factor & High & 4.77\% & 7.1\% & 1.98\% & 4.78\%\\
CHP factor picks & \textasciitilde{} TS factor & Low & 5.36\% & 5.57\% & 0.95\% & -0.21\%\\
\addlinespace
CHP factor picks & \textasciitilde{} TS factor & None & 4.54\% & 5.1\% & 1.84\% & 1.66\%\\
Market factor picks & \textasciitilde{} CHP factor & High & 7.79\% & 8.62\% & 7.1\% & 7.84\%\\
Market factor picks & \textasciitilde{} CHP factor & Low & 4.6\% & 7.78\% & 7.63\% & 7.73\%\\
Market factor picks & \textasciitilde{} CHP factor & None & 6.06\% & 8.31\% & 6.22\% & 7.07\%\\
Market factor picks & \textasciitilde{} Market factor & High & 32.85\% & 34.83\% & 48.14\% & 33.71\%\\
\addlinespace
Market factor picks & \textasciitilde{} Market factor & Low & 30.4\% & 37.35\% & 49.31\% & 29.36\%\\
Market factor picks & \textasciitilde{} Market factor & None & 31.43\% & 36.1\% & 48.63\% & 32.31\%\\
Market factor picks & \textasciitilde{} OI factor & High & 3.74\% & 0.77\% & 2.62\% & 0.52\%\\
Market factor picks & \textasciitilde{} OI factor & Low & 0.41\% & -0.45\% & 1.22\% & -0.05\%\\
Market factor picks & \textasciitilde{} OI factor & None & 1.33\% & 0.29\% & 0.78\% & 0.53\%\\
\addlinespace
Market factor picks & \textasciitilde{} TS factor & High & 6.64\% & 5.3\% & 2.45\% & 7.59\%\\
Market factor picks & \textasciitilde{} TS factor & Low & 8.53\% & 4.21\% & 11.16\% & 4.7\%\\
Market factor picks & \textasciitilde{} TS factor & None & 7.65\% & 5.2\% & 3.25\% & 6.24\%\\*
\end{longtabu}\endgroup{}

\newpage
\begingroup\fontsize{8}{10}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\caption{\label{tab:fact_pick_regs_picks_UScommos}This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models. The dependent variables are individual nearby returns on the commodities forming the entire cross-section of U.S. traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in Table 4. For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged. For each period, the models are implemented over the whole period, as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes independently. See section 2 for more details.}\\
\toprule
Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
\endfirsthead
\caption[]{continued}\\
\toprule
Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
TS factor picks & \textasciitilde{} CHP factor & High & 0.36\% & 8.95\% & 7.8\% & 3.34\%\\
TS factor picks & \textasciitilde{} CHP factor & Low & 2.38\% & 11.41\% & 4.96\% & 1.26\%\\
TS factor picks & \textasciitilde{} CHP factor & None & 1.03\% & 10.14\% & 5.65\% & 1.66\%\\
TS factor picks & \textasciitilde{} Market factor & High & 10.52\% & 10.93\% & 26.99\% & 9.22\%\\
TS factor picks & \textasciitilde{} Market factor & Low & 9.7\% & 13.71\% & 27.33\% & 7.99\%\\
\addlinespace
TS factor picks & \textasciitilde{} Market factor & None & 10.13\% & 12.29\% & 26.94\% & 8.74\%\\
TS factor picks & \textasciitilde{} OI factor & High & 0.07\% & 2.36\% & 1.42\% & 0.31\%\\
TS factor picks & \textasciitilde{} OI factor & Low & 0.69\% & 0.03\% & 0.89\% & 0.23\%\\
TS factor picks & \textasciitilde{} OI factor & None & 0.22\% & 0.77\% & 0.74\% & 0.06\%\\
TS factor picks & \textasciitilde{} TS factor & High & 0.6\% & 2.8\% & 2.09\% & 1.18\%\\
\addlinespace
TS factor picks & \textasciitilde{} TS factor & Low & 0.89\% & 3.07\% & 0.73\% & 0.72\%\\
TS factor picks & \textasciitilde{} TS factor & None & 0.18\% & 2.49\% & 1.64\% & 0.93\%\\
OI factor picks & \textasciitilde{} CHP factor & High & 0.94\% & 2.61\% & 1.57\% & 4.45\%\\
OI factor picks & \textasciitilde{} CHP factor & Low & 0.35\% & 6.44\% & 3.39\% & 2.23\%\\
OI factor picks & \textasciitilde{} CHP factor & None & 0.61\% & 3.7\% & 1.54\% & 2.53\%\\
\addlinespace
OI factor picks & \textasciitilde{} Market factor & High & 6.65\% & 9.49\% & 25.93\% & 13.83\%\\
OI factor picks & \textasciitilde{} Market factor & Low & 6.51\% & 13.26\% & 21.69\% & 9.02\%\\
OI factor picks & \textasciitilde{} Market factor & None & 6.49\% & 11.42\% & 23.87\% & 11.59\%\\
OI factor picks & \textasciitilde{} OI factor & High & 0.38\% & 0.29\% & 0.36\% & 1.01\%\\
OI factor picks & \textasciitilde{} OI factor & Low & 0.63\% & -0.58\% & 0.23\% & 1.89\%\\
\addlinespace
OI factor picks & \textasciitilde{} OI factor & None & 0.05\% & 0.08\% & 0.05\% & 0.48\%\\
OI factor picks & \textasciitilde{} TS factor & High & 1.17\% & 2.83\% & 7.46\% & 1.87\%\\
OI factor picks & \textasciitilde{} TS factor & Low & 1.09\% & 0.63\% & 1.92\% & 1.56\%\\
OI factor picks & \textasciitilde{} TS factor & None & 1.22\% & 2.08\% & 5.16\% & 1.44\%\\
CHP factor picks & \textasciitilde{} CHP factor & High & 1.97\% & 4.78\% & 6.3\% & 3.8\%\\
\addlinespace
CHP factor picks & \textasciitilde{} CHP factor & Low & 3.02\% & 3.81\% & 3.72\% & 5.47\%\\
CHP factor picks & \textasciitilde{} CHP factor & None & 2.3\% & 4.23\% & 4.14\% & 4.39\%\\
CHP factor picks & \textasciitilde{} Market factor & High & 10.52\% & 13.87\% & 25.07\% & 13.35\%\\
CHP factor picks & \textasciitilde{} Market factor & Low & 9.51\% & 16.21\% & 26.19\% & 11.69\%\\
CHP factor picks & \textasciitilde{} Market factor & None & 9.96\% & 15.3\% & 25.4\% & 12.43\%\\
\addlinespace
CHP factor picks & \textasciitilde{} OI factor & High & 0.65\% & 1.39\% & 1.39\% & 0.41\%\\
CHP factor picks & \textasciitilde{} OI factor & Low & 1.46\% & 0.29\% & 0.55\% & 1.45\%\\
CHP factor picks & \textasciitilde{} OI factor & None & 0.65\% & 0.45\% & 0.83\% & 0.12\%\\
CHP factor picks & \textasciitilde{} TS factor & High & 1.96\% & 2.85\% & 1.19\% & 1.49\%\\
CHP factor picks & \textasciitilde{} TS factor & Low & 2.44\% & 2.87\% & 0.27\% & 0.07\%\\
\addlinespace
CHP factor picks & \textasciitilde{} TS factor & None & 2\% & 2.32\% & 0.97\% & 0.5\%\\
Market factor picks & \textasciitilde{} CHP factor & High & 2.57\% & 4.52\% & 4.29\% & 2.37\%\\
Market factor picks & \textasciitilde{} CHP factor & Low & 1.89\% & 4.5\% & 4.17\% & 2.69\%\\
Market factor picks & \textasciitilde{} CHP factor & None & 1.99\% & 4.31\% & 3.47\% & 2.49\%\\
Market factor picks & \textasciitilde{} Market factor & High & 12.42\% & 15.19\% & 27.88\% & 14.87\%\\
\addlinespace
Market factor picks & \textasciitilde{} Market factor & Low & 11.32\% & 16.98\% & 27.68\% & 12.24\%\\
Market factor picks & \textasciitilde{} Market factor & None & 11.69\% & 16.13\% & 27.53\% & 13.42\%\\
Market factor picks & \textasciitilde{} OI factor & High & 1.63\% & 0.52\% & 1.29\% & 0.28\%\\
Market factor picks & \textasciitilde{} OI factor & Low & 0.14\% & 0.43\% & 0.3\% & -0.05\%\\
Market factor picks & \textasciitilde{} OI factor & None & 0.6\% & 0.36\% & 0.52\% & 0.41\%\\
\addlinespace
Market factor picks & \textasciitilde{} TS factor & High & 2.66\% & 1.84\% & 1.09\% & 2.6\%\\
Market factor picks & \textasciitilde{} TS factor & Low & 3.18\% & 2.47\% & 5.13\% & 2.36\%\\
Market factor picks & \textasciitilde{} TS factor & None & 2.97\% & 2.18\% & 1.28\% & 2.38\%\\*
\end{longtabu}\endgroup{}

\newpage
\begingroup\fontsize{8}{10}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\caption{\label{tab:fact_pick_regs_picks_UKcommos}This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models. The dependent variables are individual nearby returns on the six LME traded metals considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in Table 4. For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged. For each period, the models are implemented over the whole period, as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes independently. See section 2 for more details.}\\
\toprule
Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
\endfirsthead
\caption[]{continued}\\
\toprule
Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
TS factor picks & \textasciitilde{} CHP factor & High & -0.01\% & 2.1\% & 3.87\% & 1.05\%\\
TS factor picks & \textasciitilde{} CHP factor & Low & -0.37\% & 17.79\% & 3.32\% & 0.8\%\\
TS factor picks & \textasciitilde{} CHP factor & None & -0.05\% & 7.89\% & 0.65\% & -0.26\%\\
TS factor picks & \textasciitilde{} Market factor & High & 0.65\% & 17.55\% & 30.72\% & 5.69\%\\
TS factor picks & \textasciitilde{} Market factor & Low & 1.62\% & 22.57\% & 27.92\% & 0.68\%\\
\addlinespace
TS factor picks & \textasciitilde{} Market factor & None & 1.3\% & 20.58\% & 29.6\% & 3.01\%\\
TS factor picks & \textasciitilde{} OI factor & High & -0.36\% & 4.97\% & 0.31\% & -0.65\%\\
TS factor picks & \textasciitilde{} OI factor & Low & 0.06\% & 1.29\% & -0.33\% & -0.11\%\\
TS factor picks & \textasciitilde{} OI factor & None & 0.04\% & 3.02\% & -0.02\% & -0.18\%\\
TS factor picks & \textasciitilde{} TS factor & High & 0.45\% & 4.72\% & 0.22\% & -0.22\%\\
\addlinespace
TS factor picks & \textasciitilde{} TS factor & Low & 0.01\% & -0.67\% & 0.22\% & 1.72\%\\
TS factor picks & \textasciitilde{} TS factor & None & -0.12\% & 2.11\% & 0.44\% & 1.33\%\\
OI factor picks & \textasciitilde{} CHP factor & High & 1.63\% & 0.34\% & -0.37\% & 5.03\%\\
OI factor picks & \textasciitilde{} CHP factor & Low & -0.04\% & 8.57\% & 3.01\% & 0.43\%\\
OI factor picks & \textasciitilde{} CHP factor & None & 0.01\% & 3.54\% & 0.55\% & 0.72\%\\
\addlinespace
OI factor picks & \textasciitilde{} Market factor & High & -0.24\% & 4.93\% & 28.78\% & 12.91\%\\
OI factor picks & \textasciitilde{} Market factor & Low & 3.59\% & 10.46\% & 16.76\% & 7.99\%\\
OI factor picks & \textasciitilde{} Market factor & None & 1.17\% & 7.97\% & 24.03\% & 10.37\%\\
OI factor picks & \textasciitilde{} OI factor & High & -0.18\% & -0.68\% & 0.43\% & 0.76\%\\
OI factor picks & \textasciitilde{} OI factor & Low & 1.79\% & 0.78\% & -0.32\% & 3.01\%\\
\addlinespace
OI factor picks & \textasciitilde{} OI factor & None & 0.54\% & -0.33\% & 0.07\% & -0.12\%\\
OI factor picks & \textasciitilde{} TS factor & High & -0.26\% & -0.34\% & 7.07\% & -0.26\%\\
OI factor picks & \textasciitilde{} TS factor & Low & 0.3\% & 1.01\% & 0.58\% & -0.31\%\\
OI factor picks & \textasciitilde{} TS factor & None & 0.17\% & 0.11\% & 4.57\% & -0.17\%\\
CHP factor picks & \textasciitilde{} CHP factor & High & 0.48\% & -0.1\% & 2.96\% & 0.46\%\\
\addlinespace
CHP factor picks & \textasciitilde{} CHP factor & Low & 0.15\% & -0.55\% & 2.7\% & 0.77\%\\
CHP factor picks & \textasciitilde{} CHP factor & None & 0.05\% & -0.43\% & 0.48\% & 0.05\%\\
CHP factor picks & \textasciitilde{} Market factor & High & 4.22\% & 18.7\% & 26.41\% & 15.02\%\\
CHP factor picks & \textasciitilde{} Market factor & Low & 4.4\% & 30.16\% & 27.34\% & 14.77\%\\
CHP factor picks & \textasciitilde{} Market factor & None & 4.48\% & 25.09\% & 26.83\% & 14.99\%\\
\addlinespace
CHP factor picks & \textasciitilde{} OI factor & High & 0.28\% & 6.51\% & 0\% & -0.57\%\\
CHP factor picks & \textasciitilde{} OI factor & Low & 0.41\% & 0.18\% & 0.39\% & 0.65\%\\
CHP factor picks & \textasciitilde{} OI factor & None & 0.49\% & 3.89\% & 0.29\% & -0.1\%\\
CHP factor picks & \textasciitilde{} TS factor & High & -0.36\% & 4.19\% & -0.19\% & 2.09\%\\
CHP factor picks & \textasciitilde{} TS factor & Low & -0.26\% & -0.52\% & -0.17\% & 0.28\%\\
\addlinespace
CHP factor picks & \textasciitilde{} TS factor & None & -0.24\% & 2.07\% & 0.13\% & 1.33\%\\
Market factor picks & \textasciitilde{} CHP factor & High & -0.22\% & 3.62\% & 0.64\% & 1.88\%\\
Market factor picks & \textasciitilde{} CHP factor & Low & -0.33\% & 9.62\% & 1.72\% & 1.12\%\\
Market factor picks & \textasciitilde{} CHP factor & None & -0.1\% & 6.32\% & -0.08\% & 1.61\%\\
Market factor picks & \textasciitilde{} Market factor & High & -0.11\% & 8.95\% & 36.58\% & 11.77\%\\
\addlinespace
Market factor picks & \textasciitilde{} Market factor & Low & 2.08\% & 9.85\% & 29.63\% & 2.79\%\\
Market factor picks & \textasciitilde{} Market factor & None & 0.88\% & 9.93\% & 33.73\% & 7.69\%\\
Market factor picks & \textasciitilde{} OI factor & High & 0.24\% & -0.58\% & 0.84\% & -0.04\%\\
Market factor picks & \textasciitilde{} OI factor & Low & 0.66\% & 0.56\% & -0.17\% & -0.42\%\\
Market factor picks & \textasciitilde{} OI factor & None & -0.04\% & 0.12\% & 0.62\% & -0.24\%\\
\addlinespace
Market factor picks & \textasciitilde{} TS factor & High & -0.38\% & 1.37\% & 2.9\% & -0.37\%\\
Market factor picks & \textasciitilde{} TS factor & Low & -0.43\% & 1.41\% & 0.32\% & 0.39\%\\
Market factor picks & \textasciitilde{} TS factor & None & -0.23\% & 1.65\% & 2.15\% & 0.12\%\\*
\end{longtabu}\endgroup{}

\newpage
\begingroup\fontsize{8}{10}\selectfont

\begin{landscape}
\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\caption{\label{tab:fact_pick_regs_picks_UKcommos_legs}This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models. The dependent variables are individual nearby returns on the six LME traded metals considered in the study while the regressors are returns on the long and short legs of mimicking portfolios for risk factors considered independently, where the factor portfolios are constructed using the corresponding set of risk factor commodity picks. For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged. For each period, the models are implemented over the whole period, as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes independently. See section 2 for more details.}\\
\toprule
Factor asset pool & Model & Leg & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
\endfirsthead
\caption[]{continued}\\
\toprule
Factor asset pool & Model & Leg & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
TS factor picks & \textasciitilde{} CHP factor & Long & High & 0.91\% & 11.5\% & 13.22\% & -0.15\%\\
TS factor picks & \textasciitilde{} CHP factor & Long & Low & 1.51\% & 29.68\% & 34.77\% & 1.21\%\\
TS factor picks & \textasciitilde{} CHP factor & Long & None & 1.39\% & 19.71\% & 20.35\% & 1.09\%\\
TS factor picks & \textasciitilde{} CHP factor & Short & High & 0.01\% & 1.47\% & 28.59\% & 4.63\%\\
TS factor picks & \textasciitilde{} CHP factor & Short & Low & -0.15\% & -0.48\% & 26.72\% & -0.11\%\\
\addlinespace
TS factor picks & \textasciitilde{} CHP factor & Short & None & 0.16\% & 0.9\% & 27.93\% & 1.23\%\\
TS factor picks & \textasciitilde{} Market factor & Long & High & 0.65\% & 17.55\% & 30.72\% & 5.69\%\\
TS factor picks & \textasciitilde{} Market factor & Long & Low & 1.62\% & 22.57\% & 27.92\% & 0.68\%\\
TS factor picks & \textasciitilde{} Market factor & Long & None & 1.3\% & 20.58\% & 29.6\% & 3.01\%\\
TS factor picks & \textasciitilde{} OI factor & Long & High & 0.36\% & 4.73\% & 23.81\% & 1.72\%\\
\addlinespace
TS factor picks & \textasciitilde{} OI factor & Long & Low & 1.54\% & 11.1\% & 30.88\% & -0.57\%\\
TS factor picks & \textasciitilde{} OI factor & Long & None & 0.99\% & 8.22\% & 25.87\% & 0.26\%\\
TS factor picks & \textasciitilde{} OI factor & Short & High & 0.56\% & 22.57\% & 20.33\% & 2.35\%\\
TS factor picks & \textasciitilde{} OI factor & Short & Low & 2.01\% & 20.14\% & 28.09\% & 0.2\%\\
TS factor picks & \textasciitilde{} OI factor & Short & None & 1.42\% & 21.62\% & 22.99\% & 1.8\%\\
\addlinespace
TS factor picks & \textasciitilde{} TS factor & Long & High & -0.14\% & 24.07\% & 19.08\% & 0.51\%\\
TS factor picks & \textasciitilde{} TS factor & Long & Low & 1.18\% & 22.59\% & 23.52\% & -0.54\%\\
TS factor picks & \textasciitilde{} TS factor & Long & None & 0.37\% & 23.8\% & 20.46\% & -0.36\%\\
TS factor picks & \textasciitilde{} TS factor & Short & High & 1.14\% & 4.16\% & 25.71\% & 3.89\%\\
TS factor picks & \textasciitilde{} TS factor & Short & Low & 0.6\% & 9.27\% & 34.98\% & 2.59\%\\
\addlinespace
TS factor picks & \textasciitilde{} TS factor & Short & None & 1.06\% & 7.24\% & 28.35\% & 4.01\%\\
OI factor picks & \textasciitilde{} CHP factor & Long & High & 0.19\% & 8.36\% & 15.6\% & 1.65\%\\
OI factor picks & \textasciitilde{} CHP factor & Long & Low & 3.42\% & 16.64\% & 8.36\% & 6.14\%\\
OI factor picks & \textasciitilde{} CHP factor & Long & None & 0.03\% & 12.55\% & 13.29\% & 3.64\%\\
OI factor picks & \textasciitilde{} CHP factor & Short & High & 0.9\% & 0.79\% & 23.17\% & 13.29\%\\
\addlinespace
OI factor picks & \textasciitilde{} CHP factor & Short & Low & 0.45\% & 0.65\% & 20.93\% & 3.06\%\\
OI factor picks & \textasciitilde{} CHP factor & Short & None & 1.01\% & 1.03\% & 22.48\% & 8.42\%\\
OI factor picks & \textasciitilde{} Market factor & Long & High & -0.24\% & 4.93\% & 28.78\% & 12.91\%\\
OI factor picks & \textasciitilde{} Market factor & Long & Low & 3.59\% & 10.46\% & 16.76\% & 7.99\%\\
OI factor picks & \textasciitilde{} Market factor & Long & None & 1.17\% & 7.97\% & 24.03\% & 10.37\%\\
\addlinespace
OI factor picks & \textasciitilde{} OI factor & Long & High & -0.39\% & 1.54\% & 17.05\% & 3.59\%\\
OI factor picks & \textasciitilde{} OI factor & Long & Low & -0.18\% & 7.12\% & 16.74\% & 6.64\%\\
OI factor picks & \textasciitilde{} OI factor & Long & None & -0.22\% & 3.7\% & 17.08\% & 5.56\%\\
OI factor picks & \textasciitilde{} OI factor & Short & High & 0.01\% & 3.92\% & 24.04\% & 9.07\%\\
OI factor picks & \textasciitilde{} OI factor & Short & Low & 3.83\% & 2.41\% & 15.01\% & -1.06\%\\
\addlinespace
OI factor picks & \textasciitilde{} OI factor & Short & None & 1.55\% & 3.14\% & 20.57\% & 2.71\%\\
OI factor picks & \textasciitilde{} TS factor & Long & High & -0.24\% & 5.47\% & 22.98\% & 3.39\%\\
OI factor picks & \textasciitilde{} TS factor & Long & Low & 2.1\% & 15.43\% & 16.87\% & 0.23\%\\
OI factor picks & \textasciitilde{} TS factor & Long & None & 0.74\% & 10.28\% & 20.88\% & 1.57\%\\
OI factor picks & \textasciitilde{} TS factor & Short & High & -0.35\% & 1.99\% & 10.81\% & 8.45\%\\
\addlinespace
OI factor picks & \textasciitilde{} TS factor & Short & Low & 0.56\% & 1.8\% & 8.96\% & 0.35\%\\
OI factor picks & \textasciitilde{} TS factor & Short & None & 0.16\% & 2.25\% & 10.32\% & 4.29\%\\
CHP factor picks & \textasciitilde{} CHP factor & Long & High & 0.9\% & 10.35\% & 12.52\% & 5.81\%\\
CHP factor picks & \textasciitilde{} CHP factor & Long & Low & 3.58\% & 28.68\% & 29.36\% & 11.92\%\\
CHP factor picks & \textasciitilde{} CHP factor & Long & None & 1.87\% & 18.04\% & 18.32\% & 8.25\%\\
\addlinespace
CHP factor picks & \textasciitilde{} CHP factor & Short & High & 4.73\% & 21.64\% & 25.57\% & 13.39\%\\
CHP factor picks & \textasciitilde{} CHP factor & Short & Low & 0.15\% & 22.77\% & 21.53\% & 7.38\%\\
CHP factor picks & \textasciitilde{} CHP factor & Short & None & 2.08\% & 22.85\% & 24.23\% & 10.59\%\\
CHP factor picks & \textasciitilde{} Market factor & Long & High & 4.22\% & 18.7\% & 26.41\% & 15.02\%\\
CHP factor picks & \textasciitilde{} Market factor & Long & Low & 4.4\% & 30.16\% & 27.34\% & 14.77\%\\
\addlinespace
CHP factor picks & \textasciitilde{} Market factor & Long & None & 4.48\% & 25.09\% & 26.83\% & 14.99\%\\
CHP factor picks & \textasciitilde{} OI factor & Long & High & 0.6\% & 1.73\% & 19.04\% & 8.75\%\\
CHP factor picks & \textasciitilde{} OI factor & Long & Low & 1.32\% & 21.86\% & 29.51\% & 16.19\%\\
CHP factor picks & \textasciitilde{} OI factor & Long & None & 1.03\% & 9.08\% & 22.58\% & 11.61\%\\
CHP factor picks & \textasciitilde{} OI factor & Short & High & 2.03\% & 21.75\% & 17.79\% & 8.86\%\\
\addlinespace
CHP factor picks & \textasciitilde{} OI factor & Short & Low & 3.48\% & 23.02\% & 30.31\% & 3.59\%\\
CHP factor picks & \textasciitilde{} OI factor & Short & None & 2.83\% & 22.98\% & 21.6\% & 6.75\%\\
CHP factor picks & \textasciitilde{} TS factor & Long & High & 1.55\% & 24.47\% & 16.98\% & 4.23\%\\
CHP factor picks & \textasciitilde{} TS factor & Long & Low & 2.4\% & 29.72\% & 21.59\% & 4.46\%\\
CHP factor picks & \textasciitilde{} TS factor & Long & None & 1.91\% & 27.37\% & 18.54\% & 5.2\%\\
\addlinespace
CHP factor picks & \textasciitilde{} TS factor & Short & High & 2.04\% & 2.25\% & 21.16\% & 11.49\%\\
CHP factor picks & \textasciitilde{} TS factor & Short & Low & 0.13\% & 15.94\% & 28.57\% & 15.29\%\\
CHP factor picks & \textasciitilde{} TS factor & Short & None & 1.15\% & 8.14\% & 23.54\% & 12.87\%\\
Market factor picks & \textasciitilde{} CHP factor & Long & High & 0.14\% & 14.47\% & 24.85\% & 13.11\%\\
Market factor picks & \textasciitilde{} CHP factor & Long & Low & 1.14\% & 19\% & 33.01\% & 7.1\%\\
\addlinespace
Market factor picks & \textasciitilde{} CHP factor & Long & None & 0.66\% & 17\% & 27.85\% & 10.89\%\\
Market factor picks & \textasciitilde{} CHP factor & Short & High & -0.19\% & 1.81\% & 31.9\% & 5.71\%\\
Market factor picks & \textasciitilde{} CHP factor & Short & Low & 1.53\% & 3.86\% & 35.32\% & -0.39\%\\
Market factor picks & \textasciitilde{} CHP factor & Short & None & 0.66\% & 2.85\% & 32.76\% & 2.67\%\\
Market factor picks & \textasciitilde{} Market factor & Long & High & -0.11\% & 8.95\% & 36.58\% & 11.77\%\\
\addlinespace
Market factor picks & \textasciitilde{} Market factor & Long & Low & 2.08\% & 9.85\% & 29.63\% & 2.79\%\\
Market factor picks & \textasciitilde{} Market factor & Long & None & 0.88\% & 9.93\% & 33.73\% & 7.69\%\\
Market factor picks & \textasciitilde{} OI factor & Long & High & -0.32\% & 2.73\% & 34.04\% & 7.23\%\\
Market factor picks & \textasciitilde{} OI factor & Long & Low & 0.07\% & 5.36\% & 35.07\% & 1.56\%\\
Market factor picks & \textasciitilde{} OI factor & Long & None & 0.07\% & 4.4\% & 34.38\% & 4.78\%\\
\addlinespace
Market factor picks & \textasciitilde{} OI factor & Short & High & -0.03\% & 6.86\% & 24.78\% & 9.62\%\\
Market factor picks & \textasciitilde{} OI factor & Short & Low & 2.28\% & 9.51\% & 27.82\% & 1.38\%\\
Market factor picks & \textasciitilde{} OI factor & Short & None & 0.43\% & 8.38\% & 25.68\% & 6.05\%\\
Market factor picks & \textasciitilde{} TS factor & Long & High & -0.03\% & 11.75\% & 30.86\% & 8.57\%\\
Market factor picks & \textasciitilde{} TS factor & Long & Low & 0.84\% & 8.74\% & 30.58\% & 4.49\%\\
\addlinespace
Market factor picks & \textasciitilde{} TS factor & Long & None & 0.48\% & 10.83\% & 30.76\% & 7.34\%\\
Market factor picks & \textasciitilde{} TS factor & Short & High & -0.43\% & 2.19\% & 25.29\% & 6.6\%\\
Market factor picks & \textasciitilde{} TS factor & Short & Low & 2.06\% & 2.77\% & 24.04\% & 0.2\%\\
Market factor picks & \textasciitilde{} TS factor & Short & None & 0.53\% & 2.81\% & 24.88\% & 3.76\%\\*
\end{longtabu}
\end{landscape}\endgroup{}

\section{Appendix}\label{appendix}

\subsection{Assets}\label{assets}

\begingroup\fontsize{8}{10}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\caption{\label{tab:appendix_assets}This table shows details on the individual commodities considered in this study including trading country, sector, subsector as well as trading exchange Market Identifier Codes (MIC, ISO 10383).}\\
\toprule
Country & Sector & Subsector & Exchange & Name\\
\midrule
US & Agriculturals & Grains & XCBT & Corn\\
US & Agriculturals & Grains & XCBT & Oats\\
US & Agriculturals & Grains & XCBT & Soybean meal\\
US & Agriculturals & Grains & XCBT & Soybean oil\\
US & Agriculturals & Grains & XCBT & Soybeans\\

US & Agriculturals & Grains & XCBT & Wheat-SR\\
US & Agriculturals & Livestock & XCME & Feeder cattle\\
US & Agriculturals & Livestock & XCME & Lean hogs\\
US & Agriculturals & Livestock & XCME & Live cattle\\
US & Agriculturals & Softs & IFUS & Cocoa\\

US & Agriculturals & Softs & IFUS & Coffee\\
US & Agriculturals & Softs & IFUS & Cotton\\
US & Agriculturals & Softs & IFUS & Orange juice\\
US & Agriculturals & Softs & IFUS & Sugar\\
US & Agriculturals & Softs & XCME & Lumber\\

US & Energy & Petroleum & XNYM & Crude oil\\
US & Energy & Petroleum & XNYM & Gasoline\\
US & Energy & Petroleum & XNYM & Heating oil\\
US & Energy & Petroleum & XNYM & Natural gas\\
US & Metals & Industrial & XNYM & Copper\\

US & Metals & Precious & XNYM & Gold\\
US & Metals & Precious & XNYM & Palladium\\
US & Metals & Precious & XNYM & Platinum\\
US & Metals & Precious & XNYM & Silver\\
UK & Metals & Industrial & XLME & Aluminium\\

UK & Metals & Industrial & XLME & Copper\\
UK & Metals & Industrial & XLME & Lead\\
UK & Metals & Industrial & XLME & Nickel\\
UK & Metals & Industrial & XLME & Tin\\
UK & Metals & Industrial & XLME & Zinc\\
\bottomrule
\end{longtabu}

\endgroup{}

\clearpage

\subsection{Market factor lemma}\label{market-factor-lemma}

\[\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}\]
\(\overline{R_{mkt, p}^{2}}\equiv\) period \(p\) average \(R^{2}\) for
market risk factor returns.\\
\(R_{j, mkt, p}^{2}\equiv\) period \(p\) \(R^{2}\) for the regression
where the depent variable is the vector of returns on commodity \(j\)
nearby contract and the regressor is the vector of returns on the market
portfolio; \(j \in Y_{p}^{mkt}\).\\
\(Y_{p}^{mkt}\equiv\) commodity set considered for the formation of the
mimicking portfolio for market risk over period \(p\).\\
\(n\equiv\) number of commodities in \(Y_{p}^{mkt}\).

\textbf{Proof}

Week \(t\) market factor return:
\[r_{mkt, t} = \sum_{j} w_{j, p} \cdot r_{j, t}\] \(w_{j, p}\equiv\)
period \(p\) weight for commodity \(j\) in the mimicking portfolio for
market risk in returns.\\
\(r_{j, t}\equiv\) week \(t\) return for commodity \(j\).

Assumptions:\\
-
\(w_{j, p} = w_{k, p} = \frac{1}{n} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt}\).\\
-
\(\sigma_{r_{j}, p} = \sigma_{r_{k}, p} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt}\).\\
-
\(cov \left ( r_{j}, r_{k} \right )_{p} = 0 \: \forall \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt}\).

\[
\begin{array}{l c l}
  \sigma_{r_{j, p}}^{2} & = & \beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2} + \sigma_{\epsilon}^{2} \\
  \beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2} & = & \sigma_{r_{j, p}}^{2} - \sigma_{\epsilon}^{2} \\
  \frac{\beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2}}{\sigma_{r_{j, p}}^{2}} & = & \frac{\sigma_{r_{j, p}}^{2} - \sigma_{\epsilon}^{2}}{\sigma_{r_{j, p}}^{2}} \\
    \frac{\beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2}}{\sigma_{r_{j, p}}^{2}}  & = & R_{r_{j}, r_{mkt}, p}^{2} \\ \\
  \sigma_{r_{mkt, p}}^{2} & = & \sum_{j} w_{j, p}^{2} \cdot \sigma_{j, p}^{2} + 2 \cdot \sum_{j} \sum_{k \neq j} w_{j, p} \cdot w_{k, p} \cdot cov \left ( r_{j, p}, r_{k, p} \right ) \\
                          & = & \sum_{j} \left ( \frac{1}{n} \right )^{2} \cdot \sigma_{j, p}^{2} \\
                          & = & \frac{\sum_{j} \sigma_{j, p}^{2}}{n^{2}} \\ \\
  cov \left ( r_{j}, r_{mkt} \right )_{p} & = & cov \left ( r_{j}, \frac{1}{n} \sum_{k} r_{k} \right )_{p} \\
                                          & = & \frac{1}{n} \sum_{k} cov \left ( r_{j}, r_{k} \right )_{p} \\
                                          & = & \frac{1}{n} cov \left ( r_{j}, r_{j} \right )_{p} \\
                                          & = & \frac{\sigma_{r_{j}, p}^{2}}{n} \\ \\
  \beta_{j, mkt, p}^{2} & = & \left [ \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}}{\sigma_{r_{mkt, p}}^{2}} \right ]^{2} \\
                        & = & \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}^{2}}{\sigma_{r_{mkt, p}}^{4}} \\ \\
  \beta_{j, mkt, p}^{2} \cdot  \sigma_{r_{mkt, p}}^{2}  & = & \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}^{2}}{\sigma_{r_{mkt, p}}^{2}} \\
                                                        & = & \left ( \frac{\sigma_{r_{j}, p}^{2}}{n} \right )^{2} \cdot \frac{1}{\sigma_{r_{mkt, p}}^{2}} \\
                                                        & = & \frac{\sigma_{r_{j}, p}^{4}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\ \\
  R_{r_{j}, r_{mkt}, p}^{2} & = & \frac{\sigma_{r_{j}, p}^{4}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \cdot \frac{1}{\sigma_{r_{j, p}}^{2}} \\
                            & = & \frac{\sigma_{r_{j}, p}^{2}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\ \\  
                            & \therefore  & \\ \\
  \overline{R_{r_{mkt}, p}^{2}} & = & \frac{1}{n} \sum_{j} \frac{\sigma_{r_{j}, p}^{2}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\
                                & = & \frac{1}{n} \cdot \frac{1}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \cdot \sum_{j} \sigma_{r_{j}, p}^{2} \\
                                & = & \frac{1}{n} \cdot \frac{\sum_{j} \sigma_{r_{j}, p}^{2}}{n^{2} \cdot \frac{1}{n^{2}} \cdot \sum_{j} \sigma_{r_{j}, p}^{2}} \\
                                & = & \frac{1}{n} \\
\end{array}
\]

\newpage

\bibliography{BibTeX.bib}

\clearpage
\theendnotes

\end{document}

### 2024-06-11 others/paper/custom/anonymous.Rmd
Track 'others' folder

---
documentclass: article
# classoption: letterpaper
geometry: "letterpaper, left = 1in, right = 1in, top = 1.5in, bottom = 1.5in"
link-citations: TRUE
bibliography: BibTeX.bib
biblio-style: jf
fontsize: 12pt

output:
  pdf_document:
    template: "template.tex"
    citation: natbib
    fig_caption: TRUE
    keep_tex: TRUE
    number_sections: TRUE
    latex_engine: pdflatex
    includes:
     in_header: preamble.tex

title: 'Financialization of Commodities: an Asset Pricing Perspective'

jel:
  - G11
  - G23
  - G13
  - Q02

keywords: 
  - Commodity futures
  - financialization
  - hedging pressure
  - financial crisis

acknowledgements: |
  We thank seminar participants at IIM Ahmedabad, IIM Calcutta, SKEMA Business School and University of Gottingen, as well as Griffith inaugural alternative investment conference attendants for their feedback. We also thank Joelle Miffre, Martijn Boons, John Fan, Robert Bianchi, Chardin Wese Simen, Andrew Kaleel and particularly Olaf Korn for their extremely useful comments and suggestions.

abstract: |
  The last two decades have seen major changes in the nature of the commodity markets with the influx of financial investor inflows followed by the financial crisis. We study the effect of these events on commodity futures pricing dynamics using commodity asset pricing techniques. We find that a non-price based factor is best able to detect the effects of commodity financialization, while the effects of the financial crisis and after are most clearly visible through the performance of the market factor. The effects of financialization seem to go beyond mechanical effects induced by the rise of indexing.

---

```{r, echo = FALSE, message = FALSE}
packages.v <- c("tidyr", "magrittr", "knitr", "lettercase", "tinytex", "bookdown", "kableExtra")
invisible(sapply(packages.v, require, character.only = TRUE))
options(knitr.table.format = "latex")
knitr::opts_chunk$set(echo = FALSE, results = "asis")
# tickers.tb <- readRDS(file = paste0(getwd(), "/data/tickers.rds"))
# tables.tb <- readRDS(file = paste0(getwd(), "/explore/results/tables.rds"))
tickers.tb <- readRDS(file = "../data/tickers.rds")
tables.tb <- readRDS(file = "../explore/results/tables.rds")

```

\newpage

# Introduction

The last twenty years have seen major upheavals in the commodity markets with the onset of financialization^[Starting around 2004, with a view of commodity markets as an emerging asset class and in an effort to hedge against inflation and seek diversification benefits [@buyuksahin_speculators_2014; @singleton_investor_2013], institutional investors sent forth an unprecedented flow of capital into commodity futures markets. This phenomenon is commonly referred to as the financialization of commodities [@domanski_financial_2007].] as well as the period of the 2008 financial crisis and its aftermath. Financialization appears to have affected a number of economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres. A vigorous legislative debate has led to regulatory changes accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section \ref{background} for a detailled discussion.]. In response to immediate policy concerns the academic debate was initially framed rather narrowly. In this paper we take a fundamentally different empirical approach that is broader in scope. We consider the entire cross-section of actively traded commodities on futures markets and use a futures based asset pricing framework that includes factors constructed using both price and non-price attributes.

Commodity futures markets have a history of being the classic physical commodity risks shifting conduit for commodity specialists, and financialization may have altered this long standing paradigm with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants. This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of traders. Factor models are well suited to isolating common driving factors and detecting co-movement and building on theory we develop a bespoke commodity-based asset pricing framework that seems well adapted to study these two issues simultaneously.

The first factor model we consider (CHP) is based on the well-known hedging pressure based theory [@anderson_hedger_1983; @chang_returns_1985; @cootner_returns_1960; @dusak_futures_1973; @hicks_value_1939; @hirshleifer_risk_1988; @hirshleifer_determinants_1989; @hirshleifer_hedging_1990; @kolb_is_1992; @keynes_treatise_1930] which postulates that futures prices for a given commodity are inversely related to the extent that commercial hedgers are short or long and we use a factor mimicking portfolio that captures the impact of hedging pressure as a systemic factor [@basu_capturing_2013]. Our second factor model is based on open interest growth following @hong_what_2012 who find that open interest growth has predictive power for individual commodity returns and again we construct a long-short factor mimicking portfolio. Our third model is based on term structure following @szymanowska_anatomy_2014 and @fuertes_commodity_2015 who demonstrate that the term structure factor has explanatory power for the cross-section of commodity returns. We finally consider an equally weighted portfolio of commodities as a proxy for the market factor. Our two price based and two non-price based factors allow us to compare and contrast different channels that could have led to changes in commodity price dynamics over the last twenty years.

We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (LME exchange) base metals over the 1997/2017 period that we divide into four distinct sub-periods. The first, the pre-financialization phase, spans the 1997/2003 period; the second, the financialization phase, spans the 2004/2007 period^[Starting point based on earlier studies [@baker_financialization_2014; @christoffersen_factor_2018].]; the third, 2008/2013, encompasses both the financial crisis and the loose monetary policy regimes that followed; and the fourth spans the period starting in 2014 to present.  
Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialization period compared to pre-financialization and this pattern extends to UK traded metals.

The arrival of financial investors raises the question of whether they functioned as liquidity providers or liquidity demanders. Arguments have been made for both sides with @moskowitz_time_2012 arguing that financial investors provide liquidity while @Kangtaletwopremiums2017 argue that they demand liquidity with @cheng_convective_2014 showing that they in fact transferred risk to hedgers during the 2008 financial crisis. We study this issue by extending the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in @hong_what_2012. Our use of this measure is motivated by the cross sectional nature of financialization [@basak_model_2016; @cheng_convective_2014; @le_futures_2017]. This paradigm implies that returns for individual commodities should be high in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in periods where \textbf{CHP} is high (\textbf{contango}). Over the first period the cross sectional average returns during \textbf{backwardation} for both the US and UK commodities are positive with those for the US statistically significant, and significantly higher than during \textbf{contango}, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis. Over the second period this pattern reverses, with both the US and UK commodities having significant positive returns during \textbf{contango} with these returns being significantly higher than during \textbf{backwardation}. This change in pattern suggests that the onset of financialization altered the traditional risk shifting nature of hedger’s behaviour implied by the Keynesian hypothesis and suggests that financial investors may have been liquidity demanders during financialization leading hedgers to become liquidity providers.

@goldstein_commodity_2017 as well as @goldstein_speculation_2014 argue that the arrival of financial investors has an impact on the extent of normal backwardation in commodity futures markets. Based on their analysis we would expect our average CHP factor, which is based on backwardation measured by hedger’s positions, as well our term structure factor, which is based on backwardation measured by roll yield, to be best suited to measure the impact of financialization.  
We analyze the pricing dynamics over the different periods by first studying the time series pricing performance of the various factors on all the US traded commodities with the factors constructed using the latter set of commodities. The market based factor outperforms the other three in the first period while the CHP factor shows the greatest improvement in performance in the second period with a four-fold increase in pricing performance. The performance of the market factor is driven by agricultural commodities and metals in both the first and second period and the dramatic improvement of the CHP factor in the second period is driven by precious and precious-base metals. The best performing commodities for the market factor exhibited approximately the same level of price co-movement both before and during financialization. In contrast, the best performing commodities for the CHP factor exhibited very low pair-wise correlation in the first period, around the average for US traded commodities, while during financialization the average pairwise correlation between the top performing CHP factor commodities is higher than that for the market factor and double of the average for all the US traded commodities. This increase is due to the dramatic rise in average pairwise correlation amongst the US traded metals all of which exhibited high R^2^ with respect to the CHP factor during financialization which in turn is due to their common low level of CHP over this period. Thus the CHP factor model is able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialization.  
We explore this issue further by constructing the four factors with the top eight commodities for a given factor (factor picks) in each period^[See section \ref{methods} for further details.] and evaluating their performance on these selected commodities as well as on all US traded commodities. The results of this exercise strongly suggest that the hedging pressure co-movement and price co-movement link was concentrated in the metals sub-sector.

The UK traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialization. To that end, we examine the performance of the four factors on the six UK metals, when constructed from each set of factor picks. The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our hedging pressure based model.

The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in pricing dynamics. Returns on both US and UK traded commodities fell dramatically over both the third and fourth periods with the pattern of return for the US traded commodities across \textbf{CHP} regimes reverting to the Keynesian paradigm. The pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as strong evidence of cross-market linkages.

Commodity financialization raised societal concerns, leading to legislative action intended to alter the nature and functioning of these markets. The debate was initially framed around adequacy of speculation, the burning issue of the day, and the consequent analysis focused on the more mechanical effects of financialization. With the benefit of hindsight, it appears this approach was perhaps too narrow and it now seems necessary to address financialization from a broader perspective. Commodity price dynamics appear to have altered substantially in quite different ways over the financialization and the financial crisis periods and our commodity futures based asset pricing approach seems able to provide new insights into the nature of these changes: financialization was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and mainly concentrated in a specific sector (metals) while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of global commodities. We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialization on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2014, @EkelandSpeculationcommodityfutures2016, @goldstein_commodity_2017 as well as @le_futures_2017, one of the few empirical studies on the impact of financialization on commodity-price cross-moments.] and demonstrate that the effects of financialization extend beyond the mechanical effects induced by indexation as outlined in @basak_model_2016 as well as @tang_index_2012.

# Data & methods {#data-methods}

## Background {#background}

The period from 1998 to 2008 saw an influx of investment into commodity index linked products most of which made its way into the commodity futures market. Exposure to commodity indexes whose goal was to track the broad movement of commodity prices could be accessed by means of exchange traded funds and exchange traded notes and at least \$100 billion of new investment flowed into these products over the 1998-2008 period with this financialization phenomenon leading to substantial legislative changes. Concerns over the consequences of financialization were behind Rule 76 FR 4752 issued by the US Commodity Futures Trading Commission (CFTC) on January 26^th^, 2011. This provision emanates from the Dodd-Frank Wall Street and Consumer Protection Act of 2010 (Title VII, Section 737) that mandates the CFTC to use position limits to restrict the flow of speculative capital into a number of commodity markets. The Rule was approved in a close 3-2 vote and the ensuing rulemaking process was extremely contentious with several commissioners (Michael Dunn and Scott D. O’Malia in particular) expressing reservations about the lack of supporting evidence and the Rule also triggering thousands of comment letters as well as a lawsuit against the CFTC spearheaded by two Wall Street trade groups, the International Swaps & Derivatives Association (ISDA) and the Securities Industries & Financial Markets Association (SIFMA)^[ISDA & SIFMA v US CFTC; Complaint, 1:11-cv-02146; December 2^nd^, 2011.].

A world-wide debate has ensued about the role of index funds in commodity markets. The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs [@de_schutter_food_2010_1; @gilbert_speculative_2010; @herman_not_2011_1; @schumann_hunger-makers_2011; @unctad_global_2009]. The US and various european countries also became involved in this issue. Early US Senate investigations drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US wheat markets to the observed surges in both futures and cash prices [@masters_testimony_2008; @masters_accidental_2008]. This contention has since come to be known as the Masters’ hypothesis and was largely endorsed by the final US Senate report on the issue [@USSenate_Excessive_speculation_wheat_2009]. At this stage, the question thrust on the academic sphere was whether “excessive speculation” (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices. A number of academic studies, most of which used commodity specific causality and correlation based analysis have disproved this contention, particularly in the case of agricultural and energy commodities. @irwin_devil_2009, @sanders_adequacy_2010, @sanders_impact_2011, @sanders_new_2011, @irwin_commodity_2013, @brunetti_commodity_2014, @hamilton_effects_2015 and @bruno_financialization_2017 study the agricultural markets. @buyuksahin_speculators_2011, @tokic_speculation_2012, @fattouh_role_2013, @kilian_role_2014, @knittel_simple_2016 and @manera_modelling_2016 study the energy markets. @bohl_does_2013_2, @kim_does_2015 and @boyd_prevalence_2016 study both energy and agricultural markets while @irwin_index_2011, @irwin_financialization_2012 and @stoll_commodity_2011 study the commodity markets in general.

Other studies have underlined various alterations in commodity pricing dynamics over the period. @gilbert_role_2014 reject the view that financialization has not had any effects in the grains markets and demonstrate that trades originated by financial actors, and specifically index investors, can move prices but tend typically to be volatility-reducing. @cheng_financialization_2014 show that in the case of index commodities, financialization has transformed the risk sharing, and information discovery functions of commodity futures markets. @juvenal_speculation_2015 contend that the oil price increase between 2004 and 2008 was mainly driven by the strength of global demand but that the financialization process of commodity markets also played a role. @henderson_new_2015 show that non-information-based financial investments have important impacts on commodity prices.

## Data {#data}

Commodity index funds (CIFs), commodity based exchange traded funds (ETFs) and notes (ETNs) as well as commodity linked notes (CLNs) were amongst the main investment vehicules that allowed institutional and retail investors to build up commodity exposure in the early 2000s [@boons_stock_2012; @henderson_new_2015; @irwin_index_2011; @unctad_global_2009; @schumann_hunger-makers_2011]. Most of these products were primarily designed to track prominent commodity indexes amongst which the S&P-GSCI, the most popular. Most of its constituents at the time of writting form the basis of the broad cross-section of commodities that we consider in this study^[See section \ref{assets} for details on the commodity pool considered.]. Unleaded gasoline, the NYMEX legacy contract for gasoline stopped trading in 2006 when it was replaced by Reformulated Gasoline Blendstock for Oxygen Blending (RBOB) with the two futures series trading alongside for most of the year. For our NYMEX gasoline data series, we consider unleaded gasoline up to September 1^st^, 2006 and RBOB gasoline thereafter, date at which liquidity for the latter overtook that for the former.

The commodity futures trading commission (CFTC) operates a comprehensive system of collecting information on market participants known as the large trader reporting program (LTRP) where it records and reports to the public market position data on market particpants who have position levels in excess of a particular futures market specific threshold^[Current reporting level thresholds available at: [www.ecfr.gov](https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=&SID=970471b8455f4bab7db4110cfde50731&mc=true&r=SECTION&n=se17.1.15_103).]. The commission collects market data and position information daily from clearing members, futures commission merchants (FCMs) and foreign brokers and publishes corresponding summaries weekly in a series of market specific reports. In these reports, individual traders are categorised according to the nature of their trading activity on the basis of self-reported information^[CFTC form 40. Available at: [www.cftc.gov](https://www.cftc.gov/sites/default/files/idc/groups/public/@forms/documents/file/cftcform40.pdf).] that is subject to review by CFTC staff for reasonableness. Position information is then aggregated by category and asset type with each report providing an aggregation for a set of report specific categories and, for each category, a breakdown between futures only positions and positions in futures and options combined.  
In its legacy report, the commitment of trader report (COT) with data dating back to 1962, the CFTC distinguishes "commercial" and "non-commercial" market participants where a "commercial" participant is defined as one "[...] engaged in business activities hedged by the use of futures and option markets"^[See [CFTC regulation 1.3, 17 CFR 1.3(z)](https://www.gpo.gov/fdsys/pkg/CFR-1998-title17-vol1/xml/CFR-1998-title17-vol1-sec1-3.xml) for details.]. A third category, "non-reportable", aggregates positions for participants not meeting the reporting threshold. In response to concerns related to category accuracy^[See for example @ederington_who_2002.] the CFTC now refines its classification in the disaggregated commitment of trader report (DCOT) where participant categories include "Producer/Merchant/Processor/User", "Swap dealer", "Money manager" and "Other reportable" as well as in the supplemental commitment of trader report (SCOT) that details commodity index trader aggregate positions for thirteen agricultural commodity futures markets. Data for DCOT and SCOT dates back to 2006 and 2007 respectively.  
We study the 1997/2017 period where we observe futures only position data from the COT report, the only CFTC report with data available for the whole period of interest; as well as futures term structure price and open interest data from Bloomberg.

## Methods {#methods}

On the one hand, futures markets have a long history of serving commodity producers to allievate their commodity price and output risks. @keynes_treatise_1930 and @hicks_value_1939 emphasise the "normal" behaviour of naturally short hedgers outsourcing their commodity risk to naturally long commodity specialist speculators. This market configuration is referred to as "backwardation" where futures is expected to trade at a discount to spot, providing speculators with incentives to take the long side. The opposite market paradigm is referred to as "contango". Working [@working_theory_1948; @working_hedging_1953] and Cootner [@cootner_returns_1960; @CootnerSpeculationhedging1967] somehow relax this "supply-of-speculative-services" [@Tilllongtermperspectivecommodity2007] approach by introducing processors and merchants, also commodity experts, on the hedgers side and relating the notions of backwardation and contango more directly to the term structure via the theory of storage where the shape of the front end of the term structure (basis) is directly related to the market price of storage.  
Financialization, on the other hand, refers to the entry of financial investors into the commodity futures markets who, for the most part, are not commodity experts. Besides, these new market participants tend to exhibit herding like behaviour, often taking massive long-only positions on the whole cross-section of indexed commodities in an attempt to hedge against inflation and/or seek further diversification benefits for portfolios with, in most cases, existing large positions across various asset classes [@brunetti_speculators_2016; @boyd_prevalence_2016; @cheng_convective_2014; @juvenal_speculation_2015; @singleton_investor_2013; @tang_index_2012]. This contrasts with the traditional approaches of Keynes and Working and in this context the issues of co-movement and aggregate market participants behaviour seem particularly relevant.  
Asset pricing techniques are well suited to study co-movement. Building on theory we develop an ad-hoc commodity based asset pricing framework that we believe is well adapted to study these two issues simultaneously and implement it over four periods of interest. The first, the pre-financialization period, starts in 1997 and is naturally followed by financialization, spanning the 2004/2007 period, and the financial crisis and its aftermath, spanning the 2008/2013 period. The last period spans the 2014/present period starting with the beginning of the tapering/end of the US Quantitative Easing program (QE).  
Using the weekly price, open interest and market position data described above we construct market portfolios of commodity nearby futures as well as mimicking portfolios for market, commercial hedging pressure, term structure and liquidity risk factors in returns. While our market portfolios are long only, equally weighted portfolios of particular commodity sets, our other mimicking portfolios for risk factors are constructed as combinations of two sub-portfolios (legs), one held long, one held short, which respective constituents are pooled on a weekly basis according to risk factor specific criterias. The weekly return for a particular mimicking portfolio is calculated as the difference between the average return for constituents of the long portfolio and that for the constituents of the short portfolio. i.e, return on the mimicking portfolio for risk factor $i$ ($f_{i}$) for week $t$:

$$r_{t}^{f_{i}}=\frac{1}{x}\sum_{j=1}^{x}r_{j,t}-\frac{1}{x}\sum_{j=n-x}^{n}r_{j,t}$$
$n\equiv$ number of commodities in the set considered for mimicking portfolio construction.  
$x = \left \lceil n \cdot s \right \rceil$  
$s\equiv$ selection threshold ($\frac{1}{3}$ here).  
$r_{j,t}=\frac{C_{j,t}}{C_{j,t-1}}-1$  
$C_{j,t}\equiv$ week $t$ close price for commodity $j$.  
$j\equiv$ commodity rank in the ordered set $Y_{t}^{f_{i}}$.  
$Y_{t}^{f_{i}}\equiv$ week $t$ ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is factor specific ($f_{i}$).

For our portfolio CHP (commercial hedging pressure), we sort the set of commodities considered on past twenty six-week average CHP from lowest to highest. The bottom third constituents (lowest $\overline{CHP}$s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg:

$$Y_{t}^{CHP}\equiv\left \{ \left \{ \overline{CHP_{1}}, \overline{CHP_{2}}, ..., \overline{CHP_{n}} \right \}, \leq \right \}$$

$\overline{CHP_{j}}=\frac{1}{26}\sum_{k=0}^{25}\frac{L_{j,t-k}}{L_{j,t-k}+S_{j,t-k}}$  
$L_{j,t}\equiv$ number of long positions held by commercial hedgers for week $t$ on the futures series of commodity $j$.  
$S_{j,t}\equiv$ number of short positions held by commercial hedgers for week $t$ on the futures series of commodity $j$.

For our portfolio TS (term structure), we sort the set of commodities considered on past twenty six-week average roll-yield from highest to lowest. The bottom third constituents (highest $\overline{RY}$s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg:

$$Y_{t}^{TS}\equiv\left \{ \left \{ \overline{RY_{1}}, \overline{RY_{2}}, ..., \overline{RY_{n}} \right \}, \geq \right \}$$

$\overline{RY_{j}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{F_{j,t-k}^{1}}{F_{j,t-k}^{2}} - 1)$   
$F_{j,t}^{1}\equiv$ week $t$ close price for commodity $j$ first nearby futures contract.  
$F_{j,t}^{2}\equiv$ week $t$ close price for commodity $j$ second nearby futures contract.

For our portfolio OI (open interest), we sort the set of commodities considered on past twenty six-week average aggregate open interest growth from highest to lowest. The bottom third constituents (highest $\overline{\mathbf{OI}^{\Delta \%}}$s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg.

$$Y_{t}^{OI}\equiv\left \{ \left \{ \overline{\mathbf{OI}_{1}^{\Delta \%}}, \overline{\mathbf{OI}_{2}^{\Delta \%}}, ..., \overline{\mathbf{OI}_{n}^{\Delta \%}} \right \}, \geq \right \}$$

$\overline{\mathbf{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{\mathbf{OI}_{j,t-k}}{\mathbf{OI}_{j,t-k-1}} - 1)$  
$\mathbf{OI}_{j,t}=\sum_{k=1}^{l_{j,t}}OI_{j,t,k}$  
$OI_{j,t,k}\equiv$ open interest at close of week $t$ for the $k^{th}$ nearby contract on the futures term structure for commodity $j$.  
$l_{j,t}\equiv$ length of commodity $j$'s futures term structure on week $t$ close.

We use a time series regression approach where we start with regressions of the US traded individual commodity weekly front returns on returns to the mimicking portfolio for a particular risk factor where the portfolio is constructed using the whole cross-section of US traded commodities. The corresponding adjusted $R^{2}$s are averaged and the process is repeated for each of our four risk factors (market, hedging pressure, term structure and liquidity) and periods (1997/2003, 2004/2007, 2008/2013 and 2014/2017). i.e, average adjusted $R^{2}$ for risk factor $i$ ($f_{i}$) over period $t$:

$$\overline{\tilde{R}_{f_{i},t}^{2}}=\frac{1}{24}\sum_{j=1}^{24}\tilde{R}_{j,t}^{2}$$
$\tilde{R_{j}^{2}}=1-(1-R_{j}^{2})\frac{T-1}{T-p-1}$^[The Wherry formula-1.]  
$T\equiv$ length of period $t$ (number of weeks here).  
$p\equiv$ number of regressors (1 here).  
$R_{j,t}^{2}=1-\frac{\sum_{k=1}^{T}(y_{j,k}-\hat{y_{j,k}})^{2}}{\sum_{k=1}^{T}(y_{j,k}-\overline{y_{j}})^{2}}$  
$y_{j,t}\equiv$ week $t$ nearby return for commodity $j$.   
$\hat{y_{j,t}}=\beta_{0}+\beta_{1}f_{i,t}+\epsilon$  
$\beta s \equiv$ classic OLS coefficient estimates.  
$f_{i,t}\equiv$ week $t$ return on mimicking portfolio for risk factor $f_{i}$

The same operation is repeated for the two ($p=2$) and three ($p=3$) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectively, as well as for the four ($p=4$) factor model case where all the risk factor mimicking portfolios are included. Results are reported for the one-factor model case with the other results available from the authors upon request.  
For each period we also implement the analysis described above over periods of low and high aggregate CHP (\textbf{CHP}), a notion which we introduce in this study and which we believe is particularly relevant in the context of financialization where issues of co-movement and aggregate market participants' behaviour play a central role. We define \textbf{CHP} as the cross-sectional average of CHPs for a particular pool of assets. i.e, Week $t$ \textbf{CHP} for asset pool $x$:

$$\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}$$
$n\equiv$ number of commodities in set $x$.  
$CHP_{i,t}\equiv$ week $t$ CHP for commodity $i$ as defined above.

We further define aggregate backwardation (\textbf{backwardation}) and contango (\textbf{contango}) \textbf{CHP} regimes as, for a given period, \textbf{CHP} levels below and above the period's median respectively and, in contrast with [@hong_what_2012] who aggregate across sub-sectors, the asset pool we consider for \textbf{CHP} construction include the whole cross-section of US traded commodities.

In the next part of the analysis, our mimicking portfolios for risk factors, constructed from the set of all US traded commodities are used as commodity picking devices on the latter commodity set. For each risk factor and period, individual US traded commodity front returns are regressed on returns for the corresponding mimicking portfolio. Individual commodities are sorted by adjusted $R^{2}$ ($\tilde{R^{2}}$) accordingly from highest to lowest and the bottom third (highest $\tilde{R^{2}}$s) are selected as commodity picks for the risk factor for the period. i.e, set of picks $P_{t}^{f_{i}}$ for risk factor $i$ ($f_{i}$) over period $t$:

$$P_{t}^{f_{i}}\equiv\left \{ P_{1}, P_{2}, ..., P_{x} \right \}$$
$x = \left \lceil n \cdot s \right \rceil$  
$n\equiv$ number of commodities in the set considered for the picking excersise (twenty-four here).  
$s\equiv$ selection threshold ($\frac{1}{3}$ here).  
$P_{j}\equiv$ commodity pick $j$ for risk factor $f_{i}$ over period $t$  
$j\equiv$ rank in the ordered set $Y_{t}^{f_{i}}$  
$$Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}$$
$n\equiv$ number of commodities in the set considered for picking (twenty-four here).   
$\tilde{R_{j}^{2}}\equiv$  risk factor $f_{i}$ returns' explanatory power on commodity $j$ nearby futures returns over period $t$ as defined above.

For each period and \textbf{CHP} regime we record the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every sets of picks.

In the last part of the analysis, for each period our mimicking portfolios for risk factors in returns are constructed using each set of commodity picks independently as the asset pool for portfolio construction. A similar time series approach to that described above is then implemented using these newly formed mimicking portfolios. In this case, a first set of dependent variables includes the sets of commodity picks themselves, a second set includes the whole cross-section of US traded commodities while a third set includes the six UK traded metals considered. The latter are also used as dependent variables in the last series of regressions where the long and short legs of the newly formed risk factor mimicking portfolios described above are considered separately as regressors.

# Results & discussion

The descriptive statistics over the various time periods for our two sets of commodities (US and non-US) as well as the four factors considered are shown in Table \ref{table1}. The traditional Keynesian hedging pressure paradigm postulates a negative relationship between the return on an individual commodity and its hedging pressure. Financialization has been seen as a cross-sectional commodity market phenomenon; this naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure. The extended Keynesian hedging pressure paradigm should also imply that returns for individual commodities should be high in periods where \textbf{CHP} is low and vice et versa.  
In table \ref{table2} the mean returns are shown over high (\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP} regimes for each time period. Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of \textbf{backwardation} as compared to \textbf{contango}, with the difference being statistically significant at the 5% level for one commodity and for the remaining six commodities the higher mean return during \textbf{contango} is not statistically significant for any of them. For the six UK commodities, all metals, four of them had higher mean returns during phases of \textbf{backwardation} as compared to \textbf{contango} in the first period, with one of these differences being statistically significant at the 5% level while for the remaining two the higher mean return during \textbf{contango} is not statistically significant for either. An equally weighted portfolio of the twenty-four US commodities had a mean return of 10.98% during \textbf{backwardation} phases, statistically significant at the 1% level, and a mean return of 0.93% during \textbf{contango}, both in the first period, with the difference between them statistically significant at the 5% level. The corresponding figures for an equally weighted portfolio of the UK metals were 8.35% and -1.71%, the difference again statistically significant at the 5% level. These results provide broad support for an aggregate version of the Keynesian hedging pressure hypothesis and suggests that hedgers in the aggregate were engaged in risk transfer during this period.  
Over the second period the pattern essentially reverses. For the twenty-four US commodities over this period, eighteen have higher mean returns during phases of \textbf{backwardation} over \textbf{contango}, with the difference statistically significant for four commodities and of the remaining seven the higher mean return during \textbf{backwardation} is statistically significant for one commodity. All of the six UK metals achieved higher mean returns over \textbf{backwardation} than \textbf{contango} with the difference being statistically significant for one commodity. The equally weighted US portfolio had a mean return of 11.16% over \textbf{backwardation} while it was 26.68% during \textbf{contango}, the first statistically significant at the 5% level and the second at the 1% level, with the difference statistically significant at the 1% level. The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 6.43% during \textbf{backwardation} rising to 41.22% during \textbf{contango}, with the difference also significant at the 1% level.  
Thus the onset of financialization seems to have engendered a change in the nature of hedger’s behaviour in the aggregate, taking it away from risk shifting, the traditional Keynesian view. This phenomenon has been noted in earlier theoretical and empirical work [@DanthineInformationfuturesprices1978; @stout_why_1998] in different context from which two competing models of behaviour have emerged. The information arbitrage model implies that hedgers may often be seeking out counterparties to trade with rather than being purely passive. This issue is also raised in both @cheng_financialization_2014 and @StulzRethinkingriskmanagement1996 who point out that hedgers may be taking a view on prices just as speculators do. In fact, by hedging away some of their risk, hedgers are able to speculate more heavily based on their disagreement against speculators regarding futures price movement [@SimsekSpeculationrisksharing2013], which fits into a heterogenous expectation theory of speculation. As @stout_why_1998 points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves the speculators as this form of trading is regarded as non-productive^[@DuffieChallengespolicytreatment2014 also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.]. In the second model hedgers are seen as liquidity providers as in @Kangtaletwopremiums2017. This explanation is also consistent with the nature of financialization which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.

The average time series pricing performance of the various one factor models on the US traded assets over the four periods is shown in Table \ref{table3}. Over the first period the market factor has the best average time series performance with the highest average adjusted R^2^ with all three futures market factors performing poorly and the overall pricing performance consistent across periods of high and low \textbf{CHP} (below period median). The two factor models average R^2^s (results available upon request) are roughly the sum of the one factor R^2^s indicating that the factors are almost orthogonal over this period. The onset of financialization leads to a substantial improvement in the performance of the CHP factor with its average R^2^ increasing to 5.4% in the second period relative to 1.4% in the first. The performance of the market factor also improves though not by as much in a relative sense (18.6% from 12.2%). Both the term structure factor and the open interest growth factor show a much smaller improvement in pricing performance. Over all periods, all of our factor models show similar pricing performance across regimes of high and low \textbf{CHP}.

We next investigate the top eight of the US traded commodities which achieved the highest time series R^2^ for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \ref{table4}. For the CHP factor the commodities that achieve high R^2^ in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor. The same applies to the open interest and term structure factors with CHP replaced by open interest growth and roll yield respectively; while for the market factor the picks are those that co-vary most strongly with the market factor over that period. For the CHP factor, we observe a change in the picks between the first and the second period; the picks in the first period included five agricultural commodities and three metals while in the second period include all of the five base and precious metals and only three agricultural commodities. This pattern is also visible for the term structure factor for which there are four metals (gold, copper, palladium and platinum) picks in the second period against three in the first (gold, palladium and platinum). The market factor has two metal picks in the second period (palladium and silver) while all of the picks in the first period were agricultural or energy commodities. Over the third period, the average CHP factor has four metal picks while both the term structure factor and market factor have three. Table \ref{table4} also shows the proportion of time that these picks were constituents of the corresponding factor. All of the picks of the long-short factors (average CHP, open interest growth and term structure factors) were constituents of the corresponding factor for some proportion of time in all of the time periods. In this respect, there is a contrast between the first and second periods for the average CHP with the picks appearing predominantly on the long side in the second period, as opposed to both legs in the first. This indicates that the picks in the second period consistently exhibited low CHP. This behaviour continued over the third period.

In table \ref{table5}, we show the average pairwise correlation between each set of picks in each time period. This exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement. In the first period, the average CHP factor picks pairwise correlation is similar to the average across the US traded twenty-four commodities (around 0.1) with the market factor picks showing the highest figure (0.21). In the second period however it is the highest (0.27), comparable with the market (0.26) and double of the US traded commodities average (0.13). This increase is a consequence of the dramatic increase in average pairwise price correlation amongst the US traded metals, all of which are CHP factor picks. Taken together with the fact that four of these metals had consistently low CHP, we see that CHP co-movement in the second period is strongly correlated with price co-movement. It is also interesting to note that US traded metals returns were negatively correlated with the rest of US traded commodities in the first period and positively in the second (results available upon request).

In order to further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their pricing performance on these sets of picks. The results are shown in table \ref{table6}. The long-short factors for a particular attribute select the top and bottom three of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks. In the absence of price co-movement between the picks, this market factor will achieve an average R^2^ of around 12.5%^[Market factor lemma: $\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv$ size of market portfolio (eight here). See section \ref{market-factor-lemma} for a formal proof.], while there is no non-zero R^2^ lower bound for the corresponding long-short factors. A high average R^2^ for the market factor is indicative of strong price co-movement while for the long-short factors it is indicative of simultaneous attribute and price co-movement. The most dramatic change in pricing performance occurs for the average CHP factor picks where the market factor built from these picks has an average R^2^ of 21.3% in the first period and jumps to 37.4% in the second period indicating much high co-movement. The average CHP factor built with average CHP factor picks also shows a sharp increase in pricing performance over the second period. There is also substancial improvement in pricing performance of the CHP factor built with term structure picks (3.4% vs. 21.2%)^[In contrast to the market factor, there is no pricing performance lower bound for the CHP factor built with a set of picks.], providing evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialization. In table \ref{table7} we assess the performance of the same factors on all the commodities instead of just the picks. While the average R^2^s are expectedly lower, the relative performance of the market factors built with different sets of picks is similar to table \ref{table6}. In contrast, the increase in R^2^ for the average CHP factor built with average CHP factor picks is lower indicating that the link between CHP co-movement and price co-movement is strongest amongst the picks which are predominantly metals.  
The results from Tables \ref{table6} and \ref{table7} show that the onset of financialization seems to have had a major impact on the dynamics of US traded precious and precious-base metals and we now seek to analyse whether this phenomenon is true for the non-US metal futures. To that end we examine the pricing performance of the factors used in Table \ref{table6} on the six UK metals futures. The results are reported in Table \ref{table8}. In the first period, the average R^2^s across the board are always less than 4.5%. In the second period we see a dramatic increase in R^2^ for the market factor built with average CHP factor picks and average term structure factor picks (4.48% to 25.1% and 1.3% to 20.6% respectively) showing dramatically higher co-movement between UK traded metals and the corresponding picks all of which are US traded commodities. The increase in R^2^ for the market factor built with market factor picks is much more modest, providing further evidence of concentration of co-movement in the metal sector during financialization.

In order to understand this better, in table \ref{table9}, we examine the pricing performance of both long and short legs of the corresponding factors separately on the same set of UK traded metals. The most striking result here is the dramatic increase in R^2^ for the long leg of the term structure factor built with CHP factor picks which achieves the highest overall R^2^ in the second period (1.91% vs. 27.37%). This provides further evidence that global metals co-movement could be detected by US based factor models that combined the Keynesian and Working’s notions of backwardation.

We then turn our analysis to the crisis and post-crisis period (2008-2013). In table \ref{table1} we see that the returns on both US and non-US commodities fall dramatically over this period, going down to -4.3% for the UK metals and 8% for the US traded commodities although volatility for both sets of assets is similar to that during the second period. Two of the UK metals have negative mean returns over the third period compared to one over the first and none over the second. This trend continues in from 2014 to 2017 with the US traded commodities recording an average mean return of -0.6% and the UK metals an average of 4.9% over this period, with fourteen US traded commodities and one UK metal having negative mean returns. The volatility of both sets of assets is lower than over the 2004-2007 period, particularly for the UK metals, suggesting the impact of the investment outflows from the commodity futures markets has had a much lower impact on volatility than the corresponding inflows witnessed over the financialization period. The market factor dominates pricing performance over this period with an increase of mean average R^2^ of over 50% while that for the other factors increases slightly at best (table \ref{table3}). From table \ref{table5} we see that there is an across the board increase in pairwise correlations with a doubling in the average pairwise correlation of all US traded commodities and a levelling in the pairwise correlation of the picks of the three long-short factors. Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities. This is clearly evident in the performance of the market factor built with any set of picks on the entire set of US traded commodities (table \ref{table7}) as we see a dramatic rise across the board in pricing performance. Table \ref{table8} provides further evidence of systematic linkages, in this case between US and non-US traded commodities as the market factor built with its own picks (US traded commodities) achieves an average R^2^ of 33.7% on the UK metals compared to 9.9% in the previous period.

# Conclusion

In the early 2000s, against a backdrop of a low yield environment and poor stock market performance, a combination of financial innovation^[Tradable commodity price indexes (commonly referred to as commodity index funds or CIFs), and commodity-based exchange traded funds (ETFs) were the main financial innovations which allowed the large global banks to offer commodity investment products to institutional and retail investors. In 1991 Goldman Sachs created the S&P-GSCI which provides investors with buy-side exposure to commodities via the OTC swap market and thus without having to participate in the formal futures markets with their position limit restrictions. At this stage these restrictions still applied to the bank though, as it hedged its commodity swap exposure in the futures markets. The first commodity-based ETFs were created through buying physical precious metals with gold and silver ETFs offered as early as 2002/2003. The regulatory hurdle here related to the licensing of commodity trading professionals. Typically, investors had to sign a statement with their broker stating that they understood the risks of commodity investments; a rather inconvenient paperwork for a product designed to trade like a stock, as set forth by a number of industry players at the time.] and deregulation^[In 2000, the Commodity Futures Modernization Act (CFMA) granted non-agricultural commodity futures statutory exemption from regulation (“Enron loophole”) while it required that agricultural commodity derivatives be traded on a CFTC-regulated exchange. Notwithstanding, the CFTC classified swap dealers as “bona fide” hedgers, granting them position limits exemption (“swap dealer loophole”).  
In 2005, the CFTC waived the rule that required commodity investors to sign a statement saying they understood the risks, letting the funds replace it with their prospectus and thus unleashed commodity-based ETFs investments.] led to a large inflow of institutional and financial capital into the commodity futures markets. This process known as financialization lead to a heated public policy debate about whether the increase in open interest and trading volume in commodities exerted upward pressure on prices. Perhaps in response to this, most of the early studies focused on the more mechanical effects of financialization, relying on commodity specific causality and correlation based analysis. With the benefit of hindsight this focus appears to have been too narrow and it seems important to analyze the effects of financialization from a broader perspective which we do in this study. We consider the entire cross-section of actively traded commodities on futures markets and use a futures based asset pricing framework that includes factors constructed using both price and non-price attributes. Factor model techniques are well suited to isolating common driving factors and detecting co-movement, a central issue in financialization which we believe the existing literature has not fully analyzed. Our analysis suggests that financialization was a phenomenon endogenous to the commodity markets transmitted via the futures markets and appears to have had the deepest impact on global metal futures markets. The onset of the financial crisis and the monetary policy regimes that followed appear to have also induced significant changes in commodity pricing dynamics and our analysis suggests that in contrast with financialization, the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of global commodities.

\newpage
```{r `mean returns`}

table.tb <- tables.tb %>%
  dplyr::filter(name == "table 1") %>%
  dplyr::select(table) %>%
  tidyr::unnest(table)

caption.v <- "\\label{table1} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study. Figures labelled *** (**, *) are significant at the 1\\% (5\\%, 10\\%) level. See section \\ref{methods} for more details."

kable(table.tb, 
      align = c(rep('l', 2L), rep('r', 4L)),
      digits = getOption("digits"),
      booktabs = TRUE,
      longtable = TRUE,
      linesep = "",
      caption = caption.v) %>%
  kableExtra::kable_styling(full_width = TRUE, font_size = 10L) %>%
  kableExtra::column_spec(1L, width = "5cm") %>%
  kableExtra::column_spec(2L, width = "2cm")

```

\newpage
```{r `mean returns - aggregate CHP regimes`}
table.tb <- tables.tb %>%
  dplyr::filter(name == "table 2") %>%
  dplyr::select(table) %>%
  tidyr::unnest(table)

caption.v <- "\\label{table2} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study. For each period the results are shown for \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently. Figures labelled *** (**, *) are significant at the 1\\% (5\\%, 10\\%) level. See section \\ref{methods} for more details."

kable(table.tb, 
      align = c(rep('l', 3L), rep('r', 4L)), 
      digits = getOption("digits"), 
      booktabs = TRUE, 
      longtable = TRUE, 
      linesep = "",
      caption = caption.v) %>% 
  kableExtra::landscape() %>% 
  kableExtra::kable_styling(latex_options = "repeat_header",
                            repeat_header_method = "replace",
                            repeat_header_text = "continued",
                            font_size = 10L,
                            full_width = TRUE) %>% 
  kableExtra::column_spec(1L, width = "5cm") %>% 
  kableExtra::column_spec(2L, width = "2cm")
```

\newpage
```{r `factor regressions`}
table.tb <- tables.tb %>%
  dplyr::filter(name == "table 3") %>%
  dplyr::select(table) %>%
  tidyr::unnest(table)

caption.v <- "\\label{table3} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models. The dependent variables are individual nearby futures returns on the commodities forming the entire cross-section of US traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using whole set of US traded commodities considered. For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged. For each period, the models are implemented over the whole period, as well as over \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently. See section \\ref{methods} for more details."

kable(table.tb, 
      align = c(rep('l', 3L), rep('r', 4L)), 
      digits = getOption("digits"), 
      booktabs = TRUE, 
      longtable = TRUE, 
      linesep = "",
      caption = caption.v) %>% 
  kableExtra::kable_styling(font_size = 10L, full_width = TRUE) %>% 
  kableExtra::column_spec(1L, width = "3cm") %>% 
  kableExtra::column_spec(2L, width = "3cm") %>% 
  kableExtra::column_spec(3L, width = "2cm")
```

\newpage
```{r `factor picks`}
table.tb <- tables.tb %>%
  dplyr::filter(name == "table 4") %>%
  dplyr::select(table) %>%
  tidyr::unnest(table)

caption.v <- "\\label{table4} For each risk factor and period, this table displays the list of corresponding commodity factor picks along with the proportion of time they are individually held on the long and short legs of the corresponding risk factor mimicking portfolio. The factor portfolios are constructed from the whole set of the twenty four US traded commodities considered which is also used as asset pool for the commodity picking exercise. See section \\ref{methods} for more details."

kable(table.tb, 
      align = c(rep('l', 3L), rep('r', 2L)), 
      digits = getOption("digits"), 
      booktabs = TRUE, 
      longtable = TRUE, 
      linesep = "",
      caption = caption.v) %>% 
  kableExtra::kable_styling(latex_options = "repeat_header",
                            repeat_header_method = "replace",
                            repeat_header_text = "continued",
                            font_size = 10L,
                            full_width = TRUE) %>%
  kableExtra::column_spec(3L, width = "3.5cm")
```

\newpage
```{r correlations}
table.tb <- tables.tb %>%
  dplyr::filter(name == "table 5") %>%
  dplyr::select(table) %>%
  tidyr::unnest(table)

caption.v <- "\\label{table5} This table displays the average pairwise nearby futures returns correlations for various sets of commodities including the multiple sets of risk factor commodity picks, the whole cross-section of US traded commodities considered in the study, the latter with metals omitted, and the cross-section of US traded metals. For each period and commodity set the correlations are calculated independently over the whole period as well as over \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes. See section \\ref{methods} for more details."

kable(table.tb, 
      align = c(rep('l', 2L), rep('r', 4L)), 
      digits = getOption("digits"), 
      booktabs = TRUE, 
      longtable = TRUE, 
      linesep = "",
      caption = caption.v) %>% 
  kableExtra::kable_styling(font_size = 10L, full_width = TRUE) %>% 
  kableExtra::column_spec(1L, width = "5cm") %>% 
  kableExtra::column_spec(2L, width = "2cm")
```

\newpage
```{r `factor pick regressions - picks:picks`}
table.tb <- tables.tb %>%
  dplyr::filter(name == "table 6") %>%
  dplyr::select(table) %>%
  tidyr::unnest(table)

caption.v <- "\\label{table6} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models. The dependent variables are individual nearby futures returns on risk factors commodity picks while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in table \\ref{table4}. For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged. For each period, the models are implemented over the whole period, as well as over \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently. See section \\ref{methods} for more details."

kable(table.tb, 
      align = c(rep('l', 3L), rep('r', 4L)), 
      digits = getOption("digits"), 
      booktabs = TRUE, 
      longtable = TRUE, 
      linesep = "",
      caption = caption.v) %>% 
  kable_styling(latex_options = "repeat_header", 
                repeat_header_method = "replace", 
                repeat_header_text = "continued", 
                font_size = 10L, 
                full_width = TRUE) %>% 
  kableExtra::column_spec(1L, width = "3cm") %>% 
  kableExtra::column_spec(2L, width = "3cm") %>% 
  kableExtra::column_spec(3L, width = "2cm")

```

\newpage
```{r `factor pick regressions - picks: US commos`}
table.tb <- tables.tb %>%
  dplyr::filter(name == "table 7") %>%
  dplyr::select(table) %>%
  tidyr::unnest(table)

caption.v <- "\\label{table7} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models. The dependent variables are individual nearby futures returns on the commodities forming the entire cross-section of US traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in table \\ref{table4}. For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged. For each period, the models are implemented over the whole period, as well as over \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently. See section \\ref{methods} for more details."

kable(table.tb, 
      align = c(rep('l', 3L), rep('r', 4L)), 
      digits = getOption("digits"), 
      booktabs = TRUE, 
      longtable = TRUE, 
      linesep = "",
      caption = caption.v) %>% 
  kableExtra::kable_styling(latex_options = "repeat_header", 
                repeat_header_method = "replace", 
                repeat_header_text = "continued", 
                font_size = 10L, 
                full_width = TRUE) %>% 
  kableExtra::column_spec(1L, width = "3cm") %>% 
  kableExtra::column_spec(2L, width = "3cm") %>% 
  kableExtra::column_spec(3L, width = "2cm")

```

\newpage
```{r `factor pick regressions - picks: UK commos`}
table.tb <- tables.tb %>%
  dplyr::filter(name == "table 8") %>%
  dplyr::select(table) %>%
  tidyr::unnest(table)

caption.v <- "\\label{table8} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models. The dependent variables are individual nearby futures returns on the six LME traded metals considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in Table \\ref{table4}. For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged. For each period, the models are implemented over the whole period, as well as \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently. See section \\ref{methods} for more details."

kable(table.tb, 
      align = c(rep('l', 4L), rep('r', 4L)), 
      digits = getOption("digits"), 
      booktabs = TRUE, 
      longtable = TRUE, 
      linesep = "",
      caption = caption.v) %>% 
  kableExtra::kable_styling(latex_options = "repeat_header", 
                repeat_header_method = "replace", 
                repeat_header_text = "continued", 
                font_size = 10L, 
                full_width = TRUE) %>% 
  kableExtra::column_spec(1L, width = "3cm") %>% 
  kableExtra::column_spec(2L, width = "3cm") %>% 
  kableExtra::column_spec(3L, width = "2cm")
```

\newpage
```{r `factor pick regressions - picks: UK commos - legs`}
table.tb <- tables.tb %>%
  dplyr::filter(name == "table 9") %>%
  dplyr::select(table) %>%
  tidyr::unnest(table)

caption.v <- "\\label{table9} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models. The dependent variables are individual nearby futures returns on the six LME traded metals considered in the study while the regressors are returns on the long and short legs of mimicking portfolios for risk factors considered independently, where the factor portfolios are constructed using the corresponding set of risk factor commodity picks. For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged. For each period, the models are implemented over the whole period, as well as over \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently. See section \\ref{methods} for more details."

kable(table.tb, 
      align = c(rep('l', 4L), rep('r', 4L)), 
      digits = getOption("digits"), 
      booktabs = TRUE, 
      longtable = TRUE, 
      linesep = "",
      caption = caption.v) %>% 
  kableExtra::landscape() %>% 
  kableExtra::kable_styling(latex_options = "repeat_header", 
                repeat_header_method = "replace", 
                repeat_header_text = "continued", 
                font_size = 10L, 
                full_width = TRUE) %>% 
  kableExtra::column_spec(1L, width = "3cm") %>% 
  kableExtra::column_spec(2L, width = "3cm") %>% 
  kableExtra::column_spec(4L, width = "2cm")

```

# Appendix

## Assets {#assets}

```{r `appendix - assets`}
caption.v <- "This table shows details on the individual commodities considered in this study including trading country, sector, subsector as well as trading exchange Market Identifier Codes (MIC, ISO 10383)."

tickers.tb %>%
  dplyr::filter(Market == TRUE, Asset_class == "Commodity") %>%
  dplyr::select(Country, Sector, Subsector, Exchange, Name) %>%
  dplyr::arrange(desc(Country), Sector, Subsector, Exchange, Name) %>%
  kable(., align = rep('l', 5L),
        digits = getOption("digits"),
        booktabs = TRUE,
        longtable = TRUE,
        linesep = "",
        caption = caption.v) %>%
  kableExtra::kable_styling(full_width = TRUE, font_size = 10L) %>%
  kableExtra::column_spec(1L, width = "3cm") %>%
  kableExtra::column_spec(2L, width = "3cm")

```

\newpage

## Market factor lemma {#market-factor-lemma}

$$\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}$$
$\overline{R_{mkt, p}^{2}}\equiv$ period $p$ average $R^{2}$ for market risk factor returns.  
$R_{j, mkt, p}^{2}\equiv$ period $p$ $R^{2}$ for the regression where the dependent variable is the vector of returns on commodity $j$ nearby contract and the regressor is the vector of returns on the market portfolio; $j \in Y_{p}^{mkt}$.  
$Y_{p}^{mkt}\equiv$ commodity set considered for the formation of the mimicking portfolio for market risk over period $p$.  
$n\equiv$ number of commodities in $Y_{p}^{mkt}$.

__Proof__

Week $t$ market factor return:
$$r_{mkt, t} = \sum_{j} w_{j, p} \cdot r_{j, t}$$
$w_{j, p}\equiv$ period $p$ weight for commodity $j$ in the mimicking portfolio for market risk in returns.  
$r_{j, t}\equiv$ week $t$ return for commodity $j$.

Assumptions:

\begin{math}
  \begin{aligned}
   w_{j, p} &= w_{k, p} = \frac{1}{n} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt} \\
   \sigma_{r_{j}, p} &= \sigma_{r_{k}, p} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt} \\
   cov \left ( r_{j}, r_{k} \right )_{p} &= 0 \: \forall \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt}
  \end{aligned}
\end{math}

\newpage

$$
\begin{array}{l c l}
  \sigma_{r_{j, p}}^{2} & = & \beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2} + \sigma_{\epsilon}^{2} \\
  \beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2} & = & \sigma_{r_{j, p}}^{2} - \sigma_{\epsilon}^{2} \\
  \frac{\beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2}}{\sigma_{r_{j, p}}^{2}} & = & \frac{\sigma_{r_{j, p}}^{2} - \sigma_{\epsilon}^{2}}{\sigma_{r_{j, p}}^{2}} \\
    \frac{\beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2}}{\sigma_{r_{j, p}}^{2}}  & = & R_{r_{j}, r_{mkt}, p}^{2} \\ \\
  \sigma_{r_{mkt, p}}^{2} & = & \sum_{j} w_{j, p}^{2} \cdot \sigma_{j, p}^{2} + 2 \cdot \sum_{j} \sum_{k \neq j} w_{j, p} \cdot w_{k, p} \cdot cov \left ( r_{j, p}, r_{k, p} \right ) \\
                          & = & \sum_{j} \left ( \frac{1}{n} \right )^{2} \cdot \sigma_{j, p}^{2} \\
                          & = & \frac{\sum_{j} \sigma_{j, p}^{2}}{n^{2}} \\ \\
  cov \left ( r_{j}, r_{mkt} \right )_{p} & = & cov \left ( r_{j}, \frac{1}{n} \sum_{k} r_{k} \right )_{p} \\
                                          & = & \frac{1}{n} \sum_{k} cov \left ( r_{j}, r_{k} \right )_{p} \\
                                          & = & \frac{1}{n} cov \left ( r_{j}, r_{j} \right )_{p} \\
                                          & = & \frac{\sigma_{r_{j}, p}^{2}}{n} \\ \\
  \beta_{j, mkt, p}^{2} & = & \left [ \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}}{\sigma_{r_{mkt, p}}^{2}} \right ]^{2} \\
                        & = & \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}^{2}}{\sigma_{r_{mkt, p}}^{4}} \\ \\
  \beta_{j, mkt, p}^{2} \cdot  \sigma_{r_{mkt, p}}^{2}  & = & \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}^{2}}{\sigma_{r_{mkt, p}}^{2}} \\
                                                        & = & \left ( \frac{\sigma_{r_{j}, p}^{2}}{n} \right )^{2} \cdot \frac{1}{\sigma_{r_{mkt, p}}^{2}} \\
                                                        & = & \frac{\sigma_{r_{j}, p}^{4}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\ \\
\end{array}
$$

\newpage

$$
\begin{array}{l c l}
  R_{r_{j}, r_{mkt}, p}^{2} & = & \frac{\sigma_{r_{j}, p}^{4}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \cdot \frac{1}{\sigma_{r_{j, p}}^{2}} \\
                            & = & \frac{\sigma_{r_{j}, p}^{2}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\ \\  
                            & \therefore  & \\ \\
  \overline{R_{r_{mkt}, p}^{2}} & = & \frac{1}{n} \sum_{j} \frac{\sigma_{r_{j}, p}^{2}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\
                                & = & \frac{1}{n} \cdot \frac{1}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \cdot \sum_{j} \sigma_{r_{j}, p}^{2} \\
                                & = & \frac{1}{n} \cdot \frac{\sum_{j} \sigma_{r_{j}, p}^{2}}{n^{2} \cdot \frac{1}{n^{2}} \cdot \sum_{j} \sigma_{r_{j}, p}^{2}} \\
                                & = & \frac{1}{n} \\
\end{array}
$$

\newpage

### 2024-06-11 others/paper/custom/anonymous.tex
Track 'others' folder

--- 2024-06-11 others/paper/custom/LaTeX/main.tex
@@
-\documentclass[11pt, letterpaper, doublespacing]{article}
-
-\usepackage{setspace}
-
-\makeatletter
-
-\renewcommand{\@seccntformat}[1]{\@nameuse{the#1}.~{}}
-
-\renewcommand{\thesection}{\Roman{section}}
-\renewcommand{\thesubsection}{\Alph{subsection}}
-\renewcommand{\thesubsubsection}{\arabic{subsubsection}}
-
-\renewcommand{\section}{\@startsection {section}{1}{\z@}%
-  {-3.5ex \@plus -1ex \@minus -.2ex}%
-  {2.3ex \@plus.2ex}%
-  {\centering\normalfont\large\bfseries}}
-
-\renewcommand{\subsection}{\@startsection{subsection}{2}{\z@}%
-  {-3.25ex\@plus -1ex \@minus -.2ex}%
-  {1.5ex \@plus .2ex}%
-  {\normalfont\large\slshape}}
-
-\renewcommand{\subsubsection}{\@startsection{subsubsection}{3}{\z@}%
-  {-3.25ex\@plus -1ex \@minus -.2ex}%
-  {1.5ex \@plus .2ex}%
-  {\centering\normalfont\slshape}}
-
-\makeatother
-
-% \newtheoremstyle{plain}{9pt}{9pt}{\itshape}{0pt}{\scshape}{:}{3pt}{}
-
-% \theoremstyle{plain}
-
-% \newtheorem{assumption}{Assumption}
-% \newtheorem{corollary}{Corollary}
-% \newtheorem{definition}{Definition}
-% \newtheorem{lemma}{Lemma}  
-% \newtheorem{proposition}{Proposition}
-% \newtheorem{remark}{Remark}
-% \newtheorem{theorem}{Theorem}
-
-% \usepackage[bf,small,nooneline,normal]{caption}
-% \renewcommand*{\captionlabeldelim}{\nobreak}
-% \renewcommand*\captionlabeldelim{.}
-% \renewcommand{\captionfont}{\bfseries}
-
-\renewcommand{\thetable}{\Roman{table}}
-
-\usepackage{indentfirst}
-
-\renewcommand{\abstractname}{\bf \small ABSTRACT}
-
-\renewcommand{\refname}{\bf \small REFERENCES}
-
-\usepackage{endnotes}
-\renewcommand{\footnote}{\endnote}
-\renewcommand{\notesname}{\bf Footnotes}
-
+\documentclass[12pt,]{article}
 \usepackage{lmodern}
@@
 }{}
-\usepackage[margin=1in]{geometry}
+\usepackage[letterpaper, left = 1in, right = 1in, top = 1.5in, bottom = 1.5in]{geometry}
 \usepackage{hyperref}
 \hypersetup{unicode=true,
-            pdftitle={Financialization of commodities: an asset pricing perspective},
-            pdfauthor={Devraj Basu, Olivier Bautheac},
-            pdfkeywords={Financialization of commodities, futures contracts in agricultural
-commodities, speculative bubbles, volume, open interest, convenience
-yield.},
+            pdftitle={Financialization of Commodities: an Asset Pricing Perspective},
+            pdfkeywords={Commodity futures; financialization; hedging pressure; financial crisis},
             pdfborder={0 0 0},
@@
 \bibliographystyle{jf}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 \IfFileExists{parskip.sty}{%
@@
 
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-  \title{Financialization of commodities: an asset pricing perspective}
-  \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-  \author{Devraj Basu, Olivier Bautheac}
-  \preauthor{\centering\large\emph}
-  \postauthor{\par}
+  \title{Financialization of Commodities: an Asset Pricing Perspective}
+    \author{}
     \date{}
-  \predate{}\postdate{}
-
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage[table]{xcolor}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-
-\usepackage{caption}
-\usepackage{setspace}
+
+\usepackage{longtable, tabu, pdflscape, booktabs, caption, setspace}
 \doublespacing
+\renewcommand*{\arraystretch}{0.65}
 
@@
 commodity futures pricing dynamics using commodity asset pricing
-techniques. We consider both futures market based factors and the
-traditional market factor and find that a hedging pressure based factor
-is able to best detect the effects of commodity financialization while
-the effects of the financial crisis and after are most clearly visible
-through the performance of the market factor. The futures market seems
-to have been the main channel for the effects of commodity
-financialization, which seems to have delivered an exogenous schock to
-the cross-section of global commodities.
+techniques. We find that a non-price based factor is best able to detect
+the effects of commodity financialization, while the effects of the
+financial crisis and after are most clearly visible through the
+performance of the market factor. The effects of financialization seem
+to go beyond mechanical effects induced by the rise of indexing. 
+\newline
+JEL: G11, G23, G13, Q02
+\newline
+Keywords: Commodity futures, financialization, hedging pressure, financial crisis
+
 \end{abstract}
@@
 
-\section{Introduction}\label{introduction}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 regulatory, and academic spheres. A vigorous legislative debate has led
-to regulatory changes\footnote{Concerns over the consequences of
-  financialization were behind Rule 76 FR 4752 issued by the U.S.
-  Commodity Futures Trading Commission (CFTC) on January 26, 2011. This
-  provision emanates from the Dodd-Frank Wall Street and Consumer
-  Protection Act of 2010 (Title VII, Section 737) that mandates the CFTC
-  to use position limits to restrict the flow of speculative capital
-  into a number of commodity markets. The Rule was approved in a close
-  3-2 vote and the ensuing rulemaking process was extremely contentious
-  with several commissioners (Michael Dunn and Scott D. O'Malia in
-  particular) expressing reservations about the lack of supporting
-  evidence and the Rule also triggering thousands of comment letters as
-  well as a lawsuit against the CFTC spearheaded by two Wall Street
-  trade groups, namely the International Swaps \& Derivatives
-  Association (ISDA) and the Securities Industries \& Financial Markets
-  Association (SIFMA) (ISDA \& SIFMA v U.S. CFTC; Complaint,
-  1:11-cv-02146; December 2, 2011).} accompanied by an equally intense
-policy and academic debate across a number of disciplines about the
-perceived effects on commodity prices of the unprecedented inflow of
-institutional funds brought into commodity futures markets by new index
-type investors\footnote{The first responses to the 2007/2008 crisis of
-  escalating food and energy prices took the form of policy reports,
-  many of which reasoned that the growth of commodity index funds came
-  along with an influx of largely speculative capital that was
-  responsible for driving commodity prices beyond their historic highs
-  \citep{de_schutter_food_2010_1, gilbert_speculative_2010, herman_not_2011_1, schumann_hunger-makers_2011, unctad_global_2009}.}.
-In response to immediate policy concerns, the academic debate was
-initially framed rather narrowly\footnote{Early U.S. Senate
-  investigations drew on pricing and trading data supplied by the CFTC
-  as well as interviews with numerous experts including hedge fund
-  manager Michael Masters who linked the growing presence of index
-  investors in U.S. wheat markets to the observed surges in both futures
-  and cash prices
-  \citep{masters_testimony_2008, masters_accidental_2008}. This
-  contention has since come to be known as the Masters' hypothesis and
-  was largely endorsed by the final U.S. Senate report on the issue
-  \citep{USSenate_Excessive_speculation_wheat_2009}. At this stage, the
-  question thrust on the academic sphere was whether ``excessive
-  speculation'' (understood as the peculiar market activity of index
-  type investors) was linked to escalating energy and agricultural
-  commodity prices.} and used a fairly restricted set of statistical
-techniques\footnote{Most of the studies focused on statistical analyses
-  of the Granger type causal connections between ``excessive
-  speculation'' and commodity prices.}.
-
-In this paper we take a fundamentally different empirical approach that
-is broader in scope. We consider the entire cross-section of actively
-traded commodities on futures markets and use a futures based asset
-pricing framework that includes factors constructed using both price and
-non-price attributes. Factor model techniques are well suited to
-isolating common driving factors and detecting co-movement, a central
-issue in financialization which we believe the existing literature has
-not fully analyzed.\\
+to regulatory changes accompanied by an equally intense policy and
+academic debate across a number of disciplines about the perceived
+effects on commodity prices of the unprecedented inflow of institutional
+funds brought into commodity futures markets by new index type
+investors\footnote{See section \ref{background} for a detailled
+  discussion.}. In response to immediate policy concerns the academic
+debate was initially framed rather narrowly. In this paper we take a
+fundamentally different empirical approach that is broader in scope. We
+consider the entire cross-section of actively traded commodities on
+futures markets and use a futures based asset pricing framework that
+includes factors constructed using both price and non-price attributes.
+
+Commodity futures markets have a history of being the classic physical
+commodity risks shifting conduit for commodity specialists, and
+financialization may have altered this long standing paradigm with the
+entry of long only commodity index traders (CITs) with very different
+hedging and volume demands from traditional participants. This change
+could have altered the hedging ontology in these markets and our asset
+pricing framework is well suited to detect these more subtle effects
+driven by changes in the nature of traders. Factor models are well
+suited to isolating common driving factors and detecting co-movement and
+building on theory we develop a bespoke commodity-based asset pricing
+framework that seems well adapted to study these two issues
+simultaneously.
+
 The first factor model we consider (CHP) is based on the well-known
@@
 
-We study the performance of these models on a set of twenty-four U.S.
-traded commodities and six non-U.S. traded (LME traded) industrial
-metals over the 1997/2017 period that we divide into four distinct
-sub-periods. The first, the pre-financialization phase, spans the
-1997/2003 period; the second, the financialization phase, spans the
-2004/2007 period\footnote{Starting point based on earlier studies
-  \citep{baker_financialization_2014, christoffersen_factor_2014}.}; the
+We study the performance of these models on a set of twenty-four US
+traded commodities and six UK traded (LME exchange) base metals over the
+1997/2017 period that we divide into four distinct sub-periods. The
+first, the pre-financialization phase, spans the 1997/2003 period; the
+second, the financialization phase, spans the 2004/2007 period\footnote{Starting
+  point based on earlier studies
+  \citep{baker_financialization_2014, christoffersen_factor_2018}.}; the
 third, 2008/2013, encompasses both the financial crisis and the loose
@@
 starting in 2014 to present.\\
-Consistent with earlier studies, we observe that mean returns for the
-U.S. traded commodities are sharply higher over the financialization
-period compared to pre-financialization and this pattern extends to LME
-traded metals.
-
-The cross-sectional nature of financialization
-\citep{basak_model_2016, cheng_financialization_2014} leads us to
-extends the Keynesian indivudal hedging pressure paradigm by
-incorporating aggregate CHP (\(\mathbf{CHP}\)), a market wide measure of
-hedging pressure. This paradigm implies that returns for individual
-commodities should be high in periods where \(\mathbf{CHP}\) is low
-(\(\mathbf{backwardation}\)) and low in periods where \(\mathbf{CHP}\)
-is high (\(\mathbf{contango}\)) vice et versa. Over the first period the
-cross sectional average returns during \(\mathbf{backwardation}\) for
-both the US and UK commodities are positive with those for the US
+Consistent with earlier studies, we observe that mean returns for the US
+traded commodities are sharply higher over the financialization period
+compared to pre-financialization and this pattern extends to UK traded
+metals.
+
+The arrival of financial investors raises the question of whether they
+functioned as liquidity providers or liquidity demanders. Arguments have
+been made for both sides with \citet{moskowitz_time_2012} arguing that
+financial investors provide liquidity while
+\citet{Kangtaletwopremiums2017} argue that they demand liquidity with
+\citet{cheng_convective_2014} showing that they in fact transferred risk
+to hedgers during the 2008 financial crisis. We study this issue by
+extending the Keynesian individual hedging pressure paradigm by
+incorporating aggregate CHP (\textbf{CHP}), a market wide measure of
+hedging pressure first considered in \citet{hong_what_2012}. Our use of
+this measure is motivated by the cross sectional nature of
+financialization
+\citep{basak_model_2016, cheng_convective_2014, le_futures_2017}. This
+paradigm implies that returns for individual commodities should be high
+in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in
+periods where \textbf{CHP} is high (\textbf{contango}). Over the first
+period the cross sectional average returns during \textbf{backwardation}
+for both the US and UK commodities are positive with those for the US
 statistically significant, and significantly higher than during
-\(\mathbf{contango}\), providing broad support for an aggregate version
-of the Keynesian hedging pressure hypothesis. Over the second period
-this pattern reverses, with both the US and UK commodities having
-significant positive returns during \(\mathbf{contango}\) with these
-returns being significantly higher than during
-\(\mathbf{backwardation}\). This change in pattern suggests that the
-onset of financialization altered the traditional risk shifting nature
-of hedger's behaviour, which is implied by the Keynesian hypothesis.
-
+\textbf{contango}, providing broad support for an aggregate version of
+the Keynesian hedging pressure hypothesis. Over the second period this
+pattern reverses, with both the US and UK commodities having significant
+positive returns during \textbf{contango} with these returns being
+significantly higher than during \textbf{backwardation}. This change in
+pattern suggests that the onset of financialization altered the
+traditional risk shifting nature of hedger's behaviour implied by the
+Keynesian hypothesis and suggests that financial investors may have been
+liquidity demanders during financialization leading hedgers to become
+liquidity providers.
+
+\citet{goldstein_commodity_2017} as well as
+\citet{goldstein_speculation_2014} argue that the arrival of financial
+investors has an impact on the extent of normal backwardation in
+commodity futures markets. Based on their analysis we would expect our
+average CHP factor, which is based on backwardation measured by hedger's
+positions, as well our term structure factor, which is based on
+backwardation measured by roll yield, to be best suited to measure the
+impact of financialization.\\
 We analyze the pricing dynamics over the different periods by first
 studying the time series pricing performance of the various factors on
-all the U.S. traded commodities with the factors constructed using the
+all the US traded commodities with the factors constructed using the
 latter set of commodities. The market based factor outperforms the other
-three in the first period and it has a similar level of performance in
-the second period, while the CHP factor shows the greatest improvement
-in performance in the second period. The performance of the market
-factor is driven by agricultural commodities and metals in both the
-first and second period and the dramatic improvement of the CHP factor
-in the second period is driven by precious and precious industrial
-metals. The best performing commodities for the market factor exhibited
-approximately the same level of price co-movement both before and during
-financialization. In contrast, the best performing commodities for the
-CHP factor exhibited very low pair-wise correlation in the first period,
-around the average for U.S. traded commodities, while during
-financialization the average pairwise correlation between the top
-performing CHP factor commodities is higher than that for the market
-factor and double of the average for all the U.S. traded commodities.
-This increase is due to the dramatic rise in average pairwise
-correlation amongst the U.S. traded metals all of which exhibited high
-R\textsuperscript{2} with respect to the CHP factor during
-financialization which in turn is due to their common low level of CHP
-over this period. Thus the CHP factor model is able to establish the
-strengthening link between a non-price attribute and price dynamics in
-the U.S. metal sub-sector during financialization.\\
+three in the first period while the CHP factor shows the greatest
+improvement in performance in the second period with a four-fold
+increase in pricing performance. The performance of the market factor is
+driven by agricultural commodities and metals in both the first and
+second period and the dramatic improvement of the CHP factor in the
+second period is driven by precious and precious-base metals. The best
+performing commodities for the market factor exhibited approximately the
+same level of price co-movement both before and during financialization.
+In contrast, the best performing commodities for the CHP factor
+exhibited very low pair-wise correlation in the first period, around the
+average for US traded commodities, while during financialization the
+average pairwise correlation between the top performing CHP factor
+commodities is higher than that for the market factor and double of the
+average for all the US traded commodities. This increase is due to the
+dramatic rise in average pairwise correlation amongst the US traded
+metals all of which exhibited high R\textsuperscript{2} with respect to
+the CHP factor during financialization which in turn is due to their
+common low level of CHP over this period. Thus the CHP factor model is
+able to establish the strengthening link between a non-price attribute
+and price dynamics in the US metal sub-sector during financialization.\\
 We explore this issue further by constructing the four factors with the
 top eight commodities for a given factor (factor picks) in each
-period\footnote{See section 2.2 for further details.} and evaluating its
-performance on these selected commodities as well as on all U.S. traded
-commodities. The logic of this exercise is to determine the extent to
-which the pricing performance of these factors in each period is
-concentrated in a subset of commodities. The CHP and the market factors
-built from CHP factor picks exhibit the most dramatic increase in
-pricing performance on the corresponding factor picks in the second
-period. In contrast, the increase in pricing performance on all the U.S.
-traded commodities is roughly uniform across all sets of factor models
-and lower in magnitude. This strongly suggests that the hedging pressure
-co-movement and price co-movement link was concentrated in the metals
-sub-sector. There is also a dramatic improvement in pricing performance
-of the CHP factor built with term structure picks indicating convergence
-between Keynesian and Working's theories of the futures term structure
-in a U.S. context.
-
-The LME traded industrial metals provide a useful set of assets to test
-how widespread were the changes in pricing dynamics brought about by the
+period\footnote{See section \ref{methods} for further details.} and
+evaluating their performance on these selected commodities as well as on
+all US traded commodities. The results of this exercise strongly suggest
+that the hedging pressure co-movement and price co-movement link was
+concentrated in the metals sub-sector.
+
+The UK traded base metals provide a useful set of assets to test how
+widespread were the changes in pricing dynamics brought about by the
 onset of financialization. To that end, we examine the performance of
-the four factors on the six LME metals, when constructed from each set
-of factor picks. The performance of the market factor built with the CHP
-and term structure factor picks improves dramatically in the second
-period relative to the first while the performance of all factors built
-with the other sets of picks does not increase quite as much. The
-pricing performance of the market factor built with CHP factor picks as
-well as that of the CHP factor built with both CHP and term structure
-factor picks show a dramatic increase over the financialization period.
-The performance of the market factor built with the CHP factor picks
-suggests that there was co-movement in global metals returns in the
-second period and that this co-movement could be detected by our hedging
-pressure based model while the performance of the CHP factor built with
-term structure factor picks indicates the aforementioned convergence
-between Keynesian and Working's views of commodity futures term
-structure extends to a global context.
-
-Our analysis suggests that financialization appears to have had the
-deepest impact on global metals markets and our commodity asset pricing
-based approach allows us to better understand the channels through which
-it was transmitted. The initial view of financialization was that it
-consisted of speculative flows which had the effect to driving up and
-creating bubble like conditions in commodity future prices\footnote{\citet{de_schutter_food_2010_1};
-  \citet{gilbert_how_2010}; \citet{gilbert_speculative_2010};
-  \citet{masters_testimony_2008}; \citet{masters_accidental_2008};
-  \citet{herman_not_2011_1}; \citet{schumann_hunger-makers_2011};
-  \citet{singleton_investor_2013}; \citet{unctad_global_2009}}. A number
-of academic studies, most of which used commodity specific causality and
-correlation based analysis, have disproved this contention, particularly
-in the case of agricultural and energy commodities\footnote{\citet{irwin_devil_2009},
-  \citet{sanders_adequacy_2010}, \citet{sanders_impact_2011},
-  \citet{sanders_new_2011}, \citet{irwin_commodity_2013},
-  \citet{brunetti_commodity_2014}, \citet{hamilton_effects_2015} and
-  \citet{bruno_financialization_2017} study the agricultural markets.
-  \citet{buyuksahin_speculators_2011}, \citet{tokic_speculation_2012},
-  \citet{fattouh_role_2013}, \citet{kilian_role_2014},
-  \citet{knittel_simple_2016} and \citet{manera_modelling_2016} study
-  the energy markets. \citet{bohl_does_2013_2}, \citet{kim_does_2015}
-  and \citet{boyd_prevalence_2016} study both energy and agricultural
-  markets while \citet{irwin_index_2011},
-  \citet{irwin_financialization_2012} and \citet{stoll_commodity_2011}
-  study the commodity markets in general.}, while other studies have
-underlined various alterations in commodity pricing dynamics over the
-period\footnote{\citet{gilbert_role_2014} reject the view that
+the four factors on the six UK metals, when constructed from each set of
+factor picks. The results show that there was co-movement in global
+metals returns in the second period and that this co-movement could be
+detected by our hedging pressure based model.
+
+The onset of the financial crisis and the monetary policy regimes that
+followed, on the other hand, also appear to have induced significant
+changes in pricing dynamics. Returns on both US and UK traded
+commodities fell dramatically over both the third and fourth periods
+with the pattern of return for the US traded commodities across
+\textbf{CHP} regimes reverting to the Keynesian paradigm. The pricing
+results indicate the emergence of a systematic factor across the entire
+cross-section of the US commodities as well as strong evidence of
+cross-market linkages.
+
+Commodity financialization raised societal concerns, leading to
+legislative action intended to alter the nature and functioning of these
+markets. The debate was initially framed around adequacy of speculation,
+the burning issue of the day, and the consequent analysis focused on the
+more mechanical effects of financialization. With the benefit of
+hindsight, it appears this approach was perhaps too narrow and it now
+seems necessary to address financialization from a broader perspective.
+Commodity price dynamics appear to have altered substantially in quite
+different ways over the financialization and the financial crisis
+periods and our commodity futures based asset pricing approach seems
+able to provide new insights into the nature of these changes:
+financialization was a phenomenon endogenous to the commodity markets
+transmitted via the commodity futures markets and mainly concentrated in
+a specific sector (metals) while the crisis and its aftermath seems to
+have delivered an exogenous shock across the entire cross-section of
+global commodities. We provide an empirical complement to a new stream
+of theoretical studies that try to model the impact of financialization
+on various aspects of commodity futures markets\footnote{\citet{etula_broker-dealer_2013},
+  \citet{acharya_limits_2013}, \citet{cheng_convective_2014},
+  \citet{leclercq_equilibrium_2014}, \citet{sockin_informational_2015},
+  \citet{goldstein_speculation_2014},
+  \citet{EkelandSpeculationcommodityfutures2016},
+  \citet{goldstein_commodity_2017} as well as \citet{le_futures_2017},
+  one of the few empirical studies on the impact of financialization on
+  commodity-price cross-moments.} and demonstrate that the effects of
+financialization extend beyond the mechanical effects induced by
+indexation as outlined in \citet{basak_model_2016} as well as
+\citet{tang_index_2012}.
+
+\hypertarget{data-methods}{%
+\section{Data \& methods}\label{data-methods}}
+
+\hypertarget{background}{%
+\subsection{Background}\label{background}}
+
+The period from 1998 to 2008 saw an influx of investment into commodity
+index linked products most of which made its way into the commodity
+futures market. Exposure to commodity indexes whose goal was to track
+the broad movement of commodity prices could be accessed by means of
+exchange traded funds and exchange traded notes and at least \$100
+billion of new investment flowed into these products over the 1998-2008
+period with this financialization phenomenon leading to substantial
+legislative changes. Concerns over the consequences of financialization
+were behind Rule 76 FR 4752 issued by the US Commodity Futures Trading
+Commission (CFTC) on January 26\textsuperscript{th}, 2011. This
+provision emanates from the Dodd-Frank Wall Street and Consumer
+Protection Act of 2010 (Title VII, Section 737) that mandates the CFTC
+to use position limits to restrict the flow of speculative capital into
+a number of commodity markets. The Rule was approved in a close 3-2 vote
+and the ensuing rulemaking process was extremely contentious with
+several commissioners (Michael Dunn and Scott D. O'Malia in particular)
+expressing reservations about the lack of supporting evidence and the
+Rule also triggering thousands of comment letters as well as a lawsuit
+against the CFTC spearheaded by two Wall Street trade groups, the
+International Swaps \& Derivatives Association (ISDA) and the Securities
+Industries \& Financial Markets Association (SIFMA)\footnote{ISDA \&
+  SIFMA v US CFTC; Complaint, 1:11-cv-02146; December
+  2\textsuperscript{nd}, 2011.}.
+
+A world-wide debate has ensued about the role of index funds in
+commodity markets. The first responses to the 2007/2008 crisis of
+escalating food and energy prices took the form of policy reports, many
+of which reasoned that the growth of commodity index funds came along
+with an influx of largely speculative capital that was responsible for
+driving commodity prices beyond their historic highs
+\citep{de_schutter_food_2010_1, gilbert_speculative_2010, herman_not_2011_1, schumann_hunger-makers_2011, unctad_global_2009}.
+The US and various european countries also became involved in this
+issue. Early US Senate investigations drew on pricing and trading data
+supplied by the CFTC as well as interviews with numerous experts
+including hedge fund manager Michael Masters who linked the growing
+presence of index investors in US wheat markets to the observed surges
+in both futures and cash prices
+\citep{masters_testimony_2008, masters_accidental_2008}. This contention
+has since come to be known as the Masters' hypothesis and was largely
+endorsed by the final US Senate report on the issue
+\citep{USSenate_Excessive_speculation_wheat_2009}. At this stage, the
+question thrust on the academic sphere was whether ``excessive
+speculation'' (understood as the market activity peculiar to index type
+investors) was linked to escalating energy and agricultural commodity
+prices. A number of academic studies, most of which used commodity
+specific causality and correlation based analysis have disproved this
+contention, particularly in the case of agricultural and energy
+commodities. \citet{irwin_devil_2009}, \citet{sanders_adequacy_2010},
+\citet{sanders_impact_2011}, \citet{sanders_new_2011},
+\citet{irwin_commodity_2013}, \citet{brunetti_commodity_2014},
+\citet{hamilton_effects_2015} and \citet{bruno_financialization_2017}
+study the agricultural markets. \citet{buyuksahin_speculators_2011},
+\citet{tokic_speculation_2012}, \citet{fattouh_role_2013},
+\citet{kilian_role_2014}, \citet{knittel_simple_2016} and
+\citet{manera_modelling_2016} study the energy markets.
+\citet{bohl_does_2013_2}, \citet{kim_does_2015} and
+\citet{boyd_prevalence_2016} study both energy and agricultural markets
+while \citet{irwin_index_2011}, \citet{irwin_financialization_2012} and
+\citet{stoll_commodity_2011} study the commodity markets in general.
+
+Other studies have underlined various alterations in commodity pricing
+dynamics over the period. \citet{gilbert_role_2014} reject the view that
 financialization has not had any effects in the grains markets and
-  demonstrate that trades originated by financial actors, and
-  specifically index investors, can move prices but tend typically to be
+demonstrate that trades originated by financial actors, and specifically
+index investors, can move prices but tend typically to be
 volatility-reducing. \citet{cheng_financialization_2014} show that in
-  the case of index commodities, financialization has transformed the
-  risk sharing, and information discovery functions of commodity futures
+the case of index commodities, financialization has transformed the risk
+sharing, and information discovery functions of commodity futures
 markets. \citet{juvenal_speculation_2015} contend that the oil price
 increase between 2004 and 2008 was mainly driven by the strength of
-  global demand but that the financialization process of commodity
-  markets also played a role. \citet{henderson_new_2015} show that
+global demand but that the financialization process of commodity markets
+also played a role. \citet{henderson_new_2015} show that
 non-information-based financial investments have important impacts on
-  commodity prices.}. However, the fundamental question of the nature of
-the impact of financialization on commodity futures markets has not yet
-been completely answered. Our analysis takes a broader perspective and
-shifts the focus away from the energy and agricultural sectors. We
-provide an empirical complement to a new stream of theoretical studies
-that try to model the impact of financialization on various aspects of
-commodity futures markets\footnote{\citet{etula_broker-dealer_2013},
-  \citet{acharya_limits_2013}, \citet{cheng_convective_2014},
-  \citet{leclercq_equilibrium_2014}, \citet{sockin_informational_2015},
-  \citet{goldstein_speculation_2013},
-  \citet{EkelandSpeculationcommodityfutures2016},
-  \citet{goldstein_commodity_2017}.}, as well as extend the empirical
-findings of \citet{basak_model_2016} and \citet{tang_index_2012}. In
-contrast to the earlier purely statistical studies that were designed to
-study speculative behavior alone, our empirical approach allows us to
-isolate the more subtle effects of financialization identified in the
-theoretical studies above.
-
-The onset of the financial crisis and the monetary policy regimes that
-followed appear to have also induced significant changes in pricing
-dynamics. Returns on both U.S. and LME traded commodities fell
-dramatically over both the third and fourth periods with the pattern of
-return for the U.S. traded commodities across \(\mathbf{CHP}\) regimes
-reverting to Keynesian paradigm. The pricing results indicate the
-presence of a systematic factor across the entire cross-section of the
-U.S. commodities as the performance of the market factor built with
-every set of picks on the entire set of U.S. traded commodities shows a
-dramatic rise across the board in pricing performance. There is also
-strong evidence of cross-market linkages as the market factor built with
-its own picks (U.S. traded commodities) shows a six fold increase in
-average R\textsuperscript{2} on the LME metals compared with the
-financialization period. The market factor when built with equity index
-(S\&P 500) picks does even better, providing strong evidence of
-systematic spill-overs from the equity to the commodity markets.
-
-Financialization was an issue of such policy importance that it
-triggered legislative action. The debate was initially framed around
-adequacy of speculation, the burning issue of the day, and the
-consequent analysis focused on the more mechanical effects of
-financialization. With the benefit of hindsight, it appears this
-approach was perhaps too narrow and it now seems necessary to address
-financialization from a broader perspective. Commodity price dynamics
-appear to have altered substantially in quite different ways over the
-financialization and the financial crisis periods and our commodity
-futures based asset pricing approach seems to be able to provide new
-insights into the nature of these changes: financialization was a
-phenomenon endogenous to the commodity markets transmitted via the
-commodity futures markets and mainly concentrated in a specific sector
-(metals) while the crisis and its aftermath seems to have delivered an
-exogenous shock across the entire cross-section of global commodities.
-
-\section{Data \& methods}\label{data-methods}
-
-\subsection{Data}\label{data}
+commodity prices.
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
 
@@
 Most of these products were primarily designed to track prominent
-commodity indexes amongst which the S\&P-GSCI, the most popular. Its
-constituents at the time of writting, all U.S. traded, form the basis of
-the commodity pool we consider in this study where we also include the
-cross-section of the most liquid LME traded metals\footnote{See appendix
-  1 for details on the commodity pool considered.}. Unleaded gasoline,
-the NYMEX legacy contract for gasoline stopped trading in 2006 when it
-was replaced by Reformulated Gasoline Blendstock for Oxygen Blending
-(RBOB) with the two futures series trading alongside for most of the
-year. For our NYMEX gasoline data series, we consider unleaded gasoline
-up to Septembre 1\textsuperscript{st}, 2006 and RBOB gasoline
-thereafter, date at which liquidity for the latter overtook that for the
-former.
+commodity indexes amongst which the S\&P-GSCI, the most popular. Most of
+its constituents at the time of writting form the basis of the broad
+cross-section of commodities that we consider in this study\footnote{See
+  section \ref{assets} for details on the commodity pool considered.}.
+Unleaded gasoline, the NYMEX legacy contract for gasoline stopped
+trading in 2006 when it was replaced by Reformulated Gasoline Blendstock
+for Oxygen Blending (RBOB) with the two futures series trading alongside
+for most of the year. For our NYMEX gasoline data series, we consider
+unleaded gasoline up to September 1\textsuperscript{st}, 2006 and RBOB
+gasoline thereafter, date at which liquidity for the latter overtook
+that for the former.
 
 The commodity futures trading commission (CFTC) operates a comprehensive
-system of collecting information on market participants know as the
+system of collecting information on market participants known as the
 large trader reporting program (LTRP) where it records and reports to
@@
 information is then aggregated by category and asset type with each
-report providing an aggregatetion for a set of report specific
-categories and for each category, a breakdown between futures only
-positions and positions in futures and options combined.\\
+report providing an aggregation for a set of report specific categories
+and, for each category, a breakdown between futures only positions and
+positions in futures and options combined.\\
 In its legacy report, the commitment of trader report (COT) with data
@@
 report (DCOT) where participant categories include
-``Producer/Merhcant/Processor/User'', ``Swap dealer'', ``Money manager''
+``Producer/Merchant/Processor/User'', ``Swap dealer'', ``Money manager''
 and ``Other reportable'' as well as in the supplemental commitment of
 trader report (SCOT) that details commodity index trader aggregate
-positions for thirteen agricultural commodity futures markets.\\
-In this study we consider futures only data over the 1997/2017 period.
-Because DCOT and SCOT data series only date back to 2006 and 2007
-respectively, we rely exclusively on the legacy COT report for market
-position data. Futures market price and open interest data are from
-Bloomberg.
-
-\subsection{Methods}\label{methods}
+positions for thirteen agricultural commodity futures markets. Data for
+DCOT and SCOT dates back to 2006 and 2007 respectively.\\
+We study the 1997/2017 period where we observe futures only position
+data from the COT report, the only CFTC report with data available for
+the whole period of interest; as well as futures term structure price
+and open interest data from Bloomberg.
+
+\hypertarget{methods}{%
+\subsection{Methods}\label{methods}}
 
@@
 exhibit herding like behaviour, often taking massive long-only positions
-on the whole cross-section of indexed commodities in an attempt hedge
+on the whole cross-section of indexed commodities in an attempt to hedge
 against inflation and/or seek further diversification benefits for
@@
 Asset pricing techniques are well suited to study co-movement. Building
-on theory we thus develop an ad-hoc commodity based asset pricing
-framework that we believe is well adapted to study these two issues
-simultaneously and implement it over four periods of interest. The
-first, the pre-financialization period, starts in 1997, the earliest
-year for which LME metals' price data are available on Bloomberg, and is
-naturally followed by financialization, the second, that spans the
-2004/2007 period with the starting year based on earlier studies
-\citep{baker_financialization_2014, christoffersen_factor_2014}. The
-third spans the 2008/2013 period, encompassing both the financial crisis
-and the loose monetary policy that followed, while the fourth spans the
-period starting for the end of this unorthodox monetary policy regime in
-2014 to present.\\
+on theory we develop an ad-hoc commodity based asset pricing framework
+that we believe is well adapted to study these two issues simultaneously
+and implement it over four periods of interest. The first, the
+pre-financialization period, starts in 1997 and is naturally followed by
+financialization, spanning the 2004/2007 period, and the financial
+crisis and its aftermath, spanning the 2008/2013 period. The last period
+spans the 2014/present period starting with the beginning of the
+tapering/end of the US Quantitative Easing program (QE).\\
 Using the weekly price, open interest and market position data described
 above we construct market portfolios of commodity nearby futures as well
-as mimicking portfolios for commercial hedging pressure, term structure
-and liquidity risk factors in returns. While our market portfolios are
-long only, equally weighted portfolios of particular commodity sets, our
-other mimicking portfolios for risk factors are constructed as
-combinations of two sub-portfolios (legs), one held long, one held
-short, which respective constituents are pooled on a weekly basis
-according to risk factor specific criterias. The weekly return for a
-particular mimicking portfolio is calculated as the difference between
+as mimicking portfolios for market, commercial hedging pressure, term
+structure and liquidity risk factors in returns. While our market
+portfolios are long only, equally weighted portfolios of particular
+commodity sets, our other mimicking portfolios for risk factors are
+constructed as combinations of two sub-portfolios (legs), one held long,
+one held short, which respective constituents are pooled on a weekly
+basis according to risk factor specific criterias. The weekly return for
+a particular mimicking portfolio is calculated as the difference between
 the average return for constituents of the long portfolio and that for
@@
 considered for mimicking portfolio construction where the ordering rule
-is specific to \(f_{i}\).
+is factor specific (\(f_{i}\)).
 
@@
 the corresponding ordered set form the long leg of the portfolio while
-the top third form tje short leg:
+the top third form the short leg:
 
@@
 We use a time series regression approach where we start with regressions
-of the U.S. traded individual commodity weekly front returns on returns
-to the mimicking portfolio for a particular risk factor where the
-portfolio is constructed using the whole cross-section of U.S. traded
-commodities. The corresponding adjusted \(R^{2}\)s are averaged and the
-process is repeated for each of our four risk factors (market, hedging
-pressure, term structure and liquidity) and periods (1997/2003,
-2004/2007, 2008/2013 and 2014/2017). i.e, average adjusted \(R^{2}\) for
-risk factor \(i\) (\(f_{i}\)) over period \(t\):
+of the US traded individual commodity weekly front returns on returns to
+the mimicking portfolio for a particular risk factor where the portfolio
+is constructed using the whole cross-section of US traded commodities.
+The corresponding adjusted \(R^{2}\)s are averaged and the process is
+repeated for each of our four risk factors (market, hedging pressure,
+term structure and liquidity) and periods (1997/2003, 2004/2007,
+2008/2013 and 2014/2017). i.e, average adjusted \(R^{2}\) for risk
+factor \(i\) (\(f_{i}\)) over period \(t\):
 
@@
 factor model cases, where regressors include in turn all combinations of
-any two and three risk factors respectivly, as well as for the four
+any two and three risk factors respectively, as well as for the four
 (\(p=4\)) factor model case where all the risk factor mimicking
@@
 For each period we also implement the analysis described above over
-periods of low and high aggregate CHP (\(\mathbf{CHP}\)), a notion that
-we introduce in this study and that we believe is particularly relevant
-in the context of financialization where issues of co-movement and
+periods of low and high aggregate CHP (\textbf{CHP}), a notion which we
+introduce in this study and which we believe is particularly relevant in
+the context of financialization where issues of co-movement and
 aggregate market participants' behaviour play a central role. We define
-\(\mathbf{CHP}\) as the cross-sectional average of CHPs for a particular
-pool of asset. i.e, Week \(t\) \(\mathbf{CHP}\) for asset pool \(x\):
-
-\[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{i=1}^{n}CHP_{i,t}\] \(n\equiv\)
+\textbf{CHP} as the cross-sectional average of CHPs for a particular
+pool of assets. i.e, Week \(t\) \textbf{CHP} for asset pool \(x\):
+
+\[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}\] \(n\equiv\)
 number of commodities in set \(x\).\\
@@
 
-We further define aggregate backwardation (\(\mathbf{backwardation}\))
-and contango (\(\mathbf{contango}\)) \(\mathbf{CHP}\) regimes as, for a
-given period, \(\mathbf{CHP}\) levels below and above the period's
-median respectively.\\
-For the rest of the study, the asset pool used for \(\mathbf{CHP}\)
-construction include the whole cross-section of U.S. traded commodities.
+We further define aggregate backwardation (\textbf{backwardation}) and
+contango (\textbf{contango}) \textbf{CHP} regimes as, for a given
+period, \textbf{CHP} levels below and above the period's median
+respectively and, in contrast with \citep{hong_what_2012} who aggregate
+across sub-sectors, the asset pool we consider for \textbf{CHP}
+construction include the whole cross-section of US traded commodities.
 
 In the next part of the analysis, our mimicking portfolios for risk
-factors, constructed from the set of all U.S. traded commodities are
-used as commodity picking devices on the latter commodity set. For each
-risk factor and period, individual U.S. traded commodity front returns
-are regressed on returns for the corresponding mimicking portfolio.
+factors, constructed from the set of all US traded commodities are used
+as commodity picking devices on the latter commodity set. For each risk
+factor and period, individual US traded commodity front returns are
+regressed on returns for the corresponding mimicking portfolio.
 Individual commodities are sorted by adjusted \(R^{2}\)
@@
 \(n\equiv\) number of commodities in the set considered for the picking
-excersise (24 here).\\
+excersise (twenty-four here).\\
 \(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
@@
 \[Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}\]
-\(n\equiv\) number of commodities in the set considered for picking (24
-here).\\
+\(n\equiv\) number of commodities in the set considered for picking
+(twenty-four here).\\
 \(\tilde{R_{j}^{2}}\equiv\) risk factor \(f_{i}\) returns' explanatory
-power on commodity \(j\) nearby returns over period \(t\) as defined
-above.
-
-For each period and \(\mathbf{CHP}\) regime we record the proportion of
-time each pick is held in the long and (/or) short leg of the
-corresponding risk factor mimicking portfolio as well as the average
-pairwise correlation amongst every sets of picks.
+power on commodity \(j\) nearby futures returns over period \(t\) as
+defined above.
+
+For each period and \textbf{CHP} regime we record the proportion of time
+each pick is held in the long and (/or) short leg of the corresponding
+risk factor mimicking portfolio as well as the average pairwise
+correlation amongst every sets of picks.
 
@@
 case, a first set of dependent variables includes the sets of commodity
-picks themselves, a second set includes the whole cross-section of U.S.
-traded commodities while a third set includes the six LME traded metals
+picks themselves, a second set includes the whole cross-section of US
+traded commodities while a third set includes the six UK traded metals
 considered. The latter are also used as dependent variables in the last
@@
 risk factor mimicking portfolios described above are considered
-separately as regressor.
-
-\section{Results \& discussion}\label{results-discussion}
+separately as regressors.
+
+\hypertarget{results-discussion}{%
+\section{Results \& discussion}\label{results-discussion}}
 
 The descriptive statistics over the various time periods for our two
-sets of commodities (U.S. and non U.S.) as well as the four factors
-considered are shown in Table 1. The traditional Keynesian hedging
-pressure paradigm postulates a negative relationship between the return
-on an individual commodity and its hedging pressure. Financialization
-has been seen as an exogenous cross-sectional commodity market
-phenomenon. This naturally leads us to extend the individual hedging
-pressure paradigm by incorporating aggregate CHP (\(\mathbf{CHP}\)), a
+sets of commodities (US and non-US) as well as the four factors
+considered are shown in Table \ref{table1}. The traditional Keynesian
+hedging pressure paradigm postulates a negative relationship between the
+return on an individual commodity and its hedging pressure.
+Financialization has been seen as a cross-sectional commodity market
+phenomenon; this naturally leads us to extend the individual hedging
+pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a
 market wide measure of hedging pressure. The extended Keynesian hedging
 pressure paradigm should also imply that returns for individual
-commodities should be high in periods where \(\mathbf{CHP}\) is low and
-vice et versa.\\
-In table 2 the mean returns are shown over high (\(\mathbf{contango}\))
-and low (\(\mathbf{backwardation}\)) \(\mathbf{CHP}\) regimes for each
-time period. Over the first period 18 of the 24 US commodities have
-higher mean returns during periods of \(\mathbf{backwardation}\) as
-compared to \(\mathbf{contango}\), with the difference being
-statistically significant at the 5\% level for one commodity and for the
-remaining 6 commodities the higher mean return during
-\(\mathbf{contango}\) is not statistically significant for any of them.
-For the 6 UK commodities, all metals, 4 of them had higher mean returns
-during phases of \(\mathbf{backwardation}\) as compared to
-\(\mathbf{contango}\) in the first period, with one of these differences
+commodities should be high in periods where \textbf{CHP} is low and vice
+et versa.\\
+In table \ref{table2} the mean returns are shown over high
+(\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP}
+regimes for each time period. Over the first period eighteen of the
+twenty-four US commodities have higher mean returns during periods of
+\textbf{backwardation} as compared to \textbf{contango}, with the
+difference being statistically significant at the 5\% level for one
+commodity and for the remaining six commodities the higher mean return
+during \textbf{contango} is not statistically significant for any of
+them. For the six UK commodities, all metals, four of them had higher
+mean returns during phases of \textbf{backwardation} as compared to
+\textbf{contango} in the first period, with one of these differences
 being statistically significant at the 5\% level while for the remaining
-two the higher mean return during \(\mathbf{contango}\) is not
-statistically significant for either. An equally weighted portfolio of
-the 24 US commodities had a mean return of 10.98\% during
-\(\mathbf{backwardation}\) phases, statistically significant at the 1\%
-level, and a mean return of 0.93\% during \(\mathbf{contango}\), both in
-the first period, with the difference between them statistically
-significant at the 5\% level. The corresponding figures for an equally
-weighted portfolio of the UK metals were 8.35\% and -1.71\%, the
-difference again statistically significant at the 5\% level. These
-results provide broad support for an aggregate version of the Keynesian
-hedging pressure hypothesis and suggests that hedgers in the aggregate
-were engaged in risk transfer.\\
-Over the second period the pattern essentially reverses. For the 24 US
-commodities over this period, 18 have higher mean returns during phases
-of \(\mathbf{backwardation}\) over \(\mathbf{contango}\), with the
-difference statistically significant for 4 commodities and of the
-remaining 7 the higher mean return during \(\mathbf{backwardation}\) is
-statistically significant for one commodity. All of the 6 UK metals
-achieved higher mean returns over \(\mathbf{backwardation}\) than
-contango with the difference being statistically significant for one
-commodity. The equally weighted US portfolio had a mean return of
-11.16\% over \(\mathbf{backwardation}\) while it was 26.68\% during
-\(\mathbf{contango}\), the first statistically significant at the 5\%
-level and the second at the 1\% level, with the difference statistically
-significant at the 1\% level. The difference was considerably more
-pronounced for the equally weighted UK metals portfolio with a mean
-return of 6.43\% during \(\mathbf{backwardation}\) rising to 41.22\%
-during \(\mathbf{contango}\), with the difference also significant at
-the 1\% level.\\
+two the higher mean return during \textbf{contango} is not statistically
+significant for either. An equally weighted portfolio of the twenty-four
+US commodities had a mean return of 10.98\% during
+\textbf{backwardation} phases, statistically significant at the 1\%
+level, and a mean return of 0.93\% during \textbf{contango}, both in the
+first period, with the difference between them statistically significant
+at the 5\% level. The corresponding figures for an equally weighted
+portfolio of the UK metals were 8.35\% and -1.71\%, the difference again
+statistically significant at the 5\% level. These results provide broad
+support for an aggregate version of the Keynesian hedging pressure
+hypothesis and suggests that hedgers in the aggregate were engaged in
+risk transfer during this period.\\
+Over the second period the pattern essentially reverses. For the
+twenty-four US commodities over this period, eighteen have higher mean
+returns during phases of \textbf{backwardation} over \textbf{contango},
+with the difference statistically significant for four commodities and
+of the remaining seven the higher mean return during
+\textbf{backwardation} is statistically significant for one commodity.
+All of the six UK metals achieved higher mean returns over
+\textbf{backwardation} than \textbf{contango} with the difference being
+statistically significant for one commodity. The equally weighted US
+portfolio had a mean return of 11.16\% over \textbf{backwardation} while
+it was 26.68\% during \textbf{contango}, the first statistically
+significant at the 5\% level and the second at the 1\% level, with the
+difference statistically significant at the 1\% level. The difference
+was considerably more pronounced for the equally weighted UK metals
+portfolio with a mean return of 6.43\% during \textbf{backwardation}
+rising to 41.22\% during \textbf{contango}, with the difference also
+significant at the 1\% level.\\
 Thus the onset of financialization seems to have engendered a change in
@@
 noted in earlier theoretical and empirical work
-\citep[\citet{stout_why_1998}]{DanthineInformationfuturesprices1978} in
+\citep{DanthineInformationfuturesprices1978, stout_why_1998} in
 different context from which two competing models of behaviour have
@@
 The average time series pricing performance of the various one factor
-models on the U.S. traded assets over the four periods is shown in Table
-3. Over the first period the market factor has the best average time
-series performance with the highest average adjusted
+models on the US traded assets over the four periods is shown in Table
+\ref{table3}. Over the first period the market factor has the best
+average time series performance with the highest average adjusted
 R\textsuperscript{2} with all three futures market factors performing
 poorly and the overall pricing performance consistent across periods of
-high and low \(\mathbf{CHP}\) (below period median). The two factor
-models average R\textsuperscript{2}s (results available upon request)
-are roughly the sum of the one factor R\textsuperscript{2}s indicating
-that the factors are almost orthogonal over this period. The onset of
+high and low \textbf{CHP} (below period median). The two factor models
+average R\textsuperscript{2}s (results available upon request) are
+roughly the sum of the one factor R\textsuperscript{2}s indicating that
+the factors are almost orthogonal over this period. The onset of
 financialization leads to a substantial improvement in the performance
@@
 pricing performance. Over all periods, all of our factor models show
-similar pricing performance across regimes of high and low
-\(\mathbf{CHP}\).
-
-We next investigate the top eight of the U.S. traded commodities which
+similar pricing performance across regimes of high and low \textbf{CHP}.
+
+We next investigate the top eight of the US traded commodities which
 achieved the highest time series R\textsuperscript{2} for the CHP,
 market, open interest and term structure factors, in each of the four
-time periods with the commodity picks shown in Table 4. For the CHP
-factor the commodities that achieve high R\textsuperscript{2} in a given
-period are likely to be those with relatively high or low CHP over that
-period, or those commodities that co-vary with the short or the long
-side of the factor. The same applies to the open interest and term
-structure factors with CHP replaced by open interest growth and roll
-yield respectively; while for the market factor the picks are those that
-co-vary most strongly with the market factor over that period. For the
-CHP factor, we observe a change in the picks between the first and the
-second period; the picks in the first period included five agricultural
-commodities and three metals while in the second period include all of
-the five industrial and precious metals and only three agricultural
-commodities. This pattern is also visible for the term structure factor
-for which there are four metals (gold, copper, palladium and platinum)
-picks in the second period against three in the first (gold, palladium
-and platinum). The market factor has two metal picks in the second
-period (palladium and silver) while all of the picks in the first period
-were agricultural or energy commodities. Over the third period, the
-average CHP factor has four metal picks while both the term structure
-factor and market factor have three. Table 4 also shows the proportion
-of time that these picks were constituents of the corresponding factor.
-All of the picks of the long-short factors (average CHP, open interest
-growth and term structure factors) were constituents of the
-corresponding factor for some proportion of time in all of the time
-periods. In this respect, there is a contrast between the first and
-second periods for the average CHP with the picks appearing
-predominantly on the long side in the second period, as opposed to both
-legs in the first. This indicates that the picks in the second period
-consistently exhibited low CHP. This behaviour continued over the third
-period.
-
-In table 5, we show the average pair wise correlation between each set
-of picks in each time period. This exercise gives an indication of the
-extent to which attribute co-movement reveals price co-movement, which
-is particularly relevant for the long-short factors for which the
+time periods with the commodity picks shown in Table \ref{table4}. For
+the CHP factor the commodities that achieve high R\textsuperscript{2} in
+a given period are likely to be those with relatively high or low CHP
+over that period, or those commodities that co-vary with the short or
+the long side of the factor. The same applies to the open interest and
+term structure factors with CHP replaced by open interest growth and
+roll yield respectively; while for the market factor the picks are those
+that co-vary most strongly with the market factor over that period. For
+the CHP factor, we observe a change in the picks between the first and
+the second period; the picks in the first period included five
+agricultural commodities and three metals while in the second period
+include all of the five base and precious metals and only three
+agricultural commodities. This pattern is also visible for the term
+structure factor for which there are four metals (gold, copper,
+palladium and platinum) picks in the second period against three in the
+first (gold, palladium and platinum). The market factor has two metal
+picks in the second period (palladium and silver) while all of the picks
+in the first period were agricultural or energy commodities. Over the
+third period, the average CHP factor has four metal picks while both the
+term structure factor and market factor have three. Table \ref{table4}
+also shows the proportion of time that these picks were constituents of
+the corresponding factor. All of the picks of the long-short factors
+(average CHP, open interest growth and term structure factors) were
+constituents of the corresponding factor for some proportion of time in
+all of the time periods. In this respect, there is a contrast between
+the first and second periods for the average CHP with the picks
+appearing predominantly on the long side in the second period, as
+opposed to both legs in the first. This indicates that the picks in the
+second period consistently exhibited low CHP. This behaviour continued
+over the third period.
+
+In table \ref{table5}, we show the average pairwise correlation between
+each set of picks in each time period. This exercise gives an indication
+of the extent to which attribute co-movement reveals price co-movement,
+which is particularly relevant for the long-short factors for which the
 corresponding attribute is not directly related to price co-movement. In
-the first period, the average CHP picks pairwise correlation is similar
-to the average across the U.S. traded 24 commodities. In the second
-period however it is the highest, comparable with the market and double
-of the U.S. traded commodities average. This increase is a consequence
-of the dramatic increase in average pairwise price correlation amongst
-the U.S. traded metals, all of which are CHP factor picks. Taken
-together with the fact that four of these metals had consistently low
-CHP, we see that CHP co-movement in the second period is strongly
-correlated with price co-movement. It is also interesting to note that
-U.S. traded metals returns were negatively correlated with the rest of
-U.S. traded commodities in the first period and positively in the second
-(Results available upon request).
-
-In order further understand the link between attribute and price
+the first period, the average CHP factor picks pairwise correlation is
+similar to the average across the US traded twenty-four commodities
+(around 0.1) with the market factor picks showing the highest figure
+(0.21). In the second period however it is the highest (0.27),
+comparable with the market (0.26) and double of the US traded
+commodities average (0.13). This increase is a consequence of the
+dramatic increase in average pairwise price correlation amongst the US
+traded metals, all of which are CHP factor picks. Taken together with
+the fact that four of these metals had consistently low CHP, we see that
+CHP co-movement in the second period is strongly correlated with price
+co-movement. It is also interesting to note that US traded metals
+returns were negatively correlated with the rest of US traded
+commodities in the first period and positively in the second (results
+available upon request).
+
+In order to further understand the link between attribute and price
 co-movement we build all of the factors from every set of factor picks
 and assess their pricing performance on these sets of picks. The results
-are shown in table 6. The long-short factors for a particular attribute
-select the top and bottom three of the corresponding picks based on that
-attribute while the market factor takes an equally weighted combination
-of the eight corresponding picks. In the absence of price co-movement
-between the picks, this market factor will achieve an average
-R\textsuperscript{2} of around 12.5\%\footnote{Market factor lemma:
+are shown in table \ref{table6}. The long-short factors for a particular
+attribute select the top and bottom three of the corresponding picks
+based on that attribute while the market factor takes an equally
+weighted combination of the eight corresponding picks. In the absence of
+price co-movement between the picks, this market factor will achieve an
+average R\textsuperscript{2} of around 12.5\%\footnote{Market factor
+  lemma:
   \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\)
-  size of market portfolio (8 here). See appendix 2 for a formal proof.},
-while there is no non-zero R\textsuperscript{2} lower bound for the
-corresponding long-short factors. A high average R\textsuperscript{2}
-for the market factor is indicative of strong price co-movement while
-for the long-short factors it is indicative of a simultaneous attribute
-and price co-movement. The most dramatic change in pricing performance
-occurs for the average CHP factor picks where the market factor built
-from these picks has an average R\textsuperscript{2} of 21.3 \% in the
-first period (close to the 0 correlation situation) and jumps to 37.4 \%
-in the second period. The average CHP factor built with average CHP
-factor picks also shows a sharp increase in pricing performance over the
-second period. The most striking result is the dramatic improvement in
-pricing performance of the CHP factor built with term structure picks
-(3.4\% vs.~21.2\%)\footnote{In contrast to the market factor, there is
-  no pricing performance lower bound for the CHP factor built with a set
-  of picks.}, providing evidence of convergence of Keynesian and
-Working's theories of the term structure in detecting price co-movement
-during financialization. In table 7 we assess the performance of the
+  size of market portfolio (eight here). See section
+  \ref{market-factor-lemma} for a formal proof.}, while there is no
+non-zero R\textsuperscript{2} lower bound for the corresponding
+long-short factors. A high average R\textsuperscript{2} for the market
+factor is indicative of strong price co-movement while for the
+long-short factors it is indicative of simultaneous attribute and price
+co-movement. The most dramatic change in pricing performance occurs for
+the average CHP factor picks where the market factor built from these
+picks has an average R\textsuperscript{2} of 21.3\% in the first period
+and jumps to 37.4\% in the second period indicating much high
+co-movement. The average CHP factor built with average CHP factor picks
+also shows a sharp increase in pricing performance over the second
+period. There is also substancial improvement in pricing performance of
+the CHP factor built with term structure picks (3.4\%
+vs.~21.2\%)\footnote{In contrast to the market factor, there is no
+  pricing performance lower bound for the CHP factor built with a set of
+  picks.}, providing evidence of convergence of Keynesian and Working's
+theories of the term structure in detecting price co-movement during
+financialization. In table \ref{table7} we assess the performance of the
 same factors on all the commodities instead of just the picks. While the
@@
 performance of the market factors built with different sets of picks is
-similar to table 6. In contrast, the increase in R\textsuperscript{2}
-for the average CHP factor built with average CHP factor picks is lower
-indicating that the link between CHP co-movement and price co-movement
-is strongest amongst the picks which are predominantly metals.\\
-The conclusion from Tables 6 and 7 is that the onset of financialization
-seems to have had a major impact on the dynamics of U.S. traded precious
-and precious industrial metals and we now seek to analyse whether this
-phenomenon is true for the non US metal futures. To that end we examine
-the pricing performance of the factors constructed used in Table 6 on
-the six LME metals futures. The results are reported in Table 8. In the
-first period, the average R\textsuperscript{2} s across the board are
-always less than 4.5\%. In the second period we see a dramatic increase
-in R\textsuperscript{2} for the market factor built with average CHP
-factor picks and average term structure factor picks (4.48\% to 25.1\%
-and 1.3\% to 20.6\% respectively) showing dramatically higher
-co-movement between LME traded metals and the corresponding picks all of
-which are U.S. traded commodities. The increase in R\textsuperscript{2}
-for the market factor built with market factor picks is much more
-modest, providing further evidence of concentration of co-movement in
-the metal sector during financialization.
-
-In order to understand this better, in table 9, we examine the pricing
-performance of both long and short legs of the corresponding factors
-separately on the same set of LME traded metals. The most striking
-result here is the dramatic increase in R\textsuperscript{2} for the
-long leg of the term structure factor built with CHP factor picks which
-achieves the highest overall R\textsuperscript{2} in the second period
-(1.91\% vs.~27.37\%). This provides further evidence that global metals
-co-movement could be detected by US based factor models that combined
-the Keynesian and Working's notions of backwardation.
+similar to table \ref{table6}. In contrast, the increase in
+R\textsuperscript{2} for the average CHP factor built with average CHP
+factor picks is lower indicating that the link between CHP co-movement
+and price co-movement is strongest amongst the picks which are
+predominantly metals.\\
+The results from Tables \ref{table6} and \ref{table7} show that the
+onset of financialization seems to have had a major impact on the
+dynamics of US traded precious and precious-base metals and we now seek
+to analyse whether this phenomenon is true for the non-US metal futures.
+To that end we examine the pricing performance of the factors used in
+Table \ref{table6} on the six UK metals futures. The results are
+reported in Table \ref{table8}. In the first period, the average
+R\textsuperscript{2}s across the board are always less than 4.5\%. In
+the second period we see a dramatic increase in R\textsuperscript{2} for
+the market factor built with average CHP factor picks and average term
+structure factor picks (4.48\% to 25.1\% and 1.3\% to 20.6\%
+respectively) showing dramatically higher co-movement between UK traded
+metals and the corresponding picks all of which are US traded
+commodities. The increase in R\textsuperscript{2} for the market factor
+built with market factor picks is much more modest, providing further
+evidence of concentration of co-movement in the metal sector during
+financialization.
+
+In order to understand this better, in table \ref{table9}, we examine
+the pricing performance of both long and short legs of the corresponding
+factors separately on the same set of UK traded metals. The most
+striking result here is the dramatic increase in R\textsuperscript{2}
+for the long leg of the term structure factor built with CHP factor
+picks which achieves the highest overall R\textsuperscript{2} in the
+second period (1.91\% vs.~27.37\%). This provides further evidence that
+global metals co-movement could be detected by US based factor models
+that combined the Keynesian and Working's notions of backwardation.
 
 We then turn our analysis to the crisis and post-crisis period
-(2008-2013). In table 1 we see that the returns on both U.S. and
-non-U.S. commodities fall dramatically over this period, going down to
--4.3\% for the LME metals and 8\% for the US traded commodities although
+(2008-2013). In table \ref{table1} we see that the returns on both US
+and non-US commodities fall dramatically over this period, going down to
+-4.3\% for the UK metals and 8\% for the US traded commodities although
 volatility for both sets of assets is similar to that during the second
-period. Two of the LME metals have negative mean returns over the third
+period. Two of the UK metals have negative mean returns over the third
 period compared to one over the first and none over the second. This
 trend continues in from 2014 to 2017 with the US traded commodities
-recording an average mean return of -0.6\% and the LME metals an average
+recording an average mean return of -0.6\% and the UK metals an average
 of 4.9\% over this period, with fourteen US traded commodities and one
-LME metals having negative mean returns. The volatility of both sets of
+UK metal having negative mean returns. The volatility of both sets of
 assets is lower than over the 2004-2007 period, particularly for the UK
@@
 increase of mean average R\textsuperscript{2} of over 50\% while that
-for the other factors increases slightly at best (table 3). From table 5
-we see that there is an across the board increase in pairwise
-correlations with a doubling in the average pairwise correlation of all
-U.S. traded commodities and a levelling in the pairwise correlation of
-the picks of the three long-short factors. Taken together, these results
-indicate the presence of a systematic factor across the entire
-cross-section of the U.S. commodities. This is clearly evident in the
-performance of the market factor built with any set of picks on the
-entire set of U.S. traded commodities (table 7) as we see a dramatic
-rise across the board in pricing performance. Table 8 provides further
-evidence of systematic linkages, in this case between U.S. and
-non-U.S.traded commodities as the market factor built with its own picks
-(U.S. traded commodities) achieves an average R\textsuperscript{2} of
-33.7\% on the LME metals compared to 9.9\% in the previous period.
-
-\section{Conclusion}\label{conclusion}
+for the other factors increases slightly at best (table \ref{table3}).
+From table \ref{table5} we see that there is an across the board
+increase in pairwise correlations with a doubling in the average
+pairwise correlation of all US traded commodities and a levelling in the
+pairwise correlation of the picks of the three long-short factors. Taken
+together, these results indicate the presence of a systematic factor
+across the entire cross-section of the US commodities. This is clearly
+evident in the performance of the market factor built with any set of
+picks on the entire set of US traded commodities (table \ref{table7}) as
+we see a dramatic rise across the board in pricing performance. Table
+\ref{table8} provides further evidence of systematic linkages, in this
+case between US and non-US traded commodities as the market factor built
+with its own picks (US traded commodities) achieves an average
+R\textsuperscript{2} of 33.7\% on the UK metals compared to 9.9\% in the
+previous period.
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
@@
 significant changes in commodity pricing dynamics and our analysis
-suggest that in contrast with financialization, the crisis and its
+suggests that in contrast with financialization, the crisis and its
 aftermath have delivered an exogenous shock across the entire
@@
 \newpage
-\begingroup\fontsize{8}{10}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:mean_returns_no_CHP}This table shows descriptive statistics for nearby returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the U.S.
-traded commodities considered in the study.
-Figures labelled $***$ ($**$, $*$) are significant at the 1\% (5\%, 10\%) level.
-See section 2 for more details.}\\
+\begingroup\fontsize{10}{12}\selectfont
+
+\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\caption{\label{tab:`mean returns`}\label{table1} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study.
+Figures labelled *** (**, *) are significant at the 1\% (5\%, 10\%) level.
+See section \ref{methods} for more details.}\\
 \toprule
-Asset pool & Variable & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
+Assets & Variable & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
 \midrule
@@
 US-Agriculturals-Softs & Mean return & 1.57\% & **14.26\% & 9.53\% & 2.97\%\\
-\addlinespace
 US-Agriculturals-Softs & Volatility & 33.47\% & 30.19\% & 35.53\% & 28.08\%\\
@@
 US-Metals-Precious & Volatility & 26.2\% & 25.61\% & 31.76\% & 21.57\%\\
-\addlinespace
 US-Agriculturals & Mean return & 2.89\% & ***14.45\% & **7.86\% & -0.44\%\\
@@
 US-Metals & Mean return & *7.99\% & ***24.77\% & 9.34\% & 1.98\%\\
-\addlinespace
 US-Metals & Volatility & 25.12\% & 26.64\% & 31.73\% & 21.24\%\\
@@
 UK-Commodity & Volatility & 20.33\% & 33.43\% & 35.99\% & 22.33\%\\
+CHP factor & Mean return & 0.34\% & 1.09\% & -0.15\% & -1.98\%\\
+CHP factor & Volatility & 7.78\% & 8.05\% & 8.93\% & 7.45\%\\
+Market factor & Mean return & 5.99\% & ***18.81\% & 8.01\% & -0.55\%\\
+Market factor & Volatility & 10.2\% & 12.39\% & 17.26\% & 10.3\%\\
+OI factor & Mean return & -0.2\% & 2.79\% & -4.28\% & 2.28\%\\
+OI factor & Volatility & 8.26\% & 8.16\% & 8.1\% & 6.69\%\\
+TS factor & Mean return & **-9.49\% & *-7.15\% & -5.77\% & **-9.02\%\\
+TS factor & Volatility & 10.25\% & 8.31\% & 9.91\% & 8.52\%\\
 \bottomrule
@@
 \newpage
-\begingroup\fontsize{8}{10}\selectfont
+\begingroup\fontsize{10}{12}\selectfont
 
 \begin{landscape}
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:mean_returns_aggregate_CHP}This table shows descriptive statistics for nearby returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the U.S.
-traded commodities considered in the study.
-For each period the results are shown for periods of high (contango) and low (backwardation) aggregate CHP regimes.
-Figures labelled $***$ ($**$, $*$) are significant at the 1\% (5\%, 10\%) level.
-See section 2 for more details.}\\
+\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\caption{\label{tab:`mean returns - aggregate CHP regimes`}\label{table2} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study.
+For each period the results are shown for \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
+Figures labelled *** (**, *) are significant at the 1\% (5\%, 10\%) level.
+See section \ref{methods} for more details.}\\
 \toprule
@@
 US-Agriculturals-Livestock & High & Mean return & -2.15\% & -1.68\% & 4.05\% & -15.8\%\\
-\addlinespace
 US-Agriculturals-Livestock & High & Volatility & 29.3\% & 20.65\% & 23.59\% & 25.46\%\\
@@
 US-Agriculturals-Softs & High & Volatility & 32.54\% & 30.48\% & 36.06\% & 28.72\%\\
-\addlinespace
 US-Agriculturals-Softs & Low & Mean return & 4.47\% & 3.67\% & 7.62\% & 9.33\%\\
@@
 US-Metals-Industrial & Low & Mean return & 5.3\% & 14.86\% & 12.22\% & 16.2\%\\
-\addlinespace
 US-Metals-Industrial & Low & Volatility & 19.89\% & 29.2\% & 25.31\% & 20.85\%\\
@@
 US-Metals-Precious & Low & Volatility & 23.28\% & 27.26\% & 30.77\% & 20.42\%\\
-\addlinespace
 US-Agriculturals & High & Mean return & 0.74\% & ***21.45\% & 4.21\% & -4.72\%\\
@@
 US-Energy & High & Mean return & 3.9\% & *29.75\% & -3.1\% & -23.15\%\\
-\addlinespace
 US-Energy & High & Volatility & 43.76\% & 45.83\% & 45.46\% & 40.32\%\\
@@
 US-Metals & High & Volatility & 27.27\% & 25.45\% & 33.54\% & 21.93\%\\
-\addlinespace
 US-Metals & Low & Mean return & ***18.86\% & 9.66\% & ***20.22\% & 9.56\%\\
@@
 US-Commodity & Low & Mean return & ***10.98\% & **11.16\% & ***14.25\% & *6.93\%\\
-\addlinespace
 US-Commodity & Low & Volatility & 31.25\% & 30.04\% & 31.22\% & 26.52\%\\
@@
 UK-Commodity & Low & Volatility & 19.45\% & 33.17\% & 32.8\% & 22.69\%\\
-\addlinespace
 CHP factor & High & Mean return & 1.45\% & 7.88\% & 0.89\% & -3.48\%\\
@@
 Market factor & High & Mean return & 0.67\% & ***26.46\% & 1.81\% & -7.96\%\\
-\addlinespace
 Market factor & High & Volatility & 10.27\% & 11.96\% & 18.97\% & 11.24\%\\
@@
 OI factor & High & Volatility & 7.92\% & 8.79\% & 8.64\% & 6.7\%\\
-\addlinespace
 OI factor & Low & Mean return & 0.46\% & 0.72\% & -1.65\% & 0.7\%\\
@@
 \newpage
-\begingroup\fontsize{8}{10}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:fact_regs}This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby returns on the commodities forming the entire cross-section of U.S.
-traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using whole set of U.S.
-traded commodities considered.
+\begingroup\fontsize{10}{12}\selectfont
+
+\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\caption{\label{tab:`factor regressions`}\label{table3} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
+The dependent variables are individual nearby futures returns on the commodities forming the entire cross-section of US traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using whole set of US traded commodities considered.
 For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes independently.
-See section 2 for more details.}\\
+For each period, the models are implemented over the whole period, as well as over \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
+See section \ref{methods} for more details.}\\
 \toprule
@@
 US commodities & \textasciitilde{} Market factor & Low & 11.61\% & 19.83\% & 28.92\% & 13.53\%\\
-\addlinespace
 US commodities & \textasciitilde{} Market factor & None & 12.2\% & 18.55\% & 29.45\% & 15.57\%\\
@@
 US commodities & \textasciitilde{} TS factor & High & 2.12\% & 3.36\% & 4.68\% & 2.69\%\\
-\addlinespace
 US commodities & \textasciitilde{} TS factor & Low & 2.88\% & 2.72\% & 5.57\% & 3.09\%\\
@@
 \newpage
-\begingroup\fontsize{8}{10}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:factor_picks}For each risk factor and period, this table displays the list of corresponding commodity factor picks along with the proportion of time they are individually held on the long and short legs of the corresponding risk factor mimicking portfolio.
-The factor portfolios are constructed from the whole set of the twenty four U.S.
-traded commodities considered which is also used as asset pool for the commodity picking exercise.
-See section 2 for more details.}\\
+\begingroup\fontsize{10}{12}\selectfont
+
+\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright\arraybackslash}p{3.5cm}>{\raggedleft}X>{\raggedleft}X}
+\caption{\label{tab:`factor picks`}\label{table4} For each risk factor and period, this table displays the list of corresponding commodity factor picks along with the proportion of time they are individually held on the long and short legs of the corresponding risk factor mimicking portfolio.
+The factor portfolios are constructed from the whole set of the twenty four US traded commodities considered which is also used as asset pool for the commodity picking exercise.
+See section \ref{methods} for more details.}\\
 \toprule
@@
 CHP & 1997/2003 & XCBT - Oats & 97\% & 0\%\\
-CHP & 1997/2003 & XCBT - Soybean oil & 42\% & 32\%\\
-CHP & 1997/2003 & XCBT - Wheat-SR & 29\% & 9\%\\
-CHP & 1997/2003 & XNYM - Copper & 43\% & 18\%\\
+CHP & 1997/2003 & XCBT - Soy-oil & 42\% & 32\%\\
+CHP & 1997/2003 & XCBT - Wheat-SRW & 29\% & 9\%\\
+CHP & 1997/2003 & XCEC - Copper & 43\% & 18\%\\
+CHP & 1997/2003 & XCEC - Silver & 100\% & 0\%\\
 CHP & 1997/2003 & XNYM - Platinum & 91\% & 4\%\\
-\addlinespace
-CHP & 1997/2003 & XNYM - Silver & 100\% & 0\%\\
 CHP & 1997/2003 & IFUS - Coffee & 22\% & 17\%\\
@@
 Market & 1997/2003 & XCBT - Oats & 100\% & 0\%\\
-\addlinespace
-Market & 1997/2003 & XCBT - Soybean meal & 100\% & 0\%\\
-Market & 1997/2003 & XCBT - Wheat-SR & 100\% & 0\%\\
+Market & 1997/2003 & XCBT - Soy-meal & 100\% & 0\%\\
+Market & 1997/2003 & XCBT - Wheat-SRW & 100\% & 0\%\\
 Market & 1997/2003 & XNYM - Crude oil & 100\% & 0\%\\
@@
 Market & 1997/2003 & XNYM - Heating oil & 100\% & 0\%\\
-\addlinespace
 Market & 1997/2003 & XNYM - Natural gas & 99\% & 0\%\\
@@
 OI & 1997/2003 & XNYM - Natural gas & 46\% & 24\%\\
-\addlinespace
-OI & 1997/2003 & XNYM - Gold & 39\% & 28\%\\
+OI & 1997/2003 & XCEC - Gold & 39\% & 28\%\\
 OI & 1997/2003 & XNYM - Palladium & 46\% & 33\%\\
@@
 OI & 1997/2003 & XCME - Lumber & 42\% & 33\%\\
-TS & 1997/2003 & XCBT - Soybean meal & 71\% & 0\%\\
-\addlinespace
+TS & 1997/2003 & XCBT - Soy-meal & 71\% & 0\%\\
 TS & 1997/2003 & XNYM - Crude oil & 53\% & 9\%\\
@@
 TS & 1997/2003 & XNYM - Heating oil & 35\% & 24\%\\
-TS & 1997/2003 & XNYM - Gold & 10\% & 1\%\\
+TS & 1997/2003 & XCEC - Gold & 10\% & 1\%\\
 TS & 1997/2003 & XNYM - Palladium & 61\% & 0\%\\
-\addlinespace
 TS & 1997/2003 & XNYM - Platinum & 96\% & 0\%\\
@@
 CHP & 2004/2007 & XCBT - Oats & 100\% & 0\%\\
-CHP & 2004/2007 & XNYM - Copper & 44\% & 37\%\\
-CHP & 2004/2007 & XNYM - Gold & 100\% & 0\%\\
-\addlinespace
+CHP & 2004/2007 & XCEC - Copper & 44\% & 37\%\\
+CHP & 2004/2007 & XCEC - Gold & 100\% & 0\%\\
+CHP & 2004/2007 & XCEC - Silver & 100\% & 0\%\\
 CHP & 2004/2007 & XNYM - Palladium & 100\% & 0\%\\
 CHP & 2004/2007 & XNYM - Platinum & 100\% & 0\%\\
-CHP & 2004/2007 & XNYM - Silver & 100\% & 0\%\\
 CHP & 2004/2007 & IFUS - Coffee & 15\% & 5\%\\
 CHP & 2004/2007 & IFUS - Orange juice & 66\% & 15\%\\
-\addlinespace
 Market & 2004/2007 & XCBT - Corn & 100\% & 0\%\\
@@
 Market & 2004/2007 & XNYM - Heating oil & 100\% & 0\%\\
-\addlinespace
 Market & 2004/2007 & XNYM - Natural gas & 100\% & 0\%\\
+Market & 2004/2007 & XCEC - Silver & 100\% & 0\%\\
 Market & 2004/2007 & XNYM - Palladium & 100\% & 0\%\\
-Market & 2004/2007 & XNYM - Silver & 100\% & 0\%\\
 OI & 2004/2007 & XCME - Lean hogs & 38\% & 22\%\\
 OI & 2004/2007 & XCME - Live cattle & 32\% & 35\%\\
-\addlinespace
 OI & 2004/2007 & XNYM - Natural gas & 32\% & 35\%\\
@@
 OI & 2004/2007 & IFUS - Cotton & 33\% & 17\%\\
-\addlinespace
 OI & 2004/2007 & IFUS - Sugar & 48\% & 16\%\\
-TS & 2004/2007 & XNYM - Copper & 86\% & 0\%\\
+TS & 2004/2007 & XCEC - Copper & 86\% & 0\%\\
 TS & 2004/2007 & XCME - Feeder cattle & 86\% & 0\%\\
@@
 TS & 2004/2007 & XCME - Live cattle & 56\% & 23\%\\
-\addlinespace
-TS & 2004/2007 & XNYM - Gold & 28\% & 0\%\\
+TS & 2004/2007 & XCEC - Gold & 28\% & 0\%\\
 TS & 2004/2007 & XNYM - Palladium & 0\% & 6\%\\
@@
 TS & 2004/2007 & IFUS - Cocoa & 15\% & 12\%\\
-CHP & 2008/2013 & XCBT - Soybean meal & 79\% & 4\%\\
-\addlinespace
+CHP & 2008/2013 & XCBT - Soy-meal & 79\% & 4\%\\
 CHP & 2008/2013 & XNYM - Gasoline & 46\% & 0\%\\
 CHP & 2008/2013 & XNYM - Heating oil & 1\% & 18\%\\
-CHP & 2008/2013 & XNYM - Gold & 96\% & 0\%\\
+CHP & 2008/2013 & XCEC - Gold & 96\% & 0\%\\
+CHP & 2008/2013 & XCEC - Silver & 90\% & 0\%\\
 CHP & 2008/2013 & XNYM - Palladium & 100\% & 0\%\\
 CHP & 2008/2013 & XNYM - Platinum & 100\% & 0\%\\
-\addlinespace
-CHP & 2008/2013 & XNYM - Silver & 90\% & 0\%\\
 CHP & 2008/2013 & IFUS - Orange juice & 96\% & 0\%\\
@@
 Market & 2008/2013 & XCBT - Oats & 100\% & 0\%\\
-Market & 2008/2013 & XNYM - Copper & 100\% & 0\%\\
-\addlinespace
+Market & 2008/2013 & XCEC - Copper & 100\% & 0\%\\
 Market & 2008/2013 & XNYM - Crude oil & 100\% & 0\%\\
@@
 Market & 2008/2013 & XNYM - Heating oil & 100\% & 0\%\\
+Market & 2008/2013 & XCEC - Silver & 100\% & 0\%\\
 Market & 2008/2013 & XNYM - Palladium & 100\% & 0\%\\
-Market & 2008/2013 & XNYM - Silver & 100\% & 0\%\\
-\addlinespace
 OI & 2008/2013 & XCBT - Corn & 21\% & 37\%\\
-OI & 2008/2013 & XCBT - Soybean meal & 37\% & 34\%\\
+OI & 2008/2013 & XCBT - Soy-meal & 37\% & 34\%\\
 OI & 2008/2013 & XNYM - Crude oil & 23\% & 31\%\\
@@
 OI & 2008/2013 & XNYM - Heating oil & 27\% & 34\%\\
-\addlinespace
 OI & 2008/2013 & IFUS - Orange juice & 32\% & 43\%\\
@@
 OI & 2008/2013 & XCME - Lumber & 35\% & 38\%\\
-TS & 2008/2013 & XCBT - Soybean meal & 69\% & 1\%\\
+TS & 2008/2013 & XCBT - Soy-meal & 69\% & 1\%\\
 TS & 2008/2013 & XCBT - Soybeans & 59\% & 0\%\\
-\addlinespace
 TS & 2008/2013 & XNYM - Crude oil & 25\% & 30\%\\
@@
 TS & 2008/2013 & XNYM - Heating oil & 33\% & 6\%\\
+TS & 2008/2013 & XCEC - Silver & 64\% & 0\%\\
 TS & 2008/2013 & XNYM - Palladium & 38\% & 0\%\\
 TS & 2008/2013 & XNYM - Platinum & 47\% & 1\%\\
-\addlinespace
-TS & 2008/2013 & XNYM - Silver & 64\% & 0\%\\
-CHP & 2014/2017 & XNYM - Copper & 0\% & 79\%\\
+CHP & 2014/2017 & XCEC - Copper & 0\% & 79\%\\
 CHP & 2014/2017 & XNYM - Gasoline & 13\% & 0\%\\
-CHP & 2014/2017 & XNYM - Gold & 78\% & 0\%\\
+CHP & 2014/2017 & XCEC - Gold & 78\% & 0\%\\
+CHP & 2014/2017 & XCEC - Silver & 69\% & 0\%\\
 CHP & 2014/2017 & XNYM - Palladium & 100\% & 0\%\\
-\addlinespace
 CHP & 2014/2017 & XNYM - Platinum & 100\% & 0\%\\
-CHP & 2014/2017 & XNYM - Silver & 69\% & 0\%\\
 CHP & 2014/2017 & IFUS - Orange juice & 62\% & 2\%\\
 CHP & 2014/2017 & XCME - Lumber & 38\% & 53\%\\
-Market & 2014/2017 & XCBT - Soybean meal & 100\% & 0\%\\
-\addlinespace
+Market & 2014/2017 & XCBT - Soy-meal & 100\% & 0\%\\
 Market & 2014/2017 & XNYM - Crude oil & 100\% & 0\%\\
@@
 Market & 2014/2017 & XNYM - Palladium & 100\% & 0\%\\
-\addlinespace
 Market & 2014/2017 & IFUS - Coffee & 100\% & 0\%\\
@@
 OI & 2014/2017 & XCBT - Oats & 32\% & 45\%\\
-OI & 2014/2017 & XCBT - Soybean meal & 39\% & 27\%\\
-OI & 2014/2017 & XNYM - Copper & 48\% & 15\%\\
-\addlinespace
-OI & 2014/2017 & XNYM - Gold & 39\% & 23\%\\
-OI & 2014/2017 & XNYM - Silver & 44\% & 28\%\\
+OI & 2014/2017 & XCBT - Soy-meal & 39\% & 27\%\\
+OI & 2014/2017 & XCEC - Copper & 48\% & 15\%\\
+OI & 2014/2017 & XCEC - Gold & 39\% & 23\%\\
+OI & 2014/2017 & XCEC - Silver & 44\% & 28\%\\
 OI & 2014/2017 & IFUS - Cocoa & 33\% & 34\%\\
@@
 OI & 2014/2017 & XCME - Lumber & 50\% & 30\%\\
-\addlinespace
-TS & 2014/2017 & XCBT - Soybean meal & 68\% & 10\%\\
+TS & 2014/2017 & XCBT - Soy-meal & 68\% & 10\%\\
 TS & 2014/2017 & XCBT - Soybeans & 56\% & 10\%\\
@@
 TS & 2014/2017 & IFUS - Cocoa & 54\% & 1\%\\
-\addlinespace
 TS & 2014/2017 & IFUS - Cotton & 40\% & 2\%\\
@@
 \newpage
-\begingroup\fontsize{8}{10}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:correlations}This table displays the average pairwise correlations for various sets of commodities including the multiple sets of risk factor commodity picks, the whole cross-section of U.S.
-traded commodities considered in the study, the latter with metals omitted, and the cross-section of U.S.
-traded metals.
-For each period and commodity set the correlations are calculated independently over the whole period as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes.
-See section 2 for more details.}\\
+\begingroup\fontsize{10}{12}\selectfont
+
+\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\caption{\label{tab:correlations}\label{table5} This table displays the average pairwise nearby futures returns correlations for various sets of commodities including the multiple sets of risk factor commodity picks, the whole cross-section of US traded commodities considered in the study, the latter with metals omitted, and the cross-section of US traded metals.
+For each period and commodity set the correlations are calculated independently over the whole period as well as over \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes.
+See section \ref{methods} for more details.}\\
 \toprule
@@
 Market factor picks & Low & 0.20 & 0.28 & 0.42 & 0.19\\
-\addlinespace
 Market factor picks & None & 0.21 & 0.26 & 0.41 & 0.21\\
@@
 TS factor picks & High & 0.16 & 0.15 & 0.41 & 0.11\\
-\addlinespace
 TS factor picks & Low & 0.11 & 0.17 & 0.48 & 0.09\\
@@
 US - Commodity & None & 0.08 & 0.13 & 0.24 & 0.11\\
-\addlinespace
 US - Commodity - No metals & High & 0.09 & 0.10 & 0.26 & 0.12\\
@@
 \newpage
-\begingroup\fontsize{8}{10}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:fact_pick_regs_picks_picks}This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby returns on risk factors commodity picks while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in Table 4.
+\begingroup\fontsize{10}{12}\selectfont
+
+\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\caption{\label{tab:`factor pick regressions - picks:picks`}\label{table6} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
+The dependent variables are individual nearby futures returns on risk factors commodity picks while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in table \ref{table4}.
 For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes independently.
-See section 2 for more details.}\\
+For each period, the models are implemented over the whole period, as well as over \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
+See section \ref{methods} for more details.}\\
 \toprule
@@
 TS factor picks & \textasciitilde{} Market factor & Low & 25.53\% & 28.87\% & 54.4\% & 21.22\%\\
-\addlinespace
 TS factor picks & \textasciitilde{} Market factor & None & 27.23\% & 28.26\% & 50.95\% & 21.63\%\\
@@
 TS factor picks & \textasciitilde{} TS factor & High & 2.04\% & 7.65\% & 5.2\% & 2.98\%\\
-\addlinespace
 TS factor picks & \textasciitilde{} TS factor & Low & 2.22\% & 6.03\% & 2\% & 1.85\%\\
@@
 OI factor picks & \textasciitilde{} CHP factor & None & 1.96\% & 6.96\% & 3.95\% & 6.36\%\\
-\addlinespace
 OI factor picks & \textasciitilde{} Market factor & High & 14.4\% & 15.55\% & 39.51\% & 24.98\%\\
@@
 OI factor picks & \textasciitilde{} OI factor & Low & 0.67\% & -0.38\% & 0.95\% & 3.52\%\\
-\addlinespace
 OI factor picks & \textasciitilde{} OI factor & None & 0.29\% & 0.77\% & 0.09\% & 0.74\%\\
@@
 CHP factor picks & \textasciitilde{} CHP factor & High & 5.74\% & 15.05\% & 12.05\% & 12.46\%\\
-\addlinespace
 CHP factor picks & \textasciitilde{} CHP factor & Low & 7.05\% & 10.85\% & 8.7\% & 14.6\%\\
@@
 CHP factor picks & \textasciitilde{} Market factor & None & 21.27\% & 37.36\% & 43.49\% & 31.36\%\\
-\addlinespace
 CHP factor picks & \textasciitilde{} OI factor & High & 1.69\% & 3.9\% & 4.04\% & 0.74\%\\
@@
 CHP factor picks & \textasciitilde{} TS factor & Low & 5.36\% & 5.57\% & 0.95\% & -0.21\%\\
-\addlinespace
 CHP factor picks & \textasciitilde{} TS factor & None & 4.54\% & 5.1\% & 1.84\% & 1.66\%\\
@@
 Market factor picks & \textasciitilde{} Market factor & High & 32.85\% & 34.83\% & 48.14\% & 33.71\%\\
-\addlinespace
 Market factor picks & \textasciitilde{} Market factor & Low & 30.4\% & 37.35\% & 49.31\% & 29.36\%\\
@@
 Market factor picks & \textasciitilde{} OI factor & None & 1.33\% & 0.29\% & 0.78\% & 0.53\%\\
-\addlinespace
 Market factor picks & \textasciitilde{} TS factor & High & 6.64\% & 5.3\% & 2.45\% & 7.59\%\\
@@
 \newpage
-\begingroup\fontsize{8}{10}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:fact_pick_regs_picks_UScommos}This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby returns on the commodities forming the entire cross-section of U.S.
-traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in Table 4.
+\begingroup\fontsize{10}{12}\selectfont
+
+\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\caption{\label{tab:`factor pick regressions - picks: US commos`}\label{table7} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
+The dependent variables are individual nearby futures returns on the commodities forming the entire cross-section of US traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in table \ref{table4}.
 For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes independently.
-See section 2 for more details.}\\
+For each period, the models are implemented over the whole period, as well as over \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
+See section \ref{methods} for more details.}\\
 \toprule
@@
 \endlastfoot
-TS factor picks & \textasciitilde{} CHP factor & High & 0.36\% & 8.95\% & 7.8\% & 3.34\%\\
-TS factor picks & \textasciitilde{} CHP factor & Low & 2.38\% & 11.41\% & 4.96\% & 1.26\%\\
-TS factor picks & \textasciitilde{} CHP factor & None & 1.03\% & 10.14\% & 5.65\% & 1.66\%\\
-TS factor picks & \textasciitilde{} Market factor & High & 10.52\% & 10.93\% & 26.99\% & 9.22\%\\
-TS factor picks & \textasciitilde{} Market factor & Low & 9.7\% & 13.71\% & 27.33\% & 7.99\%\\
-\addlinespace
-TS factor picks & \textasciitilde{} Market factor & None & 10.13\% & 12.29\% & 26.94\% & 8.74\%\\
-TS factor picks & \textasciitilde{} OI factor & High & 0.07\% & 2.36\% & 1.42\% & 0.31\%\\
-TS factor picks & \textasciitilde{} OI factor & Low & 0.69\% & 0.03\% & 0.89\% & 0.23\%\\
-TS factor picks & \textasciitilde{} OI factor & None & 0.22\% & 0.77\% & 0.74\% & 0.06\%\\
-TS factor picks & \textasciitilde{} TS factor & High & 0.6\% & 2.8\% & 2.09\% & 1.18\%\\
-\addlinespace
-TS factor picks & \textasciitilde{} TS factor & Low & 0.89\% & 3.07\% & 0.73\% & 0.72\%\\
-TS factor picks & \textasciitilde{} TS factor & None & 0.18\% & 2.49\% & 1.64\% & 0.93\%\\
-OI factor picks & \textasciitilde{} CHP factor & High & 0.94\% & 2.61\% & 1.57\% & 4.45\%\\
-OI factor picks & \textasciitilde{} CHP factor & Low & 0.35\% & 6.44\% & 3.39\% & 2.23\%\\
-OI factor picks & \textasciitilde{} CHP factor & None & 0.61\% & 3.7\% & 1.54\% & 2.53\%\\
-\addlinespace
-OI factor picks & \textasciitilde{} Market factor & High & 6.65\% & 9.49\% & 25.93\% & 13.83\%\\
-OI factor picks & \textasciitilde{} Market factor & Low & 6.51\% & 13.26\% & 21.69\% & 9.02\%\\
-OI factor picks & \textasciitilde{} Market factor & None & 6.49\% & 11.42\% & 23.87\% & 11.59\%\\
-OI factor picks & \textasciitilde{} OI factor & High & 0.38\% & 0.29\% & 0.36\% & 1.01\%\\
-OI factor picks & \textasciitilde{} OI factor & Low & 0.63\% & -0.58\% & 0.23\% & 1.89\%\\
-\addlinespace
-OI factor picks & \textasciitilde{} OI factor & None & 0.05\% & 0.08\% & 0.05\% & 0.48\%\\
-OI factor picks & \textasciitilde{} TS factor & High & 1.17\% & 2.83\% & 7.46\% & 1.87\%\\
-OI factor picks & \textasciitilde{} TS factor & Low & 1.09\% & 0.63\% & 1.92\% & 1.56\%\\
-OI factor picks & \textasciitilde{} TS factor & None & 1.22\% & 2.08\% & 5.16\% & 1.44\%\\
-CHP factor picks & \textasciitilde{} CHP factor & High & 1.97\% & 4.78\% & 6.3\% & 3.8\%\\
-\addlinespace
-CHP factor picks & \textasciitilde{} CHP factor & Low & 3.02\% & 3.81\% & 3.72\% & 5.47\%\\
-CHP factor picks & \textasciitilde{} CHP factor & None & 2.3\% & 4.23\% & 4.14\% & 4.39\%\\
-CHP factor picks & \textasciitilde{} Market factor & High & 10.52\% & 13.87\% & 25.07\% & 13.35\%\\
-CHP factor picks & \textasciitilde{} Market factor & Low & 9.51\% & 16.21\% & 26.19\% & 11.69\%\\
-CHP factor picks & \textasciitilde{} Market factor & None & 9.96\% & 15.3\% & 25.4\% & 12.43\%\\
-\addlinespace
-CHP factor picks & \textasciitilde{} OI factor & High & 0.65\% & 1.39\% & 1.39\% & 0.41\%\\
-CHP factor picks & \textasciitilde{} OI factor & Low & 1.46\% & 0.29\% & 0.55\% & 1.45\%\\
-CHP factor picks & \textasciitilde{} OI factor & None & 0.65\% & 0.45\% & 0.83\% & 0.12\%\\
-CHP factor picks & \textasciitilde{} TS factor & High & 1.96\% & 2.85\% & 1.19\% & 1.49\%\\
-CHP factor picks & \textasciitilde{} TS factor & Low & 2.44\% & 2.87\% & 0.27\% & 0.07\%\\
-\addlinespace
-CHP factor picks & \textasciitilde{} TS factor & None & 2\% & 2.32\% & 0.97\% & 0.5\%\\
-Market factor picks & \textasciitilde{} CHP factor & High & 2.57\% & 4.52\% & 4.29\% & 2.37\%\\
-Market factor picks & \textasciitilde{} CHP factor & Low & 1.89\% & 4.5\% & 4.17\% & 2.69\%\\
-Market factor picks & \textasciitilde{} CHP factor & None & 1.99\% & 4.31\% & 3.47\% & 2.49\%\\
-Market factor picks & \textasciitilde{} Market factor & High & 12.42\% & 15.19\% & 27.88\% & 14.87\%\\
-\addlinespace
-Market factor picks & \textasciitilde{} Market factor & Low & 11.32\% & 16.98\% & 27.68\% & 12.24\%\\
-Market factor picks & \textasciitilde{} Market factor & None & 11.69\% & 16.13\% & 27.53\% & 13.42\%\\
-Market factor picks & \textasciitilde{} OI factor & High & 1.63\% & 0.52\% & 1.29\% & 0.28\%\\
-Market factor picks & \textasciitilde{} OI factor & Low & 0.14\% & 0.43\% & 0.3\% & -0.05\%\\
-Market factor picks & \textasciitilde{} OI factor & None & 0.6\% & 0.36\% & 0.52\% & 0.41\%\\
-\addlinespace
-Market factor picks & \textasciitilde{} TS factor & High & 2.66\% & 1.84\% & 1.09\% & 2.6\%\\
-Market factor picks & \textasciitilde{} TS factor & Low & 3.18\% & 2.47\% & 5.13\% & 2.36\%\\
-Market factor picks & \textasciitilde{} TS factor & None & 2.97\% & 2.18\% & 1.28\% & 2.38\%\\*
+TS factor picks & \textasciitilde{} CHP factor & High & 1.45\% & 20.37\% & 16.95\% & 8.81\%\\
+TS factor picks & \textasciitilde{} CHP factor & Low & 7.6\% & 21.82\% & 10.29\% & 4.84\%\\
+TS factor picks & \textasciitilde{} CHP factor & None & 3.42\% & 21.2\% & 14.09\% & 5.06\%\\
+TS factor picks & \textasciitilde{} Market factor & High & 28.64\% & 27.15\% & 48.8\% & 21.54\%\\
+TS factor picks & \textasciitilde{} Market factor & Low & 25.53\% & 28.87\% & 54.4\% & 21.22\%\\
+TS factor picks & \textasciitilde{} Market factor & None & 27.23\% & 28.26\% & 50.95\% & 21.63\%\\
+TS factor picks & \textasciitilde{} OI factor & High & 0.07\% & 6.42\% & 4.08\% & 2.13\%\\
+TS factor picks & \textasciitilde{} OI factor & Low & 2.48\% & 0.81\% & 2.68\% & 0.61\%\\
+TS factor picks & \textasciitilde{} OI factor & None & 0.68\% & 2.26\% & 1.81\% & 0.56\%\\
+TS factor picks & \textasciitilde{} TS factor & High & 2.04\% & 7.65\% & 5.2\% & 2.98\%\\
+TS factor picks & \textasciitilde{} TS factor & Low & 2.22\% & 6.03\% & 2\% & 1.85\%\\
+TS factor picks & \textasciitilde{} TS factor & None & 0.53\% & 6.91\% & 4.16\% & 2.02\%\\
+OI factor picks & \textasciitilde{} CHP factor & High & 3.02\% & 5.9\% & 4.56\% & 10.95\%\\
+OI factor picks & \textasciitilde{} CHP factor & Low & 1.32\% & 9.37\% & 7.5\% & 5.5\%\\
+OI factor picks & \textasciitilde{} CHP factor & None & 1.96\% & 6.96\% & 3.95\% & 6.36\%\\
+OI factor picks & \textasciitilde{} Market factor & High & 14.4\% & 15.55\% & 39.51\% & 24.98\%\\
+OI factor picks & \textasciitilde{} Market factor & Low & 14.99\% & 20.4\% & 32.69\% & 17.31\%\\
+OI factor picks & \textasciitilde{} Market factor & None & 14.86\% & 18\% & 36.91\% & 21.08\%\\
+OI factor picks & \textasciitilde{} OI factor & High & 1.67\% & 1.82\% & 0.87\% & 0.64\%\\
+OI factor picks & \textasciitilde{} OI factor & Low & 0.67\% & -0.38\% & 0.95\% & 3.52\%\\
+OI factor picks & \textasciitilde{} OI factor & None & 0.29\% & 0.77\% & 0.09\% & 0.74\%\\
+OI factor picks & \textasciitilde{} TS factor & High & 3.24\% & 7.15\% & 13.59\% & 3.69\%\\
+OI factor picks & \textasciitilde{} TS factor & Low & 2.92\% & 2.7\% & 4.11\% & 3\%\\
+OI factor picks & \textasciitilde{} TS factor & None & 3.07\% & 5.36\% & 9.97\% & 3.08\%\\
+CHP factor picks & \textasciitilde{} CHP factor & High & 5.74\% & 15.05\% & 12.05\% & 12.46\%\\
+CHP factor picks & \textasciitilde{} CHP factor & Low & 7.05\% & 10.85\% & 8.7\% & 14.6\%\\
+CHP factor picks & \textasciitilde{} CHP factor & None & 5.83\% & 13.23\% & 10.46\% & 12.91\%\\
+CHP factor picks & \textasciitilde{} Market factor & High & 21.09\% & 35.23\% & 41.13\% & 32.66\%\\
+CHP factor picks & \textasciitilde{} Market factor & Low & 21.6\% & 38.7\% & 46.97\% & 29.72\%\\
+CHP factor picks & \textasciitilde{} Market factor & None & 21.27\% & 37.36\% & 43.49\% & 31.36\%\\
+CHP factor picks & \textasciitilde{} OI factor & High & 1.69\% & 3.9\% & 4.04\% & 0.74\%\\
+CHP factor picks & \textasciitilde{} OI factor & Low & 3.51\% & 1.61\% & 1.03\% & 2.96\%\\
+CHP factor picks & \textasciitilde{} OI factor & None & 1.57\% & 1.64\% & 2.07\% & 0.23\%\\
+CHP factor picks & \textasciitilde{} TS factor & High & 4.77\% & 7.1\% & 1.98\% & 4.78\%\\
+CHP factor picks & \textasciitilde{} TS factor & Low & 5.36\% & 5.57\% & 0.95\% & -0.21\%\\
+CHP factor picks & \textasciitilde{} TS factor & None & 4.54\% & 5.1\% & 1.84\% & 1.66\%\\
+Market factor picks & \textasciitilde{} CHP factor & High & 7.79\% & 8.62\% & 7.1\% & 7.84\%\\
+Market factor picks & \textasciitilde{} CHP factor & Low & 4.6\% & 7.78\% & 7.63\% & 7.73\%\\
+Market factor picks & \textasciitilde{} CHP factor & None & 6.06\% & 8.31\% & 6.22\% & 7.07\%\\
+Market factor picks & \textasciitilde{} Market factor & High & 32.85\% & 34.83\% & 48.14\% & 33.71\%\\
+Market factor picks & \textasciitilde{} Market factor & Low & 30.4\% & 37.35\% & 49.31\% & 29.36\%\\
+Market factor picks & \textasciitilde{} Market factor & None & 31.43\% & 36.1\% & 48.63\% & 32.31\%\\
+Market factor picks & \textasciitilde{} OI factor & High & 3.74\% & 0.77\% & 2.62\% & 0.52\%\\
+Market factor picks & \textasciitilde{} OI factor & Low & 0.41\% & -0.45\% & 1.22\% & -0.05\%\\
+Market factor picks & \textasciitilde{} OI factor & None & 1.33\% & 0.29\% & 0.78\% & 0.53\%\\
+Market factor picks & \textasciitilde{} TS factor & High & 6.64\% & 5.3\% & 2.45\% & 7.59\%\\
+Market factor picks & \textasciitilde{} TS factor & Low & 8.53\% & 4.21\% & 11.16\% & 4.7\%\\
+Market factor picks & \textasciitilde{} TS factor & None & 7.65\% & 5.2\% & 3.25\% & 6.24\%\\*
 \end{longtabu}\endgroup{}
@@
 \newpage
-\begingroup\fontsize{8}{10}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:fact_pick_regs_picks_UKcommos}This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby returns on the six LME traded metals considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in Table 4.
+\begingroup\fontsize{10}{12}\selectfont
+
+\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\caption{\label{tab:`factor pick regressions - picks: UK commos`}\label{table8} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
+The dependent variables are individual nearby futures returns on the six LME traded metals considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in Table \ref{table4}.
 For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes independently.
-See section 2 for more details.}\\
+For each period, the models are implemented over the whole period, as well as \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
+See section \ref{methods} for more details.}\\
 \toprule
@@
 TS factor picks & \textasciitilde{} Market factor & Low & 1.62\% & 22.57\% & 27.92\% & 0.68\%\\
-\addlinespace
 TS factor picks & \textasciitilde{} Market factor & None & 1.3\% & 20.58\% & 29.6\% & 3.01\%\\
@@
 TS factor picks & \textasciitilde{} TS factor & High & 0.45\% & 4.72\% & 0.22\% & -0.22\%\\
-\addlinespace
 TS factor picks & \textasciitilde{} TS factor & Low & 0.01\% & -0.67\% & 0.22\% & 1.72\%\\
@@
 OI factor picks & \textasciitilde{} CHP factor & None & 0.01\% & 3.54\% & 0.55\% & 0.72\%\\
-\addlinespace
 OI factor picks & \textasciitilde{} Market factor & High & -0.24\% & 4.93\% & 28.78\% & 12.91\%\\
@@
 OI factor picks & \textasciitilde{} OI factor & Low & 1.79\% & 0.78\% & -0.32\% & 3.01\%\\
-\addlinespace
 OI factor picks & \textasciitilde{} OI factor & None & 0.54\% & -0.33\% & 0.07\% & -0.12\%\\
@@
 CHP factor picks & \textasciitilde{} CHP factor & High & 0.48\% & -0.1\% & 2.96\% & 0.46\%\\
-\addlinespace
 CHP factor picks & \textasciitilde{} CHP factor & Low & 0.15\% & -0.55\% & 2.7\% & 0.77\%\\
@@
 CHP factor picks & \textasciitilde{} Market factor & None & 4.48\% & 25.09\% & 26.83\% & 14.99\%\\
-\addlinespace
 CHP factor picks & \textasciitilde{} OI factor & High & 0.28\% & 6.51\% & 0\% & -0.57\%\\
@@
 CHP factor picks & \textasciitilde{} TS factor & Low & -0.26\% & -0.52\% & -0.17\% & 0.28\%\\
-\addlinespace
 CHP factor picks & \textasciitilde{} TS factor & None & -0.24\% & 2.07\% & 0.13\% & 1.33\%\\
@@
 Market factor picks & \textasciitilde{} Market factor & High & -0.11\% & 8.95\% & 36.58\% & 11.77\%\\
-\addlinespace
 Market factor picks & \textasciitilde{} Market factor & Low & 2.08\% & 9.85\% & 29.63\% & 2.79\%\\
@@
 Market factor picks & \textasciitilde{} OI factor & None & -0.04\% & 0.12\% & 0.62\% & -0.24\%\\
-\addlinespace
 Market factor picks & \textasciitilde{} TS factor & High & -0.38\% & 1.37\% & 2.9\% & -0.37\%\\
@@
 \newpage
-\begingroup\fontsize{8}{10}\selectfont
+\begingroup\fontsize{10}{12}\selectfont
 
 \begin{landscape}
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:fact_pick_regs_picks_UKcommos_legs}This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby returns on the six LME traded metals considered in the study while the regressors are returns on the long and short legs of mimicking portfolios for risk factors considered independently, where the factor portfolios are constructed using the corresponding set of risk factor commodity picks.
+\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\caption{\label{tab:`factor pick regressions - picks: UK commos - legs`}\label{table9} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
+The dependent variables are individual nearby futures returns on the six LME traded metals considered in the study while the regressors are returns on the long and short legs of mimicking portfolios for risk factors considered independently, where the factor portfolios are constructed using the corresponding set of risk factor commodity picks.
 For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over periods of high (contango) and low (backwardation) aggregate CHP regimes independently.
-See section 2 for more details.}\\
+For each period, the models are implemented over the whole period, as well as over \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
+See section \ref{methods} for more details.}\\
 \toprule
@@
 TS factor picks & \textasciitilde{} CHP factor & Short & Low & -0.15\% & -0.48\% & 26.72\% & -0.11\%\\
-\addlinespace
 TS factor picks & \textasciitilde{} CHP factor & Short & None & 0.16\% & 0.9\% & 27.93\% & 1.23\%\\
@@
 TS factor picks & \textasciitilde{} OI factor & Long & High & 0.36\% & 4.73\% & 23.81\% & 1.72\%\\
-\addlinespace
 TS factor picks & \textasciitilde{} OI factor & Long & Low & 1.54\% & 11.1\% & 30.88\% & -0.57\%\\
@@
 TS factor picks & \textasciitilde{} OI factor & Short & None & 1.42\% & 21.62\% & 22.99\% & 1.8\%\\
-\addlinespace
 TS factor picks & \textasciitilde{} TS factor & Long & High & -0.14\% & 24.07\% & 19.08\% & 0.51\%\\
@@
 TS factor picks & \textasciitilde{} TS factor & Short & Low & 0.6\% & 9.27\% & 34.98\% & 2.59\%\\
-\addlinespace
 TS factor picks & \textasciitilde{} TS factor & Short & None & 1.06\% & 7.24\% & 28.35\% & 4.01\%\\
@@
 OI factor picks & \textasciitilde{} CHP factor & Short & High & 0.9\% & 0.79\% & 23.17\% & 13.29\%\\
-\addlinespace
 OI factor picks & \textasciitilde{} CHP factor & Short & Low & 0.45\% & 0.65\% & 20.93\% & 3.06\%\\
@@
 OI factor picks & \textasciitilde{} Market factor & Long & None & 1.17\% & 7.97\% & 24.03\% & 10.37\%\\
-\addlinespace
 OI factor picks & \textasciitilde{} OI factor & Long & High & -0.39\% & 1.54\% & 17.05\% & 3.59\%\\
@@
 OI factor picks & \textasciitilde{} OI factor & Short & Low & 3.83\% & 2.41\% & 15.01\% & -1.06\%\\
-\addlinespace
 OI factor picks & \textasciitilde{} OI factor & Short & None & 1.55\% & 3.14\% & 20.57\% & 2.71\%\\
@@
 OI factor picks & \textasciitilde{} TS factor & Short & High & -0.35\% & 1.99\% & 10.81\% & 8.45\%\\
-\addlinespace
 OI factor picks & \textasciitilde{} TS factor & Short & Low & 0.56\% & 1.8\% & 8.96\% & 0.35\%\\
@@
 CHP factor picks & \textasciitilde{} CHP factor & Long & None & 1.87\% & 18.04\% & 18.32\% & 8.25\%\\
-\addlinespace
 CHP factor picks & \textasciitilde{} CHP factor & Short & High & 4.73\% & 21.64\% & 25.57\% & 13.39\%\\
@@
 CHP factor picks & \textasciitilde{} Market factor & Long & Low & 4.4\% & 30.16\% & 27.34\% & 14.77\%\\
-\addlinespace
 CHP factor picks & \textasciitilde{} Market factor & Long & None & 4.48\% & 25.09\% & 26.83\% & 14.99\%\\
@@
 CHP factor picks & \textasciitilde{} OI factor & Short & High & 2.03\% & 21.75\% & 17.79\% & 8.86\%\\
-\addlinespace
 CHP factor picks & \textasciitilde{} OI factor & Short & Low & 3.48\% & 23.02\% & 30.31\% & 3.59\%\\
@@
 CHP factor picks & \textasciitilde{} TS factor & Long & None & 1.91\% & 27.37\% & 18.54\% & 5.2\%\\
-\addlinespace
 CHP factor picks & \textasciitilde{} TS factor & Short & High & 2.04\% & 2.25\% & 21.16\% & 11.49\%\\
@@
 Market factor picks & \textasciitilde{} CHP factor & Long & Low & 1.14\% & 19\% & 33.01\% & 7.1\%\\
-\addlinespace
 Market factor picks & \textasciitilde{} CHP factor & Long & None & 0.66\% & 17\% & 27.85\% & 10.89\%\\
@@
 Market factor picks & \textasciitilde{} Market factor & Long & High & -0.11\% & 8.95\% & 36.58\% & 11.77\%\\
-\addlinespace
 Market factor picks & \textasciitilde{} Market factor & Long & Low & 2.08\% & 9.85\% & 29.63\% & 2.79\%\\
@@
 Market factor picks & \textasciitilde{} OI factor & Long & None & 0.07\% & 4.4\% & 34.38\% & 4.78\%\\
-\addlinespace
 Market factor picks & \textasciitilde{} OI factor & Short & High & -0.03\% & 6.86\% & 24.78\% & 9.62\%\\
@@
 Market factor picks & \textasciitilde{} TS factor & Long & Low & 0.84\% & 8.74\% & 30.58\% & 4.49\%\\
-\addlinespace
 Market factor picks & \textasciitilde{} TS factor & Long & None & 0.48\% & 10.83\% & 30.76\% & 7.34\%\\
@@
 
-\section{Appendix}\label{appendix}
-
-\subsection{Assets}\label{assets}
-
-\begingroup\fontsize{8}{10}\selectfont
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\hypertarget{assets}{%
+\subsection{Assets}\label{assets}}
+
+\begingroup\fontsize{10}{12}\selectfont
 
 \begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedright}X>{\raggedright}X}
-\caption{\label{tab:appendix_assets}This table shows details on the individual commodities considered in this study including trading country, sector, subsector as well as trading exchange Market Identifier Codes (MIC, ISO 10383).}\\
+\caption{\label{tab:`appendix - assets`}This table shows details on the individual commodities considered in this study including trading country, sector, subsector as well as trading exchange Market Identifier Codes (MIC, ISO 10383).}\\
 \toprule
@@
 US & Agriculturals & Grains & XCBT & Oats\\
-US & Agriculturals & Grains & XCBT & Soybean meal\\
-US & Agriculturals & Grains & XCBT & Soybean oil\\
+US & Agriculturals & Grains & XCBT & Soy-meal\\
+US & Agriculturals & Grains & XCBT & Soy-oil\\
 US & Agriculturals & Grains & XCBT & Soybeans\\
-
-US & Agriculturals & Grains & XCBT & Wheat-SR\\
+US & Agriculturals & Grains & XCBT & Wheat-SRW\\
 US & Agriculturals & Livestock & XCME & Feeder cattle\\
@@
 US & Agriculturals & Softs & IFUS & Cocoa\\
-
 US & Agriculturals & Softs & IFUS & Coffee\\
@@
 US & Agriculturals & Softs & XCME & Lumber\\
-
 US & Energy & Petroleum & XNYM & Crude oil\\
@@
 US & Energy & Petroleum & XNYM & Natural gas\\
-US & Metals & Industrial & XNYM & Copper\\
-
-US & Metals & Precious & XNYM & Gold\\
+US & Metals & Industrial & XCEC & Copper\\
+US & Metals & Precious & XCEC & Gold\\
+US & Metals & Precious & XCEC & Silver\\
 US & Metals & Precious & XNYM & Palladium\\
 US & Metals & Precious & XNYM & Platinum\\
-US & Metals & Precious & XNYM & Silver\\
 UK & Metals & Industrial & XLME & Aluminium\\
-
 UK & Metals & Industrial & XLME & Copper\\
@@
 \bottomrule
-\end{longtabu}
-
-\endgroup{}
-
-\clearpage
-
-\subsection{Market factor lemma}\label{market-factor-lemma}
+\end{longtabu}\endgroup{}
+
+\newpage
+
+\hypertarget{market-factor-lemma}{%
+\subsection{Market factor lemma}\label{market-factor-lemma}}
 
@@
 \(R_{j, mkt, p}^{2}\equiv\) period \(p\) \(R^{2}\) for the regression
-where the depent variable is the vector of returns on commodity \(j\)
+where the dependent variable is the vector of returns on commodity \(j\)
 nearby contract and the regressor is the vector of returns on the market
@@
 
-Assumptions:\\
--
-\(w_{j, p} = w_{k, p} = \frac{1}{n} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt}\).\\
--
-\(\sigma_{r_{j}, p} = \sigma_{r_{k}, p} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt}\).\\
--
-\(cov \left ( r_{j}, r_{k} \right )_{p} = 0 \: \forall \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt}\).
+Assumptions:
+
+\begin{math}
+  \begin{aligned}
+   w_{j, p} &= w_{k, p} = \frac{1}{n} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt} \\
+   \sigma_{r_{j}, p} &= \sigma_{r_{k}, p} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt} \\
+   cov \left ( r_{j}, r_{k} \right )_{p} &= 0 \: \forall \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt}
+  \end{aligned}
+\end{math}
+
+\newpage
 
@@
                                                         & = & \frac{\sigma_{r_{j}, p}^{4}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\ \\
+\end{array}
+\]
+
+\newpage
+
+\[
+\begin{array}{l c l}
   R_{r_{j}, r_{mkt}, p}^{2} & = & \frac{\sigma_{r_{j}, p}^{4}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \cdot \frac{1}{\sigma_{r_{j, p}}^{2}} \\
@@
 
-\clearpage
-\theendnotes
-
 \end{document}

### 2024-06-11 others/paper/custom/main.Rmd
Track 'others' folder

--- 2024-06-11 others/paper/custom/anonymous.Rmd
@@
 
-jel:
-  - G11
-  - G23
-  - G13
-  - Q02
+author: 
+  - name: Devraj Basu
+    surname: Basu
+    email: devraj.basu@strath.ac.uk
+    affiliation: University of Strathclyde, Glasgow, UK
+  - name: Olivier Bauthéac
+    surname: Bauthéac
+    email: olivier.bautheac@strath.ac.uk
+    affiliation: University of Strathclyde, Glasgow, UK
 
-keywords: 
-  - Commodity futures
-  - financialization
-  - hedging pressure
-  - financial crisis
+jel: G11, G23, G13, Q02
+keywords: Commodity futures, financialization, hedging pressure, financial crisis
 
@@
 ```{r, echo = FALSE, message = FALSE}
-packages.v <- c("tidyr", "magrittr", "knitr", "lettercase", "tinytex", "bookdown", "kableExtra")
-invisible(sapply(packages.v, require, character.only = TRUE))
+packages <- c("tidyr", "magrittr", "knitr", "lettercase", "tinytex", "bookdown", "kableExtra", "here")
+invisible(sapply(packages, require, character.only = TRUE))
 options(knitr.table.format = "latex")
 knitr::opts_chunk$set(echo = FALSE, results = "asis")
-# tickers.tb <- readRDS(file = paste0(getwd(), "/data/tickers.rds"))
-# tables.tb <- readRDS(file = paste0(getwd(), "/explore/results/tables.rds"))
-tickers.tb <- readRDS(file = "../data/tickers.rds")
-tables.tb <- readRDS(file = "../explore/results/tables.rds")
+tickers <- readRDS(file = file.path(here::here(), "data", "tickers.rds"))
+tables <- readRDS(file = file.path(here::here(), "explore", "results", "tables.rds.rds"))
 
 ```
+
+\newpage
+
+**Disclosure**
+
+* Devraj Basu: 
+  I am a co-author of this paper and wish to state that I have no conflict of interest, financial or otherwise.
+I do not hold paid or unpaid positions at any organization whose goals relate to the article.
+  ![](pics/signature - Devraj.png)\
+
+\newpage
+
+**Disclosure**
+
+* Olivier Bauthéac:
+  I am a co-author of this paper and wish to state that I have no conflict of interest, financial or otherwise.
+I do not hold paid or unpaid positions at any organization whose goals relate to the article.
+  ![](pics/signature - Olivier.png)\
 
@@
 A vigorous legislative debate has led to regulatory changes accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section \ref{background} for a detailled discussion.].
-In response to immediate policy concerns the academic debate was initially framed rather narrowly.
+In response to immediate policy concerns, the academic debate was initially framed rather narrowly.
 In this paper we take a fundamentally different empirical approach that is broader in scope.
@@
 This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of traders.
-Factor models are well suited to isolating common driving factors and detecting co-movement and building on theory we develop a bespoke commodity-based asset pricing framework that seems well adapted to study these two issues simultaneously.
+Factor model techniques are well suited to isolating common driving factors and detecting co-movement and building on theory we develop a bespoke commodity-based asset pricing framework that seems well adapted to study these two issues simultaneously.
 
@@
 We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (LME exchange) base metals over the 1997/2017 period that we divide into four distinct sub-periods.
-The first, the pre-financialization phase, spans the 1997/2003 period; the second, the financialization phase, spans the 2004/2007 period^[Starting point based on earlier studies [@baker_financialization_2014; @christoffersen_factor_2018].]; the third, 2008/2013, encompasses both the financial crisis and the loose monetary policy regimes that followed; and the fourth spans the period starting in 2014 to present.
+The first, the pre-financialization phase, spans the 1997/2003 period; the second, the financialization phase, spans the 2004/2007 period^[Starting point based on earlier studies [@baker_financialization_2014; @christoffersen_factor_2014].]; the third, 2008/2013, encompasses both the financial crisis and the loose monetary policy regimes that followed; and the fourth spans the period starting in 2014 to present.
 Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialization period compared to pre-financialization and this pattern extends to UK traded metals.
 
-The arrival of financial investors raises the question of whether they functioned as liquidity providers or liquidity demanders.
-Arguments have been made for both sides with @moskowitz_time_2012 arguing that financial investors provide liquidity while @Kangtaletwopremiums2017 argue that they demand liquidity with @cheng_convective_2014 showing that they in fact transferred risk to hedgers during the 2008 financial crisis.
-We study this issue by extending the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in @hong_what_2012.
-Our use of this measure is motivated by the cross sectional nature of financialization [@basak_model_2016; @cheng_convective_2014; @le_futures_2017].
+The cross-sectional nature of financialization [@basak_model_2016; @cheng_financialization_2014] leads us to extend the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in @hong_what_2012.
 This paradigm implies that returns for individual commodities should be high in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in periods where \textbf{CHP} is high (\textbf{contango}).
@@
 Over the second period this pattern reverses, with both the US and UK commodities having significant positive returns during \textbf{contango} with these returns being significantly higher than during \textbf{backwardation}.
-This change in pattern suggests that the onset of financialization altered the traditional risk shifting nature of hedger’s behaviour implied by the Keynesian hypothesis and suggests that financial investors may have been liquidity demanders during financialization leading hedgers to become liquidity providers.
+This change in pattern suggests that the onset of financialization altered the traditional risk shifting nature of hedger’s behaviour, which is implied by the Keynesian hypothesis.
+The arrival of financial investors raises the question of whether they functioned as liquidity providers or liquidity demanders.
+Arguments have been made for both of these possibilities with @moskowitz_time_2012 arguing that financial investors provide liquidity while @Kangtaletwopremiums2017 argue that they demand liquidity.
+Our analysis of returns in periods of low and high aggregate CHP before and during financialization allows us to analyse this issue from a new perspective and suggests that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
 
@@
 We analyze the pricing dynamics over the different periods by first studying the time series pricing performance of the various factors on all the US traded commodities with the factors constructed using the latter set of commodities.
-The market based factor outperforms the other three in the first period while the CHP factor shows the greatest improvement in performance in the second period with a four-fold increase in pricing performance.
+The market based factor outperforms the other three in the first period and it has a similar level of performance in the second period, while the CHP factor shows the greatest improvement in performance in the second period.
 The performance of the market factor is driven by agricultural commodities and metals in both the first and second period and the dramatic improvement of the CHP factor in the second period is driven by precious and precious-base metals.
@@
 Thus the CHP factor model is able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialization.
-We explore this issue further by constructing the four factors with the top eight commodities for a given factor (factor picks) in each period^[See section \ref{methods} for further details.] and evaluating their performance on these selected commodities as well as on all US traded commodities.
+We explore this issue further by constructing the four factors with the top eight commodities for a given factor (factor picks) in each period^[See section \ref{methods} for further details.] and evaluating its performance on these selected commodities as well as on all US traded commodities.
 The results of this exercise strongly suggest that the hedging pressure co-movement and price co-movement link was concentrated in the metals sub-sector.
@@
 To that end, we examine the performance of the four factors on the six UK metals, when constructed from each set of factor picks.
-The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our hedging pressure based model.
+The resuslts show that here was co-movement in global metals returns in the second period and that this co-movement could be detected by our hedging pressure based model.
 
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in pricing dynamics.
-Returns on both US and UK traded commodities fell dramatically over both the third and fourth periods with the pattern of return for the US traded commodities across \textbf{CHP} regimes reverting to the Keynesian paradigm.
+Returns on both US and UK traded commodities fell dramatically over both the third and fourth periods with the pattern of return for the US traded commodities across \textbf{CHP} regimes reverting to Keynesian paradigm.
 The pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as strong evidence of cross-market linkages.
 
-Commodity financialization raised societal concerns, leading to legislative action intended to alter the nature and functioning of these markets.
+Financialization was an issue of such policy importance that it triggered legislative action.
 The debate was initially framed around adequacy of speculation, the burning issue of the day, and the consequent analysis focused on the more mechanical effects of financialization.
@@
 Commodity price dynamics appear to have altered substantially in quite different ways over the financialization and the financial crisis periods and our commodity futures based asset pricing approach seems able to provide new insights into the nature of these changes: financialization was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and mainly concentrated in a specific sector (metals) while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of global commodities.
-We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialization on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2014, @EkelandSpeculationcommodityfutures2016, @goldstein_commodity_2017 as well as @le_futures_2017, one of the few empirical studies on the impact of financialization on commodity-price cross-moments.] and demonstrate that the effects of financialization extend beyond the mechanical effects induced by indexation as outlined in @basak_model_2016 as well as @tang_index_2012.
+The initial view of financialization was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity future prices^[@de_schutter_food_2010_1; @gilbert_how_2010; @gilbert_speculative_2010; @masters_testimony_2008; @masters_accidental_2008; @herman_not_2011_1; @schumann_hunger-makers_2011; @singleton_investor_2013; @unctad_global_2009.].
+However, the fundamental question of the nature of the impact of financialization across the entire cross-section of commodity futures markets has not yet been completely answered.
+We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialization on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2013, @EkelandSpeculationcommodityfutures2016, @goldstein_commodity_2017.] and demonstrate that the effects of financialization extend beyond the mechanical effects induced by indexation as outlined in @basak_model_2016 as well as @tang_index_2012.
 
@@
 The period from 1998 to 2008 saw an influx of investment into commodity index linked products most of which made its way into the commodity futures market.
-Exposure to commodity indexes whose goal was to track the broad movement of commodity prices could be accessed by means of exchange traded funds and exchange traded notes and at least \$100 billion of new investment flowed into these products over the 1998-2008 period with this financialization phenomenon leading to substantial legislative changes.
+These commodity indexes whose goal was to track the broad movement of commodity prices could be accessed by means of exchange traded funds and exchange traded notes.
+At least \$100 billion of new investment flowed into these products over the 1998-2008 period with this financialization phenomenon leading to substantial legislative changes.
 Concerns over the consequences of financialization were behind Rule 76 FR 4752 issued by the US Commodity Futures Trading Commission (CFTC) on January 26^th^, 2011.
@@
 The US and various european countries also became involved in this issue.
-Early US Senate investigations drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US wheat markets to the observed surges in both futures and cash prices [@masters_testimony_2008; @masters_accidental_2008].
+Early US Senate investigations drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US wheat markets to the observed surges in both futures and cash prices [@masters_testimony_2008; @masters_accidental_2008]).
 This contention has since come to be known as the Masters’ hypothesis and was largely endorsed by the final US Senate report on the issue [@USSenate_Excessive_speculation_wheat_2009].
@@
 The first, the pre-financialization period, starts in 1997 and is naturally followed by financialization, spanning the 2004/2007 period, and the financial crisis and its aftermath, spanning the 2008/2013 period.
-The last period spans the 2014/present period starting with the beginning of the tapering/end of the US Quantitative Easing program (QE).
+The last period spans the 2014/present period sarting with the beginning of the tapering/end of the US Quantitative Easing program (QE).
 Using the weekly price, open interest and market position data described above we construct market portfolios of commodity nearby futures as well as mimicking portfolios for market, commercial hedging pressure, term structure and liquidity risk factors in returns.
@@
 $j\equiv$ commodity rank in the ordered set $Y_{t}^{f_{i}}$.  
-$Y_{t}^{f_{i}}\equiv$ week $t$ ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is factor specific ($f_{i}$).
+$Y_{t}^{f_{i}}\equiv$ week $t$ ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is specific to $f_{i}$.
 
@@
 
-The same operation is repeated for the two ($p=2$) and three ($p=3$) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectively, as well as for the four ($p=4$) factor model case where all the risk factor mimicking portfolios are included.
+The same operation is repeated for the two ($p=2$) and three ($p=3$) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectivly, as well as for the four ($p=4$) factor model case where all the risk factor mimicking portfolios are included.
 Results are reported for the one-factor model case with the other results available from the authors upon request.
@@
 For the twenty-four US commodities over this period, eighteen have higher mean returns during phases of \textbf{backwardation} over \textbf{contango}, with the difference statistically significant for four commodities and of the remaining seven the higher mean return during \textbf{backwardation} is statistically significant for one commodity.
-All of the six UK metals achieved higher mean returns over \textbf{backwardation} than \textbf{contango} with the difference being statistically significant for one commodity.
+All of the six UK metals achieved higher mean returns over \textbf{backwardation} than contango with the difference being statistically significant for one commodity.
 The equally weighted US portfolio had a mean return of 11.16% over \textbf{backwardation} while it was 26.68% during \textbf{contango}, the first statistically significant at the 5% level and the second at the 1% level, with the difference statistically significant at the 1% level.
@@
 Thus the onset of financialization seems to have engendered a change in the nature of hedger’s behaviour in the aggregate, taking it away from risk shifting, the traditional Keynesian view.
-This phenomenon has been noted in earlier theoretical and empirical work [@DanthineInformationfuturesprices1978; @stout_why_1998] in different context from which two competing models of behaviour have emerged.
+This phenomenon has been noted in earlier theoretical and empirical work [@DanthineInformationfuturesprices1978, @stout_why_1998] in different context from which two competing models of behaviour have emerged.
 The information arbitrage model implies that hedgers may often be seeking out counterparties to trade with rather than being purely passive.
@@
 Taken together with the fact that four of these metals had consistently low CHP, we see that CHP co-movement in the second period is strongly correlated with price co-movement.
-It is also interesting to note that US traded metals returns were negatively correlated with the rest of US traded commodities in the first period and positively in the second (results available upon request).
+It is also interesting to note that US traded metals returns were negatively correlated with the rest of US traded commodities in the first period and positively in the second (Results available upon request).
 
@@
 A high average R^2^ for the market factor is indicative of strong price co-movement while for the long-short factors it is indicative of simultaneous attribute and price co-movement.
-The most dramatic change in pricing performance occurs for the average CHP factor picks where the market factor built from these picks has an average R^2^ of 21.3% in the first period and jumps to 37.4% in the second period indicating much high co-movement.
+The most dramatic change in pricing performance occurs for the average CHP factor picks where the market factor built from these picks has an average R^2^ of 21.3 % in the first period (close to the 0 correlation situation) and jumps to 37.4 % in the second period.
 The average CHP factor built with average CHP factor picks also shows a sharp increase in pricing performance over the second period.
@@
 In contrast, the increase in R^2^ for the average CHP factor built with average CHP factor picks is lower indicating that the link between CHP co-movement and price co-movement is strongest amongst the picks which are predominantly metals.
-The results from Tables \ref{table6} and \ref{table7} show that the onset of financialization seems to have had a major impact on the dynamics of US traded precious and precious-base metals and we now seek to analyse whether this phenomenon is true for the non-US metal futures.
+The conclusion from Tables \ref{table6} and \ref{table7} is that the onset of financialization seems to have had a major impact on the dynamics of US traded precious and precious-base metals and we now seek to analyse whether this phenomenon is true for the non-US metal futures.
 To that end we examine the pricing performance of the factors used in Table \ref{table6} on the six UK metals futures.
@@
 Our analysis suggests that financialization was a phenomenon endogenous to the commodity markets transmitted via the futures markets and appears to have had the deepest impact on global metal futures markets.
-The onset of the financial crisis and the monetary policy regimes that followed appear to have also induced significant changes in commodity pricing dynamics and our analysis suggests that in contrast with financialization, the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of global commodities.
+The onset of the financial crisis and the monetary policy regimes that followed appear to have also induced significant changes in commodity pricing dynamics and our analysis suggest that in contrast with financialization, the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of global commodities.
 
@@
 
-table.tb <- tables.tb %>%
-  dplyr::filter(name == "table 1") %>%
-  dplyr::select(table) %>%
-  tidyr::unnest(table)
+table <- dplyr::filter(tables, name == "table 1") %>% dplyr::select(table) %>% tidyr::unnest(table)
 
-caption.v <- "\\label{table1} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study.
+caption <- "\\label{table1} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study.
 Figures labelled *** (**, *) are significant at the 1\\% (5\\%, 10\\%) level.
@@
 
-kable(table.tb, 
-      align = c(rep('l', 2L), rep('r', 4L)),
-      digits = getOption("digits"),
-      booktabs = TRUE,
-      longtable = TRUE,
-      linesep = "",
-      caption = caption.v) %>%
+kable(table, align = c(rep('l', 2L), rep('r', 4L)), digits = getOption("digits"),
+      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>%
   kableExtra::kable_styling(full_width = TRUE, font_size = 10L) %>%
@@
 ```{r `mean returns - aggregate CHP regimes`}
-table.tb <- tables.tb %>%
-  dplyr::filter(name == "table 2") %>%
+table <- dplyr::filter(tables, name == "table 2") %>%
   dplyr::select(table) %>%
@@
 
-caption.v <- "\\label{table2} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study.
+caption <- "\\label{table2} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study.
 For each period the results are shown for \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently.
@@
 
-kable(table.tb, 
-      align = c(rep('l', 3L), rep('r', 4L)), 
-      digits = getOption("digits"), 
-      booktabs = TRUE, 
-      longtable = TRUE, 
-      linesep = "",
-      caption = caption.v) %>% 
+kable(table, align = c(rep('l', 3L), rep('r', 4L)), digits = getOption("digits"), 
+      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
   kableExtra::landscape() %>% 
@@
 ```{r `factor regressions`}
-table.tb <- tables.tb %>%
-  dplyr::filter(name == "table 3") %>%
+table <- dplyr::filter(tables, name == "table 3") %>%
   dplyr::select(table) %>%
@@
 
-caption.v <- "\\label{table3} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
+caption <- "\\label{table3} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
 The dependent variables are individual nearby futures returns on the commodities forming the entire cross-section of US traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using whole set of US traded commodities considered.
@@
 
-kable(table.tb, 
-      align = c(rep('l', 3L), rep('r', 4L)), 
-      digits = getOption("digits"), 
-      booktabs = TRUE, 
-      longtable = TRUE, 
-      linesep = "",
-      caption = caption.v) %>% 
+kable(table, align = c(rep('l', 3L), rep('r', 4L)), digits = getOption("digits"), 
+      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
   kableExtra::kable_styling(font_size = 10L, full_width = TRUE) %>% 
@@
 ```{r `factor picks`}
-table.tb <- tables.tb %>%
-  dplyr::filter(name == "table 4") %>%
-  dplyr::select(table) %>%
-  tidyr::unnest(table)
+table <- dplyr::filter(tables, name == "table 4") %>% dplyr::select(table) %>% tidyr::unnest(table)
 
-caption.v <- "\\label{table4} For each risk factor and period, this table displays the list of corresponding commodity factor picks along with the proportion of time they are individually held on the long and short legs of the corresponding risk factor mimicking portfolio.
+caption <- "\\label{table4} For each risk factor and period, this table displays the list of corresponding commodity factor picks along with the proportion of time they are individually held on the long and short legs of the corresponding risk factor mimicking portfolio.
 The factor portfolios are constructed from the whole set of the twenty four US traded commodities considered which is also used as asset pool for the commodity picking exercise.
@@
 
-kable(table.tb, 
-      align = c(rep('l', 3L), rep('r', 2L)), 
-      digits = getOption("digits"), 
-      booktabs = TRUE, 
-      longtable = TRUE, 
-      linesep = "",
-      caption = caption.v) %>% 
+kable(table, align = c(rep('l', 3L), rep('r', 2L)), digits = getOption("digits"), 
+      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
   kableExtra::kable_styling(latex_options = "repeat_header",
@@
 ```{r correlations}
-table.tb <- tables.tb %>%
-  dplyr::filter(name == "table 5") %>%
-  dplyr::select(table) %>%
-  tidyr::unnest(table)
+table <- dplyr::filter(tables, name == "table 5") %>% dplyr::select(table) %>% tidyr::unnest(table)
 
-caption.v <- "\\label{table5} This table displays the average pairwise nearby futures returns correlations for various sets of commodities including the multiple sets of risk factor commodity picks, the whole cross-section of US traded commodities considered in the study, the latter with metals omitted, and the cross-section of US traded metals.
+caption <- "\\label{table5} This table displays the average pairwise nearby futures returns correlations for various sets of commodities including the multiple sets of risk factor commodity picks, the whole cross-section of US traded commodities considered in the study, the latter with metals omitted, and the cross-section of US traded metals.
 For each period and commodity set the correlations are calculated independently over the whole period as well as over \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes.
@@
 
-kable(table.tb, 
-      align = c(rep('l', 2L), rep('r', 4L)), 
-      digits = getOption("digits"), 
-      booktabs = TRUE, 
-      longtable = TRUE, 
-      linesep = "",
-      caption = caption.v) %>% 
+kable(table, align = c(rep('l', 2L), rep('r', 4L)), digits = getOption("digits"), 
+      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
   kableExtra::kable_styling(font_size = 10L, full_width = TRUE) %>% 
@@
 ```{r `factor pick regressions - picks:picks`}
-table.tb <- tables.tb %>%
-  dplyr::filter(name == "table 6") %>%
-  dplyr::select(table) %>%
-  tidyr::unnest(table)
+table <- dplyr::filter(tables, name == "table 6") %>% dplyr::select(table) %>% tidyr::unnest(table)
 
-caption.v <- "\\label{table6} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
+caption <- "\\label{table6} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
 The dependent variables are individual nearby futures returns on risk factors commodity picks while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in table \\ref{table4}.
@@
 
-kable(table.tb, 
-      align = c(rep('l', 3L), rep('r', 4L)), 
-      digits = getOption("digits"), 
-      booktabs = TRUE, 
-      longtable = TRUE, 
-      linesep = "",
-      caption = caption.v) %>% 
+kable(table, align = c(rep('l', 3L), rep('r', 4L)), digits = getOption("digits"), 
+      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
   kable_styling(latex_options = "repeat_header", 
@@
 ```{r `factor pick regressions - picks: US commos`}
-table.tb <- tables.tb %>%
-  dplyr::filter(name == "table 7") %>%
-  dplyr::select(table) %>%
-  tidyr::unnest(table)
+table <- dplyr::filter(tables, name == "table 7") %>% dplyr::select(table) %>% tidyr::unnest(table)
 
-caption.v <- "\\label{table7} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
+caption <- "\\label{table7} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
 The dependent variables are individual nearby futures returns on the commodities forming the entire cross-section of US traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in table \\ref{table4}.
@@
 
-kable(table.tb, 
-      align = c(rep('l', 3L), rep('r', 4L)), 
-      digits = getOption("digits"), 
-      booktabs = TRUE, 
-      longtable = TRUE, 
-      linesep = "",
-      caption = caption.v) %>% 
+kable(table, align = c(rep('l', 3L), rep('r', 4L)), digits = getOption("digits"), 
+      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
   kableExtra::kable_styling(latex_options = "repeat_header", 
@@
 ```{r `factor pick regressions - picks: UK commos`}
-table.tb <- tables.tb %>%
-  dplyr::filter(name == "table 8") %>%
-  dplyr::select(table) %>%
-  tidyr::unnest(table)
+table <- dplyr::filter(tables, name == "table 8") %>% dplyr::select(table) %>% tidyr::unnest(table)
 
-caption.v <- "\\label{table8} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
+caption <- "\\label{table8} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
 The dependent variables are individual nearby futures returns on the six LME traded metals considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in Table \\ref{table4}.
@@
 
-kable(table.tb, 
-      align = c(rep('l', 4L), rep('r', 4L)), 
-      digits = getOption("digits"), 
-      booktabs = TRUE, 
-      longtable = TRUE, 
-      linesep = "",
-      caption = caption.v) %>% 
+kable(table, align = c(rep('l', 4L), rep('r', 4L)), digits = getOption("digits"), 
+      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
   kableExtra::kable_styling(latex_options = "repeat_header", 
@@
 ```{r `factor pick regressions - picks: UK commos - legs`}
-table.tb <- tables.tb %>%
-  dplyr::filter(name == "table 9") %>%
-  dplyr::select(table) %>%
-  tidyr::unnest(table)
+table <- dplyr::filter(tables, name == "table 9") %>% dplyr::select(table) %>% tidyr::unnest(table)
 
-caption.v <- "\\label{table9} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
+caption <- "\\label{table9} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
 The dependent variables are individual nearby futures returns on the six LME traded metals considered in the study while the regressors are returns on the long and short legs of mimicking portfolios for risk factors considered independently, where the factor portfolios are constructed using the corresponding set of risk factor commodity picks.
@@
 
-kable(table.tb, 
-      align = c(rep('l', 4L), rep('r', 4L)), 
-      digits = getOption("digits"), 
-      booktabs = TRUE, 
-      longtable = TRUE, 
-      linesep = "",
-      caption = caption.v) %>% 
+kable(table, align = c(rep('l', 4L), rep('r', 4L)), digits = getOption("digits"), 
+      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
   kableExtra::landscape() %>% 
@@
 ```{r `appendix - assets`}
-caption.v <- "This table shows details on the individual commodities considered in this study including trading country, sector, subsector as well as trading exchange Market Identifier Codes (MIC, ISO 10383)."
+caption <- "This table shows details on the individual commodities considered in this study including trading country, sector, subsector as well as trading exchange Market Identifier Codes (MIC, ISO 10383)."
 
-tickers.tb %>%
-  dplyr::filter(Market == TRUE, Asset_class == "Commodity") %>%
+dplyr::filter(tickers, Market == TRUE, Asset_class == "Commodity") %>%
   dplyr::select(Country, Sector, Subsector, Exchange, Name) %>%
@@
         linesep = "",
-        caption = caption.v) %>%
+        caption = caption) %>%
   kableExtra::kable_styling(full_width = TRUE, font_size = 10L) %>%

### 2024-06-11 others/paper/custom/main.tex
Track 'others' folder

--- 2024-06-11 others/paper/custom/anonymous.tex
@@
 \bibliographystyle{jf}
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 \IfFileExists{parskip.sty}{%
@@
   \title{Financialization of Commodities: an Asset Pricing Perspective}
-    \author{}
+    % \author{Devraj Basu \\ Olivier Bauthéac}
+  \author{ Devraj Basu  \\  Olivier Bauthéac  
+	  \thanks{ Basu: University of Strathclyde, Glasgow, UK, \href{mailto:devraj.basu@strath.ac.uk}{\nolinkurl{devraj.basu@strath.ac.uk}}.
+Bauthéac: University of Strathclyde, Glasgow, UK, \href{mailto:olivier.bautheac@strath.ac.uk}{\nolinkurl{olivier.bautheac@strath.ac.uk}}.
+	   \newline We thank seminar participants at IIM Ahmedabad, IIM Calcutta, SKEMA
+Business School and University of Gottingen, as well as Griffith
+inaugural alternative investment conference attendants for their
+feedback. We also thank Joelle Miffre, Martijn Boons, John Fan, Robert
+Bianchi, Chardin Wese Simen, Andrew Kaleel and particularly Olaf Korn
+for their extremely useful comments and suggestions.  }
+  }
     \date{}
@@
 \end{abstract}
+
+\newpage
+
+\textbf{Disclosure}
+
+\begin{itemize}
+\tightlist
+\item
+  Devraj Basu: I am a co-author of this paper and wish to state that I
+  have no conflict of interest, financial or otherwise. I do not hold
+  paid or unpaid positions at any organization whose goals relate to the
+  article.\\
+  \includegraphics{pics/signature - Devraj.png}\\
+\end{itemize}
+
+\newpage
+
+\textbf{Disclosure}
+
+\begin{itemize}
+\tightlist
+\item
+  Olivier Bauthéac: I am a co-author of this paper and wish to state
+  that I have no conflict of interest, financial or otherwise. I do not
+  hold paid or unpaid positions at any organization whose goals relate
+  to the article.\\
+  \includegraphics{pics/signature - Olivier.png}\\
+\end{itemize}
 
@@
 investors\footnote{See section \ref{background} for a detailled
-  discussion.}. In response to immediate policy concerns the academic
+  discussion.}. In response to immediate policy concerns, the academic
 debate was initially framed rather narrowly. In this paper we take a
@@
 pricing framework is well suited to detect these more subtle effects
-driven by changes in the nature of traders. Factor models are well
-suited to isolating common driving factors and detecting co-movement and
-building on theory we develop a bespoke commodity-based asset pricing
-framework that seems well adapted to study these two issues
-simultaneously.
+driven by changes in the nature of traders. Factor model techniques are
+well suited to isolating common driving factors and detecting
+co-movement and building on theory we develop a bespoke commodity-based
+asset pricing framework that seems well adapted to study these two
+issues simultaneously.
 
@@
   point based on earlier studies
-  \citep{baker_financialization_2014, christoffersen_factor_2018}.}; the
+  \citep{baker_financialization_2014, christoffersen_factor_2014}.}; the
 third, 2008/2013, encompasses both the financial crisis and the loose
@@
 
-The arrival of financial investors raises the question of whether they
-functioned as liquidity providers or liquidity demanders. Arguments have
-been made for both sides with \citet{moskowitz_time_2012} arguing that
-financial investors provide liquidity while
-\citet{Kangtaletwopremiums2017} argue that they demand liquidity with
-\citet{cheng_convective_2014} showing that they in fact transferred risk
-to hedgers during the 2008 financial crisis. We study this issue by
-extending the Keynesian individual hedging pressure paradigm by
-incorporating aggregate CHP (\textbf{CHP}), a market wide measure of
-hedging pressure first considered in \citet{hong_what_2012}. Our use of
-this measure is motivated by the cross sectional nature of
-financialization
-\citep{basak_model_2016, cheng_convective_2014, le_futures_2017}. This
-paradigm implies that returns for individual commodities should be high
-in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in
-periods where \textbf{CHP} is high (\textbf{contango}). Over the first
-period the cross sectional average returns during \textbf{backwardation}
-for both the US and UK commodities are positive with those for the US
+The cross-sectional nature of financialization
+\citep{basak_model_2016, cheng_financialization_2014} leads us to extend
+the Keynesian individual hedging pressure paradigm by incorporating
+aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure
+first considered in \citet{hong_what_2012}. This paradigm implies that
+returns for individual commodities should be high in periods where
+\textbf{CHP} is low (\textbf{backwardation}) and low in periods where
+\textbf{CHP} is high (\textbf{contango}). Over the first period the
+cross sectional average returns during \textbf{backwardation} for both
+the US and UK commodities are positive with those for the US
 statistically significant, and significantly higher than during
@@
 pattern suggests that the onset of financialization altered the
-traditional risk shifting nature of hedger's behaviour implied by the
-Keynesian hypothesis and suggests that financial investors may have been
-liquidity demanders during financialization leading hedgers to become
+traditional risk shifting nature of hedger's behaviour, which is implied
+by the Keynesian hypothesis. The arrival of financial investors raises
+the question of whether they functioned as liquidity providers or
+liquidity demanders. Arguments have been made for both of these
+possibilities with \citet{moskowitz_time_2012} arguing that financial
+investors provide liquidity while \citet{Kangtaletwopremiums2017} argue
+that they demand liquidity. Our analysis of returns in periods of low
+and high aggregate CHP before and during financialization allows us to
+analyse this issue from a new perspective and suggests that financial
+investors may have been liquidity demanders leading hedgers to become
 liquidity providers.
@@
 latter set of commodities. The market based factor outperforms the other
-three in the first period while the CHP factor shows the greatest
-improvement in performance in the second period with a four-fold
-increase in pricing performance. The performance of the market factor is
-driven by agricultural commodities and metals in both the first and
-second period and the dramatic improvement of the CHP factor in the
-second period is driven by precious and precious-base metals. The best
-performing commodities for the market factor exhibited approximately the
-same level of price co-movement both before and during financialization.
-In contrast, the best performing commodities for the CHP factor
-exhibited very low pair-wise correlation in the first period, around the
-average for US traded commodities, while during financialization the
-average pairwise correlation between the top performing CHP factor
-commodities is higher than that for the market factor and double of the
-average for all the US traded commodities. This increase is due to the
-dramatic rise in average pairwise correlation amongst the US traded
-metals all of which exhibited high R\textsuperscript{2} with respect to
-the CHP factor during financialization which in turn is due to their
-common low level of CHP over this period. Thus the CHP factor model is
-able to establish the strengthening link between a non-price attribute
-and price dynamics in the US metal sub-sector during financialization.\\
+three in the first period and it has a similar level of performance in
+the second period, while the CHP factor shows the greatest improvement
+in performance in the second period. The performance of the market
+factor is driven by agricultural commodities and metals in both the
+first and second period and the dramatic improvement of the CHP factor
+in the second period is driven by precious and precious-base metals. The
+best performing commodities for the market factor exhibited
+approximately the same level of price co-movement both before and during
+financialization. In contrast, the best performing commodities for the
+CHP factor exhibited very low pair-wise correlation in the first period,
+around the average for US traded commodities, while during
+financialization the average pairwise correlation between the top
+performing CHP factor commodities is higher than that for the market
+factor and double of the average for all the US traded commodities. This
+increase is due to the dramatic rise in average pairwise correlation
+amongst the US traded metals all of which exhibited high
+R\textsuperscript{2} with respect to the CHP factor during
+financialization which in turn is due to their common low level of CHP
+over this period. Thus the CHP factor model is able to establish the
+strengthening link between a non-price attribute and price dynamics in
+the US metal sub-sector during financialization.\\
 We explore this issue further by constructing the four factors with the
@@
 period\footnote{See section \ref{methods} for further details.} and
-evaluating their performance on these selected commodities as well as on
+evaluating its performance on these selected commodities as well as on
 all US traded commodities. The results of this exercise strongly suggest
@@
 the four factors on the six UK metals, when constructed from each set of
-factor picks. The results show that there was co-movement in global
+factor picks. The resuslts show that here was co-movement in global
 metals returns in the second period and that this co-movement could be
@@
 with the pattern of return for the US traded commodities across
-\textbf{CHP} regimes reverting to the Keynesian paradigm. The pricing
+\textbf{CHP} regimes reverting to Keynesian paradigm. The pricing
 results indicate the emergence of a systematic factor across the entire
@@
 
-Commodity financialization raised societal concerns, leading to
-legislative action intended to alter the nature and functioning of these
-markets. The debate was initially framed around adequacy of speculation,
-the burning issue of the day, and the consequent analysis focused on the
-more mechanical effects of financialization. With the benefit of
-hindsight, it appears this approach was perhaps too narrow and it now
-seems necessary to address financialization from a broader perspective.
-Commodity price dynamics appear to have altered substantially in quite
-different ways over the financialization and the financial crisis
-periods and our commodity futures based asset pricing approach seems
-able to provide new insights into the nature of these changes:
-financialization was a phenomenon endogenous to the commodity markets
-transmitted via the commodity futures markets and mainly concentrated in
-a specific sector (metals) while the crisis and its aftermath seems to
-have delivered an exogenous shock across the entire cross-section of
-global commodities. We provide an empirical complement to a new stream
-of theoretical studies that try to model the impact of financialization
-on various aspects of commodity futures markets\footnote{\citet{etula_broker-dealer_2013},
+Financialization was an issue of such policy importance that it
+triggered legislative action. The debate was initially framed around
+adequacy of speculation, the burning issue of the day, and the
+consequent analysis focused on the more mechanical effects of
+financialization. With the benefit of hindsight, it appears this
+approach was perhaps too narrow and it now seems necessary to address
+financialization from a broader perspective. Commodity price dynamics
+appear to have altered substantially in quite different ways over the
+financialization and the financial crisis periods and our commodity
+futures based asset pricing approach seems able to provide new insights
+into the nature of these changes: financialization was a phenomenon
+endogenous to the commodity markets transmitted via the commodity
+futures markets and mainly concentrated in a specific sector (metals)
+while the crisis and its aftermath seems to have delivered an exogenous
+shock across the entire cross-section of global commodities. The initial
+view of financialization was that it consisted of speculative flows
+which had the effect of driving up and creating bubble like conditions
+in commodity future prices\footnote{\citet{de_schutter_food_2010_1};
+  \citet{gilbert_how_2010}; \citet{gilbert_speculative_2010};
+  \citet{masters_testimony_2008}; \citet{masters_accidental_2008};
+  \citet{herman_not_2011_1}; \citet{schumann_hunger-makers_2011};
+  \citet{singleton_investor_2013}; \citet{unctad_global_2009}.}.
+However, the fundamental question of the nature of the impact of
+financialization across the entire cross-section of commodity futures
+markets has not yet been completely answered. We provide an empirical
+complement to a new stream of theoretical studies that try to model the
+impact of financialization on various aspects of commodity futures
+markets\footnote{\citet{etula_broker-dealer_2013},
   \citet{acharya_limits_2013}, \citet{cheng_convective_2014},
   \citet{leclercq_equilibrium_2014}, \citet{sockin_informational_2015},
-  \citet{goldstein_speculation_2014},
+  \citet{goldstein_speculation_2013},
   \citet{EkelandSpeculationcommodityfutures2016},
-  \citet{goldstein_commodity_2017} as well as \citet{le_futures_2017},
-  one of the few empirical studies on the impact of financialization on
-  commodity-price cross-moments.} and demonstrate that the effects of
+  \citet{goldstein_commodity_2017}.} and demonstrate that the effects of
 financialization extend beyond the mechanical effects induced by
@@
 index linked products most of which made its way into the commodity
-futures market. Exposure to commodity indexes whose goal was to track
-the broad movement of commodity prices could be accessed by means of
-exchange traded funds and exchange traded notes and at least \$100
-billion of new investment flowed into these products over the 1998-2008
-period with this financialization phenomenon leading to substantial
-legislative changes. Concerns over the consequences of financialization
-were behind Rule 76 FR 4752 issued by the US Commodity Futures Trading
-Commission (CFTC) on January 26\textsuperscript{th}, 2011. This
-provision emanates from the Dodd-Frank Wall Street and Consumer
-Protection Act of 2010 (Title VII, Section 737) that mandates the CFTC
-to use position limits to restrict the flow of speculative capital into
-a number of commodity markets. The Rule was approved in a close 3-2 vote
-and the ensuing rulemaking process was extremely contentious with
-several commissioners (Michael Dunn and Scott D. O'Malia in particular)
-expressing reservations about the lack of supporting evidence and the
-Rule also triggering thousands of comment letters as well as a lawsuit
-against the CFTC spearheaded by two Wall Street trade groups, the
-International Swaps \& Derivatives Association (ISDA) and the Securities
-Industries \& Financial Markets Association (SIFMA)\footnote{ISDA \&
-  SIFMA v US CFTC; Complaint, 1:11-cv-02146; December
-  2\textsuperscript{nd}, 2011.}.
+futures market. These commodity indexes whose goal was to track the
+broad movement of commodity prices could be accessed by means of
+exchange traded funds and exchange traded notes. At least \$100 billion
+of new investment flowed into these products over the 1998-2008 period
+with this financialization phenomenon leading to substantial legislative
+changes. Concerns over the consequences of financialization were behind
+Rule 76 FR 4752 issued by the US Commodity Futures Trading Commission
+(CFTC) on January 26\textsuperscript{th}, 2011. This provision emanates
+from the Dodd-Frank Wall Street and Consumer Protection Act of 2010
+(Title VII, Section 737) that mandates the CFTC to use position limits
+to restrict the flow of speculative capital into a number of commodity
+markets. The Rule was approved in a close 3-2 vote and the ensuing
+rulemaking process was extremely contentious with several commissioners
+(Michael Dunn and Scott D. O'Malia in particular) expressing
+reservations about the lack of supporting evidence and the Rule also
+triggering thousands of comment letters as well as a lawsuit against the
+CFTC spearheaded by two Wall Street trade groups, the International
+Swaps \& Derivatives Association (ISDA) and the Securities Industries \&
+Financial Markets Association (SIFMA)\footnote{ISDA \& SIFMA v US CFTC;
+  Complaint, 1:11-cv-02146; December 2\textsuperscript{nd}, 2011.}.
 
@@
 in both futures and cash prices
-\citep{masters_testimony_2008, masters_accidental_2008}. This contention
-has since come to be known as the Masters' hypothesis and was largely
-endorsed by the final US Senate report on the issue
+\citep{masters_testimony_2008, masters_accidental_2008}). This
+contention has since come to be known as the Masters' hypothesis and was
+largely endorsed by the final US Senate report on the issue
 \citep{USSenate_Excessive_speculation_wheat_2009}. At this stage, the
@@
 crisis and its aftermath, spanning the 2008/2013 period. The last period
-spans the 2014/present period starting with the beginning of the
+spans the 2014/present period sarting with the beginning of the
 tapering/end of the US Quantitative Easing program (QE).\\
@@
 considered for mimicking portfolio construction where the ordering rule
-is factor specific (\(f_{i}\)).
+is specific to \(f_{i}\).
 
@@
 factor model cases, where regressors include in turn all combinations of
-any two and three risk factors respectively, as well as for the four
+any two and three risk factors respectivly, as well as for the four
 (\(p=4\)) factor model case where all the risk factor mimicking
@@
 All of the six UK metals achieved higher mean returns over
-\textbf{backwardation} than \textbf{contango} with the difference being
+\textbf{backwardation} than contango with the difference being
 statistically significant for one commodity. The equally weighted US
@@
 noted in earlier theoretical and empirical work
-\citep{DanthineInformationfuturesprices1978, stout_why_1998} in
+\citep[\citet{stout_why_1998}]{DanthineInformationfuturesprices1978} in
 different context from which two competing models of behaviour have
@@
 returns were negatively correlated with the rest of US traded
-commodities in the first period and positively in the second (results
+commodities in the first period and positively in the second (Results
 available upon request).
@@
 the average CHP factor picks where the market factor built from these
-picks has an average R\textsuperscript{2} of 21.3\% in the first period
-and jumps to 37.4\% in the second period indicating much high
-co-movement. The average CHP factor built with average CHP factor picks
-also shows a sharp increase in pricing performance over the second
+picks has an average R\textsuperscript{2} of 21.3 \% in the first period
+(close to the 0 correlation situation) and jumps to 37.4 \% in the
+second period. The average CHP factor built with average CHP factor
+picks also shows a sharp increase in pricing performance over the second
 period. There is also substancial improvement in pricing performance of
@@
 predominantly metals.\\
-The results from Tables \ref{table6} and \ref{table7} show that the
+The conclusion from Tables \ref{table6} and \ref{table7} is that the
 onset of financialization seems to have had a major impact on the
@@
 significant changes in commodity pricing dynamics and our analysis
-suggests that in contrast with financialization, the crisis and its
+suggest that in contrast with financialization, the crisis and its
 aftermath have delivered an exogenous shock across the entire

### 2024-06-11 others/paper/custom/title page.Rmd
Track 'others' folder

--- 2024-06-11 others/paper/custom/main.Rmd
@@
   - name: Devraj Basu
-    surname: Basu
+    surname: Basu (corresponding author)
     email: devraj.basu@strath.ac.uk
@@
 
-jel: G11, G23, G13, Q02
-keywords: Commodity futures, financialization, hedging pressure, financial crisis
-
 acknowledgements: |
@@
 
-abstract: |
-  The last two decades have seen major changes in the nature of the commodity markets with the influx of financial investor inflows followed by the financial crisis.
-We study the effect of these events on commodity futures pricing dynamics using commodity asset pricing techniques.
-We find that a non-price based factor is best able to detect the effects of commodity financialization, while the effects of the financial crisis and after are most clearly visible through the performance of the market factor.
-The effects of financialization seem to go beyond mechanical effects induced by the rise of indexing.
-
 ---
-
-```{r, echo = FALSE, message = FALSE}
-packages <- c("tidyr", "magrittr", "knitr", "lettercase", "tinytex", "bookdown", "kableExtra", "here")
-invisible(sapply(packages, require, character.only = TRUE))
-options(knitr.table.format = "latex")
-knitr::opts_chunk$set(echo = FALSE, results = "asis")
-tickers <- readRDS(file = file.path(here::here(), "data", "tickers.rds"))
-tables <- readRDS(file = file.path(here::here(), "explore", "results", "tables.rds.rds"))
-
-```
 
@@
 \newpage
-
-# Introduction
-
-The last twenty years have seen major upheavals in the commodity markets with the onset of financialization^[Starting around 2004, with a view of commodity markets as an emerging asset class and in an effort to hedge against inflation and seek diversification benefits [@buyuksahin_speculators_2014; @singleton_investor_2013], institutional investors sent forth an unprecedented flow of capital into commodity futures markets.
-This phenomenon is commonly referred to as the financialization of commodities [@domanski_financial_2007].] as well as the period of the 2008 financial crisis and its aftermath.
-Financialization appears to have affected a number of economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres.
-A vigorous legislative debate has led to regulatory changes accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section \ref{background} for a detailled discussion.].
-In response to immediate policy concerns, the academic debate was initially framed rather narrowly.
-In this paper we take a fundamentally different empirical approach that is broader in scope.
-We consider the entire cross-section of actively traded commodities on futures markets and use a futures based asset pricing framework that includes factors constructed using both price and non-price attributes.
-
-Commodity futures markets have a history of being the classic physical commodity risks shifting conduit for commodity specialists, and financialization may have altered this long standing paradigm with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants.
-This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of traders.
-Factor model techniques are well suited to isolating common driving factors and detecting co-movement and building on theory we develop a bespoke commodity-based asset pricing framework that seems well adapted to study these two issues simultaneously.
-
-The first factor model we consider (CHP) is based on the well-known hedging pressure based theory [@anderson_hedger_1983; @chang_returns_1985; @cootner_returns_1960; @dusak_futures_1973; @hicks_value_1939; @hirshleifer_risk_1988; @hirshleifer_determinants_1989; @hirshleifer_hedging_1990; @kolb_is_1992; @keynes_treatise_1930] which postulates that futures prices for a given commodity are inversely related to the extent that commercial hedgers are short or long and we use a factor mimicking portfolio that captures the impact of hedging pressure as a systemic factor [@basu_capturing_2013].
-Our second factor model is based on open interest growth following @hong_what_2012 who find that open interest growth has predictive power for individual commodity returns and again we construct a long-short factor mimicking portfolio.
-Our third model is based on term structure following @szymanowska_anatomy_2014 and @fuertes_commodity_2015 who demonstrate that the term structure factor has explanatory power for the cross-section of commodity returns.
-We finally consider an equally weighted portfolio of commodities as a proxy for the market factor.
-Our two price based and two non-price based factors allow us to compare and contrast different channels that could have led to changes in commodity price dynamics over the last twenty years.
-
-We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (LME exchange) base metals over the 1997/2017 period that we divide into four distinct sub-periods.
-The first, the pre-financialization phase, spans the 1997/2003 period; the second, the financialization phase, spans the 2004/2007 period^[Starting point based on earlier studies [@baker_financialization_2014; @christoffersen_factor_2014].]; the third, 2008/2013, encompasses both the financial crisis and the loose monetary policy regimes that followed; and the fourth spans the period starting in 2014 to present.
-Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialization period compared to pre-financialization and this pattern extends to UK traded metals.
-
-The cross-sectional nature of financialization [@basak_model_2016; @cheng_financialization_2014] leads us to extend the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in @hong_what_2012.
-This paradigm implies that returns for individual commodities should be high in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in periods where \textbf{CHP} is high (\textbf{contango}).
-Over the first period the cross sectional average returns during \textbf{backwardation} for both the US and UK commodities are positive with those for the US statistically significant, and significantly higher than during \textbf{contango}, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
-Over the second period this pattern reverses, with both the US and UK commodities having significant positive returns during \textbf{contango} with these returns being significantly higher than during \textbf{backwardation}.
-This change in pattern suggests that the onset of financialization altered the traditional risk shifting nature of hedger’s behaviour, which is implied by the Keynesian hypothesis.
-The arrival of financial investors raises the question of whether they functioned as liquidity providers or liquidity demanders.
-Arguments have been made for both of these possibilities with @moskowitz_time_2012 arguing that financial investors provide liquidity while @Kangtaletwopremiums2017 argue that they demand liquidity.
-Our analysis of returns in periods of low and high aggregate CHP before and during financialization allows us to analyse this issue from a new perspective and suggests that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
-
-@goldstein_commodity_2017 as well as @goldstein_speculation_2014 argue that the arrival of financial investors has an impact on the extent of normal backwardation in commodity futures markets.
-Based on their analysis we would expect our average CHP factor, which is based on backwardation measured by hedger’s positions, as well our term structure factor, which is based on backwardation measured by roll yield, to be best suited to measure the impact of financialization.
-We analyze the pricing dynamics over the different periods by first studying the time series pricing performance of the various factors on all the US traded commodities with the factors constructed using the latter set of commodities.
-The market based factor outperforms the other three in the first period and it has a similar level of performance in the second period, while the CHP factor shows the greatest improvement in performance in the second period.
-The performance of the market factor is driven by agricultural commodities and metals in both the first and second period and the dramatic improvement of the CHP factor in the second period is driven by precious and precious-base metals.
-The best performing commodities for the market factor exhibited approximately the same level of price co-movement both before and during financialization.
-In contrast, the best performing commodities for the CHP factor exhibited very low pair-wise correlation in the first period, around the average for US traded commodities, while during financialization the average pairwise correlation between the top performing CHP factor commodities is higher than that for the market factor and double of the average for all the US traded commodities.
-This increase is due to the dramatic rise in average pairwise correlation amongst the US traded metals all of which exhibited high R^2^ with respect to the CHP factor during financialization which in turn is due to their common low level of CHP over this period.
-Thus the CHP factor model is able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialization.
-We explore this issue further by constructing the four factors with the top eight commodities for a given factor (factor picks) in each period^[See section \ref{methods} for further details.] and evaluating its performance on these selected commodities as well as on all US traded commodities.
-The results of this exercise strongly suggest that the hedging pressure co-movement and price co-movement link was concentrated in the metals sub-sector.
-
-The UK traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialization.
-To that end, we examine the performance of the four factors on the six UK metals, when constructed from each set of factor picks.
-The resuslts show that here was co-movement in global metals returns in the second period and that this co-movement could be detected by our hedging pressure based model.
-
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in pricing dynamics.
-Returns on both US and UK traded commodities fell dramatically over both the third and fourth periods with the pattern of return for the US traded commodities across \textbf{CHP} regimes reverting to Keynesian paradigm.
-The pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as strong evidence of cross-market linkages.
-
-Financialization was an issue of such policy importance that it triggered legislative action.
-The debate was initially framed around adequacy of speculation, the burning issue of the day, and the consequent analysis focused on the more mechanical effects of financialization.
-With the benefit of hindsight, it appears this approach was perhaps too narrow and it now seems necessary to address financialization from a broader perspective.
-Commodity price dynamics appear to have altered substantially in quite different ways over the financialization and the financial crisis periods and our commodity futures based asset pricing approach seems able to provide new insights into the nature of these changes: financialization was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and mainly concentrated in a specific sector (metals) while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of global commodities.
-The initial view of financialization was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity future prices^[@de_schutter_food_2010_1; @gilbert_how_2010; @gilbert_speculative_2010; @masters_testimony_2008; @masters_accidental_2008; @herman_not_2011_1; @schumann_hunger-makers_2011; @singleton_investor_2013; @unctad_global_2009.].
-However, the fundamental question of the nature of the impact of financialization across the entire cross-section of commodity futures markets has not yet been completely answered.
-We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialization on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2013, @EkelandSpeculationcommodityfutures2016, @goldstein_commodity_2017.] and demonstrate that the effects of financialization extend beyond the mechanical effects induced by indexation as outlined in @basak_model_2016 as well as @tang_index_2012.
-
-# Data & methods {#data-methods}
-
-## Background {#background}
-
-The period from 1998 to 2008 saw an influx of investment into commodity index linked products most of which made its way into the commodity futures market.
-These commodity indexes whose goal was to track the broad movement of commodity prices could be accessed by means of exchange traded funds and exchange traded notes.
-At least \$100 billion of new investment flowed into these products over the 1998-2008 period with this financialization phenomenon leading to substantial legislative changes.
-Concerns over the consequences of financialization were behind Rule 76 FR 4752 issued by the US Commodity Futures Trading Commission (CFTC) on January 26^th^, 2011.
-This provision emanates from the Dodd-Frank Wall Street and Consumer Protection Act of 2010 (Title VII, Section 737) that mandates the CFTC to use position limits to restrict the flow of speculative capital into a number of commodity markets.
-The Rule was approved in a close 3-2 vote and the ensuing rulemaking process was extremely contentious with several commissioners (Michael Dunn and Scott D.
-O’Malia in particular) expressing reservations about the lack of supporting evidence and the Rule also triggering thousands of comment letters as well as a lawsuit against the CFTC spearheaded by two Wall Street trade groups, the International Swaps & Derivatives Association (ISDA) and the Securities Industries & Financial Markets Association (SIFMA)^[ISDA & SIFMA v US CFTC; Complaint, 1:11-cv-02146; December 2^nd^, 2011.].
-
-A world-wide debate has ensued about the role of index funds in commodity markets.
-The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs [@de_schutter_food_2010_1; @gilbert_speculative_2010; @herman_not_2011_1; @schumann_hunger-makers_2011; @unctad_global_2009].
-The US and various european countries also became involved in this issue.
-Early US Senate investigations drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US wheat markets to the observed surges in both futures and cash prices [@masters_testimony_2008; @masters_accidental_2008]).
-This contention has since come to be known as the Masters’ hypothesis and was largely endorsed by the final US Senate report on the issue [@USSenate_Excessive_speculation_wheat_2009].
-At this stage, the question thrust on the academic sphere was whether “excessive speculation” (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices.
-A number of academic studies, most of which used commodity specific causality and correlation based analysis have disproved this contention, particularly in the case of agricultural and energy commodities.
-@irwin_devil_2009, @sanders_adequacy_2010, @sanders_impact_2011, @sanders_new_2011, @irwin_commodity_2013, @brunetti_commodity_2014, @hamilton_effects_2015 and @bruno_financialization_2017 study the agricultural markets.
-@buyuksahin_speculators_2011, @tokic_speculation_2012, @fattouh_role_2013, @kilian_role_2014, @knittel_simple_2016 and @manera_modelling_2016 study the energy markets.
-@bohl_does_2013_2, @kim_does_2015 and @boyd_prevalence_2016 study both energy and agricultural markets while @irwin_index_2011, @irwin_financialization_2012 and @stoll_commodity_2011 study the commodity markets in general.
-
-Other studies have underlined various alterations in commodity pricing dynamics over the period.
-@gilbert_role_2014 reject the view that financialization has not had any effects in the grains markets and demonstrate that trades originated by financial actors, and specifically index investors, can move prices but tend typically to be volatility-reducing.
-@cheng_financialization_2014 show that in the case of index commodities, financialization has transformed the risk sharing, and information discovery functions of commodity futures markets.
-@juvenal_speculation_2015 contend that the oil price increase between 2004 and 2008 was mainly driven by the strength of global demand but that the financialization process of commodity markets also played a role.
-@henderson_new_2015 show that non-information-based financial investments have important impacts on commodity prices.
-
-## Data {#data}
-
-Commodity index funds (CIFs), commodity based exchange traded funds (ETFs) and notes (ETNs) as well as commodity linked notes (CLNs) were amongst the main investment vehicules that allowed institutional and retail investors to build up commodity exposure in the early 2000s [@boons_stock_2012; @henderson_new_2015; @irwin_index_2011; @unctad_global_2009; @schumann_hunger-makers_2011].
-Most of these products were primarily designed to track prominent commodity indexes amongst which the S&P-GSCI, the most popular.
-Most of its constituents at the time of writting form the basis of the broad cross-section of commodities that we consider in this study^[See section \ref{assets} for details on the commodity pool considered.].
-Unleaded gasoline, the NYMEX legacy contract for gasoline stopped trading in 2006 when it was replaced by Reformulated Gasoline Blendstock for Oxygen Blending (RBOB) with the two futures series trading alongside for most of the year.
-For our NYMEX gasoline data series, we consider unleaded gasoline up to September 1^st^, 2006 and RBOB gasoline thereafter, date at which liquidity for the latter overtook that for the former.
-
-The commodity futures trading commission (CFTC) operates a comprehensive system of collecting information on market participants known as the large trader reporting program (LTRP) where it records and reports to the public market position data on market particpants who have position levels in excess of a particular futures market specific threshold^[Current reporting level thresholds available at: [www.ecfr.gov](https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=&SID=970471b8455f4bab7db4110cfde50731&mc=true&r=SECTION&n=se17.1.15_103).].
-The commission collects market data and position information daily from clearing members, futures commission merchants (FCMs) and foreign brokers and publishes corresponding summaries weekly in a series of market specific reports.
-In these reports, individual traders are categorised according to the nature of their trading activity on the basis of self-reported information^[CFTC form 40.
-Available at: [www.cftc.gov](https://www.cftc.gov/sites/default/files/idc/groups/public/@forms/documents/file/cftcform40.pdf).] that is subject to review by CFTC staff for reasonableness.
-Position information is then aggregated by category and asset type with each report providing an aggregation for a set of report specific categories and, for each category, a breakdown between futures only positions and positions in futures and options combined.
-In its legacy report, the commitment of trader report (COT) with data dating back to 1962, the CFTC distinguishes "commercial" and "non-commercial" market participants where a "commercial" participant is defined as one "[...] engaged in business activities hedged by the use of futures and option markets"^[See [CFTC regulation 1.3, 17 CFR 1.3(z)](https://www.gpo.gov/fdsys/pkg/CFR-1998-title17-vol1/xml/CFR-1998-title17-vol1-sec1-3.xml) for details.].
-A third category, "non-reportable", aggregates positions for participants not meeting the reporting threshold.
-In response to concerns related to category accuracy^[See for example @ederington_who_2002.] the CFTC now refines its classification in the disaggregated commitment of trader report (DCOT) where participant categories include "Producer/Merchant/Processor/User", "Swap dealer", "Money manager" and "Other reportable" as well as in the supplemental commitment of trader report (SCOT) that details commodity index trader aggregate positions for thirteen agricultural commodity futures markets.
-Data for DCOT and SCOT dates back to 2006 and 2007 respectively.
-We study the 1997/2017 period where we observe futures only position data from the COT report, the only CFTC report with data available for the whole period of interest; as well as futures term structure price and open interest data from Bloomberg.
-
-## Methods {#methods}
-
-On the one hand, futures markets have a long history of serving commodity producers to allievate their commodity price and output risks.
-@keynes_treatise_1930 and @hicks_value_1939 emphasise the "normal" behaviour of naturally short hedgers outsourcing their commodity risk to naturally long commodity specialist speculators.
-This market configuration is referred to as "backwardation" where futures is expected to trade at a discount to spot, providing speculators with incentives to take the long side.
-The opposite market paradigm is referred to as "contango".
-Working [@working_theory_1948; @working_hedging_1953] and Cootner [@cootner_returns_1960; @CootnerSpeculationhedging1967] somehow relax this "supply-of-speculative-services" [@Tilllongtermperspectivecommodity2007] approach by introducing processors and merchants, also commodity experts, on the hedgers side and relating the notions of backwardation and contango more directly to the term structure via the theory of storage where the shape of the front end of the term structure (basis) is directly related to the market price of storage.
-Financialization, on the other hand, refers to the entry of financial investors into the commodity futures markets who, for the most part, are not commodity experts.
-Besides, these new market participants tend to exhibit herding like behaviour, often taking massive long-only positions on the whole cross-section of indexed commodities in an attempt to hedge against inflation and/or seek further diversification benefits for portfolios with, in most cases, existing large positions across various asset classes [@brunetti_speculators_2016; @boyd_prevalence_2016; @cheng_convective_2014; @juvenal_speculation_2015; @singleton_investor_2013; @tang_index_2012].
-This contrasts with the traditional approaches of Keynes and Working and in this context the issues of co-movement and aggregate market participants behaviour seem particularly relevant.
-Asset pricing techniques are well suited to study co-movement.
-Building on theory we develop an ad-hoc commodity based asset pricing framework that we believe is well adapted to study these two issues simultaneously and implement it over four periods of interest.
-The first, the pre-financialization period, starts in 1997 and is naturally followed by financialization, spanning the 2004/2007 period, and the financial crisis and its aftermath, spanning the 2008/2013 period.
-The last period spans the 2014/present period sarting with the beginning of the tapering/end of the US Quantitative Easing program (QE).
-Using the weekly price, open interest and market position data described above we construct market portfolios of commodity nearby futures as well as mimicking portfolios for market, commercial hedging pressure, term structure and liquidity risk factors in returns.
-While our market portfolios are long only, equally weighted portfolios of particular commodity sets, our other mimicking portfolios for risk factors are constructed as combinations of two sub-portfolios (legs), one held long, one held short, which respective constituents are pooled on a weekly basis according to risk factor specific criterias.
-The weekly return for a particular mimicking portfolio is calculated as the difference between the average return for constituents of the long portfolio and that for the constituents of the short portfolio.
-i.e, return on the mimicking portfolio for risk factor $i$ ($f_{i}$) for week $t$:
-
-$$r_{t}^{f_{i}}=\frac{1}{x}\sum_{j=1}^{x}r_{j,t}-\frac{1}{x}\sum_{j=n-x}^{n}r_{j,t}$$
-$n\equiv$ number of commodities in the set considered for mimicking portfolio construction.  
-$x = \left \lceil n \cdot s \right \rceil$  
-$s\equiv$ selection threshold ($\frac{1}{3}$ here).  
-$r_{j,t}=\frac{C_{j,t}}{C_{j,t-1}}-1$  
-$C_{j,t}\equiv$ week $t$ close price for commodity $j$.  
-$j\equiv$ commodity rank in the ordered set $Y_{t}^{f_{i}}$.  
-$Y_{t}^{f_{i}}\equiv$ week $t$ ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is specific to $f_{i}$.
-
-For our portfolio CHP (commercial hedging pressure), we sort the set of commodities considered on past twenty six-week average CHP from lowest to highest.
-The bottom third constituents (lowest $\overline{CHP}$s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg:
-
-$$Y_{t}^{CHP}\equiv\left \{ \left \{ \overline{CHP_{1}}, \overline{CHP_{2}}, ..., \overline{CHP_{n}} \right \}, \leq \right \}$$
-
-$\overline{CHP_{j}}=\frac{1}{26}\sum_{k=0}^{25}\frac{L_{j,t-k}}{L_{j,t-k}+S_{j,t-k}}$  
-$L_{j,t}\equiv$ number of long positions held by commercial hedgers for week $t$ on the futures series of commodity $j$.  
-$S_{j,t}\equiv$ number of short positions held by commercial hedgers for week $t$ on the futures series of commodity $j$.
-
-For our portfolio TS (term structure), we sort the set of commodities considered on past twenty six-week average roll-yield from highest to lowest.
-The bottom third constituents (highest $\overline{RY}$s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg:
-
-$$Y_{t}^{TS}\equiv\left \{ \left \{ \overline{RY_{1}}, \overline{RY_{2}}, ..., \overline{RY_{n}} \right \}, \geq \right \}$$
-
-$\overline{RY_{j}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{F_{j,t-k}^{1}}{F_{j,t-k}^{2}} - 1)$   
-$F_{j,t}^{1}\equiv$ week $t$ close price for commodity $j$ first nearby futures contract.  
-$F_{j,t}^{2}\equiv$ week $t$ close price for commodity $j$ second nearby futures contract.
-
-For our portfolio OI (open interest), we sort the set of commodities considered on past twenty six-week average aggregate open interest growth from highest to lowest.
-The bottom third constituents (highest $\overline{\mathbf{OI}^{\Delta \%}}$s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg.
-
-$$Y_{t}^{OI}\equiv\left \{ \left \{ \overline{\mathbf{OI}_{1}^{\Delta \%}}, \overline{\mathbf{OI}_{2}^{\Delta \%}}, ..., \overline{\mathbf{OI}_{n}^{\Delta \%}} \right \}, \geq \right \}$$
-
-$\overline{\mathbf{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{\mathbf{OI}_{j,t-k}}{\mathbf{OI}_{j,t-k-1}} - 1)$  
-$\mathbf{OI}_{j,t}=\sum_{k=1}^{l_{j,t}}OI_{j,t,k}$  
-$OI_{j,t,k}\equiv$ open interest at close of week $t$ for the $k^{th}$ nearby contract on the futures term structure for commodity $j$.  
-$l_{j,t}\equiv$ length of commodity $j$'s futures term structure on week $t$ close.
-
-We use a time series regression approach where we start with regressions of the US traded individual commodity weekly front returns on returns to the mimicking portfolio for a particular risk factor where the portfolio is constructed using the whole cross-section of US traded commodities.
-The corresponding adjusted $R^{2}$s are averaged and the process is repeated for each of our four risk factors (market, hedging pressure, term structure and liquidity) and periods (1997/2003, 2004/2007, 2008/2013 and 2014/2017).
-i.e, average adjusted $R^{2}$ for risk factor $i$ ($f_{i}$) over period $t$:
-
-$$\overline{\tilde{R}_{f_{i},t}^{2}}=\frac{1}{24}\sum_{j=1}^{24}\tilde{R}_{j,t}^{2}$$
-$\tilde{R_{j}^{2}}=1-(1-R_{j}^{2})\frac{T-1}{T-p-1}$^[The Wherry formula-1.]  
-$T\equiv$ length of period $t$ (number of weeks here).  
-$p\equiv$ number of regressors (1 here).  
-$R_{j,t}^{2}=1-\frac{\sum_{k=1}^{T}(y_{j,k}-\hat{y_{j,k}})^{2}}{\sum_{k=1}^{T}(y_{j,k}-\overline{y_{j}})^{2}}$  
-$y_{j,t}\equiv$ week $t$ nearby return for commodity $j$.   
-$\hat{y_{j,t}}=\beta_{0}+\beta_{1}f_{i,t}+\epsilon$  
-$\beta s \equiv$ classic OLS coefficient estimates.  
-$f_{i,t}\equiv$ week $t$ return on mimicking portfolio for risk factor $f_{i}$
-
-The same operation is repeated for the two ($p=2$) and three ($p=3$) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectivly, as well as for the four ($p=4$) factor model case where all the risk factor mimicking portfolios are included.
-Results are reported for the one-factor model case with the other results available from the authors upon request.
-For each period we also implement the analysis described above over periods of low and high aggregate CHP (\textbf{CHP}), a notion which we introduce in this study and which we believe is particularly relevant in the context of financialization where issues of co-movement and aggregate market participants' behaviour play a central role.
-We define \textbf{CHP} as the cross-sectional average of CHPs for a particular pool of assets.
-i.e, Week $t$ \textbf{CHP} for asset pool $x$:
-
-$$\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}$$
-$n\equiv$ number of commodities in set $x$.  
-$CHP_{i,t}\equiv$ week $t$ CHP for commodity $i$ as defined above.
-
-We further define aggregate backwardation (\textbf{backwardation}) and contango (\textbf{contango}) \textbf{CHP} regimes as, for a given period, \textbf{CHP} levels below and above the period's median respectively and, in contrast with [@hong_what_2012] who aggregate across sub-sectors, the asset pool we consider for \textbf{CHP} construction include the whole cross-section of US traded commodities.
-
-In the next part of the analysis, our mimicking portfolios for risk factors, constructed from the set of all US traded commodities are used as commodity picking devices on the latter commodity set.
-For each risk factor and period, individual US traded commodity front returns are regressed on returns for the corresponding mimicking portfolio.
-Individual commodities are sorted by adjusted $R^{2}$ ($\tilde{R^{2}}$) accordingly from highest to lowest and the bottom third (highest $\tilde{R^{2}}$s) are selected as commodity picks for the risk factor for the period.
-i.e, set of picks $P_{t}^{f_{i}}$ for risk factor $i$ ($f_{i}$) over period $t$:
-
-$$P_{t}^{f_{i}}\equiv\left \{ P_{1}, P_{2}, ..., P_{x} \right \}$$
-$x = \left \lceil n \cdot s \right \rceil$  
-$n\equiv$ number of commodities in the set considered for the picking excersise (twenty-four here).  
-$s\equiv$ selection threshold ($\frac{1}{3}$ here).  
-$P_{j}\equiv$ commodity pick $j$ for risk factor $f_{i}$ over period $t$  
-$j\equiv$ rank in the ordered set $Y_{t}^{f_{i}}$  
-$$Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}$$
-$n\equiv$ number of commodities in the set considered for picking (twenty-four here).   
-$\tilde{R_{j}^{2}}\equiv$  risk factor $f_{i}$ returns' explanatory power on commodity $j$ nearby futures returns over period $t$ as defined above.
-
-For each period and \textbf{CHP} regime we record the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every sets of picks.
-
-In the last part of the analysis, for each period our mimicking portfolios for risk factors in returns are constructed using each set of commodity picks independently as the asset pool for portfolio construction.
-A similar time series approach to that described above is then implemented using these newly formed mimicking portfolios.
-In this case, a first set of dependent variables includes the sets of commodity picks themselves, a second set includes the whole cross-section of US traded commodities while a third set includes the six UK traded metals considered.
-The latter are also used as dependent variables in the last series of regressions where the long and short legs of the newly formed risk factor mimicking portfolios described above are considered separately as regressors.
-
-# Results & discussion
-
-The descriptive statistics over the various time periods for our two sets of commodities (US and non-US) as well as the four factors considered are shown in Table \ref{table1}.
-The traditional Keynesian hedging pressure paradigm postulates a negative relationship between the return on an individual commodity and its hedging pressure.
-Financialization has been seen as a cross-sectional commodity market phenomenon; this naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure.
-The extended Keynesian hedging pressure paradigm should also imply that returns for individual commodities should be high in periods where \textbf{CHP} is low and vice et versa.
-In table \ref{table2} the mean returns are shown over high (\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP} regimes for each time period.
-Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of \textbf{backwardation} as compared to \textbf{contango}, with the difference being statistically significant at the 5% level for one commodity and for the remaining six commodities the higher mean return during \textbf{contango} is not statistically significant for any of them.
-For the six UK commodities, all metals, four of them had higher mean returns during phases of \textbf{backwardation} as compared to \textbf{contango} in the first period, with one of these differences being statistically significant at the 5% level while for the remaining two the higher mean return during \textbf{contango} is not statistically significant for either.
-An equally weighted portfolio of the twenty-four US commodities had a mean return of 10.98% during \textbf{backwardation} phases, statistically significant at the 1% level, and a mean return of 0.93% during \textbf{contango}, both in the first period, with the difference between them statistically significant at the 5% level.
-The corresponding figures for an equally weighted portfolio of the UK metals were 8.35% and -1.71%, the difference again statistically significant at the 5% level.
-These results provide broad support for an aggregate version of the Keynesian hedging pressure hypothesis and suggests that hedgers in the aggregate were engaged in risk transfer during this period.
-Over the second period the pattern essentially reverses.
-For the twenty-four US commodities over this period, eighteen have higher mean returns during phases of \textbf{backwardation} over \textbf{contango}, with the difference statistically significant for four commodities and of the remaining seven the higher mean return during \textbf{backwardation} is statistically significant for one commodity.
-All of the six UK metals achieved higher mean returns over \textbf{backwardation} than contango with the difference being statistically significant for one commodity.
-The equally weighted US portfolio had a mean return of 11.16% over \textbf{backwardation} while it was 26.68% during \textbf{contango}, the first statistically significant at the 5% level and the second at the 1% level, with the difference statistically significant at the 1% level.
-The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 6.43% during \textbf{backwardation} rising to 41.22% during \textbf{contango}, with the difference also significant at the 1% level.
-Thus the onset of financialization seems to have engendered a change in the nature of hedger’s behaviour in the aggregate, taking it away from risk shifting, the traditional Keynesian view.
-This phenomenon has been noted in earlier theoretical and empirical work [@DanthineInformationfuturesprices1978, @stout_why_1998] in different context from which two competing models of behaviour have emerged.
-The information arbitrage model implies that hedgers may often be seeking out counterparties to trade with rather than being purely passive.
-This issue is also raised in both @cheng_financialization_2014 and @StulzRethinkingriskmanagement1996 who point out that hedgers may be taking a view on prices just as speculators do.
-In fact, by hedging away some of their risk, hedgers are able to speculate more heavily based on their disagreement against speculators regarding futures price movement [@SimsekSpeculationrisksharing2013], which fits into a heterogenous expectation theory of speculation.
-As @stout_why_1998 points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves the speculators as this form of trading is regarded as non-productive^[@DuffieChallengespolicytreatment2014 also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.].
-In the second model hedgers are seen as liquidity providers as in @Kangtaletwopremiums2017.
-This explanation is also consistent with the nature of financialization which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
-
-The average time series pricing performance of the various one factor models on the US traded assets over the four periods is shown in Table \ref{table3}.
-Over the first period the market factor has the best average time series performance with the highest average adjusted R^2^ with all three futures market factors performing poorly and the overall pricing performance consistent across periods of high and low \textbf{CHP} (below period median).
-The two factor models average R^2^s (results available upon request) are roughly the sum of the one factor R^2^s indicating that the factors are almost orthogonal over this period.
-The onset of financialization leads to a substantial improvement in the performance of the CHP factor with its average R^2^ increasing to 5.4% in the second period relative to 1.4% in the first.
-The performance of the market factor also improves though not by as much in a relative sense (18.6% from 12.2%).
-Both the term structure factor and the open interest growth factor show a much smaller improvement in pricing performance.
-Over all periods, all of our factor models show similar pricing performance across regimes of high and low \textbf{CHP}.
-
-We next investigate the top eight of the US traded commodities which achieved the highest time series R^2^ for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \ref{table4}.
-For the CHP factor the commodities that achieve high R^2^ in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor.
-The same applies to the open interest and term structure factors with CHP replaced by open interest growth and roll yield respectively; while for the market factor the picks are those that co-vary most strongly with the market factor over that period.
-For the CHP factor, we observe a change in the picks between the first and the second period; the picks in the first period included five agricultural commodities and three metals while in the second period include all of the five base and precious metals and only three agricultural commodities.
-This pattern is also visible for the term structure factor for which there are four metals (gold, copper, palladium and platinum) picks in the second period against three in the first (gold, palladium and platinum).
-The market factor has two metal picks in the second period (palladium and silver) while all of the picks in the first period were agricultural or energy commodities.
-Over the third period, the average CHP factor has four metal picks while both the term structure factor and market factor have three.
-Table \ref{table4} also shows the proportion of time that these picks were constituents of the corresponding factor.
-All of the picks of the long-short factors (average CHP, open interest growth and term structure factors) were constituents of the corresponding factor for some proportion of time in all of the time periods.
-In this respect, there is a contrast between the first and second periods for the average CHP with the picks appearing predominantly on the long side in the second period, as opposed to both legs in the first.
-This indicates that the picks in the second period consistently exhibited low CHP.
-This behaviour continued over the third period.
-
-In table \ref{table5}, we show the average pairwise correlation between each set of picks in each time period.
-This exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.
-In the first period, the average CHP factor picks pairwise correlation is similar to the average across the US traded twenty-four commodities (around 0.1) with the market factor picks showing the highest figure (0.21).
-In the second period however it is the highest (0.27), comparable with the market (0.26) and double of the US traded commodities average (0.13).
-This increase is a consequence of the dramatic increase in average pairwise price correlation amongst the US traded metals, all of which are CHP factor picks.
-Taken together with the fact that four of these metals had consistently low CHP, we see that CHP co-movement in the second period is strongly correlated with price co-movement.
-It is also interesting to note that US traded metals returns were negatively correlated with the rest of US traded commodities in the first period and positively in the second (Results available upon request).
-
-In order to further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their pricing performance on these sets of picks.
-The results are shown in table \ref{table6}.
-The long-short factors for a particular attribute select the top and bottom three of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks.
-In the absence of price co-movement between the picks, this market factor will achieve an average R^2^ of around 12.5%^[Market factor lemma: $\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv$ size of market portfolio (eight here).
-See section \ref{market-factor-lemma} for a formal proof.], while there is no non-zero R^2^ lower bound for the corresponding long-short factors.
-A high average R^2^ for the market factor is indicative of strong price co-movement while for the long-short factors it is indicative of simultaneous attribute and price co-movement.
-The most dramatic change in pricing performance occurs for the average CHP factor picks where the market factor built from these picks has an average R^2^ of 21.3 % in the first period (close to the 0 correlation situation) and jumps to 37.4 % in the second period.
-The average CHP factor built with average CHP factor picks also shows a sharp increase in pricing performance over the second period.
-There is also substancial improvement in pricing performance of the CHP factor built with term structure picks (3.4% vs.
-21.2%)^[In contrast to the market factor, there is no pricing performance lower bound for the CHP factor built with a set of picks.], providing evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialization.
-In table \ref{table7} we assess the performance of the same factors on all the commodities instead of just the picks.
-While the average R^2^s are expectedly lower, the relative performance of the market factors built with different sets of picks is similar to table \ref{table6}.
-In contrast, the increase in R^2^ for the average CHP factor built with average CHP factor picks is lower indicating that the link between CHP co-movement and price co-movement is strongest amongst the picks which are predominantly metals.
-The conclusion from Tables \ref{table6} and \ref{table7} is that the onset of financialization seems to have had a major impact on the dynamics of US traded precious and precious-base metals and we now seek to analyse whether this phenomenon is true for the non-US metal futures.
-To that end we examine the pricing performance of the factors used in Table \ref{table6} on the six UK metals futures.
-The results are reported in Table \ref{table8}.
-In the first period, the average R^2^s across the board are always less than 4.5%.
-In the second period we see a dramatic increase in R^2^ for the market factor built with average CHP factor picks and average term structure factor picks (4.48% to 25.1% and 1.3% to 20.6% respectively) showing dramatically higher co-movement between UK traded metals and the corresponding picks all of which are US traded commodities.
-The increase in R^2^ for the market factor built with market factor picks is much more modest, providing further evidence of concentration of co-movement in the metal sector during financialization.
-
-In order to understand this better, in table \ref{table9}, we examine the pricing performance of both long and short legs of the corresponding factors separately on the same set of UK traded metals.
-The most striking result here is the dramatic increase in R^2^ for the long leg of the term structure factor built with CHP factor picks which achieves the highest overall R^2^ in the second period (1.91% vs.
-27.37%).
-This provides further evidence that global metals co-movement could be detected by US based factor models that combined the Keynesian and Working’s notions of backwardation.
-
-We then turn our analysis to the crisis and post-crisis period (2008-2013).
-In table \ref{table1} we see that the returns on both US and non-US commodities fall dramatically over this period, going down to -4.3% for the UK metals and 8% for the US traded commodities although volatility for both sets of assets is similar to that during the second period.
-Two of the UK metals have negative mean returns over the third period compared to one over the first and none over the second.
-This trend continues in from 2014 to 2017 with the US traded commodities recording an average mean return of -0.6% and the UK metals an average of 4.9% over this period, with fourteen US traded commodities and one UK metal having negative mean returns.
-The volatility of both sets of assets is lower than over the 2004-2007 period, particularly for the UK metals, suggesting the impact of the investment outflows from the commodity futures markets has had a much lower impact on volatility than the corresponding inflows witnessed over the financialization period.
-The market factor dominates pricing performance over this period with an increase of mean average R^2^ of over 50% while that for the other factors increases slightly at best (table \ref{table3}).
-From table \ref{table5} we see that there is an across the board increase in pairwise correlations with a doubling in the average pairwise correlation of all US traded commodities and a levelling in the pairwise correlation of the picks of the three long-short factors.
-Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
-This is clearly evident in the performance of the market factor built with any set of picks on the entire set of US traded commodities (table \ref{table7}) as we see a dramatic rise across the board in pricing performance.
-Table \ref{table8} provides further evidence of systematic linkages, in this case between US and non-US traded commodities as the market factor built with its own picks (US traded commodities) achieves an average R^2^ of 33.7% on the UK metals compared to 9.9% in the previous period.
-
-# Conclusion
-
-In the early 2000s, against a backdrop of a low yield environment and poor stock market performance, a combination of financial innovation^[Tradable commodity price indexes (commonly referred to as commodity index funds or CIFs), and commodity-based exchange traded funds (ETFs) were the main financial innovations which allowed the large global banks to offer commodity investment products to institutional and retail investors.
-In 1991 Goldman Sachs created the S&P-GSCI which provides investors with buy-side exposure to commodities via the OTC swap market and thus without having to participate in the formal futures markets with their position limit restrictions.
-At this stage these restrictions still applied to the bank though, as it hedged its commodity swap exposure in the futures markets.
-The first commodity-based ETFs were created through buying physical precious metals with gold and silver ETFs offered as early as 2002/2003.
-The regulatory hurdle here related to the licensing of commodity trading professionals.
-Typically, investors had to sign a statement with their broker stating that they understood the risks of commodity investments; a rather inconvenient paperwork for a product designed to trade like a stock, as set forth by a number of industry players at the time.] and deregulation^[In 2000, the Commodity Futures Modernization Act (CFMA) granted non-agricultural commodity futures statutory exemption from regulation (“Enron loophole”) while it required that agricultural commodity derivatives be traded on a CFTC-regulated exchange.
-Notwithstanding, the CFTC classified swap dealers as “bona fide” hedgers, granting them position limits exemption (“swap dealer loophole”).
-In 2005, the CFTC waived the rule that required commodity investors to sign a statement saying they understood the risks, letting the funds replace it with their prospectus and thus unleashed commodity-based ETFs investments.] led to a large inflow of institutional and financial capital into the commodity futures markets.
-This process known as financialization lead to a heated public policy debate about whether the increase in open interest and trading volume in commodities exerted upward pressure on prices.
-Perhaps in response to this, most of the early studies focused on the more mechanical effects of financialization, relying on commodity specific causality and correlation based analysis.
-With the benefit of hindsight this focus appears to have been too narrow and it seems important to analyze the effects of financialization from a broader perspective which we do in this study.
-We consider the entire cross-section of actively traded commodities on futures markets and use a futures based asset pricing framework that includes factors constructed using both price and non-price attributes.
-Factor model techniques are well suited to isolating common driving factors and detecting co-movement, a central issue in financialization which we believe the existing literature has not fully analyzed.
-Our analysis suggests that financialization was a phenomenon endogenous to the commodity markets transmitted via the futures markets and appears to have had the deepest impact on global metal futures markets.
-The onset of the financial crisis and the monetary policy regimes that followed appear to have also induced significant changes in commodity pricing dynamics and our analysis suggest that in contrast with financialization, the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of global commodities.
-
-\newpage
-```{r `mean returns`}
-
-table <- dplyr::filter(tables, name == "table 1") %>% dplyr::select(table) %>% tidyr::unnest(table)
-
-caption <- "\\label{table1} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study.
-Figures labelled *** (**, *) are significant at the 1\\% (5\\%, 10\\%) level.
-See section \\ref{methods} for more details."
-
-kable(table, align = c(rep('l', 2L), rep('r', 4L)), digits = getOption("digits"),
-      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>%
-  kableExtra::kable_styling(full_width = TRUE, font_size = 10L) %>%
-  kableExtra::column_spec(1L, width = "5cm") %>%
-  kableExtra::column_spec(2L, width = "2cm")
-
-```
-
-\newpage
-```{r `mean returns - aggregate CHP regimes`}
-table <- dplyr::filter(tables, name == "table 2") %>%
-  dplyr::select(table) %>%
-  tidyr::unnest(table)
-
-caption <- "\\label{table2} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study.
-For each period the results are shown for \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently.
-Figures labelled *** (**, *) are significant at the 1\\% (5\\%, 10\\%) level.
-See section \\ref{methods} for more details."
-
-kable(table, align = c(rep('l', 3L), rep('r', 4L)), digits = getOption("digits"), 
-      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
-  kableExtra::landscape() %>% 
-  kableExtra::kable_styling(latex_options = "repeat_header",
-                            repeat_header_method = "replace",
-                            repeat_header_text = "continued",
-                            font_size = 10L,
-                            full_width = TRUE) %>% 
-  kableExtra::column_spec(1L, width = "5cm") %>% 
-  kableExtra::column_spec(2L, width = "2cm")
-```
-
-\newpage
-```{r `factor regressions`}
-table <- dplyr::filter(tables, name == "table 3") %>%
-  dplyr::select(table) %>%
-  tidyr::unnest(table)
-
-caption <- "\\label{table3} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby futures returns on the commodities forming the entire cross-section of US traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using whole set of US traded commodities considered.
-For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently.
-See section \\ref{methods} for more details."
-
-kable(table, align = c(rep('l', 3L), rep('r', 4L)), digits = getOption("digits"), 
-      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
-  kableExtra::kable_styling(font_size = 10L, full_width = TRUE) %>% 
-  kableExtra::column_spec(1L, width = "3cm") %>% 
-  kableExtra::column_spec(2L, width = "3cm") %>% 
-  kableExtra::column_spec(3L, width = "2cm")
-```
-
-\newpage
-```{r `factor picks`}
-table <- dplyr::filter(tables, name == "table 4") %>% dplyr::select(table) %>% tidyr::unnest(table)
-
-caption <- "\\label{table4} For each risk factor and period, this table displays the list of corresponding commodity factor picks along with the proportion of time they are individually held on the long and short legs of the corresponding risk factor mimicking portfolio.
-The factor portfolios are constructed from the whole set of the twenty four US traded commodities considered which is also used as asset pool for the commodity picking exercise.
-See section \\ref{methods} for more details."
-
-kable(table, align = c(rep('l', 3L), rep('r', 2L)), digits = getOption("digits"), 
-      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
-  kableExtra::kable_styling(latex_options = "repeat_header",
-                            repeat_header_method = "replace",
-                            repeat_header_text = "continued",
-                            font_size = 10L,
-                            full_width = TRUE) %>%
-  kableExtra::column_spec(3L, width = "3.5cm")
-```
-
-\newpage
-```{r correlations}
-table <- dplyr::filter(tables, name == "table 5") %>% dplyr::select(table) %>% tidyr::unnest(table)
-
-caption <- "\\label{table5} This table displays the average pairwise nearby futures returns correlations for various sets of commodities including the multiple sets of risk factor commodity picks, the whole cross-section of US traded commodities considered in the study, the latter with metals omitted, and the cross-section of US traded metals.
-For each period and commodity set the correlations are calculated independently over the whole period as well as over \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes.
-See section \\ref{methods} for more details."
-
-kable(table, align = c(rep('l', 2L), rep('r', 4L)), digits = getOption("digits"), 
-      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
-  kableExtra::kable_styling(font_size = 10L, full_width = TRUE) %>% 
-  kableExtra::column_spec(1L, width = "5cm") %>% 
-  kableExtra::column_spec(2L, width = "2cm")
-```
-
-\newpage
-```{r `factor pick regressions - picks:picks`}
-table <- dplyr::filter(tables, name == "table 6") %>% dplyr::select(table) %>% tidyr::unnest(table)
-
-caption <- "\\label{table6} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby futures returns on risk factors commodity picks while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in table \\ref{table4}.
-For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently.
-See section \\ref{methods} for more details."
-
-kable(table, align = c(rep('l', 3L), rep('r', 4L)), digits = getOption("digits"), 
-      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
-  kable_styling(latex_options = "repeat_header", 
-                repeat_header_method = "replace", 
-                repeat_header_text = "continued", 
-                font_size = 10L, 
-                full_width = TRUE) %>% 
-  kableExtra::column_spec(1L, width = "3cm") %>% 
-  kableExtra::column_spec(2L, width = "3cm") %>% 
-  kableExtra::column_spec(3L, width = "2cm")
-
-```
-
-\newpage
-```{r `factor pick regressions - picks: US commos`}
-table <- dplyr::filter(tables, name == "table 7") %>% dplyr::select(table) %>% tidyr::unnest(table)
-
-caption <- "\\label{table7} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby futures returns on the commodities forming the entire cross-section of US traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in table \\ref{table4}.
-For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently.
-See section \\ref{methods} for more details."
-
-kable(table, align = c(rep('l', 3L), rep('r', 4L)), digits = getOption("digits"), 
-      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
-  kableExtra::kable_styling(latex_options = "repeat_header", 
-                repeat_header_method = "replace", 
-                repeat_header_text = "continued", 
-                font_size = 10L, 
-                full_width = TRUE) %>% 
-  kableExtra::column_spec(1L, width = "3cm") %>% 
-  kableExtra::column_spec(2L, width = "3cm") %>% 
-  kableExtra::column_spec(3L, width = "2cm")
-
-```
-
-\newpage
-```{r `factor pick regressions - picks: UK commos`}
-table <- dplyr::filter(tables, name == "table 8") %>% dplyr::select(table) %>% tidyr::unnest(table)
-
-caption <- "\\label{table8} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby futures returns on the six LME traded metals considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in Table \\ref{table4}.
-For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently.
-See section \\ref{methods} for more details."
-
-kable(table, align = c(rep('l', 4L), rep('r', 4L)), digits = getOption("digits"), 
-      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
-  kableExtra::kable_styling(latex_options = "repeat_header", 
-                repeat_header_method = "replace", 
-                repeat_header_text = "continued", 
-                font_size = 10L, 
-                full_width = TRUE) %>% 
-  kableExtra::column_spec(1L, width = "3cm") %>% 
-  kableExtra::column_spec(2L, width = "3cm") %>% 
-  kableExtra::column_spec(3L, width = "2cm")
-```
-
-\newpage
-```{r `factor pick regressions - picks: UK commos - legs`}
-table <- dplyr::filter(tables, name == "table 9") %>% dplyr::select(table) %>% tidyr::unnest(table)
-
-caption <- "\\label{table9} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby futures returns on the six LME traded metals considered in the study while the regressors are returns on the long and short legs of mimicking portfolios for risk factors considered independently, where the factor portfolios are constructed using the corresponding set of risk factor commodity picks.
-For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over \\textbf{contango} (high) and \\textbf{backwardation} (low) \\textbf{CHP} regimes independently.
-See section \\ref{methods} for more details."
-
-kable(table, align = c(rep('l', 4L), rep('r', 4L)), digits = getOption("digits"), 
-      booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
-  kableExtra::landscape() %>% 
-  kableExtra::kable_styling(latex_options = "repeat_header", 
-                repeat_header_method = "replace", 
-                repeat_header_text = "continued", 
-                font_size = 10L, 
-                full_width = TRUE) %>% 
-  kableExtra::column_spec(1L, width = "3cm") %>% 
-  kableExtra::column_spec(2L, width = "3cm") %>% 
-  kableExtra::column_spec(4L, width = "2cm")
-
-```
-
-# Appendix
-
-## Assets {#assets}
-
-```{r `appendix - assets`}
-caption <- "This table shows details on the individual commodities considered in this study including trading country, sector, subsector as well as trading exchange Market Identifier Codes (MIC, ISO 10383)."
-
-dplyr::filter(tickers, Market == TRUE, Asset_class == "Commodity") %>%
-  dplyr::select(Country, Sector, Subsector, Exchange, Name) %>%
-  dplyr::arrange(desc(Country), Sector, Subsector, Exchange, Name) %>%
-  kable(., align = rep('l', 5L),
-        digits = getOption("digits"),
-        booktabs = TRUE,
-        longtable = TRUE,
-        linesep = "",
-        caption = caption) %>%
-  kableExtra::kable_styling(full_width = TRUE, font_size = 10L) %>%
-  kableExtra::column_spec(1L, width = "3cm") %>%
-  kableExtra::column_spec(2L, width = "3cm")
-
-```
-
-\newpage
-
-## Market factor lemma {#market-factor-lemma}
-
-$$\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}$$
-$\overline{R_{mkt, p}^{2}}\equiv$ period $p$ average $R^{2}$ for market risk factor returns.  
-$R_{j, mkt, p}^{2}\equiv$ period $p$ $R^{2}$ for the regression where the dependent variable is the vector of returns on commodity $j$ nearby contract and the regressor is the vector of returns on the market portfolio; $j \in Y_{p}^{mkt}$.
-$Y_{p}^{mkt}\equiv$ commodity set considered for the formation of the mimicking portfolio for market risk over period $p$.  
-$n\equiv$ number of commodities in $Y_{p}^{mkt}$.
-
-__Proof__
-
-Week $t$ market factor return:
-$$r_{mkt, t} = \sum_{j} w_{j, p} \cdot r_{j, t}$$
-$w_{j, p}\equiv$ period $p$ weight for commodity $j$ in the mimicking portfolio for market risk in returns.  
-$r_{j, t}\equiv$ week $t$ return for commodity $j$.
-
-Assumptions:
-
-\begin{math}
-  \begin{aligned}
-   w_{j, p} &= w_{k, p} = \frac{1}{n} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt} \\
-   \sigma_{r_{j}, p} &= \sigma_{r_{k}, p} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt} \\
-   cov \left ( r_{j}, r_{k} \right )_{p} &= 0 \: \forall \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt}
-  \end{aligned}
-\end{math}
-
-\newpage
-
-$$
-\begin{array}{l c l}
-  \sigma_{r_{j, p}}^{2} & = & \beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2} + \sigma_{\epsilon}^{2} \\
-  \beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2} & = & \sigma_{r_{j, p}}^{2} - \sigma_{\epsilon}^{2} \\
-  \frac{\beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2}}{\sigma_{r_{j, p}}^{2}} & = & \frac{\sigma_{r_{j, p}}^{2} - \sigma_{\epsilon}^{2}}{\sigma_{r_{j, p}}^{2}} \\
-    \frac{\beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2}}{\sigma_{r_{j, p}}^{2}}  & = & R_{r_{j}, r_{mkt}, p}^{2} \\ \\
-  \sigma_{r_{mkt, p}}^{2} & = & \sum_{j} w_{j, p}^{2} \cdot \sigma_{j, p}^{2} + 2 \cdot \sum_{j} \sum_{k \neq j} w_{j, p} \cdot w_{k, p} \cdot cov \left ( r_{j, p}, r_{k, p} \right ) \\
-                          & = & \sum_{j} \left ( \frac{1}{n} \right )^{2} \cdot \sigma_{j, p}^{2} \\
-                          & = & \frac{\sum_{j} \sigma_{j, p}^{2}}{n^{2}} \\ \\
-  cov \left ( r_{j}, r_{mkt} \right )_{p} & = & cov \left ( r_{j}, \frac{1}{n} \sum_{k} r_{k} \right )_{p} \\
-                                          & = & \frac{1}{n} \sum_{k} cov \left ( r_{j}, r_{k} \right )_{p} \\
-                                          & = & \frac{1}{n} cov \left ( r_{j}, r_{j} \right )_{p} \\
-                                          & = & \frac{\sigma_{r_{j}, p}^{2}}{n} \\ \\
-  \beta_{j, mkt, p}^{2} & = & \left [ \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}}{\sigma_{r_{mkt, p}}^{2}} \right ]^{2} \\
-                        & = & \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}^{2}}{\sigma_{r_{mkt, p}}^{4}} \\ \\
-  \beta_{j, mkt, p}^{2} \cdot  \sigma_{r_{mkt, p}}^{2}  & = & \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}^{2}}{\sigma_{r_{mkt, p}}^{2}} \\
-                                                        & = & \left ( \frac{\sigma_{r_{j}, p}^{2}}{n} \right )^{2} \cdot \frac{1}{\sigma_{r_{mkt, p}}^{2}} \\
-                                                        & = & \frac{\sigma_{r_{j}, p}^{4}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\ \\
-\end{array}
-$$
-
-\newpage
-
-$$
-\begin{array}{l c l}
-  R_{r_{j}, r_{mkt}, p}^{2} & = & \frac{\sigma_{r_{j}, p}^{4}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \cdot \frac{1}{\sigma_{r_{j, p}}^{2}} \\
-                            & = & \frac{\sigma_{r_{j}, p}^{2}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\ \\  
-                            & \therefore  & \\ \\
-  \overline{R_{r_{mkt}, p}^{2}} & = & \frac{1}{n} \sum_{j} \frac{\sigma_{r_{j}, p}^{2}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\
-                                & = & \frac{1}{n} \cdot \frac{1}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \cdot \sum_{j} \sigma_{r_{j}, p}^{2} \\
-                                & = & \frac{1}{n} \cdot \frac{\sum_{j} \sigma_{r_{j}, p}^{2}}{n^{2} \cdot \frac{1}{n^{2}} \cdot \sum_{j} \sigma_{r_{j}, p}^{2}} \\
-                                & = & \frac{1}{n} \\
-\end{array}
-$$
-
-\newpage

### 2024-06-11 others/paper/elsevier article/main.Rmd
Track 'others' folder

--- 2024-06-11 others/paper/custom/main.Rmd
@@
 ---
-documentclass: article
-# classoption: letterpaper
-geometry: "letterpaper, left = 1in, right = 1in, top = 1.5in, bottom = 1.5in"
-link-citations: TRUE
-bibliography: BibTeX.bib
-biblio-style: jf
-fontsize: 12pt
-
-output:
-  pdf_document:
-    template: "template.tex"
-    citation: natbib
-    fig_caption: TRUE
-    keep_tex: TRUE
-    number_sections: TRUE
-    latex_engine: pdflatex
-    includes:
-     in_header: preamble.tex
-
-title: 'Financialization of Commodities: an Asset Pricing Perspective'
-
+title: "Financialization of Commodities: an Asset Pricing Perspective"
 author:
   - name: Devraj Basu
-    surname: Basu
     email: devraj.basu@strath.ac.uk
-    affiliation: University of Strathclyde, Glasgow, UK
+    affiliation: strathclyde
   - name: Olivier Bauthéac
-    surname: Bauthéac
     email: olivier.bautheac@strath.ac.uk
-    affiliation: University of Strathclyde, Glasgow, UK
+    affiliation: strathclyde
+address:
+  - code: strathclyde
+    address: University of Strathclyde, Glasgow, UK
 
-jel: G11, G23, G13, Q02
-keywords: Commodity futures, financialization, hedging pressure, financial crisis
+date: "`r Sys.Date()`"
+csl: elsevier-harvard.csl
+output: rticles::elsevier_article
+# output: bookdown::pdf_document2
+bibliography: "C:/Users/yyb14214/Dropbox/research/literature/references.bib"
 
@@
 
+jel: G11, G23, G13, Q02
+keywords: Commodity futures, financialization, hedging pressure, asset pricing
 ---
-
-```{r, echo = FALSE, message = FALSE}
-packages <- c("tidyr", "magrittr", "knitr", "lettercase", "tinytex", "bookdown", "kableExtra", "here")
-invisible(sapply(packages, require, character.only = TRUE))
-options(knitr.table.format = "latex")
-knitr::opts_chunk$set(echo = FALSE, results = "asis")
-tickers <- readRDS(file = file.path(here::here(), "data", "tickers.rds"))
-tables <- readRDS(file = file.path(here::here(), "explore", "results", "tables.rds.rds"))
-
-```
 
@@
 I do not hold paid or unpaid positions at any organization whose goals relate to the article.
-  ![](pics/signature - Devraj.png)\
+  ![](Devraj.jpg)
 
@@
 I do not hold paid or unpaid positions at any organization whose goals relate to the article.
-  ![](pics/signature - Olivier.png)\
+  ![](Olivier.jpg)
 
@@
 
-# Introduction
+```{r, echo = FALSE, message = FALSE, warning = FALSE}
+packages <- c("tidyr", "magrittr", "knitr", "tinytex", "bookdown", "kableExtra", "here")
+invisible(sapply(packages, require, character.only = TRUE))
+options(knitr.table.format = "latex")
+knitr::opts_chunk$set(echo = FALSE, results = "asis")
+tickers <- readRDS(file = file.path(here::here(), "data", "tickers.rds"))
+tables <- readRDS(file = file.path(here::here(), "explore", "results", "tables.rds"))
+
+```
+
+# Introduction {#intro}
 
@@
 
-The cross-sectional nature of financialization [@basak_model_2016; @cheng_financialization_2014] leads us to extend the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in @hong_what_2012.
-This paradigm implies that returns for individual commodities should be high in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in periods where \textbf{CHP} is high (\textbf{contango}).
-Over the first period the cross sectional average returns during \textbf{backwardation} for both the US and UK commodities are positive with those for the US statistically significant, and significantly higher than during \textbf{contango}, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
-Over the second period this pattern reverses, with both the US and UK commodities having significant positive returns during \textbf{contango} with these returns being significantly higher than during \textbf{backwardation}.
+The cross-sectional nature of financialization [@basak_model_2016; @cheng_financialization_2014] leads us to extend the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure first considered in @hong_what_2012.
+This paradigm implies that returns for individual commodities should be high in periods where **CHP** is low (**backwardation**) and low in periods where **CHP** is high (**contango**).
+Over the first period the cross sectional average returns during **backwardation** for both the US and UK commodities are positive with those for the US statistically significant, and significantly higher than during **contango**, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
+Over the second period this pattern reverses, with both the US and UK commodities having significant positive returns during **contango** with these returns being significantly higher than during **backwardation}.
 This change in pattern suggests that the onset of financialization altered the traditional risk shifting nature of hedger’s behaviour, which is implied by the Keynesian hypothesis.
 The arrival of financial investors raises the question of whether they functioned as liquidity providers or liquidity demanders.
-Arguments have been made for both of these possibilities with @moskowitz_time_2012 arguing that financial investors provide liquidity while @Kangtaletwopremiums2017 argue that they demand liquidity.
+Arguments have been made for both of these possibilities with @moskowitz_time_2012 arguing that financial investors provide liquidity while @kang_tale_2017 argue that they demand liquidity.
 Our analysis of returns in periods of low and high aggregate CHP before and during financialization allows us to analyse this issue from a new perspective and suggests that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
@@
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in pricing dynamics.
-Returns on both US and UK traded commodities fell dramatically over both the third and fourth periods with the pattern of return for the US traded commodities across \textbf{CHP} regimes reverting to Keynesian paradigm.
+Returns on both US and UK traded commodities fell dramatically over both the third and fourth periods with the pattern of return for the US traded commodities across **CHP** regimes reverting to Keynesian paradigm.
 The pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as strong evidence of cross-market linkages.
@@
 Commodity price dynamics appear to have altered substantially in quite different ways over the financialization and the financial crisis periods and our commodity futures based asset pricing approach seems able to provide new insights into the nature of these changes: financialization was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and mainly concentrated in a specific sector (metals) while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of global commodities.
-The initial view of financialization was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity future prices^[@de_schutter_food_2010_1; @gilbert_how_2010; @gilbert_speculative_2010; @masters_testimony_2008; @masters_accidental_2008; @herman_not_2011_1; @schumann_hunger-makers_2011; @singleton_investor_2013; @unctad_global_2009.].
+The initial view of financialization was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity future prices^[@deschutter_food_2010; @gilbert_how_2010; @gilbert_speculative_2010; @masters_testimony_2008; @masters_accidental_2008; @herman_not_2011; @schumann_hunger_2011; @singleton_investor_2013; @unctad_global_2009.].
 However, the fundamental question of the nature of the impact of financialization across the entire cross-section of commodity futures markets has not yet been completely answered.
-We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialization on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2013, @EkelandSpeculationcommodityfutures2016, @goldstein_commodity_2017.] and demonstrate that the effects of financialization extend beyond the mechanical effects induced by indexation as outlined in @basak_model_2016 as well as @tang_index_2012.
+We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialization on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2014, @ekeland_speculation_2016, @goldstein_commodity_2017.] and demonstrate that the effects of financialization extend beyond the mechanical effects induced by indexation as outlined in @basak_model_2016 as well as @tang_index_2012.
 
@@
 A world-wide debate has ensued about the role of index funds in commodity markets.
-The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs [@de_schutter_food_2010_1; @gilbert_speculative_2010; @herman_not_2011_1; @schumann_hunger-makers_2011; @unctad_global_2009].
+The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs [@deschutter_food_2010; @gilbert_speculative_2010; @herman_not_2011; @schumann_hunger_2011; @unctad_global_2009].
 The US and various european countries also became involved in this issue.
 Early US Senate investigations drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US wheat markets to the observed surges in both futures and cash prices [@masters_testimony_2008; @masters_accidental_2008]).
-This contention has since come to be known as the Masters’ hypothesis and was largely endorsed by the final US Senate report on the issue [@USSenate_Excessive_speculation_wheat_2009].
+This contention has since come to be known as the Masters’ hypothesis and was largely endorsed by the final US Senate report on the issue [@senate_excessive_2009].
 At this stage, the question thrust on the academic sphere was whether “excessive speculation” (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices.
@@
 @buyuksahin_speculators_2011, @tokic_speculation_2012, @fattouh_role_2013, @kilian_role_2014, @knittel_simple_2016 and @manera_modelling_2016 study the energy markets.
-@bohl_does_2013_2, @kim_does_2015 and @boyd_prevalence_2016 study both energy and agricultural markets while @irwin_index_2011, @irwin_financialization_2012 and @stoll_commodity_2011 study the commodity markets in general.
+@bohl_does_2013, @kim_does_2015 and @boyd_prevalence_2016 study both energy and agricultural markets while @irwin_index_2011, @irwin_financialization_2012 and @stoll_commodity_2011 study the commodity markets in general.
 
@@
 
-Commodity index funds (CIFs), commodity based exchange traded funds (ETFs) and notes (ETNs) as well as commodity linked notes (CLNs) were amongst the main investment vehicules that allowed institutional and retail investors to build up commodity exposure in the early 2000s [@boons_stock_2012; @henderson_new_2015; @irwin_index_2011; @unctad_global_2009; @schumann_hunger-makers_2011].
+Commodity index funds (CIFs), commodity based exchange traded funds (ETFs) and notes (ETNs) as well as commodity linked notes (CLNs) were amongst the main investment vehicules that allowed institutional and retail investors to build up commodity exposure in the early 2000s [@boons_stock_2012; @henderson_new_2015; @irwin_index_2011; @unctad_global_2009; @schumann_hunger_2011].
 Most of these products were primarily designed to track prominent commodity indexes amongst which the S&P-GSCI, the most popular.
@@
 The opposite market paradigm is referred to as "contango".
-Working [@working_theory_1948; @working_hedging_1953] and Cootner [@cootner_returns_1960; @CootnerSpeculationhedging1967] somehow relax this "supply-of-speculative-services" [@Tilllongtermperspectivecommodity2007] approach by introducing processors and merchants, also commodity experts, on the hedgers side and relating the notions of backwardation and contango more directly to the term structure via the theory of storage where the shape of the front end of the term structure (basis) is directly related to the market price of storage.
+Working [@working_theory_1948; @working_hedging_1953] and Cootner [@cootner_returns_1960; @cootner_speculation_1967] somehow relax this "supply-of-speculative-services" [@till_long_2007] approach by introducing processors and merchants, also commodity experts, on the hedgers side and relating the notions of backwardation and contango more directly to the term structure via the theory of storage where the shape of the front end of the term structure (basis) is directly related to the market price of storage.
 Financialization, on the other hand, refers to the entry of financial investors into the commodity futures markets who, for the most part, are not commodity experts.
@@
 Results are reported for the one-factor model case with the other results available from the authors upon request.
-For each period we also implement the analysis described above over periods of low and high aggregate CHP (\textbf{CHP}), a notion which we introduce in this study and which we believe is particularly relevant in the context of financialization where issues of co-movement and aggregate market participants' behaviour play a central role.
-We define \textbf{CHP} as the cross-sectional average of CHPs for a particular pool of assets.
-i.e, Week $t$ \textbf{CHP} for asset pool $x$:
+For each period we also implement the analysis described above over periods of low and high aggregate CHP (**CHP**), a notion which we introduce in this study and which we believe is particularly relevant in the context of financialization where issues of co-movement and aggregate market participants' behaviour play a central role.
+We define **CHP** as the cross-sectional average of CHPs for a particular pool of assets.
+i.e, Week $t$ **CHP** for asset pool $x$:
 
@@
 
-We further define aggregate backwardation (\textbf{backwardation}) and contango (\textbf{contango}) \textbf{CHP} regimes as, for a given period, \textbf{CHP} levels below and above the period's median respectively and, in contrast with [@hong_what_2012] who aggregate across sub-sectors, the asset pool we consider for \textbf{CHP} construction include the whole cross-section of US traded commodities.
+We further define aggregate backwardation (**backwardation**) and contango (**contango**) **CHP** regimes as, for a given period, **CHP** levels below and above the period's median respectively and, in contrast with [@hong_what_2012] who aggregate across sub-sectors, the asset pool we consider for **CHP** construction include the whole cross-section of US traded commodities.
 
@@
 
-For each period and \textbf{CHP} regime we record the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every sets of picks.
+For each period and **CHP** regime we record the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every sets of picks.
 
@@
 
-# Results & discussion
+# Results & discussion {#results}
 
@@
 The traditional Keynesian hedging pressure paradigm postulates a negative relationship between the return on an individual commodity and its hedging pressure.
-Financialization has been seen as a cross-sectional commodity market phenomenon; this naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure.
-The extended Keynesian hedging pressure paradigm should also imply that returns for individual commodities should be high in periods where \textbf{CHP} is low and vice et versa.
-In table \ref{table2} the mean returns are shown over high (\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP} regimes for each time period.
-Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of \textbf{backwardation} as compared to \textbf{contango}, with the difference being statistically significant at the 5% level for one commodity and for the remaining six commodities the higher mean return during \textbf{contango} is not statistically significant for any of them.
-For the six UK commodities, all metals, four of them had higher mean returns during phases of \textbf{backwardation} as compared to \textbf{contango} in the first period, with one of these differences being statistically significant at the 5% level while for the remaining two the higher mean return during \textbf{contango} is not statistically significant for either.
-An equally weighted portfolio of the twenty-four US commodities had a mean return of 10.98% during \textbf{backwardation} phases, statistically significant at the 1% level, and a mean return of 0.93% during \textbf{contango}, both in the first period, with the difference between them statistically significant at the 5% level.
+Financialization has been seen as a cross-sectional commodity market phenomenon; this naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure.
+The extended Keynesian hedging pressure paradigm should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
+In table \ref{table2} the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
+Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 5% level for one commodity and for the remaining six commodities the higher mean return during **contango** is not statistically significant for any of them.
+For the six UK commodities, all metals, four of them had higher mean returns during phases of **backwardation** as compared to **contango** in the first period, with one of these differences being statistically significant at the 5% level while for the remaining two the higher mean return during **contango** is not statistically significant for either.
+An equally weighted portfolio of the twenty-four US commodities had a mean return of 10.98% during **backwardation** phases, statistically significant at the 1% level, and a mean return of 0.93% during **contango**, both in the first period, with the difference between them statistically significant at the 5% level.
 The corresponding figures for an equally weighted portfolio of the UK metals were 8.35% and -1.71%, the difference again statistically significant at the 5% level.
@@
 Over the second period the pattern essentially reverses.
-For the twenty-four US commodities over this period, eighteen have higher mean returns during phases of \textbf{backwardation} over \textbf{contango}, with the difference statistically significant for four commodities and of the remaining seven the higher mean return during \textbf{backwardation} is statistically significant for one commodity.
-All of the six UK metals achieved higher mean returns over \textbf{backwardation} than contango with the difference being statistically significant for one commodity.
-The equally weighted US portfolio had a mean return of 11.16% over \textbf{backwardation} while it was 26.68% during \textbf{contango}, the first statistically significant at the 5% level and the second at the 1% level, with the difference statistically significant at the 1% level.
-The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 6.43% during \textbf{backwardation} rising to 41.22% during \textbf{contango}, with the difference also significant at the 1% level.
+For the twenty-four US commodities over this period, eighteen have higher mean returns during phases of **backwardation** over **contango**, with the difference statistically significant for four commodities and of the remaining seven the higher mean return during **backwardation** is statistically significant for one commodity.
+All of the six UK metals achieved higher mean returns over **backwardation** than contango with the difference being statistically significant for one commodity.
+The equally weighted US portfolio had a mean return of 11.16% over **backwardation** while it was 26.68% during **contango**, the first statistically significant at the 5% level and the second at the 1% level, with the difference statistically significant at the 1% level.
+The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 6.43% during **backwardation** rising to 41.22% during **contango}, with the difference also significant at the 1% level.
 Thus the onset of financialization seems to have engendered a change in the nature of hedger’s behaviour in the aggregate, taking it away from risk shifting, the traditional Keynesian view.
-This phenomenon has been noted in earlier theoretical and empirical work [@DanthineInformationfuturesprices1978, @stout_why_1998] in different context from which two competing models of behaviour have emerged.
+This phenomenon has been noted in earlier theoretical and empirical work [@danthine_information_1978, @stout_why_1998] in different context from which two competing models of behaviour have emerged.
 The information arbitrage model implies that hedgers may often be seeking out counterparties to trade with rather than being purely passive.
-This issue is also raised in both @cheng_financialization_2014 and @StulzRethinkingriskmanagement1996 who point out that hedgers may be taking a view on prices just as speculators do.
-In fact, by hedging away some of their risk, hedgers are able to speculate more heavily based on their disagreement against speculators regarding futures price movement [@SimsekSpeculationrisksharing2013], which fits into a heterogenous expectation theory of speculation.
-As @stout_why_1998 points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves the speculators as this form of trading is regarded as non-productive^[@DuffieChallengespolicytreatment2014 also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.].
-In the second model hedgers are seen as liquidity providers as in @Kangtaletwopremiums2017.
+This issue is also raised in both @cheng_financialization_2014 and @stulz_rethink_1996 who point out that hedgers may be taking a view on prices just as speculators do.
+In fact, by hedging away some of their risk, hedgers are able to speculate more heavily based on their disagreement against speculators regarding futures price movement [@simsek_speculation_2013], which fits into a heterogenous expectation theory of speculation.
+As @stout_why_1998 points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves the speculators as this form of trading is regarded as non-productive^[@duffie_challenges_2014 also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.].
+In the second model hedgers are seen as liquidity providers as in @kang_tale_2017.
 This explanation is also consistent with the nature of financialization which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
@@
 The average time series pricing performance of the various one factor models on the US traded assets over the four periods is shown in Table \ref{table3}.
-Over the first period the market factor has the best average time series performance with the highest average adjusted R^2^ with all three futures market factors performing poorly and the overall pricing performance consistent across periods of high and low \textbf{CHP} (below period median).
+Over the first period the market factor has the best average time series performance with the highest average adjusted R^2^ with all three futures market factors performing poorly and the overall pricing performance consistent across periods of high and low **CHP** (below period median).
 The two factor models average R^2^s (results available upon request) are roughly the sum of the one factor R^2^s indicating that the factors are almost orthogonal over this period.
@@
 Both the term structure factor and the open interest growth factor show a much smaller improvement in pricing performance.
-Over all periods, all of our factor models show similar pricing performance across regimes of high and low \textbf{CHP}.
+Over all periods, all of our factor models show similar pricing performance across regimes of high and low **CHP}.
 
@@
       booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>%
+  kableExtra::landscape() %>% 
   kableExtra::kable_styling(full_width = TRUE, font_size = 10L) %>%
@@
       booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
+  kableExtra::landscape() %>% 
   kableExtra::kable_styling(font_size = 10L, full_width = TRUE) %>% 
@@
       booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
+  kableExtra::landscape() %>% 
   kable_styling(latex_options = "repeat_header", 
@@
       booktabs = TRUE, longtable = TRUE, linesep = "", caption = caption) %>% 
+  kableExtra::landscape() %>% 
   kableExtra::kable_styling(latex_options = "repeat_header", 

### 2024-06-11 others/paper/elsevier article/main.tex
Track 'others' folder

--- 2024-06-11 others/paper/custom/main.tex
@@
-\documentclass[12pt,]{article}
+\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
+%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
+\usepackage[hyphens]{url}
+
+\usepackage{lineno} % add
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\usepackage{graphicx}
+\usepackage{booktabs} % book-quality tables
+%%%%%%%%%%%%%%%% end my additions to header
+
+\usepackage[T1]{fontenc}
 \usepackage{lmodern}
@@
 \usepackage{fixltx2e} % provides \textsubscript
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
   \usepackage[utf8]{inputenc}
 \else % if luatex or xelatex
+  \usepackage{fontspec}
   \ifxetex
-    \usepackage{mathspec}
+    \usepackage{xltxtra,xunicode}
+  \fi
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
+\fi
+% use microtype if available
+\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\bibliographystyle{elsarticle-harv}
+\usepackage{graphicx}
+% We will generate all images so they have a width \maxwidth. This means
+% that they will get their normal width if they fit onto the page, but
+% are scaled down if they would overflow the margins.
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
+\else\Gin@nat@width\fi}
+\makeatother
+\let\Oldincludegraphics\includegraphics
+\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
 \else
-    \usepackage{fontspec}
+  \usepackage[unicode=true]{hyperref}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage[letterpaper, left = 1in, right = 1in, top = 1.5in, bottom = 1.5in]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
             pdftitle={Financialization of Commodities: an Asset Pricing Perspective},
-            pdfkeywords={Commodity futures; financialization; hedging pressure; financial crisis},
-            pdfborder={0 0 0},
-            breaklinks=true}
+            colorlinks=false,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
 \urlstyle{same}  % don't use monospace font for urls
-\usepackage{natbib}
-\bibliographystyle{jf}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
+
+\setcounter{secnumdepth}{0}
+% Pandoc toggle for numbering sections (defaults to be off)
+\setcounter{secnumdepth}{0}
+% Pandoc header
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+
+\begin{document}
+\begin{frontmatter}
 
   \title{Financialization of Commodities: an Asset Pricing Perspective}
-    % \author{Devraj Basu \\ Olivier Bauthéac}
-  \author{ Devraj Basu  \\  Olivier Bauthéac  
-	  \thanks{ Basu: University of Strathclyde, Glasgow, UK, \href{mailto:devraj.basu@strath.ac.uk}{\nolinkurl{devraj.basu@strath.ac.uk}}.
-Bauthéac: University of Strathclyde, Glasgow, UK, \href{mailto:olivier.bautheac@strath.ac.uk}{\nolinkurl{olivier.bautheac@strath.ac.uk}}.
-	   \newline We thank seminar participants at IIM Ahmedabad, IIM Calcutta, SKEMA
-Business School and University of Gottingen, as well as Griffith
-inaugural alternative investment conference attendants for their
-feedback. We also thank Joelle Miffre, Martijn Boons, John Fan, Robert
-Bianchi, Chardin Wese Simen, Andrew Kaleel and particularly Olaf Korn
-for their extremely useful comments and suggestions.  }
-  }
-    \date{}
-
-\usepackage{longtable, tabu, pdflscape, booktabs, caption, setspace}
-\doublespacing
-\renewcommand*{\arraystretch}{0.65}
-
-\begin{document}
-\maketitle
+    \author[strathclyde]{Devraj Basu}
+   \ead{devraj.basu@strath.ac.uk}
+
+    \author[strathclyde]{Olivier Bauthéac}
+   \ead{olivier.bautheac@strath.ac.uk}
+
+      \address[strathclyde]{University of Strathclyde, Glasgow, UK}
+
   \begin{abstract}
@@
   to go beyond mechanical effects induced by the rise of indexing.
-\newline
-JEL: G11, G23, G13, Q02
-\newline
-Keywords: Commodity futures, financialization, hedging pressure, financial crisis
-
   \end{abstract}
+   \begin{keyword} Commodity futures, financialization, hedging pressure, asset pricing\end{keyword}
+ \end{frontmatter}
 
@@
   article.\\
-  \includegraphics{pics/signature - Devraj.png}\\
+  \includegraphics{Devraj.jpg}
 \end{itemize}
@@
   to the article.\\
-  \includegraphics{pics/signature - Olivier.png}\\
+  \includegraphics{Olivier.jpg}
 \end{itemize}
@@
   to hedge against inflation and seek diversification benefits
-  \citep{buyuksahin_speculators_2014, singleton_investor_2013},
-  institutional investors sent forth an unprecedented flow of capital
-  into commodity futures markets. This phenomenon is commonly referred
-  to as the financialization of commodities
-  \citep{domanski_financial_2007}.} as well as the period of the 2008
-financial crisis and its aftermath. Financialization appears to have
-affected a number of economic sectors, including agriculture and energy,
-and its impact has been hotly debated in the policy, legislative,
-regulatory, and academic spheres. A vigorous legislative debate has led
-to regulatory changes accompanied by an equally intense policy and
-academic debate across a number of disciplines about the perceived
-effects on commodity prices of the unprecedented inflow of institutional
-funds brought into commodity futures markets by new index type
-investors\footnote{See section \ref{background} for a detailled
-  discussion.}. In response to immediate policy concerns, the academic
-debate was initially framed rather narrowly. In this paper we take a
-fundamentally different empirical approach that is broader in scope. We
-consider the entire cross-section of actively traded commodities on
-futures markets and use a futures based asset pricing framework that
-includes factors constructed using both price and non-price attributes.
+  (Büyükşahin and Robe, 2014; Singleton, 2013), institutional investors
+  sent forth an unprecedented flow of capital into commodity futures
+  markets. This phenomenon is commonly referred to as the
+  financialization of commodities (Domanski and Heath, 2007).} as well
+as the period of the 2008 financial crisis and its aftermath.
+Financialization appears to have affected a number of economic sectors,
+including agriculture and energy, and its impact has been hotly debated
+in the policy, legislative, regulatory, and academic spheres. A vigorous
+legislative debate has led to regulatory changes accompanied by an
+equally intense policy and academic debate across a number of
+disciplines about the perceived effects on commodity prices of the
+unprecedented inflow of institutional funds brought into commodity
+futures markets by new index type investors\footnote{See section
+  \ref{background} for a detailled discussion.}. In response to
+immediate policy concerns, the academic debate was initially framed
+rather narrowly. In this paper we take a fundamentally different
+empirical approach that is broader in scope. We consider the entire
+cross-section of actively traded commodities on futures markets and use
+a futures based asset pricing framework that includes factors
+constructed using both price and non-price attributes.
 
@@
 The first factor model we consider (CHP) is based on the well-known
-hedging pressure based theory
-\citep{anderson_hedger_1983, chang_returns_1985, cootner_returns_1960, dusak_futures_1973, hicks_value_1939, hirshleifer_risk_1988, hirshleifer_determinants_1989, hirshleifer_hedging_1990, kolb_is_1992, keynes_treatise_1930}
-which postulates that futures prices for a given commodity are inversely
-related to the extent that commercial hedgers are short or long and we
-use a factor mimicking portfolio that captures the impact of hedging
-pressure as a systemic factor \citep{basu_capturing_2013}. Our second
-factor model is based on open interest growth following
-\citet{hong_what_2012} who find that open interest growth has predictive
-power for individual commodity returns and again we construct a
-long-short factor mimicking portfolio. Our third model is based on term
-structure following \citet{szymanowska_anatomy_2014} and
-\citet{fuertes_commodity_2015} who demonstrate that the term structure
-factor has explanatory power for the cross-section of commodity returns.
-We finally consider an equally weighted portfolio of commodities as a
-proxy for the market factor. Our two price based and two non-price based
-factors allow us to compare and contrast different channels that could
-have led to changes in commodity price dynamics over the last twenty
-years.
+hedging pressure based theory (Anderson and Danthine, 1983; Chang, 1985;
+Cootner, 1960; Dusak, 1973; Hicks, 1939; Hirshleifer, 1990, 1989, 1988;
+Keynes, 1930; Kolb, 1992) which postulates that futures prices for a
+given commodity are inversely related to the extent that commercial
+hedgers are short or long and we use a factor mimicking portfolio that
+captures the impact of hedging pressure as a systemic factor (Basu and
+Miffre, 2013). Our second factor model is based on open interest growth
+following Hong and Yogo (2012) who find that open interest growth has
+predictive power for individual commodity returns and again we construct
+a long-short factor mimicking portfolio. Our third model is based on
+term structure following Szymanowska et al. (2014) and Fuertes et al.
+(2015) who demonstrate that the term structure factor has explanatory
+power for the cross-section of commodity returns. We finally consider an
+equally weighted portfolio of commodities as a proxy for the market
+factor. Our two price based and two non-price based factors allow us to
+compare and contrast different channels that could have led to changes
+in commodity price dynamics over the last twenty years.
 
@@
 second, the financialization phase, spans the 2004/2007 period\footnote{Starting
-  point based on earlier studies
-  \citep{baker_financialization_2014, christoffersen_factor_2014}.}; the
-third, 2008/2013, encompasses both the financial crisis and the loose
-monetary policy regimes that followed; and the fourth spans the period
-starting in 2014 to present.\\
+  point based on earlier studies (Baker, 2014; Christoffersen et al.,
+  2014).}; the third, 2008/2013, encompasses both the financial crisis
+and the loose monetary policy regimes that followed; and the fourth
+spans the period starting in 2014 to present.\\
 Consistent with earlier studies, we observe that mean returns for the US
@@
 
-The cross-sectional nature of financialization
-\citep{basak_model_2016, cheng_financialization_2014} leads us to extend
-the Keynesian individual hedging pressure paradigm by incorporating
-aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure
-first considered in \citet{hong_what_2012}. This paradigm implies that
-returns for individual commodities should be high in periods where
-\textbf{CHP} is low (\textbf{backwardation}) and low in periods where
-\textbf{CHP} is high (\textbf{contango}). Over the first period the
-cross sectional average returns during \textbf{backwardation} for both
-the US and UK commodities are positive with those for the US
-statistically significant, and significantly higher than during
-\textbf{contango}, providing broad support for an aggregate version of
-the Keynesian hedging pressure hypothesis. Over the second period this
-pattern reverses, with both the US and UK commodities having significant
-positive returns during \textbf{contango} with these returns being
-significantly higher than during \textbf{backwardation}. This change in
-pattern suggests that the onset of financialization altered the
-traditional risk shifting nature of hedger's behaviour, which is implied
-by the Keynesian hypothesis. The arrival of financial investors raises
-the question of whether they functioned as liquidity providers or
-liquidity demanders. Arguments have been made for both of these
-possibilities with \citet{moskowitz_time_2012} arguing that financial
-investors provide liquidity while \citet{Kangtaletwopremiums2017} argue
-that they demand liquidity. Our analysis of returns in periods of low
-and high aggregate CHP before and during financialization allows us to
-analyse this issue from a new perspective and suggests that financial
-investors may have been liquidity demanders leading hedgers to become
-liquidity providers.
-
-\citet{goldstein_commodity_2017} as well as
-\citet{goldstein_speculation_2014} argue that the arrival of financial
-investors has an impact on the extent of normal backwardation in
-commodity futures markets. Based on their analysis we would expect our
-average CHP factor, which is based on backwardation measured by hedger's
-positions, as well our term structure factor, which is based on
-backwardation measured by roll yield, to be best suited to measure the
-impact of financialization.\\
+The cross-sectional nature of financialization (Basak and Pavlova, 2016;
+Cheng and Xiong, 2014) leads us to extend the Keynesian individual
+hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}),
+a market wide measure of hedging pressure first considered in Hong and
+Yogo (2012). This paradigm implies that returns for individual
+commodities should be high in periods where \textbf{CHP} is low
+(\textbf{backwardation}) and low in periods where \textbf{CHP} is high
+(\textbf{contango}). Over the first period the cross sectional average
+returns during \textbf{backwardation} for both the US and UK commodities
+are positive with those for the US statistically significant, and
+significantly higher than during \textbf{contango}, providing broad
+support for an aggregate version of the Keynesian hedging pressure
+hypothesis. Over the second period this pattern reverses, with both the
+US and UK commodities having significant positive returns during
+\textbf{contango} with these returns being significantly higher than
+during **backwardation\}. This change in pattern suggests that the onset
+of financialization altered the traditional risk shifting nature of
+hedger's behaviour, which is implied by the Keynesian hypothesis. The
+arrival of financial investors raises the question of whether they
+functioned as liquidity providers or liquidity demanders. Arguments have
+been made for both of these possibilities with Moskowitz et al. (2012)
+arguing that financial investors provide liquidity while Kang et al.
+(2017) argue that they demand liquidity. Our analysis of returns in
+periods of low and high aggregate CHP before and during financialization
+allows us to analyse this issue from a new perspective and suggests that
+financial investors may have been liquidity demanders leading hedgers to
+become liquidity providers.
+
+Goldstein and Yang (2017) as well as Goldstein et al. (2014) argue that
+the arrival of financial investors has an impact on the extent of normal
+backwardation in commodity futures markets. Based on their analysis we
+would expect our average CHP factor, which is based on backwardation
+measured by hedger's positions, as well our term structure factor, which
+is based on backwardation measured by roll yield, to be best suited to
+measure the impact of financialization.\\
 We analyze the pricing dynamics over the different periods by first
@@
 which had the effect of driving up and creating bubble like conditions
-in commodity future prices\footnote{\citet{de_schutter_food_2010_1};
-  \citet{gilbert_how_2010}; \citet{gilbert_speculative_2010};
-  \citet{masters_testimony_2008}; \citet{masters_accidental_2008};
-  \citet{herman_not_2011_1}; \citet{schumann_hunger-makers_2011};
-  \citet{singleton_investor_2013}; \citet{unctad_global_2009}.}.
-However, the fundamental question of the nature of the impact of
-financialization across the entire cross-section of commodity futures
-markets has not yet been completely answered. We provide an empirical
-complement to a new stream of theoretical studies that try to model the
-impact of financialization on various aspects of commodity futures
-markets\footnote{\citet{etula_broker-dealer_2013},
-  \citet{acharya_limits_2013}, \citet{cheng_convective_2014},
-  \citet{leclercq_equilibrium_2014}, \citet{sockin_informational_2015},
-  \citet{goldstein_speculation_2013},
-  \citet{EkelandSpeculationcommodityfutures2016},
-  \citet{goldstein_commodity_2017}.} and demonstrate that the effects of
-financialization extend beyond the mechanical effects induced by
-indexation as outlined in \citet{basak_model_2016} as well as
-\citet{tang_index_2012}.
+in commodity future prices\footnote{De Schutter (2010); Gilbert (2010a);
+  Gilbert (2010b); Masters (2008); Masters and White (2008); Herman et
+  al. (2011); Schumann (2011); Singleton (2013); UNCTAD and Cooperation
+  (2009).}. However, the fundamental question of the nature of the
+impact of financialization across the entire cross-section of commodity
+futures markets has not yet been completely answered. We provide an
+empirical complement to a new stream of theoretical studies that try to
+model the impact of financialization on various aspects of commodity
+futures markets\footnote{Etula (2013), Acharya et al. (2013), Cheng et
+  al. (2014), Leclercq and Praz (2014), Sockin and Xiong (2015),
+  Goldstein et al. (2014), Ekeland et al. (2016), Goldstein and Yang
+  (2017).} and demonstrate that the effects of financialization extend
+beyond the mechanical effects induced by indexation as outlined in Basak
+and Pavlova (2016) as well as Tang and Xiong (2012).
 
@@
 with an influx of largely speculative capital that was responsible for
-driving commodity prices beyond their historic highs
-\citep{de_schutter_food_2010_1, gilbert_speculative_2010, herman_not_2011_1, schumann_hunger-makers_2011, unctad_global_2009}.
-The US and various european countries also became involved in this
-issue. Early US Senate investigations drew on pricing and trading data
-supplied by the CFTC as well as interviews with numerous experts
-including hedge fund manager Michael Masters who linked the growing
-presence of index investors in US wheat markets to the observed surges
-in both futures and cash prices
-\citep{masters_testimony_2008, masters_accidental_2008}). This
-contention has since come to be known as the Masters' hypothesis and was
-largely endorsed by the final US Senate report on the issue
-\citep{USSenate_Excessive_speculation_wheat_2009}. At this stage, the
-question thrust on the academic sphere was whether ``excessive
-speculation'' (understood as the market activity peculiar to index type
-investors) was linked to escalating energy and agricultural commodity
-prices. A number of academic studies, most of which used commodity
-specific causality and correlation based analysis have disproved this
-contention, particularly in the case of agricultural and energy
-commodities. \citet{irwin_devil_2009}, \citet{sanders_adequacy_2010},
-\citet{sanders_impact_2011}, \citet{sanders_new_2011},
-\citet{irwin_commodity_2013}, \citet{brunetti_commodity_2014},
-\citet{hamilton_effects_2015} and \citet{bruno_financialization_2017}
-study the agricultural markets. \citet{buyuksahin_speculators_2011},
-\citet{tokic_speculation_2012}, \citet{fattouh_role_2013},
-\citet{kilian_role_2014}, \citet{knittel_simple_2016} and
-\citet{manera_modelling_2016} study the energy markets.
-\citet{bohl_does_2013_2}, \citet{kim_does_2015} and
-\citet{boyd_prevalence_2016} study both energy and agricultural markets
-while \citet{irwin_index_2011}, \citet{irwin_financialization_2012} and
-\citet{stoll_commodity_2011} study the commodity markets in general.
+driving commodity prices beyond their historic highs (De Schutter, 2010;
+Gilbert, 2010b; Herman et al., 2011; Schumann, 2011; UNCTAD and
+Cooperation, 2009). The US and various european countries also became
+involved in this issue. Early US Senate investigations drew on pricing
+and trading data supplied by the CFTC as well as interviews with
+numerous experts including hedge fund manager Michael Masters who linked
+the growing presence of index investors in US wheat markets to the
+observed surges in both futures and cash prices (Masters, 2008; Masters
+and White, 2008)). This contention has since come to be known as the
+Masters' hypothesis and was largely endorsed by the final US Senate
+report on the issue (Senate, 2009). At this stage, the question thrust
+on the academic sphere was whether ``excessive speculation'' (understood
+as the market activity peculiar to index type investors) was linked to
+escalating energy and agricultural commodity prices. A number of
+academic studies, most of which used commodity specific causality and
+correlation based analysis have disproved this contention, particularly
+in the case of agricultural and energy commodities. Irwin et al. (2009),
+Sanders et al. (2010), Sanders and Irwin (2011a), Sanders and Irwin
+(2011b), Irwin (2013), Brunetti and Reiffen (2014), Hamilton and Wu
+(2015) and Bruno et al. (2017) study the agricultural markets.
+Büyükşahin and Harris (2011), Tokic (2012), Fattouh et al. (2013),
+Kilian and Murphy (2014), Knittel and Pindyck (2016) and Manera et al.
+(2016) study the energy markets. Bohl and Stephan (2013), Kim (2015) and
+Boyd et al. (2016) study both energy and agricultural markets while
+Irwin and Sanders (2011), Irwin and Sanders (2012) and Stoll and Whaley
+(2011) study the commodity markets in general.
 
 Other studies have underlined various alterations in commodity pricing
-dynamics over the period. \citet{gilbert_role_2014} reject the view that
-financialization has not had any effects in the grains markets and
+dynamics over the period. Gilbert and Pfuderer (2014) reject the view
+that financialization has not had any effects in the grains markets and
 demonstrate that trades originated by financial actors, and specifically
 index investors, can move prices but tend typically to be
-volatility-reducing. \citet{cheng_financialization_2014} show that in
-the case of index commodities, financialization has transformed the risk
-sharing, and information discovery functions of commodity futures
-markets. \citet{juvenal_speculation_2015} contend that the oil price
-increase between 2004 and 2008 was mainly driven by the strength of
-global demand but that the financialization process of commodity markets
-also played a role. \citet{henderson_new_2015} show that
-non-information-based financial investments have important impacts on
-commodity prices.
+volatility-reducing. Cheng and Xiong (2014) show that in the case of
+index commodities, financialization has transformed the risk sharing,
+and information discovery functions of commodity futures markets.
+Juvenal and Petrella (2015) contend that the oil price increase between
+2004 and 2008 was mainly driven by the strength of global demand but
+that the financialization process of commodity markets also played a
+role. Henderson et al. (2015) show that non-information-based financial
+investments have important impacts on commodity prices.
 
@@
 retail investors to build up commodity exposure in the early 2000s
-\citep{boons_stock_2012, henderson_new_2015, irwin_index_2011, unctad_global_2009, schumann_hunger-makers_2011}.
-Most of these products were primarily designed to track prominent
-commodity indexes amongst which the S\&P-GSCI, the most popular. Most of
-its constituents at the time of writting form the basis of the broad
-cross-section of commodities that we consider in this study\footnote{See
-  section \ref{assets} for details on the commodity pool considered.}.
-Unleaded gasoline, the NYMEX legacy contract for gasoline stopped
-trading in 2006 when it was replaced by Reformulated Gasoline Blendstock
-for Oxygen Blending (RBOB) with the two futures series trading alongside
-for most of the year. For our NYMEX gasoline data series, we consider
-unleaded gasoline up to September 1\textsuperscript{st}, 2006 and RBOB
-gasoline thereafter, date at which liquidity for the latter overtook
-that for the former.
+(Boons et al., 2012; Henderson et al., 2015; Irwin and Sanders, 2011;
+Schumann, 2011; UNCTAD and Cooperation, 2009). Most of these products
+were primarily designed to track prominent commodity indexes amongst
+which the S\&P-GSCI, the most popular. Most of its constituents at the
+time of writting form the basis of the broad cross-section of
+commodities that we consider in this study\footnote{See section
+  \ref{assets} for details on the commodity pool considered.}. Unleaded
+gasoline, the NYMEX legacy contract for gasoline stopped trading in 2006
+when it was replaced by Reformulated Gasoline Blendstock for Oxygen
+Blending (RBOB) with the two futures series trading alongside for most
+of the year. For our NYMEX gasoline data series, we consider unleaded
+gasoline up to September 1\textsuperscript{st}, 2006 and RBOB gasoline
+thereafter, date at which liquidity for the latter overtook that for the
+former.
 
@@
 the reporting threshold. In response to concerns related to category
-accuracy\footnote{See for example \citet{ederington_who_2002}.} the CFTC
+accuracy\footnote{See for example Ederington and Lee (2002).} the CFTC
 now refines its classification in the disaggregated commitment of trader
@@
 commodity producers to allievate their commodity price and output risks.
-\citet{keynes_treatise_1930} and \citet{hicks_value_1939} emphasise the
-``normal'' behaviour of naturally short hedgers outsourcing their
-commodity risk to naturally long commodity specialist speculators. This
-market configuration is referred to as ``backwardation'' where futures
-is expected to trade at a discount to spot, providing speculators with
-incentives to take the long side. The opposite market paradigm is
-referred to as ``contango''. Working
-\citep{working_theory_1948, working_hedging_1953} and Cootner
-\citep{cootner_returns_1960, CootnerSpeculationhedging1967} somehow
-relax this ``supply-of-speculative-services''
-\citep{Tilllongtermperspectivecommodity2007} approach by introducing
-processors and merchants, also commodity experts, on the hedgers side
-and relating the notions of backwardation and contango more directly to
-the term structure via the theory of storage where the shape of the
-front end of the term structure (basis) is directly related to the
-market price of storage.\\
+Keynes (1930) and Hicks (1939) emphasise the ``normal'' behaviour of
+naturally short hedgers outsourcing their commodity risk to naturally
+long commodity specialist speculators. This market configuration is
+referred to as ``backwardation'' where futures is expected to trade at a
+discount to spot, providing speculators with incentives to take the long
+side. The opposite market paradigm is referred to as ``contango''.
+Working (Working, 1953, 1948) and Cootner (Cootner, 1967, 1960) somehow
+relax this ``supply-of-speculative-services'' (Till, 2007) approach by
+introducing processors and merchants, also commodity experts, on the
+hedgers side and relating the notions of backwardation and contango more
+directly to the term structure via the theory of storage where the shape
+of the front end of the term structure (basis) is directly related to
+the market price of storage.\\
 Financialization, on the other hand, refers to the entry of financial
@@
 portfolios with, in most cases, existing large positions across various
-asset classes
-\citep{brunetti_speculators_2016, boyd_prevalence_2016, cheng_convective_2014, juvenal_speculation_2015, singleton_investor_2013, tang_index_2012}.
-This contrasts with the traditional approaches of Keynes and Working and
-in this context the issues of co-movement and aggregate market
-participants behaviour seem particularly relevant.\\
+asset classes (Boyd et al., 2016; Brunetti et al., 2016; Cheng et al.,
+2014; Juvenal and Petrella, 2015; Singleton, 2013; Tang and Xiong,
+2012). This contrasts with the traditional approaches of Keynes and
+Working and in this context the issues of co-movement and aggregate
+market participants behaviour seem particularly relevant.\\
 Asset pricing techniques are well suited to study co-movement. Building
@@
 period, \textbf{CHP} levels below and above the period's median
-respectively and, in contrast with \citep{hong_what_2012} who aggregate
+respectively and, in contrast with (Hong and Yogo, 2012) who aggregate
 across sub-sectors, the asset pool we consider for \textbf{CHP}
@@
 portfolio with a mean return of 6.43\% during \textbf{backwardation}
-rising to 41.22\% during \textbf{contango}, with the difference also
+rising to 41.22\% during **contango\}, with the difference also
 significant at the 1\% level.\\
@@
 risk shifting, the traditional Keynesian view. This phenomenon has been
-noted in earlier theoretical and empirical work
-\citep[\citet{stout_why_1998}]{DanthineInformationfuturesprices1978} in
-different context from which two competing models of behaviour have
-emerged. The information arbitrage model implies that hedgers may often
-be seeking out counterparties to trade with rather than being purely
-passive. This issue is also raised in both
-\citet{cheng_financialization_2014} and
-\citet{StulzRethinkingriskmanagement1996} who point out that hedgers may
-be taking a view on prices just as speculators do. In fact, by hedging
-away some of their risk, hedgers are able to speculate more heavily
-based on their disagreement against speculators regarding futures price
-movement \citep{SimsekSpeculationrisksharing2013}, which fits into a
-heterogenous expectation theory of speculation. As
-\citet{stout_why_1998} points out, this disagreement-based theory of
-trading is one of the main reason the public and the law disapproves the
-speculators as this form of trading is regarded as
-non-productive\footnote{\citet{DuffieChallengespolicytreatment2014} also
-  discusses some of the challenges faced by a policy treatment of
-  speculative trading motivated by differences in beliefs.}. In the
-second model hedgers are seen as liquidity providers as in
-\citet{Kangtaletwopremiums2017}. This explanation is also consistent
-with the nature of financialization which led to the arrival of long
-term, long only investors who require substantial liquidity to roll-over
-their positions.
+noted in earlier theoretical and empirical work (Danthine, 1978, p.
+@stout\_why\_1998) in different context from which two competing models
+of behaviour have emerged. The information arbitrage model implies that
+hedgers may often be seeking out counterparties to trade with rather
+than being purely passive. This issue is also raised in both Cheng and
+Xiong (2014) and Stulz (1996) who point out that hedgers may be taking a
+view on prices just as speculators do. In fact, by hedging away some of
+their risk, hedgers are able to speculate more heavily based on their
+disagreement against speculators regarding futures price movement
+(Simsek, 2013), which fits into a heterogenous expectation theory of
+speculation. As Stout (1998) points out, this disagreement-based theory
+of trading is one of the main reason the public and the law disapproves
+the speculators as this form of trading is regarded as
+non-productive\footnote{Duffie (2014) also discusses some of the
+  challenges faced by a policy treatment of speculative trading
+  motivated by differences in beliefs.}. In the second model hedgers are
+seen as liquidity providers as in Kang et al. (2017). This explanation
+is also consistent with the nature of financialization which led to the
+arrival of long term, long only investors who require substantial
+liquidity to roll-over their positions.
 
@@
 pricing performance. Over all periods, all of our factor models show
-similar pricing performance across regimes of high and low \textbf{CHP}.
+similar pricing performance across regimes of high and low **CHP\}.
 
@@
 
+\begin{landscape}
 \begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
@@
 \bottomrule
-\end{longtabu}\endgroup{}
+\end{longtabu}
+\end{landscape}
+\endgroup{}
 
@@
 \end{longtabu}
-\end{landscape}\endgroup{}
+\end{landscape}
+\endgroup{}
 
@@
 
+\begin{landscape}
 \begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
@@
 TS & 2014/2017 & XCME - Lumber & 41\% & 39\%\\*
-\end{longtabu}\endgroup{}
+\end{longtabu}
+\endgroup{}
 
@@
 Market factor picks & \textasciitilde{} TS factor & None & 7.65\% & 5.2\% & 3.25\% & 6.24\%\\*
-\end{longtabu}\endgroup{}
+\end{longtabu}
+\end{landscape}
+\endgroup{}
 
@@
 
+\begin{landscape}
 \begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
@@
 Market factor picks & \textasciitilde{} TS factor & None & -0.23\% & 1.65\% & 2.15\% & 0.12\%\\*
-\end{longtabu}\endgroup{}
+\end{longtabu}
+\end{landscape}
+\endgroup{}
 
@@
 \bottomrule
-\end{longtabu}\endgroup{}
+\end{longtabu}
+\endgroup{}
 
@@
 
-\bibliography{BibTeX.bib}
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-acharya_limits_2013}{}%
+Acharya, V.V., Lochstoer, L.A., Ramadorai, T., 2013. Limits to arbitrage
+and hedging: Evidence from commodity markets. Journal of Financial
+Economics 109, 441--465.
+doi:\href{https://doi.org/10.1016/j.jfineco.2013.03.003}{10.1016/j.jfineco.2013.03.003}
+
+\leavevmode\hypertarget{ref-anderson_hedger_1983}{}%
+Anderson, R.W., Danthine, J.-P., 1983. Hedger diversity in futures
+markets. The Economic Journal 93, 370--389.
+doi:\href{https://doi.org/10.2307/2232798}{10.2307/2232798}
+
+\leavevmode\hypertarget{ref-baker_financialization_2014}{}%
+Baker, S.D., 2014. The financialization of storable commodities. Finance
+Down Under 2014 Building on the Best from the Cellars of Finance.
+doi:\href{https://doi.org/10.2139/ssrn.2348333\%20}{10.2139/ssrn.2348333 }
+
+\leavevmode\hypertarget{ref-basak_model_2016}{}%
+Basak, S., Pavlova, A., 2016. A model of financialization of
+commodities. The Journal of Finance 71, 1511--1556.
+doi:\href{https://doi.org/10.1111/jofi.12408}{10.1111/jofi.12408}
+
+\leavevmode\hypertarget{ref-basu_capturing_2013}{}%
+Basu, D., Miffre, J., 2013. Capturing the risk premium of commodity
+futures: The role of hedging pressure. Journal of Banking \& Finance 37,
+2652--2664.
+doi:\href{https://doi.org/10.1016/j.jbankfin.2013.02.031}{10.1016/j.jbankfin.2013.02.031}
+
+\leavevmode\hypertarget{ref-bohl_does_2013}{}%
+Bohl, M.T., Stephan, P.M., 2013. Does futures speculation destabilize
+spot prices? New evidence for commodity markets. Journal of Agricultural
+and Applied Economics 45, 595--616.
+doi:\href{https://doi.org/10.1017/S1074070800005150}{10.1017/S1074070800005150}
+
+\leavevmode\hypertarget{ref-boons_stock_2012}{}%
+Boons, M., De Roon, F., Szymanowska, M., 2012. The stock market price of
+commodity risk, in: AFA 2012 Chicago Meetings Paper.
+
+\leavevmode\hypertarget{ref-boyd_prevalence_2016}{}%
+Boyd, N.E., Büyükşahin, B., Haigh, M.S., Harris, J.H., 2016. The
+prevalence, sources, and effects of herding. Journal of Futures Markets
+36, 671--694.
+doi:\href{https://doi.org/10.1002/fut.21756}{10.1002/fut.21756}
+
+\leavevmode\hypertarget{ref-brunetti_speculators_2016}{}%
+Brunetti, C., Büyükşahin, B., Harris, J.H., 2016. Speculators, prices,
+and market volatility. Journal of Financial and Quantitative Analysis
+51, 1545--1574.
+doi:\href{https://doi.org/10.1017/S0022109016000569}{10.1017/S0022109016000569}
+
+\leavevmode\hypertarget{ref-brunetti_commodity_2014}{}%
+Brunetti, C., Reiffen, D., 2014. Commodity index trading and hedging
+costs. Journal of Financial Markets 21, 153--180.
+doi:\href{https://doi.org/10.1016/j.finmar.2014.08.001}{10.1016/j.finmar.2014.08.001}
+
+\leavevmode\hypertarget{ref-bruno_financialization_2017}{}%
+Bruno, V.G., Büyükşahin, B., Robe, M.A., 2017. The financialization of
+food? American Journal of Agricultural Economics 99, 243--264.
+doi:\href{https://doi.org/10.1093/ajae/aaw059}{10.1093/ajae/aaw059}
+
+\leavevmode\hypertarget{ref-buyuksahin_speculators_2011}{}%
+Büyükşahin, B., Harris, J.H., 2011. Do speculators drive crude oil
+futures prices? The Energy Journal 167--202.
+
+\leavevmode\hypertarget{ref-buyuksahin_speculators_2014}{}%
+Büyükşahin, B., Robe, M.A., 2014. Speculators, commodities and
+cross-market linkages. Journal of International Money and Finance,
+Understanding international commodity price fluctuations 42, 38--70.
+doi:\href{https://doi.org/10.1016/j.jimonfin.2013.08.004}{10.1016/j.jimonfin.2013.08.004}
+
+\leavevmode\hypertarget{ref-chang_returns_1985}{}%
+Chang, E.C., 1985. Returns to speculators and the theory of normal
+backwardation. The Journal of Finance 40, 193--208.
+doi:\href{https://doi.org/10.1111/j.1540-6261.1985.tb04944.x}{10.1111/j.1540-6261.1985.tb04944.x}
+
+\leavevmode\hypertarget{ref-cheng_convective_2014}{}%
+Cheng, I.-H., Kirilenko, A., Xiong, W., 2014. Convective risk flows in
+commodity futures markets. Review of Finance 19, 1733--1781.
+doi:\href{https://doi.org/10.1093/rof/rfu043}{10.1093/rof/rfu043}
+
+\leavevmode\hypertarget{ref-cheng_financialization_2014}{}%
+Cheng, I.-H., Xiong, W., 2014. Financialization of commodity markets.
+Annual Review of Financial Economics 6, 419--441.
+doi:\href{https://doi.org/10.1146/annurev-financial-110613-034432}{10.1146/annurev-financial-110613-034432}
+
+\leavevmode\hypertarget{ref-christoffersen_factor_2014}{}%
+Christoffersen, P., Lunde, A., Olesen, K.V., 2014. Factor structure in
+commodity futures return and volatility. Journal of Financial and
+Quantitative Analysis 1--74.
+doi:\href{https://doi.org/10.1017/S0022109018000765}{10.1017/S0022109018000765}
+
+\leavevmode\hypertarget{ref-cootner_returns_1960}{}%
+Cootner, P.H., 1960. Returns to speculators: Telser versus keynes.
+Journal of political Economy 68, 396--404.
+doi:\href{https://doi.org/10.1086/258347}{10.1086/258347}
+
+\leavevmode\hypertarget{ref-cootner_speculation_1967}{}%
+Cootner, P.H., 1967. Speculation and hedging. Food Research Institute
+Studies 7, 65.
+
+\leavevmode\hypertarget{ref-danthine_information_1978}{}%
+Danthine, J.-P., 1978. Information, futures prices, and stabilizing
+speculation. Journal of Economic Theory 17, 79--98.
+doi:\href{https://doi.org/10.1016/0022-0531(78)90124-2}{10.1016/0022-0531(78)90124-2}
+
+\leavevmode\hypertarget{ref-deschutter_food_2010}{}%
+De Schutter, O., 2010. Food commodities speculation and food price
+crises: Regulation to reduce the risks of price volatility. United
+Nations Special Rapporteur on the Right to Food Briefing Note 2, 1--14.
+
+\leavevmode\hypertarget{ref-domanski_financial_2007}{}%
+Domanski, D., Heath, A., 2007. Financial investors and commodity
+markets. Working Paper.
+
+\leavevmode\hypertarget{ref-duffie_challenges_2014}{}%
+Duffie, D., 2014. Challenges to a policy treatment of sSpeculative
+trading motivated by differences in beliefs. The Journal of Legal
+Studies 43, S173--S182.
+doi:\href{https://doi.org/10.1086/677836}{10.1086/677836}
+
+\leavevmode\hypertarget{ref-dusak_futures_1973}{}%
+Dusak, K., 1973. Futures trading and investor returns: An investigation
+of commodity market risk premiums. Journal of Political economy 81,
+1387--1406. doi:\href{https://doi.org/10.1086/260133}{10.1086/260133}
+
+\leavevmode\hypertarget{ref-ederington_who_2002}{}%
+Ederington, L., Lee, J.H., 2002. Who trades futures and how: Evidence
+from the heating oil futures market. The Journal of Business 75,
+353--373. doi:\href{https://doi.org/10.1086/338706}{10.1086/338706}
+
+\leavevmode\hypertarget{ref-ekeland_speculation_2016}{}%
+Ekeland, I., Lautier, D., Villeneuve, B., 2016. Speculation in commodity
+futures markets: A simple equilibrium model.
+
+\leavevmode\hypertarget{ref-etula_broker-dealer_2013}{}%
+Etula, E., 2013. Broker-dealer risk appetite and commodity returns.
+Journal of Financial Econometrics 11, 486--521.
+doi:\href{https://doi.org/10.1093/jjfinec/nbs024}{10.1093/jjfinec/nbs024}
+
+\leavevmode\hypertarget{ref-fattouh_role_2013}{}%
+Fattouh, B., Kilian, L., Mahadeva, L., 2013. The role of speculation in
+oil markets: What have we learnt so far? The Energy Journal 34, 7--33.
+
+\leavevmode\hypertarget{ref-fuertes_commodity_2015}{}%
+Fuertes, A.-M., Miffre, J., Fernandez-Perez, A., 2015. Commodity
+strategies based on momentum, term structure, and idiosyncratic
+volatility. Journal of Futures Markets 35, 274--297.
+doi:\href{https://doi.org/10.1002/fut.21656}{10.1002/fut.21656}
+
+\leavevmode\hypertarget{ref-gilbert_how_2010}{}%
+Gilbert, C.L., 2010a. How to understand high food prices. Journal of
+Agricultural Economics 61, 398--425.
+doi:\href{https://doi.org/10.1111/j.1477-9552.2010.00248.x}{10.1111/j.1477-9552.2010.00248.x}
+
+\leavevmode\hypertarget{ref-gilbert_speculative_2010}{}%
+Gilbert, C.L., 2010b. Speculative influences on commodity futures prices
+2006-2008. UNCTAD, Geneva.
+
+\leavevmode\hypertarget{ref-gilbert_role_2014}{}%
+Gilbert, C.L., Pfuderer, S., 2014. The role of index trading in price
+formation in the grains and oilseeds markets. Journal of Agricultural
+Economics 65, 303--322.
+doi:\href{https://doi.org/10.1111/1477-9552.12068}{10.1111/1477-9552.12068}
+
+\leavevmode\hypertarget{ref-goldstein_speculation_2014}{}%
+Goldstein, I., Li, Y., Yang, L., 2014. Speculation and hedging in
+segmented markets. The Review of Financial Studies 27, 881--922.
+doi:\href{https://doi.org/10.1093/rfs/hht059}{10.1093/rfs/hht059}
+
+\leavevmode\hypertarget{ref-goldstein_commodity_2017}{}%
+Goldstein, I., Yang, L., 2017. Commodity financialization and
+information transmission (SSRN Scholarly Paper No. ID 2555996). Social
+Science Research Network, Rochester, NY.
+doi:\href{https://doi.org/10.2139/ssrn.2555996}{10.2139/ssrn.2555996}
+
+\leavevmode\hypertarget{ref-hamilton_effects_2015}{}%
+Hamilton, J.D., Wu, J.C., 2015. Effects of index-fund investing on
+commodity futures prices. International Economic Review 56, 187--205.
+doi:\href{https://doi.org/10.1111/iere.12099}{10.1111/iere.12099}
+
+\leavevmode\hypertarget{ref-henderson_new_2015}{}%
+Henderson, B.J., Pearson, N.D., Wang, L., 2015. New evidence on the
+financialization of commodity markets. The Review of Financial Studies
+28, 1285--1311.
+doi:\href{https://doi.org/10.1093/rfs/hhu091}{10.1093/rfs/hhu091}
+
+\leavevmode\hypertarget{ref-herman_not_2011}{}%
+Herman, M.-O., Kelly, R., Nash, R., 2011. Not a game, speculation v.
+Food security: Regulating financial markets to grow a better future.
+Oxfam policy and practice: agriculture, food and land 11, 127--138.
+
+\leavevmode\hypertarget{ref-hicks_value_1939}{}%
+Hicks, J.R., 1939. Value and capital. Oxford University Press,
+Cambridge.
+
+\leavevmode\hypertarget{ref-hirshleifer_risk_1988}{}%
+Hirshleifer, D., 1988. Risk, futures pricing, and the organization of
+production in commodity markets. Journal of Political Economy 96,
+1206--1220. doi:\href{https://doi.org/10.1086/261584}{10.1086/261584}
+
+\leavevmode\hypertarget{ref-hirshleifer_determinants_1989}{}%
+Hirshleifer, D., 1989. Determinants of hedging and risk premia in
+commodity futures markets. Journal of Financial and Quantitative
+Analysis 24, 313--331.
+doi:\href{https://doi.org/10.2307/2330814}{10.2307/2330814}
+
+\leavevmode\hypertarget{ref-hirshleifer_hedging_1990}{}%
+Hirshleifer, D., 1990. Hedging pressure and futures price movements in a
+general equilibrium model. Econometrica 58, 411--428.
+doi:\href{https://doi.org/10.2307/2938209}{10.2307/2938209}
+
+\leavevmode\hypertarget{ref-hong_what_2012}{}%
+Hong, H., Yogo, M., 2012. What does futures market interest tell us
+about the macroeconomy and asset prices? Journal of Financial Economics
+105, 473--490.
+doi:\href{https://doi.org/10.1016/j.jfineco.2012.04.005}{10.1016/j.jfineco.2012.04.005}
+
+\leavevmode\hypertarget{ref-irwin_commodity_2013}{}%
+Irwin, S.H., 2013. Commodity index investment and food prices: Does the
+``masters hypothesis'' explain recent price spikes? Agricultural
+Economics 44, 29--41.
+doi:\href{https://doi.org/10.1111/agec.12048}{10.1111/agec.12048}
+
+\leavevmode\hypertarget{ref-irwin_index_2011}{}%
+Irwin, S.H., Sanders, D.R., 2011. Index funds, financialization, and
+commodity futures markets. Applied Economic Perspectives and Policy 33,
+1--31.
+doi:\href{https://doi.org/10.1093/aepp/ppq032}{10.1093/aepp/ppq032}
+
+\leavevmode\hypertarget{ref-irwin_financialization_2012}{}%
+Irwin, S.H., Sanders, D.R., 2012. Financialization and structural change
+in commodity futures markets. Journal of Agricultural and Applied
+Economics 44, 371--396.
+doi:\href{https://doi.org/10.1017/S1074070800000481}{10.1017/S1074070800000481}
+
+\leavevmode\hypertarget{ref-irwin_devil_2009}{}%
+Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009. Devil or angel? The role
+of speculation in the recent commodity price boom (and bust). Journal of
+Agricultural and Applied Economics 41, 377--391.
+doi:\href{https://doi.org/10.1017/S1074070800002856}{10.1017/S1074070800002856}
+
+\leavevmode\hypertarget{ref-juvenal_speculation_2015}{}%
+Juvenal, L., Petrella, I., 2015. Speculation in the oil market. Journal
+of Applied Econometrics 30, 621--649.
+doi:\href{https://doi.org/10.1002/jae.2388}{10.1002/jae.2388}
+
+\leavevmode\hypertarget{ref-kang_tale_2017}{}%
+Kang, W., Rouwenhorst, K.G., Tang, K., 2017. A tale of two premiums: The
+role of hedgers and speculators in commodity futures markets.
+doi:\href{https://doi.org/10.2139/ssrn.2449315}{10.2139/ssrn.2449315}
+
+\leavevmode\hypertarget{ref-keynes_treatise_1930}{}%
+Keynes, J.M., 1930. Treatise on money. Macmillan, London.
+
+\leavevmode\hypertarget{ref-kilian_role_2014}{}%
+Kilian, L., Murphy, D.P., 2014. The role of inventories and speculative
+trading in the global market for crude oil. Journal of Applied
+Econometrics 29, 454--478.
+doi:\href{https://doi.org/10.1002/jae.2322}{10.1002/jae.2322}
+
+\leavevmode\hypertarget{ref-kim_does_2015}{}%
+Kim, A., 2015. Does futures speculation destabilize commodity markets?
+Journal of Futures Markets 35, 696--714.
+doi:\href{https://doi.org/10.1002/fut.21716}{10.1002/fut.21716}
+
+\leavevmode\hypertarget{ref-knittel_simple_2016}{}%
+Knittel, C.R., Pindyck, R.S., 2016. The simple economics of commodity
+price speculation. American Economic Journal: Macroeconomics 8, 85--110.
+doi:\href{https://doi.org/10.1257/mac.20140033}{10.1257/mac.20140033}
+
+\leavevmode\hypertarget{ref-kolb_is_1992}{}%
+Kolb, R.W., 1992. Is normal backwardation normal? Journal of Futures
+Markets 12, 75--91.
+
+\leavevmode\hypertarget{ref-leclercq_equilibrium_2014}{}%
+Leclercq, E., Praz, R., 2014. Equilibrium commodity trading (SSRN
+Scholarly Paper No. ID 2464400). Social Science Research Network,
+Rochester, NY.
+doi:\href{https://doi.org/10.2139/ssrn.2464400}{10.2139/ssrn.2464400}
+
+\leavevmode\hypertarget{ref-manera_modelling_2016}{}%
+Manera, M., Nicolini, M., Vignati, I., 2016. Modelling futures price
+volatility in energy markets: Is there a role for financial speculation?
+Energy Economics, Energy markets 53, 220--229.
+doi:\href{https://doi.org/10.1016/j.eneco.2014.07.001}{10.1016/j.eneco.2014.07.001}
+
+\leavevmode\hypertarget{ref-masters_testimony_2008}{}%
+Masters, M.W., 2008. Testimony before the committee on homeland security
+and governmental affairs. U.S. Senate 20.
+
+\leavevmode\hypertarget{ref-masters_accidental_2008}{}%
+Masters, M., White, A., 2008. The accidental hunt brothers: How
+institutional investors are driving up food and energy prices. Working
+paper.
+
+\leavevmode\hypertarget{ref-moskowitz_time_2012}{}%
+Moskowitz, T.J., Ooi, Y.H., Pedersen, L.H., 2012. Time series momentum.
+Journal of Financial Economics, Special issue on investor sentiment 104,
+228--250.
+doi:\href{https://doi.org/10.1016/j.jfineco.2011.11.003}{10.1016/j.jfineco.2011.11.003}
+
+\leavevmode\hypertarget{ref-sanders_impact_2011}{}%
+Sanders, D.R., Irwin, S.H., 2011a. The impact of index funds in
+commodity futures markets: A systems approach. The Journal of
+Alternative Investments 14, 40--49.
+
+\leavevmode\hypertarget{ref-sanders_new_2011}{}%
+Sanders, D.R., Irwin, S.H., 2011b. New evidence on the impact of index
+funds in u.s. Grain futures markets. Canadian Journal of Agricultural
+Economics/Revue canadienne d'agroeconomie 59, 519--532.
+doi:\href{https://doi.org/10.1111/j.1744-7976.2011.01226.x}{10.1111/j.1744-7976.2011.01226.x}
+
+\leavevmode\hypertarget{ref-sanders_adequacy_2010}{}%
+Sanders, D.R., Irwin, S.H., Merrin, R.P., 2010. The adequacy of
+speculation in agricultural futures markets: Too much of a good thing?
+Applied Economic Perspectives and Policy 32, 77--94.
+doi:\href{https://doi.org/10.1093/aepp/ppp006}{10.1093/aepp/ppp006}
+
+\leavevmode\hypertarget{ref-schumann_hunger_2011}{}%
+Schumann, H., 2011. The hunger-makers: How deutsche bank, goldman sachs
+and other financial institutions are speculating with food at the
+expense of the poorest. Foodwatch, Berlin.
+
+\leavevmode\hypertarget{ref-senate_excessive_2009}{}%
+Senate, U., 2009. Excessive speculation in the wheat market. Majority
+and Minority Staff Report. Permanent Subcommittee on Investigations 24,
+107--108.
+
+\leavevmode\hypertarget{ref-simsek_speculation_2013}{}%
+Simsek, A., 2013. Speculation and risk sharing with new financial
+assets. The Quarterly Journal of Economics 128, 1365--1396.
+doi:\href{https://doi.org/10.1093/qje/qjt007}{10.1093/qje/qjt007}
+
+\leavevmode\hypertarget{ref-singleton_investor_2013}{}%
+Singleton, K.J., 2013. Investor flows and the 2008 boom/bust in oil
+prices. Management Science 60, 300--318.
+doi:\href{https://doi.org/10.1287/mnsc.2013.1756}{10.1287/mnsc.2013.1756}
+
+\leavevmode\hypertarget{ref-sockin_informational_2015}{}%
+Sockin, M., Xiong, W., 2015. Informational frictions and commodity
+markets. The Journal of Finance 70, 2063--2098.
+doi:\href{https://doi.org/10.1111/jofi.12261}{10.1111/jofi.12261}
+
+\leavevmode\hypertarget{ref-stoll_commodity_2011}{}%
+Stoll, H.R., Whaley, R.E., 2011. Commodity index investing: Speculation
+or diversification? The Journal of Alternative Investments 14, 50--60.
+doi:\href{https://doi.org/10.2139/ssrn.1633908}{10.2139/ssrn.1633908}
+
+\leavevmode\hypertarget{ref-stout_why_1998}{}%
+Stout, L.A., 1998. Why the law hates speculators: Regulation and private
+ordering in the market for o.t.c. Derivatives. Duke Law Journal 48,
+701--786.
+
+\leavevmode\hypertarget{ref-stulz_rethink_1996}{}%
+Stulz, R.M., 1996. Rethinking risk management. Journal of Applied
+Corporate Finance 9, 8--25.
+doi:\href{https://doi.org/10.1111/j.1745-6622.1996.tb00295.x}{10.1111/j.1745-6622.1996.tb00295.x}
+
+\leavevmode\hypertarget{ref-szymanowska_anatomy_2014}{}%
+Szymanowska, M., De Roon, F., Nijman, T., Van Den Goorbergh, R., 2014.
+An anatomy of commodity futures risk premia. The Journal of Finance 69,
+453--482.
+doi:\href{https://doi.org/10.1111/jofi.12096}{10.1111/jofi.12096}
+
+\leavevmode\hypertarget{ref-tang_index_2012}{}%
+Tang, K., Xiong, W., 2012. Index investment and the financialization of
+commodities. Financial Analysts Journal 68, 54--74.
+doi:\href{https://doi.org/10.2469/faj.v68.n6.5}{10.2469/faj.v68.n6.5}
+
+\leavevmode\hypertarget{ref-till_long_2007}{}%
+Till, H., 2007. A long-term perspective on commodity futures returns,
+in: Intelligent Commodity Investing. Risk books, London.
+
+\leavevmode\hypertarget{ref-tokic_speculation_2012}{}%
+Tokic, D., 2012. Speculation and the 2008 oil bubble: The d.c.o.t.
+Report analysis. Energy Policy 45, 541--550.
+doi:\href{https://doi.org/10.1016/j.enpol.2012.02.069}{10.1016/j.enpol.2012.02.069}
+
+\leavevmode\hypertarget{ref-unctad_global_2009}{}%
+UNCTAD, S.T.F. on S.I., Cooperation, E., 2009. The global economic
+crisis: Systemic failures and multilateral remedies. UNCTAD, Geneva.
+
+\leavevmode\hypertarget{ref-working_theory_1948}{}%
+Working, H., 1948. Theory of the inverse carrying charge in futures
+markets. Journal of Farm Economics 30, 1--28.
+doi:\href{https://doi.org/10.2307/1232678}{10.2307/1232678}
+
+\leavevmode\hypertarget{ref-working_hedging_1953}{}%
+Working, H., 1953. Hedging reconsidered. Journal of Farm Economics 35,
+544--561. doi:\href{https://doi.org/10.2307/1233368}{10.2307/1233368}
 

### 2024-06-11 others/returns-CHP.rmd
Track 'others' folder

---
title: "Commodity returns ~ commodity CHP"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(kableExtra)
tables <- readr::read_rds(here::here("explore", "results", "regressions-time-series-clean.rds")) %>%
  dplyr::filter(stringr::str_detect(analysis, "CHP")) %>%
  dplyr::mutate(results = purrr::map(results, function(x){
    dplyr::mutate(
      x,
      period = as.character(period),
      period = ifelse(period == "present", "post.crisis", period),
      period = factor(period, levels = c("past", "financialization", "crisis", "post.crisis"))
    ) %>%
      dplyr::arrange(
        sector, subsector, commodity, regressor, period, regime.CHP.type, CHP.regime
      )
  }))
# tables$results[[1]]
percentize <- function(value) paste0(round(value, digits = 4L) * 100, "%")
```

## Individual CHP ####

Individual commodity returns ~ individual commodity CHP.

* Overall
  + Highest explanatory power: pressure relative change, contemporaneous.  
  + Explanatory power decreases over financialisation relative to the previous period with the average $R^{2}$ falling from 25.8% down to 20.8%.  
  + Bounces back in the crisis period with average $R^{2}$ rising to 22.5% and continues into the post-crisis period with average $R^{2}$ reaching 27.2%, slightly beyond pre-financialisation level.
  + Drop is strongest for the metals sector with an average $R^{2}$ of 19.1% over the financialisation period against 28.2% over the previous period and the drop driven by the base metals subsector where the $R^{2}$ for the financialisation period is 25.9% against 47.4% over the previous period. In that case the decrease continues into the crisis with the average $R^{2}$ falling down to 18.1% before bouncing back to 34.5% into the post-crisis period.  
* Regimes  
  + Based on individual CHP.  
    + Kenesian pattern in past period. Flips to contanto in financialisation; continues into crisis. Flips bask to backwardation post-crisis.
    + Difference very pronounced in financialisation period for energy. and base metals although for the latter the pattern is kenesian...
  + Based on aggregate CHP.  
    + Explanatory power slightly better over contango phases in all periods. 
    + Flips to backwardation for energy sector in financialisation. continues into crisis and post-crisis periods.
    + Difference small over the past period for the metals sector. Flips to contango in financialisation. Continues into crisis and post-crisis periods. More pronounced and interesting pattern for the base metals with larger difference in past period where backwardation dominates, flips to contango in financialisation, back to backwardation in crisis with difference very pronounced (32% vs 12%) and back to contango post-crisis albeit with difference less pronounced (37% vs 32%).

### Full Cross-section (US) ####
```{r individual-cross-section}
table <- dplyr::filter(
  tables, analysis == "US commodity returns ~ US commodity individual CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(-c(coefficients, country)) %>%
  dplyr::group_by(regressor, regime.CHP.type, period, CHP.regime) %>%
  dplyr::summarise(average.rsquared = mean(rsquared, na.rm = TRUE)) %>%
  dplyr::mutate(average.rsquared = percentize(average.rsquared)) %>%
  tidyr::pivot_wider(names_from = "period", values_from = "average.rsquared")

kbl(
  table, longtable = T, booktabs = T, full_width = TRUE, 
  # caption = "This table shows mean returns and volatility (sd) for the 24 individual US commodities and the 6 LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.",
  # col.names = c(
  #   "asset", "estimate", "past", "financialisation", "crisis", "post-crisis"
  # ),
  align = c("llllr")
) %>%
  kable_paper("striped") %>% 
  collapse_rows(columns = 1L:4L, valign = "top")
```

### Grouped by sectors ####
```{r individual-sector}
table <- dplyr::filter(
  tables, analysis == "US commodity returns ~ US commodity individual CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(-c(coefficients, country)) %>%
  dplyr::group_by(sector, regressor, regime.CHP.type, period, CHP.regime) %>%
  dplyr::summarise(average.rsquared = mean(rsquared, na.rm = TRUE)) %>%
  dplyr::mutate(average.rsquared = percentize(average.rsquared)) %>%
  tidyr::pivot_wider(names_from = "period", values_from = "average.rsquared")

kbl(
  table, longtable = T, booktabs = T, full_width = TRUE, 
  # caption = "This table shows mean returns and volatility (sd) for the 24 individual US commodities and the 6 LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.",
  # col.names = c(
  #   "asset", "estimate", "past", "financialisation", "crisis", "post-crisis"
  # ),
  align = c("lllllr")
) %>%
  kable_paper("striped") %>% 
  collapse_rows(columns = 1L:5L, valign = "top")
```

### Grouped by subsectors ####
```{r individual-subsector}
table <- dplyr::filter(
  tables, analysis == "US commodity returns ~ US commodity individual CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(-c(coefficients, country)) %>%
  dplyr::group_by(sector, subsector, regressor, regime.CHP.type, period, CHP.regime) %>%
  dplyr::summarise(average.rsquared = mean(rsquared, na.rm = TRUE)) %>%
  dplyr::mutate(average.rsquared = percentize(average.rsquared)) %>%
  tidyr::pivot_wider(names_from = "period", values_from = "average.rsquared")

kbl(
  table, longtable = T, booktabs = T, full_width = TRUE, 
  # caption = "This table shows mean returns and volatility (sd) for the 24 individual US commodities and the 6 LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.",
  # col.names = c(
  #   "asset", "estimate", "past", "financialisation", "crisis", "post-crisis"
  # ),
  align = c("lllllr")
) %>%
  kable_paper("striped") %>% 
  collapse_rows(columns = 1L:6L, valign = "top")
```

### Individual commodities ####
```{r individual}
table <- dplyr::filter(
  tables, analysis == "US commodity returns ~ US commodity individual CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(-c(coefficients, country)) %>%
  dplyr::mutate(rsquared = percentize(rsquared)) %>%
  tidyr::pivot_wider(names_from = "period", values_from = "rsquared")

kbl(
  table, longtable = T, booktabs = T, full_width = TRUE, 
  # caption = "This table shows mean returns and volatility (sd) for the 24 individual US commodities and the 6 LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.",
  # col.names = c(
  #   "asset", "estimate", "past", "financialisation", "crisis", "post-crisis"
  # ),
  align = c("lllllllr")
) %>%
  kable_paper("striped") %>% 
  collapse_rows(columns = 1L:6L, valign = "top")
```

## Aggregate CHP ####

Individual commodity returns ~ aggregate commodity CHP.

### US ####

* Overall
  + Explanatory power increases over financialisation relative to the previous period with the average $R^{2}$ rising from 5.4% up to 7.1%. 
  + Increase further in the crisis (14.7%) before pulling back post-crisis (7.5%).   
  + Increase particularly pronounced in relative sense for metals (15.7% vs 8.4%; strongest for precious: 16.4% vs 7.9%) and energy (6.3% vs 3.4%).
* Regimes  
  + Based on individual CHP.  
    + Difference not marked in past period. Contango starts slightly dominating in financialisation and continues in crisis and post-crisis.  
  + Based on aggregate CHP.  
    + Difference not marked in past period. Contango starts dominating markedly in financialisation and continues in crisis and post-crisis.  
    + Stronger pattern for metals: marked Kenesian paradigm in past period, flips to contango in financialisation with substantial difference (23.4% vs 10%), difference narrows into the crisis (23.7% vs 20.4%) before growing back wide post-crisis (21.4% vs 10.3%).  
    + Pattern for base metals: backwardation (15.4% vs 5.6%), contango (16.19% vs 10.2%), backwardation (30.7% vs 20.2%), contango (18.5% vs 1.1%).

#### Full Cross-section ####
```{r aggregate-US-cross-section}
table <- dplyr::filter(
  tables, analysis == "US commodity returns ~ US commodity aggregate CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(-c(coefficients, country)) %>%
  dplyr::group_by(regressor, regime.CHP.type, period, CHP.regime) %>%
  dplyr::summarise(average.rsquared = mean(rsquared, na.rm = TRUE)) %>%
  dplyr::mutate(average.rsquared = percentize(average.rsquared)) %>%
  tidyr::pivot_wider(names_from = "period", values_from = "average.rsquared")

kbl(
  table, longtable = T, booktabs = T, full_width = TRUE, 
  # caption = "This table shows mean returns and volatility (sd) for the 24 individual US commodities and the 6 LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.",
  # col.names = c(
  #   "asset", "estimate", "past", "financialisation", "crisis", "post-crisis"
  # ),
  align = c("llllr")
) %>%
  kable_paper("striped") %>% 
  collapse_rows(columns = 1L:4L, valign = "top")
```

#### Grouped by sectors ####
```{r aggregate-US-sector}
table <- dplyr::filter(
  tables, analysis == "US commodity returns ~ US commodity aggregate CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(-c(coefficients, country)) %>%
  dplyr::group_by(sector, regressor, regime.CHP.type, period, CHP.regime) %>%
  dplyr::summarise(average.rsquared = mean(rsquared, na.rm = TRUE)) %>%
  dplyr::mutate(average.rsquared = percentize(average.rsquared)) %>%
  tidyr::pivot_wider(names_from = "period", values_from = "average.rsquared")

kbl(
  table, longtable = T, booktabs = T, full_width = TRUE, 
  # caption = "This table shows mean returns and volatility (sd) for the 24 individual US commodities and the 6 LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.",
  # col.names = c(
  #   "asset", "estimate", "past", "financialisation", "crisis", "post-crisis"
  # ),
  align = c("lllllr")
) %>%
  kable_paper("striped") %>% 
  collapse_rows(columns = 1L:5L, valign = "top")
```

#### Grouped by subsectors ####
```{r aggregate-US-subsector}
table <- dplyr::filter(
  tables, analysis == "US commodity returns ~ US commodity aggregate CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(-c(coefficients, country)) %>%
  dplyr::group_by(sector, subsector, regressor, regime.CHP.type, period, CHP.regime) %>%
  dplyr::summarise(average.rsquared = mean(rsquared, na.rm = TRUE)) %>%
  dplyr::mutate(average.rsquared = percentize(average.rsquared)) %>%
  tidyr::pivot_wider(names_from = "period", values_from = "average.rsquared")

kbl(
  table, longtable = T, booktabs = T, full_width = TRUE, 
  # caption = "This table shows mean returns and volatility (sd) for the 24 individual US commodities and the 6 LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.",
  # col.names = c(
  #   "asset", "estimate", "past", "financialisation", "crisis", "post-crisis"
  # ),
  align = c("lllllr")
) %>%
  kable_paper("striped") %>% 
  collapse_rows(columns = 1L:6L, valign = "top")
```

#### Individual commodities ####
```{r aggregate-US}
table <- dplyr::filter(
  tables, analysis == "US commodity returns ~ US commodity aggregate CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(-c(coefficients, country)) %>%
  dplyr::mutate(rsquared = percentize(rsquared)) %>%
  tidyr::pivot_wider(names_from = "period", values_from = "rsquared")

kbl(
  table, longtable = T, booktabs = T, full_width = TRUE, 
  # caption = "This table shows mean returns and volatility (sd) for the 24 individual US commodities and the 6 LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.",
  # col.names = c(
  #   "asset", "estimate", "past", "financialisation", "crisis", "post-crisis"
  # ),
  align = c("lllllllr")
) %>%
  kable_paper("striped") %>% 
  collapse_rows(columns = 1L:6L, valign = "top")
```

### UK ####

Nothing much there.

#### Full Cross-section ####
```{r aggregate-UK-cross-section}
table <- dplyr::filter(
  tables, analysis == "UK commodity returns ~ US commodity aggregate CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(-c(coefficients, country)) %>%
  dplyr::group_by(regressor, regime.CHP.type, period, CHP.regime) %>%
  dplyr::summarise(average.rsquared = mean(rsquared, na.rm = TRUE)) %>%
  dplyr::mutate(average.rsquared = percentize(average.rsquared)) %>%
  tidyr::pivot_wider(names_from = "period", values_from = "average.rsquared")

kbl(
  table, longtable = T, booktabs = T, full_width = TRUE, 
  # caption = "This table shows mean returns and volatility (sd) for the 24 individual US commodities and the 6 LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.",
  # col.names = c(
  #   "asset", "estimate", "past", "financialisation", "crisis", "post-crisis"
  # ),
  align = c("llllr")
) %>%
  kable_paper("striped") %>% 
  collapse_rows(columns = 1L:4L, valign = "top")
```

#### Individual commodities ####
```{r aggregate-UK}
table <- dplyr::filter(
  tables, analysis == "UK commodity returns ~ US commodity aggregate CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(-c(coefficients, country)) %>%
  dplyr::mutate(rsquared = percentize(rsquared)) %>%
  tidyr::pivot_wider(names_from = "period", values_from = "rsquared")

kbl(
  table, longtable = T, booktabs = T, full_width = TRUE, 
  # caption = "This table shows mean returns and volatility (sd) for the 24 individual US commodities and the 6 LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.",
  # col.names = c(
  #   "asset", "estimate", "past", "financialisation", "crisis", "post-crisis"
  # ),
  align = c("lllllllr")
) %>%
  kable_paper("striped") %>% 
  collapse_rows(columns = 1L:6L, valign = "top")
```

### 2024-06-11 others/scratchpad-01.r

@@ -1,0 +1,14 @@
+
+
+old <- readr::read_rds(
+  paste(here::here(), "explore/results/new/regressions.rds", sep = "/")
+)
+
+new <- readr::read_rds(
+  paste(here::here(), "explore/results/new/regressions-new.rds", sep = "/")
+)
+
+head(new$results[[2L]], 100L) %>% dplyr::select()
+tail(new$results[[2L]], 100L)
+
+head(new$results[[2L]], 100L)$model

### 2024-06-11 others/scratchpad-02.r

@@ -1,0 +1,69 @@
+
+library(magrittr)
+
+
+
+statistics <- readr::read_rds(
+  paste(here::here(), "explore/results/new/descriptive statistics.rds", sep = "/")
+)
+
+commodity_futures <- dplyr::mutate(
+  statistics$results[[1L]],
+  results = purrr::map(results, function(y){
+    dplyr::mutate(
+      y, 
+      results = purrr::map(results, function(x){
+        dplyr::mutate(
+          x, 
+          p.value = purrr::map(mean, function(a){
+            tryCatch(
+              { a$p.value }, 
+              error=function(cond) {NA_real_}
+            )
+          }),
+          mean = purrr::map(mean, function(a){
+            tryCatch(
+              { a$estimate }, 
+              error=function(cond) {NA_real_}
+            )
+          })
+        ) %>%
+          dplyr::relocate(sd, .after = last_col())
+      })
+    )
+  })
+)
+
+
+factors <- dplyr::mutate(
+  statistics$results[[2L]],
+  p.value = purrr::map(mean, function(a){
+    tryCatch(
+      { a$p.value }, 
+      error=function(cond) {NA_real_}
+    )
+  }),
+  mean = purrr::map(mean, function(a){
+    tryCatch(
+      { a$estimate }, 
+      error=function(cond) {NA_real_}
+    )
+    }
+  )
+) %>%
+  dplyr::relocate(sd, .after = last_col())
+
+
+statistics_neat <- dplyr::mutate(
+  statistics, results = list(commodity_futures, factors)
+)
+
+
+
+statistics <- readr::write_rds(
+  statistics_neat,
+  paste(
+    here::here(), "explore/results/new/descriptive statistics - clean.rds", sep = "/"
+  )
+) 
+

### 2024-06-11 others/Paper highlights.Rmd

---
title: "Results highlights"
author: "Olivier Bauthéac"
date: ""
output: html_document
---

# Methods
* We consider the entire cross-section of liquid commodities (24 US, 6 UK) in 
  contrast to most other studies that focus on individual commodities or 
  sub-sectors.
* We use a futures-based asset pricing framework that includes factors 
  constructed using both price (market, term structure) and non-price (CHP, 
  open interest) attributes.   
  Helps isolating common driving factors and detecting co-movement.
* We extend the Keynesian individual hedging pressure paradigm by incorporating 
  aggregate CHP (**CHP**), a market wide measure of hedging pressure first 
  considered in @hong_what_2012.

# Results
* A non-price based factor is best able to detect the effects of commodity 
  financialization.
* The effects of the financial crisis and its aftermath are most clearly visible 
  through the performance of the market factor. 
* The effects of financialization seem to go beyond mechanical effects induced 
  by the rise of indexing.

* Over the first period the cross sectional average returns during 
  **backwardation** for both the US and UK commodities are positive with those 
  for the US statistically significant, and significantly higher than during 
  **contango**, providing broad support for an aggregate version of the 
  Keynesian hedging pressure hypothesis. Over the second period this pattern 
  reverses, with both the US and UK commodities having significant positive 
  returns during **contango** with these returns being significantly higher 
  than during **backwardation**. This change in pattern suggests the onset of 
  financialization altered the traditional risk shifting nature of hedger’s 
  behaviour, implied by the Keynesian hypothesis.
  Financial investors may have been liquidity demanders, leading hedgers to 
  become liquidity providers: because financial investors tend to be long only 
  the are liquidity demanders on the long side. Hedgers could therefore have 
  provided the required liquidity by being short as a group (**contango**) and 
  been compensated correspondingly (positive returns).

* Factors constructed with US commos, performance analysis on US commos.
  + The CHP factor shows the greatest improvement in performance in the second 
    period. 
  + The dramatic improvement of the CHP factor in the second period is driven by 
    precious and precious-base metals.  
  + The best performing commodities for the CHP factor exhibited very low 
    pair-wise correlation in the first period, around the average for US traded 
    commodities, while during financialization the average pairwise correlation 
    between the top performing CHP factor commodities is higher than that for 
    the market factor and double of the average for all the US traded 
    commodities.
  + This increase is due to the dramatic rise in average pairwise correlation 
    amongst the US traded metals all of which exhibited high R^2^ with respect 
    to the CHP factor during financialization which in turn is due to their 
    common low level of CHP over this period.  
  + The CHP factor model is therefore able to establish the strengthening link 
    between a non-price attribute and price dynamics in the US metal sub-sector 
    during financialization:

* Factors constructed with the top eight commodities for a given factor, 
  performance analysis on commodity pool used for construction + on US commos.  
  + Results strongly suggest the hedging pressure co-movement and price 
    co-movement link was concentrated in the metals sub-sector.

* Factors constructed with the top eight commodities for a given factor, 
  performance analysis on UK metals.  
  + Results show there was co-movement in global (as opposed to US only) metals 
    returns in the second period and that this co-movement could be detected by 
    our hedging pressure based model.

* Pattern of return for the US traded commodities across **CHP** regimes 
  reverted to Keynesian paradigm over the crisis and aftermath period.

* Pricing results indicate the emergence of a systematic factor across the 
  entire cross-section of the US commodities as well as strong evidence of 
  cross-market linkages.

# Conclusions
* Financialization was a phenomenon endogenous to the commodity markets 
  transmitted via the commodity futures markets and mainly concentrated in a 
  specific sector (metals).
* The crisis and its aftermath, in contrast, seems to have delivered an 
  exogenous shock across the entire cross-section of global commodities.

### 2024-06-11 others/paper/custom/title_page.tex

--- 2024-06-11 others/paper/custom/main.tex
@@
             pdftitle={Financialization of Commodities: an Asset Pricing Perspective},
-            pdfkeywords={Commodity futures; financialization; hedging pressure; financial crisis},
             pdfborder={0 0 0},
@@
   \author{ Devraj Basu  \\  Olivier Bauthéac  
-	  \thanks{ Basu: University of Strathclyde, Glasgow, UK, \href{mailto:devraj.basu@strath.ac.uk}{\nolinkurl{devraj.basu@strath.ac.uk}}.
+	  \thanks{ Basu (corresponding author): University of Strathclyde, Glasgow, UK, \href{mailto:devraj.basu@strath.ac.uk}{\nolinkurl{devraj.basu@strath.ac.uk}}.
 Bauthéac: University of Strathclyde, Glasgow, UK, \href{mailto:olivier.bautheac@strath.ac.uk}{\nolinkurl{olivier.bautheac@strath.ac.uk}}.
@@
 \maketitle
-\begin{abstract}
-The last two decades have seen major changes in the nature of the
-commodity markets with the influx of financial investor inflows followed
-by the financial crisis. We study the effect of these events on
-commodity futures pricing dynamics using commodity asset pricing
-techniques. We find that a non-price based factor is best able to detect
-the effects of commodity financialization, while the effects of the
-financial crisis and after are most clearly visible through the
-performance of the market factor. The effects of financialization seem
-to go beyond mechanical effects induced by the rise of indexing. 
-\newline
-JEL: G11, G23, G13, Q02
-\newline
-Keywords: Commodity futures, financialization, hedging pressure, financial crisis
-
-\end{abstract}
 
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-The last twenty years have seen major upheavals in the commodity markets
-with the onset of financialization\footnote{Starting around 2004, with a
-  view of commodity markets as an emerging asset class and in an effort
-  to hedge against inflation and seek diversification benefits
-  \citep{buyuksahin_speculators_2014, singleton_investor_2013},
-  institutional investors sent forth an unprecedented flow of capital
-  into commodity futures markets. This phenomenon is commonly referred
-  to as the financialization of commodities
-  \citep{domanski_financial_2007}.} as well as the period of the 2008
-financial crisis and its aftermath. Financialization appears to have
-affected a number of economic sectors, including agriculture and energy,
-and its impact has been hotly debated in the policy, legislative,
-regulatory, and academic spheres. A vigorous legislative debate has led
-to regulatory changes accompanied by an equally intense policy and
-academic debate across a number of disciplines about the perceived
-effects on commodity prices of the unprecedented inflow of institutional
-funds brought into commodity futures markets by new index type
-investors\footnote{See section \ref{background} for a detailled
-  discussion.}. In response to immediate policy concerns, the academic
-debate was initially framed rather narrowly. In this paper we take a
-fundamentally different empirical approach that is broader in scope. We
-consider the entire cross-section of actively traded commodities on
-futures markets and use a futures based asset pricing framework that
-includes factors constructed using both price and non-price attributes.
-
-Commodity futures markets have a history of being the classic physical
-commodity risks shifting conduit for commodity specialists, and
-financialization may have altered this long standing paradigm with the
-entry of long only commodity index traders (CITs) with very different
-hedging and volume demands from traditional participants. This change
-could have altered the hedging ontology in these markets and our asset
-pricing framework is well suited to detect these more subtle effects
-driven by changes in the nature of traders. Factor model techniques are
-well suited to isolating common driving factors and detecting
-co-movement and building on theory we develop a bespoke commodity-based
-asset pricing framework that seems well adapted to study these two
-issues simultaneously.
-
-The first factor model we consider (CHP) is based on the well-known
-hedging pressure based theory
-\citep{anderson_hedger_1983, chang_returns_1985, cootner_returns_1960, dusak_futures_1973, hicks_value_1939, hirshleifer_risk_1988, hirshleifer_determinants_1989, hirshleifer_hedging_1990, kolb_is_1992, keynes_treatise_1930}
-which postulates that futures prices for a given commodity are inversely
-related to the extent that commercial hedgers are short or long and we
-use a factor mimicking portfolio that captures the impact of hedging
-pressure as a systemic factor \citep{basu_capturing_2013}. Our second
-factor model is based on open interest growth following
-\citet{hong_what_2012} who find that open interest growth has predictive
-power for individual commodity returns and again we construct a
-long-short factor mimicking portfolio. Our third model is based on term
-structure following \citet{szymanowska_anatomy_2014} and
-\citet{fuertes_commodity_2015} who demonstrate that the term structure
-factor has explanatory power for the cross-section of commodity returns.
-We finally consider an equally weighted portfolio of commodities as a
-proxy for the market factor. Our two price based and two non-price based
-factors allow us to compare and contrast different channels that could
-have led to changes in commodity price dynamics over the last twenty
-years.
-
-We study the performance of these models on a set of twenty-four US
-traded commodities and six UK traded (LME exchange) base metals over the
-1997/2017 period that we divide into four distinct sub-periods. The
-first, the pre-financialization phase, spans the 1997/2003 period; the
-second, the financialization phase, spans the 2004/2007 period\footnote{Starting
-  point based on earlier studies
-  \citep{baker_financialization_2014, christoffersen_factor_2014}.}; the
-third, 2008/2013, encompasses both the financial crisis and the loose
-monetary policy regimes that followed; and the fourth spans the period
-starting in 2014 to present.\\
-Consistent with earlier studies, we observe that mean returns for the US
-traded commodities are sharply higher over the financialization period
-compared to pre-financialization and this pattern extends to UK traded
-metals.
-
-The cross-sectional nature of financialization
-\citep{basak_model_2016, cheng_financialization_2014} leads us to extend
-the Keynesian individual hedging pressure paradigm by incorporating
-aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure
-first considered in \citet{hong_what_2012}. This paradigm implies that
-returns for individual commodities should be high in periods where
-\textbf{CHP} is low (\textbf{backwardation}) and low in periods where
-\textbf{CHP} is high (\textbf{contango}). Over the first period the
-cross sectional average returns during \textbf{backwardation} for both
-the US and UK commodities are positive with those for the US
-statistically significant, and significantly higher than during
-\textbf{contango}, providing broad support for an aggregate version of
-the Keynesian hedging pressure hypothesis. Over the second period this
-pattern reverses, with both the US and UK commodities having significant
-positive returns during \textbf{contango} with these returns being
-significantly higher than during \textbf{backwardation}. This change in
-pattern suggests that the onset of financialization altered the
-traditional risk shifting nature of hedger's behaviour, which is implied
-by the Keynesian hypothesis. The arrival of financial investors raises
-the question of whether they functioned as liquidity providers or
-liquidity demanders. Arguments have been made for both of these
-possibilities with \citet{moskowitz_time_2012} arguing that financial
-investors provide liquidity while \citet{Kangtaletwopremiums2017} argue
-that they demand liquidity. Our analysis of returns in periods of low
-and high aggregate CHP before and during financialization allows us to
-analyse this issue from a new perspective and suggests that financial
-investors may have been liquidity demanders leading hedgers to become
-liquidity providers.
-
-\citet{goldstein_commodity_2017} as well as
-\citet{goldstein_speculation_2014} argue that the arrival of financial
-investors has an impact on the extent of normal backwardation in
-commodity futures markets. Based on their analysis we would expect our
-average CHP factor, which is based on backwardation measured by hedger's
-positions, as well our term structure factor, which is based on
-backwardation measured by roll yield, to be best suited to measure the
-impact of financialization.\\
-We analyze the pricing dynamics over the different periods by first
-studying the time series pricing performance of the various factors on
-all the US traded commodities with the factors constructed using the
-latter set of commodities. The market based factor outperforms the other
-three in the first period and it has a similar level of performance in
-the second period, while the CHP factor shows the greatest improvement
-in performance in the second period. The performance of the market
-factor is driven by agricultural commodities and metals in both the
-first and second period and the dramatic improvement of the CHP factor
-in the second period is driven by precious and precious-base metals. The
-best performing commodities for the market factor exhibited
-approximately the same level of price co-movement both before and during
-financialization. In contrast, the best performing commodities for the
-CHP factor exhibited very low pair-wise correlation in the first period,
-around the average for US traded commodities, while during
-financialization the average pairwise correlation between the top
-performing CHP factor commodities is higher than that for the market
-factor and double of the average for all the US traded commodities. This
-increase is due to the dramatic rise in average pairwise correlation
-amongst the US traded metals all of which exhibited high
-R\textsuperscript{2} with respect to the CHP factor during
-financialization which in turn is due to their common low level of CHP
-over this period. Thus the CHP factor model is able to establish the
-strengthening link between a non-price attribute and price dynamics in
-the US metal sub-sector during financialization.\\
-We explore this issue further by constructing the four factors with the
-top eight commodities for a given factor (factor picks) in each
-period\footnote{See section \ref{methods} for further details.} and
-evaluating its performance on these selected commodities as well as on
-all US traded commodities. The results of this exercise strongly suggest
-that the hedging pressure co-movement and price co-movement link was
-concentrated in the metals sub-sector.
-
-The UK traded base metals provide a useful set of assets to test how
-widespread were the changes in pricing dynamics brought about by the
-onset of financialization. To that end, we examine the performance of
-the four factors on the six UK metals, when constructed from each set of
-factor picks. The resuslts show that here was co-movement in global
-metals returns in the second period and that this co-movement could be
-detected by our hedging pressure based model.
-
-The onset of the financial crisis and the monetary policy regimes that
-followed, on the other hand, also appear to have induced significant
-changes in pricing dynamics. Returns on both US and UK traded
-commodities fell dramatically over both the third and fourth periods
-with the pattern of return for the US traded commodities across
-\textbf{CHP} regimes reverting to Keynesian paradigm. The pricing
-results indicate the emergence of a systematic factor across the entire
-cross-section of the US commodities as well as strong evidence of
-cross-market linkages.
-
-Financialization was an issue of such policy importance that it
-triggered legislative action. The debate was initially framed around
-adequacy of speculation, the burning issue of the day, and the
-consequent analysis focused on the more mechanical effects of
-financialization. With the benefit of hindsight, it appears this
-approach was perhaps too narrow and it now seems necessary to address
-financialization from a broader perspective. Commodity price dynamics
-appear to have altered substantially in quite different ways over the
-financialization and the financial crisis periods and our commodity
-futures based asset pricing approach seems able to provide new insights
-into the nature of these changes: financialization was a phenomenon
-endogenous to the commodity markets transmitted via the commodity
-futures markets and mainly concentrated in a specific sector (metals)
-while the crisis and its aftermath seems to have delivered an exogenous
-shock across the entire cross-section of global commodities. The initial
-view of financialization was that it consisted of speculative flows
-which had the effect of driving up and creating bubble like conditions
-in commodity future prices\footnote{\citet{de_schutter_food_2010_1};
-  \citet{gilbert_how_2010}; \citet{gilbert_speculative_2010};
-  \citet{masters_testimony_2008}; \citet{masters_accidental_2008};
-  \citet{herman_not_2011_1}; \citet{schumann_hunger-makers_2011};
-  \citet{singleton_investor_2013}; \citet{unctad_global_2009}.}.
-However, the fundamental question of the nature of the impact of
-financialization across the entire cross-section of commodity futures
-markets has not yet been completely answered. We provide an empirical
-complement to a new stream of theoretical studies that try to model the
-impact of financialization on various aspects of commodity futures
-markets\footnote{\citet{etula_broker-dealer_2013},
-  \citet{acharya_limits_2013}, \citet{cheng_convective_2014},
-  \citet{leclercq_equilibrium_2014}, \citet{sockin_informational_2015},
-  \citet{goldstein_speculation_2013},
-  \citet{EkelandSpeculationcommodityfutures2016},
-  \citet{goldstein_commodity_2017}.} and demonstrate that the effects of
-financialization extend beyond the mechanical effects induced by
-indexation as outlined in \citet{basak_model_2016} as well as
-\citet{tang_index_2012}.
-
-\hypertarget{data-methods}{%
-\section{Data \& methods}\label{data-methods}}
-
-\hypertarget{background}{%
-\subsection{Background}\label{background}}
-
-The period from 1998 to 2008 saw an influx of investment into commodity
-index linked products most of which made its way into the commodity
-futures market. These commodity indexes whose goal was to track the
-broad movement of commodity prices could be accessed by means of
-exchange traded funds and exchange traded notes. At least \$100 billion
-of new investment flowed into these products over the 1998-2008 period
-with this financialization phenomenon leading to substantial legislative
-changes. Concerns over the consequences of financialization were behind
-Rule 76 FR 4752 issued by the US Commodity Futures Trading Commission
-(CFTC) on January 26\textsuperscript{th}, 2011. This provision emanates
-from the Dodd-Frank Wall Street and Consumer Protection Act of 2010
-(Title VII, Section 737) that mandates the CFTC to use position limits
-to restrict the flow of speculative capital into a number of commodity
-markets. The Rule was approved in a close 3-2 vote and the ensuing
-rulemaking process was extremely contentious with several commissioners
-(Michael Dunn and Scott D. O'Malia in particular) expressing
-reservations about the lack of supporting evidence and the Rule also
-triggering thousands of comment letters as well as a lawsuit against the
-CFTC spearheaded by two Wall Street trade groups, the International
-Swaps \& Derivatives Association (ISDA) and the Securities Industries \&
-Financial Markets Association (SIFMA)\footnote{ISDA \& SIFMA v US CFTC;
-  Complaint, 1:11-cv-02146; December 2\textsuperscript{nd}, 2011.}.
-
-A world-wide debate has ensued about the role of index funds in
-commodity markets. The first responses to the 2007/2008 crisis of
-escalating food and energy prices took the form of policy reports, many
-of which reasoned that the growth of commodity index funds came along
-with an influx of largely speculative capital that was responsible for
-driving commodity prices beyond their historic highs
-\citep{de_schutter_food_2010_1, gilbert_speculative_2010, herman_not_2011_1, schumann_hunger-makers_2011, unctad_global_2009}.
-The US and various european countries also became involved in this
-issue. Early US Senate investigations drew on pricing and trading data
-supplied by the CFTC as well as interviews with numerous experts
-including hedge fund manager Michael Masters who linked the growing
-presence of index investors in US wheat markets to the observed surges
-in both futures and cash prices
-\citep{masters_testimony_2008, masters_accidental_2008}). This
-contention has since come to be known as the Masters' hypothesis and was
-largely endorsed by the final US Senate report on the issue
-\citep{USSenate_Excessive_speculation_wheat_2009}. At this stage, the
-question thrust on the academic sphere was whether ``excessive
-speculation'' (understood as the market activity peculiar to index type
-investors) was linked to escalating energy and agricultural commodity
-prices. A number of academic studies, most of which used commodity
-specific causality and correlation based analysis have disproved this
-contention, particularly in the case of agricultural and energy
-commodities. \citet{irwin_devil_2009}, \citet{sanders_adequacy_2010},
-\citet{sanders_impact_2011}, \citet{sanders_new_2011},
-\citet{irwin_commodity_2013}, \citet{brunetti_commodity_2014},
-\citet{hamilton_effects_2015} and \citet{bruno_financialization_2017}
-study the agricultural markets. \citet{buyuksahin_speculators_2011},
-\citet{tokic_speculation_2012}, \citet{fattouh_role_2013},
-\citet{kilian_role_2014}, \citet{knittel_simple_2016} and
-\citet{manera_modelling_2016} study the energy markets.
-\citet{bohl_does_2013_2}, \citet{kim_does_2015} and
-\citet{boyd_prevalence_2016} study both energy and agricultural markets
-while \citet{irwin_index_2011}, \citet{irwin_financialization_2012} and
-\citet{stoll_commodity_2011} study the commodity markets in general.
-
-Other studies have underlined various alterations in commodity pricing
-dynamics over the period. \citet{gilbert_role_2014} reject the view that
-financialization has not had any effects in the grains markets and
-demonstrate that trades originated by financial actors, and specifically
-index investors, can move prices but tend typically to be
-volatility-reducing. \citet{cheng_financialization_2014} show that in
-the case of index commodities, financialization has transformed the risk
-sharing, and information discovery functions of commodity futures
-markets. \citet{juvenal_speculation_2015} contend that the oil price
-increase between 2004 and 2008 was mainly driven by the strength of
-global demand but that the financialization process of commodity markets
-also played a role. \citet{henderson_new_2015} show that
-non-information-based financial investments have important impacts on
-commodity prices.
-
-\hypertarget{data}{%
-\subsection{Data}\label{data}}
-
-Commodity index funds (CIFs), commodity based exchange traded funds
-(ETFs) and notes (ETNs) as well as commodity linked notes (CLNs) were
-amongst the main investment vehicules that allowed institutional and
-retail investors to build up commodity exposure in the early 2000s
-\citep{boons_stock_2012, henderson_new_2015, irwin_index_2011, unctad_global_2009, schumann_hunger-makers_2011}.
-Most of these products were primarily designed to track prominent
-commodity indexes amongst which the S\&P-GSCI, the most popular. Most of
-its constituents at the time of writting form the basis of the broad
-cross-section of commodities that we consider in this study\footnote{See
-  section \ref{assets} for details on the commodity pool considered.}.
-Unleaded gasoline, the NYMEX legacy contract for gasoline stopped
-trading in 2006 when it was replaced by Reformulated Gasoline Blendstock
-for Oxygen Blending (RBOB) with the two futures series trading alongside
-for most of the year. For our NYMEX gasoline data series, we consider
-unleaded gasoline up to September 1\textsuperscript{st}, 2006 and RBOB
-gasoline thereafter, date at which liquidity for the latter overtook
-that for the former.
-
-The commodity futures trading commission (CFTC) operates a comprehensive
-system of collecting information on market participants known as the
-large trader reporting program (LTRP) where it records and reports to
-the public market position data on market particpants who have position
-levels in excess of a particular futures market specific
-threshold\footnote{Current reporting level thresholds available at:
-  \href{https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=\&SID=970471b8455f4bab7db4110cfde50731\&mc=true\&r=SECTION\&n=se17.1.15_103}{www.ecfr.gov}.}.
-The commission collects market data and position information daily from
-clearing members, futures commission merchants (FCMs) and foreign
-brokers and publishes corresponding summaries weekly in a series of
-market specific reports. In these reports, individual traders are
-categorised according to the nature of their trading activity on the
-basis of self-reported information\footnote{CFTC form 40. Available at:
-  \href{https://www.cftc.gov/sites/default/files/idc/groups/public/@forms/documents/file/cftcform40.pdf}{www.cftc.gov}.}
-that is subject to review by CFTC staff for reasonableness. Position
-information is then aggregated by category and asset type with each
-report providing an aggregation for a set of report specific categories
-and, for each category, a breakdown between futures only positions and
-positions in futures and options combined.\\
-In its legacy report, the commitment of trader report (COT) with data
-dating back to 1962, the CFTC distinguishes ``commercial'' and
-``non-commercial'' market participants where a ``commercial''
-participant is defined as one ``{[}\ldots{}{]} engaged in business
-activities hedged by the use of futures and option markets''\footnote{See
-  \href{https://www.gpo.gov/fdsys/pkg/CFR-1998-title17-vol1/xml/CFR-1998-title17-vol1-sec1-3.xml}{CFTC
-  regulation 1.3, 17 CFR 1.3(z)} for details.}. A third category,
-``non-reportable'', aggregates positions for participants not meeting
-the reporting threshold. In response to concerns related to category
-accuracy\footnote{See for example \citet{ederington_who_2002}.} the CFTC
-now refines its classification in the disaggregated commitment of trader
-report (DCOT) where participant categories include
-``Producer/Merchant/Processor/User'', ``Swap dealer'', ``Money manager''
-and ``Other reportable'' as well as in the supplemental commitment of
-trader report (SCOT) that details commodity index trader aggregate
-positions for thirteen agricultural commodity futures markets. Data for
-DCOT and SCOT dates back to 2006 and 2007 respectively.\\
-We study the 1997/2017 period where we observe futures only position
-data from the COT report, the only CFTC report with data available for
-the whole period of interest; as well as futures term structure price
-and open interest data from Bloomberg.
-
-\hypertarget{methods}{%
-\subsection{Methods}\label{methods}}
-
-On the one hand, futures markets have a long history of serving
-commodity producers to allievate their commodity price and output risks.
-\citet{keynes_treatise_1930} and \citet{hicks_value_1939} emphasise the
-``normal'' behaviour of naturally short hedgers outsourcing their
-commodity risk to naturally long commodity specialist speculators. This
-market configuration is referred to as ``backwardation'' where futures
-is expected to trade at a discount to spot, providing speculators with
-incentives to take the long side. The opposite market paradigm is
-referred to as ``contango''. Working
-\citep{working_theory_1948, working_hedging_1953} and Cootner
-\citep{cootner_returns_1960, CootnerSpeculationhedging1967} somehow
-relax this ``supply-of-speculative-services''
-\citep{Tilllongtermperspectivecommodity2007} approach by introducing
-processors and merchants, also commodity experts, on the hedgers side
-and relating the notions of backwardation and contango more directly to
-the term structure via the theory of storage where the shape of the
-front end of the term structure (basis) is directly related to the
-market price of storage.\\
-Financialization, on the other hand, refers to the entry of financial
-investors into the commodity futures markets who, for the most part, are
-not commodity experts. Besides, these new market participants tend to
-exhibit herding like behaviour, often taking massive long-only positions
-on the whole cross-section of indexed commodities in an attempt to hedge
-against inflation and/or seek further diversification benefits for
-portfolios with, in most cases, existing large positions across various
-asset classes
-\citep{brunetti_speculators_2016, boyd_prevalence_2016, cheng_convective_2014, juvenal_speculation_2015, singleton_investor_2013, tang_index_2012}.
-This contrasts with the traditional approaches of Keynes and Working and
-in this context the issues of co-movement and aggregate market
-participants behaviour seem particularly relevant.\\
-Asset pricing techniques are well suited to study co-movement. Building
-on theory we develop an ad-hoc commodity based asset pricing framework
-that we believe is well adapted to study these two issues simultaneously
-and implement it over four periods of interest. The first, the
-pre-financialization period, starts in 1997 and is naturally followed by
-financialization, spanning the 2004/2007 period, and the financial
-crisis and its aftermath, spanning the 2008/2013 period. The last period
-spans the 2014/present period sarting with the beginning of the
-tapering/end of the US Quantitative Easing program (QE).\\
-Using the weekly price, open interest and market position data described
-above we construct market portfolios of commodity nearby futures as well
-as mimicking portfolios for market, commercial hedging pressure, term
-structure and liquidity risk factors in returns. While our market
-portfolios are long only, equally weighted portfolios of particular
-commodity sets, our other mimicking portfolios for risk factors are
-constructed as combinations of two sub-portfolios (legs), one held long,
-one held short, which respective constituents are pooled on a weekly
-basis according to risk factor specific criterias. The weekly return for
-a particular mimicking portfolio is calculated as the difference between
-the average return for constituents of the long portfolio and that for
-the constituents of the short portfolio. i.e, return on the mimicking
-portfolio for risk factor \(i\) (\(f_{i}\)) for week \(t\):
-
-\[r_{t}^{f_{i}}=\frac{1}{x}\sum_{j=1}^{x}r_{j,t}-\frac{1}{x}\sum_{j=n-x}^{n}r_{j,t}\]
-\(n\equiv\) number of commodities in the set considered for mimicking
-portfolio construction.\\
-\(x = \left \lceil n \cdot s \right \rceil\)\\
-\(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
-\(r_{j,t}=\frac{C_{j,t}}{C_{j,t-1}}-1\)\\
-\(C_{j,t}\equiv\) week \(t\) close price for commodity \(j\).\\
-\(j\equiv\) commodity rank in the ordered set \(Y_{t}^{f_{i}}\).\\
-\(Y_{t}^{f_{i}}\equiv\) week \(t\) ordered set of the commodities
-considered for mimicking portfolio construction where the ordering rule
-is specific to \(f_{i}\).
-
-For our portfolio CHP (commercial hedging pressure), we sort the set of
-commodities considered on past twenty six-week average CHP from lowest
-to highest. The bottom third constituents (lowest \(\overline{CHP}\)s)
-of the corresponding ordered set form the long leg of the portfolio
-while the top third form the short leg:
-
-\[Y_{t}^{CHP}\equiv\left \{ \left \{ \overline{CHP_{1}}, \overline{CHP_{2}}, ..., \overline{CHP_{n}} \right \}, \leq \right \}\]
-
-\(\overline{CHP_{j}}=\frac{1}{26}\sum_{k=0}^{25}\frac{L_{j,t-k}}{L_{j,t-k}+S_{j,t-k}}\)\\
-\(L_{j,t}\equiv\) number of long positions held by commercial hedgers
-for week \(t\) on the futures series of commodity \(j\).\\
-\(S_{j,t}\equiv\) number of short positions held by commercial hedgers
-for week \(t\) on the futures series of commodity \(j\).
-
-For our portfolio TS (term structure), we sort the set of commodities
-considered on past twenty six-week average roll-yield from highest to
-lowest. The bottom third constituents (highest \(\overline{RY}\)s) of
-the corresponding ordered set form the long leg of the portfolio while
-the top third form the short leg:
-
-\[Y_{t}^{TS}\equiv\left \{ \left \{ \overline{RY_{1}}, \overline{RY_{2}}, ..., \overline{RY_{n}} \right \}, \geq \right \}\]
-
-\(\overline{RY_{j}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{F_{j,t-k}^{1}}{F_{j,t-k}^{2}} - 1)\)\\
-\(F_{j,t}^{1}\equiv\) week \(t\) close price for commodity \(j\) first
-nearby futures contract.\\
-\(F_{j,t}^{2}\equiv\) week \(t\) close price for commodity \(j\) second
-nearby futures contract.
-
-For our portfolio OI (open interest), we sort the set of commodities
-considered on past twenty six-week average aggregate open interest
-growth from highest to lowest. The bottom third constituents (highest
-\(\overline{\mathbf{OI}^{\Delta \%}}\)s) of the corresponding ordered
-set form the long leg of the portfolio while the top third form the
-short leg.
-
-\[Y_{t}^{OI}\equiv\left \{ \left \{ \overline{\mathbf{OI}_{1}^{\Delta \%}}, \overline{\mathbf{OI}_{2}^{\Delta \%}}, ..., \overline{\mathbf{OI}_{n}^{\Delta \%}} \right \}, \geq \right \}\]
-
-\(\overline{\mathbf{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{\mathbf{OI}_{j,t-k}}{\mathbf{OI}_{j,t-k-1}} - 1)\)\\
-\(\mathbf{OI}_{j,t}=\sum_{k=1}^{l_{j,t}}OI_{j,t,k}\)\\
-\(OI_{j,t,k}\equiv\) open interest at close of week \(t\) for the
-\(k^{th}\) nearby contract on the futures term structure for commodity
-\(j\).\\
-\(l_{j,t}\equiv\) length of commodity \(j\)'s futures term structure on
-week \(t\) close.
-
-We use a time series regression approach where we start with regressions
-of the US traded individual commodity weekly front returns on returns to
-the mimicking portfolio for a particular risk factor where the portfolio
-is constructed using the whole cross-section of US traded commodities.
-The corresponding adjusted \(R^{2}\)s are averaged and the process is
-repeated for each of our four risk factors (market, hedging pressure,
-term structure and liquidity) and periods (1997/2003, 2004/2007,
-2008/2013 and 2014/2017). i.e, average adjusted \(R^{2}\) for risk
-factor \(i\) (\(f_{i}\)) over period \(t\):
-
-\[\overline{\tilde{R}_{f_{i},t}^{2}}=\frac{1}{24}\sum_{j=1}^{24}\tilde{R}_{j,t}^{2}\]
-\(\tilde{R_{j}^{2}}=1-(1-R_{j}^{2})\frac{T-1}{T-p-1}\)\footnote{The
-  Wherry formula-1.}\\
-\(T\equiv\) length of period \(t\) (number of weeks here).\\
-\(p\equiv\) number of regressors (1 here).\\
-\(R_{j,t}^{2}=1-\frac{\sum_{k=1}^{T}(y_{j,k}-\hat{y_{j,k}})^{2}}{\sum_{k=1}^{T}(y_{j,k}-\overline{y_{j}})^{2}}\)\\
-\(y_{j,t}\equiv\) week \(t\) nearby return for commodity \(j\).\\
-\(\hat{y_{j,t}}=\beta_{0}+\beta_{1}f_{i,t}+\epsilon\)\\
-\(\beta s \equiv\) classic OLS coefficient estimates.\\
-\(f_{i,t}\equiv\) week \(t\) return on mimicking portfolio for risk
-factor \(f_{i}\)
-
-The same operation is repeated for the two (\(p=2\)) and three (\(p=3\))
-factor model cases, where regressors include in turn all combinations of
-any two and three risk factors respectivly, as well as for the four
-(\(p=4\)) factor model case where all the risk factor mimicking
-portfolios are included. Results are reported for the one-factor model
-case with the other results available from the authors upon request.\\
-For each period we also implement the analysis described above over
-periods of low and high aggregate CHP (\textbf{CHP}), a notion which we
-introduce in this study and which we believe is particularly relevant in
-the context of financialization where issues of co-movement and
-aggregate market participants' behaviour play a central role. We define
-\textbf{CHP} as the cross-sectional average of CHPs for a particular
-pool of assets. i.e, Week \(t\) \textbf{CHP} for asset pool \(x\):
-
-\[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}\] \(n\equiv\)
-number of commodities in set \(x\).\\
-\(CHP_{i,t}\equiv\) week \(t\) CHP for commodity \(i\) as defined above.
-
-We further define aggregate backwardation (\textbf{backwardation}) and
-contango (\textbf{contango}) \textbf{CHP} regimes as, for a given
-period, \textbf{CHP} levels below and above the period's median
-respectively and, in contrast with \citep{hong_what_2012} who aggregate
-across sub-sectors, the asset pool we consider for \textbf{CHP}
-construction include the whole cross-section of US traded commodities.
-
-In the next part of the analysis, our mimicking portfolios for risk
-factors, constructed from the set of all US traded commodities are used
-as commodity picking devices on the latter commodity set. For each risk
-factor and period, individual US traded commodity front returns are
-regressed on returns for the corresponding mimicking portfolio.
-Individual commodities are sorted by adjusted \(R^{2}\)
-(\(\tilde{R^{2}}\)) accordingly from highest to lowest and the bottom
-third (highest \(\tilde{R^{2}}\)s) are selected as commodity picks for
-the risk factor for the period. i.e, set of picks \(P_{t}^{f_{i}}\) for
-risk factor \(i\) (\(f_{i}\)) over period \(t\):
-
-\[P_{t}^{f_{i}}\equiv\left \{ P_{1}, P_{2}, ..., P_{x} \right \}\]
-\(x = \left \lceil n \cdot s \right \rceil\)\\
-\(n\equiv\) number of commodities in the set considered for the picking
-excersise (twenty-four here).\\
-\(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
-\(P_{j}\equiv\) commodity pick \(j\) for risk factor \(f_{i}\) over
-period \(t\)\\
-\(j\equiv\) rank in the ordered set \(Y_{t}^{f_{i}}\)\\
-\[Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}\]
-\(n\equiv\) number of commodities in the set considered for picking
-(twenty-four here).\\
-\(\tilde{R_{j}^{2}}\equiv\) risk factor \(f_{i}\) returns' explanatory
-power on commodity \(j\) nearby futures returns over period \(t\) as
-defined above.
-
-For each period and \textbf{CHP} regime we record the proportion of time
-each pick is held in the long and (/or) short leg of the corresponding
-risk factor mimicking portfolio as well as the average pairwise
-correlation amongst every sets of picks.
-
-In the last part of the analysis, for each period our mimicking
-portfolios for risk factors in returns are constructed using each set of
-commodity picks independently as the asset pool for portfolio
-construction. A similar time series approach to that described above is
-then implemented using these newly formed mimicking portfolios. In this
-case, a first set of dependent variables includes the sets of commodity
-picks themselves, a second set includes the whole cross-section of US
-traded commodities while a third set includes the six UK traded metals
-considered. The latter are also used as dependent variables in the last
-series of regressions where the long and short legs of the newly formed
-risk factor mimicking portfolios described above are considered
-separately as regressors.
-
-\hypertarget{results-discussion}{%
-\section{Results \& discussion}\label{results-discussion}}
-
-The descriptive statistics over the various time periods for our two
-sets of commodities (US and non-US) as well as the four factors
-considered are shown in Table \ref{table1}. The traditional Keynesian
-hedging pressure paradigm postulates a negative relationship between the
-return on an individual commodity and its hedging pressure.
-Financialization has been seen as a cross-sectional commodity market
-phenomenon; this naturally leads us to extend the individual hedging
-pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a
-market wide measure of hedging pressure. The extended Keynesian hedging
-pressure paradigm should also imply that returns for individual
-commodities should be high in periods where \textbf{CHP} is low and vice
-et versa.\\
-In table \ref{table2} the mean returns are shown over high
-(\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP}
-regimes for each time period. Over the first period eighteen of the
-twenty-four US commodities have higher mean returns during periods of
-\textbf{backwardation} as compared to \textbf{contango}, with the
-difference being statistically significant at the 5\% level for one
-commodity and for the remaining six commodities the higher mean return
-during \textbf{contango} is not statistically significant for any of
-them. For the six UK commodities, all metals, four of them had higher
-mean returns during phases of \textbf{backwardation} as compared to
-\textbf{contango} in the first period, with one of these differences
-being statistically significant at the 5\% level while for the remaining
-two the higher mean return during \textbf{contango} is not statistically
-significant for either. An equally weighted portfolio of the twenty-four
-US commodities had a mean return of 10.98\% during
-\textbf{backwardation} phases, statistically significant at the 1\%
-level, and a mean return of 0.93\% during \textbf{contango}, both in the
-first period, with the difference between them statistically significant
-at the 5\% level. The corresponding figures for an equally weighted
-portfolio of the UK metals were 8.35\% and -1.71\%, the difference again
-statistically significant at the 5\% level. These results provide broad
-support for an aggregate version of the Keynesian hedging pressure
-hypothesis and suggests that hedgers in the aggregate were engaged in
-risk transfer during this period.\\
-Over the second period the pattern essentially reverses. For the
-twenty-four US commodities over this period, eighteen have higher mean
-returns during phases of \textbf{backwardation} over \textbf{contango},
-with the difference statistically significant for four commodities and
-of the remaining seven the higher mean return during
-\textbf{backwardation} is statistically significant for one commodity.
-All of the six UK metals achieved higher mean returns over
-\textbf{backwardation} than contango with the difference being
-statistically significant for one commodity. The equally weighted US
-portfolio had a mean return of 11.16\% over \textbf{backwardation} while
-it was 26.68\% during \textbf{contango}, the first statistically
-significant at the 5\% level and the second at the 1\% level, with the
-difference statistically significant at the 1\% level. The difference
-was considerably more pronounced for the equally weighted UK metals
-portfolio with a mean return of 6.43\% during \textbf{backwardation}
-rising to 41.22\% during \textbf{contango}, with the difference also
-significant at the 1\% level.\\
-Thus the onset of financialization seems to have engendered a change in
-the nature of hedger's behaviour in the aggregate, taking it away from
-risk shifting, the traditional Keynesian view. This phenomenon has been
-noted in earlier theoretical and empirical work
-\citep[\citet{stout_why_1998}]{DanthineInformationfuturesprices1978} in
-different context from which two competing models of behaviour have
-emerged. The information arbitrage model implies that hedgers may often
-be seeking out counterparties to trade with rather than being purely
-passive. This issue is also raised in both
-\citet{cheng_financialization_2014} and
-\citet{StulzRethinkingriskmanagement1996} who point out that hedgers may
-be taking a view on prices just as speculators do. In fact, by hedging
-away some of their risk, hedgers are able to speculate more heavily
-based on their disagreement against speculators regarding futures price
-movement \citep{SimsekSpeculationrisksharing2013}, which fits into a
-heterogenous expectation theory of speculation. As
-\citet{stout_why_1998} points out, this disagreement-based theory of
-trading is one of the main reason the public and the law disapproves the
-speculators as this form of trading is regarded as
-non-productive\footnote{\citet{DuffieChallengespolicytreatment2014} also
-  discusses some of the challenges faced by a policy treatment of
-  speculative trading motivated by differences in beliefs.}. In the
-second model hedgers are seen as liquidity providers as in
-\citet{Kangtaletwopremiums2017}. This explanation is also consistent
-with the nature of financialization which led to the arrival of long
-term, long only investors who require substantial liquidity to roll-over
-their positions.
-
-The average time series pricing performance of the various one factor
-models on the US traded assets over the four periods is shown in Table
-\ref{table3}. Over the first period the market factor has the best
-average time series performance with the highest average adjusted
-R\textsuperscript{2} with all three futures market factors performing
-poorly and the overall pricing performance consistent across periods of
-high and low \textbf{CHP} (below period median). The two factor models
-average R\textsuperscript{2}s (results available upon request) are
-roughly the sum of the one factor R\textsuperscript{2}s indicating that
-the factors are almost orthogonal over this period. The onset of
-financialization leads to a substantial improvement in the performance
-of the CHP factor with its average R\textsuperscript{2} increasing to
-5.4\% in the second period relative to 1.4\% in the first. The
-performance of the market factor also improves though not by as much in
-a relative sense (18.6\% from 12.2\%). Both the term structure factor
-and the open interest growth factor show a much smaller improvement in
-pricing performance. Over all periods, all of our factor models show
-similar pricing performance across regimes of high and low \textbf{CHP}.
-
-We next investigate the top eight of the US traded commodities which
-achieved the highest time series R\textsuperscript{2} for the CHP,
-market, open interest and term structure factors, in each of the four
-time periods with the commodity picks shown in Table \ref{table4}. For
-the CHP factor the commodities that achieve high R\textsuperscript{2} in
-a given period are likely to be those with relatively high or low CHP
-over that period, or those commodities that co-vary with the short or
-the long side of the factor. The same applies to the open interest and
-term structure factors with CHP replaced by open interest growth and
-roll yield respectively; while for the market factor the picks are those
-that co-vary most strongly with the market factor over that period. For
-the CHP factor, we observe a change in the picks between the first and
-the second period; the picks in the first period included five
-agricultural commodities and three metals while in the second period
-include all of the five base and precious metals and only three
-agricultural commodities. This pattern is also visible for the term
-structure factor for which there are four metals (gold, copper,
-palladium and platinum) picks in the second period against three in the
-first (gold, palladium and platinum). The market factor has two metal
-picks in the second period (palladium and silver) while all of the picks
-in the first period were agricultural or energy commodities. Over the
-third period, the average CHP factor has four metal picks while both the
-term structure factor and market factor have three. Table \ref{table4}
-also shows the proportion of time that these picks were constituents of
-the corresponding factor. All of the picks of the long-short factors
-(average CHP, open interest growth and term structure factors) were
-constituents of the corresponding factor for some proportion of time in
-all of the time periods. In this respect, there is a contrast between
-the first and second periods for the average CHP with the picks
-appearing predominantly on the long side in the second period, as
-opposed to both legs in the first. This indicates that the picks in the
-second period consistently exhibited low CHP. This behaviour continued
-over the third period.
-
-In table \ref{table5}, we show the average pairwise correlation between
-each set of picks in each time period. This exercise gives an indication
-of the extent to which attribute co-movement reveals price co-movement,
-which is particularly relevant for the long-short factors for which the
-corresponding attribute is not directly related to price co-movement. In
-the first period, the average CHP factor picks pairwise correlation is
-similar to the average across the US traded twenty-four commodities
-(around 0.1) with the market factor picks showing the highest figure
-(0.21). In the second period however it is the highest (0.27),
-comparable with the market (0.26) and double of the US traded
-commodities average (0.13). This increase is a consequence of the
-dramatic increase in average pairwise price correlation amongst the US
-traded metals, all of which are CHP factor picks. Taken together with
-the fact that four of these metals had consistently low CHP, we see that
-CHP co-movement in the second period is strongly correlated with price
-co-movement. It is also interesting to note that US traded metals
-returns were negatively correlated with the rest of US traded
-commodities in the first period and positively in the second (Results
-available upon request).
-
-In order to further understand the link between attribute and price
-co-movement we build all of the factors from every set of factor picks
-and assess their pricing performance on these sets of picks. The results
-are shown in table \ref{table6}. The long-short factors for a particular
-attribute select the top and bottom three of the corresponding picks
-based on that attribute while the market factor takes an equally
-weighted combination of the eight corresponding picks. In the absence of
-price co-movement between the picks, this market factor will achieve an
-average R\textsuperscript{2} of around 12.5\%\footnote{Market factor
-  lemma:
-  \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\)
-  size of market portfolio (eight here). See section
-  \ref{market-factor-lemma} for a formal proof.}, while there is no
-non-zero R\textsuperscript{2} lower bound for the corresponding
-long-short factors. A high average R\textsuperscript{2} for the market
-factor is indicative of strong price co-movement while for the
-long-short factors it is indicative of simultaneous attribute and price
-co-movement. The most dramatic change in pricing performance occurs for
-the average CHP factor picks where the market factor built from these
-picks has an average R\textsuperscript{2} of 21.3 \% in the first period
-(close to the 0 correlation situation) and jumps to 37.4 \% in the
-second period. The average CHP factor built with average CHP factor
-picks also shows a sharp increase in pricing performance over the second
-period. There is also substancial improvement in pricing performance of
-the CHP factor built with term structure picks (3.4\%
-vs.~21.2\%)\footnote{In contrast to the market factor, there is no
-  pricing performance lower bound for the CHP factor built with a set of
-  picks.}, providing evidence of convergence of Keynesian and Working's
-theories of the term structure in detecting price co-movement during
-financialization. In table \ref{table7} we assess the performance of the
-same factors on all the commodities instead of just the picks. While the
-average R\textsuperscript{2}s are expectedly lower, the relative
-performance of the market factors built with different sets of picks is
-similar to table \ref{table6}. In contrast, the increase in
-R\textsuperscript{2} for the average CHP factor built with average CHP
-factor picks is lower indicating that the link between CHP co-movement
-and price co-movement is strongest amongst the picks which are
-predominantly metals.\\
-The conclusion from Tables \ref{table6} and \ref{table7} is that the
-onset of financialization seems to have had a major impact on the
-dynamics of US traded precious and precious-base metals and we now seek
-to analyse whether this phenomenon is true for the non-US metal futures.
-To that end we examine the pricing performance of the factors used in
-Table \ref{table6} on the six UK metals futures. The results are
-reported in Table \ref{table8}. In the first period, the average
-R\textsuperscript{2}s across the board are always less than 4.5\%. In
-the second period we see a dramatic increase in R\textsuperscript{2} for
-the market factor built with average CHP factor picks and average term
-structure factor picks (4.48\% to 25.1\% and 1.3\% to 20.6\%
-respectively) showing dramatically higher co-movement between UK traded
-metals and the corresponding picks all of which are US traded
-commodities. The increase in R\textsuperscript{2} for the market factor
-built with market factor picks is much more modest, providing further
-evidence of concentration of co-movement in the metal sector during
-financialization.
-
-In order to understand this better, in table \ref{table9}, we examine
-the pricing performance of both long and short legs of the corresponding
-factors separately on the same set of UK traded metals. The most
-striking result here is the dramatic increase in R\textsuperscript{2}
-for the long leg of the term structure factor built with CHP factor
-picks which achieves the highest overall R\textsuperscript{2} in the
-second period (1.91\% vs.~27.37\%). This provides further evidence that
-global metals co-movement could be detected by US based factor models
-that combined the Keynesian and Working's notions of backwardation.
-
-We then turn our analysis to the crisis and post-crisis period
-(2008-2013). In table \ref{table1} we see that the returns on both US
-and non-US commodities fall dramatically over this period, going down to
--4.3\% for the UK metals and 8\% for the US traded commodities although
-volatility for both sets of assets is similar to that during the second
-period. Two of the UK metals have negative mean returns over the third
-period compared to one over the first and none over the second. This
-trend continues in from 2014 to 2017 with the US traded commodities
-recording an average mean return of -0.6\% and the UK metals an average
-of 4.9\% over this period, with fourteen US traded commodities and one
-UK metal having negative mean returns. The volatility of both sets of
-assets is lower than over the 2004-2007 period, particularly for the UK
-metals, suggesting the impact of the investment outflows from the
-commodity futures markets has had a much lower impact on volatility than
-the corresponding inflows witnessed over the financialization period.
-The market factor dominates pricing performance over this period with an
-increase of mean average R\textsuperscript{2} of over 50\% while that
-for the other factors increases slightly at best (table \ref{table3}).
-From table \ref{table5} we see that there is an across the board
-increase in pairwise correlations with a doubling in the average
-pairwise correlation of all US traded commodities and a levelling in the
-pairwise correlation of the picks of the three long-short factors. Taken
-together, these results indicate the presence of a systematic factor
-across the entire cross-section of the US commodities. This is clearly
-evident in the performance of the market factor built with any set of
-picks on the entire set of US traded commodities (table \ref{table7}) as
-we see a dramatic rise across the board in pricing performance. Table
-\ref{table8} provides further evidence of systematic linkages, in this
-case between US and non-US traded commodities as the market factor built
-with its own picks (US traded commodities) achieves an average
-R\textsuperscript{2} of 33.7\% on the UK metals compared to 9.9\% in the
-previous period.
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-In the early 2000s, against a backdrop of a low yield environment and
-poor stock market performance, a combination of financial
-innovation\footnote{Tradable commodity price indexes (commonly referred
-  to as commodity index funds or CIFs), and commodity-based exchange
-  traded funds (ETFs) were the main financial innovations which allowed
-  the large global banks to offer commodity investment products to
-  institutional and retail investors. In 1991 Goldman Sachs created the
-  S\&P-GSCI which provides investors with buy-side exposure to
-  commodities via the OTC swap market and thus without having to
-  participate in the formal futures markets with their position limit
-  restrictions. At this stage these restrictions still applied to the
-  bank though, as it hedged its commodity swap exposure in the futures
-  markets. The first commodity-based ETFs were created through buying
-  physical precious metals with gold and silver ETFs offered as early as
-  2002/2003. The regulatory hurdle here related to the licensing of
-  commodity trading professionals. Typically, investors had to sign a
-  statement with their broker stating that they understood the risks of
-  commodity investments; a rather inconvenient paperwork for a product
-  designed to trade like a stock, as set forth by a number of industry
-  players at the time.} and deregulation\footnote{In 2000, the Commodity
-  Futures Modernization Act (CFMA) granted non-agricultural commodity
-  futures statutory exemption from regulation (``Enron loophole'') while
-  it required that agricultural commodity derivatives be traded on a
-  CFTC-regulated exchange. Notwithstanding, the CFTC classified swap
-  dealers as ``bona fide'' hedgers, granting them position limits
-  exemption (``swap dealer loophole'').\\
-  In 2005, the CFTC waived the rule that required commodity investors to
-  sign a statement saying they understood the risks, letting the funds
-  replace it with their prospectus and thus unleashed commodity-based
-  ETFs investments.} led to a large inflow of institutional and
-financial capital into the commodity futures markets. This process known
-as financialization lead to a heated public policy debate about whether
-the increase in open interest and trading volume in commodities exerted
-upward pressure on prices. Perhaps in response to this, most of the
-early studies focused on the more mechanical effects of
-financialization, relying on commodity specific causality and
-correlation based analysis. With the benefit of hindsight this focus
-appears to have been too narrow and it seems important to analyze the
-effects of financialization from a broader perspective which we do in
-this study. We consider the entire cross-section of actively traded
-commodities on futures markets and use a futures based asset pricing
-framework that includes factors constructed using both price and
-non-price attributes. Factor model techniques are well suited to
-isolating common driving factors and detecting co-movement, a central
-issue in financialization which we believe the existing literature has
-not fully analyzed. Our analysis suggests that financialization was a
-phenomenon endogenous to the commodity markets transmitted via the
-futures markets and appears to have had the deepest impact on global
-metal futures markets. The onset of the financial crisis and the
-monetary policy regimes that followed appear to have also induced
-significant changes in commodity pricing dynamics and our analysis
-suggest that in contrast with financialization, the crisis and its
-aftermath have delivered an exogenous shock across the entire
-cross-section of global commodities.
-
-\newpage
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:`mean returns`}\label{table1} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study.
-Figures labelled *** (**, *) are significant at the 1\% (5\%, 10\%) level.
-See section \ref{methods} for more details.}\\
-\toprule
-Assets & Variable & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-US-Agriculturals-Grains & Mean return & 3.75\% & ***18.99\% & 5.34\% & -4.14\%\\
-US-Agriculturals-Grains & Volatility & 27.14\% & 29.17\% & 33.52\% & 25.18\%\\
-US-Agriculturals-Livestock & Mean return & 3.81\% & 5.84\% & *9.53\% & 0.16\%\\
-US-Agriculturals-Livestock & Volatility & 26.53\% & 21.59\% & 23.94\% & 26.55\%\\
-US-Agriculturals-Softs & Mean return & 1.57\% & **14.26\% & 9.53\% & 2.97\%\\
-US-Agriculturals-Softs & Volatility & 33.47\% & 30.19\% & 35.53\% & 28.08\%\\
-US-Metals-Industrial & Mean return & 2.42\% & **33.08\% & 6.74\% & 1.35\%\\
-US-Metals-Industrial & Volatility & 20.2\% & 30.44\% & 31.66\% & 19.95\%\\
-US-Metals-Precious & Mean return & *9.39\% & ***22.7\% & 9.99\% & 2.13\%\\
-US-Metals-Precious & Volatility & 26.2\% & 25.61\% & 31.76\% & 21.57\%\\
-US-Agriculturals & Mean return & 2.89\% & ***14.45\% & **7.86\% & -0.44\%\\
-US-Agriculturals & Volatility & 29.72\% & 28.24\% & 32.69\% & 26.64\%\\
-US-Energy & Mean return & 13.56\% & ***28.33\% & 6.94\% & -4.13\%\\
-US-Energy & Volatility & 44.03\% & 42.77\% & 39.5\% & 36.52\%\\
-US-Metals & Mean return & *7.99\% & ***24.77\% & 9.34\% & 1.98\%\\
-US-Metals & Volatility & 25.12\% & 26.64\% & 31.73\% & 21.24\%\\
-US-Commodity & Mean return & **5.73\% & ***18.9\% & ***8.01\% & -0.55\%\\
-US-Commodity & Volatility & 31.73\% & 30.84\% & 33.72\% & 27.56\%\\
-UK-Commodity & Mean return & 2.95\% & ***23.91\% & 4.25\% & 4.87\%\\
-UK-Commodity & Volatility & 20.33\% & 33.43\% & 35.99\% & 22.33\%\\
-CHP factor & Mean return & 0.34\% & 1.09\% & -0.15\% & -1.98\%\\
-CHP factor & Volatility & 7.78\% & 8.05\% & 8.93\% & 7.45\%\\
-Market factor & Mean return & 5.99\% & ***18.81\% & 8.01\% & -0.55\%\\
-Market factor & Volatility & 10.2\% & 12.39\% & 17.26\% & 10.3\%\\
-OI factor & Mean return & -0.2\% & 2.79\% & -4.28\% & 2.28\%\\
-OI factor & Volatility & 8.26\% & 8.16\% & 8.1\% & 6.69\%\\
-TS factor & Mean return & **-9.49\% & *-7.15\% & -5.77\% & **-9.02\%\\
-TS factor & Volatility & 10.25\% & 8.31\% & 9.91\% & 8.52\%\\
-\bottomrule
-\end{longtabu}\endgroup{}
-
-\newpage
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{landscape}
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:`mean returns - aggregate CHP regimes`}\label{table2} This table shows descriptive statistics for nearby futures returns on various commodity groups as well as for mimicking portfolios for risk factors where the factor portfolios are constructed using the whole cross-section of the US traded commodities considered in the study.
-For each period the results are shown for \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
-Figures labelled *** (**, *) are significant at the 1\% (5\%, 10\%) level.
-See section \ref{methods} for more details.}\\
-\toprule
-Assets & CHP regime & Variable & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-\endfirsthead
-\caption[]{continued}\\
-\toprule
-Assets & CHP regime & Variable & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-\endhead
-\
-\endfoot
-\bottomrule
-\endlastfoot
-US-Agriculturals-Grains & High & Mean return & 4.25\% & ***29.78\% & -2.92\% & -0.55\%\\
-US-Agriculturals-Grains & High & Volatility & 27.61\% & 30.17\% & 36.06\% & 24.93\%\\
-US-Agriculturals-Grains & Low & Mean return & 3.24\% & 8.26\% & *13.66\% & -7.76\%\\
-US-Agriculturals-Grains & Low & Volatility & 26.67\% & 28.09\% & 30.73\% & 25.43\%\\
-US-Agriculturals-Livestock & High & Mean return & -2.15\% & -1.68\% & 4.05\% & -15.8\%\\
-US-Agriculturals-Livestock & High & Volatility & 29.3\% & 20.65\% & 23.59\% & 25.46\%\\
-US-Agriculturals-Livestock & Low & Mean return & 9.84\% & 13.43\% & *15.04\% & 16.28\%\\
-US-Agriculturals-Livestock & Low & Volatility & 23.38\% & 22.47\% & 24.29\% & 27.48\%\\
-US-Agriculturals-Softs & High & Mean return & -1.31\% & ***24.85\% & 11.43\% & -3.34\%\\
-US-Agriculturals-Softs & High & Volatility & 32.54\% & 30.48\% & 36.06\% & 28.72\%\\
-US-Agriculturals-Softs & Low & Mean return & 4.47\% & 3.67\% & 7.62\% & 9.33\%\\
-US-Agriculturals-Softs & Low & Volatility & 34.4\% & 29.84\% & 35\% & 27.42\%\\
-US-Metals-Industrial & High & Mean return & -0.45\% & **51.48\% & 1.3\% & -13.36\%\\
-US-Metals-Industrial & High & Volatility & 20.55\% & 31.58\% & 36.97\% & 18.91\%\\
-US-Metals-Industrial & Low & Mean return & 5.3\% & 14.86\% & 12.22\% & 16.2\%\\
-US-Metals-Industrial & Low & Volatility & 19.89\% & 29.2\% & 25.31\% & 20.85\%\\
-US-Metals-Precious & High & Mean return & -3.38\% & ***37.17\% & -2.16\% & -3.58\%\\
-US-Metals-Precious & High & Volatility & 28.72\% & 23.7\% & 32.66\% & 22.64\%\\
-US-Metals-Precious & Low & Mean return & ***22.26\% & 8.36\% & **22.23\% & 7.9\%\\
-US-Metals-Precious & Low & Volatility & 23.28\% & 27.26\% & 30.77\% & 20.42\%\\
-US-Agriculturals & High & Mean return & 0.74\% & ***21.45\% & 4.21\% & -4.72\%\\
-US-Agriculturals & High & Volatility & 30\% & 28.67\% & 33.93\% & 26.61\%\\
-US-Agriculturals & Low & Mean return & 5.06\% & 7.46\% & **11.52\% & 3.88\%\\
-US-Agriculturals & Low & Volatility & 29.44\% & 27.79\% & 31.39\% & 26.67\%\\
-US-Energy & High & Mean return & 3.9\% & *29.75\% & -3.1\% & -23.15\%\\
-US-Energy & High & Volatility & 43.76\% & 45.83\% & 45.46\% & 40.32\%\\
-US-Energy & Low & Mean return & *23.3\% & *26.93\% & *17.04\% & 15.07\%\\
-US-Energy & Low & Volatility & 44.3\% & 39.55\% & 32.39\% & 32.06\%\\
-US-Metals & High & Mean return & -2.79\% & ***40.04\% & -1.47\% & -5.54\%\\
-US-Metals & High & Volatility & 27.27\% & 25.45\% & 33.54\% & 21.93\%\\
-US-Metals & Low & Mean return & ***18.86\% & 9.66\% & ***20.22\% & 9.56\%\\
-US-Metals & Low & Volatility & 22.65\% & 27.63\% & 29.75\% & 20.49\%\\
-US-Commodity & High & Mean return & 0.53\% & ***26.68\% & 1.81\% & *-7.96\%\\
-US-Commodity & High & Volatility & 32.19\% & 31.59\% & 36.02\% & 28.52\%\\
-US-Commodity & Low & Mean return & ***10.98\% & **11.16\% & ***14.25\% & *6.93\%\\
-US-Commodity & Low & Volatility & 31.25\% & 30.04\% & 31.22\% & 26.52\%\\
-UK-Commodity & High & Mean return & -1.71\% & ***41.22\% & -1.32\% & **-13.66\%\\
-UK-Commodity & High & Volatility & 21.05\% & 33.54\% & 38.82\% & 21.69\%\\
-UK-Commodity & Low & Mean return & *8.35\% & 6.43\% & 10.04\% & ***23.4\%\\
-UK-Commodity & Low & Volatility & 19.45\% & 33.17\% & 32.8\% & 22.69\%\\
-CHP factor & High & Mean return & 1.45\% & 7.88\% & 0.89\% & -3.48\%\\
-CHP factor & High & Volatility & 8.08\% & 8.28\% & 9.81\% & 7.11\%\\
-CHP factor & Low & Mean return & -0.98\% & -5.63\% & -1.2\% & -0.47\%\\
-CHP factor & Low & Volatility & 7.43\% & 7.75\% & 7.97\% & 7.81\%\\
-Market factor & High & Mean return & 0.67\% & ***26.46\% & 1.81\% & -7.96\%\\
-Market factor & High & Volatility & 10.27\% & 11.96\% & 18.97\% & 11.24\%\\
-Market factor & Low & Mean return & **11.43\% & 11.16\% & 14.25\% & 6.93\%\\
-Market factor & Low & Volatility & 10.1\% & 12.78\% & 15.37\% & 9.19\%\\
-OI factor & High & Mean return & -0.76\% & 4.89\% & -6.9\% & 3.84\%\\
-OI factor & High & Volatility & 7.92\% & 8.79\% & 8.64\% & 6.7\%\\
-OI factor & Low & Mean return & 0.46\% & 0.72\% & -1.65\% & 0.7\%\\
-OI factor & Low & Volatility & 8.66\% & 7.52\% & 7.53\% & 6.7\%\\
-TS factor & High & Mean return & **-13.59\% & -7.38\% & -8.14\% & *-11.23\%\\
-TS factor & High & Volatility & 10.38\% & 8.71\% & 10.76\% & 8.39\%\\
-TS factor & Low & Mean return & -4.6\% & -6.92\% & -3.37\% & -6.79\%\\
-TS factor & Low & Volatility & 10.08\% & 7.94\% & 9\% & 8.69\%\\*
-\end{longtabu}
-\end{landscape}\endgroup{}
-
-\newpage
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:`factor regressions`}\label{table3} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby futures returns on the commodities forming the entire cross-section of US traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using whole set of US traded commodities considered.
-For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
-See section \ref{methods} for more details.}\\
-\toprule
-Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-US commodities & \textasciitilde{} CHP factor & High & 1.54\% & 5.5\% & 5.89\% & 3.73\%\\
-US commodities & \textasciitilde{} CHP factor & Low & 1.39\% & 5.64\% & 7.33\% & 5.43\%\\
-US commodities & \textasciitilde{} CHP factor & None & 1.37\% & 5.43\% & 5.99\% & 4.47\%\\
-US commodities & \textasciitilde{} Market factor & High & 13.04\% & 16.96\% & 30.45\% & 17.62\%\\
-US commodities & \textasciitilde{} Market factor & Low & 11.61\% & 19.83\% & 28.92\% & 13.53\%\\
-US commodities & \textasciitilde{} Market factor & None & 12.2\% & 18.55\% & 29.45\% & 15.57\%\\
-US commodities & \textasciitilde{} OI factor & High & 0.82\% & 1.32\% & 1.19\% & 0.31\%\\
-US commodities & \textasciitilde{} OI factor & Low & 1.42\% & -0.39\% & 0.54\% & 0.56\%\\
-US commodities & \textasciitilde{} OI factor & None & 0.66\% & 0.36\% & 0.31\% & 0.31\%\\
-US commodities & \textasciitilde{} TS factor & High & 2.12\% & 3.36\% & 4.68\% & 2.69\%\\
-US commodities & \textasciitilde{} TS factor & Low & 2.88\% & 2.72\% & 5.57\% & 3.09\%\\
-US commodities & \textasciitilde{} TS factor & None & 2.4\% & 2.7\% & 4.69\% & 2.52\%\\
-\bottomrule
-\end{longtabu}\endgroup{}
-
-\newpage
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright\arraybackslash}p{3.5cm}>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:`factor picks`}\label{table4} For each risk factor and period, this table displays the list of corresponding commodity factor picks along with the proportion of time they are individually held on the long and short legs of the corresponding risk factor mimicking portfolio.
-The factor portfolios are constructed from the whole set of the twenty four US traded commodities considered which is also used as asset pool for the commodity picking exercise.
-See section \ref{methods} for more details.}\\
-\toprule
-Factor & Period & Asset & Long & Short\\
-\midrule
-\endfirsthead
-\caption[]{continued}\\
-\toprule
-Factor & Period & Asset & Long & Short\\
-\midrule
-\endhead
-\
-\endfoot
-\bottomrule
-\endlastfoot
-CHP & 1997/2003 & XCBT - Oats & 97\% & 0\%\\
-CHP & 1997/2003 & XCBT - Soy-oil & 42\% & 32\%\\
-CHP & 1997/2003 & XCBT - Wheat-SRW & 29\% & 9\%\\
-CHP & 1997/2003 & XCEC - Copper & 43\% & 18\%\\
-CHP & 1997/2003 & XCEC - Silver & 100\% & 0\%\\
-CHP & 1997/2003 & XNYM - Platinum & 91\% & 4\%\\
-CHP & 1997/2003 & IFUS - Coffee & 22\% & 17\%\\
-CHP & 1997/2003 & IFUS - Orange juice & 67\% & 18\%\\
-Market & 1997/2003 & XCBT - Corn & 100\% & 0\%\\
-Market & 1997/2003 & XCBT - Oats & 100\% & 0\%\\
-Market & 1997/2003 & XCBT - Soy-meal & 100\% & 0\%\\
-Market & 1997/2003 & XCBT - Wheat-SRW & 100\% & 0\%\\
-Market & 1997/2003 & XNYM - Crude oil & 100\% & 0\%\\
-Market & 1997/2003 & XNYM - Gasoline & 100\% & 0\%\\
-Market & 1997/2003 & XNYM - Heating oil & 100\% & 0\%\\
-Market & 1997/2003 & XNYM - Natural gas & 99\% & 0\%\\
-OI & 1997/2003 & XCME - Feeder cattle & 27\% & 39\%\\
-OI & 1997/2003 & XCME - Lean hogs & 36\% & 30\%\\
-OI & 1997/2003 & XNYM - Crude oil & 24\% & 28\%\\
-OI & 1997/2003 & XNYM - Natural gas & 46\% & 24\%\\
-OI & 1997/2003 & XCEC - Gold & 39\% & 28\%\\
-OI & 1997/2003 & XNYM - Palladium & 46\% & 33\%\\
-OI & 1997/2003 & IFUS - Coffee & 39\% & 23\%\\
-OI & 1997/2003 & XCME - Lumber & 42\% & 33\%\\
-TS & 1997/2003 & XCBT - Soy-meal & 71\% & 0\%\\
-TS & 1997/2003 & XNYM - Crude oil & 53\% & 9\%\\
-TS & 1997/2003 & XNYM - Gasoline & 61\% & 17\%\\
-TS & 1997/2003 & XNYM - Heating oil & 35\% & 24\%\\
-TS & 1997/2003 & XCEC - Gold & 10\% & 1\%\\
-TS & 1997/2003 & XNYM - Palladium & 61\% & 0\%\\
-TS & 1997/2003 & XNYM - Platinum & 96\% & 0\%\\
-TS & 1997/2003 & IFUS - Sugar & 60\% & 26\%\\
-CHP & 2004/2007 & XCBT - Oats & 100\% & 0\%\\
-CHP & 2004/2007 & XCEC - Copper & 44\% & 37\%\\
-CHP & 2004/2007 & XCEC - Gold & 100\% & 0\%\\
-CHP & 2004/2007 & XCEC - Silver & 100\% & 0\%\\
-CHP & 2004/2007 & XNYM - Palladium & 100\% & 0\%\\
-CHP & 2004/2007 & XNYM - Platinum & 100\% & 0\%\\
-CHP & 2004/2007 & IFUS - Coffee & 15\% & 5\%\\
-CHP & 2004/2007 & IFUS - Orange juice & 66\% & 15\%\\
-Market & 2004/2007 & XCBT - Corn & 100\% & 0\%\\
-Market & 2004/2007 & XCBT - Soybeans & 100\% & 0\%\\
-Market & 2004/2007 & XNYM - Crude oil & 100\% & 0\%\\
-Market & 2004/2007 & XNYM - Gasoline & 100\% & 0\%\\
-Market & 2004/2007 & XNYM - Heating oil & 100\% & 0\%\\
-Market & 2004/2007 & XNYM - Natural gas & 100\% & 0\%\\
-Market & 2004/2007 & XCEC - Silver & 100\% & 0\%\\
-Market & 2004/2007 & XNYM - Palladium & 100\% & 0\%\\
-OI & 2004/2007 & XCME - Lean hogs & 38\% & 22\%\\
-OI & 2004/2007 & XCME - Live cattle & 32\% & 35\%\\
-OI & 2004/2007 & XNYM - Natural gas & 32\% & 35\%\\
-OI & 2004/2007 & XNYM - Palladium & 43\% & 28\%\\
-OI & 2004/2007 & IFUS - Cocoa & 18\% & 36\%\\
-OI & 2004/2007 & IFUS - Coffee & 34\% & 28\%\\
-OI & 2004/2007 & IFUS - Cotton & 33\% & 17\%\\
-OI & 2004/2007 & IFUS - Sugar & 48\% & 16\%\\
-TS & 2004/2007 & XCEC - Copper & 86\% & 0\%\\
-TS & 2004/2007 & XCME - Feeder cattle & 86\% & 0\%\\
-TS & 2004/2007 & XCME - Lean hogs & 44\% & 46\%\\
-TS & 2004/2007 & XCME - Live cattle & 56\% & 23\%\\
-TS & 2004/2007 & XCEC - Gold & 28\% & 0\%\\
-TS & 2004/2007 & XNYM - Palladium & 0\% & 6\%\\
-TS & 2004/2007 & XNYM - Platinum & 95\% & 0\%\\
-TS & 2004/2007 & IFUS - Cocoa & 15\% & 12\%\\
-CHP & 2008/2013 & XCBT - Soy-meal & 79\% & 4\%\\
-CHP & 2008/2013 & XNYM - Gasoline & 46\% & 0\%\\
-CHP & 2008/2013 & XNYM - Heating oil & 1\% & 18\%\\
-CHP & 2008/2013 & XCEC - Gold & 96\% & 0\%\\
-CHP & 2008/2013 & XCEC - Silver & 90\% & 0\%\\
-CHP & 2008/2013 & XNYM - Palladium & 100\% & 0\%\\
-CHP & 2008/2013 & XNYM - Platinum & 100\% & 0\%\\
-CHP & 2008/2013 & IFUS - Orange juice & 96\% & 0\%\\
-Market & 2008/2013 & XCBT - Corn & 100\% & 0\%\\
-Market & 2008/2013 & XCBT - Oats & 100\% & 0\%\\
-Market & 2008/2013 & XCEC - Copper & 100\% & 0\%\\
-Market & 2008/2013 & XNYM - Crude oil & 100\% & 0\%\\
-Market & 2008/2013 & XNYM - Gasoline & 100\% & 0\%\\
-Market & 2008/2013 & XNYM - Heating oil & 100\% & 0\%\\
-Market & 2008/2013 & XCEC - Silver & 100\% & 0\%\\
-Market & 2008/2013 & XNYM - Palladium & 100\% & 0\%\\
-OI & 2008/2013 & XCBT - Corn & 21\% & 37\%\\
-OI & 2008/2013 & XCBT - Soy-meal & 37\% & 34\%\\
-OI & 2008/2013 & XNYM - Crude oil & 23\% & 31\%\\
-OI & 2008/2013 & XNYM - Gasoline & 33\% & 27\%\\
-OI & 2008/2013 & XNYM - Heating oil & 27\% & 34\%\\
-OI & 2008/2013 & IFUS - Orange juice & 32\% & 43\%\\
-OI & 2008/2013 & IFUS - Sugar & 36\% & 31\%\\
-OI & 2008/2013 & XCME - Lumber & 35\% & 38\%\\
-TS & 2008/2013 & XCBT - Soy-meal & 69\% & 1\%\\
-TS & 2008/2013 & XCBT - Soybeans & 59\% & 0\%\\
-TS & 2008/2013 & XNYM - Crude oil & 25\% & 30\%\\
-TS & 2008/2013 & XNYM - Gasoline & 61\% & 6\%\\
-TS & 2008/2013 & XNYM - Heating oil & 33\% & 6\%\\
-TS & 2008/2013 & XCEC - Silver & 64\% & 0\%\\
-TS & 2008/2013 & XNYM - Palladium & 38\% & 0\%\\
-TS & 2008/2013 & XNYM - Platinum & 47\% & 1\%\\
-CHP & 2014/2017 & XCEC - Copper & 0\% & 79\%\\
-CHP & 2014/2017 & XNYM - Gasoline & 13\% & 0\%\\
-CHP & 2014/2017 & XCEC - Gold & 78\% & 0\%\\
-CHP & 2014/2017 & XCEC - Silver & 69\% & 0\%\\
-CHP & 2014/2017 & XNYM - Palladium & 100\% & 0\%\\
-CHP & 2014/2017 & XNYM - Platinum & 100\% & 0\%\\
-CHP & 2014/2017 & IFUS - Orange juice & 62\% & 2\%\\
-CHP & 2014/2017 & XCME - Lumber & 38\% & 53\%\\
-Market & 2014/2017 & XCBT - Soy-meal & 100\% & 0\%\\
-Market & 2014/2017 & XNYM - Crude oil & 100\% & 0\%\\
-Market & 2014/2017 & XNYM - Gasoline & 100\% & 0\%\\
-Market & 2014/2017 & XNYM - Heating oil & 100\% & 0\%\\
-Market & 2014/2017 & XNYM - Natural gas & 100\% & 0\%\\
-Market & 2014/2017 & XNYM - Palladium & 100\% & 0\%\\
-Market & 2014/2017 & IFUS - Coffee & 100\% & 0\%\\
-Market & 2014/2017 & IFUS - Sugar & 100\% & 0\%\\
-OI & 2014/2017 & XCBT - Oats & 32\% & 45\%\\
-OI & 2014/2017 & XCBT - Soy-meal & 39\% & 27\%\\
-OI & 2014/2017 & XCEC - Copper & 48\% & 15\%\\
-OI & 2014/2017 & XCEC - Gold & 39\% & 23\%\\
-OI & 2014/2017 & XCEC - Silver & 44\% & 28\%\\
-OI & 2014/2017 & IFUS - Cocoa & 33\% & 34\%\\
-OI & 2014/2017 & IFUS - Cotton & 42\% & 31\%\\
-OI & 2014/2017 & XCME - Lumber & 50\% & 30\%\\
-TS & 2014/2017 & XCBT - Soy-meal & 68\% & 10\%\\
-TS & 2014/2017 & XCBT - Soybeans & 56\% & 10\%\\
-TS & 2014/2017 & XCME - Feeder cattle & 75\% & 10\%\\
-TS & 2014/2017 & XCME - Live cattle & 65\% & 24\%\\
-TS & 2014/2017 & IFUS - Cocoa & 54\% & 1\%\\
-TS & 2014/2017 & IFUS - Cotton & 40\% & 2\%\\
-TS & 2014/2017 & IFUS - Orange juice & 41\% & 23\%\\
-TS & 2014/2017 & XCME - Lumber & 41\% & 39\%\\*
-\end{longtabu}\endgroup{}
-
-\newpage
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:correlations}\label{table5} This table displays the average pairwise nearby futures returns correlations for various sets of commodities including the multiple sets of risk factor commodity picks, the whole cross-section of US traded commodities considered in the study, the latter with metals omitted, and the cross-section of US traded metals.
-For each period and commodity set the correlations are calculated independently over the whole period as well as over \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes.
-See section \ref{methods} for more details.}\\
-\toprule
-Asset pool & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-CHP factor picks & High & 0.09 & 0.24 & 0.32 & 0.22\\
-CHP factor picks & Low & 0.10 & 0.28 & 0.37 & 0.19\\
-CHP factor picks & None & 0.10 & 0.27 & 0.34 & 0.21\\
-Market factor picks & High & 0.23 & 0.24 & 0.40 & 0.22\\
-Market factor picks & Low & 0.20 & 0.28 & 0.42 & 0.19\\
-Market factor picks & None & 0.21 & 0.26 & 0.41 & 0.21\\
-OI factor picks & High & 0.03 & 0.04 & 0.28 & 0.15\\
-OI factor picks & Low & 0.03 & 0.09 & 0.22 & 0.07\\
-OI factor picks & None & 0.03 & 0.07 & 0.25 & 0.11\\
-TS factor picks & High & 0.16 & 0.15 & 0.41 & 0.11\\
-TS factor picks & Low & 0.11 & 0.17 & 0.48 & 0.09\\
-TS factor picks & None & 0.13 & 0.16 & 0.44 & 0.10\\
-US - Commodity & High & 0.08 & 0.11 & 0.25 & 0.13\\
-US - Commodity & Low & 0.07 & 0.15 & 0.22 & 0.09\\
-US - Commodity & None & 0.08 & 0.13 & 0.24 & 0.11\\
-US - Commodity - No metals & High & 0.09 & 0.10 & 0.26 & 0.12\\
-US - Commodity - No metals & Low & 0.08 & 0.13 & 0.17 & 0.10\\
-US - Commodity - No metals & None & 0.09 & 0.12 & 0.22 & 0.11\\
-US - Metals & High & 0.23 & 0.55 & 0.52 & 0.44\\
-US - Metals & Low & 0.19 & 0.52 & 0.61 & 0.42\\
-US - Metals & None & 0.21 & 0.53 & 0.55 & 0.43\\
-\bottomrule
-\end{longtabu}\endgroup{}
-
-\newpage
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:`factor pick regressions - picks:picks`}\label{table6} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby futures returns on risk factors commodity picks while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in table \ref{table4}.
-For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
-See section \ref{methods} for more details.}\\
-\toprule
-Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-\endfirsthead
-\caption[]{continued}\\
-\toprule
-Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-\endhead
-\
-\endfoot
-\bottomrule
-\endlastfoot
-TS factor picks & \textasciitilde{} CHP factor & High & 1.45\% & 20.37\% & 16.95\% & 8.81\%\\
-TS factor picks & \textasciitilde{} CHP factor & Low & 7.6\% & 21.82\% & 10.29\% & 4.84\%\\
-TS factor picks & \textasciitilde{} CHP factor & None & 3.42\% & 21.2\% & 14.09\% & 5.06\%\\
-TS factor picks & \textasciitilde{} Market factor & High & 28.64\% & 27.15\% & 48.8\% & 21.54\%\\
-TS factor picks & \textasciitilde{} Market factor & Low & 25.53\% & 28.87\% & 54.4\% & 21.22\%\\
-TS factor picks & \textasciitilde{} Market factor & None & 27.23\% & 28.26\% & 50.95\% & 21.63\%\\
-TS factor picks & \textasciitilde{} OI factor & High & 0.07\% & 6.42\% & 4.08\% & 2.13\%\\
-TS factor picks & \textasciitilde{} OI factor & Low & 2.48\% & 0.81\% & 2.68\% & 0.61\%\\
-TS factor picks & \textasciitilde{} OI factor & None & 0.68\% & 2.26\% & 1.81\% & 0.56\%\\
-TS factor picks & \textasciitilde{} TS factor & High & 2.04\% & 7.65\% & 5.2\% & 2.98\%\\
-TS factor picks & \textasciitilde{} TS factor & Low & 2.22\% & 6.03\% & 2\% & 1.85\%\\
-TS factor picks & \textasciitilde{} TS factor & None & 0.53\% & 6.91\% & 4.16\% & 2.02\%\\
-OI factor picks & \textasciitilde{} CHP factor & High & 3.02\% & 5.9\% & 4.56\% & 10.95\%\\
-OI factor picks & \textasciitilde{} CHP factor & Low & 1.32\% & 9.37\% & 7.5\% & 5.5\%\\
-OI factor picks & \textasciitilde{} CHP factor & None & 1.96\% & 6.96\% & 3.95\% & 6.36\%\\
-OI factor picks & \textasciitilde{} Market factor & High & 14.4\% & 15.55\% & 39.51\% & 24.98\%\\
-OI factor picks & \textasciitilde{} Market factor & Low & 14.99\% & 20.4\% & 32.69\% & 17.31\%\\
-OI factor picks & \textasciitilde{} Market factor & None & 14.86\% & 18\% & 36.91\% & 21.08\%\\
-OI factor picks & \textasciitilde{} OI factor & High & 1.67\% & 1.82\% & 0.87\% & 0.64\%\\
-OI factor picks & \textasciitilde{} OI factor & Low & 0.67\% & -0.38\% & 0.95\% & 3.52\%\\
-OI factor picks & \textasciitilde{} OI factor & None & 0.29\% & 0.77\% & 0.09\% & 0.74\%\\
-OI factor picks & \textasciitilde{} TS factor & High & 3.24\% & 7.15\% & 13.59\% & 3.69\%\\
-OI factor picks & \textasciitilde{} TS factor & Low & 2.92\% & 2.7\% & 4.11\% & 3\%\\
-OI factor picks & \textasciitilde{} TS factor & None & 3.07\% & 5.36\% & 9.97\% & 3.08\%\\
-CHP factor picks & \textasciitilde{} CHP factor & High & 5.74\% & 15.05\% & 12.05\% & 12.46\%\\
-CHP factor picks & \textasciitilde{} CHP factor & Low & 7.05\% & 10.85\% & 8.7\% & 14.6\%\\
-CHP factor picks & \textasciitilde{} CHP factor & None & 5.83\% & 13.23\% & 10.46\% & 12.91\%\\
-CHP factor picks & \textasciitilde{} Market factor & High & 21.09\% & 35.23\% & 41.13\% & 32.66\%\\
-CHP factor picks & \textasciitilde{} Market factor & Low & 21.6\% & 38.7\% & 46.97\% & 29.72\%\\
-CHP factor picks & \textasciitilde{} Market factor & None & 21.27\% & 37.36\% & 43.49\% & 31.36\%\\
-CHP factor picks & \textasciitilde{} OI factor & High & 1.69\% & 3.9\% & 4.04\% & 0.74\%\\
-CHP factor picks & \textasciitilde{} OI factor & Low & 3.51\% & 1.61\% & 1.03\% & 2.96\%\\
-CHP factor picks & \textasciitilde{} OI factor & None & 1.57\% & 1.64\% & 2.07\% & 0.23\%\\
-CHP factor picks & \textasciitilde{} TS factor & High & 4.77\% & 7.1\% & 1.98\% & 4.78\%\\
-CHP factor picks & \textasciitilde{} TS factor & Low & 5.36\% & 5.57\% & 0.95\% & -0.21\%\\
-CHP factor picks & \textasciitilde{} TS factor & None & 4.54\% & 5.1\% & 1.84\% & 1.66\%\\
-Market factor picks & \textasciitilde{} CHP factor & High & 7.79\% & 8.62\% & 7.1\% & 7.84\%\\
-Market factor picks & \textasciitilde{} CHP factor & Low & 4.6\% & 7.78\% & 7.63\% & 7.73\%\\
-Market factor picks & \textasciitilde{} CHP factor & None & 6.06\% & 8.31\% & 6.22\% & 7.07\%\\
-Market factor picks & \textasciitilde{} Market factor & High & 32.85\% & 34.83\% & 48.14\% & 33.71\%\\
-Market factor picks & \textasciitilde{} Market factor & Low & 30.4\% & 37.35\% & 49.31\% & 29.36\%\\
-Market factor picks & \textasciitilde{} Market factor & None & 31.43\% & 36.1\% & 48.63\% & 32.31\%\\
-Market factor picks & \textasciitilde{} OI factor & High & 3.74\% & 0.77\% & 2.62\% & 0.52\%\\
-Market factor picks & \textasciitilde{} OI factor & Low & 0.41\% & -0.45\% & 1.22\% & -0.05\%\\
-Market factor picks & \textasciitilde{} OI factor & None & 1.33\% & 0.29\% & 0.78\% & 0.53\%\\
-Market factor picks & \textasciitilde{} TS factor & High & 6.64\% & 5.3\% & 2.45\% & 7.59\%\\
-Market factor picks & \textasciitilde{} TS factor & Low & 8.53\% & 4.21\% & 11.16\% & 4.7\%\\
-Market factor picks & \textasciitilde{} TS factor & None & 7.65\% & 5.2\% & 3.25\% & 6.24\%\\*
-\end{longtabu}\endgroup{}
-
-\newpage
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:`factor pick regressions - picks: US commos`}\label{table7} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby futures returns on the commodities forming the entire cross-section of US traded commodities considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in table \ref{table4}.
-For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
-See section \ref{methods} for more details.}\\
-\toprule
-Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-\endfirsthead
-\caption[]{continued}\\
-\toprule
-Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-\endhead
-\
-\endfoot
-\bottomrule
-\endlastfoot
-TS factor picks & \textasciitilde{} CHP factor & High & 1.45\% & 20.37\% & 16.95\% & 8.81\%\\
-TS factor picks & \textasciitilde{} CHP factor & Low & 7.6\% & 21.82\% & 10.29\% & 4.84\%\\
-TS factor picks & \textasciitilde{} CHP factor & None & 3.42\% & 21.2\% & 14.09\% & 5.06\%\\
-TS factor picks & \textasciitilde{} Market factor & High & 28.64\% & 27.15\% & 48.8\% & 21.54\%\\
-TS factor picks & \textasciitilde{} Market factor & Low & 25.53\% & 28.87\% & 54.4\% & 21.22\%\\
-TS factor picks & \textasciitilde{} Market factor & None & 27.23\% & 28.26\% & 50.95\% & 21.63\%\\
-TS factor picks & \textasciitilde{} OI factor & High & 0.07\% & 6.42\% & 4.08\% & 2.13\%\\
-TS factor picks & \textasciitilde{} OI factor & Low & 2.48\% & 0.81\% & 2.68\% & 0.61\%\\
-TS factor picks & \textasciitilde{} OI factor & None & 0.68\% & 2.26\% & 1.81\% & 0.56\%\\
-TS factor picks & \textasciitilde{} TS factor & High & 2.04\% & 7.65\% & 5.2\% & 2.98\%\\
-TS factor picks & \textasciitilde{} TS factor & Low & 2.22\% & 6.03\% & 2\% & 1.85\%\\
-TS factor picks & \textasciitilde{} TS factor & None & 0.53\% & 6.91\% & 4.16\% & 2.02\%\\
-OI factor picks & \textasciitilde{} CHP factor & High & 3.02\% & 5.9\% & 4.56\% & 10.95\%\\
-OI factor picks & \textasciitilde{} CHP factor & Low & 1.32\% & 9.37\% & 7.5\% & 5.5\%\\
-OI factor picks & \textasciitilde{} CHP factor & None & 1.96\% & 6.96\% & 3.95\% & 6.36\%\\
-OI factor picks & \textasciitilde{} Market factor & High & 14.4\% & 15.55\% & 39.51\% & 24.98\%\\
-OI factor picks & \textasciitilde{} Market factor & Low & 14.99\% & 20.4\% & 32.69\% & 17.31\%\\
-OI factor picks & \textasciitilde{} Market factor & None & 14.86\% & 18\% & 36.91\% & 21.08\%\\
-OI factor picks & \textasciitilde{} OI factor & High & 1.67\% & 1.82\% & 0.87\% & 0.64\%\\
-OI factor picks & \textasciitilde{} OI factor & Low & 0.67\% & -0.38\% & 0.95\% & 3.52\%\\
-OI factor picks & \textasciitilde{} OI factor & None & 0.29\% & 0.77\% & 0.09\% & 0.74\%\\
-OI factor picks & \textasciitilde{} TS factor & High & 3.24\% & 7.15\% & 13.59\% & 3.69\%\\
-OI factor picks & \textasciitilde{} TS factor & Low & 2.92\% & 2.7\% & 4.11\% & 3\%\\
-OI factor picks & \textasciitilde{} TS factor & None & 3.07\% & 5.36\% & 9.97\% & 3.08\%\\
-CHP factor picks & \textasciitilde{} CHP factor & High & 5.74\% & 15.05\% & 12.05\% & 12.46\%\\
-CHP factor picks & \textasciitilde{} CHP factor & Low & 7.05\% & 10.85\% & 8.7\% & 14.6\%\\
-CHP factor picks & \textasciitilde{} CHP factor & None & 5.83\% & 13.23\% & 10.46\% & 12.91\%\\
-CHP factor picks & \textasciitilde{} Market factor & High & 21.09\% & 35.23\% & 41.13\% & 32.66\%\\
-CHP factor picks & \textasciitilde{} Market factor & Low & 21.6\% & 38.7\% & 46.97\% & 29.72\%\\
-CHP factor picks & \textasciitilde{} Market factor & None & 21.27\% & 37.36\% & 43.49\% & 31.36\%\\
-CHP factor picks & \textasciitilde{} OI factor & High & 1.69\% & 3.9\% & 4.04\% & 0.74\%\\
-CHP factor picks & \textasciitilde{} OI factor & Low & 3.51\% & 1.61\% & 1.03\% & 2.96\%\\
-CHP factor picks & \textasciitilde{} OI factor & None & 1.57\% & 1.64\% & 2.07\% & 0.23\%\\
-CHP factor picks & \textasciitilde{} TS factor & High & 4.77\% & 7.1\% & 1.98\% & 4.78\%\\
-CHP factor picks & \textasciitilde{} TS factor & Low & 5.36\% & 5.57\% & 0.95\% & -0.21\%\\
-CHP factor picks & \textasciitilde{} TS factor & None & 4.54\% & 5.1\% & 1.84\% & 1.66\%\\
-Market factor picks & \textasciitilde{} CHP factor & High & 7.79\% & 8.62\% & 7.1\% & 7.84\%\\
-Market factor picks & \textasciitilde{} CHP factor & Low & 4.6\% & 7.78\% & 7.63\% & 7.73\%\\
-Market factor picks & \textasciitilde{} CHP factor & None & 6.06\% & 8.31\% & 6.22\% & 7.07\%\\
-Market factor picks & \textasciitilde{} Market factor & High & 32.85\% & 34.83\% & 48.14\% & 33.71\%\\
-Market factor picks & \textasciitilde{} Market factor & Low & 30.4\% & 37.35\% & 49.31\% & 29.36\%\\
-Market factor picks & \textasciitilde{} Market factor & None & 31.43\% & 36.1\% & 48.63\% & 32.31\%\\
-Market factor picks & \textasciitilde{} OI factor & High & 3.74\% & 0.77\% & 2.62\% & 0.52\%\\
-Market factor picks & \textasciitilde{} OI factor & Low & 0.41\% & -0.45\% & 1.22\% & -0.05\%\\
-Market factor picks & \textasciitilde{} OI factor & None & 1.33\% & 0.29\% & 0.78\% & 0.53\%\\
-Market factor picks & \textasciitilde{} TS factor & High & 6.64\% & 5.3\% & 2.45\% & 7.59\%\\
-Market factor picks & \textasciitilde{} TS factor & Low & 8.53\% & 4.21\% & 11.16\% & 4.7\%\\
-Market factor picks & \textasciitilde{} TS factor & None & 7.65\% & 5.2\% & 3.25\% & 6.24\%\\*
-\end{longtabu}\endgroup{}
-
-\newpage
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:`factor pick regressions - picks: UK commos`}\label{table8} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby futures returns on the six LME traded metals considered in the study while the regressors are returns on mimicking portfolios for risk factors where the factor portfolios are constructed using the corresponding set of risk factor commodity picks shown in Table \ref{table4}.
-For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
-See section \ref{methods} for more details.}\\
-\toprule
-Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-\endfirsthead
-\caption[]{continued}\\
-\toprule
-Factor asset pool & Model & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-\endhead
-\
-\endfoot
-\bottomrule
-\endlastfoot
-TS factor picks & \textasciitilde{} CHP factor & High & -0.01\% & 2.1\% & 3.87\% & 1.05\%\\
-TS factor picks & \textasciitilde{} CHP factor & Low & -0.37\% & 17.79\% & 3.32\% & 0.8\%\\
-TS factor picks & \textasciitilde{} CHP factor & None & -0.05\% & 7.89\% & 0.65\% & -0.26\%\\
-TS factor picks & \textasciitilde{} Market factor & High & 0.65\% & 17.55\% & 30.72\% & 5.69\%\\
-TS factor picks & \textasciitilde{} Market factor & Low & 1.62\% & 22.57\% & 27.92\% & 0.68\%\\
-TS factor picks & \textasciitilde{} Market factor & None & 1.3\% & 20.58\% & 29.6\% & 3.01\%\\
-TS factor picks & \textasciitilde{} OI factor & High & -0.36\% & 4.97\% & 0.31\% & -0.65\%\\
-TS factor picks & \textasciitilde{} OI factor & Low & 0.06\% & 1.29\% & -0.33\% & -0.11\%\\
-TS factor picks & \textasciitilde{} OI factor & None & 0.04\% & 3.02\% & -0.02\% & -0.18\%\\
-TS factor picks & \textasciitilde{} TS factor & High & 0.45\% & 4.72\% & 0.22\% & -0.22\%\\
-TS factor picks & \textasciitilde{} TS factor & Low & 0.01\% & -0.67\% & 0.22\% & 1.72\%\\
-TS factor picks & \textasciitilde{} TS factor & None & -0.12\% & 2.11\% & 0.44\% & 1.33\%\\
-OI factor picks & \textasciitilde{} CHP factor & High & 1.63\% & 0.34\% & -0.37\% & 5.03\%\\
-OI factor picks & \textasciitilde{} CHP factor & Low & -0.04\% & 8.57\% & 3.01\% & 0.43\%\\
-OI factor picks & \textasciitilde{} CHP factor & None & 0.01\% & 3.54\% & 0.55\% & 0.72\%\\
-OI factor picks & \textasciitilde{} Market factor & High & -0.24\% & 4.93\% & 28.78\% & 12.91\%\\
-OI factor picks & \textasciitilde{} Market factor & Low & 3.59\% & 10.46\% & 16.76\% & 7.99\%\\
-OI factor picks & \textasciitilde{} Market factor & None & 1.17\% & 7.97\% & 24.03\% & 10.37\%\\
-OI factor picks & \textasciitilde{} OI factor & High & -0.18\% & -0.68\% & 0.43\% & 0.76\%\\
-OI factor picks & \textasciitilde{} OI factor & Low & 1.79\% & 0.78\% & -0.32\% & 3.01\%\\
-OI factor picks & \textasciitilde{} OI factor & None & 0.54\% & -0.33\% & 0.07\% & -0.12\%\\
-OI factor picks & \textasciitilde{} TS factor & High & -0.26\% & -0.34\% & 7.07\% & -0.26\%\\
-OI factor picks & \textasciitilde{} TS factor & Low & 0.3\% & 1.01\% & 0.58\% & -0.31\%\\
-OI factor picks & \textasciitilde{} TS factor & None & 0.17\% & 0.11\% & 4.57\% & -0.17\%\\
-CHP factor picks & \textasciitilde{} CHP factor & High & 0.48\% & -0.1\% & 2.96\% & 0.46\%\\
-CHP factor picks & \textasciitilde{} CHP factor & Low & 0.15\% & -0.55\% & 2.7\% & 0.77\%\\
-CHP factor picks & \textasciitilde{} CHP factor & None & 0.05\% & -0.43\% & 0.48\% & 0.05\%\\
-CHP factor picks & \textasciitilde{} Market factor & High & 4.22\% & 18.7\% & 26.41\% & 15.02\%\\
-CHP factor picks & \textasciitilde{} Market factor & Low & 4.4\% & 30.16\% & 27.34\% & 14.77\%\\
-CHP factor picks & \textasciitilde{} Market factor & None & 4.48\% & 25.09\% & 26.83\% & 14.99\%\\
-CHP factor picks & \textasciitilde{} OI factor & High & 0.28\% & 6.51\% & 0\% & -0.57\%\\
-CHP factor picks & \textasciitilde{} OI factor & Low & 0.41\% & 0.18\% & 0.39\% & 0.65\%\\
-CHP factor picks & \textasciitilde{} OI factor & None & 0.49\% & 3.89\% & 0.29\% & -0.1\%\\
-CHP factor picks & \textasciitilde{} TS factor & High & -0.36\% & 4.19\% & -0.19\% & 2.09\%\\
-CHP factor picks & \textasciitilde{} TS factor & Low & -0.26\% & -0.52\% & -0.17\% & 0.28\%\\
-CHP factor picks & \textasciitilde{} TS factor & None & -0.24\% & 2.07\% & 0.13\% & 1.33\%\\
-Market factor picks & \textasciitilde{} CHP factor & High & -0.22\% & 3.62\% & 0.64\% & 1.88\%\\
-Market factor picks & \textasciitilde{} CHP factor & Low & -0.33\% & 9.62\% & 1.72\% & 1.12\%\\
-Market factor picks & \textasciitilde{} CHP factor & None & -0.1\% & 6.32\% & -0.08\% & 1.61\%\\
-Market factor picks & \textasciitilde{} Market factor & High & -0.11\% & 8.95\% & 36.58\% & 11.77\%\\
-Market factor picks & \textasciitilde{} Market factor & Low & 2.08\% & 9.85\% & 29.63\% & 2.79\%\\
-Market factor picks & \textasciitilde{} Market factor & None & 0.88\% & 9.93\% & 33.73\% & 7.69\%\\
-Market factor picks & \textasciitilde{} OI factor & High & 0.24\% & -0.58\% & 0.84\% & -0.04\%\\
-Market factor picks & \textasciitilde{} OI factor & Low & 0.66\% & 0.56\% & -0.17\% & -0.42\%\\
-Market factor picks & \textasciitilde{} OI factor & None & -0.04\% & 0.12\% & 0.62\% & -0.24\%\\
-Market factor picks & \textasciitilde{} TS factor & High & -0.38\% & 1.37\% & 2.9\% & -0.37\%\\
-Market factor picks & \textasciitilde{} TS factor & Low & -0.43\% & 1.41\% & 0.32\% & 0.39\%\\
-Market factor picks & \textasciitilde{} TS factor & None & -0.23\% & 1.65\% & 2.15\% & 0.12\%\\*
-\end{longtabu}\endgroup{}
-
-\newpage
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{landscape}
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
-\caption{\label{tab:`factor pick regressions - picks: UK commos - legs`}\label{table9} This table shows the average time series adjusted $R^{2}$s for a set of commodity factor models.
-The dependent variables are individual nearby futures returns on the six LME traded metals considered in the study while the regressors are returns on the long and short legs of mimicking portfolios for risk factors considered independently, where the factor portfolios are constructed using the corresponding set of risk factor commodity picks.
-For each period and model, the corresponding individual commodity adjusted $R^{2}$s are averaged.
-For each period, the models are implemented over the whole period, as well as over \textbf{contango} (high) and \textbf{backwardation} (low) \textbf{CHP} regimes independently.
-See section \ref{methods} for more details.}\\
-\toprule
-Factor asset pool & Model & Leg & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-\endfirsthead
-\caption[]{continued}\\
-\toprule
-Factor asset pool & Model & Leg & CHP regime & 1997/2003 & 2004/2007 & 2008/2013 & 2014/2017\\
-\midrule
-\endhead
-\
-\endfoot
-\bottomrule
-\endlastfoot
-TS factor picks & \textasciitilde{} CHP factor & Long & High & 0.91\% & 11.5\% & 13.22\% & -0.15\%\\
-TS factor picks & \textasciitilde{} CHP factor & Long & Low & 1.51\% & 29.68\% & 34.77\% & 1.21\%\\
-TS factor picks & \textasciitilde{} CHP factor & Long & None & 1.39\% & 19.71\% & 20.35\% & 1.09\%\\
-TS factor picks & \textasciitilde{} CHP factor & Short & High & 0.01\% & 1.47\% & 28.59\% & 4.63\%\\
-TS factor picks & \textasciitilde{} CHP factor & Short & Low & -0.15\% & -0.48\% & 26.72\% & -0.11\%\\
-TS factor picks & \textasciitilde{} CHP factor & Short & None & 0.16\% & 0.9\% & 27.93\% & 1.23\%\\
-TS factor picks & \textasciitilde{} Market factor & Long & High & 0.65\% & 17.55\% & 30.72\% & 5.69\%\\
-TS factor picks & \textasciitilde{} Market factor & Long & Low & 1.62\% & 22.57\% & 27.92\% & 0.68\%\\
-TS factor picks & \textasciitilde{} Market factor & Long & None & 1.3\% & 20.58\% & 29.6\% & 3.01\%\\
-TS factor picks & \textasciitilde{} OI factor & Long & High & 0.36\% & 4.73\% & 23.81\% & 1.72\%\\
-TS factor picks & \textasciitilde{} OI factor & Long & Low & 1.54\% & 11.1\% & 30.88\% & -0.57\%\\
-TS factor picks & \textasciitilde{} OI factor & Long & None & 0.99\% & 8.22\% & 25.87\% & 0.26\%\\
-TS factor picks & \textasciitilde{} OI factor & Short & High & 0.56\% & 22.57\% & 20.33\% & 2.35\%\\
-TS factor picks & \textasciitilde{} OI factor & Short & Low & 2.01\% & 20.14\% & 28.09\% & 0.2\%\\
-TS factor picks & \textasciitilde{} OI factor & Short & None & 1.42\% & 21.62\% & 22.99\% & 1.8\%\\
-TS factor picks & \textasciitilde{} TS factor & Long & High & -0.14\% & 24.07\% & 19.08\% & 0.51\%\\
-TS factor picks & \textasciitilde{} TS factor & Long & Low & 1.18\% & 22.59\% & 23.52\% & -0.54\%\\
-TS factor picks & \textasciitilde{} TS factor & Long & None & 0.37\% & 23.8\% & 20.46\% & -0.36\%\\
-TS factor picks & \textasciitilde{} TS factor & Short & High & 1.14\% & 4.16\% & 25.71\% & 3.89\%\\
-TS factor picks & \textasciitilde{} TS factor & Short & Low & 0.6\% & 9.27\% & 34.98\% & 2.59\%\\
-TS factor picks & \textasciitilde{} TS factor & Short & None & 1.06\% & 7.24\% & 28.35\% & 4.01\%\\
-OI factor picks & \textasciitilde{} CHP factor & Long & High & 0.19\% & 8.36\% & 15.6\% & 1.65\%\\
-OI factor picks & \textasciitilde{} CHP factor & Long & Low & 3.42\% & 16.64\% & 8.36\% & 6.14\%\\
-OI factor picks & \textasciitilde{} CHP factor & Long & None & 0.03\% & 12.55\% & 13.29\% & 3.64\%\\
-OI factor picks & \textasciitilde{} CHP factor & Short & High & 0.9\% & 0.79\% & 23.17\% & 13.29\%\\
-OI factor picks & \textasciitilde{} CHP factor & Short & Low & 0.45\% & 0.65\% & 20.93\% & 3.06\%\\
-OI factor picks & \textasciitilde{} CHP factor & Short & None & 1.01\% & 1.03\% & 22.48\% & 8.42\%\\
-OI factor picks & \textasciitilde{} Market factor & Long & High & -0.24\% & 4.93\% & 28.78\% & 12.91\%\\
-OI factor picks & \textasciitilde{} Market factor & Long & Low & 3.59\% & 10.46\% & 16.76\% & 7.99\%\\
-OI factor picks & \textasciitilde{} Market factor & Long & None & 1.17\% & 7.97\% & 24.03\% & 10.37\%\\
-OI factor picks & \textasciitilde{} OI factor & Long & High & -0.39\% & 1.54\% & 17.05\% & 3.59\%\\
-OI factor picks & \textasciitilde{} OI factor & Long & Low & -0.18\% & 7.12\% & 16.74\% & 6.64\%\\
-OI factor picks & \textasciitilde{} OI factor & Long & None & -0.22\% & 3.7\% & 17.08\% & 5.56\%\\
-OI factor picks & \textasciitilde{} OI factor & Short & High & 0.01\% & 3.92\% & 24.04\% & 9.07\%\\
-OI factor picks & \textasciitilde{} OI factor & Short & Low & 3.83\% & 2.41\% & 15.01\% & -1.06\%\\
-OI factor picks & \textasciitilde{} OI factor & Short & None & 1.55\% & 3.14\% & 20.57\% & 2.71\%\\
-OI factor picks & \textasciitilde{} TS factor & Long & High & -0.24\% & 5.47\% & 22.98\% & 3.39\%\\
-OI factor picks & \textasciitilde{} TS factor & Long & Low & 2.1\% & 15.43\% & 16.87\% & 0.23\%\\
-OI factor picks & \textasciitilde{} TS factor & Long & None & 0.74\% & 10.28\% & 20.88\% & 1.57\%\\
-OI factor picks & \textasciitilde{} TS factor & Short & High & -0.35\% & 1.99\% & 10.81\% & 8.45\%\\
-OI factor picks & \textasciitilde{} TS factor & Short & Low & 0.56\% & 1.8\% & 8.96\% & 0.35\%\\
-OI factor picks & \textasciitilde{} TS factor & Short & None & 0.16\% & 2.25\% & 10.32\% & 4.29\%\\
-CHP factor picks & \textasciitilde{} CHP factor & Long & High & 0.9\% & 10.35\% & 12.52\% & 5.81\%\\
-CHP factor picks & \textasciitilde{} CHP factor & Long & Low & 3.58\% & 28.68\% & 29.36\% & 11.92\%\\
-CHP factor picks & \textasciitilde{} CHP factor & Long & None & 1.87\% & 18.04\% & 18.32\% & 8.25\%\\
-CHP factor picks & \textasciitilde{} CHP factor & Short & High & 4.73\% & 21.64\% & 25.57\% & 13.39\%\\
-CHP factor picks & \textasciitilde{} CHP factor & Short & Low & 0.15\% & 22.77\% & 21.53\% & 7.38\%\\
-CHP factor picks & \textasciitilde{} CHP factor & Short & None & 2.08\% & 22.85\% & 24.23\% & 10.59\%\\
-CHP factor picks & \textasciitilde{} Market factor & Long & High & 4.22\% & 18.7\% & 26.41\% & 15.02\%\\
-CHP factor picks & \textasciitilde{} Market factor & Long & Low & 4.4\% & 30.16\% & 27.34\% & 14.77\%\\
-CHP factor picks & \textasciitilde{} Market factor & Long & None & 4.48\% & 25.09\% & 26.83\% & 14.99\%\\
-CHP factor picks & \textasciitilde{} OI factor & Long & High & 0.6\% & 1.73\% & 19.04\% & 8.75\%\\
-CHP factor picks & \textasciitilde{} OI factor & Long & Low & 1.32\% & 21.86\% & 29.51\% & 16.19\%\\
-CHP factor picks & \textasciitilde{} OI factor & Long & None & 1.03\% & 9.08\% & 22.58\% & 11.61\%\\
-CHP factor picks & \textasciitilde{} OI factor & Short & High & 2.03\% & 21.75\% & 17.79\% & 8.86\%\\
-CHP factor picks & \textasciitilde{} OI factor & Short & Low & 3.48\% & 23.02\% & 30.31\% & 3.59\%\\
-CHP factor picks & \textasciitilde{} OI factor & Short & None & 2.83\% & 22.98\% & 21.6\% & 6.75\%\\
-CHP factor picks & \textasciitilde{} TS factor & Long & High & 1.55\% & 24.47\% & 16.98\% & 4.23\%\\
-CHP factor picks & \textasciitilde{} TS factor & Long & Low & 2.4\% & 29.72\% & 21.59\% & 4.46\%\\
-CHP factor picks & \textasciitilde{} TS factor & Long & None & 1.91\% & 27.37\% & 18.54\% & 5.2\%\\
-CHP factor picks & \textasciitilde{} TS factor & Short & High & 2.04\% & 2.25\% & 21.16\% & 11.49\%\\
-CHP factor picks & \textasciitilde{} TS factor & Short & Low & 0.13\% & 15.94\% & 28.57\% & 15.29\%\\
-CHP factor picks & \textasciitilde{} TS factor & Short & None & 1.15\% & 8.14\% & 23.54\% & 12.87\%\\
-Market factor picks & \textasciitilde{} CHP factor & Long & High & 0.14\% & 14.47\% & 24.85\% & 13.11\%\\
-Market factor picks & \textasciitilde{} CHP factor & Long & Low & 1.14\% & 19\% & 33.01\% & 7.1\%\\
-Market factor picks & \textasciitilde{} CHP factor & Long & None & 0.66\% & 17\% & 27.85\% & 10.89\%\\
-Market factor picks & \textasciitilde{} CHP factor & Short & High & -0.19\% & 1.81\% & 31.9\% & 5.71\%\\
-Market factor picks & \textasciitilde{} CHP factor & Short & Low & 1.53\% & 3.86\% & 35.32\% & -0.39\%\\
-Market factor picks & \textasciitilde{} CHP factor & Short & None & 0.66\% & 2.85\% & 32.76\% & 2.67\%\\
-Market factor picks & \textasciitilde{} Market factor & Long & High & -0.11\% & 8.95\% & 36.58\% & 11.77\%\\
-Market factor picks & \textasciitilde{} Market factor & Long & Low & 2.08\% & 9.85\% & 29.63\% & 2.79\%\\
-Market factor picks & \textasciitilde{} Market factor & Long & None & 0.88\% & 9.93\% & 33.73\% & 7.69\%\\
-Market factor picks & \textasciitilde{} OI factor & Long & High & -0.32\% & 2.73\% & 34.04\% & 7.23\%\\
-Market factor picks & \textasciitilde{} OI factor & Long & Low & 0.07\% & 5.36\% & 35.07\% & 1.56\%\\
-Market factor picks & \textasciitilde{} OI factor & Long & None & 0.07\% & 4.4\% & 34.38\% & 4.78\%\\
-Market factor picks & \textasciitilde{} OI factor & Short & High & -0.03\% & 6.86\% & 24.78\% & 9.62\%\\
-Market factor picks & \textasciitilde{} OI factor & Short & Low & 2.28\% & 9.51\% & 27.82\% & 1.38\%\\
-Market factor picks & \textasciitilde{} OI factor & Short & None & 0.43\% & 8.38\% & 25.68\% & 6.05\%\\
-Market factor picks & \textasciitilde{} TS factor & Long & High & -0.03\% & 11.75\% & 30.86\% & 8.57\%\\
-Market factor picks & \textasciitilde{} TS factor & Long & Low & 0.84\% & 8.74\% & 30.58\% & 4.49\%\\
-Market factor picks & \textasciitilde{} TS factor & Long & None & 0.48\% & 10.83\% & 30.76\% & 7.34\%\\
-Market factor picks & \textasciitilde{} TS factor & Short & High & -0.43\% & 2.19\% & 25.29\% & 6.6\%\\
-Market factor picks & \textasciitilde{} TS factor & Short & Low & 2.06\% & 2.77\% & 24.04\% & 0.2\%\\
-Market factor picks & \textasciitilde{} TS factor & Short & None & 0.53\% & 2.81\% & 24.88\% & 3.76\%\\*
-\end{longtabu}
-\end{landscape}\endgroup{}
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\hypertarget{assets}{%
-\subsection{Assets}\label{assets}}
-
-\begingroup\fontsize{10}{12}\selectfont
-
-\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright}X>{\raggedright}X>{\raggedright}X}
-\caption{\label{tab:`appendix - assets`}This table shows details on the individual commodities considered in this study including trading country, sector, subsector as well as trading exchange Market Identifier Codes (MIC, ISO 10383).}\\
-\toprule
-Country & Sector & Subsector & Exchange & Name\\
-\midrule
-US & Agriculturals & Grains & XCBT & Corn\\
-US & Agriculturals & Grains & XCBT & Oats\\
-US & Agriculturals & Grains & XCBT & Soy-meal\\
-US & Agriculturals & Grains & XCBT & Soy-oil\\
-US & Agriculturals & Grains & XCBT & Soybeans\\
-US & Agriculturals & Grains & XCBT & Wheat-SRW\\
-US & Agriculturals & Livestock & XCME & Feeder cattle\\
-US & Agriculturals & Livestock & XCME & Lean hogs\\
-US & Agriculturals & Livestock & XCME & Live cattle\\
-US & Agriculturals & Softs & IFUS & Cocoa\\
-US & Agriculturals & Softs & IFUS & Coffee\\
-US & Agriculturals & Softs & IFUS & Cotton\\
-US & Agriculturals & Softs & IFUS & Orange juice\\
-US & Agriculturals & Softs & IFUS & Sugar\\
-US & Agriculturals & Softs & XCME & Lumber\\
-US & Energy & Petroleum & XNYM & Crude oil\\
-US & Energy & Petroleum & XNYM & Gasoline\\
-US & Energy & Petroleum & XNYM & Heating oil\\
-US & Energy & Petroleum & XNYM & Natural gas\\
-US & Metals & Industrial & XCEC & Copper\\
-US & Metals & Precious & XCEC & Gold\\
-US & Metals & Precious & XCEC & Silver\\
-US & Metals & Precious & XNYM & Palladium\\
-US & Metals & Precious & XNYM & Platinum\\
-UK & Metals & Industrial & XLME & Aluminium\\
-UK & Metals & Industrial & XLME & Copper\\
-UK & Metals & Industrial & XLME & Lead\\
-UK & Metals & Industrial & XLME & Nickel\\
-UK & Metals & Industrial & XLME & Tin\\
-UK & Metals & Industrial & XLME & Zinc\\
-\bottomrule
-\end{longtabu}\endgroup{}
-
-\newpage
-
-\hypertarget{market-factor-lemma}{%
-\subsection{Market factor lemma}\label{market-factor-lemma}}
-
-\[\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}\]
-\(\overline{R_{mkt, p}^{2}}\equiv\) period \(p\) average \(R^{2}\) for
-market risk factor returns.\\
-\(R_{j, mkt, p}^{2}\equiv\) period \(p\) \(R^{2}\) for the regression
-where the dependent variable is the vector of returns on commodity \(j\)
-nearby contract and the regressor is the vector of returns on the market
-portfolio; \(j \in Y_{p}^{mkt}\).\\
-\(Y_{p}^{mkt}\equiv\) commodity set considered for the formation of the
-mimicking portfolio for market risk over period \(p\).\\
-\(n\equiv\) number of commodities in \(Y_{p}^{mkt}\).
-
-\textbf{Proof}
-
-Week \(t\) market factor return:
-\[r_{mkt, t} = \sum_{j} w_{j, p} \cdot r_{j, t}\] \(w_{j, p}\equiv\)
-period \(p\) weight for commodity \(j\) in the mimicking portfolio for
-market risk in returns.\\
-\(r_{j, t}\equiv\) week \(t\) return for commodity \(j\).
-
-Assumptions:
-
-\begin{math}
-  \begin{aligned}
-   w_{j, p} &= w_{k, p} = \frac{1}{n} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt} \\
-   \sigma_{r_{j}, p} &= \sigma_{r_{k}, p} \: \forall \: \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt} \\
-   cov \left ( r_{j}, r_{k} \right )_{p} &= 0 \: \forall \left \{ j, \: k \right \}; \: j, \: k \: \in Y_{p}^{mkt}
-  \end{aligned}
-\end{math}
-
-\newpage
-
-\[
-\begin{array}{l c l}
-  \sigma_{r_{j, p}}^{2} & = & \beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2} + \sigma_{\epsilon}^{2} \\
-  \beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2} & = & \sigma_{r_{j, p}}^{2} - \sigma_{\epsilon}^{2} \\
-  \frac{\beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2}}{\sigma_{r_{j, p}}^{2}} & = & \frac{\sigma_{r_{j, p}}^{2} - \sigma_{\epsilon}^{2}}{\sigma_{r_{j, p}}^{2}} \\
-    \frac{\beta_{r_{j}, r_{mkt}, p}^{2} \cdot \sigma_{r_{mkt, p}}^{2}}{\sigma_{r_{j, p}}^{2}}  & = & R_{r_{j}, r_{mkt}, p}^{2} \\ \\
-  \sigma_{r_{mkt, p}}^{2} & = & \sum_{j} w_{j, p}^{2} \cdot \sigma_{j, p}^{2} + 2 \cdot \sum_{j} \sum_{k \neq j} w_{j, p} \cdot w_{k, p} \cdot cov \left ( r_{j, p}, r_{k, p} \right ) \\
-                          & = & \sum_{j} \left ( \frac{1}{n} \right )^{2} \cdot \sigma_{j, p}^{2} \\
-                          & = & \frac{\sum_{j} \sigma_{j, p}^{2}}{n^{2}} \\ \\
-  cov \left ( r_{j}, r_{mkt} \right )_{p} & = & cov \left ( r_{j}, \frac{1}{n} \sum_{k} r_{k} \right )_{p} \\
-                                          & = & \frac{1}{n} \sum_{k} cov \left ( r_{j}, r_{k} \right )_{p} \\
-                                          & = & \frac{1}{n} cov \left ( r_{j}, r_{j} \right )_{p} \\
-                                          & = & \frac{\sigma_{r_{j}, p}^{2}}{n} \\ \\
-  \beta_{j, mkt, p}^{2} & = & \left [ \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}}{\sigma_{r_{mkt, p}}^{2}} \right ]^{2} \\
-                        & = & \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}^{2}}{\sigma_{r_{mkt, p}}^{4}} \\ \\
-  \beta_{j, mkt, p}^{2} \cdot  \sigma_{r_{mkt, p}}^{2}  & = & \frac{cov \left ( r_{j}, r_{mkt} \right )_{p}^{2}}{\sigma_{r_{mkt, p}}^{2}} \\
-                                                        & = & \left ( \frac{\sigma_{r_{j}, p}^{2}}{n} \right )^{2} \cdot \frac{1}{\sigma_{r_{mkt, p}}^{2}} \\
-                                                        & = & \frac{\sigma_{r_{j}, p}^{4}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\ \\
-\end{array}
-\]
-
-\newpage
-
-\[
-\begin{array}{l c l}
-  R_{r_{j}, r_{mkt}, p}^{2} & = & \frac{\sigma_{r_{j}, p}^{4}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \cdot \frac{1}{\sigma_{r_{j, p}}^{2}} \\
-                            & = & \frac{\sigma_{r_{j}, p}^{2}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\ \\  
-                            & \therefore  & \\ \\
-  \overline{R_{r_{mkt}, p}^{2}} & = & \frac{1}{n} \sum_{j} \frac{\sigma_{r_{j}, p}^{2}}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \\
-                                & = & \frac{1}{n} \cdot \frac{1}{n^{2} \cdot \sigma_{r_{mkt, p}}^{2}} \cdot \sum_{j} \sigma_{r_{j}, p}^{2} \\
-                                & = & \frac{1}{n} \cdot \frac{\sum_{j} \sigma_{r_{j}, p}^{2}}{n^{2} \cdot \frac{1}{n^{2}} \cdot \sum_{j} \sigma_{r_{j}, p}^{2}} \\
-                                & = & \frac{1}{n} \\
-\end{array}
-\]
-
-\newpage
-
 \bibliography{BibTeX.bib}

### 2024-06-11 others/revision-jfm.qmd

---
title: "journal of futures markets - revision"
execute:
  echo: false
  message: false
  warning: false
format:
  html:
    page-layout: full
    toc: true
    toc-title: Contents
    toc-depth: 5
    theme: 
      - Minty
      - style.css
editor: visual
bibliography: references.bib
---

<style>
<!-- .main-container { -->
<!--   max-width: 95vw; /* Adjust this value as needed */ -->
<!--   margin: 0 auto; /* Center align the content */ -->
<!--   padding: 0; -->
<!-- } -->

#quarto-content {
  max-width: 95vw;
  margin: 0 auto;
  padding: 0;
}

.no-wrap-table th, .no-wrap-table td {
  white-space: nowrap;
}
</style>

```{r globals, echo=FALSE}
url_css <- "https://www.dropbox.com/scl/fi/hca7tog3830ir7ro9fszt/styles.css?rlkey=pma97454kb75qzuj9znv86zrf&dl=1"
url_references <- "https://www.dropbox.com/scl/fi/n7t8g3hn32d8e5gf2rcti/references.bib?rlkey=xy251n44q3y0t3omxpqk0dvyf&dl=1"
file_css <- "style.css"
file_references <- "references.bib"
urls <- c(url_css, url_references)
files <- c(file_css, file_references)

purrr::walk2(urls, files, ~download.file(.x, .y))

####
library(magrittr)

####
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

####
tables_collapse_rows_align <- "top"
tables_cut <- TRUE
tables_hline <- "major"

output_type <- "html"
```

# Correlation analysis

```{r correlations-load, echo=FALSE}
correlations <- readr::read_rds(paste0(here::here(), "/explore/tables/revision-jfm/correlations.rds"))
```

## Pairwise relative change correlations by period

```{r correlations-relative-periods, echo=FALSE}
filtered_correlations <- dplyr::filter(correlations, timespan == "period", type == "return") %>%
  dplyr::select(-c(timespan, year, type)) %>% dplyr::relocate(period, .before = regime) %>%
  dplyr::relocate(field, .before = frequency)

align <- "lllllllrllr"

knitr::kable(filtered_correlations, format = "html", table.attr = 'class="no-wrap-table"') %>% 
  kableExtra::kable_styling(full_width = TRUE) %>%
  kableExtra::scroll_box(width = "100%", height = "800px")
```

### 2024-06-24 others/journal submissions/journal of futures markets/initial/cover letter - draft.qmd
directory structure management

---
title: "Financialisation of Commodity Markets"
subtitle: "Co-movement Behind-the-scenes"
format: pdf
bibliography: literature_files/references.bib
---

```{r globals, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# folder <- "literature_files"; dir.create(folder); path <- paste(folder, "references.bib", sep = "/")
# download.file("https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", path)

```

Dear Editor-in-Chief and the Journal of Futures Markets Editorial Board,  
  \
I am pleased to submit our manuscript titled "Financialisation of Commodity Markets: Co-movement Behind-the-scenes" for consideration for publication in the Journal of Futures Markets.
  \
  \
Our paper advances the ongoing debates in the Journal of Futures Markets by providing an alternative examination of the financialisation of commodity markets which serves as a unique contribution to the literature. Specifically, our research extends the dialogue on the impact of the phenomenon on various aspects of the commodity complex including on co-movement and market integration, both within the commodity space [@liu_analyzing_2021; @sehgal_who_2021; @yang_volatility_2021; @gong_time_2022] and with legacy asset classes [@conghui_liquidity_2020; @isleimeyyeh_role_2020; @daskalaki_new_2021; @han_trend_2022; @saishree_exploring_2022]; on market fundamentals [@isleimeyyeh_role_2020; @marechal_tale_2020; @yin_intermediary_2021], particularly risk transfer [@ahmadi_theory_2020] and price formation [@adammer_price_2018; @merkoulova_predictive_2020; @kupabado_financialisation_2021; @sehgal_who_2021]; as well as on investment in the sector [@daskalaki_new_2021; @han_trend_2022]. The paper also addresses the consequences of financialisation from a regulatory perspective, effectively contributing to the debate on futures markets oversight: @janardanan_commodity_2019, @fan_untold_2020, @hu_impact_2020, @mixon_us_2022, @szabo_margin_2022. Additionally, our study further extends the collection of recent seminal works that study financialisation using asset pricing techniques [@fan_untold_2020; @marechal_tale_2020; @yin_intermediary_2020; @han_trend_2022]. More generally, the paper provides an empirical complement to the growing body of research on co-movement and market integration within the commodity complex [@xiao_estimating_2020; @yang_return_2020; @luo_how_2021; @prokopczuk_dynamics_2021; @deBoer_intraday_2022; @dhaene_volatility_2022; @zhang_impact_2022] and beyond [@alquist_effect_2020; @kang_commodity_2020; @wong_impact_2020; @dark_lead_2021; @li_forecasting_2021; @liu_does_2022; @ming_contagion_2022; @zhang_do_2022; @zhang_influence_2023]; on commodity market fundamentals [@brooks_samuelson_2020; @llorente_trading_2020; @marechal_do_2021; @li_hedging_2022] including risk transfer [@fan_speculative_2020; @oglend_futures_2020; @huang_good_2023] and price formation [@bohmann_price_2019; @janardanan_commodity_2019; @arroyo_old_2020; @bohl_return_2020; @frino_sensitivity_2020; @siklos_metal_2020; @andersen_efficiency_2021; @figuerola_oil_2021; @geyer_determinants_2021; @gilbert_regional_2021; @yang_price_2021; @fuertes_risk_2022; @li_robust_2022; @bandyopadhyay_impact_2023; @chen_temperature_2023; @fan_wisdom_2023; @filippidis_evaluating_2023]; and on asset pricing in the context of commodity markets [@kang_commodity_2020; @yuan_pobability_2023].  
  \
Drawing upon the issues and methods discussed in these studies, our research provides a broader perspective on the phenomenon of financialisation by examining its effects on a large cross-section of liquid commodities, rather than focusing on individual markets. This approach allows us to capture the global nature of financialisation and its influence on market fundamentals, an area of research that we believed has not yet been fully explored. We argue that the global nature of the phenomenon makes cross-sectional co-movement a cornerstone issue and we provide new insights into this issue through our novel approach, using a bespoke futures-based asset pricing framework. We view this contribution as important because it helps to deepen our understanding of the consequences of financialisation for commodity markets and provides a more nuanced perspective on the debates about the phenomenon. We further believe this understanding is beneficial for regulator, policymakers and investors in shaping risk management practices and investment strategies in the age of heightened market participation.  
  \
If published, we believe that this paper will be cited for its innovative approach to studying the phenomenon of commodity markets financialisation. The paper challenges the conventional focus on individual markets and instead emphasises the importance of considering the global and cross-sectional impact of financialisation. Our results provide compelling evidence that the phenomenon had ontological consequences for the commodity complex, offering a key reference for future studies on financialisation and commodity markets. By further emphasising the regulatory implications of financialisation, our study also contributes to the discourse on futures markets oversight, offering an additional strong reference point.
  \
  \
The manuscript is original, has not been submitted elsewhere, and all the authors have approved it for submission to your journal. There are no conflicts of interest to declare.  
  \
We look forward to the possibility of our paper being published in the Journal of Futures Markets and contributing to the ongoing debates in this field.  
  \
Thank you for considering our submission.
  \
  \
Best regards,  
  \
Devraj Basu, Olivier Bauthéac

\pagebreak

## References

### 2024-06-25 explore/scripts/revision-jfm-tables.r
Run regressions with equally weighted factors.
US commodities ~ factors from US commodities.
Closes #43

@@ -1,0 +1,34 @@
+library(magrittr)
+
+significance <- function(p.value, estimate){
+  if(p.value <= 0.01) paste0("***", estimate)
+  else if (p.value > 0.01 && p.value <= 0.05) paste0("**", estimate)
+  else if (p.value > 0.05 && p.value <= 0.10) paste0("*", estimate)
+  else estimate
+}
+
+percentize <- function(value) paste0(round(value, digits = 4L) * 100, "%")
+
+factors <- c("market", "CHP", "`OI nearby`", "`OI aggregate`", "`term structure`")
+sector_levels <- c("all", "agriculturals", "energy", "metals")
+subsector_levels <- c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")
+
+# `US commodities ~ factors from US commodities ####
+path <- paste0(here::here(), "/explore/results/revision-jfm/regressions-factors.rds")
+raw <- readRDS(path)
+
+formatted <- dplyr::filter(raw, regressors %in% factors) %>%
+  dplyr::group_by(regressors, leg, period, regime) %>%
+  dplyr::summarise(`average rsquared` = mean(rsquared, na.rm = TRUE)) %>%
+  dplyr::ungroup() %>%
+  dplyr::mutate(
+    period = factor(period, levels = c("past", "financialization", "crisis", "present")),
+    regressors = factor(regressors, levels = c("market", factors[ factors != "market"])),
+    `average rsquared` = percentize(`average rsquared`)
+  ) %>% dplyr::arrange(regressors, leg, period, regime) %>%
+  tidyr::pivot_wider(names_from = "period", values_from = "average rsquared") %>%
+  dplyr::rename(factor = regressors) %>% dplyr::filter(factor != "`OI aggregate`")
+
+path <- paste0(here::here(), "/explore/tables/revision-jfm/regressions-factors.csv")
+readr::write_csv(formatted, path)
+

### 2024-06-25 others/journal submissions/journal of futures markets/initial/financialisation of commodity markets - blind.tex

--- 2022-07-04 docs/paper.tex
@@
 
-  \journal{no journal yet} % Sets Journal name
+  \journal{Journal of Futures Markets} % Sets Journal name
 
@@
             pdfauthor={},
-            pdftitle={Financialisation of commodities: co-movement behind-the-scenes},
+            pdftitle={Financialisation of Commodities: Co-movement Behind-the-scenes},
             colorlinks=false,
@@
 
-  \title{Financialisation of commodities: co-movement behind-the-scenes}
-    \author[strath]{Devraj Basu\corref{1}}
-   \ead{devraj.basu@strath.ac.uk} 
-    \author[strath]{Olivier Bauthéac}
-
-      \address[strath]{University of Strathclyde Business school}
-      \cortext[1]{Corresponding Author}
+  \title{Financialisation of Commodities: Co-movement Behind-the-scenes}
 
@@
 (2020) taking the opposite stance.
-Our analysis of individual commodity returns' relation with both CHP and \textbf{CHP} before and during financialisation sheds new lights on this issue with our results suggesting that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
+Our analysis of individual commodity returns' relation with both CHP and \textbf{CHP} before and during financialisation sheds a new light on this issue with our results suggesting that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
 
@@
 Besides, starting in the crisis the Keneysian paradigm of returns begins to revert with higher mean returns during low (\textbf{backwardation}) relative to high (\textbf{contango}) \textbf{CHP} phases and this pattern continues, more pronounced, over the post-crisis period.
-As pointed out in Basu and Bauthéac (2021), the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
+As pointed out in Basu and Bauthéac (2023), the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
 
@@
 (2014), Ekeland et al.
-(2016), Goldstein and Yang (2017).} and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in Tang and Xiong (2012) and Basak and Pavlova (2016).
+(2016), Goldstein and Yang (2017), Ekeland et al.
+(2019), Isleimeyyeh (2020).} and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in Tang and Xiong (2012) and Basak and Pavlova (2016).
 
@@
 
-Taken together the patterns of results over the crisis and post-crisis periods echo those in Basu and Bauthéac (2021) in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex.
+Taken together the patterns of results over the crisis and post-crisis periods echo those in Basu and Bauthéac (2023) in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-basu_definancialisation}{}}%
-Basu, D., Bauthéac, O., 2021. Commodity definancialisation. Working paper.
+Basu, D., Bauthéac, O., 2023. Commodity definancialisation. Working paper.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ekeland_hedging_2019}{}}%
+Ekeland, I., Lautier, D., Villeneuve, B., 2019. \href{https://doi.org/10.1007/s00199-018-1115-y}{Hedging pressure and speculation in commodity markets}. Economic Theory 68, 83--123.
+
 \leavevmode\vadjust pre{\hypertarget{ref-etula_broker-dealer_2013}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-isleimeyyeh_role_2020}{}}%
+Isleimeyyeh, M., 2020. \href{https://doi.org/10.1002/fut.22122}{The role of financial investors in determining the commodity futures risk premium}. Journal of Futures Markets 40, 1375--1397.
+
 \leavevmode\vadjust pre{\hypertarget{ref-juvenal_speculation_2015}{}}%

### 2024-08-20 explore/scripts/revision-jfm-functions.r
Refined subsector regression analysis
Closes #50

@@ -92,13 +92,24 @@ filter_commodity_futures_tickers <- function(
   tickers$ticker
 }
 
-make_US_commodity_pool_combinations <- function(){
+make_US_commodity_pool_combinations_for_correlations_analysis <- function(){
   
   tibble::tibble(
     country = rep("US", 8L),
     sector = c(rep("agriculturals", 4L), rep("energy", 2L), rep("metals", 2L)),
     subsector = c(
       "all", "grains", "livestock", "softs", "all", "petroleum", "all", "precious"
+      )
+  )
+}
+
+make_US_commodity_pool_combinations_for_regressions_analysis <- function(){
+  
+  tibble::tibble(
+    country = rep("US", 10L),
+    sector = c(rep("agriculturals", 4L), rep("energy", 3L), rep("metals", 3L)),
+    subsector = c(
+      "all", "grains", "livestock", "softs", "all", "gas", "petroleum", "all", "base", "precious"
       )
   )
 }
@@ -111,7 +122,7 @@ make_commodity_pool_tickers_dataframe_for_country_sectors_subsectors_combination
     )
 }
 
-make_commodity_pool_tickers_dataframe <- function(all_tickers){
+make_commodity_pool_tickers_dataframe <- function(all_tickers, analysis = c("correlations", "regressions")){
   
   all_all_all <- tibble::tibble(
     country = "all", sector = "all", subsector = "all", 
@@ -122,16 +133,23 @@ make_commodity_pool_tickers_dataframe <- function(all_tickers){
     country = "US", sector = "all", subsector = "all", 
     tickers = list(filter_commodity_futures_tickers(all_tickers, "US"))
   )
+
+  US_combinations <- if(analysis == "correlations"){
+    make_US_commodity_pool_combinations_for_correlations_analysis()
+  } else {
+    make_US_commodity_pool_combinations_for_regressions_analysis()
+  }
+  US_combinations <-
+    make_commodity_pool_tickers_dataframe_for_country_sectors_subsectors_combinations(
+      US_combinations, all_tickers
+    )
   
-  US_combinations <- make_US_commodity_pool_combinations() %>%
-    make_commodity_pool_tickers_dataframe_for_country_sectors_subsectors_combinations(all_tickers)
-  
-  GB <- tibble::tibble(
+  GB_all_all <- tibble::tibble(
     country = "GB", sector = "all", subsector = "all", 
[…]

### 2024-08-20 explore/scripts/revision-jfm-tables.r

@@ -31,7 +31,7 @@ path <- paste0(here::here(), "/explore/tables/revision-jfm/regressions-factors.c
 readr::write_csv(formatted, path)
 
 # `all commodities ~ factors from US commodities ####
-path <- paste0(here::here(), "/explore/results/revision-jfm/regressions-factors.rds")
+path <- paste0(here::here(), "/explore/tables/revision-jfm/regressions-factors.rds")
 raw <- readRDS(path)
 
 formatted <- dplyr::filter(raw, factor %in% factors, timespan == "period") %>%
@@ -39,7 +39,7 @@ formatted <- dplyr::filter(raw, factor %in% factors, timespan == "period") %>%
   dplyr::mutate(
     country = factor(country, levels = c("all", "US", "GB")),
     sector = factor(sector, levels = c("all", "agriculturals", "energy", "metals")),
-    subsector = factor(subsector, levels = c("all", "grains", "livestock", "petroleum", "precious", "softs")),
+    subsector = factor(subsector, levels = c("all", "base", "gas", "grains", "livestock", "petroleum", "precious", "softs")),
     period = factor(period, levels = c("past", "financialization", "crisis", "present")),
     factor = factor(factor, levels = factors),
     average = percentize(average)

### 2024-08-20 docs/paper.Rmd

@@
 Both patterns suggest that the phenomenon may have altered this long-standing paradigm of commercial risk transfer with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants.
-This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of market participation.
+This change could have altered the hedging ontology in these markets and our asset pricing framework is tailored to detect these more subtle effects driven by changes in the nature of market participation.
 Factor model techniques are well suited to isolating common driving factors and detecting co-movement [@fama_common_1993; @carhart_persistence_1997; @asness_devil_2013; @fama_five_factor_2015; @hou_digesting_2015; @asness_fact_2015; @frazzini_betting_2014; @asness_quality_2019] at a broader level, beyond individual pairs of assets, and are commonly used to study commodity market fundamentals [@schwartz_short_2000; @miffre_momentum_2007; @gorton_fundamentals_2012; @cortazar_commodity_2013; @yang_investment_2013; @daskalaki_factors_2014; @szymanowska_anatomy_2014; @fernandez_skewness_2018; @bakshi_understanding_2019; @boons_basis_2019; @sakkas_factor_2020]; they consequently seem well adapted to study these two issues simultaneously.
@@
 
-By grouping together assets by shared attribute dynamics in common portfolios asset pricing techniques and factor models in particular are well suited to study co-movement [@fama_common_1993; @carhart_persistence_1997; @asness_devil_2013; @fama_five_factor_2015; @hou_digesting_2015; @asness_fact_2015; @frazzini_betting_2014; @asness_quality_2019].
+By grouping together assets by shared attribute dynamics in common portfolios, asset pricing techniques--and factor models in particular--are well suited to study co-movement [@fama_common_1993; @carhart_persistence_1997; @asness_devil_2013; @fama_five_factor_2015; @hou_digesting_2015; @asness_fact_2015; @frazzini_betting_2014; @asness_quality_2019].
 Careful, theory-based, attribute selection further enables a refined analysis of market fundamentals [@schwartz_short_2000; @miffre_momentum_2007; @gorton_fundamentals_2012; @cortazar_commodity_2013; @yang_investment_2013; @daskalaki_factors_2014; @szymanowska_anatomy_2014; @fernandez_skewness_2018; @bakshi_understanding_2019; @boons_basis_2019; @sakkas_factor_2020].
@@
 The explanatory power for the other commodities is typically low or even 0 for the case where commodities are perfectly uncorrelated with one-another.
-A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities.
-and therefore provides evidence that pairwise return correlation relates to factor attribute.
+A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities; and therefore provides evidence that pairwise return correlation relates to factor attribute.
 The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \@ref(tab:co-movement-time-reg-US-facts-US).

### 2024-08-21 others/revision-jfm - notes.Rmd
Analysis of new factor regressions results

---
title: "revision-jfm - notes"
output: html_document
date: '2024-08-20'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Factor regressions results overview ####

### All, all, all ####

#### First period ####

##### Market factor ####

- Best overall performance: fits story.
- Overall performance consistent across periods of high and low CHP: fits story.

##### CHP factor ####

- Lower performance relative to market factor: fits story.
- Higher performance in backwardation: fits overall story but not current text, rewrite.

##### Open interest nearby factor ####

- Lower performance relative to market factor but higher than CHP.
- Higher performance in contango.
- Not included in story yet, could potentially include, not sure how.

##### Open interest aggregate factor ####

- Lowest performance overall for the factor itself.
- Moderate performance (slightly lower than that for OI nearby) for both legs. Indicates that the legs are negatively correlated.
- Higher performance in contango.
- Not included in story yet, could potentially include, not sure how.

##### Term structure factor ####

- Similar pattern to OI aggregate.
- Not included in story yet, could potentially include, not sure how.

#### Second period ####

##### Market factor ####

- Substantial improvement in performance (19.70% vs. 9.69%) albeit not as strong as that for the CHP factor in a relative sense: fits story.
- Stronger performance in backwardation: not included in story.

##### CHP factor ####

- Strongest improvement in performance in relative sense (5.39% vs 1.93%). Improvement comes from long leg (16.95% vs. 5.77%), not as strong for short leg (10.49% vs. 5.41%): fits story.
- Stronger performance in backwardation: not included in story.

##### Open interest nearby factor ####

- No notable change in performance for the factor itself (5.63% vs 5.98%).
- Both legs show substantial improvement however (long: 14.18% vs 8.12%; short: 14.04% vs. 6.13%), indicating that they become negatively correlated.
- Stronger performance switches to backwardation.
- Not included in story, include?

##### Open interest aggregate factor ####

- Increase in performance similar in a relative sense for the factor itself and the legs indicating legs maintain similar level of negative correlation.
- Performance of the factor itself remains low.
- Not included in story, include?

##### Term structure factor ####

- Increase in performance (2.95%vs 1.52%) although performance remains low. Better performance switches to contango.
- More pronouced increase for the short leg (15.77% vs. 5.28%).
- Gap widens between performance of factor itselfs and that of legs; indicates legs become less positively correlated.
- Better performance switches to backwardation on both legs.

### 2024-08-21 paper.Rmd
Deploying to gh-pages from @ bautheac/financialisation-co-movement@dfa0c60f2c66f588ddc7f5b86d4f8f206e8368a5 🚀

@@
 output:
+  bookdown::pdf_book:
+      pandoc_args: latex-blind.yaml
+      base_format: rticles::elsevier_article
+      latex_engine: xelatex
+      toc_depth: 3
+      includes:
+        in_header: preamble.tex
   bookdown::gitbook:
@@
 
-We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008^[Starting point based on earlier studies [@baker_financialisation_2014; @christoffersen_factor_2014].]); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).
+We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008^[Starting point based on earlier studies [@baker_financialization_2021; @christoffersen_factor_2014].]); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).
 Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.

### 2024-08-21 explore/scripts/revision-jfm-tables.r
Table 1: descriptive statistics (no regimes)

@@ -13,41 +13,70 @@ factors <- c("market", "CHP", "open interest nearby", "open interest aggregate",
 sector_levels <- c("all", "agriculturals", "energy", "metals")
 subsector_levels <- c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")
 
-# `US commodities ~ factors from US commodities ####
-path <- paste0(here::here(), "/explore/results/revision-jfm/regressions-factor.rds")
-raw <- readRDS(path)
 
-formatted <- dplyr::filter(raw, factor %in% factors, timespan == "period") %>%
-  dplyr::select(-c(timespan, year, field, type, frequency, sector, subsector)) %>%
+# descriptive stats ####
+stats <- readr::read_rds(
+  here::here("explore", "results", "revision-jfm", "descriptive-statistics-clean.rds")
+)
+
+commodities_market_individuals <- dplyr::filter(stats, analysis == "commodity futures") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(analysis == "market variables") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(assets == "individual commodities") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(
+    type == "returns", period != "year", frequency == "daily", 
+    field == "close price"
+  ) %>% dplyr::select(-c(ticker, type, frequency, field, year)) %>%
+  dplyr::mutate_if(.predicate = is.list, .funs = unlist)
+
+commodities_market_countries <- dplyr::filter(stats, analysis == "commodity futures") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(analysis == "market variables") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(assets == "countries - sectors - subsectors") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(
+    sector == "all", subsector == "all", field == "close price",
+    type == "returns", period != "year", frequency == "daily"
+  ) %>% dplyr::select(-c(type, frequency, field, year)) %>%
+  dplyr::mutate_if(.predicate = is.list, .funs = unlist)
+
+## whole ####
+commodities <- dplyr::filter(commodities_market_individuals, regime == "all") %>%
[…]

### 2024-08-21 explore/scripts/revision-jfm-tables.r
Table 2: descriptive statistics (regimes)

@@ -69,12 +69,37 @@ countries <- dplyr::filter(commodities_market_countries, regime == "all") %>%
     cols = c("mean", "sd"), names_to = "estimate", values_to = "value"
   ) %>% tidyr::pivot_wider(names_from = "period", values_from = "value")
 
-whole <- dplyr::bind_rows(commodities, countries)
+descriptive_stats_whole <- dplyr::bind_rows(commodities, countries)
 
 
-tables <- tibble::tibble(
-  analysis = "descriptive statistics (no regimes)", results = list(whole)
-)
+## regimes ####
+commodities <- dplyr::filter(commodities_market_individuals, regime != "all") %>%
+  dplyr::select(-c(min, max)) %>% 
+  dplyr::mutate(
+    mean = percentize(mean), sd = percentize(sd),
+    mean = purrr::map2_chr(p.value, mean, ~ significance(.x, .y))
+  ) %>% dplyr::select(-p.value) %>%
+  tidyr::pivot_longer(
+    cols = c("mean", "sd"), names_to = "estimate", values_to = "value"
+  ) %>% tidyr::pivot_wider(names_from = "period", values_from = "value") %>%
+  dplyr::arrange(dplyr::desc(country), sector, subsector, commodity) %>%
+  dplyr::select(-c(country, sector, subsector)) %>%
+  dplyr::rename(asset = commodity)
+
+countries <- dplyr::filter(commodities_market_countries, regime != "all") %>%
+  dplyr::select(-c(min, max, sector, subsector)) %>% 
+  dplyr::mutate(asset = paste(country, "commodities", sep = " ")) %>%
+  dplyr::select(-country) %>% 
+  dplyr::mutate(
+    mean = percentize(mean), sd = percentize(sd),
+    mean = purrr::map2_chr(p.value, mean, ~ significance(.x, .y))
+  ) %>% dplyr::select(-p.value) %>%
+  tidyr::pivot_longer(
+    cols = c("mean", "sd"), names_to = "estimate", values_to = "value"
+  ) %>% tidyr::pivot_wider(names_from = "period", values_from = "value")
+
+descriptive_stats_regimes <- dplyr::bind_rows(commodities, countries)
+
 
 
 path <- here::here("explore", "tables", "revision-jfm", "regressions-factors.csv")

### 2024-08-21 explore/scripts/revision-jfm-tables.r
Table 3: US commodity returns ~ CHP

@@ -101,7 +101,90 @@ countries <- dplyr::filter(commodities_market_countries, regime != "all") %>%
 descriptive_stats_regimes <- dplyr::bind_rows(commodities, countries)
 
 
+# regressions ####
+regressions <- readr::read_rds(
+  here::here("explore", "results", "revision-jfm", "regressions-time-series-clean.rds")
+)
 
-path <- here::here("explore", "tables", "revision-jfm", "regressions-factors.csv")
-readr::write_csv(formatted, path)
+## US commodity returns ~ US commodity individual CHP ####
+subsectors <- dplyr::filter(
+  regressions, analysis == "US commodity returns ~ US commodity individual CHP"
+) %>% dplyr::select(results) %>% tidyr::unnest(results) %>% 
+  dplyr::filter(regressor == "pressure change contemporaneous") %>%
+  dplyr::group_by(country, sector, subsector, period, regressor, regime.CHP.type, CHP.regime) %>%
+  dplyr::summarise(`average rsquared` = mean(rsquared, na.rm = TRUE)) %>%
+  dplyr::ungroup()
+sectors <- dplyr::filter(
+  regressions, analysis == "US commodity returns ~ US commodity individual CHP"
+) %>% dplyr::select(results) %>% tidyr::unnest(results) %>% 
+  dplyr::filter(regressor == "pressure change contemporaneous") %>%
+  dplyr::group_by(country, sector, period, regressor, regime.CHP.type, CHP.regime) %>%
+  dplyr::summarise(`average rsquared` = mean(rsquared, na.rm = TRUE)) %>%
+  dplyr::mutate(subsector = "all") %>% dplyr::ungroup()
+countries <- dplyr::filter(
+  regressions, analysis == "US commodity returns ~ US commodity individual CHP"
+) %>% dplyr::select(results) %>% tidyr::unnest(results) %>% 
+  dplyr::filter(regressor == "pressure change contemporaneous") %>%
+  dplyr::group_by(country, period, regressor, regime.CHP.type, CHP.regime) %>%
+  dplyr::summarise(`average rsquared` = mean(rsquared, na.rm = TRUE)) %>%
+  dplyr::mutate(sector = "all", subsector = "all") %>% dplyr::ungroup()
+
+`US commodity returns ~ US commodity individual CHP` <- dplyr::bind_rows(
+  countries, sectors, subsectors 
+) %>%
+  dplyr::mutate(
[…]

### 2024-08-27 docs/paper.Rmd
Update table IDs

@@
 The CHP factor model thus seems able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialisation.
-We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period^[See section \@ref(co-movement-methods) for further details.] and evaluating its performance on these selected commodities as well as on all US traded commodities.
+We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period^[See section \@ref(methods) for further details.] and evaluating its performance on these selected commodities as well as on all US traded commodities.
 The results of this exercise provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
@@
 
-## Methods {#co-movement-methods}
+## Methods {#methods}
 
@@
 
-# Results & discussion {#co-movement-results}
-<!-- Results & discussion {#co-movement-results} -->
+# Results & discussion {#results}
+<!-- Results & discussion {#results} -->
 <!-- =================== -->
 
-The descriptive statistics for the commodity series considered in the study displayed in table \@ref(tab:co-movement-stats-no-regimes) show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
+The descriptive statistics for the commodity series considered in the study displayed in table \@ref(tab:stats-no-regimes) show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
 6.9% with a 10% significance in the pre-financialisation period.
@@
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
-In table \@ref(tab:co-movement-stats-regimes) the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
+In table \@ref(tab:stats-no-regimes) the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
 Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another.
@@
 In the second model hedgers are seen as liquidity providers as in @kang_tale_2020 with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
-Table \@ref(tab:co-movement-time-reg-US-CHP) supports this view.
+Table \@ref(tab:time-reg-US-CHP) supports this view.
 We regress commodity futures front returns on individual commercial hedging pressure (CHP) as well as aggregate CHP (**CHP**), our market wide measure of CHP, in separate models and find that the explanatory power of CHP at the individual commodity level decreases over the financialisation period with the US cross-sectional average $R^{2}$ falling down to 20.8% from 25.8% in the previous period while that of **CHP** increases (7.1% vs 5.4%).
@@
 The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results.
-Returns fall sharply relative to the financialisation period (table \@ref(tab:co-movement-stats-no-regimes)) with eighteen US commodities along with all six UK traded metals showing lower mean returns.
+Returns fall sharply relative to the financialisation period (table \@ref(tab:stats-no-regimes)) with eighteen US commodities along with all six UK traded metals showing lower mean returns.
 Returns for equally weighted portfolios of both sets of assets fall down to 9.4% and 5.3% from 15.9% and 21.8% respectively.
-Returns are mostly higher during phases of **backwardation** relative to **contango** (table \@ref(tab:co-movement-stats-regimes)) with fifteen US assets and five of the UK traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets.
+Returns are mostly higher during phases of **backwardation** relative to **contango** (table \@ref(tab:stats-no-regimes)) with fifteen US assets and five of the UK traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets.
 Volatility is moderately higher for both sets with fifteen US commodities and three UK metals showing higher figures and interestingly eminently higher over phases of **contango**; out of the US complex only Sugar-#11 (IFUS) and none of the UK traded metals show higher volatility figures over **backwardation** phases.
@@
 
-The returns pullback continues into the post-crisis period (table \@ref(tab:co-movement-stats-no-regimes)) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively.
+The returns pullback continues into the post-crisis period (table \@ref(tab:stats-no-regimes)) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively.
 Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
 The figures for the equally weighted portfolios of US and UK assets drop to 9.9% and 16.2% respectively, very close to pre-financialisation levels.
-The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (table \@ref(tab:co-movement-stats-regimes)) with mean returns higher during phases of **backwardation** relative to **contango** (table \@ref(tab:co-movement-stats-regimes)), more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
+The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (table \@ref(tab:stats-no-regimes)) with mean returns higher during phases of **backwardation** relative to **contango** (table \@ref(tab:stats-no-regimes)), more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
 The difference is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
@@
 Over the financialisation period in contrast volatilities were predominantly higher in **backwardation** for US traded assets with fourteen commodities showing higher volatility figures in these phases; the post-crisis pattern of results for volatilities thus likewise shows signs of reversion to pre-financialisation standards.
-After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and **CHP** part ways (table \@ref(tab:co-movement-time-reg-US-CHP)), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
+After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and **CHP** part ways (table \@ref(tab:time-reg-US-CHP)), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
 The recovery initiated in the crisis period for that of CHP is confirmed with a stronger increase in the post-crisis period, 27.2% vs.
@@
 
-```{r co-movement-stats-no-regimes}
-caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+```{r stats-no-regimes}
+caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
 Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.
-The results are discussed in section \\@ref(co-movement-results)."
+The results are discussed in section \\@ref(results)."
 caption <- if (latex) caption_latex(x = caption) else if (html) caption
@@
 
-```{r co-movement-stats-regimes}
-caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+```{r stats-no-regimes}
+caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
 Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
 Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.
-Aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
+Aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
 caption <- if (latex) caption_latex(x = caption) else if (html) caption
@@
 
-```{r co-movement-time-reg-US-CHP}
-caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \\@ref(co-movement-methods).
+```{r time-reg-US-CHP}
+caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \\@ref(methods).
 Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The results are discussed in section \\@ref(co-movement-results)."
+The results are discussed in section \\@ref(results)."
 caption <- if (latex) caption_latex(x = caption) else if (html) caption
@@
 The results are reported in order for the market, CHP, open interest and term structure factors, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
+Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
 caption <- if (latex) caption_latex(x = caption) else if (html) caption
@@
 The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor.
-Factors construction details are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
+Factors construction details are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
 caption <- if (latex) caption_latex(x = caption) else if (html) caption
@@
 The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor.
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
+Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
 caption <- if (latex) caption_latex(x = caption) else if (html) caption
@@
 The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
+Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
 caption <- if (latex) caption_latex(x = caption) else if (html) caption

### 2024-08-27 explore/scripts/revision-jfm-tables.r
export formatted tables

@@ -1,18 +1,10 @@
 library(magrittr)
 
+# Globals ####
+
+## variables ####
 results_directory_path <- here::here("explore", "results", "revision-jfm")
 tables_directory_path <- here::here("explore", "tables", "revision-jfm")
-paste_forward_slash <- function(...) paste(..., sep = "/")
-
-significance <- function(p.value, estimate){
-  if(p.value <= 0.01) paste0("***", estimate)
-  else if (p.value > 0.01 && p.value <= 0.05) paste0("**", estimate)
-  else if (p.value > 0.05 && p.value <= 0.10) paste0("*", estimate)
-  else estimate
-}
-
-percentize <- function(value) paste0(round(value, digits = 4L) * 100, "%")
-
 factors <- c("market", "CHP", "open interest nearby", "open interest aggregate", "term structure")
 sector_levels <- c("all", "agriculturals", "energy", "metals")
 subsector_levels <- c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")
@@ -23,6 +15,15 @@ sort_levels <- c(
   "US-metals-precious", "GB-all-all"
 )
 
+## functions ####
+paste_forward_slash <- function(...) paste(..., sep = "/")
+significance <- function(p.value, estimate){
+  if(p.value <= 0.01) paste0("***", estimate)
+  else if (p.value > 0.01 && p.value <= 0.05) paste0("**", estimate)
+  else if (p.value > 0.05 && p.value <= 0.10) paste0("*", estimate)
+  else estimate
+}
+percentize <- function(value) paste0(round(value, digits = 4L) * 100, "%")
 sort_table_by_country_sector_subsector <- function(tb, sort_levels){
   dplyr::mutate(
     tb,
@@ -30,7 +31,6 @@ sort_table_by_country_sector_subsector <- function(tb, sort_levels){
     sort = factor(sort, levels = sort_levels)
   ) %>% dplyr::arrange(sort) %>% dplyr::select(-sort)
 }
-
 
 
 # descriptive stats ####
@@ -89,7 +89,6 @@ countries <- dplyr::filter(commodities_market_countries, regime == "all") %>%
   ) %>% tidyr::pivot_wider(names_from = "period", values_from = "value")
 
 descriptive_stats_whole <- dplyr::bind_rows(commodities, countries)
-
 
 ## regimes ####
[…]

### 2024-08-27 explore/scripts/revision-jfm-tables.r
reformat table 3 (US returns ~ CHP)

@@ -224,7 +224,7 @@ countries <- dplyr::filter(
     subsector = factor(subsector, levels = subsector_levels)
   ) %>% 
   dplyr::filter(regime.CHP.type == "none") %>%
-  dplyr::select(sector, subsector, period, `average rsquared`) %>%
+  dplyr::select(regressor, sector, subsector, period, `average rsquared`) %>%
   dplyr::arrange(sector, subsector, period) %>%
   tidyr::pivot_wider(names_from = period, values_from = `average rsquared`)
 

### 2024-08-27 docs/paper.Rmd
Update reference + reformat table 3 + caption table 4
goldstein_commodity_2017 -> goldstein_commodity_2022
Table 3: US returns ~ CHP
Table 4: correlations - periods

@@
 
-# folder <- "literature_files"; dir.create(folder); path <- paste(folder, "references.bib", sep = "/")
-# download.file("https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", path)
+folder <- "literature_files"; dir.create(folder); path <- paste(folder, "references.bib", sep = "/")
+download.file("https://www.dropbox.com/scl/fi/n7t8g3hn32d8e5gf2rcti/references.bib?rlkey=xy251n44q3y0t3omxpqk0dvyf&dl=1", path)
+
+tables_directory_path <- here::here("explore", "tables", "revision-jfm")
+paste_forward_slash <- function(...) paste(..., sep = "/")
 
@@
 
-@goldstein_speculation_2014 and @goldstein_commodity_2017 argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
+@goldstein_speculation_2014 and @goldstein_commodity_2022 argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
 Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger’s positions (Keynesian perspective, theory of normal backwardation: @keynes_treatise_1930, @hicks_value_1939, @houthakker_speculators_1957, @telser_futures_1958), as well our term structure factor, based on backwardation as measured by roll yield (Working's perspective, theory of storage: @working_price_1933, @kaldor_speculation_1939, @working_theory_1948, @brennan_supply_1958, @cootner_returns_1960, @weymar_supply_1966, @danthine_information_1978, @turnovsky_determination_1983, @schwartz_stochastic_1997), to be best suited to measure the impact of financialisation.
@@
 However, the fundamental question of the nature of the impact of financialisation across the entire cross-section of commodity futures markets has not yet been completely answered.
-We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2014, @ekeland_speculation_2016, @goldstein_commodity_2017, @ekeland_hedging_2019, @isleimeyyeh_role_2020.] and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in @tang_index_2012 and @basak_model_2016.
+We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2014, @ekeland_speculation_2016, @goldstein_commodity_2022, @ekeland_hedging_2019, @isleimeyyeh_role_2020.] and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in @tang_index_2012 and @basak_model_2016.
 
@@
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
-In table \@ref(tab:stats-no-regimes) the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
+In table \@ref(tab:stats-regimes) the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
 Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another.
@@
 A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities; and therefore provides evidence that pairwise return correlation relates to factor attribute.
-The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \@ref(tab:co-movement-time-reg-US-facts-US).
+The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \@ref(tab:time-reg-US-facts-US).
 Over the first period the market factor has the best average time series performance with the highest average $R^{2}$ with all three futures market factors performing poorly, indicating that the commodities with extreme factor attributes (high or low CHP for example) are uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of high and low **CHP** (below period median).
@@
 
-We next investigate the top eight of the US traded commodities which achieved the highest time series $R^{2}$ for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \@ref(tab:co-movement-picks).
+We next investigate the top eight of the US traded commodities which achieved the highest time series $R^{2}$ for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \@ref(tab:picks).
 For the CHP factor the commodities that achieve high $R^{2}$ in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor.
@@
 
-In table \@ref(tab:co-movement-correlations), we show the average pairwise returns correlation between each set of picks in each time period.
+In table \@ref(tab:correlations), we show the average pairwise returns correlation between each set of picks in each time period.
 Following on form the earlier observations, this exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.
@@
 To further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their explanatory performance on these sets of picks over the four periods independently.
-The results are shown in table \@ref(tab:co-movement-time-reg-picks-facts-picks).
+The results are shown in table \@ref(tab:time-reg-picks-facts-picks).
 The long-short factors for a particular attribute select the top and bottom two of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks.
@@
 
-In table \@ref(tab:co-movement-time-reg-US-facts-picks) we assess the performance of the same factors on all the commodities instead of just the picks.
-While the average $R^{2}$s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table \@ref(tab:co-movement-time-reg-picks-facts-picks).
+In table \@ref(tab:time-reg-US-facts-picks) we assess the performance of the same factors on all the commodities instead of just the picks.
+While the average $R^{2}$s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table \@ref(tab:time-reg-picks-facts-picks).
 In contrast, the average CHP factor built with average CHP factor picks shows a smaller absolute increase in average $R^{2}$ indicating that the link between CHP co-movement and price co-movement is stronger amongst the picks which are predominantly metals.
-Taken together, the results in tables \@ref(tab:co-movement-time-reg-picks-facts-picks) and \@ref(tab:co-movement-time-reg-US-facts-picks) suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.
-To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in table \@ref(tab:co-movement-time-reg-UK-facts-picks).
+Taken together, the results in tables \@ref(tab:time-reg-picks-facts-picks) and \@ref(tab:time-reg-US-facts-picks) suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.
+To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in table \@ref(tab:time-reg-UK-facts-picks).
 In the first period, although all sets of picks, except that of the market factor, included at least one metal, the average $R^{2}$s are very low; close to zero in most cases.
@@
 The symmetry between the dynamics of CHP and **CHP**'s explanatory power on individual commodity returns breaks in the crisis period with both now seemingly converging; the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%).
-The performance of the market factor dominates the US commodity complex over the period with a 50% increase in mean average $R^{2}$ to over 30% (table \@ref(tab:co-movement-time-reg-US-facts-US)) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
-The average pairwise correlation amongst the market factor picks increases beyond 50% while there is a leveling in that amongst the picks of the long-short factors as shown in table \@ref(tab:co-movement-correlations).
-Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table \@ref(tab:co-movement-time-reg-US-facts-picks)).
+The performance of the market factor dominates the US commodity complex over the period with a 50% increase in mean average $R^{2}$ to over 30% (table \@ref(tab:time-reg-US-facts-US)) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
+The average pairwise correlation amongst the market factor picks increases beyond 50% while there is a leveling in that amongst the picks of the long-short factors as shown in table \@ref(tab:correlations).
+Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table \@ref(tab:time-reg-US-facts-picks)).
 Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
-Table \@ref(tab:co-movement-time-reg-UK-facts-picks) provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average $R^{2}$ increasing to 31.7% from 10.2% in the previous period.
+Table \@ref(tab:time-reg-UK-facts-picks) provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average $R^{2}$ increasing to 31.7% from 10.2% in the previous period.
 
@@
 14.8%.
-Average pairwise correlations amongst factor picks (table \@ref(tab:co-movement-correlations)) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1% to 26.1%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
-The performance of the market factor on the US complex declines below financialisation levels (table \@ref(tab:co-movement-time-reg-US-facts-US)) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table \@ref(tab:co-movement-time-reg-US-facts-picks)) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors.
-Table \@ref(tab:co-movement-time-reg-UK-facts-picks) provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
+Average pairwise correlations amongst factor picks (table \@ref(tab:correlations)) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1% to 26.1%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
+The performance of the market factor on the US complex declines below financialisation levels (table \@ref(tab:time-reg-US-facts-US)) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table \@ref(tab:time-reg-US-facts-picks)) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors.
+Table \@ref(tab:time-reg-UK-facts-picks) provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
 
@@
 ```{r}
-tables <- readr::read_rds(here::here("explore", "tables", "tables.rds"))
+tables <- readr::read_rds(paste_forward_slash(tables_directory_path, "tables-formatted.rds"))
 ```
@@
 
-table <- get_results(tables, "descriptive statistics (no regimes)") %>%
+table <- get_results(tables, "stats - whole") %>%
   kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
@@
 
-```{r stats-no-regimes}
+```{r stats-regimes}
 caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
@@
 
-table <- get_results(tables, "descriptive statistics (regimes)") %>% 
+table <- get_results(tables, "stats - regimes") %>% 
   kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
@@
 
-table <- get_results(tables, "regressions - time series - US commodities ~ CHP") %>% 
+table <- get_results(tables, "regressions - US returns ~ US CHP") %>% 
   kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
@@
 
-```{r co-movement-time-reg-US-facts-US}
-caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities.
-The asset pool for the factor mimicking portfolio construction includes the twenty four US commodities.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
+```{r correlations-periods}
+caption <- "This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+For each period, the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
+Aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
 caption <- if (latex) caption_latex(x = caption) else if (html) caption
+colnames <- c("country", "sector", "subsector", "past", "regime", "financialisation", "crisis", "post-crisis")
+align <- c("lllrrrrr")
 
-colnames <- c("factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
-align <- c("lllrrrr")
-
-table <- get_results(tables, "regressions - time series - US commodities ~ factors from US commodities") %>%
-  dplyr::mutate(
-    factor = as.character(factor),
-    factor = ifelse(factor == "OI nearby", "open interest", factor)
-  ) %>% 
-  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, col.names = colnames, align = align) %>%
+table <- get_results(tables, "correlations - periods") %>% 
+  kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
   column_spec(1L, bold = TRUE) %>%
-  collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)
+  collapse_rows(columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)
 
@@
 
-```{r co-movement-picks}
-caption <- "This table shows the factor 'picks' for the market as well as the long-short factors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-For each factor and period the twenty four US commodities are regressed against the corresponding factor mimicking portfolio and ranked by $R^{2}$.
-The top eight commodities are selected as 'picks' for the corresponding factor and period.
-The table also shows the proportion of time, for each period, each individual pick lives on both legs (long vs.
-short) of its picking factor.
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor.
-Factors construction details are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
-caption <- if (latex) caption_latex(x = caption) else if (html) caption
-colnames <- c("picking factor", "period", "pick", "long", "short")
-align <- c("lllrr")
-
-table <- get_results(tables, "proportions") %>%
-  dplyr::mutate(period = stringr::str_replace_all(period, "present", "post-crisis")) %>%
-  dplyr::mutate(
-    factor = as.character(factor),
-    factor = ifelse(factor == "OI nearby", "open interest", factor)
-  ) %>% 
-  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
-  column_spec(1L, bold = TRUE) %>%
-  collapse_rows(
-    columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
-  )
-
-style_table(output_type, table)
-```
-
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
-```{r, include=latex}
-knitr::asis_output('\\newpage')
-```
-
-```{r co-movement-correlations}
-caption <- "This table shows the average pairwise correlation amongst factor picks for each factor and period independently.
-The figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor.
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
-caption <- if (latex) caption_latex(x = caption) else if (html) caption
-colnames <- c("picking factor", "regime", "past", "financialisation", "crisis", "post-crisis")
-align <- c("llrrrr")
-
-table <- get_results(tables, "average correlations (amongst factor picks)") %>%
-  dplyr::mutate( factor = as.character(factor), factor = ifelse(factor == "OI nearby", "open interest", factor)) %>% 
-  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
-  column_spec(1L, bold = TRUE) %>%
-  collapse_rows(
-    columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
-  )
-
-style_table(output_type, table)
-```
-
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
-
-```{r co-movement-time-reg-picks-facts-picks, fig.pos = 'htbp'}
-caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the various sets of factor picks are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the picks.
-For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
-caption <- if (latex) caption_latex(x = caption) else if (html) caption
-colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
-align <- c("llllrrrr")
-
-table <- get_results(tables, "regressions - time series - factor picks ~ factors from picks") %>% 
-  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
-  column_spec(1L, bold = TRUE) %>%
-  collapse_rows(
-    columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
-  )
-
-style_table(output_type, table)
-```
-
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
-```{r, include=latex}
-knitr::asis_output('\\newpage')
-```
-
-```{r co-movement-time-reg-US-facts-picks}
-caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities.
-For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
-caption <- if (latex) caption_latex(x = caption) else if (html) caption
-colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
-align <- c("llllrrrr")
-
-table <- get_results(tables, "regressions - time series - US commodities ~ factors from picks") %>% 
-  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
-  column_spec(1L, bold = TRUE) %>%
-  collapse_rows(
-    columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
-  )
-
-style_table(output_type, table)
-```
-
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
-```{r, include=latex}
-knitr::asis_output('\\newpage')
-```
-
-```{r co-movement-time-reg-UK-facts-picks}
-caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the six UK metals are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the six UK metals.
-For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
-caption <- if (latex) caption_latex(x = caption) else if (html) caption
-colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
-align <- c("llllrrrr")
-
-table <- get_results(tables, "regressions - time series - UK metals ~ factors from picks") %>% 
-  kbl(format = output_type, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames) %>%
-  column_spec(1L, bold = TRUE) %>%
-  collapse_rows(
-    columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
-  )
-
-style_table(output_type, table)
-```
-
-```{r, include=latex}
-knitr::asis_output('\\restoregeometry')
-knitr::asis_output('\\newpage')
-```
-
 # References {#references .unnumbered}

### 2024-08-27 docs/paper.tex
Update reference + reformat table 3 + caption table 4
goldstein_commodity_2017 -> goldstein_commodity_2022
Table 3: US returns ~ CHP
Table 4: correlations - periods

@@
 Both patterns suggest that the phenomenon may have altered this long-standing paradigm of commercial risk transfer with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants.
-This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of market participation.\\
+This change could have altered the hedging ontology in these markets and our asset pricing framework is tailored to detect these more subtle effects driven by changes in the nature of market participation.\\
 Factor model techniques are well suited to isolating common driving factors and detecting co-movement (Asness et al., 2015; Asness and Frazzini, 2013; Asness et al., 2019; Carhart, 1997; Fama and French, 2015, 1993; Frazzini and Pedersen, 2014; Hou et al., 2015) at a broader level, beyond individual pairs of assets, and are commonly used to study commodity market fundamentals (Bakshi et al., 2019; Boons and Prado, 2019; Cortazar et al., 2013; Daskalaki et al., 2014; Fernandez-Perez et al., 2018; Gorton et al., 2012; Miffre and Rallis, 2007; Sakkas and Tessaromatis, 2020; Schwartz and Smith, 2000; Szymanowska et al., 2014; Yang, 2013); they consequently seem well adapted to study these two issues simultaneously.
@@
 
-We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008\footnote{Starting point based on earlier studies (Baker, 2014; Christoffersen et al., 2014).}); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).\\
+We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008\footnote{Starting point based on earlier studies (Baker, 2021; Christoffersen et al., 2014).}); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).\\
 Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.
@@
 Goldstein et al.
-(2014) and Goldstein and Yang (2017) argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
+(2014) and Goldstein and Yang (2022) argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
 Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger's positions (Keynesian perspective, theory of normal backwardation: Keynes (1930), Hicks (1939), H.
@@
 The CHP factor model thus seems able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialisation.\\
-We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period\footnote{See section \ref{co-movement-methods} for further details.} and evaluating its performance on these selected commodities as well as on all US traded commodities.
+We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period\footnote{See section \ref{methods} for further details.} and evaluating its performance on these selected commodities as well as on all US traded commodities.
 The results of this exercise provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
@@
 Besides, starting in the crisis the Keneysian paradigm of returns begins to revert with higher mean returns during low (\textbf{backwardation}) relative to high (\textbf{contango}) \textbf{CHP} phases and this pattern continues, more pronounced, over the post-crisis period.
-As pointed out in Basu and Bauthéac (2021), the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
+As pointed out in Basu and Bauthéac (2024), the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
 
@@
 (2014), Ekeland et al.
-(2016), Goldstein and Yang (2017).} and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in Tang and Xiong (2012) and Basak and Pavlova (2016).
+(2016), Goldstein and Yang (2022), Ekeland et al.
+(2019), Isleimeyyeh (2020).} and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in Tang and Xiong (2012) and Basak and Pavlova (2016).
 
@@
 
-\hypertarget{co-movement-methods}{%
-\subsection{Methods}\label{co-movement-methods}}
+\hypertarget{methods}{%
+\subsection{Methods}\label{methods}}
 
@@
 
-By grouping together assets by shared attribute dynamics in common portfolios asset pricing techniques and factor models in particular are well suited to study co-movement (Asness et al., 2015; Asness and Frazzini, 2013; Asness et al., 2019; Carhart, 1997; Fama and French, 2015, 1993; Frazzini and Pedersen, 2014; Hou et al., 2015).
+By grouping together assets by shared attribute dynamics in common portfolios, asset pricing techniques--and factor models in particular--are well suited to study co-movement (Asness et al., 2015; Asness and Frazzini, 2013; Asness et al., 2019; Carhart, 1997; Fama and French, 2015, 1993; Frazzini and Pedersen, 2014; Hou et al., 2015).
 Careful, theory-based, attribute selection further enables a refined analysis of market fundamentals (Bakshi et al., 2019; Boons and Prado, 2019; Cortazar et al., 2013; Daskalaki et al., 2014; Fernandez-Perez et al., 2018; Gorton et al., 2012; Miffre and Rallis, 2007; Sakkas and Tessaromatis, 2020; Schwartz and Smith, 2000; Szymanowska et al., 2014; Yang, 2013).
@@
 
-\hypertarget{co-movement-results}{%
-\section{Results \& discussion}\label{co-movement-results}}
-
-The descriptive statistics for the commodity series considered in the study displayed in table \ref{tab:co-movement-stats-no-regimes} show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9\% significant at the 5\% level vs.~6.9\% with a 10\% significance in the pre-financialisation period.
+\hypertarget{results}{%
+\section{Results \& discussion}\label{results}}
+
+The descriptive statistics for the commodity series considered in the study displayed in table \ref{tab:stats-no-regimes} show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9\% significant at the 5\% level vs.~6.9\% with a 10\% significance in the pre-financialisation period.
 The increase is even more pronounced for an equally weighted portfolio of UK traded assets (metals), 2.47\% (not significant) to 21.8\% (significant at the 10\% level), which sets out the global nature of the phenomenon.
@@
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where \textbf{CHP} is low and vice et versa.
-In table \ref{tab:co-movement-stats-regimes} the mean returns are shown over high (\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP} regimes for each time period.\\
+In table \ref{tab:stats-regimes} the mean returns are shown over high (\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP} regimes for each time period.\\
 Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of \textbf{backwardation} as compared to \textbf{contango}, with the difference being statistically significant at the 10\% level for two commodities, at the 5\% level for one and at the 1\% level for another.
@@
 (2020) with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
-Table \ref{tab:co-movement-time-reg-US-CHP} supports this view.
+Table \ref{tab:time-reg-US-CHP} supports this view.
 We regress commodity futures front returns on individual commercial hedging pressure (CHP) as well as aggregate CHP (\textbf{CHP}), our market wide measure of CHP, in separate models and find that the explanatory power of CHP at the individual commodity level decreases over the financialisation period with the US cross-sectional average \(R^{2}\) falling down to 20.8\% from 25.8\% in the previous period while that of \textbf{CHP} increases (7.1\% vs 5.4\%).
@@
 The explanatory power for the other commodities is typically low or even 0 for the case where commodities are perfectly uncorrelated with one-another.
-A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities.
-and therefore provides evidence that pairwise return correlation relates to factor attribute.\\
-The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \ref{tab:co-movement-time-reg-US-facts-US}.
+A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities; and therefore provides evidence that pairwise return correlation relates to factor attribute.\\
+The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \ref{tab:time-reg-US-facts-US}.
 Over the first period the market factor has the best average time series performance with the highest average \(R^{2}\) with all three futures market factors performing poorly, indicating that the commodities with extreme factor attributes (high or low CHP for example) are uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of high and low \textbf{CHP} (below period median).
@@
 
-We next investigate the top eight of the US traded commodities which achieved the highest time series \(R^{2}\) for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \ref{tab:co-movement-picks}.\\
+We next investigate the top eight of the US traded commodities which achieved the highest time series \(R^{2}\) for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \ref{tab:picks}.\\
 For the CHP factor the commodities that achieve high \(R^{2}\) in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor.
@@
 
-In table \ref{tab:co-movement-correlations}, we show the average pairwise returns correlation between each set of picks in each time period.
+In table \ref{tab:correlations}, we show the average pairwise returns correlation between each set of picks in each time period.
 Following on form the earlier observations, this exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.\\
@@
 To further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their explanatory performance on these sets of picks over the four periods independently.
-The results are shown in table \ref{tab:co-movement-time-reg-picks-facts-picks}.
+The results are shown in table \ref{tab:time-reg-picks-facts-picks}.
 The long-short factors for a particular attribute select the top and bottom two of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks.
@@
 
-In table \ref{tab:co-movement-time-reg-US-facts-picks} we assess the performance of the same factors on all the commodities instead of just the picks.
-While the average \(R^{2}\)s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table \ref{tab:co-movement-time-reg-picks-facts-picks}.
+In table \ref{tab:time-reg-US-facts-picks} we assess the performance of the same factors on all the commodities instead of just the picks.
+While the average \(R^{2}\)s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table \ref{tab:time-reg-picks-facts-picks}.
 In contrast, the average CHP factor built with average CHP factor picks shows a smaller absolute increase in average \(R^{2}\) indicating that the link between CHP co-movement and price co-movement is stronger amongst the picks which are predominantly metals.
-Taken together, the results in tables \ref{tab:co-movement-time-reg-picks-facts-picks} and \ref{tab:co-movement-time-reg-US-facts-picks} suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.\\
-To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in table \ref{tab:co-movement-time-reg-UK-facts-picks}.
+Taken together, the results in tables \ref{tab:time-reg-picks-facts-picks} and \ref{tab:time-reg-US-facts-picks} suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.\\
+To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in table \ref{tab:time-reg-UK-facts-picks}.
 In the first period, although all sets of picks, except that of the market factor, included at least one metal, the average \(R^{2}\)s are very low; close to zero in most cases.
@@
 The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results.
-Returns fall sharply relative to the financialisation period (table \ref{tab:co-movement-stats-no-regimes}) with eighteen US commodities along with all six UK traded metals showing lower mean returns.
+Returns fall sharply relative to the financialisation period (table \ref{tab:stats-no-regimes}) with eighteen US commodities along with all six UK traded metals showing lower mean returns.
 Returns for equally weighted portfolios of both sets of assets fall down to 9.4\% and 5.3\% from 15.9\% and 21.8\% respectively.
-Returns are mostly higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:co-movement-stats-regimes}) with fifteen US assets and five of the UK traded metals showing higher mean returns in \textbf{backwardation} and the pattern extending to equally weighted portfolios of the two sets of assets.
+Returns are mostly higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:stats-no-regimes}) with fifteen US assets and five of the UK traded metals showing higher mean returns in \textbf{backwardation} and the pattern extending to equally weighted portfolios of the two sets of assets.
 Volatility is moderately higher for both sets with fifteen US commodities and three UK metals showing higher figures and interestingly eminently higher over phases of \textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none of the UK traded metals show higher volatility figures over \textbf{backwardation} phases.
 The symmetry between the dynamics of CHP and \textbf{CHP}'s explanatory power on individual commodity returns breaks in the crisis period with both now seemingly converging; the US cross-sectional average \(R^{2}\) at the individual level bouncing back up (22.5\% vs 20.8\%) while that at the aggregate level rises further (14.7\% vs 7.1\%).\\
-The performance of the market factor dominates the US commodity complex over the period with a 50\% increase in mean average \(R^{2}\) to over 30\% (table \ref{tab:co-movement-time-reg-US-facts-US}) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
-The average pairwise correlation amongst the market factor picks increases beyond 50\% while there is a leveling in that amongst the picks of the long-short factors as shown in table \ref{tab:co-movement-correlations}.
-Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table \ref{tab:co-movement-time-reg-US-facts-picks}).\\
+The performance of the market factor dominates the US commodity complex over the period with a 50\% increase in mean average \(R^{2}\) to over 30\% (table \ref{tab:time-reg-US-facts-US}) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
+The average pairwise correlation amongst the market factor picks increases beyond 50\% while there is a leveling in that amongst the picks of the long-short factors as shown in table \ref{tab:correlations}.
+Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table \ref{tab:time-reg-US-facts-picks}).\\
 Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
-Table \ref{tab:co-movement-time-reg-UK-facts-picks} provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average \(R^{2}\) increasing to 31.7\% from 10.2\% in the previous period.
-
-\medskip\setlength{\parindent}{0pt}
-
-The returns pullback continues into the post-crisis period (table \ref{tab:co-movement-stats-no-regimes}) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2\% and 2.7\% respectively.
+Table \ref{tab:time-reg-UK-facts-picks} provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average \(R^{2}\) increasing to 31.7\% from 10.2\% in the previous period.
+
+\medskip\setlength{\parindent}{0pt}
+
+The returns pullback continues into the post-crisis period (table \ref{tab:stats-no-regimes}) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2\% and 2.7\% respectively.
 Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
 The figures for the equally weighted portfolios of US and UK assets drop to 9.9\% and 16.2\% respectively, very close to pre-financialisation levels.\\
-The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (table \ref{tab:co-movement-stats-regimes}) with mean returns higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:co-movement-stats-regimes}), more so than over the crisis period with seventeen US commodities showing higher mean returns over \textbf{backwardation} phases.
+The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (table \ref{tab:stats-no-regimes}) with mean returns higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:stats-no-regimes}), more so than over the crisis period with seventeen US commodities showing higher mean returns over \textbf{backwardation} phases.
 The difference is significant at the 5\% level for Lumber (XCME) and at the 10\% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of \textbf{contango}.
@@
 Over the financialisation period in contrast volatilities were predominantly higher in \textbf{backwardation} for US traded assets with fourteen commodities showing higher volatility figures in these phases; the post-crisis pattern of results for volatilities thus likewise shows signs of reversion to pre-financialisation standards.
-After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and \textbf{CHP} part ways (table \ref{tab:co-movement-time-reg-US-CHP}), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
+After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and \textbf{CHP} part ways (table \ref{tab:time-reg-US-CHP}), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
 The recovery initiated in the crisis period for that of CHP is confirmed with a stronger increase in the post-crisis period, 27.2\% vs.~22.5\%, strongest for the metals sector, 37.3\% vs.~23.7\%, while the energy sector shows the opposite pattern: 11\% vs.~16\%.
 In contrast, after increasing stronger in the crisis, that for \textbf{CHP} falls overall in the post-crisis period, 7.5\% vs 14.7\%, with the decrease strongest for the energy sector in a relative sense: 2.5\% vs.~14.8\%.\\
-Average pairwise correlations amongst factor picks (table \ref{tab:co-movement-correlations}) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1\% to 26.1\%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
-The performance of the market factor on the US complex declines below financialisation levels (table \ref{tab:co-movement-time-reg-US-facts-US}) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table \ref{tab:co-movement-time-reg-US-facts-picks}) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors.
-Table \ref{tab:co-movement-time-reg-UK-facts-picks} provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
-
-\medskip\setlength{\parindent}{0pt}
-
-Taken together the patterns of results over the crisis and post-crisis periods echo those in Basu and Bauthéac (2021) in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex.
+Average pairwise correlations amongst factor picks (table \ref{tab:correlations}) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1\% to 26.1\%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
+The performance of the market factor on the US complex declines below financialisation levels (table \ref{tab:time-reg-US-facts-US}) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table \ref{tab:time-reg-US-facts-picks}) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors.
+Table \ref{tab:time-reg-UK-facts-picks} provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
+
+\medskip\setlength{\parindent}{0pt}
+
+Taken together the patterns of results over the crisis and post-crisis periods echo those in Basu and Bauthéac (2024) in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex.
 
@@
 \begin{longtable}[t]{>{}llrrrr}
-\caption{\label{tab:co-movement-stats-no-regimes}This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+\caption{\label{tab:stats-no-regimes}This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
 Mean values significant at the 1\%, 5\% and 10\% level are marked with ***, ** and * respectively.
-The results are discussed in section \ref{co-movement-results}.}\\
+The results are discussed in section \ref{results}.}\\
 \toprule
@@
 \begin{longtable}[t]{>{}lllrrrr}
-\caption{\label{tab:co-movement-stats-regimes}This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+\caption{\label{tab:stats-regimes}This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
 Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
 Mean values significant at the 1\%, 5\% and 10\% level are marked with ***, ** and * respectively.
-Aggregate CHP construction and corresponding regime definitions are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
+Aggregate CHP construction and corresponding regime definitions are discussed in section \ref{methods} while the results are discussed in section \ref{results}.}\\
 \toprule
@@
 \begin{longtable}[t]{>{}lllrrrr}
-\caption{\label{tab:co-movement-time-reg-US-CHP}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \ref{co-movement-methods}.
+\caption{\label{tab:time-reg-US-CHP}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \ref{methods}.
 Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The results are discussed in section \ref{co-movement-results}.}\\
+The results are discussed in section \ref{results}.}\\
 \toprule
@@
 \nopagebreak
- & agriculturals &  & 25.19\% & 21.6\% & 23.91\% & 28.12\%\\
-\nopagebreak
- & energy &  & 25.12\% & 19.45\% & 16\% & 10.96\%\\
-\nopagebreak
- & metals & \multirow[t]{-4}{*}{\raggedright\arraybackslash all} & 28.12\% & 19.1\% & 23.27\% & 37.32\%\\
+ &  & \multirow[t]{-2}{*}{\raggedright\arraybackslash all} & 25.19\% & 21.6\% & 23.91\% & 28.12\%\\
 \nopagebreak
@@
 \nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash agriculturals} & softs & 26.68\% & 20.89\% & 27.19\% & 31.88\%\\
+ & \multirow[t]{-4}{*}{\raggedright\arraybackslash agriculturals} & softs & 26.68\% & 20.89\% & 27.19\% & 31.88\%\\
+\nopagebreak
+ &  & all & 25.12\% & 19.45\% & 16\% & 10.96\%\\
 \nopagebreak
@@
 \nopagebreak
- & \multirow[t]{-2}{*}{\raggedright\arraybackslash energy} & petroleum & 26.93\% & 20.71\% & 18.87\% & 12.85\%\\
+ & \multirow[t]{-3}{*}{\raggedright\arraybackslash energy} & petroleum & 26.93\% & 20.71\% & 18.87\% & 12.85\%\\
+\nopagebreak
+ &  & all & 28.12\% & 19.1\% & 23.27\% & 37.32\%\\
 \nopagebreak
@@
 \nopagebreak
-\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{individual CHP}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash metals} & precious & 23.3\% & 17.41\% & 24.57\% & 37.93\%\\
+\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{Δ\% commodity CHP}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash metals} & precious & 23.3\% & 17.41\% & 24.57\% & 37.93\%\\
 \cmidrule{1-7}\pagebreak[0]
@@
 \nopagebreak
- & agriculturals &  & 4.91\% & 4.5\% & 12.14\% & 6.23\%\\
-\nopagebreak
- & energy &  & 3.35\% & 6.27\% & 14.83\% & 2.45\%\\
-\nopagebreak
- & metals & \multirow[t]{-4}{*}{\raggedright\arraybackslash all} & 8.36\% & 15.67\% & 22.37\% & 15.33\%\\
+ &  & \multirow[t]{-2}{*}{\raggedright\arraybackslash all} & 4.91\% & 4.5\% & 12.14\% & 6.23\%\\
 \nopagebreak
@@
 \nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash agriculturals} & softs & 4.34\% & 5.64\% & 10.35\% & 6.98\%\\
+ & \multirow[t]{-4}{*}{\raggedright\arraybackslash agriculturals} & softs & 4.34\% & 5.64\% & 10.35\% & 6.98\%\\
+\nopagebreak
+ &  & all & 3.35\% & 6.27\% & 14.83\% & 2.45\%\\
 \nopagebreak
@@
 \nopagebreak
- & \multirow[t]{-2}{*}{\raggedright\arraybackslash energy} & petroleum & 3.59\% & 7.49\% & 18.9\% & 3.17\%\\
+ & \multirow[t]{-3}{*}{\raggedright\arraybackslash energy} & petroleum & 3.59\% & 7.49\% & 18.9\% & 3.17\%\\
+\nopagebreak
+ &  & all & 8.36\% & 15.67\% & 22.37\% & 15.33\%\\
 \nopagebreak
@@
 \nopagebreak
-\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{aggregate CHP}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash metals} & precious & 7.92\% & 16.4\% & 21.98\% & 17.25\%\\*
+\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{Δ\% aggregate CHP}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash metals} & precious & 7.92\% & 16.4\% & 21.98\% & 17.25\%\\*
 \end{longtable}
@@
 
-\begin{longtable}[t]{>{}lllrrrr}
-\caption{\label{tab:co-movement-time-reg-US-facts-US}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities.
-The asset pool for the factor mimicking portfolio construction includes the twenty four US commodities.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
+\begin{longtable}[t]{>{}lllrrrrr}
+\caption{\label{tab:correlations-periods}This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+For each period, the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
+Aggregate CHP construction and corresponding regime definitions are discussed in section \ref{methods} while the results are discussed in section \ref{results}.}\\
 \toprule
-factor & leg & regime & past & financialisation & crisis & post-crisis\\
+country & sector & subsector & past & regime & financialisation & crisis & post-crisis\\
 \midrule
@@
 \toprule
-factor & leg & regime & past & financialisation & crisis & post-crisis\\
+country & sector & subsector & past & regime & financialisation & crisis & post-crisis\\
 \midrule
@@
 \endlastfoot
- &  & all & 11.68\% & 21.6\% & 30.72\% & 15.57\%\\
-\nopagebreak
- &  & backwardation & 11.28\% & 23.51\% & 28.95\% & 13.12\%\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{market}} &  & contango & 12.23\% & 19.96\% & 32.47\% & 17.66\%\\
-\nopagebreak
- &  & all & 1.67\% & 8.24\% & 5.67\% & 4.07\%\\
-\nopagebreak
- &  & backwardation & 1.84\% & 8.81\% & 5.01\% & 5.74\%\\
-\nopagebreak
- & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 2.05\% & 8.25\% & 6.81\% & 3.58\%\\
-\nopagebreak
- &  & all & 4.53\% & 15.14\% & 21.88\% & 9.31\%\\
-\nopagebreak
- &  & backwardation & 4.77\% & 17.25\% & 21.46\% & 8.07\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.85\% & 13.8\% & 22.56\% & 10.53\%\\
-\nopagebreak
- &  & all & 3.02\% & 4\% & 9.1\% & 4.36\%\\
-\nopagebreak
- &  & backwardation & 2.51\% & 4.03\% & 7.14\% & 6.24\%\\
-\nopagebreak
-\multirow[t]{-9}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 4\% & 4.81\% & 12.42\% & 3.88\%\\
-\cmidrule{1-7}\pagebreak[0]
- &  & all & 2.91\% & 3.84\% & 6.21\% & 5.12\%\\
-\nopagebreak
- &  & backwardation & 3.61\% & 2.93\% & 4.99\% & 5.04\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.5\% & 5.21\% & 7.39\% & 5.41\%\\
-\nopagebreak
- &  & all & 5.94\% & 13.15\% & 21.23\% & 8.72\%\\
-\nopagebreak
- &  & backwardation & 6.78\% & 14.01\% & 18.83\% & 8.01\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 5.47\% & 12.78\% & 23.07\% & 9.34\%\\
-\nopagebreak
- &  & all & 3.55\% & 7.41\% & 12.39\% & 4.25\%\\
-\nopagebreak
- &  & backwardation & 3.32\% & 9.77\% & 10.61\% & 3.97\%\\
-\nopagebreak
-\multirow[t]{-9}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.98\% & 5.16\% & 13.83\% & 4.86\%\\
-\cmidrule{1-7}\pagebreak[0]
- &  & all & 1.12\% & 1.46\% & 2.93\% & 0.94\%\\
-\nopagebreak
- &  & backwardation & 1.16\% & 2.17\% & 2.53\% & 1.28\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1.55\% & 2.02\% & 3.6\% & 1.22\%\\
-\nopagebreak
- &  & all & 4.15\% & 6.36\% & 8.39\% & 5.07\%\\
-\nopagebreak
- &  & backwardation & 4.38\% & 8.41\% & 9.91\% & 4.98\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.28\% & 5.73\% & 7.99\% & 5.5\%\\
-\nopagebreak
- &  & all & 2.59\% & 8.79\% & 14.46\% & 4\%\\
-\nopagebreak
- &  & backwardation & 2.78\% & 10.16\% & 10.18\% & 2.69\%\\
-\nopagebreak
-\multirow[t]{-9}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.9\% & 7.9\% & 18.16\% & 6.25\%\\*
+ &  &  & whole period & 0.0737 & 0.1638 & 0.2849 & 0.1282\\
+\nopagebreak
+ &  &  & backwardation & 0.0724 & 0.1790 & 0.2709 & 0.1001\\
+\nopagebreak
+\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{all}} &  &  & contango & 0.0748 & 0.1501 & 0.2985 & 0.1495\\
+\nopagebreak
+ &  &  & whole period & 0.0684 & 0.1545 & 0.2526 & 0.1096\\
+\nopagebreak
+ &  &  & backwardation & 0.0642 & 0.1697 & 0.2323 & 0.0859\\
+\nopagebreak
+ & \multirow[t]{-6}{*}{\raggedright\arraybackslash all} &  & contango & 0.0720 & 0.1402 & 0.2706 & 0.1268\\
+\nopagebreak
+ &  &  & whole period & 0.0910 & 0.1305 & 0.2322 & 0.1075\\
+\nopagebreak
+ &  &  & backwardation & 0.0799 & 0.1421 & 0.1975 & 0.0955\\
+\nopagebreak
+ &  & \multirow[t]{-9}{*}{\raggedright\arraybackslash all} & contango & 0.1018 & 0.1184 & 0.2611 & 0.1186\\
+\nopagebreak
+ &  &  & whole period & 0.4421 & 0.4898 & 0.5673 & 0.3728\\
+\nopagebreak
+ &  &  & backwardation & 0.4312 & 0.5283 & 0.5749 & 0.3289\\
+\nopagebreak
+ &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash grains} & contango & 0.4570 & 0.4510 & 0.5675 & 0.4161\\
+\nopagebreak
+ &  &  & whole period & 0.3340 & 0.2868 & 0.3707 & 0.3333\\
+\nopagebreak
+ &  &  & backwardation & 0.3053 & 0.2652 & 0.3906 & 0.3220\\
+\nopagebreak
+ &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash livestock} & contango & 0.3605 & 0.3150 & 0.3557 & 0.3483\\
+\nopagebreak
+ &  &  & whole period & 0.0391 & 0.0853 & 0.1584 & 0.0764\\
+\nopagebreak
+ &  &  & backwardation & 0.0437 & 0.0845 & 0.1210 & 0.0685\\
+\nopagebreak
+ & \multirow[t]{-12}{*}{\raggedright\arraybackslash agriculturals} & \multirow[t]{-3}{*}{\raggedright\arraybackslash softs} & contango & 0.0334 & 0.0874 & 0.1937 & 0.0833\\
+\nopagebreak
+ &  &  & whole period & 0.4908 & 0.5892 & 0.4687 & 0.4203\\
+\nopagebreak
+ &  &  & backwardation & 0.4844 & 0.5949 & 0.4601 & 0.4179\\
+\nopagebreak
+ &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & contango & 0.4957 & 0.5869 & 0.4779 & 0.4210\\
+\nopagebreak
+ &  &  & whole period & 0.7278 & 0.7846 & 0.7692 & 0.7175\\
+\nopagebreak
+ &  &  & backwardation & 0.6962 & 0.7854 & 0.7727 & 0.7282\\
+\nopagebreak
+ & \multirow[t]{-6}{*}{\raggedright\arraybackslash energy} & \multirow[t]{-3}{*}{\raggedright\arraybackslash petroleum} & contango & 0.7606 & 0.7856 & 0.7716 & 0.7134\\
+\nopagebreak
+ &  &  & whole period & 0.2167 & 0.5553 & 0.5877 & 0.4721\\
+\nopagebreak
+ &  &  & backwardation & 0.2201 & 0.5418 & 0.6353 & 0.4155\\
+\nopagebreak
+ &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & contango & 0.2145 & 0.5727 & 0.5709 & 0.5035\\
+\nopagebreak
+ &  &  & whole period & 0.2883 & 0.6305 & 0.6704 & 0.5762\\
+\nopagebreak
+ &  &  & backwardation & 0.3070 & 0.6061 & 0.6991 & 0.5386\\
+\nopagebreak
+\multirow[t]{-27}{*}{\raggedright\arraybackslash \textbf{US}} & \multirow[t]{-6}{*}{\raggedright\arraybackslash metals} & \multirow[t]{-3}{*}{\raggedright\arraybackslash precious} & contango & 0.2713 & 0.6591 & 0.6615 & 0.5949\\
+\cmidrule{1-8}\pagebreak[0]
+ &  &  & whole period & 0.4047 & 0.4691 & 0.6536 & 0.4412\\
+\nopagebreak
+ &  &  & backwardation & 0.3987 & 0.4753 & 0.6729 & 0.3954\\
+\nopagebreak
+\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{GB}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & contango & 0.4108 & 0.4652 & 0.6456 & 0.4797\\*
 \end{longtable}
@@
 \newpage
-
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}lllrr}
-\caption{\label{tab:co-movement-picks}This table shows the factor 'picks' for the market as well as the long-short factors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-For each factor and period the twenty four US commodities are regressed against the corresponding factor mimicking portfolio and ranked by $R^{2}$.
-The top eight commodities are selected as 'picks' for the corresponding factor and period.
-The table also shows the proportion of time, for each period, each individual pick lives on both legs (long vs.
-short) of its picking factor.
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor.
-Factors construction details are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
-\toprule
-picking factor & period & pick & long & short\\
-\midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-picking factor & period & pick & long & short\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
- &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Wheat-SRW (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 100\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Heating oil (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybean oil (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Gold (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Palladium (XNYM) & 100\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybean oil (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Wheat-SRW (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 100\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Copper (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybean oil (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Copper (XCEC) & 100\% & 0\%\\
-\nopagebreak
-\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Silver (XCEC) & 100\% & 0\%\\
-\cmidrule{1-5}\pagebreak[0]
- &  & Cattle-feeder (XCME) & 12.28\% & 67.96\%\\
-\nopagebreak
- &  & Cattle-live (XCME) & 16.47\% & 50.3\%\\
-\nopagebreak
- &  & Lean hogs (XCME) & 13.77\% & 58.98\%\\
-\nopagebreak
- &  & Cotton-\#2 (IFUS) & 18.56\% & 46.11\%\\
-\nopagebreak
- &  & Orange juice (IFUS) & 55.39\% & 18.56\%\\
-\nopagebreak
- &  & Gold (XCEC) & 36.83\% & 61.68\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 91.92\% & 2.1\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Silver (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Oats (XCBT) & 97.91\% & 0\%\\
-\nopagebreak
- &  & Cattle-feeder (XCME) & 0\% & 97.49\%\\
-\nopagebreak
- &  & Lean hogs (XCME) & 0\% & 72.38\%\\
-\nopagebreak
- &  & Copper (XCEC) & 28.45\% & 46.44\%\\
-\nopagebreak
- &  & Gold (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Palladium (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 100\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 0\% & 100\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 5.76\% & 46.09\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 52.67\% & 0\%\\
-\nopagebreak
- &  & Copper (XCEC) & 0\% & 81.48\%\\
-\nopagebreak
- &  & Gold (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Palladium (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 100\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Silver (XCEC) & 99.59\% & 0\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 0\% & 62.77\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 34.04\% & 0\%\\
-\nopagebreak
- &  & Wheat-SRW (XCBT) & 0\% & 97.52\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 0\% & 100\%\\
-\nopagebreak
- &  & Gold (XCEC) & 80.14\% & 0\%\\
-\nopagebreak
- &  & Palladium (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 96.81\% & 0\%\\
-\nopagebreak
-\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Silver (XCEC) & 57.45\% & 0\%\\
-\cmidrule{1-5}\pagebreak[0]
- &  & Oats (XCBT) & 17.1\% & 50.3\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 19.71\% & 49.1\%\\
-\nopagebreak
- &  & Cattle-live (XCME) & 12.46\% & 58.68\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 82.61\% & 1.2\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 99.71\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 99.71\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 99.71\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Palladium (XNYM) & 10.14\% & 52.69\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 0.75\% & 80.09\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 87.97\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 92.48\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 92.11\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 92.11\% & 0\%\\
-\nopagebreak
- &  & Gold (XCEC) & 16.54\% & 37.04\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 19.55\% & 31.02\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 49.25\% & 17.13\%\\
-\nopagebreak
- &  & Soybean oil (XCBT) & 10.61\% & 58.38\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 95.45\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 95.45\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 92.05\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 94.7\% & 0\%\\
-\nopagebreak
- &  & Copper (XCEC) & 23.11\% & 35.14\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 51.14\% & 17.84\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Silver (XCEC) & 25.76\% & 34.05\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 14.97\% & 48.33\%\\
-\nopagebreak
- &  & Oats (XCBT) & 19.73\% & 53.53\%\\
-\nopagebreak
- &  & Wheat-SRW (XCBT) & 10.54\% & 43.49\%\\
-\nopagebreak
- &  & Cattle-feeder (XCME) & 26.53\% & 54.65\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 98.64\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 98.64\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 97.28\% & 0\%\\
-\nopagebreak
-\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Heating oil (XNYM) & 97.28\% & 0\%\\
-\cmidrule{1-5}\pagebreak[0]
- &  & Corn-\#2 yellow (XCBT) & 94.52\% & 1.15\%\\
-\nopagebreak
- &  & Lean hogs (XCME) & 43.8\% & 36.68\%\\
-\nopagebreak
- &  & Cotton-\#2 (IFUS) & 77.81\% & 13.18\%\\
-\nopagebreak
- &  & Sugar-\#11 (IFUS) & 25.07\% & 55.87\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 16.43\% & 60.17\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 15.56\% & 33.24\%\\
-\nopagebreak
- &  & Palladium (XNYM) & 0\% & 59.03\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Platinum (XNYM) & 0\% & 89.68\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 17.27\% & 48.18\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 20.45\% & 31.98\%\\
-\nopagebreak
- &  & Cattle-live (XCME) & 19.09\% & 48.18\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 78.18\% & 0\%\\
-\nopagebreak
- &  & Copper (XCEC) & 0\% & 89.88\%\\
-\nopagebreak
- &  & Gold (XCEC) & 0\% & 17\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 0\% & 92.71\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 0\% & 30.77\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 0\% & 82.54\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 0\% & 58.33\%\\
-\nopagebreak
- &  & Lean hogs (XCME) & 69.84\% & 21.83\%\\
-\nopagebreak
- &  & Cotton-\#2 (IFUS) & 38.1\% & 48.02\%\\
-\nopagebreak
- &  & Sugar-\#11 (IFUS) & 34.52\% & 50.79\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 76.59\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 8.33\% & 60.32\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Copper (XCEC) & 0\% & 40.87\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 89.69\% & 6.77\%\\
-\nopagebreak
- &  & Wheat-SRW (XCBT) & 96.91\% & 0\%\\
-\nopagebreak
- &  & Cattle-feeder (XCME) & 17.87\% & 69.55\%\\
-\nopagebreak
- &  & Cattle-live (XCME) & 27.84\% & 60.9\%\\
-\nopagebreak
- &  & Coffee-C (IFUS) & 100\% & 0\%\\
-\nopagebreak
- &  & Lumber (XCME) & 40.89\% & 39.85\%\\
-\nopagebreak
- &  & Sugar-\#11 (IFUS) & 69.07\% & 20.68\%\\
-\nopagebreak
-\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Natural gas (XNYM) & 71.48\% & 17.29\%\\*
-\end{longtable}
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}llrrrr}
-\caption{\label{tab:co-movement-correlations}This table shows the average pairwise correlation amongst factor picks for each factor and period independently.
-The figures are shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor.
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
-\toprule
-picking factor & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-picking factor & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
- & all & 23.68\% & 34.2\% & 50.07\% & 26.13\%\\
-\nopagebreak
- & backwardation & 22.21\% & 36.28\% & 45.4\% & 22.53\%\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{market}} & contango & 25.31\% & 32.6\% & 52.73\% & 29.07\%\\
-\cmidrule{1-6}\pagebreak[0]
- & all & 8.05\% & 22.94\% & 40.1\% & 19.84\%\\
-\nopagebreak
- & backwardation & 8.4\% & 22.48\% & 43.5\% & 16.63\%\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{CHP}} & contango & 7.64\% & 23.6\% & 38.72\% & 22.32\%\\
-\cmidrule{1-6}\pagebreak[0]
- & all & 12.42\% & 32.35\% & 41.96\% & 16.13\%\\
-\nopagebreak
- & backwardation & 11.62\% & 35.44\% & 41.9\% & 14.44\%\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{open interest}} & contango & 12.99\% & 29.69\% & 42.18\% & 17.75\%\\
-\cmidrule{1-6}\pagebreak[0]
- & all & 7.07\% & 23.41\% & 23.15\% & 8.86\%\\
-\nopagebreak
- & backwardation & 5.63\% & 24.56\% & 18.99\% & 8.37\%\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{term structure}} & contango & 8.3\% & 22.66\% & 26.34\% & 9.15\%\\*
-\end{longtable}
-\endgroup{}
-
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}llllrrrr}
-\caption{\label{tab:co-movement-time-reg-picks-facts-picks}This table shows the average time series $R^{2}$ for models where the returns series for the various sets of factor picks are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the picks.
-For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
- &  &  & all & 32.72\% & 42.33\% & 56.22\% & 36.48\%\\
-\nopagebreak
- &  &  & backwardation & 31.67\% & 43.85\% & 52.22\% & 34.13\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 33.87\% & 41.14\% & 58.62\% & 38.39\%\\
-\nopagebreak
- &  &  & all & 5.61\% & 12.44\% & 6.89\% & 6.83\%\\
-\nopagebreak
- &  &  & backwardation & 5.02\% & 11.4\% & 7.33\% & 5.58\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 7.73\% & 15.34\% & 8.2\% & 9.49\%\\
-\nopagebreak
- &  &  & all & 17.09\% & 27.87\% & 40.38\% & 17.61\%\\
-\nopagebreak
- &  &  & backwardation & 17.36\% & 26.97\% & 33.21\% & 13.37\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 17.39\% & 29.12\% & 44.06\% & 21.69\%\\
-\nopagebreak
- &  &  & all & 16.49\% & 21.39\% & 35.95\% & 16.37\%\\
-\nopagebreak
- &  &  & backwardation & 13.19\% & 25.78\% & 32.18\% & 12.42\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 20.53\% & 18.68\% & 39.1\% & 20.49\%\\
-\nopagebreak
- &  &  & all & 23.2\% & 7.78\% & 11.68\% & 19.69\%\\
-\nopagebreak
- &  &  & backwardation & 24.03\% & 8.65\% & 8.56\% & 19.29\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 22.67\% & 7.38\% & 14.32\% & 20.15\%\\
-\nopagebreak
- &  &  & all & 25.03\% & 26.41\% & 39.29\% & 27.68\%\\
-\nopagebreak
- &  &  & backwardation & 26.05\% & 28.34\% & 34.39\% & 27.3\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 24.42\% & 24.86\% & 41.79\% & 28.25\%\\
-\nopagebreak
- &  &  & all & 23.67\% & 22.99\% & 34.48\% & 17.13\%\\
-\nopagebreak
- &  &  & backwardation & 21.81\% & 26.13\% & 33.14\% & 14.96\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 26.47\% & 20.67\% & 35.71\% & 19.57\%\\
-\nopagebreak
- &  &  & all & 5.92\% & 7.26\% & 4.29\% & 1.98\%\\
-\nopagebreak
- &  &  & backwardation & 6.44\% & 7.24\% & 9.11\% & 1.51\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 5.52\% & 9.23\% & 3.01\% & 2.81\%\\
-\nopagebreak
- &  &  & all & 11.61\% & 24.74\% & 35.76\% & 17.54\%\\
-\nopagebreak
- &  &  & backwardation & 10.72\% & 27.25\% & 33.61\% & 18.51\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 12.92\% & 23.08\% & 37.43\% & 17.53\%\\
-\nopagebreak
- &  &  & all & 16.22\% & 24.13\% & 35.98\% & 20.6\%\\
-\nopagebreak
- &  &  & backwardation & 17.07\% & 25.62\% & 30.3\% & 16.38\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 16.15\% & 24.36\% & 39.28\% & 23.56\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 18.62\% & 38.1\% & 47.61\% & 28.42\%\\
-\nopagebreak
- &  &  & backwardation & 19.04\% & 36.9\% & 50.48\% & 25.17\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 18.39\% & 39.54\% & 46.48\% & 30.9\%\\
-\nopagebreak
- &  &  & all & 7.19\% & 21.38\% & 13\% & 14.34\%\\
-\nopagebreak
- &  &  & backwardation & 6.78\% & 19.58\% & 12.57\% & 18.44\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 8.32\% & 23.66\% & 13.51\% & 14.5\%\\
-\nopagebreak
- &  &  & all & 10.45\% & 31.09\% & 38.06\% & 24.09\%\\
-\nopagebreak
- &  &  & backwardation & 11.18\% & 30.55\% & 41.19\% & 22.78\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 10.21\% & 31.88\% & 36.81\% & 25.3\%\\
-\nopagebreak
- &  &  & all & 8.27\% & 9.84\% & 15.7\% & 10.44\%\\
-\nopagebreak
- &  &  & backwardation & 8.12\% & 9.87\% & 16.25\% & 15.17\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 9.33\% & 9.98\% & 15.57\% & 11.21\%\\
-\nopagebreak
- &  &  & all & 1.47\% & 4.76\% & 9.16\% & 11.59\%\\
-\nopagebreak
- &  &  & backwardation & 2.34\% & 4.23\% & 7.98\% & 11.57\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1\% & 5.64\% & 10.58\% & 11.9\%\\
-\nopagebreak
- &  &  & all & 6.27\% & 24.94\% & 25.22\% & 12.58\%\\
-\nopagebreak
- &  &  & backwardation & 6.82\% & 26.16\% & 19.14\% & 12.47\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 6.42\% & 24.13\% & 28.34\% & 12.75\%\\
-\nopagebreak
- &  &  & all & 5.59\% & 13.44\% & 35.65\% & 14.08\%\\
-\nopagebreak
- &  &  & backwardation & 6.49\% & 16.16\% & 39.06\% & 12.01\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 5.2\% & 11.43\% & 34.37\% & 16.51\%\\
-\nopagebreak
- &  &  & all & 3.5\% & 5.28\% & 8.11\% & 5.96\%\\
-\nopagebreak
- &  &  & backwardation & 3.79\% & 8.13\% & 9.48\% & 6.88\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 4.9\% & 4.01\% & 7.64\% & 5.86\%\\
-\nopagebreak
- &  &  & all & 7.45\% & 9.78\% & 15.63\% & 12.48\%\\
-\nopagebreak
- &  &  & backwardation & 7.12\% & 9.85\% & 15.97\% & 11.94\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.85\% & 10.75\% & 15.59\% & 13.31\%\\
-\nopagebreak
- &  &  & all & 6.26\% & 15.74\% & 28.56\% & 13.03\%\\
-\nopagebreak
- &  &  & backwardation & 6.51\% & 19.46\% & 28.59\% & 10.21\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 6.58\% & 13.22\% & 28.76\% & 17.2\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 28.43\% & 41.66\% & 49.79\% & 29.2\%\\
-\nopagebreak
- &  &  & backwardation & 28\% & 44.29\% & 49.09\% & 27.73\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 28.84\% & 39.55\% & 50.49\% & 30.43\%\\
-\nopagebreak
- &  &  & all & 9.58\% & 14.48\% & 11.28\% & 9.83\%\\
-\nopagebreak
- &  &  & backwardation & 9.81\% & 13.64\% & 11.15\% & 10.3\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 9.47\% & 16.17\% & 11.62\% & 11.76\%\\
-\nopagebreak
- &  &  & all & 12.63\% & 27.21\% & 32.29\% & 18.56\%\\
-\nopagebreak
- &  &  & backwardation & 12.41\% & 28.26\% & 35.25\% & 15.67\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 13.06\% & 26.85\% & 31.22\% & 20.78\%\\
-\nopagebreak
- &  &  & all & 10.71\% & 23.23\% & 16.94\% & 8.09\%\\
-\nopagebreak
- &  &  & backwardation & 9.72\% & 24.06\% & 16.56\% & 13.98\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 11.79\% & 23.43\% & 17.35\% & 9.21\%\\
-\nopagebreak
- &  &  & all & 18.25\% & 15.83\% & 9.45\% & 11.79\%\\
-\nopagebreak
- &  &  & backwardation & 19.96\% & 14.24\% & 6.39\% & 12.24\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 16.97\% & 17.33\% & 11.49\% & 11.87\%\\
-\nopagebreak
- &  &  & all & 24.83\% & 30.24\% & 33.8\% & 13.61\%\\
-\nopagebreak
- &  &  & backwardation & 25.07\% & 31.83\% & 26.7\% & 13.11\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 24.77\% & 29.24\% & 37.38\% & 14.3\%\\
-\nopagebreak
- &  &  & all & 8.32\% & 17.57\% & 31.68\% & 11.76\%\\
-\nopagebreak
- &  &  & backwardation & 7.65\% & 17.99\% & 32.14\% & 11.62\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 9.17\% & 17.62\% & 31.72\% & 12.44\%\\
-\nopagebreak
- &  &  & all & 2.3\% & 6.95\% & 7.93\% & 3.63\%\\
-\nopagebreak
- &  &  & backwardation & 3.56\% & 5.35\% & 10.01\% & 5.48\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.61\% & 8.26\% & 7.22\% & 3.24\%\\
-\nopagebreak
- &  &  & all & 7.54\% & 20.81\% & 17.64\% & 12.3\%\\
-\nopagebreak
- &  &  & backwardation & 7.45\% & 22.37\% & 16.44\% & 14.08\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 7.84\% & 19.88\% & 18.58\% & 11.56\%\\
-\nopagebreak
- &  &  & all & 8.85\% & 19.61\% & 32.42\% & 11.02\%\\
-\nopagebreak
- &  &  & backwardation & 12.38\% & 24.66\% & 32.66\% & 7.46\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 7.69\% & 16.26\% & 32.72\% & 14.76\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 20\% & 33.71\% & 33.64\% & 19.37\%\\
-\nopagebreak
- &  &  & backwardation & 18.65\% & 35.1\% & 29.47\% & 19.58\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 21.25\% & 32.72\% & 36.91\% & 19.29\%\\
-\nopagebreak
- &  &  & all & 4.68\% & 7.97\% & 8.75\% & 3.74\%\\
-\nopagebreak
- &  &  & backwardation & 4.7\% & 7.11\% & 10.38\% & 8.99\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 5.19\% & 9.3\% & 8.01\% & 3.69\%\\
-\nopagebreak
- &  &  & all & 11.93\% & 28.13\% & 22.6\% & 7.81\%\\
-\nopagebreak
- &  &  & backwardation & 14.34\% & 27.9\% & 21.19\% & 8.65\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 10.77\% & 28.61\% & 24.63\% & 8.45\%\\
-\nopagebreak
- &  &  & all & 5.54\% & 9.15\% & 13.2\% & 5.52\%\\
-\nopagebreak
- &  &  & backwardation & 4.6\% & 8.86\% & 12.38\% & 11.89\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 7.11\% & 10.4\% & 14.58\% & 5.3\%\\
-\nopagebreak
- &  &  & all & 8.62\% & 8.02\% & 5.96\% & 10.47\%\\
-\nopagebreak
- &  &  & backwardation & 9.54\% & 7.27\% & 6.5\% & 10.93\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 7.77\% & 8.87\% & 6.99\% & 10.46\%\\
-\nopagebreak
- &  &  & all & 13.53\% & 15.51\% & 16.65\% & 12.44\%\\
-\nopagebreak
- &  &  & backwardation & 13.3\% & 16.33\% & 12.47\% & 12.45\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 13.92\% & 15.23\% & 20.05\% & 12.48\%\\
-\nopagebreak
- &  &  & all & 5.94\% & 14.55\% & 14.78\% & 7.79\%\\
-\nopagebreak
- &  &  & backwardation & 5.61\% & 16.34\% & 13.08\% & 8.88\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 6.29\% & 13.09\% & 17.1\% & 7.81\%\\
-\nopagebreak
- &  &  & all & 5.1\% & 8.38\% & 8.8\% & 6.83\%\\
-\nopagebreak
- &  &  & backwardation & 7.27\% & 6.31\% & 8.91\% & 9.15\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 5.15\% & 10.07\% & 9.39\% & 5.96\%\\
-\nopagebreak
- &  &  & all & 7.6\% & 12.13\% & 11.03\% & 7.86\%\\
-\nopagebreak
- &  &  & backwardation & 7.13\% & 12.38\% & 10.13\% & 9.57\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.38\% & 12.17\% & 12.68\% & 7.96\%\\
-\nopagebreak
- &  &  & all & 6.03\% & 16.11\% & 20.26\% & 9.96\%\\
-\nopagebreak
- &  &  & backwardation & 9.07\% & 15.15\% & 15.34\% & 10.19\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 6.06\% & 17.5\% & 24.31\% & 10.3\%\\*
-\end{longtable}
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}llllrrrr}
-\caption{\label{tab:co-movement-time-reg-US-facts-picks}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities.
-For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
- &  &  & all & 11.67\% & 21.24\% & 28.16\% & 14.85\%\\
-\nopagebreak
- &  &  & backwardation & 11.34\% & 22.98\% & 26.68\% & 13.36\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 12.09\% & 19.79\% & 29.81\% & 16.31\%\\
-\nopagebreak
- &  &  & all & 1.96\% & 5.44\% & 2.52\% & 3.24\%\\
-\nopagebreak
- &  &  & backwardation & 1.83\% & 4.93\% & 3.16\% & 4.06\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 2.85\% & 6.82\% & 2.83\% & 3.73\%\\
-\nopagebreak
- &  &  & all & 6.64\% & 13.42\% & 18.81\% & 7.99\%\\
-\nopagebreak
- &  &  & backwardation & 6.99\% & 13.31\% & 16.43\% & 7.93\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 6.6\% & 13.78\% & 20.61\% & 9.08\%\\
-\nopagebreak
- &  &  & all & 6.12\% & 10.75\% & 18.35\% & 7.61\%\\
-\nopagebreak
- &  &  & backwardation & 4.75\% & 13.22\% & 16.28\% & 5.87\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 7.85\% & 9.05\% & 20.59\% & 9.7\%\\
-\nopagebreak
- &  &  & all & 8.25\% & 3.72\% & 4.49\% & 6.9\%\\
-\nopagebreak
- &  &  & backwardation & 8.64\% & 4.35\% & 3.3\% & 6.81\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 8.08\% & 3.44\% & 5.7\% & 7.11\%\\
-\nopagebreak
- &  &  & all & 8.51\% & 12.69\% & 18.26\% & 9.71\%\\
-\nopagebreak
- &  &  & backwardation & 8.85\% & 13.94\% & 17.03\% & 9.45\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.4\% & 11.82\% & 19.42\% & 10.13\%\\
-\nopagebreak
- &  &  & all & 9.47\% & 11.69\% & 17.99\% & 8.18\%\\
-\nopagebreak
- &  &  & backwardation & 8.98\% & 14.42\% & 17.72\% & 6.81\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 10.39\% & 9.76\% & 18.66\% & 9.79\%\\
-\nopagebreak
- &  &  & all & 2.1\% & 3.26\% & 1.76\% & 0.79\%\\
-\nopagebreak
- &  &  & backwardation & 2.31\% & 3.4\% & 4.15\% & 0.77\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.06\% & 4.12\% & 1.21\% & 1.05\%\\
-\nopagebreak
- &  &  & all & 4.51\% & 13.46\% & 17.75\% & 7.25\%\\
-\nopagebreak
- &  &  & backwardation & 4.26\% & 15.48\% & 17.21\% & 7.69\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 5.01\% & 12.06\% & 18.8\% & 7.44\%\\
-\nopagebreak
- &  &  & all & 5.69\% & 11.42\% & 17.51\% & 7.68\%\\
-\nopagebreak
- &  &  & backwardation & 5.91\% & 12.62\% & 15.24\% & 6.11\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 5.87\% & 11.09\% & 19.48\% & 8.94\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 6.77\% & 16.67\% & 25.41\% & 12.77\%\\
-\nopagebreak
- &  &  & backwardation & 6.85\% & 17.81\% & 24.61\% & 10.81\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 6.84\% & 15.98\% & 26.51\% & 14.52\%\\
-\nopagebreak
- &  &  & all & 2.54\% & 8.73\% & 4.39\% & 5.06\%\\
-\nopagebreak
- &  &  & backwardation & 2.46\% & 8.28\% & 4.36\% & 6.61\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 3.04\% & 9.5\% & 4.67\% & 5.16\%\\
-\nopagebreak
- &  &  & all & 3.9\% & 12.72\% & 17.36\% & 9.4\%\\
-\nopagebreak
- &  &  & backwardation & 4.13\% & 13.64\% & 19.11\% & 8.14\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4\% & 12.3\% & 16.6\% & 10.8\%\\
-\nopagebreak
- &  &  & all & 2.83\% & 3.82\% & 7.51\% & 4.17\%\\
-\nopagebreak
- &  &  & backwardation & 2.82\% & 3.72\% & 7.27\% & 6.11\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.31\% & 4.19\% & 7.95\% & 4.3\%\\
-\nopagebreak
- &  &  & all & 0.54\% & 1.68\% & 4.1\% & 4.1\%\\
-\nopagebreak
- &  &  & backwardation & 0.9\% & 1.54\% & 2.96\% & 4.14\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.38\% & 2.27\% & 5.48\% & 4.26\%\\
-\nopagebreak
- &  &  & all & 2.36\% & 10.1\% & 15.23\% & 4.56\%\\
-\nopagebreak
- &  &  & backwardation & 2.57\% & 10.72\% & 10.19\% & 4.46\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 2.45\% & 9.77\% & 18.64\% & 4.71\%\\
-\nopagebreak
- &  &  & all & 1.94\% & 6.35\% & 17.65\% & 6.96\%\\
-\nopagebreak
- &  &  & backwardation & 2.25\% & 8.71\% & 17.99\% & 5.62\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 1.88\% & 4.71\% & 17.98\% & 8.46\%\\
-\nopagebreak
- &  &  & all & 1.31\% & 1.97\% & 2.83\% & 2.2\%\\
-\nopagebreak
- &  &  & backwardation & 1.59\% & 2.9\% & 3.32\% & 2.55\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1.85\% & 1.65\% & 2.74\% & 2.37\%\\
-\nopagebreak
- &  &  & all & 2.62\% & 4.52\% & 8.05\% & 5.5\%\\
-\nopagebreak
- &  &  & backwardation & 2.65\% & 5.03\% & 7.26\% & 5.11\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 3.08\% & 4.51\% & 8.86\% & 6.15\%\\
-\nopagebreak
- &  &  & all & 2.43\% & 7\% & 15.51\% & 6.71\%\\
-\nopagebreak
- &  &  & backwardation & 2.49\% & 9.01\% & 13.83\% & 4.78\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.94\% & 5.61\% & 16.98\% & 9.57\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 10.6\% & 18.43\% & 26.36\% & 12.03\%\\
-\nopagebreak
- &  &  & backwardation & 10.25\% & 20.18\% & 25.13\% & 10.91\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 11.05\% & 17.11\% & 27.83\% & 13.17\%\\
-\nopagebreak
- &  &  & all & 4\% & 5.34\% & 4.54\% & 3.71\%\\
-\nopagebreak
- &  &  & backwardation & 4.1\% & 4.98\% & 4.37\% & 3.61\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 4.02\% & 6.14\% & 4.86\% & 4.74\%\\
-\nopagebreak
- &  &  & all & 6.78\% & 13.48\% & 18.66\% & 7.42\%\\
-\nopagebreak
- &  &  & backwardation & 6.63\% & 14.34\% & 20.18\% & 5.9\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 7.12\% & 13.11\% & 18.16\% & 8.77\%\\
-\nopagebreak
- &  &  & all & 3.94\% & 9.11\% & 7.49\% & 3.11\%\\
-\nopagebreak
- &  &  & backwardation & 3.56\% & 9.31\% & 7.08\% & 5.61\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 4.45\% & 9.44\% & 8.05\% & 3.32\%\\
-\nopagebreak
- &  &  & all & 6.4\% & 5.64\% & 3.37\% & 4.11\%\\
-\nopagebreak
- &  &  & backwardation & 6.93\% & 5.3\% & 2.53\% & 4.35\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 6.07\% & 6.09\% & 4.25\% & 4.1\%\\
-\nopagebreak
- &  &  & all & 8.48\% & 12.35\% & 15.81\% & 4.76\%\\
-\nopagebreak
- &  &  & backwardation & 8.5\% & 13.24\% & 11.7\% & 4.54\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.63\% & 11.82\% & 18.57\% & 5.08\%\\
-\nopagebreak
- &  &  & all & 4.07\% & 12.5\% & 19.46\% & 4.99\%\\
-\nopagebreak
- &  &  & backwardation & 3.64\% & 13.52\% & 18.93\% & 4.95\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 4.64\% & 11.82\% & 20.29\% & 5.39\%\\
-\nopagebreak
- &  &  & all & 0.83\% & 2.54\% & 3.13\% & 1.45\%\\
-\nopagebreak
- &  &  & backwardation & 1.3\% & 2.22\% & 3.71\% & 2.52\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1.13\% & 2.95\% & 3.02\% & 1.16\%\\
-\nopagebreak
- &  &  & all & 3.09\% & 7.65\% & 8.04\% & 5.26\%\\
-\nopagebreak
- &  &  & backwardation & 2.8\% & 8.53\% & 7.11\% & 5.96\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 3.73\% & 7.22\% & 9\% & 5.21\%\\
-\nopagebreak
- &  &  & all & 3.55\% & 9.48\% & 16.63\% & 4.56\%\\
-\nopagebreak
- &  &  & backwardation & 4.8\% & 12.03\% & 15.62\% & 3.13\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.21\% & 7.83\% & 17.77\% & 6.32\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 9.13\% & 18.37\% & 25.17\% & 8.95\%\\
-\nopagebreak
- &  &  & backwardation & 8.79\% & 20.14\% & 22.77\% & 8.19\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 9.55\% & 16.99\% & 27.12\% & 10.02\%\\
-\nopagebreak
- &  &  & all & 1.98\% & 3.42\% & 3.3\% & 1.38\%\\
-\nopagebreak
- &  &  & backwardation & 1.89\% & 3.08\% & 3.79\% & 3.4\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 2.33\% & 4.07\% & 3.17\% & 1.32\%\\
-\nopagebreak
- &  &  & all & 4.8\% & 13.48\% & 15.65\% & 3.14\%\\
-\nopagebreak
- &  &  & backwardation & 5.63\% & 14.34\% & 13.9\% & 3.23\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.55\% & 13.11\% & 17.32\% & 3.58\%\\
-\nopagebreak
- &  &  & all & 2.58\% & 5.81\% & 7.05\% & 2.51\%\\
-\nopagebreak
- &  &  & backwardation & 1.91\% & 5.91\% & 5.92\% & 5.04\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.55\% & 6.2\% & 8.3\% & 2.29\%\\
-\nopagebreak
- &  &  & all & 3.93\% & 3.97\% & 2.83\% & 3.6\%\\
-\nopagebreak
- &  &  & backwardation & 4.31\% & 3.56\% & 2.88\% & 3.87\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 3.67\% & 4.63\% & 3.53\% & 3.57\%\\
-\nopagebreak
- &  &  & all & 6.42\% & 8.62\% & 12.51\% & 4.45\%\\
-\nopagebreak
- &  &  & backwardation & 6.24\% & 9.01\% & 9.32\% & 4.44\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 6.73\% & 8.59\% & 14.98\% & 4.53\%\\
-\nopagebreak
- &  &  & all & 2.49\% & 8.49\% & 10.4\% & 3.46\%\\
-\nopagebreak
- &  &  & backwardation & 2.6\% & 10.34\% & 8.32\% & 3.83\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.58\% & 6.84\% & 12.73\% & 3.64\%\\
-\nopagebreak
- &  &  & all & 2.17\% & 3.38\% & 3.69\% & 2.53\%\\
-\nopagebreak
- &  &  & backwardation & 3.39\% & 2.69\% & 3.48\% & 3.52\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.06\% & 4.03\% & 4.16\% & 2.16\%\\
-\nopagebreak
- &  &  & all & 3.91\% & 5.88\% & 5.59\% & 3.55\%\\
-\nopagebreak
- &  &  & backwardation & 3.65\% & 6.37\% & 4.61\% & 3.98\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.38\% & 5.7\% & 6.74\% & 3.94\%\\
-\nopagebreak
- &  &  & all & 2.44\% & 7.8\% & 12.81\% & 3.63\%\\
-\nopagebreak
- &  &  & backwardation & 4.14\% & 8.02\% & 9.12\% & 3.54\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.27\% & 8.05\% & 15.82\% & 4.21\%\\*
-\end{longtable}
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}llllrrrr}
-\caption{\label{tab:co-movement-time-reg-UK-facts-picks}This table shows the average time series $R^{2}$ for models where the returns series for the six UK metals are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the six UK metals.
-For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
- &  &  & all & 0.25\% & 10.17\% & 31.69\% & 11.52\%\\
-\nopagebreak
- &  &  & backwardation & 0.32\% & 11.66\% & 31.95\% & 8.64\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 0.3\% & 9.16\% & 31.72\% & 14.26\%\\
-\nopagebreak
- &  &  & all & 0.06\% & 3.39\% & 0.42\% & 0.38\%\\
-\nopagebreak
- &  &  & backwardation & 0.36\% & 1.84\% & 0.26\% & 0.25\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.05\% & 5.36\% & 0.66\% & 0.82\%\\
-\nopagebreak
- &  &  & all & 0.15\% & 13.12\% & 18.65\% & 5.45\%\\
-\nopagebreak
- &  &  & backwardation & 0.58\% & 12.24\% & 18.24\% & 5.07\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.1\% & 14.17\% & 19.06\% & 5.98\%\\
-\nopagebreak
- &  &  & all & 0.05\% & 3\% & 24.38\% & 16.07\%\\
-\nopagebreak
- &  &  & backwardation & 0.11\% & 4.23\% & 14.79\% & 6.56\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.06\% & 2.24\% & 32.21\% & 26.59\%\\
-\nopagebreak
- &  &  & all & 0.04\% & 0.83\% & 1.45\% & 0.07\%\\
-\nopagebreak
- &  &  & backwardation & 0.05\% & 1.4\% & 0.07\% & 0.03\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.2\% & 0.55\% & 3.21\% & 0.15\%\\
-\nopagebreak
- &  &  & all & 0.11\% & 6.59\% & 17.68\% & 2.57\%\\
-\nopagebreak
- &  &  & backwardation & 0.17\% & 7.76\% & 17.27\% & 1.58\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.17\% & 5.85\% & 18.2\% & 3.57\%\\
-\nopagebreak
- &  &  & all & 0.05\% & 3.99\% & 17.16\% & 6.86\%\\
-\nopagebreak
- &  &  & backwardation & 0.39\% & 4.23\% & 19.91\% & 3.79\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.09\% & 3.85\% & 15.74\% & 10.3\%\\
-\nopagebreak
- &  &  & all & 0.1\% & 1.82\% & 0.98\% & 0.17\%\\
-\nopagebreak
- &  &  & backwardation & 0.42\% & 1.22\% & 0.04\% & 0.35\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.06\% & 2.64\% & 2.2\% & 0.11\%\\
-\nopagebreak
- &  &  & all & 0.26\% & 1.85\% & 11.63\% & 2.82\%\\
-\nopagebreak
- &  &  & backwardation & 1.06\% & 2.98\% & 11.17\% & 1.53\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.03\% & 1.24\% & 12.09\% & 4.32\%\\
-\nopagebreak
- &  &  & all & 0.03\% & 5.78\% & 20.53\% & 3.27\%\\
-\nopagebreak
- &  &  & backwardation & 0.1\% & 5.75\% & 18.66\% & 2.59\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.12\% & 6.04\% & 21.67\% & 4.01\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 1.55\% & 20.13\% & 34.54\% & 7.43\%\\
-\nopagebreak
- &  &  & backwardation & 1.53\% & 20.93\% & 35.18\% & 5.21\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 1.75\% & 19.83\% & 34.3\% & 9.41\%\\
-\nopagebreak
- &  &  & all & 0.07\% & 5.5\% & 0.47\% & 2.12\%\\
-\nopagebreak
- &  &  & backwardation & 0.12\% & 4.05\% & 1.15\% & 1.4\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.09\% & 7.36\% & 0.25\% & 2.78\%\\
-\nopagebreak
- &  &  & all & 1.02\% & 10.98\% & 21.81\% & 8.99\%\\
-\nopagebreak
- &  &  & backwardation & 0.77\% & 10.77\% & 25.33\% & 5.57\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 1.36\% & 11.39\% & 19.89\% & 12.11\%\\
-\nopagebreak
- &  &  & all & 0.41\% & 0.25\% & 6.19\% & 0.19\%\\
-\nopagebreak
- &  &  & backwardation & 0.21\% & 0.47\% & 5.55\% & 0.24\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.61\% & 0.22\% & 6.67\% & 0.2\%\\
-\nopagebreak
- &  &  & all & 0.03\% & 0.64\% & 0.06\% & 0.27\%\\
-\nopagebreak
- &  &  & backwardation & 0.21\% & 0.06\% & 1.07\% & 0.12\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.08\% & 1.68\% & 0.18\% & 1.33\%\\
-\nopagebreak
- &  &  & all & 0.28\% & 10.41\% & 15.26\% & 0.52\%\\
-\nopagebreak
- &  &  & backwardation & 0.39\% & 10.56\% & 10.18\% & 0.82\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.34\% & 10.47\% & 18.21\% & 0.38\%\\
-\nopagebreak
- &  &  & all & 0.31\% & 8.77\% & 29.79\% & 4.53\%\\
-\nopagebreak
- &  &  & backwardation & 0.25\% & 12.85\% & 30.49\% & 1.57\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.49\% & 5.85\% & 29.59\% & 8.33\%\\
-\nopagebreak
- &  &  & all & 0.05\% & 4.73\% & 0.83\% & 0.6\%\\
-\nopagebreak
- &  &  & backwardation & 0.1\% & 4.5\% & 0.6\% & 1.11\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.27\% & 5.11\% & 0.95\% & 0.31\%\\
-\nopagebreak
- &  &  & all & 0.32\% & 1.38\% & 5.13\% & 0.65\%\\
-\nopagebreak
- &  &  & backwardation & 0.2\% & 1.98\% & 4.85\% & 0.44\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.58\% & 1.03\% & 5.35\% & 0.86\%\\
-\nopagebreak
- &  &  & all & 0.26\% & 19.23\% & 18.98\% & 3.91\%\\
-\nopagebreak
- &  &  & backwardation & 0.48\% & 21.81\% & 17.8\% & 4.62\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.22\% & 17.21\% & 19.65\% & 3.4\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 0.31\% & 8.13\% & 34.43\% & 3.37\%\\
-\nopagebreak
- &  &  & backwardation & 0.35\% & 9.97\% & 35.43\% & 1.72\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 0.39\% & 6.8\% & 34.06\% & 5.08\%\\
-\nopagebreak
- &  &  & all & 0.02\% & 1.39\% & 0.15\% & 1.38\%\\
-\nopagebreak
- &  &  & backwardation & 0.06\% & 0.83\% & 0.45\% & 0.45\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.07\% & 2.07\% & 0.11\% & 2.46\%\\
-\nopagebreak
- &  &  & all & 0.11\% & 11.35\% & 19.64\% & 2.84\%\\
-\nopagebreak
- &  &  & backwardation & 0.29\% & 11.19\% & 23.58\% & 1.06\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.07\% & 11.68\% & 17.62\% & 4.84\%\\
-\nopagebreak
- &  &  & all & 0.15\% & 1.41\% & 5.91\% & 0.21\%\\
-\nopagebreak
- &  &  & backwardation & 0.17\% & 1.89\% & 5.05\% & 0.25\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.24\% & 1.11\% & 6.54\% & 0.2\%\\
-\nopagebreak
- &  &  & all & 0.04\% & 0.37\% & 0.03\% & 0.16\%\\
-\nopagebreak
- &  &  & backwardation & 0.05\% & 0.3\% & 0.33\% & 0.46\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.15\% & 0.46\% & 0.13\% & 0.09\%\\
-\nopagebreak
- &  &  & all & 0.2\% & 5.54\% & 15.97\% & 0.62\%\\
-\nopagebreak
- &  &  & backwardation & 0.14\% & 6.38\% & 12.59\% & 0.89\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.38\% & 5.01\% & 17.83\% & 0.53\%\\
-\nopagebreak
- &  &  & all & 0.14\% & 7.03\% & 30.65\% & 0.26\%\\
-\nopagebreak
- &  &  & backwardation & 0.35\% & 7.6\% & 30.31\% & 0.07\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.08\% & 6.65\% & 30.96\% & 0.9\%\\
-\nopagebreak
- &  &  & all & 0.06\% & 0.1\% & 1.96\% & 0.05\%\\
-\nopagebreak
- &  &  & backwardation & 0.31\% & 0.2\% & 1.75\% & 0.12\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.07\% & 0.15\% & 2.05\% & 0.06\%\\
-\nopagebreak
- &  &  & all & 0.19\% & 1.2\% & 4.58\% & 1.01\%\\
-\nopagebreak
- &  &  & backwardation & 0.7\% & 2.21\% & 4.31\% & 0.29\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.06\% & 0.69\% & 4.78\% & 2.14\%\\
-\nopagebreak
- &  &  & all & 0.07\% & 3.46\% & 22.01\% & 0.93\%\\
-\nopagebreak
- &  &  & backwardation & 0.14\% & 4.11\% & 21.24\% & 0.08\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.08\% & 3.05\% & 22.44\% & 2.18\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 0.75\% & 15.9\% & 28.49\% & 1.27\%\\
-\nopagebreak
- &  &  & backwardation & 0.59\% & 17.08\% & 27.92\% & 0.43\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 0.94\% & 15.1\% & 28.9\% & 2.52\%\\
-\nopagebreak
- &  &  & all & 0.04\% & 0.34\% & 0.03\% & 0.03\%\\
-\nopagebreak
- &  &  & backwardation & 0.09\% & 0.33\% & 0.06\% & 0.11\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.03\% & 0.46\% & 0.05\% & 0.11\%\\
-\nopagebreak
- &  &  & all & 0.68\% & 11.35\% & 10.54\% & 0.44\%\\
-\nopagebreak
- &  &  & backwardation & 0.4\% & 11.19\% & 8.88\% & 0.57\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 1\% & 11.68\% & 11.43\% & 0.34\%\\
-\nopagebreak
- &  &  & all & 0.34\% & 6.03\% & 5.82\% & 0.25\%\\
-\nopagebreak
- &  &  & backwardation & 0.18\% & 6.06\% & 3.33\% & 0.13\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.53\% & 6.1\% & 7.87\% & 0.4\%\\
-\nopagebreak
- &  &  & all & 0.05\% & 0.08\% & 0.27\% & 0.07\%\\
-\nopagebreak
- &  &  & backwardation & 0.03\% & 0.13\% & 0.05\% & 0.51\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.26\% & 0.33\% & 0.67\% & 0.25\%\\
-\nopagebreak
- &  &  & all & 0.38\% & 3.41\% & 11.21\% & 0.29\%\\
-\nopagebreak
- &  &  & backwardation & 0.16\% & 3.72\% & 7.67\% & 0.6\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.75\% & 3.24\% & 13.44\% & 0.18\%\\
-\nopagebreak
- &  &  & all & 0.19\% & 7.89\% & 11.78\% & 0.3\%\\
-\nopagebreak
- &  &  & backwardation & 0.34\% & 10.15\% & 8.1\% & 0.07\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.13\% & 6.06\% & 15.31\% & 1.33\%\\
-\nopagebreak
- &  &  & all & 0.05\% & 2.34\% & 1.67\% & 0.3\%\\
-\nopagebreak
- &  &  & backwardation & 0.09\% & 1.07\% & 0.86\% & 0.35\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.04\% & 3.61\% & 2.43\% & 0.31\%\\
-\nopagebreak
- &  &  & all & 0.29\% & 0.88\% & 2.66\% & 0.92\%\\
-\nopagebreak
- &  &  & backwardation & 0.44\% & 1.81\% & 1.5\% & 0.44\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.22\% & 0.44\% & 3.64\% & 1.65\%\\
-\nopagebreak
- &  &  & all & 0.09\% & 13.93\% & 11.04\% & 0.17\%\\
-\nopagebreak
- &  &  & backwardation & 0.08\% & 10.91\% & 6.36\% & 0.06\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.11\% & 16.59\% & 14.67\% & 0.6\%\\*
-\end{longtable}
-\endgroup{}
-
-\restoregeometry\newpage
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-baker_financialisation_2014}{}}%
-Baker, S.D., 2014. \href{https://doi.org/10.2139/ssrn.2348333}{The financialization of storable commodities} (SSRN Scholarly Paper No. ID 2348333). Social Science Research Network, Rochester, NY.
+\leavevmode\vadjust pre{\hypertarget{ref-baker_financialization_2021}{}}%
+Baker, S.D., 2021. \href{https://doi.org/10.1287/mnsc.2019.3445}{The financialization of storable commodities}. Management Science 67, 471--499.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-basu_definancialisation}{}}%
-Basu, D., Bauthéac, O., 2021. Commodity definancialisation. Working paper.
+Basu, D., Bauthéac, O., 2024. Commodity definancialisation. Working paper.
 
@@
 Bohl, M.T., Stephan, P.M., 2013.
-\href{https://doi.org/10.1017/S1074070800005150}{Does futures speculation destabilize spot prices?
+\href{https://doi.org/10.1017/s1074070800005150}{Does futures speculation destabilize spot prices?
 New evidence for commodity markets}.
@@
 Brunetti, C., Büyükşahin, B., Harris, J.H., 2016.
-\href{https://doi.org/10.1017/S0022109016000569}{Speculators, prices, and market volatility}.
+\href{https://doi.org/10.1017/s0022109016000569}{Speculators, prices, and market volatility}.
 Journal of Financial and Quantitative Analysis 51, 1545--1574.
@@
 Christoffersen, P., Lunde, A., Olesen, K.V., 2014.
-\href{https://doi.org/10.1017/S0022109018000765}{Factor structure in commodity futures return and volatility}.
+\href{https://doi.org/10.1017/s0022109018000765}{Factor structure in commodity futures return and volatility}.
 Journal of Financial and Quantitative Analysis 1--74.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-duffie_challenges_2014}{}}%
-Duffie, D., 2014. \href{https://doi.org/10.1086/677836}{Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs}. The Journal of Legal Studies 43, S173--S182.
+Duffie, D., 2014. \href{https://doi.org/10.1086/677836}{Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs}. The Journal of Legal Studies 43, S173--s182.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-fama_common_1993}{}}%
-Fama, E.F., French, K.R., 1993. \href{https://doi.org/10.1016/0304-405X(93)90023-5}{Common risk factors in the returns on stocks and bonds}. Journal of Financial Economics 33, 3--56.
+Fama, E.F., French, K.R., 1993. \href{https://doi.org/10.1016/0304-405x(93)90023-5}{Common risk factors in the returns on stocks and bonds}. Journal of Financial Economics 33, 3--56.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-goldstein_commodity_2017}{}}%
-Goldstein, I., Yang, L., 2017.
-\href{https://doi.org/10.2139/ssrn.2555996}{Commodity financialization and information transmission} (SSRN Scholarly Paper No.
-ID 2555996).
-Social Science Research Network, Rochester, NY.
+\leavevmode\vadjust pre{\hypertarget{ref-goldstein_commodity_2022}{}}%
+Goldstein, I., Yang, L., 2022. \href{https://doi.org/10.1111/jofi.13165}{Commodity financialization and information transmission}. The Journal of Finance 77, 2613--2667.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-grossman_impossibility_1980}{}}%
-Grossman, S.J., Stiglitz, J.E., 1980. \href{https://doi.org/10.7916/D8765R99}{On the impossibility of informationally efficient markets}. The American economic review 70, 393--408.
+Grossman, S.J., Stiglitz, J.E., 1980. \href{https://doi.org/10.7916/d8765r99}{On the impossibility of informationally efficient markets}. The American economic review 70, 393--408.
 
@@
 Irwin, S.H., Sanders, D.R., 2012.
-\href{https://doi.org/10.1017/S1074070800000481}{Financialization and structural change in commodity futures markets}.
+\href{https://doi.org/10.1017/s1074070800000481}{Financialization and structural change in commodity futures markets}.
 Journal of Agricultural and Applied Economics 44, 371--396.
@@
 Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009.
-\href{https://doi.org/10.1017/S1074070800002856}{Devil or angel?
+\href{https://doi.org/10.1017/s1074070800002856}{Devil or angel?
 The role of speculation in the recent commodity price boom (and bust)}.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kaldor_speculation_1939}{}}%
-Kaldor, N., 1939. \href{https://doi.org/10.2307/2967593}{{Speculation and economic stability}}. The Review of Economic Studies 7, 1--27.
+Kaldor, N., 1939. \href{https://doi.org/10.2307/2967593}{Speculation and economic stability}. The Review of Economic Studies 7, 1--27.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-leclercq_equilibrium_2014}{}}%
-Leclercq, E., Praz, R., 2014. \href{https://doi.org/10.2139/ssrn.2464400}{Equilibrium commodity trading} (SSRN Scholarly Paper No. ID 2464400). Social Science Research Network, Rochester, NY.
+Leclercq, E., Praz, R., 2014. \href{https://doi.org/10.2139/ssrn.2464400}{Equilibrium commodity trading} (SSRN Scholarly Paper No. Id 2464400). Social Science Research Network, Rochester, NY.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-masters_accidental_2008}{}}%
-Masters, M., White, A., 2008. The accidental hunt brothers: How institutional investors are driving up food and energy prices. Working paper.
+Masters, M.W., White, A.K., 2008. The accidental hunt brothers: How institutional investors are driving up food and energy prices. Working paper.
 

### 2024-08-29 docs/paper.Rmd
Captioned and formatted tables 1 to 5

@@
 tables_directory_path <- here::here("explore", "tables", "revision-jfm")
-paste_forward_slash <- function(...) paste(..., sep = "/")
 
@@
 colnames <- c("asset", "estimate", "past", "financialisation", "crisis", "post-crisis")
-align <- c("llrrrr")
+align <- make_series_of_repeated_chars(list(l = 2L, r = 4L))
 
@@
   pack_rows("individual commodities", 1, 60) %>% 
-  pack_rows("equally weighted portfolios", 61, 64)
+  pack_rows("equally weighted portfolios", 61, 64) %>%
+  style_table(output_type)
 
-style_table(output_type, table)
+table
 ```
@@
 colnames <- c("asset", "regime", "estimate", "past", "financialisation", "crisis", "post-crisis")
-align <- c("lllrrrr")
+align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
 
@@
   pack_rows("individual commodities", 1, 120) %>%
-  pack_rows("equally weighted portfolios", 121, 128)
+  pack_rows("equally weighted portfolios", 121, 128) %>%
+  style_table(output_type)
 
-style_table(output_type, table)
+table
 ```
@@
 colnames <- c("regressor", "sector", "subsector", "past", "financialisation", "crisis", "post-crisis")
-align <- c("lllrrrr")
+align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
 
@@
   column_spec(1L, bold = TRUE) %>%
-  collapse_rows(columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)
+  collapse_rows(columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
+  style_table(output_type)
 
-style_table(output_type, table)
+table
 ```
@@
 colnames <- c("country", "sector", "subsector", "past", "regime", "financialisation", "crisis", "post-crisis")
-align <- c("lllrrrrr")
+align <- make_series_of_repeated_chars(list(l = 3L, r = 5L))
 
@@
   column_spec(1L, bold = TRUE) %>%
-  collapse_rows(columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)
+  collapse_rows(columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
+  style_table(output_type)
 
-style_table(output_type, table)
+table
+```
+
+```{r, include=html}
+knitr::asis_output('<br/><br/>')
+```
+```{r, include=latex}
+knitr::asis_output('\\newpage')
+```
+
+```{r correlations-years}
+caption <- "This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors by year for the whole periods of interest (1997-2018).
+For each year, the results are calculated independently over the entire year as well as over phases of aggregate backwardation and contango.
+Aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
+caption <- if (latex) caption_latex(x = caption) else if (html) caption
+colnames <- c("country", "sector", "subsector", "decade", 0L:9L)
+align <- make_series_of_repeated_chars(list(l = 4L, r = 10L))
+
+table <- get_results(tables, "correlations - years") %>% 
+  kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
+  column_spec(1L, bold = TRUE) %>%
+  collapse_rows(columns = 1L:4L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
+  style_table(output_type)
+
+landscape(table, margin = NULL)
 ```

### 2024-08-29 docs/paper.tex
Captioned and formatted tables 1 to 5

@@
 \usepackage{hyperref}
-\usepackage{lscape}
+\usepackage{pdflscape}
 \usepackage[margin=0pt]{caption}
@@
 
+\begin{landscape}\begingroup\fontsize{9}{11}\selectfont
+
+\begin{longtable}[t]{>{}llllrrrrrrrrrr}
+\caption{\label{tab:correlations-years}This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors by year for the whole periods of interest (1997-2018).
+For each year, the results are calculated independently over the entire year as well as over phases of aggregate backwardation and contango.
+Aggregate CHP construction and corresponding regime definitions are discussed in section \ref{methods} while the results are discussed in section \ref{results}.}\\
+\toprule
+country & sector & subsector & decade & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9\\
+\midrule
+\endfirsthead
+\caption[]{\textit{(continued)}}\\
+\toprule
+country & sector & subsector & decade & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\endlastfoot
+ &  &  & 1990 &  &  &  &  &  &  &  & 0.0401 & 0.0812 & 0.0822\\
+\nopagebreak
+ &  &  & 2000 & 0.0652 & 0.0719 & 0.0796 & 0.0848 & 0.1242 & 0.1247 & 0.1650 & 0.1541 & 0.3334 & 0.2913\\
+\nopagebreak
+\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{all}} &  &  & 2010 & 0.2743 & 0.2837 & 0.2235 & 0.1432 & 0.1139 & 0.1547 & 0.1339 & 0.0963 & 0.1374 & \\
+\nopagebreak
+ &  &  & 1990 &  &  &  &  &  &  &  & 0.0536 & 0.0811 & 0.0803\\
+\nopagebreak
+ &  &  & 2000 & 0.0597 & 0.0652 & 0.0600 & 0.0723 & 0.1073 & 0.1164 & 0.1502 & 0.1479 & 0.3284 & 0.2621\\
+\nopagebreak
+ & \multirow[t]{-6}{*}{\raggedright\arraybackslash all} &  & 2010 & 0.2275 & 0.2541 & 0.1850 & 0.1018 & 0.0986 & 0.1371 & 0.1064 & 0.0905 & 0.1197 & \\
+\nopagebreak
+ &  &  & 1990 &  &  &  &  &  &  &  & 0.0827 & 0.0916 & 0.1121\\
+\nopagebreak
+ &  &  & 2000 & 0.0918 & 0.0967 & 0.0734 & 0.0827 & 0.1111 & 0.1090 & 0.1125 & 0.1131 & 0.3034 & 0.2507\\
+\nopagebreak
+ &  & \multirow[t]{-9}{*}{\raggedright\arraybackslash all} & 2010 & 0.2038 & 0.2304 & 0.1583 & 0.0716 & 0.0846 & 0.1360 & 0.1121 & 0.1148 & 0.1181 & \\
+\nopagebreak
+ &  &  & 1990 &  &  &  &  &  &  &  & 0.5243 & 0.4882 & 0.5650\\
+\nopagebreak
+ &  &  & 2000 & 0.4870 & 0.4337 & 0.3851 & 0.3402 & 0.4473 & 0.5335 & 0.4594 & 0.5040 & 0.6325 & 0.5681\\
+\nopagebreak
+ &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash grains} & 2010 & 0.5389 & 0.6424 & 0.5592 & 0.3199 & 0.3134 & 0.4390 & 0.3872 & 0.4123 & 0.3618 & \\
+\nopagebreak
+ &  &  & 1990 &  &  &  &  &  &  &  & 0.2192 & 0.3724 & 0.3453\\
+\nopagebreak
+ &  &  & 2000 & 0.2762 & 0.3315 & 0.3243 & 0.3497 & 0.2937 & 0.4170 & 0.2784 & 0.2744 & 0.2822 & 0.3365\\
+\nopagebreak
+ &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash livestock} & 2010 & 0.3568 & 0.4772 & 0.3585 & 0.1783 & 0.3532 & 0.4246 & 0.3445 & 0.2948 & 0.2994 & \\
+\nopagebreak
+ &  &  & 1990 &  &  &  &  &  &  &  & -0.0042 & -0.0001 & 0.0128\\
+\nopagebreak
+ &  &  & 2000 & 0.0603 & 0.0289 & 0.0470 & 0.0807 & 0.0577 & 0.0624 & 0.0765 & 0.0485 & 0.2484 & 0.1710\\
+\nopagebreak
+ & \multirow[t]{-12}{*}{\raggedright\arraybackslash agriculturals} & \multirow[t]{-3}{*}{\raggedright\arraybackslash softs} & 2010 & 0.1273 & 0.1400 & 0.1038 & 0.0568 & 0.0413 & 0.0983 & 0.1280 & 0.0825 & 0.0565 & \\
+\nopagebreak
+ &  &  & 1990 &  &  &  &  &  &  &  & 0.4060 & 0.4552 & 0.5256\\
+\nopagebreak
+ &  &  & 2000 & 0.4362 & 0.5186 & 0.5682 & 0.5248 & 0.6212 & 0.6402 & 0.5082 & 0.5530 & 0.6278 & 0.4840\\
+\nopagebreak
+ &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & 2010 & 0.4549 & 0.4752 & 0.3796 & 0.2889 & 0.4103 & 0.4282 & 0.4442 & 0.3890 & 0.4270 & \\
+\nopagebreak
+ &  &  & 1990 &  &  &  &  &  &  &  & 0.7207 & 0.7946 & 0.8527\\
+\nopagebreak
+ &  &  & 2000 & 0.6122 & 0.7632 & 0.8072 & 0.6948 & 0.8321 & 0.7377 & 0.7703 & 0.7895 & 0.8184 & 0.7460\\
+\nopagebreak
+ & \multirow[t]{-6}{*}{\raggedright\arraybackslash energy} & \multirow[t]{-3}{*}{\raggedright\arraybackslash petroleum} & 2010 & 0.8835 & 0.7867 & 0.6692 & 0.6075 & 0.6710 & 0.7069 & 0.7547 & 0.6672 & 0.7786 & \\
+\nopagebreak
+ &  &  & 1990 &  &  &  &  &  &  &  & 0.2296 & 0.2877 & 0.2449\\
+\nopagebreak
+ &  &  & 2000 & 0.1860 & 0.1832 & 0.1992 & 0.2290 & 0.4923 & 0.4480 & 0.6328 & 0.5426 & 0.5664 & 0.5547\\
+\nopagebreak
+ &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & 2010 & 0.6297 & 0.6458 & 0.6649 & 0.6160 & 0.4531 & 0.4850 & 0.4269 & 0.3584 & 0.5259 & \\
+\nopagebreak
+ &  &  & 1990 &  &  &  &  &  &  &  & 0.3063 & 0.3451 & 0.3308\\
+\nopagebreak
+ &  &  & 2000 & 0.2934 & 0.2337 & 0.3053 & 0.2959 & 0.5688 & 0.5674 & 0.6969 & 0.6143 & 0.6428 & 0.6713\\
+\nopagebreak
+\multirow[t]{-27}{*}{\raggedright\arraybackslash \textbf{US}} & \multirow[t]{-6}{*}{\raggedright\arraybackslash metals} & \multirow[t]{-3}{*}{\raggedright\arraybackslash precious} & 2010 & 0.7004 & 0.7107 & 0.7089 & 0.6988 & 0.5620 & 0.6088 & 0.5652 & 0.4746 & 0.5716 & \\
+\cmidrule{1-14}\pagebreak[0]
+ &  &  & 1990 &  &  &  &  &  &  &  & 0.2289 & 0.3601 & 0.4487\\
+\nopagebreak
+ &  &  & 2000 & 0.3550 & 0.4082 & 0.4775 & 0.5526 & 0.5068 & 0.4792 & 0.4340 & 0.4653 & 0.5795 & 0.6647\\
+\nopagebreak
+\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{GB}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & 2010 & 0.6886 & 0.6742 & 0.6122 & 0.6606 & 0.4700 & 0.5003 & 0.4636 & 0.3810 & 0.3598 & \\*
+\end{longtable}
+\endgroup{}
+\end{landscape}
+
+\newpage
+
 \hypertarget{references}{%

### 2024-08-29 explore/scripts/revision-jfm-tables.r

@@ -142,8 +142,17 @@ correlations_years <- dplyr::filter(
   dplyr::select(country, sector, subsector, year, average) %>%
   dplyr::group_by(country, sector, subsector, year) %>%
   dplyr::slice_tail(n = 1L) %>% dplyr::ungroup() %>%
+  dplyr::mutate(
+    decade = slituR::floor_year_to_nearest_decade(year),
+    year = slituR::remove_decade_from_year(year)
+    ) %>%
+  sort_table_by_country_sector_subsector(sort_levels) %>%
   tidyr::pivot_wider(names_from = "year", values_from = "average") %>%
-  sort_table_by_country_sector_subsector(sort_levels)
+  dplyr::relocate(`0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, .after = dplyr::last_col()) %>%
+  dplyr::mutate(
+    dplyr::across(c(`0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`), ~ format(.x, scientific = FALSE)),
+    dplyr::across(c(`0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`), ~ stringr::str_replace_all(.x, "    NA", ""))
+    )
 
 
 # regressions ####

### 2024-08-30 docs/paper.Rmd
Captioned and output table 6
Table 6: regressions - all returns ~ marke index

@@
 caption <- if (latex) caption_latex(x = caption) else if (html) caption
-colnames <- c("country", "sector", "subsector", "past", "regime", "financialisation", "crisis", "post-crisis")
+colnames <- c("country", "sector", "subsector", "regime", "past", "financialisation", "crisis", "post-crisis")
 align <- make_series_of_repeated_chars(list(l = 3L, r = 5L))
@@
 
+```{r regressions-index}
+caption <- "This table shows the average time series regression coefficients for models where the returns series for all the commodity assets considered in the study are independently regressed against the return series for our market factor, an equally weighted portfolio of the 24 US commodities considered in the study.
+The results are calculated independently across countries as well as commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+The market factor construction is discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
+caption <- if (latex) caption_latex(x = caption) else if (html) caption
+colnames <- c("country", "sector", "subsector", "past", "financialisation", "crisis", "post-crisis")
+align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+
+table <- get_results(tables, "regressions - all returns ~ marke index") %>% 
+  kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
+  column_spec(1L, bold = TRUE) %>%
+  collapse_rows(columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
+  style_table(output_type)
+
+table
+```
+
+```{r, include=html}
+knitr::asis_output('<br/><br/>')
+```
+```{r, include=latex}
+knitr::asis_output('\\newpage')
+```
+
 # References {#references .unnumbered}

### 2024-08-30 docs/paper.tex
Captioned and output table 6
Table 6: regressions - all returns ~ marke index

@@
 \toprule
-country & sector & subsector & past & regime & financialisation & crisis & post-crisis\\
+country & sector & subsector & regime & past & financialisation & crisis & post-crisis\\
 \midrule
@@
 
+\begingroup\fontsize{9}{11}\selectfont
+
+\begin{longtable}[t]{>{}lllrrrr}
+\caption{\label{tab:regressions-index}This table shows the average time series regression coefficients for models where the returns series for all the commodity assets considered in the study are independently regressed against the return series for our market factor, an equally weighted portfolio of the 24 US commodities considered in the study.
+The results are calculated independently across countries as well as commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+The market factor construction is discussed in section \ref{methods} while the results are discussed in section \ref{results}.}\\
+\toprule
+country & sector & subsector & past & financialisation & crisis & post-crisis\\
+\midrule
+\endfirsthead
+\caption[]{\textit{(continued)}}\\
+\toprule
+country & sector & subsector & past & financialisation & crisis & post-crisis\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\endlastfoot
+\textbf{all} & all &  & 0.8556 & 0.9709 & 1.0352 & 0.9438\\
+\nopagebreak
+ &  & \multirow[t]{-2}{*}{\raggedright\arraybackslash all} & 0.7706 & 0.7965 & 0.8535 & 0.8252\\
+\nopagebreak
+ &  & grains & 0.9891 & 1.1982 & 1.1727 & 1.0301\\
+\nopagebreak
+ &  & livestock & 0.4320 & 0.2059 & 0.3317 & 0.5484\\
+\nopagebreak
+ & \multirow[t]{-4}{*}{\raggedright\arraybackslash agriculturals} & softs & 0.7213 & 0.6900 & 0.7953 & 0.7589\\
+\nopagebreak
+ &  & all & 2.3308 & 1.6106 & 1.3977 & 1.7639\\
+\nopagebreak
+ &  & gas & 2.6992 & 1.7090 & 1.0044 & 1.2585\\
+\nopagebreak
+ & \multirow[t]{-3}{*}{\raggedright\arraybackslash energy} & petroleum & 2.2080 & 1.5778 & 1.5288 & 1.9324\\
+\nopagebreak
+ &  & all & 0.6320 & 1.1252 & 1.1212 & 0.9131\\
+\nopagebreak
+ &  & base & 0.4902 & 1.1178 & 1.4140 & 0.8780\\
+\nopagebreak
+\multirow[t]{-10}{*}{\raggedright\arraybackslash \textbf{US}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash metals} & precious & 0.6674 & 1.1271 & 1.0480 & 0.9219\\
+\cmidrule{1-7}\pagebreak[0]
+\textbf{GB} & all & all & 0.2713 & 0.8520 & 1.1761 & 0.7192\\*
+\end{longtable}
+\endgroup{}
+
+\newpage
+
 \hypertarget{references}{%

### 2024-09-13 docs/paper.qmd
Get rid of rmarkdown
Switch to Quarto

--- 2024-08-27 docs/paper.Rmd
@@
 ---
-title: 'Financialisation of Commodities: Co-movement Behind-the-scenes'
-date: "`r format(Sys.Date(), '%B %Y')`"
-bibliography: literature_files/references.bib
-github-repo: bautheac/financialisation-co-movement
+title: Financialisation of Commodity Markets
+subtitle: Co-movement Behind-the-Scenes
+author:
+  - name: Devraj Basu
+    email: devraj.basu@strath.ac.uk
+    affiliations: 
+        - id: strathclyde
+          name: University of Strathclyde Business School
+          department: Accounting & Finance
+          address: 199 Cathedral Street
+          city: Glasgow
+          state: Scotland
+          postal-code: G4 0QU
+    attributes:
+        corresponding: true
+  - name: Olivier Bauthéac
+    email: olivier.bautheac@strath.ac.uk
+    affiliations:
+        - ref: strathclyde
 abstract: |
@@
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals.
-output:
-  bookdown::pdf_book:
-      pandoc_args: latex-blind.yaml
-      base_format: rticles::elsevier_article
-      latex_engine: xelatex
+keywords: 
+  - Commodity markets
+  - Financialisation
+  - Asset pricing
+date: last-modified
+bibliography: bibliography.bib
+code_repository: https://github.com/bautheac/financialisation-co-movement
+format:
+  elsevier-pdf:
+    keep-tex: true
+    journal:  
+      name: Journal of Futures Markets
+      formatting: preprint
+      model: 3p
+      cite-style: authoryear
+  html:
+    grid:
+      body-width: 1000px
+    toc: true
     toc_depth: 3
-      includes:
-        in_header: preamble.tex
-  bookdown::gitbook:
-    pandoc_args: html.yaml
-    split_by: "chapter"
+    toc-title: Contents
     css: style.css
-    toc_depth: 3
-    fig_caption: true
-    number_sections: true
-    global_numbering: true
-    config:
-      toc:
-        collapse: subsection
-        scroll_highlight: true
-        before: |
-          <li><a href="index.html">Financialization: co-movement</a></li>
-        after: |
-          <li id="github"><a href="https://github.com/bautheac/financialisation-co-movement"><img src="github.png" alt="github" width="50" height="50"></a></li>
-      sharing:
-        facebook: true
-        twitter: true
-        whatsapp: true
-        all: ['whatsapp', 'twitter', 'facebook']
-      download: [ ["paper.pdf", "pdf"] ]
-      info: false
-    includes:
-      after_body: doc_suffix.html
+    code-links:
+      - text: github repository
+        icon: github
+        href: https://github.com/bautheac/financialisation-co-movement
 ---
 
-```{r globals, include = FALSE}
+```{r}
+#| label: globals
+#| include: false
+
 library(kableExtra); library(slituR)
@@
 
-folder <- "literature_files"; dir.create(folder); path <- paste(folder, "references.bib", sep = "/")
-download.file("https://www.dropbox.com/scl/fi/n7t8g3hn32d8e5gf2rcti/references.bib?rlkey=xy251n44q3y0t3omxpqk0dvyf&dl=1", path)
+urls <- c(
+  "https://www.dropbox.com/scl/fi/n7t8g3hn32d8e5gf2rcti/references.bib?rlkey=xy251n44q3y0t3omxpqk0dvyf&dl=1",
+  "https://www.dropbox.com/scl/fi/c46nb5xpxwgvjdspla9p5/style.css?rlkey=d666hnaxod2stvkxel33or0cg&dl=1"
+)
+file_names <- c("bibliography.bib", "style.css")
+purrr::walk2(urls, file_names, function(url, file_name) download.file(url, file_name))
 
 tables_directory_path <- here::here("explore", "tables", "revision-jfm")
-paste_forward_slash <- function(...) paste(..., sep = "/")
 
@@
 tables_hline <- "major"
-
-html <- knitr::is_html_output(); latex <- knitr::is_latex_output()
-output_type <- ""
-if (html){ output_type <- "html" }
-if (latex){ output_type <- "latex" }
-
 ```
 
-```{r, include=latex}
-knitr::asis_output('\\newgeometry{left=1in,right=1in,top=1in,bottom=1in,nohead}')
-knitr::asis_output('\\savegeometry{tables}')
-knitr::asis_output('\\restoregeometry')
-```
+\newpage
 
-```{r, include=latex}
-knitr::asis_output('\\cleardoublepage')
-```
+\setlength{\parindent}{0pt}
 
-# Introduction {#index}
-<!-- Introduction {#introduction} -->
-<!-- ========================== -->
+# Introduction {#sec-introduction}
 
@@
 Financialisation appears to have affected multiple economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres.
-A vigorous legislative debate accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section \@ref(co-movement-background) for a detailed discussion.] eventually led to regulatory changes in several individual markets.
+A vigorous legislative debate accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section @sec-background for a detailed discussion.] eventually led to regulatory changes in several individual markets.
 In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation--the burning issue of the day--at the individual commodity market level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
@@
 
-```{r, include=latex}
-knitr::asis_output('\\medskip')
-knitr::asis_output('\\setlength{\\parindent}{0pt}')
-```
+\medskip
 
@@
 
-```{r, include=html}
-knitr::asis_output('<br/>')
-```
-```{r, include=latex}
-knitr::asis_output('\\bigskip')
-knitr::asis_output('\\bigskip')
-knitr::asis_output('\\setlength{\\parindent}{0pt}')
-```
+\bigskip
+\bigskip
 
@@
 The CHP factor model thus seems able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialisation.
-We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period^[See section \@ref(methods) for further details.] and evaluating its performance on these selected commodities as well as on all US traded commodities.
+We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period^[See section @sec-methods for further details.] and evaluating its performance on these selected commodities as well as on all US traded commodities.
 The results of this exercise provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
 
-```{r, include=latex}
-knitr::asis_output('\\medskip')
-knitr::asis_output('\\setlength{\\parindent}{0pt}')
-```
+\medskip
 
@@
 
-```{r, include=latex}
-knitr::asis_output('\\newpage')
-```
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
+\newpage
 
-# Data & methods {#co-movement-data-methods}
-<!-- Data & methods {#co-movement-data-methods} -->
-<!-- ============ -->
+# Data & methods {#sec-data-methods}
 
-## Background {#co-movement-background}
+## Background {#sec-background}
 
@@
 
-```{r, include=html}
-knitr::asis_output('<br/>')
-```
+## Data {#sec-data}
 
-## Data {#co-movement-data}
 Commodity index swaps, commodity index funds (CIFs), commodity-based exchange traded funds (ETFs) and notes (ETNs) or commodity linked notes (CLNs) were amongst the main investment vehicles that allowed institutional and retail investors to build up commodity exposure in the early 2000s [@boons_stock_2012; @henderson_new_2015; @irwin_index_2011; @unctad_global_2009; @schumann_hunger_2011].
@@
 
-```{r, include=html}
-knitr::asis_output('<br/>')
-```
-
-## Methods {#methods}
+## Methods {#sec-methods}
 
@@
 
-```{r, include=latex}
-knitr::asis_output('\\newpage')
-```
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
+\newpage
 
-# Results & discussion {#results}
-<!-- Results & discussion {#results} -->
-<!-- =================== -->
+# Results & discussion {#sec-results}
 
-The descriptive statistics for the commodity series considered in the study displayed in table \@ref(tab:stats-no-regimes) show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
+The descriptive statistics for the commodity series considered in the study displayed in table @tbl-stats-no-regimes show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
 6.9% with a 10% significance in the pre-financialisation period.
@@
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
-In table \@ref(tab:stats-regimes) the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
+In table @tbl-stats-regimes the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
 Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another.
@@
 In the second model hedgers are seen as liquidity providers as in @kang_tale_2020 with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
-Table \@ref(tab:time-reg-US-CHP) supports this view.
+Table @tbl-time-reg-US-CHP supports this view.
 We regress commodity futures front returns on individual commercial hedging pressure (CHP) as well as aggregate CHP (**CHP**), our market wide measure of CHP, in separate models and find that the explanatory power of CHP at the individual commodity level decreases over the financialisation period with the US cross-sectional average $R^{2}$ falling down to 20.8% from 25.8% in the previous period while that of **CHP** increases (7.1% vs 5.4%).
@@
 A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities; and therefore provides evidence that pairwise return correlation relates to factor attribute.
-The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \@ref(tab:time-reg-US-facts-US).
+The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table .
 Over the first period the market factor has the best average time series performance with the highest average $R^{2}$ with all three futures market factors performing poorly, indicating that the commodities with extreme factor attributes (high or low CHP for example) are uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of high and low **CHP** (below period median).
@@
 
-```{r, include=latex}
-knitr::asis_output('\\medskip')
-knitr::asis_output('\\setlength{\\parindent}{0pt}')
-```
+\medskip
 
-We next investigate the top eight of the US traded commodities which achieved the highest time series $R^{2}$ for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \@ref(tab:picks).
+We next investigate the top eight of the US traded commodities which achieved the highest time series $R^{2}$ for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table .
 For the CHP factor the commodities that achieve high $R^{2}$ in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor.
@@
 
-```{r, include=latex}
-knitr::asis_output('\\medskip')
-knitr::asis_output('\\setlength{\\parindent}{0pt}')
-```
+\medskip
 
-In table \@ref(tab:correlations), we show the average pairwise returns correlation between each set of picks in each time period.
+In table , we show the average pairwise returns correlation between each set of picks in each time period.
 Following on form the earlier observations, this exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.
@@
 
-```{r, include=latex}
-knitr::asis_output('\\medskip')
-knitr::asis_output('\\setlength{\\parindent}{0pt}')
-```
+\medskip
 
 To further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their explanatory performance on these sets of picks over the four periods independently.
-The results are shown in table \@ref(tab:time-reg-picks-facts-picks).
+The results are shown in table .
 The long-short factors for a particular attribute select the top and bottom two of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks.
@@
 
-```{r, include=latex}
-knitr::asis_output('\\medskip')
-knitr::asis_output('\\setlength{\\parindent}{0pt}')
-```
+\medskip
 
-In table \@ref(tab:time-reg-US-facts-picks) we assess the performance of the same factors on all the commodities instead of just the picks.
-While the average $R^{2}$s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table \@ref(tab:time-reg-picks-facts-picks).
+In table we assess the performance of the same factors on all the commodities instead of just the picks.
+While the average $R^{2}$s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table .
 In contrast, the average CHP factor built with average CHP factor picks shows a smaller absolute increase in average $R^{2}$ indicating that the link between CHP co-movement and price co-movement is stronger amongst the picks which are predominantly metals.
-Taken together, the results in tables \@ref(tab:time-reg-picks-facts-picks) and \@ref(tab:time-reg-US-facts-picks) suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.
-To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in table \@ref(tab:time-reg-UK-facts-picks).
+Taken together, the results in tables and suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.
+To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in table .
 In the first period, although all sets of picks, except that of the market factor, included at least one metal, the average $R^{2}$s are very low; close to zero in most cases.
@@
 
-```{r, include=html}
-knitr::asis_output('<br/>')
-```
-```{r, include=latex}
-knitr::asis_output('\\bigskip')
-knitr::asis_output('\\bigskip')
-knitr::asis_output('\\setlength{\\parindent}{0pt}')
-```
+\bigskip
+\bigskip
 
 The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results.
-Returns fall sharply relative to the financialisation period (table \@ref(tab:stats-no-regimes)) with eighteen US commodities along with all six UK traded metals showing lower mean returns.
+Returns fall sharply relative to the financialisation period (table ) with eighteen US commodities along with all six UK traded metals showing lower mean returns.
 Returns for equally weighted portfolios of both sets of assets fall down to 9.4% and 5.3% from 15.9% and 21.8% respectively.
-Returns are mostly higher during phases of **backwardation** relative to **contango** (table \@ref(tab:stats-no-regimes)) with fifteen US assets and five of the UK traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets.
+Returns are mostly higher during phases of **backwardation** relative to **contango** (table ) with fifteen US assets and five of the UK traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets.
 Volatility is moderately higher for both sets with fifteen US commodities and three UK metals showing higher figures and interestingly eminently higher over phases of **contango**; out of the US complex only Sugar-#11 (IFUS) and none of the UK traded metals show higher volatility figures over **backwardation** phases.
 The symmetry between the dynamics of CHP and **CHP**'s explanatory power on individual commodity returns breaks in the crisis period with both now seemingly converging; the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%).
-The performance of the market factor dominates the US commodity complex over the period with a 50% increase in mean average $R^{2}$ to over 30% (table \@ref(tab:time-reg-US-facts-US)) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
-The average pairwise correlation amongst the market factor picks increases beyond 50% while there is a leveling in that amongst the picks of the long-short factors as shown in table \@ref(tab:correlations).
-Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table \@ref(tab:time-reg-US-facts-picks)).
+The performance of the market factor dominates the US commodity complex over the period with a 50% increase in mean average $R^{2}$ to over 30% (table ) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
+The average pairwise correlation amongst the market factor picks increases beyond 50% while there is a leveling in that amongst the picks of the long-short factors as shown in table .
+Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table ).
 Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
-Table \@ref(tab:time-reg-UK-facts-picks) provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average $R^{2}$ increasing to 31.7% from 10.2% in the previous period.
+Table  provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average $R^{2}$ increasing to 31.7% from 10.2% in the previous period.
 
-```{r, include=latex}
-knitr::asis_output('\\medskip')
-knitr::asis_output('\\setlength{\\parindent}{0pt}')
-```
+\medskip
 
-The returns pullback continues into the post-crisis period (table \@ref(tab:stats-no-regimes)) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively.
+The returns pullback continues into the post-crisis period (table ) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively.
 Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
 The figures for the equally weighted portfolios of US and UK assets drop to 9.9% and 16.2% respectively, very close to pre-financialisation levels.
-The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (table \@ref(tab:stats-no-regimes)) with mean returns higher during phases of **backwardation** relative to **contango** (table \@ref(tab:stats-no-regimes)), more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
+The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (table ) with mean returns higher during phases of **backwardation** relative to **contango** (table ), more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
 The difference is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
@@
 Over the financialisation period in contrast volatilities were predominantly higher in **backwardation** for US traded assets with fourteen commodities showing higher volatility figures in these phases; the post-crisis pattern of results for volatilities thus likewise shows signs of reversion to pre-financialisation standards.
-After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and **CHP** part ways (table \@ref(tab:time-reg-US-CHP)), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
+After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and **CHP** part ways (table ), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
 The recovery initiated in the crisis period for that of CHP is confirmed with a stronger increase in the post-crisis period, 27.2% vs.
@@
 14.8%.
-Average pairwise correlations amongst factor picks (table \@ref(tab:correlations)) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1% to 26.1%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
-The performance of the market factor on the US complex declines below financialisation levels (table \@ref(tab:time-reg-US-facts-US)) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table \@ref(tab:time-reg-US-facts-picks)) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors.
-Table \@ref(tab:time-reg-UK-facts-picks) provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
+Average pairwise correlations amongst factor picks (table ) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1% to 26.1%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
+The performance of the market factor on the US complex declines below financialisation levels (table ) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table ) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors.
+Table  provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
 
-```{r, include=latex}
-knitr::asis_output('\\medskip')
-knitr::asis_output('\\setlength{\\parindent}{0pt}')
-```
+\medskip
 
@@
 
-```{r, include=latex}
-knitr::asis_output('\\newpage')
-```
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
+\newpage
 
 # Conclusion {#conclusion}
-<!-- Conclusion {#conclusion} -->
-<!-- ============ -->
+
 In the early 2000s, against a backdrop of a low yield environment and poor stock market performance, a combination of financial innovations^[Commodity price indexes and the ad-hoc financial instruments enabling investment in them were the main financial innovations which allowed large global banks to offer commodity investment products to institutional and retail investors.
@@
 
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
-```{r, include=latex}
-knitr::asis_output('\\newpage')
-knitr::asis_output('\\loadgeometry{tables}')
-```
+\newpage
 
-# Tables {#tables}
-<!-- # Tables {#tables .unnumbered} -->
-<!-- ============ -->
+# Tables
 
@@
 tables <- readr::read_rds(paste_forward_slash(tables_directory_path, "tables-formatted.rds"))
+sectors <- c("country", "sector", "subsector")
+periods <- c("past", "financialisation", "crisis", "post-crisis")
+
+make_table <- function(table_name, colnames, align, bold_columns, coloured_columns){
+  get_results(tables, table_name) %>%
+  kbl(booktabs = T, longtable = T, col.names = colnames, align = align) %>%
+  kable_styling(latex_options = "striped", font_size = 7L) %>%
+  row_spec(0L, bold = TRUE, color = "black") %>%
+  column_spec(bold_columns, bold = TRUE) %>% column_spec(coloured_columns, color = "#4285f4")
+}
 ```
 
-```{r stats-no-regimes}
-caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.
-The results are discussed in section \\@ref(results)."
-caption <- if (latex) caption_latex(x = caption) else if (html) caption
-colnames <- c("asset", "estimate", "past", "financialisation", "crisis", "post-crisis")
-align <- c("llrrrr")
+```{r}
+#| label: tbl-stats-no-regimes
+#| tbl-cap: "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+Mean values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
+The results are discussed in section \\@sec-results."
 
-table <- get_results(tables, "stats - whole") %>%
-  kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
-  column_spec(1L, bold = TRUE) %>%
-  collapse_rows(columns = 1L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
-  pack_rows("individual commodities", 1, 60) %>%
-  pack_rows("equally weighted portfolios", 61, 64)
+colnames <- c("asset", "estimate", periods)
+align <- make_series_of_repeated_chars(list(l = 2L, r = 4L))
 
-style_table(output_type, table)
+make_table("stats - whole", colnames, align, 1L:6L, 3L:6L)
 ```
 
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
-```{r, include=latex}
-knitr::asis_output('\\newpage')
+\newpage
+
+```{r}
+#| label: tbl-stats-regimes
+#| tbl-cap: "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
+Mean values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
+Aggregate CHP construction and corresponding regime definitions are discussed in section \\@sec-methods while the results are discussed in section \\@sec-results."
+
+colnames <- c("asset", "regime", "estimate", periods)
+align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+
+make_table("stats - regimes", colnames, align, 1L:7L, 4L:7L)
 ```
 
-```{r stats-regimes}
-caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively.
-Aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
-caption <- if (latex) caption_latex(x = caption) else if (html) caption
-colnames <- c("asset", "regime", "estimate", "past", "financialisation", "crisis", "post-crisis")
-align <- c("lllrrrr")
+\newpage
 
-table <- get_results(tables, "stats - regimes") %>% 
-  kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
-  column_spec(1L, bold = TRUE) %>%
-  collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
-  pack_rows("individual commodities", 1, 120) %>%
-  pack_rows("equally weighted portfolios", 121, 128)
+```{r}
+#| label: tbl-time-reg-US-CHP
+#| tbl-cap: "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \\@sec-methods.
+Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+The results are discussed in section \\@sec-results."
 
-style_table(output_type, table)
+colnames <- c("regressor", "sector", "subsector", periods)
+align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+
+make_table("regressions - US returns ~ US CHP", colnames, align, 1L:7L, 4L:7L)
 ```
 
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
-```{r, include=latex}
-knitr::asis_output('\\newpage')
+\newpage
+
+```{r}
+#| label: tbl-correlations-periods
+#| tbl-cap: "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \\@sec-methods.
+Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+The results are discussed in section \\@sec-results."
+
+colnames <- c(sectors, "regime", periods)
+align <- make_series_of_repeated_chars(list(l = 3L, r = 5L))
+
+make_table("correlations - periods", colnames, align, 1L:8L, 5L:8L)
 ```
 
-```{r time-reg-US-CHP}
-caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \\@ref(methods).
-Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The results are discussed in section \\@ref(results)."
-caption <- if (latex) caption_latex(x = caption) else if (html) caption
-colnames <- c("regressor", "sector", "subsector", "past", "financialisation", "crisis", "post-crisis")
-align <- c("lllrrrr")
+\newpage
 
-table <- get_results(tables, "regressions - US returns ~ US CHP") %>% 
-  kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
-  column_spec(1L, bold = TRUE) %>%
-  collapse_rows(columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)
+```{r}
+#| label: tbl-correlations-years
+#| tbl-cap: "This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors by year for the whole periods of interest (1997-2018).
+For each year, the results are calculated independently over the entire year as well as over phases of aggregate backwardation and contango.
+Aggregate CHP construction and corresponding regime definitions are discussed in section \\@sec-methods while the results are discussed in section \\@sec-results."
 
-style_table(output_type, table)
+colnames <- c(sectors, "decade", 0L:9L)
+align <- make_series_of_repeated_chars(list(l = 4L, r = 10L))
+
+make_table("correlations - years", colnames, align, 1L:14L, 5L:14L) %>%
+  landscape()
 ```
 
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
-```{r, include=latex}
-knitr::asis_output('\\newpage')
+\newpage
+
+```{r}
+#| label: tbl-regressions-index
+#| tbl-cap: "This table shows the average time series regression coefficients for models where the returns series for all the commodity assets considered in the study are independently regressed against the return series for our market factor, an equally weighted portfolio of the 24 US commodities considered in the study.
+The results are calculated independently across countries as well as commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+The market factor construction is discussed in section \\@sec-methods while the results are discussed in section \\@sec-results."
+
+colnames <- c(sectors, periods)
+align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+
+make_table("regressions - all returns ~ marke index", colnames, align, 1L:7L, 4L:7L)
 ```
 
-```{r correlations-periods}
-caption <- "This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-For each period, the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
-Aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(methods) while the results are discussed in section \\@ref(results)."
-caption <- if (latex) caption_latex(x = caption) else if (html) caption
-colnames <- c("country", "sector", "subsector", "past", "regime", "financialisation", "crisis", "post-crisis")
-align <- c("lllrrrrr")
+\newpage
 
-table <- get_results(tables, "correlations - periods") %>% 
-  kbl(format = output_type, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align) %>%
-  column_spec(1L, bold = TRUE) %>%
-  collapse_rows(columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)
+```{r}
+#| label: tbl-regressions-factors
+#| tbl-cap: "This table shows the average time series regression $R^{2}$ for models where the returns series for all the commodity assets considered in the study are independently regressed against the return series for our mimicking portfolios for risk factors in returns, including the market, CHP, open interest and term structure factors.
+The results are calculated independently across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018); for earch period the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
+Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \\@sec-methods while the results are discussed in section \\@sec-results."
 
-style_table(output_type, table)
+colnames <- c(sectors, "factor", "regime", periods)
+align <- make_series_of_repeated_chars(list(l = 5L, r = 4L))
+
+make_table("regressions - all returns ~ factors", colnames, align, 1L:9L, 6L:9L) %>%
+  landscape()
 ```
 
-```{r, include=html}
-knitr::asis_output('<br/><br/>')
-```
-```{r, include=latex}
-knitr::asis_output('\\newpage')
-```
+\newpage
 
-# References {#references .unnumbered}
-<!-- References {#references .unnumbered} -->
-<!-- ========== -->
+# References {-}

### 2024-09-13 docs/paper.tex
Get rid of rmarkdown
Switch to Quarto

--- 2024-08-27 docs/paper.tex
@@
-\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
-%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
-\usepackage[hyphens]{url}
-
-  \journal{Journal of Futures Markets} % Sets Journal name
-
-\usepackage{lineno} % add
-
-\usepackage{graphicx}
-%%%%%%%%%%%%%%%% end my additions to header
-
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  authoryear,
+  preprint,
+  3p]{elsarticle}
+
+\usepackage{amsmath,amssymb}
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-% use upquote if available, for straight quotes in verbatim environments
+\ifPDFTeX\else  
+    % xetex/luatex font selection
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \usepackage{fontspec}
-  \ifxetex
-    \usepackage{xltxtra,xunicode}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
+% Make \paragraph and \subparagraph free-standing
+\makeatletter
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
-  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
-  \newcommand{\euro}{€}
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
-% use microtype if available
-\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
-\bibliographystyle{elsarticle-harv}
-\ifxetex
-  \usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \usepackage[unicode=true]{hyperref}
-\fi
-\hypersetup{breaklinks=true,
-            bookmarks=true,
-            pdfauthor={},
-            pdftitle={Financialisation of Commodities: Co-movement Behind-the-scenes},
-            colorlinks=false,
-            urlcolor=blue,
-            linkcolor=magenta,
-            pdfborder={0 0 0}}
-\urlstyle{same}  % don't use monospace font for urls
-
-\setcounter{secnumdepth}{5}
-% Pandoc toggle for numbering sections (defaults to be off)
-
-% tightlist command for lists without linebreak
+\makeatother
+
 \providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% From pandoc table feature
-\usepackage{longtable,booktabs,array}
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makesavenoteenv{longtable}
-
-% Pandoc citation processing
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\usepackage{geometry}
-\usepackage{hyperref}
-\usepackage{lscape}
-\usepackage[margin=0pt]{caption}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
-
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\journal{Journal of Futures Markets}
+
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage[]{natbib}
+\bibliographystyle{elsarticle-harv}
+\usepackage{bookmark}
+
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={financialisation of Commodity Markets},
+  pdfauthor={Devraj Basu; Olivier Bauthéac},
+  pdfkeywords={Commodity markets, Financialisation, Asset pricing},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
+
+\setlength{\parindent}{6pt}
 \begin{document}
@@
 \begin{frontmatter}
-
-  \title{Financialisation of Commodities: Co-movement Behind-the-scenes}
+\title{financialisation of Commodity Markets \\\large{Co-movement
+Behind-the-Scenes} }
+\author[1]{Devraj Basu%
+\corref{cor1}%
+}
+ \ead{devraj.basu@strath.ac.uk} 
+\author[1]{Olivier Bauthéac%
+%
+}
+ \ead{olivier.bautheac@strath.ac.uk}
+
+\affiliation[1]{organization={University of Strathclyde Business
+School, Accounting \& Finance},addressline={199 Cathedral
+Street},city={Glasgow},postcode={G4 0QU},postcodesep={}}
+
+\cortext[cor1]{Corresponding author}
 
 \begin{abstract}
-  In the early 2000s institutional investors entered the commodity futures markets en masse with passive, long only, index type positions in sharp contrast with those typically assumed by traditional expert participants.
-A heated public debate soon erupted over the perceived consequences of the phenomenon--commonly referred to as ``financialisation''---and, in response to immediate policy concerns, the matter was thrust onto the academic sphere as a burning issue.
-With the benefit of hindsight it now seems that the academic debate was framed rather narrowly, used contentious research methods, and eventually led to regulatory changes that were therefore perhaps unwarranted.
-In contrast, we take a broader approach where we consider a large cross-section of liquid commodities as suggested by the nature of financilisation that comprehends commodity futures as an asset class.
-Using a bespoke asset pricing factors based framework we study the issue through the lens of co-movement and find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals.
+In the early 2000s institutional investors entered the commodity futures
+markets en masse with passive, long only, index type positions in sharp
+contrast with those typically assumed by traditional expert
+participants. A heated public debate soon erupted over the perceived
+consequences of the phenomenon--commonly referred to as
+``financialisation''---and, in response to immediate policy concerns,
+the matter was thrust onto the academic sphere as a burning issue. With
+the benefit of hindsight it now seems that the academic debate was
+framed rather narrowly, used contentious research methods, and
+eventually led to regulatory changes that were therefore perhaps
+unwarranted. In contrast, we take a broader approach where we consider a
+large cross-section of liquid commodities as suggested by the nature of
+financilisation that comprehends commodity futures as an asset class.
+Using a bespoke asset pricing factors based framework we study the issue
+through the lens of co-movement and find that the phenomenon had
+ontological consequences for the commodity complex with its impact
+extending beyond the mechanical effects induced by indexation. The onset
+of the financial crisis and the monetary policy regimes that followed,
+on the other hand, seem to have set off a motion of reversion to legacy
+pre-financialisation fundamentals.
 \end{abstract}
 
+\begin{keyword}
+    Commodity markets \sep Financialisation \sep 
+    Asset pricing
+\end{keyword}
 \end{frontmatter}
 
-\newgeometry{left=1in,right=1in,top=1in,bottom=1in,nohead}\savegeometry{tables}\restoregeometry
-
-\cleardoublepage
-
-\hypertarget{index}{%
-\section{Introduction}\label{index}}
-
-The last twenty years have seen major upheavals in the commodity markets with the onset of financialisation\footnote{Starting around 2004, with a view of commodity markets as an emerging asset class and in an effort to hedge against inflation and seek diversification benefits (Büyükşahin and Robe, 2014; Singleton, 2013), institutional investors sent forth an unprecedented flow of capital into commodity futures markets.
-This phenomenon is commonly referred to as the financialisation of commodities (Domanski and Heath, 2007).} as well as the period of the 2008 financial crisis and its aftermath.
-Financialisation appears to have affected multiple economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres.
-A vigorous legislative debate accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors\footnote{See section \ref{co-movement-background} for a detailed discussion.} eventually led to regulatory changes in several individual markets.\\
-In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation--the burning issue of the day--at the individual commodity market level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
-With the benefit of hindsight, this approach seems to lack a fundamental understanding of the phenomenon it endeavoured to study and which consequences it attempted to address.\\
-Financialisation was a phenomenon global in nature; through the channel of index investment it affected the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
-Focusing on individual markets in this context thus seems limited.
-Most of the studies underpinning the regulatory response to financialisation took the form of pairwise correlation, causation and to some extent co-integration analysis, all of which are idiosyncratic in nature for they study single pairs of individual assets.
-Besides, some of these techniques since proved controversial and seem to produce results the quality of which may fall short of the standards that may reasonably be expected to lay the ground for legislative action.
-Although appealing, for it comes with the promise of prompt ``significant'' results, this approach misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure (Hicks, 1939; Keynes, 1930).\\
-While essential to the understanding of the phenomenon, the global nature of financialisation and its impact on market fundamentals therefore appear to have been originally overlooked and another approach, perhaps more refined, seems warranted.
-
-\medskip\setlength{\parindent}{0pt}
-
-We strive to provide one in this study by taking a fundamentally different empirical perspective that is broader in scope.
-We consider the entire cross-section of actively traded commodities on futures markets and use a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations.\\
-The global nature of financialisation makes cross-sectional co-movement a cornerstone issue that the direct impact of increased market participation alone might not be able to fully explain for it potentially had deeper effects, for example on market fundamentals as our results suggest.
-Commodity futures markets have a history of being the classic physical commodity price risk shifting conduit for commodity specialists.
-Over the financialisation period we observe a decrease in effectiveness of commercial hedging pressure (CHP) at explaining commodity futures returns at the individual level accompanied by a more pronounced increase at the aggregate level.
-We further note an overall shift in the nature of hedger's behaviour away from the traditional Keynesian view of risk transfer with higher individual risk premiums over phases of cross-sectional contango as opposed to backwardation.
-Both patterns suggest that the phenomenon may have altered this long-standing paradigm of commercial risk transfer with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants.
-This change could have altered the hedging ontology in these markets and our asset pricing framework is tailored to detect these more subtle effects driven by changes in the nature of market participation.\\
-Factor model techniques are well suited to isolating common driving factors and detecting co-movement (Asness et al., 2015; Asness and Frazzini, 2013; Asness et al., 2019; Carhart, 1997; Fama and French, 2015, 1993; Frazzini and Pedersen, 2014; Hou et al., 2015) at a broader level, beyond individual pairs of assets, and are commonly used to study commodity market fundamentals (Bakshi et al., 2019; Boons and Prado, 2019; Cortazar et al., 2013; Daskalaki et al., 2014; Fernandez-Perez et al., 2018; Gorton et al., 2012; Miffre and Rallis, 2007; Sakkas and Tessaromatis, 2020; Schwartz and Smith, 2000; Szymanowska et al., 2014; Yang, 2013); they consequently seem well adapted to study these two issues simultaneously.
-Building on theory we therefore develop a bespoke commodity-based asset pricing framework comprised of factor models based both on fundamentals as well as liquidity considerations.\\
-One of these is based on the Keynes-Hicks (Hicks, 1946, 1939; Keynes, 1930, 1923) risk transfer approach to the term structure; the corresponding ``theory of normal backwardation'', complemented for the possibility of contango (Cootner, 1960; H.
-Houthakker, 1957), postulates that futures prices for a given commodity are inversely related to the extent that commercial hedgers are short or long and using commercial hedging pressure (CHP) as a proxy for hedgers net market position we construct factor mimicking portfolios that capture the impact of hedging pressure as a systemic factor (Basu and Miffre, 2013).
-The cross-sectional nature of financialisation (Basak and Pavlova, 2016; Cheng and Xiong, 2014) further leads us to extend this paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in Hong and Yogo (2012).
-In this context, returns for individual commodities should be high in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in periods where \textbf{CHP} is high (\textbf{contango}).
-Working's contending approach that relates futures price formation to storage costs in the theory of ``the price of storage'' (Working, 1949) forms the basis of another model that we consider where, following Szymanowska et al.
-(2014) and Fuertes et al.
-(2015) who demonstrate that the term structure factor has explanatory power for the cross-section of commodity returns, we construct factor mimicking portfolios using roll-yield as a proxy for the front end shape of individual commodity term structures.
-We further consider a liquidity-based model following Hong and Yogo (2012) who find that open interest growth has predictive power for individual commodity returns and again, using the latter measure as a proxy for individual commodity liquidity, we construct long-short factor mimicking portfolios.
-
-\bigskip\bigskip\setlength{\parindent}{0pt}
-
-We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008\footnote{Starting point based on earlier studies (Baker, 2021; Christoffersen et al., 2014).}); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).\\
-Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.
-
-\medskip\setlength{\parindent}{0pt}
-
-Over the first period the cross-sectional average returns during phases of \textbf{backwardation} for both the US and UK commodities are positive and overall higher than during phases of \textbf{contango}, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
-Over the second period this pattern reverses, with both the US and UK commodities having higher returns during phases of \textbf{contango} as opposed to \textbf{backwardation}.
-This change in pattern suggests the onset of financialisation altered the traditional risk shifting nature of hedger's behaviour, implied by the Keynesian hypothesis.\\
-This change of paradigm due to the arrival of financial investors, on the other hand, raises the question of whether they functioned as liquidity providers or demanders.
-Arguments have been put forward in favour of both possibilities with Moskowitz et al.
-(2012) arguing that financial investors provide liquidity and Kang et al.
-(2020) taking the opposite stance.
-Our analysis of individual commodity returns' relation with both CHP and \textbf{CHP} before and during financialisation sheds a new light on this issue with our results suggesting that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
-
-\medskip\setlength{\parindent}{0pt}
-
-Goldstein et al.
-(2014) and Goldstein and Yang (2022) argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
-Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger's positions (Keynesian perspective, theory of normal backwardation: Keynes (1930), Hicks (1939), H.
-S.
-Houthakker (1957), Telser (1958)), as well our term structure factor, based on backwardation as measured by roll yield (Working's perspective, theory of storage: Working (1933), Kaldor (1939), Working (1948), Brennan (1958), Cootner (1960), Weymar (1966), Danthine (1978), Turnovsky (1983), Schwartz (1997)), to be best suited to measure the impact of financialisation.\\
-We analyse the pricing dynamics over the different periods by first studying the time series explanatory performance of the various factors on all the US traded commodities with the factors constructed using the latter set of commodities.
-The market-based factor outperforms the other three in the first period and, although its performance increases over the financialisation period, that of the CHP factor shows a greater improvement in a relative sense.
-The performance of the market factor is driven by agricultural and energy commodities in the first period while metals strongly contribute to the performance improvement observed over the second period.
-Similarly, the dramatic improvement of the CHP factor in the second period, is driven by the metals complex, particularly that of the long leg where they predominantly load.
-Average pairwise correlations amongst individual factors' best performing commodities increase across the board over the financialisation period, far beyond the average for the whole cross-section of US traded commodities.
-The increase is particularly strong for the long-short factors, in a relative sense, on which the metal complex loads significantly more during financialisation.
-This increase is due to the dramatic rise in average pairwise correlation amongst the US traded metals all of which exhibited high \(R^{2}\) with respect to the CHP factor during financialisation which in turn is due to their common low level of CHP over this period.
-The CHP factor model thus seems able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialisation.\\
-We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period\footnote{See section \ref{methods} for further details.} and evaluating its performance on these selected commodities as well as on all US traded commodities.
-The results of this exercise provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
-
-\medskip\setlength{\parindent}{0pt}
-
-The UK traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialisation.
-To that end, we examine the performance of the four factors on the six UK metals, when constructed from each set of factor picks.
-The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.
-
-\medskip\setlength{\parindent}{0pt}
-
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes.
-Commodity futures returns fell dramatically into the crisis and the pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as evidence of cross-market linkages with the UK traded commodity subset.
-The post-crisis results, in contrast, show a substancial pullback in performance for the market factor across the board as well as evidence of decoupling between the US and UK markets.
-Besides, starting in the crisis the Keneysian paradigm of returns begins to revert with higher mean returns during low (\textbf{backwardation}) relative to high (\textbf{contango}) \textbf{CHP} phases and this pattern continues, more pronounced, over the post-crisis period.
-As pointed out in Basu and Bauthéac (2024), the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
-
-\bigskip\bigskip\setlength{\parindent}{0pt}
-
-Financialisation was an issue of such policy importance that it triggered legislative action.
-The debate was initially framed around adequacy of speculation, the burning issue of the day, and the ensuing academic analysis focused on the more mechanical effects of financialisation.\\
-With the benefit of hindsight, it appears this approach was perhaps too narrow, and it now seems necessary to address the phenomenon from a broader perspective.
-Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggering a reversion to pre-financialisation dynamics.
-
-The initial view of financialisation was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity futures prices\footnote{Masters (2008); Masters and White (2008); UNCTAD and Cooperation (2009); De Schutter (2010); Gilbert (2010a); Gilbert (2010b); Herman et al.
-(2011); Schumann (2011); Singleton (2013).}.
-However, the fundamental question of the nature of the impact of financialisation across the entire cross-section of commodity futures markets has not yet been completely answered.
-We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets\footnote{Etula (2013), Acharya et al.
-(2013), Cheng et al.
-(2014), Leclercq and Praz (2014), Sockin and Xiong (2015), Goldstein et al.
-(2014), Ekeland et al.
-(2016), Goldstein and Yang (2022), Ekeland et al.
-(2019), Isleimeyyeh (2020).} and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in Tang and Xiong (2012) and Basak and Pavlova (2016).
-
 \newpage
 
-\hypertarget{co-movement-data-methods}{%
-\section{Data \& methods}\label{co-movement-data-methods}}
-
-\hypertarget{co-movement-background}{%
-\subsection{Background}\label{co-movement-background}}
-
-The period from 1998 to 2008 saw an influx of investment into commodity index linked products most of which made its way into the commodity futures market.
-Popular commodity indexes whose goal was to track the broad movement of commodity prices became accessible by means of swaps, exchange traded funds and exchange traded notes and attracted at least \$100 billion of net super-hoc investment over the 1998-2008 period.
-
-\medskip\setlength{\parindent}{0pt}
-
-Concerns over the consequences of this financialisation phenomenon eventually led to legislative changes including the approval of Rule 76 FR 4752 issued by the US Commodity Futures Trading Commission (CFTC) on January 26\textsuperscript{th}, 2011.
-This provision emanates from the Dodd-Frank Wall Street and Consumer Protection Act of 2010 (Title VII, Section 737) that mandates the CFTC to use position limits to restrict the flow of speculative capital into a number of commodity markets.
-The Rule was approved in a close 3-2 vote and the ensuing rule-making process was extremely contentious with several commissioners (Michael Dunn and Scott D.
-O'Malia in particular) expressing reservations about the lack of supporting evidence and the Rule also triggering thousands of comment letters as well as a lawsuit against the CFTC spearheaded by two Wall Street trade groups, the International Swaps \& Derivatives Association (ISDA) and the Securities Industries \& Financial Markets Association (SIFMA)\footnote{ISDA \& SIFMA v US CFTC; Complaint, 1:11-cv-02146; December 2\textsuperscript{nd}, 2011.}.
-
-\medskip\setlength{\parindent}{0pt}
-
-A world-wide debate ensued about the role of index funds in commodity markets.
-The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs (De Schutter, 2010; Gilbert, 2010b; Herman et al., 2011; Schumann, 2011; UNCTAD and Cooperation, 2009).\\
-Early US Senate investigations on the matter drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US agricultural and energy markets to the observed surges in both futures and cash prices (Masters, 2008; Masters and White, 2008).
-This contention has since come to be known as the Masters' hypothesis and was largely endorsed by the final US Senate report on the issue (Senate, 2009).\\
-At this stage, the question thrust on the academic sphere was whether ``excessive speculation'' (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices.
-A number of ensuing academic studies, most of which used commodity specific correlation and causality based analysis have since disproved this contention: Irwin et al.
-(2009), Sanders et al.
-(2010), Sanders and Irwin (2011a), Sanders and Irwin (2011b), Irwin (2013), Brunetti and Reiffen (2014), Hamilton and Wu (2015) and Bruno et al.
-(2017) investigated the issue in the context of the agricultural markets; meanwhile, Büyükşahin and Harris (2011), Tokic (2012), Fattouh et al.
-(2013), Kilian and Murphy (2014), Knittel and Pindyck (2016) and Manera et al.
-(2016) examined the energy markets while Bohl and Stephan (2013), Kim (2015) and Boyd et al.
-(2016) studied both energy and agricultural markets and Irwin and Sanders (2011), Irwin and Sanders (2012) as well as Stoll and Whaley (2011) examined the commodity markets in general.
-Other studies have underlined various alterations in commodity pricing dynamics over the period.
-Gilbert and Pfuderer (2014) reject the view that financialisation has not had any effects in the grains markets and demonstrate that trades originated by financial market participants, and specifically index investors, can move prices but tend to be typically volatility-reducing.
-Juvenal and Petrella (2015) contend that the oil price increase between 2004 and 2008 was mainly driven by the strength of global demand but that the financialisation process of commodity markets also played a role.
-Likewise, Henderson et al.
-(2015) show that non-information-based financial investments have important impacts on commodity prices.
-Cheng and Xiong (2014), on the other hand, show that in the case of index commodities, financialisation has transformed the risk sharing, and information discovery functions of commodity futures markets.
-
-\hypertarget{co-movement-data}{%
-\subsection{Data}\label{co-movement-data}}
-
-Commodity index swaps, commodity index funds (CIFs), commodity-based exchange traded funds (ETFs) and notes (ETNs) or commodity linked notes (CLNs) were amongst the main investment vehicles that allowed institutional and retail investors to build up commodity exposure in the early 2000s (Boons et al., 2012; Henderson et al., 2015; Irwin and Sanders, 2011; Schumann, 2011; UNCTAD and Cooperation, 2009).
-Most of these products were primarily designed to track prominent commodity indexes among which the S\&P-GSCI, the most popular.\\
-Most of its constituents at the time of writing form the basis of the broad cross-section of commodities that we consider in this study: corn-\#2 yellow (XCBT), oats (XCBT), soybean meal (XCBT), soybean oil (XCBT), soybeans (XCBT), wheat-SRW (XCBT), cattle-feeder (XCME), cattle-live (XCME), lean hogs (XCME), cocoa (IFUS), coffee-C (IFUS), cotton-\#2 (IFUS), lumber (XCME), orange juice (IFUS), sugar-\#11 (IFUS), natural gas (XNYM), crude oil-WTI (XNYM), gasoline (XNYM), heating oil (XNYM), copper (XCEC), gold (XCEC), palladium (XNYM), platinum (XNYM) and silver (XCEC).
-Unleaded gasoline, the NYMEX legacy contract for gasoline, stopped trading in 2006 when it was replaced by Reformulated Gasoline Blendstock for Oxygen Blending (RBOB) with the two futures series trading alongside for most of the year.
-For our NYMEX gasoline data series, we consider unleaded gasoline up to September 1\textsuperscript{st}, 2006 and RBOB gasoline thereafter, date at which liquidity for the latter overtook that for the former.\\
-We also consider the UK metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).
-
-\medskip\setlength{\parindent}{0pt}
-
-The commodity futures trading commission (CFTC) operates a comprehensive system of collecting information on market participants known as the large trader reporting program (LTRP) where it records and reports to the public position data on market participants who have position levels in excess of a particular market specific threshold\footnote{Current reporting level thresholds available at: \href{https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=\&SID=970471b8455f4bab7db4110cfde50731\&mc=true\&r=SECTION\&n=se17.1.15_103}{www.ecfr.gov}.}.
-The commission collects market data and position information daily from clearing members, futures commission merchants (FCMs) and foreign brokers and publishes corresponding summaries weekly in a series of market specific reports.
-In these reports, individual traders are categorised according to the nature of their trading activity on the basis of self-reported information\footnote{CFTC form 40.
-Available at: \href{https://www.cftc.gov/sites/default/files/idc/groups/public/@forms/documents/file/cftcform40.pdf}{www.cftc.gov}.} that is subject to review by CFTC staff for reasonableness.
-Position information is then aggregated by category and asset type with each report providing an aggregation for a set of report specific categories and, for each category, a breakdown between futures only positions and positions in futures and options combined.\\
-In its legacy report, the commitment of trader report (COT) with data dating back to 1962, the CFTC distinguishes ``commercial'' and ``non-commercial'' market participants where a ``commercial'' participant is defined as one ``{[}\ldots{]} engaged in business activities hedged by the use of futures and option markets''\footnote{See \href{https://www.gpo.gov/fdsys/pkg/CFR-1998-title17-vol1/xml/CFR-1998-title17-vol1-sec1-3.xml}{CFTC regulation 1.3, 17 CFR 1.3(z)} for details.}.
-A third category, ``non-reportable'', aggregates positions for participants not meeting the reporting threshold.
-In response to concerns related to category accuracy\footnote{See for example Ederington and Lee (2002).} the CFTC now refines its classification in the disaggregated commitment of trader report (DCOT) where participant categories include ``Producer/Merchant/Processor/User'', ``Swap dealer'', ``Money manager'' and ``Other reportable'' as well as in the supplemental commitment of trader report (SCOT) that details commodity index trader aggregate positions for thirteen agricultural commodity futures markets.
-Data for DCOT and SCOT date back to 2006 and 2007 respectively.\\
-We study the 1997/2018 period where we observe futures only position data from the COT report, the only CFTC report with data available for the whole period of interest; as well as futures term structure price and open interest data from Bloomberg.
-
-\hypertarget{methods}{%
-\subsection{Methods}\label{methods}}
-
-On the one hand, futures markets have a long history of serving commodity producers to alleviate their commodity price and output risks.
-Keynes (1930) and Hicks (1939) emphasise the ``normal'' behaviour of naturally short hedgers outsourcing their commodity risk to naturally long commodity specialist speculators.
-This market configuration is referred to as ``backwardation'' where futures are expected to trade at a discount to spot prices, providing speculators with incentives to take the long side.
-The opposite market paradigm is referred to as ``contango''.
-Working (Working, 1953, 1948, 1933) and Kaldor (Kaldor, 1939) somehow relax this ``supply-of-speculative-services'' (Till, 2007) approach by introducing processors and merchants, also commodity experts, on the hedgers side and relating the notions of backwardation and contango more directly to the term structure via the theory of storage where the shape of the front end of the term structure (basis) is directly related to the market price of storage.\\
-Financialisation, on the other hand, refers to the entry of financial investors into the commodity futures markets who, for the most part, are not commodity experts.
-Besides, these new market participants tend to exhibit herding like behaviour, often taking massive long-only positions on the whole cross-section of indexed commodities in an attempt to enhance returns while hedging against inflation and reaping further diversification benefits for portfolios with, in most cases, existing large positions across various asset classes (Boyd et al., 2016; Brunetti et al., 2016; Cheng et al., 2014; Juvenal and Petrella, 2015; Singleton, 2013; Tang and Xiong, 2012).
-This contrasts with the traditional approaches of Keynes and Working and in this context the issues of co-movement and aggregate market participants behaviour seem particularly relevant.
-
-\medskip\setlength{\parindent}{0pt}
-
-By grouping together assets by shared attribute dynamics in common portfolios, asset pricing techniques--and factor models in particular--are well suited to study co-movement (Asness et al., 2015; Asness and Frazzini, 2013; Asness et al., 2019; Carhart, 1997; Fama and French, 2015, 1993; Frazzini and Pedersen, 2014; Hou et al., 2015).
-Careful, theory-based, attribute selection further enables a refined analysis of market fundamentals (Bakshi et al., 2019; Boons and Prado, 2019; Cortazar et al., 2013; Daskalaki et al., 2014; Fernandez-Perez et al., 2018; Gorton et al., 2012; Miffre and Rallis, 2007; Sakkas and Tessaromatis, 2020; Schwartz and Smith, 2000; Szymanowska et al., 2014; Yang, 2013).
-We therefore develop a futures-based asset pricing framework that includes factors constructed using both theoretical and liquidity considerations and use this framework to carry out our analysis over four periods of interest.
-The first, the pre-financialisation period, starts in 1997 and is naturally followed by financialisation, spanning the 2004/2008 period, and the financial crisis and its aftermath, spanning the 2008/2013 period.
-The last period spans the 2014/2018 period starting with the beginning of the tapering/end of the US Quantitative Easing program (QE).\\
-Using the weekly price, open interest and market position data described above we construct market portfolios of individual commodity nearby futures as well as mimicking portfolios for market, commercial hedging pressure, term structure and liquidity risk factors in returns.
-While our market portfolios are long only, equally weighted portfolios of particular commodity sets, our other mimicking portfolios for risk factors are constructed as combinations of two sub-portfolios (legs), one held long, one held short, which respective constituents are pooled on a weekly basis according to risk factor specific criteria.\\
-For each leg, the position weight for a particular asset for a particular period is contingent on the value of the corresponding sorting variable and its rank relative to the other assets in the pool.
-The sorting variable values for the asset pool are first rescaled so that the highest (lowest) value becomes 1 (0).
-Weights are then determined pairwise, starting from the extremes with the highest and lowest figures.
-A coefficient \(\alpha\) is determined by dividing their difference (1 in this case) by the mean of the rescaled values.
-The high figure is attributed a score of \(\frac{1}{n} \times \alpha\) where \(n\) is the number of assets in the pool while the score for the low figure is \(\frac{1/n}{\alpha}\).
-The operation is repeated for the pair of assets showing the second highest and second lowest values for the sorting variable and so on until all the assets in the pool are attributed a score.
-The individual asset weights are then determined by dividing each score by the sum of the scores.\\
-The period return for a particular mimicking portfolio is calculated as the difference between the weighted average return for constituents of the long portfolio and that for the constituents of the short portfolio.
-i.e, return on the mimicking portfolio for risk factor \(i\) (\(f_{i}\)) for period \(t\):
+\setlength{\parindent}{0pt}
+
+\section{Introduction}\label{sec-introduction}
+
+The last twenty years have seen major upheavals in the commodity markets
+with the onset of financialisation\footnote{Starting around 2004, with a
+  view of commodity markets as an emerging asset class and in an effort
+  to hedge against inflation and seek diversification benefits
+  \citep{buyuksahin_speculators_2014, singleton_investor_2013},
+  institutional investors sent forth an unprecedented flow of capital
+  into commodity futures markets. This phenomenon is commonly referred
+  to as the financialisation of commodities
+  \citep{domanski_financial_2007}.} as well as the period of the 2008
+financial crisis and its aftermath. Financialisation appears to have
+affected multiple economic sectors, including agriculture and energy,
+and its impact has been hotly debated in the policy, legislative,
+regulatory, and academic spheres. A vigorous legislative debate
+accompanied by an equally intense policy and academic debate across a
+number of disciplines about the perceived effects on commodity prices of
+the unprecedented inflow of institutional funds brought into commodity
+futures markets by new index type investors\footnote{See section
+  Section~\ref{sec-background} for a detailed discussion.} eventually
+led to regulatory changes in several individual markets.\\
+In response to immediate policy concerns, the academic debate was
+initially framed rather narrowly around adequacy of speculation--the
+burning issue of the day--at the individual commodity market level and
+the ensuing academic analysis focused on the more mechanical effects of
+financialisation. With the benefit of hindsight, this approach seems to
+lack a fundamental understanding of the phenomenon it endeavoured to
+study and which consequences it attempted to address.\\
+Financialisation was a phenomenon global in nature; through the channel
+of index investment it affected the whole cross-section of liquid
+commodities at once, eventually spurring its transition away from a
+collection of idiosyncratic markets to its emergence as an asset class.
+Focusing on individual markets in this context thus seems limited. Most
+of the studies underpinning the regulatory response to financialisation
+took the form of pairwise correlation, causation and to some extent
+co-integration analysis, all of which are idiosyncratic in nature for
+they study single pairs of individual assets. Besides, some of these
+techniques since proved controversial and seem to produce results the
+quality of which may fall short of the standards that may reasonably be
+expected to lay the ground for legislative action. Although appealing,
+for it comes with the promise of prompt ``significant'' results, this
+approach misses a critical corollary of the substantial advent of a new
+category of players in a (set of) market(s): the alteration of market
+fundamentals it potentially induces, best observed in this context
+through the lens of commercial hedging pressure
+\citep{keynes_treatise_1930, hicks_value_1939}.\\
+While essential to the understanding of the phenomenon, the global
+nature of financialisation and its impact on market fundamentals
+therefore appear to have been originally overlooked and another
+approach, perhaps more refined, seems warranted.
+
+\medskip
+
+We strive to provide one in this study by taking a fundamentally
+different empirical perspective that is broader in scope. We consider
+the entire cross-section of actively traded commodities on futures
+markets and use a futures-based asset pricing framework that includes
+factors constructed using both theoretical fundamentals and liquidity
+considerations.\\
+The global nature of financialisation makes cross-sectional co-movement
+a cornerstone issue that the direct impact of increased market
+participation alone might not be able to fully explain for it
+potentially had deeper effects, for example on market fundamentals as
+our results suggest. Commodity futures markets have a history of being
+the classic physical commodity price risk shifting conduit for commodity
+specialists. Over the financialisation period we observe a decrease in
+effectiveness of commercial hedging pressure (CHP) at explaining
+commodity futures returns at the individual level accompanied by a more
+pronounced increase at the aggregate level. We further note an overall
+shift in the nature of hedger's behaviour away from the traditional
+Keynesian view of risk transfer with higher individual risk premiums
+over phases of cross-sectional contango as opposed to backwardation.
+Both patterns suggest that the phenomenon may have altered this
+long-standing paradigm of commercial risk transfer with the entry of
+long only commodity index traders (CITs) with very different hedging and
+volume demands from traditional participants. This change could have
+altered the hedging ontology in these markets and our asset pricing
+framework is tailored to detect these more subtle effects driven by
+changes in the nature of market participation.\\
+Factor model techniques are well suited to isolating common driving
+factors and detecting co-movement
+\citep{fama_common_1993, carhart_persistence_1997, asness_devil_2013, fama_five_factor_2015, hou_digesting_2015, asness_fact_2015, frazzini_betting_2014, asness_quality_2019}
+at a broader level, beyond individual pairs of assets, and are commonly
+used to study commodity market fundamentals
+\citep{schwartz_short_2000, miffre_momentum_2007, gorton_fundamentals_2012, cortazar_commodity_2013, yang_investment_2013, daskalaki_factors_2014, szymanowska_anatomy_2014, fernandez_skewness_2018, bakshi_understanding_2019, boons_basis_2019, sakkas_factor_2020};
+they consequently seem well adapted to study these two issues
+simultaneously. Building on theory we therefore develop a bespoke
+commodity-based asset pricing framework comprised of factor models based
+both on fundamentals as well as liquidity considerations.\\
+One of these is based on the Keynes-Hicks
+\citep{keynes_some_1923, keynes_treatise_1930, hicks_value_1939, hicks_value_1946}
+risk transfer approach to the term structure; the corresponding ``theory
+of normal backwardation'', complemented for the possibility of contango
+\citep{houthakker_restatement_1957, cootner_returns_1960}, postulates
+that futures prices for a given commodity are inversely related to the
+extent that commercial hedgers are short or long and using commercial
+hedging pressure (CHP) as a proxy for hedgers net market position we
+construct factor mimicking portfolios that capture the impact of hedging
+pressure as a systemic factor \citep{basu_capturing_2013}. The
+cross-sectional nature of financialisation
+\citep{cheng_financialisation_2014, basak_model_2016} further leads us
+to extend this paradigm by incorporating aggregate CHP (\textbf{CHP}), a
+market wide measure of hedging pressure first considered in
+\citet{hong_what_2012}. In this context, returns for individual
+commodities should be high in periods where \textbf{CHP} is low
+(\textbf{backwardation}) and low in periods where \textbf{CHP} is high
+(\textbf{contango}). Working's contending approach that relates futures
+price formation to storage costs in the theory of ``the price of
+storage'' \citep{working_theory_1949} forms the basis of another model
+that we consider where, following \citet{szymanowska_anatomy_2014} and
+\citet{fuertes_commodity_2015} who demonstrate that the term structure
+factor has explanatory power for the cross-section of commodity returns,
+we construct factor mimicking portfolios using roll-yield as a proxy for
+the front end shape of individual commodity term structures. We further
+consider a liquidity-based model following \citet{hong_what_2012} who
+find that open interest growth has predictive power for individual
+commodity returns and again, using the latter measure as a proxy for
+individual commodity liquidity, we construct long-short factor mimicking
+portfolios.
+
+\bigskip
+\bigskip
+
+We study the performance of these models on a set of twenty-four US
+traded commodities and six UK traded (London Metal Exchange) base metals
+over the 1997/2018 period that we divide into four distinct sub-periods:
+pre-financialisation (1997/2003); financialisation
+(2004/2008\footnote{Starting point based on earlier studies
+  \citep{baker_financialization_2021, christoffersen_factor_2014}.});
+financial crisis and aftermath, including loose monetary policy regimes
+that followed (2008/2013); and post-crisis (2014-2018).\\
+Consistent with earlier studies, we observe that mean returns for the US
+traded commodities are sharply higher over the financialisation period
+compared to pre-financialisation and this pattern extends to UK traded
+metals.
+
+\medskip
+
+Over the first period the cross-sectional average returns during phases
+of \textbf{backwardation} for both the US and UK commodities are
+positive and overall higher than during phases of \textbf{contango},
+providing broad support for an aggregate version of the Keynesian
+hedging pressure hypothesis. Over the second period this pattern
+reverses, with both the US and UK commodities having higher returns
+during phases of \textbf{contango} as opposed to \textbf{backwardation}.
+This change in pattern suggests the onset of financialisation altered
+the traditional risk shifting nature of hedger's behaviour, implied by
+the Keynesian hypothesis.\\
+This change of paradigm due to the arrival of financial investors, on
+the other hand, raises the question of whether they functioned as
+liquidity providers or demanders. Arguments have been put forward in
+favour of both possibilities with \citet{moskowitz_time_2012} arguing
+that financial investors provide liquidity and \citet{kang_tale_2020}
+taking the opposite stance. Our analysis of individual commodity
+returns' relation with both CHP and \textbf{CHP} before and during
+financialisation sheds a new light on this issue with our results
+suggesting that financial investors may have been liquidity demanders
+leading hedgers to become liquidity providers.
+
+\medskip
+
+\citet{goldstein_speculation_2014} and \citet{goldstein_commodity_2022}
+argue that the arrival of financial investors had an impact on the
+extent of normal backwardation in commodity futures markets. Based on
+their analysis we would expect our average CHP factor, based on
+backwardation as measured by hedger's positions (Keynesian perspective,
+theory of normal backwardation: \citet{keynes_treatise_1930},
+\citet{hicks_value_1939}, \citet{houthakker_speculators_1957},
+\citet{telser_futures_1958}), as well our term structure factor, based
+on backwardation as measured by roll yield (Working's perspective,
+theory of storage: \citet{working_price_1933},
+\citet{kaldor_speculation_1939}, \citet{working_theory_1948},
+\citet{brennan_supply_1958}, \citet{cootner_returns_1960},
+\citet{weymar_supply_1966}, \citet{danthine_information_1978},
+\citet{turnovsky_determination_1983}, \citet{schwartz_stochastic_1997}),
+to be best suited to measure the impact of financialisation.\\
+We analyse the pricing dynamics over the different periods by first
+studying the time series explanatory performance of the various factors
+on all the US traded commodities with the factors constructed using the
+latter set of commodities. The market-based factor outperforms the other
+three in the first period and, although its performance increases over
+the financialisation period, that of the CHP factor shows a greater
+improvement in a relative sense. The performance of the market factor is
+driven by agricultural and energy commodities in the first period while
+metals strongly contribute to the performance improvement observed over
+the second period. Similarly, the dramatic improvement of the CHP factor
+in the second period, is driven by the metals complex, particularly that
+of the long leg where they predominantly load. Average pairwise
+correlations amongst individual factors' best performing commodities
+increase across the board over the financialisation period, far beyond
+the average for the whole cross-section of US traded commodities. The
+increase is particularly strong for the long-short factors, in a
+relative sense, on which the metal complex loads significantly more
+during financialisation. This increase is due to the dramatic rise in
+average pairwise correlation amongst the US traded metals all of which
+exhibited high \(R^{2}\) with respect to the CHP factor during
+financialisation which in turn is due to their common low level of CHP
+over this period. The CHP factor model thus seems able to establish the
+strengthening link between a non-price attribute and price dynamics in
+the US metal sub-sector during financialisation.\\
+We explore this issue further by constructing the four factors
+independently with the top eight commodities for a given factor (factor
+picks) in each period\footnote{See section Section~\ref{sec-methods} for
+  further details.} and evaluating its performance on these selected
+commodities as well as on all US traded commodities. The results of this
+exercise provide evidence of convergence of Keynesian and Working's
+theories of the term structure in detecting price co-movement during
+financialisation and strongly suggest that the term structure related
+attributes (hedging pressure/roll) co-movement and price co-movement
+link was concentrated in the metals sub-sector.
+
+\medskip
+
+The UK traded base metals provide a useful set of assets to test how
+widespread were the changes in pricing dynamics brought about by the
+onset of financialisation. To that end, we examine the performance of
+the four factors on the six UK metals, when constructed from each set of
+factor picks. The results show that there was co-movement in global
+metals returns in the second period and that this co-movement could be
+detected by our term structure related models, particularly so by our
+hedging pressure-based model.
+
+\medskip
+
+The onset of the financial crisis and the monetary policy regimes that
+followed, on the other hand, also appear to have induced significant
+changes. Commodity futures returns fell dramatically into the crisis and
+the pricing results indicate the emergence of a systematic factor across
+the entire cross-section of the US commodities as well as evidence of
+cross-market linkages with the UK traded commodity subset. The
+post-crisis results, in contrast, show a substancial pullback in
+performance for the market factor across the board as well as evidence
+of decoupling between the US and UK markets. Besides, starting in the
+crisis the Keneysian paradigm of returns begins to revert with higher
+mean returns during low (\textbf{backwardation}) relative to high
+(\textbf{contango}) \textbf{CHP} phases and this pattern continues, more
+pronounced, over the post-crisis period. As pointed out in
+\citet{basu_definancialisation}, the financial crisis and ensuing
+accommodative monetary policy therefore seem to have initiated a process
+of reversion toward pre-financialisation fundamentals in the global
+commodity futures complex.
+
+\bigskip
+\bigskip
+
+Financialisation was an issue of such policy importance that it
+triggered legislative action. The debate was initially framed around
+adequacy of speculation, the burning issue of the day, and the ensuing
+academic analysis focused on the more mechanical effects of
+financialisation.\\
+With the benefit of hindsight, it appears this approach was perhaps too
+narrow, and it now seems necessary to address the phenomenon from a
+broader perspective. Commodity price dynamics appear to have altered
+substantially in quite different ways over the financialisation and the
+financial crisis periods and our commodity futures asset pricing factors
+based approach seems able to provide new insights into the nature of
+these changes: financialisation was a phenomenon endogenous to the
+commodity markets transmitted via the commodity futures markets and
+which effects were particularly strong for the metals sector while the
+crisis and its aftermath seems to have delivered an exogenous shock
+across the entire cross-section of liquid commodities and thereby
+potentially triggering a reversion to pre-financialisation dynamics.
+
+The initial view of financialisation was that it consisted of
+speculative flows which had the effect of driving up and creating bubble
+like conditions in commodity futures prices\footnote{\citet{masters_testimony_2008};
+  \citet{masters_accidental_2008}; \citet{unctad_global_2009};
+  \citet{deschutter_food_2010}; \citet{gilbert_how_2010};
+  \citet{gilbert_speculative_2010}; \citet{herman_not_2011};
+  \citet{schumann_hunger_2011}; \citet{singleton_investor_2013}.}.
+However, the fundamental question of the nature of the impact of
+financialisation across the entire cross-section of commodity futures
+markets has not yet been completely answered. We provide an empirical
+complement to a new stream of theoretical studies that try to model the
+impact of financialisation on various aspects of commodity futures
+markets\footnote{\citet{etula_broker-dealer_2013},
+  \citet{acharya_limits_2013}, \citet{cheng_convective_2014},
+  \citet{leclercq_equilibrium_2014}, \citet{sockin_informational_2015},
+  \citet{goldstein_speculation_2014}, \citet{ekeland_speculation_2016},
+  \citet{goldstein_commodity_2022}, \citet{ekeland_hedging_2019},
+  \citet{isleimeyyeh_role_2020}.} and demonstrate that the effects of
+financialisation extend beyond the mechanical effects induced by
+indexation as outlined in \citet{tang_index_2012} and
+\citet{basak_model_2016}.
+
+\newpage
+
+\section{Data \& methods}\label{sec-data-methods}
+
+\subsection{Background}\label{sec-background}
+
+The period from 1998 to 2008 saw an influx of investment into commodity
+index linked products most of which made its way into the commodity
+futures market. Popular commodity indexes whose goal was to track the
+broad movement of commodity prices became accessible by means of swaps,
+exchange traded funds and exchange traded notes and attracted at least
+\$100 billion of net super-hoc investment over the 1998-2008 period.
+
+\medskip
+
+Concerns over the consequences of this financialisation phenomenon
+eventually led to legislative changes including the approval of Rule 76
+FR 4752 issued by the US Commodity Futures Trading Commission (CFTC) on
+January 26\textsuperscript{th}, 2011. This provision emanates from the
+Dodd-Frank Wall Street and Consumer Protection Act of 2010 (Title VII,
+Section 737) that mandates the CFTC to use position limits to restrict
+the flow of speculative capital into a number of commodity markets. The
+Rule was approved in a close 3-2 vote and the ensuing rule-making
+process was extremely contentious with several commissioners (Michael
+Dunn and Scott D. O'Malia in particular) expressing reservations about
+the lack of supporting evidence and the Rule also triggering thousands
+of comment letters as well as a lawsuit against the CFTC spearheaded by
+two Wall Street trade groups, the International Swaps \& Derivatives
+Association (ISDA) and the Securities Industries \& Financial Markets
+Association (SIFMA)\footnote{ISDA \& SIFMA v US CFTC; Complaint,
+  1:11-cv-02146; December 2\textsuperscript{nd}, 2011.}.
+
+\medskip
+
+A world-wide debate ensued about the role of index funds in commodity
+markets. The first responses to the 2007/2008 crisis of escalating food
+and energy prices took the form of policy reports, many of which
+reasoned that the growth of commodity index funds came along with an
+influx of largely speculative capital that was responsible for driving
+commodity prices beyond their historic highs
+\citep{deschutter_food_2010, gilbert_speculative_2010, herman_not_2011, schumann_hunger_2011, unctad_global_2009}.\\
+Early US Senate investigations on the matter drew on pricing and trading
+data supplied by the CFTC as well as interviews with numerous experts
+including hedge fund manager Michael Masters who linked the growing
+presence of index investors in US agricultural and energy markets to the
+observed surges in both futures and cash prices
+\citep{masters_testimony_2008, masters_accidental_2008}. This contention
+has since come to be known as the Masters' hypothesis and was largely
+endorsed by the final US Senate report on the issue
+\citep{senate_excessive_2009}.\\
+At this stage, the question thrust on the academic sphere was whether
+``excessive speculation'' (understood as the market activity peculiar to
+index type investors) was linked to escalating energy and agricultural
+commodity prices. A number of ensuing academic studies, most of which
+used commodity specific correlation and causality based analysis have
+since disproved this contention: \citet{irwin_devil_2009},
+\citet{sanders_adequacy_2010}, \citet{sanders_impact_2011},
+\citet{sanders_new_2011}, \citet{irwin_commodity_2013},
+\citet{brunetti_commodity_2014}, \citet{hamilton_effects_2015} and
+\citet{bruno_financialisation_2017} investigated the issue in the
+context of the agricultural markets; meanwhile,
+\citet{buyuksahin_speculators_2011}, \citet{tokic_speculation_2012},
+\citet{fattouh_role_2013}, \citet{kilian_role_2014},
+\citet{knittel_simple_2016} and \citet{manera_modeling_2016} examined
+the energy markets while \citet{bohl_does_2013}, \citet{kim_does_2015}
+and \citet{boyd_prevalence_2016} studied both energy and agricultural
+markets and \citet{irwin_index_2011},
+\citet{irwin_financialisation_2012} as well as
+\citet{stoll_commodity_2011} examined the commodity markets in general.
+Other studies have underlined various alterations in commodity pricing
+dynamics over the period. \citet{gilbert_role_2014} reject the view that
+financialisation has not had any effects in the grains markets and
+demonstrate that trades originated by financial market participants, and
+specifically index investors, can move prices but tend to be typically
+volatility-reducing. \citet{juvenal_speculation_2015} contend that the
+oil price increase between 2004 and 2008 was mainly driven by the
+strength of global demand but that the financialisation process of
+commodity markets also played a role. Likewise,
+\citet{henderson_new_2015} show that non-information-based financial
+investments have important impacts on commodity prices.
+\citet{cheng_financialisation_2014}, on the other hand, show that in the
+case of index commodities, financialisation has transformed the risk
+sharing, and information discovery functions of commodity futures
+markets.
+
+\subsection{Data}\label{sec-data}
+
+Commodity index swaps, commodity index funds (CIFs), commodity-based
+exchange traded funds (ETFs) and notes (ETNs) or commodity linked notes
+(CLNs) were amongst the main investment vehicles that allowed
+institutional and retail investors to build up commodity exposure in the
+early 2000s
+\citep{boons_stock_2012, henderson_new_2015, irwin_index_2011, unctad_global_2009, schumann_hunger_2011}.
+Most of these products were primarily designed to track prominent
+commodity indexes among which the S\&P-GSCI, the most popular.\\
+Most of its constituents at the time of writing form the basis of the
+broad cross-section of commodities that we consider in this study:
+corn-\#2 yellow (XCBT), oats (XCBT), soybean meal (XCBT), soybean oil
+(XCBT), soybeans (XCBT), wheat-SRW (XCBT), cattle-feeder (XCME),
+cattle-live (XCME), lean hogs (XCME), cocoa (IFUS), coffee-C (IFUS),
+cotton-\#2 (IFUS), lumber (XCME), orange juice (IFUS), sugar-\#11
+(IFUS), natural gas (XNYM), crude oil-WTI (XNYM), gasoline (XNYM),
+heating oil (XNYM), copper (XCEC), gold (XCEC), palladium (XNYM),
+platinum (XNYM) and silver (XCEC). Unleaded gasoline, the NYMEX legacy
+contract for gasoline, stopped trading in 2006 when it was replaced by
+Reformulated Gasoline Blendstock for Oxygen Blending (RBOB) with the two
+futures series trading alongside for most of the year. For our NYMEX
+gasoline data series, we consider unleaded gasoline up to September
+1\textsuperscript{st}, 2006 and RBOB gasoline thereafter, date at which
+liquidity for the latter overtook that for the former.\\
+We also consider the UK metal complex with aluminium (XLME), copper
+(XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc
+(XLME).
+
+\medskip
+
+The commodity futures trading commission (CFTC) operates a comprehensive
+system of collecting information on market participants known as the
+large trader reporting program (LTRP) where it records and reports to
+the public position data on market participants who have position levels
+in excess of a particular market specific threshold\footnote{Current
+  reporting level thresholds available at:
+  \href{https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=&SID=970471b8455f4bab7db4110cfde50731&mc=true&r=SECTION&n=se17.1.15_103}{www.ecfr.gov}.}.
+The commission collects market data and position information daily from
+clearing members, futures commission merchants (FCMs) and foreign
+brokers and publishes corresponding summaries weekly in a series of
+market specific reports. In these reports, individual traders are
+categorised according to the nature of their trading activity on the
+basis of self-reported information\footnote{CFTC form 40. Available at:
+  \href{https://www.cftc.gov/sites/default/files/idc/groups/public/@forms/documents/file/cftcform40.pdf}{www.cftc.gov}.}
+that is subject to review by CFTC staff for reasonableness. Position
+information is then aggregated by category and asset type with each
+report providing an aggregation for a set of report specific categories
+and, for each category, a breakdown between futures only positions and
+positions in futures and options combined.\\
+In its legacy report, the commitment of trader report (COT) with data
+dating back to 1962, the CFTC distinguishes ``commercial'' and
+``non-commercial'' market participants where a ``commercial''
+participant is defined as one ``{[}\ldots{]} engaged in business
+activities hedged by the use of futures and option markets''\footnote{See
+  \href{https://www.gpo.gov/fdsys/pkg/CFR-1998-title17-vol1/xml/CFR-1998-title17-vol1-sec1-3.xml}{CFTC
+  regulation 1.3, 17 CFR 1.3(z)} for details.}. A third category,
+``non-reportable'', aggregates positions for participants not meeting
+the reporting threshold. In response to concerns related to category
+accuracy\footnote{See for example \citet{ederington_who_2002}.} the CFTC
+now refines its classification in the disaggregated commitment of trader
+report (DCOT) where participant categories include
+``Producer/Merchant/Processor/User'', ``Swap dealer'', ``Money manager''
+and ``Other reportable'' as well as in the supplemental commitment of
+trader report (SCOT) that details commodity index trader aggregate
+positions for thirteen agricultural commodity futures markets. Data for
+DCOT and SCOT date back to 2006 and 2007 respectively.\\
+We study the 1997/2018 period where we observe futures only position
+data from the COT report, the only CFTC report with data available for
+the whole period of interest; as well as futures term structure price
+and open interest data from Bloomberg.
+
+\subsection{Methods}\label{sec-methods}
+
+On the one hand, futures markets have a long history of serving
+commodity producers to alleviate their commodity price and output risks.
+\citet{keynes_treatise_1930} and \citet{hicks_value_1939} emphasise the
+``normal'' behaviour of naturally short hedgers outsourcing their
+commodity risk to naturally long commodity specialist speculators. This
+market configuration is referred to as ``backwardation'' where futures
+are expected to trade at a discount to spot prices, providing
+speculators with incentives to take the long side. The opposite market
+paradigm is referred to as ``contango''. Working
+\citep{working_price_1933, working_theory_1948, working_hedging_1953}
+and Kaldor \citep{kaldor_speculation_1939} somehow relax this
+``supply-of-speculative-services'' \citep{till_long_2007} approach by
+introducing processors and merchants, also commodity experts, on the
+hedgers side and relating the notions of backwardation and contango more
+directly to the term structure via the theory of storage where the shape
+of the front end of the term structure (basis) is directly related to
+the market price of storage.\\
+Financialisation, on the other hand, refers to the entry of financial
+investors into the commodity futures markets who, for the most part, are
+not commodity experts. Besides, these new market participants tend to
+exhibit herding like behaviour, often taking massive long-only positions
+on the whole cross-section of indexed commodities in an attempt to
+enhance returns while hedging against inflation and reaping further
+diversification benefits for portfolios with, in most cases, existing
+large positions across various asset classes
+\citep{brunetti_speculators_2016, boyd_prevalence_2016, cheng_convective_2014, juvenal_speculation_2015, singleton_investor_2013, tang_index_2012}.
+This contrasts with the traditional approaches of Keynes and Working and
+in this context the issues of co-movement and aggregate market
+participants behaviour seem particularly relevant.
+
+\medskip
+
+By grouping together assets by shared attribute dynamics in common
+portfolios, asset pricing techniques--and factor models in
+particular--are well suited to study co-movement
+\citep{fama_common_1993, carhart_persistence_1997, asness_devil_2013, fama_five_factor_2015, hou_digesting_2015, asness_fact_2015, frazzini_betting_2014, asness_quality_2019}.
+Careful, theory-based, attribute selection further enables a refined
+analysis of market fundamentals
+\citep{schwartz_short_2000, miffre_momentum_2007, gorton_fundamentals_2012, cortazar_commodity_2013, yang_investment_2013, daskalaki_factors_2014, szymanowska_anatomy_2014, fernandez_skewness_2018, bakshi_understanding_2019, boons_basis_2019, sakkas_factor_2020}.
+We therefore develop a futures-based asset pricing framework that
+includes factors constructed using both theoretical and liquidity
+considerations and use this framework to carry out our analysis over
+four periods of interest. The first, the pre-financialisation period,
+starts in 1997 and is naturally followed by financialisation, spanning
+the 2004/2008 period, and the financial crisis and its aftermath,
+spanning the 2008/2013 period. The last period spans the 2014/2018
+period starting with the beginning of the tapering/end of the US
+Quantitative Easing program (QE).\\
+Using the weekly price, open interest and market position data described
+above we construct market portfolios of individual commodity nearby
+futures as well as mimicking portfolios for market, commercial hedging
+pressure, term structure and liquidity risk factors in returns. While
+our market portfolios are long only, equally weighted portfolios of
+particular commodity sets, our other mimicking portfolios for risk
+factors are constructed as combinations of two sub-portfolios (legs),
+one held long, one held short, which respective constituents are pooled
+on a weekly basis according to risk factor specific criteria.\\
+For each leg, the position weight for a particular asset for a
+particular period is contingent on the value of the corresponding
+sorting variable and its rank relative to the other assets in the pool.
+The sorting variable values for the asset pool are first rescaled so
+that the highest (lowest) value becomes 1 (0). Weights are then
+determined pairwise, starting from the extremes with the highest and
+lowest figures. A coefficient \(\alpha\) is determined by dividing their
+difference (1 in this case) by the mean of the rescaled values. The high
+figure is attributed a score of \(\frac{1}{n} \times \alpha\) where
+\(n\) is the number of assets in the pool while the score for the low
+figure is \(\frac{1/n}{\alpha}\). The operation is repeated for the pair
+of assets showing the second highest and second lowest values for the
+sorting variable and so on until all the assets in the pool are
+attributed a score. The individual asset weights are then determined by
+dividing each score by the sum of the scores.\\
+The period return for a particular mimicking portfolio is calculated as
+the difference between the weighted average return for constituents of
+the long portfolio and that for the constituents of the short portfolio.
+i.e, return on the mimicking portfolio for risk factor \(i\) (\(f_{i}\))
+for period \(t\):
 
 \[r_{t}^{f_{i}}=\sum_{j=1}^{x}w^{long}_{j,t} \times r_{j,t}-\sum_{j=n-x}^{n}w^{short}_{j,t} \times r_{j,t}\]
-\(n\equiv\) number of commodities in the set considered for mimicking portfolio construction.\\
+\(n\equiv\) number of commodities in the set considered for mimicking
+portfolio construction.\\
 \(x = n \cdot s\).\\
 \(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
-\(w^{*}_{j,t}\equiv\) period \(t\) weight for commodity \(j\) on the long or short leg.\\
-\(r_{j,t}\equiv\) period \(t\) front contract return for commodity \(j\).\\
+\(w^{*}_{j,t}\equiv\) period \(t\) weight for commodity \(j\) on the
+long or short leg.\\
+\(r_{j,t}\equiv\) period \(t\) front contract return for commodity
+\(j\).\\
 \(j\equiv\) commodity rank in the ordered set \(Y_{t}^{f_{i}}\).\\
-\(Y_{t}^{f_{i}}\equiv\) period \(t\) ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is specific to \(f_{i}\).
-
-\medskip\setlength{\parindent}{0pt}
-
-For our portfolio CHP (commercial hedging pressure), we sort the set of commodities considered on past twenty-six-week average CHP from lowest to highest.
-The bottom third constituents (lowest \(\overline{CHP}\)s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg:
+\(Y_{t}^{f_{i}}\equiv\) period \(t\) ordered set of the commodities
+considered for mimicking portfolio construction where the ordering rule
+is specific to \(f_{i}\).
+
+\medskip
+
+For our portfolio CHP (commercial hedging pressure), we sort the set of
+commodities considered on past twenty-six-week average CHP from lowest
+to highest. The bottom third constituents (lowest \(\overline{CHP}\)s)
+of the corresponding ordered set form the long leg of the portfolio
+while the top third form the short leg:
 
@@
 \(\overline{CHP_{j}}=\frac{1}{26}\sum_{k=0}^{25}\frac{L_{j,t-k}}{L_{j,t-k}+S_{j,t-k}}\)\\
-\(L_{j,t}\equiv\) number of long positions held by commercial hedgers for period \(t\) on the futures series of commodity \(j\).\\
-\(S_{j,t}\equiv\) number of short positions held by commercial hedgers for period \(t\) on the futures series of commodity \(j\).
-
-\medskip\setlength{\parindent}{0pt}
-
-For our portfolio TS (term structure), we sort the set of commodities considered on past twenty-six-week average roll-yield from highest to lowest.
-The bottom third constituents (highest \(\overline{RY}\)s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg:
+\(L_{j,t}\equiv\) number of long positions held by commercial hedgers
+for period \(t\) on the futures series of commodity \(j\).\\
+\(S_{j,t}\equiv\) number of short positions held by commercial hedgers
+for period \(t\) on the futures series of commodity \(j\).
+
+\medskip
+
+For our portfolio TS (term structure), we sort the set of commodities
+considered on past twenty-six-week average roll-yield from highest to
+lowest. The bottom third constituents (highest \(\overline{RY}\)s) of
+the corresponding ordered set form the long leg of the portfolio while
+the top third form the short leg:
 
@@
 \(\overline{RY_{j}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{F_{j,t-k}^{1}}{F_{j,t-k}^{2}} - 1)\)\\
-\(F_{j,t}^{1}\equiv\) period \(t\) close price for commodity \(j\) first nearby futures contract.\\
-\(F_{j,t}^{2}\equiv\) period \(t\) close price for commodity \(j\) second nearby futures contract.
-
-\medskip\setlength{\parindent}{0pt}
-
-For our portfolio OI (open interest), we sort the set of commodities considered on past twenty-six-week average front contract open interest growth from highest to lowest.
-The bottom third constituents (highest \(\overline{OI^{\Delta \%}}\)s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg.
+\(F_{j,t}^{1}\equiv\) period \(t\) close price for commodity \(j\) first
+nearby futures contract.\\
+\(F_{j,t}^{2}\equiv\) period \(t\) close price for commodity \(j\)
+second nearby futures contract.
+
+\medskip
+
+For our portfolio OI (open interest), we sort the set of commodities
+considered on past twenty-six-week average front contract open interest
+growth from highest to lowest. The bottom third constituents (highest
+\(\overline{OI^{\Delta \%}}\)s) of the corresponding ordered set form
+the long leg of the portfolio while the top third form the short leg.
 
@@
 \(\overline{{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{{OI}_{j,t-k}}{{OI}_{j,t-k-1}} - 1)\)\\
-\(OI_{j,t}\equiv\) open interest at close of period \(t\) on the front (nearby) contract for commodity \(j\).
-
-\medskip\setlength{\parindent}{0pt}
-
-We use a time series regression approach where we start with regressions of the US traded individual commodity weekly front contract returns on returns to the mimicking portfolio for a particular risk factor where the portfolio is constructed using the whole cross-section of US traded commodities.
-The corresponding \(R^{2}\)s are averaged and the process is repeated for each of our four risk factors (market, hedging pressure, term structure and liquidity) and periods (1997/2003, 2004/2008, 2008/2013 and 2014/2018).
-For the long-short factors the results are reported independently for models where the regressor is the factor itself or one of its legs (long vs.~short).
-The same operation is repeated for the two (\(p=2\)) and three (\(p=3\)) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectively, as well as for the four (\(p=4\)) factor model case where all the risk factor mimicking portfolios are included.
-Results are reported for the one-factor model case with the other results available upon request.
-
-\medskip\setlength{\parindent}{0pt}
-
-For each period we also implement the analysis described above over periods of low and high aggregate CHP (\textbf{CHP}), a notion that we believe is particularly relevant in the context of financialisation where issues of co-movement and aggregate market behaviour play a central role.
-We define \textbf{CHP} as the cross-sectional average of individual CHPs for a particular pool of assets.
-i.e., period \(t\) \textbf{CHP} for asset pool \(x\):
-
-\[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}\]
-\(n\equiv\) number of commodities in set \(x\).\\
-\(CHP_{i,t}\equiv\) period \(t\) CHP for commodity \(i\) as defined above.
-
-\medskip\setlength{\parindent}{0pt}
-
-We further define aggregate backwardation (\textbf{backwardation}) and contango (\textbf{contango}) \textbf{CHP} regimes as, for a given period, \textbf{CHP} levels below and above the period's median respectively and, in contrast with (Hong and Yogo, 2012) who aggregate across sub-sectors, the asset pool we consider for \textbf{CHP} construction include the whole cross-section of US traded commodities.
-
-\medskip\setlength{\parindent}{0pt}
-
-In the next part of the analysis, our mimicking portfolios for risk factors, constructed from the set of all US traded commodities are used as commodity picking devices on the latter commodity set.
-For each risk factor and period, individual US traded commodity front returns are regressed on returns for the corresponding mimicking portfolio.
-Individual commodities are sorted by \(R^{2}\) accordingly from highest to lowest and the top third (highest \(R^{2}\)s) are selected as commodity picks for the risk factor for the period.
-i.e, set of picks \(P_{t}^{f_{i}}\) for risk factor \(i\) (\(f_{i}\)) over period \(t\):
+\(OI_{j,t}\equiv\) open interest at close of period \(t\) on the front
+(nearby) contract for commodity \(j\).
+
+\medskip
+
+We use a time series regression approach where we start with regressions
+of the US traded individual commodity weekly front contract returns on
+returns to the mimicking portfolio for a particular risk factor where
+the portfolio is constructed using the whole cross-section of US traded
+commodities. The corresponding \(R^{2}\)s are averaged and the process
+is repeated for each of our four risk factors (market, hedging pressure,
+term structure and liquidity) and periods (1997/2003, 2004/2008,
+2008/2013 and 2014/2018). For the long-short factors the results are
+reported independently for models where the regressor is the factor
+itself or one of its legs (long vs.~short). The same operation is
+repeated for the two (\(p=2\)) and three (\(p=3\)) factor model cases,
+where regressors include in turn all combinations of any two and three
+risk factors respectively, as well as for the four (\(p=4\)) factor
+model case where all the risk factor mimicking portfolios are included.
+Results are reported for the one-factor model case with the other
+results available upon request.
+
+\medskip
+
+For each period we also implement the analysis described above over
+periods of low and high aggregate CHP (\textbf{CHP}), a notion that we
+believe is particularly relevant in the context of financialisation
+where issues of co-movement and aggregate market behaviour play a
+central role. We define \textbf{CHP} as the cross-sectional average of
+individual CHPs for a particular pool of assets. i.e., period \(t\)
+\textbf{CHP} for asset pool \(x\):
+
+\[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}\] \(n\equiv\)
+number of commodities in set \(x\).\\
+\(CHP_{i,t}\equiv\) period \(t\) CHP for commodity \(i\) as defined
+above.
+
+\medskip
+
+We further define aggregate backwardation (\textbf{backwardation}) and
+contango (\textbf{contango}) \textbf{CHP} regimes as, for a given
+period, \textbf{CHP} levels below and above the period's median
+respectively and, in contrast with \citep{hong_what_2012} who aggregate
+across sub-sectors, the asset pool we consider for \textbf{CHP}
+construction include the whole cross-section of US traded commodities.
+
+\medskip
+
+In the next part of the analysis, our mimicking portfolios for risk
+factors, constructed from the set of all US traded commodities are used
+as commodity picking devices on the latter commodity set. For each risk
+factor and period, individual US traded commodity front returns are
+regressed on returns for the corresponding mimicking portfolio.
+Individual commodities are sorted by \(R^{2}\) accordingly from highest
+to lowest and the top third (highest \(R^{2}\)s) are selected as
+commodity picks for the risk factor for the period. i.e, set of picks
+\(P_{t}^{f_{i}}\) for risk factor \(i\) (\(f_{i}\)) over period \(t\):
 
@@
 \(x = n \cdot s\).\\
-\(n\equiv\) number of commodities in the set considered for the picking exercise (twenty-four here).\\
+\(n\equiv\) number of commodities in the set considered for the picking
+exercise (twenty-four here).\\
 \(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
-\(P_{j}\equiv\) commodity pick \(j\) for risk factor \(f_{i}\) over period \(t\)\\
+\(P_{j}\equiv\) commodity pick \(j\) for risk factor \(f_{i}\) over
+period \(t\)\\
 \(j\equiv\) rank in the ordered set \(Y_{t}^{f_{i}}\)\\
 \[Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}\]
-\(n\equiv\) number of commodities in the set considered for picking (twenty-four here).\\
-\(\tilde{R_{j}^{2}}\equiv\) risk factor \(f_{i}\) returns' explanatory power on commodity \(j\) nearby futures returns over period \(t\) as defined above.
-
-\medskip\setlength{\parindent}{0pt}
-
-For each period we report the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every set of picks.
-
-\medskip\setlength{\parindent}{0pt}
-
-In the last part of the analysis, for each period our mimicking portfolios for risk factors in returns are constructed using each set of commodity picks independently as the asset pool for portfolio construction.
-A similar time series approach to that described above is then implemented using these newly formed mimicking portfolios.
-In this case, a first set of dependent variables includes the sets of commodity picks themselves, a second set includes the whole cross-section of US traded commodities while a third set includes the six UK traded metals considered in the study.
-
-\bigskip\bigskip\setlength{\parindent}{0pt}
-
-By relating returns on attribute based risk factor mimicking portfolios to returns on individual as well as group of assets, our time series approach therefore draws the link between attribute and pricing dynamics over different, theory-based market regimes, and thereby enables us to study market fundamentals and co-movement simultaneously, two key issues in the financialisation phenomenon.
+\(n\equiv\) number of commodities in the set considered for picking
+(twenty-four here).\\
+\(\tilde{R_{j}^{2}}\equiv\) risk factor \(f_{i}\) returns' explanatory
+power on commodity \(j\) nearby futures returns over period \(t\) as
+defined above.
+
+\medskip
+
+For each period we report the proportion of time each pick is held in
+the long and (/or) short leg of the corresponding risk factor mimicking
+portfolio as well as the average pairwise correlation amongst every set
+of picks.
+
+\medskip
+
+In the last part of the analysis, for each period our mimicking
+portfolios for risk factors in returns are constructed using each set of
+commodity picks independently as the asset pool for portfolio
+construction. A similar time series approach to that described above is
+then implemented using these newly formed mimicking portfolios. In this
+case, a first set of dependent variables includes the sets of commodity
+picks themselves, a second set includes the whole cross-section of US
+traded commodities while a third set includes the six UK traded metals
+considered in the study.
+
+\bigskip
+\bigskip
+
+By relating returns on attribute based risk factor mimicking portfolios
+to returns on individual as well as group of assets, our time series
+approach therefore draws the link between attribute and pricing dynamics
+over different, theory-based market regimes, and thereby enables us to
+study market fundamentals and co-movement simultaneously, two key issues
+in the financialisation phenomenon.
 
@@
 
-\hypertarget{results}{%
-\section{Results \& discussion}\label{results}}
-
-The descriptive statistics for the commodity series considered in the study displayed in table \ref{tab:stats-no-regimes} show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9\% significant at the 5\% level vs.~6.9\% with a 10\% significance in the pre-financialisation period.
-The increase is even more pronounced for an equally weighted portfolio of UK traded assets (metals), 2.47\% (not significant) to 21.8\% (significant at the 10\% level), which sets out the global nature of the phenomenon.
-Most commodities show a higher mean return while five--Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)--show a lower figure with five significant figures--Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)--against none pre-financialisation.
-Sugar-\#11 wins the race with a mean return increasing from -4.6\% to 24.9\% followed by copper with sizeable increases for both markets: 1.5\% to 28.2\% (XCEC) and 0.5\% to 28.6\% (XLME).\\
-The pattern of results for volatilities is similar although the increase is less pronounced.
-Both equally weighted portfolios shows an increase, more pronounced for the UK assets, 10\% to 13.6\% (US) vs.~15.7\% to 26.9\% (UK), while out of the thirty assets, eleven show a drop in volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C (IFUS), Lumber (XCME), Sugar-\#11 (IFUS), Natural gas (XNYM), Crude oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
-Financialisation seems however to have impacted the commodity complex beyond these mechanical effects of increased long participation ensuing from the entry on index type investments as our results suggest next.
-
-\medskip\setlength{\parindent}{0pt}
-
-The cross-sectional nature of financialisation naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure.
-The traditional Keynesian hedging pressure paradigm postulates a negative relationship between the return on an individual commodity futures and its hedging pressure.
-The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where \textbf{CHP} is low and vice et versa.
-In table \ref{tab:stats-regimes} the mean returns are shown over high (\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP} regimes for each time period.\\
-Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of \textbf{backwardation} as compared to \textbf{contango}, with the difference being statistically significant at the 10\% level for two commodities, at the 5\% level for one and at the 1\% level for another.
-For the remaining six commodities the higher mean return during \textbf{contango} is not statistically significant for any of them.
-For the six UK commodities, all metals, five of them had higher mean returns during phases of \textbf{backwardation} as compared to \textbf{contango} in the first period, with one of these differences being statistically significant at the 10\% level while for the remaining asset (Zinc) the higher mean return during \textbf{contango} is not statistically significant.
-An equally weighted portfolio of the twenty-four US commodities had a mean return of 15.4\% during \textbf{backwardation} phases, statistically significant at the 1\% level, and a mean return of -1.1\% during \textbf{contango}, both in the first period, with the difference between them statistically significant at the 5\% level.
-The corresponding figures for an equally weighted portfolio of the UK metals were 4.4\% and 0.3\% respectively.
-These results provide broad support for an aggregate version of the Keynesian hedging pressure hypothesis and suggest that hedgers in the aggregate were engaged in risk transfer during this period.\\
-Over the second period the pattern essentially reverses.
-For the twenty-four US commodities over this period, fourteen have higher mean returns during phases of \textbf{contango} over \textbf{backwardation}.
-Four of the six UK metals achieved higher mean returns over \textbf{contango} relative to \textbf{backwardation} phases with the difference being statistically significant for one commodity.
-The equally weighted US portfolio had a mean return of 15.7\% over \textbf{backwardation} against 16.2\% during phases of \textbf{contango}, both statistically significant at the 10\% level.
-The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 8\% during \textbf{backwardation} rising to 35.6\% during \textbf{contango}.
-
-\medskip\setlength{\parindent}{0pt}
-
-The onset of financialisation thus seems to have engendered a change in the nature of hedger's behaviour, at the aggregate level in particular, taking it away from the traditional Keynesian view of risk shifting.
-This phenomenon has been noted in earlier theoretical and empirical work (Danthine, 1978; Stout, 1998) in different contexts from which two competing models of behaviour have emerged.\\
-The information arbitrage model (Danthine, 1978; Grossman and Stiglitz, 1980; Kyle, 1989) implies that hedgers may often be seeking out counterparties to trade with rather than being purely passive.
-This issue is also raised in both Cheng and Xiong (2014) and Stulz (1996) who point out that hedgers may be taking a view on prices just as speculators do.
-In fact, by hedging away some of their risk, hedgers are able to speculate more heavily based on their disagreement against speculators regarding futures price movement (Simsek, 2013), which fits into a heterogeneous expectation theory of speculation\footnote{Hirshleifer (1975); Hirshleifer (1976); Hirshleifer (1977)}.
-As Stout (1998) points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves speculation as this form of trading is regarded as non-productive\footnote{Duffie (2014) also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.}.\\
-In the second model hedgers are seen as liquidity providers as in Kang et al.
-(2020) with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
-Table \ref{tab:time-reg-US-CHP} supports this view.
-We regress commodity futures front returns on individual commercial hedging pressure (CHP) as well as aggregate CHP (\textbf{CHP}), our market wide measure of CHP, in separate models and find that the explanatory power of CHP at the individual commodity level decreases over the financialisation period with the US cross-sectional average \(R^{2}\) falling down to 20.8\% from 25.8\% in the previous period while that of \textbf{CHP} increases (7.1\% vs 5.4\%).
-Financialisation therefore seems to have had the effect of loosening the extent to which futures risk premiums relate to commodity specific commercial hedging motives while strengthening that to which they relate to broader dynamics such as cross-sectional liquidity provision.
-The pattern is strongest for the metals sector where the average \(R^{2}\) drops down to 19.1\% from 28.1\% between the two periods at the individual level while it rises from 8.4\% to 15.7\% at the aggregate level.
-The symmetry breaks in the crisis period, with the US cross-sectional average \(R^{2}\) at the individual level bouncing back up (22.5\% vs 20.8\%) while that at the aggregate level rises further (14.7\% vs 7.1\%), before eventually resuming post-crisis with a further rise at the individual level (27.2\% vs 22.5\%) and a drop at the aggregate level (7.5\% vs 14.7\%) suggesting a return to legacy commodity specific dynamics.
-
-\bigskip\bigskip\setlength{\parindent}{0pt}
-
-Using our bespoke commodity-based asset pricing framework we strive to shed new light on the phenomenon by first regressing returns series for the twenty four individual US commodities against our factor mimicking portfolios independently.
-The resulting individual explanatory powers (\(R^2\)s), once averaged by factor and period, offer a refined perspective on the relation between return and factor attribute co-movement.
-A low figure indicates low cross-sectional return co-movement for, in this context, return on the corresponding factor mimicking portfolio only has explanatory power on return for commodities that are constituents of one of its legs over the corresponding period.
-The explanatory power for the other commodities is typically low or even 0 for the case where commodities are perfectly uncorrelated with one-another.
-A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities; and therefore provides evidence that pairwise return correlation relates to factor attribute.\\
-The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \ref{tab:time-reg-US-facts-US}.
-Over the first period the market factor has the best average time series performance with the highest average \(R^{2}\) with all three futures market factors performing poorly, indicating that the commodities with extreme factor attributes (high or low CHP for example) are uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of high and low \textbf{CHP} (below period median).
-The two factor models average \(R^{2}\)s (available upon request) are roughly the sum of the one factor \(R^{2}\)s indicating that the factors are almost orthogonal over this period.\\
-The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average \(R^{2}\) increasing to 8.2\% in the second period relative to 1.7\% in the first with this improvement coming from the long leg that shows a greater improvement (4.5\% to 15.1\%) relative to the short (3\% to 4\%), suggesting that ``normally'' backwardated commodities (Keynesian perspective) have higher correlation with the rest of the commodity cross-section, and thereby bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period.
-The performance of the market factor also improves though not by as much in a relative sense (21.6\% from 11.7\%) and both the term structure factor and the open interest growth factor show a much smaller improvement in performance with smaller differences between legs.
-Over all periods, all of our factor models show similar performance across regimes of high and low \textbf{CHP}.
-
-\medskip\setlength{\parindent}{0pt}
-
-We next investigate the top eight of the US traded commodities which achieved the highest time series \(R^{2}\) for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \ref{tab:picks}.\\
-For the CHP factor the commodities that achieve high \(R^{2}\) in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor.
-The same applies to the open interest and term structure factors with CHP replaced by open interest growth and roll yield respectively; while for the market factor the picks are those that co-vary most strongly with the market factor over that period.\\
-For the CHP factor, we observe a change in the picks between the first and the second period; the picks in the first period included five agricultural commodities and three metals while in the second period they include all the five base and precious metals and only three agricultural commodities.
-This pattern is also visible for the term structure factor for which there are four metals (copper, silver, gold and platinum) picks in the second period against two in the first (palladium and platinum) as well as for the open interest nearby growth factor for which there are three metals (silver, gold and platinum) picks in the second period against one in the first (platinum).
-The market factor has three metal picks in the second period (palladium, gold and silver) while all the picks in the first period were agricultural or energy commodities.\\
-Over the third period, the average CHP factor shows the same metal picks with the agriculturals replaced by energy commodity; the open interest nearby growth factor still has three metal picks with gold swapped for copper and both the market and term structure factors have one, copper.\\
-The table also shows the proportion of time that these picks were constituents of the corresponding factor.
-All the picks of the long-short factors (average CHP, open interest nearby growth and term structure factors) were constituents of the corresponding factor for some proportion of time in all of the time periods.
-In this respect, there is a contrast between the first and second periods with the average CHP and open interest nearby growth factor picks appearing predominantly on the long side of the corresponding factor in the second period, as opposed to both legs in the first.
-The pattern is particularly strong for the metals and energy commodities respectively, with the exception of copper for the average CHP factor that lives in the short leg a higher proportion of the time over the financialisation period.
-The pattern is reversed for the term structure factor where the picks appear predominantly on the short leg in the second period, as opposed to both legs in the first with the pattern again strongest for the metals.
-This behaviour continues over the third period for the average CHP and open interest nearby growth factors and indicates that their picks consistently exhibited low commercial hedging pressure and high front contract open interest growth respectively while indicating that the term structure factor picks showed low roll yield in the first and second period.
-
-\medskip\setlength{\parindent}{0pt}
-
-In table \ref{tab:correlations}, we show the average pairwise returns correlation between each set of picks in each time period.
-Following on form the earlier observations, this exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.\\
-In the first period the average picks pairwise correlation for the long-short factors ranges from 7.1\% (term structure factor picks) to 12.4\% (open interest factor picks) while the market factor picks show the highest figure (23.7\%).
-In the second period the figures for the long-short factors rise sharply; up to 22.9\% from 8.1\% for the average CHP factor picks, up to 32.4\% from 12.4\% for the open interest factor picks and up to 23.4\% from 7.1\% for the term structure factor picks.
-This increase is stronger than that for the market factor picks in a relative sense and is a consequence of the dramatic increase in average pairwise price correlation amongst the US traded metals which dominate the average CHP factor set of picks and which presence is stronger amongst both the open interest and term structure factor sets of picks over the financialisation period.
-The higher figures for the open interest factor are driven by the strong presence of the energy complex amongst the corresponding picks.
-The latter exhibits much higher average pairwise correlations than the other sectors in both periods although lower in the second relative to the first which reinforces the role played by the metals in the sharp increase in average pairwise correlation amongst picks for this factor.\\
-With regards to \textbf{CHP} regimes, although not very pronounced, a pattern is noticeable.
-For the market, open interest and term structure factor picks, average pairwise correlations are stronger over phases of \textbf{contango} in the first period and over phases of \textbf{backwardation} in the financialisation period, eventually reverting back to being stronger over \textbf{contango} phases in the crisis period with the CHP factor sets of picks showing the opposite pattern.
-Overall, these results suggest an increase in correlation between non-price attributes co-movement and price co-movement over the financialisation period.
-It is also interesting to note that US traded metals returns were negatively correlated with the rest of US traded commodities in the first period and positively in the second.
-
-\medskip\setlength{\parindent}{0pt}
-
-To further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their explanatory performance on these sets of picks over the four periods independently.
-The results are shown in table \ref{tab:time-reg-picks-facts-picks}.
-The long-short factors for a particular attribute select the top and bottom two of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks.
-In the absence of price co-movement between the picks, the market factor will achieve an average \(R^{2}\) of around 12.5\%\footnote{Market factor lemma: \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\) size of market portfolio (eight here).}, while there is no non-zero \(R^{2}\) lower bound for the corresponding long-short factors.\\
-A high average \(R^{2}\) for the market factor is indicative of strong price co-movement.
-In this respect, the most remarkable change in performance in a relative sense is that of the market factor built from the CHP factor sets of picks with the average \(R^{2}\) more than doubling, from 18.6\% up to 38.1\%.
-For the long-short factors on the other hand it is indicative of simultaneous attribute and price co-movement.
-For the factors built from the market factor picks the increase is strongest in a relative sense for the CHP factor with the \(R^{2}\) more than doubling, going from 5.6\% in the first period up to 12.4\% in the second with the increase stronger for the long leg (17.1\% vs.~27.9\%) relative to the short (16.5\% vs.~21.4\%).
-In the case of the factors built from the CHP factor picks, the CHP factor built with its own picks shows a remarkable increase in a relative sense with the \(R^{2}\) tripling, from 7.2\% to 21.4\% and the long leg showing a much greater increase relative to the short (10.4\% to 31.1\% vs.~8.3\% to 9.8\%).
-The performance of the term structure factor built from the CHP factor sets of picks also shows a sizable increase in a relative sense, from 3.5\% to 5.3\% and even more remarkable in this case is the substantial increase in performance of the short leg, from 6.3\% to 15.7\% relative to the long (7.5\% to 9.8\%).
-The pattern is reversed for the CHP factor built from the term structure factor picks where the average \(R^{2}\) increases from 4.7\% to 8\% with the performance of the long leg increasing from 11.9\% to 28.1\% vs.~5.5\% to 9.1\% for the short.
-The performance of the term structure factor constructed from its own sets of picks also shows a substantial increase, from 5.1\% to 8.4\% with, here again the increase in performance relatively stronger for the short leg, from 6\% to 16.1\% vs.~7.6\% to 12.1\% for the long.\\
-Taken together with the previous results showing that the metal complex predominantly loads on the long and short legs of the original CHP and term structure factors respectively, these results provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation perhaps as a result of spillover effects between the corresponding futures and spot markets as suggested in Basak and Pavlova (2016).
-
-\medskip\setlength{\parindent}{0pt}
-
-In table \ref{tab:time-reg-US-facts-picks} we assess the performance of the same factors on all the commodities instead of just the picks.
-While the average \(R^{2}\)s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table \ref{tab:time-reg-picks-facts-picks}.
-In contrast, the average CHP factor built with average CHP factor picks shows a smaller absolute increase in average \(R^{2}\) indicating that the link between CHP co-movement and price co-movement is stronger amongst the picks which are predominantly metals.
-Taken together, the results in tables \ref{tab:time-reg-picks-facts-picks} and \ref{tab:time-reg-US-facts-picks} suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.\\
-To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in table \ref{tab:time-reg-UK-facts-picks}.
-In the first period, although all sets of picks, except that of the market factor, included at least one metal, the average \(R^{2}\)s are very low; close to zero in most cases.
-These figures drastically increase across the board in the financialisation period and show a pattern similar to that observed in the US complex.
-The market factor built from the CHP and term structure factor sets of picks shows the sharpest increase in performance, relative to using the other sets of factor picks; rising to 20.1\% from 1.5\% and to 15\% from 0.8\% respectively.
-The increase in \(R^{2}\) for the market factor built with market factor picks is more modest, providing further evidence of concentration of co-movement in the metals sector during financialisation.\\
-Here again the change in performance for the CHP and term structure factor legs stands out where the factors are built with their own as well as each other's sets of picks.
-The average \(R^{2}\) for the long leg of the CHP factor built with its own sets of picks increases from 1\% to 11\% while the short leg shows no significant change.
-The opposite holds for the term structure factor built from its own set of picks with the short leg performance increasing from 0.1\% to 14\% while that of the long leg remains below 1\%.
-Building these factors from each other's sets of picks produces a similar pattern with the performance of the long leg of the CHP factor built from the term structure factor picks increasing from 0.7\% to 11.4\%; a much greater increase relative to the short leg although in this case the latter also shows a sizable increase in performance (0.3\% to 6\%).
-The performance of the short leg of the term structure factor built from the CHP factor sets of picks on the other hand increases from 0.3\% to 19.2\% while the performance for the long leg in the second period remains below 1.5\%.\\
-Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working's term structure paradigms.
-There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of Kang et al.
-(2020) who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
-
-\bigskip\bigskip\setlength{\parindent}{0pt}
-
-The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results.
-Returns fall sharply relative to the financialisation period (table \ref{tab:stats-no-regimes}) with eighteen US commodities along with all six UK traded metals showing lower mean returns.
-Returns for equally weighted portfolios of both sets of assets fall down to 9.4\% and 5.3\% from 15.9\% and 21.8\% respectively.
-Returns are mostly higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:stats-no-regimes}) with fifteen US assets and five of the UK traded metals showing higher mean returns in \textbf{backwardation} and the pattern extending to equally weighted portfolios of the two sets of assets.
-Volatility is moderately higher for both sets with fifteen US commodities and three UK metals showing higher figures and interestingly eminently higher over phases of \textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none of the UK traded metals show higher volatility figures over \textbf{backwardation} phases.
-The symmetry between the dynamics of CHP and \textbf{CHP}'s explanatory power on individual commodity returns breaks in the crisis period with both now seemingly converging; the US cross-sectional average \(R^{2}\) at the individual level bouncing back up (22.5\% vs 20.8\%) while that at the aggregate level rises further (14.7\% vs 7.1\%).\\
-The performance of the market factor dominates the US commodity complex over the period with a 50\% increase in mean average \(R^{2}\) to over 30\% (table \ref{tab:time-reg-US-facts-US}) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
-The average pairwise correlation amongst the market factor picks increases beyond 50\% while there is a leveling in that amongst the picks of the long-short factors as shown in table \ref{tab:correlations}.
-Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table \ref{tab:time-reg-US-facts-picks}).\\
-Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
-Table \ref{tab:time-reg-UK-facts-picks} provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average \(R^{2}\) increasing to 31.7\% from 10.2\% in the previous period.
-
-\medskip\setlength{\parindent}{0pt}
-
-The returns pullback continues into the post-crisis period (table \ref{tab:stats-no-regimes}) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2\% and 2.7\% respectively.
-Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
-The figures for the equally weighted portfolios of US and UK assets drop to 9.9\% and 16.2\% respectively, very close to pre-financialisation levels.\\
-The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (table \ref{tab:stats-no-regimes}) with mean returns higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:stats-no-regimes}), more so than over the crisis period with seventeen US commodities showing higher mean returns over \textbf{backwardation} phases.
-The difference is significant at the 5\% level for Lumber (XCME) and at the 10\% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of \textbf{contango}.
-The pattern is more pronounced for the UK traded subset with all six assets showing higher mean returns in \textbf{backwardation} with the difference significant at the 1\% level for Nickel-primary (XLME), 5\% level for Aluminium (XLME) and 10\% level for Zinc (XLME).
-It also extends to equally weighted portfolios of US and UK traded assets that both show higher mean returns during \textbf{backwardation} with the difference significant at the 5\% level for the UK portfolio and the figure close to the 10\% level significance threshold for the portfolio of US assets.
-Volatilities are overall higher in \textbf{contango} although less so than over the previous period with seventeen US commodities showing higher figures over \textbf{contango} against twenty-three in the crisis period.
-The pattern extends to three of the six UK traded metals with the difference significant at the 1\% level for Copper (XLME) and Tin (XLME) and at the 5\% level for Zinc (XLME) while differences are not significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit higher volatility over \textbf{backwardation} phases.
-Equally weighted portfolios of US and UK traded assets on the other hand both show higher volatility in \textbf{contango} with the difference significant at the 1\% level for both.
-Over the financialisation period in contrast volatilities were predominantly higher in \textbf{backwardation} for US traded assets with fourteen commodities showing higher volatility figures in these phases; the post-crisis pattern of results for volatilities thus likewise shows signs of reversion to pre-financialisation standards.
-After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and \textbf{CHP} part ways (table \ref{tab:time-reg-US-CHP}), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
-The recovery initiated in the crisis period for that of CHP is confirmed with a stronger increase in the post-crisis period, 27.2\% vs.~22.5\%, strongest for the metals sector, 37.3\% vs.~23.7\%, while the energy sector shows the opposite pattern: 11\% vs.~16\%.
-In contrast, after increasing stronger in the crisis, that for \textbf{CHP} falls overall in the post-crisis period, 7.5\% vs 14.7\%, with the decrease strongest for the energy sector in a relative sense: 2.5\% vs.~14.8\%.\\
-Average pairwise correlations amongst factor picks (table \ref{tab:correlations}) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1\% to 26.1\%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
-The performance of the market factor on the US complex declines below financialisation levels (table \ref{tab:time-reg-US-facts-US}) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table \ref{tab:time-reg-US-facts-picks}) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors.
-Table \ref{tab:time-reg-UK-facts-picks} provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
-
-\medskip\setlength{\parindent}{0pt}
-
-Taken together the patterns of results over the crisis and post-crisis periods echo those in Basu and Bauthéac (2024) in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex.
+\section{Results \& discussion}\label{sec-results}
+
+The descriptive statistics for the commodity series considered in the
+study displayed in table Table~\ref{tbl-stats-no-regimes} show a clear
+pattern of increase in average return during financialisation with an
+equally weighted portfolio of the US traded assets showing a mean
+returns of 15.9\% significant at the 5\% level vs.~6.9\% with a 10\%
+significance in the pre-financialisation period. The increase is even
+more pronounced for an equally weighted portfolio of UK traded assets
+(metals), 2.47\% (not significant) to 21.8\% (significant at the 10\%
+level), which sets out the global nature of the phenomenon. Most
+commodities show a higher mean return while five--Lumber (XCME), Natural
+gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary
+(XLME)--show a lower figure with five significant figures--Crude oil-WTI
+(XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined
+(XLME)--against none pre-financialisation. Sugar-\#11 wins the race with
+a mean return increasing from -4.6\% to 24.9\% followed by copper with
+sizeable increases for both markets: 1.5\% to 28.2\% (XCEC) and 0.5\% to
+28.6\% (XLME).\\
+The pattern of results for volatilities is similar although the increase
+is less pronounced. Both equally weighted portfolios shows an increase,
+more pronounced for the UK assets, 10\% to 13.6\% (US) vs.~15.7\% to
+26.9\% (UK), while out of the thirty assets, eleven show a drop in
+volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C
+(IFUS), Lumber (XCME), Sugar-\#11 (IFUS), Natural gas (XNYM), Crude
+oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
+Financialisation seems however to have impacted the commodity complex
+beyond these mechanical effects of increased long participation ensuing
+from the entry on index type investments as our results suggest next.
+
+\medskip
+
+The cross-sectional nature of financialisation naturally leads us to
+extend the individual hedging pressure paradigm by incorporating
+aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure.
+The traditional Keynesian hedging pressure paradigm postulates a
+negative relationship between the return on an individual commodity
+futures and its hedging pressure. The extended Keynesian hedging
+pressure paradigm, in the context of financialisation, should also imply
+that returns for individual commodities should be high in periods where
+\textbf{CHP} is low and vice et versa. In table
+Table~\ref{tbl-stats-regimes} the mean returns are shown over high
+(\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP}
+regimes for each time period.\\
+Over the first period eighteen of the twenty-four US commodities have
+higher mean returns during periods of \textbf{backwardation} as compared
+to \textbf{contango}, with the difference being statistically
+significant at the 10\% level for two commodities, at the 5\% level for
+one and at the 1\% level for another. For the remaining six commodities
+the higher mean return during \textbf{contango} is not statistically
+significant for any of them. For the six UK commodities, all metals,
+five of them had higher mean returns during phases of
+\textbf{backwardation} as compared to \textbf{contango} in the first
+period, with one of these differences being statistically significant at
+the 10\% level while for the remaining asset (Zinc) the higher mean
+return during \textbf{contango} is not statistically significant. An
+equally weighted portfolio of the twenty-four US commodities had a mean
+return of 15.4\% during \textbf{backwardation} phases, statistically
+significant at the 1\% level, and a mean return of -1.1\% during
+\textbf{contango}, both in the first period, with the difference between
+them statistically significant at the 5\% level. The corresponding
+figures for an equally weighted portfolio of the UK metals were 4.4\%
+and 0.3\% respectively. These results provide broad support for an
+aggregate version of the Keynesian hedging pressure hypothesis and
+suggest that hedgers in the aggregate were engaged in risk transfer
+during this period.\\
+Over the second period the pattern essentially reverses. For the
+twenty-four US commodities over this period, fourteen have higher mean
+returns during phases of \textbf{contango} over \textbf{backwardation}.
+Four of the six UK metals achieved higher mean returns over
+\textbf{contango} relative to \textbf{backwardation} phases with the
+difference being statistically significant for one commodity. The
+equally weighted US portfolio had a mean return of 15.7\% over
+\textbf{backwardation} against 16.2\% during phases of
+\textbf{contango}, both statistically significant at the 10\% level. The
+difference was considerably more pronounced for the equally weighted UK
+metals portfolio with a mean return of 8\% during \textbf{backwardation}
+rising to 35.6\% during \textbf{contango}.
+
+\medskip
+
+The onset of financialisation thus seems to have engendered a change in
+the nature of hedger's behaviour, at the aggregate level in particular,
+taking it away from the traditional Keynesian view of risk shifting.
+This phenomenon has been noted in earlier theoretical and empirical work
+\citep{danthine_information_1978, stout_why_1998} in different contexts
+from which two competing models of behaviour have emerged.\\
+The information arbitrage model
+\citep{grossman_impossibility_1980, danthine_information_1978, kyle_informed_1989}
+implies that hedgers may often be seeking out counterparties to trade
+with rather than being purely passive. This issue is also raised in both
+\citet{cheng_financialisation_2014} and \citet{stulz_rethink_1996} who
+point out that hedgers may be taking a view on prices just as
+speculators do. In fact, by hedging away some of their risk, hedgers are
+able to speculate more heavily based on their disagreement against
+speculators regarding futures price movement
+\citep{simsek_speculation_2013}, which fits into a heterogeneous
+expectation theory of speculation\footnote{\citet{hirshleifer_speculation_1975};
+  \citet{hirshleifer_reply_1976}; \citet{hirshleifer_theory_1977}}. As
+\citet{stout_why_1998} points out, this disagreement-based theory of
+trading is one of the main reason the public and the law disapproves
+speculation as this form of trading is regarded as
+non-productive\footnote{\citet{duffie_challenges_2014} also discusses
+  some of the challenges faced by a policy treatment of speculative
+  trading motivated by differences in beliefs.}.\\
+In the second model hedgers are seen as liquidity providers as in
+\citet{kang_tale_2020} with this explanation also consistent with the
+nature of financialisation which led to the arrival of long term, long
+only investors who require substantial liquidity to roll-over their
+positions. Table Table~\ref{tbl-time-reg-US-CHP} supports this view. We
+regress commodity futures front returns on individual commercial hedging
+pressure (CHP) as well as aggregate CHP (\textbf{CHP}), our market wide
+measure of CHP, in separate models and find that the explanatory power
+of CHP at the individual commodity level decreases over the
+financialisation period with the US cross-sectional average \(R^{2}\)
+falling down to 20.8\% from 25.8\% in the previous period while that of
+\textbf{CHP} increases (7.1\% vs 5.4\%). Financialisation therefore
+seems to have had the effect of loosening the extent to which futures
+risk premiums relate to commodity specific commercial hedging motives
+while strengthening that to which they relate to broader dynamics such
+as cross-sectional liquidity provision. The pattern is strongest for the
+metals sector where the average \(R^{2}\) drops down to 19.1\% from
+28.1\% between the two periods at the individual level while it rises
+from 8.4\% to 15.7\% at the aggregate level. The symmetry breaks in the
+crisis period, with the US cross-sectional average \(R^{2}\) at the
+individual level bouncing back up (22.5\% vs 20.8\%) while that at the
+aggregate level rises further (14.7\% vs 7.1\%), before eventually
+resuming post-crisis with a further rise at the individual level (27.2\%
+vs 22.5\%) and a drop at the aggregate level (7.5\% vs 14.7\%)
+suggesting a return to legacy commodity specific dynamics.
+
+\bigskip
+\bigskip
+
+Using our bespoke commodity-based asset pricing framework we strive to
+shed new light on the phenomenon by first regressing returns series for
+the twenty four individual US commodities against our factor mimicking
+portfolios independently. The resulting individual explanatory powers
+(\(R^2\)s), once averaged by factor and period, offer a refined
+perspective on the relation between return and factor attribute
+co-movement. A low figure indicates low cross-sectional return
+co-movement for, in this context, return on the corresponding factor
+mimicking portfolio only has explanatory power on return for commodities
+that are constituents of one of its legs over the corresponding period.
+The explanatory power for the other commodities is typically low or even
+0 for the case where commodities are perfectly uncorrelated with
+one-another. A rising figure on the other hand thus indicates increased
+pairwise correlations, positive or negative, including amongst factor
+leg mimicking portfolio constituent commodities; and therefore provides
+evidence that pairwise return correlation relates to factor attribute.\\
+The average time series explanatory power of the various one factor
+models on the US traded assets over the four periods is shown in Table .
+Over the first period the market factor has the best average time series
+performance with the highest average \(R^{2}\) with all three futures
+market factors performing poorly, indicating that the commodities with
+extreme factor attributes (high or low CHP for example) are uncorrelated
+with the rest of the commodity cross-section, and the overall
+performance consistent across periods of high and low \textbf{CHP}
+(below period median). The two factor models average \(R^{2}\)s
+(available upon request) are roughly the sum of the one factor
+\(R^{2}\)s indicating that the factors are almost orthogonal over this
+period.\\
+The onset of financialisation leads to a substantial improvement in the
+performance of the CHP factor with its average \(R^{2}\) increasing to
+8.2\% in the second period relative to 1.7\% in the first with this
+improvement coming from the long leg that shows a greater improvement
+(4.5\% to 15.1\%) relative to the short (3\% to 4\%), suggesting that
+``normally'' backwardated commodities (Keynesian perspective) have
+higher correlation with the rest of the commodity cross-section, and
+thereby bringing more evidence of the important role played by long only
+investors in the change in nature of these markets over that period. The
+performance of the market factor also improves though not by as much in
+a relative sense (21.6\% from 11.7\%) and both the term structure factor
+and the open interest growth factor show a much smaller improvement in
+performance with smaller differences between legs. Over all periods, all
+of our factor models show similar performance across regimes of high and
+low \textbf{CHP}.
+
+\medskip
+
+We next investigate the top eight of the US traded commodities which
+achieved the highest time series \(R^{2}\) for the CHP, market, open
+interest and term structure factors, in each of the four time periods
+with the commodity picks shown in Table .\\
+For the CHP factor the commodities that achieve high \(R^{2}\) in a
+given period are likely to be those with relatively high or low CHP over
+that period, or those commodities that co-vary with the short or the
+long side of the factor. The same applies to the open interest and term
+structure factors with CHP replaced by open interest growth and roll
+yield respectively; while for the market factor the picks are those that
+co-vary most strongly with the market factor over that period.\\
+For the CHP factor, we observe a change in the picks between the first
+and the second period; the picks in the first period included five
+agricultural commodities and three metals while in the second period
+they include all the five base and precious metals and only three
+agricultural commodities. This pattern is also visible for the term
+structure factor for which there are four metals (copper, silver, gold
+and platinum) picks in the second period against two in the first
+(palladium and platinum) as well as for the open interest nearby growth
+factor for which there are three metals (silver, gold and platinum)
+picks in the second period against one in the first (platinum). The
+market factor has three metal picks in the second period (palladium,
+gold and silver) while all the picks in the first period were
+agricultural or energy commodities.\\
+Over the third period, the average CHP factor shows the same metal picks
+with the agriculturals replaced by energy commodity; the open interest
+nearby growth factor still has three metal picks with gold swapped for
+copper and both the market and term structure factors have one,
+copper.\\
+The table also shows the proportion of time that these picks were
+constituents of the corresponding factor. All the picks of the
+long-short factors (average CHP, open interest nearby growth and term
+structure factors) were constituents of the corresponding factor for
+some proportion of time in all of the time periods. In this respect,
+there is a contrast between the first and second periods with the
+average CHP and open interest nearby growth factor picks appearing
+predominantly on the long side of the corresponding factor in the second
+period, as opposed to both legs in the first. The pattern is
+particularly strong for the metals and energy commodities respectively,
+with the exception of copper for the average CHP factor that lives in
+the short leg a higher proportion of the time over the financialisation
+period. The pattern is reversed for the term structure factor where the
+picks appear predominantly on the short leg in the second period, as
+opposed to both legs in the first with the pattern again strongest for
+the metals. This behaviour continues over the third period for the
+average CHP and open interest nearby growth factors and indicates that
+their picks consistently exhibited low commercial hedging pressure and
+high front contract open interest growth respectively while indicating
+that the term structure factor picks showed low roll yield in the first
+and second period.
+
+\medskip
+
+In table , we show the average pairwise returns correlation between each
+set of picks in each time period. Following on form the earlier
+observations, this exercise gives an indication of the extent to which
+attribute co-movement reveals price co-movement, which is particularly
+relevant for the long-short factors for which the corresponding
+attribute is not directly related to price co-movement.\\
+In the first period the average picks pairwise correlation for the
+long-short factors ranges from 7.1\% (term structure factor picks) to
+12.4\% (open interest factor picks) while the market factor picks show
+the highest figure (23.7\%). In the second period the figures for the
+long-short factors rise sharply; up to 22.9\% from 8.1\% for the average
+CHP factor picks, up to 32.4\% from 12.4\% for the open interest factor
+picks and up to 23.4\% from 7.1\% for the term structure factor picks.
+This increase is stronger than that for the market factor picks in a
+relative sense and is a consequence of the dramatic increase in average
+pairwise price correlation amongst the US traded metals which dominate
+the average CHP factor set of picks and which presence is stronger
+amongst both the open interest and term structure factor sets of picks
+over the financialisation period. The higher figures for the open
+interest factor are driven by the strong presence of the energy complex
+amongst the corresponding picks. The latter exhibits much higher average
+pairwise correlations than the other sectors in both periods although
+lower in the second relative to the first which reinforces the role
+played by the metals in the sharp increase in average pairwise
+correlation amongst picks for this factor.\\
+With regards to \textbf{CHP} regimes, although not very pronounced, a
+pattern is noticeable. For the market, open interest and term structure
+factor picks, average pairwise correlations are stronger over phases of
+\textbf{contango} in the first period and over phases of
+\textbf{backwardation} in the financialisation period, eventually
+reverting back to being stronger over \textbf{contango} phases in the
+crisis period with the CHP factor sets of picks showing the opposite
+pattern. Overall, these results suggest an increase in correlation
+between non-price attributes co-movement and price co-movement over the
+financialisation period. It is also interesting to note that US traded
+metals returns were negatively correlated with the rest of US traded
+commodities in the first period and positively in the second.
+
+\medskip
+
+To further understand the link between attribute and price co-movement
+we build all of the factors from every set of factor picks and assess
+their explanatory performance on these sets of picks over the four
+periods independently. The results are shown in table . The long-short
+factors for a particular attribute select the top and bottom two of the
+corresponding picks based on that attribute while the market factor
+takes an equally weighted combination of the eight corresponding picks.
+In the absence of price co-movement between the picks, the market factor
+will achieve an average \(R^{2}\) of around 12.5\%\footnote{Market
+  factor lemma:
+  \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\)
+  size of market portfolio (eight here).}, while there is no non-zero
+\(R^{2}\) lower bound for the corresponding long-short factors.\\
+A high average \(R^{2}\) for the market factor is indicative of strong
+price co-movement. In this respect, the most remarkable change in
+performance in a relative sense is that of the market factor built from
+the CHP factor sets of picks with the average \(R^{2}\) more than
+doubling, from 18.6\% up to 38.1\%. For the long-short factors on the
+other hand it is indicative of simultaneous attribute and price
+co-movement. For the factors built from the market factor picks the
+increase is strongest in a relative sense for the CHP factor with the
+\(R^{2}\) more than doubling, going from 5.6\% in the first period up to
+12.4\% in the second with the increase stronger for the long leg (17.1\%
+vs.~27.9\%) relative to the short (16.5\% vs.~21.4\%). In the case of
+the factors built from the CHP factor picks, the CHP factor built with
+its own picks shows a remarkable increase in a relative sense with the
+\(R^{2}\) tripling, from 7.2\% to 21.4\% and the long leg showing a much
+greater increase relative to the short (10.4\% to 31.1\% vs.~8.3\% to
+9.8\%). The performance of the term structure factor built from the CHP
+factor sets of picks also shows a sizable increase in a relative sense,
+from 3.5\% to 5.3\% and even more remarkable in this case is the
+substantial increase in performance of the short leg, from 6.3\% to
+15.7\% relative to the long (7.5\% to 9.8\%). The pattern is reversed
+for the CHP factor built from the term structure factor picks where the
+average \(R^{2}\) increases from 4.7\% to 8\% with the performance of
+the long leg increasing from 11.9\% to 28.1\% vs.~5.5\% to 9.1\% for the
+short. The performance of the term structure factor constructed from its
+own sets of picks also shows a substantial increase, from 5.1\% to 8.4\%
+with, here again the increase in performance relatively stronger for the
+short leg, from 6\% to 16.1\% vs.~7.6\% to 12.1\% for the long.\\
+Taken together with the previous results showing that the metal complex
+predominantly loads on the long and short legs of the original CHP and
+term structure factors respectively, these results provide evidence of
+convergence of Keynesian and Working's theories of the term structure in
+detecting price co-movement during financialisation perhaps as a result
+of spillover effects between the corresponding futures and spot markets
+as suggested in \citet{basak_model_2016}.
+
+\medskip
+
+In table we assess the performance of the same factors on all the
+commodities instead of just the picks. While the average \(R^{2}\)s are
+expectedly lower, the pattern of results mostly holds with the relative
+performance of the market factors built with different sets of picks as
+well as that of the CHP and term structure factors built with each
+other's picks similar to table . In contrast, the average CHP factor
+built with average CHP factor picks shows a smaller absolute increase in
+average \(R^{2}\) indicating that the link between CHP co-movement and
+price co-movement is stronger amongst the picks which are predominantly
+metals. Taken together, the results in tables and suggest that the onset
+of financialisation had a major impact on the dynamics of US traded
+precious and precious-base metals.\\
+To assess whether this phenomenon extended beyond US borders we examine
+the performance of the factors used in the last two tables above on the
+six UK metals futures traded on the London Metal Exchange with the
+results reported in table . In the first period, although all sets of
+picks, except that of the market factor, included at least one metal,
+the average \(R^{2}\)s are very low; close to zero in most cases. These
+figures drastically increase across the board in the financialisation
+period and show a pattern similar to that observed in the US complex.
+The market factor built from the CHP and term structure factor sets of
+picks shows the sharpest increase in performance, relative to using the
+other sets of factor picks; rising to 20.1\% from 1.5\% and to 15\% from
+0.8\% respectively. The increase in \(R^{2}\) for the market factor
+built with market factor picks is more modest, providing further
+evidence of concentration of co-movement in the metals sector during
+financialisation.\\
+Here again the change in performance for the CHP and term structure
+factor legs stands out where the factors are built with their own as
+well as each other's sets of picks. The average \(R^{2}\) for the long
+leg of the CHP factor built with its own sets of picks increases from
+1\% to 11\% while the short leg shows no significant change. The
+opposite holds for the term structure factor built from its own set of
+picks with the short leg performance increasing from 0.1\% to 14\% while
+that of the long leg remains below 1\%. Building these factors from each
+other's sets of picks produces a similar pattern with the performance of
+the long leg of the CHP factor built from the term structure factor
+picks increasing from 0.7\% to 11.4\%; a much greater increase relative
+to the short leg although in this case the latter also shows a sizable
+increase in performance (0.3\% to 6\%). The performance of the short leg
+of the term structure factor built from the CHP factor sets of picks on
+the other hand increases from 0.3\% to 19.2\% while the performance for
+the long leg in the second period remains below 1.5\%.\\
+Taken together these results emphasise the global nature of the impact
+of financialisation on the metals complex and provide further evidence
+that global metals co-movement could be detected by US based factor
+models that combine the Keynesian and Working's term structure
+paradigms. There seems thus to be information in the factor constructed
+from hedging pressure based on the Keynesian paradigm relevant to the
+term structure factor built on the Working paradigm and these findings
+therefore appear to complement the results of \citet{kang_tale_2020} who
+find that hedging pressure both conveys information about liquidity
+provision in the short term (Working paradigm) and risk transfer in the
+longer term (Keynesian paradigm).
+
+\bigskip
+\bigskip
+
+The crisis period (late 2008 to mid-2013) shows a contrasting pattern of
+results. Returns fall sharply relative to the financialisation period
+(table ) with eighteen US commodities along with all six UK traded
+metals showing lower mean returns. Returns for equally weighted
+portfolios of both sets of assets fall down to 9.4\% and 5.3\% from
+15.9\% and 21.8\% respectively. Returns are mostly higher during phases
+of \textbf{backwardation} relative to \textbf{contango} (table ) with
+fifteen US assets and five of the UK traded metals showing higher mean
+returns in \textbf{backwardation} and the pattern extending to equally
+weighted portfolios of the two sets of assets. Volatility is moderately
+higher for both sets with fifteen US commodities and three UK metals
+showing higher figures and interestingly eminently higher over phases of
+\textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none
+of the UK traded metals show higher volatility figures over
+\textbf{backwardation} phases. The symmetry between the dynamics of CHP
+and \textbf{CHP}'s explanatory power on individual commodity returns
+breaks in the crisis period with both now seemingly converging; the US
+cross-sectional average \(R^{2}\) at the individual level bouncing back
+up (22.5\% vs 20.8\%) while that at the aggregate level rises further
+(14.7\% vs 7.1\%).\\
+The performance of the market factor dominates the US commodity complex
+over the period with a 50\% increase in mean average \(R^{2}\) to over
+30\% (table ) while that of the CHP factor decreases and, although
+increasing, remains modest for the open interest growth and term
+structure factors. The average pairwise correlation amongst the market
+factor picks increases beyond 50\% while there is a leveling in that
+amongst the picks of the long-short factors as shown in table .
+Notwithstanding, the market factor built from any sets of picks shows a
+significant rise across the board in performance on the US complex
+(table ).\\
+Taken together, these results indicate the presence of a systematic
+factor across the entire cross-section of the US commodities. Table
+provides further evidence of systematic linkages, in this case between
+US and non-US traded commodities with a similar, albeit more pronounced
+pattern, where the market factor constructed with any sets of picks (US
+traded commodities) shows a dramatic increase in performance on the UK
+metals with for example, when constructed from its own sets of picks,
+the average \(R^{2}\) increasing to 31.7\% from 10.2\% in the previous
+period.
+
+\medskip
+
+The returns pullback continues into the post-crisis period (table ) with
+twenty-two US and four UK traded assets showing lower mean returns
+relative to the crisis while the same number of US commodities and all
+UK metals show lower figures relative to the financialisation period;
+mean returns for equally weighted portfolios of US and UK assets drop
+down to -0.2\% and 2.7\% respectively. Interestingly volatility also
+recedes substantially with twenty US assets and all UK metals showing
+lower volatility figures relative to both the crisis and
+financialisation periods suggesting that investment outflows from the
+commodity futures complex have had a lower impact on volatility than the
+corresponding inflows witnessed over the financialisation period. The
+figures for the equally weighted portfolios of US and UK assets drop to
+9.9\% and 16.2\% respectively, very close to pre-financialisation
+levels.\\
+The pattern of reversion toward the pre-financialisation Keynesian
+paradigm initiated during the crisis continues stronger into the
+post-crisis period (table ) with mean returns higher during phases of
+\textbf{backwardation} relative to \textbf{contango} (table ), more so
+than over the crisis period with seventeen US commodities showing higher
+mean returns over \textbf{backwardation} phases. The difference is
+significant at the 5\% level for Lumber (XCME) and at the 10\% level for
+Palladium (XNYM) while no difference is significant for the assets
+showing higher figures over phases of \textbf{contango}. The pattern is
+more pronounced for the UK traded subset with all six assets showing
+higher mean returns in \textbf{backwardation} with the difference
+significant at the 1\% level for Nickel-primary (XLME), 5\% level for
+Aluminium (XLME) and 10\% level for Zinc (XLME). It also extends to
+equally weighted portfolios of US and UK traded assets that both show
+higher mean returns during \textbf{backwardation} with the difference
+significant at the 5\% level for the UK portfolio and the figure close
+to the 10\% level significance threshold for the portfolio of US assets.
+Volatilities are overall higher in \textbf{contango} although less so
+than over the previous period with seventeen US commodities showing
+higher figures over \textbf{contango} against twenty-three in the crisis
+period. The pattern extends to three of the six UK traded metals with
+the difference significant at the 1\% level for Copper (XLME) and Tin
+(XLME) and at the 5\% level for Zinc (XLME) while differences are not
+significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME)
+that exhibit higher volatility over \textbf{backwardation} phases.
+Equally weighted portfolios of US and UK traded assets on the other hand
+both show higher volatility in \textbf{contango} with the difference
+significant at the 1\% level for both. Over the financialisation period
+in contrast volatilities were predominantly higher in
+\textbf{backwardation} for US traded assets with fourteen commodities
+showing higher volatility figures in these phases; the post-crisis
+pattern of results for volatilities thus likewise shows signs of
+reversion to pre-financialisation standards. After showing signs of
+convergence in the crisis period the dynamics of the explanatory power
+of CHP and \textbf{CHP} part ways (table ), seemingly reverting to the
+Keynesian paradigm observed pre-financialisation, further suggesting a
+return to legacy commodity specific dynamics. The recovery initiated in
+the crisis period for that of CHP is confirmed with a stronger increase
+in the post-crisis period, 27.2\% vs.~22.5\%, strongest for the metals
+sector, 37.3\% vs.~23.7\%, while the energy sector shows the opposite
+pattern: 11\% vs.~16\%. In contrast, after increasing stronger in the
+crisis, that for \textbf{CHP} falls overall in the post-crisis period,
+7.5\% vs 14.7\%, with the decrease strongest for the energy sector in a
+relative sense: 2.5\% vs.~14.8\%.\\
+Average pairwise correlations amongst factor picks (table ) fall
+substantially in the post-crisis period with for example the figure for
+the market factor picks dropping from 50.1\% to 26.1\%, almost down to
+pre-financialisation levels; results are similar for the long-short
+factor picks with figures below financialisation levels in all cases and
+very close to pre-financialisation standards for the term structure and
+liquidity factor picks. The performance of the market factor on the US
+complex declines below financialisation levels (table ) with the pattern
+similar albeit stronger when the factor is built from the sets of factor
+picks with a decline in performance on the US complex (table ) to almost
+pre-financialisation levels when constructed with its own set of picks
+as well as with those of the long-short factors, in particular the term
+structure and liquidity factors. Table provides further evidence of
+decoupling, in this case between US and non-US traded commodities with a
+sharp decline in performance of the market factor constructed with any
+set of picks on the UK complex below financialisation, down to almost
+pre-financialisation levels when constructed with the sets of long-short
+factors picks.
+
+\medskip
+
+Taken together the patterns of results over the crisis and post-crisis
+periods echo those in \citet{basu_definancialisation} in suggesting that
+the exogenous shock delivered by the financial crisis combined with the
+accommodative monetary policy that ensued seem to have initiated a
+reversion toward pre-financialisation fundamentals in the commodity
+futures complex.
 
@@
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-In the early 2000s, against a backdrop of a low yield environment and poor stock market performance, a combination of financial innovations\footnote{Commodity price indexes and the ad-hoc financial instruments enabling investment in them were the main financial innovations which allowed large global banks to offer commodity investment products to institutional and retail investors.
-In 1991 Goldman Sachs created the S\&P-GSCI which provides investors with buy-side exposure to commodities via the OTC swap market and thus without having to participate in the formal futures markets with their position limit restrictions.
-At this stage, these restrictions still applied to the issuing institutions though, as they hedged the corresponding commodity swap exposure in the futures markets.
-The first commodity-based ETFs were created through buying physical precious metals with gold and silver ETFs offered as early as 2002/2003.
-The regulatory hurdle here related to the licensing of commodity trading professionals.
-Typically, investors had to sign a statement with their broker stating that they understood the risks of commodity investments; a rather inconvenient paperwork for a product designed to trade like a stock, as set forth by a number of industry players at the time.} and regulatory changes\footnote{In 2000, the Commodity Futures Modernization Act (CFMA) granted non-agricultural commodity futures statutory exemption from regulation (``Enron loophole'').
-It still required agricultural commodity derivatives be traded on a CFTC-regulated exchange however.
-Eventually, the CFTC classified swap dealers as ``bona fide'' hedgers, granting them position limits exemption (``swap dealer loophole'').
-In 2005, the CFTC waived the rule that required commodity investors to sign a statement saying they understood the risks, letting the funds replace it with their prospectus.
-The regulatory bottleneck that prevented the large-scale expansion of commodity index investment was no more.} led to large inflows of institutional capital into the commodity futures markets.
-This process known as ``financialisation'' spurred a heated public policy debate about whether the ensuing increase in open interest and trading volume in commodity futures exerted upward pressure on prices.\\
-The debate spread to the legislative sphere, with the US senate launching formal investigations, and was thrust onto the academic community as a matter of urgency.
-Perhaps in response to this, most of the early studies focused on the more mechanical effects of financialisation in individual markets, relying on commodity specific causality and correlation-based analysis.
-The contention eventually triggered legislative action and new position limits were introduced in a number of grains and energy futures markets.
-
-\medskip\setlength{\parindent}{0pt}
-
-With the benefit of hindsight, this focus appears to have been too narrow.
-As our results suggests, financialisation was a phenomenon global in nature and studying the direct effects of increased market participation in single markets thus seems amiss in this context.\\
-The results of our analysis further suggest that financialisation had cross-sectional effects on market fundamentals across the commodity complex beyond energy and agricultural commodities and in fact strongest for the metals sector at the global level; an aspect largely overlooked in the original approach that we believe the existing literature has not fully analysed.\\
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in commodity pricing dynamics.
-In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have triggered a motion of reversion to legacy pre-financialisation fundamentals.
-
-\newpage\loadgeometry{tables}
-
-\hypertarget{tables}{%
-\section{Tables}\label{tables}}
-
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}llrrrr}
-\caption{\label{tab:stats-no-regimes}This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Mean values significant at the 1\%, 5\% and 10\% level are marked with ***, ** and * respectively.
-The results are discussed in section \ref{results}.}\\
+\section{Conclusion}\label{conclusion}
+
+In the early 2000s, against a backdrop of a low yield environment and
+poor stock market performance, a combination of financial
+innovations\footnote{Commodity price indexes and the ad-hoc financial
+  instruments enabling investment in them were the main financial
+  innovations which allowed large global banks to offer commodity
+  investment products to institutional and retail investors. In 1991
+  Goldman Sachs created the S\&P-GSCI which provides investors with
+  buy-side exposure to commodities via the OTC swap market and thus
+  without having to participate in the formal futures markets with their
+  position limit restrictions. At this stage, these restrictions still
+  applied to the issuing institutions though, as they hedged the
+  corresponding commodity swap exposure in the futures markets. The
+  first commodity-based ETFs were created through buying physical
+  precious metals with gold and silver ETFs offered as early as
+  2002/2003. The regulatory hurdle here related to the licensing of
+  commodity trading professionals. Typically, investors had to sign a
+  statement with their broker stating that they understood the risks of
+  commodity investments; a rather inconvenient paperwork for a product
+  designed to trade like a stock, as set forth by a number of industry
+  players at the time.} and regulatory changes\footnote{In 2000, the
+  Commodity Futures Modernization Act (CFMA) granted non-agricultural
+  commodity futures statutory exemption from regulation (``Enron
+  loophole''). It still required agricultural commodity derivatives be
+  traded on a CFTC-regulated exchange however. Eventually, the CFTC
+  classified swap dealers as ``bona fide'' hedgers, granting them
+  position limits exemption (``swap dealer loophole''). In 2005, the
+  CFTC waived the rule that required commodity investors to sign a
+  statement saying they understood the risks, letting the funds replace
+  it with their prospectus. The regulatory bottleneck that prevented the
+  large-scale expansion of commodity index investment was no more.} led
+to large inflows of institutional capital into the commodity futures
+markets. This process known as ``financialisation'' spurred a heated
+public policy debate about whether the ensuing increase in open interest
+and trading volume in commodity futures exerted upward pressure on
+prices.\\
+The debate spread to the legislative sphere, with the US senate
+launching formal investigations, and was thrust onto the academic
+community as a matter of urgency. Perhaps in response to this, most of
+the early studies focused on the more mechanical effects of
+financialisation in individual markets, relying on commodity specific
+causality and correlation-based analysis. The contention eventually
+triggered legislative action and new position limits were introduced in
+a number of grains and energy futures markets.
+
+\medskip
+
+With the benefit of hindsight, this focus appears to have been too
+narrow. As our results suggests, financialisation was a phenomenon
+global in nature and studying the direct effects of increased market
+participation in single markets thus seems amiss in this context.\\
+The results of our analysis further suggest that financialisation had
+cross-sectional effects on market fundamentals across the commodity
+complex beyond energy and agricultural commodities and in fact strongest
+for the metals sector at the global level; an aspect largely overlooked
+in the original approach that we believe the existing literature has not
+fully analysed.\\
+The onset of the financial crisis and the monetary policy regimes that
+followed, on the other hand, also appear to have induced significant
+changes in commodity pricing dynamics. In contrast with
+financialisation, our results suggest that the crisis and its aftermath
+have delivered an exogenous shock across the entire cross-section of
+liquid commodities and seem to have triggered a motion of reversion to
+legacy pre-financialisation fundamentals.
+
+\newpage
+
+\section{Tables}\label{tables}
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-stats-no-regimes}This table shows mean returns and
+volatility (sd) for the twenty four individual US commodities and the
+six GB metals considered in the study as well as for two equally
+weighted portfolios formed from the US commodities and the GB metals
+respectively across the four periods of interest (past: 1997-2003;
+financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+Mean values significant at the 1\%, 5\% and 10\% level are marked with
+***, ** and * respectively. The results are discussed in section
+Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-asset & estimate & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
+\textbf{Oats (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
+\addlinespace
+\textbf{Soybean meal (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
+\textbf{Soybeans (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}}\\
+\addlinespace
+\textbf{Cattle-live (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}}\\
+\textbf{Lean hogs (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.65\%}}}\\
+\textbf{Cocoa (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.99\%}}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
+\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.06\%}}}\\
+\addlinespace
+\textbf{Lumber (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
+\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.8\%}}}\\
+\textbf{Orange juice (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.16\%}}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.33\%}}}\\
+\textbf{Natural gas (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.64\%}}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.37\%}}}\\
+\addlinespace
+\textbf{Gasoline (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.44\%}}}\\
+\textbf{Heating oil (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.1\%}}}\\
+\textbf{Copper (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.53\%}}}\\
+\textbf{Gold (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.75\%}}}\\
+\textbf{Palladium (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.92\%}}}\\
+\addlinespace
+\textbf{Platinum (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.43\%}}}\\
+\textbf{Silver (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
+\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.15\%}}}\\
+\textbf{Aluminium (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**28.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.03\%}}}\\
+\textbf{Copper (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
+\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}}\\
+\textbf{Lead (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.31\%}}}\\
+\addlinespace
+\textbf{Nickel-primary (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.68\%}}}\\
+\textbf{Tin-refined (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.07\%}}}\\
+\textbf{Zinc (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**15.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.18\%}}}\\
+\textbf{US commodities} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*21.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.72\%}}}\\
+\textbf{GB commodities} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
+\newpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-stats-regimes}This table shows mean returns and
+volatility (sd) for the twenty four individual US commodities and the
+six GB metals considered in the study as well as for two equally
+weighted portfolios formed from the US commodities and the GB metals
+respectively across the four periods of interest (past: 1997-2003;
+financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+Figures are shown independently for phases of aggregate backwardation
+(aggregate CHP \(\leq\) period median) and aggregate contango (aggregate
+CHP \textgreater{} period median). Mean values significant at the 1\%,
+5\% and 10\% level are marked with ***, ** and * respectively. Aggregate
+CHP construction and corresponding regime definitions are discussed in
+section Section~\ref{sec-methods} while the results are discussed in
+section Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-asset & estimate & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endhead
-
-\endfoot
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.74\%}}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23.07\%}} & \textcolor[HTML]{4285f4}{\textbf{29.14\%}} & \textcolor[HTML]{4285f4}{\textbf{31.59\%}} & \textcolor[HTML]{4285f4}{\textbf{21\%}}\\
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.78\%}}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
+\addlinespace
+\textbf{Oats (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.17\%}}}\\
+\textbf{Oats (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.52\%}}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.44\%}}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.35\%}} & \textcolor[HTML]{4285f4}{\textbf{28.94\%}} & \textcolor[HTML]{4285f4}{\textbf{22.33\%}} & \textcolor[HTML]{4285f4}{\textbf{18.19\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.12\%}}}\\
+\addlinespace
+\textbf{Soybean oil (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.45\%}}}\\
+\textbf{Soybeans (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.93\%}} & \textcolor[HTML]{4285f4}{\textbf{34.58\%}} & \textcolor[HTML]{4285f4}{\textbf{24.39\%}} & \textcolor[HTML]{4285f4}{\textbf{22.04\%}}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}}\\
+\textbf{Soybeans (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.09\%}} & \textcolor[HTML]{4285f4}{\textbf{24.74\%}} & \textcolor[HTML]{4285f4}{\textbf{31.11\%}} & \textcolor[HTML]{4285f4}{\textbf{20.56\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.44\%}}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{36\%}} & \textcolor[HTML]{4285f4}{\textbf{37.53\%}} & \textcolor[HTML]{4285f4}{\textbf{26.57\%}}\\
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.77\%}}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.04\%}} & \textcolor[HTML]{4285f4}{\textbf{29.84\%}} & \textcolor[HTML]{4285f4}{\textbf{37.73\%}} & \textcolor[HTML]{4285f4}{\textbf{26.72\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**20.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.58\%}}}\\
+\addlinespace
+\textbf{Cattle-feeder (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}} & \textcolor[HTML]{4285f4}{\textbf{14.93\%}} & \textcolor[HTML]{4285f4}{\textbf{13.39\%}} & \textcolor[HTML]{4285f4}{\textbf{20.14\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.12\%}}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.67\%}} & \textcolor[HTML]{4285f4}{\textbf{15.35\%}} & \textcolor[HTML]{4285f4}{\textbf{16.91\%}} & \textcolor[HTML]{4285f4}{\textbf{17.23\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.07\%}}}\\
+\textbf{Cattle-live (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.65\%}} & \textcolor[HTML]{4285f4}{\textbf{17.91\%}} & \textcolor[HTML]{4285f4}{\textbf{14.97\%}} & \textcolor[HTML]{4285f4}{\textbf{19.9\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
+\textbf{Cattle-live (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.49\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}} & \textcolor[HTML]{4285f4}{\textbf{17.57\%}} & \textcolor[HTML]{4285f4}{\textbf{16.66\%}}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.23\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.24\%}}}\\
+\textbf{Lean hogs (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{37.6\%}} & \textcolor[HTML]{4285f4}{\textbf{35.73\%}} & \textcolor[HTML]{4285f4}{\textbf{27.83\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.66\%}}}\\
+\addlinespace
+\textbf{Lean hogs (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.22\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}} & \textcolor[HTML]{4285f4}{\textbf{32.78\%}} & \textcolor[HTML]{4285f4}{\textbf{38.28\%}}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.98\%}}}\\
+\textbf{Cocoa (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{33.57\%}} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.29\%}}}\\
+\textbf{Cocoa (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{31.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.91\%}} & \textcolor[HTML]{4285f4}{\textbf{34.66\%}} & \textcolor[HTML]{4285f4}{\textbf{23.57\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.36\%}}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{48.82\%}} & \textcolor[HTML]{4285f4}{\textbf{32.6\%}} & \textcolor[HTML]{4285f4}{\textbf{29.92\%}} & \textcolor[HTML]{4285f4}{\textbf{31.52\%}}\\
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.24\%}}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.22\%}} & \textcolor[HTML]{4285f4}{\textbf{32.24\%}}\\
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.84\%}}}\\
+\addlinespace
+\textbf{Cotton-\#2 (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.02\%}} & \textcolor[HTML]{4285f4}{\textbf{29.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.94\%}} & \textcolor[HTML]{4285f4}{\textbf{21.33\%}}\\
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.91\%}}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.77\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.59\%}} & \textcolor[HTML]{4285f4}{\textbf{19.95\%}}\\
+\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**26.99\%}}}\\
+\textbf{Lumber (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.43\%}} & \textcolor[HTML]{4285f4}{\textbf{30.72\%}} & \textcolor[HTML]{4285f4}{\textbf{35.45\%}} & \textcolor[HTML]{4285f4}{\textbf{21.26\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.14\%}}}\\
+\textbf{Lumber (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}} & \textcolor[HTML]{4285f4}{\textbf{28.2\%}} & \textcolor[HTML]{4285f4}{\textbf{37.23\%}} & \textcolor[HTML]{4285f4}{\textbf{28.45\%}}\\
+\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.64\%}}}\\
+\textbf{Orange juice (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{30.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.64\%}}\\
+\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.64\%}}}\\
+\addlinespace
+\textbf{Orange juice (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{38.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.11\%}}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.07\%}}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{33.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.6\%}} & \textcolor[HTML]{4285f4}{\textbf{41.29\%}} & \textcolor[HTML]{4285f4}{\textbf{27.69\%}}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.7\%}}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{36.48\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.09\%}} & \textcolor[HTML]{4285f4}{\textbf{29.83\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**85.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.76\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.33\%}}}\\
+\textbf{Natural gas (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{63.46\%}} & \textcolor[HTML]{4285f4}{\textbf{47.3\%}} & \textcolor[HTML]{4285f4}{\textbf{48.85\%}} & \textcolor[HTML]{4285f4}{\textbf{42.59\%}}\\
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.25\%}}}\\
+\textbf{Natural gas (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{59.76\%}} & \textcolor[HTML]{4285f4}{\textbf{61.3\%}} & \textcolor[HTML]{4285f4}{\textbf{58.18\%}} & \textcolor[HTML]{4285f4}{\textbf{46.41\%}}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.24\%}}}\\
+\addlinespace
+\textbf{Crude oil-WTI (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{36.74\%}} & \textcolor[HTML]{4285f4}{\textbf{32.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.19\%}} & \textcolor[HTML]{4285f4}{\textbf{26.94\%}}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-24.85\%}}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.74\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{53.7\%}} & \textcolor[HTML]{4285f4}{\textbf{41.08\%}}\\
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}}\\
+\textbf{Gasoline (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.47\%}} & \textcolor[HTML]{4285f4}{\textbf{39.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.1\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-19.47\%}}}\\
+\textbf{Gasoline (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.14\%}} & \textcolor[HTML]{4285f4}{\textbf{44.13\%}} & \textcolor[HTML]{4285f4}{\textbf{47.11\%}} & \textcolor[HTML]{4285f4}{\textbf{41.71\%}}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.16\%}}}\\
+\textbf{Heating oil (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{41.37\%}} & \textcolor[HTML]{4285f4}{\textbf{33.33\%}} & \textcolor[HTML]{4285f4}{\textbf{25.95\%}} & \textcolor[HTML]{4285f4}{\textbf{24.62\%}}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-21.62\%}}}\\
+\addlinespace
+\textbf{Heating oil (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.98\%}} & \textcolor[HTML]{4285f4}{\textbf{39.16\%}} & \textcolor[HTML]{4285f4}{\textbf{35.69\%}}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.1\%}}}\\
+\textbf{Copper (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{30.05\%}} & \textcolor[HTML]{4285f4}{\textbf{25.73\%}} & \textcolor[HTML]{4285f4}{\textbf{18.16\%}}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-12.15\%}}}\\
+\textbf{Copper (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.78\%}} & \textcolor[HTML]{4285f4}{\textbf{33.69\%}} & \textcolor[HTML]{4285f4}{\textbf{42.28\%}} & \textcolor[HTML]{4285f4}{\textbf{20.87\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.21\%}}}\\
+\textbf{Gold (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.89\%}} & \textcolor[HTML]{4285f4}{\textbf{19.2\%}} & \textcolor[HTML]{4285f4}{\textbf{17.03\%}} & \textcolor[HTML]{4285f4}{\textbf{12.36\%}}\\
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.1\%}}}\\
+\textbf{Gold (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}} & \textcolor[HTML]{4285f4}{\textbf{25.21\%}} & \textcolor[HTML]{4285f4}{\textbf{16.23\%}}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**49.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**31.93\%}}}\\
+\addlinespace
+\textbf{Palladium (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.49\%}} & \textcolor[HTML]{4285f4}{\textbf{23.82\%}}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.88\%}}}\\
+\textbf{Palladium (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{41.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.2\%}} & \textcolor[HTML]{4285f4}{\textbf{38.71\%}} & \textcolor[HTML]{4285f4}{\textbf{26.8\%}}\\
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*25.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.17\%}}}\\
+\textbf{Platinum (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.1\%}} & \textcolor[HTML]{4285f4}{\textbf{22.51\%}} & \textcolor[HTML]{4285f4}{\textbf{21.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.04\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.28\%}}}\\
+\textbf{Platinum (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23.12\%}} & \textcolor[HTML]{4285f4}{\textbf{22.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.75\%}} & \textcolor[HTML]{4285f4}{\textbf{20.8\%}}\\
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.44\%}}}\\
+\textbf{Silver (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.07\%}} & \textcolor[HTML]{4285f4}{\textbf{32.5\%}} & \textcolor[HTML]{4285f4}{\textbf{37.17\%}} & \textcolor[HTML]{4285f4}{\textbf{20.3\%}}\\
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.09\%}}}\\
+\addlinespace
+\textbf{Silver (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.93\%}} & \textcolor[HTML]{4285f4}{\textbf{35.34\%}} & \textcolor[HTML]{4285f4}{\textbf{42.44\%}} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}}\\
+\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**23.68\%}}}\\
+\textbf{Aluminium (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.57\%}} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{18.94\%}}\\
+\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-23.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.74\%}}}\\
+\textbf{Aluminium (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.13\%}} & \textcolor[HTML]{4285f4}{\textbf{27.29\%}} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{18.23\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.99\%}}}\\
+\textbf{Copper (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.98\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{17.92\%}}\\
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.89\%}}}\\
+\textbf{Copper (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{41.31\%}} & \textcolor[HTML]{4285f4}{\textbf{19.86\%}}\\
+\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.05\%}}}\\
+\addlinespace
+\textbf{Lead (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.16\%}} & \textcolor[HTML]{4285f4}{\textbf{39.91\%}} & \textcolor[HTML]{4285f4}{\textbf{35.35\%}} & \textcolor[HTML]{4285f4}{\textbf{23.37\%}}\\
+\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*46.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-13.41\%}}}\\
+\textbf{Lead (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.12\%}} & \textcolor[HTML]{4285f4}{\textbf{43.16\%}} & \textcolor[HTML]{4285f4}{\textbf{46.22\%}} & \textcolor[HTML]{4285f4}{\textbf{23.09\%}}\\
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-39.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**35.09\%}}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.23\%}} & \textcolor[HTML]{4285f4}{\textbf{41.62\%}} & \textcolor[HTML]{4285f4}{\textbf{34.48\%}} & \textcolor[HTML]{4285f4}{\textbf{29.13\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**63.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**-34.64\%}}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.28\%}} & \textcolor[HTML]{4285f4}{\textbf{46.72\%}} & \textcolor[HTML]{4285f4}{\textbf{47.44\%}} & \textcolor[HTML]{4285f4}{\textbf{28.6\%}}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.48\%}}}\\
+\textbf{Tin-refined (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.4\%}} & \textcolor[HTML]{4285f4}{\textbf{29.09\%}} & \textcolor[HTML]{4285f4}{\textbf{15.27\%}}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.69\%}}}\\
+\addlinespace
+\textbf{Tin-refined (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.77\%}} & \textcolor[HTML]{4285f4}{\textbf{32.08\%}} & \textcolor[HTML]{4285f4}{\textbf{41.13\%}} & \textcolor[HTML]{4285f4}{\textbf{21.68\%}}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.05\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.42\%}}}\\
+\textbf{Zinc (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.86\%}} & \textcolor[HTML]{4285f4}{\textbf{33.28\%}} & \textcolor[HTML]{4285f4}{\textbf{22.12\%}}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.31\%}}}\\
+\textbf{Zinc (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.38\%}} & \textcolor[HTML]{4285f4}{\textbf{40.51\%}} & \textcolor[HTML]{4285f4}{\textbf{39.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.32\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{***15.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.82\%}}}\\
+\textbf{US commodities} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*16.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.33\%}}}\\
+\textbf{US commodities} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**19.95\%}}}\\
+\addlinespace
+\textbf{GB commodities} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-14.05\%}}}\\
+\textbf{GB commodities} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
 \bottomrule
-\endlastfoot
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{individual commodities}}\\
-\hspace{1em} & mean & 3.48\% & 21.37\% & 6.89\% & -4.51\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Corn-\#2 yellow (XCBT)}} & sd & 23\% & 29.54\% & 36.15\% & 21.8\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 5.49\% & 21.62\% & 8.89\% & -0.87\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Oats (XCBT)}} & sd & 32.22\% & 31.04\% & 34.67\% & 29.5\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 7.29\% & 12.06\% & 8.12\% & -0.33\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Soybean meal (XCBT)}} & sd & 26.34\% & 32.55\% & 31.78\% & 25.11\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 6.21\% & 15.57\% & 4.04\% & -7.39\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Soybean oil (XCBT)}} & sd & 21.43\% & 28.35\% & 25.75\% & 18.95\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 6.89\% & 13.36\% & 6.19\% & -3.82\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Soybeans (XCBT)}} & sd & 21.47\% & 30.04\% & 28\% & 21.22\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 5.07\% & 17.63\% & 6.68\% & -1.58\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Wheat-SRW (XCBT)}} & sd & 24.93\% & 33.03\% & 37.62\% & 26.58\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 0.39\% & 7.43\% & 7.13\% & 1.87\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cattle-feeder (XCME)}} & sd & 13.23\% & 15.16\% & 15.24\% & 18.69\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 3.45\% & 8.77\% & 4.13\% & 1.92\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cattle-live (XCME)}} & sd & 17.1\% & 17.43\% & 16.32\% & 18.3\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 0.73\% & 8.4\% & 12.69\% & -1.09\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Lean hogs (XCME)}} & sd & 38.33\% & 31.89\% & 30.37\% & 36.94\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 3.66\% & 16.35\% & 1.39\% & 3.65\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cocoa (IFUS)}} & sd & 32.66\% & 29.99\% & 31.03\% & 24.69\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & -5.91\% & 20.38\% & 2.2\% & 1.99\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Coffee-C (IFUS)}} & sd & 43.84\% & 32.3\% & 30.17\% & 31.86\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 3.24\% & 0.95\% & 12.53\% & 0.5\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cotton-\#2 (IFUS)}} & sd & 26.38\% & 29.01\% & 33.26\% & 20.61\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 1.9\% & -3.58\% & 11.74\% & 5.06\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Lumber (XCME)}} & sd & 30.58\% & 29.39\% & 36.31\% & 25.1\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 1.67\% & 13.87\% & 14.4\% & 3.8\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Orange juice (IFUS)}} & sd & 29.5\% & 33.01\% & 34.43\% & 29.37\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & -4.56\% & 24.87\% & 11.82\% & -1.16\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Sugar-\#11 (IFUS)}} & sd & 34.88\% & 33.25\% & 37.9\% & 28.72\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 35.38\% & 16.25\% & 0.93\% & 8.33\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Natural gas (XNYM)}} & sd & 61.55\% & 54.6\% & 53.58\% & 44.58\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 15.43\% & *28.74\% & 9.67\% & -5.64\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Crude oil-WTI (XNYM)}} & sd & 39.87\% & 32.56\% & 42.84\% & 34.69\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 16.65\% & 30.95\% & 10.59\% & -5.37\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Gasoline (XNYM)}} & sd & 42.77\% & 41.76\% & 40.07\% & 37.09\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 16.31\% & *29.88\% & 6.83\% & -3.44\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Heating oil (XNYM)}} & sd & 40.75\% & 35.09\% & 33.17\% & 30.56\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 1.45\% & *28.15\% & 6.19\% & -0.1\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Copper (XCEC)}} & sd & 21.23\% & 31.89\% & 34.91\% & 19.56\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 4.5\% & 14.35\% & 14.01\% & 0.53\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Gold (XCEC)}} & sd & 15.14\% & 18.89\% & 21.46\% & 14.41\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 9.12\% & 9.03\% & *29.12\% & 13.75\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Palladium (XNYM)}} & sd & 38.27\% & 32.71\% & 36.14\% & 25.38\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 12.93\% & 10.56\% & 7.29\% & -7.92\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Platinum (XNYM)}} & sd & 22.62\% & 22.66\% & 25.53\% & 19.48\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 6.19\% & 17.54\% & 21.96\% & -2.43\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Silver (XCEC)}} & sd & 22\% & 33.92\% & 39.87\% & 24.35\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 1.13\% & 13.78\% & -3.58\% & 3.15\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Aluminium (XLME)}} & sd & 17.6\% & 26.41\% & 26.48\% & 18.56\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 0.45\% & **28.59\% & 5.74\% & 0.03\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Copper (XLME)}} & sd & 19.25\% & 31.09\% & 34.27\% & 18.92\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 3.83\% & 28.99\% & 10.74\% & 2.07\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Lead (XLME)}} & sd & 19.64\% & 41.74\% & 41.05\% & 23.26\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 19.31\% & 12.5\% & 3.52\% & 0.31\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Nickel-primary (XLME)}} & sd & 32.26\% & 44.27\% & 41.45\% & 28.98\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 4.07\% & *29.1\% & 7.46\% & 1.68\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Tin-refined (XLME)}} & sd & 15.38\% & 31.71\% & 35.61\% & 18.79\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & -4.52\% & 20.13\% & 7.62\% & 9.07\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Zinc (XLME)}} & sd & 21.73\% & 38.77\% & 36.17\% & 23.25\%\\
-\cmidrule{1-6}\pagebreak[0]
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{equally weighted portfolios}}\\
-\hspace{1em} & mean & *6.89\% & **15.89\% & 9.39\% & -0.18\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{US commodities}} & sd & 10\% & 13.62\% & 17.58\% & 9.86\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 2.47\% & *21.77\% & 5.25\% & 2.72\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{GB commodities}} & sd & 15.66\% & 26.91\% & 30.24\% & 16.19\%\\*
+
 \end{longtable}
+
 \endgroup{}
@@
 
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}lllrrrr}
-\caption{\label{tab:stats-regimes}This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Mean values significant at the 1\%, 5\% and 10\% level are marked with ***, ** and * respectively.
-Aggregate CHP construction and corresponding regime definitions are discussed in section \ref{methods} while the results are discussed in section \ref{results}.}\\
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-time-reg-US-CHP}This table shows the average time
+series \(R^{2}\) for models where the returns series for the twenty four
+individual US commodities are independently regressed against relative
+change in their own commercial hedging pressure (CHP) series as well as
+against that in aggregate CHP, a market wide measure of CHP which
+calculation method is discussed in section Section~\ref{sec-methods}.
+Averages are calculated independently across the whole cross-section of
+US traded commodity assets considered in the study as well as across
+commodity sectors and subsectors for the four periods of interest (past:
+1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
+2013-2018). The results are discussed in section
+Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-asset & regime & estimate & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{regressor}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.17\%}}}\\
+\textbf{Δ\% commodity CHP} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.19\%}} & \textcolor[HTML]{4285f4}{\textbf{21.6\%}} & \textcolor[HTML]{4285f4}{\textbf{23.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.12\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.24\%}}}\\
+\textbf{Δ\% commodity CHP} & \textbf{agriculturals} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{6.23\%}} & \textcolor[HTML]{4285f4}{\textbf{10.53\%}} & \textcolor[HTML]{4285f4}{\textbf{6.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.88\%}}}\\
+\addlinespace
+\textbf{Δ\% commodity CHP} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.12\%}} & \textcolor[HTML]{4285f4}{\textbf{19.45\%}} & \textcolor[HTML]{4285f4}{\textbf{16\%}} & \textcolor[HTML]{4285f4}{\textbf{10.96\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
+\textbf{Δ\% commodity CHP} & \textbf{energy} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{18.87\%}} & \textcolor[HTML]{4285f4}{\textbf{12.85\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.32\%}}}\\
+\textbf{Δ\% commodity CHP} & \textbf{metals} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{47.38\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}} & \textcolor[HTML]{4285f4}{\textbf{18.07\%}} & \textcolor[HTML]{4285f4}{\textbf{34.9\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.93\%}}}\\
+\textbf{Δ\% aggregate CHP} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{5.37\%}} & \textcolor[HTML]{4285f4}{\textbf{7.12\%}} & \textcolor[HTML]{4285f4}{\textbf{14.72\%}} & \textcolor[HTML]{4285f4}{\textbf{7.49\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.23\%}}}\\
+\textbf{Δ\% aggregate CHP} & \textbf{agriculturals} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{7.25\%}} & \textcolor[HTML]{4285f4}{\textbf{5.4\%}} & \textcolor[HTML]{4285f4}{\textbf{19.75\%}} & \textcolor[HTML]{4285f4}{\textbf{8.45\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.26\%}}}\\
+\addlinespace
+\textbf{Δ\% aggregate CHP} & \textbf{agriculturals} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{5.64\%}} & \textcolor[HTML]{4285f4}{\textbf{10.35\%}} & \textcolor[HTML]{4285f4}{\textbf{6.98\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.45\%}}}\\
+\textbf{Δ\% aggregate CHP} & \textbf{energy} & \textbf{gas} & \textcolor[HTML]{4285f4}{\textbf{2.65\%}} & \textcolor[HTML]{4285f4}{\textbf{2.58\%}} & \textcolor[HTML]{4285f4}{\textbf{2.6\%}} & \textcolor[HTML]{4285f4}{\textbf{0.27\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.17\%}}}\\
+\textbf{Δ\% aggregate CHP} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{8.36\%}} & \textcolor[HTML]{4285f4}{\textbf{15.67\%}} & \textcolor[HTML]{4285f4}{\textbf{22.37\%}} & \textcolor[HTML]{4285f4}{\textbf{15.33\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.67\%}}}\\
+\textbf{Δ\% aggregate CHP} & \textbf{metals} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{7.92\%}} & \textcolor[HTML]{4285f4}{\textbf{16.4\%}} & \textcolor[HTML]{4285f4}{\textbf{21.98\%}} & \textcolor[HTML]{4285f4}{\textbf{17.25\%}}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
+\newpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-correlations-periods}This table shows the average
+time series \(R^{2}\) for models where the returns series for the twenty
+four individual US commodities are independently regressed against
+relative change in their own commercial hedging pressure (CHP) series as
+well as against that in aggregate CHP, a market wide measure of CHP
+which calculation method is discussed in section
+Section~\ref{sec-methods}. Averages are calculated independently across
+the whole cross-section of US traded commodity assets considered in the
+study as well as across commodity sectors and subsectors for the four
+periods of interest (past: 1997-2003; financialisation: 2004-2008;
+crisis: 2008-2013; post-crisis: 2013-2018). The results are discussed in
+section Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-asset & regime & estimate & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endhead
-
-\endfoot
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0737}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1638}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2849}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1282}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0724}} & \textcolor[HTML]{4285f4}{\textbf{0.1790}} & \textcolor[HTML]{4285f4}{\textbf{0.2709}} & \textcolor[HTML]{4285f4}{\textbf{0.1001}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0748}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1501}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2985}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1495}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0684}} & \textcolor[HTML]{4285f4}{\textbf{0.1545}} & \textcolor[HTML]{4285f4}{\textbf{0.2526}} & \textcolor[HTML]{4285f4}{\textbf{0.1096}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0642}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1697}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2323}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0859}}}\\
+\addlinespace
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0720}} & \textcolor[HTML]{4285f4}{\textbf{0.1402}} & \textcolor[HTML]{4285f4}{\textbf{0.2706}} & \textcolor[HTML]{4285f4}{\textbf{0.1268}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0910}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1305}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2322}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1075}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0799}} & \textcolor[HTML]{4285f4}{\textbf{0.1421}} & \textcolor[HTML]{4285f4}{\textbf{0.1975}} & \textcolor[HTML]{4285f4}{\textbf{0.0955}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1018}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2611}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1186}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4421}} & \textcolor[HTML]{4285f4}{\textbf{0.4898}} & \textcolor[HTML]{4285f4}{\textbf{0.5673}} & \textcolor[HTML]{4285f4}{\textbf{0.3728}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4312}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5283}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5749}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3289}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4570}} & \textcolor[HTML]{4285f4}{\textbf{0.4510}} & \textcolor[HTML]{4285f4}{\textbf{0.5675}} & \textcolor[HTML]{4285f4}{\textbf{0.4161}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3340}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2868}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3707}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3333}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3053}} & \textcolor[HTML]{4285f4}{\textbf{0.2652}} & \textcolor[HTML]{4285f4}{\textbf{0.3906}} & \textcolor[HTML]{4285f4}{\textbf{0.3220}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3605}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3150}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3557}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3483}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0391}} & \textcolor[HTML]{4285f4}{\textbf{0.0853}} & \textcolor[HTML]{4285f4}{\textbf{0.1584}} & \textcolor[HTML]{4285f4}{\textbf{0.0764}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0437}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0845}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1210}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0685}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0334}} & \textcolor[HTML]{4285f4}{\textbf{0.0874}} & \textcolor[HTML]{4285f4}{\textbf{0.1937}} & \textcolor[HTML]{4285f4}{\textbf{0.0833}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4908}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5892}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4687}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4203}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.4844}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}} & \textcolor[HTML]{4285f4}{\textbf{0.4601}} & \textcolor[HTML]{4285f4}{\textbf{0.4179}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4957}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5869}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4779}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4210}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.7278}} & \textcolor[HTML]{4285f4}{\textbf{0.7846}} & \textcolor[HTML]{4285f4}{\textbf{0.7692}} & \textcolor[HTML]{4285f4}{\textbf{0.7175}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6962}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7854}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7282}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7606}} & \textcolor[HTML]{4285f4}{\textbf{0.7856}} & \textcolor[HTML]{4285f4}{\textbf{0.7716}} & \textcolor[HTML]{4285f4}{\textbf{0.7134}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2167}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5553}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4721}}}\\
+\addlinespace
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.2201}} & \textcolor[HTML]{4285f4}{\textbf{0.5418}} & \textcolor[HTML]{4285f4}{\textbf{0.6353}} & \textcolor[HTML]{4285f4}{\textbf{0.4155}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2145}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5709}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5035}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.2883}} & \textcolor[HTML]{4285f4}{\textbf{0.6305}} & \textcolor[HTML]{4285f4}{\textbf{0.6704}} & \textcolor[HTML]{4285f4}{\textbf{0.5762}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3070}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6061}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6991}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5386}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.6591}} & \textcolor[HTML]{4285f4}{\textbf{0.6615}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4047}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4691}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6536}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4412}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3987}} & \textcolor[HTML]{4285f4}{\textbf{0.4753}} & \textcolor[HTML]{4285f4}{\textbf{0.6729}} & \textcolor[HTML]{4285f4}{\textbf{0.3954}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4108}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6456}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4797}}}\\
 \bottomrule
-\endlastfoot
-\addlinespace[0.3em]
-\multicolumn{7}{l}{\textbf{individual commodities}}\\
-\hspace{1em} &  & mean & -4.86\% & 19.26\% & 20.48\% & -8.74\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 23.07\% & 29.14\% & 31.59\% & 21\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 11.3\% & 23.54\% & -4.43\% & 0.78\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Corn-\#2 yellow (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 23\% & 30.01\% & 40.14\% & 22.68\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & -5.39\% & 7.82\% & 7.85\% & 2.56\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 29.02\% & 33.82\% & 31.43\% & 31.55\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 16.95\% & *35.38\% & 11.68\% & -3.17\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Oats (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 35.22\% & 28.1\% & 37.7\% & 27.5\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 13.15\% & 8.22\% & 16.04\% & -3.52\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 27.77\% & 33.06\% & 25.7\% & 25.1\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 1.52\% & 15.91\% & 2.32\% & 2.22\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Soybean meal (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 24.94\% & 32.13\% & 36.85\% & 25.32\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 14.79\% & 14.62\% & 20.34\% & -9.44\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.35\% & 28.94\% & 22.33\% & 18.19\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -2.68\% & 16.62\% & -10.01\% & -4.12\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Soybean oil (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 21.55\% & 27.91\% & 28.65\% & 19.79\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 13.69\% & 0.93\% & 13.42\% & -11.45\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.93\% & 34.58\% & 24.39\% & 22.04\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.16\% & 25.71\% & 0.96\% & 3.75\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Soybeans (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 21.09\% & 24.74\% & 31.11\% & 20.56\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & -2.7\% & 19.02\% & 0.98\% & 0.44\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 25.79\% & 36\% & 37.53\% & 26.57\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 11.78\% & 16.29\% & 14.57\% & -2.77\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Wheat-SRW (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 24.04\% & 29.84\% & 37.73\% & 26.72\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 2.31\% & **20.52\% & 7.51\% & 6.58\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 12.79\% & 14.93\% & 13.39\% & 20.14\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.81\% & -5.49\% & 7.28\% & -3.12\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cattle-feeder (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 13.67\% & 15.35\% & 16.91\% & 17.23\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 8.39\% & 14.2\% & 5.87\% & -2.07\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 16.65\% & 17.91\% & 14.97\% & 19.9\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.34\% & 3.43\% & 2.7\% & 5.82\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cattle-live (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 17.49\% & 16.99\% & 17.57\% & 16.66\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 12.34\% & 16.3\% & 18.23\% & 19.24\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 37.6\% & 35.73\% & 27.83\% & 35.61\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -10.5\% & 0.6\% & 7.5\% & -20.66\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Lean hogs (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 39.22\% & 27.67\% & 32.78\% & 38.28\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 4.12\% & 9.25\% & -9.56\% & -2.98\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 33.57\% & 31.05\% & 26.93\% & 25.86\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 3.67\% & 23.43\% & 12.92\% & 10.29\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cocoa (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 31.81\% & 28.91\% & 34.66\% & 23.57\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 4.51\% & 26.49\% & 2.66\% & 14.36\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 48.82\% & 32.6\% & 29.92\% & 31.52\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -16.87\% & 14.38\% & 3.4\% & -10.24\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Coffee-C (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 38.35\% & 32.06\% & 30.22\% & 32.24\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 22.64\% & 7.85\% & 35.53\% & 10.84\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 26.02\% & 29.71\% & 33.94\% & 21.33\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -16.46\% & -5.92\% & -9.36\% & -8.91\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cotton-\#2 (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 26.77\% & 28.35\% & 32.59\% & 19.95\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & -8.48\% & -2.37\% & 29.11\% & **26.99\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 30.43\% & 30.72\% & 35.45\% & 21.26\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 11.68\% & -4.77\% & -5.04\% & -17.14\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Lumber (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 30.56\% & 28.2\% & 37.23\% & 28.45\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & -2.38\% & -2.22\% & 18.24\% & 18.64\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 28.01\% & 33.01\% & 30.09\% & 28.64\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 5.83\% & 29.93\% & 12.29\% & -8.64\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Orange juice (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 31.05\% & 33.1\% & 38.06\% & 30.11\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 11.98\% & 29.51\% & 2.7\% & -8.07\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 33.23\% & 33.6\% & 41.29\% & 27.69\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -20.49\% & 20.35\% & 21.47\% & 4.7\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Sugar-\#11 (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 36.48\% & 32.98\% & 34.09\% & 29.83\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & **85.84\% & 4.76\% & -2.32\% & 18.33\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 63.46\% & 47.3\% & 48.85\% & 42.59\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -11.98\% & 27.84\% & 4.77\% & 3.25\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Natural gas (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 59.76\% & 61.3\% & 58.18\% & 46.41\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 29.17\% & *35.61\% & 11.47\% & 14.24\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 36.74\% & 32.09\% & 28.19\% & 26.94\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 2.21\% & 22.04\% & 9.95\% & -24.85\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Crude oil-WTI (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 42.74\% & 33.1\% & 53.7\% & 41.08\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 39\% & 19.82\% & 23.98\% & 9.69\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 42.47\% & 39.38\% & 31.41\% & 32.1\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -5.22\% & 42.13\% & -0.09\% & -19.47\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Gasoline (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 43.14\% & 44.13\% & 47.11\% & 41.71\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 36.32\% & 29.41\% & 25.56\% & 15.16\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 41.37\% & 33.33\% & 25.95\% & 24.62\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -2.74\% & 30.5\% & -10.77\% & -21.62\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Heating oil (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 40.19\% & 36.98\% & 39.16\% & 35.69\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 3.14\% & 22.17\% & 16.53\% & 12.1\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 20.71\% & 30.05\% & 25.73\% & 18.16\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.28\% & 34.17\% & -3.46\% & -12.15\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Copper (XCEC)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 21.78\% & 33.69\% & 42.28\% & 20.87\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 9.19\% & 13.37\% & 9.37\% & 4.21\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 16.89\% & 19.2\% & 17.03\% & 12.36\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.01\% & 15.37\% & 19.1\% & -3.1\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Gold (XCEC)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 13.24\% & 18.58\% & 25.21\% & 16.23\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & **49.79\% & 24.47\% & 30.01\% & **31.93\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 34.98\% & 34.23\% & 33.49\% & 23.82\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -30.19\% & -6.3\% & 30.58\% & -4.88\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Palladium (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 41.22\% & 31.2\% & 38.71\% & 26.8\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & **29.46\% & *25.07\% & 10.46\% & 1.17\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 22.1\% & 22.51\% & 21.24\% & 18.04\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -3.22\% & -3.81\% & 8.04\% & -17.28\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Platinum (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 23.12\% & 22.81\% & 28.75\% & 20.8\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 5.98\% & 14.29\% & 19.66\% & 3.44\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.07\% & 32.5\% & 37.17\% & 20.3\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 6.57\% & 20.83\% & 26.77\% & -8.09\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Silver (XCEC)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 22.93\% & 35.34\% & 42.44\% & 27.77\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 2.56\% & 14.78\% & 16.25\% & **23.68\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 14.82\% & 25.57\% & 24.94\% & 18.94\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.38\% & 12.86\% & -23.04\% & -16.74\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Aluminium (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 20.13\% & 27.29\% & 28.01\% & 18.23\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 1.54\% & 25.22\% & 18.66\% & 11.99\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 17.98\% & 29.01\% & 25.53\% & 17.92\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.95\% & 32\% & -6.78\% & -11.89\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Copper (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 20.41\% & 32.98\% & 41.31\% & 19.86\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 7.59\% & 11.21\% & 9.87\% & 17.05\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 19.16\% & 39.91\% & 35.35\% & 23.37\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.09\% & *46.48\% & 12.65\% & -13.41\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Lead (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 20.12\% & 43.16\% & 46.22\% & 23.09\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 23.25\% & -39.24\% & 16.3\% & **35.09\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 30.23\% & 41.62\% & 34.48\% & 29.13\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 15.46\% & **63.47\% & -7.67\% & **-34.64\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Nickel-primary (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 34.28\% & 46.72\% & 47.44\% & 28.6\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & *15.83\% & 34.62\% & 23.7\% & 4.48\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 14.99\% & 31.4\% & 29.09\% & 15.27\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -7.78\% & 23.88\% & -6.82\% & -1.69\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Tin-refined (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 15.77\% & 32.08\% & 41.13\% & 21.68\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & -9.06\% & 2.95\% & 10.05\% & **29.42\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.15\% & 36.86\% & 33.28\% & 22.12\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.13\% & 37.11\% & 5.43\% & -11.31\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Zinc (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 22.38\% & 40.51\% & 39.03\% & 24.32\%\\
-\cmidrule{1-7}\pagebreak[0]
-\addlinespace[0.3em]
-\multicolumn{7}{l}{\textbf{equally weighted portfolios}}\\
-\hspace{1em} &  & mean & ***15.44\% & *15.66\% & 13.4\% & 6.82\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 9.88\% & 14.21\% & 14.83\% & 8.59\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -1.09\% & *16.16\% & 4.9\% & -6.33\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{US commodities}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 10.09\% & 13.05\% & 19.98\% & 10.95\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 4.41\% & 8.01\% & 15.06\% & **19.95\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 14.39\% & 25.92\% & 25.94\% & 15.13\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 0.34\% & *35.56\% & -5.24\% & -14.05\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{GB commodities}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 16.87\% & 27.88\% & 34.06\% & 17.1\%\\*
+
 \end{longtable}
+
 \endgroup{}
@@
 
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}lllrrrr}
-\caption{\label{tab:time-reg-US-CHP}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \ref{methods}.
-Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The results are discussed in section \ref{results}.}\\
+\begin{landscape}\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}l>{}r>{}r>{}r>{}r>{}r>{}r>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-correlations-years}This table shows the average
+pairwise correlation coefficients calculated independently across the
+whole cross-section of commodity assets considered in the study as well
+as across countries and commodity sectors and subsectors by year for the
+whole periods of interest (1997-2018). For each year, the results are
+calculated independently over the entire year as well as over phases of
+aggregate backwardation and contango. Aggregate CHP construction and
+corresponding regime definitions are discussed in section
+Section~\ref{sec-methods} while the results are discussed in section
+Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-regressor & sector & subsector & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{decade}} & \textcolor{black}{\textbf{0}} & \textcolor{black}{\textbf{1}} & \textcolor{black}{\textbf{2}} & \textcolor{black}{\textbf{3}} & \textcolor{black}{\textbf{4}} & \textcolor{black}{\textbf{5}} & \textcolor{black}{\textbf{6}} & \textcolor{black}{\textbf{7}} & \textcolor{black}{\textbf{8}} & \textcolor{black}{\textbf{9}}\\
 \midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0401}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0812}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0822}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0652}} & \textcolor[HTML]{4285f4}{\textbf{0.0719}} & \textcolor[HTML]{4285f4}{\textbf{0.0796}} & \textcolor[HTML]{4285f4}{\textbf{0.0848}} & \textcolor[HTML]{4285f4}{\textbf{0.1242}} & \textcolor[HTML]{4285f4}{\textbf{0.1247}} & \textcolor[HTML]{4285f4}{\textbf{0.1650}} & \textcolor[HTML]{4285f4}{\textbf{0.1541}} & \textcolor[HTML]{4285f4}{\textbf{0.3334}} & \textcolor[HTML]{4285f4}{\textbf{0.2913}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2743}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2837}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2235}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1432}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1139}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1547}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1339}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0963}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1374}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0536}} & \textcolor[HTML]{4285f4}{\textbf{0.0811}} & \textcolor[HTML]{4285f4}{\textbf{0.0803}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0597}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0600}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0723}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1073}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1164}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1502}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1479}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3284}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2621}}}\\
+\addlinespace
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2275}} & \textcolor[HTML]{4285f4}{\textbf{0.2541}} & \textcolor[HTML]{4285f4}{\textbf{0.1850}} & \textcolor[HTML]{4285f4}{\textbf{0.1018}} & \textcolor[HTML]{4285f4}{\textbf{0.0986}} & \textcolor[HTML]{4285f4}{\textbf{0.1371}} & \textcolor[HTML]{4285f4}{\textbf{0.1064}} & \textcolor[HTML]{4285f4}{\textbf{0.0905}} & \textcolor[HTML]{4285f4}{\textbf{0.1197}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0827}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0916}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0918}} & \textcolor[HTML]{4285f4}{\textbf{0.0967}} & \textcolor[HTML]{4285f4}{\textbf{0.0734}} & \textcolor[HTML]{4285f4}{\textbf{0.0827}} & \textcolor[HTML]{4285f4}{\textbf{0.1111}} & \textcolor[HTML]{4285f4}{\textbf{0.1090}} & \textcolor[HTML]{4285f4}{\textbf{0.1125}} & \textcolor[HTML]{4285f4}{\textbf{0.1131}} & \textcolor[HTML]{4285f4}{\textbf{0.3034}} & \textcolor[HTML]{4285f4}{\textbf{0.2507}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2038}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2304}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1583}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0716}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0846}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1360}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1148}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1181}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.5243}} & \textcolor[HTML]{4285f4}{\textbf{0.4882}} & \textcolor[HTML]{4285f4}{\textbf{0.5650}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4870}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3851}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3402}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4473}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5335}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4594}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5040}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6325}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5681}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.5389}} & \textcolor[HTML]{4285f4}{\textbf{0.6424}} & \textcolor[HTML]{4285f4}{\textbf{0.5592}} & \textcolor[HTML]{4285f4}{\textbf{0.3199}} & \textcolor[HTML]{4285f4}{\textbf{0.3134}} & \textcolor[HTML]{4285f4}{\textbf{0.4390}} & \textcolor[HTML]{4285f4}{\textbf{0.3872}} & \textcolor[HTML]{4285f4}{\textbf{0.4123}} & \textcolor[HTML]{4285f4}{\textbf{0.3618}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2192}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3724}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3453}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.2762}} & \textcolor[HTML]{4285f4}{\textbf{0.3315}} & \textcolor[HTML]{4285f4}{\textbf{0.3243}} & \textcolor[HTML]{4285f4}{\textbf{0.3497}} & \textcolor[HTML]{4285f4}{\textbf{0.2937}} & \textcolor[HTML]{4285f4}{\textbf{0.4170}} & \textcolor[HTML]{4285f4}{\textbf{0.2784}} & \textcolor[HTML]{4285f4}{\textbf{0.2744}} & \textcolor[HTML]{4285f4}{\textbf{0.2822}} & \textcolor[HTML]{4285f4}{\textbf{0.3365}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3568}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4772}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3585}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1783}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3532}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4246}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3445}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2994}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{-0.0042}} & \textcolor[HTML]{4285f4}{\textbf{-0.0001}} & \textcolor[HTML]{4285f4}{\textbf{0.0128}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0603}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0289}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0470}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0807}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0577}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0624}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0765}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0485}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2484}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1710}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.1273}} & \textcolor[HTML]{4285f4}{\textbf{0.1400}} & \textcolor[HTML]{4285f4}{\textbf{0.1038}} & \textcolor[HTML]{4285f4}{\textbf{0.0568}} & \textcolor[HTML]{4285f4}{\textbf{0.0413}} & \textcolor[HTML]{4285f4}{\textbf{0.0983}} & \textcolor[HTML]{4285f4}{\textbf{0.1280}} & \textcolor[HTML]{4285f4}{\textbf{0.0825}} & \textcolor[HTML]{4285f4}{\textbf{0.0565}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4060}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4552}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5256}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.4362}} & \textcolor[HTML]{4285f4}{\textbf{0.5186}} & \textcolor[HTML]{4285f4}{\textbf{0.5682}} & \textcolor[HTML]{4285f4}{\textbf{0.5248}} & \textcolor[HTML]{4285f4}{\textbf{0.6212}} & \textcolor[HTML]{4285f4}{\textbf{0.6402}} & \textcolor[HTML]{4285f4}{\textbf{0.5082}} & \textcolor[HTML]{4285f4}{\textbf{0.5530}} & \textcolor[HTML]{4285f4}{\textbf{0.6278}} & \textcolor[HTML]{4285f4}{\textbf{0.4840}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4549}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4752}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3796}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2889}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4103}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4282}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4442}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3890}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4270}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.7207}} & \textcolor[HTML]{4285f4}{\textbf{0.7946}} & \textcolor[HTML]{4285f4}{\textbf{0.8527}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7632}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8072}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8321}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7377}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7703}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7895}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7460}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.8835}} & \textcolor[HTML]{4285f4}{\textbf{0.7867}} & \textcolor[HTML]{4285f4}{\textbf{0.6692}} & \textcolor[HTML]{4285f4}{\textbf{0.6075}} & \textcolor[HTML]{4285f4}{\textbf{0.6710}} & \textcolor[HTML]{4285f4}{\textbf{0.7069}} & \textcolor[HTML]{4285f4}{\textbf{0.7547}} & \textcolor[HTML]{4285f4}{\textbf{0.6672}} & \textcolor[HTML]{4285f4}{\textbf{0.7786}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2296}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2449}}}\\
+\addlinespace
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.1860}} & \textcolor[HTML]{4285f4}{\textbf{0.1832}} & \textcolor[HTML]{4285f4}{\textbf{0.1992}} & \textcolor[HTML]{4285f4}{\textbf{0.2290}} & \textcolor[HTML]{4285f4}{\textbf{0.4923}} & \textcolor[HTML]{4285f4}{\textbf{0.4480}} & \textcolor[HTML]{4285f4}{\textbf{0.6328}} & \textcolor[HTML]{4285f4}{\textbf{0.5426}} & \textcolor[HTML]{4285f4}{\textbf{0.5664}} & \textcolor[HTML]{4285f4}{\textbf{0.5547}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6297}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6458}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6649}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6160}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4531}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4850}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4269}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3584}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5259}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.3063}} & \textcolor[HTML]{4285f4}{\textbf{0.3451}} & \textcolor[HTML]{4285f4}{\textbf{0.3308}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2934}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3053}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2959}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5688}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6969}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6143}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6428}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6713}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.7004}} & \textcolor[HTML]{4285f4}{\textbf{0.7107}} & \textcolor[HTML]{4285f4}{\textbf{0.7089}} & \textcolor[HTML]{4285f4}{\textbf{0.6988}} & \textcolor[HTML]{4285f4}{\textbf{0.5620}} & \textcolor[HTML]{4285f4}{\textbf{0.6088}} & \textcolor[HTML]{4285f4}{\textbf{0.5652}} & \textcolor[HTML]{4285f4}{\textbf{0.4746}} & \textcolor[HTML]{4285f4}{\textbf{0.5716}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2289}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3601}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4487}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.3550}} & \textcolor[HTML]{4285f4}{\textbf{0.4082}} & \textcolor[HTML]{4285f4}{\textbf{0.4775}} & \textcolor[HTML]{4285f4}{\textbf{0.5526}} & \textcolor[HTML]{4285f4}{\textbf{0.5068}} & \textcolor[HTML]{4285f4}{\textbf{0.4792}} & \textcolor[HTML]{4285f4}{\textbf{0.4340}} & \textcolor[HTML]{4285f4}{\textbf{0.4653}} & \textcolor[HTML]{4285f4}{\textbf{0.5795}} & \textcolor[HTML]{4285f4}{\textbf{0.6647}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6886}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6742}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6606}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4700}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5003}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4636}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3810}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3598}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+\end{landscape}
+
+\newpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-regressions-index}This table shows the average time
+series regression coefficients for models where the returns series for
+all the commodity assets considered in the study are independently
+regressed against the return series for our market factor, an equally
+weighted portfolio of the 24 US commodities considered in the study. The
+results are calculated independently across countries as well as
+commodity sectors and subsectors for the four periods of interest (past:
+1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
+2013-2018). The market factor construction is discussed in section
+Section~\ref{sec-methods} while the results are discussed in section
+Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-regressor & sector & subsector & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endhead
-
-\endfoot
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8556}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9709}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0352}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9438}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.7706}} & \textcolor[HTML]{4285f4}{\textbf{0.7965}} & \textcolor[HTML]{4285f4}{\textbf{0.8535}} & \textcolor[HTML]{4285f4}{\textbf{0.8252}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9891}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1982}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0301}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{0.4320}} & \textcolor[HTML]{4285f4}{\textbf{0.2059}} & \textcolor[HTML]{4285f4}{\textbf{0.3317}} & \textcolor[HTML]{4285f4}{\textbf{0.5484}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7213}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6900}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7953}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7589}}}\\
+\addlinespace
+\textbf{US} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{2.3308}} & \textcolor[HTML]{4285f4}{\textbf{1.6106}} & \textcolor[HTML]{4285f4}{\textbf{1.3977}} & \textcolor[HTML]{4285f4}{\textbf{1.7639}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6992}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.7090}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0044}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2585}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{2.2080}} & \textcolor[HTML]{4285f4}{\textbf{1.5778}} & \textcolor[HTML]{4285f4}{\textbf{1.5288}} & \textcolor[HTML]{4285f4}{\textbf{1.9324}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6320}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1252}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1212}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9131}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{0.4902}} & \textcolor[HTML]{4285f4}{\textbf{1.1178}} & \textcolor[HTML]{4285f4}{\textbf{1.4140}} & \textcolor[HTML]{4285f4}{\textbf{0.8780}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1271}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0480}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9219}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.8520}} & \textcolor[HTML]{4285f4}{\textbf{1.1761}} & \textcolor[HTML]{4285f4}{\textbf{0.7192}}\\
 \bottomrule
-\endlastfoot
- & all &  & 25.79\% & 20.72\% & 22.46\% & 27.17\%\\
-\nopagebreak
- &  & \multirow[t]{-2}{*}{\raggedright\arraybackslash all} & 25.19\% & 21.6\% & 23.91\% & 28.12\%\\
-\nopagebreak
- &  & grains & 33.18\% & 27.86\% & 29.15\% & 36.24\%\\
-\nopagebreak
- &  & livestock & 6.23\% & 10.53\% & 6.89\% & 4.34\%\\
-\nopagebreak
- & \multirow[t]{-4}{*}{\raggedright\arraybackslash agriculturals} & softs & 26.68\% & 20.89\% & 27.19\% & 31.88\%\\
-\nopagebreak
- &  & all & 25.12\% & 19.45\% & 16\% & 10.96\%\\
-\nopagebreak
- &  & gas & 19.69\% & 15.65\% & 7.36\% & 5.29\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash energy} & petroleum & 26.93\% & 20.71\% & 18.87\% & 12.85\%\\
-\nopagebreak
- &  & all & 28.12\% & 19.1\% & 23.27\% & 37.32\%\\
-\nopagebreak
- &  & base & 47.38\% & 25.86\% & 18.07\% & 34.9\%\\
-\nopagebreak
-\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{Δ\% commodity CHP}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash metals} & precious & 23.3\% & 17.41\% & 24.57\% & 37.93\%\\
-\cmidrule{1-7}\pagebreak[0]
- & all &  & 5.37\% & 7.12\% & 14.72\% & 7.49\%\\
-\nopagebreak
- &  & \multirow[t]{-2}{*}{\raggedright\arraybackslash all} & 4.91\% & 4.5\% & 12.14\% & 6.23\%\\
-\nopagebreak
- &  & grains & 7.25\% & 5.4\% & 19.75\% & 8.45\%\\
-\nopagebreak
- &  & livestock & 1.35\% & 0.41\% & 0.52\% & 0.26\%\\
-\nopagebreak
- & \multirow[t]{-4}{*}{\raggedright\arraybackslash agriculturals} & softs & 4.34\% & 5.64\% & 10.35\% & 6.98\%\\
-\nopagebreak
- &  & all & 3.35\% & 6.27\% & 14.83\% & 2.45\%\\
-\nopagebreak
- &  & gas & 2.65\% & 2.58\% & 2.6\% & 0.27\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash energy} & petroleum & 3.59\% & 7.49\% & 18.9\% & 3.17\%\\
-\nopagebreak
- &  & all & 8.36\% & 15.67\% & 22.37\% & 15.33\%\\
-\nopagebreak
- &  & base & 10.12\% & 12.74\% & 23.94\% & 7.67\%\\
-\nopagebreak
-\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{Δ\% aggregate CHP}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash metals} & precious & 7.92\% & 16.4\% & 21.98\% & 17.25\%\\*
+
 \end{longtable}
+
 \endgroup{}
@@
 
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}lllrrrrr}
-\caption{\label{tab:correlations-periods}This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-For each period, the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
-Aggregate CHP construction and corresponding regime definitions are discussed in section \ref{methods} while the results are discussed in section \ref{results}.}\\
+\begin{landscape}\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-regressions-factors}This table shows the average
+time series regression \(R^{2}\) for models where the returns series for
+all the commodity assets considered in the study are independently
+regressed against the return series for our mimicking portfolios for
+risk factors in returns, including the market, CHP, open interest and
+term structure factors. The results are calculated independently across
+countries and commodity sectors and subsectors for the four periods of
+interest (past: 1997-2003; financialisation: 2004-2008; crisis:
+2008-2013; post-crisis: 2013-2018); for earch period the results are
+calculated independently over the entire period as well as over phases
+of aggregate backwardation and contango. Factors as well as aggregate
+CHP construction and corresponding regime definitions are discussed in
+section Section~\ref{sec-methods} while the results are discussed in
+section Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-country & sector & subsector & past & regime & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{factor}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-country & sector & subsector & past & regime & financialisation & crisis & post-crisis\\
-\midrule
-\endhead
-
-\endfoot
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.73\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.44\%}} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{11.82\%}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.99\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.93\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.43\%}} & \textcolor[HTML]{4285f4}{\textbf{3.78\%}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}}\\
+\addlinespace
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.54\%}} & \textcolor[HTML]{4285f4}{\textbf{5.55\%}} & \textcolor[HTML]{4285f4}{\textbf{4.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.69\%}} & \textcolor[HTML]{4285f4}{\textbf{5.47\%}} & \textcolor[HTML]{4285f4}{\textbf{3.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.12\%}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.74\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{2.95\%}} & \textcolor[HTML]{4285f4}{\textbf{5.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.39\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{3.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.73\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{11.26\%}} & \textcolor[HTML]{4285f4}{\textbf{23.68\%}} & \textcolor[HTML]{4285f4}{\textbf{28.95\%}} & \textcolor[HTML]{4285f4}{\textbf{13.12\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.66\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.4\%}} & \textcolor[HTML]{4285f4}{\textbf{5.8\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.54\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{6.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.14\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.79\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{5\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{2.87\%}} & \textcolor[HTML]{4285f4}{\textbf{5.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.85\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{5.73\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.07\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.57\%}} & \textcolor[HTML]{4285f4}{\textbf{18.68\%}} & \textcolor[HTML]{4285f4}{\textbf{23.01\%}} & \textcolor[HTML]{4285f4}{\textbf{11.56\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.91\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.03\%}} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.11\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.21\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}} & \textcolor[HTML]{4285f4}{\textbf{1.56\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.85\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.73\%}} & \textcolor[HTML]{4285f4}{\textbf{2.16\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.55\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.69\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.27\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{14.54\%}} & \textcolor[HTML]{4285f4}{\textbf{34.68\%}} & \textcolor[HTML]{4285f4}{\textbf{38.84\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{44.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.71\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.64\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{0.78\%}} & \textcolor[HTML]{4285f4}{\textbf{2.98\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.46\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.06\%}} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.04\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{7.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.5\%}} & \textcolor[HTML]{4285f4}{\textbf{3.8\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.24\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}} & \textcolor[HTML]{4285f4}{\textbf{2.08\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.56\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.25\%}} & \textcolor[HTML]{4285f4}{\textbf{2.18\%}} & \textcolor[HTML]{4285f4}{\textbf{3.3\%}} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.84\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{6.2\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{2.06\%}} & \textcolor[HTML]{4285f4}{\textbf{3.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.94\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.35\%}} & \textcolor[HTML]{4285f4}{\textbf{1.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.71\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.47\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.48\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.82\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}} & \textcolor[HTML]{4285f4}{\textbf{15.58\%}} & \textcolor[HTML]{4285f4}{\textbf{8.44\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.6\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.51\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}} & \textcolor[HTML]{4285f4}{\textbf{0.9\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.41\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}} & \textcolor[HTML]{4285f4}{\textbf{2.42\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.08\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.9\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{26.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{33.74\%}} & \textcolor[HTML]{4285f4}{\textbf{20.94\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.77\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{3.5\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.68\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{6.05\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{7.91\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.67\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{38.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.93\%}} & \textcolor[HTML]{4285f4}{\textbf{17.59\%}} & \textcolor[HTML]{4285f4}{\textbf{22.07\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{41.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.13\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.99\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{1.86\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.16\%}} & \textcolor[HTML]{4285f4}{\textbf{2.76\%}} & \textcolor[HTML]{4285f4}{\textbf{5.88\%}} & \textcolor[HTML]{4285f4}{\textbf{1.26\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.86\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{21.36\%}} & \textcolor[HTML]{4285f4}{\textbf{17.54\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{7.17\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.96\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.37\%}} & \textcolor[HTML]{4285f4}{\textbf{3.62\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{16.2\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.3\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.26\%}} & \textcolor[HTML]{4285f4}{\textbf{13.46\%}} & \textcolor[HTML]{4285f4}{\textbf{13.84\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.03\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{23.23\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{14.53\%}} & \textcolor[HTML]{4285f4}{\textbf{16.64\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.41\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{4.24\%}} & \textcolor[HTML]{4285f4}{\textbf{7.16\%}} & \textcolor[HTML]{4285f4}{\textbf{5.22\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.9\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.48\%}} & \textcolor[HTML]{4285f4}{\textbf{6.51\%}} & \textcolor[HTML]{4285f4}{\textbf{4.6\%}} & \textcolor[HTML]{4285f4}{\textbf{4.55\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{48.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.91\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{27.65\%}} & \textcolor[HTML]{4285f4}{\textbf{37.22\%}} & \textcolor[HTML]{4285f4}{\textbf{40.79\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.71\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.99\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}} & \textcolor[HTML]{4285f4}{\textbf{0.96\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{45.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.56\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{44.02\%}} & \textcolor[HTML]{4285f4}{\textbf{27.52\%}} & \textcolor[HTML]{4285f4}{\textbf{18.61\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{47.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{43.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.7\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.57\%}} & \textcolor[HTML]{4285f4}{\textbf{4.95\%}} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{6.3\%}} & \textcolor[HTML]{4285f4}{\textbf{0.16\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.58\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.5\%}} & \textcolor[HTML]{4285f4}{\textbf{31.77\%}} & \textcolor[HTML]{4285f4}{\textbf{42.95\%}} & \textcolor[HTML]{4285f4}{\textbf{11.54\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.76\%}} & \textcolor[HTML]{4285f4}{\textbf{18.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.33\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.71\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.72\%}} & \textcolor[HTML]{4285f4}{\textbf{23.49\%}} & \textcolor[HTML]{4285f4}{\textbf{21.5\%}} & \textcolor[HTML]{4285f4}{\textbf{13.38\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.27\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{2.83\%}} & \textcolor[HTML]{4285f4}{\textbf{0.32\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.48\%}} & \textcolor[HTML]{4285f4}{\textbf{7.31\%}} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.33\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.57\%}} & \textcolor[HTML]{4285f4}{\textbf{8.4\%}} & \textcolor[HTML]{4285f4}{\textbf{16.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{50.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.74\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{4.96\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}} & \textcolor[HTML]{4285f4}{\textbf{48.58\%}} & \textcolor[HTML]{4285f4}{\textbf{10.15\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.5\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.58\%}} & \textcolor[HTML]{4285f4}{\textbf{5.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.46\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{1.84\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.06\%}} & \textcolor[HTML]{4285f4}{\textbf{9.72\%}} & \textcolor[HTML]{4285f4}{\textbf{9.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.12\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{11.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.3\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.13\%}} & \textcolor[HTML]{4285f4}{\textbf{33.37\%}} & \textcolor[HTML]{4285f4}{\textbf{41.54\%}} & \textcolor[HTML]{4285f4}{\textbf{11.89\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.88\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{25.76\%}} & \textcolor[HTML]{4285f4}{\textbf{23.19\%}} & \textcolor[HTML]{4285f4}{\textbf{15.84\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.81\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.76\%}} & \textcolor[HTML]{4285f4}{\textbf{26.82\%}} & \textcolor[HTML]{4285f4}{\textbf{16.5\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.56\%}} & \textcolor[HTML]{4285f4}{\textbf{0.68\%}} & \textcolor[HTML]{4285f4}{\textbf{3.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.21\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}} & \textcolor[HTML]{4285f4}{\textbf{6.71\%}} & \textcolor[HTML]{4285f4}{\textbf{16.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{4.46\%}} & \textcolor[HTML]{4285f4}{\textbf{7.58\%}} & \textcolor[HTML]{4285f4}{\textbf{17.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.31\%}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.75\%}}}\\
+\addlinespace
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{13.03\%}} & \textcolor[HTML]{4285f4}{\textbf{34.39\%}} & \textcolor[HTML]{4285f4}{\textbf{6.62\%}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.72\%}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.03\%}} & \textcolor[HTML]{4285f4}{\textbf{3.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.42\%}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.28\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.09\%}}}\\
+\addlinespace
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{6.72\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
 \bottomrule
-\endlastfoot
- &  &  & whole period & 0.0737 & 0.1638 & 0.2849 & 0.1282\\
-\nopagebreak
- &  &  & backwardation & 0.0724 & 0.1790 & 0.2709 & 0.1001\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{all}} &  &  & contango & 0.0748 & 0.1501 & 0.2985 & 0.1495\\
-\nopagebreak
- &  &  & whole period & 0.0684 & 0.1545 & 0.2526 & 0.1096\\
-\nopagebreak
- &  &  & backwardation & 0.0642 & 0.1697 & 0.2323 & 0.0859\\
-\nopagebreak
- & \multirow[t]{-6}{*}{\raggedright\arraybackslash all} &  & contango & 0.0720 & 0.1402 & 0.2706 & 0.1268\\
-\nopagebreak
- &  &  & whole period & 0.0910 & 0.1305 & 0.2322 & 0.1075\\
-\nopagebreak
- &  &  & backwardation & 0.0799 & 0.1421 & 0.1975 & 0.0955\\
-\nopagebreak
- &  & \multirow[t]{-9}{*}{\raggedright\arraybackslash all} & contango & 0.1018 & 0.1184 & 0.2611 & 0.1186\\
-\nopagebreak
- &  &  & whole period & 0.4421 & 0.4898 & 0.5673 & 0.3728\\
-\nopagebreak
- &  &  & backwardation & 0.4312 & 0.5283 & 0.5749 & 0.3289\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash grains} & contango & 0.4570 & 0.4510 & 0.5675 & 0.4161\\
-\nopagebreak
- &  &  & whole period & 0.3340 & 0.2868 & 0.3707 & 0.3333\\
-\nopagebreak
- &  &  & backwardation & 0.3053 & 0.2652 & 0.3906 & 0.3220\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash livestock} & contango & 0.3605 & 0.3150 & 0.3557 & 0.3483\\
-\nopagebreak
- &  &  & whole period & 0.0391 & 0.0853 & 0.1584 & 0.0764\\
-\nopagebreak
- &  &  & backwardation & 0.0437 & 0.0845 & 0.1210 & 0.0685\\
-\nopagebreak
- & \multirow[t]{-12}{*}{\raggedright\arraybackslash agriculturals} & \multirow[t]{-3}{*}{\raggedright\arraybackslash softs} & contango & 0.0334 & 0.0874 & 0.1937 & 0.0833\\
-\nopagebreak
- &  &  & whole period & 0.4908 & 0.5892 & 0.4687 & 0.4203\\
-\nopagebreak
- &  &  & backwardation & 0.4844 & 0.5949 & 0.4601 & 0.4179\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & contango & 0.4957 & 0.5869 & 0.4779 & 0.4210\\
-\nopagebreak
- &  &  & whole period & 0.7278 & 0.7846 & 0.7692 & 0.7175\\
-\nopagebreak
- &  &  & backwardation & 0.6962 & 0.7854 & 0.7727 & 0.7282\\
-\nopagebreak
- & \multirow[t]{-6}{*}{\raggedright\arraybackslash energy} & \multirow[t]{-3}{*}{\raggedright\arraybackslash petroleum} & contango & 0.7606 & 0.7856 & 0.7716 & 0.7134\\
-\nopagebreak
- &  &  & whole period & 0.2167 & 0.5553 & 0.5877 & 0.4721\\
-\nopagebreak
- &  &  & backwardation & 0.2201 & 0.5418 & 0.6353 & 0.4155\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & contango & 0.2145 & 0.5727 & 0.5709 & 0.5035\\
-\nopagebreak
- &  &  & whole period & 0.2883 & 0.6305 & 0.6704 & 0.5762\\
-\nopagebreak
- &  &  & backwardation & 0.3070 & 0.6061 & 0.6991 & 0.5386\\
-\nopagebreak
-\multirow[t]{-27}{*}{\raggedright\arraybackslash \textbf{US}} & \multirow[t]{-6}{*}{\raggedright\arraybackslash metals} & \multirow[t]{-3}{*}{\raggedright\arraybackslash precious} & contango & 0.2713 & 0.6591 & 0.6615 & 0.5949\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & whole period & 0.4047 & 0.4691 & 0.6536 & 0.4412\\
-\nopagebreak
- &  &  & backwardation & 0.3987 & 0.4753 & 0.6729 & 0.3954\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{GB}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & \multirow[t]{-3}{*}{\raggedright\arraybackslash all} & contango & 0.4108 & 0.4652 & 0.6456 & 0.4797\\*
+
 \end{longtable}
+
 \endgroup{}
+\end{landscape}
 
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-acharya_limits_2013}{}}%
-Acharya, V.V., Lochstoer, L.A., Ramadorai, T., 2013.
-\href{https://doi.org/10.1016/j.jfineco.2013.03.003}{Limits to arbitrage and hedging: Evidence from commodity markets}.
-Journal of Financial Economics 109, 441--465.
-
-\leavevmode\vadjust pre{\hypertarget{ref-asness_devil_2013}{}}%
-Asness, C., Frazzini, A., 2013. \href{https://doi.org/10.3905/jpm.2013.39.4.049}{The devil in HML{'}s details}. The Journal of Portfolio Management 39, 49--68.
-
-\leavevmode\vadjust pre{\hypertarget{ref-asness_fact_2015}{}}%
-Asness, C., Frazzini, A., Israel, R., Moskowitz, T., 2015. \href{https://doi.org/10.3905/jpm.2015.42.1.034}{Fact, fiction, and value investing}. The Journal of Portfolio Management 42, 34--52.
-
-\leavevmode\vadjust pre{\hypertarget{ref-asness_quality_2019}{}}%
-Asness, C.S., Frazzini, A., Pedersen, L.H., 2019. \href{https://doi.org/10.1007/s11142-018-9470-2}{Quality minus junk}. Review of Accounting Studies 24, 34--112.
-
-\leavevmode\vadjust pre{\hypertarget{ref-baker_financialization_2021}{}}%
-Baker, S.D., 2021. \href{https://doi.org/10.1287/mnsc.2019.3445}{The financialization of storable commodities}. Management Science 67, 471--499.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bakshi_understanding_2019}{}}%
-Bakshi, G., Gao, X., Rossi, A.G., 2019.
-\href{https://doi.org/10.1287/mnsc.2017.2840}{Understanding the sources of risk underlying the cross section of commodity returns}.
-Management Science 65, 619--641.
-
-\leavevmode\vadjust pre{\hypertarget{ref-basak_model_2016}{}}%
-Basak, S., Pavlova, A., 2016. \href{https://doi.org/10.1111/jofi.12408}{A model of financialization of commodities}. The Journal of Finance 71, 1511--1556.
-
-\leavevmode\vadjust pre{\hypertarget{ref-basu_definancialisation}{}}%
-Basu, D., Bauthéac, O., 2024. Commodity definancialisation. Working paper.
-
-\leavevmode\vadjust pre{\hypertarget{ref-basu_capturing_2013}{}}%
-Basu, D., Miffre, J., 2013.
-\href{https://doi.org/10.1016/j.jbankfin.2013.02.031}{Capturing the risk premium of commodity futures: The role of hedging pressure}.
-Journal of Banking \& Finance 37, 2652--2664.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bohl_does_2013}{}}%
-Bohl, M.T., Stephan, P.M., 2013.
-\href{https://doi.org/10.1017/s1074070800005150}{Does futures speculation destabilize spot prices?
-New evidence for commodity markets}.
-Journal of Agricultural and Applied Economics 45, 595--616.
-
-\leavevmode\vadjust pre{\hypertarget{ref-boons_stock_2012}{}}%
-Boons, M., De Roon, F., Szymanowska, M., 2012. \href{https://doi.org/10.2139/ssrn.1785728}{The stock market price of commodity risk}, in: AFA 2012 Chicago Meetings Paper.
-
-\leavevmode\vadjust pre{\hypertarget{ref-boons_basis_2019}{}}%
-Boons, M., Prado, M.P., 2019. \href{https://doi.org/10.1111/jofi.12738}{Basis-momentum}. The Journal of Finance 74, 239--279.
-
-\leavevmode\vadjust pre{\hypertarget{ref-boyd_prevalence_2016}{}}%
-Boyd, N.E., Büyükşahin, B., Haigh, M.S., Harris, J.H., 2016. \href{https://doi.org/10.1002/fut.21756}{The prevalence, sources, and effects of herding}. Journal of Futures Markets 36, 671--694.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brennan_supply_1958}{}}%
-Brennan, M.J., 1958. \href{https://www.jstor.org/stable/1812340}{The supply of storage}. The American Economic Review 48, 50--72.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brunetti_speculators_2016}{}}%
-Brunetti, C., Büyükşahin, B., Harris, J.H., 2016.
-\href{https://doi.org/10.1017/s0022109016000569}{Speculators, prices, and market volatility}.
-Journal of Financial and Quantitative Analysis 51, 1545--1574.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brunetti_commodity_2014}{}}%
-Brunetti, C., Reiffen, D., 2014. \href{https://doi.org/10.1016/j.finmar.2014.08.001}{Commodity index trading and hedging costs}. Journal of Financial Markets 21, 153--180.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bruno_financialisation_2017}{}}%
-Bruno, V.G., Büyükşahin, B., Robe, M.A., 2017. \href{https://doi.org/10.1093/ajae/aaw059}{The financialization of food?} American Journal of Agricultural Economics 99, 243--264.
-
-\leavevmode\vadjust pre{\hypertarget{ref-buyuksahin_speculators_2011}{}}%
-Büyükşahin, B., Harris, J.H., 2011. \href{https://www.jstor.org/stable/41323326}{Do speculators drive crude oil futures prices?} The Energy Journal 167--202.
-
-\leavevmode\vadjust pre{\hypertarget{ref-buyuksahin_speculators_2014}{}}%
-Büyükşahin, B., Robe, M.A., 2014.
-\href{https://doi.org/10.1016/j.jimonfin.2013.08.004}{Speculators, commodities and cross-market linkages}.
-Journal of International Money and Finance, Understanding international commodity price fluctuations 42, 38--70.
-
-\leavevmode\vadjust pre{\hypertarget{ref-carhart_persistence_1997}{}}%
-Carhart, M.M., 1997. \href{https://doi.org/10.2307/2329556}{On persistence in mutual fund performance}. The Journal of finance 52, 57--82.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cheng_convective_2014}{}}%
-Cheng, I.-H., Kirilenko, A., Xiong, W., 2014. \href{https://doi.org/10.1093/rof/rfu043}{Convective risk flows in commodity futures markets}. Review of Finance 19, 1733--1781.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cheng_financialisation_2014}{}}%
-Cheng, I.-H., Xiong, W., 2014. \href{https://doi.org/10.1146/annurev-financial-110613-034432}{Financialization of commodity markets}. Annual Review of Financial Economics 6, 419--441.
-
-\leavevmode\vadjust pre{\hypertarget{ref-christoffersen_factor_2014}{}}%
-Christoffersen, P., Lunde, A., Olesen, K.V., 2014.
-\href{https://doi.org/10.1017/s0022109018000765}{Factor structure in commodity futures return and volatility}.
-Journal of Financial and Quantitative Analysis 1--74.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cootner_returns_1960}{}}%
-Cootner, P.H., 1960. \href{https://doi.org/10.1086/258347}{Returns to speculators: Telser versus keynes}. Journal of political Economy 68, 396--404.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cortazar_commodity_2013}{}}%
-Cortazar, G., Kovacevic, I., Schwartz, E.S., 2013.
-\href{https://ssrn.com/abstract=2287027}{Commodity and asset pricing models: An integration} (NBER Working Papers No.
-19167).
-National Bureau of Economic Research, Inc.
-
-\leavevmode\vadjust pre{\hypertarget{ref-danthine_information_1978}{}}%
-Danthine, J.-P., 1978. \href{https://doi.org/10.1016/0022-0531(78)90124-2}{Information, futures prices, and stabilizing speculation}. Journal of Economic Theory 17, 79--98.
-
-\leavevmode\vadjust pre{\hypertarget{ref-daskalaki_factors_2014}{}}%
-Daskalaki, C., Kostakis, A., Skiadopoulos, G., 2014.
-\href{https://doi.org/10.1016/j.jbankfin.2013.11.034}{Are there common factors in individual commodity futures returns?} Journal of Banking {\&} Finance 40, 346--363.
-
-\leavevmode\vadjust pre{\hypertarget{ref-deschutter_food_2010}{}}%
-De Schutter, O., 2010.
-\href{https://www2.ohchr.org/english/issues/food/docs/briefing_note_02_september_2010_en.pdf}{Food commodities speculation and food price crises: Regulation to reduce the risks of price volatility}.
-United Nations Special Rapporteur on the Right to Food Briefing Note 2, 1--14.
-
-\leavevmode\vadjust pre{\hypertarget{ref-domanski_financial_2007}{}}%
-Domanski, D., Heath, A., 2007. \href{https://www.bis.org/publ/qtrpdf/r_qt0703g.pdf}{Financial investors and commodity markets}. Working Paper.
-
-\leavevmode\vadjust pre{\hypertarget{ref-duffie_challenges_2014}{}}%
-Duffie, D., 2014. \href{https://doi.org/10.1086/677836}{Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs}. The Journal of Legal Studies 43, S173--s182.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ederington_who_2002}{}}%
-Ederington, L., Lee, J.H., 2002. \href{https://doi.org/10.1086/338706}{Who trades futures and how: Evidence from the heating oil futures market}. The Journal of Business 75, 353--373.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ekeland_speculation_2016}{}}%
-Ekeland, I., Lautier, D., Villeneuve, B., 2016. \href{https://hal.archives-ouvertes.fr/hal-01655848}{Speculation in commodity futures markets: A simple equilibrium model}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ekeland_hedging_2019}{}}%
-Ekeland, I., Lautier, D., Villeneuve, B., 2019. \href{https://doi.org/10.1007/s00199-018-1115-y}{Hedging pressure and speculation in commodity markets}. Economic Theory 68, 83--123.
-
-\leavevmode\vadjust pre{\hypertarget{ref-etula_broker-dealer_2013}{}}%
-Etula, E., 2013. \href{https://doi.org/10.1093/jjfinec/nbs024}{Broker-dealer risk appetite and commodity returns}. Journal of Financial Econometrics 11, 486--521.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fama_common_1993}{}}%
-Fama, E.F., French, K.R., 1993. \href{https://doi.org/10.1016/0304-405x(93)90023-5}{Common risk factors in the returns on stocks and bonds}. Journal of Financial Economics 33, 3--56.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fama_five_factor_2015}{}}%
-Fama, E.F., French, K.R., 2015. \href{https://doi.org/10.1016/j.jfineco.2014.10.010}{A five-factor asset pricing model}. Journal of Financial Economics 116, 1--22.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fattouh_role_2013}{}}%
-Fattouh, B., Kilian, L., Mahadeva, L., 2013. \href{https://www.jstor.org/stable/41970495}{The role of speculation in oil markets: What have we learnt so far?} The Energy Journal 34, 7--33.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fernandez_skewness_2018}{}}%
-Fernandez-Perez, A., Frijns, B., Fuertes, A.-M., Miffre, J., 2018.
-\href{https://doi.org/10.1016/j.jbankfin.2017.06.015}{The skewness of commodity futures returns}.
-Journal of Banking \& Finance 86, 143--158.
-
-\leavevmode\vadjust pre{\hypertarget{ref-frazzini_betting_2014}{}}%
-Frazzini, A., Pedersen, L.H., 2014. \href{https://doi.org/10.1016/j.jfineco.2013.10.005}{Betting against beta}. Journal of Financial Economics 111, 1--25.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fuertes_commodity_2015}{}}%
-Fuertes, A.-M., Miffre, J., Fernandez-Perez, A., 2015.
-\href{https://doi.org/10.1002/fut.21656}{Commodity strategies based on momentum, term structure, and idiosyncratic volatility}.
-Journal of Futures Markets 35, 274--297.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gilbert_how_2010}{}}%
-Gilbert, C.L., 2010a. \href{https://doi.org/10.1111/j.1477-9552.2010.00248.x}{How to understand high food prices}. Journal of Agricultural Economics 61, 398--425.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gilbert_speculative_2010}{}}%
-Gilbert, C.L., 2010b.
-\href{https://www.cftc.gov/sites/default/files/idc/groups/public/@swaps/documents/file/plstudy_14_cifrem.pdf}{Speculative influences on commodity futures prices 2006-2008}.
-UNCTAD, Geneva.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gilbert_role_2014}{}}%
-Gilbert, C.L., Pfuderer, S., 2014.
-\href{https://doi.org/10.1111/1477-9552.12068}{The role of index trading in price formation in the grains and oilseeds markets}.
-Journal of Agricultural Economics 65, 303--322.
-
-\leavevmode\vadjust pre{\hypertarget{ref-goldstein_speculation_2014}{}}%
-Goldstein, I., Li, Y., Yang, L., 2014. \href{https://doi.org/10.1093/rfs/hht059}{Speculation and hedging in segmented markets}. The Review of Financial Studies 27, 881--922.
-
-\leavevmode\vadjust pre{\hypertarget{ref-goldstein_commodity_2022}{}}%
-Goldstein, I., Yang, L., 2022. \href{https://doi.org/10.1111/jofi.13165}{Commodity financialization and information transmission}. The Journal of Finance 77, 2613--2667.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gorton_fundamentals_2012}{}}%
-Gorton, G.B., Hayashi, F., Rouwenhorst, K.G., 2012. \href{https://doi.org/10.1093/rof/rfs019}{The fundamentals of commodity futures returns}. Review of Finance 17, 35--105.
-
-\leavevmode\vadjust pre{\hypertarget{ref-grossman_impossibility_1980}{}}%
-Grossman, S.J., Stiglitz, J.E., 1980. \href{https://doi.org/10.7916/d8765r99}{On the impossibility of informationally efficient markets}. The American economic review 70, 393--408.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hamilton_effects_2015}{}}%
-Hamilton, J.D., Wu, J.C., 2015. \href{https://doi.org/10.1111/iere.12099}{Effects of index-fund investing on commodity futures prices}. International Economic Review 56, 187--205.
-
-\leavevmode\vadjust pre{\hypertarget{ref-henderson_new_2015}{}}%
-Henderson, B.J., Pearson, N.D., Wang, L., 2015. \href{https://doi.org/10.1093/rfs/hhu091}{New evidence on the financialization of commodity markets}. The Review of Financial Studies 28, 1285--1311.
-
-\leavevmode\vadjust pre{\hypertarget{ref-herman_not_2011}{}}%
-Herman, M.-O., Kelly, R., Nash, R., 2011.
-\href{https://www.ingentaconnect.com/content/oxpp/oppafl/2011/00000011/00000007/art00005}{Not a game, speculation v.
-Food security: Regulating financial markets to grow a better future}.
-Oxfam policy and practice: agriculture, food and land 11, 127--138.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hicks_value_1939}{}}%
-Hicks, J.R., 1939. Value and capital, 1st ed. Oxford University Press, Cambridge.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hicks_value_1946}{}}%
-Hicks, J.R., 1946. Value and capital, 2nd ed. Oxford University Press, Cambridge.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hirshleifer_speculation_1975}{}}%
-Hirshleifer, J., 1975. \href{https://doi.org/10.2307/1884690}{Speculation and equilibrium: Information, risk, and markets}. The Quarterly Journal of Economics 89, 519--542.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hirshleifer_reply_1976}{}}%
-Hirshleifer, J., 1976. \href{https://doi.org/10.2307/1885330}{Reply to comments on" speculation and equilibrium: Information, risk, and markets"}. The Quarterly Journal of Economics 689--696.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hirshleifer_theory_1977}{}}%
-Hirshleifer, J., 1977. \href{https://doi.org/10.2307/2326507}{The theory of speculation under alternative regimes of markets}. The Journal of Finance 32, 975--999.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hong_what_2012}{}}%
-Hong, H., Yogo, M., 2012.
-\href{https://doi.org/10.1016/j.jfineco.2012.04.005}{What does futures market interest tell us about the macroeconomy and asset prices?} Journal of Financial Economics 105, 473--490.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hou_digesting_2015}{}}%
-Hou, K., Xue, C., Zhang, L., 2015. \href{https://doi.org/10.1093/rfs/hhu068}{Digesting anomalies: An investment approach}. The Review of Financial Studies 28, 650--705.
-
-\leavevmode\vadjust pre{\hypertarget{ref-houthakker_restatement_1957}{}}%
-Houthakker, H., 1957.
-\href{https://EconPapers.repec.org/RePEc:cwl:cwldpp:44}{Restatement of the theory of normal backwardation} (Cowles Foundation Discussion Papers No.
-44).
-Cowles Foundation for Research in Economics, Yale University.
-
-\leavevmode\vadjust pre{\hypertarget{ref-houthakker_speculators_1957}{}}%
-Houthakker, H.S., 1957. \href{https://doi.org/10.2307/1928531}{Can speculators forecast prices?} The Review of Economics and Statistics 39, 143--151.
-
-\leavevmode\vadjust pre{\hypertarget{ref-irwin_commodity_2013}{}}%
-Irwin, S.H., 2013. \href{https://doi.org/10.1111/agec.12048}{Commodity index investment and food prices: Does the "masters hypothesis" explain recent price spikes?} Agricultural Economics 44, 29--41.
-
-\leavevmode\vadjust pre{\hypertarget{ref-irwin_index_2011}{}}%
-Irwin, S.H., Sanders, D.R., 2011. \href{https://doi.org/10.1093/aepp/ppq032}{Index funds, financialization, and commodity futures markets}. Applied Economic Perspectives and Policy 33, 1--31.
-
-\leavevmode\vadjust pre{\hypertarget{ref-irwin_financialisation_2012}{}}%
-Irwin, S.H., Sanders, D.R., 2012.
-\href{https://doi.org/10.1017/s1074070800000481}{Financialization and structural change in commodity futures markets}.
-Journal of Agricultural and Applied Economics 44, 371--396.
-
-\leavevmode\vadjust pre{\hypertarget{ref-irwin_devil_2009}{}}%
-Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009.
-\href{https://doi.org/10.1017/s1074070800002856}{Devil or angel?
-The role of speculation in the recent commodity price boom (and bust)}.
-Journal of Agricultural and Applied Economics 41, 377--391.
-
-\leavevmode\vadjust pre{\hypertarget{ref-isleimeyyeh_role_2020}{}}%
-Isleimeyyeh, M., 2020. \href{https://doi.org/10.1002/fut.22122}{The role of financial investors in determining the commodity futures risk premium}. Journal of Futures Markets 40, 1375--1397.
-
-\leavevmode\vadjust pre{\hypertarget{ref-juvenal_speculation_2015}{}}%
-Juvenal, L., Petrella, I., 2015. \href{https://doi.org/10.1002/jae.2388}{Speculation in the oil market}. Journal of Applied Econometrics 30, 621--649.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kaldor_speculation_1939}{}}%
-Kaldor, N., 1939. \href{https://doi.org/10.2307/2967593}{Speculation and economic stability}. The Review of Economic Studies 7, 1--27.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kang_tale_2020}{}}%
-Kang, W., Rouwenhorst, K.G., Tang, K., 2020.
-\href{https://doi.org/10.1111/jofi.12845}{A tale of two premiums: The role of hedgers and speculators in commodity futures markets}.
-The Journal of Finance 75, 377--417.
-
-\leavevmode\vadjust pre{\hypertarget{ref-keynes_some_1923}{}}%
-Keynes, J.M., 1923. Some aspects of commodity markets. Manchester Guardian Commercial: European Reconstruction Series 13, 784--786.
-
-\leavevmode\vadjust pre{\hypertarget{ref-keynes_treatise_1930}{}}%
-Keynes, J.M., 1930. Treatise on money. Macmillan, London.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kilian_role_2014}{}}%
-Kilian, L., Murphy, D.P., 2014.
-\href{https://doi.org/10.1002/jae.2322}{The role of inventories and speculative trading in the global market for crude oil}.
-Journal of Applied Econometrics 29, 454--478.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kim_does_2015}{}}%
-Kim, A., 2015. \href{https://doi.org/10.1002/fut.21716}{Does futures speculation destabilize commodity markets?} Journal of Futures Markets 35, 696--714.
-
-\leavevmode\vadjust pre{\hypertarget{ref-knittel_simple_2016}{}}%
-Knittel, C.R., Pindyck, R.S., 2016. \href{https://doi.org/10.1257/mac.20140033}{The simple economics of commodity price speculation}. American Economic Journal: Macroeconomics 8, 85--110.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kyle_informed_1989}{}}%
-Kyle, A.S., 1989. \href{https://doi.org/10.2307/2297551}{Informed speculation with imperfect competition}. The Review of Economic Studies 56, 317--355.
-
-\leavevmode\vadjust pre{\hypertarget{ref-leclercq_equilibrium_2014}{}}%
-Leclercq, E., Praz, R., 2014. \href{https://doi.org/10.2139/ssrn.2464400}{Equilibrium commodity trading} (SSRN Scholarly Paper No. Id 2464400). Social Science Research Network, Rochester, NY.
-
-\leavevmode\vadjust pre{\hypertarget{ref-manera_modeling_2016}{}}%
-Manera, M., Nicolini, M., Vignati, I., 2016.
-\href{https://doi.org/10.1016/j.eneco.2014.07.001}{Modeling futures price volatility in energy markets: Is there a role for financial speculation?} Energy Economics, Energy markets 53, 220--229.
-
-\leavevmode\vadjust pre{\hypertarget{ref-masters_testimony_2008}{}}%
-Masters, M.W., 2008. Testimony before the committee on homeland security and governmental affairs. U.S. Senate 20.
-
-\leavevmode\vadjust pre{\hypertarget{ref-masters_accidental_2008}{}}%
-Masters, M.W., White, A.K., 2008. The accidental hunt brothers: How institutional investors are driving up food and energy prices. Working paper.
-
-\leavevmode\vadjust pre{\hypertarget{ref-miffre_momentum_2007}{}}%
-Miffre, J., Rallis, G., 2007. \href{https://doi.org/10.1016/j.jbankfin.2006.12.005}{Momentum strategies in commodity futures markets}. Journal of Banking \& Finance 31, 1863--1886.
-
-\leavevmode\vadjust pre{\hypertarget{ref-moskowitz_time_2012}{}}%
-Moskowitz, T.J., Ooi, Y.H., Pedersen, L.H., 2012.
-\href{https://doi.org/10.1016/j.jfineco.2011.11.003}{Time series momentum}.
-Journal of Financial Economics, Special issue on investor sentiment 104, 228--250.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sakkas_factor_2020}{}}%
-Sakkas, A., Tessaromatis, N., 2020. \href{https://doi.org/10.1016/j.jbankfin.2020.105807}{Factor based commodity investing}. Journal of Banking \& Finance 115, 105807.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sanders_impact_2011}{}}%
-Sanders, D.R., Irwin, S.H., 2011a.
-\href{https://doi.org/10.3905/jai.2011.14.1.040}{The impact of index funds in commodity futures markets: A systems approach}.
-The Journal of Alternative Investments 14, 40--49.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sanders_new_2011}{}}%
-Sanders, D.R., Irwin, S.H., 2011b.
-\href{https://doi.org/10.1111/j.1744-7976.2011.01226.x}{New evidence on the impact of index funds in u.s.
-Grain futures markets}.
-Canadian Journal of Agricultural Economics/Revue canadienne d'agroeconomie 59, 519--532.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sanders_adequacy_2010}{}}%
-Sanders, D.R., Irwin, S.H., Merrin, R.P., 2010.
-\href{https://doi.org/10.1093/aepp/ppp006}{The adequacy of speculation in agricultural futures markets: Too much of a good thing?} Applied Economic Perspectives and Policy 32, 77--94.
-
-\leavevmode\vadjust pre{\hypertarget{ref-schumann_hunger_2011}{}}%
-Schumann, H., 2011.
-\href{https://www.foodwatch.org/uploads/media/foodwatchreport_TheHungerMakers_observationsandcallsforaction_ger_03.pdf}{The hunger-makers: How deutsche bank, goldman sachs and other financial institutions are speculating with food at the expense of the poorest}.
-Foodwatch, Berlin.
-
-\leavevmode\vadjust pre{\hypertarget{ref-schwartz_stochastic_1997}{}}%
-Schwartz, E.S., 1997.
-\href{https://doi.org/10.1111/j.1540-6261.1997.tb02721.x}{The stochastic behavior of commodity prices: Implications for valuation and hedging}.
-The Journal of Finance 52, 923--973.
-
-\leavevmode\vadjust pre{\hypertarget{ref-schwartz_short_2000}{}}%
-Schwartz, E., Smith, J.E., 2000. \href{https://www.jstor.org/stable/2661607}{Short-term variations and long-term dynamics in commodity prices}. Management Science 46, 893--911.
-
-\leavevmode\vadjust pre{\hypertarget{ref-senate_excessive_2009}{}}%
-Senate, U.S., 2009.
-\href{https://www.hsgac.senate.gov/imo/media/doc/REPORTExcessiveSpecullationintheWheatMarketwoexhibitschartsJune2409.pdf?attempt=2}{Excessive speculation in the wheat market}.
-Majority and Minority Staff Report.
-Permanent Subcommittee on Investigations 24, 107--108.
-
-\leavevmode\vadjust pre{\hypertarget{ref-simsek_speculation_2013}{}}%
-Simsek, A., 2013. \href{https://doi.org/10.1093/qje/qjt007}{Speculation and risk sharing with new financial assets}. The Quarterly Journal of Economics 128, 1365--1396.
-
-\leavevmode\vadjust pre{\hypertarget{ref-singleton_investor_2013}{}}%
-Singleton, K.J., 2013. \href{https://doi.org/10.1287/mnsc.2013.1756}{Investor flows and the 2008 boom/bust in oil prices}. Management Science 60, 300--318.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sockin_informational_2015}{}}%
-Sockin, M., Xiong, W., 2015. \href{https://doi.org/10.1111/jofi.12261}{Informational frictions and commodity markets}. The Journal of Finance 70, 2063--2098.
-
-\leavevmode\vadjust pre{\hypertarget{ref-stoll_commodity_2011}{}}%
-Stoll, H.R., Whaley, R.E., 2011. \href{https://doi.org/10.2139/ssrn.1633908}{Commodity index investing: Speculation or diversification?} The Journal of Alternative Investments 14, 50--60.
-
-\leavevmode\vadjust pre{\hypertarget{ref-stout_why_1998}{}}%
-Stout, L.A., 1998. \href{https://doi.org/10.2307/1373070}{Why the law hates speculators: Regulation and private ordering in the market for OTC derivatives}. Duke Law Journal 48, 701--786.
-
-\leavevmode\vadjust pre{\hypertarget{ref-stulz_rethink_1996}{}}%
-Stulz, R.M., 1996. \href{https://doi.org/10.1111/j.1745-6622.1996.tb00295.x}{Rethinking risk management}. Journal of Applied Corporate Finance 9, 8--25.
-
-\leavevmode\vadjust pre{\hypertarget{ref-szymanowska_anatomy_2014}{}}%
-Szymanowska, M., De Roon, F., Nijman, T., Van Den Goorbergh, R., 2014. \href{https://doi.org/10.1111/jofi.12096}{An anatomy of commodity futures risk premia}. The Journal of Finance 69, 453--482.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tang_index_2012}{}}%
-Tang, K., Xiong, W., 2012. \href{https://doi.org/10.2469/faj.v68.n6.5}{Index investment and the financialization of commodities}. Financial Analysts Journal 68, 54--74.
-
-\leavevmode\vadjust pre{\hypertarget{ref-telser_futures_1958}{}}%
-Telser, L.G., 1958. \href{https://doi.org/10.1086/258036}{Futures trading and the storage of cotton and wheat}. Journal of Political Economy 66, 233--255.
-
-\leavevmode\vadjust pre{\hypertarget{ref-till_long_2007}{}}%
-Till, H., 2007. A long-term perspective on commodity futures returns, in: Intelligent Commodity Investing. Risk books, London.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tokic_speculation_2012}{}}%
-Tokic, D., 2012. \href{https://doi.org/10.1016/j.enpol.2012.02.069}{Speculation and the 2008 oil bubble: The DCOT report analysis}. Energy Policy 45, 541--550.
-
-\leavevmode\vadjust pre{\hypertarget{ref-turnovsky_determination_1983}{}}%
-Turnovsky, S.J., 1983. \href{https://doi.org/10.2307/1912279}{The determination of spot and futures prices with storable commodities}. Econometrica 51, 1363--1387.
-
-\leavevmode\vadjust pre{\hypertarget{ref-unctad_global_2009}{}}%
-UNCTAD, S.T.F.
-on S.I., Cooperation, E., 2009.
-\href{https://unctad.org/system/files/official-document/gds20091_en.pdf}{The global economic crisis: Systemic failures and multilateral remedies}.
-UNCTAD, Geneva.
-
-\leavevmode\vadjust pre{\hypertarget{ref-weymar_supply_1966}{}}%
-Weymar, F.H., 1966. \href{http://www.jstor.org/stable/1815306}{The supply of storage revisited}. The American Economic Review 56, 1226--1234.
-
-\leavevmode\vadjust pre{\hypertarget{ref-working_price_1933}{}}%
-Working, H., 1933. \href{https://doi.org/10.22004/ag.econ.142876}{Price relations between july and september wheat futures at chicago since 1885}. Wheat Studies 9, 187.
-
-\leavevmode\vadjust pre{\hypertarget{ref-working_theory_1948}{}}%
-Working, H., 1948. \href{https://doi.org/10.2307/1232678}{Theory of the inverse carrying charge in futures markets}. Journal of Farm Economics 30, 1--28.
-
-\leavevmode\vadjust pre{\hypertarget{ref-working_theory_1949}{}}%
-Working, H., 1949. \href{https://www.jstor.org/stable/1816601}{The theory of price of storage}. The American Economic Review 1254--1262.
-
-\leavevmode\vadjust pre{\hypertarget{ref-working_hedging_1953}{}}%
-Working, H., 1953. \href{https://doi.org/10.2307/1233368}{Hedging reconsidered}. Journal of Farm Economics 35, 544--561.
-
-\leavevmode\vadjust pre{\hypertarget{ref-yang_investment_2013}{}}%
-Yang, F., 2013. \href{https://doi.org/10.1016/j.jfineco.2013.04.012}{Investment shocks and the commodity basis spread}. Journal of Financial Economics 110, 164--184.
-
-\end{CSLReferences}
+\renewcommand\refname{References}
+  \bibliography{bibliography.bib}
 

### 2024-09-13 explore/scripts/descriptive-statistics.r
Refactor compute

@@ -1,3670 +1,0 @@
-library(magrittr)
-library(doParallel)
-library(storethat)
-library(pullit)
-library(factorem)
-
-# start cluster ####
-cluster <- makeCluster(detectCores(), outfile = ""); registerDoParallel(cluster)
-
-# globals ####
-data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
-data("exchanges", package = "fewISOs")
-
-storethat <- paste0(here::here(), "/data/storethat.sqlite")
-
-
-periods <- tibble::tibble(
-  period = c(
-    rep("past", 2L), 
-    rep("financialization", 2L), 
-    rep("crisis", 2L), 
-    rep("present", 2L)
-  ),
-  bound = rep(c("start", "end"), 4L),
-  date = c(
-    "1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", "2008-09-15", 
-    "2013-06-19", "2013-06-20", "2018-12-31"
-  )
-)
-
-
-# load data ####
-start <- "1996-01-01"; end <- "2018-12-31"
-# could add COA Comdty (Crude oil-brent - IFEU) ENA Comdty (Crude oil-WTI - IFEU), 
-# PGA Comdty (Gasoline-RBOB - IFEU), NVA Comdty (Heating oil - IFEU), 
-# FNA Comdty (Natural gas - IFEU), QSA Comdty (Gasoil-low sulfur - IFEU)
-`commodity futures tickers` <- c(
-  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
-  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
-  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
-  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
-  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
-  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty",
-  "LAA Comdty", "LPA Comdty", "LLA Comdty", "LNA Comdty", "LTA Comdty",
-  "LXA Comdty"
-)
-
-`commodity futures data` <- pullit::pull_futures_market(
-  source = "storethat", type = "term structure", 
[…]

### 2024-09-13 explore/scripts/factor-from-picks.r

@@ -1,171 +1,0 @@
-library(finRes)
-library(magrittr)
-library(doParallel)
-# source("explore/scripts/functions - shared.r")
-
-# start cluster ####
-cluster <- makeCluster(detectCores() - 1L);
-registerDoParallel(cluster, cores = detectCores() - 1L)
-
-# globals ####
-data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
-data("exchanges", package = "fewISOs")
-
-storethat <- paste0(here::here(), "/data/storethat.sqlite")
-
-periods <- tibble::tibble(
-  period = c(
-    rep("past", 2L), rep("financialization", 2L), 
-    rep("crisis", 2L), rep("present", 2L)
-  ),
-  bound = rep(c("start", "end"), 4L),
-  date = c("1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", 
-           "2008-09-15", "2013-06-19", "2013-06-20", "2018-12-31")
-)
-
-# load data ####
-start <- "1996-01-01"; end <- "2018-12-31"
-# could add COA Comdty (Crude oil-brent - IFEU) ENA Comdty (Crude oil-WTI - IFEU), PGA Comdty (Gasoline-RBOB - IFEU), NVA Comdty (Heating oil - IFEU), 
-# FNA Comdty (Natural gas - IFEU), QSA Comdty (Gasoil-low sulfur - IFEU)
-`commodity futures tickers` <- c(
-  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
-  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
-  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
-  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
-  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
-  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty"
-)
-
-`commodity futures data` <- pullit::pull_futures_market(
-  source = "storethat", type = "term structure", 
-  active_contract_tickers = `commodity futures tickers`,
-  start = start, end = end, 
-  TS_positions = 1L:2L, roll_type = "A", roll_days = 0L, roll_months = 0L,
[…]

### 2024-09-13 explore/scripts/factor-picks.r

@@ -1,526 +1,0 @@
-library(finRes)
-library(magrittr)
-library(doParallel)
-# source("explore/scripts/functions - shared.r")
-
-# start cluster ####
-cluster <- makeCluster(detectCores() - 1L);
-registerDoParallel(cluster, cores = detectCores() - 1L)
-
-# globals ####
-data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
-data("exchanges", package = "fewISOs")
-
-storethat <- paste0(here::here(), "/data/storethat.sqlite")
-
-periods <- tibble::tibble(
-  period = c(
-    rep("past", 2L), rep("financialization", 2L), 
-    rep("crisis", 2L), rep("present", 2L)
-  ),
-  bound = rep(c("start", "end"), 4L),
-  date = c("1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", 
-           "2008-09-15", "2013-06-19", "2013-06-20", "2018-12-31")
-)
-
-# load data ####
-start <- "1996-01-01"; end <- "2018-12-31"
-# could add COA Comdty (Crude oil-brent - IFEU) ENA Comdty (Crude oil-WTI - IFEU), PGA Comdty (Gasoline-RBOB - IFEU), NVA Comdty (Heating oil - IFEU), 
-# FNA Comdty (Natural gas - IFEU), QSA Comdty (Gasoil-low sulfur - IFEU)
-`commodity futures tickers` <- c(
-  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
-  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
-  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
-  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
-  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
-  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty"
-)
-
-`commodity futures data` <- pullit::pull_futures_market(
-  source = "storethat", type = "term structure", 
-  active_contract_tickers = `commodity futures tickers`,
-  start = start, end = end, 
-  TS_positions = 1L:2L, roll_type = "A", roll_days = 0L, roll_months = 0L,
[…]

### 2024-09-13 explore/scripts/original/descriptive-statistics.r

@@ -1,0 +1,3670 @@
+library(magrittr)
+library(doParallel)
+library(storethat)
+library(pullit)
+library(factorem)
+
+# start cluster ####
+cluster <- makeCluster(detectCores(), outfile = ""); registerDoParallel(cluster)
+
+# globals ####
+data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
+data("exchanges", package = "fewISOs")
+
+storethat <- paste0(here::here(), "/data/storethat.sqlite")
+
+
+periods <- tibble::tibble(
+  period = c(
+    rep("past", 2L), 
+    rep("financialization", 2L), 
+    rep("crisis", 2L), 
+    rep("present", 2L)
+  ),
+  bound = rep(c("start", "end"), 4L),
+  date = c(
+    "1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", "2008-09-15", 
+    "2013-06-19", "2013-06-20", "2018-12-31"
+  )
+)
+
+
+# load data ####
+start <- "1996-01-01"; end <- "2018-12-31"
+# could add COA Comdty (Crude oil-brent - IFEU) ENA Comdty (Crude oil-WTI - IFEU), 
+# PGA Comdty (Gasoline-RBOB - IFEU), NVA Comdty (Heating oil - IFEU), 
+# FNA Comdty (Natural gas - IFEU), QSA Comdty (Gasoil-low sulfur - IFEU)
+`commodity futures tickers` <- c(
+  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
+  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
+  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
+  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
+  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
+  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty",
+  "LAA Comdty", "LPA Comdty", "LLA Comdty", "LNA Comdty", "LTA Comdty",
+  "LXA Comdty"
+)
+
+`commodity futures data` <- pullit::pull_futures_market(
+  source = "storethat", type = "term structure", 
[…]

### 2024-09-13 explore/scripts/original/factor-from-picks.r

@@ -1,0 +1,171 @@
+library(finRes)
+library(magrittr)
+library(doParallel)
+# source("explore/scripts/functions - shared.r")
+
+# start cluster ####
+cluster <- makeCluster(detectCores() - 1L);
+registerDoParallel(cluster, cores = detectCores() - 1L)
+
+# globals ####
+data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
+data("exchanges", package = "fewISOs")
+
+storethat <- paste0(here::here(), "/data/storethat.sqlite")
+
+periods <- tibble::tibble(
+  period = c(
+    rep("past", 2L), rep("financialization", 2L), 
+    rep("crisis", 2L), rep("present", 2L)
+  ),
+  bound = rep(c("start", "end"), 4L),
+  date = c("1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", 
+           "2008-09-15", "2013-06-19", "2013-06-20", "2018-12-31")
+)
+
+# load data ####
+start <- "1996-01-01"; end <- "2018-12-31"
+# could add COA Comdty (Crude oil-brent - IFEU) ENA Comdty (Crude oil-WTI - IFEU), PGA Comdty (Gasoline-RBOB - IFEU), NVA Comdty (Heating oil - IFEU), 
+# FNA Comdty (Natural gas - IFEU), QSA Comdty (Gasoil-low sulfur - IFEU)
+`commodity futures tickers` <- c(
+  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
+  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
+  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
+  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
+  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
+  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty"
+)
+
+`commodity futures data` <- pullit::pull_futures_market(
+  source = "storethat", type = "term structure", 
+  active_contract_tickers = `commodity futures tickers`,
+  start = start, end = end, 
+  TS_positions = 1L:2L, roll_type = "A", roll_days = 0L, roll_months = 0L,
[…]

### 2024-09-13 explore/scripts/original/factor-picks.r

@@ -1,0 +1,526 @@
+library(finRes)
+library(magrittr)
+library(doParallel)
+# source("explore/scripts/functions - shared.r")
+
+# start cluster ####
+cluster <- makeCluster(detectCores() - 1L);
+registerDoParallel(cluster, cores = detectCores() - 1L)
+
+# globals ####
+data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
+data("exchanges", package = "fewISOs")
+
+storethat <- paste0(here::here(), "/data/storethat.sqlite")
+
+periods <- tibble::tibble(
+  period = c(
+    rep("past", 2L), rep("financialization", 2L), 
+    rep("crisis", 2L), rep("present", 2L)
+  ),
+  bound = rep(c("start", "end"), 4L),
+  date = c("1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", 
+           "2008-09-15", "2013-06-19", "2013-06-20", "2018-12-31")
+)
+
+# load data ####
+start <- "1996-01-01"; end <- "2018-12-31"
+# could add COA Comdty (Crude oil-brent - IFEU) ENA Comdty (Crude oil-WTI - IFEU), PGA Comdty (Gasoline-RBOB - IFEU), NVA Comdty (Heating oil - IFEU), 
+# FNA Comdty (Natural gas - IFEU), QSA Comdty (Gasoil-low sulfur - IFEU)
+`commodity futures tickers` <- c(
+  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
+  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
+  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
+  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
+  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
+  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty"
+)
+
+`commodity futures data` <- pullit::pull_futures_market(
+  source = "storethat", type = "term structure", 
+  active_contract_tickers = `commodity futures tickers`,
+  start = start, end = end, 
+  TS_positions = 1L:2L, roll_type = "A", roll_days = 0L, roll_months = 0L,
[…]

### 2024-09-13 explore/scripts/original/regressions-cross-section.r

@@ -1,0 +1,1747 @@
+library(finRes); library(magrittr); library(doParallel); library(lubridate)
+
+
+# start cluster ####
+cluster <- makeCluster(detectCores() - 1L, outfile = "")
+registerDoParallel(cluster, cores = detectCores() - 1L)
+
+
+# globals ####
+data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
+data("exchanges", package = "fewISOs")
+rf <- readr::read_rds(here::here("data", "risk-free-rate.rds"))
+
+storethat <- here::here("data", "storethat.sqlite")
+
+
+periods <- tibble::tibble(
+  period = c(
+    rep("past", 2L), rep("financialization", 2L), 
+    rep("crisis", 2L), rep("present", 2L)
+  ), 
+  bound = rep(c("start", "end"), 4L),
+  date = c(
+    "1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", "2008-09-15", 
+    "2013-06-19", "2013-06-20", "2018-12-31"
+  )
+)
+# load data ####
+start <- "1996-01-01"; end <- "2018-12-31"
+# could add COA Comdty (Crude oil-brent - IFEU) ENA Comdty (Crude oil-WTI - IFEU), 
+# PGA Comdty (Gasoline-RBOB - IFEU), NVA Comdty (Heating oil - IFEU), 
+# FNA Comdty (Natural gas - IFEU), QSA Comdty (Gasoil-low sulfur - IFEU)
+`commodity futures tickers` <- c(
+  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
+  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
+  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
+  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
+  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
+  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty"
+)
+
+`US commodity futures tickers` <- dplyr::left_join(
+  dplyr::select(tickers_futures, ticker, MIC), 
+  dplyr::select(exchanges, MIC, country), 
+  by = "MIC"
+) %>% 
[…]

### 2024-09-13 explore/scripts/regressions-cross-section.r

@@ -1,1747 +1,0 @@
-library(finRes); library(magrittr); library(doParallel); library(lubridate)
-
-
-# start cluster ####
-cluster <- makeCluster(detectCores() - 1L, outfile = "")
-registerDoParallel(cluster, cores = detectCores() - 1L)
-
-
-# globals ####
-data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
-data("exchanges", package = "fewISOs")
-rf <- readr::read_rds(here::here("data", "risk-free-rate.rds"))
-
-storethat <- here::here("data", "storethat.sqlite")
-
-
-periods <- tibble::tibble(
-  period = c(
-    rep("past", 2L), rep("financialization", 2L), 
-    rep("crisis", 2L), rep("present", 2L)
-  ), 
-  bound = rep(c("start", "end"), 4L),
-  date = c(
-    "1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", "2008-09-15", 
-    "2013-06-19", "2013-06-20", "2018-12-31"
-  )
-)
-# load data ####
-start <- "1996-01-01"; end <- "2018-12-31"
-# could add COA Comdty (Crude oil-brent - IFEU) ENA Comdty (Crude oil-WTI - IFEU), 
-# PGA Comdty (Gasoline-RBOB - IFEU), NVA Comdty (Heating oil - IFEU), 
-# FNA Comdty (Natural gas - IFEU), QSA Comdty (Gasoil-low sulfur - IFEU)
-`commodity futures tickers` <- c(
-  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
-  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
-  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
-  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
-  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
-  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty"
-)
-
-`US commodity futures tickers` <- dplyr::left_join(
-  dplyr::select(tickers_futures, ticker, MIC), 
-  dplyr::select(exchanges, MIC, country), 
-  by = "MIC"
-) %>% 
[…]

### 2024-09-13 explore/scripts/revision-jfm-analysis.r

@@ -1,243 +1,0 @@
-library(finRes); library(magrittr)
-
-# source functions ####
-source(here::here("explore", "scripts", "revision-jfm-functions.r"))
-
-# globals ####
-## datasets ####
-data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
-data("exchanges", package = "fewISOs")
-
-## variables ####
-storethat_db_path <- make_path_to_storethat_database()
-results_directory_path <- here::here("explore", "results", "revision-jfm")
-
-period_bounds <- list(
-  past = list(start = "1997-07-01", end = "2003-12-31"),
-  financialization = list(start = "2004-01-01", end = "2008-09-14"),
-  crisis = list(start = "2008-09-15", end = "2013-06-19"),
-  present = list(start = "2013-06-20", end = "2018-12-31")
-)
-periods <- make_periods_data_frame(period_bounds)
-
-rf <- readr::read_rds(here::here("data", "risk-free-rate.rds"))
-
-# load data ####
-## time boundaries ####
-start <- "1996-01-01"; end <- "2018-12-14"
-
-## individual commodity futures tickers ####
-commodity_futures_tickers <- c(
-  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
-  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
-  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
-  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
-  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
-  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty",
-  "LAA Comdty", "LPA Comdty", "LLA Comdty", "LNA Comdty", "LTA Comdty",
-  "LXA Comdty"
-)
-
-## commodity futures levels data ####
-### individual data ####
-commodity_futures_individual_data_levels <- get_commodity_futures_individual_data_levels(
-  commodity_futures_tickers, start, end, storethat_db_path
-    )
-
-### aggregate data ####
-commodity_futures_aggregate_data_levels <- get_commodity_futures_aggregate_data_levels(
-  commodity_futures_tickers, start, end, storethat_db_path
-)
-
[…]

### 2024-09-13 explore/scripts/revision-jfm-functions.r

@@ -1,1147 +1,0 @@
-# utils ####
-paste_forward_slash <- function(...) paste(..., sep = "/")
-
-# globals ####
-## variables ####
-### local function ####
-make_path_to_storethat_database <- function(){
-  paste0(here::here(), "/data/storethat.sqlite")
-}
-
-make_periods_data_frame <- function(period_bounds){
-  purrr::imap_dfr(period_bounds, function(bounds, name){
-    purrr::imap_dfr(bounds, function(date, bound){
-      tibble::tibble(bound = bound, date = date)
-    }) %>% dplyr::mutate(period = name) %>% dplyr::select(period, dplyr::everything())
-  })
-}
-
-## functions ####
-get_commodity_futures_individual_data_levels <- function(
-    commodity_futures_tickers, start, end, storethat_db_path
-    ){
-  
-  raw_data_object <- pullit::pull_futures_market(
-    source = "storethat", type = "term structure", 
-    active_contract_tickers = commodity_futures_tickers, start = start, end = end, 
-    TS_positions = 1L:2L, roll_type = "A", roll_days = 0L, roll_months = 0L,
-    roll_adjustment = "N", file = storethat_db_path
-  )
-  
-  raw_data <- pullit::get_data(raw_data_object)
-  term_structure_tickers <- dplyr::select(
-    pullit::get_term_structure_tickers(raw_data_object), `active contract ticker`, ticker, `TS position`
-  )
-  
-    dplyr::left_join(raw_data, term_structure_tickers, by = "ticker") %>% 
-    dplyr::select( `active contract ticker`, ticker, `TS position`, field, date, value)
-}
-
-get_commodity_futures_aggregate_data_levels <- function(
-    commodity_futures_tickers, start, end, storethat_db_path
-    ){
-  
-  pullit::pull_futures_market(
-    source = "storethat", type = "aggregate", 
-    active_contract_tickers = commodity_futures_tickers, 
-    start = start, end = end, file = storethat_db_path
-  )
-}
-
-get_period_boundaries <- function(periods, period_id){
-  start <- dplyr::filter(periods, period == period_id, bound == "start") %>% 
-    dplyr::select(date) %>% purrr::flatten_chr()
-  end <- dplyr::filter(periods, period == period_id, bound == "end") %>% 
-    dplyr::select(date) %>% purrr::flatten_chr()
-  
[…]

### 2024-09-13 explore/scripts/revision-jfm-tables.r

@@ -1,290 +1,0 @@
-library(magrittr)
-
-# Globals ####
-
-## variables ####
-results_directory_path <- here::here("explore", "results", "revision-jfm")
-tables_directory_path <- here::here("explore", "tables", "revision-jfm")
-factors <- c("market", "CHP", "open interest nearby", "open interest aggregate", "term structure")
-sector_levels <- c("all", "agriculturals", "energy", "metals")
-subsector_levels <- c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")
-sort_levels <- c(
-  "all-all-all", "US-all-all", "US-agriculturals-all", "US-agriculturals-grains",
-  "US-agriculturals-livestock", "US-agriculturals-softs", "US-energy-all", 
-  "US-energy-gas", "US-energy-petroleum", "US-metals-all", "US-metals-base", 
-  "US-metals-precious", "GB-all-all"
-)
-
-## functions ####
-paste_forward_slash <- function(...) paste(..., sep = "/")
-significance <- function(p.value, estimate){
-  if(p.value <= 0.01) paste0("***", estimate)
-  else if (p.value > 0.01 && p.value <= 0.05) paste0("**", estimate)
-  else if (p.value > 0.05 && p.value <= 0.10) paste0("*", estimate)
-  else estimate
-}
-percentize <- function(value) paste0(round(value, digits = 4L) * 100, "%")
-sort_table_by_country_sector_subsector <- function(tb, sort_levels){
-  dplyr::mutate(
-    tb,
-    sort = paste(country, sector, subsector, sep = "-"),
-    sort = factor(sort, levels = sort_levels)
-  ) %>% dplyr::arrange(sort) %>% dplyr::select(-sort)
-}
-
-
-# descriptive stats ####
-stats <- readr::read_rds(
-  paste_forward_slash(results_directory_path, "descriptive-statistics-clean.rds")
-  )
-
-commodities_market_individuals <- dplyr::filter(stats, analysis == "commodity futures") %>%
-  dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::filter(analysis == "market variables") %>%
-  dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::filter(assets == "individual commodities") %>%
-  dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::filter(
[…]

### 2024-09-13 explore/scripts/revision-jfm/analysis.r

@@ -1,0 +1,271 @@
+library(finRes); library(magrittr)
+
+# source functions ####
+source(here::here("explore", "scripts", "revision-jfm-functions.r"))
+
+# globals ####
+## datasets ####
+data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
+data("exchanges", package = "fewISOs")
+
+## variables ####
+storethat_db_path <- make_path_to_storethat_database()
+results_directory_path <- here::here("explore", "results", "revision-jfm")
+
+period_bounds <- list(
+  past = list(start = "1997-07-01", end = "2003-12-31"),
+  financialization = list(start = "2004-01-01", end = "2008-09-14"),
+  crisis = list(start = "2008-09-15", end = "2013-06-19"),
+  present = list(start = "2013-06-20", end = "2018-12-31")
+)
+periods <- make_periods_data_frame(period_bounds)
+
+rf <- readr::read_rds(here::here("data", "risk-free-rate.rds"))
+
+# load data ####
+## time boundaries ####
+start <- "1996-01-01"; end <- "2018-12-14"
+
+## individual commodity futures tickers ####
+commodity_futures_tickers <- c(
+  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
+  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
+  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
+  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
+  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
+  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty",
+  "LAA Comdty", "LPA Comdty", "LLA Comdty", "LNA Comdty", "LTA Comdty",
+  "LXA Comdty"
+)
+
+## commodity futures levels data ####
+### individual data ####
+commodity_futures_individual_data_levels <- get_commodity_futures_individual_data_levels(
+  commodity_futures_tickers, start, end, storethat_db_path
+    )
+
+### aggregate data ####
+commodity_futures_aggregate_data_levels <- get_commodity_futures_aggregate_data_levels(
+  commodity_futures_tickers, start, end, storethat_db_path
+)
+
[…]

### 2024-09-13 explore/scripts/revision-jfm/tables.r

@@ -1,0 +1,290 @@
+library(magrittr)
+
+# Globals ####
+
+## variables ####
+results_directory_path <- here::here("explore", "results", "revision-jfm")
+tables_directory_path <- here::here("explore", "tables", "revision-jfm")
+factors <- c("market", "CHP", "open interest nearby", "open interest aggregate", "term structure")
+sector_levels <- c("all", "agriculturals", "energy", "metals")
+subsector_levels <- c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")
+sort_levels <- c(
+  "all-all-all", "US-all-all", "US-agriculturals-all", "US-agriculturals-grains",
+  "US-agriculturals-livestock", "US-agriculturals-softs", "US-energy-all", 
+  "US-energy-gas", "US-energy-petroleum", "US-metals-all", "US-metals-base", 
+  "US-metals-precious", "GB-all-all"
+)
+
+## functions ####
+paste_forward_slash <- function(...) paste(..., sep = "/")
+significance <- function(p.value, estimate){
+  if(p.value <= 0.01) paste0("***", estimate)
+  else if (p.value > 0.01 && p.value <= 0.05) paste0("**", estimate)
+  else if (p.value > 0.05 && p.value <= 0.10) paste0("*", estimate)
+  else estimate
+}
+percentize <- function(value) paste0(round(value, digits = 4L) * 100, "%")
+sort_table_by_country_sector_subsector <- function(tb, sort_levels){
+  dplyr::mutate(
+    tb,
+    sort = paste(country, sector, subsector, sep = "-"),
+    sort = factor(sort, levels = sort_levels)
+  ) %>% dplyr::arrange(sort) %>% dplyr::select(-sort)
+}
+
+
+# descriptive stats ####
+stats <- readr::read_rds(
+  paste_forward_slash(results_directory_path, "descriptive-statistics-clean.rds")
+  )
+
+commodities_market_individuals <- dplyr::filter(stats, analysis == "commodity futures") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(analysis == "market variables") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(assets == "individual commodities") %>%
+  dplyr::select(results) %>% tidyr::unnest(results) %>%
+  dplyr::filter(
[…]

### 2024-09-13 explore/scripts/tables.r

@@ -1,603 +1,0 @@
-library(magrittr)
-
-significance <- function(p.value, estimate){
-  if(p.value <= 0.01) paste0("***", estimate)
-  else if (p.value > 0.01 && p.value <= 0.05) paste0("**", estimate)
-  else if (p.value > 0.05 && p.value <= 0.10) paste0("*", estimate)
-  else estimate
-}
-
-percentize <- function(value) paste0(round(value, digits = 4L) * 100, "%")
-
-factors <- c("market", "CHP", "OI nearby", "OI aggregate", "term structure")
-sector_levels <- c("all", "agriculturals", "energy", "metals")
-subsector_levels <- c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")
-
-# descriptive stats ####
-stats <- readr::read_rds(
-  here::here("explore", "results", "descriptive-statistics-clean.rds")
-)
-
-commodities_market_individuals <- dplyr::filter(stats, analysis == "commodity futures") %>%
-  dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::filter(analysis == "market variables") %>%
-  dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::filter(assets == "individual commodities") %>%
-  dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::filter(
-    type == "returns", period != "year", frequency == "daily", 
-    field == "close price"
-  ) %>% dplyr::select(-c(ticker, type, frequency, field, year)) %>%
-  dplyr::mutate_if(.predicate = is.list, .funs = unlist)
-
-commodities_market_countries <- dplyr::filter(stats, analysis == "commodity futures") %>%
-  dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::filter(analysis == "market variables") %>%
-  dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::filter(assets == "countries - sectors - subsectors") %>%
-  dplyr::select(results) %>% tidyr::unnest(results) %>%
-  dplyr::filter(
-    sector == "all", subsector == "all", field == "close price",
-    type == "returns", period != "year", frequency == "daily"
-  ) %>% dplyr::select(-c(type, frequency, field, year)) %>%
-  dplyr::mutate_if(.predicate = is.list, .funs = unlist)
-
[…]

### 2024-09-13 explore/shiny/original/datasets.r

@@ -1,0 +1,1233 @@
+library(magrittr)
+
+# data(tickers_futures, package = "BBGsymbols")
+
+factor_parameters <- tibble::tibble(
+  `update frequency` = "week",
+  `return frequency` = "day",
+  `ranking period` = 26L,
+  `long threshold` = 0.67,
+  `short threshold` = 0.33,
+  weighted = TRUE
+)
+
+periods <- tibble::tibble(
+  period = c(
+    rep("past", 2L), rep("financialization", 2L), 
+    rep("crisis", 2L), rep("present", 2L)
+  ), 
+  bound = rep(c("start", "end"), 4L),
+  date = c(
+    "1997-07-01", "2003-12-31", "2004-01-01", "2008-09-14", "2008-09-15", 
+    "2013-06-19", "2013-06-20", "2018-12-31"
+  )
+)
+
+# Descriptive statistics ####
+statistics <- readr::read_rds("results/descriptive-statistics-clean.rds")
+
+## Commodity futures 
+
+### market variables 
+
+#### individuals
+
+##### by year 
+
+###### levels 
+# Commodity futures - market variables - individuals - by year - levels
+statistics_commodity_futures_market_individuals_years_levels <-
+  dplyr::filter(statistics, analysis == "commodity futures") %>%
+  dplyr::select(-analysis) %>%
+  tidyr::unnest(results) %>%
+  dplyr::filter(analysis == "market variables") %>%
+  dplyr::select(-analysis) %>%
+  tidyr::unnest(results) %>%
+  dplyr::filter(assets == "individual commodities") %>%
+  dplyr::select(-assets) %>%
+  tidyr::unnest(results) %>% 
+  dplyr::filter(type == "levels", period == "year") %>%
+  dplyr::select(-c(ticker, type, frequency, period)) %>%
+  dplyr::select(
+    country, sector, subsector, commodity, field, dplyr::everything()
+  ) %>%
+  dplyr::mutate(year = as.integer(year)) %>%
+  dplyr::mutate_at(.vars = c("mean", "p.value"), .funs = unlist) %>%
+  dplyr::arrange(dplyr::desc(country), sector, subsector, commodity)
+
+###### returns 
+# Commodity futures - market variables - individuals - by year - returns
+statistics_commodity_futures_market_individuals_years_returns <-
+  dplyr::filter(statistics, analysis == "commodity futures") %>%
+  dplyr::select(-analysis) %>%
[…]

### 2024-09-16 docs/paper.qmd
Update table captions

@@
 #| label: tbl-correlations-periods
-#| tbl-cap: "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \\@sec-methods.
-Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The results are discussed in section \\@sec-results."
+#| tbl-cap: "This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+For each period, the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
+Aggregate CHP construction and corresponding regime definitions are discussed in section \\@sec-methods while the results are discussed in section \\@sec-results."
 
@@
 #| label: tbl-correlations-years
-#| tbl-cap: "This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors by year for the whole periods of interest (1997-2018).
-For each year, the results are calculated independently over the entire year as well as over phases of aggregate backwardation and contango.
-Aggregate CHP construction and corresponding regime definitions are discussed in section \\@sec-methods while the results are discussed in section \\@sec-results."
+#| tbl-cap: "This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors by year for the whole period of interest (1997-2018).
+The results are discussed in section \\@sec-results."
 

### 2024-09-16 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@e5894f3377647e114fcf7c4fb7a7b3fe006775cd 🚀

--- 2022-05-26 docs/paper.tex
@@
-\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
-%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
-\usepackage[hyphens]{url}
-
-  \journal{no journal yet} % Sets Journal name
-
-\usepackage{lineno} % add
-
-\usepackage{graphicx}
-%%%%%%%%%%%%%%%% end my additions to header
-
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  authoryear,
+  preprint,
+  3p]{elsarticle}
+
+\usepackage{amsmath,amssymb}
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-% use upquote if available, for straight quotes in verbatim environments
+\ifPDFTeX\else  
+    % xetex/luatex font selection
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \usepackage{fontspec}
-  \ifxetex
-    \usepackage{xltxtra,xunicode}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
+% Make \paragraph and \subparagraph free-standing
+\makeatletter
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
-  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
-  \newcommand{\euro}{€}
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
-% use microtype if available
-\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
-\bibliographystyle{elsarticle-harv}
-\ifxetex
-  \usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \usepackage[unicode=true]{hyperref}
-\fi
-\hypersetup{breaklinks=true,
-            bookmarks=true,
-            pdfauthor={},
-            pdftitle={Financialisation of commodities: co-movement behind-the-scenes},
-            colorlinks=false,
-            urlcolor=blue,
-            linkcolor=magenta,
-            pdfborder={0 0 0}}
-\urlstyle{same}  % don't use monospace font for urls
-
-\setcounter{secnumdepth}{5}
-% Pandoc toggle for numbering sections (defaults to be off)
-
-% tightlist command for lists without linebreak
+\makeatother
+
 \providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% From pandoc table feature
-\usepackage{longtable,booktabs,array}
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makesavenoteenv{longtable}
-
-\usepackage{geometry}
-\usepackage{hyperref}
-\usepackage{lscape}
-\usepackage[margin=0pt]{caption}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
-
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\journal{Journal of Futures Markets}
+
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage[]{natbib}
+\bibliographystyle{elsarticle-harv}
+\usepackage{bookmark}
+
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Financialisation of Commodity Markets},
+  pdfauthor={Devraj Basu; Olivier Bauthéac},
+  pdfkeywords={Commodity markets, Financialisation, Asset pricing},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
+
+\setlength{\parindent}{6pt}
 \begin{document}
@@
 \begin{frontmatter}
-
-  \title{Financialisation of commodities: co-movement behind-the-scenes}
-    \author[strath]{Devraj Basu\corref{1}}
+\title{Financialisation of Commodity Markets \\\large{Co-movement
+Behind-the-Scenes} }
+\author[1]{Devraj Basu%
+\corref{cor1}%
+}
  \ead{devraj.basu@strath.ac.uk} 
-    \author[strath]{Olivier Bauthéac}
-
-      \address[strath]{University of Strathclyde Business school}
-      \cortext[1]{Corresponding Author}
+\author[1]{Olivier Bauthéac%
+%
+}
+ \ead{olivier.bautheac@strath.ac.uk}
+
+\affiliation[1]{organization={University of Strathclyde Business
+School, Accounting \& Finance},addressline={199 Cathedral
+Street},city={Glasgow},postcode={G4 0QU},postcodesep={}}
+
+\cortext[cor1]{Corresponding author}
 
 \begin{abstract}
-  In the early 2000s institutional investors entered the commodity futures markets en masse with passive, long only, index type positions in sharp contrast with those typically assumed by traditional expert participants.
-A heated public debate soon erupted over the perceived consequences of the phenomenon--commonly referred to as ``financialisation''---and, in response to immediate policy concerns, the matter was thrust onto the academic sphere as a burning issue.
-With the benefit of hindsight it now seems that the academic debate was framed rather narrowly, used contentious research methods, and eventually led to regulatory changes that were therefore perhaps unwarranted.
-In contrast, we take a broader approach where we consider a large cross-section of liquid commodities as suggested by the nature of financilisation that comprehends commodity futures as an asset class.
-Using a bespoke asset pricing factors based framework we study the issue through the lens of co-movement and find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals.
+In the early 2000s institutional investors entered the commodity futures
+markets en masse with passive, long only, index type positions in sharp
+contrast with those typically assumed by traditional expert
+participants. A heated public debate soon erupted over the perceived
+consequences of the phenomenon--commonly referred to as
+``financialisation''---and, in response to immediate policy concerns,
+the matter was thrust onto the academic sphere as a burning issue. With
+the benefit of hindsight it now seems that the academic debate was
+framed rather narrowly, used contentious research methods, and
+eventually led to regulatory changes that were therefore perhaps
+unwarranted. In contrast, we take a broader approach where we consider a
+large cross-section of liquid commodities as suggested by the nature of
+financilisation that comprehends commodity futures as an asset class.
+Using a bespoke asset pricing factors based framework we study the issue
+through the lens of co-movement and find that the phenomenon had
+ontological consequences for the commodity complex with its impact
+extending beyond the mechanical effects induced by indexation. The onset
+of the financial crisis and the monetary policy regimes that followed,
+on the other hand, seem to have set off a motion of reversion to legacy
+pre-financialisation fundamentals.
 \end{abstract}
 
+\begin{keyword}
+    Commodity markets \sep Financialisation \sep 
+    Asset pricing
+\end{keyword}
 \end{frontmatter}
 
-\newgeometry{a4paper,left=1in,right=1in,top=1in,bottom=1in,nohead}\savegeometry{tables}\restoregeometry
-
-\cleardoublepage
-
-\hypertarget{index}{%
-\section{Introduction}\label{index}}
-
-The last twenty years have seen major upheavals in the commodity markets with the onset of financialisation\footnote{Starting around 2004, with a view of commodity markets as an emerging asset class and in an effort to hedge against inflation and seek diversification benefits (Büyükşahin and Robe, 2014; Singleton, 2013), institutional investors sent forth an unprecedented flow of capital into commodity futures markets.
-This phenomenon is commonly referred to as the financialisation of commodities (Domanski and Heath, 2007).} as well as the period of the 2008 financial crisis and its aftermath.
-Financialisation appears to have affected multiple economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres.
-A vigorous legislative debate accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors\footnote{See section \ref{co-movement-background} for a detailed discussion.} eventually led to regulatory changes in several individual markets.\\
-In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation--the burning issue of the day--at the individual commodity market level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
-With the benefit of hindsight, this approach seems to lack a fundamental understanding of the phenomenon it endeavoured to study and which consequences it attempted to address.\\
-Financialisation was a phenomenon global in nature; through the channel of index investment it affected the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
-Focusing on individual markets in this context thus seems limited.
-Most of the studies underpinning the regulatory response to financialisation took the form of pairwise correlation, causation and to some extent co-integration analysis, all of which are idiosyncratic in nature for they study single pairs of individual assets.
-Besides, some of these techniques since proved controversial and seem to produce results the quality of which may fall short of the standards that may reasonably be expected to lay the ground for legislative action.
-Although appealing, for it comes with the promise of prompt ``significant'' results, this approach misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure (Hicks, 1939; Keynes, 1930).\\
-While essential to the understanding of the phenomenon, the global nature of financialisation and its impact on market fundamentals therefore appear to have been originally overlooked and another approach, perhaps more refined, seems warranted.
-
-\medskip\setlength{\parindent}{0pt}
-
-We strive to provide one in this study by taking a fundamentally different empirical perspective that is broader in scope.
-We consider the entire cross-section of actively traded commodities on futures markets and use a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations.\\
-The global nature of financialisation makes cross-sectional co-movement a cornerstone issue that the direct impact of increased market participation alone might not be able to fully explain for it potentially had deeper effects, for example on market fundamentals as our results suggest.
-Commodity futures markets have a history of being the classic physical commodity price risk shifting conduit for commodity specialists.
-Over the financialisation period we observe a decrease in effectiveness of commercial hedging pressure (CHP) at explaining commodity futures returns at the individual level accompanied by a more pronounced increase at the aggregate level.
-We further note an overall shift in the nature of hedger's behaviour away from the traditional Keynesian view of risk transfer with higher individual risk premiums over phases of cross-sectional contango as opposed to backwardation.
-Both patterns suggest that the phenomenon may have altered this long-standing paradigm of commercial risk transfer with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants.
-This change could have altered the hedging ontology in these markets and our asset pricing framework is well suited to detect these more subtle effects driven by changes in the nature of market participation.\\
-Factor model techniques are well suited to isolating common driving factors and detecting co-movement (Asness and Frazzini, 2013; Asness et al., 2015, 2019; Carhart, 1997; Fama and French, 2015, 1993; Frazzini and Pedersen, 2014; Hou et al., 2015) at a broader level, beyond individual pairs of assets, and are commonly used to study commodity market fundamentals (Bakshi et al., 2019; Boons and Prado, 2019; Cortazar et al., 2013; Daskalaki et al., 2014; Fernandez-Perez et al., 2018; Gorton et al., 2012; Miffre and Rallis, 2007; Sakkas and Tessaromatis, 2020; Schwartz and Smith, 2000; Szymanowska et al., 2014; Yang, 2013); they consequently seem well adapted to study these two issues simultaneously.
-Building on theory we therefore develop a bespoke commodity-based asset pricing framework comprised of factor models based both on fundamentals as well as liquidity considerations.\\
-One of these is based on the Keynes-Hicks (Hicks, 1946, 1939; Keynes, 1930, 1923) risk transfer approach to the term structure; the corresponding ``theory of normal backwardation'', complemented for the possibility of contango (Cootner, 1960; H.
-Houthakker, 1957), postulates that futures prices for a given commodity are inversely related to the extent that commercial hedgers are short or long and using commercial hedging pressure (CHP) as a proxy for hedgers net market position we construct factor mimicking portfolios that capture the impact of hedging pressure as a systemic factor (Basu and Miffre, 2013).
-Working's contending approach that relates futures price formation to storage costs in the theory of ``the price of storage'' (Working, 1949) forms the basis of another model that we consider where, following Szymanowska et al.
-(2014) and Fuertes et al.
-(2015) who demonstrate that the term structure factor has explanatory power for the cross-section of commodity returns, we construct factor mimicking portfolios using roll-yield as a proxy for the front end shape of individual commodity term structures.
-We further consider a liquidity-based model following Hong and Yogo (2012) who find that open interest growth has predictive power for individual commodity returns and again, using the latter measure as a proxy for individual commodity liquidity, we construct long-short factor mimicking portfolios.
-
-\bigskip\bigskip\setlength{\parindent}{0pt}
-
-We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008\footnote{Starting point based on earlier studies (Baker, 2014; Christoffersen et al., 2014).}); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).\\
-Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.
-
-\medskip\setlength{\parindent}{0pt}
-
-The cross-sectional nature of financialisation (Basak and Pavlova, 2016; Cheng and Xiong, 2014) leads us to extend the Keynesian individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure first considered in Hong and Yogo (2012).
-This paradigm implies that returns for individual commodities should be high in periods where \textbf{CHP} is low (\textbf{backwardation}) and low in periods where \textbf{CHP} is high (\textbf{contango}).
-Over the first period the cross-sectional average returns during phases of \textbf{backwardation} for both the US and UK commodities are positive and overall higher than during phases of \textbf{contango}, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
-Over the second period this pattern reverses, with both the US and UK commodities having higher returns during phases of \textbf{contango} as opposed to \textbf{backwardation}.
-This change in pattern suggests the onset of financialisation altered the traditional risk shifting nature of hedger's behaviour, implied by the Keynesian hypothesis.\\
-This change of paradigm due to the arrival of financial investors, on the other hand, raises the question of whether they functioned as liquidity providers or demanders.
-Arguments have been put forward in favour of both possibilities with Moskowitz et al.
-(2012) arguing that financial investors provide liquidity and Kang et al.
-(2020) taking the opposite stance.
-Our analysis of individual commodity returns' relation with both CHP and \textbf{CHP} before and during financialisation sheds new lights on this issue with our results suggesting that financial investors may have been liquidity demanders leading hedgers to become liquidity providers.
-
-\medskip\setlength{\parindent}{0pt}
-
-Goldstein et al.
-(2014) and Goldstein and Yang (2017) argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
-Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger's positions (Keynesian perspective, theory of normal backwardation: Keynes (1930), Hicks (1939), H.
-S.
-Houthakker (1957), Telser (1958)), as well our term structure factor, based on backwardation as measured by roll yield (Working's perspective, theory of storage: Working (1933), Kaldor (1939), Working (1948), Brennan (1958), Cootner (1960), Weymar (1966), Danthine (1978), Turnovsky (1983), Schwartz (1997)), to be best suited to measure the impact of financialisation.\\
-We analyse the pricing dynamics over the different periods by first studying the time series explanatory performance of the various factors on all the US traded commodities with the factors constructed using the latter set of commodities.
-The market-based factor outperforms the other three in the first period and, although its performance increases over the financialisation period, that of the CHP factor shows a greater improvement in a relative sense.
-The performance of the market factor is driven by agricultural and energy commodities in the first period while metals strongly contribute to the performance improvement observed over the second period.
-Similarly, the dramatic improvement of the CHP factor in the second period, is driven by the metals complex, particularly that of the long leg where they predominantly load.
-Average pairwise correlations amongst individual factors' best performing commodities increase across the board over the financialisation period, far beyond the average for the whole cross-section of US traded commodities.
-The increase is particularly strong for the long-short factors, in a relative sense, on which the metal complex loads significantly more during financialisation.
-This increase is due to the dramatic rise in average pairwise correlation amongst the US traded metals all of which exhibited high \(R^{2}\) with respect to the CHP factor during financialisation which in turn is due to their common low level of CHP over this period.
-The CHP factor model thus seems able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialisation.\\
-We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period\footnote{See section \ref{co-movement-methods} for further details.} and evaluating its performance on these selected commodities as well as on all US traded commodities.
-The results of this exercise provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
-
-\medskip\setlength{\parindent}{0pt}
-
-The UK traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialisation.
-To that end, we examine the performance of the four factors on the six UK metals, when constructed from each set of factor picks.
-The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.
-
-\medskip\setlength{\parindent}{0pt}
-
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes.
-Commodity futures returns fell dramatically into the crisis and the pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as evidence of cross-market linkages with the UK traded commodity subset.
-The post-crisis results, in contrast, show a substancial pullback in performance for the market factor across the board as well as evidence of decoupling between the US and UK markets.
-Besides, starting in the crisis the Keneysian paradigm of returns begins to revert with higher mean returns during low (\textbf{backwardation}) relative to high (\textbf{contango}) \textbf{CHP} phases and this pattern continues, more pronounced, over the post-crisis period.
-As pointed out in Basu and Bauthéac (2021), the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
-
-\bigskip\bigskip\setlength{\parindent}{0pt}
-
-Financialisation was an issue of such policy importance that it triggered legislative action.
-The debate was initially framed around adequacy of speculation, the burning issue of the day, and the ensuing academic analysis focused on the more mechanical effects of financialisation.\\
-With the benefit of hindsight, it appears this approach was perhaps too narrow, and it now seems necessary to address the phenomenon from a broader perspective.
-Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggering a reversion to pre-financialisation dynamics.
-
-The initial view of financialisation was that it consisted of speculative flows which had the effect of driving up and creating bubble like conditions in commodity futures prices\footnote{Masters (2008); Masters and White (2008); UNCTAD and Cooperation (2009); De Schutter (2010); Gilbert (2010a); Gilbert (2010b); Herman et al.
-(2011); Schumann (2011); Singleton (2013).}.
-However, the fundamental question of the nature of the impact of financialisation across the entire cross-section of commodity futures markets has not yet been completely answered.
-We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets\footnote{Etula (2013), Acharya et al.
-(2013), Cheng et al.
-(2014), Leclercq and Praz (2014), Sockin and Xiong (2015), Goldstein et al.
-(2014), Ekeland et al.
-(2016), Goldstein and Yang (2017).} and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in Tang and Xiong (2012) and Basak and Pavlova (2016).
-
 \newpage
 
-\hypertarget{co-movement-data-methods}{%
-\section{Data \& methods}\label{co-movement-data-methods}}
-
-\hypertarget{co-movement-background}{%
-\subsection{Background}\label{co-movement-background}}
-
-The period from 1998 to 2008 saw an influx of investment into commodity index linked products most of which made its way into the commodity futures market.
-Popular commodity indexes whose goal was to track the broad movement of commodity prices became accessible by means of swaps, exchange traded funds and exchange traded notes and attracted at least \$100 billion of net super-hoc investment over the 1998-2008 period.
-
-\medskip\setlength{\parindent}{0pt}
-
-Concerns over the consequences of this financialisation phenomenon eventually led to legislative changes including the approval of Rule 76 FR 4752 issued by the US Commodity Futures Trading Commission (CFTC) on January 26\textsuperscript{th}, 2011.
-This provision emanates from the Dodd-Frank Wall Street and Consumer Protection Act of 2010 (Title VII, Section 737) that mandates the CFTC to use position limits to restrict the flow of speculative capital into a number of commodity markets.
-The Rule was approved in a close 3-2 vote and the ensuing rule-making process was extremely contentious with several commissioners (Michael Dunn and Scott D.
-O'Malia in particular) expressing reservations about the lack of supporting evidence and the Rule also triggering thousands of comment letters as well as a lawsuit against the CFTC spearheaded by two Wall Street trade groups, the International Swaps \& Derivatives Association (ISDA) and the Securities Industries \& Financial Markets Association (SIFMA)\footnote{ISDA \& SIFMA v US CFTC; Complaint, 1:11-cv-02146; December 2\textsuperscript{nd}, 2011.}.
-
-\medskip\setlength{\parindent}{0pt}
-
-A world-wide debate ensued about the role of index funds in commodity markets.
-The first responses to the 2007/2008 crisis of escalating food and energy prices took the form of policy reports, many of which reasoned that the growth of commodity index funds came along with an influx of largely speculative capital that was responsible for driving commodity prices beyond their historic highs (De Schutter, 2010; Gilbert, 2010b; Herman et al., 2011; Schumann, 2011; UNCTAD and Cooperation, 2009).\\
-Early US Senate investigations on the matter drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US agricultural and energy markets to the observed surges in both futures and cash prices (Masters, 2008; Masters and White, 2008).
-This contention has since come to be known as the Masters' hypothesis and was largely endorsed by the final US Senate report on the issue (Senate, 2009).\\
-At this stage, the question thrust on the academic sphere was whether ``excessive speculation'' (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices.
-A number of ensuing academic studies, most of which used commodity specific correlation and causality based analysis have since disproved this contention: Irwin et al.
-(2009), Sanders et al.
-(2010), Sanders and Irwin (2011a), Sanders and Irwin (2011b), Irwin (2013), Brunetti and Reiffen (2014), Hamilton and Wu (2015) and Bruno et al.
-(2017) investigated the issue in the context of the agricultural markets; meanwhile, Büyükşahin and Harris (2011), Tokic (2012), Fattouh et al.
-(2013), Kilian and Murphy (2014), Knittel and Pindyck (2016) and Manera et al.
-(2016) examined the energy markets while Bohl and Stephan (2013), Kim (2015) and Boyd et al.
-(2016) studied both energy and agricultural markets and Irwin and Sanders (2011), Irwin and Sanders (2012) as well as Stoll and Whaley (2011) examined the commodity markets in general.
-Other studies have underlined various alterations in commodity pricing dynamics over the period.
-Gilbert and Pfuderer (2014) reject the view that financialisation has not had any effects in the grains markets and demonstrate that trades originated by financial market participants, and specifically index investors, can move prices but tend to be typically volatility-reducing.
-Juvenal and Petrella (2015) contend that the oil price increase between 2004 and 2008 was mainly driven by the strength of global demand but that the financialisation process of commodity markets also played a role.
-Likewise, Henderson et al.
-(2015) show that non-information-based financial investments have important impacts on commodity prices.
-Cheng and Xiong (2014), on the other hand, show that in the case of index commodities, financialisation has transformed the risk sharing, and information discovery functions of commodity futures markets.
-
-\hypertarget{co-movement-data}{%
-\subsection{Data}\label{co-movement-data}}
-
-Commodity index swaps, commodity index funds (CIFs), commodity-based exchange traded funds (ETFs) and notes (ETNs) or commodity linked notes (CLNs) were amongst the main investment vehicles that allowed institutional and retail investors to build up commodity exposure in the early 2000s (Boons et al., 2012; Henderson et al., 2015; Irwin and Sanders, 2011; Schumann, 2011; UNCTAD and Cooperation, 2009).
-Most of these products were primarily designed to track prominent commodity indexes among which the S\&P-GSCI, the most popular.\\
-Most of its constituents at the time of writing form the basis of the broad cross-section of commodities that we consider in this study: corn-\#2 yellow (XCBT), oats (XCBT), soybean meal (XCBT), soybean oil (XCBT), soybeans (XCBT), wheat-SRW (XCBT), cattle-feeder (XCME), cattle-live (XCME), lean hogs (XCME), cocoa (IFUS), coffee-C (IFUS), cotton-\#2 (IFUS), lumber (XCME), orange juice (IFUS), sugar-\#11 (IFUS), natural gas (XNYM), crude oil-WTI (XNYM), gasoline (XNYM), heating oil (XNYM), copper (XCEC), gold (XCEC), palladium (XNYM), platinum (XNYM) and silver (XCEC).
-Unleaded gasoline, the NYMEX legacy contract for gasoline, stopped trading in 2006 when it was replaced by Reformulated Gasoline Blendstock for Oxygen Blending (RBOB) with the two futures series trading alongside for most of the year.
-For our NYMEX gasoline data series, we consider unleaded gasoline up to September 1\textsuperscript{st}, 2006 and RBOB gasoline thereafter, date at which liquidity for the latter overtook that for the former.\\
-We also consider the UK metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).
-
-\medskip\setlength{\parindent}{0pt}
-
-The commodity futures trading commission (CFTC) operates a comprehensive system of collecting information on market participants known as the large trader reporting program (LTRP) where it records and reports to the public position data on market participants who have position levels in excess of a particular market specific threshold\footnote{Current reporting level thresholds available at: \href{https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=\&SID=970471b8455f4bab7db4110cfde50731\&mc=true\&r=SECTION\&n=se17.1.15_103}{www.ecfr.gov}.}.
-The commission collects market data and position information daily from clearing members, futures commission merchants (FCMs) and foreign brokers and publishes corresponding summaries weekly in a series of market specific reports.
-In these reports, individual traders are categorised according to the nature of their trading activity on the basis of self-reported information\footnote{CFTC form 40.
-Available at: \href{https://www.cftc.gov/sites/default/files/idc/groups/public/@forms/documents/file/cftcform40.pdf}{www.cftc.gov}.} that is subject to review by CFTC staff for reasonableness.
-Position information is then aggregated by category and asset type with each report providing an aggregation for a set of report specific categories and, for each category, a breakdown between futures only positions and positions in futures and options combined.\\
-In its legacy report, the commitment of trader report (COT) with data dating back to 1962, the CFTC distinguishes ``commercial'' and ``non-commercial'' market participants where a ``commercial'' participant is defined as one ``{[}\ldots{]} engaged in business activities hedged by the use of futures and option markets''\footnote{See \href{https://www.gpo.gov/fdsys/pkg/CFR-1998-title17-vol1/xml/CFR-1998-title17-vol1-sec1-3.xml}{CFTC regulation 1.3, 17 CFR 1.3(z)} for details.}.
-A third category, ``non-reportable'', aggregates positions for participants not meeting the reporting threshold.
-In response to concerns related to category accuracy\footnote{See for example Ederington and Lee (2002).} the CFTC now refines its classification in the disaggregated commitment of trader report (DCOT) where participant categories include ``Producer/Merchant/Processor/User'', ``Swap dealer'', ``Money manager'' and ``Other reportable'' as well as in the supplemental commitment of trader report (SCOT) that details commodity index trader aggregate positions for thirteen agricultural commodity futures markets.
-Data for DCOT and SCOT date back to 2006 and 2007 respectively.\\
-We study the 1997/2018 period where we observe futures only position data from the COT report, the only CFTC report with data available for the whole period of interest; as well as futures term structure price and open interest data from Bloomberg.
-
-\hypertarget{co-movement-methods}{%
-\subsection{Methods}\label{co-movement-methods}}
-
-On the one hand, futures markets have a long history of serving commodity producers to alleviate their commodity price and output risks.
-Keynes (1930) and Hicks (1939) emphasise the ``normal'' behaviour of naturally short hedgers outsourcing their commodity risk to naturally long commodity specialist speculators.
-This market configuration is referred to as ``backwardation'' where futures are expected to trade at a discount to spot prices, providing speculators with incentives to take the long side.
-The opposite market paradigm is referred to as ``contango''.
-Working (Working, 1953, 1948, 1933) and Kaldor (Kaldor, 1939) somehow relax this ``supply-of-speculative-services'' (Till, 2007) approach by introducing processors and merchants, also commodity experts, on the hedgers side and relating the notions of backwardation and contango more directly to the term structure via the theory of storage where the shape of the front end of the term structure (basis) is directly related to the market price of storage.\\
-Financialisation, on the other hand, refers to the entry of financial investors into the commodity futures markets who, for the most part, are not commodity experts.
-Besides, these new market participants tend to exhibit herding like behaviour, often taking massive long-only positions on the whole cross-section of indexed commodities in an attempt to enhance returns while hedging against inflation and reaping further diversification benefits for portfolios with, in most cases, existing large positions across various asset classes (Boyd et al., 2016; Brunetti et al., 2016; Cheng et al., 2014; Juvenal and Petrella, 2015; Singleton, 2013; Tang and Xiong, 2012).
-This contrasts with the traditional approaches of Keynes and Working and in this context the issues of co-movement and aggregate market participants behaviour seem particularly relevant.
-
-\medskip\setlength{\parindent}{0pt}
-
-Asset pricing techniques are well suited to study co-movement.
-Building on theory we therefore develop an ad-hoc commodity-based asset pricing framework that we believe is well adapted to study these two issues simultaneously and implement it over four periods of interest.
-The first, the pre-financialisation period, starts in 1997 and is naturally followed by financialisation, spanning the 2004/2008 period, and the financial crisis and its aftermath, spanning the 2008/2013 period.
-The last period spans the 2014/2018 period starting with the beginning of the tapering/end of the US Quantitative Easing program (QE).\\
-Using the weekly price, open interest and market position data described above we construct market portfolios of individual commodity nearby futures as well as mimicking portfolios for market, commercial hedging pressure, term structure and liquidity risk factors in returns.
-While our market portfolios are long only, equally weighted portfolios of particular commodity sets, our other mimicking portfolios for risk factors are constructed as combinations of two sub-portfolios (legs), one held long, one held short, which respective constituents are pooled on a weekly basis according to risk factor specific criteria.\\
-For each leg, the position weight for a particular asset for a particular period is contingent on the value of the corresponding sorting variable and its rank relative to the other assets in the pool.
-The sorting variable values for the asset pool are first rescaled so that the highest (lowest) value becomes 1 (0).
-Weights are then determined pairwise, starting from the extremes with the highest and lowest figures.
-A coefficient \(\alpha\) is determined by dividing their difference (1 in this case) by the mean of the rescaled values.
-The high figure is attributed a score of \(\frac{1}{n} \times \alpha\) where \(n\) is the number of assets in the pool while the score for the low figure is \(\frac{1/n}{\alpha}\).
-The operation is repeated for the pair of assets showing the second highest and second lowest values for the sorting variable and so on until all the assets in the pool are attributed a score.
-The individual asset weights are then determined by dividing each score by the sum of the scores.\\
-The period return for a particular mimicking portfolio is calculated as the difference between the weighted average return for constituents of the long portfolio and that for the constituents of the short portfolio.
-i.e, return on the mimicking portfolio for risk factor \(i\) (\(f_{i}\)) for period \(t\):
+\setlength{\parindent}{0pt}
+
+\section{Introduction}\label{sec-introduction}
+
+The last twenty years have seen major upheavals in the commodity markets
+with the onset of financialisation\footnote{Starting around 2004, with a
+  view of commodity markets as an emerging asset class and in an effort
+  to hedge against inflation and seek diversification benefits
+  \citep{buyuksahin_speculators_2014, singleton_investor_2013},
+  institutional investors sent forth an unprecedented flow of capital
+  into commodity futures markets. This phenomenon is commonly referred
+  to as the financialisation of commodities
+  \citep{domanski_financial_2007}.} as well as the period of the 2008
+financial crisis and its aftermath. Financialisation appears to have
+affected multiple economic sectors, including agriculture and energy,
+and its impact has been hotly debated in the policy, legislative,
+regulatory, and academic spheres. A vigorous legislative debate
+accompanied by an equally intense policy and academic debate across a
+number of disciplines about the perceived effects on commodity prices of
+the unprecedented inflow of institutional funds brought into commodity
+futures markets by new index type investors\footnote{See section
+  Section~\ref{sec-background} for a detailed discussion.} eventually
+led to regulatory changes in several individual markets.\\
+In response to immediate policy concerns, the academic debate was
+initially framed rather narrowly around adequacy of speculation--the
+burning issue of the day--at the individual commodity market level and
+the ensuing academic analysis focused on the more mechanical effects of
+financialisation. With the benefit of hindsight, this approach seems to
+lack a fundamental understanding of the phenomenon it endeavoured to
+study and which consequences it attempted to address.\\
+Financialisation was a phenomenon global in nature; through the channel
+of index investment it affected the whole cross-section of liquid
+commodities at once, eventually spurring its transition away from a
+collection of idiosyncratic markets to its emergence as an asset class.
+Focusing on individual markets in this context thus seems limited. Most
+of the studies underpinning the regulatory response to financialisation
+took the form of pairwise correlation, causation and to some extent
+co-integration analysis, all of which are idiosyncratic in nature for
+they study single pairs of individual assets. Besides, some of these
+techniques since proved controversial and seem to produce results the
+quality of which may fall short of the standards that may reasonably be
+expected to lay the ground for legislative action. Although appealing,
+for it comes with the promise of prompt ``significant'' results, this
+approach misses a critical corollary of the substantial advent of a new
+category of players in a (set of) market(s): the alteration of market
+fundamentals it potentially induces, best observed in this context
+through the lens of commercial hedging pressure
+\citep{keynes_treatise_1930, hicks_value_1939}.\\
+While essential to the understanding of the phenomenon, the global
+nature of financialisation and its impact on market fundamentals
+therefore appear to have been originally overlooked and another
+approach, perhaps more refined, seems warranted.
+
+\medskip
+
+We strive to provide one in this study by taking a fundamentally
+different empirical perspective that is broader in scope. We consider
+the entire cross-section of actively traded commodities on futures
+markets and use a futures-based asset pricing framework that includes
+factors constructed using both theoretical fundamentals and liquidity
+considerations.\\
+The global nature of financialisation makes cross-sectional co-movement
+a cornerstone issue that the direct impact of increased market
+participation alone might not be able to fully explain for it
+potentially had deeper effects, for example on market fundamentals as
+our results suggest. Commodity futures markets have a history of being
+the classic physical commodity price risk shifting conduit for commodity
+specialists. Over the financialisation period we observe a decrease in
+effectiveness of commercial hedging pressure (CHP) at explaining
+commodity futures returns at the individual level accompanied by a more
+pronounced increase at the aggregate level. We further note an overall
+shift in the nature of hedger's behaviour away from the traditional
+Keynesian view of risk transfer with higher individual risk premiums
+over phases of cross-sectional contango as opposed to backwardation.
+Both patterns suggest that the phenomenon may have altered this
+long-standing paradigm of commercial risk transfer with the entry of
+long only commodity index traders (CITs) with very different hedging and
+volume demands from traditional participants. This change could have
+altered the hedging ontology in these markets and our asset pricing
+framework is tailored to detect these more subtle effects driven by
+changes in the nature of market participation.\\
+Factor model techniques are well suited to isolating common driving
+factors and detecting co-movement
+\citep{fama_common_1993, carhart_persistence_1997, asness_devil_2013, fama_five_factor_2015, hou_digesting_2015, asness_fact_2015, frazzini_betting_2014, asness_quality_2019}
+at a broader level, beyond individual pairs of assets, and are commonly
+used to study commodity market fundamentals
+\citep{schwartz_short_2000, miffre_momentum_2007, gorton_fundamentals_2012, cortazar_commodity_2013, yang_investment_2013, daskalaki_factors_2014, szymanowska_anatomy_2014, fernandez_skewness_2018, bakshi_understanding_2019, boons_basis_2019, sakkas_factor_2020};
+they consequently seem well adapted to study these two issues
+simultaneously. Building on theory we therefore develop a bespoke
+commodity-based asset pricing framework comprised of factor models based
+both on fundamentals as well as liquidity considerations.\\
+One of these is based on the Keynes-Hicks
+\citep{keynes_some_1923, keynes_treatise_1930, hicks_value_1939, hicks_value_1946}
+risk transfer approach to the term structure; the corresponding ``theory
+of normal backwardation'', complemented for the possibility of contango
+\citep{houthakker_restatement_1957, cootner_returns_1960}, postulates
+that futures prices for a given commodity are inversely related to the
+extent that commercial hedgers are short or long and using commercial
+hedging pressure (CHP) as a proxy for hedgers net market position we
+construct factor mimicking portfolios that capture the impact of hedging
+pressure as a systemic factor \citep{basu_capturing_2013}. The
+cross-sectional nature of financialisation
+\citep{cheng_financialisation_2014, basak_model_2016} further leads us
+to extend this paradigm by incorporating aggregate CHP (\textbf{CHP}), a
+market wide measure of hedging pressure first considered in
+\citet{hong_what_2012}. In this context, returns for individual
+commodities should be high in periods where \textbf{CHP} is low
+(\textbf{backwardation}) and low in periods where \textbf{CHP} is high
+(\textbf{contango}). Working's contending approach that relates futures
+price formation to storage costs in the theory of ``the price of
+storage'' \citep{working_theory_1949} forms the basis of another model
+that we consider where, following \citet{szymanowska_anatomy_2014} and
+\citet{fuertes_commodity_2015} who demonstrate that the term structure
+factor has explanatory power for the cross-section of commodity returns,
+we construct factor mimicking portfolios using roll-yield as a proxy for
+the front end shape of individual commodity term structures. We further
+consider a liquidity-based model following \citet{hong_what_2012} who
+find that open interest growth has predictive power for individual
+commodity returns and again, using the latter measure as a proxy for
+individual commodity liquidity, we construct long-short factor mimicking
+portfolios.
+
+\bigskip
+\bigskip
+
+We study the performance of these models on a set of twenty-four US
+traded commodities and six UK traded (London Metal Exchange) base metals
+over the 1997/2018 period that we divide into four distinct sub-periods:
+pre-financialisation (1997/2003); financialisation
+(2004/2008\footnote{Starting point based on earlier studies
+  \citep{baker_financialization_2021, christoffersen_factor_2014}.});
+financial crisis and aftermath, including loose monetary policy regimes
+that followed (2008/2013); and post-crisis (2014-2018).\\
+Consistent with earlier studies, we observe that mean returns for the US
+traded commodities are sharply higher over the financialisation period
+compared to pre-financialisation and this pattern extends to UK traded
+metals.
+
+\medskip
+
+Over the first period the cross-sectional average returns during phases
+of \textbf{backwardation} for both the US and UK commodities are
+positive and overall higher than during phases of \textbf{contango},
+providing broad support for an aggregate version of the Keynesian
+hedging pressure hypothesis. Over the second period this pattern
+reverses, with both the US and UK commodities having higher returns
+during phases of \textbf{contango} as opposed to \textbf{backwardation}.
+This change in pattern suggests the onset of financialisation altered
+the traditional risk shifting nature of hedger's behaviour, implied by
+the Keynesian hypothesis.\\
+This change of paradigm due to the arrival of financial investors, on
+the other hand, raises the question of whether they functioned as
+liquidity providers or demanders. Arguments have been put forward in
+favour of both possibilities with \citet{moskowitz_time_2012} arguing
+that financial investors provide liquidity and \citet{kang_tale_2020}
+taking the opposite stance. Our analysis of individual commodity
+returns' relation with both CHP and \textbf{CHP} before and during
+financialisation sheds a new light on this issue with our results
+suggesting that financial investors may have been liquidity demanders
+leading hedgers to become liquidity providers.
+
+\medskip
+
+\citet{goldstein_speculation_2014} and \citet{goldstein_commodity_2022}
+argue that the arrival of financial investors had an impact on the
+extent of normal backwardation in commodity futures markets. Based on
+their analysis we would expect our average CHP factor, based on
+backwardation as measured by hedger's positions (Keynesian perspective,
+theory of normal backwardation: \citet{keynes_treatise_1930},
+\citet{hicks_value_1939}, \citet{houthakker_speculators_1957},
+\citet{telser_futures_1958}), as well our term structure factor, based
+on backwardation as measured by roll yield (Working's perspective,
+theory of storage: \citet{working_price_1933},
+\citet{kaldor_speculation_1939}, \citet{working_theory_1948},
+\citet{brennan_supply_1958}, \citet{cootner_returns_1960},
+\citet{weymar_supply_1966}, \citet{danthine_information_1978},
+\citet{turnovsky_determination_1983}, \citet{schwartz_stochastic_1997}),
+to be best suited to measure the impact of financialisation.\\
+We analyse the pricing dynamics over the different periods by first
+studying the time series explanatory performance of the various factors
+on all the US traded commodities with the factors constructed using the
+latter set of commodities. The market-based factor outperforms the other
+three in the first period and, although its performance increases over
+the financialisation period, that of the CHP factor shows a greater
+improvement in a relative sense. The performance of the market factor is
+driven by agricultural and energy commodities in the first period while
+metals strongly contribute to the performance improvement observed over
+the second period. Similarly, the dramatic improvement of the CHP factor
+in the second period, is driven by the metals complex, particularly that
+of the long leg where they predominantly load. Average pairwise
+correlations amongst individual factors' best performing commodities
+increase across the board over the financialisation period, far beyond
+the average for the whole cross-section of US traded commodities. The
+increase is particularly strong for the long-short factors, in a
+relative sense, on which the metal complex loads significantly more
+during financialisation. This increase is due to the dramatic rise in
+average pairwise correlation amongst the US traded metals all of which
+exhibited high \(R^{2}\) with respect to the CHP factor during
+financialisation which in turn is due to their common low level of CHP
+over this period. The CHP factor model thus seems able to establish the
+strengthening link between a non-price attribute and price dynamics in
+the US metal sub-sector during financialisation.\\
+We explore this issue further by constructing the four factors
+independently with the top eight commodities for a given factor (factor
+picks) in each period\footnote{See section Section~\ref{sec-methods} for
+  further details.} and evaluating its performance on these selected
+commodities as well as on all US traded commodities. The results of this
+exercise provide evidence of convergence of Keynesian and Working's
+theories of the term structure in detecting price co-movement during
+financialisation and strongly suggest that the term structure related
+attributes (hedging pressure/roll) co-movement and price co-movement
+link was concentrated in the metals sub-sector.
+
+\medskip
+
+The UK traded base metals provide a useful set of assets to test how
+widespread were the changes in pricing dynamics brought about by the
+onset of financialisation. To that end, we examine the performance of
+the four factors on the six UK metals, when constructed from each set of
+factor picks. The results show that there was co-movement in global
+metals returns in the second period and that this co-movement could be
+detected by our term structure related models, particularly so by our
+hedging pressure-based model.
+
+\medskip
+
+The onset of the financial crisis and the monetary policy regimes that
+followed, on the other hand, also appear to have induced significant
+changes. Commodity futures returns fell dramatically into the crisis and
+the pricing results indicate the emergence of a systematic factor across
+the entire cross-section of the US commodities as well as evidence of
+cross-market linkages with the UK traded commodity subset. The
+post-crisis results, in contrast, show a substancial pullback in
+performance for the market factor across the board as well as evidence
+of decoupling between the US and UK markets. Besides, starting in the
+crisis the Keneysian paradigm of returns begins to revert with higher
+mean returns during low (\textbf{backwardation}) relative to high
+(\textbf{contango}) \textbf{CHP} phases and this pattern continues, more
+pronounced, over the post-crisis period. As pointed out in
+\citet{basu_definancialisation}, the financial crisis and ensuing
+accommodative monetary policy therefore seem to have initiated a process
+of reversion toward pre-financialisation fundamentals in the global
+commodity futures complex.
+
+\bigskip
+\bigskip
+
+Financialisation was an issue of such policy importance that it
+triggered legislative action. The debate was initially framed around
+adequacy of speculation, the burning issue of the day, and the ensuing
+academic analysis focused on the more mechanical effects of
+financialisation.\\
+With the benefit of hindsight, it appears this approach was perhaps too
+narrow, and it now seems necessary to address the phenomenon from a
+broader perspective. Commodity price dynamics appear to have altered
+substantially in quite different ways over the financialisation and the
+financial crisis periods and our commodity futures asset pricing factors
+based approach seems able to provide new insights into the nature of
+these changes: financialisation was a phenomenon endogenous to the
+commodity markets transmitted via the commodity futures markets and
+which effects were particularly strong for the metals sector while the
+crisis and its aftermath seems to have delivered an exogenous shock
+across the entire cross-section of liquid commodities and thereby
+potentially triggering a reversion to pre-financialisation dynamics.
+
+The initial view of financialisation was that it consisted of
+speculative flows which had the effect of driving up and creating bubble
+like conditions in commodity futures prices\footnote{\citet{masters_testimony_2008};
+  \citet{masters_accidental_2008}; \citet{unctad_global_2009};
+  \citet{deschutter_food_2010}; \citet{gilbert_how_2010};
+  \citet{gilbert_speculative_2010}; \citet{herman_not_2011};
+  \citet{schumann_hunger_2011}; \citet{singleton_investor_2013}.}.
+However, the fundamental question of the nature of the impact of
+financialisation across the entire cross-section of commodity futures
+markets has not yet been completely answered. We provide an empirical
+complement to a new stream of theoretical studies that try to model the
+impact of financialisation on various aspects of commodity futures
+markets\footnote{\citet{etula_broker-dealer_2013},
+  \citet{acharya_limits_2013}, \citet{cheng_convective_2014},
+  \citet{leclercq_equilibrium_2014}, \citet{sockin_informational_2015},
+  \citet{goldstein_speculation_2014}, \citet{ekeland_speculation_2016},
+  \citet{goldstein_commodity_2022}, \citet{ekeland_hedging_2019},
+  \citet{isleimeyyeh_role_2020}.} and demonstrate that the effects of
+financialisation extend beyond the mechanical effects induced by
+indexation as outlined in \citet{tang_index_2012} and
+\citet{basak_model_2016}.
+
+\newpage
+
+\section{Data \& methods}\label{sec-data-methods}
+
+\subsection{Background}\label{sec-background}
+
+The period from 1998 to 2008 saw an influx of investment into commodity
+index linked products most of which made its way into the commodity
+futures market. Popular commodity indexes whose goal was to track the
+broad movement of commodity prices became accessible by means of swaps,
+exchange traded funds and exchange traded notes and attracted at least
+\$100 billion of net super-hoc investment over the 1998-2008 period.
+
+\medskip
+
+Concerns over the consequences of this financialisation phenomenon
+eventually led to legislative changes including the approval of Rule 76
+FR 4752 issued by the US Commodity Futures Trading Commission (CFTC) on
+January 26\textsuperscript{th}, 2011. This provision emanates from the
+Dodd-Frank Wall Street and Consumer Protection Act of 2010 (Title VII,
+Section 737) that mandates the CFTC to use position limits to restrict
+the flow of speculative capital into a number of commodity markets. The
+Rule was approved in a close 3-2 vote and the ensuing rule-making
+process was extremely contentious with several commissioners (Michael
+Dunn and Scott D. O'Malia in particular) expressing reservations about
+the lack of supporting evidence and the Rule also triggering thousands
+of comment letters as well as a lawsuit against the CFTC spearheaded by
+two Wall Street trade groups, the International Swaps \& Derivatives
+Association (ISDA) and the Securities Industries \& Financial Markets
+Association (SIFMA)\footnote{ISDA \& SIFMA v US CFTC; Complaint,
+  1:11-cv-02146; December 2\textsuperscript{nd}, 2011.}.
+
+\medskip
+
+A world-wide debate ensued about the role of index funds in commodity
+markets. The first responses to the 2007/2008 crisis of escalating food
+and energy prices took the form of policy reports, many of which
+reasoned that the growth of commodity index funds came along with an
+influx of largely speculative capital that was responsible for driving
+commodity prices beyond their historic highs
+\citep{deschutter_food_2010, gilbert_speculative_2010, herman_not_2011, schumann_hunger_2011, unctad_global_2009}.\\
+Early US Senate investigations on the matter drew on pricing and trading
+data supplied by the CFTC as well as interviews with numerous experts
+including hedge fund manager Michael Masters who linked the growing
+presence of index investors in US agricultural and energy markets to the
+observed surges in both futures and cash prices
+\citep{masters_testimony_2008, masters_accidental_2008}. This contention
+has since come to be known as the Masters' hypothesis and was largely
+endorsed by the final US Senate report on the issue
+\citep{senate_excessive_2009}.\\
+At this stage, the question thrust on the academic sphere was whether
+``excessive speculation'' (understood as the market activity peculiar to
+index type investors) was linked to escalating energy and agricultural
+commodity prices. A number of ensuing academic studies, most of which
+used commodity specific correlation and causality based analysis have
+since disproved this contention: \citet{irwin_devil_2009},
+\citet{sanders_adequacy_2010}, \citet{sanders_impact_2011},
+\citet{sanders_new_2011}, \citet{irwin_commodity_2013},
+\citet{brunetti_commodity_2014}, \citet{hamilton_effects_2015} and
+\citet{bruno_financialisation_2017} investigated the issue in the
+context of the agricultural markets; meanwhile,
+\citet{buyuksahin_speculators_2011}, \citet{tokic_speculation_2012},
+\citet{fattouh_role_2013}, \citet{kilian_role_2014},
+\citet{knittel_simple_2016} and \citet{manera_modeling_2016} examined
+the energy markets while \citet{bohl_does_2013}, \citet{kim_does_2015}
+and \citet{boyd_prevalence_2016} studied both energy and agricultural
+markets and \citet{irwin_index_2011},
+\citet{irwin_financialisation_2012} as well as
+\citet{stoll_commodity_2011} examined the commodity markets in general.
+Other studies have underlined various alterations in commodity pricing
+dynamics over the period. \citet{gilbert_role_2014} reject the view that
+financialisation has not had any effects in the grains markets and
+demonstrate that trades originated by financial market participants, and
+specifically index investors, can move prices but tend to be typically
+volatility-reducing. \citet{juvenal_speculation_2015} contend that the
+oil price increase between 2004 and 2008 was mainly driven by the
+strength of global demand but that the financialisation process of
+commodity markets also played a role. Likewise,
+\citet{henderson_new_2015} show that non-information-based financial
+investments have important impacts on commodity prices.
+\citet{cheng_financialisation_2014}, on the other hand, show that in the
+case of index commodities, financialisation has transformed the risk
+sharing, and information discovery functions of commodity futures
+markets.
+
+\subsection{Data}\label{sec-data}
+
+Commodity index swaps, commodity index funds (CIFs), commodity-based
+exchange traded funds (ETFs) and notes (ETNs) or commodity linked notes
+(CLNs) were amongst the main investment vehicles that allowed
+institutional and retail investors to build up commodity exposure in the
+early 2000s
+\citep{boons_stock_2012, henderson_new_2015, irwin_index_2011, unctad_global_2009, schumann_hunger_2011}.
+Most of these products were primarily designed to track prominent
+commodity indexes among which the S\&P-GSCI, the most popular.\\
+Most of its constituents at the time of writing form the basis of the
+broad cross-section of commodities that we consider in this study:
+corn-\#2 yellow (XCBT), oats (XCBT), soybean meal (XCBT), soybean oil
+(XCBT), soybeans (XCBT), wheat-SRW (XCBT), cattle-feeder (XCME),
+cattle-live (XCME), lean hogs (XCME), cocoa (IFUS), coffee-C (IFUS),
+cotton-\#2 (IFUS), lumber (XCME), orange juice (IFUS), sugar-\#11
+(IFUS), natural gas (XNYM), crude oil-WTI (XNYM), gasoline (XNYM),
+heating oil (XNYM), copper (XCEC), gold (XCEC), palladium (XNYM),
+platinum (XNYM) and silver (XCEC). Unleaded gasoline, the NYMEX legacy
+contract for gasoline, stopped trading in 2006 when it was replaced by
+Reformulated Gasoline Blendstock for Oxygen Blending (RBOB) with the two
+futures series trading alongside for most of the year. For our NYMEX
+gasoline data series, we consider unleaded gasoline up to September
+1\textsuperscript{st}, 2006 and RBOB gasoline thereafter, date at which
+liquidity for the latter overtook that for the former.\\
+We also consider the UK metal complex with aluminium (XLME), copper
+(XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc
+(XLME).
+
+\medskip
+
+The commodity futures trading commission (CFTC) operates a comprehensive
+system of collecting information on market participants known as the
+large trader reporting program (LTRP) where it records and reports to
+the public position data on market participants who have position levels
+in excess of a particular market specific threshold\footnote{Current
+  reporting level thresholds available at:
+  \href{https://www.ecfr.gov/cgi-bin/retrieveECFR?gp=&SID=970471b8455f4bab7db4110cfde50731&mc=true&r=SECTION&n=se17.1.15_103}{www.ecfr.gov}.}.
+The commission collects market data and position information daily from
+clearing members, futures commission merchants (FCMs) and foreign
+brokers and publishes corresponding summaries weekly in a series of
+market specific reports. In these reports, individual traders are
+categorised according to the nature of their trading activity on the
+basis of self-reported information\footnote{CFTC form 40. Available at:
+  \href{https://www.cftc.gov/sites/default/files/idc/groups/public/@forms/documents/file/cftcform40.pdf}{www.cftc.gov}.}
+that is subject to review by CFTC staff for reasonableness. Position
+information is then aggregated by category and asset type with each
+report providing an aggregation for a set of report specific categories
+and, for each category, a breakdown between futures only positions and
+positions in futures and options combined.\\
+In its legacy report, the commitment of trader report (COT) with data
+dating back to 1962, the CFTC distinguishes ``commercial'' and
+``non-commercial'' market participants where a ``commercial''
+participant is defined as one ``{[}\ldots{]} engaged in business
+activities hedged by the use of futures and option markets''\footnote{See
+  \href{https://www.gpo.gov/fdsys/pkg/CFR-1998-title17-vol1/xml/CFR-1998-title17-vol1-sec1-3.xml}{CFTC
+  regulation 1.3, 17 CFR 1.3(z)} for details.}. A third category,
+``non-reportable'', aggregates positions for participants not meeting
+the reporting threshold. In response to concerns related to category
+accuracy\footnote{See for example \citet{ederington_who_2002}.} the CFTC
+now refines its classification in the disaggregated commitment of trader
+report (DCOT) where participant categories include
+``Producer/Merchant/Processor/User'', ``Swap dealer'', ``Money manager''
+and ``Other reportable'' as well as in the supplemental commitment of
+trader report (SCOT) that details commodity index trader aggregate
+positions for thirteen agricultural commodity futures markets. Data for
+DCOT and SCOT date back to 2006 and 2007 respectively.\\
+We study the 1997/2018 period where we observe futures only position
+data from the COT report, the only CFTC report with data available for
+the whole period of interest; as well as futures term structure price
+and open interest data from Bloomberg.
+
+\subsection{Methods}\label{sec-methods}
+
+On the one hand, futures markets have a long history of serving
+commodity producers to alleviate their commodity price and output risks.
+\citet{keynes_treatise_1930} and \citet{hicks_value_1939} emphasise the
+``normal'' behaviour of naturally short hedgers outsourcing their
+commodity risk to naturally long commodity specialist speculators. This
+market configuration is referred to as ``backwardation'' where futures
+are expected to trade at a discount to spot prices, providing
+speculators with incentives to take the long side. The opposite market
+paradigm is referred to as ``contango''. Working
+\citep{working_price_1933, working_theory_1948, working_hedging_1953}
+and Kaldor \citep{kaldor_speculation_1939} somehow relax this
+``supply-of-speculative-services'' \citep{till_long_2007} approach by
+introducing processors and merchants, also commodity experts, on the
+hedgers side and relating the notions of backwardation and contango more
+directly to the term structure via the theory of storage where the shape
+of the front end of the term structure (basis) is directly related to
+the market price of storage.\\
+Financialisation, on the other hand, refers to the entry of financial
+investors into the commodity futures markets who, for the most part, are
+not commodity experts. Besides, these new market participants tend to
+exhibit herding like behaviour, often taking massive long-only positions
+on the whole cross-section of indexed commodities in an attempt to
+enhance returns while hedging against inflation and reaping further
+diversification benefits for portfolios with, in most cases, existing
+large positions across various asset classes
+\citep{brunetti_speculators_2016, boyd_prevalence_2016, cheng_convective_2014, juvenal_speculation_2015, singleton_investor_2013, tang_index_2012}.
+This contrasts with the traditional approaches of Keynes and Working and
+in this context the issues of co-movement and aggregate market
+participants behaviour seem particularly relevant.
+
+\medskip
+
+By grouping together assets by shared attribute dynamics in common
+portfolios, asset pricing techniques--and factor models in
+particular--are well suited to study co-movement
+\citep{fama_common_1993, carhart_persistence_1997, asness_devil_2013, fama_five_factor_2015, hou_digesting_2015, asness_fact_2015, frazzini_betting_2014, asness_quality_2019}.
+Careful, theory-based, attribute selection further enables a refined
+analysis of market fundamentals
+\citep{schwartz_short_2000, miffre_momentum_2007, gorton_fundamentals_2012, cortazar_commodity_2013, yang_investment_2013, daskalaki_factors_2014, szymanowska_anatomy_2014, fernandez_skewness_2018, bakshi_understanding_2019, boons_basis_2019, sakkas_factor_2020}.
+We therefore develop a futures-based asset pricing framework that
+includes factors constructed using both theoretical and liquidity
+considerations and use this framework to carry out our analysis over
+four periods of interest. The first, the pre-financialisation period,
+starts in 1997 and is naturally followed by financialisation, spanning
+the 2004/2008 period, and the financial crisis and its aftermath,
+spanning the 2008/2013 period. The last period spans the 2014/2018
+period starting with the beginning of the tapering/end of the US
+Quantitative Easing program (QE).\\
+Using the weekly price, open interest and market position data described
+above we construct market portfolios of individual commodity nearby
+futures as well as mimicking portfolios for market, commercial hedging
+pressure, term structure and liquidity risk factors in returns. While
+our market portfolios are long only, equally weighted portfolios of
+particular commodity sets, our other mimicking portfolios for risk
+factors are constructed as combinations of two sub-portfolios (legs),
+one held long, one held short, which respective constituents are pooled
+on a weekly basis according to risk factor specific criteria.\\
+For each leg, the position weight for a particular asset for a
+particular period is contingent on the value of the corresponding
+sorting variable and its rank relative to the other assets in the pool.
+The sorting variable values for the asset pool are first rescaled so
+that the highest (lowest) value becomes 1 (0). Weights are then
+determined pairwise, starting from the extremes with the highest and
+lowest figures. A coefficient \(\alpha\) is determined by dividing their
+difference (1 in this case) by the mean of the rescaled values. The high
+figure is attributed a score of \(\frac{1}{n} \times \alpha\) where
+\(n\) is the number of assets in the pool while the score for the low
+figure is \(\frac{1/n}{\alpha}\). The operation is repeated for the pair
+of assets showing the second highest and second lowest values for the
+sorting variable and so on until all the assets in the pool are
+attributed a score. The individual asset weights are then determined by
+dividing each score by the sum of the scores.\\
+The period return for a particular mimicking portfolio is calculated as
+the difference between the weighted average return for constituents of
+the long portfolio and that for the constituents of the short portfolio.
+i.e, return on the mimicking portfolio for risk factor \(i\) (\(f_{i}\))
+for period \(t\):
 
 \[r_{t}^{f_{i}}=\sum_{j=1}^{x}w^{long}_{j,t} \times r_{j,t}-\sum_{j=n-x}^{n}w^{short}_{j,t} \times r_{j,t}\]
-\(n\equiv\) number of commodities in the set considered for mimicking portfolio construction.\\
+\(n\equiv\) number of commodities in the set considered for mimicking
+portfolio construction.\\
 \(x = n \cdot s\).\\
 \(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
-\(w^{*}_{j,t}\equiv\) period \(t\) weight for commodity \(j\) on the long or short leg.\\
-\(r_{j,t}\equiv\) period \(t\) front contract return for commodity \(j\).\\
+\(w^{*}_{j,t}\equiv\) period \(t\) weight for commodity \(j\) on the
+long or short leg.\\
+\(r_{j,t}\equiv\) period \(t\) front contract return for commodity
+\(j\).\\
 \(j\equiv\) commodity rank in the ordered set \(Y_{t}^{f_{i}}\).\\
-\(Y_{t}^{f_{i}}\equiv\) period \(t\) ordered set of the commodities considered for mimicking portfolio construction where the ordering rule is specific to \(f_{i}\).
-
-\medskip\setlength{\parindent}{0pt}
-
-For our portfolio CHP (commercial hedging pressure), we sort the set of commodities considered on past twenty-six-week average CHP from lowest to highest.
-The bottom third constituents (lowest \(\overline{CHP}\)s) of the corresponding ordered set form the long leg of the portfolio while the top third form the short leg:
+\(Y_{t}^{f_{i}}\equiv\) period \(t\) ordered set of the commodities
+considered for mimicking portfolio construction where the ordering rule
+is specific to \(f_{i}\).
+
+\medskip
+
+For our portfolio CHP (commercial hedging pressure), we sort the set of
+commodities considered on past twenty-six-week average CHP from lowest
+to highest. The bottom third constituents (lowest \(\overline{CHP}\)s)
+of the corresponding ordered set form the long leg of the portfolio
+while the top third form the short leg:
 
@@
 \(\overline{{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{{OI}_{j,t-k}}{{OI}_{j,t-k-1}} - 1)\)\\
-\(OI_{j,t}\equiv\) open interest at close of period \(t\) on the front (nearby) contract for commodity \(j\).
-
-\medskip\setlength{\parindent}{0pt}
-
-We use a time series regression approach where we start with regressions of the US traded individual commodity weekly front contract returns on returns to the mimicking portfolio for a particular risk factor where the portfolio is constructed using the whole cross-section of US traded commodities.
-The corresponding \(R^{2}\)s are averaged and the process is repeated for each of our four risk factors (market, hedging pressure, term structure and liquidity) and periods (1997/2003, 2004/2008, 2008/2013 and 2014/2018).
-For the long-short factors the results are reported independently for models where the regressor is the factor itself or one of its legs (long vs.~short).
-The same operation is repeated for the two (\(p=2\)) and three (\(p=3\)) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectively, as well as for the four (\(p=4\)) factor model case where all the risk factor mimicking portfolios are included.
-Results are reported for the one-factor model case with the other results available on the \href{http://18.135.131.217:3838/financialization-asset-pricing/}{online results dashboard}.
-
-\medskip\setlength{\parindent}{0pt}
-
-For each period we also implement the analysis described above over periods of low and high aggregate CHP (\textbf{CHP}), a notion that we believe is particularly relevant in the context of financialisation where issues of co-movement and aggregate market behaviour play a central role.
-We define \textbf{CHP} as the cross-sectional average of CHPs for a particular pool of assets.
-i.e., period \(t\) \textbf{CHP} for asset pool \(x\):
-
-\[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}\]
-\(n\equiv\) number of commodities in set \(x\).\\
-\(CHP_{i,t}\equiv\) period \(t\) CHP for commodity \(i\) as defined above.
-
-\medskip\setlength{\parindent}{0pt}
-
-We further define aggregate backwardation (\textbf{backwardation}) and contango (\textbf{contango}) \textbf{CHP} regimes as, for a given period, \textbf{CHP} levels below and above the period's median respectively and, in contrast with (Hong and Yogo, 2012) who aggregate across sub-sectors, the asset pool we consider for \textbf{CHP} construction include the whole cross-section of US traded commodities.
-
-\medskip\setlength{\parindent}{0pt}
-
-In the next part of the analysis, our mimicking portfolios for risk factors, constructed from the set of all US traded commodities are used as commodity picking devices on the latter commodity set.
-For each risk factor and period, individual US traded commodity front returns are regressed on returns for the corresponding mimicking portfolio.
-Individual commodities are sorted by \(R^{2}\) accordingly from highest to lowest and the top third (highest \(R^{2}\)s) are selected as commodity picks for the risk factor for the period.
-i.e, set of picks \(P_{t}^{f_{i}}\) for risk factor \(i\) (\(f_{i}\)) over period \(t\):
+\(OI_{j,t}\equiv\) open interest at close of period \(t\) on the front
+(nearby) contract for commodity \(j\).
+
+\medskip
+
+We use a time series regression approach where we start with regressions
+of the US traded individual commodity weekly front contract returns on
+returns to the mimicking portfolio for a particular risk factor where
+the portfolio is constructed using the whole cross-section of US traded
+commodities. The corresponding \(R^{2}\)s are averaged and the process
+is repeated for each of our four risk factors (market, hedging pressure,
+term structure and liquidity) and periods (1997/2003, 2004/2008,
+2008/2013 and 2014/2018). For the long-short factors the results are
+reported independently for models where the regressor is the factor
+itself or one of its legs (long vs.~short). The same operation is
+repeated for the two (\(p=2\)) and three (\(p=3\)) factor model cases,
+where regressors include in turn all combinations of any two and three
+risk factors respectively, as well as for the four (\(p=4\)) factor
+model case where all the risk factor mimicking portfolios are included.
+Results are reported for the one-factor model case with the other
+results available upon request.
+
+\medskip
+
+For each period we also implement the analysis described above over
+periods of low and high aggregate CHP (\textbf{CHP}), a notion that we
+believe is particularly relevant in the context of financialisation
+where issues of co-movement and aggregate market behaviour play a
+central role. We define \textbf{CHP} as the cross-sectional average of
+individual CHPs for a particular pool of assets. i.e., period \(t\)
+\textbf{CHP} for asset pool \(x\):
+
+\[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}\] \(n\equiv\)
+number of commodities in set \(x\).\\
+\(CHP_{i,t}\equiv\) period \(t\) CHP for commodity \(i\) as defined
+above.
+
+\medskip
+
+We further define aggregate backwardation (\textbf{backwardation}) and
+contango (\textbf{contango}) \textbf{CHP} regimes as, for a given
+period, \textbf{CHP} levels below and above the period's median
+respectively and, in contrast with \citep{hong_what_2012} who aggregate
+across sub-sectors, the asset pool we consider for \textbf{CHP}
+construction include the whole cross-section of US traded commodities.
+
+\medskip
+
+In the next part of the analysis, our mimicking portfolios for risk
+factors, constructed from the set of all US traded commodities are used
+as commodity picking devices on the latter commodity set. For each risk
+factor and period, individual US traded commodity front returns are
+regressed on returns for the corresponding mimicking portfolio.
+Individual commodities are sorted by \(R^{2}\) accordingly from highest
+to lowest and the top third (highest \(R^{2}\)s) are selected as
+commodity picks for the risk factor for the period. i.e, set of picks
+\(P_{t}^{f_{i}}\) for risk factor \(i\) (\(f_{i}\)) over period \(t\):
 
@@
 \(x = n \cdot s\).\\
-\(n\equiv\) number of commodities in the set considered for the picking exercise (twenty-four here).\\
+\(n\equiv\) number of commodities in the set considered for the picking
+exercise (twenty-four here).\\
 \(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
-\(P_{j}\equiv\) commodity pick \(j\) for risk factor \(f_{i}\) over period \(t\)\\
+\(P_{j}\equiv\) commodity pick \(j\) for risk factor \(f_{i}\) over
+period \(t\)\\
 \(j\equiv\) rank in the ordered set \(Y_{t}^{f_{i}}\)\\
 \[Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}\]
-\(n\equiv\) number of commodities in the set considered for picking (twenty-four here).\\
-\(\tilde{R_{j}^{2}}\equiv\) risk factor \(f_{i}\) returns' explanatory power on commodity \(j\) nearby futures returns over period \(t\) as defined above.
-
-\medskip\setlength{\parindent}{0pt}
-
-For each period we report the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every set of picks.
-
-\medskip\setlength{\parindent}{0pt}
-
-In the last part of the analysis, for each period our mimicking portfolios for risk factors in returns are constructed using each set of commodity picks independently as the asset pool for portfolio construction.
-A similar time series approach to that described above is then implemented using these newly formed mimicking portfolios.
-In this case, a first set of dependent variables includes the sets of commodity picks themselves, a second set includes the whole cross-section of US traded commodities while a third set includes the six UK traded metals considered in the study.
+\(n\equiv\) number of commodities in the set considered for picking
+(twenty-four here).\\
+\(\tilde{R_{j}^{2}}\equiv\) risk factor \(f_{i}\) returns' explanatory
+power on commodity \(j\) nearby futures returns over period \(t\) as
+defined above.
+
+\medskip
+
+For each period we report the proportion of time each pick is held in
+the long and (/or) short leg of the corresponding risk factor mimicking
+portfolio as well as the average pairwise correlation amongst every set
+of picks.
+
+\medskip
+
+In the last part of the analysis, for each period our mimicking
+portfolios for risk factors in returns are constructed using each set of
+commodity picks independently as the asset pool for portfolio
+construction. A similar time series approach to that described above is
+then implemented using these newly formed mimicking portfolios. In this
+case, a first set of dependent variables includes the sets of commodity
+picks themselves, a second set includes the whole cross-section of US
+traded commodities while a third set includes the six UK traded metals
+considered in the study.
+
+\bigskip
+\bigskip
+
+By relating returns on attribute based risk factor mimicking portfolios
+to returns on individual as well as group of assets, our time series
+approach therefore draws the link between attribute and pricing dynamics
+over different, theory-based market regimes, and thereby enables us to
+study market fundamentals and co-movement simultaneously, two key issues
+in the financialisation phenomenon.
 
@@
 
-\hypertarget{co-movement-results}{%
-\section{Results \& discussion}\label{co-movement-results}}
-
-The descriptive statistics for the commodity series considered in the study displayed in table \ref{tab:co-movement-stats-no-regimes} show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9\% significant at the 5\% level vs.~6.9\% with a 10\% significance in the pre-financialisation period.
-The increase is even more pronounced for an equally weighted portfolio of UK traded assets (metals), 2.47\% (not significant) to 21.8\% (significant at the 10\% level), which sets out the global nature of the phenomenon.
-Most commodities show a higher mean return while five--Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)--show a lower figure with five significant figures--Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)--against none pre-financialisation.
-Sugar-\#11 wins the race with a mean return increasing from -4.6\% to 24.9\% followed by copper with sizeable increases for both markets: 1.5\% to 28.2\% (XCEC) and 0.5\% to 28.6\% (XLME).\\
-The pattern of results for volatilities is similar although the increase is less pronounced.
-Both equally weighted portfolios shows an increase, more pronounced for the UK assets, 10\% to 13.6\% (US) vs.~15.7\% to 26.9\% (UK), while out of the thirty assets, eleven show a drop in volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C (IFUS), Lumber (XCME), Sugar-\#11 (IFUS), Natural gas (XNYM), Crude oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
-Financialisation seems however to have impacted the commodity complex beyond these mechanical effects of increased long participation ensuing from the entry on index type investments as our results suggest next.
-
-\medskip\setlength{\parindent}{0pt}
-
-The cross-sectional nature of financialisation naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure.
-The traditional Keynesian hedging pressure paradigm postulates a negative relationship between the return on an individual commodity futures and its hedging pressure.
-The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where \textbf{CHP} is low and vice et versa.
-In table \ref{tab:co-movement-stats-regimes} the mean returns are shown over high (\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP} regimes for each time period.\\
-Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of \textbf{backwardation} as compared to \textbf{contango}, with the difference being statistically significant at the 10\% level for two commodities, at the 5\% level for one and at the 1\% level for another.
-For the remaining six commodities the higher mean return during \textbf{contango} is not statistically significant for any of them.
-For the six UK commodities, all metals, five of them had higher mean returns during phases of \textbf{backwardation} as compared to \textbf{contango} in the first period, with one of these differences being statistically significant at the 10\% level while for the remaining asset (Zinc) the higher mean return during \textbf{contango} is not statistically significant.
-An equally weighted portfolio of the twenty-four US commodities had a mean return of 15.4\% during \textbf{backwardation} phases, statistically significant at the 1\% level, and a mean return of -1.1\% during \textbf{contango}, both in the first period, with the difference between them statistically significant at the 5\% level.
-The corresponding figures for an equally weighted portfolio of the UK metals were 4.4\% and 0.3\% respectively.
-These results provide broad support for an aggregate version of the Keynesian hedging pressure hypothesis and suggest that hedgers in the aggregate were engaged in risk transfer during this period.\\
-Over the second period the pattern essentially reverses.
-For the twenty-four US commodities over this period, fourteen have higher mean returns during phases of \textbf{contango} over \textbf{backwardation}.
-Four of the six UK metals achieved higher mean returns over \textbf{contango} relative to \textbf{backwardation} phases with the difference being statistically significant for one commodity.
-The equally weighted US portfolio had a mean return of 15.7\% over \textbf{backwardation} against 16.2\% during phases of \textbf{contango}, both statistically significant at the 10\% level.
-The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 8\% during \textbf{backwardation} rising to 35.6\% during \textbf{contango}.
-
-\medskip\setlength{\parindent}{0pt}
-
-The onset of financialisation thus seems to have engendered a change in the nature of hedger's behaviour, at the aggregate level in particular, taking it away from the traditional Keynesian view of risk shifting.
-This phenomenon has been noted in earlier theoretical and empirical work (Danthine, 1978; Stout, 1998) in different contexts from which two competing models of behaviour have emerged.\\
-The information arbitrage model (Danthine, 1978; Grossman and Stiglitz, 1980; Kyle, 1989) implies that hedgers may often be seeking out counterparties to trade with rather than being purely passive.
-This issue is also raised in both Cheng and Xiong (2014) and Stulz (1996) who point out that hedgers may be taking a view on prices just as speculators do.
-In fact, by hedging away some of their risk, hedgers are able to speculate more heavily based on their disagreement against speculators regarding futures price movement (Simsek, 2013), which fits into a heterogeneous expectation theory of speculation\footnote{Hirshleifer (1975); Hirshleifer (1976); Hirshleifer (1977)}.
-As Stout (1998) points out, this disagreement-based theory of trading is one of the main reason the public and the law disapproves speculation as this form of trading is regarded as non-productive\footnote{Duffie (2014) also discusses some of the challenges faced by a policy treatment of speculative trading motivated by differences in beliefs.}.\\
-In the second model hedgers are seen as liquidity providers as in Kang et al.
-(2020) with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
-Table \ref{tab:co-movement-time-reg-US-CHP} supports this view.
-We regress commodity futures front returns on individual commercial hedging pressure (CHP) as well as aggregate CHP (\textbf{CHP}), our market wide measure of CHP, in separate models and find that the explanatory power of CHP at the individual commodity level decreases over the financialisation period with the US cross-sectional average \(R^{2}\) falling down to 20.8\% from 25.8\% in the previous period while that of \textbf{CHP} increases (7.1\% vs 5.4\%).
-Financialisation therefore seems to have had the effect of loosening the extent to which futures risk premiums relate to commodity specific commercial hedging motives while strengthening that to which they relate to broader dynamics such as cross-sectional liquidity provision.
-The pattern is strongest for the metals sector where the average \(R^{2}\) drops down to 19.1\% from 28.1\% between the two periods at the individual level while it rises from 8.4\% to 15.7\% at the aggregate level.
-The symmetry breaks in the crisis period, with the US cross-sectional average \(R^{2}\) at the individual level bouncing back up (22.5\% vs 20.8\%) while that at the aggregate level rises further (14.7\% vs 7.1\%), before eventually resuming post-crisis with a further rise at the individual level (27.2\% vs 22.5\%) and a drop at the aggregate level (7.5\% vs 14.7\%) suggesting a return to legacy commodity specific dynamics.
-
-\bigskip\bigskip\setlength{\parindent}{0pt}
-
-Using our bespoke commodity-based asset pricing framework we strive to shed new light on the phenomenon by first regressing returns series for the twenty four individual US commodities against our factor mimicking portfolios independently.
-The resulting individual explanatory powers (\(R^2\)s), once averaged by factor and period, offer a refined perspective on the relation between return and factor attribute co-movement.
-A low figure indicates low cross-sectional return co-movement for, in this context, return on the corresponding factor mimicking portfolio only has explanatory power on return for commodities that are constituents of one of its legs over the corresponding period.
-The explanatory power for the other commodities is typically low or even 0 for the case where commodities are perfectly uncorrelated with one-another.
-A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities, which suggests that pairwise correlation relate to factor attribute.\\
-The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table \ref{tab:co-movement-time-reg-US-facts-US}.
-Over the first period the market factor has the best average time series performance with the highest average \(R^{2}\) with all three futures market factors performing poorly, indicating that the commodities with extreme factor attributes (high or low CHP for example) are uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of high and low \textbf{CHP} (below period median).
-The two factor models average \(R^{2}\)s (results available on the \href{http://18.135.131.217:3838/financialization-asset-pricing/}{online results dashboard}) are roughly the sum of the one factor \(R^{2}\)s indicating that the factors are almost orthogonal over this period.\\
-The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average \(R^{2}\) increasing to 8.2\% in the second period relative to 1.7\% in the first with this improvement coming from the long leg that shows a greater improvement (4.5\% to 15.1\%) relative to the short (3\% to 4\%), suggesting that ``normally'' backwardated commodities (Keynesian perspective) have higher correlation with the rest of the commodity cross-section, and thereby bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period.
-The performance of the market factor also improves though not by as much in a relative sense (21.6\% from 11.7\%) and both the term structure factor and the open interest growth factor show a much smaller improvement in performance with smaller differences between legs.
-Over all periods, all of our factor models show similar performance across regimes of high and low \textbf{CHP}.
-
-\medskip\setlength{\parindent}{0pt}
-
-We next investigate the top eight of the US traded commodities which achieved the highest time series \(R^{2}\) for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table \ref{tab:co-movement-picks}.\\
-For the CHP factor the commodities that achieve high \(R^{2}\) in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor.
-The same applies to the open interest and term structure factors with CHP replaced by open interest growth and roll yield respectively; while for the market factor the picks are those that co-vary most strongly with the market factor over that period.\\
-For the CHP factor, we observe a change in the picks between the first and the second period; the picks in the first period included five agricultural commodities and three metals while in the second period they include all the five base and precious metals and only three agricultural commodities.
-This pattern is also visible for the term structure factor for which there are four metals (copper, silver, gold and platinum) picks in the second period against two in the first (palladium and platinum) as well as for the open interest nearby growth factor for which there are three metals (silver, gold and platinum) picks in the second period against one in the first (platinum).
-The market factor has three metal picks in the second period (palladium, gold and silver) while all the picks in the first period were agricultural or energy commodities.\\
-Over the third period, the average CHP factor shows the same metal picks with the agriculturals replaced by energy commodity; the open interest nearby growth factor still has three metal picks with gold swapped for copper and both the market and term structure factors have one, copper.\\
-The table also shows the proportion of time that these picks were constituents of the corresponding factor.
-All the picks of the long-short factors (average CHP, open interest nearby growth and term structure factors) were constituents of the corresponding factor for some proportion of time in all of the time periods.
-In this respect, there is a contrast between the first and second periods with the average CHP and open interest nearby growth factor picks appearing predominantly on the long side of the corresponding factor in the second period, as opposed to both legs in the first.
-The pattern is particularly strong for the metals and energy commodities respectively, with the exception of copper for the average CHP factor that lives in the short leg a higher proportion of the time over the financialisation period.
-The pattern is reversed for the term structure factor where the picks appear predominantly on the short leg in the second period, as opposed to both legs in the first with the pattern again strongest for the metals.
-This behaviour continues over the third period for the average CHP and open interest nearby growth factors and indicates that their picks consistently exhibited low commercial hedging pressure and high front contract open interest growth respectively while indicating that the term structure factor picks showed low roll yield in the first and second period.
-
-\medskip\setlength{\parindent}{0pt}
-
-In table \ref{tab:co-movement-correlations}, we show the average pairwise returns correlation between each set of picks in each time period.
-Following on form the earlier observations, this exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.\\
-In the first period the average picks pairwise correlation for the long-short factors ranges from 7.1\% (term structure factor picks) to 12.4\% (open interest factor picks) while the market factor picks show the highest figure (23.7\%).
-In the second period the figures for the long-short factors rise sharply; up to 22.9\% from 8.1\% for the average CHP factor picks, up to 32.4\% from 12.4\% for the open interest factor picks and up to 23.4\% from 7.1\% for the term structure factor picks.
-This increase is stronger than that for the market factor picks in a relative sense and is a consequence of the dramatic increase in average pairwise price correlation amongst the US traded metals which dominate the average CHP factor set of picks and which presence is stronger amongst both the open interest and term structure factor sets of picks over the financialisation period.
-The higher figures for the open interest factor are driven by the strong presence of the energy complex amongst the corresponding picks.
-The latter exhibits much higher average pairwise correlations than the other sectors in both periods although lower in the second relative to the first which reinforces the role played by the metals in the sharp increase in average pairwise correlation amongst picks for this factor.\\
-With regards to \textbf{CHP} regimes, although not very pronounced, a pattern is noticeable.
-For the market, open interest and term structure factor picks, average pairwise correlations are stronger over phases of \textbf{contango} in the first period and over phases of \textbf{backwardation} in the financialisation period, eventually reverting back to being stronger over \textbf{contango} phases in the crisis period with the CHP factor sets of picks showing the opposite pattern.
-Overall, these results suggest an increase in correlation between non-price attributes co-movement and price co-movement over the financialisation period.
-It is also interesting to note that US traded metals returns were negatively correlated with the rest of US traded commodities in the first period and positively in the second.
-
-\medskip\setlength{\parindent}{0pt}
-
-To further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their explanatory performance on these sets of picks over the four periods independently.
-The results are shown in table \ref{tab:co-movement-time-reg-picks-facts-picks}.
-The long-short factors for a particular attribute select the top and bottom two of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks.
-In the absence of price co-movement between the picks, the market factor will achieve an average \(R^{2}\) of around 12.5\%\footnote{Market factor lemma: \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\) size of market portfolio (eight here).}, while there is no non-zero \(R^{2}\) lower bound for the corresponding long-short factors.\\
-A high average \(R^{2}\) for the market factor is indicative of strong price co-movement.
-In this respect, the most remarkable change in performance in a relative sense is that of the market factor built from the CHP factor sets of picks with the average \(R^{2}\) more than doubling, from 18.6\% up to 38.1\%.
-For the long-short factors on the other hand it is indicative of simultaneous attribute and price co-movement.
-For the factors built from the market factor picks the increase is strongest in a relative sense for the CHP factor with the \(R^{2}\) more than doubling, going from 5.6\% in the first period up to 12.4\% in the second with the increase stronger for the long leg (17.1\% vs.~27.9\%) relative to the short (16.5\% vs.~21.4\%).
-In the case of the factors built from the CHP factor picks, the CHP factor built with its own picks shows a remarkable increase in a relative sense with the \(R^{2}\) tripling, from 7.2\% to 21.4\% and the long leg showing a much greater increase relative to the short (10.4\% to 31.1\% vs.~8.3\% to 9.8\%).
-The performance of the term structure factor built from the CHP factor sets of picks also shows a sizable increase in a relative sense, from 3.5\% to 5.3\% and even more remarkable in this case is the substantial increase in performance of the short leg, from 6.3\% to 15.7\% relative to the long (7.5\% to 9.8\%).
-The pattern is reversed for the CHP factor built from the term structure factor picks where the average \(R^{2}\) increases from 4.7\% to 8\% with the performance of the long leg increasing from 11.9\% to 28.1\% vs.~5.5\% to 9.1\% for the short.
-The performance of the term structure factor constructed from its own sets of picks also shows a substantial increase, from 5.1\% to 8.4\% with, here again the increase in performance relatively stronger for the short leg, from 6\% to 16.1\% vs.~7.6\% to 12.1\% for the long.\\
-Taken together with the previous results showing that the metal complex predominantly loads on the long and short legs of the original CHP and term structure factors respectively, these results provide evidence of convergence of Keynesian and Working's theories of the term structure in detecting price co-movement during financialisation perhaps as a result of spillover effects between the corresponding futures and spot markets as suggested in Basak and Pavlova (2016).
-
-\medskip\setlength{\parindent}{0pt}
-
-In table \ref{tab:co-movement-time-reg-US-facts-picks} we assess the performance of the same factors on all the commodities instead of just the picks.
-While the average \(R^{2}\)s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table \ref{tab:co-movement-time-reg-picks-facts-picks}.
-In contrast, the average CHP factor built with average CHP factor picks shows a smaller absolute increase in average \(R^{2}\) indicating that the link between CHP co-movement and price co-movement is stronger amongst the picks which are predominantly metals.
-Taken together, the results in tables \ref{tab:co-movement-time-reg-picks-facts-picks} and \ref{tab:co-movement-time-reg-US-facts-picks} suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.\\
-To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in table \ref{tab:co-movement-time-reg-UK-facts-picks}.
-In the first period, although all sets of picks, except that of the market factor, included at least one metal, the average \(R^{2}\)s are very low; close to zero in most cases.
-These figures drastically increase across the board in the financialisation period and show a pattern similar to that observed in the US complex.
-The market factor built from the CHP and term structure factor sets of picks shows the sharpest increase in performance, relative to using the other sets of factor picks; rising to 20.1\% from 1.5\% and to 15\% from 0.8\% respectively.
-The increase in \(R^{2}\) for the market factor built with market factor picks is more modest, providing further evidence of concentration of co-movement in the metals sector during financialisation.\\
-Here again the change in performance for the CHP and term structure factor legs stands out where the factors are built with their own as well as each other's sets of picks.
-The average \(R^{2}\) for the long leg of the CHP factor built with its own sets of picks increases from 1\% to 11\% while the short leg shows no significant change.
-The opposite holds for the term structure factor built from its own set of picks with the short leg performance increasing from 0.1\% to 14\% while that of the long leg remains below 1\%.
-Building these factors from each other's sets of picks produces a similar pattern with the performance of the long leg of the CHP factor built from the term structure factor picks increasing from 0.7\% to 11.4\%; a much greater increase relative to the short leg although in this case the latter also shows a sizable increase in performance (0.3\% to 6\%).
-The performance of the short leg of the term structure factor built from the CHP factor sets of picks on the other hand increases from 0.3\% to 19.2\% while the performance for the long leg in the second period remains below 1.5\%.\\
-Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working's term structure paradigms.
-There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of Kang et al.
-(2020) who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
-
-\bigskip\bigskip\setlength{\parindent}{0pt}
-
-The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results.
-Returns fall sharply relative to the financialisation period (table \ref{tab:co-movement-stats-no-regimes}) with eighteen US commodities along with all six UK traded metals showing lower mean returns.
-Returns for equally weighted portfolios of both sets of assets fall down to 9.4\% and 5.3\% from 15.9\% and 21.8\% respectively.
-Returns are mostly higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:co-movement-stats-regimes}) with fifteen US assets and five of the UK traded metals showing higher mean returns in \textbf{backwardation} and the pattern extending to equally weighted portfolios of the two sets of assets.
-Volatility is moderately higher for both sets with fifteen US commodities and three UK metals showing higher figures and interestingly eminently higher over phases of \textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none of the UK traded metals show higher volatility figures over \textbf{backwardation} phases.
-The symmetry between the dynamics of CHP and \textbf{CHP}'s explanatory power on individual commodity returns breaks in the crisis period with both now seemingly converging; the US cross-sectional average \(R^{2}\) at the individual level bouncing back up (22.5\% vs 20.8\%) while that at the aggregate level rises further (14.7\% vs 7.1\%).\\
-The performance of the market factor dominates the US commodity complex over the period with a 50\% increase in mean average \(R^{2}\) to over 30\% (table \ref{tab:co-movement-time-reg-US-facts-US}) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
-The average pairwise correlation amongst the market factor picks increases beyond 50\% while there is a leveling in that amongst the picks of the long-short factors as shown in table \ref{tab:co-movement-correlations}.
-Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table \ref{tab:co-movement-time-reg-US-facts-picks}).\\
-Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
-Table \ref{tab:co-movement-time-reg-UK-facts-picks} provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average \(R^{2}\) increasing to 31.7\% from 10.2\% in the previous period.
-
-\medskip\setlength{\parindent}{0pt}
-
-The returns pullback continues into the post-crisis period (table \ref{tab:co-movement-stats-no-regimes}) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2\% and 2.7\% respectively.
-Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
-The figures for the equally weighted portfolios of US and UK assets drop to 9.9\% and 16.2\% respectively, very close to pre-financialisation levels.\\
-The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (table \ref{tab:co-movement-stats-regimes}) with mean returns higher during phases of \textbf{backwardation} relative to \textbf{contango} (table \ref{tab:co-movement-stats-regimes}), more so than over the crisis period with seventeen US commodities showing higher mean returns over \textbf{backwardation} phases.
-The difference is significant at the 5\% level for Lumber (XCME) and at the 10\% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of \textbf{contango}.
-The pattern is more pronounced for the UK traded subset with all six assets showing higher mean returns in \textbf{backwardation} with the difference significant at the 1\% level for Nickel-primary (XLME), 5\% level for Aluminium (XLME) and 10\% level for Zinc (XLME).
-It also extends to equally weighted portfolios of US and UK traded assets that both show higher mean returns during \textbf{backwardation} with the difference significant at the 5\% level for the UK portfolio and the figure close to the 10\% level significance threshold for the portfolio of US assets.
-Volatilities are overall higher in \textbf{contango} although less so than over the previous period with seventeen US commodities showing higher figures over \textbf{contango} against twenty-three in the crisis period.
-The pattern extends to three of the six UK traded metals with the difference significant at the 1\% level for Copper (XLME) and Tin (XLME) and at the 5\% level for Zinc (XLME) while differences are not significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit higher volatility over \textbf{backwardation} phases.
-Equally weighted portfolios of US and UK traded assets on the other hand both show higher volatility in \textbf{contango} with the difference significant at the 1\% level for both.
-Over the financialisation period in contrast volatilities were predominantly higher in \textbf{backwardation} for US traded assets with fourteen commodities showing higher volatility figures in these phases; the post-crisis pattern of results for volatilities thus likewise shows signs of reversion to pre-financialisation standards.
-After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and \textbf{CHP} part ways (table \ref{tab:co-movement-time-reg-US-CHP}), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
-The recovery initiated in the crisis period for that of CHP is confirmed with a stronger increase in the post-crisis period, 27.2\% vs.~22.5\%, strongest for the metals sector, 37.3\% vs.~23.7\%, while the energy sector shows the opposite pattern: 11\% vs.~16\%.
-In contrast, after increasing stronger in the crisis, that for \textbf{CHP} falls overall in the post-crisis period, 7.5\% vs 14.7\%, with the decrease strongest for the energy sector in a relative sense: 2.5\% vs.~14.8\%.\\
-Average pairwise correlations amongst factor picks (table \ref{tab:co-movement-correlations}) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1\% to 26.1\%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
-The performance of the market factor on the US complex declines below financialisation levels (table \ref{tab:co-movement-time-reg-US-facts-US}) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table \ref{tab:co-movement-time-reg-US-facts-picks}) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors.
-Table \ref{tab:co-movement-time-reg-UK-facts-picks} provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
-
-\medskip\setlength{\parindent}{0pt}
-
-Taken together the patterns of results over the crisis and post-crisis periods echo those in Basu and Bauthéac (2021) in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex.
+\section{Results \& discussion}\label{sec-results}
+
+The descriptive statistics for the commodity series considered in the
+study displayed in table Table~\ref{tbl-stats-no-regimes} show a clear
+pattern of increase in average return during financialisation with an
+equally weighted portfolio of the US traded assets showing a mean
+returns of 15.9\% significant at the 5\% level vs.~6.9\% with a 10\%
+significance in the pre-financialisation period. The increase is even
+more pronounced for an equally weighted portfolio of UK traded assets
+(metals), 2.47\% (not significant) to 21.8\% (significant at the 10\%
+level), which sets out the global nature of the phenomenon. Most
+commodities show a higher mean return while five--Lumber (XCME), Natural
+gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary
+(XLME)--show a lower figure with five significant figures--Crude oil-WTI
+(XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined
+(XLME)--against none pre-financialisation. Sugar-\#11 wins the race with
+a mean return increasing from -4.6\% to 24.9\% followed by copper with
+sizeable increases for both markets: 1.5\% to 28.2\% (XCEC) and 0.5\% to
+28.6\% (XLME).\\
+The pattern of results for volatilities is similar although the increase
+is less pronounced. Both equally weighted portfolios shows an increase,
+more pronounced for the UK assets, 10\% to 13.6\% (US) vs.~15.7\% to
+26.9\% (UK), while out of the thirty assets, eleven show a drop in
+volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C
+(IFUS), Lumber (XCME), Sugar-\#11 (IFUS), Natural gas (XNYM), Crude
+oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
+Financialisation seems however to have impacted the commodity complex
+beyond these mechanical effects of increased long participation ensuing
+from the entry on index type investments as our results suggest next.
+
+\medskip
+
+The cross-sectional nature of financialisation naturally leads us to
+extend the individual hedging pressure paradigm by incorporating
+aggregate CHP (\textbf{CHP}), a market wide measure of hedging pressure.
+The traditional Keynesian hedging pressure paradigm postulates a
+negative relationship between the return on an individual commodity
+futures and its hedging pressure. The extended Keynesian hedging
+pressure paradigm, in the context of financialisation, should also imply
+that returns for individual commodities should be high in periods where
+\textbf{CHP} is low and vice et versa. In table
+Table~\ref{tbl-stats-regimes} the mean returns are shown over high
+(\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP}
+regimes for each time period.\\
+Over the first period eighteen of the twenty-four US commodities have
+higher mean returns during periods of \textbf{backwardation} as compared
+to \textbf{contango}, with the difference being statistically
+significant at the 10\% level for two commodities, at the 5\% level for
+one and at the 1\% level for another. For the remaining six commodities
+the higher mean return during \textbf{contango} is not statistically
+significant for any of them. For the six UK commodities, all metals,
+five of them had higher mean returns during phases of
+\textbf{backwardation} as compared to \textbf{contango} in the first
+period, with one of these differences being statistically significant at
+the 10\% level while for the remaining asset (Zinc) the higher mean
+return during \textbf{contango} is not statistically significant. An
+equally weighted portfolio of the twenty-four US commodities had a mean
+return of 15.4\% during \textbf{backwardation} phases, statistically
+significant at the 1\% level, and a mean return of -1.1\% during
+\textbf{contango}, both in the first period, with the difference between
+them statistically significant at the 5\% level. The corresponding
+figures for an equally weighted portfolio of the UK metals were 4.4\%
+and 0.3\% respectively. These results provide broad support for an
+aggregate version of the Keynesian hedging pressure hypothesis and
+suggest that hedgers in the aggregate were engaged in risk transfer
+during this period.\\
+Over the second period the pattern essentially reverses. For the
+twenty-four US commodities over this period, fourteen have higher mean
+returns during phases of \textbf{contango} over \textbf{backwardation}.
+Four of the six UK metals achieved higher mean returns over
+\textbf{contango} relative to \textbf{backwardation} phases with the
+difference being statistically significant for one commodity. The
+equally weighted US portfolio had a mean return of 15.7\% over
+\textbf{backwardation} against 16.2\% during phases of
+\textbf{contango}, both statistically significant at the 10\% level. The
+difference was considerably more pronounced for the equally weighted UK
+metals portfolio with a mean return of 8\% during \textbf{backwardation}
+rising to 35.6\% during \textbf{contango}.
+
+\medskip
+
+The onset of financialisation thus seems to have engendered a change in
+the nature of hedger's behaviour, at the aggregate level in particular,
+taking it away from the traditional Keynesian view of risk shifting.
+This phenomenon has been noted in earlier theoretical and empirical work
+\citep{danthine_information_1978, stout_why_1998} in different contexts
+from which two competing models of behaviour have emerged.\\
+The information arbitrage model
+\citep{grossman_impossibility_1980, danthine_information_1978, kyle_informed_1989}
+implies that hedgers may often be seeking out counterparties to trade
+with rather than being purely passive. This issue is also raised in both
+\citet{cheng_financialisation_2014} and \citet{stulz_rethink_1996} who
+point out that hedgers may be taking a view on prices just as
+speculators do. In fact, by hedging away some of their risk, hedgers are
+able to speculate more heavily based on their disagreement against
+speculators regarding futures price movement
+\citep{simsek_speculation_2013}, which fits into a heterogeneous
+expectation theory of speculation\footnote{\citet{hirshleifer_speculation_1975};
+  \citet{hirshleifer_reply_1976}; \citet{hirshleifer_theory_1977}}. As
+\citet{stout_why_1998} points out, this disagreement-based theory of
+trading is one of the main reason the public and the law disapproves
+speculation as this form of trading is regarded as
+non-productive\footnote{\citet{duffie_challenges_2014} also discusses
+  some of the challenges faced by a policy treatment of speculative
+  trading motivated by differences in beliefs.}.\\
+In the second model hedgers are seen as liquidity providers as in
+\citet{kang_tale_2020} with this explanation also consistent with the
+nature of financialisation which led to the arrival of long term, long
+only investors who require substantial liquidity to roll-over their
+positions. Table Table~\ref{tbl-time-reg-US-CHP} supports this view. We
+regress commodity futures front returns on individual commercial hedging
+pressure (CHP) as well as aggregate CHP (\textbf{CHP}), our market wide
+measure of CHP, in separate models and find that the explanatory power
+of CHP at the individual commodity level decreases over the
+financialisation period with the US cross-sectional average \(R^{2}\)
+falling down to 20.8\% from 25.8\% in the previous period while that of
+\textbf{CHP} increases (7.1\% vs 5.4\%). Financialisation therefore
+seems to have had the effect of loosening the extent to which futures
+risk premiums relate to commodity specific commercial hedging motives
+while strengthening that to which they relate to broader dynamics such
+as cross-sectional liquidity provision. The pattern is strongest for the
+metals sector where the average \(R^{2}\) drops down to 19.1\% from
+28.1\% between the two periods at the individual level while it rises
+from 8.4\% to 15.7\% at the aggregate level. The symmetry breaks in the
+crisis period, with the US cross-sectional average \(R^{2}\) at the
+individual level bouncing back up (22.5\% vs 20.8\%) while that at the
+aggregate level rises further (14.7\% vs 7.1\%), before eventually
+resuming post-crisis with a further rise at the individual level (27.2\%
+vs 22.5\%) and a drop at the aggregate level (7.5\% vs 14.7\%)
+suggesting a return to legacy commodity specific dynamics.
+
+\bigskip
+\bigskip
+
+Using our bespoke commodity-based asset pricing framework we strive to
+shed new light on the phenomenon by first regressing returns series for
+the twenty four individual US commodities against our factor mimicking
+portfolios independently. The resulting individual explanatory powers
+(\(R^2\)s), once averaged by factor and period, offer a refined
+perspective on the relation between return and factor attribute
+co-movement. A low figure indicates low cross-sectional return
+co-movement for, in this context, return on the corresponding factor
+mimicking portfolio only has explanatory power on return for commodities
+that are constituents of one of its legs over the corresponding period.
+The explanatory power for the other commodities is typically low or even
+0 for the case where commodities are perfectly uncorrelated with
+one-another. A rising figure on the other hand thus indicates increased
+pairwise correlations, positive or negative, including amongst factor
+leg mimicking portfolio constituent commodities; and therefore provides
+evidence that pairwise return correlation relates to factor attribute.\\
+The average time series explanatory power of the various one factor
+models on the US traded assets over the four periods is shown in Table .
+Over the first period the market factor has the best average time series
+performance with the highest average \(R^{2}\) with all three futures
+market factors performing poorly, indicating that the commodities with
+extreme factor attributes (high or low CHP for example) are uncorrelated
+with the rest of the commodity cross-section, and the overall
+performance consistent across periods of high and low \textbf{CHP}
+(below period median). The two factor models average \(R^{2}\)s
+(available upon request) are roughly the sum of the one factor
+\(R^{2}\)s indicating that the factors are almost orthogonal over this
+period.\\
+The onset of financialisation leads to a substantial improvement in the
+performance of the CHP factor with its average \(R^{2}\) increasing to
+8.2\% in the second period relative to 1.7\% in the first with this
+improvement coming from the long leg that shows a greater improvement
+(4.5\% to 15.1\%) relative to the short (3\% to 4\%), suggesting that
+``normally'' backwardated commodities (Keynesian perspective) have
+higher correlation with the rest of the commodity cross-section, and
+thereby bringing more evidence of the important role played by long only
+investors in the change in nature of these markets over that period. The
+performance of the market factor also improves though not by as much in
+a relative sense (21.6\% from 11.7\%) and both the term structure factor
+and the open interest growth factor show a much smaller improvement in
+performance with smaller differences between legs. Over all periods, all
+of our factor models show similar performance across regimes of high and
+low \textbf{CHP}.
+
+\medskip
+
+We next investigate the top eight of the US traded commodities which
+achieved the highest time series \(R^{2}\) for the CHP, market, open
+interest and term structure factors, in each of the four time periods
+with the commodity picks shown in Table .\\
+For the CHP factor the commodities that achieve high \(R^{2}\) in a
+given period are likely to be those with relatively high or low CHP over
+that period, or those commodities that co-vary with the short or the
+long side of the factor. The same applies to the open interest and term
+structure factors with CHP replaced by open interest growth and roll
+yield respectively; while for the market factor the picks are those that
+co-vary most strongly with the market factor over that period.\\
+For the CHP factor, we observe a change in the picks between the first
+and the second period; the picks in the first period included five
+agricultural commodities and three metals while in the second period
+they include all the five base and precious metals and only three
+agricultural commodities. This pattern is also visible for the term
+structure factor for which there are four metals (copper, silver, gold
+and platinum) picks in the second period against two in the first
+(palladium and platinum) as well as for the open interest nearby growth
+factor for which there are three metals (silver, gold and platinum)
+picks in the second period against one in the first (platinum). The
+market factor has three metal picks in the second period (palladium,
+gold and silver) while all the picks in the first period were
+agricultural or energy commodities.\\
+Over the third period, the average CHP factor shows the same metal picks
+with the agriculturals replaced by energy commodity; the open interest
+nearby growth factor still has three metal picks with gold swapped for
+copper and both the market and term structure factors have one,
+copper.\\
+The table also shows the proportion of time that these picks were
+constituents of the corresponding factor. All the picks of the
+long-short factors (average CHP, open interest nearby growth and term
+structure factors) were constituents of the corresponding factor for
+some proportion of time in all of the time periods. In this respect,
+there is a contrast between the first and second periods with the
+average CHP and open interest nearby growth factor picks appearing
+predominantly on the long side of the corresponding factor in the second
+period, as opposed to both legs in the first. The pattern is
+particularly strong for the metals and energy commodities respectively,
+with the exception of copper for the average CHP factor that lives in
+the short leg a higher proportion of the time over the financialisation
+period. The pattern is reversed for the term structure factor where the
+picks appear predominantly on the short leg in the second period, as
+opposed to both legs in the first with the pattern again strongest for
+the metals. This behaviour continues over the third period for the
+average CHP and open interest nearby growth factors and indicates that
+their picks consistently exhibited low commercial hedging pressure and
+high front contract open interest growth respectively while indicating
+that the term structure factor picks showed low roll yield in the first
+and second period.
+
+\medskip
+
+In table , we show the average pairwise returns correlation between each
+set of picks in each time period. Following on form the earlier
+observations, this exercise gives an indication of the extent to which
+attribute co-movement reveals price co-movement, which is particularly
+relevant for the long-short factors for which the corresponding
+attribute is not directly related to price co-movement.\\
+In the first period the average picks pairwise correlation for the
+long-short factors ranges from 7.1\% (term structure factor picks) to
+12.4\% (open interest factor picks) while the market factor picks show
+the highest figure (23.7\%). In the second period the figures for the
+long-short factors rise sharply; up to 22.9\% from 8.1\% for the average
+CHP factor picks, up to 32.4\% from 12.4\% for the open interest factor
+picks and up to 23.4\% from 7.1\% for the term structure factor picks.
+This increase is stronger than that for the market factor picks in a
+relative sense and is a consequence of the dramatic increase in average
+pairwise price correlation amongst the US traded metals which dominate
+the average CHP factor set of picks and which presence is stronger
+amongst both the open interest and term structure factor sets of picks
+over the financialisation period. The higher figures for the open
+interest factor are driven by the strong presence of the energy complex
+amongst the corresponding picks. The latter exhibits much higher average
+pairwise correlations than the other sectors in both periods although
+lower in the second relative to the first which reinforces the role
+played by the metals in the sharp increase in average pairwise
+correlation amongst picks for this factor.\\
+With regards to \textbf{CHP} regimes, although not very pronounced, a
+pattern is noticeable. For the market, open interest and term structure
+factor picks, average pairwise correlations are stronger over phases of
+\textbf{contango} in the first period and over phases of
+\textbf{backwardation} in the financialisation period, eventually
+reverting back to being stronger over \textbf{contango} phases in the
+crisis period with the CHP factor sets of picks showing the opposite
+pattern. Overall, these results suggest an increase in correlation
+between non-price attributes co-movement and price co-movement over the
+financialisation period. It is also interesting to note that US traded
+metals returns were negatively correlated with the rest of US traded
+commodities in the first period and positively in the second.
+
+\medskip
+
+To further understand the link between attribute and price co-movement
+we build all of the factors from every set of factor picks and assess
+their explanatory performance on these sets of picks over the four
+periods independently. The results are shown in table . The long-short
+factors for a particular attribute select the top and bottom two of the
+corresponding picks based on that attribute while the market factor
+takes an equally weighted combination of the eight corresponding picks.
+In the absence of price co-movement between the picks, the market factor
+will achieve an average \(R^{2}\) of around 12.5\%\footnote{Market
+  factor lemma:
+  \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\)
+  size of market portfolio (eight here).}, while there is no non-zero
+\(R^{2}\) lower bound for the corresponding long-short factors.\\
+A high average \(R^{2}\) for the market factor is indicative of strong
+price co-movement. In this respect, the most remarkable change in
+performance in a relative sense is that of the market factor built from
+the CHP factor sets of picks with the average \(R^{2}\) more than
+doubling, from 18.6\% up to 38.1\%. For the long-short factors on the
+other hand it is indicative of simultaneous attribute and price
+co-movement. For the factors built from the market factor picks the
+increase is strongest in a relative sense for the CHP factor with the
+\(R^{2}\) more than doubling, going from 5.6\% in the first period up to
+12.4\% in the second with the increase stronger for the long leg (17.1\%
+vs.~27.9\%) relative to the short (16.5\% vs.~21.4\%). In the case of
+the factors built from the CHP factor picks, the CHP factor built with
+its own picks shows a remarkable increase in a relative sense with the
+\(R^{2}\) tripling, from 7.2\% to 21.4\% and the long leg showing a much
+greater increase relative to the short (10.4\% to 31.1\% vs.~8.3\% to
+9.8\%). The performance of the term structure factor built from the CHP
+factor sets of picks also shows a sizable increase in a relative sense,
+from 3.5\% to 5.3\% and even more remarkable in this case is the
+substantial increase in performance of the short leg, from 6.3\% to
+15.7\% relative to the long (7.5\% to 9.8\%). The pattern is reversed
+for the CHP factor built from the term structure factor picks where the
+average \(R^{2}\) increases from 4.7\% to 8\% with the performance of
+the long leg increasing from 11.9\% to 28.1\% vs.~5.5\% to 9.1\% for the
+short. The performance of the term structure factor constructed from its
+own sets of picks also shows a substantial increase, from 5.1\% to 8.4\%
+with, here again the increase in performance relatively stronger for the
+short leg, from 6\% to 16.1\% vs.~7.6\% to 12.1\% for the long.\\
+Taken together with the previous results showing that the metal complex
+predominantly loads on the long and short legs of the original CHP and
+term structure factors respectively, these results provide evidence of
+convergence of Keynesian and Working's theories of the term structure in
+detecting price co-movement during financialisation perhaps as a result
+of spillover effects between the corresponding futures and spot markets
+as suggested in \citet{basak_model_2016}.
+
+\medskip
+
+In table we assess the performance of the same factors on all the
+commodities instead of just the picks. While the average \(R^{2}\)s are
+expectedly lower, the pattern of results mostly holds with the relative
+performance of the market factors built with different sets of picks as
+well as that of the CHP and term structure factors built with each
+other's picks similar to table . In contrast, the average CHP factor
+built with average CHP factor picks shows a smaller absolute increase in
+average \(R^{2}\) indicating that the link between CHP co-movement and
+price co-movement is stronger amongst the picks which are predominantly
+metals. Taken together, the results in tables and suggest that the onset
+of financialisation had a major impact on the dynamics of US traded
+precious and precious-base metals.\\
+To assess whether this phenomenon extended beyond US borders we examine
+the performance of the factors used in the last two tables above on the
+six UK metals futures traded on the London Metal Exchange with the
+results reported in table . In the first period, although all sets of
+picks, except that of the market factor, included at least one metal,
+the average \(R^{2}\)s are very low; close to zero in most cases. These
+figures drastically increase across the board in the financialisation
+period and show a pattern similar to that observed in the US complex.
+The market factor built from the CHP and term structure factor sets of
+picks shows the sharpest increase in performance, relative to using the
+other sets of factor picks; rising to 20.1\% from 1.5\% and to 15\% from
+0.8\% respectively. The increase in \(R^{2}\) for the market factor
+built with market factor picks is more modest, providing further
+evidence of concentration of co-movement in the metals sector during
+financialisation.\\
+Here again the change in performance for the CHP and term structure
+factor legs stands out where the factors are built with their own as
+well as each other's sets of picks. The average \(R^{2}\) for the long
+leg of the CHP factor built with its own sets of picks increases from
+1\% to 11\% while the short leg shows no significant change. The
+opposite holds for the term structure factor built from its own set of
+picks with the short leg performance increasing from 0.1\% to 14\% while
+that of the long leg remains below 1\%. Building these factors from each
+other's sets of picks produces a similar pattern with the performance of
+the long leg of the CHP factor built from the term structure factor
+picks increasing from 0.7\% to 11.4\%; a much greater increase relative
+to the short leg although in this case the latter also shows a sizable
+increase in performance (0.3\% to 6\%). The performance of the short leg
+of the term structure factor built from the CHP factor sets of picks on
+the other hand increases from 0.3\% to 19.2\% while the performance for
+the long leg in the second period remains below 1.5\%.\\
+Taken together these results emphasise the global nature of the impact
+of financialisation on the metals complex and provide further evidence
+that global metals co-movement could be detected by US based factor
+models that combine the Keynesian and Working's term structure
+paradigms. There seems thus to be information in the factor constructed
+from hedging pressure based on the Keynesian paradigm relevant to the
+term structure factor built on the Working paradigm and these findings
+therefore appear to complement the results of \citet{kang_tale_2020} who
+find that hedging pressure both conveys information about liquidity
+provision in the short term (Working paradigm) and risk transfer in the
+longer term (Keynesian paradigm).
+
+\bigskip
+\bigskip
+
+The crisis period (late 2008 to mid-2013) shows a contrasting pattern of
+results. Returns fall sharply relative to the financialisation period
+(table ) with eighteen US commodities along with all six UK traded
+metals showing lower mean returns. Returns for equally weighted
+portfolios of both sets of assets fall down to 9.4\% and 5.3\% from
+15.9\% and 21.8\% respectively. Returns are mostly higher during phases
+of \textbf{backwardation} relative to \textbf{contango} (table ) with
+fifteen US assets and five of the UK traded metals showing higher mean
+returns in \textbf{backwardation} and the pattern extending to equally
+weighted portfolios of the two sets of assets. Volatility is moderately
+higher for both sets with fifteen US commodities and three UK metals
+showing higher figures and interestingly eminently higher over phases of
+\textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none
+of the UK traded metals show higher volatility figures over
+\textbf{backwardation} phases. The symmetry between the dynamics of CHP
+and \textbf{CHP}'s explanatory power on individual commodity returns
+breaks in the crisis period with both now seemingly converging; the US
+cross-sectional average \(R^{2}\) at the individual level bouncing back
+up (22.5\% vs 20.8\%) while that at the aggregate level rises further
+(14.7\% vs 7.1\%).\\
+The performance of the market factor dominates the US commodity complex
+over the period with a 50\% increase in mean average \(R^{2}\) to over
+30\% (table ) while that of the CHP factor decreases and, although
+increasing, remains modest for the open interest growth and term
+structure factors. The average pairwise correlation amongst the market
+factor picks increases beyond 50\% while there is a leveling in that
+amongst the picks of the long-short factors as shown in table .
+Notwithstanding, the market factor built from any sets of picks shows a
+significant rise across the board in performance on the US complex
+(table ).\\
+Taken together, these results indicate the presence of a systematic
+factor across the entire cross-section of the US commodities. Table
+provides further evidence of systematic linkages, in this case between
+US and non-US traded commodities with a similar, albeit more pronounced
+pattern, where the market factor constructed with any sets of picks (US
+traded commodities) shows a dramatic increase in performance on the UK
+metals with for example, when constructed from its own sets of picks,
+the average \(R^{2}\) increasing to 31.7\% from 10.2\% in the previous
+period.
+
+\medskip
+
+The returns pullback continues into the post-crisis period (table ) with
+twenty-two US and four UK traded assets showing lower mean returns
+relative to the crisis while the same number of US commodities and all
+UK metals show lower figures relative to the financialisation period;
+mean returns for equally weighted portfolios of US and UK assets drop
+down to -0.2\% and 2.7\% respectively. Interestingly volatility also
+recedes substantially with twenty US assets and all UK metals showing
+lower volatility figures relative to both the crisis and
+financialisation periods suggesting that investment outflows from the
+commodity futures complex have had a lower impact on volatility than the
+corresponding inflows witnessed over the financialisation period. The
+figures for the equally weighted portfolios of US and UK assets drop to
+9.9\% and 16.2\% respectively, very close to pre-financialisation
+levels.\\
+The pattern of reversion toward the pre-financialisation Keynesian
+paradigm initiated during the crisis continues stronger into the
+post-crisis period (table ) with mean returns higher during phases of
+\textbf{backwardation} relative to \textbf{contango} (table ), more so
+than over the crisis period with seventeen US commodities showing higher
+mean returns over \textbf{backwardation} phases. The difference is
+significant at the 5\% level for Lumber (XCME) and at the 10\% level for
+Palladium (XNYM) while no difference is significant for the assets
+showing higher figures over phases of \textbf{contango}. The pattern is
+more pronounced for the UK traded subset with all six assets showing
+higher mean returns in \textbf{backwardation} with the difference
+significant at the 1\% level for Nickel-primary (XLME), 5\% level for
+Aluminium (XLME) and 10\% level for Zinc (XLME). It also extends to
+equally weighted portfolios of US and UK traded assets that both show
+higher mean returns during \textbf{backwardation} with the difference
+significant at the 5\% level for the UK portfolio and the figure close
+to the 10\% level significance threshold for the portfolio of US assets.
+Volatilities are overall higher in \textbf{contango} although less so
+than over the previous period with seventeen US commodities showing
+higher figures over \textbf{contango} against twenty-three in the crisis
+period. The pattern extends to three of the six UK traded metals with
+the difference significant at the 1\% level for Copper (XLME) and Tin
+(XLME) and at the 5\% level for Zinc (XLME) while differences are not
+significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME)
+that exhibit higher volatility over \textbf{backwardation} phases.
+Equally weighted portfolios of US and UK traded assets on the other hand
+both show higher volatility in \textbf{contango} with the difference
+significant at the 1\% level for both. Over the financialisation period
+in contrast volatilities were predominantly higher in
+\textbf{backwardation} for US traded assets with fourteen commodities
+showing higher volatility figures in these phases; the post-crisis
+pattern of results for volatilities thus likewise shows signs of
+reversion to pre-financialisation standards. After showing signs of
+convergence in the crisis period the dynamics of the explanatory power
+of CHP and \textbf{CHP} part ways (table ), seemingly reverting to the
+Keynesian paradigm observed pre-financialisation, further suggesting a
+return to legacy commodity specific dynamics. The recovery initiated in
+the crisis period for that of CHP is confirmed with a stronger increase
+in the post-crisis period, 27.2\% vs.~22.5\%, strongest for the metals
+sector, 37.3\% vs.~23.7\%, while the energy sector shows the opposite
+pattern: 11\% vs.~16\%. In contrast, after increasing stronger in the
+crisis, that for \textbf{CHP} falls overall in the post-crisis period,
+7.5\% vs 14.7\%, with the decrease strongest for the energy sector in a
+relative sense: 2.5\% vs.~14.8\%.\\
+Average pairwise correlations amongst factor picks (table ) fall
+substantially in the post-crisis period with for example the figure for
+the market factor picks dropping from 50.1\% to 26.1\%, almost down to
+pre-financialisation levels; results are similar for the long-short
+factor picks with figures below financialisation levels in all cases and
+very close to pre-financialisation standards for the term structure and
+liquidity factor picks. The performance of the market factor on the US
+complex declines below financialisation levels (table ) with the pattern
+similar albeit stronger when the factor is built from the sets of factor
+picks with a decline in performance on the US complex (table ) to almost
+pre-financialisation levels when constructed with its own set of picks
+as well as with those of the long-short factors, in particular the term
+structure and liquidity factors. Table provides further evidence of
+decoupling, in this case between US and non-US traded commodities with a
+sharp decline in performance of the market factor constructed with any
+set of picks on the UK complex below financialisation, down to almost
+pre-financialisation levels when constructed with the sets of long-short
+factors picks.
+
+\medskip
+
+Taken together the patterns of results over the crisis and post-crisis
+periods echo those in \citet{basu_definancialisation} in suggesting that
+the exogenous shock delivered by the financial crisis combined with the
+accommodative monetary policy that ensued seem to have initiated a
+reversion toward pre-financialisation fundamentals in the commodity
+futures complex.
 
@@
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-In the early 2000s, against a backdrop of a low yield environment and poor stock market performance, a combination of financial innovations\footnote{Commodity price indexes and the ad-hoc financial instruments enabling investment in them were the main financial innovations which allowed large global banks to offer commodity investment products to institutional and retail investors.
-In 1991 Goldman Sachs created the S\&P-GSCI which provides investors with buy-side exposure to commodities via the OTC swap market and thus without having to participate in the formal futures markets with their position limit restrictions.
-At this stage, these restrictions still applied to the issuing institutions though, as they hedged the corresponding commodity swap exposure in the futures markets.
-The first commodity-based ETFs were created through buying physical precious metals with gold and silver ETFs offered as early as 2002/2003.
-The regulatory hurdle here related to the licensing of commodity trading professionals.
-Typically, investors had to sign a statement with their broker stating that they understood the risks of commodity investments; a rather inconvenient paperwork for a product designed to trade like a stock, as set forth by a number of industry players at the time.} and regulatory changes\footnote{In 2000, the Commodity Futures Modernization Act (CFMA) granted non-agricultural commodity futures statutory exemption from regulation (``Enron loophole'').
-It still required agricultural commodity derivatives be traded on a CFTC-regulated exchange however.
-Eventually, the CFTC classified swap dealers as ``bona fide'' hedgers, granting them position limits exemption (``swap dealer loophole'').
-In 2005, the CFTC waived the rule that required commodity investors to sign a statement saying they understood the risks, letting the funds replace it with their prospectus.
-The regulatory bottleneck that prevented the large-scale expansion of commodity index investment was no more.} led to large inflows of institutional capital into the commodity futures markets.
-This process known as ``financialisation'' spurred a heated public policy debate about whether the ensuing increase in open interest and trading volume in commodity futures exerted upward pressure on prices.\\
-The debate spread to the legislative sphere, with the US senate launching formal investigations, and was thrust onto the academic community as a matter of urgency.
-Perhaps in response to this, most of the early studies focused on the more mechanical effects of financialisation in individual markets, relying on commodity specific causality and correlation-based analysis.
-The contention eventually triggered legislative action and new position limits were introduced in a number of grains and energy futures markets.
-
-\medskip\setlength{\parindent}{0pt}
-
-With the benefit of hindsight, this focus appears to have been too narrow.
-As our results suggests, financialisation was a phenomenon global in nature and studying the direct effects of increased market participation in single markets thus seems amiss in this context.\\
-The results of our analysis further suggest that financialisation had cross-sectional effects on market fundamentals across the commodity complex beyond energy and agricultural commodities and in fact strongest for the metals sector at the global level; an aspect largely overlooked in the original approach that we believe the existing literature has not fully analysed.\\
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in commodity pricing dynamics.
-In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have triggered a motion of reversion to legacy pre-financialisation fundamentals.
-
-\newpage\loadgeometry{tables}
-
-\hypertarget{tables}{%
-\section{Tables}\label{tables}}
-
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}llrrrr}
-\caption{\label{tab:co-movement-stats-no-regimes}This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Mean values significant at the 1\%, 5\% and 10\% level are marked with ***, ** and * respectively.
-The results are discussed in section \ref{co-movement-results}.}\\
+\section{Conclusion}\label{conclusion}
+
+In the early 2000s, against a backdrop of a low yield environment and
+poor stock market performance, a combination of financial
+innovations\footnote{Commodity price indexes and the ad-hoc financial
+  instruments enabling investment in them were the main financial
+  innovations which allowed large global banks to offer commodity
+  investment products to institutional and retail investors. In 1991
+  Goldman Sachs created the S\&P-GSCI which provides investors with
+  buy-side exposure to commodities via the OTC swap market and thus
+  without having to participate in the formal futures markets with their
+  position limit restrictions. At this stage, these restrictions still
+  applied to the issuing institutions though, as they hedged the
+  corresponding commodity swap exposure in the futures markets. The
+  first commodity-based ETFs were created through buying physical
+  precious metals with gold and silver ETFs offered as early as
+  2002/2003. The regulatory hurdle here related to the licensing of
+  commodity trading professionals. Typically, investors had to sign a
+  statement with their broker stating that they understood the risks of
+  commodity investments; a rather inconvenient paperwork for a product
+  designed to trade like a stock, as set forth by a number of industry
+  players at the time.} and regulatory changes\footnote{In 2000, the
+  Commodity Futures Modernization Act (CFMA) granted non-agricultural
+  commodity futures statutory exemption from regulation (``Enron
+  loophole''). It still required agricultural commodity derivatives be
+  traded on a CFTC-regulated exchange however. Eventually, the CFTC
+  classified swap dealers as ``bona fide'' hedgers, granting them
+  position limits exemption (``swap dealer loophole''). In 2005, the
+  CFTC waived the rule that required commodity investors to sign a
+  statement saying they understood the risks, letting the funds replace
+  it with their prospectus. The regulatory bottleneck that prevented the
+  large-scale expansion of commodity index investment was no more.} led
+to large inflows of institutional capital into the commodity futures
+markets. This process known as ``financialisation'' spurred a heated
+public policy debate about whether the ensuing increase in open interest
+and trading volume in commodity futures exerted upward pressure on
+prices.\\
+The debate spread to the legislative sphere, with the US senate
+launching formal investigations, and was thrust onto the academic
+community as a matter of urgency. Perhaps in response to this, most of
+the early studies focused on the more mechanical effects of
+financialisation in individual markets, relying on commodity specific
+causality and correlation-based analysis. The contention eventually
+triggered legislative action and new position limits were introduced in
+a number of grains and energy futures markets.
+
+\medskip
+
+With the benefit of hindsight, this focus appears to have been too
+narrow. As our results suggests, financialisation was a phenomenon
+global in nature and studying the direct effects of increased market
+participation in single markets thus seems amiss in this context.\\
+The results of our analysis further suggest that financialisation had
+cross-sectional effects on market fundamentals across the commodity
+complex beyond energy and agricultural commodities and in fact strongest
+for the metals sector at the global level; an aspect largely overlooked
+in the original approach that we believe the existing literature has not
+fully analysed.\\
+The onset of the financial crisis and the monetary policy regimes that
+followed, on the other hand, also appear to have induced significant
+changes in commodity pricing dynamics. In contrast with
+financialisation, our results suggest that the crisis and its aftermath
+have delivered an exogenous shock across the entire cross-section of
+liquid commodities and seem to have triggered a motion of reversion to
+legacy pre-financialisation fundamentals.
+
+\newpage
+
+\section{Tables}\label{tables}
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-stats-no-regimes}This table shows mean returns and
+volatility (sd) for the twenty four individual US commodities and the
+six GB metals considered in the study as well as for two equally
+weighted portfolios formed from the US commodities and the GB metals
+respectively across the four periods of interest (past: 1997-2003;
+financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+Mean values significant at the 1\%, 5\% and 10\% level are marked with
+***, ** and * respectively. The results are discussed in section
+Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-asset & estimate & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
+\textbf{Oats (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
+\addlinespace
+\textbf{Soybean meal (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
+\textbf{Soybeans (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}}\\
+\addlinespace
+\textbf{Cattle-live (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}}\\
+\textbf{Lean hogs (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.65\%}}}\\
+\textbf{Cocoa (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.99\%}}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
+\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.06\%}}}\\
+\addlinespace
+\textbf{Lumber (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
+\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.8\%}}}\\
+\textbf{Orange juice (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.16\%}}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.33\%}}}\\
+\textbf{Natural gas (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.64\%}}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.37\%}}}\\
+\addlinespace
+\textbf{Gasoline (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.44\%}}}\\
+\textbf{Heating oil (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.1\%}}}\\
+\textbf{Copper (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.53\%}}}\\
+\textbf{Gold (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.75\%}}}\\
+\textbf{Palladium (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.92\%}}}\\
+\addlinespace
+\textbf{Platinum (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.43\%}}}\\
+\textbf{Silver (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
+\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.15\%}}}\\
+\textbf{Aluminium (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**28.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.03\%}}}\\
+\textbf{Copper (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
+\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}}\\
+\textbf{Lead (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.31\%}}}\\
+\addlinespace
+\textbf{Nickel-primary (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.68\%}}}\\
+\textbf{Tin-refined (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.07\%}}}\\
+\textbf{Zinc (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**15.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.18\%}}}\\
+\textbf{US commodities} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*21.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.72\%}}}\\
+\textbf{GB commodities} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
+\newpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-stats-regimes}This table shows mean returns and
+volatility (sd) for the twenty four individual US commodities and the
+six GB metals considered in the study as well as for two equally
+weighted portfolios formed from the US commodities and the GB metals
+respectively across the four periods of interest (past: 1997-2003;
+financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+Figures are shown independently for phases of aggregate backwardation
+(aggregate CHP \(\leq\) period median) and aggregate contango (aggregate
+CHP \textgreater{} period median). Mean values significant at the 1\%,
+5\% and 10\% level are marked with ***, ** and * respectively. Aggregate
+CHP construction and corresponding regime definitions are discussed in
+section Section~\ref{sec-methods} while the results are discussed in
+section Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-asset & estimate & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endhead
-
-\endfoot
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.74\%}}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23.07\%}} & \textcolor[HTML]{4285f4}{\textbf{29.14\%}} & \textcolor[HTML]{4285f4}{\textbf{31.59\%}} & \textcolor[HTML]{4285f4}{\textbf{21\%}}\\
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.78\%}}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
+\addlinespace
+\textbf{Oats (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.17\%}}}\\
+\textbf{Oats (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.52\%}}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.44\%}}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.35\%}} & \textcolor[HTML]{4285f4}{\textbf{28.94\%}} & \textcolor[HTML]{4285f4}{\textbf{22.33\%}} & \textcolor[HTML]{4285f4}{\textbf{18.19\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.12\%}}}\\
+\addlinespace
+\textbf{Soybean oil (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.45\%}}}\\
+\textbf{Soybeans (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.93\%}} & \textcolor[HTML]{4285f4}{\textbf{34.58\%}} & \textcolor[HTML]{4285f4}{\textbf{24.39\%}} & \textcolor[HTML]{4285f4}{\textbf{22.04\%}}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}}\\
+\textbf{Soybeans (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.09\%}} & \textcolor[HTML]{4285f4}{\textbf{24.74\%}} & \textcolor[HTML]{4285f4}{\textbf{31.11\%}} & \textcolor[HTML]{4285f4}{\textbf{20.56\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.44\%}}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{36\%}} & \textcolor[HTML]{4285f4}{\textbf{37.53\%}} & \textcolor[HTML]{4285f4}{\textbf{26.57\%}}\\
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.77\%}}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.04\%}} & \textcolor[HTML]{4285f4}{\textbf{29.84\%}} & \textcolor[HTML]{4285f4}{\textbf{37.73\%}} & \textcolor[HTML]{4285f4}{\textbf{26.72\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**20.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.58\%}}}\\
+\addlinespace
+\textbf{Cattle-feeder (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}} & \textcolor[HTML]{4285f4}{\textbf{14.93\%}} & \textcolor[HTML]{4285f4}{\textbf{13.39\%}} & \textcolor[HTML]{4285f4}{\textbf{20.14\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.12\%}}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.67\%}} & \textcolor[HTML]{4285f4}{\textbf{15.35\%}} & \textcolor[HTML]{4285f4}{\textbf{16.91\%}} & \textcolor[HTML]{4285f4}{\textbf{17.23\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.07\%}}}\\
+\textbf{Cattle-live (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.65\%}} & \textcolor[HTML]{4285f4}{\textbf{17.91\%}} & \textcolor[HTML]{4285f4}{\textbf{14.97\%}} & \textcolor[HTML]{4285f4}{\textbf{19.9\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
+\textbf{Cattle-live (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.49\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}} & \textcolor[HTML]{4285f4}{\textbf{17.57\%}} & \textcolor[HTML]{4285f4}{\textbf{16.66\%}}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.23\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.24\%}}}\\
+\textbf{Lean hogs (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{37.6\%}} & \textcolor[HTML]{4285f4}{\textbf{35.73\%}} & \textcolor[HTML]{4285f4}{\textbf{27.83\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.66\%}}}\\
+\addlinespace
+\textbf{Lean hogs (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.22\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}} & \textcolor[HTML]{4285f4}{\textbf{32.78\%}} & \textcolor[HTML]{4285f4}{\textbf{38.28\%}}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.98\%}}}\\
+\textbf{Cocoa (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{33.57\%}} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.29\%}}}\\
+\textbf{Cocoa (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{31.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.91\%}} & \textcolor[HTML]{4285f4}{\textbf{34.66\%}} & \textcolor[HTML]{4285f4}{\textbf{23.57\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.36\%}}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{48.82\%}} & \textcolor[HTML]{4285f4}{\textbf{32.6\%}} & \textcolor[HTML]{4285f4}{\textbf{29.92\%}} & \textcolor[HTML]{4285f4}{\textbf{31.52\%}}\\
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.24\%}}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.22\%}} & \textcolor[HTML]{4285f4}{\textbf{32.24\%}}\\
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.84\%}}}\\
+\addlinespace
+\textbf{Cotton-\#2 (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.02\%}} & \textcolor[HTML]{4285f4}{\textbf{29.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.94\%}} & \textcolor[HTML]{4285f4}{\textbf{21.33\%}}\\
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.91\%}}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.77\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.59\%}} & \textcolor[HTML]{4285f4}{\textbf{19.95\%}}\\
+\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**26.99\%}}}\\
+\textbf{Lumber (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.43\%}} & \textcolor[HTML]{4285f4}{\textbf{30.72\%}} & \textcolor[HTML]{4285f4}{\textbf{35.45\%}} & \textcolor[HTML]{4285f4}{\textbf{21.26\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.14\%}}}\\
+\textbf{Lumber (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}} & \textcolor[HTML]{4285f4}{\textbf{28.2\%}} & \textcolor[HTML]{4285f4}{\textbf{37.23\%}} & \textcolor[HTML]{4285f4}{\textbf{28.45\%}}\\
+\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.64\%}}}\\
+\textbf{Orange juice (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{30.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.64\%}}\\
+\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.64\%}}}\\
+\addlinespace
+\textbf{Orange juice (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{38.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.11\%}}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.07\%}}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{33.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.6\%}} & \textcolor[HTML]{4285f4}{\textbf{41.29\%}} & \textcolor[HTML]{4285f4}{\textbf{27.69\%}}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.7\%}}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{36.48\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.09\%}} & \textcolor[HTML]{4285f4}{\textbf{29.83\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**85.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.76\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.33\%}}}\\
+\textbf{Natural gas (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{63.46\%}} & \textcolor[HTML]{4285f4}{\textbf{47.3\%}} & \textcolor[HTML]{4285f4}{\textbf{48.85\%}} & \textcolor[HTML]{4285f4}{\textbf{42.59\%}}\\
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.25\%}}}\\
+\textbf{Natural gas (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{59.76\%}} & \textcolor[HTML]{4285f4}{\textbf{61.3\%}} & \textcolor[HTML]{4285f4}{\textbf{58.18\%}} & \textcolor[HTML]{4285f4}{\textbf{46.41\%}}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.24\%}}}\\
+\addlinespace
+\textbf{Crude oil-WTI (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{36.74\%}} & \textcolor[HTML]{4285f4}{\textbf{32.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.19\%}} & \textcolor[HTML]{4285f4}{\textbf{26.94\%}}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-24.85\%}}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.74\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{53.7\%}} & \textcolor[HTML]{4285f4}{\textbf{41.08\%}}\\
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}}\\
+\textbf{Gasoline (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.47\%}} & \textcolor[HTML]{4285f4}{\textbf{39.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.1\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-19.47\%}}}\\
+\textbf{Gasoline (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.14\%}} & \textcolor[HTML]{4285f4}{\textbf{44.13\%}} & \textcolor[HTML]{4285f4}{\textbf{47.11\%}} & \textcolor[HTML]{4285f4}{\textbf{41.71\%}}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.16\%}}}\\
+\textbf{Heating oil (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{41.37\%}} & \textcolor[HTML]{4285f4}{\textbf{33.33\%}} & \textcolor[HTML]{4285f4}{\textbf{25.95\%}} & \textcolor[HTML]{4285f4}{\textbf{24.62\%}}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-21.62\%}}}\\
+\addlinespace
+\textbf{Heating oil (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.98\%}} & \textcolor[HTML]{4285f4}{\textbf{39.16\%}} & \textcolor[HTML]{4285f4}{\textbf{35.69\%}}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.1\%}}}\\
+\textbf{Copper (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{30.05\%}} & \textcolor[HTML]{4285f4}{\textbf{25.73\%}} & \textcolor[HTML]{4285f4}{\textbf{18.16\%}}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-12.15\%}}}\\
+\textbf{Copper (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.78\%}} & \textcolor[HTML]{4285f4}{\textbf{33.69\%}} & \textcolor[HTML]{4285f4}{\textbf{42.28\%}} & \textcolor[HTML]{4285f4}{\textbf{20.87\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.21\%}}}\\
+\textbf{Gold (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.89\%}} & \textcolor[HTML]{4285f4}{\textbf{19.2\%}} & \textcolor[HTML]{4285f4}{\textbf{17.03\%}} & \textcolor[HTML]{4285f4}{\textbf{12.36\%}}\\
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.1\%}}}\\
+\textbf{Gold (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}} & \textcolor[HTML]{4285f4}{\textbf{25.21\%}} & \textcolor[HTML]{4285f4}{\textbf{16.23\%}}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**49.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**31.93\%}}}\\
+\addlinespace
+\textbf{Palladium (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.49\%}} & \textcolor[HTML]{4285f4}{\textbf{23.82\%}}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.88\%}}}\\
+\textbf{Palladium (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{41.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.2\%}} & \textcolor[HTML]{4285f4}{\textbf{38.71\%}} & \textcolor[HTML]{4285f4}{\textbf{26.8\%}}\\
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*25.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.17\%}}}\\
+\textbf{Platinum (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.1\%}} & \textcolor[HTML]{4285f4}{\textbf{22.51\%}} & \textcolor[HTML]{4285f4}{\textbf{21.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.04\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.28\%}}}\\
+\textbf{Platinum (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23.12\%}} & \textcolor[HTML]{4285f4}{\textbf{22.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.75\%}} & \textcolor[HTML]{4285f4}{\textbf{20.8\%}}\\
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.44\%}}}\\
+\textbf{Silver (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.07\%}} & \textcolor[HTML]{4285f4}{\textbf{32.5\%}} & \textcolor[HTML]{4285f4}{\textbf{37.17\%}} & \textcolor[HTML]{4285f4}{\textbf{20.3\%}}\\
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.09\%}}}\\
+\addlinespace
+\textbf{Silver (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.93\%}} & \textcolor[HTML]{4285f4}{\textbf{35.34\%}} & \textcolor[HTML]{4285f4}{\textbf{42.44\%}} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}}\\
+\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**23.68\%}}}\\
+\textbf{Aluminium (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.57\%}} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{18.94\%}}\\
+\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-23.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.74\%}}}\\
+\textbf{Aluminium (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.13\%}} & \textcolor[HTML]{4285f4}{\textbf{27.29\%}} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{18.23\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.99\%}}}\\
+\textbf{Copper (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.98\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{17.92\%}}\\
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.89\%}}}\\
+\textbf{Copper (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{41.31\%}} & \textcolor[HTML]{4285f4}{\textbf{19.86\%}}\\
+\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.05\%}}}\\
+\addlinespace
+\textbf{Lead (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.16\%}} & \textcolor[HTML]{4285f4}{\textbf{39.91\%}} & \textcolor[HTML]{4285f4}{\textbf{35.35\%}} & \textcolor[HTML]{4285f4}{\textbf{23.37\%}}\\
+\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*46.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-13.41\%}}}\\
+\textbf{Lead (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.12\%}} & \textcolor[HTML]{4285f4}{\textbf{43.16\%}} & \textcolor[HTML]{4285f4}{\textbf{46.22\%}} & \textcolor[HTML]{4285f4}{\textbf{23.09\%}}\\
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-39.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**35.09\%}}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.23\%}} & \textcolor[HTML]{4285f4}{\textbf{41.62\%}} & \textcolor[HTML]{4285f4}{\textbf{34.48\%}} & \textcolor[HTML]{4285f4}{\textbf{29.13\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**63.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**-34.64\%}}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.28\%}} & \textcolor[HTML]{4285f4}{\textbf{46.72\%}} & \textcolor[HTML]{4285f4}{\textbf{47.44\%}} & \textcolor[HTML]{4285f4}{\textbf{28.6\%}}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.48\%}}}\\
+\textbf{Tin-refined (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.4\%}} & \textcolor[HTML]{4285f4}{\textbf{29.09\%}} & \textcolor[HTML]{4285f4}{\textbf{15.27\%}}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.69\%}}}\\
+\addlinespace
+\textbf{Tin-refined (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.77\%}} & \textcolor[HTML]{4285f4}{\textbf{32.08\%}} & \textcolor[HTML]{4285f4}{\textbf{41.13\%}} & \textcolor[HTML]{4285f4}{\textbf{21.68\%}}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.05\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.42\%}}}\\
+\textbf{Zinc (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.86\%}} & \textcolor[HTML]{4285f4}{\textbf{33.28\%}} & \textcolor[HTML]{4285f4}{\textbf{22.12\%}}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.31\%}}}\\
+\textbf{Zinc (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.38\%}} & \textcolor[HTML]{4285f4}{\textbf{40.51\%}} & \textcolor[HTML]{4285f4}{\textbf{39.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.32\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{***15.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.82\%}}}\\
+\textbf{US commodities} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*16.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.33\%}}}\\
+\textbf{US commodities} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**19.95\%}}}\\
+\addlinespace
+\textbf{GB commodities} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-14.05\%}}}\\
+\textbf{GB commodities} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
 \bottomrule
-\endlastfoot
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{individual commodities}}\\
-\hspace{1em} & mean & 3.48\% & 21.37\% & 6.89\% & -4.51\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Corn-\#2 yellow (XCBT)}} & sd & 23\% & 29.54\% & 36.15\% & 21.8\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 5.49\% & 21.62\% & 8.89\% & -0.87\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Oats (XCBT)}} & sd & 32.22\% & 31.04\% & 34.67\% & 29.5\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 7.29\% & 12.06\% & 8.12\% & -0.33\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Soybean meal (XCBT)}} & sd & 26.34\% & 32.55\% & 31.78\% & 25.11\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 6.21\% & 15.57\% & 4.04\% & -7.39\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Soybean oil (XCBT)}} & sd & 21.43\% & 28.35\% & 25.75\% & 18.95\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 6.89\% & 13.36\% & 6.19\% & -3.82\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Soybeans (XCBT)}} & sd & 21.47\% & 30.04\% & 28\% & 21.22\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 5.07\% & 17.63\% & 6.68\% & -1.58\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Wheat-SRW (XCBT)}} & sd & 24.93\% & 33.03\% & 37.62\% & 26.58\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 0.39\% & 7.43\% & 7.13\% & 1.87\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cattle-feeder (XCME)}} & sd & 13.23\% & 15.16\% & 15.24\% & 18.69\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 3.45\% & 8.77\% & 4.13\% & 1.92\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cattle-live (XCME)}} & sd & 17.1\% & 17.43\% & 16.32\% & 18.3\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 0.73\% & 8.4\% & 12.69\% & -1.09\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Lean hogs (XCME)}} & sd & 38.33\% & 31.89\% & 30.37\% & 36.94\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 3.66\% & 16.35\% & 1.39\% & 3.65\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cocoa (IFUS)}} & sd & 32.66\% & 29.99\% & 31.03\% & 24.69\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & -5.91\% & 20.38\% & 2.2\% & 1.99\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Coffee-C (IFUS)}} & sd & 43.84\% & 32.3\% & 30.17\% & 31.86\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 3.24\% & 0.95\% & 12.53\% & 0.5\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Cotton-\#2 (IFUS)}} & sd & 26.38\% & 29.01\% & 33.26\% & 20.61\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 1.9\% & -3.58\% & 11.74\% & 5.06\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Lumber (XCME)}} & sd & 30.58\% & 29.39\% & 36.31\% & 25.1\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 1.67\% & 13.87\% & 14.4\% & 3.8\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Orange juice (IFUS)}} & sd & 29.5\% & 33.01\% & 34.43\% & 29.37\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & -4.56\% & 24.87\% & 11.82\% & -1.16\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Sugar-\#11 (IFUS)}} & sd & 34.88\% & 33.25\% & 37.9\% & 28.72\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 35.38\% & 16.25\% & 0.93\% & 8.33\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Natural gas (XNYM)}} & sd & 61.55\% & 54.6\% & 53.58\% & 44.58\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 15.43\% & *28.74\% & 9.67\% & -5.64\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Crude oil-WTI (XNYM)}} & sd & 39.87\% & 32.56\% & 42.84\% & 34.69\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 16.65\% & 30.95\% & 10.59\% & -5.37\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Gasoline (XNYM)}} & sd & 42.77\% & 41.76\% & 40.07\% & 37.09\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 16.31\% & *29.88\% & 6.83\% & -3.44\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Heating oil (XNYM)}} & sd & 40.75\% & 35.09\% & 33.17\% & 30.56\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 1.45\% & *28.15\% & 6.19\% & -0.1\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Copper (XCEC)}} & sd & 21.23\% & 31.89\% & 34.91\% & 19.56\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 4.5\% & 14.35\% & 14.01\% & 0.53\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Gold (XCEC)}} & sd & 15.14\% & 18.89\% & 21.46\% & 14.41\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 9.12\% & 9.03\% & *29.12\% & 13.75\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Palladium (XNYM)}} & sd & 38.27\% & 32.71\% & 36.14\% & 25.38\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 12.93\% & 10.56\% & 7.29\% & -7.92\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Platinum (XNYM)}} & sd & 22.62\% & 22.66\% & 25.53\% & 19.48\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 6.19\% & 17.54\% & 21.96\% & -2.43\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Silver (XCEC)}} & sd & 22\% & 33.92\% & 39.87\% & 24.35\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 1.13\% & 13.78\% & -3.58\% & 3.15\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Aluminium (XLME)}} & sd & 17.6\% & 26.41\% & 26.48\% & 18.56\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 0.45\% & **28.59\% & 5.74\% & 0.03\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Copper (XLME)}} & sd & 19.25\% & 31.09\% & 34.27\% & 18.92\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 3.83\% & 28.99\% & 10.74\% & 2.07\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Lead (XLME)}} & sd & 19.64\% & 41.74\% & 41.05\% & 23.26\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 19.31\% & 12.5\% & 3.52\% & 0.31\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Nickel-primary (XLME)}} & sd & 32.26\% & 44.27\% & 41.45\% & 28.98\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 4.07\% & *29.1\% & 7.46\% & 1.68\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Tin-refined (XLME)}} & sd & 15.38\% & 31.71\% & 35.61\% & 18.79\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & -4.52\% & 20.13\% & 7.62\% & 9.07\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{Zinc (XLME)}} & sd & 21.73\% & 38.77\% & 36.17\% & 23.25\%\\
-\cmidrule{1-6}\pagebreak[0]
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{equally weighted portfolios}}\\
-\hspace{1em} & mean & *6.89\% & **15.89\% & 9.39\% & -0.18\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{US commodities}} & sd & 10\% & 13.62\% & 17.58\% & 9.86\%\\
-\cmidrule{1-6}\pagebreak[0]
-\hspace{1em} & mean & 2.47\% & *21.77\% & 5.25\% & 2.72\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-2}{*}{\raggedright\arraybackslash \textbf{GB commodities}} & sd & 15.66\% & 26.91\% & 30.24\% & 16.19\%\\*
+
 \end{longtable}
+
 \endgroup{}
@@
 
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}lllrrrr}
-\caption{\label{tab:co-movement-stats-regimes}This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Mean values significant at the 1\%, 5\% and 10\% level are marked with ***, ** and * respectively.
-Aggregate CHP construction and corresponding regime definitions are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-time-reg-US-CHP}This table shows the average time
+series \(R^{2}\) for models where the returns series for the twenty four
+individual US commodities are independently regressed against relative
+change in their own commercial hedging pressure (CHP) series as well as
+against that in aggregate CHP, a market wide measure of CHP which
+calculation method is discussed in section Section~\ref{sec-methods}.
+Averages are calculated independently across the whole cross-section of
+US traded commodity assets considered in the study as well as across
+commodity sectors and subsectors for the four periods of interest (past:
+1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
+2013-2018). The results are discussed in section
+Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-asset & regime & estimate & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{regressor}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.17\%}}}\\
+\textbf{Δ\% commodity CHP} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.19\%}} & \textcolor[HTML]{4285f4}{\textbf{21.6\%}} & \textcolor[HTML]{4285f4}{\textbf{23.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.12\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.24\%}}}\\
+\textbf{Δ\% commodity CHP} & \textbf{agriculturals} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{6.23\%}} & \textcolor[HTML]{4285f4}{\textbf{10.53\%}} & \textcolor[HTML]{4285f4}{\textbf{6.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.88\%}}}\\
+\addlinespace
+\textbf{Δ\% commodity CHP} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.12\%}} & \textcolor[HTML]{4285f4}{\textbf{19.45\%}} & \textcolor[HTML]{4285f4}{\textbf{16\%}} & \textcolor[HTML]{4285f4}{\textbf{10.96\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
+\textbf{Δ\% commodity CHP} & \textbf{energy} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{18.87\%}} & \textcolor[HTML]{4285f4}{\textbf{12.85\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.32\%}}}\\
+\textbf{Δ\% commodity CHP} & \textbf{metals} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{47.38\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}} & \textcolor[HTML]{4285f4}{\textbf{18.07\%}} & \textcolor[HTML]{4285f4}{\textbf{34.9\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.93\%}}}\\
+\textbf{Δ\% aggregate CHP} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{5.37\%}} & \textcolor[HTML]{4285f4}{\textbf{7.12\%}} & \textcolor[HTML]{4285f4}{\textbf{14.72\%}} & \textcolor[HTML]{4285f4}{\textbf{7.49\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.23\%}}}\\
+\textbf{Δ\% aggregate CHP} & \textbf{agriculturals} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{7.25\%}} & \textcolor[HTML]{4285f4}{\textbf{5.4\%}} & \textcolor[HTML]{4285f4}{\textbf{19.75\%}} & \textcolor[HTML]{4285f4}{\textbf{8.45\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.26\%}}}\\
+\addlinespace
+\textbf{Δ\% aggregate CHP} & \textbf{agriculturals} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{5.64\%}} & \textcolor[HTML]{4285f4}{\textbf{10.35\%}} & \textcolor[HTML]{4285f4}{\textbf{6.98\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.45\%}}}\\
+\textbf{Δ\% aggregate CHP} & \textbf{energy} & \textbf{gas} & \textcolor[HTML]{4285f4}{\textbf{2.65\%}} & \textcolor[HTML]{4285f4}{\textbf{2.58\%}} & \textcolor[HTML]{4285f4}{\textbf{2.6\%}} & \textcolor[HTML]{4285f4}{\textbf{0.27\%}}\\
+\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.17\%}}}\\
+\textbf{Δ\% aggregate CHP} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{8.36\%}} & \textcolor[HTML]{4285f4}{\textbf{15.67\%}} & \textcolor[HTML]{4285f4}{\textbf{22.37\%}} & \textcolor[HTML]{4285f4}{\textbf{15.33\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.67\%}}}\\
+\textbf{Δ\% aggregate CHP} & \textbf{metals} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{7.92\%}} & \textcolor[HTML]{4285f4}{\textbf{16.4\%}} & \textcolor[HTML]{4285f4}{\textbf{21.98\%}} & \textcolor[HTML]{4285f4}{\textbf{17.25\%}}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
+\newpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-correlations-periods}This table shows the average
+pairwise correlation coefficients calculated independently across the
+whole cross-section of commodity assets considered in the study as well
+as across countries and commodity sectors and subsectors for the four
+periods of interest (past: 1997-2003; financialisation: 2004-2008;
+crisis: 2008-2013; post-crisis: 2013-2018). For each period, the results
+are calculated independently over the entire period as well as over
+phases of aggregate backwardation and contango. Aggregate CHP
+construction and corresponding regime definitions are discussed in
+section Section~\ref{sec-methods} while the results are discussed in
+section Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-asset & regime & estimate & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endhead
-
-\endfoot
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0737}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1638}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2849}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1282}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0724}} & \textcolor[HTML]{4285f4}{\textbf{0.1790}} & \textcolor[HTML]{4285f4}{\textbf{0.2709}} & \textcolor[HTML]{4285f4}{\textbf{0.1001}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0748}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1501}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2985}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1495}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0684}} & \textcolor[HTML]{4285f4}{\textbf{0.1545}} & \textcolor[HTML]{4285f4}{\textbf{0.2526}} & \textcolor[HTML]{4285f4}{\textbf{0.1096}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0642}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1697}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2323}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0859}}}\\
+\addlinespace
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0720}} & \textcolor[HTML]{4285f4}{\textbf{0.1402}} & \textcolor[HTML]{4285f4}{\textbf{0.2706}} & \textcolor[HTML]{4285f4}{\textbf{0.1268}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0910}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1305}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2322}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1075}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0799}} & \textcolor[HTML]{4285f4}{\textbf{0.1421}} & \textcolor[HTML]{4285f4}{\textbf{0.1975}} & \textcolor[HTML]{4285f4}{\textbf{0.0955}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1018}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2611}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1186}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4421}} & \textcolor[HTML]{4285f4}{\textbf{0.4898}} & \textcolor[HTML]{4285f4}{\textbf{0.5673}} & \textcolor[HTML]{4285f4}{\textbf{0.3728}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4312}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5283}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5749}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3289}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4570}} & \textcolor[HTML]{4285f4}{\textbf{0.4510}} & \textcolor[HTML]{4285f4}{\textbf{0.5675}} & \textcolor[HTML]{4285f4}{\textbf{0.4161}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3340}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2868}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3707}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3333}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3053}} & \textcolor[HTML]{4285f4}{\textbf{0.2652}} & \textcolor[HTML]{4285f4}{\textbf{0.3906}} & \textcolor[HTML]{4285f4}{\textbf{0.3220}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3605}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3150}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3557}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3483}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0391}} & \textcolor[HTML]{4285f4}{\textbf{0.0853}} & \textcolor[HTML]{4285f4}{\textbf{0.1584}} & \textcolor[HTML]{4285f4}{\textbf{0.0764}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0437}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0845}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1210}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0685}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0334}} & \textcolor[HTML]{4285f4}{\textbf{0.0874}} & \textcolor[HTML]{4285f4}{\textbf{0.1937}} & \textcolor[HTML]{4285f4}{\textbf{0.0833}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4908}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5892}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4687}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4203}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.4844}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}} & \textcolor[HTML]{4285f4}{\textbf{0.4601}} & \textcolor[HTML]{4285f4}{\textbf{0.4179}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4957}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5869}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4779}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4210}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.7278}} & \textcolor[HTML]{4285f4}{\textbf{0.7846}} & \textcolor[HTML]{4285f4}{\textbf{0.7692}} & \textcolor[HTML]{4285f4}{\textbf{0.7175}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6962}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7854}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7282}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7606}} & \textcolor[HTML]{4285f4}{\textbf{0.7856}} & \textcolor[HTML]{4285f4}{\textbf{0.7716}} & \textcolor[HTML]{4285f4}{\textbf{0.7134}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2167}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5553}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4721}}}\\
+\addlinespace
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.2201}} & \textcolor[HTML]{4285f4}{\textbf{0.5418}} & \textcolor[HTML]{4285f4}{\textbf{0.6353}} & \textcolor[HTML]{4285f4}{\textbf{0.4155}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2145}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5709}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5035}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.2883}} & \textcolor[HTML]{4285f4}{\textbf{0.6305}} & \textcolor[HTML]{4285f4}{\textbf{0.6704}} & \textcolor[HTML]{4285f4}{\textbf{0.5762}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3070}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6061}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6991}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5386}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.6591}} & \textcolor[HTML]{4285f4}{\textbf{0.6615}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4047}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4691}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6536}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4412}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3987}} & \textcolor[HTML]{4285f4}{\textbf{0.4753}} & \textcolor[HTML]{4285f4}{\textbf{0.6729}} & \textcolor[HTML]{4285f4}{\textbf{0.3954}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4108}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6456}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4797}}}\\
 \bottomrule
-\endlastfoot
-\addlinespace[0.3em]
-\multicolumn{7}{l}{\textbf{individual commodities}}\\
-\hspace{1em} &  & mean & -4.86\% & 19.26\% & 20.48\% & -8.74\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 23.07\% & 29.14\% & 31.59\% & 21\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 11.3\% & 23.54\% & -4.43\% & 0.78\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Corn-\#2 yellow (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 23\% & 30.01\% & 40.14\% & 22.68\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & -5.39\% & 7.82\% & 7.85\% & 2.56\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 29.02\% & 33.82\% & 31.43\% & 31.55\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 16.95\% & *35.38\% & 11.68\% & -3.17\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Oats (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 35.22\% & 28.1\% & 37.7\% & 27.5\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 13.15\% & 8.22\% & 16.04\% & -3.52\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 27.77\% & 33.06\% & 25.7\% & 25.1\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 1.52\% & 15.91\% & 2.32\% & 2.22\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Soybean meal (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 24.94\% & 32.13\% & 36.85\% & 25.32\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 14.79\% & 14.62\% & 20.34\% & -9.44\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.35\% & 28.94\% & 22.33\% & 18.19\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -2.68\% & 16.62\% & -10.01\% & -4.12\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Soybean oil (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 21.55\% & 27.91\% & 28.65\% & 19.79\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 13.69\% & 0.93\% & 13.42\% & -11.45\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.93\% & 34.58\% & 24.39\% & 22.04\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.16\% & 25.71\% & 0.96\% & 3.75\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Soybeans (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 21.09\% & 24.74\% & 31.11\% & 20.56\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & -2.7\% & 19.02\% & 0.98\% & 0.44\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 25.79\% & 36\% & 37.53\% & 26.57\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 11.78\% & 16.29\% & 14.57\% & -2.77\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Wheat-SRW (XCBT)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 24.04\% & 29.84\% & 37.73\% & 26.72\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 2.31\% & **20.52\% & 7.51\% & 6.58\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 12.79\% & 14.93\% & 13.39\% & 20.14\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.81\% & -5.49\% & 7.28\% & -3.12\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cattle-feeder (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 13.67\% & 15.35\% & 16.91\% & 17.23\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 8.39\% & 14.2\% & 5.87\% & -2.07\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 16.65\% & 17.91\% & 14.97\% & 19.9\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.34\% & 3.43\% & 2.7\% & 5.82\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cattle-live (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 17.49\% & 16.99\% & 17.57\% & 16.66\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 12.34\% & 16.3\% & 18.23\% & 19.24\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 37.6\% & 35.73\% & 27.83\% & 35.61\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -10.5\% & 0.6\% & 7.5\% & -20.66\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Lean hogs (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 39.22\% & 27.67\% & 32.78\% & 38.28\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 4.12\% & 9.25\% & -9.56\% & -2.98\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 33.57\% & 31.05\% & 26.93\% & 25.86\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 3.67\% & 23.43\% & 12.92\% & 10.29\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cocoa (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 31.81\% & 28.91\% & 34.66\% & 23.57\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 4.51\% & 26.49\% & 2.66\% & 14.36\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 48.82\% & 32.6\% & 29.92\% & 31.52\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -16.87\% & 14.38\% & 3.4\% & -10.24\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Coffee-C (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 38.35\% & 32.06\% & 30.22\% & 32.24\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 22.64\% & 7.85\% & 35.53\% & 10.84\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 26.02\% & 29.71\% & 33.94\% & 21.33\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -16.46\% & -5.92\% & -9.36\% & -8.91\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Cotton-\#2 (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 26.77\% & 28.35\% & 32.59\% & 19.95\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & -8.48\% & -2.37\% & 29.11\% & **26.99\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 30.43\% & 30.72\% & 35.45\% & 21.26\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 11.68\% & -4.77\% & -5.04\% & -17.14\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Lumber (XCME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 30.56\% & 28.2\% & 37.23\% & 28.45\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & -2.38\% & -2.22\% & 18.24\% & 18.64\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 28.01\% & 33.01\% & 30.09\% & 28.64\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 5.83\% & 29.93\% & 12.29\% & -8.64\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Orange juice (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 31.05\% & 33.1\% & 38.06\% & 30.11\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 11.98\% & 29.51\% & 2.7\% & -8.07\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 33.23\% & 33.6\% & 41.29\% & 27.69\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -20.49\% & 20.35\% & 21.47\% & 4.7\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Sugar-\#11 (IFUS)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 36.48\% & 32.98\% & 34.09\% & 29.83\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & **85.84\% & 4.76\% & -2.32\% & 18.33\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 63.46\% & 47.3\% & 48.85\% & 42.59\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -11.98\% & 27.84\% & 4.77\% & 3.25\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Natural gas (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 59.76\% & 61.3\% & 58.18\% & 46.41\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 29.17\% & *35.61\% & 11.47\% & 14.24\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 36.74\% & 32.09\% & 28.19\% & 26.94\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 2.21\% & 22.04\% & 9.95\% & -24.85\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Crude oil-WTI (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 42.74\% & 33.1\% & 53.7\% & 41.08\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 39\% & 19.82\% & 23.98\% & 9.69\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 42.47\% & 39.38\% & 31.41\% & 32.1\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -5.22\% & 42.13\% & -0.09\% & -19.47\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Gasoline (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 43.14\% & 44.13\% & 47.11\% & 41.71\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 36.32\% & 29.41\% & 25.56\% & 15.16\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 41.37\% & 33.33\% & 25.95\% & 24.62\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -2.74\% & 30.5\% & -10.77\% & -21.62\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Heating oil (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 40.19\% & 36.98\% & 39.16\% & 35.69\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 3.14\% & 22.17\% & 16.53\% & 12.1\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 20.71\% & 30.05\% & 25.73\% & 18.16\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.28\% & 34.17\% & -3.46\% & -12.15\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Copper (XCEC)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 21.78\% & 33.69\% & 42.28\% & 20.87\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 9.19\% & 13.37\% & 9.37\% & 4.21\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 16.89\% & 19.2\% & 17.03\% & 12.36\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.01\% & 15.37\% & 19.1\% & -3.1\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Gold (XCEC)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 13.24\% & 18.58\% & 25.21\% & 16.23\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & **49.79\% & 24.47\% & 30.01\% & **31.93\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 34.98\% & 34.23\% & 33.49\% & 23.82\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -30.19\% & -6.3\% & 30.58\% & -4.88\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Palladium (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 41.22\% & 31.2\% & 38.71\% & 26.8\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & **29.46\% & *25.07\% & 10.46\% & 1.17\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 22.1\% & 22.51\% & 21.24\% & 18.04\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -3.22\% & -3.81\% & 8.04\% & -17.28\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Platinum (XNYM)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 23.12\% & 22.81\% & 28.75\% & 20.8\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 5.98\% & 14.29\% & 19.66\% & 3.44\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.07\% & 32.5\% & 37.17\% & 20.3\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 6.57\% & 20.83\% & 26.77\% & -8.09\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Silver (XCEC)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 22.93\% & 35.34\% & 42.44\% & 27.77\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 2.56\% & 14.78\% & 16.25\% & **23.68\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 14.82\% & 25.57\% & 24.94\% & 18.94\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.38\% & 12.86\% & -23.04\% & -16.74\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Aluminium (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 20.13\% & 27.29\% & 28.01\% & 18.23\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 1.54\% & 25.22\% & 18.66\% & 11.99\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 17.98\% & 29.01\% & 25.53\% & 17.92\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.95\% & 32\% & -6.78\% & -11.89\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Copper (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 20.41\% & 32.98\% & 41.31\% & 19.86\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 7.59\% & 11.21\% & 9.87\% & 17.05\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 19.16\% & 39.91\% & 35.35\% & 23.37\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.09\% & *46.48\% & 12.65\% & -13.41\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Lead (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 20.12\% & 43.16\% & 46.22\% & 23.09\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 23.25\% & -39.24\% & 16.3\% & **35.09\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 30.23\% & 41.62\% & 34.48\% & 29.13\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 15.46\% & **63.47\% & -7.67\% & **-34.64\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Nickel-primary (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 34.28\% & 46.72\% & 47.44\% & 28.6\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & *15.83\% & 34.62\% & 23.7\% & 4.48\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 14.99\% & 31.4\% & 29.09\% & 15.27\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -7.78\% & 23.88\% & -6.82\% & -1.69\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Tin-refined (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 15.77\% & 32.08\% & 41.13\% & 21.68\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & -9.06\% & 2.95\% & 10.05\% & **29.42\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 21.15\% & 36.86\% & 33.28\% & 22.12\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -0.13\% & 37.11\% & 5.43\% & -11.31\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{Zinc (XLME)}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 22.38\% & 40.51\% & 39.03\% & 24.32\%\\
-\cmidrule{1-7}\pagebreak[0]
-\addlinespace[0.3em]
-\multicolumn{7}{l}{\textbf{equally weighted portfolios}}\\
-\hspace{1em} &  & mean & ***15.44\% & *15.66\% & 13.4\% & 6.82\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 9.88\% & 14.21\% & 14.83\% & 8.59\%\\
-\nopagebreak
-\hspace{1em} &  & mean & -1.09\% & *16.16\% & 4.9\% & -6.33\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{US commodities}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 10.09\% & 13.05\% & 19.98\% & 10.95\%\\
-\cmidrule{1-7}\pagebreak[0]
-\hspace{1em} &  & mean & 4.41\% & 8.01\% & 15.06\% & **19.95\%\\
-\nopagebreak
-\hspace{1em} & \multirow[t]{-2}{*}{\raggedright\arraybackslash backwardation} & sd & 14.39\% & 25.92\% & 25.94\% & 15.13\%\\
-\nopagebreak
-\hspace{1em} &  & mean & 0.34\% & *35.56\% & -5.24\% & -14.05\%\\
-\nopagebreak
-\hspace{1em}\multirow[t]{-4}{*}{\raggedright\arraybackslash \textbf{GB commodities}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash contango} & sd & 16.87\% & 27.88\% & 34.06\% & 17.1\%\\*
+
 \end{longtable}
+
 \endgroup{}
@@
 
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}lllrrrr}
-\caption{\label{tab:co-movement-time-reg-US-CHP}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \ref{co-movement-methods}.
-Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The results are discussed in section \ref{co-movement-results}.}\\
+\begin{landscape}\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}l>{}r>{}r>{}r>{}r>{}r>{}r>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-correlations-years}This table shows the average
+pairwise correlation coefficients calculated independently across the
+whole cross-section of commodity assets considered in the study as well
+as across countries and commodity sectors and subsectors by year for the
+whole period of interest (1997-2018). The results are discussed in
+section Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-regressor & sector & subsector & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{decade}} & \textcolor{black}{\textbf{0}} & \textcolor{black}{\textbf{1}} & \textcolor{black}{\textbf{2}} & \textcolor{black}{\textbf{3}} & \textcolor{black}{\textbf{4}} & \textcolor{black}{\textbf{5}} & \textcolor{black}{\textbf{6}} & \textcolor{black}{\textbf{7}} & \textcolor{black}{\textbf{8}} & \textcolor{black}{\textbf{9}}\\
 \midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0401}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0812}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0822}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0652}} & \textcolor[HTML]{4285f4}{\textbf{0.0719}} & \textcolor[HTML]{4285f4}{\textbf{0.0796}} & \textcolor[HTML]{4285f4}{\textbf{0.0848}} & \textcolor[HTML]{4285f4}{\textbf{0.1242}} & \textcolor[HTML]{4285f4}{\textbf{0.1247}} & \textcolor[HTML]{4285f4}{\textbf{0.1650}} & \textcolor[HTML]{4285f4}{\textbf{0.1541}} & \textcolor[HTML]{4285f4}{\textbf{0.3334}} & \textcolor[HTML]{4285f4}{\textbf{0.2913}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2743}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2837}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2235}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1432}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1139}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1547}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1339}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0963}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1374}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0536}} & \textcolor[HTML]{4285f4}{\textbf{0.0811}} & \textcolor[HTML]{4285f4}{\textbf{0.0803}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0597}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0600}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0723}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1073}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1164}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1502}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1479}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3284}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2621}}}\\
+\addlinespace
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2275}} & \textcolor[HTML]{4285f4}{\textbf{0.2541}} & \textcolor[HTML]{4285f4}{\textbf{0.1850}} & \textcolor[HTML]{4285f4}{\textbf{0.1018}} & \textcolor[HTML]{4285f4}{\textbf{0.0986}} & \textcolor[HTML]{4285f4}{\textbf{0.1371}} & \textcolor[HTML]{4285f4}{\textbf{0.1064}} & \textcolor[HTML]{4285f4}{\textbf{0.0905}} & \textcolor[HTML]{4285f4}{\textbf{0.1197}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0827}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0916}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0918}} & \textcolor[HTML]{4285f4}{\textbf{0.0967}} & \textcolor[HTML]{4285f4}{\textbf{0.0734}} & \textcolor[HTML]{4285f4}{\textbf{0.0827}} & \textcolor[HTML]{4285f4}{\textbf{0.1111}} & \textcolor[HTML]{4285f4}{\textbf{0.1090}} & \textcolor[HTML]{4285f4}{\textbf{0.1125}} & \textcolor[HTML]{4285f4}{\textbf{0.1131}} & \textcolor[HTML]{4285f4}{\textbf{0.3034}} & \textcolor[HTML]{4285f4}{\textbf{0.2507}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2038}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2304}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1583}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0716}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0846}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1360}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1148}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1181}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.5243}} & \textcolor[HTML]{4285f4}{\textbf{0.4882}} & \textcolor[HTML]{4285f4}{\textbf{0.5650}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4870}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3851}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3402}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4473}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5335}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4594}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5040}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6325}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5681}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.5389}} & \textcolor[HTML]{4285f4}{\textbf{0.6424}} & \textcolor[HTML]{4285f4}{\textbf{0.5592}} & \textcolor[HTML]{4285f4}{\textbf{0.3199}} & \textcolor[HTML]{4285f4}{\textbf{0.3134}} & \textcolor[HTML]{4285f4}{\textbf{0.4390}} & \textcolor[HTML]{4285f4}{\textbf{0.3872}} & \textcolor[HTML]{4285f4}{\textbf{0.4123}} & \textcolor[HTML]{4285f4}{\textbf{0.3618}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2192}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3724}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3453}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.2762}} & \textcolor[HTML]{4285f4}{\textbf{0.3315}} & \textcolor[HTML]{4285f4}{\textbf{0.3243}} & \textcolor[HTML]{4285f4}{\textbf{0.3497}} & \textcolor[HTML]{4285f4}{\textbf{0.2937}} & \textcolor[HTML]{4285f4}{\textbf{0.4170}} & \textcolor[HTML]{4285f4}{\textbf{0.2784}} & \textcolor[HTML]{4285f4}{\textbf{0.2744}} & \textcolor[HTML]{4285f4}{\textbf{0.2822}} & \textcolor[HTML]{4285f4}{\textbf{0.3365}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3568}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4772}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3585}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1783}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3532}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4246}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3445}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2994}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{-0.0042}} & \textcolor[HTML]{4285f4}{\textbf{-0.0001}} & \textcolor[HTML]{4285f4}{\textbf{0.0128}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0603}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0289}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0470}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0807}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0577}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0624}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0765}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0485}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2484}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1710}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.1273}} & \textcolor[HTML]{4285f4}{\textbf{0.1400}} & \textcolor[HTML]{4285f4}{\textbf{0.1038}} & \textcolor[HTML]{4285f4}{\textbf{0.0568}} & \textcolor[HTML]{4285f4}{\textbf{0.0413}} & \textcolor[HTML]{4285f4}{\textbf{0.0983}} & \textcolor[HTML]{4285f4}{\textbf{0.1280}} & \textcolor[HTML]{4285f4}{\textbf{0.0825}} & \textcolor[HTML]{4285f4}{\textbf{0.0565}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4060}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4552}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5256}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.4362}} & \textcolor[HTML]{4285f4}{\textbf{0.5186}} & \textcolor[HTML]{4285f4}{\textbf{0.5682}} & \textcolor[HTML]{4285f4}{\textbf{0.5248}} & \textcolor[HTML]{4285f4}{\textbf{0.6212}} & \textcolor[HTML]{4285f4}{\textbf{0.6402}} & \textcolor[HTML]{4285f4}{\textbf{0.5082}} & \textcolor[HTML]{4285f4}{\textbf{0.5530}} & \textcolor[HTML]{4285f4}{\textbf{0.6278}} & \textcolor[HTML]{4285f4}{\textbf{0.4840}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4549}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4752}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3796}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2889}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4103}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4282}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4442}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3890}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4270}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.7207}} & \textcolor[HTML]{4285f4}{\textbf{0.7946}} & \textcolor[HTML]{4285f4}{\textbf{0.8527}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7632}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8072}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8321}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7377}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7703}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7895}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7460}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.8835}} & \textcolor[HTML]{4285f4}{\textbf{0.7867}} & \textcolor[HTML]{4285f4}{\textbf{0.6692}} & \textcolor[HTML]{4285f4}{\textbf{0.6075}} & \textcolor[HTML]{4285f4}{\textbf{0.6710}} & \textcolor[HTML]{4285f4}{\textbf{0.7069}} & \textcolor[HTML]{4285f4}{\textbf{0.7547}} & \textcolor[HTML]{4285f4}{\textbf{0.6672}} & \textcolor[HTML]{4285f4}{\textbf{0.7786}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2296}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2449}}}\\
+\addlinespace
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.1860}} & \textcolor[HTML]{4285f4}{\textbf{0.1832}} & \textcolor[HTML]{4285f4}{\textbf{0.1992}} & \textcolor[HTML]{4285f4}{\textbf{0.2290}} & \textcolor[HTML]{4285f4}{\textbf{0.4923}} & \textcolor[HTML]{4285f4}{\textbf{0.4480}} & \textcolor[HTML]{4285f4}{\textbf{0.6328}} & \textcolor[HTML]{4285f4}{\textbf{0.5426}} & \textcolor[HTML]{4285f4}{\textbf{0.5664}} & \textcolor[HTML]{4285f4}{\textbf{0.5547}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6297}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6458}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6649}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6160}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4531}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4850}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4269}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3584}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5259}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.3063}} & \textcolor[HTML]{4285f4}{\textbf{0.3451}} & \textcolor[HTML]{4285f4}{\textbf{0.3308}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2934}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3053}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2959}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5688}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6969}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6143}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6428}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6713}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.7004}} & \textcolor[HTML]{4285f4}{\textbf{0.7107}} & \textcolor[HTML]{4285f4}{\textbf{0.7089}} & \textcolor[HTML]{4285f4}{\textbf{0.6988}} & \textcolor[HTML]{4285f4}{\textbf{0.5620}} & \textcolor[HTML]{4285f4}{\textbf{0.6088}} & \textcolor[HTML]{4285f4}{\textbf{0.5652}} & \textcolor[HTML]{4285f4}{\textbf{0.4746}} & \textcolor[HTML]{4285f4}{\textbf{0.5716}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2289}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3601}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4487}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.3550}} & \textcolor[HTML]{4285f4}{\textbf{0.4082}} & \textcolor[HTML]{4285f4}{\textbf{0.4775}} & \textcolor[HTML]{4285f4}{\textbf{0.5526}} & \textcolor[HTML]{4285f4}{\textbf{0.5068}} & \textcolor[HTML]{4285f4}{\textbf{0.4792}} & \textcolor[HTML]{4285f4}{\textbf{0.4340}} & \textcolor[HTML]{4285f4}{\textbf{0.4653}} & \textcolor[HTML]{4285f4}{\textbf{0.5795}} & \textcolor[HTML]{4285f4}{\textbf{0.6647}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6886}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6742}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6606}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4700}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5003}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4636}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3810}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3598}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+\end{landscape}
+
+\newpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-regressions-index}This table shows the average time
+series regression coefficients for models where the returns series for
+all the commodity assets considered in the study are independently
+regressed against the return series for our market factor, an equally
+weighted portfolio of the 24 US commodities considered in the study. The
+results are calculated independently across countries as well as
+commodity sectors and subsectors for the four periods of interest (past:
+1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
+2013-2018). The market factor construction is discussed in section
+Section~\ref{sec-methods} while the results are discussed in section
+Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-regressor & sector & subsector & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endhead
-
-\endfoot
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8556}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9709}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0352}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9438}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.7706}} & \textcolor[HTML]{4285f4}{\textbf{0.7965}} & \textcolor[HTML]{4285f4}{\textbf{0.8535}} & \textcolor[HTML]{4285f4}{\textbf{0.8252}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9891}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1982}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0301}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{0.4320}} & \textcolor[HTML]{4285f4}{\textbf{0.2059}} & \textcolor[HTML]{4285f4}{\textbf{0.3317}} & \textcolor[HTML]{4285f4}{\textbf{0.5484}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7213}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6900}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7953}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7589}}}\\
+\addlinespace
+\textbf{US} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{2.3308}} & \textcolor[HTML]{4285f4}{\textbf{1.6106}} & \textcolor[HTML]{4285f4}{\textbf{1.3977}} & \textcolor[HTML]{4285f4}{\textbf{1.7639}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6992}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.7090}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0044}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2585}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{2.2080}} & \textcolor[HTML]{4285f4}{\textbf{1.5778}} & \textcolor[HTML]{4285f4}{\textbf{1.5288}} & \textcolor[HTML]{4285f4}{\textbf{1.9324}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6320}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1252}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1212}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9131}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{0.4902}} & \textcolor[HTML]{4285f4}{\textbf{1.1178}} & \textcolor[HTML]{4285f4}{\textbf{1.4140}} & \textcolor[HTML]{4285f4}{\textbf{0.8780}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1271}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0480}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9219}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.8520}} & \textcolor[HTML]{4285f4}{\textbf{1.1761}} & \textcolor[HTML]{4285f4}{\textbf{0.7192}}\\
 \bottomrule
-\endlastfoot
- & all &  & 25.79\% & 20.72\% & 22.46\% & 27.17\%\\
-\nopagebreak
- & agriculturals &  & 25.19\% & 21.6\% & 23.91\% & 28.12\%\\
-\nopagebreak
- & energy &  & 25.12\% & 19.45\% & 16\% & 10.96\%\\
-\nopagebreak
- & metals & \multirow[t]{-4}{*}{\raggedright\arraybackslash all} & 28.12\% & 19.1\% & 23.27\% & 37.32\%\\
-\nopagebreak
- &  & grains & 33.18\% & 27.86\% & 29.15\% & 36.24\%\\
-\nopagebreak
- &  & livestock & 6.23\% & 10.53\% & 6.89\% & 4.34\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash agriculturals} & softs & 26.68\% & 20.89\% & 27.19\% & 31.88\%\\
-\nopagebreak
- &  & gas & 19.69\% & 15.65\% & 7.36\% & 5.29\%\\
-\nopagebreak
- & \multirow[t]{-2}{*}{\raggedright\arraybackslash energy} & petroleum & 26.93\% & 20.71\% & 18.87\% & 12.85\%\\
-\nopagebreak
- &  & base & 47.38\% & 25.86\% & 18.07\% & 34.9\%\\
-\nopagebreak
-\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{individual CHP}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash metals} & precious & 23.3\% & 17.41\% & 24.57\% & 37.93\%\\
-\cmidrule{1-7}\pagebreak[0]
- & all &  & 5.37\% & 7.12\% & 14.72\% & 7.49\%\\
-\nopagebreak
- & agriculturals &  & 4.91\% & 4.5\% & 12.14\% & 6.23\%\\
-\nopagebreak
- & energy &  & 3.35\% & 6.27\% & 14.83\% & 2.45\%\\
-\nopagebreak
- & metals & \multirow[t]{-4}{*}{\raggedright\arraybackslash all} & 8.36\% & 15.67\% & 22.37\% & 15.33\%\\
-\nopagebreak
- &  & grains & 7.25\% & 5.4\% & 19.75\% & 8.45\%\\
-\nopagebreak
- &  & livestock & 1.35\% & 0.41\% & 0.52\% & 0.26\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash agriculturals} & softs & 4.34\% & 5.64\% & 10.35\% & 6.98\%\\
-\nopagebreak
- &  & gas & 2.65\% & 2.58\% & 2.6\% & 0.27\%\\
-\nopagebreak
- & \multirow[t]{-2}{*}{\raggedright\arraybackslash energy} & petroleum & 3.59\% & 7.49\% & 18.9\% & 3.17\%\\
-\nopagebreak
- &  & base & 10.12\% & 12.74\% & 23.94\% & 7.67\%\\
-\nopagebreak
-\multirow[t]{-11}{*}{\raggedright\arraybackslash \textbf{aggregate CHP}} & \multirow[t]{-2}{*}{\raggedright\arraybackslash metals} & precious & 7.92\% & 16.4\% & 21.98\% & 17.25\%\\*
+
 \end{longtable}
+
 \endgroup{}
@@
 
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}lllrrrr}
-\caption{\label{tab:co-movement-time-reg-US-facts-US}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities.
-The asset pool for the factor mimicking portfolio construction includes the twenty four US commodities.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
+\begin{landscape}\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-regressions-factors}This table shows the average
+time series regression \(R^{2}\) for models where the returns series for
+all the commodity assets considered in the study are independently
+regressed against the return series for our mimicking portfolios for
+risk factors in returns, including the market, CHP, open interest and
+term structure factors. The results are calculated independently across
+countries and commodity sectors and subsectors for the four periods of
+interest (past: 1997-2003; financialisation: 2004-2008; crisis:
+2008-2013; post-crisis: 2013-2018); for earch period the results are
+calculated independently over the entire period as well as over phases
+of aggregate backwardation and contango. Factors as well as aggregate
+CHP construction and corresponding regime definitions are discussed in
+section Section~\ref{sec-methods} while the results are discussed in
+section Section~\ref{sec-results}.}
+
+\tabularnewline
+
 \toprule
-factor & leg & regime & past & financialisation & crisis & post-crisis\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{factor}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endhead
-
-\endfoot
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.73\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.44\%}} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{11.82\%}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.99\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.93\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.43\%}} & \textcolor[HTML]{4285f4}{\textbf{3.78\%}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}}\\
+\addlinespace
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.54\%}} & \textcolor[HTML]{4285f4}{\textbf{5.55\%}} & \textcolor[HTML]{4285f4}{\textbf{4.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.69\%}} & \textcolor[HTML]{4285f4}{\textbf{5.47\%}} & \textcolor[HTML]{4285f4}{\textbf{3.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.12\%}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.74\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{2.95\%}} & \textcolor[HTML]{4285f4}{\textbf{5.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.39\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{3.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.73\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{11.26\%}} & \textcolor[HTML]{4285f4}{\textbf{23.68\%}} & \textcolor[HTML]{4285f4}{\textbf{28.95\%}} & \textcolor[HTML]{4285f4}{\textbf{13.12\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.66\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.4\%}} & \textcolor[HTML]{4285f4}{\textbf{5.8\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.54\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{6.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.14\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.79\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{5\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{2.87\%}} & \textcolor[HTML]{4285f4}{\textbf{5.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.85\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{5.73\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.07\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.57\%}} & \textcolor[HTML]{4285f4}{\textbf{18.68\%}} & \textcolor[HTML]{4285f4}{\textbf{23.01\%}} & \textcolor[HTML]{4285f4}{\textbf{11.56\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.91\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.03\%}} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.11\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.21\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}} & \textcolor[HTML]{4285f4}{\textbf{1.56\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.85\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.73\%}} & \textcolor[HTML]{4285f4}{\textbf{2.16\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.55\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.69\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.27\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{14.54\%}} & \textcolor[HTML]{4285f4}{\textbf{34.68\%}} & \textcolor[HTML]{4285f4}{\textbf{38.84\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{44.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.71\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.64\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{0.78\%}} & \textcolor[HTML]{4285f4}{\textbf{2.98\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.46\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.06\%}} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.04\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{7.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.5\%}} & \textcolor[HTML]{4285f4}{\textbf{3.8\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.24\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}} & \textcolor[HTML]{4285f4}{\textbf{2.08\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.56\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.25\%}} & \textcolor[HTML]{4285f4}{\textbf{2.18\%}} & \textcolor[HTML]{4285f4}{\textbf{3.3\%}} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.84\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{6.2\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{2.06\%}} & \textcolor[HTML]{4285f4}{\textbf{3.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.94\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.35\%}} & \textcolor[HTML]{4285f4}{\textbf{1.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.71\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.47\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.48\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.82\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}} & \textcolor[HTML]{4285f4}{\textbf{15.58\%}} & \textcolor[HTML]{4285f4}{\textbf{8.44\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.6\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.51\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}} & \textcolor[HTML]{4285f4}{\textbf{0.9\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.41\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}} & \textcolor[HTML]{4285f4}{\textbf{2.42\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.08\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.9\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{26.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{33.74\%}} & \textcolor[HTML]{4285f4}{\textbf{20.94\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.77\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{3.5\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.68\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{6.05\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{7.91\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.67\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{38.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.93\%}} & \textcolor[HTML]{4285f4}{\textbf{17.59\%}} & \textcolor[HTML]{4285f4}{\textbf{22.07\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{41.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.13\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.99\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{1.86\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.16\%}} & \textcolor[HTML]{4285f4}{\textbf{2.76\%}} & \textcolor[HTML]{4285f4}{\textbf{5.88\%}} & \textcolor[HTML]{4285f4}{\textbf{1.26\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.86\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{21.36\%}} & \textcolor[HTML]{4285f4}{\textbf{17.54\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{7.17\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.96\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.37\%}} & \textcolor[HTML]{4285f4}{\textbf{3.62\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{16.2\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.3\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.26\%}} & \textcolor[HTML]{4285f4}{\textbf{13.46\%}} & \textcolor[HTML]{4285f4}{\textbf{13.84\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.03\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{23.23\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{14.53\%}} & \textcolor[HTML]{4285f4}{\textbf{16.64\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.41\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{4.24\%}} & \textcolor[HTML]{4285f4}{\textbf{7.16\%}} & \textcolor[HTML]{4285f4}{\textbf{5.22\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.9\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.48\%}} & \textcolor[HTML]{4285f4}{\textbf{6.51\%}} & \textcolor[HTML]{4285f4}{\textbf{4.6\%}} & \textcolor[HTML]{4285f4}{\textbf{4.55\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{48.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.91\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{27.65\%}} & \textcolor[HTML]{4285f4}{\textbf{37.22\%}} & \textcolor[HTML]{4285f4}{\textbf{40.79\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.71\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.99\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}} & \textcolor[HTML]{4285f4}{\textbf{0.96\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{45.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.56\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{44.02\%}} & \textcolor[HTML]{4285f4}{\textbf{27.52\%}} & \textcolor[HTML]{4285f4}{\textbf{18.61\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{47.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{43.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.7\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.57\%}} & \textcolor[HTML]{4285f4}{\textbf{4.95\%}} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{6.3\%}} & \textcolor[HTML]{4285f4}{\textbf{0.16\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.58\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.5\%}} & \textcolor[HTML]{4285f4}{\textbf{31.77\%}} & \textcolor[HTML]{4285f4}{\textbf{42.95\%}} & \textcolor[HTML]{4285f4}{\textbf{11.54\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.76\%}} & \textcolor[HTML]{4285f4}{\textbf{18.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.33\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.71\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.72\%}} & \textcolor[HTML]{4285f4}{\textbf{23.49\%}} & \textcolor[HTML]{4285f4}{\textbf{21.5\%}} & \textcolor[HTML]{4285f4}{\textbf{13.38\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.27\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{2.83\%}} & \textcolor[HTML]{4285f4}{\textbf{0.32\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.48\%}} & \textcolor[HTML]{4285f4}{\textbf{7.31\%}} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.33\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.57\%}} & \textcolor[HTML]{4285f4}{\textbf{8.4\%}} & \textcolor[HTML]{4285f4}{\textbf{16.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{50.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.74\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{4.96\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}} & \textcolor[HTML]{4285f4}{\textbf{48.58\%}} & \textcolor[HTML]{4285f4}{\textbf{10.15\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.5\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.58\%}} & \textcolor[HTML]{4285f4}{\textbf{5.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.46\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{1.84\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.06\%}} & \textcolor[HTML]{4285f4}{\textbf{9.72\%}} & \textcolor[HTML]{4285f4}{\textbf{9.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.12\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{11.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.3\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.13\%}} & \textcolor[HTML]{4285f4}{\textbf{33.37\%}} & \textcolor[HTML]{4285f4}{\textbf{41.54\%}} & \textcolor[HTML]{4285f4}{\textbf{11.89\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.88\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{25.76\%}} & \textcolor[HTML]{4285f4}{\textbf{23.19\%}} & \textcolor[HTML]{4285f4}{\textbf{15.84\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.81\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.76\%}} & \textcolor[HTML]{4285f4}{\textbf{26.82\%}} & \textcolor[HTML]{4285f4}{\textbf{16.5\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.56\%}} & \textcolor[HTML]{4285f4}{\textbf{0.68\%}} & \textcolor[HTML]{4285f4}{\textbf{3.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.21\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}} & \textcolor[HTML]{4285f4}{\textbf{6.71\%}} & \textcolor[HTML]{4285f4}{\textbf{16.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{4.46\%}} & \textcolor[HTML]{4285f4}{\textbf{7.58\%}} & \textcolor[HTML]{4285f4}{\textbf{17.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.31\%}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.75\%}}}\\
+\addlinespace
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{13.03\%}} & \textcolor[HTML]{4285f4}{\textbf{34.39\%}} & \textcolor[HTML]{4285f4}{\textbf{6.62\%}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.72\%}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.03\%}} & \textcolor[HTML]{4285f4}{\textbf{3.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.42\%}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.28\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.09\%}}}\\
+\addlinespace
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{6.72\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
 \bottomrule
-\endlastfoot
- &  & all & 11.68\% & 21.6\% & 30.72\% & 15.57\%\\
-\nopagebreak
- &  & backwardation & 11.28\% & 23.51\% & 28.95\% & 13.12\%\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{market}} &  & contango & 12.23\% & 19.96\% & 32.47\% & 17.66\%\\
-\nopagebreak
- &  & all & 1.67\% & 8.24\% & 5.67\% & 4.07\%\\
-\nopagebreak
- &  & backwardation & 1.84\% & 8.81\% & 5.01\% & 5.74\%\\
-\nopagebreak
- & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 2.05\% & 8.25\% & 6.81\% & 3.58\%\\
-\nopagebreak
- &  & all & 4.53\% & 15.14\% & 21.88\% & 9.31\%\\
-\nopagebreak
- &  & backwardation & 4.77\% & 17.25\% & 21.46\% & 8.07\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.85\% & 13.8\% & 22.56\% & 10.53\%\\
-\nopagebreak
- &  & all & 3.02\% & 4\% & 9.1\% & 4.36\%\\
-\nopagebreak
- &  & backwardation & 2.51\% & 4.03\% & 7.14\% & 6.24\%\\
-\nopagebreak
-\multirow[t]{-9}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 4\% & 4.81\% & 12.42\% & 3.88\%\\
-\cmidrule{1-7}\pagebreak[0]
- &  & all & 2.91\% & 3.84\% & 6.21\% & 5.12\%\\
-\nopagebreak
- &  & backwardation & 3.61\% & 2.93\% & 4.99\% & 5.04\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.5\% & 5.21\% & 7.39\% & 5.41\%\\
-\nopagebreak
- &  & all & 5.94\% & 13.15\% & 21.23\% & 8.72\%\\
-\nopagebreak
- &  & backwardation & 6.78\% & 14.01\% & 18.83\% & 8.01\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 5.47\% & 12.78\% & 23.07\% & 9.34\%\\
-\nopagebreak
- &  & all & 3.55\% & 7.41\% & 12.39\% & 4.25\%\\
-\nopagebreak
- &  & backwardation & 3.32\% & 9.77\% & 10.61\% & 3.97\%\\
-\nopagebreak
-\multirow[t]{-9}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.98\% & 5.16\% & 13.83\% & 4.86\%\\
-\cmidrule{1-7}\pagebreak[0]
- &  & all & 1.12\% & 1.46\% & 2.93\% & 0.94\%\\
-\nopagebreak
- &  & backwardation & 1.16\% & 2.17\% & 2.53\% & 1.28\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1.55\% & 2.02\% & 3.6\% & 1.22\%\\
-\nopagebreak
- &  & all & 4.15\% & 6.36\% & 8.39\% & 5.07\%\\
-\nopagebreak
- &  & backwardation & 4.38\% & 8.41\% & 9.91\% & 4.98\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.28\% & 5.73\% & 7.99\% & 5.5\%\\
-\nopagebreak
- &  & all & 2.59\% & 8.79\% & 14.46\% & 4\%\\
-\nopagebreak
- &  & backwardation & 2.78\% & 10.16\% & 10.18\% & 2.69\%\\
-\nopagebreak
-\multirow[t]{-9}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.9\% & 7.9\% & 18.16\% & 6.25\%\\*
+
 \end{longtable}
+
 \endgroup{}
+\end{landscape}
 
@@
 
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}lllrr}
-\caption{\label{tab:co-movement-picks}This table shows the factor 'picks' for the market as well as the long-short factors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-For each factor and period the twenty four US commodities are regressed against the corresponding factor mimicking portfolio and ranked by $R^{2}$.
-The top eight commodities are selected as 'picks' for the corresponding factor and period.
-The table also shows the proportion of time, for each period, each individual pick lives on both legs (long vs.
-short) of its picking factor.
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor.
-Factors construction details are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
-\toprule
-picking factor & period & pick & long & short\\
-\midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-picking factor & period & pick & long & short\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
- &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Wheat-SRW (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 100\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Heating oil (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybean oil (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Gold (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Palladium (XNYM) & 100\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybean oil (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Wheat-SRW (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 100\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Copper (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybean oil (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 100\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Copper (XCEC) & 100\% & 0\%\\
-\nopagebreak
-\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Silver (XCEC) & 100\% & 0\%\\
-\cmidrule{1-5}\pagebreak[0]
- &  & Cattle-feeder (XCME) & 12.28\% & 67.96\%\\
-\nopagebreak
- &  & Cattle-live (XCME) & 16.47\% & 50.3\%\\
-\nopagebreak
- &  & Lean hogs (XCME) & 13.77\% & 58.98\%\\
-\nopagebreak
- &  & Cotton-\#2 (IFUS) & 18.56\% & 46.11\%\\
-\nopagebreak
- &  & Orange juice (IFUS) & 55.39\% & 18.56\%\\
-\nopagebreak
- &  & Gold (XCEC) & 36.83\% & 61.68\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 91.92\% & 2.1\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Silver (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Oats (XCBT) & 97.91\% & 0\%\\
-\nopagebreak
- &  & Cattle-feeder (XCME) & 0\% & 97.49\%\\
-\nopagebreak
- &  & Lean hogs (XCME) & 0\% & 72.38\%\\
-\nopagebreak
- &  & Copper (XCEC) & 28.45\% & 46.44\%\\
-\nopagebreak
- &  & Gold (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Palladium (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 100\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 0\% & 100\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 5.76\% & 46.09\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 52.67\% & 0\%\\
-\nopagebreak
- &  & Copper (XCEC) & 0\% & 81.48\%\\
-\nopagebreak
- &  & Gold (XCEC) & 100\% & 0\%\\
-\nopagebreak
- &  & Palladium (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 100\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Silver (XCEC) & 99.59\% & 0\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 0\% & 62.77\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 34.04\% & 0\%\\
-\nopagebreak
- &  & Wheat-SRW (XCBT) & 0\% & 97.52\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 0\% & 100\%\\
-\nopagebreak
- &  & Gold (XCEC) & 80.14\% & 0\%\\
-\nopagebreak
- &  & Palladium (XNYM) & 100\% & 0\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 96.81\% & 0\%\\
-\nopagebreak
-\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Silver (XCEC) & 57.45\% & 0\%\\
-\cmidrule{1-5}\pagebreak[0]
- &  & Oats (XCBT) & 17.1\% & 50.3\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 19.71\% & 49.1\%\\
-\nopagebreak
- &  & Cattle-live (XCME) & 12.46\% & 58.68\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 82.61\% & 1.2\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 99.71\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 99.71\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 99.71\% & 0\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Palladium (XNYM) & 10.14\% & 52.69\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 0.75\% & 80.09\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 87.97\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 92.48\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 92.11\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 92.11\% & 0\%\\
-\nopagebreak
- &  & Gold (XCEC) & 16.54\% & 37.04\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 19.55\% & 31.02\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 49.25\% & 17.13\%\\
-\nopagebreak
- &  & Soybean oil (XCBT) & 10.61\% & 58.38\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 95.45\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 95.45\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 92.05\% & 0\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 94.7\% & 0\%\\
-\nopagebreak
- &  & Copper (XCEC) & 23.11\% & 35.14\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 51.14\% & 17.84\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Silver (XCEC) & 25.76\% & 34.05\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 14.97\% & 48.33\%\\
-\nopagebreak
- &  & Oats (XCBT) & 19.73\% & 53.53\%\\
-\nopagebreak
- &  & Wheat-SRW (XCBT) & 10.54\% & 43.49\%\\
-\nopagebreak
- &  & Cattle-feeder (XCME) & 26.53\% & 54.65\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 98.64\% & 0\%\\
-\nopagebreak
- &  & Crude oil-WTI (XNYM) & 98.64\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 97.28\% & 0\%\\
-\nopagebreak
-\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Heating oil (XNYM) & 97.28\% & 0\%\\
-\cmidrule{1-5}\pagebreak[0]
- &  & Corn-\#2 yellow (XCBT) & 94.52\% & 1.15\%\\
-\nopagebreak
- &  & Lean hogs (XCME) & 43.8\% & 36.68\%\\
-\nopagebreak
- &  & Cotton-\#2 (IFUS) & 77.81\% & 13.18\%\\
-\nopagebreak
- &  & Sugar-\#11 (IFUS) & 25.07\% & 55.87\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 16.43\% & 60.17\%\\
-\nopagebreak
- &  & Heating oil (XNYM) & 15.56\% & 33.24\%\\
-\nopagebreak
- &  & Palladium (XNYM) & 0\% & 59.03\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash past} & Platinum (XNYM) & 0\% & 89.68\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 17.27\% & 48.18\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 20.45\% & 31.98\%\\
-\nopagebreak
- &  & Cattle-live (XCME) & 19.09\% & 48.18\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 78.18\% & 0\%\\
-\nopagebreak
- &  & Copper (XCEC) & 0\% & 89.88\%\\
-\nopagebreak
- &  & Gold (XCEC) & 0\% & 17\%\\
-\nopagebreak
- &  & Platinum (XNYM) & 0\% & 92.71\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash financialization} & Silver (XCEC) & 0\% & 30.77\%\\
-\nopagebreak
- &  & Soybean meal (XCBT) & 0\% & 82.54\%\\
-\nopagebreak
- &  & Soybeans (XCBT) & 0\% & 58.33\%\\
-\nopagebreak
- &  & Lean hogs (XCME) & 69.84\% & 21.83\%\\
-\nopagebreak
- &  & Cotton-\#2 (IFUS) & 38.1\% & 48.02\%\\
-\nopagebreak
- &  & Sugar-\#11 (IFUS) & 34.52\% & 50.79\%\\
-\nopagebreak
- &  & Natural gas (XNYM) & 76.59\% & 0\%\\
-\nopagebreak
- &  & Gasoline (XNYM) & 8.33\% & 60.32\%\\
-\nopagebreak
- & \multirow[t]{-8}{*}{\raggedright\arraybackslash crisis} & Copper (XCEC) & 0\% & 40.87\%\\
-\nopagebreak
- &  & Corn-\#2 yellow (XCBT) & 89.69\% & 6.77\%\\
-\nopagebreak
- &  & Wheat-SRW (XCBT) & 96.91\% & 0\%\\
-\nopagebreak
- &  & Cattle-feeder (XCME) & 17.87\% & 69.55\%\\
-\nopagebreak
- &  & Cattle-live (XCME) & 27.84\% & 60.9\%\\
-\nopagebreak
- &  & Coffee-C (IFUS) & 100\% & 0\%\\
-\nopagebreak
- &  & Lumber (XCME) & 40.89\% & 39.85\%\\
-\nopagebreak
- &  & Sugar-\#11 (IFUS) & 69.07\% & 20.68\%\\
-\nopagebreak
-\multirow[t]{-32}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-8}{*}{\raggedright\arraybackslash post-crisis} & Natural gas (XNYM) & 71.48\% & 17.29\%\\*
-\end{longtable}
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}llrrrr}
-\caption{\label{tab:co-movement-correlations}This table shows the average pairwise correlation amongst factor picks for each factor and period independently.
-The figures are shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor.
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
-\toprule
-picking factor & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-picking factor & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
- & all & 23.68\% & 34.2\% & 50.07\% & 26.13\%\\
-\nopagebreak
- & backwardation & 22.21\% & 36.28\% & 45.4\% & 22.53\%\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{market}} & contango & 25.31\% & 32.6\% & 52.73\% & 29.07\%\\
-\cmidrule{1-6}\pagebreak[0]
- & all & 8.05\% & 22.94\% & 40.1\% & 19.84\%\\
-\nopagebreak
- & backwardation & 8.4\% & 22.48\% & 43.5\% & 16.63\%\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{CHP}} & contango & 7.64\% & 23.6\% & 38.72\% & 22.32\%\\
-\cmidrule{1-6}\pagebreak[0]
- & all & 12.42\% & 32.35\% & 41.96\% & 16.13\%\\
-\nopagebreak
- & backwardation & 11.62\% & 35.44\% & 41.9\% & 14.44\%\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{open interest}} & contango & 12.99\% & 29.69\% & 42.18\% & 17.75\%\\
-\cmidrule{1-6}\pagebreak[0]
- & all & 7.07\% & 23.41\% & 23.15\% & 8.86\%\\
-\nopagebreak
- & backwardation & 5.63\% & 24.56\% & 18.99\% & 8.37\%\\
-\nopagebreak
-\multirow[t]{-3}{*}{\raggedright\arraybackslash \textbf{term structure}} & contango & 8.3\% & 22.66\% & 26.34\% & 9.15\%\\*
-\end{longtable}
-\endgroup{}
-
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}llllrrrr}
-\caption{\label{tab:co-movement-time-reg-picks-facts-picks}This table shows the average time series $R^{2}$ for models where the returns series for the various sets of factor picks are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the picks.
-For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
- &  &  & all & 32.72\% & 42.33\% & 56.22\% & 36.48\%\\
-\nopagebreak
- &  &  & backwardation & 31.67\% & 43.85\% & 52.22\% & 34.13\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 33.87\% & 41.14\% & 58.62\% & 38.39\%\\
-\nopagebreak
- &  &  & all & 5.61\% & 12.44\% & 6.89\% & 6.83\%\\
-\nopagebreak
- &  &  & backwardation & 5.02\% & 11.4\% & 7.33\% & 5.58\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 7.73\% & 15.34\% & 8.2\% & 9.49\%\\
-\nopagebreak
- &  &  & all & 17.09\% & 27.87\% & 40.38\% & 17.61\%\\
-\nopagebreak
- &  &  & backwardation & 17.36\% & 26.97\% & 33.21\% & 13.37\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 17.39\% & 29.12\% & 44.06\% & 21.69\%\\
-\nopagebreak
- &  &  & all & 16.49\% & 21.39\% & 35.95\% & 16.37\%\\
-\nopagebreak
- &  &  & backwardation & 13.19\% & 25.78\% & 32.18\% & 12.42\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 20.53\% & 18.68\% & 39.1\% & 20.49\%\\
-\nopagebreak
- &  &  & all & 23.2\% & 7.78\% & 11.68\% & 19.69\%\\
-\nopagebreak
- &  &  & backwardation & 24.03\% & 8.65\% & 8.56\% & 19.29\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 22.67\% & 7.38\% & 14.32\% & 20.15\%\\
-\nopagebreak
- &  &  & all & 25.03\% & 26.41\% & 39.29\% & 27.68\%\\
-\nopagebreak
- &  &  & backwardation & 26.05\% & 28.34\% & 34.39\% & 27.3\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 24.42\% & 24.86\% & 41.79\% & 28.25\%\\
-\nopagebreak
- &  &  & all & 23.67\% & 22.99\% & 34.48\% & 17.13\%\\
-\nopagebreak
- &  &  & backwardation & 21.81\% & 26.13\% & 33.14\% & 14.96\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 26.47\% & 20.67\% & 35.71\% & 19.57\%\\
-\nopagebreak
- &  &  & all & 5.92\% & 7.26\% & 4.29\% & 1.98\%\\
-\nopagebreak
- &  &  & backwardation & 6.44\% & 7.24\% & 9.11\% & 1.51\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 5.52\% & 9.23\% & 3.01\% & 2.81\%\\
-\nopagebreak
- &  &  & all & 11.61\% & 24.74\% & 35.76\% & 17.54\%\\
-\nopagebreak
- &  &  & backwardation & 10.72\% & 27.25\% & 33.61\% & 18.51\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 12.92\% & 23.08\% & 37.43\% & 17.53\%\\
-\nopagebreak
- &  &  & all & 16.22\% & 24.13\% & 35.98\% & 20.6\%\\
-\nopagebreak
- &  &  & backwardation & 17.07\% & 25.62\% & 30.3\% & 16.38\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 16.15\% & 24.36\% & 39.28\% & 23.56\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 18.62\% & 38.1\% & 47.61\% & 28.42\%\\
-\nopagebreak
- &  &  & backwardation & 19.04\% & 36.9\% & 50.48\% & 25.17\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 18.39\% & 39.54\% & 46.48\% & 30.9\%\\
-\nopagebreak
- &  &  & all & 7.19\% & 21.38\% & 13\% & 14.34\%\\
-\nopagebreak
- &  &  & backwardation & 6.78\% & 19.58\% & 12.57\% & 18.44\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 8.32\% & 23.66\% & 13.51\% & 14.5\%\\
-\nopagebreak
- &  &  & all & 10.45\% & 31.09\% & 38.06\% & 24.09\%\\
-\nopagebreak
- &  &  & backwardation & 11.18\% & 30.55\% & 41.19\% & 22.78\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 10.21\% & 31.88\% & 36.81\% & 25.3\%\\
-\nopagebreak
- &  &  & all & 8.27\% & 9.84\% & 15.7\% & 10.44\%\\
-\nopagebreak
- &  &  & backwardation & 8.12\% & 9.87\% & 16.25\% & 15.17\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 9.33\% & 9.98\% & 15.57\% & 11.21\%\\
-\nopagebreak
- &  &  & all & 1.47\% & 4.76\% & 9.16\% & 11.59\%\\
-\nopagebreak
- &  &  & backwardation & 2.34\% & 4.23\% & 7.98\% & 11.57\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1\% & 5.64\% & 10.58\% & 11.9\%\\
-\nopagebreak
- &  &  & all & 6.27\% & 24.94\% & 25.22\% & 12.58\%\\
-\nopagebreak
- &  &  & backwardation & 6.82\% & 26.16\% & 19.14\% & 12.47\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 6.42\% & 24.13\% & 28.34\% & 12.75\%\\
-\nopagebreak
- &  &  & all & 5.59\% & 13.44\% & 35.65\% & 14.08\%\\
-\nopagebreak
- &  &  & backwardation & 6.49\% & 16.16\% & 39.06\% & 12.01\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 5.2\% & 11.43\% & 34.37\% & 16.51\%\\
-\nopagebreak
- &  &  & all & 3.5\% & 5.28\% & 8.11\% & 5.96\%\\
-\nopagebreak
- &  &  & backwardation & 3.79\% & 8.13\% & 9.48\% & 6.88\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 4.9\% & 4.01\% & 7.64\% & 5.86\%\\
-\nopagebreak
- &  &  & all & 7.45\% & 9.78\% & 15.63\% & 12.48\%\\
-\nopagebreak
- &  &  & backwardation & 7.12\% & 9.85\% & 15.97\% & 11.94\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.85\% & 10.75\% & 15.59\% & 13.31\%\\
-\nopagebreak
- &  &  & all & 6.26\% & 15.74\% & 28.56\% & 13.03\%\\
-\nopagebreak
- &  &  & backwardation & 6.51\% & 19.46\% & 28.59\% & 10.21\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 6.58\% & 13.22\% & 28.76\% & 17.2\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 28.43\% & 41.66\% & 49.79\% & 29.2\%\\
-\nopagebreak
- &  &  & backwardation & 28\% & 44.29\% & 49.09\% & 27.73\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 28.84\% & 39.55\% & 50.49\% & 30.43\%\\
-\nopagebreak
- &  &  & all & 9.58\% & 14.48\% & 11.28\% & 9.83\%\\
-\nopagebreak
- &  &  & backwardation & 9.81\% & 13.64\% & 11.15\% & 10.3\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 9.47\% & 16.17\% & 11.62\% & 11.76\%\\
-\nopagebreak
- &  &  & all & 12.63\% & 27.21\% & 32.29\% & 18.56\%\\
-\nopagebreak
- &  &  & backwardation & 12.41\% & 28.26\% & 35.25\% & 15.67\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 13.06\% & 26.85\% & 31.22\% & 20.78\%\\
-\nopagebreak
- &  &  & all & 10.71\% & 23.23\% & 16.94\% & 8.09\%\\
-\nopagebreak
- &  &  & backwardation & 9.72\% & 24.06\% & 16.56\% & 13.98\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 11.79\% & 23.43\% & 17.35\% & 9.21\%\\
-\nopagebreak
- &  &  & all & 18.25\% & 15.83\% & 9.45\% & 11.79\%\\
-\nopagebreak
- &  &  & backwardation & 19.96\% & 14.24\% & 6.39\% & 12.24\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 16.97\% & 17.33\% & 11.49\% & 11.87\%\\
-\nopagebreak
- &  &  & all & 24.83\% & 30.24\% & 33.8\% & 13.61\%\\
-\nopagebreak
- &  &  & backwardation & 25.07\% & 31.83\% & 26.7\% & 13.11\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 24.77\% & 29.24\% & 37.38\% & 14.3\%\\
-\nopagebreak
- &  &  & all & 8.32\% & 17.57\% & 31.68\% & 11.76\%\\
-\nopagebreak
- &  &  & backwardation & 7.65\% & 17.99\% & 32.14\% & 11.62\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 9.17\% & 17.62\% & 31.72\% & 12.44\%\\
-\nopagebreak
- &  &  & all & 2.3\% & 6.95\% & 7.93\% & 3.63\%\\
-\nopagebreak
- &  &  & backwardation & 3.56\% & 5.35\% & 10.01\% & 5.48\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.61\% & 8.26\% & 7.22\% & 3.24\%\\
-\nopagebreak
- &  &  & all & 7.54\% & 20.81\% & 17.64\% & 12.3\%\\
-\nopagebreak
- &  &  & backwardation & 7.45\% & 22.37\% & 16.44\% & 14.08\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 7.84\% & 19.88\% & 18.58\% & 11.56\%\\
-\nopagebreak
- &  &  & all & 8.85\% & 19.61\% & 32.42\% & 11.02\%\\
-\nopagebreak
- &  &  & backwardation & 12.38\% & 24.66\% & 32.66\% & 7.46\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 7.69\% & 16.26\% & 32.72\% & 14.76\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 20\% & 33.71\% & 33.64\% & 19.37\%\\
-\nopagebreak
- &  &  & backwardation & 18.65\% & 35.1\% & 29.47\% & 19.58\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 21.25\% & 32.72\% & 36.91\% & 19.29\%\\
-\nopagebreak
- &  &  & all & 4.68\% & 7.97\% & 8.75\% & 3.74\%\\
-\nopagebreak
- &  &  & backwardation & 4.7\% & 7.11\% & 10.38\% & 8.99\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 5.19\% & 9.3\% & 8.01\% & 3.69\%\\
-\nopagebreak
- &  &  & all & 11.93\% & 28.13\% & 22.6\% & 7.81\%\\
-\nopagebreak
- &  &  & backwardation & 14.34\% & 27.9\% & 21.19\% & 8.65\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 10.77\% & 28.61\% & 24.63\% & 8.45\%\\
-\nopagebreak
- &  &  & all & 5.54\% & 9.15\% & 13.2\% & 5.52\%\\
-\nopagebreak
- &  &  & backwardation & 4.6\% & 8.86\% & 12.38\% & 11.89\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 7.11\% & 10.4\% & 14.58\% & 5.3\%\\
-\nopagebreak
- &  &  & all & 8.62\% & 8.02\% & 5.96\% & 10.47\%\\
-\nopagebreak
- &  &  & backwardation & 9.54\% & 7.27\% & 6.5\% & 10.93\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 7.77\% & 8.87\% & 6.99\% & 10.46\%\\
-\nopagebreak
- &  &  & all & 13.53\% & 15.51\% & 16.65\% & 12.44\%\\
-\nopagebreak
- &  &  & backwardation & 13.3\% & 16.33\% & 12.47\% & 12.45\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 13.92\% & 15.23\% & 20.05\% & 12.48\%\\
-\nopagebreak
- &  &  & all & 5.94\% & 14.55\% & 14.78\% & 7.79\%\\
-\nopagebreak
- &  &  & backwardation & 5.61\% & 16.34\% & 13.08\% & 8.88\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 6.29\% & 13.09\% & 17.1\% & 7.81\%\\
-\nopagebreak
- &  &  & all & 5.1\% & 8.38\% & 8.8\% & 6.83\%\\
-\nopagebreak
- &  &  & backwardation & 7.27\% & 6.31\% & 8.91\% & 9.15\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 5.15\% & 10.07\% & 9.39\% & 5.96\%\\
-\nopagebreak
- &  &  & all & 7.6\% & 12.13\% & 11.03\% & 7.86\%\\
-\nopagebreak
- &  &  & backwardation & 7.13\% & 12.38\% & 10.13\% & 9.57\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.38\% & 12.17\% & 12.68\% & 7.96\%\\
-\nopagebreak
- &  &  & all & 6.03\% & 16.11\% & 20.26\% & 9.96\%\\
-\nopagebreak
- &  &  & backwardation & 9.07\% & 15.15\% & 15.34\% & 10.19\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 6.06\% & 17.5\% & 24.31\% & 10.3\%\\*
-\end{longtable}
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}llllrrrr}
-\caption{\label{tab:co-movement-time-reg-US-facts-picks}This table shows the average time series $R^{2}$ for models where the returns series for the twenty four US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities.
-For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
- &  &  & all & 11.67\% & 21.24\% & 28.16\% & 14.85\%\\
-\nopagebreak
- &  &  & backwardation & 11.34\% & 22.98\% & 26.68\% & 13.36\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 12.09\% & 19.79\% & 29.81\% & 16.31\%\\
-\nopagebreak
- &  &  & all & 1.96\% & 5.44\% & 2.52\% & 3.24\%\\
-\nopagebreak
- &  &  & backwardation & 1.83\% & 4.93\% & 3.16\% & 4.06\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 2.85\% & 6.82\% & 2.83\% & 3.73\%\\
-\nopagebreak
- &  &  & all & 6.64\% & 13.42\% & 18.81\% & 7.99\%\\
-\nopagebreak
- &  &  & backwardation & 6.99\% & 13.31\% & 16.43\% & 7.93\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 6.6\% & 13.78\% & 20.61\% & 9.08\%\\
-\nopagebreak
- &  &  & all & 6.12\% & 10.75\% & 18.35\% & 7.61\%\\
-\nopagebreak
- &  &  & backwardation & 4.75\% & 13.22\% & 16.28\% & 5.87\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 7.85\% & 9.05\% & 20.59\% & 9.7\%\\
-\nopagebreak
- &  &  & all & 8.25\% & 3.72\% & 4.49\% & 6.9\%\\
-\nopagebreak
- &  &  & backwardation & 8.64\% & 4.35\% & 3.3\% & 6.81\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 8.08\% & 3.44\% & 5.7\% & 7.11\%\\
-\nopagebreak
- &  &  & all & 8.51\% & 12.69\% & 18.26\% & 9.71\%\\
-\nopagebreak
- &  &  & backwardation & 8.85\% & 13.94\% & 17.03\% & 9.45\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.4\% & 11.82\% & 19.42\% & 10.13\%\\
-\nopagebreak
- &  &  & all & 9.47\% & 11.69\% & 17.99\% & 8.18\%\\
-\nopagebreak
- &  &  & backwardation & 8.98\% & 14.42\% & 17.72\% & 6.81\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 10.39\% & 9.76\% & 18.66\% & 9.79\%\\
-\nopagebreak
- &  &  & all & 2.1\% & 3.26\% & 1.76\% & 0.79\%\\
-\nopagebreak
- &  &  & backwardation & 2.31\% & 3.4\% & 4.15\% & 0.77\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.06\% & 4.12\% & 1.21\% & 1.05\%\\
-\nopagebreak
- &  &  & all & 4.51\% & 13.46\% & 17.75\% & 7.25\%\\
-\nopagebreak
- &  &  & backwardation & 4.26\% & 15.48\% & 17.21\% & 7.69\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 5.01\% & 12.06\% & 18.8\% & 7.44\%\\
-\nopagebreak
- &  &  & all & 5.69\% & 11.42\% & 17.51\% & 7.68\%\\
-\nopagebreak
- &  &  & backwardation & 5.91\% & 12.62\% & 15.24\% & 6.11\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 5.87\% & 11.09\% & 19.48\% & 8.94\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 6.77\% & 16.67\% & 25.41\% & 12.77\%\\
-\nopagebreak
- &  &  & backwardation & 6.85\% & 17.81\% & 24.61\% & 10.81\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 6.84\% & 15.98\% & 26.51\% & 14.52\%\\
-\nopagebreak
- &  &  & all & 2.54\% & 8.73\% & 4.39\% & 5.06\%\\
-\nopagebreak
- &  &  & backwardation & 2.46\% & 8.28\% & 4.36\% & 6.61\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 3.04\% & 9.5\% & 4.67\% & 5.16\%\\
-\nopagebreak
- &  &  & all & 3.9\% & 12.72\% & 17.36\% & 9.4\%\\
-\nopagebreak
- &  &  & backwardation & 4.13\% & 13.64\% & 19.11\% & 8.14\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4\% & 12.3\% & 16.6\% & 10.8\%\\
-\nopagebreak
- &  &  & all & 2.83\% & 3.82\% & 7.51\% & 4.17\%\\
-\nopagebreak
- &  &  & backwardation & 2.82\% & 3.72\% & 7.27\% & 6.11\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.31\% & 4.19\% & 7.95\% & 4.3\%\\
-\nopagebreak
- &  &  & all & 0.54\% & 1.68\% & 4.1\% & 4.1\%\\
-\nopagebreak
- &  &  & backwardation & 0.9\% & 1.54\% & 2.96\% & 4.14\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.38\% & 2.27\% & 5.48\% & 4.26\%\\
-\nopagebreak
- &  &  & all & 2.36\% & 10.1\% & 15.23\% & 4.56\%\\
-\nopagebreak
- &  &  & backwardation & 2.57\% & 10.72\% & 10.19\% & 4.46\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 2.45\% & 9.77\% & 18.64\% & 4.71\%\\
-\nopagebreak
- &  &  & all & 1.94\% & 6.35\% & 17.65\% & 6.96\%\\
-\nopagebreak
- &  &  & backwardation & 2.25\% & 8.71\% & 17.99\% & 5.62\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 1.88\% & 4.71\% & 17.98\% & 8.46\%\\
-\nopagebreak
- &  &  & all & 1.31\% & 1.97\% & 2.83\% & 2.2\%\\
-\nopagebreak
- &  &  & backwardation & 1.59\% & 2.9\% & 3.32\% & 2.55\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1.85\% & 1.65\% & 2.74\% & 2.37\%\\
-\nopagebreak
- &  &  & all & 2.62\% & 4.52\% & 8.05\% & 5.5\%\\
-\nopagebreak
- &  &  & backwardation & 2.65\% & 5.03\% & 7.26\% & 5.11\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 3.08\% & 4.51\% & 8.86\% & 6.15\%\\
-\nopagebreak
- &  &  & all & 2.43\% & 7\% & 15.51\% & 6.71\%\\
-\nopagebreak
- &  &  & backwardation & 2.49\% & 9.01\% & 13.83\% & 4.78\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.94\% & 5.61\% & 16.98\% & 9.57\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 10.6\% & 18.43\% & 26.36\% & 12.03\%\\
-\nopagebreak
- &  &  & backwardation & 10.25\% & 20.18\% & 25.13\% & 10.91\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 11.05\% & 17.11\% & 27.83\% & 13.17\%\\
-\nopagebreak
- &  &  & all & 4\% & 5.34\% & 4.54\% & 3.71\%\\
-\nopagebreak
- &  &  & backwardation & 4.1\% & 4.98\% & 4.37\% & 3.61\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 4.02\% & 6.14\% & 4.86\% & 4.74\%\\
-\nopagebreak
- &  &  & all & 6.78\% & 13.48\% & 18.66\% & 7.42\%\\
-\nopagebreak
- &  &  & backwardation & 6.63\% & 14.34\% & 20.18\% & 5.9\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 7.12\% & 13.11\% & 18.16\% & 8.77\%\\
-\nopagebreak
- &  &  & all & 3.94\% & 9.11\% & 7.49\% & 3.11\%\\
-\nopagebreak
- &  &  & backwardation & 3.56\% & 9.31\% & 7.08\% & 5.61\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 4.45\% & 9.44\% & 8.05\% & 3.32\%\\
-\nopagebreak
- &  &  & all & 6.4\% & 5.64\% & 3.37\% & 4.11\%\\
-\nopagebreak
- &  &  & backwardation & 6.93\% & 5.3\% & 2.53\% & 4.35\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 6.07\% & 6.09\% & 4.25\% & 4.1\%\\
-\nopagebreak
- &  &  & all & 8.48\% & 12.35\% & 15.81\% & 4.76\%\\
-\nopagebreak
- &  &  & backwardation & 8.5\% & 13.24\% & 11.7\% & 4.54\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 8.63\% & 11.82\% & 18.57\% & 5.08\%\\
-\nopagebreak
- &  &  & all & 4.07\% & 12.5\% & 19.46\% & 4.99\%\\
-\nopagebreak
- &  &  & backwardation & 3.64\% & 13.52\% & 18.93\% & 4.95\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 4.64\% & 11.82\% & 20.29\% & 5.39\%\\
-\nopagebreak
- &  &  & all & 0.83\% & 2.54\% & 3.13\% & 1.45\%\\
-\nopagebreak
- &  &  & backwardation & 1.3\% & 2.22\% & 3.71\% & 2.52\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 1.13\% & 2.95\% & 3.02\% & 1.16\%\\
-\nopagebreak
- &  &  & all & 3.09\% & 7.65\% & 8.04\% & 5.26\%\\
-\nopagebreak
- &  &  & backwardation & 2.8\% & 8.53\% & 7.11\% & 5.96\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 3.73\% & 7.22\% & 9\% & 5.21\%\\
-\nopagebreak
- &  &  & all & 3.55\% & 9.48\% & 16.63\% & 4.56\%\\
-\nopagebreak
- &  &  & backwardation & 4.8\% & 12.03\% & 15.62\% & 3.13\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.21\% & 7.83\% & 17.77\% & 6.32\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 9.13\% & 18.37\% & 25.17\% & 8.95\%\\
-\nopagebreak
- &  &  & backwardation & 8.79\% & 20.14\% & 22.77\% & 8.19\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 9.55\% & 16.99\% & 27.12\% & 10.02\%\\
-\nopagebreak
- &  &  & all & 1.98\% & 3.42\% & 3.3\% & 1.38\%\\
-\nopagebreak
- &  &  & backwardation & 1.89\% & 3.08\% & 3.79\% & 3.4\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 2.33\% & 4.07\% & 3.17\% & 1.32\%\\
-\nopagebreak
- &  &  & all & 4.8\% & 13.48\% & 15.65\% & 3.14\%\\
-\nopagebreak
- &  &  & backwardation & 5.63\% & 14.34\% & 13.9\% & 3.23\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.55\% & 13.11\% & 17.32\% & 3.58\%\\
-\nopagebreak
- &  &  & all & 2.58\% & 5.81\% & 7.05\% & 2.51\%\\
-\nopagebreak
- &  &  & backwardation & 1.91\% & 5.91\% & 5.92\% & 5.04\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 3.55\% & 6.2\% & 8.3\% & 2.29\%\\
-\nopagebreak
- &  &  & all & 3.93\% & 3.97\% & 2.83\% & 3.6\%\\
-\nopagebreak
- &  &  & backwardation & 4.31\% & 3.56\% & 2.88\% & 3.87\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 3.67\% & 4.63\% & 3.53\% & 3.57\%\\
-\nopagebreak
- &  &  & all & 6.42\% & 8.62\% & 12.51\% & 4.45\%\\
-\nopagebreak
- &  &  & backwardation & 6.24\% & 9.01\% & 9.32\% & 4.44\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 6.73\% & 8.59\% & 14.98\% & 4.53\%\\
-\nopagebreak
- &  &  & all & 2.49\% & 8.49\% & 10.4\% & 3.46\%\\
-\nopagebreak
- &  &  & backwardation & 2.6\% & 10.34\% & 8.32\% & 3.83\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.58\% & 6.84\% & 12.73\% & 3.64\%\\
-\nopagebreak
- &  &  & all & 2.17\% & 3.38\% & 3.69\% & 2.53\%\\
-\nopagebreak
- &  &  & backwardation & 3.39\% & 2.69\% & 3.48\% & 3.52\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 2.06\% & 4.03\% & 4.16\% & 2.16\%\\
-\nopagebreak
- &  &  & all & 3.91\% & 5.88\% & 5.59\% & 3.55\%\\
-\nopagebreak
- &  &  & backwardation & 3.65\% & 6.37\% & 4.61\% & 3.98\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 4.38\% & 5.7\% & 6.74\% & 3.94\%\\
-\nopagebreak
- &  &  & all & 2.44\% & 7.8\% & 12.81\% & 3.63\%\\
-\nopagebreak
- &  &  & backwardation & 4.14\% & 8.02\% & 9.12\% & 3.54\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 2.27\% & 8.05\% & 15.82\% & 4.21\%\\*
-\end{longtable}
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{9}{11}\selectfont
-
-\begin{longtable}[t]{>{}llllrrrr}
-\caption{\label{tab:co-movement-time-reg-UK-facts-picks}This table shows the average time series $R^{2}$ for models where the returns series for the six UK metals are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the six UK metals.
-For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks.
-For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs.
-short).
-The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \ref{co-movement-methods} while the results are discussed in section \ref{co-movement-results}.}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endfirsthead
-\caption[]{\textit{(continued)}}\\
-\toprule
-picking factor & factor & leg & regime & past & financialisation & crisis & post-crisis\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
- &  &  & all & 0.25\% & 10.17\% & 31.69\% & 11.52\%\\
-\nopagebreak
- &  &  & backwardation & 0.32\% & 11.66\% & 31.95\% & 8.64\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 0.3\% & 9.16\% & 31.72\% & 14.26\%\\
-\nopagebreak
- &  &  & all & 0.06\% & 3.39\% & 0.42\% & 0.38\%\\
-\nopagebreak
- &  &  & backwardation & 0.36\% & 1.84\% & 0.26\% & 0.25\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.05\% & 5.36\% & 0.66\% & 0.82\%\\
-\nopagebreak
- &  &  & all & 0.15\% & 13.12\% & 18.65\% & 5.45\%\\
-\nopagebreak
- &  &  & backwardation & 0.58\% & 12.24\% & 18.24\% & 5.07\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.1\% & 14.17\% & 19.06\% & 5.98\%\\
-\nopagebreak
- &  &  & all & 0.05\% & 3\% & 24.38\% & 16.07\%\\
-\nopagebreak
- &  &  & backwardation & 0.11\% & 4.23\% & 14.79\% & 6.56\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.06\% & 2.24\% & 32.21\% & 26.59\%\\
-\nopagebreak
- &  &  & all & 0.04\% & 0.83\% & 1.45\% & 0.07\%\\
-\nopagebreak
- &  &  & backwardation & 0.05\% & 1.4\% & 0.07\% & 0.03\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.2\% & 0.55\% & 3.21\% & 0.15\%\\
-\nopagebreak
- &  &  & all & 0.11\% & 6.59\% & 17.68\% & 2.57\%\\
-\nopagebreak
- &  &  & backwardation & 0.17\% & 7.76\% & 17.27\% & 1.58\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.17\% & 5.85\% & 18.2\% & 3.57\%\\
-\nopagebreak
- &  &  & all & 0.05\% & 3.99\% & 17.16\% & 6.86\%\\
-\nopagebreak
- &  &  & backwardation & 0.39\% & 4.23\% & 19.91\% & 3.79\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.09\% & 3.85\% & 15.74\% & 10.3\%\\
-\nopagebreak
- &  &  & all & 0.1\% & 1.82\% & 0.98\% & 0.17\%\\
-\nopagebreak
- &  &  & backwardation & 0.42\% & 1.22\% & 0.04\% & 0.35\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.06\% & 2.64\% & 2.2\% & 0.11\%\\
-\nopagebreak
- &  &  & all & 0.26\% & 1.85\% & 11.63\% & 2.82\%\\
-\nopagebreak
- &  &  & backwardation & 1.06\% & 2.98\% & 11.17\% & 1.53\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.03\% & 1.24\% & 12.09\% & 4.32\%\\
-\nopagebreak
- &  &  & all & 0.03\% & 5.78\% & 20.53\% & 3.27\%\\
-\nopagebreak
- &  &  & backwardation & 0.1\% & 5.75\% & 18.66\% & 2.59\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{market}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.12\% & 6.04\% & 21.67\% & 4.01\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 1.55\% & 20.13\% & 34.54\% & 7.43\%\\
-\nopagebreak
- &  &  & backwardation & 1.53\% & 20.93\% & 35.18\% & 5.21\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 1.75\% & 19.83\% & 34.3\% & 9.41\%\\
-\nopagebreak
- &  &  & all & 0.07\% & 5.5\% & 0.47\% & 2.12\%\\
-\nopagebreak
- &  &  & backwardation & 0.12\% & 4.05\% & 1.15\% & 1.4\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.09\% & 7.36\% & 0.25\% & 2.78\%\\
-\nopagebreak
- &  &  & all & 1.02\% & 10.98\% & 21.81\% & 8.99\%\\
-\nopagebreak
- &  &  & backwardation & 0.77\% & 10.77\% & 25.33\% & 5.57\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 1.36\% & 11.39\% & 19.89\% & 12.11\%\\
-\nopagebreak
- &  &  & all & 0.41\% & 0.25\% & 6.19\% & 0.19\%\\
-\nopagebreak
- &  &  & backwardation & 0.21\% & 0.47\% & 5.55\% & 0.24\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.61\% & 0.22\% & 6.67\% & 0.2\%\\
-\nopagebreak
- &  &  & all & 0.03\% & 0.64\% & 0.06\% & 0.27\%\\
-\nopagebreak
- &  &  & backwardation & 0.21\% & 0.06\% & 1.07\% & 0.12\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.08\% & 1.68\% & 0.18\% & 1.33\%\\
-\nopagebreak
- &  &  & all & 0.28\% & 10.41\% & 15.26\% & 0.52\%\\
-\nopagebreak
- &  &  & backwardation & 0.39\% & 10.56\% & 10.18\% & 0.82\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.34\% & 10.47\% & 18.21\% & 0.38\%\\
-\nopagebreak
- &  &  & all & 0.31\% & 8.77\% & 29.79\% & 4.53\%\\
-\nopagebreak
- &  &  & backwardation & 0.25\% & 12.85\% & 30.49\% & 1.57\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.49\% & 5.85\% & 29.59\% & 8.33\%\\
-\nopagebreak
- &  &  & all & 0.05\% & 4.73\% & 0.83\% & 0.6\%\\
-\nopagebreak
- &  &  & backwardation & 0.1\% & 4.5\% & 0.6\% & 1.11\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.27\% & 5.11\% & 0.95\% & 0.31\%\\
-\nopagebreak
- &  &  & all & 0.32\% & 1.38\% & 5.13\% & 0.65\%\\
-\nopagebreak
- &  &  & backwardation & 0.2\% & 1.98\% & 4.85\% & 0.44\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.58\% & 1.03\% & 5.35\% & 0.86\%\\
-\nopagebreak
- &  &  & all & 0.26\% & 19.23\% & 18.98\% & 3.91\%\\
-\nopagebreak
- &  &  & backwardation & 0.48\% & 21.81\% & 17.8\% & 4.62\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{CHP}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.22\% & 17.21\% & 19.65\% & 3.4\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 0.31\% & 8.13\% & 34.43\% & 3.37\%\\
-\nopagebreak
- &  &  & backwardation & 0.35\% & 9.97\% & 35.43\% & 1.72\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 0.39\% & 6.8\% & 34.06\% & 5.08\%\\
-\nopagebreak
- &  &  & all & 0.02\% & 1.39\% & 0.15\% & 1.38\%\\
-\nopagebreak
- &  &  & backwardation & 0.06\% & 0.83\% & 0.45\% & 0.45\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.07\% & 2.07\% & 0.11\% & 2.46\%\\
-\nopagebreak
- &  &  & all & 0.11\% & 11.35\% & 19.64\% & 2.84\%\\
-\nopagebreak
- &  &  & backwardation & 0.29\% & 11.19\% & 23.58\% & 1.06\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.07\% & 11.68\% & 17.62\% & 4.84\%\\
-\nopagebreak
- &  &  & all & 0.15\% & 1.41\% & 5.91\% & 0.21\%\\
-\nopagebreak
- &  &  & backwardation & 0.17\% & 1.89\% & 5.05\% & 0.25\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.24\% & 1.11\% & 6.54\% & 0.2\%\\
-\nopagebreak
- &  &  & all & 0.04\% & 0.37\% & 0.03\% & 0.16\%\\
-\nopagebreak
- &  &  & backwardation & 0.05\% & 0.3\% & 0.33\% & 0.46\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.15\% & 0.46\% & 0.13\% & 0.09\%\\
-\nopagebreak
- &  &  & all & 0.2\% & 5.54\% & 15.97\% & 0.62\%\\
-\nopagebreak
- &  &  & backwardation & 0.14\% & 6.38\% & 12.59\% & 0.89\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.38\% & 5.01\% & 17.83\% & 0.53\%\\
-\nopagebreak
- &  &  & all & 0.14\% & 7.03\% & 30.65\% & 0.26\%\\
-\nopagebreak
- &  &  & backwardation & 0.35\% & 7.6\% & 30.31\% & 0.07\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.08\% & 6.65\% & 30.96\% & 0.9\%\\
-\nopagebreak
- &  &  & all & 0.06\% & 0.1\% & 1.96\% & 0.05\%\\
-\nopagebreak
- &  &  & backwardation & 0.31\% & 0.2\% & 1.75\% & 0.12\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.07\% & 0.15\% & 2.05\% & 0.06\%\\
-\nopagebreak
- &  &  & all & 0.19\% & 1.2\% & 4.58\% & 1.01\%\\
-\nopagebreak
- &  &  & backwardation & 0.7\% & 2.21\% & 4.31\% & 0.29\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.06\% & 0.69\% & 4.78\% & 2.14\%\\
-\nopagebreak
- &  &  & all & 0.07\% & 3.46\% & 22.01\% & 0.93\%\\
-\nopagebreak
- &  &  & backwardation & 0.14\% & 4.11\% & 21.24\% & 0.08\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{open interest}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.08\% & 3.05\% & 22.44\% & 2.18\%\\
-\cmidrule{1-8}\pagebreak[0]
- &  &  & all & 0.75\% & 15.9\% & 28.49\% & 1.27\%\\
-\nopagebreak
- &  &  & backwardation & 0.59\% & 17.08\% & 27.92\% & 0.43\%\\
-\nopagebreak
- & \multirow[t]{-3}{*}{\raggedright\arraybackslash market} &  & contango & 0.94\% & 15.1\% & 28.9\% & 2.52\%\\
-\nopagebreak
- &  &  & all & 0.04\% & 0.34\% & 0.03\% & 0.03\%\\
-\nopagebreak
- &  &  & backwardation & 0.09\% & 0.33\% & 0.06\% & 0.11\%\\
-\nopagebreak
- &  & \multirow[t]{-6}{*}{\raggedright\arraybackslash factor} & contango & 0.03\% & 0.46\% & 0.05\% & 0.11\%\\
-\nopagebreak
- &  &  & all & 0.68\% & 11.35\% & 10.54\% & 0.44\%\\
-\nopagebreak
- &  &  & backwardation & 0.4\% & 11.19\% & 8.88\% & 0.57\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 1\% & 11.68\% & 11.43\% & 0.34\%\\
-\nopagebreak
- &  &  & all & 0.34\% & 6.03\% & 5.82\% & 0.25\%\\
-\nopagebreak
- &  &  & backwardation & 0.18\% & 6.06\% & 3.33\% & 0.13\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash CHP} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.53\% & 6.1\% & 7.87\% & 0.4\%\\
-\nopagebreak
- &  &  & all & 0.05\% & 0.08\% & 0.27\% & 0.07\%\\
-\nopagebreak
- &  &  & backwardation & 0.03\% & 0.13\% & 0.05\% & 0.51\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.26\% & 0.33\% & 0.67\% & 0.25\%\\
-\nopagebreak
- &  &  & all & 0.38\% & 3.41\% & 11.21\% & 0.29\%\\
-\nopagebreak
- &  &  & backwardation & 0.16\% & 3.72\% & 7.67\% & 0.6\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.75\% & 3.24\% & 13.44\% & 0.18\%\\
-\nopagebreak
- &  &  & all & 0.19\% & 7.89\% & 11.78\% & 0.3\%\\
-\nopagebreak
- &  &  & backwardation & 0.34\% & 10.15\% & 8.1\% & 0.07\%\\
-\nopagebreak
- & \multirow[t]{-9}{*}{\raggedright\arraybackslash open interest} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.13\% & 6.06\% & 15.31\% & 1.33\%\\
-\nopagebreak
- &  &  & all & 0.05\% & 2.34\% & 1.67\% & 0.3\%\\
-\nopagebreak
- &  &  & backwardation & 0.09\% & 1.07\% & 0.86\% & 0.35\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash factor} & contango & 0.04\% & 3.61\% & 2.43\% & 0.31\%\\
-\nopagebreak
- &  &  & all & 0.29\% & 0.88\% & 2.66\% & 0.92\%\\
-\nopagebreak
- &  &  & backwardation & 0.44\% & 1.81\% & 1.5\% & 0.44\%\\
-\nopagebreak
- &  & \multirow[t]{-3}{*}{\raggedright\arraybackslash long} & contango & 0.22\% & 0.44\% & 3.64\% & 1.65\%\\
-\nopagebreak
- &  &  & all & 0.09\% & 13.93\% & 11.04\% & 0.17\%\\
-\nopagebreak
- &  &  & backwardation & 0.08\% & 10.91\% & 6.36\% & 0.06\%\\
-\nopagebreak
-\multirow[t]{-30}{*}{\raggedright\arraybackslash \textbf{term structure}} & \multirow[t]{-9}{*}{\raggedright\arraybackslash term structure} & \multirow[t]{-3}{*}{\raggedright\arraybackslash short} & contango & 0.11\% & 16.59\% & 14.67\% & 0.6\%\\*
-\end{longtable}
-\endgroup{}
-
-\restoregeometry\newpage
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-acharya_limits_2013}{}%
-Acharya, V.V., Lochstoer, L.A., Ramadorai, T., 2013. Limits to arbitrage and hedging: Evidence from commodity markets. Journal of Financial Economics 109, 441--465.
-
-\leavevmode\hypertarget{ref-asness_devil_2013}{}%
-Asness, C., Frazzini, A., 2013. The devil in hml's details. The Journal of Portfolio Management 39, 49--68.
-
-\leavevmode\hypertarget{ref-asness_fact_2015}{}%
-Asness, C., Frazzini, A., Israel, R., Moskowitz, T., 2015. Fact, fiction, and value investing. The Journal of Portfolio Management 42, 34--52.
-
-\leavevmode\hypertarget{ref-asness_quality_2019}{}%
-Asness, C.S., Frazzini, A., Pedersen, L.H., 2019. Quality minus junk. Review of Accounting Studies 24, 34--112.
-
-\leavevmode\hypertarget{ref-baker_financialisation_2014}{}%
-Baker, S.D., 2014. The financialization of storable commodities (SSRN Scholarly Paper No. ID 2348333). Social Science Research Network, Rochester, NY.
-
-\leavevmode\hypertarget{ref-bakshi_understanding_2019}{}%
-Bakshi, G., Gao, X., Rossi, A.G., 2019. Understanding the sources of risk underlying the cross section of commodity returns. Management Science 65, 619--641.
-
-\leavevmode\hypertarget{ref-basak_model_2016}{}%
-Basak, S., Pavlova, A., 2016. A model of financialization of commodities. The Journal of Finance 71, 1511--1556.
-
-\leavevmode\hypertarget{ref-basu_definancialisation}{}%
-Basu, D., Bauthéac, O., 2021. Commodity definancialisation. Working paper.
-
-\leavevmode\hypertarget{ref-basu_capturing_2013}{}%
-Basu, D., Miffre, J., 2013. Capturing the risk premium of commodity futures: The role of hedging pressure. Journal of Banking \& Finance 37, 2652--2664.
-
-\leavevmode\hypertarget{ref-bohl_does_2013}{}%
-Bohl, M.T., Stephan, P.M., 2013. Does futures speculation destabilize spot prices? New evidence for commodity markets. Journal of Agricultural and Applied Economics 45, 595--616.
-
-\leavevmode\hypertarget{ref-boons_stock_2012}{}%
-Boons, M., De Roon, F., Szymanowska, M., 2012. The stock market price of commodity risk, in: AFA 2012 Chicago Meetings Paper.
-
-\leavevmode\hypertarget{ref-boons_basis_2019}{}%
-Boons, M., Prado, M.P., 2019. Basis-momentum. The Journal of Finance 74, 239--279.
-
-\leavevmode\hypertarget{ref-boyd_prevalence_2016}{}%
-Boyd, N.E., Büyükşahin, B., Haigh, M.S., Harris, J.H., 2016. The prevalence, sources, and effects of herding. Journal of Futures Markets 36, 671--694.
-
-\leavevmode\hypertarget{ref-brennan_supply_1958}{}%
-Brennan, M.J., 1958. The supply of storage. The American Economic Review 48, 50--72.
-
-\leavevmode\hypertarget{ref-brunetti_speculators_2016}{}%
-Brunetti, C., Büyükşahin, B., Harris, J.H., 2016. Speculators, prices, and market volatility. Journal of Financial and Quantitative Analysis 51, 1545--1574.
-
-\leavevmode\hypertarget{ref-brunetti_commodity_2014}{}%
-Brunetti, C., Reiffen, D., 2014. Commodity index trading and hedging costs. Journal of Financial Markets 21, 153--180.
-
-\leavevmode\hypertarget{ref-bruno_financialisation_2017}{}%
-Bruno, V.G., Büyükşahin, B., Robe, M.A., 2017. The financialization of food? American Journal of Agricultural Economics 99, 243--264.
-
-\leavevmode\hypertarget{ref-buyuksahin_speculators_2011}{}%
-Büyükşahin, B., Harris, J.H., 2011. Do speculators drive crude oil futures prices? The Energy Journal 167--202.
-
-\leavevmode\hypertarget{ref-buyuksahin_speculators_2014}{}%
-Büyükşahin, B., Robe, M.A., 2014. Speculators, commodities and cross-market linkages. Journal of International Money and Finance, Understanding international commodity price fluctuations 42, 38--70.
-
-\leavevmode\hypertarget{ref-carhart_persistence_1997}{}%
-Carhart, M.M., 1997. On persistence in mutual fund performance. The Journal of finance 52, 57--82.
-
-\leavevmode\hypertarget{ref-cheng_convective_2014}{}%
-Cheng, I.-H., Kirilenko, A., Xiong, W., 2014. Convective risk flows in commodity futures markets. Review of Finance 19, 1733--1781.
-
-\leavevmode\hypertarget{ref-cheng_financialisation_2014}{}%
-Cheng, I.-H., Xiong, W., 2014. Financialization of commodity markets. Annual Review of Financial Economics 6, 419--441.
-
-\leavevmode\hypertarget{ref-christoffersen_factor_2014}{}%
-Christoffersen, P., Lunde, A., Olesen, K.V., 2014. Factor structure in commodity futures return and volatility. Journal of Financial and Quantitative Analysis 1--74.
-
-\leavevmode\hypertarget{ref-cootner_returns_1960}{}%
-Cootner, P.H., 1960. Returns to speculators: Telser versus keynes. Journal of political Economy 68, 396--404.
-
-\leavevmode\hypertarget{ref-cortazar_commodity_2013}{}%
-Cortazar, G., Kovacevic, I., Schwartz, E.S., 2013. Commodity and asset pricing models: An integration (NBER Working Papers No. 19167). National Bureau of Economic Research, Inc.
-
-\leavevmode\hypertarget{ref-danthine_information_1978}{}%
-Danthine, J.-P., 1978. Information, futures prices, and stabilizing speculation. Journal of Economic Theory 17, 79--98.
-
-\leavevmode\hypertarget{ref-daskalaki_factors_2014}{}%
-Daskalaki, C., Kostakis, A., Skiadopoulos, G., 2014. Are there common factors in individual commodity futures returns? Journal of Banking \& Finance 40, 346--363.
-
-\leavevmode\hypertarget{ref-deschutter_food_2010}{}%
-De Schutter, O., 2010.
-Food commodities speculation and food price crises: Regulation to reduce the risks of price volatility.
-United Nations Special Rapporteur on the Right to Food Briefing Note 2, 1--14.
-
-\leavevmode\hypertarget{ref-domanski_financial_2007}{}%
-Domanski, D., Heath, A., 2007. Financial investors and commodity markets. Working Paper.
-
-\leavevmode\hypertarget{ref-duffie_challenges_2014}{}%
-Duffie, D., 2014. Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs. The Journal of Legal Studies 43, S173--S182.
-
-\leavevmode\hypertarget{ref-ederington_who_2002}{}%
-Ederington, L., Lee, J.H., 2002. Who trades futures and how: Evidence from the heating oil futures market. The Journal of Business 75, 353--373.
-
-\leavevmode\hypertarget{ref-ekeland_speculation_2016}{}%
-Ekeland, I., Lautier, D., Villeneuve, B., 2016. Speculation in commodity futures markets: A simple equilibrium model.
-
-\leavevmode\hypertarget{ref-etula_broker-dealer_2013}{}%
-Etula, E., 2013. Broker-dealer risk appetite and commodity returns. Journal of Financial Econometrics 11, 486--521.
-
-\leavevmode\hypertarget{ref-fama_common_1993}{}%
-Fama, E.F., French, K.R., 1993. Common risk factors in the returns on stocks and bonds. Journal of Financial Economics 33, 3--56.
-
-\leavevmode\hypertarget{ref-fama_five_factor_2015}{}%
-Fama, E.F., French, K.R., 2015. A five-factor asset pricing model. Journal of Financial Economics 116, 1--22.
-
-\leavevmode\hypertarget{ref-fattouh_role_2013}{}%
-Fattouh, B., Kilian, L., Mahadeva, L., 2013. The role of speculation in oil markets: What have we learnt so far? The Energy Journal 34, 7--33.
-
-\leavevmode\hypertarget{ref-fernandez_skewness_2018}{}%
-Fernandez-Perez, A., Frijns, B., Fuertes, A.-M., Miffre, J., 2018. The skewness of commodity futures returns. Journal of Banking \& Finance 86, 143--158.
-
-\leavevmode\hypertarget{ref-frazzini_betting_2014}{}%
-Frazzini, A., Pedersen, L.H., 2014. Betting against beta. Journal of Financial Economics 111, 1--25.
-
-\leavevmode\hypertarget{ref-fuertes_commodity_2015}{}%
-Fuertes, A.-M., Miffre, J., Fernandez-Perez, A., 2015. Commodity strategies based on momentum, term structure, and idiosyncratic volatility. Journal of Futures Markets 35, 274--297.
-
-\leavevmode\hypertarget{ref-gilbert_how_2010}{}%
-Gilbert, C.L., 2010a. How to understand high food prices. Journal of Agricultural Economics 61, 398--425.
-
-\leavevmode\hypertarget{ref-gilbert_speculative_2010}{}%
-Gilbert, C.L., 2010b. Speculative influences on commodity futures prices 2006-2008. UNCTAD, Geneva.
-
-\leavevmode\hypertarget{ref-gilbert_role_2014}{}%
-Gilbert, C.L., Pfuderer, S., 2014. The role of index trading in price formation in the grains and oilseeds markets. Journal of Agricultural Economics 65, 303--322.
-
-\leavevmode\hypertarget{ref-goldstein_speculation_2014}{}%
-Goldstein, I., Li, Y., Yang, L., 2014. Speculation and hedging in segmented markets. The Review of Financial Studies 27, 881--922.
-
-\leavevmode\hypertarget{ref-goldstein_commodity_2017}{}%
-Goldstein, I., Yang, L., 2017. Commodity financialization and information transmission (SSRN Scholarly Paper No. ID 2555996). Social Science Research Network, Rochester, NY.
-
-\leavevmode\hypertarget{ref-gorton_fundamentals_2012}{}%
-Gorton, G.B., Hayashi, F., Rouwenhorst, K.G., 2012. The fundamentals of commodity futures returns. Review of Finance 17, 35--105.
-
-\leavevmode\hypertarget{ref-grossman_impossibility_1980}{}%
-Grossman, S.J., Stiglitz, J.E., 1980. On the impossibility of informationally efficient markets. The American economic review 70, 393--408.
-
-\leavevmode\hypertarget{ref-hamilton_effects_2015}{}%
-Hamilton, J.D., Wu, J.C., 2015. Effects of index-fund investing on commodity futures prices. International Economic Review 56, 187--205.
-
-\leavevmode\hypertarget{ref-henderson_new_2015}{}%
-Henderson, B.J., Pearson, N.D., Wang, L., 2015. New evidence on the financialization of commodity markets. The Review of Financial Studies 28, 1285--1311.
-
-\leavevmode\hypertarget{ref-herman_not_2011}{}%
-Herman, M.-O., Kelly, R., Nash, R., 2011.
-Not a game, speculation v.
-Food security: Regulating financial markets to grow a better future.
-Oxfam policy and practice: agriculture, food and land 11, 127--138.
-
-\leavevmode\hypertarget{ref-hicks_value_1939}{}%
-Hicks, J.R., 1939. Value and capital, 1st ed. Oxford University Press, Cambridge.
-
-\leavevmode\hypertarget{ref-hicks_value_1946}{}%
-Hicks, J.R., 1946. Value and capital, 2nd ed. Oxford University Press, Cambridge.
-
-\leavevmode\hypertarget{ref-hirshleifer_speculation_1975}{}%
-Hirshleifer, J., 1975. Speculation and equilibrium: Information, risk, and markets. The Quarterly Journal of Economics 89, 519--542.
-
-\leavevmode\hypertarget{ref-hirshleifer_reply_1976}{}%
-Hirshleifer, J., 1976. Reply to comments on" speculation and equilibrium: Information, risk, and markets". The Quarterly Journal of Economics 689--696.
-
-\leavevmode\hypertarget{ref-hirshleifer_theory_1977}{}%
-Hirshleifer, J., 1977. The theory of speculation under alternative regimes of markets. The Journal of Finance 32, 975--999.
-
-\leavevmode\hypertarget{ref-hong_what_2012}{}%
-Hong, H., Yogo, M., 2012. What does futures market interest tell us about the macroeconomy and asset prices? Journal of Financial Economics 105, 473--490.
-
-\leavevmode\hypertarget{ref-hou_digesting_2015}{}%
-Hou, K., Xue, C., Zhang, L., 2015. Digesting anomalies: An investment approach. The Review of Financial Studies 28, 650--705.
-
-\leavevmode\hypertarget{ref-houthakker_restatement_1957}{}%
-Houthakker, H., 1957. Restatement of the theory of normal backwardation (Cowles Foundation Discussion Papers No. 44). Cowles Foundation for Research in Economics, Yale University.
-
-\leavevmode\hypertarget{ref-houthakker_speculators_1957}{}%
-Houthakker, H.S., 1957. Can speculators forecast prices? The Review of Economics and Statistics 39, 143--151.
-
-\leavevmode\hypertarget{ref-irwin_commodity_2013}{}%
-Irwin, S.H., 2013. Commodity index investment and food prices: Does the "masters hypothesis" explain recent price spikes? Agricultural Economics 44, 29--41.
-
-\leavevmode\hypertarget{ref-irwin_index_2011}{}%
-Irwin, S.H., Sanders, D.R., 2011. Index funds, financialization, and commodity futures markets. Applied Economic Perspectives and Policy 33, 1--31.
-
-\leavevmode\hypertarget{ref-irwin_financialisation_2012}{}%
-Irwin, S.H., Sanders, D.R., 2012. Financialization and structural change in commodity futures markets. Journal of Agricultural and Applied Economics 44, 371--396.
-
-\leavevmode\hypertarget{ref-irwin_devil_2009}{}%
-Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009. Devil or angel? The role of speculation in the recent commodity price boom (and bust). Journal of Agricultural and Applied Economics 41, 377--391.
-
-\leavevmode\hypertarget{ref-juvenal_speculation_2015}{}%
-Juvenal, L., Petrella, I., 2015. Speculation in the oil market. Journal of Applied Econometrics 30, 621--649.
-
-\leavevmode\hypertarget{ref-kaldor_speculation_1939}{}%
-Kaldor, N., 1939. Speculation and economic stability. The Review of Economic Studies 7, 1--27.
-
-\leavevmode\hypertarget{ref-kang_tale_2020}{}%
-Kang, W., Rouwenhorst, K.G., Tang, K., 2020. A tale of two premiums: The role of hedgers and speculators in commodity futures markets. The Journal of Finance 75, 377--417.
-
-\leavevmode\hypertarget{ref-keynes_some_1923}{}%
-Keynes, J.M., 1923. Some aspects of commodity markets. Manchester Guardian Commercial: European Reconstruction Series 13, 784--786.
-
-\leavevmode\hypertarget{ref-keynes_treatise_1930}{}%
-Keynes, J.M., 1930. Treatise on money. Macmillan, London.
-
-\leavevmode\hypertarget{ref-kilian_role_2014}{}%
-Kilian, L., Murphy, D.P., 2014. The role of inventories and speculative trading in the global market for crude oil. Journal of Applied Econometrics 29, 454--478.
-
-\leavevmode\hypertarget{ref-kim_does_2015}{}%
-Kim, A., 2015. Does futures speculation destabilize commodity markets? Journal of Futures Markets 35, 696--714.
-
-\leavevmode\hypertarget{ref-knittel_simple_2016}{}%
-Knittel, C.R., Pindyck, R.S., 2016. The simple economics of commodity price speculation. American Economic Journal: Macroeconomics 8, 85--110.
-
-\leavevmode\hypertarget{ref-kyle_informed_1989}{}%
-Kyle, A.S., 1989. Informed speculation with imperfect competition. The Review of Economic Studies 56, 317--355.
-
-\leavevmode\hypertarget{ref-leclercq_equilibrium_2014}{}%
-Leclercq, E., Praz, R., 2014. Equilibrium commodity trading (SSRN Scholarly Paper No. ID 2464400). Social Science Research Network, Rochester, NY.
-
-\leavevmode\hypertarget{ref-manera_modeling_2016}{}%
-Manera, M., Nicolini, M., Vignati, I., 2016. Modeling futures price volatility in energy markets: Is there a role for financial speculation? Energy Economics, Energy markets 53, 220--229.
-
-\leavevmode\hypertarget{ref-masters_testimony_2008}{}%
-Masters, M.W., 2008. Testimony before the committee on homeland security and governmental affairs. U.S. Senate 20.
-
-\leavevmode\hypertarget{ref-masters_accidental_2008}{}%
-Masters, M., White, A., 2008. The accidental hunt brothers: How institutional investors are driving up food and energy prices. Working paper.
-
-\leavevmode\hypertarget{ref-miffre_momentum_2007}{}%
-Miffre, J., Rallis, G., 2007. Momentum strategies in commodity futures markets. Journal of Banking \& Finance 31, 1863--1886.
-
-\leavevmode\hypertarget{ref-moskowitz_time_2012}{}%
-Moskowitz, T.J., Ooi, Y.H., Pedersen, L.H., 2012. Time series momentum. Journal of Financial Economics, Special issue on investor sentiment 104, 228--250.
-
-\leavevmode\hypertarget{ref-sakkas_factor_2020}{}%
-Sakkas, A., Tessaromatis, N., 2020. Factor based commodity investing. Journal of Banking \& Finance 115, 105807.
-
-\leavevmode\hypertarget{ref-sanders_impact_2011}{}%
-Sanders, D.R., Irwin, S.H., 2011a. The impact of index funds in commodity futures markets: A systems approach. The Journal of Alternative Investments 14, 40--49.
-
-\leavevmode\hypertarget{ref-sanders_new_2011}{}%
-Sanders, D.R., Irwin, S.H., 2011b. New evidence on the impact of index funds in u.s. Grain futures markets. Canadian Journal of Agricultural Economics/Revue canadienne d'agroeconomie 59, 519--532.
-
-\leavevmode\hypertarget{ref-sanders_adequacy_2010}{}%
-Sanders, D.R., Irwin, S.H., Merrin, R.P., 2010. The adequacy of speculation in agricultural futures markets: Too much of a good thing? Applied Economic Perspectives and Policy 32, 77--94.
-
-\leavevmode\hypertarget{ref-schumann_hunger_2011}{}%
-Schumann, H., 2011. The hunger-makers: How deutsche bank, goldman sachs and other financial institutions are speculating with food at the expense of the poorest. Foodwatch, Berlin.
-
-\leavevmode\hypertarget{ref-schwartz_stochastic_1997}{}%
-Schwartz, E.S., 1997. The stochastic behavior of commodity prices: Implications for valuation and hedging. The Journal of Finance 52, 923--973.
-
-\leavevmode\hypertarget{ref-schwartz_short_2000}{}%
-Schwartz, E., Smith, J.E., 2000. Short-term variations and long-term dynamics in commodity prices. Management Science 46, 893--911.
-
-\leavevmode\hypertarget{ref-senate_excessive_2009}{}%
-Senate, U.S., 2009. Excessive speculation in the wheat market. Majority and Minority Staff Report. Permanent Subcommittee on Investigations 24, 107--108.
-
-\leavevmode\hypertarget{ref-simsek_speculation_2013}{}%
-Simsek, A., 2013. Speculation and risk sharing with new financial assets. The Quarterly Journal of Economics 128, 1365--1396.
-
-\leavevmode\hypertarget{ref-singleton_investor_2013}{}%
-Singleton, K.J., 2013. Investor flows and the 2008 boom/bust in oil prices. Management Science 60, 300--318.
-
-\leavevmode\hypertarget{ref-sockin_informational_2015}{}%
-Sockin, M., Xiong, W., 2015. Informational frictions and commodity markets. The Journal of Finance 70, 2063--2098.
-
-\leavevmode\hypertarget{ref-stoll_commodity_2011}{}%
-Stoll, H.R., Whaley, R.E., 2011. Commodity index investing: Speculation or diversification? The Journal of Alternative Investments 14, 50--60.
-
-\leavevmode\hypertarget{ref-stout_why_1998}{}%
-Stout, L.A., 1998. Why the law hates speculators: Regulation and private ordering in the market for otc derivatives. Duke Law Journal 48, 701--786.
-
-\leavevmode\hypertarget{ref-stulz_rethink_1996}{}%
-Stulz, R.M., 1996. Rethinking risk management. Journal of Applied Corporate Finance 9, 8--25.
-
-\leavevmode\hypertarget{ref-szymanowska_anatomy_2014}{}%
-Szymanowska, M., De Roon, F., Nijman, T., Van Den Goorbergh, R., 2014. An anatomy of commodity futures risk premia. The Journal of Finance 69, 453--482.
-
-\leavevmode\hypertarget{ref-tang_index_2012}{}%
-Tang, K., Xiong, W., 2012. Index investment and the financialization of commodities. Financial Analysts Journal 68, 54--74.
-
-\leavevmode\hypertarget{ref-telser_futures_1958}{}%
-Telser, L.G., 1958. Futures trading and the storage of cotton and wheat. Journal of Political Economy 66, 233--255.
-
-\leavevmode\hypertarget{ref-till_long_2007}{}%
-Till, H., 2007. A long-term perspective on commodity futures returns, in: Intelligent Commodity Investing. Risk books, London.
-
-\leavevmode\hypertarget{ref-tokic_speculation_2012}{}%
-Tokic, D., 2012. Speculation and the 2008 oil bubble: The dcot report analysis. Energy Policy 45, 541--550.
-
-\leavevmode\hypertarget{ref-turnovsky_determination_1983}{}%
-Turnovsky, S.J., 1983. The determination of spot and futures prices with storable commodities. Econometrica 51, 1363--1387.
-
-\leavevmode\hypertarget{ref-unctad_global_2009}{}%
-UNCTAD, S.T.F. on S.I., Cooperation, E., 2009. The global economic crisis: Systemic failures and multilateral remedies. UNCTAD, Geneva.
-
-\leavevmode\hypertarget{ref-weymar_supply_1966}{}%
-Weymar, F.H., 1966. The supply of storage revisited. The American Economic Review 56, 1226--1234.
-
-\leavevmode\hypertarget{ref-working_price_1933}{}%
-Working, H., 1933. Price relations between july and september wheat futures at chicago since 1885. Wheat Studies 9, 187.
-
-\leavevmode\hypertarget{ref-working_theory_1948}{}%
-Working, H., 1948. Theory of the inverse carrying charge in futures markets. Journal of Farm Economics 30, 1--28.
-
-\leavevmode\hypertarget{ref-working_theory_1949}{}%
-Working, H., 1949. The theory of price of storage. The American Economic Review 1254--1262.
-
-\leavevmode\hypertarget{ref-working_hedging_1953}{}%
-Working, H., 1953. Hedging reconsidered. Journal of Farm Economics 35, 544--561.
-
-\leavevmode\hypertarget{ref-yang_investment_2013}{}%
-Yang, F., 2013. Investment shocks and the commodity basis spread. Journal of Financial Economics 110, 164--184.
+\renewcommand\refname{References}
+  \bibliography{bibliography.bib}
 

### 2024-09-16 docs/paper.qmd
Harmonize equations syntax

@@
 
-$$Y_{t}^{OI}\equiv\left \{ \left \{ \overline{{OI}_{1}^{\Delta \%}}, \overline{{OI}_{2}^{\Delta \%}}, ..., \overline{{OI}_{n}^{\Delta \%}} \right \}, \geq \right \}$$
+$$Y_{t}^{OI}\equiv\left \{ \left \{ \overline{OI_{1}^{\Delta \%}}, \overline{OI_{2}^{\Delta \%}}, ..., \overline{OI_{n}^{\Delta \%}} \right \}, \geq \right \}$$
 
-$\overline{{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{{OI}_{j,t-k}}{{OI}_{j,t-k-1}} - 1)$  
+$\overline{OI_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{OI_{j,t-k}}{OI_{j,t-k-1}} - 1)$  
 $OI_{j,t}\equiv$ open interest at close of period $t$ on the front (nearby) contract for commodity $j$.

### 2024-09-16 docs/paper.tex
Harmonize equations syntax

@@
 \hypersetup{
-  pdftitle={financialisation of Commodity Markets},
+  pdftitle={Financialisation of Commodity Markets},
   pdfauthor={Devraj Basu; Olivier Bauthéac},
@@
 \begin{frontmatter}
-\title{financialisation of Commodity Markets \\\large{Co-movement
+\title{Financialisation of Commodity Markets \\\large{Co-movement
 Behind-the-Scenes} }
@@
 
-\[Y_{t}^{OI}\equiv\left \{ \left \{ \overline{{OI}_{1}^{\Delta \%}}, \overline{{OI}_{2}^{\Delta \%}}, ..., \overline{{OI}_{n}^{\Delta \%}} \right \}, \geq \right \}\]
-
-\(\overline{{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{{OI}_{j,t-k}}{{OI}_{j,t-k-1}} - 1)\)\\
+\[Y_{t}^{OI}\equiv\left \{ \left \{ \overline{OI_{1}^{\Delta \%}}, \overline{OI_{2}^{\Delta \%}}, ..., \overline{OI_{n}^{\Delta \%}} \right \}, \geq \right \}\]
+
+\(\overline{OI_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{OI_{j,t-k}}{OI_{j,t-k-1}} - 1)\)\\
 \(OI_{j,t}\equiv\) open interest at close of period \(t\) on the front
@@
 \caption{\label{tbl-correlations-periods}This table shows the average
-time series \(R^{2}\) for models where the returns series for the twenty
-four individual US commodities are independently regressed against
-relative change in their own commercial hedging pressure (CHP) series as
-well as against that in aggregate CHP, a market wide measure of CHP
-which calculation method is discussed in section
-Section~\ref{sec-methods}. Averages are calculated independently across
-the whole cross-section of US traded commodity assets considered in the
-study as well as across commodity sectors and subsectors for the four
+pairwise correlation coefficients calculated independently across the
+whole cross-section of commodity assets considered in the study as well
+as across countries and commodity sectors and subsectors for the four
 periods of interest (past: 1997-2003; financialisation: 2004-2008;
-crisis: 2008-2013; post-crisis: 2013-2018). The results are discussed in
+crisis: 2008-2013; post-crisis: 2013-2018). For each period, the results
+are calculated independently over the entire period as well as over
+phases of aggregate backwardation and contango. Aggregate CHP
+construction and corresponding regime definitions are discussed in
+section Section~\ref{sec-methods} while the results are discussed in
 section Section~\ref{sec-results}.}
@@
 as across countries and commodity sectors and subsectors by year for the
-whole periods of interest (1997-2018). For each year, the results are
-calculated independently over the entire year as well as over phases of
-aggregate backwardation and contango. Aggregate CHP construction and
-corresponding regime definitions are discussed in section
-Section~\ref{sec-methods} while the results are discussed in section
-Section~\ref{sec-results}.}
+whole period of interest (1997-2018). The results are discussed in
+section Section~\ref{sec-results}.}
 

### 2024-09-16 docs/_extensions/quarto-journals/elsevier/partials/before-body.tex
Copy html output
To create an index.html file for deployment

\begin{frontmatter}
\title{$title$$if(subtitle)$ \\\large{$subtitle$} $endif$}
$for(by-author)$\author[$for(by-author.affiliations)$$it.number$$sep$,$endfor$]{$by-author.name.literal$%
$if(by-author.attributes.corresponding)$\corref{cor1}$endif$%
$if(by-author.note.text)$\fnref{fn$by-author.note.number$}$endif$}
$if(by-author.email)$ \ead{$by-author.email$} $endif$
$endfor$
$for(by-affiliation)$
\affiliation[$it.number$]{organization={$it.name$$if(it.department)$, $it.department$$endif$},$if(it.address)$addressline={$it.address$}$endif$$if(it.city)$$if(it.address)$,$endif$city={$it.city$}$endif$$if(it.country)$$if(it.city)$,$elseif(it.address)$,$endif$country={$it.country$},countrysep={,}$endif$$if(it.postal-code)$$if(it.country)$,$elseif(it.city)$,$elseif(it.address)$,$endif$postcode={$it.postal-code$}$endif$,postcodesep={}}
$endfor$

\cortext[cor1]{Corresponding author}
$for(by-author)$
$if(by-author.note.text)$\fntext[fn$by-author.note.number$]{$by-author.note.text$}$endif$
$endfor$

$if(abstract)$
\begin{abstract}
$abstract$
\end{abstract}
$endif$

$if(journal.graphical-abstract)$\begin{graphicalabstract}
$journal.graphical-abstract$
\end{graphicalabstract}
$endif$

$if(journal.highlights)$\begin{highlights}
$for(journal.highlights)$\item $it$$endfor$
\end{highlights}
$endif$

$if(keywords)$
\begin{keyword}
    $for(keywords/allbutlast)$$keywords$ \sep $endfor$
    $for(keywords/last)$$keywords$$endfor$
\end{keyword}
$endif$
\end{frontmatter}

### 2024-09-16 docs/style-guide/elsdoc.tex
Copy html output
To create an index.html file for deployment

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
%% $Id: elsdoc.tex 192 2020-11-23 11:14:41Z rishi $
%%
\documentclass[a4paper,12pt]{article}

\usepackage[xcolor,qtwo]{rvdtx}
\usepackage{multicol}
\usepackage{color}
\usepackage{xspace}
\usepackage{pdfwidgets}
\usepackage{enumerate}

\def\ttdefault{cmtt}

\headsep4pc

\makeatletter
\def\bs{\expandafter\@gobble\string\\}
\def\lb{\expandafter\@gobble\string\{}
\def\rb{\expandafter\@gobble\string\}}
\def\@pdfauthor{C.V.Radhakrishnan}
\def\@pdftitle{elsarticle.cls -- A documentation}
\def\@pdfsubject{Document formatting with elsarticle.cls}
\def\@pdfkeywords{LaTeX, Elsevier Ltd, document class}
\def\file#1{\textsf{#1}\xspace}

%\def\LastPage{19}

\DeclareRobustCommand{\LaTeX}{L\kern-.26em%
        {\sbox\z@ T%
         \vbox to\ht\z@{\hbox{\check@mathfonts
           \fontsize\sf@size\z@
           \math@fontsfalse\selectfont
          A\,}%
         \vss}%
        }%
     \kern-.15em%
    \TeX}
\makeatother

\def\figurename{Clip}

\setcounter{tocdepth}{1}

\begin{document}

\def\testa{This is a specimen document. }
\def\testc{\testa\testa\testa\testa}
\def\testb{\testc\testc\testc\testc\testc}
\long\def\test{\testb\par\testb\par\testb\par}

\pinclude{\copy\contbox\printSq{\LastPage}}

\title{elsarticle.cls -- A better way to format your document}

\author{Elsevier Ltd}
\contact{elsarticle@stmdocs.in}

\version{3.3}
\date{\today}
\maketitle

\section{Introduction}

\file{elsarticle.cls} is a thoroughly re-written document class
for formatting \LaTeX{} submissions to Elsevier journals.
The class uses the environments and commands defined in \LaTeX{} kernel
without any change in the signature so that clashes with other
contributed \LaTeX{} packages such as \file{hyperref.sty},
\file{preview-latex.sty}, etc., will be minimal.
\file{elsarticle.cls} is primarily built upon the default
\file{article.cls}.  This class depends on the following packages
for its proper functioning:

\begin{enumerate}
\item \file{natbib.sty} for citation processing;
\item \file{geometry.sty} for margin settings;
\item \file{fleqn.clo} for left aligned equations;
\item \file{graphicx.sty} for graphics inclusion;
\item \file{txfonts.sty} optional font package, if the document is to
  be formatted with Times and compatible math fonts;
\item \file{hyperref.sty} optional packages if hyperlinking is
  required in the document;
%*%
\item \file{endfloat.sty} optional packages if floats to be placed at
 end of the PDF.
\end{enumerate}

All the above packages (except some optional packages) are part of any
standard \LaTeX{} installation. Therefore, the users need not be
bothered about downloading any extra packages.  Furthermore, users are
free to make use of \textsc{ams} math packages such as
\file{amsmath.sty}, \file{amsthm.sty}, \file{amssymb.sty},
\file{amsfonts.sty}, etc., if they want to.  All these packages work in
tandem with \file{elsarticle.cls} without any problems.

\section{Major Differences}

Following are the major differences between \file{elsarticle.cls}
and its predecessor package, \file{elsart.cls}:

\begin{enumerate}[\textbullet]
\item \file{elsarticle.cls} is built upon \file{article.cls}
while \file{elsart.cls} is not. \file{elsart.cls} redefines
many of the commands in the \LaTeX{} classes/kernel, which can
possibly cause surprising clashes with other contributed
\LaTeX{} packages;

\item provides preprint document formatting by default, and
optionally formats the document as per the final
style of models $1+$, $3+$ and $5+$ of Elsevier journals;

\item some easier ways for formatting \verb+list+ and
\verb+theorem+ environments are provided while people can still
use \file{amsthm.sty} package;

\item \file{natbib.sty} is the main citation processing package
  which can comprehensively handle all kinds of citations and
works perfectly with \file{hyperref.sty} in combination with
\file{hypernat.sty};

\item long title pages are processed correctly in preprint and
  final formats.

\end{enumerate}

\section{Installation}

The package is available at author resources page at Elsevier
(\url{http://www.elsevier.com/locate/latex}).
It can also be found in any of the nodes of the Comprehensive
\TeX{} Archive Network (\textsc{ctan}), one of the primary nodes
being
\url{http://tug.ctan.org/tex-archive/macros/latex/contrib/elsarticle/}.
Please download the \file{elsarticle.dtx} which is a composite
class with documentation and \file{elsarticle.ins} which is the
\LaTeX{} installer file. When we compile the
\file{elsarticle.ins} with \LaTeX{} it provides the class file,
\file{elsarticle.cls} by
stripping off all the documentation from the \verb+*.dtx+ file.
The class may be moved or copied to a place, usually,
\verb+$TEXMF/tex/latex/elsevier/+, %$%%%%%%%%%%%%%%%%%%%%%%%%%%%%
or a folder which will be read                   
by \LaTeX{} during document compilation.  The \TeX{} file
database needs updation after moving/copying class file.  Usually,
we use commands like \verb+mktexlsr+ or \verb+texhash+ depending
upon the distribution and operating system.

\section{Usage}\label{sec:usage}
The class should be loaded with the command:

\begin{vquote}
 \documentclass[<options>]{elsarticle}
\end{vquote}

\noindent where the \verb+options+ can be the following:

\begin{description}

\item [{\tt\color{verbcolor} preprint}]  default option which format the
  document for submission to Elsevier journals.

\item [{\tt\color{verbcolor} review}]  similar to the \verb+preprint+
option, but increases the baselineskip to facilitate easier review
process.

\item [{\tt\color{verbcolor} 1p}]  formats the article to the look and
feel of the final format of model 1+ journals. This is always single
column style.

\item [{\tt\color{verbcolor} 3p}] formats the article to the look and
feel of the final format of model 3+ journals. If the journal is a two
column model, use \verb+twocolumn+ option in combination.

\item [{\tt\color{verbcolor} 5p}] formats for model 5+ journals. This
is always of two column style.

\item [{\tt\color{verbcolor} authoryear}] author-year citation style of
\file{natbib.sty}. If you want to add extra options of
\file{natbib.sty}, you may use the options as comma delimited strings
as arguments to \verb+\biboptions+ command. An example would be:
\end{description}

\begin{vquote}
 \biboptions{longnamesfirst,angle,semicolon}
\end{vquote}

\begin{description}
\item [{\tt\color{verbcolor} number}] numbered citation style. Extra options
  can be loaded with\linebreak \verb+\biboptions+ command.

\item [{\tt\color{verbcolor} sort\&compress}] sorts and compresses the
numbered citations. For example, citation [1,2,3] will become [1--3].

\item [{\tt\color{verbcolor} longtitle}] if front matter is unusually long, use
  this option to split the title page across pages with the correct
placement of title and author footnotes in the first page.

\item [{\tt\color{verbcolor} times}] loads \file{txfonts.sty}, if
available in the system to use Times and compatible math fonts.

%*%
\item [{\tt\color{verbcolor} reversenotenum}] Use alphabets as
author--affiliation linking labels and use numbers for author
footnotes. By default, numbers will be used as author--affiliation
linking labels and alphabets for author footnotes.

\item [{\tt\color{verbcolor} lefttitle}] To move title and
author/affiliation block to flushleft. \verb+centertitle+ is the
default option which produces center alignment.

\item [{\tt\color{verbcolor} endfloat}] To place all floats at the end
of the document.

\item [{\tt\color{verbcolor} nonatbib}] To unload natbib.sty.
%*%

\item [{\tt\color{verbcolor} doubleblind}] To hide author name, 
affiliation, email address etc. for double blind refereeing purpose.
%*%

\item[] All options of \file{article.cls} can be used with this
  document class.

\item[] The default options loaded are \verb+a4paper+, \verb+10pt+,
  \verb+oneside+, \verb+onecolumn+ and \verb+preprint+.

\end{description}

\section{Frontmatter}

There are two types of frontmatter coding:
\begin{enumerate}[(1)]
\item each author is
connected to an affiliation with a footnote marker; hence all
authors are grouped together and affiliations follow;
\pagebreak
\item authors of same affiliations are grouped together and the
relevant affiliation follows this group. 
\end{enumerate}

An example of coding the first type is provided below.

\begin{vquote}
 \title{This is a specimen title\tnoteref{t1,t2}}
 \tnotetext[t1]{This document is the results of the research
    project funded by the National Science Foundation.}
 \tnotetext[t2]{The second title footnote which is a longer 
    text matter to fill through the whole text width and 
    overflow into another line in the footnotes area of the 
    first page.}
\end{vquote}

\begin{vquote}
\author[1]{Jos Migchielsen\corref{cor1}%
  \fnref{fn1}}
\ead{J.Migchielsen@elsevier.com}

\author[2]{CV Radhakrishnan\fnref{fn2}}
\ead{cvr@sayahna.org}

\author[3]{CV Rajagopal\fnref{fn1,fn3}}
\ead[url]{www.stmdocs.in}

 \cortext[cor1]{Corresponding author}
 \fntext[fn1]{This is the first author footnote.}
 \fntext[fn2]{Another author footnote, this is a very long 
   footnote and it should be a really long footnote. But this 
   footnote is not yet sufficiently long enough to make two 
   lines of footnote text.}
 \fntext[fn3]{Yet another author footnote.}

 \affiliation[1]{organization={Elsevier B.V.}, 
                 addressline={Radarweg 29},
                 postcode={1043 NX}, 
                 city={Amsterdam}, 
                 country={The Netherlands}}

 \affiliation[2]{organization={Sayahna Foundation},
                 addressline={JWRA 34, Jagathy}, 
                 city={Trivandrum}
                 postcode={695014}, 
                 country={India}}
\end{vquote}

\begin{vquote}

 \affiliation[3]{organization={STM Document Engineering 
                               Pvt Ltd.},
                 addressline={Mepukada, Malayinkil}, 
                 city={Trivandrum}
                 postcode={695571}, 
                 country={India}}
\end{vquote}

The output of the above \TeX{} source is given in Clips~\ref{clip1} and
\ref{clip2}. The header portion or title area is given in
Clip~\ref{clip1} and the footer area is given in Clip~\ref{clip2}.

\def\rulecolor{blue!70}
\src{Header of the title page.}
\includeclip{1}{130 612 477 707}{1psingleauthorgroup.pdf}%%{elstest-1p.pdf}%single author group
\def\rulecolor{orange}

\def\rulecolor{blue!70}
\src{Footer of the title page.}
\includeclip{1}{93 135 499 255}{1pseperateaug.pdf}%%{elstest-1p.pdf}%single author group
\def\rulecolor{orange}

Most of the commands such as \verb+\title+, \verb+\author+,
\verb+\affiliation+ are self explanatory.  Various components are
linked to each other by a label--reference mechanism; for
instance, title footnote is linked to the title with a footnote
mark generated by referring to the \verb+\label+ string of
the \verb=\tnotetext=.  We have used similar commands
such as \verb=\tnoteref= (to link title note to title);
\verb=\corref= (to link corresponding author text to
corresponding author); \verb=\fnref= (to link footnote text to
the relevant author names).  \TeX{} needs two compilations to
resolve the footnote marks in the preamble part.  
Given below are the syntax of various note marks and note texts.

\begin{vquote}
  \tnoteref{<label(s)>}
  \corref{<label(s)>}
  \fnref{<label(s)>}
  \tnotetext[<label>]{<title note text>}
  \cortext[<label>]{<corresponding author note text>}
  \fntext[<label>]{<author footnote text>}
\end{vquote}

\noindent where \verb=<label(s)>= can be either one or more comma
delimited label strings. The optional arguments to the
\verb=\author= command holds the ref label(s) of the address(es)
to which the author is affiliated while each \verb=\affiliation=
command can have an optional argument of a label. In the same
manner, \verb=\tnotetext=, \verb=\fntext=, \verb=\cortext= will
have optional arguments as their respective labels and note text
as their mandatory argument.

The following example code provides the markup of the second type
of author-affiliation.

\begin{vquote}
\author{Jos Migchielsen\corref{cor1}%
  \fnref{fn1}}
\ead{J.Migchielsen@elsevier.com}
 \affiliation[1]{organization={Elsevier B.V.}, 
                 addressline={Radarweg 29},
                 postcode={1043 NX}, 
                 city={Amsterdam}, 
                 country={The Netherlands}}

\author{CV Radhakrishnan\fnref{fn2}}
\ead{cvr@sayahna.org}
 \affiliation[2]{organization={Sayahna Foundation},
                 addressline={JWRA 34, Jagathy}, 
                 city={Trivandrum}
                 postcode={695014}, 
                 country={India}}

\author{CV Rajagopal\fnref{fn1,fn3}}
\ead[url]{www.stmdocs.in}
 \affiliation[3]{organization={STM Document Engineering 
                               Pvt Ltd.},
                 addressline={Mepukada, Malayinkil}, 
                 city={Trivandrum}
                 postcode={695571}, 
                 country={India}}
\end{vquote}

\vspace*{-.5pc}

\begin{vquote}
\cortext[cor1]{Corresponding author}
\fntext[fn1]{This is the first author footnote.}
\fntext[fn2]{Another author footnote, this is a very long 
  footnote and it should be a really long footnote. But this 
  footnote is not yet sufficiently long enough to make two lines 
  of footnote text.}
\end{vquote}

The output of the above \TeX{} source is given in Clip~\ref{clip3}.

\def\rulecolor{blue!70}
\src{Header of the title page..}
\includeclip{1}{119 563 468 709}{1pseperateaug.pdf}%%{elstest-1p.pdf}%seperate author groups
\def\rulecolor{orange}
%\pagebreak

Clip~\ref{clip4} shows the output after giving \verb+doubleblind+ class option.

\def\rulecolor{blue!70}
\src{Double blind article}
\includeclip{1}{124 567 477 670}{elstest-1pdoubleblind.pdf}%%{elstest-1p.pdf}%single author group%%doubleblind
\def\rulecolor{orange}

\vspace*{-.5pc}
The frontmatter part has further environments such as abstracts and
keywords.  These can be marked up in the following manner:

\begin{vquote}
 \begin{abstract}
  In this work we demonstrate the formation of a new type of 
  polariton on the interface between a ....
 \end{abstract}
\end{vquote}

\vspace*{-.5pc}
\begin{vquote}
 \begin{keyword}
  quadruple exiton \sep polariton \sep WGM
 \end{keyword}
\end{vquote}

\noindent Each keyword shall be separated by a \verb+\sep+ command.
\textsc{msc} classifications shall be provided in 
the keyword environment with the commands
\verb+\MSC+. \verb+\MSC+ accepts an optional
argument to accommodate future revisions.
eg., \verb=\MSC[2008]=. The default is 2000.\looseness=-1

\subsection{New page}
Sometimes you may need to give a page-break and start a new page after
title, author or abstract. Following commands can be used for this
purpose.

\begin{vquote}
  \newpageafter{title}
  \newpageafter{author}
  \newpageafter{abstract}
\end{vquote}

\begin{itemize}
\leftskip-2pc
\item [] {\tt\color{verbcolor} \verb+\newpageafter{title}+} typeset the title alone on one page.

\item [] {\tt\color{verbcolor} \verb+\newpageafter{author}+}  typeset the title
and author details on one page.

\item [] {\tt\color{verbcolor} \verb+\newpageafter{abstract}+}
typeset the title,
author details and abstract \& keywords one one page.

\end{itemize}

\section{Floats}
{Figures} may be included using the command, \verb+\includegraphics+ in
combination with or without its several options to further control
graphic. \verb+\includegraphics+ is provided by \file{graphic[s,x].sty}
which is part of any standard \LaTeX{} distribution.
\file{graphicx.sty} is loaded by default. \LaTeX{} accepts figures in
the postscript format while pdf\LaTeX{} accepts \file{*.pdf},
\file{*.mps} (metapost), \file{*.jpg} and \file{*.png} formats. 
pdf\LaTeX{} does not accept graphic files in the postscript format.

The \verb+table+ environment is handy for marking up tabular
material. If users want to use \file{multirow.sty},
\file{array.sty}, etc., to fine control/enhance the tables, they
are welcome to load any package of their choice and
\file{elsarticle.cls} will work in combination with all loaded
packages.

\section[Theorem and ...]{Theorem and theorem like environments}

\file{elsarticle.cls} provides a few shortcuts to format theorems and
theorem-like environments with ease. In all commands the options that
are used with the \verb+\newtheorem+ command will work exactly in the same
manner. \file{elsarticle.cls} provides three commands to format theorem or
theorem-like environments:

\begin{vquote}
 \newtheorem{thm}{Theorem}
 \newtheorem{lem}[thm]{Lemma}
 \newdefinition{rmk}{Remark}
 \newproof{pf}{Proof}
 \newproof{pot}{Proof of Theorem \ref{thm2}}
\end{vquote}

The \verb+\newtheorem+ command formats a
theorem in \LaTeX's default style with italicized font, bold font
for theorem heading and theorem number at the right hand side of the
theorem heading.  It also optionally accepts an argument which
will be printed as an extra heading in parentheses.

\begin{vquote}
  \begin{thm} 
   For system (8), consensus can be achieved with 
   $\|T_{\omega z}$
   ...
     \begin{eqnarray}\label{10}
     ....
     \end{eqnarray}
  \end{thm}
\end{vquote}

Clip~\ref{clip5} will show you how some text enclosed between the
above code\goodbreak \noindent looks like:

\vspace*{6pt}
\def\rulecolor{blue!70}
\src{{\ttfamily\color{verbcolor}\bs newtheorem}}
\includeclip{2}{1 1 453 120}{jfigs.pdf}
\def\rulecolor{orange}

The \verb+\newdefinition+ command is the same in
all respects as its\linebreak \verb+\newtheorem+ counterpart except that
the font shape is roman instead of italic.  Both
\verb+\newdefinition+ and \verb+\newtheorem+ commands
automatically define counters for the environments defined.

\vspace*{6pt}
\def\rulecolor{blue!70}
\src{{\ttfamily\color{verbcolor}\bs newdefinition}}
\includeclip{1}{1 1 453 105}{jfigs.pdf}
\def\rulecolor{orange}

The \verb+\newproof+ command defines proof environments with
upright font shape.  No counters are defined.

\vspace*{6pt}
\def\rulecolor{blue!70}
\src{{\ttfamily\color{verbcolor}\bs newproof}}
\includeclip{3}{1 1 453 65}{jfigs.pdf}
\def\rulecolor{orange}

Users can also make use of \verb+amsthm.sty+ which will override
all the default definitions described above.

\section[Enumerated ...]{Enumerated and Itemized Lists}
\file{elsarticle.cls} provides an extended list processing macros
which makes the usage a bit more user friendly than the default
\LaTeX{} list macros.   With an optional argument to the
\verb+\begin{enumerate}+ command, you can change the list counter
type and its attributes.

\begin{vquote}
 \begin{enumerate}[1.]
 \item The enumerate environment starts with an optional
   argument `1.', so that the item counter will be suffixed
   by a period.
 \item You can use `a)' for alphabetical counter and '(i)' for
   roman counter.
  \begin{enumerate}[a)]
    \item Another level of list with alphabetical counter.
    \item One more item before we start another.
\end{vquote}

\def\rulecolor{blue!70}
\src{List -- Enumerate}
\includeclip{4}{1 1 453 185}{jfigs.pdf}
\def\rulecolor{orange}

Further, the enhanced list environment allows one to prefix a
string like `step' to all the item numbers.

\begin{vquote}
 \begin{enumerate}[Step 1.]
  \item This is the first step of the example list.
  \item Obviously this is the second step.
  \item The final step to wind up this example.
 \end{enumerate}
\end{vquote}

\def\rulecolor{blue!70}
\src{List -- enhanced}
\includeclip{5}{1 1 313 83}{jfigs.pdf}
\def\rulecolor{orange}

\section{Cross-references}
In electronic publications, articles may be internally
hyperlinked. Hyperlinks are generated from proper
cross-references in the article.  For example, the words
\textcolor{black!80}{Fig.~1} will never be more than simple text,
whereas the proper cross-reference \verb+\ref{tiger}+ may be
turned into a hyperlink to the figure itself:
\textcolor{blue}{Fig.~1}.  In the same way,
the words \textcolor{blue}{Ref.~[1]} will fail to turn into a
hyperlink; the proper cross-reference is \verb+\cite{Knuth96}+.
Cross-referencing is possible in \LaTeX{} for sections,
subsections, formulae, figures, tables, and literature
references.

\section[Mathematical ...]{Mathematical symbols and formulae}

Many physical/mathematical sciences authors require more
mathematical symbols than the few that are provided in standard
\LaTeX. A useful package for additional symbols is the
\file{amssymb} package, developed by the American Mathematical
Society. This package includes such oft-used symbols as
$\lesssim$ (\verb+\lesssim+), $\gtrsim$ (\verb+\gtrsim+)  or 
$\hbar$ (\verb+\hbar+). Note that your \TeX{}
system should have the \file{msam} and \file{msbm} fonts installed. If
you need only a few symbols, such as $\Box$ (\verb+\Box+), you might try the
package \file{latexsym}.

Another point which would require authors' attention is the
breaking up of long equations.  When you use
\file{elsarticle.cls} for formatting your submissions in the 
\verb+preprint+ mode, the document is formatted in single column
style with a text width of 384pt or 5.3in.  When this document is
formatted for final print and if the journal happens to be a double column
journal, the text width will be reduced to 224pt at for 3+
double column and 5+ journals respectively. All the nifty 
fine-tuning in equation breaking done by the author goes to waste in
such cases.  Therefore, authors are requested to check this
problem by typesetting their submissions in final format as well
just to see if their equations are broken at appropriate places,
by changing appropriate options in the document class loading
command, which is explained in section~\ref{sec:usage},
\nameref{sec:usage}. This allows authors to fix any equation breaking
problem before submission for publication.
\file{elsarticle.cls} supports formatting the author submission
in different types of final format.  This is further discussed in
section \ref{sec:final}, \nameref{sec:final}.

\enlargethispage*{\baselineskip}

\subsection*{Displayed equations and double column journals}

Many Elsevier journals print their text in two columns. Since
the preprint layout uses a larger line width than such columns,
the formulae are too wide for the line width in print. Here is an
example of an equation  (see equation 6) which is perfect in a
single column preprint format:

In normal course, articles are prepared and submitted in single column
format even if the final printed article will come in a double column
format journal. Here the problem is that when the article is typeset by
the typesetters for paginating and fit within the single column width,
they have to break the lengthy equations and align them properly. Even
if most of the tasks in preparing your proof is automated, the equation
breaking and aligning requires manual judgement, hence this task is manual.
When there comes a manual operation that area is error prone. Author
needs to check that equation pretty well.

However if authors themselves break the equation to the single column
width typesetters need not want to touch these area and the proof authors
get will be without any errors.

%\bigskip
\setlength\Sep{6pt}
\src{See equation (6)}
\def\rulecolor{blue!70}
%\includeclip{<page>}{l b scale }{file.pdf}
\includeclip{4}{105 500 500 700}{1psingleauthorgroup.pdf}
\def\rulecolor{orange}

\noindent When this document is typeset for publication in a
model 3+ journal with double columns, the equation will overlap
the second column text matter if the equation is not broken at
the appropriate location.

\vspace*{6pt}
\def\rulecolor{blue!70}
\src{See equation (6) overprints into second column}
\includeclip{3}{59 421 532 635}{elstest-3pd.pdf}
\def\rulecolor{orange}
\vspace*{6pt}

\noindent The typesetter will try to break the equation which
need not necessarily be to the liking of the author or as it
happens, typesetter's break point may be semantically incorrect.
Therefore, authors may check their submissions for the incidence
of such long equations and break the equations at the correct
places so that the final typeset copy will be as they wish.

\section{Bibliography}

Three bibliographic style files (\verb+*.bst+) are provided ---
\file{elsarticle-num.bst}, \file{elsarticle-num-names.bst} and
\file{elsarticle-harv.bst} --- the first one can be used for the
numbered scheme, second one for numbered with new options of 
\file{natbib.sty}. The third one is for the author year
scheme.

In \LaTeX{} literature, references are listed in the
\verb+thebibliography+ environment.  Each reference is a
\verb+\bibitem+ and each \verb+\bibitem+ is identified by a label,
by which it can be cited in the text:

\verb+\bibitem[Elson et al.(1996)]{ESG96}+ is cited as
\verb+\citet{ESG96}+.

\noindent In connection with cross-referencing and
possible future hyperlinking it is not a good idea to collect
more that one literature item in one \verb+\bibitem+.  The
so-called Harvard or author-year style of referencing is enabled
by the \LaTeX{} package \file{natbib}. With this package the
literature can be cited as follows:

\begin{enumerate}[\textbullet]
\item Parenthetical: \verb+\citep{WB96}+ produces (Wettig \& Brown, 1996).
\item Textual: \verb+\citet{ESG96}+ produces Elson et al. (1996).
\item An affix and part of a reference:
\verb+\citep[e.g.][Ch. 2]{Gea97}+ produces (e.g. Governato et
al., 1997, Ch. 2).
\end{enumerate}

In the numbered scheme of citation, \verb+\cite{<label>}+ is used,
since \verb+\citep+ or \verb+\citet+ has no relevance in the numbered
scheme.  \file{natbib} package is loaded by \file{elsarticle} with
\verb+numbers+ as default option.  You can change this to author-year
or harvard scheme by adding option \verb+authoryear+ in the class
loading command.  If you want to use more options of the \file{natbib}
package, you can do so with the \verb+\biboptions+ command, which is
described in the section \ref{sec:usage}, \nameref{sec:usage}.  For
details of various options of the \file{natbib} package, please take a
look at the \file{natbib} documentation, which is part of any standard
\LaTeX{} installation.

In addition to the above standard \verb+.bst+ files, there are 10
journal-specific \verb+.bst+ files also available.
Instruction for using these \verb+.bst+ files can be found at 
\href{http://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}
{http://support.stmdocs.in}

\section[Graphical ...]{Graphical abstract and highlights}
A template for adding graphical abstract and highlights are available
now. This will appear as the first two pages of the PDF before the
article content begins.

\pagebreak
Please refer below to see how to code them.

\begin{vquote}
....
....

\end{abstract}

%%Graphical abstract
\begin{graphicalabstract}
%\includegraphics{grabs}
\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item Research highlight 1
\item Research highlight 2
\end{highlights}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
....
....
\end{vquote}

\section{Final print}\label{sec:final}

The authors can format their submission to the page size and margins
of their preferred journal.  \file{elsarticle} provides four
class options for the same. But it does not mean that using these
options you can emulate the exact page layout of the final print copy.

\lmrgn=3em
\begin{description}
\item [\texttt{1p}:] $1+$ journals with a text area of
384pt $\times$ 562pt or 13.5cm $\times$ 19.75cm or 5.3in $\times$
7.78in, single column style only.

\item [\texttt{3p}:] $3+$ journals with a text area of 468pt
$\times$ 622pt or 16.45cm $\times$ 21.9cm or 6.5in $\times$
8.6in, single column style.

\item [\texttt{twocolumn}:] should be used along with 3p option if the
journal is $3+$ with the same text area as above, but double column
style.

\item [\texttt{5p}:] $5+$ with text area of 522pt $\times$
682pt or 18.35cm $\times$ 24cm or 7.22in $\times$ 9.45in,
double column style only.
\end{description}

Following pages have the clippings of different parts of
the title page of different journal models typeset in final
format.

Model $1+$ and $3+$  will have the same look and
feel in the typeset copy when presented in this document. That is
also the case with the double column $3+$ and $5+$ journal article
pages. The only difference will be wider text width of
higher models.  Here are the specimen single and double column journal 
pages.

%Therefore we will look at the
%different portions of a typical single column journal page and
%that of a double column article in the final format.

\begin{comment}
\begin{center}
\hypertarget{bsc}{}
\hyperlink{sc}{
{\bf [Specimen single column article -- Click here]}
}

\hypertarget{bsc}{}
\hyperlink{dc}{
{\bf [Specimen double column article -- Click here]}
}
\end{center}
\end{comment}

\vspace*{-.5pc}

\enlargethispage*{\baselineskip}

\src{}\hypertarget{sc}{}
\def\rulecolor{blue!70}
\hyperlink{bsc}{\includeclip{1}{88 120 514 724}{elstest-1p.pdf}}
\def\rulecolor{orange}

\src{}\hypertarget{dc}{}
\def\rulecolor{blue!70}
\hyperlink{bsc}{\includeclip{1}{27 61 562 758}{elstest-5p.pdf}}
\def\rulecolor{orange}

~\hfill $\Box$

\end{document}

### 2024-09-20 explore/scripts/revision-jfm/tables.r
Fix typo in table name

@@ -278,14 +278,14 @@ regressions_factors <- readr::read_rds(
 
 # export ####
 tables <- tibble::tribble(
-    ~analysis,                                 ~results,
-    "stats - whole",                           descriptive_stats_whole,
-    "stats - regimes",                         descriptive_stats_regimes,
-    "regressions - US returns ~ US CHP",       `US commodity returns ~ CHP`,
-    "correlations - periods",                  correlations_periods,
-    "correlations - years",                    correlations_years,
-    "regressions - all returns ~ marke index", `all commodity returns ~ market index`,
-    "regressions - all returns ~ factors",     `all commodity returns ~ factors`
+    ~analysis,                                  ~results,
+    "stats - whole",                            descriptive_stats_whole,
+    "stats - regimes",                          descriptive_stats_regimes,
+    "regressions - US returns ~ US CHP",        `US commodity returns ~ CHP`,
+    "correlations - periods",                   correlations_periods,
+    "correlations - years",                     correlations_years,
+    "regressions - all returns ~ market index", `all commodity returns ~ market index`,
+    "regressions - all returns ~ factors",      `all commodity returns ~ factors`
   )
 
 readr::write_rds(

### 2024-09-20 docs/paper.qmd
Copy html output
To create an index.html file for deployment
Write up result section for past and financialisation periods

@@
 With the benefit of hindsight it now seems that the academic debate was framed rather narrowly, used contentious research methods, and eventually led to regulatory changes that were therefore perhaps unwarranted.
-In contrast, we take a broader approach where we consider a large cross-section of liquid commodities as suggested by the nature of financilisation that comprehends commodity futures as an asset class.
+In contrast, we take a broader approach where we consider a large cross-section of liquid commodities as suggested by the nature of financialisation that comprehends commodity futures as an asset class.
 Using a bespoke asset pricing factors based framework we study the issue through the lens of co-movement and find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
@@
 Commodity futures returns fell dramatically into the crisis and the pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as evidence of cross-market linkages with the UK traded commodity subset.
-The post-crisis results, in contrast, show a substancial pullback in performance for the market factor across the board as well as evidence of decoupling between the US and UK markets.
+The post-crisis results, in contrast, show a substantial pull-back in performance for the market factor across the board as well as evidence of decoupling between the US and UK markets.
 Besides, starting in the crisis the Keneysian paradigm of returns begins to revert with higher mean returns during low (**backwardation**) relative to high (**contango**) **CHP** phases and this pattern continues, more pronounced, over the post-crisis period.
@@
 The Rule was approved in a close 3-2 vote and the ensuing rule-making process was extremely contentious with several commissioners (Michael Dunn and Scott D.
-O’Malia in particular) expressing reservations about the lack of supporting evidence and the Rule also triggering thousands of comment letters as well as a lawsuit against the CFTC spearheaded by two Wall Street trade groups, the International Swaps & Derivatives Association (ISDA) and the Securities Industries & Financial Markets Association (SIFMA)^[ISDA & SIFMA v US CFTC; Complaint, 1:11-cv-02146; December 2^nd^, 2011.].
+O'Malia in particular) expressing reservations about the lack of supporting evidence and the Rule also triggering thousands of comment letters as well as a lawsuit against the CFTC spearheaded by two Wall Street trade groups, the International Swaps & Derivatives Association (ISDA) and the Securities Industries & Financial Markets Association (SIFMA)^[ISDA & SIFMA v US CFTC; Complaint, 1:11-cv-02146; December 2^nd^, 2011.].
 
@@
 At this stage, the question thrust on the academic sphere was whether "excessive speculation" (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices.
-A number of ensuing academic studies, most of which used commodity specific correlation and causality based analysis have since disproved this contention: @irwin_devil_2009, @sanders_adequacy_2010, @sanders_impact_2011, @sanders_new_2011, @irwin_commodity_2013, @brunetti_commodity_2014, @hamilton_effects_2015 and @bruno_financialisation_2017 investigated the issue in the context of the agricultural markets; meanwhile, @buyuksahin_speculators_2011, @tokic_speculation_2012, @fattouh_role_2013, @kilian_role_2014, @knittel_simple_2016 and @manera_modeling_2016 examined the energy markets while @bohl_does_2013, @kim_does_2015 and @boyd_prevalence_2016 studied both energy and agricultural markets and @irwin_index_2011, @irwin_financialisation_2012 as well as @stoll_commodity_2011 examined the commodity markets in general.
+A number of ensuing academic studies, most of which used commodity specific correlation and causality based analysis have since disproved this contention: @irwin_devil_2009, @sanders_adequacy_2010, @sanders_impact_2011, @sanders_new_2011, @irwin_commodity_2013, @brunetti_commodity_2014, @hamilton_effects_2015 and @bruno_financialisation_2017 investigated the issue in the context of the agricultural markets; meanwhile, @buyuksahin_speculators_2011, @tokic_speculation_2012, @fattouh_role_2013, @kilian_role_2014, @knittel_simple_2016 and @manera_modelling_2016 examined the energy markets while @bohl_does_2013, @kim_does_2015 and @boyd_prevalence_2016 studied both energy and agricultural markets and @irwin_index_2011, @irwin_financialisation_2012 as well as @stoll_commodity_2011 examined the commodity markets in general.
 Other studies have underlined various alterations in commodity pricing dynamics over the period.
@@
 
-The descriptive statistics for the commodity series considered in the study displayed in table @tbl-stats-no-regimes show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
+@tbl-stats-no-regimes displays descriptive statistics for the commodity series considered in the study; the results show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
 6.9% with a 10% significance in the pre-financialisation period.
-The increase is even more pronounced for an equally weighted portfolio of UK traded assets (metals), 2.47% (not significant) to 21.8% (significant at the 10% level), which sets out the global nature of the phenomenon.
+The increase is even more pronounced for an equally weighted portfolio of GB traded assets (metals), 2.47% (not significant) to 21.8% (significant at the 10% level), which sets out the global nature of the phenomenon.
 Most commodities show a higher mean return while five--Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)--show a lower figure with five significant figures--Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)--against none pre-financialisation.
@@
 The pattern of results for volatilities is similar although the increase is less pronounced.
-Both equally weighted portfolios shows an increase, more pronounced for the UK assets, 10% to 13.6% (US) vs.
-15.7% to 26.9% (UK), while out of the thirty assets, eleven show a drop in volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C (IFUS), Lumber (XCME), Sugar-#11 (IFUS), Natural gas (XNYM), Crude oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
+Both equally weighted portfolios shows an increase, more pronounced for the GB assets, 10% to 13.6% (US) vs.
+15.7% to 26.9% (GB), while out of the thirty assets, eleven show a drop in volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C (IFUS), Lumber (XCME), Sugar-#11 (IFUS), Natural gas (XNYM), Crude oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
 Financialisation seems however to have impacted the commodity complex beyond these mechanical effects of increased long participation ensuing from the entry on index type investments as our results suggest next.
@@
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
-In table @tbl-stats-regimes the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
+In @tbl-stats-regimes the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
 Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another.
 For the remaining six commodities the higher mean return during **contango** is not statistically significant for any of them.
-For the six UK commodities, all metals, five of them had higher mean returns during phases of **backwardation** as compared to **contango** in the first period, with one of these differences being statistically significant at the 10% level while for the remaining asset (Zinc) the higher mean return during **contango** is not statistically significant.
+For the six GB commodities, all metals, five of them had higher mean returns during phases of **backwardation** as compared to **contango** in the first period, with one of these differences being statistically significant at the 10% level while for the remaining asset (Zinc (XLME)) the higher mean return during **contango** is not statistically significant.
 An equally weighted portfolio of the twenty-four US commodities had a mean return of 15.4% during **backwardation** phases, statistically significant at the 1% level, and a mean return of -1.1% during **contango**, both in the first period, with the difference between them statistically significant at the 5% level.
-The corresponding figures for an equally weighted portfolio of the UK metals were 4.4% and 0.3% respectively.
+The corresponding figures for an equally weighted portfolio of the GB metals were 4.4% and 0.3% respectively.
 These results provide broad support for an aggregate version of the Keynesian hedging pressure hypothesis and suggest that hedgers in the aggregate were engaged in risk transfer during this period.
@@
 For the twenty-four US commodities over this period, fourteen have higher mean returns during phases of **contango** over **backwardation**.
-Four of the six UK metals achieved higher mean returns over **contango** relative to **backwardation** phases with the difference being statistically significant for one commodity.
+Four of the six GB metals achieved higher mean returns over **contango** relative to **backwardation** phases with the difference being statistically significant for one commodity.
 The equally weighted US portfolio had a mean return of 15.7% over **backwardation** against 16.2% during phases of **contango**, both statistically significant at the 10% level.
-The difference was considerably more pronounced for the equally weighted UK metals portfolio with a mean return of 8% during **backwardation** rising to 35.6% during **contango**.
+The difference was considerably more pronounced for the equally weighted GB metals portfolio with a mean return of 8% during **backwardation** rising to 35.6% during **contango**.
 
@@
 In the second model hedgers are seen as liquidity providers as in @kang_tale_2020 with this explanation also consistent with the nature of financialisation which led to the arrival of long term, long only investors who require substantial liquidity to roll-over their positions.
-Table @tbl-time-reg-US-CHP supports this view.
+@tbl-time-reg-US-CHP supports this view.
 We regress commodity futures front returns on individual commercial hedging pressure (CHP) as well as aggregate CHP (**CHP**), our market wide measure of CHP, in separate models and find that the explanatory power of CHP at the individual commodity level decreases over the financialisation period with the US cross-sectional average $R^{2}$ falling down to 20.8% from 25.8% in the previous period while that of **CHP** increases (7.1% vs 5.4%).
@@
 
-\bigskip
-\bigskip
+\medskip
 
-Using our bespoke commodity-based asset pricing framework we strive to shed new light on the phenomenon by first regressing returns series for the twenty four individual US commodities against our factor mimicking portfolios independently.
-The resulting individual explanatory powers ($R^2$s), once averaged by factor and period, offer a refined perspective on the relation between return and factor attribute co-movement.
-A low figure indicates low cross-sectional return co-movement for, in this context, return on the corresponding factor mimicking portfolio only has explanatory power on return for commodities that are constituents of one of its legs over the corresponding period.
-The explanatory power for the other commodities is typically low or even 0 for the case where commodities are perfectly uncorrelated with one-another.
-A rising figure on the other hand thus indicates increased pairwise correlations, positive or negative, including amongst factor leg mimicking portfolio constituent commodities; and therefore provides evidence that pairwise return correlation relates to factor attribute.
-The average time series explanatory power of the various one factor models on the US traded assets over the four periods is shown in Table .
-Over the first period the market factor has the best average time series performance with the highest average $R^{2}$ with all three futures market factors performing poorly, indicating that the commodities with extreme factor attributes (high or low CHP for example) are uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of high and low **CHP** (below period median).
-The two factor models average $R^{2}$s (available upon request) are roughly the sum of the one factor $R^{2}$s indicating that the factors are almost orthogonal over this period.
-The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average $R^{2}$ increasing to 8.2% in the second period relative to 1.7% in the first with this improvement coming from the long leg that shows a greater improvement (4.5% to 15.1%) relative to the short (3% to 4%), suggesting that "normally" backwardated commodities (Keynesian perspective) have higher correlation with the rest of the commodity cross-section, and thereby bringing more evidence of the important role played by long only investors in the change in nature of these markets over that period.
-The performance of the market factor also improves though not by as much in a relative sense (21.6% from 11.7%) and both the term structure factor and the open interest growth factor show a much smaller improvement in performance with smaller differences between legs.
-Over all periods, all of our factor models show similar performance across regimes of high and low **CHP**.
+Financialisation was a global phenomenon that, through the channel of index investment, simultaneously influenced the entire spectrum of liquid commodities.
+This sweeping impact spurred the transformation of commodity markets from a collection of idiosyncratic markets into a unified asset class with interconnectedness emerging as a crucial aspect that warrants thorough examination.
+We set out to address this issue by first examining the average of weekly returns pairwise correlations between commodities across the entire cross-section of the commodity assets considered in the study as well as by country, sector and sub-sector.
+@tbl-correlations-periods shows the results for the four periods of interest with the results reported for the entire period as well as for periods of **backwardation** and **contango**.
+For the entire sample the average pairwise correlation jumps from 0.07 in the first period to 0.16 over financialisation.
+These findings indicate higher interdependence within the full cross-section of commodities starting with the financialisation period, consistent with the empirical findings in @fryMcKibbin_evolution_2023 and @mayer_financialization_2017 as well as with the theoretical model of @basak_model_2016.
+The sector analysis sheds light on the driving force behind these changes.
+The US metals see the sharpest increase in pairwise correlations going from 0.22 over the past period to 0.56 over financialisation while the three other sectors see a much smaller percentage increase during financialisation relative to the past period.
+These findings thus suggest that the US metals sector was the driving force behind increased average pairwise correlations during financialisation, a new observation to the best of our knowledge.
+The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods which indicates that increased commodity interdependence over financialisation was not a phase driven phenomenon in the same way that individual commodity returns are, as demonstrated in @tbl-stats-regimes.
+We further examine these correlations by year in @tbl-correlations-years to uncover any distinct breakpoints.
+For the full sample of assets, the average pairwise correlations increase from 0.08 to 0.12 from 2003 to 2004 seemingly driven by US metals average pairwise correlations, more than doubling from 0.22 to 0.49, suggesting 2004 as the onset of financialization as noted in several studies [@baker_financialization_2021; @tang_index_2012] and our contribution is to observe that the US metals sub-sector seems to have played a major role in this.
 
@@
 
-We next investigate the top eight of the US traded commodities which achieved the highest time series $R^{2}$ for the CHP, market, open interest and term structure factors, in each of the four time periods with the commodity picks shown in Table .
-For the CHP factor the commodities that achieve high $R^{2}$ in a given period are likely to be those with relatively high or low CHP over that period, or those commodities that co-vary with the short or the long side of the factor.
-The same applies to the open interest and term structure factors with CHP replaced by open interest growth and roll yield respectively; while for the market factor the picks are those that co-vary most strongly with the market factor over that period.
-For the CHP factor, we observe a change in the picks between the first and the second period; the picks in the first period included five agricultural commodities and three metals while in the second period they include all the five base and precious metals and only three agricultural commodities.
-This pattern is also visible for the term structure factor for which there are four metals (copper, silver, gold and platinum) picks in the second period against two in the first (palladium and platinum) as well as for the open interest nearby growth factor for which there are three metals (silver, gold and platinum) picks in the second period against one in the first (platinum).
-The market factor has three metal picks in the second period (palladium, gold and silver) while all the picks in the first period were agricultural or energy commodities.
-Over the third period, the average CHP factor shows the same metal picks with the agriculturals replaced by energy commodity; the open interest nearby growth factor still has three metal picks with gold swapped for copper and both the market and term structure factors have one, copper.
-The table also shows the proportion of time that these picks were constituents of the corresponding factor.
-All the picks of the long-short factors (average CHP, open interest nearby growth and term structure factors) were constituents of the corresponding factor for some proportion of time in all of the time periods.
-In this respect, there is a contrast between the first and second periods with the average CHP and open interest nearby growth factor picks appearing predominantly on the long side of the corresponding factor in the second period, as opposed to both legs in the first.
-The pattern is particularly strong for the metals and energy commodities respectively, with the exception of copper for the average CHP factor that lives in the short leg a higher proportion of the time over the financialisation period.
-The pattern is reversed for the term structure factor where the picks appear predominantly on the short leg in the second period, as opposed to both legs in the first with the pattern again strongest for the metals.
-This behaviour continues over the third period for the average CHP and open interest nearby growth factors and indicates that their picks consistently exhibited low commercial hedging pressure and high front contract open interest growth respectively while indicating that the term structure factor picks showed low roll yield in the first and second period.
-
-\medskip
-
-In table , we show the average pairwise returns correlation between each set of picks in each time period.
-Following on form the earlier observations, this exercise gives an indication of the extent to which attribute co-movement reveals price co-movement, which is particularly relevant for the long-short factors for which the corresponding attribute is not directly related to price co-movement.
-In the first period the average picks pairwise correlation for the long-short factors ranges from 7.1% (term structure factor picks) to 12.4% (open interest factor picks) while the market factor picks show the highest figure (23.7%).
-In the second period the figures for the long-short factors rise sharply; up to 22.9% from 8.1% for the average CHP factor picks, up to 32.4% from 12.4% for the open interest factor picks and up to 23.4% from 7.1% for the term structure factor picks.
-This increase is stronger than that for the market factor picks in a relative sense and is a consequence of the dramatic increase in average pairwise price correlation amongst the US traded metals which dominate the average CHP factor set of picks and which presence is stronger amongst both the open interest and term structure factor sets of picks over the financialisation period.
-The higher figures for the open interest factor are driven by the strong presence of the energy complex amongst the corresponding picks.
-The latter exhibits much higher average pairwise correlations than the other sectors in both periods although lower in the second relative to the first which reinforces the role played by the metals in the sharp increase in average pairwise correlation amongst picks for this factor.
-With regards to **CHP** regimes, although not very pronounced, a pattern is noticeable.
-For the market, open interest and term structure factor picks, average pairwise correlations are stronger over phases of **contango** in the first period and over phases of **backwardation** in the financialisation period, eventually reverting back to being stronger over **contango** phases in the crisis period with the CHP factor sets of picks showing the opposite pattern.
-Overall, these results suggest an increase in correlation between non-price attributes co-movement and price co-movement over the financialisation period.
-It is also interesting to note that US traded metals returns were negatively correlated with the rest of US traded commodities in the first period and positively in the second.
-
-\medskip
-
-To further understand the link between attribute and price co-movement we build all of the factors from every set of factor picks and assess their explanatory performance on these sets of picks over the four periods independently.
-The results are shown in table .
-The long-short factors for a particular attribute select the top and bottom two of the corresponding picks based on that attribute while the market factor takes an equally weighted combination of the eight corresponding picks.
-In the absence of price co-movement between the picks, the market factor will achieve an average $R^{2}$ of around 12.5%^[Market factor lemma: $\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv$ size of market portfolio (eight here).], while there is no non-zero $R^{2}$ lower bound for the corresponding long-short factors.
-A high average $R^{2}$ for the market factor is indicative of strong price co-movement.
-In this respect, the most remarkable change in performance in a relative sense is that of the market factor built from the CHP factor sets of picks with the average $R^{2}$ more than doubling, from 18.6% up to 38.1%.
-For the long-short factors on the other hand it is indicative of simultaneous attribute and price co-movement.
-For the factors built from the market factor picks the increase is strongest in a relative sense for the CHP factor with the $R^{2}$ more than doubling, going from 5.6% in the first period up to 12.4% in the second with the increase stronger for the long leg (17.1% vs.
-27.9%) relative to the short (16.5% vs.
-21.4%).
-In the case of the factors built from the CHP factor picks, the CHP factor built with its own picks shows a remarkable increase in a relative sense with the $R^{2}$ tripling, from 7.2% to 21.4% and the long leg showing a much greater increase relative to the short (10.4% to 31.1% vs.
-8.3% to 9.8%).
-The performance of the term structure factor built from the CHP factor sets of picks also shows a sizable increase in a relative sense, from 3.5% to 5.3% and even more remarkable in this case is the substantial increase in performance of the short leg, from 6.3% to 15.7% relative to the long (7.5% to 9.8%).
-The pattern is reversed for the CHP factor built from the term structure factor picks where the average $R^{2}$ increases from 4.7% to 8% with the performance of the long leg increasing from 11.9% to 28.1% vs.
-5.5% to 9.1% for the short.
-The performance of the term structure factor constructed from its own sets of picks also shows a substantial increase, from 5.1% to 8.4%  with, here again the increase in performance relatively stronger for the short leg, from 6% to 16.1% vs.
-7.6% to 12.1% for the long.
-Taken together with the previous results showing that the metal complex predominantly loads on the long and short legs of the original CHP and term structure factors respectively, these results provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation perhaps as a result of spillover effects between the corresponding futures and spot markets as suggested in @basak_model_2016.
-
-\medskip
-
-In table we assess the performance of the same factors on all the commodities instead of just the picks.
-While the average $R^{2}$s are expectedly lower, the pattern of results mostly holds with the relative performance of the market factors built with different sets of picks as well as that of the CHP and term structure factors built with each other's picks similar to table .
-In contrast, the average CHP factor built with average CHP factor picks shows a smaller absolute increase in average $R^{2}$ indicating that the link between CHP co-movement and price co-movement is stronger amongst the picks which are predominantly metals.
-Taken together, the results in tables and suggest that the onset of financialisation had a major impact on the dynamics of US traded precious and precious-base metals.
-To assess whether this phenomenon extended beyond US borders we examine the performance of the factors used in the last two tables above on the six UK metals futures traded on the London Metal Exchange with the results reported in table .
-In the first period, although all sets of picks, except that of the market factor, included at least one metal, the average $R^{2}$s are very low; close to zero in most cases.
-These figures drastically increase across the board in the financialisation period and show a pattern similar to that observed in the US complex.
-The market factor built from the CHP and term structure factor sets of picks shows the sharpest increase in performance, relative to using the other sets of factor picks; rising to 20.1% from 1.5% and to 15% from 0.8% respectively.
-The increase in $R^{2}$ for the market factor built with market factor picks is more modest, providing further evidence of concentration of co-movement in the metals sector during financialisation.
-Here again the change in performance for the CHP and term structure factor legs stands out where the factors are built with their own as well as each other's sets of picks.
-The average $R^{2}$ for the long leg of the CHP factor built with its own sets of picks increases from 1% to 11% while the short leg shows no significant change.
-The opposite holds for the term structure factor built from its own set of picks with the short leg performance increasing from 0.1% to 14% while that of the long leg remains below 1%.
-Building these factors from each other's sets of picks produces a similar pattern with the performance of the long leg of the CHP factor built from the term structure factor picks increasing from 0.7% to 11.4%; a much greater increase relative to the short leg although in this case the latter also shows a sizable increase in performance (0.3% to 6%).
-The performance of the short leg of the term structure factor built from the CHP factor sets of picks on the other hand increases from 0.3% to 19.2% while the performance for the long leg in the second period remains below 1.5%.
-Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working's term structure paradigms.
-There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of @kang_tale_2020 who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
+We investigate further the issue of co-movement from an asset pricing perspective using a bespoke asset pricing framework starting with a market factor mimicking portfolio constituted of the twenty-four US traded commodities considered in the study with equal weighting.
+This portfolio enables a refined examination of cross correlations across sectors as the numerator of the beta of the regression of the returns for an individual commodity against those for the market factor is driven by covariances while the denominator is driven by the individual commodity variance.
+Thus, an increase in a commodity's correlation with other commodities should lead to an increase in its beta relative to the market factor portfolio.
+We therefore regress the weekly individual commodity front futures returns against those for our market factor portfolio and average the resulting betas across the entire set of commodity assets considered as well as by country, sector and sub-sector for each of the four periods of interest with the results shown in @tbl-regressions-index.
+The average beta for the US metals sector jumps sharply to 1.12 over financialisation from 0.63 over the previous period; the increase is even more dramatic for the base metals sub-sector (GB traded assets) in a relative sense.
+The group had a much lower beta of 0.27 over the past period, suggesting a low level of correlation with US commodities; this figure increases to 0.85 over the financialisation period, even beyond that for the US agricultural sector of 0.80.
+In contrast, the corresponding figures for the energy sector show a substantial decrease, down to 1.61 during financialisation from 2.33 over the past period.
+The corresponding pricing performance displays a similar pattern as shown in @tbl-regressions-factors where for each period the corresponding $R^{2}$ values are independently averaged over the entire period as well as over periods of **contango** and **backwardation**.
+The average $R^{2}$ for the market factor across the entire cross-section of commodity assets considered in the study, including the GB traded base metals, increases to around 20% during financialisation compared to around 10% over the previous period with the rise driven by the metals sector at large.
+The sector average for the US traded assets jumps to 31% during financialisation from 7.5% over the past period while for the GB traded assets the corresponding figure increases from less than 2%, or virtually no explanatory power for the (US based) market factor to almost 12% over the financialisation period.
+The results for our other risk factor mimicking portfolios show a similar pattern and provide a deeper insights into co-movement dynamics in this context.
+All three factors---CHP, open interest and term structure---performed poorly in the first period, indicating that the commodities with extreme factor attributes (high or low CHP for example) were uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of **contango** and **backwardation**.
+The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average $R^{2}$, albeit still small at 5.4%, almost tripling from the past to the financialisation period in contrast to the other factors that show weaker dynamics with a slight decrease and a much smaller increase for the open interest and term structure factors respectively.
+Here again the dramatic increase in pricing performance for the CHP factor is driven by the metals sector, particularly the precious sub-sector with the average $R^{2}$ for the group jumping to almost 26% during financialisation from 1.2% over the past period.
+The corresponding figures of 22% and 1.1% for the entire US metals sector stand in sharp contrast with the agricultural sector, which exhibits no notable change, and the energy sector, where pricing performance drops substantially from 9.2% down to 1.6%.
+The improvement in the CHP factor's pricing performance remarkably comes predominantly from the long leg (low CHP assets: Keynesian "normal backwardation") of the factor^{Results available from the authors upon request.} with the corresponding mimicking portfolio's performance itself driven by the metals, the precious sub-sector in particular.
+The average $R^{2}$ for the group jumps to 55% during financialisation from less than 12% over the past period while the short leg sees a far smaller increase, up to 8.9% from 3.3% over the past period.
+Interestingly, although the factor itself only sees a very modest increase, its short leg (low roll-yield assets: Working's backwardation) shows a sizeable rise in pricing performance, yet again driven the metals sector, with the average $R^{2}$ for the group's US traded assets jumping to 28.2% during financialisation from 6.2% over the past period.
+The pattern of results for both factors extends to the GB trade assets and suggest a convergence of Keneysian and Working's term structure perspective over the financialisation period.
+Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working’s term structure paradigms.
+There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of Kang et al.
+(2020) who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
 
@@
 The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results.
-Returns fall sharply relative to the financialisation period (table ) with eighteen US commodities along with all six UK traded metals showing lower mean returns.
+Returns fall sharply relative to the financialisation period (@tbl-stats-no-regimes) with eighteen US commodities along with all six GB traded metals showing lower mean returns.
 Returns for equally weighted portfolios of both sets of assets fall down to 9.4% and 5.3% from 15.9% and 21.8% respectively.
-Returns are mostly higher during phases of **backwardation** relative to **contango** (table ) with fifteen US assets and five of the UK traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets.
-Volatility is moderately higher for both sets with fifteen US commodities and three UK metals showing higher figures and interestingly eminently higher over phases of **contango**; out of the US complex only Sugar-#11 (IFUS) and none of the UK traded metals show higher volatility figures over **backwardation** phases.
-The symmetry between the dynamics of CHP and **CHP**'s explanatory power on individual commodity returns breaks in the crisis period with both now seemingly converging; the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%).
-The performance of the market factor dominates the US commodity complex over the period with a 50% increase in mean average $R^{2}$ to over 30% (table ) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
-The average pairwise correlation amongst the market factor picks increases beyond 50% while there is a leveling in that amongst the picks of the long-short factors as shown in table .
-Notwithstanding, the market factor built from any sets of picks shows a significant rise across the board in performance on the US complex (table ).
+Returns are mostly higher during phases of **backwardation** relative to **contango** (@tbl-stats-regimes) with fifteen US assets and five of the GB traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets.
+Volatility is moderately higher for both sets with fifteen US commodities and three GB metals showing higher figures and interestingly eminently higher over phases of **contango**; out of the US complex only Sugar-#11 (IFUS) and none of the GB traded metals show higher volatility figures over **backwardation** phases.
+The symmetry between the dynamics of CHP and **CHP**'s explanatory power on individual commodity returns breaks in the crisis period (@tbl-time-reg-US-CHP) with both now seemingly converging; the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%).
+
+// TODO Add correlation results discussion here.
+
+The performance of the market factor dominates the US commodity complex over the period with a 50% increase in mean average $R^{2}$ to over 30% (@tbl-regressions-factors) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
 Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
-Table  provides further evidence of systematic linkages, in this case between US and non-US traded commodities with a similar, albeit more pronounced pattern, where the market factor constructed with any sets of picks (US traded commodities) shows a dramatic increase in performance on the UK metals with for example, when constructed from its own sets of picks, the average $R^{2}$ increasing to 31.7% from 10.2% in the previous period.
 
@@
 
-The returns pullback continues into the post-crisis period (table ) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively.
+The returns pull-back continues into the post-crisis period (@tbl-stats-no-regimes) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively.
 Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
 The figures for the equally weighted portfolios of US and UK assets drop to 9.9% and 16.2% respectively, very close to pre-financialisation levels.
-The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (table ) with mean returns higher during phases of **backwardation** relative to **contango** (table ), more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
+The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (@tbl-stats-regimes) with mean returns higher during phases of **backwardation** relative to **contango**, more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
 The difference is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
@@
 Over the financialisation period in contrast volatilities were predominantly higher in **backwardation** for US traded assets with fourteen commodities showing higher volatility figures in these phases; the post-crisis pattern of results for volatilities thus likewise shows signs of reversion to pre-financialisation standards.
-After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and **CHP** part ways (table ), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
+After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and **CHP** part ways (@tbl-time-reg-US-CHP), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
 The recovery initiated in the crisis period for that of CHP is confirmed with a stronger increase in the post-crisis period, 27.2% vs.
@@
 14.8%.
-Average pairwise correlations amongst factor picks (table ) fall substantially in the post-crisis period with for example the figure for the market factor picks dropping from 50.1% to 26.1%, almost down to pre-financialisation levels; results are similar for the long-short factor picks with figures below financialisation levels in all cases and very close to pre-financialisation standards for the term structure and liquidity factor picks.
-The performance of the market factor on the US complex declines below financialisation levels (table ) with the pattern similar albeit stronger when the factor is built from the sets of factor picks with a decline in performance on the US complex (table ) to almost pre-financialisation levels when constructed with its own set of picks as well as with those of the long-short factors, in particular the term structure and liquidity factors.
-Table  provides further evidence of decoupling, in this case between US and non-US traded commodities with a sharp decline in performance of the market factor constructed with any set of picks on the UK complex below financialisation, down to almost pre-financialisation levels when constructed with the sets of long-short factors picks.
 
@@
 
-make_table("regressions - all returns ~ marke index", colnames, align, 1L:7L, 4L:7L)
+make_table("regressions - all returns ~ market index", colnames, align, 1L:7L, 4L:7L)
 ```
@@
 #| tbl-cap: "This table shows the average time series regression $R^{2}$ for models where the returns series for all the commodity assets considered in the study are independently regressed against the return series for our mimicking portfolios for risk factors in returns, including the market, CHP, open interest and term structure factors.
-The results are calculated independently across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018); for earch period the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
+The results are calculated independently across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018); for each period the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
 Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \\@sec-methods while the results are discussed in section \\@sec-results."

### 2024-09-20 docs/paper.tex
Write up result section for past and financialisation periods

@@
 large cross-section of liquid commodities as suggested by the nature of
-financilisation that comprehends commodity futures as an asset class.
+financialisation that comprehends commodity futures as an asset class.
 Using a bespoke asset pricing factors based framework we study the issue
@@
 cross-market linkages with the UK traded commodity subset. The
-post-crisis results, in contrast, show a substancial pullback in
+post-crisis results, in contrast, show a substantial pull-back in
 performance for the market factor across the board as well as evidence
@@
 \citet{fattouh_role_2013}, \citet{kilian_role_2014},
-\citet{knittel_simple_2016} and \citet{manera_modeling_2016} examined
+\citet{knittel_simple_2016} and \citet{manera_modelling_2016} examined
 the energy markets while \citet{bohl_does_2013}, \citet{kim_does_2015}
@@
 
-The descriptive statistics for the commodity series considered in the
-study displayed in table Table~\ref{tbl-stats-no-regimes} show a clear
+Table~\ref{tbl-stats-no-regimes} displays descriptive statistics for the
+commodity series considered in the study; the results show a clear
 pattern of increase in average return during financialisation with an
@@
 significance in the pre-financialisation period. The increase is even
-more pronounced for an equally weighted portfolio of UK traded assets
+more pronounced for an equally weighted portfolio of GB traded assets
 (metals), 2.47\% (not significant) to 21.8\% (significant at the 10\%
@@
 is less pronounced. Both equally weighted portfolios shows an increase,
-more pronounced for the UK assets, 10\% to 13.6\% (US) vs.~15.7\% to
-26.9\% (UK), while out of the thirty assets, eleven show a drop in
+more pronounced for the GB assets, 10\% to 13.6\% (US) vs.~15.7\% to
+26.9\% (GB), while out of the thirty assets, eleven show a drop in
 volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C
@@
 that returns for individual commodities should be high in periods where
-\textbf{CHP} is low and vice et versa. In table
-Table~\ref{tbl-stats-regimes} the mean returns are shown over high
-(\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP}
-regimes for each time period.\\
+\textbf{CHP} is low and vice et versa. In Table~\ref{tbl-stats-regimes}
+the mean returns are shown over high (\textbf{contango}) and low
+(\textbf{backwardation}) \textbf{CHP} regimes for each time period.\\
 Over the first period eighteen of the twenty-four US commodities have
@@
 the higher mean return during \textbf{contango} is not statistically
-significant for any of them. For the six UK commodities, all metals,
+significant for any of them. For the six GB commodities, all metals,
 five of them had higher mean returns during phases of
@@
 period, with one of these differences being statistically significant at
-the 10\% level while for the remaining asset (Zinc) the higher mean
-return during \textbf{contango} is not statistically significant. An
-equally weighted portfolio of the twenty-four US commodities had a mean
-return of 15.4\% during \textbf{backwardation} phases, statistically
-significant at the 1\% level, and a mean return of -1.1\% during
-\textbf{contango}, both in the first period, with the difference between
-them statistically significant at the 5\% level. The corresponding
-figures for an equally weighted portfolio of the UK metals were 4.4\%
-and 0.3\% respectively. These results provide broad support for an
-aggregate version of the Keynesian hedging pressure hypothesis and
-suggest that hedgers in the aggregate were engaged in risk transfer
+the 10\% level while for the remaining asset (Zinc (XLME)) the higher
+mean return during \textbf{contango} is not statistically significant.
+An equally weighted portfolio of the twenty-four US commodities had a
+mean return of 15.4\% during \textbf{backwardation} phases,
+statistically significant at the 1\% level, and a mean return of -1.1\%
+during \textbf{contango}, both in the first period, with the difference
+between them statistically significant at the 5\% level. The
+corresponding figures for an equally weighted portfolio of the GB metals
+were 4.4\% and 0.3\% respectively. These results provide broad support
+for an aggregate version of the Keynesian hedging pressure hypothesis
+and suggest that hedgers in the aggregate were engaged in risk transfer
 during this period.\\
@@
 returns during phases of \textbf{contango} over \textbf{backwardation}.
-Four of the six UK metals achieved higher mean returns over
+Four of the six GB metals achieved higher mean returns over
 \textbf{contango} relative to \textbf{backwardation} phases with the
@@
 \textbf{contango}, both statistically significant at the 10\% level. The
-difference was considerably more pronounced for the equally weighted UK
+difference was considerably more pronounced for the equally weighted GB
 metals portfolio with a mean return of 8\% during \textbf{backwardation}
@@
 only investors who require substantial liquidity to roll-over their
-positions. Table Table~\ref{tbl-time-reg-US-CHP} supports this view. We
+positions. Table~\ref{tbl-time-reg-US-CHP} supports this view. We
 regress commodity futures front returns on individual commercial hedging
@@
 
-\bigskip
-\bigskip
-
-Using our bespoke commodity-based asset pricing framework we strive to
-shed new light on the phenomenon by first regressing returns series for
-the twenty four individual US commodities against our factor mimicking
-portfolios independently. The resulting individual explanatory powers
-(\(R^2\)s), once averaged by factor and period, offer a refined
-perspective on the relation between return and factor attribute
-co-movement. A low figure indicates low cross-sectional return
-co-movement for, in this context, return on the corresponding factor
-mimicking portfolio only has explanatory power on return for commodities
-that are constituents of one of its legs over the corresponding period.
-The explanatory power for the other commodities is typically low or even
-0 for the case where commodities are perfectly uncorrelated with
-one-another. A rising figure on the other hand thus indicates increased
-pairwise correlations, positive or negative, including amongst factor
-leg mimicking portfolio constituent commodities; and therefore provides
-evidence that pairwise return correlation relates to factor attribute.\\
-The average time series explanatory power of the various one factor
-models on the US traded assets over the four periods is shown in Table .
-Over the first period the market factor has the best average time series
-performance with the highest average \(R^{2}\) with all three futures
-market factors performing poorly, indicating that the commodities with
-extreme factor attributes (high or low CHP for example) are uncorrelated
-with the rest of the commodity cross-section, and the overall
-performance consistent across periods of high and low \textbf{CHP}
-(below period median). The two factor models average \(R^{2}\)s
-(available upon request) are roughly the sum of the one factor
-\(R^{2}\)s indicating that the factors are almost orthogonal over this
-period.\\
-The onset of financialisation leads to a substantial improvement in the
-performance of the CHP factor with its average \(R^{2}\) increasing to
-8.2\% in the second period relative to 1.7\% in the first with this
-improvement coming from the long leg that shows a greater improvement
-(4.5\% to 15.1\%) relative to the short (3\% to 4\%), suggesting that
-``normally'' backwardated commodities (Keynesian perspective) have
-higher correlation with the rest of the commodity cross-section, and
-thereby bringing more evidence of the important role played by long only
-investors in the change in nature of these markets over that period. The
-performance of the market factor also improves though not by as much in
-a relative sense (21.6\% from 11.7\%) and both the term structure factor
-and the open interest growth factor show a much smaller improvement in
-performance with smaller differences between legs. Over all periods, all
-of our factor models show similar performance across regimes of high and
-low \textbf{CHP}.
-
-\medskip
-
-We next investigate the top eight of the US traded commodities which
-achieved the highest time series \(R^{2}\) for the CHP, market, open
-interest and term structure factors, in each of the four time periods
-with the commodity picks shown in Table .\\
-For the CHP factor the commodities that achieve high \(R^{2}\) in a
-given period are likely to be those with relatively high or low CHP over
-that period, or those commodities that co-vary with the short or the
-long side of the factor. The same applies to the open interest and term
-structure factors with CHP replaced by open interest growth and roll
-yield respectively; while for the market factor the picks are those that
-co-vary most strongly with the market factor over that period.\\
-For the CHP factor, we observe a change in the picks between the first
-and the second period; the picks in the first period included five
-agricultural commodities and three metals while in the second period
-they include all the five base and precious metals and only three
-agricultural commodities. This pattern is also visible for the term
-structure factor for which there are four metals (copper, silver, gold
-and platinum) picks in the second period against two in the first
-(palladium and platinum) as well as for the open interest nearby growth
-factor for which there are three metals (silver, gold and platinum)
-picks in the second period against one in the first (platinum). The
-market factor has three metal picks in the second period (palladium,
-gold and silver) while all the picks in the first period were
-agricultural or energy commodities.\\
-Over the third period, the average CHP factor shows the same metal picks
-with the agriculturals replaced by energy commodity; the open interest
-nearby growth factor still has three metal picks with gold swapped for
-copper and both the market and term structure factors have one,
-copper.\\
-The table also shows the proportion of time that these picks were
-constituents of the corresponding factor. All the picks of the
-long-short factors (average CHP, open interest nearby growth and term
-structure factors) were constituents of the corresponding factor for
-some proportion of time in all of the time periods. In this respect,
-there is a contrast between the first and second periods with the
-average CHP and open interest nearby growth factor picks appearing
-predominantly on the long side of the corresponding factor in the second
-period, as opposed to both legs in the first. The pattern is
-particularly strong for the metals and energy commodities respectively,
-with the exception of copper for the average CHP factor that lives in
-the short leg a higher proportion of the time over the financialisation
-period. The pattern is reversed for the term structure factor where the
-picks appear predominantly on the short leg in the second period, as
-opposed to both legs in the first with the pattern again strongest for
-the metals. This behaviour continues over the third period for the
-average CHP and open interest nearby growth factors and indicates that
-their picks consistently exhibited low commercial hedging pressure and
-high front contract open interest growth respectively while indicating
-that the term structure factor picks showed low roll yield in the first
-and second period.
-
-\medskip
-
-In table , we show the average pairwise returns correlation between each
-set of picks in each time period. Following on form the earlier
-observations, this exercise gives an indication of the extent to which
-attribute co-movement reveals price co-movement, which is particularly
-relevant for the long-short factors for which the corresponding
-attribute is not directly related to price co-movement.\\
-In the first period the average picks pairwise correlation for the
-long-short factors ranges from 7.1\% (term structure factor picks) to
-12.4\% (open interest factor picks) while the market factor picks show
-the highest figure (23.7\%). In the second period the figures for the
-long-short factors rise sharply; up to 22.9\% from 8.1\% for the average
-CHP factor picks, up to 32.4\% from 12.4\% for the open interest factor
-picks and up to 23.4\% from 7.1\% for the term structure factor picks.
-This increase is stronger than that for the market factor picks in a
-relative sense and is a consequence of the dramatic increase in average
-pairwise price correlation amongst the US traded metals which dominate
-the average CHP factor set of picks and which presence is stronger
-amongst both the open interest and term structure factor sets of picks
-over the financialisation period. The higher figures for the open
-interest factor are driven by the strong presence of the energy complex
-amongst the corresponding picks. The latter exhibits much higher average
-pairwise correlations than the other sectors in both periods although
-lower in the second relative to the first which reinforces the role
-played by the metals in the sharp increase in average pairwise
-correlation amongst picks for this factor.\\
-With regards to \textbf{CHP} regimes, although not very pronounced, a
-pattern is noticeable. For the market, open interest and term structure
-factor picks, average pairwise correlations are stronger over phases of
-\textbf{contango} in the first period and over phases of
-\textbf{backwardation} in the financialisation period, eventually
-reverting back to being stronger over \textbf{contango} phases in the
-crisis period with the CHP factor sets of picks showing the opposite
-pattern. Overall, these results suggest an increase in correlation
-between non-price attributes co-movement and price co-movement over the
-financialisation period. It is also interesting to note that US traded
-metals returns were negatively correlated with the rest of US traded
-commodities in the first period and positively in the second.
-
-\medskip
-
-To further understand the link between attribute and price co-movement
-we build all of the factors from every set of factor picks and assess
-their explanatory performance on these sets of picks over the four
-periods independently. The results are shown in table . The long-short
-factors for a particular attribute select the top and bottom two of the
-corresponding picks based on that attribute while the market factor
-takes an equally weighted combination of the eight corresponding picks.
-In the absence of price co-movement between the picks, the market factor
-will achieve an average \(R^{2}\) of around 12.5\%\footnote{Market
-  factor lemma:
-  \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\)
-  size of market portfolio (eight here).}, while there is no non-zero
-\(R^{2}\) lower bound for the corresponding long-short factors.\\
-A high average \(R^{2}\) for the market factor is indicative of strong
-price co-movement. In this respect, the most remarkable change in
-performance in a relative sense is that of the market factor built from
-the CHP factor sets of picks with the average \(R^{2}\) more than
-doubling, from 18.6\% up to 38.1\%. For the long-short factors on the
-other hand it is indicative of simultaneous attribute and price
-co-movement. For the factors built from the market factor picks the
-increase is strongest in a relative sense for the CHP factor with the
-\(R^{2}\) more than doubling, going from 5.6\% in the first period up to
-12.4\% in the second with the increase stronger for the long leg (17.1\%
-vs.~27.9\%) relative to the short (16.5\% vs.~21.4\%). In the case of
-the factors built from the CHP factor picks, the CHP factor built with
-its own picks shows a remarkable increase in a relative sense with the
-\(R^{2}\) tripling, from 7.2\% to 21.4\% and the long leg showing a much
-greater increase relative to the short (10.4\% to 31.1\% vs.~8.3\% to
-9.8\%). The performance of the term structure factor built from the CHP
-factor sets of picks also shows a sizable increase in a relative sense,
-from 3.5\% to 5.3\% and even more remarkable in this case is the
-substantial increase in performance of the short leg, from 6.3\% to
-15.7\% relative to the long (7.5\% to 9.8\%). The pattern is reversed
-for the CHP factor built from the term structure factor picks where the
-average \(R^{2}\) increases from 4.7\% to 8\% with the performance of
-the long leg increasing from 11.9\% to 28.1\% vs.~5.5\% to 9.1\% for the
-short. The performance of the term structure factor constructed from its
-own sets of picks also shows a substantial increase, from 5.1\% to 8.4\%
-with, here again the increase in performance relatively stronger for the
-short leg, from 6\% to 16.1\% vs.~7.6\% to 12.1\% for the long.\\
-Taken together with the previous results showing that the metal complex
-predominantly loads on the long and short legs of the original CHP and
-term structure factors respectively, these results provide evidence of
-convergence of Keynesian and Working's theories of the term structure in
-detecting price co-movement during financialisation perhaps as a result
-of spillover effects between the corresponding futures and spot markets
-as suggested in \citet{basak_model_2016}.
-
-\medskip
-
-In table we assess the performance of the same factors on all the
-commodities instead of just the picks. While the average \(R^{2}\)s are
-expectedly lower, the pattern of results mostly holds with the relative
-performance of the market factors built with different sets of picks as
-well as that of the CHP and term structure factors built with each
-other's picks similar to table . In contrast, the average CHP factor
-built with average CHP factor picks shows a smaller absolute increase in
-average \(R^{2}\) indicating that the link between CHP co-movement and
-price co-movement is stronger amongst the picks which are predominantly
-metals. Taken together, the results in tables and suggest that the onset
-of financialisation had a major impact on the dynamics of US traded
-precious and precious-base metals.\\
-To assess whether this phenomenon extended beyond US borders we examine
-the performance of the factors used in the last two tables above on the
-six UK metals futures traded on the London Metal Exchange with the
-results reported in table . In the first period, although all sets of
-picks, except that of the market factor, included at least one metal,
-the average \(R^{2}\)s are very low; close to zero in most cases. These
-figures drastically increase across the board in the financialisation
-period and show a pattern similar to that observed in the US complex.
-The market factor built from the CHP and term structure factor sets of
-picks shows the sharpest increase in performance, relative to using the
-other sets of factor picks; rising to 20.1\% from 1.5\% and to 15\% from
-0.8\% respectively. The increase in \(R^{2}\) for the market factor
-built with market factor picks is more modest, providing further
-evidence of concentration of co-movement in the metals sector during
-financialisation.\\
-Here again the change in performance for the CHP and term structure
-factor legs stands out where the factors are built with their own as
-well as each other's sets of picks. The average \(R^{2}\) for the long
-leg of the CHP factor built with its own sets of picks increases from
-1\% to 11\% while the short leg shows no significant change. The
-opposite holds for the term structure factor built from its own set of
-picks with the short leg performance increasing from 0.1\% to 14\% while
-that of the long leg remains below 1\%. Building these factors from each
-other's sets of picks produces a similar pattern with the performance of
-the long leg of the CHP factor built from the term structure factor
-picks increasing from 0.7\% to 11.4\%; a much greater increase relative
-to the short leg although in this case the latter also shows a sizable
-increase in performance (0.3\% to 6\%). The performance of the short leg
-of the term structure factor built from the CHP factor sets of picks on
-the other hand increases from 0.3\% to 19.2\% while the performance for
-the long leg in the second period remains below 1.5\%.\\
+\medskip
+
+Financialisation was a global phenomenon that, through the channel of
+index investment, simultaneously influenced the entire spectrum of
+liquid commodities. This sweeping impact spurred the transformation of
+commodity markets from a collection of idiosyncratic markets into a
+unified asset class with interconnectedness emerging as a crucial aspect
+that warrants thorough examination.\\
+We set out to address this issue by first examining the average of
+weekly pairwise correlations between commodities across the entire
+cross-section of the commodity assets considered in the study as well as
+by country, sector and sub-sector. Table~\ref{tbl-correlations-periods}
+shows the results for the four periods of interest with the results
+reported for the entire period as well as for periods of
+\textbf{backwardation} and \textbf{contango}. For the entire sample the
+average pairwise correlation jumps from 0.07 in the first period to 0.16
+over financialisation. These findings indicate higher interdependence
+within the full cross-section of commodities starting with the
+financialisation period, consistent with the empirical findings in
+\citet{fryMcKibbin_evolution_2023} and
+\citet{mayer_financialization_2017} as well as with the theoretical
+model of \citet{basak_model_2016}. The sector analysis sheds light on
+the driving force behind these changes. The US metals see the sharpest
+increase in pairwise correlations going from 0.22 over the past period
+to 0.56 over financialisation while the three other sectors see a much
+smaller percentage increase during financialisation relative to the past
+period. These findings thus suggest that the US metals sector was the
+driving force behind increased average pairwise correlations during
+financialisation, a new observation to the best of our knowledge. The
+pattern of correlations is very similar across phases of
+\textbf{backwardation} and \textbf{contango} for all the sectors and
+sub-sectors over the past and financialisation periods which indicates
+that increased commodity interdependence over financialisation was not a
+phase driven phenomenon in the same way that individual commodity
+returns are, as demonstrated in Table~\ref{tbl-stats-regimes}.\\
+We further examine these correlations by year in
+Table~\ref{tbl-correlations-years} to uncover any distinct breakpoints.
+For the full sample of assets, the average pairwise correlations
+increase from 0.08 to 0.12 from 2003 to 2004 seemingly driven by US
+metals average pairwise correlations, more than doubling from 0.22 to
+0.49, suggesting 2004 as the onset of financialization as noted in
+several studies \citep{baker_financialization_2021, tang_index_2012} and
+our contribution is to observe that the US metals sub-sector seems to
+have played a major role in this.
+
+\medskip
+
+We investigate further the issue of co-movement from an asset pricing
+perspective using a bespoke asset pricing framework starting with a
+market factor mimicking portfolio constituted of the twenty-four US
+traded commodities considered in the study with equal weighting. This
+portfolio enables a refined examination of cross correlations across
+sectors as the numerator of the beta of the regression of the returns
+for an individual commodity against those for the market factor is
+driven by covariances while the denominator is driven by the individual
+commodity variance. Thus, an increase in a commodity's correlation with
+other commodities should lead to an increase in its beta relative to the
+market factor portfolio. We therefore regress the weekly individual
+commodity front futures returns against those for our market factor
+portfolio and average the resulting betas across the entire set of
+commodity assets considered as well as by country, sector and sub-sector
+for each of the four periods of interest with the results shown in
+Table~\ref{tbl-regressions-index}. The average beta for the US metals
+sector jumps sharply to 1.12 over financialisation from 0.63 over the
+previous period; the increase is even more dramatic for the base metals
+sub-sector (GB traded assets) in a relative sense. The group had a much
+lower beta of 0.27 over the past period, suggesting a low level of
+correlation with US commodities; this figure increases to 0.85 over the
+financialisation period, even beyond that for the US agricultural sector
+of 0.80. In contrast, the corresponding figures for the energy sector
+show a substantial decrease, down to 1.61 during financialisation from
+2.33 over the past period.\\
+The corresponding pricing performance displays a similar pattern as
+shown in Table~\ref{tbl-regressions-factors} where for each period the
+corresponding \(R^{2}\) values are independently averaged over the
+entire period as well as over periods of \textbf{contango} and
+\textbf{backwardation}. The average \(R^{2}\) for the market factor
+across the entire cross-section of commodity assets considered in the
+study, including the GB traded base metals, increases to around 20\%
+during financialisation compared to around 10\% over the previous period
+with the rise driven by the metals sector at large. The sector average
+for the US traded assets jumps to 31\% during financialisation from
+7.5\% over the past period while for the GB traded assets the
+corresponding figure increases from less than 2\%, or virtually no
+explanatory power for the (US based) market factor to almost 12\% over
+the financialisation period. The results for our other risk factor
+mimicking portfolios show a similar pattern and provide a deeper
+insights into co-movement dynamics in this context. All three
+factors---CHP, open interest and term structure---performed poorly in
+the first period, indicating that the commodities with extreme factor
+attributes (high or low CHP for example) were uncorrelated with the rest
+of the commodity cross-section, and the overall performance consistent
+across periods of \textbf{contango} and \textbf{backwardation}. The
+onset of financialisation leads to a substantial improvement in the
+performance of the CHP factor with its average \(R^{2}\), albeit still
+small at 5.4\%, almost tripling from the past to the financialisation
+period in contrast to the other factors that show weaker dynamics with a
+slight decrease and a much smaller increase for the open interest and
+term structure factors respectively. Here again the dramatic increase in
+pricing performance for the CHP factor is driven by the metals sector,
+particularly the precious sub-sector with the average \(R^{2}\) for the
+group jumping to almost 26\% during financialisation from 1.2\% over the
+past period. The corresponding figures of 22\% and 1.1\% for the entire
+US metals sector stand in sharp contrast with the agricultural sector,
+which exhibits no notable change, and the energy sector, where pricing
+performance drops substantially from 9.2\% down to 1.6\%. The
+improvement in the CHP factor's pricing performance remarkably comes
+predominantly from the long leg (low CHP assets: Keynesian ``normal
+backwardation'') of the factor\^{}\{Results available from the authors
+upon request.\} with the corresponding mimicking portfolio's performance
+itself driven by the metals, the precious sub-sector in particular. The
+average \(R^{2}\) for the group jumps to 55\% during financialisation
+from less than 12\% over the past period while the short leg sees a far
+smaller increase, up to 8.9\% from 3.3\% over the past period.
+Interestingly, although the factor itself only sees a very modest
+increase, its short leg (low roll-yield assets: Working's backwardation)
+shows a sizeable rise in pricing performance, yet again driven the
+metals sector, with the average \(R^{2}\) for the group's US traded
+assets jumping to 28.2\% during financialisation from 6.2\% over the
+past period. The pattern of results for both factors extends to the GB
+trade assets and suggest a convergence of Keneysian and Working's term
+structure perspective over the financialisation period.\\
 Taken together these results emphasise the global nature of the impact
@@
 term structure factor built on the Working paradigm and these findings
-therefore appear to complement the results of \citet{kang_tale_2020} who
+therefore appear to complement the results of Kang et al.~(2020) who
 find that hedging pressure both conveys information about liquidity
@@
 results. Returns fall sharply relative to the financialisation period
-(table ) with eighteen US commodities along with all six UK traded
-metals showing lower mean returns. Returns for equally weighted
-portfolios of both sets of assets fall down to 9.4\% and 5.3\% from
-15.9\% and 21.8\% respectively. Returns are mostly higher during phases
-of \textbf{backwardation} relative to \textbf{contango} (table ) with
-fifteen US assets and five of the UK traded metals showing higher mean
-returns in \textbf{backwardation} and the pattern extending to equally
-weighted portfolios of the two sets of assets. Volatility is moderately
-higher for both sets with fifteen US commodities and three UK metals
-showing higher figures and interestingly eminently higher over phases of
-\textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none
-of the UK traded metals show higher volatility figures over
-\textbf{backwardation} phases. The symmetry between the dynamics of CHP
-and \textbf{CHP}'s explanatory power on individual commodity returns
-breaks in the crisis period with both now seemingly converging; the US
-cross-sectional average \(R^{2}\) at the individual level bouncing back
-up (22.5\% vs 20.8\%) while that at the aggregate level rises further
-(14.7\% vs 7.1\%).\\
+(Table~\ref{tbl-stats-no-regimes}) with eighteen US commodities along
+with all six GB traded metals showing lower mean returns. Returns for
+equally weighted portfolios of both sets of assets fall down to 9.4\%
+and 5.3\% from 15.9\% and 21.8\% respectively. Returns are mostly higher
+during phases of \textbf{backwardation} relative to \textbf{contango}
+(Table~\ref{tbl-stats-regimes}) with fifteen US assets and five of the
+GB traded metals showing higher mean returns in \textbf{backwardation}
+and the pattern extending to equally weighted portfolios of the two sets
+of assets. Volatility is moderately higher for both sets with fifteen US
+commodities and three GB metals showing higher figures and interestingly
+eminently higher over phases of \textbf{contango}; out of the US complex
+only Sugar-\#11 (IFUS) and none of the GB traded metals show higher
+volatility figures over \textbf{backwardation} phases. The symmetry
+between the dynamics of CHP and \textbf{CHP}'s explanatory power on
+individual commodity returns breaks in the crisis period
+(Table~\ref{tbl-time-reg-US-CHP}) with both now seemingly converging;
+the US cross-sectional average \(R^{2}\) at the individual level
+bouncing back up (22.5\% vs 20.8\%) while that at the aggregate level
+rises further (14.7\% vs 7.1\%).
+
+// TODO Add correlation results discussion here.
+
 The performance of the market factor dominates the US commodity complex
 over the period with a 50\% increase in mean average \(R^{2}\) to over
-30\% (table ) while that of the CHP factor decreases and, although
-increasing, remains modest for the open interest growth and term
-structure factors. The average pairwise correlation amongst the market
-factor picks increases beyond 50\% while there is a leveling in that
-amongst the picks of the long-short factors as shown in table .
-Notwithstanding, the market factor built from any sets of picks shows a
-significant rise across the board in performance on the US complex
-(table ).\\
-Taken together, these results indicate the presence of a systematic
-factor across the entire cross-section of the US commodities. Table
-provides further evidence of systematic linkages, in this case between
-US and non-US traded commodities with a similar, albeit more pronounced
-pattern, where the market factor constructed with any sets of picks (US
-traded commodities) shows a dramatic increase in performance on the UK
-metals with for example, when constructed from its own sets of picks,
-the average \(R^{2}\) increasing to 31.7\% from 10.2\% in the previous
-period.
-
-\medskip
-
-The returns pullback continues into the post-crisis period (table ) with
-twenty-two US and four UK traded assets showing lower mean returns
-relative to the crisis while the same number of US commodities and all
-UK metals show lower figures relative to the financialisation period;
-mean returns for equally weighted portfolios of US and UK assets drop
-down to -0.2\% and 2.7\% respectively. Interestingly volatility also
-recedes substantially with twenty US assets and all UK metals showing
-lower volatility figures relative to both the crisis and
-financialisation periods suggesting that investment outflows from the
-commodity futures complex have had a lower impact on volatility than the
-corresponding inflows witnessed over the financialisation period. The
-figures for the equally weighted portfolios of US and UK assets drop to
-9.9\% and 16.2\% respectively, very close to pre-financialisation
-levels.\\
+30\% (Table~\ref{tbl-regressions-factors}) while that of the CHP factor
+decreases and, although increasing, remains modest for the open interest
+growth and term structure factors. Taken together, these results
+indicate the presence of a systematic factor across the entire
+cross-section of the US commodities.
+
+\medskip
+
+The returns pull-back continues into the post-crisis period
+(Table~\ref{tbl-stats-no-regimes}) with twenty-two US and four UK traded
+assets showing lower mean returns relative to the crisis while the same
+number of US commodities and all UK metals show lower figures relative
+to the financialisation period; mean returns for equally weighted
+portfolios of US and UK assets drop down to -0.2\% and 2.7\%
+respectively. Interestingly volatility also recedes substantially with
+twenty US assets and all UK metals showing lower volatility figures
+relative to both the crisis and financialisation periods suggesting that
+investment outflows from the commodity futures complex have had a lower
+impact on volatility than the corresponding inflows witnessed over the
+financialisation period. The figures for the equally weighted portfolios
+of US and UK assets drop to 9.9\% and 16.2\% respectively, very close to
+pre-financialisation levels.\\
 The pattern of reversion toward the pre-financialisation Keynesian
 paradigm initiated during the crisis continues stronger into the
-post-crisis period (table ) with mean returns higher during phases of
-\textbf{backwardation} relative to \textbf{contango} (table ), more so
-than over the crisis period with seventeen US commodities showing higher
-mean returns over \textbf{backwardation} phases. The difference is
-significant at the 5\% level for Lumber (XCME) and at the 10\% level for
-Palladium (XNYM) while no difference is significant for the assets
-showing higher figures over phases of \textbf{contango}. The pattern is
-more pronounced for the UK traded subset with all six assets showing
-higher mean returns in \textbf{backwardation} with the difference
-significant at the 1\% level for Nickel-primary (XLME), 5\% level for
-Aluminium (XLME) and 10\% level for Zinc (XLME). It also extends to
-equally weighted portfolios of US and UK traded assets that both show
-higher mean returns during \textbf{backwardation} with the difference
-significant at the 5\% level for the UK portfolio and the figure close
-to the 10\% level significance threshold for the portfolio of US assets.
-Volatilities are overall higher in \textbf{contango} although less so
-than over the previous period with seventeen US commodities showing
-higher figures over \textbf{contango} against twenty-three in the crisis
-period. The pattern extends to three of the six UK traded metals with
-the difference significant at the 1\% level for Copper (XLME) and Tin
-(XLME) and at the 5\% level for Zinc (XLME) while differences are not
-significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME)
-that exhibit higher volatility over \textbf{backwardation} phases.
-Equally weighted portfolios of US and UK traded assets on the other hand
-both show higher volatility in \textbf{contango} with the difference
-significant at the 1\% level for both. Over the financialisation period
-in contrast volatilities were predominantly higher in
-\textbf{backwardation} for US traded assets with fourteen commodities
-showing higher volatility figures in these phases; the post-crisis
-pattern of results for volatilities thus likewise shows signs of
-reversion to pre-financialisation standards. After showing signs of
-convergence in the crisis period the dynamics of the explanatory power
-of CHP and \textbf{CHP} part ways (table ), seemingly reverting to the
-Keynesian paradigm observed pre-financialisation, further suggesting a
-return to legacy commodity specific dynamics. The recovery initiated in
-the crisis period for that of CHP is confirmed with a stronger increase
-in the post-crisis period, 27.2\% vs.~22.5\%, strongest for the metals
-sector, 37.3\% vs.~23.7\%, while the energy sector shows the opposite
-pattern: 11\% vs.~16\%. In contrast, after increasing stronger in the
-crisis, that for \textbf{CHP} falls overall in the post-crisis period,
-7.5\% vs 14.7\%, with the decrease strongest for the energy sector in a
-relative sense: 2.5\% vs.~14.8\%.\\
-Average pairwise correlations amongst factor picks (table ) fall
-substantially in the post-crisis period with for example the figure for
-the market factor picks dropping from 50.1\% to 26.1\%, almost down to
-pre-financialisation levels; results are similar for the long-short
-factor picks with figures below financialisation levels in all cases and
-very close to pre-financialisation standards for the term structure and
-liquidity factor picks. The performance of the market factor on the US
-complex declines below financialisation levels (table ) with the pattern
-similar albeit stronger when the factor is built from the sets of factor
-picks with a decline in performance on the US complex (table ) to almost
-pre-financialisation levels when constructed with its own set of picks
-as well as with those of the long-short factors, in particular the term
-structure and liquidity factors. Table provides further evidence of
-decoupling, in this case between US and non-US traded commodities with a
-sharp decline in performance of the market factor constructed with any
-set of picks on the UK complex below financialisation, down to almost
-pre-financialisation levels when constructed with the sets of long-short
-factors picks.
+post-crisis period (Table~\ref{tbl-stats-regimes}) with mean returns
+higher during phases of \textbf{backwardation} relative to
+\textbf{contango}, more so than over the crisis period with seventeen US
+commodities showing higher mean returns over \textbf{backwardation}
+phases. The difference is significant at the 5\% level for Lumber (XCME)
+and at the 10\% level for Palladium (XNYM) while no difference is
+significant for the assets showing higher figures over phases of
+\textbf{contango}. The pattern is more pronounced for the UK traded
+subset with all six assets showing higher mean returns in
+\textbf{backwardation} with the difference significant at the 1\% level
+for Nickel-primary (XLME), 5\% level for Aluminium (XLME) and 10\% level
+for Zinc (XLME). It also extends to equally weighted portfolios of US
+and UK traded assets that both show higher mean returns during
+\textbf{backwardation} with the difference significant at the 5\% level
+for the UK portfolio and the figure close to the 10\% level significance
+threshold for the portfolio of US assets. Volatilities are overall
+higher in \textbf{contango} although less so than over the previous
+period with seventeen US commodities showing higher figures over
+\textbf{contango} against twenty-three in the crisis period. The pattern
+extends to three of the six UK traded metals with the difference
+significant at the 1\% level for Copper (XLME) and Tin (XLME) and at the
+5\% level for Zinc (XLME) while differences are not significant for
+Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit
+higher volatility over \textbf{backwardation} phases. Equally weighted
+portfolios of US and UK traded assets on the other hand both show higher
+volatility in \textbf{contango} with the difference significant at the
+1\% level for both. Over the financialisation period in contrast
+volatilities were predominantly higher in \textbf{backwardation} for US
+traded assets with fourteen commodities showing higher volatility
+figures in these phases; the post-crisis pattern of results for
+volatilities thus likewise shows signs of reversion to
+pre-financialisation standards. After showing signs of convergence in
+the crisis period the dynamics of the explanatory power of CHP and
+\textbf{CHP} part ways (Table~\ref{tbl-time-reg-US-CHP}), seemingly
+reverting to the Keynesian paradigm observed pre-financialisation,
+further suggesting a return to legacy commodity specific dynamics. The
+recovery initiated in the crisis period for that of CHP is confirmed
+with a stronger increase in the post-crisis period, 27.2\% vs.~22.5\%,
+strongest for the metals sector, 37.3\% vs.~23.7\%, while the energy
+sector shows the opposite pattern: 11\% vs.~16\%. In contrast, after
+increasing stronger in the crisis, that for \textbf{CHP} falls overall
+in the post-crisis period, 7.5\% vs 14.7\%, with the decrease strongest
+for the energy sector in a relative sense: 2.5\% vs.~14.8\%.
 
@@
 interest (past: 1997-2003; financialisation: 2004-2008; crisis:
-2008-2013; post-crisis: 2013-2018); for earch period the results are
+2008-2013; post-crisis: 2013-2018); for each period the results are
 calculated independently over the entire period as well as over phases
@@
 \textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.54\%}} & \textcolor[HTML]{4285f4}{\textbf{5.55\%}} & \textcolor[HTML]{4285f4}{\textbf{4.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.69\%}} & \textcolor[HTML]{4285f4}{\textbf{5.47\%}} & \textcolor[HTML]{4285f4}{\textbf{3.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.12\%}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.74\%}}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.69\%}} & \textcolor[HTML]{4285f4}{\textbf{5.47\%}} & \textcolor[HTML]{4285f4}{\textbf{3.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.12\%}}\\
+\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.74\%}}}\\
 \textbf{all} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{2.95\%}} & \textcolor[HTML]{4285f4}{\textbf{5.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.39\%}}\\
@@
 \textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{6.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.14\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.79\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{5\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.79\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{5\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
 \textbf{US} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{2.87\%}} & \textcolor[HTML]{4285f4}{\textbf{5.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}}\\
@@
 \addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.85\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.85\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}}\\
 \textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.73\%}} & \textcolor[HTML]{4285f4}{\textbf{2.16\%}}\\
@@
 \textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.06\%}} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.04\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{7.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.5\%}} & \textcolor[HTML]{4285f4}{\textbf{3.8\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.24\%}}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.04\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{7.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.5\%}} & \textcolor[HTML]{4285f4}{\textbf{3.8\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.24\%}}}\\
 \addlinespace
@@
 \textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.35\%}} & \textcolor[HTML]{4285f4}{\textbf{1.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.71\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
 \textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}}\\
@@
 \textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.51\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}} & \textcolor[HTML]{4285f4}{\textbf{0.9\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.51\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}} & \textcolor[HTML]{4285f4}{\textbf{0.9\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}}\\
 \textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.41\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}} & \textcolor[HTML]{4285f4}{\textbf{2.42\%}}\\
@@
 \textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{6.05\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{7.91\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.67\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{38.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.93\%}} & \textcolor[HTML]{4285f4}{\textbf{17.59\%}} & \textcolor[HTML]{4285f4}{\textbf{22.07\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{41.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.13\%}}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.67\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{38.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.93\%}} & \textcolor[HTML]{4285f4}{\textbf{17.59\%}} & \textcolor[HTML]{4285f4}{\textbf{22.07\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{41.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.13\%}}}\\
 \textbf{US} & \textbf{energy} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.99\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{1.86\%}}\\
@@
 \addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.03\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{23.23\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{14.53\%}} & \textcolor[HTML]{4285f4}{\textbf{16.64\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.41\%}}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.03\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{23.23\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{14.53\%}} & \textcolor[HTML]{4285f4}{\textbf{16.64\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.41\%}}}\\
 \textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{4.24\%}} & \textcolor[HTML]{4285f4}{\textbf{7.16\%}} & \textcolor[HTML]{4285f4}{\textbf{5.22\%}}\\
@@
 \textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}} & \textcolor[HTML]{4285f4}{\textbf{0.96\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{45.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.56\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{44.02\%}} & \textcolor[HTML]{4285f4}{\textbf{27.52\%}} & \textcolor[HTML]{4285f4}{\textbf{18.61\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{47.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{43.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.7\%}}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{45.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.56\%}}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{44.02\%}} & \textcolor[HTML]{4285f4}{\textbf{27.52\%}} & \textcolor[HTML]{4285f4}{\textbf{18.61\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{47.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{43.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.7\%}}}\\
 \addlinespace
@@
 \textbf{US} & \textbf{metals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.72\%}} & \textcolor[HTML]{4285f4}{\textbf{23.49\%}} & \textcolor[HTML]{4285f4}{\textbf{21.5\%}} & \textcolor[HTML]{4285f4}{\textbf{13.38\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.27\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{2.83\%}} & \textcolor[HTML]{4285f4}{\textbf{0.32\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.27\%}}}\\
+\addlinespace
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{2.83\%}} & \textcolor[HTML]{4285f4}{\textbf{0.32\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}}\\
 \textbf{US} & \textbf{metals} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.48\%}} & \textcolor[HTML]{4285f4}{\textbf{7.31\%}} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
@@
 \textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.46\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{1.84\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.46\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{1.84\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}}\\
 \textbf{US} & \textbf{metals} & \textbf{base} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.06\%}} & \textcolor[HTML]{4285f4}{\textbf{9.72\%}} & \textcolor[HTML]{4285f4}{\textbf{9.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
@@
 \textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.76\%}} & \textcolor[HTML]{4285f4}{\textbf{26.82\%}} & \textcolor[HTML]{4285f4}{\textbf{16.5\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.56\%}} & \textcolor[HTML]{4285f4}{\textbf{0.68\%}} & \textcolor[HTML]{4285f4}{\textbf{3.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.21\%}}}\\
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.56\%}} & \textcolor[HTML]{4285f4}{\textbf{0.68\%}} & \textcolor[HTML]{4285f4}{\textbf{3.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.21\%}}}\\
 \textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}} & \textcolor[HTML]{4285f4}{\textbf{6.71\%}} & \textcolor[HTML]{4285f4}{\textbf{16.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
@@
 \addlinespace
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.42\%}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{open interest nearby} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest nearby}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.42\%}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}}\\
+\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
 \textbf{GB} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.28\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\

### 2024-09-25 docs/paper.qmd
financilisation results + correlation results for crisis

@@
 
-Financialisation was a global phenomenon that, through the channel of index investment, simultaneously influenced the entire spectrum of liquid commodities.
-This sweeping impact spurred the transformation of commodity markets from a collection of idiosyncratic markets into a unified asset class with interconnectedness emerging as a crucial aspect that warrants thorough examination.
-We set out to address this issue by first examining the average of weekly returns pairwise correlations between commodities across the entire cross-section of the commodity assets considered in the study as well as by country, sector and sub-sector.
+Financialisation was a global phenomenon, through the channel of index investment it simultaneously influenced the entire spectrum of liquid commodities; this sweeping impact spurred the transformation of commodity markets from a collection of idiosyncratic markets into a unified asset class with interconnectedness emerging as a crucial aspect that warrants thorough examination.
+We strive to address this issue by first examining the average of weekly returns pairwise correlations between commodities across the entire cross-section of the commodity assets considered in the study as well as by country, sector and sub-sector.
 @tbl-correlations-periods shows the results for the four periods of interest with the results reported for the entire period as well as for periods of **backwardation** and **contango**.
 For the entire sample the average pairwise correlation jumps from 0.07 in the first period to 0.16 over financialisation.
-These findings indicate higher interdependence within the full cross-section of commodities starting with the financialisation period, consistent with the empirical findings in @fryMcKibbin_evolution_2023 and @mayer_financialization_2017 as well as with the theoretical model of @basak_model_2016.
+This finding indicate higher interdependence within the full cross-section of commodities starting with the financialisation period, consistent with the empirical findings in @fryMcKibbin_evolution_2023 and @mayer_financialization_2017 as well as with the theoretical model of @basak_model_2016.
 The sector analysis sheds light on the driving force behind these changes.
 The US metals see the sharpest increase in pairwise correlations going from 0.22 over the past period to 0.56 over financialisation while the three other sectors see a much smaller percentage increase during financialisation relative to the past period.
-These findings thus suggest that the US metals sector was the driving force behind increased average pairwise correlations during financialisation, a new observation to the best of our knowledge.
+These results thus suggest that the US metals sector was the driving force behind increased average pairwise correlations during financialisation, a new observation to the best of our knowledge.
 The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods which indicates that increased commodity interdependence over financialisation was not a phase driven phenomenon in the same way that individual commodity returns are, as demonstrated in @tbl-stats-regimes.
@@
 Thus, an increase in a commodity's correlation with other commodities should lead to an increase in its beta relative to the market factor portfolio.
-We therefore regress the weekly individual commodity front futures returns against those for our market factor portfolio and average the resulting betas across the entire set of commodity assets considered as well as by country, sector and sub-sector for each of the four periods of interest with the results shown in @tbl-regressions-index.
+We accordingly regress the weekly individual commodity front futures returns against those for our market factor portfolio and average the resulting betas across the entire set of commodity assets considered as well as by country, sector and sub-sector for each of the four periods of interest with the results shown in @tbl-regressions-index.
 The average beta for the US metals sector jumps sharply to 1.12 over financialisation from 0.63 over the previous period; the increase is even more dramatic for the base metals sub-sector (GB traded assets) in a relative sense.
 The group had a much lower beta of 0.27 over the past period, suggesting a low level of correlation with US commodities; this figure increases to 0.85 over the financialisation period, even beyond that for the US agricultural sector of 0.80.
-In contrast, the corresponding figures for the energy sector show a substantial decrease, down to 1.61 during financialisation from 2.33 over the past period.
+In contrast, the corresponding figure for the energy sector show a substantial decrease, down to 1.61 during financialisation from 2.33 over the past period.
 The corresponding pricing performance displays a similar pattern as shown in @tbl-regressions-factors where for each period the corresponding $R^{2}$ values are independently averaged over the entire period as well as over periods of **contango** and **backwardation**.
 The average $R^{2}$ for the market factor across the entire cross-section of commodity assets considered in the study, including the GB traded base metals, increases to around 20% during financialisation compared to around 10% over the previous period with the rise driven by the metals sector at large.
-The sector average for the US traded assets jumps to 31% during financialisation from 7.5% over the past period while for the GB traded assets the corresponding figure increases from less than 2%, or virtually no explanatory power for the (US based) market factor to almost 12% over the financialisation period.
+The sector average for the US traded assets jumps to 31% during financialisation from 7.5% over the past period while for the GB traded assets the corresponding figure increases from less than 2%, or virtually no explanatory power for the (US based) market factor, to almost 12% over the financialisation period.
 The results for our other risk factor mimicking portfolios show a similar pattern and provide a deeper insights into co-movement dynamics in this context.
@@
 The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average $R^{2}$, albeit still small at 5.4%, almost tripling from the past to the financialisation period in contrast to the other factors that show weaker dynamics with a slight decrease and a much smaller increase for the open interest and term structure factors respectively.
-Here again the dramatic increase in pricing performance for the CHP factor is driven by the metals sector, particularly the precious sub-sector with the average $R^{2}$ for the group jumping to almost 26% during financialisation from 1.2% over the past period.
+Here again the increase in pricing performance for the CHP factor is driven by the metals sector, particularly the precious sub-sector with the average $R^{2}$ for the group jumping to almost 26% during financialisation from 1.2% over the past period.
 The corresponding figures of 22% and 1.1% for the entire US metals sector stand in sharp contrast with the agricultural sector, which exhibits no notable change, and the energy sector, where pricing performance drops substantially from 9.2% down to 1.6%.
@@
 The average $R^{2}$ for the group jumps to 55% during financialisation from less than 12% over the past period while the short leg sees a far smaller increase, up to 8.9% from 3.3% over the past period.
-Interestingly, although the factor itself only sees a very modest increase, its short leg (low roll-yield assets: Working's backwardation) shows a sizeable rise in pricing performance, yet again driven the metals sector, with the average $R^{2}$ for the group's US traded assets jumping to 28.2% during financialisation from 6.2% over the past period.
+Interestingly, although the term structure factor itself only sees a very modest increase, its short leg (low roll-yield assets: Working's backwardation) shows a sizeable rise in pricing performance, yet again driven the metals sector, with the average $R^{2}$ for the group's US traded assets jumping to 28.2% during financialisation from 6.2% over the past period.
 The pattern of results for both factors extends to the GB trade assets and suggest a convergence of Keneysian and Working's term structure perspective over the financialisation period.
 Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working’s term structure paradigms.
-There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of Kang et al.
-(2020) who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
+There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of @kang_tale_2020 who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
 
@@
 The symmetry between the dynamics of CHP and **CHP**'s explanatory power on individual commodity returns breaks in the crisis period (@tbl-time-reg-US-CHP) with both now seemingly converging; the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%).
-
-// TODO Add correlation results discussion here.
+The average pairwise correlation for the entire cross-section of commodities considered in the study (@tbl-correlations-periods) increases further into the crisis to 0.28 indicating an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation.
+The result is consistent with the greater interdependence between equity and commodity markets over this period documented in @silvennoinen_financialisation_2013.
+The figure for the US traded section of the metals sector only progresses modestly to 0.59 after peaking at 0.63 in 2006 (@tbl-correlations-years).
+In contrast, the GB traded assets see a sharp increase to over 0.65 in the crisis starting in 2007 up to a peak of 0.69 in 2010.
+The agricultural sector on the other hand shows a substantial rise in the crisis period with the sharpest increase in 2008 when the average pairwise correlation for the sector jumps to 0.30.
+Meanwhile, the energy sector also shows a notable progression starting in 2007 and peaking at 0.63 in 2008 before levelling back down over the rest of the period.
+The onset of the financial crisis seems therefore to have had an across the board impact on the interdependence of commodities in contrast with financilisation, much more closely related to the metals sector.
 

### 2024-09-25 docs/paper.qmd
Complete results for the crisis period

@@
 The symmetry between the dynamics of CHP and **CHP**'s explanatory power on individual commodity returns breaks in the crisis period (@tbl-time-reg-US-CHP) with both now seemingly converging; the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%).
+
+\medskip
+
 The average pairwise correlation for the entire cross-section of commodities considered in the study (@tbl-correlations-periods) increases further into the crisis to 0.28 indicating an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation.
@@
 Meanwhile, the energy sector also shows a notable progression starting in 2007 and peaking at 0.63 in 2008 before levelling back down over the rest of the period.
-The onset of the financial crisis seems therefore to have had an across the board impact on the interdependence of commodities in contrast with financilisation, much more closely related to the metals sector.
-
-The performance of the market factor dominates the US commodity complex over the period with a 50% increase in mean average $R^{2}$ to over 30% (@tbl-regressions-factors) while that of the CHP factor decreases and, although increasing, remains modest for the open interest growth and term structure factors.
-Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
+The onset of the financial crisis seems therefore to have had an across the board impact on the interdependence of commodities in contrast with financialisation, much more closely related to the metals sector.
 
 \medskip
+
+The entire cross-section sees an increase in average regression coefficient relative to the market factor over the crisis period with the strongest progression for the GB traded metals followed by the agricultural sector (@tbl-regressions-index).
+The pricing performance of the factor
+dominates the US commodity complex over the period, showing a 50% increase in mean average $R^{2}$ to over 31%, while that for both the CHP and open interest factor decreases and, although increasing, remains modest for the term structure factors; the increase in strongest for the GB traded metal assets with an average $R^{2}$ of almost 34% for the period.
+Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
+For both the CHP and term structure factors, both legs show an increase in average $R^{2}$ and while substantially diverging over the preceding financialisation period the pricing performance for both legs seem to converge back to the pattern observed pre-financialisation.
+
+\bigskip
+\bigskip
 

### 2024-09-25 docs/paper.qmd
Complete first draft of results for the post-crisis period

@@
 Financialisation seems however to have impacted the commodity complex beyond these mechanical effects of increased long participation ensuing from the entry on index type investments as our results suggest next.
-
-\medskip
-
 The cross-sectional nature of financialisation naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure.
@@
 The pricing performance of the factor
-dominates the US commodity complex over the period, showing a 50% increase in mean average $R^{2}$ to over 31%, while that for both the CHP and open interest factor decreases and, although increasing, remains modest for the term structure factors; the increase in strongest for the GB traded metal assets with an average $R^{2}$ of almost 34% for the period.
+dominates the US commodity complex over the period (@tbl-regressions-factors), showing a 50% increase in mean average $R^{2}$ to over 31%, while that for both the CHP and open interest factor decreases and, although increasing, remains modest for the term structure factors; the increase is strongest for the GB traded metal assets with an average $R^{2}$ of almost 34% for the period.
 Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
-For both the CHP and term structure factors, both legs show an increase in average $R^{2}$ and while substantially diverging over the preceding financialisation period the pricing performance for both legs seem to converge back to the pattern observed pre-financialisation.
+For both the CHP and term structure factors, both legs show an increase in average $R^{2}$ and while substantially diverging over the preceding financialisation period the pricing performance for both legs seems to converge back to a pattern closer to that observed pre-financialisation.
 
@@
 
-Taken together the patterns of results over the crisis and post-crisis periods echo those in @basu_definancialisation in suggesting that the exogenous shock delivered by the financial crisis combined with the accommodative monetary policy that ensued seem to have initiated a reversion toward pre-financialisation fundamentals in the commodity futures complex.
+The average pairwise correlations fall across the board in the post-crisis period, below the levels observed during financialisation, with the figure for the entire cross-section (@tbl-correlations-periods) dropping down to 0.12 from 0.28 over the crisis.
+This substantial decline, that does not appear to have been widely noted, appears to begin in the latter part of the crisis period, around 2012 (@tbl-correlations-years), before levelling down over the whole post-crisis period.
+
+\medskip
+
+In a similar vein, the average market factor beta for the entire cross-section drops down to 0.94 (@tbl-regressions-index), below the level observed during financialization.
+The decline seems driven by the metals sector, particularly the GB traded segment, with the figures for the US and GB traded assets at 0.91 and 0.72, down from 1.12 and 1.18, respectively.
+Meanwhile, the pricing performance of the market factor also retreats to below financialisation levels with the average $R^{2}$ for the entire cross-section dropping down to 14.7% (@tbl-regressions-factors).
+All sectors seem affected with agriculturals, energy and metals all seeing their average $R^{2}$ decline below the levels observed during the financialisation period albeit remaining above 10% for the GB traded metals against less than 2% pre-financialisation.
+Similarly, the performance for both the CHP and term structure factors falls back to levels below those attained over financialisation while the gap between their long and short legs remains narrower than observed during that period.
+Taken together, these results, along with those from the crisis period, suggest that the exogenous shock of the financial crisis, combined with the subsequent accommodative monetary policy, may have triggered a reversion toward pre-financialization fundamentals in the commodity futures complex; an issue that, to our knowledge, has not been widely noted in the existing literature.
+Meanwhile the regime based analysis is also revealing starting with the average correlations are higher during phases of **contango** and the pattern stronger for the metals assets both US and GB traded.
+Similarly, for these the pricing performance of the market factor is considerably better during phase of **contango** in contrast with the previous periods that showed no substantial difference between phase of **contango** and **backwardation**.
+The figures for the US and GB traded segments of the sector are 23% (**contango**) vs 11.5% (**backwardation**) against 36.2% vs 43% during financialisation and 14.4% (**contango**) vs 6.6% (**backwardation**) against 33.5% vs 34.4% during financialisation respectively which indicate some recent changes in the correlation structure within the sector.
+Taken together with the decline in interdependence in the commodity sector at large documented above, this observation could form a valuable basis for future research.
 
@@
 Mean values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
-The results are discussed in section \\@sec-results."
+The results are discussed in \\@sec-results."
 
@@
 Mean values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
-Aggregate CHP construction and corresponding regime definitions are discussed in section \\@sec-methods while the results are discussed in section \\@sec-results."
+Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
 
@@
 #| label: tbl-time-reg-US-CHP
-#| tbl-cap: "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in section \\@sec-methods.
+#| tbl-cap: "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in \\@sec-methods.
 Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The results are discussed in section \\@sec-results."
+The results are discussed in \\@sec-results."
 
@@
 For each period, the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
-Aggregate CHP construction and corresponding regime definitions are discussed in section \\@sec-methods while the results are discussed in section \\@sec-results."
+Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
 
@@
 #| tbl-cap: "This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors by year for the whole period of interest (1997-2018).
-The results are discussed in section \\@sec-results."
+The results are discussed in \\@sec-results."
 
@@
 The results are calculated independently across countries as well as commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The market factor construction is discussed in section \\@sec-methods while the results are discussed in section \\@sec-results."
+The market factor construction is discussed in \\@sec-methods while the results are discussed in \\@sec-results."
 
@@
 The results are calculated independently across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018); for each period the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
-Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \\@sec-methods while the results are discussed in section \\@sec-results."
+Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
 

### 2024-09-26 docs/paper.qmd

@@
 Similarly, the performance for both the CHP and term structure factors falls back to levels below those attained over financialisation while the gap between their long and short legs remains narrower than observed during that period.
-Taken together, these results, along with those from the crisis period, suggest that the exogenous shock of the financial crisis, combined with the subsequent accommodative monetary policy, may have triggered a reversion toward pre-financialization fundamentals in the commodity futures complex; an issue that, to our knowledge, has not been widely noted in the existing literature.
-Meanwhile the regime based analysis is also revealing starting with the average correlations are higher during phases of **contango** and the pattern stronger for the metals assets both US and GB traded.
-Similarly, for these the pricing performance of the market factor is considerably better during phase of **contango** in contrast with the previous periods that showed no substantial difference between phase of **contango** and **backwardation**.
-The figures for the US and GB traded segments of the sector are 23% (**contango**) vs 11.5% (**backwardation**) against 36.2% vs 43% during financialisation and 14.4% (**contango**) vs 6.6% (**backwardation**) against 33.5% vs 34.4% during financialisation respectively which indicate some recent changes in the correlation structure within the sector.
-Taken together with the decline in interdependence in the commodity sector at large documented above, this observation could form a valuable basis for future research.
+These results, along with those from the crisis period, suggest that the exogenous shock of the financial crisis, combined with the subsequent accommodative monetary policy, may have triggered a reversion toward pre-financialization fundamentals in the commodity futures complex; an issue that, to our knowledge, has not been widely discussed in the existing literature.
+The phases analysis further documents the emerging role/dominance of the **contango** regime post-crisis with average correlations higher during those phases and the pattern stronger for the metal assets both US and GB traded.
+Similarly, for the latter the pricing performance of the market factor is considerably better during phase of **contango** in contrast with the previous periods that showed no substantial difference between phase of **contango** and **backwardation**.
+The figures for the US and GB traded segments of the sector are 23% (**contango**) vs 11.5% (**backwardation**) against 36.2% vs 43% during financialisation and 14.4% (**contango**) vs 6.6% (**backwardation**) against 33.5% vs 34.4% during financialisation respectively.
+Taken together, these results indicate some recent changes in the correlation structure within the sector and along with the decline in interdependence in the commodity sector at large documented above, this observation could form a valuable basis for future research.
+These findings further providence additional evidence that the interdependence effects of financialization seems to have been strongest for the entire cross-section of the metals sector with a lesser impact for the other sectors.
 

### 2024-09-26 docs/paper.qmd

@@
 We also consider the UK metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).
+This sample cross-section of assets is further divided into groups for the purpose of the analysis by country (US, GB), sector (agriculturals, energy, metals) and by sub-sector (agriculturals: grains, livestock, softs; energy: gas, petroleum; metals: base, precious).
 
@@
 Data for DCOT and SCOT date back to 2006 and 2007 respectively.
-We study the 1997/2018 period where we observe futures only position data from the COT report, the only CFTC report with data available for the whole period of interest; as well as futures term structure price and open interest data from Bloomberg.
+We examine the period from 1997 to 2018, during which we utilize futures-only position data from the COT report---the only CFTC report providing data for the entire duration of interest---as well as futures term structure price and open interest data sourced from Bloomberg.
+The sample period is further divided into four distinct intervals.
+The pre-financialisation era spans the 1997-2003 period and is naturally followed by the financialisation phase running from 2004 to 2008 which in turn leads into the financial crisis and its aftermath, covering 2008 to 2013.
+The final interval starts in 2013 with the onset of tapering and the conclusion of the US Quantitative Easing (QE) program.
 
 ## Methods {#sec-methods}
+
+For each commodity asset we compute the weekly front futures return and commercial hedging pressure (CHP) time series with the CHP calculated as the ratio of the number of long commercial positions to the total number of commercial positions for the considered asset-week combination.
+For each asset-period combination we compute the average return and corresponding volatility over the entire period as well as over phases of cross-sectional low and high CHP^[Aggregate CHP or **CHP**: see below for a formal definition and description of the phase construction process.].
+These statistics are also computed for equally weighted portfolios of the US and GB traded commodity assets independently.
+
+For each period, the return series for the individual US-traded assets are regressed on both the relative change on their respective CHP series and that on the cross-sectional CHP independently.
+The resulting $R^{2}$ values are then averaged by sector and subsector.
+Additionally, pairwise correlations are computed for each combination of assets across the periods of interest and for each individual year within the full sample period.
+These correlation coefficients are subsequently averaged across the entire cross-section of assets, as well as by country, sector, and subsector.
+For each period, the coefficients are also calculated and averaged across phases of low and high cross-sectional CHP.
+
+This approach sheds light on the evolving interconnectedness among commodity assets as the complex transitions from traditional market dynamics---where commodity producers and speculators had distinct roles---to a more intricate landscape shaped by the influx of financial investors.
+
+\bigskip
+\bigskip
 
@@
 Careful, theory-based, attribute selection further enables a refined analysis of market fundamentals [@schwartz_short_2000; @miffre_momentum_2007; @gorton_fundamentals_2012; @cortazar_commodity_2013; @yang_investment_2013; @daskalaki_factors_2014; @szymanowska_anatomy_2014; @fernandez_skewness_2018; @bakshi_understanding_2019; @boons_basis_2019; @sakkas_factor_2020].
-We therefore develop a futures-based asset pricing framework that includes factors constructed using both theoretical and liquidity considerations and use this framework to carry out our analysis over four periods of interest.
-The first, the pre-financialisation period, starts in 1997 and is naturally followed by financialisation, spanning the 2004/2008 period, and the financial crisis and its aftermath, spanning the 2008/2013 period.
-The last period spans the 2014/2018 period starting with the beginning of the tapering/end of the US Quantitative Easing program (QE).
-Using the weekly price, open interest and market position data described above we construct market portfolios of individual commodity nearby futures as well as mimicking portfolios for market, commercial hedging pressure, term structure and liquidity risk factors in returns.
-While our market portfolios are long only, equally weighted portfolios of particular commodity sets, our other mimicking portfolios for risk factors are constructed as combinations of two sub-portfolios (legs), one held long, one held short, which respective constituents are pooled on a weekly basis according to risk factor specific criteria.
-For each leg, the position weight for a particular asset for a particular period is contingent on the value of the corresponding sorting variable and its rank relative to the other assets in the pool.
-The sorting variable values for the asset pool are first rescaled so that the highest (lowest) value becomes 1 (0).
-Weights are then determined pairwise, starting from the extremes with the highest and lowest figures.
-A coefficient $\alpha$ is determined by dividing their difference (1 in this case) by the mean of the rescaled values.
-The high figure is attributed a score of $\frac{1}{n} \times \alpha$ where $n$ is the number of assets in the pool while the score for the low figure is $\frac{1/n}{\alpha}$.
-The operation is repeated for the pair of assets showing the second highest and second lowest values for the sorting variable and so on until all the assets in the pool are attributed a score.
-The individual asset weights are then determined by dividing each score by the sum of the scores.
-The period return for a particular mimicking portfolio is calculated as the difference between the weighted average return for constituents of the long portfolio and that for the constituents of the short portfolio.
+We therefore develop a futures-based asset pricing framework that includes factors constructed using both theoretical and liquidity considerations.
+Using the weekly returns, open interest and market position data described above we construct market portfolios of individual commodity nearby futures as well as mimicking portfolios for market, commercial hedging pressure, term structure and liquidity risk factors in returns.
+While our market portfolios are long only combinations of particular commodity sets, our other mimicking portfolios for risk factors are constructed as combinations of two sub-portfolios (legs), one held long, one held short, which respective constituents are pooled on a weekly basis according to risk factor specific criteria.
+All portfolios are equally weighted and returns for the two-legged factors are calculated as the difference between the average return for constituents of the long leg and that for the constituents of the short.
 i.e, return on the mimicking portfolio for risk factor $i$ ($f_{i}$) for period $t$:
 
-$$r_{t}^{f_{i}}=\sum_{j=1}^{x}w^{long}_{j,t} \times r_{j,t}-\sum_{j=n-x}^{n}w^{short}_{j,t} \times r_{j,t}$$
+$$r_{t}^{f_{i}} = \frac{1}{x} \left ( \sum_{j=1}^{x}r_{j,t} - \sum_{j=n-x}^{n} r_{j,t} \right )$$
 $n\equiv$ number of commodities in the set considered for mimicking portfolio construction.  
-<!-- $x = \left \lceil n \cdot s \right \rceil$   -->
 $x = n \cdot s$.  
 $s\equiv$ selection threshold ($\frac{1}{3}$ here).  
-$w^{*}_{j,t}\equiv$ period $t$ weight for commodity $j$ on the long or short leg.  
 $r_{j,t}\equiv$ period $t$ front contract return for commodity $j$.  
@@
 
-We use a time series regression approach where we start with regressions of the US traded individual commodity weekly front contract returns on returns to the mimicking portfolio for a particular risk factor where the portfolio is constructed using the whole cross-section of US traded commodities.
-The corresponding $R^{2}$s are averaged and the process is repeated for each of our four risk factors (market, hedging pressure, term structure and liquidity) and periods (1997/2003, 2004/2008, 2008/2013 and 2014/2018).
-For the long-short factors the results are reported independently for models where the regressor is the factor itself or one of its legs (long vs.
-short).
-The same operation is repeated for the two ($p=2$) and three ($p=3$) factor model cases, where regressors include in turn all combinations of any two and three risk factors respectively, as well as for the four ($p=4$) factor model case where all the risk factor mimicking portfolios are included.
-Results are reported for the one-factor model case with the other results available upon request.
+We use a time series regression approach where individual commodity weekly front futures contract returns are regressed on returns to the mimicking portfolio for a particular risk factor with the corresponding $\beta$s and $R^{2}$s averaged.
+For the long-short factors the $\beta$s and $R^{2}$s are computed for models where the regressor is the factor itself as well as both its long and short legs independently (results available upon request).
 
-\medskip
-
-For each period we also implement the analysis described above over periods of low and high aggregate CHP (**CHP**), a notion that we believe is particularly relevant in the context of financialisation where issues of co-movement and aggregate market behaviour play a central role.
+For each time period considered in the study, being one of the four multi-year periods described above or any individual year over the entire sample time period, we carry out our analysis over the entire period as well as over phases of low and high aggregate CHP (**CHP**) over the period; a notion that we believe is particularly relevant in the context of financialisation where issues of co-movement and aggregate market behaviour play a central role.
 We define **CHP** as the cross-sectional average of individual CHPs for a particular pool of assets.
 i.e., period $t$ **CHP** for asset pool $x$:
-
 $$\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}$$
@@
 
-We further define aggregate backwardation (**backwardation**) and contango (**contango**) **CHP** regimes as, for a given period, **CHP** levels below and above the period's median respectively and, in contrast with [@hong_what_2012] who aggregate across sub-sectors, the asset pool we consider for **CHP** construction include the whole cross-section of US traded commodities.
-
-\medskip
-
-In the next part of the analysis, our mimicking portfolios for risk factors, constructed from the set of all US traded commodities are used as commodity picking devices on the latter commodity set.
-For each risk factor and period, individual US traded commodity front returns are regressed on returns for the corresponding mimicking portfolio.
-Individual commodities are sorted by $R^{2}$ accordingly from highest to lowest and the top third (highest $R^{2}$s) are selected as commodity picks for the risk factor for the period.
-i.e, set of picks $P_{t}^{f_{i}}$ for risk factor $i$ ($f_{i}$) over period $t$:
-
-$$P_{t}^{f_{i}}\equiv\left \{ P_{1}, P_{2}, ..., P_{x} \right \}$$
-$x = n \cdot s$.    
-$n\equiv$ number of commodities in the set considered for the picking exercise (twenty-four here).  
-$s\equiv$ selection threshold ($\frac{1}{3}$ here).  
-$P_{j}\equiv$ commodity pick $j$ for risk factor $f_{i}$ over period $t$  
-$j\equiv$ rank in the ordered set $Y_{t}^{f_{i}}$  
-$$Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}$$
-$n\equiv$ number of commodities in the set considered for picking (twenty-four here).   
-$\tilde{R_{j}^{2}}\equiv$ risk factor $f_{i}$ returns' explanatory power on commodity $j$ nearby futures returns over period $t$ as defined above.
-
-\medskip
-
-For each period we report the proportion of time each pick is held in the long and (/or) short leg of the corresponding risk factor mimicking portfolio as well as the average pairwise correlation amongst every set of picks.
-
-\medskip
-
-In the last part of the analysis, for each period our mimicking portfolios for risk factors in returns are constructed using each set of commodity picks independently as the asset pool for portfolio construction.
-A similar time series approach to that described above is then implemented using these newly formed mimicking portfolios.
-In this case, a first set of dependent variables includes the sets of commodity picks themselves, a second set includes the whole cross-section of US traded commodities while a third set includes the six UK traded metals considered in the study.
+We further define aggregate backwardation (**backwardation**) and contango (**contango**) **CHP** regimes as, for a given period, sub-periods with **CHP** levels below and above the period's median respectively and, in contrast with [@hong_what_2012] who aggregate across sub-sectors, our **CHP** construction draws on the full cross-section of US-traded assets considered in the study.
 

### 2024-09-26 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@64fa6fe96b1e1f8608bf2d0a2d12598e80634503 🚀

@@
 (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc
-(XLME).
+(XLME). This sample cross-section of assets is further divided into
+groups for the purpose of the analysis by country (US, GB), sector
+(agriculturals, energy, metals) and by sub-sector (agriculturals:
+grains, livestock, softs; energy: gas, petroleum; metals: base,
+precious).
 
@@
 DCOT and SCOT date back to 2006 and 2007 respectively.\\
-We study the 1997/2018 period where we observe futures only position
-data from the COT report, the only CFTC report with data available for
-the whole period of interest; as well as futures term structure price
-and open interest data from Bloomberg.
+We examine the period from 1997 to 2018, during which we utilize
+futures-only position data from the COT report---the only CFTC report
+providing data for the entire duration of interest---as well as futures
+term structure price and open interest data sourced from Bloomberg. The
+sample period is further divided into four distinct intervals. The
+pre-financialisation era spans the 1997-2003 period and is naturally
+followed by the financialisation phase running from 2004 to 2008 which
+in turn leads into the financial crisis and its aftermath, covering 2008
+to 2013. The final interval starts in 2013 with the onset of tapering
+and the conclusion of the US Quantitative Easing (QE) program.
 
 \subsection{Methods}\label{sec-methods}
+
+For each commodity asset we compute the weekly front futures return and
+commercial hedging pressure (CHP) time series with the CHP calculated as
+the ratio of the number of long commercial positions to the total number
+of commercial positions for the considered asset-week combination. For
+each asset-period combination we compute the average return and
+corresponding volatility over the entire period as well as over phases
+of cross-sectional low and high CHP\footnote{Aggregate CHP or
+  \textbf{CHP}: see below for a formal definition and description of the
+  phase construction process.}. These statistics are also computed for
+equally weighted portfolios of the US and GB traded commodity assets
+independently.
+
+For each period, the return series for the individual US-traded assets
+are regressed on both the relative change on their respective CHP series
+and that on the cross-sectional CHP independently. The resulting
+\(R^{2}\) values are then averaged by sector and subsector.
+Additionally, pairwise correlations are computed for each combination of
+assets across the periods of interest and for each individual year
+within the full sample period. These correlation coefficients are
+subsequently averaged across the entire cross-section of assets, as well
+as by country, sector, and subsector. For each period, the coefficients
+are also calculated and averaged across phases of low and high
+cross-sectional CHP.
+
+This approach sheds light on the evolving interconnectedness among
+commodity assets as the complex transitions from traditional market
+dynamics---where commodity producers and speculators had distinct
+roles---to a more intricate landscape shaped by the influx of financial
+investors.
+
+\bigskip
+\bigskip
 
@@
 includes factors constructed using both theoretical and liquidity
-considerations and use this framework to carry out our analysis over
-four periods of interest. The first, the pre-financialisation period,
-starts in 1997 and is naturally followed by financialisation, spanning
-the 2004/2008 period, and the financial crisis and its aftermath,
-spanning the 2008/2013 period. The last period spans the 2014/2018
-period starting with the beginning of the tapering/end of the US
-Quantitative Easing program (QE).\\
-Using the weekly price, open interest and market position data described
-above we construct market portfolios of individual commodity nearby
-futures as well as mimicking portfolios for market, commercial hedging
-pressure, term structure and liquidity risk factors in returns. While
-our market portfolios are long only, equally weighted portfolios of
-particular commodity sets, our other mimicking portfolios for risk
-factors are constructed as combinations of two sub-portfolios (legs),
-one held long, one held short, which respective constituents are pooled
-on a weekly basis according to risk factor specific criteria.\\
-For each leg, the position weight for a particular asset for a
-particular period is contingent on the value of the corresponding
-sorting variable and its rank relative to the other assets in the pool.
-The sorting variable values for the asset pool are first rescaled so
-that the highest (lowest) value becomes 1 (0). Weights are then
-determined pairwise, starting from the extremes with the highest and
-lowest figures. A coefficient \(\alpha\) is determined by dividing their
-difference (1 in this case) by the mean of the rescaled values. The high
-figure is attributed a score of \(\frac{1}{n} \times \alpha\) where
-\(n\) is the number of assets in the pool while the score for the low
-figure is \(\frac{1/n}{\alpha}\). The operation is repeated for the pair
-of assets showing the second highest and second lowest values for the
-sorting variable and so on until all the assets in the pool are
-attributed a score. The individual asset weights are then determined by
-dividing each score by the sum of the scores.\\
-The period return for a particular mimicking portfolio is calculated as
-the difference between the weighted average return for constituents of
-the long portfolio and that for the constituents of the short portfolio.
+considerations. Using the weekly price, open interest and market
+position data described above we construct market portfolios of
+individual commodity nearby futures as well as mimicking portfolios for
+market, commercial hedging pressure, term structure and liquidity risk
+factors in returns. While our market portfolios are long only
+combinations of particular commodity sets, our other mimicking
+portfolios for risk factors are constructed as combinations of two
+sub-portfolios (legs), one held long, one held short, which respective
+constituents are pooled on a weekly basis according to risk factor
+specific criteria.\\
+All portfolios are equally weighted and returns for the two-legged
+factors are calculated as the difference between the average return for
+constituents of the long leg and that for the constituents of the short.
 i.e, return on the mimicking portfolio for risk factor \(i\) (\(f_{i}\))
@@
 
-\[r_{t}^{f_{i}}=\sum_{j=1}^{x}w^{long}_{j,t} \times r_{j,t}-\sum_{j=n-x}^{n}w^{short}_{j,t} \times r_{j,t}\]
+\[r_{t}^{f_{i}} = \frac{1}{x} \left ( \sum_{j=1}^{x}r_{j,t} - \sum_{j=n-x}^{n} r_{j,t} \right )\]
 \(n\equiv\) number of commodities in the set considered for mimicking
@@
 \(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
-\(w^{*}_{j,t}\equiv\) period \(t\) weight for commodity \(j\) on the
-long or short leg.\\
 \(r_{j,t}\equiv\) period \(t\) front contract return for commodity
@@
 
-We use a time series regression approach where we start with regressions
-of the US traded individual commodity weekly front contract returns on
-returns to the mimicking portfolio for a particular risk factor where
-the portfolio is constructed using the whole cross-section of US traded
-commodities. The corresponding \(R^{2}\)s are averaged and the process
-is repeated for each of our four risk factors (market, hedging pressure,
-term structure and liquidity) and periods (1997/2003, 2004/2008,
-2008/2013 and 2014/2018). For the long-short factors the results are
-reported independently for models where the regressor is the factor
-itself or one of its legs (long vs.~short). The same operation is
-repeated for the two (\(p=2\)) and three (\(p=3\)) factor model cases,
-where regressors include in turn all combinations of any two and three
-risk factors respectively, as well as for the four (\(p=4\)) factor
-model case where all the risk factor mimicking portfolios are included.
-Results are reported for the one-factor model case with the other
-results available upon request.
-
-\medskip
-
-For each period we also implement the analysis described above over
-periods of low and high aggregate CHP (\textbf{CHP}), a notion that we
-believe is particularly relevant in the context of financialisation
-where issues of co-movement and aggregate market behaviour play a
-central role. We define \textbf{CHP} as the cross-sectional average of
-individual CHPs for a particular pool of assets. i.e., period \(t\)
-\textbf{CHP} for asset pool \(x\):
-
-\[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}\] \(n\equiv\)
-number of commodities in set \(x\).\\
+We use a time series regression approach where individual commodity
+weekly front futures contract returns are regressed on returns to the
+mimicking portfolio for a particular risk factor with the corresponding
+\(\beta\)s and \(R^{2}\)s averaged. For the long-short factors the
+results are reported independently for models where the regressor is the
+factor itself or one of its legs (results available upon request).
+
+For each time period considered in the study, being one of the four
+multi-year periods described above or any individual year over the
+entire sample time period, we carry out our analysis over the entire
+period as well as over phases of low and high aggregate CHP
+(\textbf{CHP}) over the period; a notion that we believe is particularly
+relevant in the context of financialisation where issues of co-movement
+and aggregate market behaviour play a central role. We define
+\textbf{CHP} as the cross-sectional average of individual CHPs for a
+particular pool of assets. i.e., period \(t\) \textbf{CHP} for asset
+pool \(x\): \[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}\]
+\(n\equiv\) number of commodities in set \(x\).\\
 \(CHP_{i,t}\equiv\) period \(t\) CHP for commodity \(i\) as defined
@@
 respectively and, in contrast with \citep{hong_what_2012} who aggregate
-across sub-sectors, the asset pool we consider for \textbf{CHP}
-construction include the whole cross-section of US traded commodities.
-
-\medskip
-
-In the next part of the analysis, our mimicking portfolios for risk
-factors, constructed from the set of all US traded commodities are used
-as commodity picking devices on the latter commodity set. For each risk
-factor and period, individual US traded commodity front returns are
-regressed on returns for the corresponding mimicking portfolio.
-Individual commodities are sorted by \(R^{2}\) accordingly from highest
-to lowest and the top third (highest \(R^{2}\)s) are selected as
-commodity picks for the risk factor for the period. i.e, set of picks
-\(P_{t}^{f_{i}}\) for risk factor \(i\) (\(f_{i}\)) over period \(t\):
-
-\[P_{t}^{f_{i}}\equiv\left \{ P_{1}, P_{2}, ..., P_{x} \right \}\]
-\(x = n \cdot s\).\\
-\(n\equiv\) number of commodities in the set considered for the picking
-exercise (twenty-four here).\\
-\(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
-\(P_{j}\equiv\) commodity pick \(j\) for risk factor \(f_{i}\) over
-period \(t\)\\
-\(j\equiv\) rank in the ordered set \(Y_{t}^{f_{i}}\)\\
-\[Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}\]
-\(n\equiv\) number of commodities in the set considered for picking
-(twenty-four here).\\
-\(\tilde{R_{j}^{2}}\equiv\) risk factor \(f_{i}\) returns' explanatory
-power on commodity \(j\) nearby futures returns over period \(t\) as
-defined above.
-
-\medskip
-
-For each period we report the proportion of time each pick is held in
-the long and (/or) short leg of the corresponding risk factor mimicking
-portfolio as well as the average pairwise correlation amongst every set
-of picks.
-
-\medskip
-
-In the last part of the analysis, for each period our mimicking
-portfolios for risk factors in returns are constructed using each set of
-commodity picks independently as the asset pool for portfolio
-construction. A similar time series approach to that described above is
-then implemented using these newly formed mimicking portfolios. In this
-case, a first set of dependent variables includes the sets of commodity
-picks themselves, a second set includes the whole cross-section of US
-traded commodities while a third set includes the six UK traded metals
-considered in the study.
+across sub-sectors, our \textbf{CHP} construction draws on the full
+cross-section of US-traded assets considered in the study.
 
@@
 beyond these mechanical effects of increased long participation ensuing
-from the entry on index type investments as our results suggest next.
-
-\medskip
-
+from the entry on index type investments as our results suggest next.\\
 The cross-sectional nature of financialisation naturally leads us to
@@
 
-\bigskip
-\bigskip
-
-Using our bespoke commodity-based asset pricing framework we strive to
-shed new light on the phenomenon by first regressing returns series for
-the twenty four individual US commodities against our factor mimicking
-portfolios independently. The resulting individual explanatory powers
-(\(R^2\)s), once averaged by factor and period, offer a refined
-perspective on the relation between return and factor attribute
-co-movement. A low figure indicates low cross-sectional return
-co-movement for, in this context, return on the corresponding factor
-mimicking portfolio only has explanatory power on return for commodities
-that are constituents of one of its legs over the corresponding period.
-The explanatory power for the other commodities is typically low or even
-0 for the case where commodities are perfectly uncorrelated with
-one-another. A rising figure on the other hand thus indicates increased
-pairwise correlations, positive or negative, including amongst factor
-leg mimicking portfolio constituent commodities; and therefore provides
-evidence that pairwise return correlation relates to factor attribute.\\
-The average time series explanatory power of the various one factor
-models on the US traded assets over the four periods is shown in Table .
-Over the first period the market factor has the best average time series
-performance with the highest average \(R^{2}\) with all three futures
-market factors performing poorly, indicating that the commodities with
-extreme factor attributes (high or low CHP for example) are uncorrelated
-with the rest of the commodity cross-section, and the overall
-performance consistent across periods of high and low \textbf{CHP}
-(below period median). The two factor models average \(R^{2}\)s
-(available upon request) are roughly the sum of the one factor
-\(R^{2}\)s indicating that the factors are almost orthogonal over this
-period.\\
-The onset of financialisation leads to a substantial improvement in the
-performance of the CHP factor with its average \(R^{2}\) increasing to
-8.2\% in the second period relative to 1.7\% in the first with this
-improvement coming from the long leg that shows a greater improvement
-(4.5\% to 15.1\%) relative to the short (3\% to 4\%), suggesting that
-``normally'' backwardated commodities (Keynesian perspective) have
-higher correlation with the rest of the commodity cross-section, and
-thereby bringing more evidence of the important role played by long only
-investors in the change in nature of these markets over that period. The
-performance of the market factor also improves though not by as much in
-a relative sense (21.6\% from 11.7\%) and both the term structure factor
-and the open interest growth factor show a much smaller improvement in
-performance with smaller differences between legs. Over all periods, all
-of our factor models show similar performance across regimes of high and
-low \textbf{CHP}.
-
 \medskip
 
-We next investigate the top eight of the US traded commodities which
-achieved the highest time series \(R^{2}\) for the CHP, market, open
-interest and term structure factors, in each of the four time periods
-with the commodity picks shown in Table .\\
-For the CHP factor the commodities that achieve high \(R^{2}\) in a
-given period are likely to be those with relatively high or low CHP over
-that period, or those commodities that co-vary with the short or the
-long side of the factor. The same applies to the open interest and term
-structure factors with CHP replaced by open interest growth and roll
-yield respectively; while for the market factor the picks are those that
-co-vary most strongly with the market factor over that period.\\
-For the CHP factor, we observe a change in the picks between the first
-and the second period; the picks in the first period included five
-agricultural commodities and three metals while in the second period
-they include all the five base and precious metals and only three
-agricultural commodities. This pattern is also visible for the term
-structure factor for which there are four metals (copper, silver, gold
-and platinum) picks in the second period against two in the first
-(palladium and platinum) as well as for the open interest nearby growth
-factor for which there are three metals (silver, gold and platinum)
-picks in the second period against one in the first (platinum). The
-market factor has three metal picks in the second period (palladium,
-gold and silver) while all the picks in the first period were
-agricultural or energy commodities.\\
-Over the third period, the average CHP factor shows the same metal picks
-with the agriculturals replaced by energy commodity; the open interest
-nearby growth factor still has three metal picks with gold swapped for
-copper and both the market and term structure factors have one,
-copper.\\
-The table also shows the proportion of time that these picks were
-constituents of the corresponding factor. All the picks of the
-long-short factors (average CHP, open interest nearby growth and term
-structure factors) were constituents of the corresponding factor for
-some proportion of time in all of the time periods. In this respect,
-there is a contrast between the first and second periods with the
-average CHP and open interest nearby growth factor picks appearing
-predominantly on the long side of the corresponding factor in the second
-period, as opposed to both legs in the first. The pattern is
-particularly strong for the metals and energy commodities respectively,
-with the exception of copper for the average CHP factor that lives in
-the short leg a higher proportion of the time over the financialisation
-period. The pattern is reversed for the term structure factor where the
-picks appear predominantly on the short leg in the second period, as
-opposed to both legs in the first with the pattern again strongest for
-the metals. This behaviour continues over the third period for the
-average CHP and open interest nearby growth factors and indicates that
-their picks consistently exhibited low commercial hedging pressure and
-high front contract open interest growth respectively while indicating
-that the term structure factor picks showed low roll yield in the first
-and second period.
+Financialisation was a global phenomenon, through the channel of index
+investment it simultaneously influenced the entire spectrum of liquid
+commodities; this sweeping impact spurred the transformation of
+commodity markets from a collection of idiosyncratic markets into a
+unified asset class with interconnectedness emerging as a crucial aspect
+that warrants thorough examination.\\
+We strive to address this issue by first examining the average of weekly
+returns pairwise correlations between commodities across the entire
+cross-section of the commodity assets considered in the study as well as
+by country, sector and sub-sector. Table~\ref{tbl-correlations-periods}
+shows the results for the four periods of interest with the results
+reported for the entire period as well as for periods of
+\textbf{backwardation} and \textbf{contango}. For the entire sample the
+average pairwise correlation jumps from 0.07 in the first period to 0.16
+over financialisation. This finding indicate higher interdependence
+within the full cross-section of commodities starting with the
+financialisation period, consistent with the empirical findings in
+\citet{fryMcKibbin_evolution_2023} and
+\citet{mayer_financialization_2017} as well as with the theoretical
+model of \citet{basak_model_2016}. The sector analysis sheds light on
+the driving force behind these changes. The US metals see the sharpest
+increase in pairwise correlations going from 0.22 over the past period
+to 0.56 over financialisation while the three other sectors see a much
+smaller percentage increase during financialisation relative to the past
+period. These results thus suggest that the US metals sector was the
+driving force behind increased average pairwise correlations during
+financialisation, a new observation to the best of our knowledge. The
+pattern of correlations is very similar across phases of
+\textbf{backwardation} and \textbf{contango} for all the sectors and
+sub-sectors over the past and financialisation periods which indicates
+that increased commodity interdependence over financialisation was not a
+phase driven phenomenon in the same way that individual commodity
+returns are, as demonstrated in Table~\ref{tbl-stats-regimes}.\\
+We further examine these correlations by year in
+Table~\ref{tbl-correlations-years} to uncover any distinct breakpoints.
+For the full sample of assets, the average pairwise correlations
+increase from 0.08 to 0.12 from 2003 to 2004 seemingly driven by US
+metals average pairwise correlations, more than doubling from 0.22 to
+0.49, suggesting 2004 as the onset of financialization as noted in
+several studies \citep{baker_financialization_2021, tang_index_2012} and
+our contribution is to observe that the US metals sub-sector seems to
+have played a major role in this.
 
@@
 
-In table , we show the average pairwise returns correlation between each
-set of picks in each time period. Following on form the earlier
-observations, this exercise gives an indication of the extent to which
-attribute co-movement reveals price co-movement, which is particularly
-relevant for the long-short factors for which the corresponding
-attribute is not directly related to price co-movement.\\
-In the first period the average picks pairwise correlation for the
-long-short factors ranges from 7.1\% (term structure factor picks) to
-12.4\% (open interest factor picks) while the market factor picks show
-the highest figure (23.7\%). In the second period the figures for the
-long-short factors rise sharply; up to 22.9\% from 8.1\% for the average
-CHP factor picks, up to 32.4\% from 12.4\% for the open interest factor
-picks and up to 23.4\% from 7.1\% for the term structure factor picks.
-This increase is stronger than that for the market factor picks in a
-relative sense and is a consequence of the dramatic increase in average
-pairwise price correlation amongst the US traded metals which dominate
-the average CHP factor set of picks and which presence is stronger
-amongst both the open interest and term structure factor sets of picks
-over the financialisation period. The higher figures for the open
-interest factor are driven by the strong presence of the energy complex
-amongst the corresponding picks. The latter exhibits much higher average
-pairwise correlations than the other sectors in both periods although
-lower in the second relative to the first which reinforces the role
-played by the metals in the sharp increase in average pairwise
-correlation amongst picks for this factor.\\
-With regards to \textbf{CHP} regimes, although not very pronounced, a
-pattern is noticeable. For the market, open interest and term structure
-factor picks, average pairwise correlations are stronger over phases of
-\textbf{contango} in the first period and over phases of
-\textbf{backwardation} in the financialisation period, eventually
-reverting back to being stronger over \textbf{contango} phases in the
-crisis period with the CHP factor sets of picks showing the opposite
-pattern. Overall, these results suggest an increase in correlation
-between non-price attributes co-movement and price co-movement over the
-financialisation period. It is also interesting to note that US traded
-metals returns were negatively correlated with the rest of US traded
-commodities in the first period and positively in the second.
-
-\medskip
-
-To further understand the link between attribute and price co-movement
-we build all of the factors from every set of factor picks and assess
-their explanatory performance on these sets of picks over the four
-periods independently. The results are shown in table . The long-short
-factors for a particular attribute select the top and bottom two of the
-corresponding picks based on that attribute while the market factor
-takes an equally weighted combination of the eight corresponding picks.
-In the absence of price co-movement between the picks, the market factor
-will achieve an average \(R^{2}\) of around 12.5\%\footnote{Market
-  factor lemma:
-  \(\overline{R_{r_{mkt}, p}^{2}} = \frac{1}{n} \sum_{j} R_{r_{j}, r_{mkt}, p}^{2} = \frac{1}{n}; \: n\equiv\)
-  size of market portfolio (eight here).}, while there is no non-zero
-\(R^{2}\) lower bound for the corresponding long-short factors.\\
-A high average \(R^{2}\) for the market factor is indicative of strong
-price co-movement. In this respect, the most remarkable change in
-performance in a relative sense is that of the market factor built from
-the CHP factor sets of picks with the average \(R^{2}\) more than
-doubling, from 18.6\% up to 38.1\%. For the long-short factors on the
-other hand it is indicative of simultaneous attribute and price
-co-movement. For the factors built from the market factor picks the
-increase is strongest in a relative sense for the CHP factor with the
-\(R^{2}\) more than doubling, going from 5.6\% in the first period up to
-12.4\% in the second with the increase stronger for the long leg (17.1\%
-vs.~27.9\%) relative to the short (16.5\% vs.~21.4\%). In the case of
-the factors built from the CHP factor picks, the CHP factor built with
-its own picks shows a remarkable increase in a relative sense with the
-\(R^{2}\) tripling, from 7.2\% to 21.4\% and the long leg showing a much
-greater increase relative to the short (10.4\% to 31.1\% vs.~8.3\% to
-9.8\%). The performance of the term structure factor built from the CHP
-factor sets of picks also shows a sizable increase in a relative sense,
-from 3.5\% to 5.3\% and even more remarkable in this case is the
-substantial increase in performance of the short leg, from 6.3\% to
-15.7\% relative to the long (7.5\% to 9.8\%). The pattern is reversed
-for the CHP factor built from the term structure factor picks where the
-average \(R^{2}\) increases from 4.7\% to 8\% with the performance of
-the long leg increasing from 11.9\% to 28.1\% vs.~5.5\% to 9.1\% for the
-short. The performance of the term structure factor constructed from its
-own sets of picks also shows a substantial increase, from 5.1\% to 8.4\%
-with, here again the increase in performance relatively stronger for the
-short leg, from 6\% to 16.1\% vs.~7.6\% to 12.1\% for the long.\\
-Taken together with the previous results showing that the metal complex
-predominantly loads on the long and short legs of the original CHP and
-term structure factors respectively, these results provide evidence of
-convergence of Keynesian and Working's theories of the term structure in
-detecting price co-movement during financialisation perhaps as a result
-of spillover effects between the corresponding futures and spot markets
-as suggested in \citet{basak_model_2016}.
-
-\medskip
-
-In table we assess the performance of the same factors on all the
-commodities instead of just the picks. While the average \(R^{2}\)s are
-expectedly lower, the pattern of results mostly holds with the relative
-performance of the market factors built with different sets of picks as
-well as that of the CHP and term structure factors built with each
-other's picks similar to table . In contrast, the average CHP factor
-built with average CHP factor picks shows a smaller absolute increase in
-average \(R^{2}\) indicating that the link between CHP co-movement and
-price co-movement is stronger amongst the picks which are predominantly
-metals. Taken together, the results in tables and suggest that the onset
-of financialisation had a major impact on the dynamics of US traded
-precious and precious-base metals.\\
-To assess whether this phenomenon extended beyond US borders we examine
-the performance of the factors used in the last two tables above on the
-six UK metals futures traded on the London Metal Exchange with the
-results reported in table . In the first period, although all sets of
-picks, except that of the market factor, included at least one metal,
-the average \(R^{2}\)s are very low; close to zero in most cases. These
-figures drastically increase across the board in the financialisation
-period and show a pattern similar to that observed in the US complex.
-The market factor built from the CHP and term structure factor sets of
-picks shows the sharpest increase in performance, relative to using the
-other sets of factor picks; rising to 20.1\% from 1.5\% and to 15\% from
-0.8\% respectively. The increase in \(R^{2}\) for the market factor
-built with market factor picks is more modest, providing further
-evidence of concentration of co-movement in the metals sector during
-financialisation.\\
-Here again the change in performance for the CHP and term structure
-factor legs stands out where the factors are built with their own as
-well as each other's sets of picks. The average \(R^{2}\) for the long
-leg of the CHP factor built with its own sets of picks increases from
-1\% to 11\% while the short leg shows no significant change. The
-opposite holds for the term structure factor built from its own set of
-picks with the short leg performance increasing from 0.1\% to 14\% while
-that of the long leg remains below 1\%. Building these factors from each
-other's sets of picks produces a similar pattern with the performance of
-the long leg of the CHP factor built from the term structure factor
-picks increasing from 0.7\% to 11.4\%; a much greater increase relative
-to the short leg although in this case the latter also shows a sizable
-increase in performance (0.3\% to 6\%). The performance of the short leg
-of the term structure factor built from the CHP factor sets of picks on
-the other hand increases from 0.3\% to 19.2\% while the performance for
-the long leg in the second period remains below 1.5\%.\\
+We investigate further the issue of co-movement from an asset pricing
+perspective using a bespoke asset pricing framework starting with a
+market factor mimicking portfolio constituted of the twenty-four US
+traded commodities considered in the study with equal weighting. This
+portfolio enables a refined examination of cross correlations across
+sectors as the numerator of the beta of the regression of the returns
+for an individual commodity against those for the market factor is
+driven by covariances while the denominator is driven by the individual
+commodity variance. Thus, an increase in a commodity's correlation with
+other commodities should lead to an increase in its beta relative to the
+market factor portfolio. We accordingly regress the weekly individual
+commodity front futures returns against those for our market factor
+portfolio and average the resulting betas across the entire set of
+commodity assets considered as well as by country, sector and sub-sector
+for each of the four periods of interest with the results shown in
+Table~\ref{tbl-regressions-index}. The average beta for the US metals
+sector jumps sharply to 1.12 over financialisation from 0.63 over the
+previous period; the increase is even more dramatic for the base metals
+sub-sector (GB traded assets) in a relative sense. The group had a much
+lower beta of 0.27 over the past period, suggesting a low level of
+correlation with US commodities; this figure increases to 0.85 over the
+financialisation period, even beyond that for the US agricultural sector
+of 0.80. In contrast, the corresponding figure for the energy sector
+show a substantial decrease, down to 1.61 during financialisation from
+2.33 over the past period.\\
+The corresponding pricing performance displays a similar pattern as
+shown in Table~\ref{tbl-regressions-factors} where for each period the
+corresponding \(R^{2}\) values are independently averaged over the
+entire period as well as over periods of \textbf{contango} and
+\textbf{backwardation}. The average \(R^{2}\) for the market factor
+across the entire cross-section of commodity assets considered in the
+study, including the GB traded base metals, increases to around 20\%
+during financialisation compared to around 10\% over the previous period
+with the rise driven by the metals sector at large. The sector average
+for the US traded assets jumps to 31\% during financialisation from
+7.5\% over the past period while for the GB traded assets the
+corresponding figure increases from less than 2\%, or virtually no
+explanatory power for the (US based) market factor, to almost 12\% over
+the financialisation period. The results for our other risk factor
+mimicking portfolios show a similar pattern and provide a deeper
+insights into co-movement dynamics in this context. All three
+factors---CHP, open interest and term structure---performed poorly in
+the first period, indicating that the commodities with extreme factor
+attributes (high or low CHP for example) were uncorrelated with the rest
+of the commodity cross-section, and the overall performance consistent
+across periods of \textbf{contango} and \textbf{backwardation}. The
+onset of financialisation leads to a substantial improvement in the
+performance of the CHP factor with its average \(R^{2}\), albeit still
+small at 5.4\%, almost tripling from the past to the financialisation
+period in contrast to the other factors that show weaker dynamics with a
+slight decrease and a much smaller increase for the open interest and
+term structure factors respectively. Here again the increase in pricing
+performance for the CHP factor is driven by the metals sector,
+particularly the precious sub-sector with the average \(R^{2}\) for the
+group jumping to almost 26\% during financialisation from 1.2\% over the
+past period. The corresponding figures of 22\% and 1.1\% for the entire
+US metals sector stand in sharp contrast with the agricultural sector,
+which exhibits no notable change, and the energy sector, where pricing
+performance drops substantially from 9.2\% down to 1.6\%. The
+improvement in the CHP factor's pricing performance remarkably comes
+predominantly from the long leg (low CHP assets: Keynesian ``normal
+backwardation'') of the factor\^{}\{Results available from the authors
+upon request.\} with the corresponding mimicking portfolio's performance
+itself driven by the metals, the precious sub-sector in particular. The
+average \(R^{2}\) for the group jumps to 55\% during financialisation
+from less than 12\% over the past period while the short leg sees a far
+smaller increase, up to 8.9\% from 3.3\% over the past period.
+Interestingly, although the term structure factor itself only sees a
+very modest increase, its short leg (low roll-yield assets: Working's
+backwardation) shows a sizeable rise in pricing performance, yet again
+driven the metals sector, with the average \(R^{2}\) for the group's US
+traded assets jumping to 28.2\% during financialisation from 6.2\% over
+the past period. The pattern of results for both factors extends to the
+GB trade assets and suggest a convergence of Keneysian and Working's
+term structure perspective over the financialisation period.\\
 Taken together these results emphasise the global nature of the impact
@@
 results. Returns fall sharply relative to the financialisation period
-(table ) with eighteen US commodities along with all six UK traded
-metals showing lower mean returns. Returns for equally weighted
-portfolios of both sets of assets fall down to 9.4\% and 5.3\% from
-15.9\% and 21.8\% respectively. Returns are mostly higher during phases
-of \textbf{backwardation} relative to \textbf{contango} (table ) with
-fifteen US assets and five of the UK traded metals showing higher mean
-returns in \textbf{backwardation} and the pattern extending to equally
-weighted portfolios of the two sets of assets. Volatility is moderately
-higher for both sets with fifteen US commodities and three UK metals
-showing higher figures and interestingly eminently higher over phases of
-\textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none
-of the UK traded metals show higher volatility figures over
-\textbf{backwardation} phases. The symmetry between the dynamics of CHP
-and \textbf{CHP}'s explanatory power on individual commodity returns
-breaks in the crisis period with both now seemingly converging; the US
-cross-sectional average \(R^{2}\) at the individual level bouncing back
-up (22.5\% vs 20.8\%) while that at the aggregate level rises further
-(14.7\% vs 7.1\%).\\
-The performance of the market factor dominates the US commodity complex
-over the period with a 50\% increase in mean average \(R^{2}\) to over
-30\% (table ) while that of the CHP factor decreases and, although
-increasing, remains modest for the open interest growth and term
-structure factors. The average pairwise correlation amongst the market
-factor picks increases beyond 50\% while there is a leveling in that
-amongst the picks of the long-short factors as shown in table .
-Notwithstanding, the market factor built from any sets of picks shows a
-significant rise across the board in performance on the US complex
-(table ).\\
-Taken together, these results indicate the presence of a systematic
-factor across the entire cross-section of the US commodities. Table
-provides further evidence of systematic linkages, in this case between
-US and non-US traded commodities with a similar, albeit more pronounced
-pattern, where the market factor constructed with any sets of picks (US
-traded commodities) shows a dramatic increase in performance on the UK
-metals with for example, when constructed from its own sets of picks,
-the average \(R^{2}\) increasing to 31.7\% from 10.2\% in the previous
-period.
+(Table~\ref{tbl-stats-no-regimes}) with eighteen US commodities along
+with all six GB traded metals showing lower mean returns. Returns for
+equally weighted portfolios of both sets of assets fall down to 9.4\%
+and 5.3\% from 15.9\% and 21.8\% respectively. Returns are mostly higher
+during phases of \textbf{backwardation} relative to \textbf{contango}
+(Table~\ref{tbl-stats-regimes}) with fifteen US assets and five of the
+GB traded metals showing higher mean returns in \textbf{backwardation}
+and the pattern extending to equally weighted portfolios of the two sets
+of assets. Volatility is moderately higher for both sets with fifteen US
+commodities and three GB metals showing higher figures and interestingly
+eminently higher over phases of \textbf{contango}; out of the US complex
+only Sugar-\#11 (IFUS) and none of the GB traded metals show higher
+volatility figures over \textbf{backwardation} phases. The symmetry
+between the dynamics of CHP and \textbf{CHP}'s explanatory power on
+individual commodity returns breaks in the crisis period
+(Table~\ref{tbl-time-reg-US-CHP}) with both now seemingly converging;
+the US cross-sectional average \(R^{2}\) at the individual level
+bouncing back up (22.5\% vs 20.8\%) while that at the aggregate level
+rises further (14.7\% vs 7.1\%).
 
@@
 
-The returns pullback continues into the post-crisis period (table ) with
-twenty-two US and four UK traded assets showing lower mean returns
-relative to the crisis while the same number of US commodities and all
-UK metals show lower figures relative to the financialisation period;
-mean returns for equally weighted portfolios of US and UK assets drop
-down to -0.2\% and 2.7\% respectively. Interestingly volatility also
-recedes substantially with twenty US assets and all UK metals showing
-lower volatility figures relative to both the crisis and
-financialisation periods suggesting that investment outflows from the
-commodity futures complex have had a lower impact on volatility than the
-corresponding inflows witnessed over the financialisation period. The
-figures for the equally weighted portfolios of US and UK assets drop to
-9.9\% and 16.2\% respectively, very close to pre-financialisation
-levels.\\
+The average pairwise correlation for the entire cross-section of
+commodities considered in the study
+(Table~\ref{tbl-correlations-periods}) increases further into the crisis
+to 0.28 indicating an intensification of the higher interdependence
+within the full cross-section of commodities prompted by
+financialisation. The result is consistent with the greater
+interdependence between equity and commodity markets over this period
+documented in \citet{silvennoinen_financialisation_2013}. The figure for
+the US traded section of the metals sector only progresses modestly to
+0.59 after peaking at 0.63 in 2006 (Table~\ref{tbl-correlations-years}).
+In contrast, the GB traded assets see a sharp increase to over 0.65 in
+the crisis starting in 2007 up to a peak of 0.69 in 2010. The
+agricultural sector on the other hand shows a substantial rise in the
+crisis period with the sharpest increase in 2008 when the average
+pairwise correlation for the sector jumps to 0.30. Meanwhile, the energy
+sector also shows a notable progression starting in 2007 and peaking at
+0.63 in 2008 before levelling back down over the rest of the period. The
+onset of the financial crisis seems therefore to have had an across the
+board impact on the interdependence of commodities in contrast with
+financialisation, much more closely related to the metals sector.
+
+\medskip
+
+The entire cross-section sees an increase in average regression
+coefficient relative to the market factor over the crisis period with
+the strongest progression for the GB traded metals followed by the
+agricultural sector (Table~\ref{tbl-regressions-index}). The pricing
+performance of the factor dominates the US commodity complex over the
+period (Table~\ref{tbl-regressions-factors}), showing a 50\% increase in
+mean average \(R^{2}\) to over 31\%, while that for both the CHP and
+open interest factor decreases and, although increasing, remains modest
+for the term structure factors; the increase is strongest for the GB
+traded metal assets with an average \(R^{2}\) of almost 34\% for the
+period. Taken together, these results indicate the presence of a
+systematic factor across the entire cross-section of the US commodities.
+For both the CHP and term structure factors, both legs show an increase
+in average \(R^{2}\) and while substantially diverging over the
+preceding financialisation period the pricing performance for both legs
+seems to converge back to a pattern closer to that observed
+pre-financialisation.
+
+\bigskip
+\bigskip
+
+The returns pull-back continues into the post-crisis period
+(Table~\ref{tbl-stats-no-regimes}) with twenty-two US and four UK traded
+assets showing lower mean returns relative to the crisis while the same
+number of US commodities and all UK metals show lower figures relative
+to the financialisation period; mean returns for equally weighted
+portfolios of US and UK assets drop down to -0.2\% and 2.7\%
+respectively. Interestingly volatility also recedes substantially with
+twenty US assets and all UK metals showing lower volatility figures
+relative to both the crisis and financialisation periods suggesting that
+investment outflows from the commodity futures complex have had a lower
+impact on volatility than the corresponding inflows witnessed over the
+financialisation period. The figures for the equally weighted portfolios
+of US and UK assets drop to 9.9\% and 16.2\% respectively, very close to
+pre-financialisation levels.\\
 The pattern of reversion toward the pre-financialisation Keynesian
 paradigm initiated during the crisis continues stronger into the
-post-crisis period (table ) with mean returns higher during phases of
-\textbf{backwardation} relative to \textbf{contango} (table ), more so
-than over the crisis period with seventeen US commodities showing higher
-mean returns over \textbf{backwardation} phases. The difference is
-significant at the 5\% level for Lumber (XCME) and at the 10\% level for
-Palladium (XNYM) while no difference is significant for the assets
-showing higher figures over phases of \textbf{contango}. The pattern is
-more pronounced for the UK traded subset with all six assets showing
-higher mean returns in \textbf{backwardation} with the difference
-significant at the 1\% level for Nickel-primary (XLME), 5\% level for
-Aluminium (XLME) and 10\% level for Zinc (XLME). It also extends to
-equally weighted portfolios of US and UK traded assets that both show
-higher mean returns during \textbf{backwardation} with the difference
-significant at the 5\% level for the UK portfolio and the figure close
-to the 10\% level significance threshold for the portfolio of US assets.
-Volatilities are overall higher in \textbf{contango} although less so
-than over the previous period with seventeen US commodities showing
-higher figures over \textbf{contango} against twenty-three in the crisis
-period. The pattern extends to three of the six UK traded metals with
-the difference significant at the 1\% level for Copper (XLME) and Tin
-(XLME) and at the 5\% level for Zinc (XLME) while differences are not
-significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME)
-that exhibit higher volatility over \textbf{backwardation} phases.
-Equally weighted portfolios of US and UK traded assets on the other hand
-both show higher volatility in \textbf{contango} with the difference
-significant at the 1\% level for both. Over the financialisation period
-in contrast volatilities were predominantly higher in
-\textbf{backwardation} for US traded assets with fourteen commodities
-showing higher volatility figures in these phases; the post-crisis
-pattern of results for volatilities thus likewise shows signs of
-reversion to pre-financialisation standards. After showing signs of
-convergence in the crisis period the dynamics of the explanatory power
-of CHP and \textbf{CHP} part ways (table ), seemingly reverting to the
-Keynesian paradigm observed pre-financialisation, further suggesting a
-return to legacy commodity specific dynamics. The recovery initiated in
-the crisis period for that of CHP is confirmed with a stronger increase
-in the post-crisis period, 27.2\% vs.~22.5\%, strongest for the metals
-sector, 37.3\% vs.~23.7\%, while the energy sector shows the opposite
-pattern: 11\% vs.~16\%. In contrast, after increasing stronger in the
-crisis, that for \textbf{CHP} falls overall in the post-crisis period,
-7.5\% vs 14.7\%, with the decrease strongest for the energy sector in a
-relative sense: 2.5\% vs.~14.8\%.\\
-Average pairwise correlations amongst factor picks (table ) fall
-substantially in the post-crisis period with for example the figure for
-the market factor picks dropping from 50.1\% to 26.1\%, almost down to
-pre-financialisation levels; results are similar for the long-short
-factor picks with figures below financialisation levels in all cases and
-very close to pre-financialisation standards for the term structure and
-liquidity factor picks. The performance of the market factor on the US
-complex declines below financialisation levels (table ) with the pattern
-similar albeit stronger when the factor is built from the sets of factor
-picks with a decline in performance on the US complex (table ) to almost
-pre-financialisation levels when constructed with its own set of picks
-as well as with those of the long-short factors, in particular the term
-structure and liquidity factors. Table provides further evidence of
-decoupling, in this case between US and non-US traded commodities with a
-sharp decline in performance of the market factor constructed with any
-set of picks on the UK complex below financialisation, down to almost
-pre-financialisation levels when constructed with the sets of long-short
-factors picks.
+post-crisis period (Table~\ref{tbl-stats-regimes}) with mean returns
+higher during phases of \textbf{backwardation} relative to
+\textbf{contango}, more so than over the crisis period with seventeen US
+commodities showing higher mean returns over \textbf{backwardation}
+phases. The difference is significant at the 5\% level for Lumber (XCME)
+and at the 10\% level for Palladium (XNYM) while no difference is
+significant for the assets showing higher figures over phases of
+\textbf{contango}. The pattern is more pronounced for the UK traded
+subset with all six assets showing higher mean returns in
+\textbf{backwardation} with the difference significant at the 1\% level
+for Nickel-primary (XLME), 5\% level for Aluminium (XLME) and 10\% level
+for Zinc (XLME). It also extends to equally weighted portfolios of US
+and UK traded assets that both show higher mean returns during
+\textbf{backwardation} with the difference significant at the 5\% level
+for the UK portfolio and the figure close to the 10\% level significance
+threshold for the portfolio of US assets. Volatilities are overall
+higher in \textbf{contango} although less so than over the previous
+period with seventeen US commodities showing higher figures over
+\textbf{contango} against twenty-three in the crisis period. The pattern
+extends to three of the six UK traded metals with the difference
+significant at the 1\% level for Copper (XLME) and Tin (XLME) and at the
+5\% level for Zinc (XLME) while differences are not significant for
+Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit
+higher volatility over \textbf{backwardation} phases. Equally weighted
+portfolios of US and UK traded assets on the other hand both show higher
+volatility in \textbf{contango} with the difference significant at the
+1\% level for both. Over the financialisation period in contrast
+volatilities were predominantly higher in \textbf{backwardation} for US
+traded assets with fourteen commodities showing higher volatility
+figures in these phases; the post-crisis pattern of results for
+volatilities thus likewise shows signs of reversion to
+pre-financialisation standards. After showing signs of convergence in
+the crisis period the dynamics of the explanatory power of CHP and
+\textbf{CHP} part ways (Table~\ref{tbl-time-reg-US-CHP}), seemingly
+reverting to the Keynesian paradigm observed pre-financialisation,
+further suggesting a return to legacy commodity specific dynamics. The
+recovery initiated in the crisis period for that of CHP is confirmed
+with a stronger increase in the post-crisis period, 27.2\% vs.~22.5\%,
+strongest for the metals sector, 37.3\% vs.~23.7\%, while the energy
+sector shows the opposite pattern: 11\% vs.~16\%. In contrast, after
+increasing stronger in the crisis, that for \textbf{CHP} falls overall
+in the post-crisis period, 7.5\% vs 14.7\%, with the decrease strongest
+for the energy sector in a relative sense: 2.5\% vs.~14.8\%.
 
@@
 
-Taken together the patterns of results over the crisis and post-crisis
-periods echo those in \citet{basu_definancialisation} in suggesting that
-the exogenous shock delivered by the financial crisis combined with the
-accommodative monetary policy that ensued seem to have initiated a
-reversion toward pre-financialisation fundamentals in the commodity
-futures complex.
+The average pairwise correlations fall across the board in the
+post-crisis period, below the levels observed during financialisation,
+with the figure for the entire cross-section
+(Table~\ref{tbl-correlations-periods}) dropping down to 0.12 from 0.28
+over the crisis. This substantial decline, that does not appear to have
+been widely noted, appears to begin in the latter part of the crisis
+period, around 2012 (Table~\ref{tbl-correlations-years}), before
+levelling down over the whole post-crisis period.
+
+\medskip
+
+In a similar vein, the average market factor beta for the entire
+cross-section drops down to 0.94 (Table~\ref{tbl-regressions-index}),
+below the level observed during financialization. The decline seems
+driven by the metals sector, particularly the GB traded segment, with
+the figures for the US and GB traded assets at 0.91 and 0.72, down from
+1.12 and 1.18, respectively. Meanwhile, the pricing performance of the
+market factor also retreats to below financialisation levels with the
+average \(R^{2}\) for the entire cross-section dropping down to 14.7\%
+(Table~\ref{tbl-regressions-factors}). All sectors seem affected with
+agriculturals, energy and metals all seeing their average \(R^{2}\)
+decline below the levels observed during the financialisation period
+albeit remaining above 10\% for the GB traded metals against less than
+2\% pre-financialisation. Similarly, the performance for both the CHP
+and term structure factors falls back to levels below those attained
+over financialisation while the gap between their long and short legs
+remains narrower than observed during that period. These results, along
+with those from the crisis period, suggest that the exogenous shock of
+the financial crisis, combined with the subsequent accommodative
+monetary policy, may have triggered a reversion toward
+pre-financialization fundamentals in the commodity futures complex; an
+issue that, to our knowledge, has not been widely discussed in the
+existing literature.\\
+The phases analysis further documents the emerging role/dominance of the
+\textbf{contango} regime post-crisis with average correlations higher
+during those phases and the pattern stronger for the metal assets both
+US and GB traded. Similarly, for the latter the pricing performance of
+the market factor is considerably better during phase of
+\textbf{contango} in contrast with the previous periods that showed no
+substantial difference between phase of \textbf{contango} and
+\textbf{backwardation}. The figures for the US and GB traded segments of
+the sector are 23\% (\textbf{contango}) vs 11.5\%
+(\textbf{backwardation}) against 36.2\% vs 43\% during financialisation
+and 14.4\% (\textbf{contango}) vs 6.6\% (\textbf{backwardation}) against
+33.5\% vs 34.4\% during financialisation respectively. Taken together,
+these results indicate some recent changes in the correlation structure
+within the sector and along with the decline in interdependence in the
+commodity sector at large documented above, this observation could form
+a valuable basis for future research.\\
+These findings further providence additional evidence that the
+interdependence effects of financialization seems to have been strongest
+for the entire cross-section of the metals sector with a lesser impact
+for the other sectors.
 
@@
 Mean values significant at the 1\%, 5\% and 10\% level are marked with
-***, ** and * respectively. The results are discussed in section
+***, ** and * respectively. The results are discussed in
 Section~\ref{sec-results}.}
@@
 CHP construction and corresponding regime definitions are discussed in
-section Section~\ref{sec-methods} while the results are discussed in
-section Section~\ref{sec-results}.}
+Section~\ref{sec-methods} while the results are discussed in
+Section~\ref{sec-results}.}
 
@@
 against that in aggregate CHP, a market wide measure of CHP which
-calculation method is discussed in section Section~\ref{sec-methods}.
-Averages are calculated independently across the whole cross-section of
-US traded commodity assets considered in the study as well as across
-commodity sectors and subsectors for the four periods of interest (past:
+calculation method is discussed in Section~\ref{sec-methods}. Averages
+are calculated independently across the whole cross-section of US traded
+commodity assets considered in the study as well as across commodity
+sectors and subsectors for the four periods of interest (past:
 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
-2013-2018). The results are discussed in section
-Section~\ref{sec-results}.}
+2013-2018). The results are discussed in Section~\ref{sec-results}.}
 
@@
 construction and corresponding regime definitions are discussed in
-section Section~\ref{sec-methods} while the results are discussed in
-section Section~\ref{sec-results}.}
+Section~\ref{sec-methods} while the results are discussed in
+Section~\ref{sec-results}.}
 
@@
 whole period of interest (1997-2018). The results are discussed in
-section Section~\ref{sec-results}.}
+Section~\ref{sec-results}.}
 
@@
 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
-2013-2018). The market factor construction is discussed in section
-Section~\ref{sec-methods} while the results are discussed in section
+2013-2018). The market factor construction is discussed in
+Section~\ref{sec-methods} while the results are discussed in
 Section~\ref{sec-results}.}

### 2024-09-27 explore/scripts/revision-jfm/tables.r
Combined table 1 and 2 into new "combined" table

@@ -118,6 +118,32 @@ countries <- dplyr::filter(commodities_market_countries, regime != "all") %>%
 
 descriptive_stats_regimes <- dplyr::bind_rows(commodities, countries)
 
+## combined ####
+commodities <- dplyr::select(commodities_market_individuals, -c(min, max)) %>% 
+  dplyr::mutate(
+    mean = percentize(mean), sd = percentize(sd),
+    mean = purrr::map2_chr(p.value, mean, ~ significance(.x, .y))
+  ) %>% dplyr::select(-p.value) %>%
+  tidyr::pivot_longer(
+    cols = c("mean", "sd"), names_to = "estimate", values_to = "value"
+  ) %>% tidyr::pivot_wider(names_from = "period", values_from = "value") %>%
+  dplyr::arrange(dplyr::desc(country), sector, subsector, commodity, regime) %>%
+  dplyr::select(-c(country, sector, subsector)) %>%
+  dplyr::rename(asset = commodity)
+
+countries <- dplyr::select(commodities_market_countries, -c(min, max, sector, subsector)) %>% 
+  dplyr::mutate(asset = paste(country, "commodities", sep = " ")) %>%
+  dplyr::select(-country) %>% 
+  dplyr::mutate(
+    mean = percentize(mean), sd = percentize(sd),
+    mean = purrr::map2_chr(p.value, mean, ~ significance(.x, .y))
+  ) %>% dplyr::select(-p.value) %>%
+  tidyr::pivot_longer(
+    cols = c("mean", "sd"), names_to = "estimate", values_to = "value"
+  ) %>% tidyr::pivot_wider(names_from = "period", values_from = "value")
+
+descriptive_stats_combined <- dplyr::bind_rows(commodities, countries)
+
 
 # correlations ####
 correlations <- readr::read_rds(
@@ -281,6 +307,7 @@ tables <- tibble::tribble(
     ~analysis,                                  ~results,
     "stats - whole",                            descriptive_stats_whole,
     "stats - regimes",                          descriptive_stats_regimes,
+    "stats - combined",                         descriptive_stats_combined,
     "regressions - US returns ~ US CHP",        `US commodity returns ~ CHP`,
     "correlations - periods",                   correlations_periods,
     "correlations - years",                     correlations_years,

### 2024-09-27 explore/scripts/revision-jfm/tables.r
Update regime label in combined table

@@ -142,7 +142,8 @@ countries <- dplyr::select(commodities_market_countries, -c(min, max, sector, su
     cols = c("mean", "sd"), names_to = "estimate", values_to = "value"
   ) %>% tidyr::pivot_wider(names_from = "period", values_from = "value")
 
-descriptive_stats_combined <- dplyr::bind_rows(commodities, countries)
+descriptive_stats_combined <- dplyr::bind_rows(commodities, countries) %>%
+dplyr::mutate(regime = ifelse(regime == "all", "whole period", regime))
 
 
 # correlations ####

### 2024-09-27 docs/paper.qmd

@@
 ```{r}
+#| label: tbl-stats-combined
+#| tbl-cap: "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+for each period the figures are shown independently for the entire period as well as for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
+Mean values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
+Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
+
+colnames <- c("asset", "regime", "estimate", periods)
+align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+
+make_table("stats - combined", colnames, align, 1L:7L, 4L:7L)
+```
+
+```{r}
+#| eval: false
 #| label: tbl-stats-no-regimes
@@
 ```{r}
+#| eval: false
 #| label: tbl-stats-regimes

### 2024-09-27 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@17d928f09a98f0737dd9464bd9d461c9a21907ca 🚀

@@
 includes factors constructed using both theoretical and liquidity
-considerations. Using the weekly price, open interest and market
+considerations. Using the weekly returns, open interest and market
 position data described above we construct market portfolios of
@@
 \(\beta\)s and \(R^{2}\)s averaged. For the long-short factors the
-results are reported independently for models where the regressor is the
-factor itself or one of its legs (results available upon request).
+\(\beta\)s and \(R^{2}\)s are computed for models where the regressor is
+the factor itself as well as both its long and short legs independently
+(results available upon request).
 
@@
 contango (\textbf{contango}) \textbf{CHP} regimes as, for a given
-period, \textbf{CHP} levels below and above the period's median
-respectively and, in contrast with \citep{hong_what_2012} who aggregate
-across sub-sectors, our \textbf{CHP} construction draws on the full
-cross-section of US-traded assets considered in the study.
+period, sub-periods with \textbf{CHP} levels below and above the
+period's median respectively and, in contrast with
+\citep{hong_what_2012} who aggregate across sub-sectors, our
+\textbf{CHP} construction draws on the full cross-section of US-traded
+assets considered in the study.
 
@@
 
-\begin{longtable}[t]{>{}l>{}l>{}r>{}r>{}r>{}r}
-
-\caption{\label{tbl-stats-no-regimes}This table shows mean returns and
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-stats-combined}This table shows mean returns and
 volatility (sd) for the twenty four individual US commodities and the
@@
 financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Mean values significant at the 1\%, 5\% and 10\% level are marked with
-***, ** and * respectively. The results are discussed in
-Section~\ref{sec-results}.}
-
-\tabularnewline
-
-\toprule
-\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
-\midrule
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
-\addlinespace
-\textbf{Soybean meal (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
-\textbf{Soybeans (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}}\\
-\addlinespace
-\textbf{Cattle-live (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.65\%}}}\\
-\textbf{Cocoa (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.99\%}}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
-\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.06\%}}}\\
-\addlinespace
-\textbf{Lumber (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
-\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.8\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.16\%}}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.33\%}}}\\
-\textbf{Natural gas (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.64\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.37\%}}}\\
-\addlinespace
-\textbf{Gasoline (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.44\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.1\%}}}\\
-\textbf{Copper (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.53\%}}}\\
-\textbf{Gold (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.75\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.92\%}}}\\
-\addlinespace
-\textbf{Platinum (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.43\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
-\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.15\%}}}\\
-\textbf{Aluminium (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**28.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.03\%}}}\\
-\textbf{Copper (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
-\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}}\\
-\textbf{Lead (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.31\%}}}\\
-\addlinespace
-\textbf{Nickel-primary (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.68\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.07\%}}}\\
-\textbf{Zinc (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**15.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.18\%}}}\\
-\textbf{US commodities} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*21.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.72\%}}}\\
-\textbf{GB commodities} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
-\bottomrule
-
-\end{longtable}
-
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{7}{9}\selectfont
-
-\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
-
-\caption{\label{tbl-stats-regimes}This table shows mean returns and
-volatility (sd) for the twenty four individual US commodities and the
-six GB metals considered in the study as well as for two equally
-weighted portfolios formed from the US commodities and the GB metals
-respectively across the four periods of interest (past: 1997-2003;
-financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Figures are shown independently for phases of aggregate backwardation
-(aggregate CHP \(\leq\) period median) and aggregate contango (aggregate
-CHP \textgreater{} period median). Mean values significant at the 1\%,
-5\% and 10\% level are marked with ***, ** and * respectively. Aggregate
-CHP construction and corresponding regime definitions are discussed in
+for each period the figures are shown independently for the entire
+period as well as for phases of aggregate backwardation (aggregate CHP
+\(\leq\) period median) and aggregate contango (aggregate CHP
+\textgreater{} period median). Mean values significant at the 1\%, 5\%
+and 10\% level are marked with ***, ** and * respectively. Aggregate CHP
+construction and corresponding regime definitions are discussed in
 Section~\ref{sec-methods} while the results are discussed in
@@
 \midrule
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
 \textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.74\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.78\%}}}\\
+\addlinespace
 \textbf{Corn-\#2 yellow (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
+\textbf{Oats (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
 \textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
-\addlinespace
 \textbf{Oats (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.17\%}}}\\
 \textbf{Oats (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
 \textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.52\%}}}\\
+\addlinespace
 \textbf{Soybean meal (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
-\addlinespace
 \textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}}\\
 \textbf{Soybean meal (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.44\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.12\%}}}\\
-\addlinespace
 \textbf{Soybean oil (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
+\addlinespace
+\textbf{Soybeans (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
 \textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.45\%}}}\\
@@
 \addlinespace
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
 \textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.44\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.77\%}}}\\
+\addlinespace
 \textbf{Wheat-SRW (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.04\%}} & \textcolor[HTML]{4285f4}{\textbf{29.84\%}} & \textcolor[HTML]{4285f4}{\textbf{37.73\%}} & \textcolor[HTML]{4285f4}{\textbf{26.72\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**20.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.58\%}}}\\
-\addlinespace
 \textbf{Cattle-feeder (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}} & \textcolor[HTML]{4285f4}{\textbf{14.93\%}} & \textcolor[HTML]{4285f4}{\textbf{13.39\%}} & \textcolor[HTML]{4285f4}{\textbf{20.14\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.12\%}}}\\
 \textbf{Cattle-feeder (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.67\%}} & \textcolor[HTML]{4285f4}{\textbf{15.35\%}} & \textcolor[HTML]{4285f4}{\textbf{16.91\%}} & \textcolor[HTML]{4285f4}{\textbf{17.23\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}}\\
+\textbf{Cattle-live (XCME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.07\%}}}\\
+\addlinespace
 \textbf{Cattle-live (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.65\%}} & \textcolor[HTML]{4285f4}{\textbf{17.91\%}} & \textcolor[HTML]{4285f4}{\textbf{14.97\%}} & \textcolor[HTML]{4285f4}{\textbf{19.9\%}}\\
-\addlinespace
 \textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
 \textbf{Cattle-live (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.49\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}} & \textcolor[HTML]{4285f4}{\textbf{17.57\%}} & \textcolor[HTML]{4285f4}{\textbf{16.66\%}}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}}\\
+\textbf{Lean hogs (XCME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.23\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.24\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.66\%}}}\\
-\addlinespace
 \textbf{Lean hogs (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.22\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}} & \textcolor[HTML]{4285f4}{\textbf{32.78\%}} & \textcolor[HTML]{4285f4}{\textbf{38.28\%}}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.65\%}}}\\
+\addlinespace
+\textbf{Cocoa (IFUS)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
 \textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.98\%}}}\\
@@
 \addlinespace
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.99\%}}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
 \textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.36\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.24\%}}}\\
+\addlinespace
 \textbf{Coffee-C (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.22\%}} & \textcolor[HTML]{4285f4}{\textbf{32.24\%}}\\
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
 \textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.84\%}}}\\
-\addlinespace
 \textbf{Cotton-\#2 (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.02\%}} & \textcolor[HTML]{4285f4}{\textbf{29.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.94\%}} & \textcolor[HTML]{4285f4}{\textbf{21.33\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.91\%}}}\\
 \textbf{Cotton-\#2 (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.77\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.59\%}} & \textcolor[HTML]{4285f4}{\textbf{19.95\%}}\\
+\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.06\%}}}\\
+\textbf{Lumber (XCME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
 \textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**26.99\%}}}\\
+\addlinespace
 \textbf{Lumber (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.43\%}} & \textcolor[HTML]{4285f4}{\textbf{30.72\%}} & \textcolor[HTML]{4285f4}{\textbf{35.45\%}} & \textcolor[HTML]{4285f4}{\textbf{21.26\%}}\\
-\addlinespace
 \textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.14\%}}}\\
 \textbf{Lumber (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}} & \textcolor[HTML]{4285f4}{\textbf{28.2\%}} & \textcolor[HTML]{4285f4}{\textbf{37.23\%}} & \textcolor[HTML]{4285f4}{\textbf{28.45\%}}\\
+\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.8\%}}}\\
+\textbf{Orange juice (IFUS)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.64\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.64\%}}}\\
-\addlinespace
 \textbf{Orange juice (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{38.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.11\%}}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.16\%}}}\\
+\addlinespace
+\textbf{Sugar-\#11 (IFUS)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
 \textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.07\%}}}\\
@@
 \addlinespace
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.33\%}}}\\
+\textbf{Natural gas (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
 \textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**85.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.76\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.33\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.25\%}}}\\
+\addlinespace
 \textbf{Natural gas (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{59.76\%}} & \textcolor[HTML]{4285f4}{\textbf{61.3\%}} & \textcolor[HTML]{4285f4}{\textbf{58.18\%}} & \textcolor[HTML]{4285f4}{\textbf{46.41\%}}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.64\%}}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
 \textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.24\%}}}\\
-\addlinespace
 \textbf{Crude oil-WTI (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{36.74\%}} & \textcolor[HTML]{4285f4}{\textbf{32.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.19\%}} & \textcolor[HTML]{4285f4}{\textbf{26.94\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-24.85\%}}}\\
 \textbf{Crude oil-WTI (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.74\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{53.7\%}} & \textcolor[HTML]{4285f4}{\textbf{41.08\%}}\\
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.37\%}}}\\
+\textbf{Gasoline (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
 \textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}}\\
+\addlinespace
 \textbf{Gasoline (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.47\%}} & \textcolor[HTML]{4285f4}{\textbf{39.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.1\%}}\\
-\addlinespace
 \textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-19.47\%}}}\\
 \textbf{Gasoline (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.14\%}} & \textcolor[HTML]{4285f4}{\textbf{44.13\%}} & \textcolor[HTML]{4285f4}{\textbf{47.11\%}} & \textcolor[HTML]{4285f4}{\textbf{41.71\%}}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.44\%}}}\\
+\textbf{Heating oil (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.16\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-21.62\%}}}\\
-\addlinespace
 \textbf{Heating oil (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.98\%}} & \textcolor[HTML]{4285f4}{\textbf{39.16\%}} & \textcolor[HTML]{4285f4}{\textbf{35.69\%}}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.1\%}}}\\
+\addlinespace
+\textbf{Copper (XCEC)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.1\%}}}\\
@@
 \addlinespace
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.53\%}}}\\
+\textbf{Gold (XCEC)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
 \textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.21\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.1\%}}}\\
+\addlinespace
 \textbf{Gold (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}} & \textcolor[HTML]{4285f4}{\textbf{25.21\%}} & \textcolor[HTML]{4285f4}{\textbf{16.23\%}}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.75\%}}}\\
+\textbf{Palladium (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
 \textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**49.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**31.93\%}}}\\
-\addlinespace
 \textbf{Palladium (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.49\%}} & \textcolor[HTML]{4285f4}{\textbf{23.82\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.88\%}}}\\
 \textbf{Palladium (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{41.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.2\%}} & \textcolor[HTML]{4285f4}{\textbf{38.71\%}} & \textcolor[HTML]{4285f4}{\textbf{26.8\%}}\\
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.92\%}}}\\
+\textbf{Platinum (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
 \textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*25.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.17\%}}}\\
+\addlinespace
 \textbf{Platinum (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.1\%}} & \textcolor[HTML]{4285f4}{\textbf{22.51\%}} & \textcolor[HTML]{4285f4}{\textbf{21.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.04\%}}\\
-\addlinespace
 \textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.28\%}}}\\
 \textbf{Platinum (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23.12\%}} & \textcolor[HTML]{4285f4}{\textbf{22.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.75\%}} & \textcolor[HTML]{4285f4}{\textbf{20.8\%}}\\
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.43\%}}}\\
+\textbf{Silver (XCEC)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.44\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.09\%}}}\\
-\addlinespace
 \textbf{Silver (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.93\%}} & \textcolor[HTML]{4285f4}{\textbf{35.34\%}} & \textcolor[HTML]{4285f4}{\textbf{42.44\%}} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}}\\
+\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.15\%}}}\\
+\addlinespace
+\textbf{Aluminium (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
 \textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**23.68\%}}}\\
@@
 \addlinespace
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**28.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.03\%}}}\\
+\textbf{Copper (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.99\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.89\%}}}\\
+\addlinespace
 \textbf{Copper (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{41.31\%}} & \textcolor[HTML]{4285f4}{\textbf{19.86\%}}\\
+\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}}\\
+\textbf{Lead (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
 \textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.05\%}}}\\
-\addlinespace
 \textbf{Lead (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.16\%}} & \textcolor[HTML]{4285f4}{\textbf{39.91\%}} & \textcolor[HTML]{4285f4}{\textbf{35.35\%}} & \textcolor[HTML]{4285f4}{\textbf{23.37\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*46.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-13.41\%}}}\\
 \textbf{Lead (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.12\%}} & \textcolor[HTML]{4285f4}{\textbf{43.16\%}} & \textcolor[HTML]{4285f4}{\textbf{46.22\%}} & \textcolor[HTML]{4285f4}{\textbf{23.09\%}}\\
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.31\%}}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
 \textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-39.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**35.09\%}}}\\
+\addlinespace
 \textbf{Nickel-primary (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.23\%}} & \textcolor[HTML]{4285f4}{\textbf{41.62\%}} & \textcolor[HTML]{4285f4}{\textbf{34.48\%}} & \textcolor[HTML]{4285f4}{\textbf{29.13\%}}\\
-\addlinespace
 \textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**63.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**-34.64\%}}}\\
 \textbf{Nickel-primary (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.28\%}} & \textcolor[HTML]{4285f4}{\textbf{46.72\%}} & \textcolor[HTML]{4285f4}{\textbf{47.44\%}} & \textcolor[HTML]{4285f4}{\textbf{28.6\%}}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.68\%}}}\\
+\textbf{Tin-refined (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.48\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.69\%}}}\\
-\addlinespace
 \textbf{Tin-refined (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.77\%}} & \textcolor[HTML]{4285f4}{\textbf{32.08\%}} & \textcolor[HTML]{4285f4}{\textbf{41.13\%}} & \textcolor[HTML]{4285f4}{\textbf{21.68\%}}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.07\%}}}\\
+\addlinespace
+\textbf{Zinc (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
 \textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.05\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.42\%}}}\\
@@
 \addlinespace
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**15.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.18\%}}}\\
+\textbf{US commodities} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
 \textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{***15.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.82\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*16.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.33\%}}}\\
+\addlinespace
 \textbf{US commodities} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*21.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.72\%}}}\\
+\textbf{GB commodities} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
 \textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**19.95\%}}}\\
-\addlinespace
 \textbf{GB commodities} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-14.05\%}}}\\
@@
 \endgroup{}
+
+\newpage
 

### 2024-09-27 docs/paper.tex

@@
 includes factors constructed using both theoretical and liquidity
-considerations and use this framework to carry out our analysis over
-four periods of interest. The first, the pre-financialisation period,
-starts in 1997 and is naturally followed by financialisation, spanning
-the 2004/2008 period, and the financial crisis and its aftermath,
-spanning the 2008/2013 period. The last period spans the 2014/2018
-period starting with the beginning of the tapering/end of the US
-Quantitative Easing program (QE).\\
-Using the weekly price, open interest and market position data described
-above we construct market portfolios of individual commodity nearby
-futures as well as mimicking portfolios for market, commercial hedging
-pressure, term structure and liquidity risk factors in returns. While
-our market portfolios are long only, equally weighted portfolios of
-particular commodity sets, our other mimicking portfolios for risk
-factors are constructed as combinations of two sub-portfolios (legs),
-one held long, one held short, which respective constituents are pooled
-on a weekly basis according to risk factor specific criteria.\\
-For each leg, the position weight for a particular asset for a
-particular period is contingent on the value of the corresponding
-sorting variable and its rank relative to the other assets in the pool.
-The sorting variable values for the asset pool are first rescaled so
-that the highest (lowest) value becomes 1 (0). Weights are then
-determined pairwise, starting from the extremes with the highest and
-lowest figures. A coefficient \(\alpha\) is determined by dividing their
-difference (1 in this case) by the mean of the rescaled values. The high
-figure is attributed a score of \(\frac{1}{n} \times \alpha\) where
-\(n\) is the number of assets in the pool while the score for the low
-figure is \(\frac{1/n}{\alpha}\). The operation is repeated for the pair
-of assets showing the second highest and second lowest values for the
-sorting variable and so on until all the assets in the pool are
-attributed a score. The individual asset weights are then determined by
-dividing each score by the sum of the scores.\\
-The period return for a particular mimicking portfolio is calculated as
-the difference between the weighted average return for constituents of
-the long portfolio and that for the constituents of the short portfolio.
+considerations. Using the weekly returns, open interest and market
+position data described above we construct market portfolios of
+individual commodity nearby futures as well as mimicking portfolios for
+market, commercial hedging pressure, term structure and liquidity risk
+factors in returns. While our market portfolios are long only
+combinations of particular commodity sets, our other mimicking
+portfolios for risk factors are constructed as combinations of two
+sub-portfolios (legs), one held long, one held short, which respective
+constituents are pooled on a weekly basis according to risk factor
+specific criteria.\\
+All portfolios are equally weighted and returns for the two-legged
+factors are calculated as the difference between the average return for
+constituents of the long leg and that for the constituents of the short.
 i.e, return on the mimicking portfolio for risk factor \(i\) (\(f_{i}\))
@@
 
-We use a time series regression approach where we start with regressions
-of the US traded individual commodity weekly front contract returns on
-returns to the mimicking portfolio for a particular risk factor where
-the portfolio is constructed using the whole cross-section of US traded
-commodities. The corresponding \(R^{2}\)s are averaged and the process
-is repeated for each of our four risk factors (market, hedging pressure,
-term structure and liquidity) and periods (1997/2003, 2004/2008,
-2008/2013 and 2014/2018). For the long-short factors the results are
-reported independently for models where the regressor is the factor
-itself or one of its legs (long vs.~short). The same operation is
-repeated for the two (\(p=2\)) and three (\(p=3\)) factor model cases,
-where regressors include in turn all combinations of any two and three
-risk factors respectively, as well as for the four (\(p=4\)) factor
-model case where all the risk factor mimicking portfolios are included.
-Results are reported for the one-factor model case with the other
-results available upon request.
-
-\medskip
-
-For each period we also implement the analysis described above over
-periods of low and high aggregate CHP (\textbf{CHP}), a notion that we
-believe is particularly relevant in the context of financialisation
-where issues of co-movement and aggregate market behaviour play a
-central role. We define \textbf{CHP} as the cross-sectional average of
-individual CHPs for a particular pool of assets. i.e., period \(t\)
-\textbf{CHP} for asset pool \(x\):
-
-\[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}\] \(n\equiv\)
-number of commodities in set \(x\).\\
+We use a time series regression approach where individual commodity
+weekly front futures contract returns are regressed on returns to the
+mimicking portfolio for a particular risk factor with the corresponding
+\(\beta\)s and \(R^{2}\)s averaged. For the long-short factors the
+\(\beta\)s and \(R^{2}\)s are computed for models where the regressor is
+the factor itself as well as both its long and short legs independently
+(results available upon request).
+
+For each time period considered in the study, being one of the four
+multi-year periods described above or any individual year over the
+entire sample time period, we carry out our analysis over the entire
+period as well as over phases of low and high aggregate CHP
+(\textbf{CHP}) over the period; a notion that we believe is particularly
+relevant in the context of financialisation where issues of co-movement
+and aggregate market behaviour play a central role. We define
+\textbf{CHP} as the cross-sectional average of individual CHPs for a
+particular pool of assets. i.e., period \(t\) \textbf{CHP} for asset
+pool \(x\): \[\mathbf{CHP}_{t}^{x}=\frac{1}{n}\sum_{j=1}^{n}CHP_{j,t}\]
+\(n\equiv\) number of commodities in set \(x\).\\
 \(CHP_{i,t}\equiv\) period \(t\) CHP for commodity \(i\) as defined
@@
 contango (\textbf{contango}) \textbf{CHP} regimes as, for a given
-period, \textbf{CHP} levels below and above the period's median
-respectively and, in contrast with \citep{hong_what_2012} who aggregate
-across sub-sectors, the asset pool we consider for \textbf{CHP}
-construction include the whole cross-section of US traded commodities.
-
-\medskip
-
-In the next part of the analysis, our mimicking portfolios for risk
-factors, constructed from the set of all US traded commodities are used
-as commodity picking devices on the latter commodity set. For each risk
-factor and period, individual US traded commodity front returns are
-regressed on returns for the corresponding mimicking portfolio.
-Individual commodities are sorted by \(R^{2}\) accordingly from highest
-to lowest and the top third (highest \(R^{2}\)s) are selected as
-commodity picks for the risk factor for the period. i.e, set of picks
-\(P_{t}^{f_{i}}\) for risk factor \(i\) (\(f_{i}\)) over period \(t\):
-
-\[P_{t}^{f_{i}}\equiv\left \{ P_{1}, P_{2}, ..., P_{x} \right \}\]
-\(x = n \cdot s\).\\
-\(n\equiv\) number of commodities in the set considered for the picking
-exercise (twenty-four here).\\
-\(s\equiv\) selection threshold (\(\frac{1}{3}\) here).\\
-\(P_{j}\equiv\) commodity pick \(j\) for risk factor \(f_{i}\) over
-period \(t\)\\
-\(j\equiv\) rank in the ordered set \(Y_{t}^{f_{i}}\)\\
-\[Y_{t}^{f_{i}}\equiv\left \{ \left \{ \tilde{R_{1}^{2}}, \tilde{R_{2}^{2}}, ..., \tilde{R_{n}^{2}} \right \}, \geq \right \}\]
-\(n\equiv\) number of commodities in the set considered for picking
-(twenty-four here).\\
-\(\tilde{R_{j}^{2}}\equiv\) risk factor \(f_{i}\) returns' explanatory
-power on commodity \(j\) nearby futures returns over period \(t\) as
-defined above.
-
-\medskip
-
-For each period we report the proportion of time each pick is held in
-the long and (/or) short leg of the corresponding risk factor mimicking
-portfolio as well as the average pairwise correlation amongst every set
-of picks.
-
-\medskip
-
-In the last part of the analysis, for each period our mimicking
-portfolios for risk factors in returns are constructed using each set of
-commodity picks independently as the asset pool for portfolio
-construction. A similar time series approach to that described above is
-then implemented using these newly formed mimicking portfolios. In this
-case, a first set of dependent variables includes the sets of commodity
-picks themselves, a second set includes the whole cross-section of US
-traded commodities while a third set includes the six UK traded metals
-considered in the study.
+period, sub-periods with \textbf{CHP} levels below and above the
+period's median respectively and, in contrast with
+\citep{hong_what_2012} who aggregate across sub-sectors, our
+\textbf{CHP} construction draws on the full cross-section of US-traded
+assets considered in the study.
 
@@
 
-Table~\ref{tbl-stats-no-regimes} displays descriptive statistics for the
+Table~\ref{tbl-stats-combined} displays descriptive statistics for the
 commodity series considered in the study; the results show a clear
@@
 that returns for individual commodities should be high in periods where
-\textbf{CHP} is low and vice et versa. In Table~\ref{tbl-stats-regimes}
-the mean returns are shown over high (\textbf{contango}) and low
-(\textbf{backwardation}) \textbf{CHP} regimes for each time period.\\
+\textbf{CHP} is low and vice et versa. Table~\ref{tbl-stats-combined}
+further shows the mean returns and volatilities for high
+(\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP}
+regimes for each time period.\\
 Over the first period eighteen of the twenty-four US commodities have
@@
 
-Financialisation was a global phenomenon that, through the channel of
-index investment, simultaneously influenced the entire spectrum of
-liquid commodities. This sweeping impact spurred the transformation of
+Financialisation was a global phenomenon, through the channel of index
+investment it simultaneously influenced the entire spectrum of liquid
+commodities; this sweeping impact spurred the transformation of
 commodity markets from a collection of idiosyncratic markets into a
@@
 that warrants thorough examination.\\
-We set out to address this issue by first examining the average of
-weekly pairwise correlations between commodities across the entire
+We strive to address this issue by first examining the average of weekly
+returns pairwise correlations between commodities across the entire
 cross-section of the commodity assets considered in the study as well as
@@
 average pairwise correlation jumps from 0.07 in the first period to 0.16
-over financialisation. These findings indicate higher interdependence
+over financialisation. This finding indicate higher interdependence
 within the full cross-section of commodities starting with the
@@
 smaller percentage increase during financialisation relative to the past
-period. These findings thus suggest that the US metals sector was the
+period. These results thus suggest that the US metals sector was the
 driving force behind increased average pairwise correlations during
@@
 phase driven phenomenon in the same way that individual commodity
-returns are, as demonstrated in Table~\ref{tbl-stats-regimes}.\\
+returns are, as demonstrated in Table~\ref{tbl-stats-combined}.\\
 We further examine these correlations by year in
@@
 other commodities should lead to an increase in its beta relative to the
-market factor portfolio. We therefore regress the weekly individual
+market factor portfolio. We accordingly regress the weekly individual
 commodity front futures returns against those for our market factor
@@
 financialisation period, even beyond that for the US agricultural sector
-of 0.80. In contrast, the corresponding figures for the energy sector
+of 0.80. In contrast, the corresponding figure for the energy sector
 show a substantial decrease, down to 1.61 during financialisation from
@@
 corresponding figure increases from less than 2\%, or virtually no
-explanatory power for the (US based) market factor to almost 12\% over
+explanatory power for the (US based) market factor, to almost 12\% over
 the financialisation period. The results for our other risk factor
@@
 slight decrease and a much smaller increase for the open interest and
-term structure factors respectively. Here again the dramatic increase in
-pricing performance for the CHP factor is driven by the metals sector,
+term structure factors respectively. Here again the increase in pricing
+performance for the CHP factor is driven by the metals sector,
 particularly the precious sub-sector with the average \(R^{2}\) for the
@@
 smaller increase, up to 8.9\% from 3.3\% over the past period.
-Interestingly, although the factor itself only sees a very modest
-increase, its short leg (low roll-yield assets: Working's backwardation)
-shows a sizeable rise in pricing performance, yet again driven the
-metals sector, with the average \(R^{2}\) for the group's US traded
-assets jumping to 28.2\% during financialisation from 6.2\% over the
-past period. The pattern of results for both factors extends to the GB
-trade assets and suggest a convergence of Keneysian and Working's term
-structure perspective over the financialisation period.\\
+Interestingly, although the term structure factor itself only sees a
+very modest increase, its short leg (low roll-yield assets: Working's
+backwardation) shows a sizeable rise in pricing performance, yet again
+driven the metals sector, with the average \(R^{2}\) for the group's US
+traded assets jumping to 28.2\% during financialisation from 6.2\% over
+the past period. The pattern of results for both factors extends to the
+GB trade assets and suggest a convergence of Keneysian and Working's
+term structure perspective over the financialisation period.\\
 Taken together these results emphasise the global nature of the impact
@@
 term structure factor built on the Working paradigm and these findings
-therefore appear to complement the results of Kang et al.~(2020) who
+therefore appear to complement the results of \citet{kang_tale_2020} who
 find that hedging pressure both conveys information about liquidity
@@
 results. Returns fall sharply relative to the financialisation period
-(Table~\ref{tbl-stats-no-regimes}) with eighteen US commodities along
-with all six GB traded metals showing lower mean returns. Returns for
-equally weighted portfolios of both sets of assets fall down to 9.4\%
-and 5.3\% from 15.9\% and 21.8\% respectively. Returns are mostly higher
-during phases of \textbf{backwardation} relative to \textbf{contango}
-(Table~\ref{tbl-stats-regimes}) with fifteen US assets and five of the
-GB traded metals showing higher mean returns in \textbf{backwardation}
-and the pattern extending to equally weighted portfolios of the two sets
-of assets. Volatility is moderately higher for both sets with fifteen US
-commodities and three GB metals showing higher figures and interestingly
-eminently higher over phases of \textbf{contango}; out of the US complex
-only Sugar-\#11 (IFUS) and none of the GB traded metals show higher
-volatility figures over \textbf{backwardation} phases. The symmetry
-between the dynamics of CHP and \textbf{CHP}'s explanatory power on
-individual commodity returns breaks in the crisis period
-(Table~\ref{tbl-time-reg-US-CHP}) with both now seemingly converging;
-the US cross-sectional average \(R^{2}\) at the individual level
-bouncing back up (22.5\% vs 20.8\%) while that at the aggregate level
-rises further (14.7\% vs 7.1\%).
-
-// TODO Add correlation results discussion here.
-
-The performance of the market factor dominates the US commodity complex
-over the period with a 50\% increase in mean average \(R^{2}\) to over
-30\% (Table~\ref{tbl-regressions-factors}) while that of the CHP factor
-decreases and, although increasing, remains modest for the open interest
-growth and term structure factors. Taken together, these results
-indicate the presence of a systematic factor across the entire
-cross-section of the US commodities.
+(Table~\ref{tbl-stats-combined}) with eighteen US commodities along with
+all six GB traded metals showing lower mean returns. Returns for equally
+weighted portfolios of both sets of assets fall down to 9.4\% and 5.3\%
+from 15.9\% and 21.8\% respectively. Returns are mostly higher during
+phases of \textbf{backwardation} relative to \textbf{contango} with
+fifteen US assets and five of the GB traded metals showing higher mean
+returns in \textbf{backwardation} and the pattern extending to equally
+weighted portfolios of the two sets of assets. Volatility is moderately
+higher for both sets with fifteen US commodities and three GB metals
+showing higher figures and interestingly eminently higher over phases of
+\textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none
+of the GB traded metals show higher volatility figures over
+\textbf{backwardation} phases. The symmetry between the dynamics of CHP
+and \textbf{CHP}'s explanatory power on individual commodity returns
+breaks in the crisis period (Table~\ref{tbl-time-reg-US-CHP}) with both
+now seemingly converging; the US cross-sectional average \(R^{2}\) at
+the individual level bouncing back up (22.5\% vs 20.8\%) while that at
+the aggregate level rises further (14.7\% vs 7.1\%).
 
@@
 
+The average pairwise correlation for the entire cross-section of
+commodities considered in the study
+(Table~\ref{tbl-correlations-periods}) increases further into the crisis
+to 0.28 indicating an intensification of the higher interdependence
+within the full cross-section of commodities prompted by
+financialisation. The result is consistent with the greater
+interdependence between equity and commodity markets over this period
+documented in \citet{silvennoinen_financialisation_2013}. The figure for
+the US traded section of the metals sector only progresses modestly to
+0.59 after peaking at 0.63 in 2006 (Table~\ref{tbl-correlations-years}).
+In contrast, the GB traded assets see a sharp increase to over 0.65 in
+the crisis starting in 2007 up to a peak of 0.69 in 2010. The
+agricultural sector on the other hand shows a substantial rise in the
+crisis period with the sharpest increase in 2008 when the average
+pairwise correlation for the sector jumps to 0.30. Meanwhile, the energy
+sector also shows a notable progression starting in 2007 and peaking at
+0.63 in 2008 before levelling back down over the rest of the period. The
+onset of the financial crisis seems therefore to have had an across the
+board impact on the interdependence of commodities in contrast with
+financialisation, much more closely related to the metals sector.
+
+\medskip
+
+The entire cross-section sees an increase in average regression
+coefficient relative to the market factor over the crisis period with
+the strongest progression for the GB traded metals followed by the
+agricultural sector (Table~\ref{tbl-regressions-index}). The pricing
+performance of the factor dominates the US commodity complex over the
+period (Table~\ref{tbl-regressions-factors}), showing a 50\% increase in
+mean average \(R^{2}\) to over 31\%, while that for both the CHP and
+open interest factor decreases and, although increasing, remains modest
+for the term structure factors; the increase is strongest for the GB
+traded metal assets with an average \(R^{2}\) of almost 34\% for the
+period. Taken together, these results indicate the presence of a
+systematic factor across the entire cross-section of the US commodities.
+For both the CHP and term structure factors, both legs show an increase
+in average \(R^{2}\) and while substantially diverging over the
+preceding financialisation period the pricing performance for both legs
+seems to converge back to a pattern closer to that observed
+pre-financialisation.
+
+\bigskip
+\bigskip
+
 The returns pull-back continues into the post-crisis period
-(Table~\ref{tbl-stats-no-regimes}) with twenty-two US and four UK traded
+(Table~\ref{tbl-stats-combined}) with twenty-two US and four UK traded
 assets showing lower mean returns relative to the crisis while the same
@@
 paradigm initiated during the crisis continues stronger into the
-post-crisis period (Table~\ref{tbl-stats-regimes}) with mean returns
-higher during phases of \textbf{backwardation} relative to
-\textbf{contango}, more so than over the crisis period with seventeen US
-commodities showing higher mean returns over \textbf{backwardation}
-phases. The difference is significant at the 5\% level for Lumber (XCME)
-and at the 10\% level for Palladium (XNYM) while no difference is
-significant for the assets showing higher figures over phases of
-\textbf{contango}. The pattern is more pronounced for the UK traded
-subset with all six assets showing higher mean returns in
-\textbf{backwardation} with the difference significant at the 1\% level
-for Nickel-primary (XLME), 5\% level for Aluminium (XLME) and 10\% level
-for Zinc (XLME). It also extends to equally weighted portfolios of US
-and UK traded assets that both show higher mean returns during
-\textbf{backwardation} with the difference significant at the 5\% level
-for the UK portfolio and the figure close to the 10\% level significance
-threshold for the portfolio of US assets. Volatilities are overall
-higher in \textbf{contango} although less so than over the previous
-period with seventeen US commodities showing higher figures over
-\textbf{contango} against twenty-three in the crisis period. The pattern
-extends to three of the six UK traded metals with the difference
-significant at the 1\% level for Copper (XLME) and Tin (XLME) and at the
-5\% level for Zinc (XLME) while differences are not significant for
-Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit
-higher volatility over \textbf{backwardation} phases. Equally weighted
-portfolios of US and UK traded assets on the other hand both show higher
-volatility in \textbf{contango} with the difference significant at the
-1\% level for both. Over the financialisation period in contrast
-volatilities were predominantly higher in \textbf{backwardation} for US
-traded assets with fourteen commodities showing higher volatility
-figures in these phases; the post-crisis pattern of results for
-volatilities thus likewise shows signs of reversion to
-pre-financialisation standards. After showing signs of convergence in
-the crisis period the dynamics of the explanatory power of CHP and
-\textbf{CHP} part ways (Table~\ref{tbl-time-reg-US-CHP}), seemingly
-reverting to the Keynesian paradigm observed pre-financialisation,
-further suggesting a return to legacy commodity specific dynamics. The
-recovery initiated in the crisis period for that of CHP is confirmed
-with a stronger increase in the post-crisis period, 27.2\% vs.~22.5\%,
-strongest for the metals sector, 37.3\% vs.~23.7\%, while the energy
-sector shows the opposite pattern: 11\% vs.~16\%. In contrast, after
-increasing stronger in the crisis, that for \textbf{CHP} falls overall
-in the post-crisis period, 7.5\% vs 14.7\%, with the decrease strongest
-for the energy sector in a relative sense: 2.5\% vs.~14.8\%.
+post-crisis period with mean returns higher during phases of
+\textbf{backwardation} relative to \textbf{contango}, more so than over
+the crisis period with seventeen US commodities showing higher mean
+returns over \textbf{backwardation} phases. The difference is
+significant at the 5\% level for Lumber (XCME) and at the 10\% level for
+Palladium (XNYM) while no difference is significant for the assets
+showing higher figures over phases of \textbf{contango}. The pattern is
+more pronounced for the UK traded subset with all six assets showing
+higher mean returns in \textbf{backwardation} with the difference
+significant at the 1\% level for Nickel-primary (XLME), 5\% level for
+Aluminium (XLME) and 10\% level for Zinc (XLME). It also extends to
+equally weighted portfolios of US and UK traded assets that both show
+higher mean returns during \textbf{backwardation} with the difference
+significant at the 5\% level for the UK portfolio and the figure close
+to the 10\% level significance threshold for the portfolio of US assets.
+Volatilities are overall higher in \textbf{contango} although less so
+than over the previous period with seventeen US commodities showing
+higher figures over \textbf{contango} against twenty-three in the crisis
+period. The pattern extends to three of the six UK traded metals with
+the difference significant at the 1\% level for Copper (XLME) and Tin
+(XLME) and at the 5\% level for Zinc (XLME) while differences are not
+significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME)
+that exhibit higher volatility over \textbf{backwardation} phases.
+Equally weighted portfolios of US and UK traded assets on the other hand
+both show higher volatility in \textbf{contango} with the difference
+significant at the 1\% level for both. Over the financialisation period
+in contrast volatilities were predominantly higher in
+\textbf{backwardation} for US traded assets with fourteen commodities
+showing higher volatility figures in these phases; the post-crisis
+pattern of results for volatilities thus likewise shows signs of
+reversion to pre-financialisation standards. After showing signs of
+convergence in the crisis period the dynamics of the explanatory power
+of CHP and \textbf{CHP} part ways (Table~\ref{tbl-time-reg-US-CHP}),
+seemingly reverting to the Keynesian paradigm observed
+pre-financialisation, further suggesting a return to legacy commodity
+specific dynamics. The recovery initiated in the crisis period for that
+of CHP is confirmed with a stronger increase in the post-crisis period,
+27.2\% vs.~22.5\%, strongest for the metals sector, 37.3\% vs.~23.7\%,
+while the energy sector shows the opposite pattern: 11\% vs.~16\%. In
+contrast, after increasing stronger in the crisis, that for \textbf{CHP}
+falls overall in the post-crisis period, 7.5\% vs 14.7\%, with the
+decrease strongest for the energy sector in a relative sense: 2.5\%
+vs.~14.8\%.
 
@@
 
-\begin{longtable}[t]{>{}l>{}l>{}r>{}r>{}r>{}r}
-
-\caption{\label{tbl-stats-no-regimes}This table shows mean returns and
-volatility (sd) for the twenty four individual US commodities and the
-six GB metals considered in the study as well as for two equally
-weighted portfolios formed from the US commodities and the GB metals
-respectively across the four periods of interest (past: 1997-2003;
-financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-stats-combined}This table shows mean returns and
+volatility for the twenty four individual US commodities and the six GB
+metals considered in the study as well as for two equally weighted
+portfolios formed from the US commodities and the GB metals respectively
+across the four periods of interest (past: 1997-2003; financialisation:
+2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). for each period
+the figures are shown independently for the entire period as well as for
+phases of aggregate backwardation (aggregate CHP \(\leq\) period median)
+and aggregate contango (aggregate CHP \textgreater{} period median).
 Mean values significant at the 1\%, 5\% and 10\% level are marked with
-***, ** and * respectively. The results are discussed in section
-Section~\ref{sec-results}.}
-
-\tabularnewline
-
-\toprule
-\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
-\midrule
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
-\addlinespace
-\textbf{Soybean meal (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
-\textbf{Soybeans (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}}\\
-\addlinespace
-\textbf{Cattle-live (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.65\%}}}\\
-\textbf{Cocoa (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.99\%}}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
-\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.06\%}}}\\
-\addlinespace
-\textbf{Lumber (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
-\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.8\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.16\%}}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.33\%}}}\\
-\textbf{Natural gas (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.64\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.37\%}}}\\
-\addlinespace
-\textbf{Gasoline (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.44\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.1\%}}}\\
-\textbf{Copper (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.53\%}}}\\
-\textbf{Gold (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.75\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.92\%}}}\\
-\addlinespace
-\textbf{Platinum (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.43\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
-\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.15\%}}}\\
-\textbf{Aluminium (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**28.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.03\%}}}\\
-\textbf{Copper (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
-\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}}\\
-\textbf{Lead (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.31\%}}}\\
-\addlinespace
-\textbf{Nickel-primary (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.68\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.07\%}}}\\
-\textbf{Zinc (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**15.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.18\%}}}\\
-\textbf{US commodities} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*21.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.72\%}}}\\
-\textbf{GB commodities} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
-\bottomrule
-
-\end{longtable}
-
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{7}{9}\selectfont
-
-\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
-
-\caption{\label{tbl-stats-regimes}This table shows mean returns and
-volatility (sd) for the twenty four individual US commodities and the
-six GB metals considered in the study as well as for two equally
-weighted portfolios formed from the US commodities and the GB metals
-respectively across the four periods of interest (past: 1997-2003;
-financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Figures are shown independently for phases of aggregate backwardation
-(aggregate CHP \(\leq\) period median) and aggregate contango (aggregate
-CHP \textgreater{} period median). Mean values significant at the 1\%,
-5\% and 10\% level are marked with ***, ** and * respectively. Aggregate
-CHP construction and corresponding regime definitions are discussed in
-section Section~\ref{sec-methods} while the results are discussed in
-section Section~\ref{sec-results}.}
+***, ** and * respectively. Aggregate CHP construction and corresponding
+regime definitions are discussed in Section~\ref{sec-methods} while the
+results are discussed in Section~\ref{sec-results}.}
 
@@
 \midrule
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
 \textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.74\%}}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23.07\%}} & \textcolor[HTML]{4285f4}{\textbf{29.14\%}} & \textcolor[HTML]{4285f4}{\textbf{31.59\%}} & \textcolor[HTML]{4285f4}{\textbf{21\%}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.07\%}} & \textcolor[HTML]{4285f4}{\textbf{29.14\%}} & \textcolor[HTML]{4285f4}{\textbf{31.59\%}} & \textcolor[HTML]{4285f4}{\textbf{21\%}}\\
 \textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.78\%}}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
+\addlinespace
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
+\textbf{Oats (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
 \textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
-\addlinespace
-\textbf{Oats (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
+\textbf{Oats (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.17\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
+\textbf{Oats (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
 \textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.52\%}}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
-\addlinespace
+\addlinespace
+\textbf{Soybean meal (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
 \textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.44\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.35\%}} & \textcolor[HTML]{4285f4}{\textbf{28.94\%}} & \textcolor[HTML]{4285f4}{\textbf{22.33\%}} & \textcolor[HTML]{4285f4}{\textbf{18.19\%}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.35\%}} & \textcolor[HTML]{4285f4}{\textbf{28.94\%}} & \textcolor[HTML]{4285f4}{\textbf{22.33\%}} & \textcolor[HTML]{4285f4}{\textbf{18.19\%}}\\
 \textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.12\%}}}\\
-\addlinespace
-\textbf{Soybean oil (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
+\addlinespace
+\textbf{Soybeans (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
 \textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.45\%}}}\\
-\textbf{Soybeans (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.93\%}} & \textcolor[HTML]{4285f4}{\textbf{34.58\%}} & \textcolor[HTML]{4285f4}{\textbf{24.39\%}} & \textcolor[HTML]{4285f4}{\textbf{22.04\%}}\\
+\textbf{Soybeans (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.93\%}} & \textcolor[HTML]{4285f4}{\textbf{34.58\%}} & \textcolor[HTML]{4285f4}{\textbf{24.39\%}} & \textcolor[HTML]{4285f4}{\textbf{22.04\%}}\\
 \textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}}\\
-\textbf{Soybeans (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.09\%}} & \textcolor[HTML]{4285f4}{\textbf{24.74\%}} & \textcolor[HTML]{4285f4}{\textbf{31.11\%}} & \textcolor[HTML]{4285f4}{\textbf{20.56\%}}\\
-\addlinespace
+\textbf{Soybeans (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.09\%}} & \textcolor[HTML]{4285f4}{\textbf{24.74\%}} & \textcolor[HTML]{4285f4}{\textbf{31.11\%}} & \textcolor[HTML]{4285f4}{\textbf{20.56\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
 \textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.44\%}}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{36\%}} & \textcolor[HTML]{4285f4}{\textbf{37.53\%}} & \textcolor[HTML]{4285f4}{\textbf{26.57\%}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{36\%}} & \textcolor[HTML]{4285f4}{\textbf{37.53\%}} & \textcolor[HTML]{4285f4}{\textbf{26.57\%}}\\
 \textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.77\%}}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.04\%}} & \textcolor[HTML]{4285f4}{\textbf{29.84\%}} & \textcolor[HTML]{4285f4}{\textbf{37.73\%}} & \textcolor[HTML]{4285f4}{\textbf{26.72\%}}\\
+\addlinespace
+\textbf{Wheat-SRW (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.04\%}} & \textcolor[HTML]{4285f4}{\textbf{29.84\%}} & \textcolor[HTML]{4285f4}{\textbf{37.73\%}} & \textcolor[HTML]{4285f4}{\textbf{26.72\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**20.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.58\%}}}\\
-\addlinespace
-\textbf{Cattle-feeder (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}} & \textcolor[HTML]{4285f4}{\textbf{14.93\%}} & \textcolor[HTML]{4285f4}{\textbf{13.39\%}} & \textcolor[HTML]{4285f4}{\textbf{20.14\%}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}} & \textcolor[HTML]{4285f4}{\textbf{14.93\%}} & \textcolor[HTML]{4285f4}{\textbf{13.39\%}} & \textcolor[HTML]{4285f4}{\textbf{20.14\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.12\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.67\%}} & \textcolor[HTML]{4285f4}{\textbf{15.35\%}} & \textcolor[HTML]{4285f4}{\textbf{16.91\%}} & \textcolor[HTML]{4285f4}{\textbf{17.23\%}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.67\%}} & \textcolor[HTML]{4285f4}{\textbf{15.35\%}} & \textcolor[HTML]{4285f4}{\textbf{16.91\%}} & \textcolor[HTML]{4285f4}{\textbf{17.23\%}}\\
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}}\\
+\textbf{Cattle-live (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.07\%}}}\\
-\textbf{Cattle-live (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.65\%}} & \textcolor[HTML]{4285f4}{\textbf{17.91\%}} & \textcolor[HTML]{4285f4}{\textbf{14.97\%}} & \textcolor[HTML]{4285f4}{\textbf{19.9\%}}\\
-\addlinespace
+\addlinespace
+\textbf{Cattle-live (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.65\%}} & \textcolor[HTML]{4285f4}{\textbf{17.91\%}} & \textcolor[HTML]{4285f4}{\textbf{14.97\%}} & \textcolor[HTML]{4285f4}{\textbf{19.9\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
-\textbf{Cattle-live (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.49\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}} & \textcolor[HTML]{4285f4}{\textbf{17.57\%}} & \textcolor[HTML]{4285f4}{\textbf{16.66\%}}\\
+\textbf{Cattle-live (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.49\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}} & \textcolor[HTML]{4285f4}{\textbf{17.57\%}} & \textcolor[HTML]{4285f4}{\textbf{16.66\%}}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}}\\
+\textbf{Lean hogs (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.23\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.24\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{37.6\%}} & \textcolor[HTML]{4285f4}{\textbf{35.73\%}} & \textcolor[HTML]{4285f4}{\textbf{27.83\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}}\\
+\textbf{Lean hogs (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{37.6\%}} & \textcolor[HTML]{4285f4}{\textbf{35.73\%}} & \textcolor[HTML]{4285f4}{\textbf{27.83\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}}\\
 \textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.66\%}}}\\
-\addlinespace
-\textbf{Lean hogs (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.22\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}} & \textcolor[HTML]{4285f4}{\textbf{32.78\%}} & \textcolor[HTML]{4285f4}{\textbf{38.28\%}}\\
+\textbf{Lean hogs (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.22\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}} & \textcolor[HTML]{4285f4}{\textbf{32.78\%}} & \textcolor[HTML]{4285f4}{\textbf{38.28\%}}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.65\%}}}\\
+\addlinespace
+\textbf{Cocoa (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
 \textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.98\%}}}\\
-\textbf{Cocoa (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{33.57\%}} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}}\\
+\textbf{Cocoa (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.57\%}} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}}\\
 \textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.29\%}}}\\
-\textbf{Cocoa (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{31.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.91\%}} & \textcolor[HTML]{4285f4}{\textbf{34.66\%}} & \textcolor[HTML]{4285f4}{\textbf{23.57\%}}\\
-\addlinespace
+\textbf{Cocoa (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.91\%}} & \textcolor[HTML]{4285f4}{\textbf{34.66\%}} & \textcolor[HTML]{4285f4}{\textbf{23.57\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.99\%}}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
 \textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.36\%}}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{48.82\%}} & \textcolor[HTML]{4285f4}{\textbf{32.6\%}} & \textcolor[HTML]{4285f4}{\textbf{29.92\%}} & \textcolor[HTML]{4285f4}{\textbf{31.52\%}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{48.82\%}} & \textcolor[HTML]{4285f4}{\textbf{32.6\%}} & \textcolor[HTML]{4285f4}{\textbf{29.92\%}} & \textcolor[HTML]{4285f4}{\textbf{31.52\%}}\\
 \textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.24\%}}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.22\%}} & \textcolor[HTML]{4285f4}{\textbf{32.24\%}}\\
+\addlinespace
+\textbf{Coffee-C (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.22\%}} & \textcolor[HTML]{4285f4}{\textbf{32.24\%}}\\
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
 \textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.84\%}}}\\
-\addlinespace
-\textbf{Cotton-\#2 (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.02\%}} & \textcolor[HTML]{4285f4}{\textbf{29.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.94\%}} & \textcolor[HTML]{4285f4}{\textbf{21.33\%}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.02\%}} & \textcolor[HTML]{4285f4}{\textbf{29.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.94\%}} & \textcolor[HTML]{4285f4}{\textbf{21.33\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.91\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.77\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.59\%}} & \textcolor[HTML]{4285f4}{\textbf{19.95\%}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.77\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.59\%}} & \textcolor[HTML]{4285f4}{\textbf{19.95\%}}\\
+\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.06\%}}}\\
+\textbf{Lumber (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
 \textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**26.99\%}}}\\
-\textbf{Lumber (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.43\%}} & \textcolor[HTML]{4285f4}{\textbf{30.72\%}} & \textcolor[HTML]{4285f4}{\textbf{35.45\%}} & \textcolor[HTML]{4285f4}{\textbf{21.26\%}}\\
-\addlinespace
+\addlinespace
+\textbf{Lumber (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.43\%}} & \textcolor[HTML]{4285f4}{\textbf{30.72\%}} & \textcolor[HTML]{4285f4}{\textbf{35.45\%}} & \textcolor[HTML]{4285f4}{\textbf{21.26\%}}\\
 \textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.14\%}}}\\
-\textbf{Lumber (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}} & \textcolor[HTML]{4285f4}{\textbf{28.2\%}} & \textcolor[HTML]{4285f4}{\textbf{37.23\%}} & \textcolor[HTML]{4285f4}{\textbf{28.45\%}}\\
+\textbf{Lumber (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}} & \textcolor[HTML]{4285f4}{\textbf{28.2\%}} & \textcolor[HTML]{4285f4}{\textbf{37.23\%}} & \textcolor[HTML]{4285f4}{\textbf{28.45\%}}\\
+\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.8\%}}}\\
+\textbf{Orange juice (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.64\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{30.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.64\%}}\\
+\textbf{Orange juice (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{30.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.64\%}}\\
 \textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.64\%}}}\\
-\addlinespace
-\textbf{Orange juice (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{38.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.11\%}}\\
+\textbf{Orange juice (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{38.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.11\%}}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.16\%}}}\\
+\addlinespace
+\textbf{Sugar-\#11 (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
 \textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.07\%}}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{33.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.6\%}} & \textcolor[HTML]{4285f4}{\textbf{41.29\%}} & \textcolor[HTML]{4285f4}{\textbf{27.69\%}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.6\%}} & \textcolor[HTML]{4285f4}{\textbf{41.29\%}} & \textcolor[HTML]{4285f4}{\textbf{27.69\%}}\\
 \textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.7\%}}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{36.48\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.09\%}} & \textcolor[HTML]{4285f4}{\textbf{29.83\%}}\\
-\addlinespace
+\textbf{Sugar-\#11 (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.48\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.09\%}} & \textcolor[HTML]{4285f4}{\textbf{29.83\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.33\%}}}\\
+\textbf{Natural gas (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
 \textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**85.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.76\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.33\%}}}\\
-\textbf{Natural gas (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{63.46\%}} & \textcolor[HTML]{4285f4}{\textbf{47.3\%}} & \textcolor[HTML]{4285f4}{\textbf{48.85\%}} & \textcolor[HTML]{4285f4}{\textbf{42.59\%}}\\
+\textbf{Natural gas (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{63.46\%}} & \textcolor[HTML]{4285f4}{\textbf{47.3\%}} & \textcolor[HTML]{4285f4}{\textbf{48.85\%}} & \textcolor[HTML]{4285f4}{\textbf{42.59\%}}\\
 \textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.25\%}}}\\
-\textbf{Natural gas (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{59.76\%}} & \textcolor[HTML]{4285f4}{\textbf{61.3\%}} & \textcolor[HTML]{4285f4}{\textbf{58.18\%}} & \textcolor[HTML]{4285f4}{\textbf{46.41\%}}\\
+\addlinespace
+\textbf{Natural gas (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{59.76\%}} & \textcolor[HTML]{4285f4}{\textbf{61.3\%}} & \textcolor[HTML]{4285f4}{\textbf{58.18\%}} & \textcolor[HTML]{4285f4}{\textbf{46.41\%}}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.64\%}}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
 \textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.24\%}}}\\
-\addlinespace
-\textbf{Crude oil-WTI (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{36.74\%}} & \textcolor[HTML]{4285f4}{\textbf{32.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.19\%}} & \textcolor[HTML]{4285f4}{\textbf{26.94\%}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.74\%}} & \textcolor[HTML]{4285f4}{\textbf{32.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.19\%}} & \textcolor[HTML]{4285f4}{\textbf{26.94\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-24.85\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.74\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{53.7\%}} & \textcolor[HTML]{4285f4}{\textbf{41.08\%}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.74\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{53.7\%}} & \textcolor[HTML]{4285f4}{\textbf{41.08\%}}\\
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.37\%}}}\\
+\textbf{Gasoline (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
 \textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}}\\
-\textbf{Gasoline (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.47\%}} & \textcolor[HTML]{4285f4}{\textbf{39.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.1\%}}\\
-\addlinespace
+\addlinespace
+\textbf{Gasoline (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.47\%}} & \textcolor[HTML]{4285f4}{\textbf{39.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.1\%}}\\
 \textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-19.47\%}}}\\
-\textbf{Gasoline (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.14\%}} & \textcolor[HTML]{4285f4}{\textbf{44.13\%}} & \textcolor[HTML]{4285f4}{\textbf{47.11\%}} & \textcolor[HTML]{4285f4}{\textbf{41.71\%}}\\
+\textbf{Gasoline (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.14\%}} & \textcolor[HTML]{4285f4}{\textbf{44.13\%}} & \textcolor[HTML]{4285f4}{\textbf{47.11\%}} & \textcolor[HTML]{4285f4}{\textbf{41.71\%}}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.44\%}}}\\
+\textbf{Heating oil (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.16\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{41.37\%}} & \textcolor[HTML]{4285f4}{\textbf{33.33\%}} & \textcolor[HTML]{4285f4}{\textbf{25.95\%}} & \textcolor[HTML]{4285f4}{\textbf{24.62\%}}\\
+\textbf{Heating oil (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.37\%}} & \textcolor[HTML]{4285f4}{\textbf{33.33\%}} & \textcolor[HTML]{4285f4}{\textbf{25.95\%}} & \textcolor[HTML]{4285f4}{\textbf{24.62\%}}\\
 \textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-21.62\%}}}\\
-\addlinespace
-\textbf{Heating oil (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.98\%}} & \textcolor[HTML]{4285f4}{\textbf{39.16\%}} & \textcolor[HTML]{4285f4}{\textbf{35.69\%}}\\
+\textbf{Heating oil (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.98\%}} & \textcolor[HTML]{4285f4}{\textbf{39.16\%}} & \textcolor[HTML]{4285f4}{\textbf{35.69\%}}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.1\%}}}\\
+\addlinespace
+\textbf{Copper (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.1\%}}}\\
-\textbf{Copper (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{30.05\%}} & \textcolor[HTML]{4285f4}{\textbf{25.73\%}} & \textcolor[HTML]{4285f4}{\textbf{18.16\%}}\\
+\textbf{Copper (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{30.05\%}} & \textcolor[HTML]{4285f4}{\textbf{25.73\%}} & \textcolor[HTML]{4285f4}{\textbf{18.16\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-12.15\%}}}\\
-\textbf{Copper (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.78\%}} & \textcolor[HTML]{4285f4}{\textbf{33.69\%}} & \textcolor[HTML]{4285f4}{\textbf{42.28\%}} & \textcolor[HTML]{4285f4}{\textbf{20.87\%}}\\
-\addlinespace
+\textbf{Copper (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.78\%}} & \textcolor[HTML]{4285f4}{\textbf{33.69\%}} & \textcolor[HTML]{4285f4}{\textbf{42.28\%}} & \textcolor[HTML]{4285f4}{\textbf{20.87\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.53\%}}}\\
+\textbf{Gold (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
 \textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.21\%}}}\\
-\textbf{Gold (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.89\%}} & \textcolor[HTML]{4285f4}{\textbf{19.2\%}} & \textcolor[HTML]{4285f4}{\textbf{17.03\%}} & \textcolor[HTML]{4285f4}{\textbf{12.36\%}}\\
+\textbf{Gold (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.89\%}} & \textcolor[HTML]{4285f4}{\textbf{19.2\%}} & \textcolor[HTML]{4285f4}{\textbf{17.03\%}} & \textcolor[HTML]{4285f4}{\textbf{12.36\%}}\\
 \textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.1\%}}}\\
-\textbf{Gold (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}} & \textcolor[HTML]{4285f4}{\textbf{25.21\%}} & \textcolor[HTML]{4285f4}{\textbf{16.23\%}}\\
+\addlinespace
+\textbf{Gold (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}} & \textcolor[HTML]{4285f4}{\textbf{25.21\%}} & \textcolor[HTML]{4285f4}{\textbf{16.23\%}}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.75\%}}}\\
+\textbf{Palladium (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
 \textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**49.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**31.93\%}}}\\
-\addlinespace
-\textbf{Palladium (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.49\%}} & \textcolor[HTML]{4285f4}{\textbf{23.82\%}}\\
+\textbf{Palladium (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.49\%}} & \textcolor[HTML]{4285f4}{\textbf{23.82\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.88\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{41.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.2\%}} & \textcolor[HTML]{4285f4}{\textbf{38.71\%}} & \textcolor[HTML]{4285f4}{\textbf{26.8\%}}\\
+\textbf{Palladium (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.2\%}} & \textcolor[HTML]{4285f4}{\textbf{38.71\%}} & \textcolor[HTML]{4285f4}{\textbf{26.8\%}}\\
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.92\%}}}\\
+\textbf{Platinum (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
 \textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*25.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.17\%}}}\\
-\textbf{Platinum (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.1\%}} & \textcolor[HTML]{4285f4}{\textbf{22.51\%}} & \textcolor[HTML]{4285f4}{\textbf{21.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.04\%}}\\
-\addlinespace
+\addlinespace
+\textbf{Platinum (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.1\%}} & \textcolor[HTML]{4285f4}{\textbf{22.51\%}} & \textcolor[HTML]{4285f4}{\textbf{21.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.04\%}}\\
 \textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.28\%}}}\\
-\textbf{Platinum (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23.12\%}} & \textcolor[HTML]{4285f4}{\textbf{22.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.75\%}} & \textcolor[HTML]{4285f4}{\textbf{20.8\%}}\\
+\textbf{Platinum (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.12\%}} & \textcolor[HTML]{4285f4}{\textbf{22.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.75\%}} & \textcolor[HTML]{4285f4}{\textbf{20.8\%}}\\
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.43\%}}}\\
+\textbf{Silver (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.44\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.07\%}} & \textcolor[HTML]{4285f4}{\textbf{32.5\%}} & \textcolor[HTML]{4285f4}{\textbf{37.17\%}} & \textcolor[HTML]{4285f4}{\textbf{20.3\%}}\\
+\textbf{Silver (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.07\%}} & \textcolor[HTML]{4285f4}{\textbf{32.5\%}} & \textcolor[HTML]{4285f4}{\textbf{37.17\%}} & \textcolor[HTML]{4285f4}{\textbf{20.3\%}}\\
 \textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.09\%}}}\\
-\addlinespace
-\textbf{Silver (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.93\%}} & \textcolor[HTML]{4285f4}{\textbf{35.34\%}} & \textcolor[HTML]{4285f4}{\textbf{42.44\%}} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}}\\
+\textbf{Silver (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.93\%}} & \textcolor[HTML]{4285f4}{\textbf{35.34\%}} & \textcolor[HTML]{4285f4}{\textbf{42.44\%}} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}}\\
+\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.15\%}}}\\
+\addlinespace
+\textbf{Aluminium (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
 \textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**23.68\%}}}\\
-\textbf{Aluminium (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.57\%}} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{18.94\%}}\\
+\textbf{Aluminium (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.57\%}} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{18.94\%}}\\
 \textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-23.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.74\%}}}\\
-\textbf{Aluminium (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.13\%}} & \textcolor[HTML]{4285f4}{\textbf{27.29\%}} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{18.23\%}}\\
-\addlinespace
+\textbf{Aluminium (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.13\%}} & \textcolor[HTML]{4285f4}{\textbf{27.29\%}} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{18.23\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**28.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.03\%}}}\\
+\textbf{Copper (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.99\%}}}\\
-\textbf{Copper (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.98\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{17.92\%}}\\
+\textbf{Copper (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.98\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{17.92\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.89\%}}}\\
-\textbf{Copper (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{41.31\%}} & \textcolor[HTML]{4285f4}{\textbf{19.86\%}}\\
+\addlinespace
+\textbf{Copper (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{41.31\%}} & \textcolor[HTML]{4285f4}{\textbf{19.86\%}}\\
+\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}}\\
+\textbf{Lead (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
 \textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.05\%}}}\\
-\addlinespace
-\textbf{Lead (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.16\%}} & \textcolor[HTML]{4285f4}{\textbf{39.91\%}} & \textcolor[HTML]{4285f4}{\textbf{35.35\%}} & \textcolor[HTML]{4285f4}{\textbf{23.37\%}}\\
+\textbf{Lead (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.16\%}} & \textcolor[HTML]{4285f4}{\textbf{39.91\%}} & \textcolor[HTML]{4285f4}{\textbf{35.35\%}} & \textcolor[HTML]{4285f4}{\textbf{23.37\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*46.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-13.41\%}}}\\
-\textbf{Lead (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.12\%}} & \textcolor[HTML]{4285f4}{\textbf{43.16\%}} & \textcolor[HTML]{4285f4}{\textbf{46.22\%}} & \textcolor[HTML]{4285f4}{\textbf{23.09\%}}\\
+\textbf{Lead (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.12\%}} & \textcolor[HTML]{4285f4}{\textbf{43.16\%}} & \textcolor[HTML]{4285f4}{\textbf{46.22\%}} & \textcolor[HTML]{4285f4}{\textbf{23.09\%}}\\
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.31\%}}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
 \textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-39.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**35.09\%}}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.23\%}} & \textcolor[HTML]{4285f4}{\textbf{41.62\%}} & \textcolor[HTML]{4285f4}{\textbf{34.48\%}} & \textcolor[HTML]{4285f4}{\textbf{29.13\%}}\\
-\addlinespace
+\addlinespace
+\textbf{Nickel-primary (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.23\%}} & \textcolor[HTML]{4285f4}{\textbf{41.62\%}} & \textcolor[HTML]{4285f4}{\textbf{34.48\%}} & \textcolor[HTML]{4285f4}{\textbf{29.13\%}}\\
 \textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**63.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**-34.64\%}}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.28\%}} & \textcolor[HTML]{4285f4}{\textbf{46.72\%}} & \textcolor[HTML]{4285f4}{\textbf{47.44\%}} & \textcolor[HTML]{4285f4}{\textbf{28.6\%}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.28\%}} & \textcolor[HTML]{4285f4}{\textbf{46.72\%}} & \textcolor[HTML]{4285f4}{\textbf{47.44\%}} & \textcolor[HTML]{4285f4}{\textbf{28.6\%}}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.68\%}}}\\
+\textbf{Tin-refined (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.48\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.4\%}} & \textcolor[HTML]{4285f4}{\textbf{29.09\%}} & \textcolor[HTML]{4285f4}{\textbf{15.27\%}}\\
+\textbf{Tin-refined (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.4\%}} & \textcolor[HTML]{4285f4}{\textbf{29.09\%}} & \textcolor[HTML]{4285f4}{\textbf{15.27\%}}\\
 \textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.69\%}}}\\
-\addlinespace
-\textbf{Tin-refined (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.77\%}} & \textcolor[HTML]{4285f4}{\textbf{32.08\%}} & \textcolor[HTML]{4285f4}{\textbf{41.13\%}} & \textcolor[HTML]{4285f4}{\textbf{21.68\%}}\\
+\textbf{Tin-refined (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.77\%}} & \textcolor[HTML]{4285f4}{\textbf{32.08\%}} & \textcolor[HTML]{4285f4}{\textbf{41.13\%}} & \textcolor[HTML]{4285f4}{\textbf{21.68\%}}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.07\%}}}\\
+\addlinespace
+\textbf{Zinc (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
 \textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.05\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.42\%}}}\\
-\textbf{Zinc (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.86\%}} & \textcolor[HTML]{4285f4}{\textbf{33.28\%}} & \textcolor[HTML]{4285f4}{\textbf{22.12\%}}\\
+\textbf{Zinc (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.86\%}} & \textcolor[HTML]{4285f4}{\textbf{33.28\%}} & \textcolor[HTML]{4285f4}{\textbf{22.12\%}}\\
 \textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.31\%}}}\\
-\textbf{Zinc (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.38\%}} & \textcolor[HTML]{4285f4}{\textbf{40.51\%}} & \textcolor[HTML]{4285f4}{\textbf{39.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.32\%}}\\
-\addlinespace
+\textbf{Zinc (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.38\%}} & \textcolor[HTML]{4285f4}{\textbf{40.51\%}} & \textcolor[HTML]{4285f4}{\textbf{39.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.32\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**15.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.18\%}}}\\
+\textbf{US commodities} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
 \textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{***15.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.82\%}}}\\
-\textbf{US commodities} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
+\textbf{US commodities} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
 \textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*16.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.33\%}}}\\
-\textbf{US commodities} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
+\addlinespace
+\textbf{US commodities} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*21.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.72\%}}}\\
+\textbf{GB commodities} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
 \textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**19.95\%}}}\\
-\addlinespace
-\textbf{GB commodities} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
+\textbf{GB commodities} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
+\addlinespace
 \textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-14.05\%}}}\\
-\textbf{GB commodities} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
+\textbf{GB commodities} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
 \bottomrule

### 2024-09-27 paper.qmd
Deploying to gh-pages from @ bautheac/financialisation-co-movement@397e55df85c0dbe7b31df1a919835e095b429d17 🚀

--- 2024-09-26 docs/paper.qmd
@@
 
-@tbl-stats-no-regimes displays descriptive statistics for the commodity series considered in the study; the results show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
+@tbl-stats-combined displays descriptive statistics for the commodity series considered in the study; the results show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
 6.9% with a 10% significance in the pre-financialisation period.
@@
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
-In @tbl-stats-regimes the mean returns are shown over high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
+@tbl-stats-combined further shows the mean returns and volatilities for high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
 Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another.
@@
 These results thus suggest that the US metals sector was the driving force behind increased average pairwise correlations during financialisation, a new observation to the best of our knowledge.
-The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods which indicates that increased commodity interdependence over financialisation was not a phase driven phenomenon in the same way that individual commodity returns are, as demonstrated in @tbl-stats-regimes.
+The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods which indicates that increased commodity interdependence over financialisation was not a phase driven phenomenon in the same way that individual commodity returns are, as demonstrated in @tbl-stats-combined.
 We further examine these correlations by year in @tbl-correlations-years to uncover any distinct breakpoints.
@@
 The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results.
-Returns fall sharply relative to the financialisation period (@tbl-stats-no-regimes) with eighteen US commodities along with all six GB traded metals showing lower mean returns.
+Returns fall sharply relative to the financialisation period (@tbl-stats-combined) with eighteen US commodities along with all six GB traded metals showing lower mean returns.
 Returns for equally weighted portfolios of both sets of assets fall down to 9.4% and 5.3% from 15.9% and 21.8% respectively.
-Returns are mostly higher during phases of **backwardation** relative to **contango** (@tbl-stats-regimes) with fifteen US assets and five of the GB traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets.
+Returns are mostly higher during phases of **backwardation** relative to **contango** with fifteen US assets and five of the GB traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets.
 Volatility is moderately higher for both sets with fifteen US commodities and three GB metals showing higher figures and interestingly eminently higher over phases of **contango**; out of the US complex only Sugar-#11 (IFUS) and none of the GB traded metals show higher volatility figures over **backwardation** phases.
@@
 
-The returns pull-back continues into the post-crisis period (@tbl-stats-no-regimes) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively.
+The returns pull-back continues into the post-crisis period (@tbl-stats-combined) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively.
 Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
 The figures for the equally weighted portfolios of US and UK assets drop to 9.9% and 16.2% respectively, very close to pre-financialisation levels.
-The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period (@tbl-stats-regimes) with mean returns higher during phases of **backwardation** relative to **contango**, more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
+The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of **backwardation** relative to **contango**, more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
 The difference is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
@@
 ```{r}
-#| label: tbl-stats-no-regimes
-#| tbl-cap: "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Mean values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
-The results are discussed in \\@sec-results."
-
-colnames <- c("asset", "estimate", periods)
-align <- make_series_of_repeated_chars(list(l = 2L, r = 4L))
-
-make_table("stats - whole", colnames, align, 1L:6L, 3L:6L)
-```
-
-\newpage
-
-```{r}
-#| label: tbl-stats-regimes
-#| tbl-cap: "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
+#| label: tbl-stats-combined
+#| tbl-cap: "This table shows mean returns and volatility for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+for each period the figures are shown independently for the entire period as well as for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
 Mean values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
@@
 
-make_table("stats - regimes", colnames, align, 1L:7L, 4L:7L)
+make_table("stats - combined", colnames, align, 1L:7L, 4L:7L)
 ```

### 2024-09-27 explore/scripts/revision-jfm/tables.r
Made asset taxonomy table

@@ -1,29 +1,51 @@
 library(magrittr)
 
 # Globals ####
+## datasets ####
+data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
+data("exchanges", package = "fewISOs")
 
 ## variables ####
-results_directory_path <- here::here("explore", "results", "revision-jfm")
-tables_directory_path <- here::here("explore", "tables", "revision-jfm")
 factors <- c("market", "CHP", "open interest nearby", "open interest aggregate", "term structure")
+results_directory_path <- here::here("explore", "results", "revision-jfm")
 sector_levels <- c("all", "agriculturals", "energy", "metals")
-subsector_levels <- c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")
 sort_levels <- c(
   "all-all-all", "US-all-all", "US-agriculturals-all", "US-agriculturals-grains",
   "US-agriculturals-livestock", "US-agriculturals-softs", "US-energy-all", 
   "US-energy-gas", "US-energy-petroleum", "US-metals-all", "US-metals-base", 
   "US-metals-precious", "GB-all-all"
 )
+subsector_levels <- c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")
+tables_directory_path <- here::here("explore", "tables", "revision-jfm")
+commodity_futures_tickers <- c(
+  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
+  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
+  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
+  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
+  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
+  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty",
+  "LAA Comdty", "LPA Comdty", "LLA Comdty", "LNA Comdty", "LTA Comdty",
+  "LXA Comdty"
+)
 
 ## functions ####
+make_asset_name_country_sector_subsector_dataframe <- function(tickers){
+  
+  dplyr::left_join(
[…]

### 2024-09-27 docs/paper.qmd
Make appendix section
Refer to it in data section + update table captions

--- 2024-09-26 docs/paper.qmd
@@
 tables_hline <- "major"
+
+tables <- readr::read_rds(paste_forward_slash(tables_directory_path, "tables-formatted.rds"))
+sectors <- c("country", "sector", "subsector")
+periods <- c("past", "financialisation", "crisis", "post-crisis")
+
+make_table <- function(table_name, colnames, align, bold_columns, coloured_columns){
+  get_results(tables, table_name) %>%
+  kbl(booktabs = T, longtable = T, col.names = colnames, align = align) %>%
+  kable_styling(latex_options = "striped", font_size = 7L) %>%
+  row_spec(0L, bold = TRUE, color = "black") %>%
+  column_spec(bold_columns, bold = TRUE) %>% column_spec(coloured_columns, color = "#4285f4")
+}
 ```
@@
 We also consider the UK metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).
-This sample cross-section of assets is further divided into groups for the purpose of the analysis by country (US, GB), sector (agriculturals, energy, metals) and by sub-sector (agriculturals: grains, livestock, softs; energy: gas, petroleum; metals: base, precious).
+This sample cross-section of assets is further divided into groups for the purpose of the analysis by country (US, GB), sector (agriculturals, energy, metals) and by sub-sector (agriculturals: grains, livestock, softs; energy: gas, petroleum; metals: base, precious)^[See @sec-taxonomy for a detailed taxonomy of the commodity assets considered in the study.].
 
@@
 ```{r}
-tables <- readr::read_rds(paste_forward_slash(tables_directory_path, "tables-formatted.rds"))
-sectors <- c("country", "sector", "subsector")
-periods <- c("past", "financialisation", "crisis", "post-crisis")
-
-make_table <- function(table_name, colnames, align, bold_columns, coloured_columns){
-  get_results(tables, table_name) %>%
-  kbl(booktabs = T, longtable = T, col.names = colnames, align = align) %>%
-  kable_styling(latex_options = "striped", font_size = 7L) %>%
-  row_spec(0L, bold = TRUE, color = "black") %>%
-  column_spec(bold_columns, bold = TRUE) %>% column_spec(coloured_columns, color = "#4285f4")
-}
-```
-
-```{r}
-#| label: tbl-stats-no-regimes
-#| tbl-cap: "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Mean values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
-The results are discussed in \\@sec-results."
-
-colnames <- c("asset", "estimate", periods)
-align <- make_series_of_repeated_chars(list(l = 2L, r = 4L))
-
-make_table("stats - whole", colnames, align, 1L:6L, 3L:6L)
-```
-
-\newpage
-
-```{r}
-#| label: tbl-stats-regimes
-#| tbl-cap: "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
+#| label: tbl-stats-combined
+#| tbl-cap: "This table shows mean returns and volatility for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+for each period the figures are shown independently for the entire period as well as for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
 Mean values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
@@
 Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The results are discussed in \\@sec-results."
+The results are discussed in \\@sec-results while \\@sec-taxonomy details the taxonomy for the commodity assets considered."
 
@@
 For each period, the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
-Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
+Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the taxonomy for the commodity assets considered is detailed in \\@sec-taxonomy."
 
@@
 #| tbl-cap: "This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors by year for the whole period of interest (1997-2018).
-The results are discussed in \\@sec-results."
+The results are discussed in \\@sec-results while \\@sec-taxonomy details the taxonomy for the commodity assets considered."
 
@@
 The results are calculated independently across countries as well as commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The market factor construction is discussed in \\@sec-methods while the results are discussed in \\@sec-results."
+The market factor construction is discussed in \\@sec-methods while the results are discussed in \\@sec-results and the taxonomy for the commodity assets considered is detailed in \\@sec-taxonomy."
 
@@
 The results are calculated independently across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018); for each period the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
-Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
+Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the taxonomy for the commodity assets considered is detailed in \\@sec-taxonomy."
 
@@
 
+# Appendix
+
+## Commodity assets taxonomy {#sec-taxonomy}
+
+```{r}
+#| label: tbl-assets-taxonomy
+#| tbl-cap: "This table shows the detailed taxonomy for the thirty commodity assets considered in the study.
+The assets are classified by the country of residence of the exchange where they are traded as well as by sector and subsector according to the nature of the asset."
+
+colnames <- c("asset", "country", "sector", "subsector")
+align <- make_series_of_repeated_chars(list(l = 4L))
+
+make_table("assets taxonomy", colnames, align, 1L, 2L:4L)
+```
+
+\newpage
+
 # References {-}

### 2024-09-27 explore/scripts/revision-jfm/tables.r

@@ -54,8 +54,8 @@ sort_table_by_country_sector_subsector <- function(tb, sort_levels){
   ) %>% dplyr::arrange(sort) %>% dplyr::select(-sort)
 }
 
-# asset taxonomy ####
-`asset taxonomy` <- 
+# assets taxonomy ####
+`assets taxonomy` <- 
   make_asset_name_country_sector_subsector_dataframe(commodity_futures_tickers) %>%
   dplyr::mutate(
     asset = paste0(name, " (", MIC, ")"),
@@ -358,11 +358,11 @@ tables <- tibble::tribble(
     "correlations - years",                     correlations_years,
     "regressions - all returns ~ market index", `all commodity returns ~ market index`,
     "regressions - all returns ~ factors",      `all commodity returns ~ factors`,
-    "asset taxonomy",                           `asset taxonomy`
+    "assets taxonomy",                          `assets taxonomy`
   )
 
 readr::write_rds(
   tables, paste_forward_slash(tables_directory_path, "tables-formatted.rds")
   )
 
-rm(list = ls())
+# rm(list = ls())

### 2024-09-27 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@c328f0b9c5a755b03d340f3f58900773e4ce888e 🚀

@@
 grains, livestock, softs; energy: gas, petroleum; metals: base,
-precious).
+precious)\footnote{See Section~\ref{sec-taxonomy} for a detailed
+  taxonomy of the commodity assets considered in the study.}.
 
@@
 results. Returns fall sharply relative to the financialisation period
-(Table~\ref{tbl-stats-no-regimes}) with eighteen US commodities along
-with all six GB traded metals showing lower mean returns. Returns for
-equally weighted portfolios of both sets of assets fall down to 9.4\%
-and 5.3\% from 15.9\% and 21.8\% respectively. Returns are mostly higher
-during phases of \textbf{backwardation} relative to \textbf{contango}
-(Table~\ref{tbl-stats-regimes}) with fifteen US assets and five of the
-GB traded metals showing higher mean returns in \textbf{backwardation}
-and the pattern extending to equally weighted portfolios of the two sets
-of assets. Volatility is moderately higher for both sets with fifteen US
-commodities and three GB metals showing higher figures and interestingly
-eminently higher over phases of \textbf{contango}; out of the US complex
-only Sugar-\#11 (IFUS) and none of the GB traded metals show higher
-volatility figures over \textbf{backwardation} phases. The symmetry
-between the dynamics of CHP and \textbf{CHP}'s explanatory power on
-individual commodity returns breaks in the crisis period
-(Table~\ref{tbl-time-reg-US-CHP}) with both now seemingly converging;
-the US cross-sectional average \(R^{2}\) at the individual level
-bouncing back up (22.5\% vs 20.8\%) while that at the aggregate level
-rises further (14.7\% vs 7.1\%).
+(Table~\ref{tbl-stats-combined}) with eighteen US commodities along with
+all six GB traded metals showing lower mean returns. Returns for equally
+weighted portfolios of both sets of assets fall down to 9.4\% and 5.3\%
+from 15.9\% and 21.8\% respectively. Returns are mostly higher during
+phases of \textbf{backwardation} relative to \textbf{contango} with
+fifteen US assets and five of the GB traded metals showing higher mean
+returns in \textbf{backwardation} and the pattern extending to equally
+weighted portfolios of the two sets of assets. Volatility is moderately
+higher for both sets with fifteen US commodities and three GB metals
+showing higher figures and interestingly eminently higher over phases of
+\textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none
+of the GB traded metals show higher volatility figures over
+\textbf{backwardation} phases. The symmetry between the dynamics of CHP
+and \textbf{CHP}'s explanatory power on individual commodity returns
+breaks in the crisis period (Table~\ref{tbl-time-reg-US-CHP}) with both
+now seemingly converging; the US cross-sectional average \(R^{2}\) at
+the individual level bouncing back up (22.5\% vs 20.8\%) while that at
+the aggregate level rises further (14.7\% vs 7.1\%).
 
@@
 The returns pull-back continues into the post-crisis period
-(Table~\ref{tbl-stats-no-regimes}) with twenty-two US and four UK traded
+(Table~\ref{tbl-stats-combined}) with twenty-two US and four UK traded
 assets showing lower mean returns relative to the crisis while the same
@@
 \caption{\label{tbl-stats-combined}This table shows mean returns and
-volatility (sd) for the twenty four individual US commodities and the
-six GB metals considered in the study as well as for two equally
-weighted portfolios formed from the US commodities and the GB metals
-respectively across the four periods of interest (past: 1997-2003;
-financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-for each period the figures are shown independently for the entire
-period as well as for phases of aggregate backwardation (aggregate CHP
-\(\leq\) period median) and aggregate contango (aggregate CHP
-\textgreater{} period median). Mean values significant at the 1\%, 5\%
-and 10\% level are marked with ***, ** and * respectively. Aggregate CHP
-construction and corresponding regime definitions are discussed in
-Section~\ref{sec-methods} while the results are discussed in
-Section~\ref{sec-results}.}
+volatility for the twenty four individual US commodities and the six GB
+metals considered in the study as well as for two equally weighted
+portfolios formed from the US commodities and the GB metals respectively
+across the four periods of interest (past: 1997-2003; financialisation:
+2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). for each period
+the figures are shown independently for the entire period as well as for
+phases of aggregate backwardation (aggregate CHP \(\leq\) period median)
+and aggregate contango (aggregate CHP \textgreater{} period median).
+Mean values significant at the 1\%, 5\% and 10\% level are marked with
+***, ** and * respectively. Aggregate CHP construction and corresponding
+regime definitions are discussed in Section~\ref{sec-methods} while the
+results are discussed in Section~\ref{sec-results}.}
 
@@
 \textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
 \textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.74\%}}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23.07\%}} & \textcolor[HTML]{4285f4}{\textbf{29.14\%}} & \textcolor[HTML]{4285f4}{\textbf{31.59\%}} & \textcolor[HTML]{4285f4}{\textbf{21\%}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.07\%}} & \textcolor[HTML]{4285f4}{\textbf{29.14\%}} & \textcolor[HTML]{4285f4}{\textbf{31.59\%}} & \textcolor[HTML]{4285f4}{\textbf{21\%}}\\
 \textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.78\%}}}\\
 \addlinespace
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
 \textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
+\textbf{Oats (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
 \textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
+\textbf{Oats (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.17\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
+\textbf{Oats (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
 \textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
 \textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.52\%}}}\\
 \addlinespace
-\textbf{Soybean meal (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
 \textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
 \textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.44\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.35\%}} & \textcolor[HTML]{4285f4}{\textbf{28.94\%}} & \textcolor[HTML]{4285f4}{\textbf{22.33\%}} & \textcolor[HTML]{4285f4}{\textbf{18.19\%}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.35\%}} & \textcolor[HTML]{4285f4}{\textbf{28.94\%}} & \textcolor[HTML]{4285f4}{\textbf{22.33\%}} & \textcolor[HTML]{4285f4}{\textbf{18.19\%}}\\
 \textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.12\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
 \textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
 \addlinespace
-\textbf{Soybeans (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
+\textbf{Soybeans (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
 \textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.45\%}}}\\
-\textbf{Soybeans (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.93\%}} & \textcolor[HTML]{4285f4}{\textbf{34.58\%}} & \textcolor[HTML]{4285f4}{\textbf{24.39\%}} & \textcolor[HTML]{4285f4}{\textbf{22.04\%}}\\
+\textbf{Soybeans (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.93\%}} & \textcolor[HTML]{4285f4}{\textbf{34.58\%}} & \textcolor[HTML]{4285f4}{\textbf{24.39\%}} & \textcolor[HTML]{4285f4}{\textbf{22.04\%}}\\
 \textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}}\\
-\textbf{Soybeans (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.09\%}} & \textcolor[HTML]{4285f4}{\textbf{24.74\%}} & \textcolor[HTML]{4285f4}{\textbf{31.11\%}} & \textcolor[HTML]{4285f4}{\textbf{20.56\%}}\\
+\textbf{Soybeans (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.09\%}} & \textcolor[HTML]{4285f4}{\textbf{24.74\%}} & \textcolor[HTML]{4285f4}{\textbf{31.11\%}} & \textcolor[HTML]{4285f4}{\textbf{20.56\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
 \textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.44\%}}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{36\%}} & \textcolor[HTML]{4285f4}{\textbf{37.53\%}} & \textcolor[HTML]{4285f4}{\textbf{26.57\%}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{36\%}} & \textcolor[HTML]{4285f4}{\textbf{37.53\%}} & \textcolor[HTML]{4285f4}{\textbf{26.57\%}}\\
 \textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.77\%}}}\\
 \addlinespace
-\textbf{Wheat-SRW (XCBT)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.04\%}} & \textcolor[HTML]{4285f4}{\textbf{29.84\%}} & \textcolor[HTML]{4285f4}{\textbf{37.73\%}} & \textcolor[HTML]{4285f4}{\textbf{26.72\%}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.04\%}} & \textcolor[HTML]{4285f4}{\textbf{29.84\%}} & \textcolor[HTML]{4285f4}{\textbf{37.73\%}} & \textcolor[HTML]{4285f4}{\textbf{26.72\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**20.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.58\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}} & \textcolor[HTML]{4285f4}{\textbf{14.93\%}} & \textcolor[HTML]{4285f4}{\textbf{13.39\%}} & \textcolor[HTML]{4285f4}{\textbf{20.14\%}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}} & \textcolor[HTML]{4285f4}{\textbf{14.93\%}} & \textcolor[HTML]{4285f4}{\textbf{13.39\%}} & \textcolor[HTML]{4285f4}{\textbf{20.14\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.12\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.67\%}} & \textcolor[HTML]{4285f4}{\textbf{15.35\%}} & \textcolor[HTML]{4285f4}{\textbf{16.91\%}} & \textcolor[HTML]{4285f4}{\textbf{17.23\%}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.67\%}} & \textcolor[HTML]{4285f4}{\textbf{15.35\%}} & \textcolor[HTML]{4285f4}{\textbf{16.91\%}} & \textcolor[HTML]{4285f4}{\textbf{17.23\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}}\\
-\textbf{Cattle-live (XCME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
+\textbf{Cattle-live (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.07\%}}}\\
 \addlinespace
-\textbf{Cattle-live (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.65\%}} & \textcolor[HTML]{4285f4}{\textbf{17.91\%}} & \textcolor[HTML]{4285f4}{\textbf{14.97\%}} & \textcolor[HTML]{4285f4}{\textbf{19.9\%}}\\
+\textbf{Cattle-live (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.65\%}} & \textcolor[HTML]{4285f4}{\textbf{17.91\%}} & \textcolor[HTML]{4285f4}{\textbf{14.97\%}} & \textcolor[HTML]{4285f4}{\textbf{19.9\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
-\textbf{Cattle-live (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.49\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}} & \textcolor[HTML]{4285f4}{\textbf{17.57\%}} & \textcolor[HTML]{4285f4}{\textbf{16.66\%}}\\
+\textbf{Cattle-live (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.49\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}} & \textcolor[HTML]{4285f4}{\textbf{17.57\%}} & \textcolor[HTML]{4285f4}{\textbf{16.66\%}}\\
 \textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
+\textbf{Lean hogs (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.23\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.24\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{37.6\%}} & \textcolor[HTML]{4285f4}{\textbf{35.73\%}} & \textcolor[HTML]{4285f4}{\textbf{27.83\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}}\\
+\textbf{Lean hogs (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{37.6\%}} & \textcolor[HTML]{4285f4}{\textbf{35.73\%}} & \textcolor[HTML]{4285f4}{\textbf{27.83\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}}\\
 \textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.66\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.22\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}} & \textcolor[HTML]{4285f4}{\textbf{32.78\%}} & \textcolor[HTML]{4285f4}{\textbf{38.28\%}}\\
+\textbf{Lean hogs (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.22\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}} & \textcolor[HTML]{4285f4}{\textbf{32.78\%}} & \textcolor[HTML]{4285f4}{\textbf{38.28\%}}\\
 \textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.65\%}}}\\
 \addlinespace
-\textbf{Cocoa (IFUS)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
+\textbf{Cocoa (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
 \textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.98\%}}}\\
-\textbf{Cocoa (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{33.57\%}} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}}\\
+\textbf{Cocoa (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.57\%}} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}}\\
 \textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.29\%}}}\\
-\textbf{Cocoa (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{31.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.91\%}} & \textcolor[HTML]{4285f4}{\textbf{34.66\%}} & \textcolor[HTML]{4285f4}{\textbf{23.57\%}}\\
+\textbf{Cocoa (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.91\%}} & \textcolor[HTML]{4285f4}{\textbf{34.66\%}} & \textcolor[HTML]{4285f4}{\textbf{23.57\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.99\%}}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
 \textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.36\%}}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{48.82\%}} & \textcolor[HTML]{4285f4}{\textbf{32.6\%}} & \textcolor[HTML]{4285f4}{\textbf{29.92\%}} & \textcolor[HTML]{4285f4}{\textbf{31.52\%}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{48.82\%}} & \textcolor[HTML]{4285f4}{\textbf{32.6\%}} & \textcolor[HTML]{4285f4}{\textbf{29.92\%}} & \textcolor[HTML]{4285f4}{\textbf{31.52\%}}\\
 \textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.24\%}}}\\
 \addlinespace
-\textbf{Coffee-C (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.22\%}} & \textcolor[HTML]{4285f4}{\textbf{32.24\%}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.22\%}} & \textcolor[HTML]{4285f4}{\textbf{32.24\%}}\\
 \textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
 \textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.84\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.02\%}} & \textcolor[HTML]{4285f4}{\textbf{29.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.94\%}} & \textcolor[HTML]{4285f4}{\textbf{21.33\%}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.02\%}} & \textcolor[HTML]{4285f4}{\textbf{29.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.94\%}} & \textcolor[HTML]{4285f4}{\textbf{21.33\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.91\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.77\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.59\%}} & \textcolor[HTML]{4285f4}{\textbf{19.95\%}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.77\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.59\%}} & \textcolor[HTML]{4285f4}{\textbf{19.95\%}}\\
 \textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.06\%}}}\\
-\textbf{Lumber (XCME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
+\textbf{Lumber (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
 \textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**26.99\%}}}\\
 \addlinespace
-\textbf{Lumber (XCME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.43\%}} & \textcolor[HTML]{4285f4}{\textbf{30.72\%}} & \textcolor[HTML]{4285f4}{\textbf{35.45\%}} & \textcolor[HTML]{4285f4}{\textbf{21.26\%}}\\
+\textbf{Lumber (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.43\%}} & \textcolor[HTML]{4285f4}{\textbf{30.72\%}} & \textcolor[HTML]{4285f4}{\textbf{35.45\%}} & \textcolor[HTML]{4285f4}{\textbf{21.26\%}}\\
 \textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.14\%}}}\\
-\textbf{Lumber (XCME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}} & \textcolor[HTML]{4285f4}{\textbf{28.2\%}} & \textcolor[HTML]{4285f4}{\textbf{37.23\%}} & \textcolor[HTML]{4285f4}{\textbf{28.45\%}}\\
+\textbf{Lumber (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}} & \textcolor[HTML]{4285f4}{\textbf{28.2\%}} & \textcolor[HTML]{4285f4}{\textbf{37.23\%}} & \textcolor[HTML]{4285f4}{\textbf{28.45\%}}\\
 \textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.8\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
+\textbf{Orange juice (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.64\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{30.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.64\%}}\\
+\textbf{Orange juice (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{30.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.64\%}}\\
 \textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.64\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{38.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.11\%}}\\
+\textbf{Orange juice (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{38.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.11\%}}\\
 \textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.16\%}}}\\
 \addlinespace
-\textbf{Sugar-\#11 (IFUS)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
 \textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.07\%}}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{33.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.6\%}} & \textcolor[HTML]{4285f4}{\textbf{41.29\%}} & \textcolor[HTML]{4285f4}{\textbf{27.69\%}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.6\%}} & \textcolor[HTML]{4285f4}{\textbf{41.29\%}} & \textcolor[HTML]{4285f4}{\textbf{27.69\%}}\\
 \textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.7\%}}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{36.48\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.09\%}} & \textcolor[HTML]{4285f4}{\textbf{29.83\%}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.48\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.09\%}} & \textcolor[HTML]{4285f4}{\textbf{29.83\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.33\%}}}\\
-\textbf{Natural gas (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
+\textbf{Natural gas (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
 \textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**85.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.76\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.33\%}}}\\
-\textbf{Natural gas (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{63.46\%}} & \textcolor[HTML]{4285f4}{\textbf{47.3\%}} & \textcolor[HTML]{4285f4}{\textbf{48.85\%}} & \textcolor[HTML]{4285f4}{\textbf{42.59\%}}\\
+\textbf{Natural gas (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{63.46\%}} & \textcolor[HTML]{4285f4}{\textbf{47.3\%}} & \textcolor[HTML]{4285f4}{\textbf{48.85\%}} & \textcolor[HTML]{4285f4}{\textbf{42.59\%}}\\
 \textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.25\%}}}\\
 \addlinespace
-\textbf{Natural gas (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{59.76\%}} & \textcolor[HTML]{4285f4}{\textbf{61.3\%}} & \textcolor[HTML]{4285f4}{\textbf{58.18\%}} & \textcolor[HTML]{4285f4}{\textbf{46.41\%}}\\
+\textbf{Natural gas (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{59.76\%}} & \textcolor[HTML]{4285f4}{\textbf{61.3\%}} & \textcolor[HTML]{4285f4}{\textbf{58.18\%}} & \textcolor[HTML]{4285f4}{\textbf{46.41\%}}\\
 \textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.64\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
 \textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.24\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{36.74\%}} & \textcolor[HTML]{4285f4}{\textbf{32.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.19\%}} & \textcolor[HTML]{4285f4}{\textbf{26.94\%}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.74\%}} & \textcolor[HTML]{4285f4}{\textbf{32.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.19\%}} & \textcolor[HTML]{4285f4}{\textbf{26.94\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-24.85\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.74\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{53.7\%}} & \textcolor[HTML]{4285f4}{\textbf{41.08\%}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.74\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{53.7\%}} & \textcolor[HTML]{4285f4}{\textbf{41.08\%}}\\
 \textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.37\%}}}\\
-\textbf{Gasoline (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
+\textbf{Gasoline (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
 \textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}}\\
 \addlinespace
-\textbf{Gasoline (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.47\%}} & \textcolor[HTML]{4285f4}{\textbf{39.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.1\%}}\\
+\textbf{Gasoline (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.47\%}} & \textcolor[HTML]{4285f4}{\textbf{39.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.1\%}}\\
 \textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-19.47\%}}}\\
-\textbf{Gasoline (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.14\%}} & \textcolor[HTML]{4285f4}{\textbf{44.13\%}} & \textcolor[HTML]{4285f4}{\textbf{47.11\%}} & \textcolor[HTML]{4285f4}{\textbf{41.71\%}}\\
+\textbf{Gasoline (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.14\%}} & \textcolor[HTML]{4285f4}{\textbf{44.13\%}} & \textcolor[HTML]{4285f4}{\textbf{47.11\%}} & \textcolor[HTML]{4285f4}{\textbf{41.71\%}}\\
 \textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.44\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
+\textbf{Heating oil (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.16\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{41.37\%}} & \textcolor[HTML]{4285f4}{\textbf{33.33\%}} & \textcolor[HTML]{4285f4}{\textbf{25.95\%}} & \textcolor[HTML]{4285f4}{\textbf{24.62\%}}\\
+\textbf{Heating oil (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.37\%}} & \textcolor[HTML]{4285f4}{\textbf{33.33\%}} & \textcolor[HTML]{4285f4}{\textbf{25.95\%}} & \textcolor[HTML]{4285f4}{\textbf{24.62\%}}\\
 \textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-21.62\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.98\%}} & \textcolor[HTML]{4285f4}{\textbf{39.16\%}} & \textcolor[HTML]{4285f4}{\textbf{35.69\%}}\\
+\textbf{Heating oil (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.98\%}} & \textcolor[HTML]{4285f4}{\textbf{39.16\%}} & \textcolor[HTML]{4285f4}{\textbf{35.69\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.1\%}}}\\
 \addlinespace
-\textbf{Copper (XCEC)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
+\textbf{Copper (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.1\%}}}\\
-\textbf{Copper (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{30.05\%}} & \textcolor[HTML]{4285f4}{\textbf{25.73\%}} & \textcolor[HTML]{4285f4}{\textbf{18.16\%}}\\
+\textbf{Copper (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{30.05\%}} & \textcolor[HTML]{4285f4}{\textbf{25.73\%}} & \textcolor[HTML]{4285f4}{\textbf{18.16\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-12.15\%}}}\\
-\textbf{Copper (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.78\%}} & \textcolor[HTML]{4285f4}{\textbf{33.69\%}} & \textcolor[HTML]{4285f4}{\textbf{42.28\%}} & \textcolor[HTML]{4285f4}{\textbf{20.87\%}}\\
+\textbf{Copper (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.78\%}} & \textcolor[HTML]{4285f4}{\textbf{33.69\%}} & \textcolor[HTML]{4285f4}{\textbf{42.28\%}} & \textcolor[HTML]{4285f4}{\textbf{20.87\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.53\%}}}\\
-\textbf{Gold (XCEC)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
+\textbf{Gold (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
 \textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.21\%}}}\\
-\textbf{Gold (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.89\%}} & \textcolor[HTML]{4285f4}{\textbf{19.2\%}} & \textcolor[HTML]{4285f4}{\textbf{17.03\%}} & \textcolor[HTML]{4285f4}{\textbf{12.36\%}}\\
+\textbf{Gold (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.89\%}} & \textcolor[HTML]{4285f4}{\textbf{19.2\%}} & \textcolor[HTML]{4285f4}{\textbf{17.03\%}} & \textcolor[HTML]{4285f4}{\textbf{12.36\%}}\\
 \textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.1\%}}}\\
 \addlinespace
-\textbf{Gold (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}} & \textcolor[HTML]{4285f4}{\textbf{25.21\%}} & \textcolor[HTML]{4285f4}{\textbf{16.23\%}}\\
+\textbf{Gold (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}} & \textcolor[HTML]{4285f4}{\textbf{25.21\%}} & \textcolor[HTML]{4285f4}{\textbf{16.23\%}}\\
 \textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.75\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
+\textbf{Palladium (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
 \textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**49.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**31.93\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.49\%}} & \textcolor[HTML]{4285f4}{\textbf{23.82\%}}\\
+\textbf{Palladium (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.49\%}} & \textcolor[HTML]{4285f4}{\textbf{23.82\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.88\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{41.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.2\%}} & \textcolor[HTML]{4285f4}{\textbf{38.71\%}} & \textcolor[HTML]{4285f4}{\textbf{26.8\%}}\\
+\textbf{Palladium (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.2\%}} & \textcolor[HTML]{4285f4}{\textbf{38.71\%}} & \textcolor[HTML]{4285f4}{\textbf{26.8\%}}\\
 \textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.92\%}}}\\
-\textbf{Platinum (XNYM)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
+\textbf{Platinum (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
 \textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*25.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.17\%}}}\\
 \addlinespace
-\textbf{Platinum (XNYM)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.1\%}} & \textcolor[HTML]{4285f4}{\textbf{22.51\%}} & \textcolor[HTML]{4285f4}{\textbf{21.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.04\%}}\\
+\textbf{Platinum (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.1\%}} & \textcolor[HTML]{4285f4}{\textbf{22.51\%}} & \textcolor[HTML]{4285f4}{\textbf{21.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.04\%}}\\
 \textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.28\%}}}\\
-\textbf{Platinum (XNYM)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23.12\%}} & \textcolor[HTML]{4285f4}{\textbf{22.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.75\%}} & \textcolor[HTML]{4285f4}{\textbf{20.8\%}}\\
+\textbf{Platinum (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.12\%}} & \textcolor[HTML]{4285f4}{\textbf{22.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.75\%}} & \textcolor[HTML]{4285f4}{\textbf{20.8\%}}\\
 \textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.43\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
+\textbf{Silver (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.44\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.07\%}} & \textcolor[HTML]{4285f4}{\textbf{32.5\%}} & \textcolor[HTML]{4285f4}{\textbf{37.17\%}} & \textcolor[HTML]{4285f4}{\textbf{20.3\%}}\\
+\textbf{Silver (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.07\%}} & \textcolor[HTML]{4285f4}{\textbf{32.5\%}} & \textcolor[HTML]{4285f4}{\textbf{37.17\%}} & \textcolor[HTML]{4285f4}{\textbf{20.3\%}}\\
 \textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.09\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.93\%}} & \textcolor[HTML]{4285f4}{\textbf{35.34\%}} & \textcolor[HTML]{4285f4}{\textbf{42.44\%}} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}}\\
+\textbf{Silver (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.93\%}} & \textcolor[HTML]{4285f4}{\textbf{35.34\%}} & \textcolor[HTML]{4285f4}{\textbf{42.44\%}} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}}\\
 \textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.15\%}}}\\
 \addlinespace
-\textbf{Aluminium (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
+\textbf{Aluminium (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
 \textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**23.68\%}}}\\
-\textbf{Aluminium (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.57\%}} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{18.94\%}}\\
+\textbf{Aluminium (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.57\%}} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{18.94\%}}\\
 \textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-23.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.74\%}}}\\
-\textbf{Aluminium (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.13\%}} & \textcolor[HTML]{4285f4}{\textbf{27.29\%}} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{18.23\%}}\\
+\textbf{Aluminium (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.13\%}} & \textcolor[HTML]{4285f4}{\textbf{27.29\%}} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{18.23\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**28.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.03\%}}}\\
-\textbf{Copper (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
+\textbf{Copper (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.99\%}}}\\
-\textbf{Copper (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.98\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{17.92\%}}\\
+\textbf{Copper (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.98\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{17.92\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.89\%}}}\\
 \addlinespace
-\textbf{Copper (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{41.31\%}} & \textcolor[HTML]{4285f4}{\textbf{19.86\%}}\\
+\textbf{Copper (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{41.31\%}} & \textcolor[HTML]{4285f4}{\textbf{19.86\%}}\\
 \textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}}\\
-\textbf{Lead (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
+\textbf{Lead (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
 \textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.05\%}}}\\
-\textbf{Lead (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.16\%}} & \textcolor[HTML]{4285f4}{\textbf{39.91\%}} & \textcolor[HTML]{4285f4}{\textbf{35.35\%}} & \textcolor[HTML]{4285f4}{\textbf{23.37\%}}\\
+\textbf{Lead (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.16\%}} & \textcolor[HTML]{4285f4}{\textbf{39.91\%}} & \textcolor[HTML]{4285f4}{\textbf{35.35\%}} & \textcolor[HTML]{4285f4}{\textbf{23.37\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*46.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-13.41\%}}}\\
-\textbf{Lead (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{20.12\%}} & \textcolor[HTML]{4285f4}{\textbf{43.16\%}} & \textcolor[HTML]{4285f4}{\textbf{46.22\%}} & \textcolor[HTML]{4285f4}{\textbf{23.09\%}}\\
+\textbf{Lead (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.12\%}} & \textcolor[HTML]{4285f4}{\textbf{43.16\%}} & \textcolor[HTML]{4285f4}{\textbf{46.22\%}} & \textcolor[HTML]{4285f4}{\textbf{23.09\%}}\\
 \textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.31\%}}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
 \textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-39.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**35.09\%}}}\\
 \addlinespace
-\textbf{Nickel-primary (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.23\%}} & \textcolor[HTML]{4285f4}{\textbf{41.62\%}} & \textcolor[HTML]{4285f4}{\textbf{34.48\%}} & \textcolor[HTML]{4285f4}{\textbf{29.13\%}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.23\%}} & \textcolor[HTML]{4285f4}{\textbf{41.62\%}} & \textcolor[HTML]{4285f4}{\textbf{34.48\%}} & \textcolor[HTML]{4285f4}{\textbf{29.13\%}}\\
 \textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**63.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**-34.64\%}}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.28\%}} & \textcolor[HTML]{4285f4}{\textbf{46.72\%}} & \textcolor[HTML]{4285f4}{\textbf{47.44\%}} & \textcolor[HTML]{4285f4}{\textbf{28.6\%}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.28\%}} & \textcolor[HTML]{4285f4}{\textbf{46.72\%}} & \textcolor[HTML]{4285f4}{\textbf{47.44\%}} & \textcolor[HTML]{4285f4}{\textbf{28.6\%}}\\
 \textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.68\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
+\textbf{Tin-refined (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.48\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.4\%}} & \textcolor[HTML]{4285f4}{\textbf{29.09\%}} & \textcolor[HTML]{4285f4}{\textbf{15.27\%}}\\
+\textbf{Tin-refined (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.4\%}} & \textcolor[HTML]{4285f4}{\textbf{29.09\%}} & \textcolor[HTML]{4285f4}{\textbf{15.27\%}}\\
 \textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.69\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.77\%}} & \textcolor[HTML]{4285f4}{\textbf{32.08\%}} & \textcolor[HTML]{4285f4}{\textbf{41.13\%}} & \textcolor[HTML]{4285f4}{\textbf{21.68\%}}\\
+\textbf{Tin-refined (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.77\%}} & \textcolor[HTML]{4285f4}{\textbf{32.08\%}} & \textcolor[HTML]{4285f4}{\textbf{41.13\%}} & \textcolor[HTML]{4285f4}{\textbf{21.68\%}}\\
 \textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.07\%}}}\\
 \addlinespace
-\textbf{Zinc (XLME)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
+\textbf{Zinc (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
 \textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.05\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.42\%}}}\\
-\textbf{Zinc (XLME)} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.86\%}} & \textcolor[HTML]{4285f4}{\textbf{33.28\%}} & \textcolor[HTML]{4285f4}{\textbf{22.12\%}}\\
+\textbf{Zinc (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.86\%}} & \textcolor[HTML]{4285f4}{\textbf{33.28\%}} & \textcolor[HTML]{4285f4}{\textbf{22.12\%}}\\
 \textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.31\%}}}\\
-\textbf{Zinc (XLME)} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.38\%}} & \textcolor[HTML]{4285f4}{\textbf{40.51\%}} & \textcolor[HTML]{4285f4}{\textbf{39.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.32\%}}\\
+\textbf{Zinc (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.38\%}} & \textcolor[HTML]{4285f4}{\textbf{40.51\%}} & \textcolor[HTML]{4285f4}{\textbf{39.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.32\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**15.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.18\%}}}\\
-\textbf{US commodities} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
+\textbf{US commodities} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
 \textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{***15.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.82\%}}}\\
-\textbf{US commodities} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
+\textbf{US commodities} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
 \textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*16.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.33\%}}}\\
 \addlinespace
-\textbf{US commodities} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
+\textbf{US commodities} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
 \textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*21.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.72\%}}}\\
-\textbf{GB commodities} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
+\textbf{GB commodities} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
 \textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**19.95\%}}}\\
-\textbf{GB commodities} & \textbf{backwardation} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
+\textbf{GB commodities} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-14.05\%}}}\\
-\textbf{GB commodities} & \textbf{contango} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
+\textbf{GB commodities} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
 \bottomrule
@@
 \endgroup{}
-
-\newpage
 
@@
 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
-2013-2018). The results are discussed in Section~\ref{sec-results}.}
+2013-2018). The results are discussed in Section~\ref{sec-results} while
+Section~\ref{sec-taxonomy} details the taxonomy for the commodity assets
+considered.}
 
@@
 Section~\ref{sec-methods} while the results are discussed in
-Section~\ref{sec-results}.}
+Section~\ref{sec-results} and the taxonomy for the commodity assets
+considered is detailed in Section~\ref{sec-taxonomy}.}
 
@@
 whole period of interest (1997-2018). The results are discussed in
-Section~\ref{sec-results}.}
+Section~\ref{sec-results} while Section~\ref{sec-taxonomy} details the
+taxonomy for the commodity assets considered.}
 
@@
 
+\section{Appendix}\label{appendix}
+
+\subsection{Commodity assets taxonomy}\label{sec-taxonomy}
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}l}
+
+\caption{\label{tbl-assets-taxonomy}This table shows the detailed
+taxonomy for the thirty commodity assets considered in the study. The
+assets are classified by the country of residence of the exchange where
+they are traded as well as by sector and subsector according to the
+nature of the asset.}
+
+\tabularnewline
+
+\toprule
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}}\\
+\midrule
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{grains}}\\
+\textbf{Oats (XCBT)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{grains}\\
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{grains}}\\
+\textbf{Soybean oil (XCBT)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{grains}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{grains}}\\
+\addlinespace
+\textbf{Wheat-SRW (XCBT)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{grains}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{livestock}}\\
+\textbf{Cattle-live (XCME)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{livestock}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{livestock}}\\
+\textbf{Cocoa (IFUS)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{softs}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{softs}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{softs}\\
+\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{softs}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{softs}\\
+\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{softs}}\\
+\addlinespace
+\textbf{Natural gas (XNYM)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{energy} & \textcolor[HTML]{4285f4}{gas}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{energy}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{petroleum}}\\
+\textbf{Gasoline (XNYM)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{energy} & \textcolor[HTML]{4285f4}{petroleum}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{energy}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{petroleum}}\\
+\textbf{Copper (XCEC)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{precious}}\\
+\textbf{Silver (XCEC)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{precious}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{precious}}\\
+\textbf{Platinum (XNYM)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{precious}\\
+\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{GB}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{base}}\\
+\addlinespace
+\textbf{Copper (XLME)} & \textcolor[HTML]{4285f4}{GB} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
+\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{GB}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{base}}\\
+\textbf{Nickel-primary (XLME)} & \textcolor[HTML]{4285f4}{GB} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{GB}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{base}}\\
+\textbf{Zinc (XLME)} & \textcolor[HTML]{4285f4}{GB} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
+\newpage
+
 \renewcommand\refname{References}

### 2024-10-01 docs/paper.qmd
Incorporate asset pricing results

@@
 Financialisation appears to have affected multiple economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres.
-A vigorous legislative debate accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section @sec-background for a detailed discussion.] eventually led to regulatory changes in several individual markets.
+A vigorous legislative scrutiny accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section @sec-background for a detailed discussion.] eventually led to regulatory changes in several individual markets.
 In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation--the burning issue of the day--at the individual commodity market level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
 With the benefit of hindsight, this approach seems to lack a fundamental understanding of the phenomenon it endeavoured to study and which consequences it attempted to address.
-Financialisation was a phenomenon global in nature; through the channel of index investment it affected the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
+Financialisation was a phenomenon global in nature that, through the channel of index investment, affected the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
 Focusing on individual markets in this context thus seems limited.
@@
 We further consider a liquidity-based model following @hong_what_2012 who find that open interest growth has predictive power for individual commodity returns and again, using the latter measure as a proxy for individual commodity liquidity, we construct long-short factor mimicking portfolios.
+We study the performance of these models on a set of twenty-four US traded commodities and six GB traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008^[Starting point based on earlier studies [@baker_financialization_2021; @christoffersen_factor_2014].]); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).
 
@@
 
-We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008^[Starting point based on earlier studies [@baker_financialization_2021; @christoffersen_factor_2014].]); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).
-Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.
+Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation with the pattern extending to GB traded metals.
 
@@
 
-Over the first period the cross-sectional average returns during phases of **backwardation** for both the US and UK commodities are positive and overall higher than during phases of **contango**, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
-Over the second period this pattern reverses, with both the US and UK commodities having higher returns during phases of **contango** as opposed to **backwardation**.
+Over the first period the cross-sectional average returns during phases of **backwardation** for both the US and GB commodities are positive and overall higher than during phases of **contango**, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
+Over the second period this pattern reverses, with both the US and GB commodities having higher returns during phases of **contango** as opposed to **backwardation**.
 This change in pattern suggests the onset of financialisation altered the traditional risk shifting nature of hedger’s behaviour, implied by the Keynesian hypothesis.
@@
 The performance of the market factor is driven by agricultural and energy commodities in the first period while metals strongly contribute to the performance improvement observed over the second period.
-Similarly, the dramatic improvement of the CHP factor in the second period, is driven by the metals complex, particularly that of the long leg where they predominantly load.
-Average pairwise correlations amongst individual factors' best performing commodities increase across the board over the financialisation period, far beyond the average for the whole cross-section of US traded commodities.
-The increase is particularly strong for the long-short factors, in a relative sense, on which the metal complex loads significantly more during financialisation.
-This increase is due to the dramatic rise in average pairwise correlation amongst the US traded metals all of which exhibited high $R^{2}$ with respect to the CHP factor during financialisation which in turn is due to their common low level of CHP over this period.
-The CHP factor model thus seems able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialisation.
-We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period^[See section @sec-methods for further details.] and evaluating its performance on these selected commodities as well as on all US traded commodities.
-The results of this exercise provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
+The sector is also the driving force behind the dramatic improvement of the CHP factor during financialisation, led by the long leg of the factor on which metals predominantly load.
+The sector is similarly responsible for the improved performance of the short leg of the term structure factor of the period, on which the metals also predominantly load.
+Taken together, these results provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
 
@@
 
-The UK traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialisation.
-To that end, we examine the performance of the four factors on the six UK metals, when constructed from each set of factor picks.
-The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.
+The GB traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialisation.
+To that end, we examine the performance of the four factors on the six GB metals; the results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.
 
@@
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes.
-Commodity futures returns fell dramatically into the crisis and the pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as evidence of cross-market linkages with the UK traded commodity subset.
-The post-crisis results, in contrast, show a substantial pull-back in performance for the market factor across the board as well as evidence of decoupling between the US and UK markets.
+Commodity futures returns fell dramatically into the crisis and the pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as evidence of cross-market linkages with the GB traded commodity subset.
+The post-crisis results, in contrast, show a substantial pull-back in performance for the market factor across the board as well as evidence of decoupling between the US and GB markets.
 Besides, starting in the crisis the Keneysian paradigm of returns begins to revert with higher mean returns during low (**backwardation**) relative to high (**contango**) **CHP** phases and this pattern continues, more pronounced, over the post-crisis period.
-As pointed out in @basu_definancialisation, the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
+The financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
+Furthermore, both the average correlations and the pricing performance of the market factor are considerably stronger during phases of **contango** in contrast with the previous periods that showed no substantial difference between phases of **contango** and **backwardation** with this pattern being more pronounced for metal assets globally, both US and GB traded.
+These results document the emerging role/dominance of the contango regime post-crisis and could provide a valuable basis for further research.
 
@@
 For our NYMEX gasoline data series, we consider unleaded gasoline up to September 1^st^, 2006 and RBOB gasoline thereafter, date at which liquidity for the latter overtook that for the former.
-We also consider the UK metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).
+We also consider the GB metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).
 This sample cross-section of assets is further divided into groups for the purpose of the analysis by country (US, GB), sector (agriculturals, energy, metals) and by sub-sector (agriculturals: grains, livestock, softs; energy: gas, petroleum; metals: base, precious)^[See @sec-taxonomy for a detailed taxonomy of the commodity assets considered in the study.].
@@
 
-The returns pull-back continues into the post-crisis period (@tbl-stats-combined) with twenty-two US and four UK traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all UK metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and UK assets drop down to -0.2% and 2.7% respectively.
-Interestingly volatility also recedes substantially with twenty US assets and all UK metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
-The figures for the equally weighted portfolios of US and UK assets drop to 9.9% and 16.2% respectively, very close to pre-financialisation levels.
+The returns pull-back continues into the post-crisis period (@tbl-stats-combined) with twenty-two US and four GB traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all GB metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and GB assets drop down to -0.2% and 2.7% respectively.
+Interestingly volatility also recedes substantially with twenty US assets and all GB metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
+The figures for the equally weighted portfolios of US and GB assets drop to 9.9% and 16.2% respectively, very close to pre-financialisation levels.
 The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of **backwardation** relative to **contango**, more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
 The difference is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
-The pattern is more pronounced for the UK traded subset with all six assets showing higher mean returns in **backwardation** with the difference significant at the 1% level for Nickel-primary (XLME), 5% level for Aluminium (XLME) and 10% level for Zinc (XLME).
-It also extends to equally weighted portfolios of US and UK traded assets that both show higher mean returns during **backwardation** with the difference significant at the 5% level for the UK portfolio and the figure close to the 10% level significance threshold for the portfolio of US assets.
+The pattern is more pronounced for the GB traded subset with all six assets showing higher mean returns in **backwardation** with the difference significant at the 1% level for Nickel-primary (XLME), 5% level for Aluminium (XLME) and 10% level for Zinc (XLME).
+It also extends to equally weighted portfolios of US and GB traded assets that both show higher mean returns during **backwardation** with the difference significant at the 5% level for the GB portfolio and the figure close to the 10% level significance threshold for the portfolio of US assets.
 Volatilities are overall higher in **contango** although less so than over the previous period with seventeen US commodities showing higher figures over **contango** against twenty-three in the crisis period.
-The pattern extends to three of the six UK traded metals with the difference significant at the 1% level for Copper (XLME) and Tin (XLME) and at the 5% level for Zinc (XLME) while differences are not significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit higher volatility over **backwardation** phases.
-Equally weighted portfolios of US and UK traded assets on the other hand both show higher volatility in **contango** with the difference significant at the 1% level for both.
+The pattern extends to three of the six GB traded metals with the difference significant at the 1% level for Copper (XLME) and Tin (XLME) and at the 5% level for Zinc (XLME) while differences are not significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit higher volatility over **backwardation** phases.
+Equally weighted portfolios of US and GB traded assets on the other hand both show higher volatility in **contango** with the difference significant at the 1% level for both.
 Over the financialisation period in contrast volatilities were predominantly higher in **backwardation** for US traded assets with fourteen commodities showing higher volatility figures in these phases; the post-crisis pattern of results for volatilities thus likewise shows signs of reversion to pre-financialisation standards.

### 2024-10-02 docs/paper.qmd
Incorporate correlation results

@@
 Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation with the pattern extending to GB traded metals.
-
-\medskip
-
 Over the first period the cross-sectional average returns during phases of **backwardation** for both the US and GB commodities are positive and overall higher than during phases of **contango**, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
@@
 
-@goldstein_speculation_2014 and @goldstein_commodity_2022 argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
-Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger’s positions (Keynesian perspective, theory of normal backwardation: @keynes_treatise_1930, @hicks_value_1939, @houthakker_speculators_1957, @telser_futures_1958), as well our term structure factor, based on backwardation as measured by roll yield (Working's perspective, theory of storage: @working_price_1933, @kaldor_speculation_1939, @working_theory_1948, @brennan_supply_1958, @cootner_returns_1960, @weymar_supply_1966, @danthine_information_1978, @turnovsky_determination_1983, @schwartz_stochastic_1997), to be best suited to measure the impact of financialisation.
-We analyse the pricing dynamics over the different periods by first studying the time series explanatory performance of the various factors on all the US traded commodities with the factors constructed using the latter set of commodities.
-The market-based factor outperforms the other three in the first period and, although its performance increases over the financialisation period, that of the CHP factor shows a greater improvement in a relative sense.
-The performance of the market factor is driven by agricultural and energy commodities in the first period while metals strongly contribute to the performance improvement observed over the second period.
-The sector is also the driving force behind the dramatic improvement of the CHP factor during financialisation, led by the long leg of the factor on which metals predominantly load.
-The sector is similarly responsible for the improved performance of the short leg of the term structure factor of the period, on which the metals also predominantly load.
-Taken together, these results provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
+These entered the commodity spectrum en masse with across-the-board index type positions propping the transition of the complex from a collection of idiosyncratic markets towards a more congruent ensemble akin to an asset class.
+In this context of heightened cross-asset market participation the issue of interconnectedness stands out as paramount and we strive to investigate it by first examining the correlation structure of our sample set of assets at the global, country, sector and subsector levels.
+Our results indicate higher interdependence within the full cross-section of commodities over the financialisation period, consistent with both the empirical and theoretical literature.
+The increase appears to be driven by the US metals sector, a new observation to the best of our knowledge, and, unlike individual commodity returns, does not seem to be regime-driven, as a similar pattern of results is observed across phases of **backwardation** and **contango**.
 
@@
 
+@goldstein_speculation_2014 and @goldstein_commodity_2022 argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
+Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger’s positions (Keynesian perspective, theory of normal backwardation: @keynes_treatise_1930, @hicks_value_1939, @houthakker_speculators_1957, @telser_futures_1958), as well our term structure factor, based on backwardation as measured by roll yield (Working's perspective, theory of storage: @working_price_1933, @kaldor_speculation_1939, @working_theory_1948, @brennan_supply_1958, @cootner_returns_1960, @weymar_supply_1966, @danthine_information_1978, @turnovsky_determination_1983, @schwartz_stochastic_1997), to be best suited to measure the impact of financialisation.
+We analyse the pricing dynamics over the different periods by first studying the time series explanatory performance of the various factors on our commodity assets sample.
+The market-based factor outperforms the other three in the first period and, although its performance increases over the financialisation period, that of the CHP factor shows a greater improvement in a relative sense.
+The performance of the market factor is driven by agricultural and energy commodities in the first period while metals strongly contribute to the performance improvement observed over the second period.
+The sector is also the driving force behind the dramatic improvement of the CHP factor during financialisation, led by its long leg on which metals predominantly load.
+The sector is similarly responsible for the improved performance of the short leg of the term structure factor of the period, on which the metals also predominantly load.
+Taken together, these results provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
 The GB traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialisation.
@@
 
+\bigskip
+
+The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes.
+Commodity futures returns fell dramatically while the symmetry between the dynamics of CHP and **CHP**'s' explanatory power on individual commodity returns breaks with both now seemingly converging.
+The correlation structure is also affected with evidence of an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation, consistent with the greater interdependence between equity and commodity markets over the period documented in the literature.
+The pricing results further indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as evidence of cross-market linkages with the GB traded commodity subset.
+The onset of the financial crisis thus seems to have had a global impact on the commodity complex in contrast with financialisation, much more closely related to the metals sector.
+
 \medskip
 
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes.
-Commodity futures returns fell dramatically into the crisis and the pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as evidence of cross-market linkages with the GB traded commodity subset.
-The post-crisis results, in contrast, show a substantial pull-back in performance for the market factor across the board as well as evidence of decoupling between the US and GB markets.
-Besides, starting in the crisis the Keneysian paradigm of returns begins to revert with higher mean returns during low (**backwardation**) relative to high (**contango**) **CHP** phases and this pattern continues, more pronounced, over the post-crisis period.
-The financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
-Furthermore, both the average correlations and the pricing performance of the market factor are considerably stronger during phases of **contango** in contrast with the previous periods that showed no substantial difference between phases of **contango** and **backwardation** with this pattern being more pronounced for metal assets globally, both US and GB traded.
-These results document the emerging role/dominance of the contango regime post-crisis and could provide a valuable basis for further research.
+The returns pull-back continues into the post-crisis period, interestingly amidst a lower volatility environment, suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed during financialisation.
+The pattern of reversion toward the pre-financialisation Keynesian paradigm continues stronger with mean returns higher during phases of **backwardation** relative to **contango** and the difference more pronounced than over the crisis period.
+In contrast to the crisis period when they seemed to be converging, the pricing performance of CHP and **CHP** now part way, seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a reversion to legacy commodity specific dynamics.
+The pull back extends to the correlation structure with an across-the-board decrease in average pairwise correlations down to levels below those observed during financialisation.
+The average market factor beta for the entire cross-section shows a similar pattern, dropping down below the level observed during financialization with the decline seemingly driven by the metals sector, particularly the GB traded segment.
+The pattern extends to the pricing performance of all factors that drops below levels observed during financialisation while the gap between the legs of the long-short factors remains narrower than observed during that period.
+Moreover, both the average correlations and the pricing performance of the market factor are considerably stronger during **contango** phases, unlike previous periods, which showed no substantial difference between regimes with especially pronounced for metal assets globally, both US and GB traded.
+These results document the emerging role/dominance of the **contango** regime post-crisis and could provide a valuable basis for further research.
 
@@
 With the benefit of hindsight, it appears this approach was perhaps too narrow, and it now seems necessary to address the phenomenon from a broader perspective.
-Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and our commodity futures asset pricing factors based approach seems able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seems to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggering a reversion to pre-financialisation dynamics.
+Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and both our cross-sectional approach to examining interconnectedness in the complex as well as our commodity futures asset pricing framework together seem able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seem to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggering a reversion to pre-financialisation dynamics.
 
@@
 
-The average pairwise correlation for the entire cross-section of commodities considered in the study (@tbl-correlations-periods) increases further into the crisis to 0.28 indicating an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation.
+The average pairwise correlation for the entire set of sample assets increases further into the crisis to 0.28 (@tbl-correlations-periods) indicating an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation.
 The result is consistent with the greater interdependence between equity and commodity markets over this period documented in @silvennoinen_financialisation_2013.
 The figure for the US traded section of the metals sector only progresses modestly to 0.59 after peaking at 0.63 in 2006 (@tbl-correlations-years).
-In contrast, the GB traded assets see a sharp increase to over 0.65 in the crisis starting in 2007 up to a peak of 0.69 in 2010.
-The agricultural sector on the other hand shows a substantial rise in the crisis period with the sharpest increase in 2008 when the average pairwise correlation for the sector jumps to 0.30.
-Meanwhile, the energy sector also shows a notable progression starting in 2007 and peaking at 0.63 in 2008 before levelling back down over the rest of the period.
+In contrast, the GB traded assets see a sharp increase to over 0.65 in the crisis starting in 2007 up to a peak of 0.69 in 2010, and so does the agricultural sector with the sharpest increase in 2008 when the average pairwise correlation for the sector jumps to 0.30.
+The energy sector also shows a substantial progression starting in 2007 and peaking at 0.63 in 2008 before levelling back down over the rest of the period.
 The onset of the financial crisis seems therefore to have had an across the board impact on the interdependence of commodities in contrast with financialisation, much more closely related to the metals sector.
@@
 
-In a similar vein, the average market factor beta for the entire cross-section drops down to 0.94 (@tbl-regressions-index), below the level observed during financialization.
+Similarly, the average market factor beta for the entire cross-section drops down to 0.94 (@tbl-regressions-index), below the level observed during financialization.
 The decline seems driven by the metals sector, particularly the GB traded segment, with the figures for the US and GB traded assets at 0.91 and 0.72, down from 1.12 and 1.18, respectively.
@@
 Taken together, these results indicate some recent changes in the correlation structure within the sector and along with the decline in interdependence in the commodity sector at large documented above, this observation could form a valuable basis for future research.
-These findings further providence additional evidence that the interdependence effects of financialization seems to have been strongest for the entire cross-section of the metals sector with a lesser impact for the other sectors.
+These findings providence additional evidence that the interdependence effects of financialization seems to have been strongest for the entire cross-section of the metals sector with a lesser impact for the other sectors.
 

### 2024-10-02 docs/paper.qmd
First draft introduction

@@
   In the early 2000s institutional investors entered the commodity futures markets en masse with passive, long only, index type positions in sharp contrast with those typically assumed by traditional expert participants.
-A heated public debate soon erupted over the perceived consequences of the phenomenon--commonly referred to as "financialisation"—and, in response to immediate policy concerns, the matter was thrust onto the academic sphere as a burning issue.
+A heated public debate soon erupted over the perceived consequences of the phenomenon---commonly referred to as "financialisation"---and, in response to immediate policy concerns, the matter was thrust onto the academic sphere as a burning issue.
 With the benefit of hindsight it now seems that the academic debate was framed rather narrowly, used contentious research methods, and eventually led to regulatory changes that were therefore perhaps unwarranted.
@@
 Financialisation appears to have affected multiple economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres.
-A vigorous legislative scrutiny accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section @sec-background for a detailed discussion.] eventually led to regulatory changes in several individual markets.
-In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation--the burning issue of the day--at the individual commodity market level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
+A rigorous legislative scrutiny accompanied by a vigorous policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section @sec-background for a detailed discussion.] eventually led to regulatory changes in several individual markets.
+In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation---the burning issue of the day---at the individual commodity market level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
 With the benefit of hindsight, this approach seems to lack a fundamental understanding of the phenomenon it endeavoured to study and which consequences it attempted to address.
@@
 Besides, some of these techniques since proved controversial and seem to produce results the quality of which may fall short of the standards that may reasonably be expected to lay the ground for legislative action.
-Although appealing, for it comes with the promise of prompt "significant" results, this approach misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of market fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure [@keynes_treatise_1930; @hicks_value_1939].
+Although appealing, for it comes with the promise of prompt "significant" results, this approach misses a critical corollary of the substantial advent of a new category of players in a (set of) market(s): the alteration of fundamentals it potentially induces, best observed in this context through the lens of commercial hedging pressure [@keynes_treatise_1930; @hicks_value_1939].
 While essential to the understanding of the phenomenon, the global nature of financialisation and its impact on market fundamentals therefore appear to have been originally overlooked and another approach, perhaps more refined, seems warranted.
@@
 We strive to provide one in this study by taking a fundamentally different empirical perspective that is broader in scope.
-We consider the entire cross-section of actively traded commodities on futures markets and use a futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations.
+We examine the interconnectedness of the commodity complex at the cross-sectional level, considering the entire cross-section of actively traded commodities on futures markets and use a bespoke futures-based asset pricing framework that includes factors constructed using both theoretical fundamentals and liquidity considerations.
 The global nature of financialisation makes cross-sectional co-movement a cornerstone issue that the direct impact of increased market participation alone might not be able to fully explain for it potentially had deeper effects, for example on market fundamentals as our results suggest.
@@
 
-By grouping together assets by shared attribute dynamics in common portfolios, asset pricing techniques--and factor models in particular--are well suited to study co-movement [@fama_common_1993; @carhart_persistence_1997; @asness_devil_2013; @fama_five_factor_2015; @hou_digesting_2015; @asness_fact_2015; @frazzini_betting_2014; @asness_quality_2019].
+By grouping together assets by shared attribute dynamics in common portfolios, asset pricing techniques---and factor models in particular---are well suited to study co-movement [@fama_common_1993; @carhart_persistence_1997; @asness_devil_2013; @fama_five_factor_2015; @hou_digesting_2015; @asness_fact_2015; @frazzini_betting_2014; @asness_quality_2019].
 Careful, theory-based, attribute selection further enables a refined analysis of market fundamentals [@schwartz_short_2000; @miffre_momentum_2007; @gorton_fundamentals_2012; @cortazar_commodity_2013; @yang_investment_2013; @daskalaki_factors_2014; @szymanowska_anatomy_2014; @fernandez_skewness_2018; @bakshi_understanding_2019; @boons_basis_2019; @sakkas_factor_2020].
@@
 The increase is even more pronounced for an equally weighted portfolio of GB traded assets (metals), 2.47% (not significant) to 21.8% (significant at the 10% level), which sets out the global nature of the phenomenon.
-Most commodities show a higher mean return while five--Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)--show a lower figure with five significant figures--Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)--against none pre-financialisation.
+Most commodities show a higher mean return while five---Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)---show a lower figure with five significant figures---Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)---against none pre-financialisation.
 Sugar-#11 wins the race with a mean return increasing from -4.6% to 24.9% followed by copper with sizeable increases for both markets: 1.5% to 28.2% (XCEC) and 0.5% to 28.6% (XLME).

### 2024-10-02 docs/paper.tex

@@
 participants. A heated public debate soon erupted over the perceived
-consequences of the phenomenon--commonly referred to as
+consequences of the phenomenon---commonly referred to as
 ``financialisation''---and, in response to immediate policy concerns,
@@
 and its impact has been hotly debated in the policy, legislative,
-regulatory, and academic spheres. A vigorous legislative debate
-accompanied by an equally intense policy and academic debate across a
-number of disciplines about the perceived effects on commodity prices of
-the unprecedented inflow of institutional funds brought into commodity
+regulatory, and academic spheres. A rigorous legislative scrutiny
+accompanied by a vigorous policy and academic debate across a number of
+disciplines about the perceived effects on commodity prices of the
+unprecedented inflow of institutional funds brought into commodity
 futures markets by new index type investors\footnote{See section
@@
 In response to immediate policy concerns, the academic debate was
-initially framed rather narrowly around adequacy of speculation--the
-burning issue of the day--at the individual commodity market level and
+initially framed rather narrowly around adequacy of speculation---the
+burning issue of the day---at the individual commodity market level and
 the ensuing academic analysis focused on the more mechanical effects of
@@
 study and which consequences it attempted to address.\\
-Financialisation was a phenomenon global in nature; through the channel
-of index investment it affected the whole cross-section of liquid
+Financialisation was a phenomenon global in nature that, through the
+channel of index investment, affected the whole cross-section of liquid
 commodities at once, eventually spurring its transition away from a
@@
 approach misses a critical corollary of the substantial advent of a new
-category of players in a (set of) market(s): the alteration of market
+category of players in a (set of) market(s): the alteration of
 fundamentals it potentially induces, best observed in this context
@@
 We strive to provide one in this study by taking a fundamentally
-different empirical perspective that is broader in scope. We consider
-the entire cross-section of actively traded commodities on futures
-markets and use a futures-based asset pricing framework that includes
-factors constructed using both theoretical fundamentals and liquidity
-considerations.\\
+different empirical perspective that is broader in scope. We examine the
+interconnectedness of the commodity complex at the cross-sectional
+level, considering the entire cross-section of actively traded
+commodities on futures markets and use a bespoke futures-based asset
+pricing framework that includes factors constructed using both
+theoretical fundamentals and liquidity considerations.\\
 The global nature of financialisation makes cross-sectional co-movement
@@
 individual commodity liquidity, we construct long-short factor mimicking
-portfolios.
-
-\bigskip
-\bigskip
-
+portfolios.\\
 We study the performance of these models on a set of twenty-four US
-traded commodities and six UK traded (London Metal Exchange) base metals
+traded commodities and six GB traded (London Metal Exchange) base metals
 over the 1997/2018 period that we divide into four distinct sub-periods:
@@
 financial crisis and aftermath, including loose monetary policy regimes
-that followed (2008/2013); and post-crisis (2014-2018).\\
+that followed (2008/2013); and post-crisis (2014-2018).
+
+\bigskip
+\bigskip
+
 Consistent with earlier studies, we observe that mean returns for the US
 traded commodities are sharply higher over the financialisation period
-compared to pre-financialisation and this pattern extends to UK traded
-metals.
-
-\medskip
-
+compared to pre-financialisation with the pattern extending to GB traded
+metals.\\
 Over the first period the cross-sectional average returns during phases
-of \textbf{backwardation} for both the US and UK commodities are
+of \textbf{backwardation} for both the US and GB commodities are
 positive and overall higher than during phases of \textbf{contango},
@@
 hedging pressure hypothesis. Over the second period this pattern
-reverses, with both the US and UK commodities having higher returns
+reverses, with both the US and GB commodities having higher returns
 during phases of \textbf{contango} as opposed to \textbf{backwardation}.
@@
 leading hedgers to become liquidity providers.
+
+\medskip
+
+These entered the commodity spectrum en masse with across-the-board
+index type positions propping the transition of the complex from a
+collection of idiosyncratic markets towards a more congruent ensemble
+akin to an asset class. In this context of heightened cross-asset market
+participation the issue of interconnectedness stands out as paramount
+and we strive to investigate it by first examining the correlation
+structure of our sample set of assets at the global, country, sector and
+subsector levels. Our results indicate higher interdependence within the
+full cross-section of commodities over the financialisation period,
+consistent with both the empirical and theoretical literature. The
+increase appears to be driven by the US metals sector, a new observation
+to the best of our knowledge, and, unlike individual commodity returns,
+does not seem to be regime-driven, as a similar pattern of results is
+observed across phases of \textbf{backwardation} and \textbf{contango}.
 
@@
 studying the time series explanatory performance of the various factors
-on all the US traded commodities with the factors constructed using the
-latter set of commodities. The market-based factor outperforms the other
-three in the first period and, although its performance increases over
-the financialisation period, that of the CHP factor shows a greater
+on our commodity assets sample. The market-based factor outperforms the
+other three in the first period and, although its performance increases
+over the financialisation period, that of the CHP factor shows a greater
 improvement in a relative sense. The performance of the market factor is
@@
 metals strongly contribute to the performance improvement observed over
-the second period. Similarly, the dramatic improvement of the CHP factor
-in the second period, is driven by the metals complex, particularly that
-of the long leg where they predominantly load. Average pairwise
-correlations amongst individual factors' best performing commodities
-increase across the board over the financialisation period, far beyond
-the average for the whole cross-section of US traded commodities. The
-increase is particularly strong for the long-short factors, in a
-relative sense, on which the metal complex loads significantly more
-during financialisation. This increase is due to the dramatic rise in
-average pairwise correlation amongst the US traded metals all of which
-exhibited high \(R^{2}\) with respect to the CHP factor during
-financialisation which in turn is due to their common low level of CHP
-over this period. The CHP factor model thus seems able to establish the
-strengthening link between a non-price attribute and price dynamics in
-the US metal sub-sector during financialisation.\\
-We explore this issue further by constructing the four factors
-independently with the top eight commodities for a given factor (factor
-picks) in each period\footnote{See section Section~\ref{sec-methods} for
-  further details.} and evaluating its performance on these selected
-commodities as well as on all US traded commodities. The results of this
-exercise provide evidence of convergence of Keynesian and Working's
-theories of the term structure in detecting price co-movement during
-financialisation and strongly suggest that the term structure related
-attributes (hedging pressure/roll) co-movement and price co-movement
-link was concentrated in the metals sub-sector.
-
-\medskip
-
-The UK traded base metals provide a useful set of assets to test how
+the second period. The sector is also the driving force behind the
+dramatic improvement of the CHP factor during financialisation, led by
+its long leg on which metals predominantly load. The sector is similarly
+responsible for the improved performance of the short leg of the term
+structure factor of the period, on which the metals also predominantly
+load. Taken together, these results provide evidence of convergence of
+Keynesian and Working's theories of the term structure in detecting
+price co-movement during financialisation and strongly suggest that the
+term structure related attributes (hedging pressure/roll) co-movement
+and price co-movement link was concentrated in the metals sub-sector.\\
+The GB traded base metals provide a useful set of assets to test how
 widespread were the changes in pricing dynamics brought about by the
 onset of financialisation. To that end, we examine the performance of
-the four factors on the six UK metals, when constructed from each set of
-factor picks. The results show that there was co-movement in global
-metals returns in the second period and that this co-movement could be
-detected by our term structure related models, particularly so by our
-hedging pressure-based model.
-
-\medskip
+the four factors on the six GB metals; the results show that there was
+co-movement in global metals returns in the second period and that this
+co-movement could be detected by our term structure related models,
+particularly so by our hedging pressure-based model.
+
+\bigskip
 
@@
 followed, on the other hand, also appear to have induced significant
-changes. Commodity futures returns fell dramatically into the crisis and
-the pricing results indicate the emergence of a systematic factor across
-the entire cross-section of the US commodities as well as evidence of
-cross-market linkages with the UK traded commodity subset. The
-post-crisis results, in contrast, show a substantial pull-back in
-performance for the market factor across the board as well as evidence
-of decoupling between the US and UK markets. Besides, starting in the
-crisis the Keneysian paradigm of returns begins to revert with higher
-mean returns during low (\textbf{backwardation}) relative to high
-(\textbf{contango}) \textbf{CHP} phases and this pattern continues, more
-pronounced, over the post-crisis period. As pointed out in
-\citet{basu_definancialisation}, the financial crisis and ensuing
-accommodative monetary policy therefore seem to have initiated a process
-of reversion toward pre-financialisation fundamentals in the global
-commodity futures complex.
+changes. Commodity futures returns fell dramatically while the symmetry
+between the dynamics of CHP and \textbf{CHP}'s' explanatory power on
+individual commodity returns breaks with both now seemingly converging.
+The correlation structure is also affected with evidence of an
+intensification of the higher interdependence within the full
+cross-section of commodities prompted by financialisation, consistent
+with the greater interdependence between equity and commodity markets
+over the period documented in the literature. The pricing results
+further indicate the emergence of a systematic factor across the entire
+cross-section of the US commodities as well as evidence of cross-market
+linkages with the GB traded commodity subset. The onset of the financial
+crisis thus seems to have had a global impact on the commodity complex
+in contrast with financialisation, much more closely related to the
+metals sector.
+
+\medskip
+
+The returns pull-back continues into the post-crisis period,
+interestingly amidst a lower volatility environment, suggesting that
+investment outflows from the commodity futures complex have had a lower
+impact on volatility than the corresponding inflows witnessed during
+financialisation. The pattern of reversion toward the
+pre-financialisation Keynesian paradigm continues stronger with mean
+returns higher during phases of \textbf{backwardation} relative to
+\textbf{contango} and the difference more pronounced than over the
+crisis period. In contrast to the crisis period when they seemed to be
+converging, the pricing performance of CHP and \textbf{CHP} now part
+way, seemingly reverting to the Keynesian paradigm observed
+pre-financialisation, further suggesting a reversion to legacy commodity
+specific dynamics. The pull back extends to the correlation structure
+with an across-the-board decrease in average pairwise correlations down
+to levels below those observed during financialisation. The average
+market factor beta for the entire cross-section shows a similar pattern,
+dropping down below the level observed during financialization with the
+decline seemingly driven by the metals sector, particularly the GB
+traded segment. The pattern extends to the pricing performance of all
+factors that drops below levels observed during financialisation while
+the gap between the legs of the long-short factors remains narrower than
+observed during that period.\\
+Moreover, both the average correlations and the pricing performance of
+the market factor are considerably stronger during \textbf{contango}
+phases, unlike previous periods, which showed no substantial difference
+between regimes with especially pronounced for metal assets globally,
+both US and GB traded. These results document the emerging
+role/dominance of the \textbf{contango} regime post-crisis and could
+provide a valuable basis for further research.
 
@@
 substantially in quite different ways over the financialisation and the
-financial crisis periods and our commodity futures asset pricing factors
-based approach seems able to provide new insights into the nature of
-these changes: financialisation was a phenomenon endogenous to the
-commodity markets transmitted via the commodity futures markets and
-which effects were particularly strong for the metals sector while the
-crisis and its aftermath seems to have delivered an exogenous shock
-across the entire cross-section of liquid commodities and thereby
-potentially triggering a reversion to pre-financialisation dynamics.
+financial crisis periods and both our cross-sectional approach to
+examining interconnectedness in the complex as well as our commodity
+futures asset pricing framework together seem able to provide new
+insights into the nature of these changes: financialisation was a
+phenomenon endogenous to the commodity markets transmitted via the
+commodity futures markets and which effects were particularly strong for
+the metals sector while the crisis and its aftermath seem to have
+delivered an exogenous shock across the entire cross-section of liquid
+commodities and thereby potentially triggering a reversion to
+pre-financialisation dynamics.
 
@@
 liquidity for the latter overtook that for the former.\\
-We also consider the UK metal complex with aluminium (XLME), copper
+We also consider the GB metal complex with aluminium (XLME), copper
 (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc
@@
 By grouping together assets by shared attribute dynamics in common
-portfolios, asset pricing techniques--and factor models in
-particular--are well suited to study co-movement
+portfolios, asset pricing techniques---and factor models in
+particular---are well suited to study co-movement
 \citep{fama_common_1993, carhart_persistence_1997, asness_devil_2013, fama_five_factor_2015, hou_digesting_2015, asness_fact_2015, frazzini_betting_2014, asness_quality_2019}.
@@
 level), which sets out the global nature of the phenomenon. Most
-commodities show a higher mean return while five--Lumber (XCME), Natural
-gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary
-(XLME)--show a lower figure with five significant figures--Crude oil-WTI
-(XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined
-(XLME)--against none pre-financialisation. Sugar-\#11 wins the race with
-a mean return increasing from -4.6\% to 24.9\% followed by copper with
-sizeable increases for both markets: 1.5\% to 28.2\% (XCEC) and 0.5\% to
-28.6\% (XLME).\\
+commodities show a higher mean return while five---Lumber (XCME),
+Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary
+(XLME)---show a lower figure with five significant figures---Crude
+oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and
+Tin-refined (XLME)---against none pre-financialisation. Sugar-\#11 wins
+the race with a mean return increasing from -4.6\% to 24.9\% followed by
+copper with sizeable increases for both markets: 1.5\% to 28.2\% (XCEC)
+and 0.5\% to 28.6\% (XLME).\\
 The pattern of results for volatilities is similar although the increase
@@
 
-The average pairwise correlation for the entire cross-section of
-commodities considered in the study
-(Table~\ref{tbl-correlations-periods}) increases further into the crisis
-to 0.28 indicating an intensification of the higher interdependence
-within the full cross-section of commodities prompted by
-financialisation. The result is consistent with the greater
+The average pairwise correlation for the entire set of sample assets
+increases further into the crisis to 0.28
+(Table~\ref{tbl-correlations-periods}) indicating an intensification of
+the higher interdependence within the full cross-section of commodities
+prompted by financialisation. The result is consistent with the greater
 interdependence between equity and commodity markets over this period
@@
 In contrast, the GB traded assets see a sharp increase to over 0.65 in
-the crisis starting in 2007 up to a peak of 0.69 in 2010. The
-agricultural sector on the other hand shows a substantial rise in the
-crisis period with the sharpest increase in 2008 when the average
-pairwise correlation for the sector jumps to 0.30. Meanwhile, the energy
-sector also shows a notable progression starting in 2007 and peaking at
-0.63 in 2008 before levelling back down over the rest of the period. The
-onset of the financial crisis seems therefore to have had an across the
-board impact on the interdependence of commodities in contrast with
+the crisis starting in 2007 up to a peak of 0.69 in 2010, and so does
+the agricultural sector with the sharpest increase in 2008 when the
+average pairwise correlation for the sector jumps to 0.30. The energy
+sector also shows a substantial progression starting in 2007 and peaking
+at 0.63 in 2008 before levelling back down over the rest of the period.
+The onset of the financial crisis seems therefore to have had an across
+the board impact on the interdependence of commodities in contrast with
 financialisation, much more closely related to the metals sector.
@@
 The returns pull-back continues into the post-crisis period
-(Table~\ref{tbl-stats-combined}) with twenty-two US and four UK traded
+(Table~\ref{tbl-stats-combined}) with twenty-two US and four GB traded
 assets showing lower mean returns relative to the crisis while the same
-number of US commodities and all UK metals show lower figures relative
+number of US commodities and all GB metals show lower figures relative
 to the financialisation period; mean returns for equally weighted
-portfolios of US and UK assets drop down to -0.2\% and 2.7\%
+portfolios of US and GB assets drop down to -0.2\% and 2.7\%
 respectively. Interestingly volatility also recedes substantially with
-twenty US assets and all UK metals showing lower volatility figures
+twenty US assets and all GB metals showing lower volatility figures
 relative to both the crisis and financialisation periods suggesting that
@@
 financialisation period. The figures for the equally weighted portfolios
-of US and UK assets drop to 9.9\% and 16.2\% respectively, very close to
+of US and GB assets drop to 9.9\% and 16.2\% respectively, very close to
 pre-financialisation levels.\\
@@
 showing higher figures over phases of \textbf{contango}. The pattern is
-more pronounced for the UK traded subset with all six assets showing
+more pronounced for the GB traded subset with all six assets showing
 higher mean returns in \textbf{backwardation} with the difference
@@
 Aluminium (XLME) and 10\% level for Zinc (XLME). It also extends to
-equally weighted portfolios of US and UK traded assets that both show
+equally weighted portfolios of US and GB traded assets that both show
 higher mean returns during \textbf{backwardation} with the difference
-significant at the 5\% level for the UK portfolio and the figure close
+significant at the 5\% level for the GB portfolio and the figure close
 to the 10\% level significance threshold for the portfolio of US assets.
@@
 higher figures over \textbf{contango} against twenty-three in the crisis
-period. The pattern extends to three of the six UK traded metals with
+period. The pattern extends to three of the six GB traded metals with
 the difference significant at the 1\% level for Copper (XLME) and Tin
@@
 that exhibit higher volatility over \textbf{backwardation} phases.
-Equally weighted portfolios of US and UK traded assets on the other hand
+Equally weighted portfolios of US and GB traded assets on the other hand
 both show higher volatility in \textbf{contango} with the difference
@@
 
-In a similar vein, the average market factor beta for the entire
-cross-section drops down to 0.94 (Table~\ref{tbl-regressions-index}),
-below the level observed during financialization. The decline seems
-driven by the metals sector, particularly the GB traded segment, with
-the figures for the US and GB traded assets at 0.91 and 0.72, down from
-1.12 and 1.18, respectively. Meanwhile, the pricing performance of the
-market factor also retreats to below financialisation levels with the
-average \(R^{2}\) for the entire cross-section dropping down to 14.7\%
+Similarly, the average market factor beta for the entire cross-section
+drops down to 0.94 (Table~\ref{tbl-regressions-index}), below the level
+observed during financialization. The decline seems driven by the metals
+sector, particularly the GB traded segment, with the figures for the US
+and GB traded assets at 0.91 and 0.72, down from 1.12 and 1.18,
+respectively. Meanwhile, the pricing performance of the market factor
+also retreats to below financialisation levels with the average
+\(R^{2}\) for the entire cross-section dropping down to 14.7\%
 (Table~\ref{tbl-regressions-factors}). All sectors seem affected with
@@
 a valuable basis for future research.\\
-These findings further providence additional evidence that the
-interdependence effects of financialization seems to have been strongest
-for the entire cross-section of the metals sector with a lesser impact
-for the other sectors.
+These findings providence additional evidence that the interdependence
+effects of financialization seems to have been strongest for the entire
+cross-section of the metals sector with a lesser impact for the other
+sectors.
 

### 2024-10-03 paper.qmd
Deploying to gh-pages from @ bautheac/financialisation-co-movement@5f931608ae9f9c663575798052089bbbe19c54fa 🚀

@@
   In the early 2000s institutional investors entered the commodity futures markets en masse with passive, long only, index type positions in sharp contrast with those typically assumed by traditional expert participants.
-A heated public debate soon erupted over the perceived consequences of the phenomenon--commonly referred to as "financialisation"—and, in response to immediate policy concerns, the matter was thrust onto the academic sphere as a burning issue.
+A heated public debate soon erupted over the perceived consequences of the phenomenon---commonly referred to as "financialisation"---and, in response to immediate policy concerns, the matter was thrust onto the academic sphere as a burning issue.
 With the benefit of hindsight it now seems that the academic debate was framed rather narrowly, used contentious research methods, and eventually led to regulatory changes that were therefore perhaps unwarranted.
 In contrast, we take a broader approach where we consider a large cross-section of liquid commodities as suggested by the nature of financialisation that comprehends commodity futures as an asset class.
-Using a bespoke asset pricing factors based framework we study the issue through the lens of co-movement and find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
+We examine the cross-sectional interconnectedness of these assets and uses a bespoke asset pricing factors based framework to study the issue through the lens of co-movement and find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals.
@@
 Financialisation appears to have affected multiple economic sectors, including agriculture and energy, and its impact has been hotly debated in the policy, legislative, regulatory, and academic spheres.
-A vigorous legislative debate accompanied by an equally intense policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section @sec-background for a detailed discussion.] eventually led to regulatory changes in several individual markets.
-In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation--the burning issue of the day--at the individual commodity market level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
+A rigorous legislative scrutiny accompanied by a vigorous policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section @sec-background for a detailed discussion.] eventually led to regulatory changes in several individual markets.
+In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation---the burning issue of the day---at the individual commodity market level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
 With the benefit of hindsight, this approach seems to lack a fundamental understanding of the phenomenon it endeavoured to study and which consequences it attempted to address.
-Financialisation was a phenomenon global in nature; through the channel of index investment it affected the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
+Financialisation was a phenomenon global in nature that, through the channel of index investment, affected the whole cross-section of liquid commodities at once, eventually spurring its transition away from a collection of idiosyncratic markets to its emergence as an asset class.
 Focusing on individual markets in this context thus seems limited.
@@
 
-We study the performance of these models on a set of twenty-four US traded commodities and six UK traded (London Metal Exchange) base metals over the 1997/2018 period that we divide into four distinct sub-periods: pre-financialisation (1997/2003); financialisation (2004/2008^[Starting point based on earlier studies [@baker_financialization_2021; @christoffersen_factor_2014].]); financial crisis and aftermath, including loose monetary policy regimes that followed (2008/2013); and post-crisis (2014-2018).
-Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation and this pattern extends to UK traded metals.
-
-\medskip
-
-Over the first period the cross-sectional average returns during phases of **backwardation** for both the US and UK commodities are positive and overall higher than during phases of **contango**, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
-Over the second period this pattern reverses, with both the US and UK commodities having higher returns during phases of **contango** as opposed to **backwardation**.
+Consistent with earlier studies, we observe that mean returns for the US traded commodities are sharply higher over the financialisation period compared to pre-financialisation with the pattern extending to GB traded metals.
+Over the first period the cross-sectional average returns during phases of **backwardation** for both the US and GB commodities are positive and overall higher than during phases of **contango**, providing broad support for an aggregate version of the Keynesian hedging pressure hypothesis.
+Over the second period this pattern reverses, with both the US and GB commodities having higher returns during phases of **contango** as opposed to **backwardation**.
 This change in pattern suggests the onset of financialisation altered the traditional risk shifting nature of hedger’s behaviour, implied by the Keynesian hypothesis.
@@
 
-@goldstein_speculation_2014 and @goldstein_commodity_2022 argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
-Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger’s positions (Keynesian perspective, theory of normal backwardation: @keynes_treatise_1930, @hicks_value_1939, @houthakker_speculators_1957, @telser_futures_1958), as well our term structure factor, based on backwardation as measured by roll yield (Working's perspective, theory of storage: @working_price_1933, @kaldor_speculation_1939, @working_theory_1948, @brennan_supply_1958, @cootner_returns_1960, @weymar_supply_1966, @danthine_information_1978, @turnovsky_determination_1983, @schwartz_stochastic_1997), to be best suited to measure the impact of financialisation.
-We analyse the pricing dynamics over the different periods by first studying the time series explanatory performance of the various factors on all the US traded commodities with the factors constructed using the latter set of commodities.
-The market-based factor outperforms the other three in the first period and, although its performance increases over the financialisation period, that of the CHP factor shows a greater improvement in a relative sense.
-The performance of the market factor is driven by agricultural and energy commodities in the first period while metals strongly contribute to the performance improvement observed over the second period.
-Similarly, the dramatic improvement of the CHP factor in the second period, is driven by the metals complex, particularly that of the long leg where they predominantly load.
-Average pairwise correlations amongst individual factors' best performing commodities increase across the board over the financialisation period, far beyond the average for the whole cross-section of US traded commodities.
-The increase is particularly strong for the long-short factors, in a relative sense, on which the metal complex loads significantly more during financialisation.
-This increase is due to the dramatic rise in average pairwise correlation amongst the US traded metals all of which exhibited high $R^{2}$ with respect to the CHP factor during financialisation which in turn is due to their common low level of CHP over this period.
-The CHP factor model thus seems able to establish the strengthening link between a non-price attribute and price dynamics in the US metal sub-sector during financialisation.
-We explore this issue further by constructing the four factors independently with the top eight commodities for a given factor (factor picks) in each period^[See section @sec-methods for further details.] and evaluating its performance on these selected commodities as well as on all US traded commodities.
-The results of this exercise provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
+These entered the commodity spectrum en masse with across-the-board index type positions propping the transition of the complex from a collection of idiosyncratic markets towards a more congruent ensemble akin to an asset class.
+In this context of heightened cross-asset market participation the issue of interconnectedness stands out as paramount and we strive to investigate it by first examining the correlation structure of our sample set of assets at the global, country, sector and subsector levels.
+Our results indicate higher interdependence within the full cross-section of commodities over the financialisation period, consistent with both the empirical and theoretical literature.
+The increase appears to be driven by the US metals sector, a new observation to the best of our knowledge, and, unlike individual commodity returns, does not seem to be regime-driven, as a similar pattern of results is observed across phases of **backwardation** and **contango**.
 
@@
 
-The UK traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialisation.
-To that end, we examine the performance of the four factors on the six UK metals, when constructed from each set of factor picks.
-The results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.
+@goldstein_speculation_2014 and @goldstein_commodity_2022 argue that the arrival of financial investors had an impact on the extent of normal backwardation in commodity futures markets.
+Based on their analysis we would expect our average CHP factor, based on backwardation as measured by hedger’s positions (Keynesian perspective, theory of normal backwardation: @keynes_treatise_1930, @hicks_value_1939, @houthakker_speculators_1957, @telser_futures_1958), as well our term structure factor, based on backwardation as measured by roll yield (Working's perspective, theory of storage: @working_price_1933, @kaldor_speculation_1939, @working_theory_1948, @brennan_supply_1958, @cootner_returns_1960, @weymar_supply_1966, @danthine_information_1978, @turnovsky_determination_1983, @schwartz_stochastic_1997), to be best suited to measure the impact of financialisation.
+We analyse the pricing dynamics over the different periods by first studying the time series explanatory performance of the various factors on our commodity assets sample.
+The market-based factor outperforms the other three in the first period and, although its performance increases over the financialisation period, that of the CHP factor shows a greater improvement in a relative sense.
+The performance of the market factor is driven by agricultural and energy commodities in the first period while metals strongly contribute to the performance improvement observed over the second period.
+The sector is also the driving force behind the dramatic improvement of the CHP factor during financialisation, led by its long leg on which metals predominantly load.
+The sector is similarly responsible for the improved performance of the short leg of the term structure factor of the period, on which the metals also predominantly load.
+Taken together, these results provide evidence of convergence of Keynesian and Working’s theories of the term structure in detecting price co-movement during financialisation and strongly suggest that the term structure related attributes (hedging pressure/roll) co-movement and price co-movement link was concentrated in the metals sub-sector.
+The GB traded base metals provide a useful set of assets to test how widespread were the changes in pricing dynamics brought about by the onset of financialisation.
+To that end, we examine the performance of the four factors on the six GB metals; the results show that there was co-movement in global metals returns in the second period and that this co-movement could be detected by our term structure related models, particularly so by our hedging pressure-based model.
+
+\bigskip
+
+The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes.
+Commodity futures returns fell dramatically while the symmetry between the dynamics of CHP and **CHP**'s' explanatory power on individual commodity returns breaks with both now seemingly converging.
+The correlation structure is also affected with evidence of an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation, consistent with the greater interdependence between equity and commodity markets over the period documented in the literature.
+The pricing results further indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as evidence of cross-market linkages with the GB traded commodity subset.
+The onset of the financial crisis thus seems to have had a global impact on the commodity complex in contrast with financialisation, much more closely related to the metals sector.
 
@@
 
-The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes.
-Commodity futures returns fell dramatically into the crisis and the pricing results indicate the emergence of a systematic factor across the entire cross-section of the US commodities as well as evidence of cross-market linkages with the UK traded commodity subset.
-The post-crisis results, in contrast, show a substantial pull-back in performance for the market factor across the board as well as evidence of decoupling between the US and UK markets.
-Besides, starting in the crisis the Keneysian paradigm of returns begins to revert with higher mean returns during low (**backwardation**) relative to high (**contango**) **CHP** phases and this pattern continues, more pronounced, over the post-crisis period.
-As pointed out in @basu_definancialisation, the financial crisis and ensuing accommodative monetary policy therefore seem to have initiated a process of reversion toward pre-financialisation fundamentals in the global commodity futures complex.
+The returns pull-back continues into the post-crisis period, interestingly amidst a lower volatility environment, suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed during financialisation.
+The pattern of reversion toward the pre-financialisation Keynesian paradigm continues stronger with mean returns higher during phases of **backwardation** relative to **contango** and the difference more pronounced than over the crisis period.
+In contrast to the crisis period when they seemed to be converging, the pricing performance of CHP and **CHP** now part way, seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a reversion to legacy commodity specific dynamics.
+The pull back extends to the correlation structure with an across-the-board decrease in average pairwise correlations down to levels below those observed during financialisation.
+The average market factor beta for the entire cross-section shows a similar pattern, dropping down below the level observed during financialization with the decline seemingly driven by the metals sector, particularly the GB traded segment.
+The pattern extends to the pricing performance of all factors that drops below levels observed during financialisation while the gap between the legs of the long-short factors remains narrower than observed during that period.
+Moreover, both the average correlations and the pricing performance of the market factor are considerably stronger during **contango** phases, unlike previous periods, which showed no substantial difference between regimes with especially pronounced for metal assets globally, both US and GB traded.
+These results document the emerging role/dominance of the **contango** regime post-crisis and could provide a valuable basis for further research.
 
@@
 For our NYMEX gasoline data series, we consider unleaded gasoline up to September 1^st^, 2006 and RBOB gasoline thereafter, date at which liquidity for the latter overtook that for the former.
-We also consider the UK metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).
-This sample cross-section of assets is further divided into groups for the purpose of the analysis by country (US, GB), sector (agriculturals, energy, metals) and by sub-sector (agriculturals: grains, livestock, softs; energy: gas, petroleum; metals: base, precious).
+We also consider the GB metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).
+This sample cross-section of assets is further divided into groups for the purpose of the analysis by country (US, GB), sector (agriculturals, energy, metals) and by sub-sector (agriculturals: grains, livestock, softs; energy: gas, petroleum; metals: base, precious)^[See @sec-taxonomy for a detailed taxonomy of the commodity assets considered in the study.].
 
@@
 
-In the early 2000s, against a backdrop of a low yield environment and poor stock market performance, a combination of financial innovations^[Commodity price indexes and the ad-hoc financial instruments enabling investment in them were the main financial innovations which allowed large global banks to offer commodity investment products to institutional and retail investors.
+In the early 2000s, against the backdrop of a low yield environment and poor stock market performance, a combination of financial innovations^[Commodity price indexes and the ad-hoc financial instruments enabling investment in them were the main financial innovations which allowed large global banks to offer commodity investment products to institutional and retail investors.
 In 1991 Goldman Sachs created the S&P-GSCI which provides investors with buy-side exposure to commodities via the OTC swap market and thus without having to participate in the formal futures markets with their position limit restrictions.
@@
 ```{r}
-tables <- readr::read_rds(paste_forward_slash(tables_directory_path, "tables-formatted.rds"))
-sectors <- c("country", "sector", "subsector")
-periods <- c("past", "financialisation", "crisis", "post-crisis")
-
-make_table <- function(table_name, colnames, align, bold_columns, coloured_columns){
-  get_results(tables, table_name) %>%
-  kbl(booktabs = T, longtable = T, col.names = colnames, align = align) %>%
-  kable_styling(latex_options = "striped", font_size = 7L) %>%
-  row_spec(0L, bold = TRUE, color = "black") %>%
-  column_spec(bold_columns, bold = TRUE) %>% column_spec(coloured_columns, color = "#4285f4")
-}
-```
-
-```{r}
 #| label: tbl-stats-combined

### 2024-10-03 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@5f931608ae9f9c663575798052089bbbe19c54fa 🚀

@@
 financialisation that comprehends commodity futures as an asset class.
-Using a bespoke asset pricing factors based framework we study the issue
+We examine the cross-sectional interconnectedness of these assets and
+uses a bespoke asset pricing factors based framework to study the issue
 through the lens of co-movement and find that the phenomenon had
@@
 
-In the early 2000s, against a backdrop of a low yield environment and
+In the early 2000s, against the backdrop of a low yield environment and
 poor stock market performance, a combination of financial

### 2024-10-23 docs/paper.qmd
Editorial polishing

@@
 In contrast, we take a broader approach where we consider a large cross-section of liquid commodities as suggested by the nature of financialisation that comprehends commodity futures as an asset class.
-Using a bespoke asset pricing factors based framework we study the issue through the lens of co-movement and find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
+We examine the cross-sectional interconnectedness of these assets and uses a bespoke asset pricing factors based framework to study the issue through the lens of co-movement.
+We find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals.
@@
 A rigorous legislative scrutiny accompanied by a vigorous policy and academic debate across a number of disciplines about the perceived effects on commodity prices of the unprecedented inflow of institutional funds brought into commodity futures markets by new index type investors^[See section @sec-background for a detailed discussion.] eventually led to regulatory changes in several individual markets.
-In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation---the burning issue of the day---at the individual commodity market level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
+In response to immediate policy concerns, the academic debate was initially framed rather narrowly around adequacy of speculation---the burning issue of the day---at the individual commodity level and the ensuing academic analysis focused on the more mechanical effects of financialisation.
 With the benefit of hindsight, this approach seems to lack a fundamental understanding of the phenomenon it endeavoured to study and which consequences it attempted to address.
@@
 
-These entered the commodity spectrum en masse with across-the-board index type positions propping the transition of the complex from a collection of idiosyncratic markets towards a more congruent ensemble akin to an asset class.
+These entered the commodity spectrum en masse with across-the-board index type positions propping the transition of the complex from a collection of idiosyncratic markets towards a more homogeneous ensemble akin to an asset class.
 In this context of heightened cross-asset market participation the issue of interconnectedness stands out as paramount and we strive to investigate it by first examining the correlation structure of our sample set of assets at the global, country, sector and subsector levels.
@@
 The average market factor beta for the entire cross-section shows a similar pattern, dropping down below the level observed during financialization with the decline seemingly driven by the metals sector, particularly the GB traded segment.
-The pattern extends to the pricing performance of all factors that drops below levels observed during financialisation while the gap between the legs of the long-short factors remains narrower than observed during that period.
-Moreover, both the average correlations and the pricing performance of the market factor are considerably stronger during **contango** phases, unlike previous periods, which showed no substantial difference between regimes with especially pronounced for metal assets globally, both US and GB traded.
+The pattern extends to the pricing performance of all factors that drops below levels observed during financialisation.
+Moreover, both the average correlations and the pricing performance of the market factor are considerably stronger during **contango** phases, unlike previous periods, which showed no substantial difference between regimes with the pattern particularly pronounced for metal assets globally, both US and GB traded.
 These results document the emerging role/dominance of the **contango** regime post-crisis and could provide a valuable basis for further research.
@@
 Early US Senate investigations on the matter drew on pricing and trading data supplied by the CFTC as well as interviews with numerous experts including hedge fund manager Michael Masters who linked the growing presence of index investors in US agricultural and energy markets to the observed surges in both futures and cash prices [@masters_testimony_2008; @masters_accidental_2008].
-This contention has since come to be known as the Masters’ hypothesis and was largely endorsed by the final US Senate report on the issue [@senate_excessive_2009].
+This contention has since come to be known as the "Masters’ hypothesis" and was largely endorsed by the final US Senate report on the issue [@senate_excessive_2009].
 At this stage, the question thrust on the academic sphere was whether "excessive speculation" (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices.
@@
 Additionally, pairwise correlations are computed for each combination of assets across the periods of interest and for each individual year within the full sample period.
-These correlation coefficients are subsequently averaged across the entire cross-section of assets, as well as by country, sector, and subsector.
+These correlation coefficients are then averaged across the entire cross-section of assets, as well as by country, sector, and subsector.
 For each period, the coefficients are also calculated and averaged across phases of low and high cross-sectional CHP.
@@
 The increase is even more pronounced for an equally weighted portfolio of GB traded assets (metals), 2.47% (not significant) to 21.8% (significant at the 10% level), which sets out the global nature of the phenomenon.
-Most commodities show a higher mean return while five---Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)---show a lower figure with five significant figures---Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)---against none pre-financialisation.
+Most commodities show a higher mean return while five---Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)---show a lower figure with five og them significant---Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)---against none pre-financialisation.
 Sugar-#11 wins the race with a mean return increasing from -4.6% to 24.9% followed by copper with sizeable increases for both markets: 1.5% to 28.2% (XCEC) and 0.5% to 28.6% (XLME).
@@
 The pattern is strongest for the metals sector where the average $R^{2}$ drops down to 19.1% from 28.1% between the two periods at the individual level while it rises from 8.4% to 15.7% at the aggregate level.
-The symmetry breaks in the crisis period, with the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%), before eventually resuming post-crisis with a further rise at the individual level (27.2% vs 22.5%) and a drop at the aggregate level (7.5% vs 14.7%) suggesting a return to legacy commodity specific dynamics.
 
@@
 
-Financialisation was a global phenomenon, through the channel of index investment it simultaneously influenced the entire spectrum of liquid commodities; this sweeping impact spurred the transformation of commodity markets from a collection of idiosyncratic markets into a unified asset class with interconnectedness emerging as a crucial aspect that warrants thorough examination.
+Financialisation was a global phenomenon, through the channel of index investment it simultaneously influenced the entire spectrum of liquid commodities, eventually spurring the transformation of commodity markets from a collection of idiosyncratic markets into a more homogeneous collection akin to an asset class.
+In this context, interconnectedness emerges as a crucial aspect that warrants thorough examination.
 We strive to address this issue by first examining the average of weekly returns pairwise correlations between commodities across the entire cross-section of the commodity assets considered in the study as well as by country, sector and sub-sector.
@@
 For the entire sample the average pairwise correlation jumps from 0.07 in the first period to 0.16 over financialisation.
-This finding indicate higher interdependence within the full cross-section of commodities starting with the financialisation period, consistent with the empirical findings in @fryMcKibbin_evolution_2023 and @mayer_financialization_2017 as well as with the theoretical model of @basak_model_2016.
+This finding indicates higher interdependence within the full cross-section of commodities starting with the financialisation period, consistent with the empirical findings in @fryMcKibbin_evolution_2023 and @mayer_financialization_2017 as well as with the theoretical model of @basak_model_2016.
 The sector analysis sheds light on the driving force behind these changes.
@@
 The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods which indicates that increased commodity interdependence over financialisation was not a phase driven phenomenon in the same way that individual commodity returns are, as demonstrated in @tbl-stats-combined.
-We further examine these correlations by year in @tbl-correlations-years to uncover any distinct breakpoints.
-For the full sample of assets, the average pairwise correlations increase from 0.08 to 0.12 from 2003 to 2004 seemingly driven by US metals average pairwise correlations, more than doubling from 0.22 to 0.49, suggesting 2004 as the onset of financialization as noted in several studies [@baker_financialization_2021; @tang_index_2012] and our contribution is to observe that the US metals sub-sector seems to have played a major role in this.
+We break down these average correlations by years in @tbl-correlations-years.
+For the full sample of assets, the average pairwise correlations remain in the 0.06–0.08 range from 1998 through 2003, before suddenly increasing to 0.12 from 2003 to 2004.
+This suggests 2004 as a distinct break point for the onset of financialisation, as noted in several studies [@baker_financialization_2021; @tang_index_2012].
+We further observe that the US metals appear to have played a major role in this as the increase seems driven by the sector which average pairwise correlation more than doubles (0.49 vs 0.22) over the period.
 
@@
 
-We investigate further the issue of co-movement from an asset pricing perspective using a bespoke asset pricing framework starting with a market factor mimicking portfolio constituted of the twenty-four US traded commodities considered in the study with equal weighting.
-This portfolio enables a refined examination of cross correlations across sectors as the numerator of the beta of the regression of the returns for an individual commodity against those for the market factor is driven by covariances while the denominator is driven by the individual commodity variance.
+We investigate further the issue of co-movement from an asset pricing perspective using a bespoke asset pricing framework starting with a market factor mimicking portfolio constituted of the twenty-four US traded commodities with equal weighting.
+This portfolio enables a refined examination of cross-correlations across sectors as the numerator of the beta of the regression of the returns for an individual commodity against those for the market factor is driven by covariances while the denominator is driven by the individual commodity variance.
 Thus, an increase in a commodity's correlation with other commodities should lead to an increase in its beta relative to the market factor portfolio.
@@
 The corresponding pricing performance displays a similar pattern as shown in @tbl-regressions-factors where for each period the corresponding $R^{2}$ values are independently averaged over the entire period as well as over periods of **contango** and **backwardation**.
-The average $R^{2}$ for the market factor across the entire cross-section of commodity assets considered in the study, including the GB traded base metals, increases to around 20% during financialisation compared to around 10% over the previous period with the rise driven by the metals sector at large.
+The average $R^{2}$ for the market factor across the entire cross-section of commodity assets, including the GB traded base metals, increases to around 20% during financialisation compared to around 10% over the previous period with the rise driven by the metals sector at large.
 The sector average for the US traded assets jumps to 31% during financialisation from 7.5% over the past period while for the GB traded assets the corresponding figure increases from less than 2%, or virtually no explanatory power for the (US based) market factor, to almost 12% over the financialisation period.
@@
 The corresponding figures of 22% and 1.1% for the entire US metals sector stand in sharp contrast with the agricultural sector, which exhibits no notable change, and the energy sector, where pricing performance drops substantially from 9.2% down to 1.6%.
-The improvement in the CHP factor's pricing performance remarkably comes predominantly from the long leg (low CHP assets: Keynesian "normal backwardation") of the factor^{Results available from the authors upon request.} with the corresponding mimicking portfolio's performance itself driven by the metals, the precious sub-sector in particular.
+The improvement in the CHP factor's pricing performance remarkably comes predominantly from the long leg (low CHP assets: Keynesian "normal backwardation") of the factor^[Results available from the authors upon request.] with the corresponding mimicking portfolio's performance itself driven by the metals, the precious sub-sector in particular.
 The average $R^{2}$ for the group jumps to 55% during financialisation from less than 12% over the past period while the short leg sees a far smaller increase, up to 8.9% from 3.3% over the past period.
 Interestingly, although the term structure factor itself only sees a very modest increase, its short leg (low roll-yield assets: Working's backwardation) shows a sizeable rise in pricing performance, yet again driven the metals sector, with the average $R^{2}$ for the group's US traded assets jumping to 28.2% during financialisation from 6.2% over the past period.
-The pattern of results for both factors extends to the GB trade assets and suggest a convergence of Keneysian and Working's term structure perspective over the financialisation period.
+The pattern of results for both factors extends to the GB traded assets and suggest a convergence of Keneysian and Working's term structure perspective over the financialisation period.
 Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working’s term structure paradigms.

### 2024-10-23 docs/paper.tex
Editorial polishing

@@
 financialisation that comprehends commodity futures as an asset class.
-Using a bespoke asset pricing factors based framework we study the issue
-through the lens of co-movement and find that the phenomenon had
+We examine the cross-sectional interconnectedness of these assets and
+uses a bespoke asset pricing factors based framework to study the issue
+through the lens of co-movement. We find that the phenomenon had
 ontological consequences for the commodity complex with its impact
@@
 initially framed rather narrowly around adequacy of speculation---the
-burning issue of the day---at the individual commodity market level and
-the ensuing academic analysis focused on the more mechanical effects of
+burning issue of the day---at the individual commodity level and the
+ensuing academic analysis focused on the more mechanical effects of
 financialisation. With the benefit of hindsight, this approach seems to
@@
 index type positions propping the transition of the complex from a
-collection of idiosyncratic markets towards a more congruent ensemble
+collection of idiosyncratic markets towards a more homogeneous ensemble
 akin to an asset class. In this context of heightened cross-asset market
@@
 traded segment. The pattern extends to the pricing performance of all
-factors that drops below levels observed during financialisation while
-the gap between the legs of the long-short factors remains narrower than
-observed during that period.\\
+factors that drops below levels observed during financialisation.\\
 Moreover, both the average correlations and the pricing performance of
@@
 phases, unlike previous periods, which showed no substantial difference
-between regimes with especially pronounced for metal assets globally,
-both US and GB traded. These results document the emerging
-role/dominance of the \textbf{contango} regime post-crisis and could
-provide a valuable basis for further research.
+between regimes with the pattern particularly pronounced for metal
+assets globally, both US and GB traded. These results document the
+emerging role/dominance of the \textbf{contango} regime post-crisis and
+could provide a valuable basis for further research.
 
@@
 \citep{masters_testimony_2008, masters_accidental_2008}. This contention
-has since come to be known as the Masters' hypothesis and was largely
-endorsed by the final US Senate report on the issue
+has since come to be known as the ``Masters' hypothesis'' and was
+largely endorsed by the final US Senate report on the issue
 \citep{senate_excessive_2009}.\\
@@
 assets across the periods of interest and for each individual year
-within the full sample period. These correlation coefficients are
-subsequently averaged across the entire cross-section of assets, as well
-as by country, sector, and subsector. For each period, the coefficients
-are also calculated and averaged across phases of low and high
+within the full sample period. These correlation coefficients are then
+averaged across the entire cross-section of assets, as well as by
+country, sector, and subsector. For each period, the coefficients are
+also calculated and averaged across phases of low and high
 cross-sectional CHP.
@@
 Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary
-(XLME)---show a lower figure with five significant figures---Crude
+(XLME)---show a lower figure with five og them significant---Crude
 oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and
@@
 28.1\% between the two periods at the individual level while it rises
-from 8.4\% to 15.7\% at the aggregate level. The symmetry breaks in the
-crisis period, with the US cross-sectional average \(R^{2}\) at the
-individual level bouncing back up (22.5\% vs 20.8\%) while that at the
-aggregate level rises further (14.7\% vs 7.1\%), before eventually
-resuming post-crisis with a further rise at the individual level (27.2\%
-vs 22.5\%) and a drop at the aggregate level (7.5\% vs 14.7\%)
-suggesting a return to legacy commodity specific dynamics.
+from 8.4\% to 15.7\% at the aggregate level.
 
@@
 commodities; this sweeping impact spurred the transformation of
-commodity markets from a collection of idiosyncratic markets into a
-unified asset class with interconnectedness emerging as a crucial aspect
-that warrants thorough examination.\\
+commodity markets from a collection of idiosyncratic markets into a more
+homogeneous collection akin to an asset class. In this context
+interconnectedness emerges as a crucial aspect that warrants thorough
+examination.\\
 We strive to address this issue by first examining the average of weekly
@@
 average pairwise correlation jumps from 0.07 in the first period to 0.16
-over financialisation. This finding indicate higher interdependence
+over financialisation. This finding indicates higher interdependence
 within the full cross-section of commodities starting with the
@@
 We further examine these correlations by year in
-Table~\ref{tbl-correlations-years} to uncover any distinct breakpoints.
-For the full sample of assets, the average pairwise correlations
-increase from 0.08 to 0.12 from 2003 to 2004 seemingly driven by US
-metals average pairwise correlations, more than doubling from 0.22 to
-0.49, suggesting 2004 as the onset of financialization as noted in
-several studies \citep{baker_financialization_2021, tang_index_2012} and
-our contribution is to observe that the US metals sub-sector seems to
-have played a major role in this.
+Table~\ref{tbl-correlations-years}. For the full sample of assets, the
+average pairwise correlations remain in the 0.06--0.08 range from 1998
+through 2003, before suddenly increasing to 0.12 from 2003 to 2004,
+suggesting 2004 as a distinct break point corresponding to the onset of
+financialisation, as noted in several studies
+\citep{baker_financialization_2021, tang_index_2012}. We further observe
+that the US metals appear to have played a major role in this as the
+increase seems driven by the sector which average pairwise correlation
+more than doubles (0.49 vs 0.22) over the period.
 
@@
 traded commodities considered in the study with equal weighting. This
-portfolio enables a refined examination of cross correlations across
+portfolio enables a refined examination of cross-correlations across
 sectors as the numerator of the beta of the regression of the returns
@@
 \textbf{backwardation}. The average \(R^{2}\) for the market factor
-across the entire cross-section of commodity assets considered in the
-study, including the GB traded base metals, increases to around 20\%
-during financialisation compared to around 10\% over the previous period
-with the rise driven by the metals sector at large. The sector average
-for the US traded assets jumps to 31\% during financialisation from
-7.5\% over the past period while for the GB traded assets the
-corresponding figure increases from less than 2\%, or virtually no
-explanatory power for the (US based) market factor, to almost 12\% over
-the financialisation period. The results for our other risk factor
-mimicking portfolios show a similar pattern and provide a deeper
-insights into co-movement dynamics in this context. All three
-factors---CHP, open interest and term structure---performed poorly in
-the first period, indicating that the commodities with extreme factor
-attributes (high or low CHP for example) were uncorrelated with the rest
-of the commodity cross-section, and the overall performance consistent
-across periods of \textbf{contango} and \textbf{backwardation}. The
-onset of financialisation leads to a substantial improvement in the
-performance of the CHP factor with its average \(R^{2}\), albeit still
-small at 5.4\%, almost tripling from the past to the financialisation
-period in contrast to the other factors that show weaker dynamics with a
-slight decrease and a much smaller increase for the open interest and
-term structure factors respectively. Here again the increase in pricing
-performance for the CHP factor is driven by the metals sector,
-particularly the precious sub-sector with the average \(R^{2}\) for the
-group jumping to almost 26\% during financialisation from 1.2\% over the
-past period. The corresponding figures of 22\% and 1.1\% for the entire
-US metals sector stand in sharp contrast with the agricultural sector,
-which exhibits no notable change, and the energy sector, where pricing
-performance drops substantially from 9.2\% down to 1.6\%. The
-improvement in the CHP factor's pricing performance remarkably comes
-predominantly from the long leg (low CHP assets: Keynesian ``normal
-backwardation'') of the factor\^{}\{Results available from the authors
-upon request.\} with the corresponding mimicking portfolio's performance
-itself driven by the metals, the precious sub-sector in particular. The
-average \(R^{2}\) for the group jumps to 55\% during financialisation
-from less than 12\% over the past period while the short leg sees a far
-smaller increase, up to 8.9\% from 3.3\% over the past period.
-Interestingly, although the term structure factor itself only sees a
-very modest increase, its short leg (low roll-yield assets: Working's
-backwardation) shows a sizeable rise in pricing performance, yet again
-driven the metals sector, with the average \(R^{2}\) for the group's US
-traded assets jumping to 28.2\% during financialisation from 6.2\% over
-the past period. The pattern of results for both factors extends to the
-GB trade assets and suggest a convergence of Keneysian and Working's
-term structure perspective over the financialisation period.\\
+across the entire cross-section of commodity assets, including the GB
+traded base metals, increases to around 20\% during financialisation
+compared to around 10\% over the previous period with the rise driven by
+the metals sector at large. The sector average for the US traded assets
+jumps to 31\% during financialisation from 7.5\% over the past period
+while for the GB traded assets the corresponding figure increases from
+less than 2\%, or virtually no explanatory power for the (US based)
+market factor, to almost 12\% over the financialisation period. The
+results for our other risk factor mimicking portfolios show a similar
+pattern and provide a deeper insights into co-movement dynamics in this
+context. All three factors---CHP, open interest and term
+structure---performed poorly in the first period, indicating that the
+commodities with extreme factor attributes (high or low CHP for example)
+were uncorrelated with the rest of the commodity cross-section, and the
+overall performance consistent across periods of \textbf{contango} and
+\textbf{backwardation}. The onset of financialisation leads to a
+substantial improvement in the performance of the CHP factor with its
+average \(R^{2}\), albeit still small at 5.4\%, almost tripling from the
+past to the financialisation period in contrast to the other factors
+that show weaker dynamics with a slight decrease and a much smaller
+increase for the open interest and term structure factors respectively.
+Here again the increase in pricing performance for the CHP factor is
+driven by the metals sector, particularly the precious sub-sector with
+the average \(R^{2}\) for the group jumping to almost 26\% during
+financialisation from 1.2\% over the past period. The corresponding
+figures of 22\% and 1.1\% for the entire US metals sector stand in sharp
+contrast with the agricultural sector, which exhibits no notable change,
+and the energy sector, where pricing performance drops substantially
+from 9.2\% down to 1.6\%. The improvement in the CHP factor's pricing
+performance remarkably comes predominantly from the long leg (low CHP
+assets: Keynesian ``normal backwardation'') of the factor\footnote{Results
+  available from the authors upon request.} with the corresponding
+mimicking portfolio's performance itself driven by the metals, the
+precious sub-sector in particular. The average \(R^{2}\) for the group
+jumps to 55\% during financialisation from less than 12\% over the past
+period while the short leg sees a far smaller increase, up to 8.9\% from
+3.3\% over the past period. Interestingly, although the term structure
+factor itself only sees a very modest increase, its short leg (low
+roll-yield assets: Working's backwardation) shows a sizeable rise in
+pricing performance, yet again driven the metals sector, with the
+average \(R^{2}\) for the group's US traded assets jumping to 28.2\%
+during financialisation from 6.2\% over the past period. The pattern of
+results for both factors extends to the GB traded assets and suggest a
+convergence of Keneysian and Working's term structure perspective over
+the financialisation period.\\
 Taken together these results emphasise the global nature of the impact

### 2024-10-24 paper.qmd
Deploying to gh-pages from @ bautheac/financialisation-co-movement@a81132a46357bde84d303bf39d5aeeb632576e3e 🚀

@@
 In contrast, we take a broader approach where we consider a large cross-section of liquid commodities as suggested by the nature of financialisation that comprehends commodity futures as an asset class.
-We examine the cross-sectional interconnectedness of these assets and uses a bespoke asset pricing factors based framework to study the issue through the lens of co-movement and find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
+We examine the cross-sectional interconnectedness of these assets and uses a bespoke asset pricing factors based framework to study the issue through the lens of co-movement.
+We find that the phenomenon had ontological consequences for the commodity complex with its impact extending beyond the mechanical effects induced by indexation.
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, seem to have set off a motion of reversion to legacy pre-financialisation fundamentals.
@@
 The corresponding figures of 22% and 1.1% for the entire US metals sector stand in sharp contrast with the agricultural sector, which exhibits no notable change, and the energy sector, where pricing performance drops substantially from 9.2% down to 1.6%.
-The improvement in the CHP factor's pricing performance remarkably comes predominantly from the long leg (low CHP assets: Keynesian "normal backwardation") of the factor^{Results available from the authors upon request.} with the corresponding mimicking portfolio's performance itself driven by the metals, the precious sub-sector in particular.
-The average $R^{2}$ for the group jumps to 55% during financialisation from less than 12% over the past period while the short leg sees a far smaller increase, up to 8.9% from 3.3% over the past period.
-Interestingly, although the term structure factor itself only sees a very modest increase, its short leg (low roll-yield assets: Working's backwardation) shows a sizeable rise in pricing performance, yet again driven the metals sector, with the average $R^{2}$ for the group's US traded assets jumping to 28.2% during financialisation from 6.2% over the past period.
-The pattern of results for both factors extends to the GB trade assets and suggest a convergence of Keneysian and Working's term structure perspective over the financialisation period.
-Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working’s term structure paradigms.
-There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of @kang_tale_2020 who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
+The improvement in the CHP factor's pricing performance remarkably comes predominantly from the long leg (low CHP assets: Keynesian "normal backwardation") of the factor^[Results available from the authors upon request.] with the corresponding mimicking portfolio's performance itself driven by the metals, the precious sub-sector in particular.
+Interestingly, although the term structure factor itself only sees a very modest increase, its short leg (low roll-yield assets: Working's backwardation) shows a sizeable rise in pricing performance, yet again driven the metals sector.
+The pattern of results for both factors extends to the GB traded assets and suggest a convergence of Keneysian and Working's term structure perspective over the financialisation period.
+Taken together these results emphasise the global nature of the impact of financialisation on the metals complex suggest that there is information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm.
+These findings therefore appear to complement the results of @kang_tale_2020 who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
 
@@
 Volatility is moderately higher for both sets with fifteen US commodities and three GB metals showing higher figures and interestingly eminently higher over phases of **contango**; out of the US complex only Sugar-#11 (IFUS) and none of the GB traded metals show higher volatility figures over **backwardation** phases.
-The symmetry between the dynamics of CHP and **CHP**'s explanatory power on individual commodity returns breaks in the crisis period (@tbl-time-reg-US-CHP) with both now seemingly converging; the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%).
+The symmetry between the dynamics of CHP and **CHP**'s explanatory power on individual commodity returns breaks (@tbl-time-reg-US-CHP) with both now seemingly converging; the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%).
 
@@
 
-The average pairwise correlation for the entire set of sample assets increases further into the crisis to 0.28 (@tbl-correlations-periods) indicating an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation.
+The average pairwise correlation for the entire set of sample assets increases further to 0.28 (@tbl-correlations-periods) indicating an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation.
 The result is consistent with the greater interdependence between equity and commodity markets over this period documented in @silvennoinen_financialisation_2013.
 The figure for the US traded section of the metals sector only progresses modestly to 0.59 after peaking at 0.63 in 2006 (@tbl-correlations-years).
-In contrast, the GB traded assets see a sharp increase to over 0.65 in the crisis starting in 2007 up to a peak of 0.69 in 2010, and so does the agricultural sector with the sharpest increase in 2008 when the average pairwise correlation for the sector jumps to 0.30.
+In contrast, the GB traded assets see a sharp increase to over 0.65  starting in 2007 up to a peak of 0.69 in 2010, and so does the agricultural sector with the sharpest increase in 2008 when the average pairwise correlation for the sector jumps to 0.30.
 The energy sector also shows a substantial progression starting in 2007 and peaking at 0.63 in 2008 before levelling back down over the rest of the period.
@@
 
-The entire cross-section sees an increase in average regression coefficient relative to the market factor over the crisis period with the strongest progression for the GB traded metals followed by the agricultural sector (@tbl-regressions-index).
+The entire cross-section sees an increase in average regression coefficient relative to the market factor with the strongest progression for the GB traded metals followed by the agricultural sector (@tbl-regressions-index).
 The pricing performance of the factor
-dominates the US commodity complex over the period (@tbl-regressions-factors), showing a 50% increase in mean average $R^{2}$ to over 31%, while that for both the CHP and open interest factor decreases and, although increasing, remains modest for the term structure factors; the increase is strongest for the GB traded metal assets with an average $R^{2}$ of almost 34% for the period.
+dominates the US commodity complex (@tbl-regressions-factors), showing a 50% increase in mean average $R^{2}$ to over 31%, while that for both the CHP and open interest factor decreases and, although increasing, remains modest for the term structure factors; the increase is strongest for the GB traded metal assets with an average $R^{2}$ of almost 34%.
 Taken together, these results indicate the presence of a systematic factor across the entire cross-section of the US commodities.
-For both the CHP and term structure factors, both legs show an increase in average $R^{2}$ and while substantially diverging over the preceding financialisation period the pricing performance for both legs seems to converge back to a pattern closer to that observed pre-financialisation.
 
@@
 After showing signs of convergence in the crisis period the dynamics of the explanatory power of CHP and **CHP** part ways (@tbl-time-reg-US-CHP), seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a return to legacy commodity specific dynamics.
-The recovery initiated in the crisis period for that of CHP is confirmed with a stronger increase in the post-crisis period, 27.2% vs.
+The recovery initiated in the crisis period for that of CHP is confirmed with a stronger increase, 27.2% vs.
 22.5%, strongest for the metals sector, 37.3% vs.
@@
 16%.
-In contrast, after increasing stronger in the crisis, that for **CHP** falls overall in the post-crisis period, 7.5% vs 14.7%, with the decrease strongest for the energy sector in a relative sense: 2.5% vs.
+In contrast, after increasing stronger in the crisis, that for **CHP** falls overall post-crisis, 7.5% vs 14.7%, with the decrease strongest for the energy sector in a relative sense: 2.5% vs.
 14.8%.
@@
 
-The average pairwise correlations fall across the board in the post-crisis period, below the levels observed during financialisation, with the figure for the entire cross-section (@tbl-correlations-periods) dropping down to 0.12 from 0.28 over the crisis.
-This substantial decline, that does not appear to have been widely noted, appears to begin in the latter part of the crisis period, around 2012 (@tbl-correlations-years), before levelling down over the whole post-crisis period.
+The average pairwise correlations fall across the board, below the levels observed during financialisation, with the figure for the entire cross-section (@tbl-correlations-periods) dropping down to 0.12 from 0.28 over the crisis.
+This substantial decline, that does not seem to have been widely noted, appears to begin in the latter part of the crisis period, around 2012 (@tbl-correlations-years), before levelling down over the whole post-crisis period.
 
@@
 All sectors seem affected with agriculturals, energy and metals all seeing their average $R^{2}$ decline below the levels observed during the financialisation period albeit remaining above 10% for the GB traded metals against less than 2% pre-financialisation.
-Similarly, the performance for both the CHP and term structure factors falls back to levels below those attained over financialisation while the gap between their long and short legs remains narrower than observed during that period.
+Similarly, the performance for both the CHP and term structure factors falls back to levels below those attained over financialisation.
 These results, along with those from the crisis period, suggest that the exogenous shock of the financial crisis, combined with the subsequent accommodative monetary policy, may have triggered a reversion toward pre-financialization fundamentals in the commodity futures complex; an issue that, to our knowledge, has not been widely discussed in the existing literature.
@@
 The figures for the US and GB traded segments of the sector are 23% (**contango**) vs 11.5% (**backwardation**) against 36.2% vs 43% during financialisation and 14.4% (**contango**) vs 6.6% (**backwardation**) against 33.5% vs 34.4% during financialisation respectively.
-Taken together, these results indicate some recent changes in the correlation structure within the sector and along with the decline in interdependence in the commodity sector at large documented above, this observation could form a valuable basis for future research.
-These findings providence additional evidence that the interdependence effects of financialization seems to have been strongest for the entire cross-section of the metals sector with a lesser impact for the other sectors.
+Taken together, these results indicate some recent changes in the correlation structure within the sector and provide additional evidence that the interdependence effects of financialization seems to have been strongest for the entire cross-section of the metals sector with a lesser impact for the other sectors.
+This observation, along with the decline in interdependence in the commodity sector at large documented above, could form a valuable basis for future research.
 

### 2024-10-24 explore/scripts/original/test-differences.r
Fix bug in legacy code

@@ -190,7 +190,7 @@ carry <- dplyr::filter(
 ## commodity futures ####
 ### market variables ####
 #### by single commodity ####
-combinations <- t(combn(unique(periods$period), 2L)) %>% as.data.frame() %>%
+combinations <- t(combn(unique(as.character(periods$period)), 2L)) %>% as.data.frame() %>%
   rlang::set_names(c("period 1", "period 2"))
 combinations <- tidyr::expand_grid(
   dplyr::distinct(`market data`, `active contract ticker`, field),
@@ -464,7 +464,7 @@ countries <- dplyr::left_join(
   by = "active contract ticker"
 ) %>% dplyr::distinct(country)
 
-combinations <- t(combn(unique(periods$period), 2L)) %>% as.data.frame() %>%
+combinations <- t(combn(unique(as.character(periods$period)), 2L)) %>% as.data.frame() %>%
   rlang::set_names(c("period 1", "period 2"))
 combinations <- tidyr::expand_grid(
   countries, dplyr::distinct(`market data`, field), combinations
@@ -746,7 +746,7 @@ sectors <- dplyr::left_join(
   by = "active contract ticker"
 ) %>% dplyr::distinct(country, sector) %>% dplyr::select(country, sector)
 
-combinations <- t(combn(unique(periods$period), 2L)) %>% as.data.frame() %>%
+combinations <- t(combn(unique(as.character(periods$period)), 2L)) %>% as.data.frame() %>%
   rlang::set_names(c("period 1", "period 2"))
 combinations <- tidyr::expand_grid(
   sectors, dplyr::distinct(`market data`, field), combinations
@@ -1030,7 +1030,7 @@ subsectors <- dplyr::left_join(
 ) %>% dplyr::distinct(country, sector, subsector) %>% 
   dplyr::select(country, sector, subsector)
 
-combinations <- t(combn(unique(periods$period), 2L)) %>% as.data.frame() %>%
+combinations <- t(combn(unique(as.character(periods$period)), 2L)) %>% as.data.frame() %>%
   rlang::set_names(c("period 1", "period 2"))
 combinations <- tidyr::expand_grid(
   subsectors, dplyr::distinct(`market data`, field), combinations
@@ -1352,7 +1352,7 @@ pressure <- dplyr::left_join(
 
 
 #### by single commodity ####
-combinations <- t(combn(unique(periods$period), 2L)) %>% as.data.frame() %>%
[…]

### 2024-10-30 explore/scripts/revision-jfm/functions.r
Added country portfolios to regime difference tests

@@ -106,6 +106,19 @@ make_ticker_country_sector_subsector_dataframe <- function(tickers){
   rm(tickers_futures, exchanges, envir = .GlobalEnv); return(df)
 }
 
+make_ticker_country_dataframe <- function(tickers){
+  data("tickers_futures", package = "BBGsymbols")
+  data("exchanges", package = "fewISOs")
+  
+  df <- dplyr::left_join(
+    dplyr::filter(tickers_futures, ticker %in% tickers) %>% dplyr::select(ticker, MIC), 
+    dplyr::select(exchanges, MIC, country), 
+    by = "MIC"
+  ) %>% dplyr::select(-MIC)
+  
+  rm(tickers_futures, exchanges, envir = .GlobalEnv); return(df)
+}
+
 filter_commodity_futures_tickers <- function(
     all_tickers, filter_country = "all", filter_sector = "all", filter_subsector = "all"
 ){
@@ -845,8 +858,17 @@ make_analysis_for_ticker_combinations_dataframe <- function(
 }
 
 ## regime difference tests #####################################################
+make_tickers_list_for_regime_difference_tests <- function(){
+  c(
+    commodity_futures_tickers,
+    unique(commodity_futures_country_indexes_returns$ticker)
+    )
+}
+
 make_tickers_periods_combinations <- function(){
-  tidyr::expand_grid(commodity_futures_tickers, dplyr::distinct(period_dates, period))  %>%
+  tickers <- make_tickers_list_for_regime_difference_tests()
+  
+  tidyr::expand_grid(tickers, dplyr::distinct(period_dates, period))  %>%
     setNames(c("ticker", "period"))
 }
 
@@ -857,13 +879,29 @@ make_period_boundary_dates <- function(period){
   )
 }
 
-make_returns_timseries_for_ticker_period_combination <- function(ticker, period){
-  
+extract_commodity_individual_futures_returns <- function(){
   dplyr::filter(
-    commodity_futures_data, type == "return", frequency == "day", field == "PX_LAST",
-    `active contract ticker` == ticker, date >= date_start, date <= date_end
+    commodity_futures_data, type == "return", frequency == "day", field == "PX_LAST"
+  ) %>%
+    dplyr::filter(!is.na(value)) %>%
+    dplyr::select(ticker = `active contract ticker`, date, return = value)
+}
+
+combine_commodity_individual_and_country_indexes_futures_returns <- function(){
[…]

### 2024-10-30 explore/scripts/revision-jfm/analysis.r
Harmonise section separation

@@ -1,6 +1,6 @@
 library(finRes); library(magrittr)
 
-# source functions ####
+# source functions #############################################################
 source(here::here("explore", "scripts", "revision-jfm", "functions.r"))
 
 # load global variables ########################################################

### 2024-10-30 explore/scripts/revision-jfm/tables.r
Format regime difference test results into table
for inclusion in paper

@@ -189,6 +189,32 @@ descriptive_stats_combined <- dplyr::bind_rows(commodities, countries) %>%
     estimate = ifelse(estimate == "mean", estimate, "volatility")
     )
 
+# regime difference tests ####
+regime_difference_tests <- readr::read_rds(
+  paste_forward_slash(results_directory_path, "regime-difference-tests.rds")
+)
+
+ticker_asset_map <- dplyr::left_join(
+    dplyr::filter(tickers_futures, ticker %in% commodity_futures_tickers) %>% 
+      dplyr::select(ticker, name, sector, subsector, MIC), 
+    dplyr::select(exchanges, MIC, country), 
+    by = "MIC"
+  )
+  
+regime_difference_tests <- 
+  dplyr::left_join(regime_difference_tests, ticker_asset_map, by = c("ticker" = "ticker")) %>%
+  dplyr::mutate(
+    name = ifelse(is.na(name), ticker, name),
+    name = ifelse(is.na(MIC), name, paste0(name, " (", MIC, ")")),
+    moment = ifelse(moment == "mean", "mean", "volatility"),
+    country = factor(country, levels = c("US", "GB")),
+    `p-value` = percentize(as.numeric(`p-value`)),
+    sector = factor(sector, levels = sector_levels),
+    subsector = factor(subsector, levels = subsector_levels)
+    ) %>%
+  dplyr::arrange(country, sector, subsector, name) %>%
+  dplyr::select(asset = name, period, moment, `dominant regime`, `p-value`)
+
 
 # correlations ####
 correlations <- readr::read_rds(
@@ -239,22 +265,21 @@ subsectors <- dplyr::filter(
 ) %>% dplyr::select(results) %>% tidyr::unnest(results) %>% 
   dplyr::filter(regressor == "pressure change contemporaneous") %>%
   dplyr::group_by(country, sector, subsector, period, regressor, regime.CHP.type, CHP.regime) %>%
-  dplyr::summarise(`average rsquared` = mean(rsquared, na.rm = TRUE)) %>%
-  dplyr::ungroup()
+  dplyr::summarise(`average rsquared` = mean(rsquared, na.rm = TRUE), .groups = "drop")
 sectors <- dplyr::filter(
   regressions_CHP, analysis == "US commodity returns ~ US commodity individual CHP"
 ) %>% dplyr::select(results) %>% tidyr::unnest(results) %>% 
[…]

### 2024-10-30 others/regime difference test results analysis.qmd
make regime difference test results analysis dashboard

---
title: "Analysis of regime difference test results"
format: 
  html:
    grid:
      body-width: 1000px
---

```{r}
#| label: globals
#| include: false

# Load required packages
library(dplyr)
library(readr)
library(here)
library(slituR)
library(BBGsymbols)
library(fewISOs)

# Load data
data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
data("exchanges", package = "fewISOs")

results_directory_path <- here::here("explore", "results", "revision-jfm")
commodity_futures_tickers <- c(
  "BOA Comdty", "C A Comdty", "CCA Comdty", "CLA Comdty", "CTA Comdty", 
  "FCA Comdty", "GCA Comdty", "HGA Comdty", "HOA Comdty", "JOA Comdty", 
  "KCA Comdty", "LAA Comdty", "LBA Comdty", "LCA Comdty", "LHA Comdty", 
  "LLA Comdty", "LNA Comdty", "LPA Comdty", "LTA Comdty", "LXA Comdty", 
  "NGA Comdty", "O A Comdty", "PAA Comdty", "PLA Comdty", "S A Comdty", 
  "SBA Comdty", "SIA Comdty", "SMA Comdty", "W A Comdty", "XBWA Comdty",
  "LAA Comdty", "LPA Comdty", "LLA Comdty", "LNA Comdty", "LTA Comdty",
  "LXA Comdty"
)
period_levels <- c("past", "financialization", "crisis", "present")
sector_levels <- c("all", "agriculturals", "energy", "metals")
subsector_levels <- c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")

results <- readr::read_rds(
  slituR::paste_forward_slash(results_directory_path, "regime-difference-tests.rds")
)
ticker_asset_map <- dplyr::left_join(
  dplyr::filter(tickers_futures, ticker %in% commodity_futures_tickers) %>% 
    dplyr::select(ticker, name, sector, subsector, MIC), 
  dplyr::select(exchanges, MIC, country), 
  by = "MIC"
)
results <- 
  dplyr::left_join(results, ticker_asset_map, by = c("ticker" = "ticker")) %>%
  dplyr::mutate(
    country = factor(country, levels = c("US", "GB")),
    moment = ifelse(moment == "mean", "mean", "volatility"),
    name = ifelse(is.na(name), ticker, name),
    name = ifelse(is.na(MIC), name, paste0(name, " (", MIC, ")")),
    period = factor(period, levels = period_levels),
    sector = factor(sector, levels = sector_levels),
    subsector = factor(subsector, levels = subsector_levels)
  ) %>%
  dplyr::arrange(country, sector, subsector, name, period) %>%
  dplyr::select(country, name, moment, period, `dominant regime`, `p-value`)

individuals <- dplyr::filter(results, !name %in% c("GB commodities", "US commodities"))
countries <- dplyr::filter(results, name %in% c("GB commodities", "US commodities")) %>%
  dplyr::select(-country)
```

## Individuals

### Numbers
```{r}
#| label: individuals-numbers
#| echo: false

summary_individuals <- group_by(individuals, country, period, moment) %>%
  summarise(
    `10%` = sum(`p-value` > 0.05 & `p-value` <= 0.1, na.rm = TRUE),
    `5%` = sum(`p-value` > 0.01 & `p-value` <= 0.05, na.rm = TRUE),
    `1%` = sum(`p-value` > 0 & `p-value` <= 0.01, na.rm = TRUE),
    .groups = "drop"
  )

knitr::kable(summary_individuals)
```

### Names
```{r}
#| label: individuals-names
#| echo: false

summary_individuals <- group_by(individuals, country, period, moment) %>%
  summarise(
    `10%` = list(name[`p-value` >= 0.05 & `p-value` < 0.1]),
    `5%` = list(name[`p-value` >= 0.01 & `p-value` < 0.05]),
    `1%` = list(name[`p-value` >= 0 & `p-value` < 0.01]),
    .groups = "drop"
  )

knitr::kable(summary_individuals)
```

## countries
```{r}
#| label: countries
#| echo: false

significance <- function(x) {
  case_when(
    x > 0.1 ~ "",
    x > 0.05 ~ "*",
    x > 0.01 ~ "**",
    TRUE ~ "***"
  )
}

summary_countries <- dplyr::mutate(
  countries, significance = significance(as.numeric(`p-value`))
  )

knitr::kable(summary_countries)
```

### 2024-10-30 explore/scripts/revision-jfm/tables.r
Use slituR when possible
for utility functions

@@ -38,8 +38,6 @@ make_asset_name_country_sector_subsector_dataframe <- function(tickers){
     by = "MIC"
   ) %>% dplyr::select(-ticker)
 }
-paste_forward_slash <- function(...) paste(..., sep = "/")
-percentize <- function(value) paste0(round(value, digits = 4L) * 100, "%")
 significance <- function(p.value, estimate){
   if(p.value <= 0.01) paste0("***", estimate)
   else if (p.value > 0.01 && p.value <= 0.05) paste0("**", estimate)
@@ -74,7 +72,7 @@ sort_table_by_country_sector_subsector <- function(tb, sort_levels){
 
 # descriptive stats ####
 stats <- readr::read_rds(
-  paste_forward_slash(results_directory_path, "descriptive-statistics-clean.rds")
+  slituR::paste_forward_slash(results_directory_path, "descriptive-statistics-clean.rds")
   )
 
 commodities_market_individuals <- dplyr::filter(stats, analysis == "commodity futures") %>%
@@ -105,7 +103,7 @@ commodities_market_countries <- dplyr::filter(stats, analysis == "commodity futu
 commodities <- dplyr::filter(commodities_market_individuals, regime == "all") %>%
   dplyr::select(-c(regime, min, max)) %>% 
   dplyr::mutate(
-    mean = percentize(mean), sd = percentize(sd),
+    mean = slituR::percentize(mean), sd = slituR::percentize(sd),
     mean = purrr::map2_chr(p.value, mean, ~ significance(.x, .y))
   ) %>% dplyr::select(-p.value) %>%
   tidyr::pivot_longer(
@@ -120,7 +118,7 @@ countries <- dplyr::filter(commodities_market_countries, regime == "all") %>%
   dplyr::mutate(asset = paste(country, "commodities", sep = " ")) %>%
   dplyr::select(-country) %>% 
   dplyr::mutate(
-    mean = percentize(mean), sd = percentize(sd),
+    mean = slituR::percentize(mean), sd = slituR::percentize(sd),
     mean = purrr::map2_chr(p.value, mean, ~ significance(.x, .y))
   ) %>% dplyr::select(-p.value) %>%
   tidyr::pivot_longer(
@@ -133,7 +131,7 @@ descriptive_stats_whole <- dplyr::bind_rows(commodities, countries)
 commodities <- dplyr::filter(commodities_market_individuals, regime != "all") %>%
   dplyr::select(-c(min, max)) %>% 
   dplyr::mutate(
[…]

### 2024-10-30 docs/paper.qmd
minor regime difference test results section edit

@@
 For the twenty-four US commodities over this period, fourteen have higher mean returns during phases of **contango** over **backwardation**.
-Four of the six GB metals achieved higher mean returns over **contango** relative to **backwardation** phases with the difference being statistically significant for one commodity.
+Four of the six GB metals achieved higher mean returns over **contango** relative to **backwardation** phases with the difference being statistically significant at the 5% level for one commodity (Nickel-primary (XLME)).
 The equally weighted US portfolio had a mean return of 15.7% over **backwardation** against 16.2% during phases of **contango**, both statistically significant at the 10% level.
@@
 The improvement in the CHP factor's pricing performance remarkably comes predominantly from the long leg (low CHP assets: Keynesian "normal backwardation") of the factor^[Results available from the authors upon request.] with the corresponding mimicking portfolio's performance itself driven by the metals, the precious sub-sector in particular.
-The average $R^{2}$ for the group jumps to 55% during financialisation from less than 12% over the past period while the short leg sees a far smaller increase, up to 8.9% from 3.3% over the past period.
-Interestingly, although the term structure factor itself only sees a very modest increase, its short leg (low roll-yield assets: Working's backwardation) shows a sizeable rise in pricing performance, yet again driven the metals sector, with the average $R^{2}$ for the group's US traded assets jumping to 28.2% during financialisation from 6.2% over the past period.
+Interestingly, although the term structure factor itself only sees a very modest increase, its short leg (low roll-yield assets: Working's backwardation) shows a sizeable rise in pricing performance, yet again driven the metals sector.
 The pattern of results for both factors extends to the GB traded assets and suggest a convergence of Keneysian and Working's term structure perspective over the financialisation period.
-Taken together these results emphasise the global nature of the impact of financialisation on the metals complex and provide further evidence that global metals co-movement could be detected by US based factor models that combine the Keynesian and Working’s term structure paradigms.
-There seems thus to be information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm and these findings therefore appear to complement the results of @kang_tale_2020 who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
+Taken together these results emphasise the global nature of the impact of financialisation on the metals complex suggest that there is information in the factor constructed from hedging pressure based on the Keynesian paradigm relevant to the term structure factor built on the Working paradigm.
+These findings therefore appear to complement the results of @kang_tale_2020 who find that hedging pressure both conveys information about liquidity provision in the short term (Working paradigm) and risk transfer in the longer term (Keynesian paradigm).
 

### 2024-10-30 explore/scripts/revision-jfm/tables.r
Harmonise period labels + EW portfolios sort
in regime difference test results table

@@ -7,6 +7,7 @@ data("exchanges", package = "fewISOs")
 
 ## variables ####
 factors <- c("market", "CHP", "open interest nearby", "open interest aggregate", "term structure")
+period_levels <- c("past", "financialisation", "crisis", "post-crisis")
 results_directory_path <- here::here("explore", "results", "revision-jfm")
 sector_levels <- c("all", "agriculturals", "energy", "metals")
 sort_levels <- c(
@@ -209,11 +210,24 @@ regime_difference_tests <-
     significance = slituR::significance(`p-value`),
     `p-value` = slituR::percentize(as.numeric(`p-value`)),
     sector = factor(sector, levels = sector_levels),
-    subsector = factor(subsector, levels = subsector_levels)
+    subsector = factor(subsector, levels = subsector_levels),
+    period = ifelse(period == "financialization", "financialisation", period),
+    period = ifelse(period == "present", "post-crisis", period),
+    period = factor(period, levels = period_levels)
     ) %>%
-  dplyr::arrange(country, sector, subsector, name) %>%
+  dplyr::arrange(country, sector, subsector, name, period) %>%
   dplyr::select(asset = name, period, moment, `dominant regime`, `p-value`, significance)
 
+individuals <- dplyr::filter(
+    regime_difference_tests, !asset %in% c("US commodities", "GB commodities")
+  )
+countries = dplyr::filter(
+  regime_difference_tests, asset %in% c("US commodities", "GB commodities")
+  ) %>% dplyr::mutate(
+    asset = factor(asset, levels = c("US commodities", "GB commodities"))
+  ) %>% dplyr::arrange(asset, period)
+
+regime_difference_tests <- dplyr::bind_rows(individuals, countries)
 
 # correlations ####
 correlations <- readr::read_rds(

### 2024-10-30 docs/paper.qmd
Include regime difference test results table

@@
 ```{r}
+#| label: tbl-regime-diference-tests
+#| tbl-cap: "This table shows the results for tests of difference in mean (t-test) and variance (F-test) between phases of aggregate backwardation and contango for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+1%, 5% and 10% p-value levels are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively in the significance column.
+Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
+
+colnames <- c("asset", "period", "moment", "dominant regime", "p-value", "significance")
+align <- make_series_of_repeated_chars(list(l = 4L, r = 2L))
+
+make_table("regime difference tests", colnames, align, 1L:4L, 5L:6L)
+```
+
+\newpage
+
+```{r}
 #| label: tbl-time-reg-US-CHP

### 2024-10-30 docs/paper.tex
Include regime difference test results table

@@
 \textbf{contango} relative to \textbf{backwardation} phases with the
-difference being statistically significant for one commodity. The
-equally weighted US portfolio had a mean return of 15.7\% over
-\textbf{backwardation} against 16.2\% during phases of
-\textbf{contango}, both statistically significant at the 10\% level. The
-difference was considerably more pronounced for the equally weighted GB
-metals portfolio with a mean return of 8\% during \textbf{backwardation}
-rising to 35.6\% during \textbf{contango}.
+difference being statistically significant at the 5\% level for one
+commodity (Nickel-primary (XLME)). The equally weighted US portfolio had
+a mean return of 15.7\% over \textbf{backwardation} against 16.2\%
+during phases of \textbf{contango}, both statistically significant at
+the 10\% level. The difference was considerably more pronounced for the
+equally weighted GB metals portfolio with a mean return of 8\% during
+\textbf{backwardation} rising to 35.6\% during \textbf{contango}.
 
@@
 investment it simultaneously influenced the entire spectrum of liquid
-commodities; this sweeping impact spurred the transformation of
-commodity markets from a collection of idiosyncratic markets into a more
-homogeneous collection akin to an asset class. In this context
-interconnectedness emerges as a crucial aspect that warrants thorough
-examination.\\
+commodities, eventually spurring the transformation of commodity markets
+from a collection of idiosyncratic markets into a more homogeneous
+collection akin to an asset class. In this context, interconnectedness
+emerges as a crucial aspect that warrants thorough examination.\\
 We strive to address this issue by first examining the average of weekly
@@
 returns are, as demonstrated in Table~\ref{tbl-stats-combined}.\\
-We further examine these correlations by year in
+We break down these average correlations by years in
 Table~\ref{tbl-correlations-years}. For the full sample of assets, the
 average pairwise correlations remain in the 0.06--0.08 range from 1998
-through 2003, before suddenly increasing to 0.12 from 2003 to 2004,
-suggesting 2004 as a distinct break point corresponding to the onset of
+through 2003, before suddenly increasing to 0.12 from 2003 to 2004. This
+suggests 2004 as a distinct break point for the onset of
 financialisation, as noted in several studies
@@
 market factor mimicking portfolio constituted of the twenty-four US
-traded commodities considered in the study with equal weighting. This
-portfolio enables a refined examination of cross-correlations across
-sectors as the numerator of the beta of the regression of the returns
-for an individual commodity against those for the market factor is
-driven by covariances while the denominator is driven by the individual
-commodity variance. Thus, an increase in a commodity's correlation with
-other commodities should lead to an increase in its beta relative to the
-market factor portfolio. We accordingly regress the weekly individual
-commodity front futures returns against those for our market factor
-portfolio and average the resulting betas across the entire set of
-commodity assets considered as well as by country, sector and sub-sector
-for each of the four periods of interest with the results shown in
+traded commodities with equal weighting. This portfolio enables a
+refined examination of cross-correlations across sectors as the
+numerator of the beta of the regression of the returns for an individual
+commodity against those for the market factor is driven by covariances
+while the denominator is driven by the individual commodity variance.
+Thus, an increase in a commodity's correlation with other commodities
+should lead to an increase in its beta relative to the market factor
+portfolio. We accordingly regress the weekly individual commodity front
+futures returns against those for our market factor portfolio and
+average the resulting betas across the entire set of commodity assets
+considered as well as by country, sector and sub-sector for each of the
+four periods of interest with the results shown in
 Table~\ref{tbl-regressions-index}. The average beta for the US metals
@@
 mimicking portfolio's performance itself driven by the metals, the
-precious sub-sector in particular. The average \(R^{2}\) for the group
-jumps to 55\% during financialisation from less than 12\% over the past
-period while the short leg sees a far smaller increase, up to 8.9\% from
-3.3\% over the past period. Interestingly, although the term structure
-factor itself only sees a very modest increase, its short leg (low
-roll-yield assets: Working's backwardation) shows a sizeable rise in
-pricing performance, yet again driven the metals sector, with the
-average \(R^{2}\) for the group's US traded assets jumping to 28.2\%
-during financialisation from 6.2\% over the past period. The pattern of
-results for both factors extends to the GB traded assets and suggest a
-convergence of Keneysian and Working's term structure perspective over
+precious sub-sector in particular. Interestingly, although the term
+structure factor itself only sees a very modest increase, its short leg
+(low roll-yield assets: Working's backwardation) shows a sizeable rise
+in pricing performance, yet again driven the metals sector. The pattern
+of results for both factors extends to the GB traded assets and suggest
+a convergence of Keneysian and Working's term structure perspective over
 the financialisation period.\\
 Taken together these results emphasise the global nature of the impact
-of financialisation on the metals complex and provide further evidence
-that global metals co-movement could be detected by US based factor
-models that combine the Keynesian and Working's term structure
-paradigms. There seems thus to be information in the factor constructed
-from hedging pressure based on the Keynesian paradigm relevant to the
-term structure factor built on the Working paradigm and these findings
-therefore appear to complement the results of \citet{kang_tale_2020} who
-find that hedging pressure both conveys information about liquidity
-provision in the short term (Working paradigm) and risk transfer in the
-longer term (Keynesian paradigm).
+of financialisation on the metals complex suggest that there is
+information in the factor constructed from hedging pressure based on the
+Keynesian paradigm relevant to the term structure factor built on the
+Working paradigm. These findings therefore appear to complement the
+results of \citet{kang_tale_2020} who find that hedging pressure both
+conveys information about liquidity provision in the short term (Working
+paradigm) and risk transfer in the longer term (Keynesian paradigm).
 
@@
 and \textbf{CHP}'s explanatory power on individual commodity returns
-breaks in the crisis period (Table~\ref{tbl-time-reg-US-CHP}) with both
-now seemingly converging; the US cross-sectional average \(R^{2}\) at
-the individual level bouncing back up (22.5\% vs 20.8\%) while that at
-the aggregate level rises further (14.7\% vs 7.1\%).
+breaks (Table~\ref{tbl-time-reg-US-CHP}) with both now seemingly
+converging; the US cross-sectional average \(R^{2}\) at the individual
+level bouncing back up (22.5\% vs 20.8\%) while that at the aggregate
+level rises further (14.7\% vs 7.1\%).
 
@@
 The average pairwise correlation for the entire set of sample assets
-increases further into the crisis to 0.28
-(Table~\ref{tbl-correlations-periods}) indicating an intensification of
-the higher interdependence within the full cross-section of commodities
-prompted by financialisation. The result is consistent with the greater
-interdependence between equity and commodity markets over this period
-documented in \citet{silvennoinen_financialisation_2013}. The figure for
-the US traded section of the metals sector only progresses modestly to
-0.59 after peaking at 0.63 in 2006 (Table~\ref{tbl-correlations-years}).
-In contrast, the GB traded assets see a sharp increase to over 0.65 in
-the crisis starting in 2007 up to a peak of 0.69 in 2010, and so does
-the agricultural sector with the sharpest increase in 2008 when the
-average pairwise correlation for the sector jumps to 0.30. The energy
-sector also shows a substantial progression starting in 2007 and peaking
-at 0.63 in 2008 before levelling back down over the rest of the period.
-The onset of the financial crisis seems therefore to have had an across
-the board impact on the interdependence of commodities in contrast with
+increases further to 0.28 (Table~\ref{tbl-correlations-periods})
+indicating an intensification of the higher interdependence within the
+full cross-section of commodities prompted by financialisation. The
+result is consistent with the greater interdependence between equity and
+commodity markets over this period documented in
+\citet{silvennoinen_financialisation_2013}. The figure for the US traded
+section of the metals sector only progresses modestly to 0.59 after
+peaking at 0.63 in 2006 (Table~\ref{tbl-correlations-years}). In
+contrast, the GB traded assets see a sharp increase to over 0.65
+starting in 2007 up to a peak of 0.69 in 2010, and so does the
+agricultural sector with the sharpest increase in 2008 when the average
+pairwise correlation for the sector jumps to 0.30. The energy sector
+also shows a substantial progression starting in 2007 and peaking at
+0.63 in 2008 before levelling back down over the rest of the period. The
+onset of the financial crisis seems therefore to have had an across the
+board impact on the interdependence of commodities in contrast with
 financialisation, much more closely related to the metals sector.
@@
 The entire cross-section sees an increase in average regression
-coefficient relative to the market factor over the crisis period with
-the strongest progression for the GB traded metals followed by the
-agricultural sector (Table~\ref{tbl-regressions-index}). The pricing
-performance of the factor dominates the US commodity complex over the
-period (Table~\ref{tbl-regressions-factors}), showing a 50\% increase in
-mean average \(R^{2}\) to over 31\%, while that for both the CHP and
-open interest factor decreases and, although increasing, remains modest
-for the term structure factors; the increase is strongest for the GB
-traded metal assets with an average \(R^{2}\) of almost 34\% for the
-period. Taken together, these results indicate the presence of a
-systematic factor across the entire cross-section of the US commodities.
-For both the CHP and term structure factors, both legs show an increase
-in average \(R^{2}\) and while substantially diverging over the
-preceding financialisation period the pricing performance for both legs
-seems to converge back to a pattern closer to that observed
-pre-financialisation.
+coefficient relative to the market factor with the strongest progression
+for the GB traded metals followed by the agricultural sector
+(Table~\ref{tbl-regressions-index}). The pricing performance of the
+factor dominates the US commodity complex
+(Table~\ref{tbl-regressions-factors}), showing a 50\% increase in mean
+average \(R^{2}\) to over 31\%, while that for both the CHP and open
+interest factor decreases and, although increasing, remains modest for
+the term structure factors; the increase is strongest for the GB traded
+metal assets with an average \(R^{2}\) of almost 34\%. Taken together,
+these results indicate the presence of a systematic factor across the
+entire cross-section of the US commodities.
 
@@
 specific dynamics. The recovery initiated in the crisis period for that
-of CHP is confirmed with a stronger increase in the post-crisis period,
-27.2\% vs.~22.5\%, strongest for the metals sector, 37.3\% vs.~23.7\%,
-while the energy sector shows the opposite pattern: 11\% vs.~16\%. In
-contrast, after increasing stronger in the crisis, that for \textbf{CHP}
-falls overall in the post-crisis period, 7.5\% vs 14.7\%, with the
-decrease strongest for the energy sector in a relative sense: 2.5\%
-vs.~14.8\%.
+of CHP is confirmed with a stronger increase, 27.2\% vs.~22.5\%,
+strongest for the metals sector, 37.3\% vs.~23.7\%, while the energy
+sector shows the opposite pattern: 11\% vs.~16\%. In contrast, after
+increasing stronger in the crisis, that for \textbf{CHP} falls overall
+post-crisis, 7.5\% vs 14.7\%, with the decrease strongest for the energy
+sector in a relative sense: 2.5\% vs.~14.8\%.
 
@@
 
-The average pairwise correlations fall across the board in the
-post-crisis period, below the levels observed during financialisation,
-with the figure for the entire cross-section
-(Table~\ref{tbl-correlations-periods}) dropping down to 0.12 from 0.28
-over the crisis. This substantial decline, that does not appear to have
-been widely noted, appears to begin in the latter part of the crisis
-period, around 2012 (Table~\ref{tbl-correlations-years}), before
-levelling down over the whole post-crisis period.
+The average pairwise correlations fall across the board, below the
+levels observed during financialisation, with the figure for the entire
+cross-section (Table~\ref{tbl-correlations-periods}) dropping down to
+0.12 from 0.28 over the crisis. This substantial decline, that does not
+seem to have been widely noted, appears to begin in the latter part of
+the crisis period, around 2012 (Table~\ref{tbl-correlations-years}),
+before levelling down over the whole post-crisis period.
 
@@
 and term structure factors falls back to levels below those attained
-over financialisation while the gap between their long and short legs
-remains narrower than observed during that period. These results, along
-with those from the crisis period, suggest that the exogenous shock of
-the financial crisis, combined with the subsequent accommodative
-monetary policy, may have triggered a reversion toward
-pre-financialization fundamentals in the commodity futures complex; an
-issue that, to our knowledge, has not been widely discussed in the
-existing literature.\\
+over financialisation. These results, along with those from the crisis
+period, suggest that the exogenous shock of the financial crisis,
+combined with the subsequent accommodative monetary policy, may have
+triggered a reversion toward pre-financialization fundamentals in the
+commodity futures complex; an issue that, to our knowledge, has not been
+widely discussed in the existing literature.\\
 The phases analysis further documents the emerging role/dominance of the
@@
 these results indicate some recent changes in the correlation structure
-within the sector and along with the decline in interdependence in the
-commodity sector at large documented above, this observation could form
-a valuable basis for future research.\\
-These findings providence additional evidence that the interdependence
-effects of financialization seems to have been strongest for the entire
-cross-section of the metals sector with a lesser impact for the other
-sectors.
+within the sector and provide additional evidence that the
+interdependence effects of financialization seems to have been strongest
+for the entire cross-section of the metals sector with a lesser impact
+for the other sectors. This observation, along with the decline in
+interdependence in the commodity sector at large documented above, could
+form a valuable basis for future research.
 
@@
 
+\begin{longtable}[t]{>{}l>{}l>{}l>{}l>{}r>{}r}
+
+\caption{\label{tbl-regime-diference-tests}This table shows the results
+for tests of difference in mean (t-test) and variance (F-test) between
+phases of aggregate backwardation and contango for the twenty four
+individual US commodities and the six GB metals considered in the study
+as well as for two equally weighted portfolios formed from the US
+commodities and the GB metals respectively across the four periods of
+interest (past: 1997-2003; financialisation: 2004-2008; crisis:
+2008-2013; post-crisis: 2013-2018). 1\%, 5\% and 10\% p-value levels are
+marked with ***, ** and * respectively in the significance column.
+Aggregate CHP construction and corresponding regime definitions are
+discussed in Section~\ref{sec-methods} while the results are discussed
+in Section~\ref{sec-results}.}
+
+\tabularnewline
+
+\toprule
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{period}} & \textcolor{black}{\textbf{moment}} & \textcolor{black}{\textbf{dominant regime}} & \textcolor{black}{\textbf{p-value}} & \textcolor{black}{\textbf{significance}}\\
+\midrule
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{34.26\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{89.69\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.01\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{47.46\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{40.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{57.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.02\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{38.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Oats (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{35.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Oats (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.66\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Oats (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{82.72\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Oats (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{66.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{81.2\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.83\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.57\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{75.13\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.31\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{31.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Soybean oil (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{81.72\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{92.18\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.2\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{18.64\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{69.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.36\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{48.92\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybeans (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{17.18\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{38.74\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Soybeans (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{57.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybeans (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{37.95\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybeans (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.05\%} & \textcolor[HTML]{4285f4}{*}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{44.86\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.79\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{83.21\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{76.2\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Wheat-SRW (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.51\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.81\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{94.9\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{76.82\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.34\%} & \textcolor[HTML]{4285f4}{*}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{6.35\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{62.38\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{99.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{50.04\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Cattle-feeder (XCME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{51.11\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cattle-live (XCME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{15.26\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{51.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cattle-live (XCME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{20.96\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{82.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cattle-live (XCME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{63.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cattle-live (XCME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{45.71\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Lean hogs (XCME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{24.77\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{55.51\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lean hogs (XCME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{68.46\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lean hogs (XCME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{21.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lean hogs (XCME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{6.81\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{99.36\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cocoa (IFUS)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{12.33\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.85\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Cocoa (IFUS)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{7.73\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{42.98\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cocoa (IFUS)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{51.48\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cocoa (IFUS)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.17\%} & \textcolor[HTML]{4285f4}{**}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{53.38\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{69.3\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.63\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{95.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Coffee-C (IFUS)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{82.84\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{35.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{52.86\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{6.02\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{41.38\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.06\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{26.81\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{14.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{33.04\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{32.06\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Cotton-\#2 (IFUS)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.67\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{\cellcolor{gray!10}{Lumber-random length (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{37.56\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lumber-random length (XCME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{75.67\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Lumber-random length (XCME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{84.3\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lumber-random length (XCME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.36\%} & \textcolor[HTML]{4285f4}{**}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Lumber-random length (XCME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{28.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lumber-random length (XCME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{22.82\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Lumber-random length (XCME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{4.31\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{Lumber-random length (XCME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Orange juice-frozen concentrated (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{66.85\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Orange juice-frozen concentrated (IFUS)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Orange juice-frozen concentrated (IFUS)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{28.81\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Orange juice-frozen concentrated (IFUS)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{92.47\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Orange juice-frozen concentrated (IFUS)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{67.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Orange juice-frozen concentrated (IFUS)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Orange juice-frozen concentrated (IFUS)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{25.72\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Orange juice-frozen concentrated (IFUS)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.01\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{24.1\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.76\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{75.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Sugar-\#11 (IFUS)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.89\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.08\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.22\%} & \textcolor[HTML]{4285f4}{*}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{4.66\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{Natural gas (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.01\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{68.1\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Natural gas (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.28\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Natural gas (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{67.04\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Natural gas (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.08\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{38.33\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{61.91\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{49.38\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{95.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{18.99\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Crude oil-WTI (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{18.96\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Gasoline (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{66.51\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{58.35\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Gasoline (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.58\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{49.08\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Gasoline (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{34.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Gasoline (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{21.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Heating oil (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.45\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{99.52\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Heating oil (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.52\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{23.31\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Heating oil (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{15.71\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Heating oil (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{90.64\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Copper (XCEC)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{17.88\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{74.37\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Copper (XCEC)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.71\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{55.78\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Copper (XCEC)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{17.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Copper (XCEC)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{43.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Gold (XCEC)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{96.63\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Gold (XCEC)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.92\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{60.22\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Gold (XCEC)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.58\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Gold (XCEC)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.77\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{***}}\\
+\textbf{Palladium (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{30.26\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Palladium (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.38\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{96.05\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Palladium (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{9.4\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\addlinespace
+\textbf{Palladium (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{6.08\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{Platinum (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{14.41\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Platinum (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.86\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{85.5\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Platinum (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{27.26\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Platinum (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{96.07\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Silver (XCEC)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.09\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{88.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Silver (XCEC)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.01\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{87.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Silver (XCEC)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.08\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{61.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Silver (XCEC)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Aluminium-primary (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{86.1\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Aluminium-primary (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Aluminium-primary (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Aluminium-primary (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.33\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Aluminium-primary (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{10.79\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Aluminium-primary (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.41\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Aluminium-primary (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.33\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{Aluminium-primary (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{25.99\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{88.51\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Copper (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{87.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Copper (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.15\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{43.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Copper (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{16.36\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Copper (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Lead-refined pig (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{58.96\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lead-refined pig (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.81\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Lead-refined pig (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{40.11\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lead-refined pig (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.11\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{Lead-refined pig (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.17\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lead-refined pig (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Lead-refined pig (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{15.62\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Lead-refined pig (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{85.45\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{76.56\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.04\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.24\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.62\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{49.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.46\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{***}}\\
+\textbf{Nickel-primary (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{69.15\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{5.22\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\addlinespace
+\textbf{Tin-refined (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{14.94\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{70.17\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Tin-refined (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{58.14\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{34.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Tin-refined (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{73.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Tin-refined (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Zinc (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.75\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{37.67\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Zinc (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.29\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.89\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Zinc (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{5.05\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{Zinc (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{1.77\%} & \textcolor[HTML]{4285f4}{**}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{3.63\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{US commodities} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{54.29\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.09\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{US commodities} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.22\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{58.92\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{US commodities} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{11.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{US commodities} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{78.74\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{GB commodities} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{27.95\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{GB commodities} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.65\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{46.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{GB commodities} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.37\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\addlinespace
+\textbf{GB commodities} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.13\%} & \textcolor[HTML]{4285f4}{***}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
+\newpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
 \begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}

### 2024-10-31 docs/paper.qmd
Reference new table in results section

@@
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
-@tbl-stats-combined further shows the mean returns and volatilities for high (**contango**) and low (**backwardation**) **CHP** regimes for each time period.
+@tbl-stats-combined further shows the mean returns and volatilities for high (**contango**) and low (**backwardation**) **CHP** regimes for each time period while @tbl-regime-diference-tests shows the results of difference tests for returns mean and variance between the two regimes.
 Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another.
@@
 The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of **backwardation** relative to **contango**, more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
-The difference is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
+The difference (@tbl-regime-diference-tests) is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
 The pattern is more pronounced for the GB traded subset with all six assets showing higher mean returns in **backwardation** with the difference significant at the 1% level for Nickel-primary (XLME), 5% level for Aluminium (XLME) and 10% level for Zinc (XLME).

### 2024-10-31 docs/paper.tex
Reference new table in results section

@@
 (\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP}
-regimes for each time period.\\
+regimes for each time period while
+Table~\ref{tbl-regime-diference-tests} shows the results of difference
+tests for returns mean and variance between the two regimes.\\
 Over the first period eighteen of the twenty-four US commodities have
@@
 the crisis period with seventeen US commodities showing higher mean
-returns over \textbf{backwardation} phases. The difference is
-significant at the 5\% level for Lumber (XCME) and at the 10\% level for
-Palladium (XNYM) while no difference is significant for the assets
-showing higher figures over phases of \textbf{contango}. The pattern is
-more pronounced for the GB traded subset with all six assets showing
-higher mean returns in \textbf{backwardation} with the difference
-significant at the 1\% level for Nickel-primary (XLME), 5\% level for
-Aluminium (XLME) and 10\% level for Zinc (XLME). It also extends to
-equally weighted portfolios of US and GB traded assets that both show
-higher mean returns during \textbf{backwardation} with the difference
-significant at the 5\% level for the GB portfolio and the figure close
-to the 10\% level significance threshold for the portfolio of US assets.
-Volatilities are overall higher in \textbf{contango} although less so
-than over the previous period with seventeen US commodities showing
-higher figures over \textbf{contango} against twenty-three in the crisis
-period. The pattern extends to three of the six GB traded metals with
-the difference significant at the 1\% level for Copper (XLME) and Tin
-(XLME) and at the 5\% level for Zinc (XLME) while differences are not
-significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME)
-that exhibit higher volatility over \textbf{backwardation} phases.
-Equally weighted portfolios of US and GB traded assets on the other hand
-both show higher volatility in \textbf{contango} with the difference
-significant at the 1\% level for both. Over the financialisation period
-in contrast volatilities were predominantly higher in
-\textbf{backwardation} for US traded assets with fourteen commodities
-showing higher volatility figures in these phases; the post-crisis
-pattern of results for volatilities thus likewise shows signs of
-reversion to pre-financialisation standards. After showing signs of
-convergence in the crisis period the dynamics of the explanatory power
-of CHP and \textbf{CHP} part ways (Table~\ref{tbl-time-reg-US-CHP}),
-seemingly reverting to the Keynesian paradigm observed
-pre-financialisation, further suggesting a return to legacy commodity
-specific dynamics. The recovery initiated in the crisis period for that
-of CHP is confirmed with a stronger increase, 27.2\% vs.~22.5\%,
-strongest for the metals sector, 37.3\% vs.~23.7\%, while the energy
-sector shows the opposite pattern: 11\% vs.~16\%. In contrast, after
-increasing stronger in the crisis, that for \textbf{CHP} falls overall
-post-crisis, 7.5\% vs 14.7\%, with the decrease strongest for the energy
-sector in a relative sense: 2.5\% vs.~14.8\%.
+returns over \textbf{backwardation} phases. The difference
+(Table~\ref{tbl-regime-diference-tests}) is significant at the 5\% level
+for Lumber (XCME) and at the 10\% level for Palladium (XNYM) while no
+difference is significant for the assets showing higher figures over
+phases of \textbf{contango}. The pattern is more pronounced for the GB
+traded subset with all six assets showing higher mean returns in
+\textbf{backwardation} with the difference significant at the 1\% level
+for Nickel-primary (XLME), 5\% level for Aluminium (XLME) and 10\% level
+for Zinc (XLME). It also extends to equally weighted portfolios of US
+and GB traded assets that both show higher mean returns during
+\textbf{backwardation} with the difference significant at the 5\% level
+for the GB portfolio and the figure close to the 10\% level significance
+threshold for the portfolio of US assets. Volatilities are overall
+higher in \textbf{contango} although less so than over the previous
+period with seventeen US commodities showing higher figures over
+\textbf{contango} against twenty-three in the crisis period. The pattern
+extends to three of the six GB traded metals with the difference
+significant at the 1\% level for Copper (XLME) and Tin (XLME) and at the
+5\% level for Zinc (XLME) while differences are not significant for
+Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit
+higher volatility over \textbf{backwardation} phases. Equally weighted
+portfolios of US and GB traded assets on the other hand both show higher
+volatility in \textbf{contango} with the difference significant at the
+1\% level for both. Over the financialisation period in contrast
+volatilities were predominantly higher in \textbf{backwardation} for US
+traded assets with fourteen commodities showing higher volatility
+figures in these phases; the post-crisis pattern of results for
+volatilities thus likewise shows signs of reversion to
+pre-financialisation standards. After showing signs of convergence in
+the crisis period the dynamics of the explanatory power of CHP and
+\textbf{CHP} part ways (Table~\ref{tbl-time-reg-US-CHP}), seemingly
+reverting to the Keynesian paradigm observed pre-financialisation,
+further suggesting a return to legacy commodity specific dynamics. The
+recovery initiated in the crisis period for that of CHP is confirmed
+with a stronger increase, 27.2\% vs.~22.5\%, strongest for the metals
+sector, 37.3\% vs.~23.7\%, while the energy sector shows the opposite
+pattern: 11\% vs.~16\%. In contrast, after increasing stronger in the
+crisis, that for \textbf{CHP} falls overall post-crisis, 7.5\% vs
+14.7\%, with the decrease strongest for the energy sector in a relative
+sense: 2.5\% vs.~14.8\%.
 

### 2024-10-31 explore/scripts/revision-jfm/functions.r
suppress group_by warnings + format variables

@@ -280,8 +280,7 @@ compute_individual_CHP <- function(filtered_CFTC_data){
 
 compute_aggregate_CHP <- function(individual_CHP){
   dplyr::group_by(individual_CHP, date) %>% 
-    dplyr::summarise(aggregate_CHP = mean(pressure, na.rm = T)) %>%
-    dplyr::ungroup()
+    dplyr::summarise(aggregate_CHP = mean(pressure, na.rm = T), .groups = "drop") 
 }
 
 make_aggregate_CHP <- function(){
@@ -402,8 +401,7 @@ compute_commodity_futures_index_returns <- function(price_levels){
   dplyr::group_by(price_levels, `active contract ticker`) %>%
     dplyr::mutate(return = value/dplyr::lag(value) - 1L) %>%
     dplyr::select(-value) %>% dplyr::group_by(date) %>%
-    dplyr::summarise(return = mean(return, na.rm = T)) %>%
-    dplyr::ungroup()
+    dplyr::summarise(return = mean(return, na.rm = T), .groups = "drop")
 }
 
 make_commodity_futures_index_returns_dataframe <- function(
@@ -913,7 +911,7 @@ split_returns_by_regime <- function(returns, regimes){
   
   dplyr::left_join(returns, regimes, by = "date") %>% 
     dplyr::filter(! is.na(regime)) %>% dplyr::group_by(regime) %>% 
-    dplyr::summarise(returns = list(return)) %>%  
+    dplyr::summarise(returns = list(return), .groups = "drop") %>%  
     tibble::deframe()
 }
 
@@ -978,7 +976,7 @@ make_commodity_futures_country_indexes_returns_dataframe <- function(){
       make_ticker_country_dataframe(unique(individual_commodity_returns$ticker)),
       by = "ticker"
     ) %>% dplyr::group_by(country, date) %>% 
-      dplyr::summarise(return = mean(return, na.rm = TRUE)) %>% dplyr::ungroup() %>%
+      dplyr::summarise(return = mean(return, na.rm = TRUE), .groups = "drop") %>%
       dplyr::mutate(ticker = paste(country, "commodities", sep = " ")) %>%
       dplyr::select(ticker, date, return)
 }
@@ -1294,8 +1292,7 @@ average_Rsquared_by_factor_leg_for_each_type_frequency_field_period_regime_combi
       dplyr::mutate(averages, averages = purrr::map(results, function(averages){
[…]

### 2024-10-31 docs/paper.tex
rerender paper

@@
 \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.99\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.93\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.43\%}} & \textcolor[HTML]{4285f4}{\textbf{3.78\%}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.92\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.43\%}} & \textcolor[HTML]{4285f4}{\textbf{3.78\%}}\\
 \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}}\\
 \addlinespace
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.54\%}} & \textcolor[HTML]{4285f4}{\textbf{5.55\%}} & \textcolor[HTML]{4285f4}{\textbf{4.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{5.55\%}} & \textcolor[HTML]{4285f4}{\textbf{4.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}}\\
 \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}}\\
@@
 \addlinespace
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.4\%}} & \textcolor[HTML]{4285f4}{\textbf{5.8\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.38\%}} & \textcolor[HTML]{4285f4}{\textbf{5.8\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.54\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{6.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.14\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{6.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.14\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.91\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.03\%}} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.11\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.21\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}} & \textcolor[HTML]{4285f4}{\textbf{1.56\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}} & \textcolor[HTML]{4285f4}{\textbf{1.56\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}}\\
 \addlinespace
@@
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{44.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.71\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.64\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{0.78\%}} & \textcolor[HTML]{4285f4}{\textbf{2.98\%}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{0.78\%}} & \textcolor[HTML]{4285f4}{\textbf{2.98\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.46\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.06\%}} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.06\%}} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.04\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{2.06\%}} & \textcolor[HTML]{4285f4}{\textbf{3.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.63\%}} & \textcolor[HTML]{4285f4}{\textbf{2.06\%}} & \textcolor[HTML]{4285f4}{\textbf{3.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.94\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.35\%}} & \textcolor[HTML]{4285f4}{\textbf{1.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.71\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{1.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.71\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.6\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}}\\
 \addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
@@
 \addlinespace
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{3.5\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{3.5\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.68\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{6.05\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{7.91\%}}\\
+\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{5.95\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{7.91\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.67\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.96\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.37\%}} & \textcolor[HTML]{4285f4}{\textbf{3.62\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{16.2\%}}\\
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.62\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{16.2\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.3\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.26\%}} & \textcolor[HTML]{4285f4}{\textbf{13.46\%}} & \textcolor[HTML]{4285f4}{\textbf{13.84\%}}\\
+\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.46\%}} & \textcolor[HTML]{4285f4}{\textbf{5.26\%}} & \textcolor[HTML]{4285f4}{\textbf{13.46\%}} & \textcolor[HTML]{4285f4}{\textbf{13.84\%}}\\
 \addlinespace
@@
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.71\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.99\%}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10.41\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.99\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}} & \textcolor[HTML]{4285f4}{\textbf{0.96\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}}\\
+\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.45\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}} & \textcolor[HTML]{4285f4}{\textbf{0.96\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{45.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.56\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.33\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.71\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.72\%}} & \textcolor[HTML]{4285f4}{\textbf{23.49\%}} & \textcolor[HTML]{4285f4}{\textbf{21.5\%}} & \textcolor[HTML]{4285f4}{\textbf{13.38\%}}\\
+\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{23.49\%}} & \textcolor[HTML]{4285f4}{\textbf{21.5\%}} & \textcolor[HTML]{4285f4}{\textbf{13.38\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.27\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.5\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.58\%}} & \textcolor[HTML]{4285f4}{\textbf{5.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{5.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}}\\
 \addlinespace
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}}\\
+\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}} & \textcolor[HTML]{4285f4}{\textbf{6.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.46\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.81\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.76\%}} & \textcolor[HTML]{4285f4}{\textbf{26.82\%}} & \textcolor[HTML]{4285f4}{\textbf{16.5\%}}\\
+\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.86\%}} & \textcolor[HTML]{4285f4}{\textbf{27.76\%}} & \textcolor[HTML]{4285f4}{\textbf{26.82\%}} & \textcolor[HTML]{4285f4}{\textbf{16.5\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}}\\
@@
 \textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.72\%}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.03\%}} & \textcolor[HTML]{4285f4}{\textbf{3.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}}\\
 \addlinespace

### 2024-11-01 docs/paper.qmd
Corrections: semantics + frequencies

@@
   - Financialisation
+  - Co-movement
   - Asset pricing
@@
 tables <- readr::read_rds(paste_forward_slash(tables_directory_path, "tables-formatted.rds"))
-sectors <- c("country", "sector", "subsector")
+sectors <- c("country", "sector", "sub-sector")
 periods <- c("past", "financialisation", "crisis", "post-crisis")
@@
 
-These entered the commodity spectrum en masse with across-the-board index type positions propping the transition of the complex from a collection of idiosyncratic markets towards a more homogeneous ensemble akin to an asset class.
-In this context of heightened cross-asset market participation the issue of interconnectedness stands out as paramount and we strive to investigate it by first examining the correlation structure of our sample set of assets at the global, country, sector and subsector levels.
+These entered the commodity spectrum en masse with across-the-board index type positions prompting the transition of the complex from a collection of idiosyncratic markets towards a more cohesive ensemble akin to an asset class.
+In this context of heightened cross-asset market participation the issue of interconnectedness stands out as paramount and we strive to investigate it by first examining the correlation structure of our sample set of assets at the global, country, sector and sub-sector levels.
 Our results indicate higher interdependence within the full cross-section of commodities over the financialisation period, consistent with both the empirical and theoretical literature.
@@
 This contention has since come to be known as the "Masters’ hypothesis" and was largely endorsed by the final US Senate report on the issue [@senate_excessive_2009].
-At this stage, the question thrust on the academic sphere was whether "excessive speculation" (understood as the market activity peculiar to index type investors) was linked to escalating energy and agricultural commodity prices.
+At this stage, the question thrust on the academic sphere was whether "excessive speculation"^[Understood as the market activity peculiar to index type investors.] was linked to escalating energy and agricultural commodity prices.
 A number of ensuing academic studies, most of which used commodity specific correlation and causality based analysis have since disproved this contention: @irwin_devil_2009, @sanders_adequacy_2010, @sanders_impact_2011, @sanders_new_2011, @irwin_commodity_2013, @brunetti_commodity_2014, @hamilton_effects_2015 and @bruno_financialisation_2017 investigated the issue in the context of the agricultural markets; meanwhile, @buyuksahin_speculators_2011, @tokic_speculation_2012, @fattouh_role_2013, @kilian_role_2014, @knittel_simple_2016 and @manera_modelling_2016 examined the energy markets while @bohl_does_2013, @kim_does_2015 and @boyd_prevalence_2016 studied both energy and agricultural markets and @irwin_index_2011, @irwin_financialisation_2012 as well as @stoll_commodity_2011 examined the commodity markets in general.
@@
 
-For each commodity asset we compute the weekly front futures return and commercial hedging pressure (CHP) time series with the CHP calculated as the ratio of the number of long commercial positions to the total number of commercial positions for the considered asset-week combination.
-For each asset-period combination we compute the average return and corresponding volatility over the entire period as well as over phases of cross-sectional low and high CHP^[Aggregate CHP or **CHP**: see below for a formal definition and description of the phase construction process.].
-These statistics are also computed for equally weighted portfolios of the US and GB traded commodity assets independently.
+For each commodity asset we compute the daily and weekly front futures return as well as weekly commercial hedging pressure (CHP) time series with the CHP calculated as the ratio of the number of long commercial positions to the total number of commercial positions for the considered asset-week combination.
+For each asset-period combination we compute the average annual daily return and corresponding volatility over the entire period as well as over phases of cross-sectional low and high CHP^[Aggregate CHP or **CHP**: see below for a formal definition and description of the phase construction process.] and further test for significance in difference between the two regimes using t-tests for mean returns and F-test for corresponding variances.
+These statistics are also computed, and their difference between regimes tested, for equally weighted portfolios of the US and GB traded commodity assets independently.
 
-For each period, the return series for the individual US-traded assets are regressed on both the relative change on their respective CHP series and that on the cross-sectional CHP independently.
-The resulting $R^{2}$ values are then averaged by sector and subsector.
-Additionally, pairwise correlations are computed for each combination of assets across the periods of interest and for each individual year within the full sample period.
-These correlation coefficients are then averaged across the entire cross-section of assets, as well as by country, sector, and subsector.
+For each period, the weekly return series for the individual US-traded assets are regressed on both the relative change on their respective CHP series and that on the cross-sectional CHP independently.
+The resulting $R^{2}$ values are then averaged by sector and sub-sector.
+Additionally, pairwise daily return correlations are computed for each combination of assets across the periods of interest and for each individual year within the full sample period.
+These correlation coefficients are then averaged across the entire cross-section of assets, as well as by country, sector, and sub-sector.
 For each period, the coefficients are also calculated and averaged across phases of low and high cross-sectional CHP.
@@
 
-We use a time series regression approach where individual commodity weekly front futures contract returns are regressed on returns to the mimicking portfolio for a particular risk factor with the corresponding $\beta$s and $R^{2}$s averaged.
+We use a time series regression approach where individual commodity front futures contract daily returns are regressed on returns to the mimicking portfolio for a particular risk factor with the corresponding $\beta$s and $R^{2}$s averaged.
 For the long-short factors the $\beta$s and $R^{2}$s are computed for models where the regressor is the factor itself as well as both its long and short legs independently (results available upon request).
@@
 
-Financialisation was a global phenomenon, through the channel of index investment it simultaneously influenced the entire spectrum of liquid commodities, eventually spurring the transformation of commodity markets from a collection of idiosyncratic markets into a more homogeneous collection akin to an asset class.
+Financialisation was a global phenomenon, through the channel of index investment it simultaneously influenced the entire spectrum of liquid commodities, eventually spurring the transformation of commodity markets from a collection of idiosyncratic markets into a more cohesive collection akin to an asset class.
 In this context, interconnectedness emerges as a crucial aspect that warrants thorough examination.
-We strive to address this issue by first examining the average of weekly returns pairwise correlations between commodities across the entire cross-section of the commodity assets considered in the study as well as by country, sector and sub-sector.
+We strive to address this issue by first examining the average returns pairwise correlations between commodities across the entire cross-section of the commodity assets considered in the study as well as by country, sector and sub-sector.
 @tbl-correlations-periods shows the results for the four periods of interest with the results reported for the entire period as well as for periods of **backwardation** and **contango**.
@@
 Thus, an increase in a commodity's correlation with other commodities should lead to an increase in its beta relative to the market factor portfolio.
-We accordingly regress the weekly individual commodity front futures returns against those for our market factor portfolio and average the resulting betas across the entire set of commodity assets considered as well as by country, sector and sub-sector for each of the four periods of interest with the results shown in @tbl-regressions-index.
+We accordingly regress the individual commodity front futures returns against those for our market factor portfolio and average the resulting betas across the entire set of commodity assets considered as well as by country, sector and sub-sector for each of the four periods of interest with the results shown in @tbl-regressions-index.
 The average beta for the US metals sector jumps sharply to 1.12 over financialisation from 0.63 over the previous period; the increase is even more dramatic for the base metals sub-sector (GB traded assets) in a relative sense.
-The group had a much lower beta of 0.27 over the past period, suggesting a low level of correlation with US commodities; this figure increases to 0.85 over the financialisation period, even beyond that for the US agricultural sector of 0.80.
-In contrast, the corresponding figure for the energy sector show a substantial decrease, down to 1.61 during financialisation from 2.33 over the past period.
+The group had a much lower average beta of 0.27 over the past period, suggesting a low level of correlation with US commodities; this figure increases to 0.85 over the financialisation period, even beyond that for the US agricultural sector of 0.80.
+In contrast, the corresponding figure for the energy sector shows a substantial decrease, down to 1.61 during financialisation from 2.33 over the past period.
 The corresponding pricing performance displays a similar pattern as shown in @tbl-regressions-factors where for each period the corresponding $R^{2}$ values are independently averaged over the entire period as well as over periods of **contango** and **backwardation**.
@@
 The decline seems driven by the metals sector, particularly the GB traded segment, with the figures for the US and GB traded assets at 0.91 and 0.72, down from 1.12 and 1.18, respectively.
-Meanwhile, the pricing performance of the market factor also retreats to below financialisation levels with the average $R^{2}$ for the entire cross-section dropping down to 14.7% (@tbl-regressions-factors).
+Meanwhile, the pricing performance of the market factor also recedes to below financialisation levels with the average $R^{2}$ for the entire cross-section dropping down to 14.7% (@tbl-regressions-factors).
 All sectors seem affected with agriculturals, energy and metals all seeing their average $R^{2}$ decline below the levels observed during the financialisation period albeit remaining above 10% for the GB traded metals against less than 2% pre-financialisation.
@@
 #| label: tbl-stats-combined
-#| tbl-cap: "This table shows mean returns and volatility for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+#| tbl-cap: "This table shows mean returns and corresponding volatility for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
 for each period the figures are shown independently for the entire period as well as for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
@@
 #| tbl-cap: "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in \\@sec-methods.
-Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
 The results are discussed in \\@sec-results while \\@sec-taxonomy details the taxonomy for the commodity assets considered."
 
-colnames <- c("regressor", "sector", "subsector", periods)
+colnames <- c("regressor", "sector", "sub-sector", periods)
 align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
@@
 #| label: tbl-correlations-periods
-#| tbl-cap: "This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+#| tbl-cap: "This table shows the average return pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
 For each period, the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
@@
 #| label: tbl-correlations-years
-#| tbl-cap: "This table shows the average pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and subsectors by year for the whole period of interest (1997-2018).
+#| tbl-cap: "This table shows the average return pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and sub-sectors by year for the whole period of interest (1997-2018).
 The results are discussed in \\@sec-results while \\@sec-taxonomy details the taxonomy for the commodity assets considered."
@@
 #| tbl-cap: "This table shows the average time series regression coefficients for models where the returns series for all the commodity assets considered in the study are independently regressed against the return series for our market factor, an equally weighted portfolio of the 24 US commodities considered in the study.
-The results are calculated independently across countries as well as commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+The results are calculated independently across countries as well as commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
 The market factor construction is discussed in \\@sec-methods while the results are discussed in \\@sec-results and the taxonomy for the commodity assets considered is detailed in \\@sec-taxonomy."
@@
 #| tbl-cap: "This table shows the average time series regression $R^{2}$ for models where the returns series for all the commodity assets considered in the study are independently regressed against the return series for our mimicking portfolios for risk factors in returns, including the market, CHP, open interest and term structure factors.
-The results are calculated independently across countries and commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018); for each period the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
+The results are calculated independently across countries and commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018); for each period the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
 Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the taxonomy for the commodity assets considered is detailed in \\@sec-taxonomy."
@@
 #| tbl-cap: "This table shows the detailed taxonomy for the thirty commodity assets considered in the study.
-The assets are classified by the country of residence of the exchange where they are traded as well as by sector and subsector according to the nature of the asset."
+The assets are classified by the country of residence of the exchange where they are traded as well as by sector and sub-sector according to the nature of the asset."
 
-colnames <- c("asset", "country", "sector", "subsector")
+colnames <- c("asset", "country", "sector", "sub-sector")
 align <- make_series_of_repeated_chars(list(l = 4L))

### 2024-11-01 docs/paper.tex
Corrections: semantics + frequencies

@@
   pdfauthor={Devraj Basu; Olivier Bauthéac},
-  pdfkeywords={Commodity markets, Financialisation, Asset pricing},
+  pdfkeywords={Commodity markets, Financialisation, Co-movement, Asset
+pricing},
   colorlinks=true,
@@
 \begin{keyword}
-    Commodity markets \sep Financialisation \sep 
+    Commodity markets \sep Financialisation \sep Co-movement \sep 
     Asset pricing
@@
 These entered the commodity spectrum en masse with across-the-board
-index type positions propping the transition of the complex from a
-collection of idiosyncratic markets towards a more homogeneous ensemble
+index type positions prompting the transition of the complex from a
+collection of idiosyncratic markets towards a more cohesive ensemble
 akin to an asset class. In this context of heightened cross-asset market
@@
 structure of our sample set of assets at the global, country, sector and
-subsector levels. Our results indicate higher interdependence within the
-full cross-section of commodities over the financialisation period,
+sub-sector levels. Our results indicate higher interdependence within
+the full cross-section of commodities over the financialisation period,
 consistent with both the empirical and theoretical literature. The
@@
 At this stage, the question thrust on the academic sphere was whether
-``excessive speculation'' (understood as the market activity peculiar to
-index type investors) was linked to escalating energy and agricultural
-commodity prices. A number of ensuing academic studies, most of which
-used commodity specific correlation and causality based analysis have
-since disproved this contention: \citet{irwin_devil_2009},
+``excessive speculation''\footnote{Understood as the market activity
+  peculiar to index type investors.} was linked to escalating energy and
+agricultural commodity prices. A number of ensuing academic studies,
+most of which used commodity specific correlation and causality based
+analysis have since disproved this contention: \citet{irwin_devil_2009},
 \citet{sanders_adequacy_2010}, \citet{sanders_impact_2011},
@@
 
-For each commodity asset we compute the weekly front futures return and
-commercial hedging pressure (CHP) time series with the CHP calculated as
-the ratio of the number of long commercial positions to the total number
-of commercial positions for the considered asset-week combination. For
-each asset-period combination we compute the average return and
-corresponding volatility over the entire period as well as over phases
-of cross-sectional low and high CHP\footnote{Aggregate CHP or
-  \textbf{CHP}: see below for a formal definition and description of the
-  phase construction process.}. These statistics are also computed for
-equally weighted portfolios of the US and GB traded commodity assets
-independently.
-
-For each period, the return series for the individual US-traded assets
-are regressed on both the relative change on their respective CHP series
-and that on the cross-sectional CHP independently. The resulting
-\(R^{2}\) values are then averaged by sector and subsector.
-Additionally, pairwise correlations are computed for each combination of
-assets across the periods of interest and for each individual year
-within the full sample period. These correlation coefficients are then
-averaged across the entire cross-section of assets, as well as by
-country, sector, and subsector. For each period, the coefficients are
-also calculated and averaged across phases of low and high
-cross-sectional CHP.
+For each commodity asset we compute the daily and weekly front futures
+return as well as weekly commercial hedging pressure (CHP) time series
+with the CHP calculated as the ratio of the number of long commercial
+positions to the total number of commercial positions for the considered
+asset-week combination. For each asset-period combination we compute the
+average annual daily return and corresponding volatility over the entire
+period as well as over phases of cross-sectional low and high
+CHP\footnote{Aggregate CHP or \textbf{CHP}: see below for a formal
+  definition and description of the phase construction process.} and
+further test for significance in difference between the two regimes
+using t-tests for mean returns and F-test for corresponding variances.
+These statistics are also computed, and their difference between regimes
+tested, for equally weighted portfolios of the US and GB traded
+commodity assets independently.
+
+For each period, the weekly return series for the individual US-traded
+assets are regressed on both the relative change on their respective CHP
+series and that on the cross-sectional CHP independently. The resulting
+\(R^{2}\) values are then averaged by sector and sub-sector.
+Additionally, pairwise daily return correlations are computed for each
+combination of assets across the periods of interest and for each
+individual year within the full sample period. These correlation
+coefficients are then averaged across the entire cross-section of
+assets, as well as by country, sector, and sub-sector. For each period,
+the coefficients are also calculated and averaged across phases of low
+and high cross-sectional CHP.
 
@@
 We use a time series regression approach where individual commodity
-weekly front futures contract returns are regressed on returns to the
+front futures contract daily returns are regressed on returns to the
 mimicking portfolio for a particular risk factor with the corresponding
@@
 commodities, eventually spurring the transformation of commodity markets
-from a collection of idiosyncratic markets into a more homogeneous
+from a collection of idiosyncratic markets into a more cohesive
 collection akin to an asset class. In this context, interconnectedness
 emerges as a crucial aspect that warrants thorough examination.\\
-We strive to address this issue by first examining the average of weekly
-returns pairwise correlations between commodities across the entire
+We strive to address this issue by first examining the average returns
+pairwise correlations between commodities across the entire
 cross-section of the commodity assets considered in the study as well as
@@
 should lead to an increase in its beta relative to the market factor
-portfolio. We accordingly regress the weekly individual commodity front
-futures returns against those for our market factor portfolio and
-average the resulting betas across the entire set of commodity assets
-considered as well as by country, sector and sub-sector for each of the
-four periods of interest with the results shown in
-Table~\ref{tbl-regressions-index}. The average beta for the US metals
-sector jumps sharply to 1.12 over financialisation from 0.63 over the
-previous period; the increase is even more dramatic for the base metals
-sub-sector (GB traded assets) in a relative sense. The group had a much
-lower beta of 0.27 over the past period, suggesting a low level of
-correlation with US commodities; this figure increases to 0.85 over the
-financialisation period, even beyond that for the US agricultural sector
-of 0.80. In contrast, the corresponding figure for the energy sector
-show a substantial decrease, down to 1.61 during financialisation from
-2.33 over the past period.\\
+portfolio. We accordingly regress the individual commodity front futures
+returns against those for our market factor portfolio and average the
+resulting betas across the entire set of commodity assets considered as
+well as by country, sector and sub-sector for each of the four periods
+of interest with the results shown in Table~\ref{tbl-regressions-index}.
+The average beta for the US metals sector jumps sharply to 1.12 over
+financialisation from 0.63 over the previous period; the increase is
+even more dramatic for the base metals sub-sector (GB traded assets) in
+a relative sense. The group had a much lower average beta of 0.27 over
+the past period, suggesting a low level of correlation with US
+commodities; this figure increases to 0.85 over the financialisation
+period, even beyond that for the US agricultural sector of 0.80. In
+contrast, the corresponding figure for the energy sector shows a
+substantial decrease, down to 1.61 during financialisation from 2.33
+over the past period.\\
 The corresponding pricing performance displays a similar pattern as
@@
 respectively. Meanwhile, the pricing performance of the market factor
-also retreats to below financialisation levels with the average
-\(R^{2}\) for the entire cross-section dropping down to 14.7\%
+also recedes to below financialisation levels with the average \(R^{2}\)
+for the entire cross-section dropping down to 14.7\%
 (Table~\ref{tbl-regressions-factors}). All sectors seem affected with
@@
 \caption{\label{tbl-stats-combined}This table shows mean returns and
-volatility for the twenty four individual US commodities and the six GB
-metals considered in the study as well as for two equally weighted
-portfolios formed from the US commodities and the GB metals respectively
-across the four periods of interest (past: 1997-2003; financialisation:
-2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). for each period
-the figures are shown independently for the entire period as well as for
-phases of aggregate backwardation (aggregate CHP \(\leq\) period median)
-and aggregate contango (aggregate CHP \textgreater{} period median).
-Mean values significant at the 1\%, 5\% and 10\% level are marked with
-***, ** and * respectively. Aggregate CHP construction and corresponding
-regime definitions are discussed in Section~\ref{sec-methods} while the
-results are discussed in Section~\ref{sec-results}.}
+corresponding volatility for the twenty four individual US commodities
+and the six GB metals considered in the study as well as for two equally
+weighted portfolios formed from the US commodities and the GB metals
+respectively across the four periods of interest (past: 1997-2003;
+financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+for each period the figures are shown independently for the entire
+period as well as for phases of aggregate backwardation (aggregate CHP
+\(\leq\) period median) and aggregate contango (aggregate CHP
+\textgreater{} period median). Mean values significant at the 1\%, 5\%
+and 10\% level are marked with ***, ** and * respectively. Aggregate CHP
+construction and corresponding regime definitions are discussed in
+Section~\ref{sec-methods} while the results are discussed in
+Section~\ref{sec-results}.}
 
@@
 commodity assets considered in the study as well as across commodity
-sectors and subsectors for the four periods of interest (past:
+sectors and sub-sectors for the four periods of interest (past:
 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
@@
 \toprule
-\textcolor{black}{\textbf{regressor}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{regressor}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
@@
 \caption{\label{tbl-correlations-periods}This table shows the average
-pairwise correlation coefficients calculated independently across the
-whole cross-section of commodity assets considered in the study as well
-as across countries and commodity sectors and subsectors for the four
-periods of interest (past: 1997-2003; financialisation: 2004-2008;
+return pairwise correlation coefficients calculated independently across
+the whole cross-section of commodity assets considered in the study as
+well as across countries and commodity sectors and sub-sectors for the
+four periods of interest (past: 1997-2003; financialisation: 2004-2008;
 crisis: 2008-2013; post-crisis: 2013-2018). For each period, the results
@@
 \toprule
-\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
@@
 \caption{\label{tbl-correlations-years}This table shows the average
-pairwise correlation coefficients calculated independently across the
-whole cross-section of commodity assets considered in the study as well
-as across countries and commodity sectors and subsectors by year for the
-whole period of interest (1997-2018). The results are discussed in
-Section~\ref{sec-results} while Section~\ref{sec-taxonomy} details the
-taxonomy for the commodity assets considered.}
+return pairwise correlation coefficients calculated independently across
+the whole cross-section of commodity assets considered in the study as
+well as across countries and commodity sectors and sub-sectors by year
+for the whole period of interest (1997-2018). The results are discussed
+in Section~\ref{sec-results} while Section~\ref{sec-taxonomy} details
+the taxonomy for the commodity assets considered.}
 
@@
 \toprule
-\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{decade}} & \textcolor{black}{\textbf{0}} & \textcolor{black}{\textbf{1}} & \textcolor{black}{\textbf{2}} & \textcolor{black}{\textbf{3}} & \textcolor{black}{\textbf{4}} & \textcolor{black}{\textbf{5}} & \textcolor{black}{\textbf{6}} & \textcolor{black}{\textbf{7}} & \textcolor{black}{\textbf{8}} & \textcolor{black}{\textbf{9}}\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{decade}} & \textcolor{black}{\textbf{0}} & \textcolor{black}{\textbf{1}} & \textcolor{black}{\textbf{2}} & \textcolor{black}{\textbf{3}} & \textcolor{black}{\textbf{4}} & \textcolor{black}{\textbf{5}} & \textcolor{black}{\textbf{6}} & \textcolor{black}{\textbf{7}} & \textcolor{black}{\textbf{8}} & \textcolor{black}{\textbf{9}}\\
 \midrule
@@
 results are calculated independently across countries as well as
-commodity sectors and subsectors for the four periods of interest (past:
-1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
-2013-2018). The market factor construction is discussed in
+commodity sectors and sub-sectors for the four periods of interest
+(past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013;
+post-crisis: 2013-2018). The market factor construction is discussed in
 Section~\ref{sec-methods} while the results are discussed in
@@
 \toprule
-\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
@@
 term structure factors. The results are calculated independently across
-countries and commodity sectors and subsectors for the four periods of
+countries and commodity sectors and sub-sectors for the four periods of
 interest (past: 1997-2003; financialisation: 2004-2008; crisis:
@@
 \toprule
-\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{factor}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{factor}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
@@
 assets are classified by the country of residence of the exchange where
-they are traded as well as by sector and subsector according to the
+they are traded as well as by sector and sub-sector according to the
 nature of the asset.}
@@
 \toprule
-\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}}\\
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}}\\
 \midrule

### 2024-11-01 others/regime difference test results analysis.qmd

@@
 
-summary_individuals <- group_by(individuals, country, period, moment) %>%
-  summarise(
+summary_individuals <- dplyr::group_by(individuals, country, period, moment) %>%
+ dplyr::summarise(
     `10%` = sum(`p-value` > 0.05 & `p-value` <= 0.1, na.rm = TRUE),
@@
 
-summary_individuals <- group_by(individuals, country, period, moment) %>%
-  summarise(
+summary_individuals <- dplyr::group_by(individuals, country, period, moment) %>%
+  dplyr::summarise(
     `10%` = list(name[`p-value` >= 0.05 & `p-value` < 0.1]),
@@
 significance <- function(x) {
-  case_when(
-    x > 0.1 ~ "",
-    x > 0.05 ~ "*",
-    x > 0.01 ~ "**",
-    TRUE ~ "***"
-  )
+  dplyr::case_when(x > 0.1 ~ "", x > 0.05 ~ "*", x > 0.01 ~ "**", TRUE ~ "***")
 }

### 2024-11-14 paper.qmd
Deploying to gh-pages from @ bautheac/financialisation-co-movement@43da43602eb23751ec866d4c23bd220e312f26e0 🚀

@@
 We further note an overall shift in the nature of hedger’s behaviour away from the traditional Keynesian view of risk transfer with higher individual risk premiums over phases of cross-sectional contango as opposed to backwardation.
-Both patterns suggest that the phenomenon may have altered this long-standing paradigm of commercial risk transfer with the entry of long only commodity index traders (CITs) with very different hedging and volume demands from traditional participants.
+Both patterns suggest that the phenomenon may have altered this long-standing paradigm of commercial risk transfer with the entry of long only commodity index traders (CITs) with very different demands from traditional participants.
 This change could have altered the hedging ontology in these markets and our asset pricing framework is tailored to detect these more subtle effects driven by changes in the nature of market participation.
@@
 The pattern of reversion toward the pre-financialisation Keynesian paradigm continues stronger with mean returns higher during phases of **backwardation** relative to **contango** and the difference more pronounced than over the crisis period.
-In contrast to the crisis period when they seemed to be converging, the pricing performance of CHP and **CHP** now part way, seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a reversion to legacy commodity specific dynamics.
+In contrast to the crisis period when they seemed to be converging, the pricing performance of CHP and **CHP** now part ways, seemingly reverting to the Keynesian paradigm observed pre-financialisation, further suggesting a reversion to legacy commodity specific dynamics.
 The pull back extends to the correlation structure with an across-the-board decrease in average pairwise correlations down to levels below those observed during financialisation.
@@
 With the benefit of hindsight, it appears this approach was perhaps too narrow, and it now seems necessary to address the phenomenon from a broader perspective.
-Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and both our cross-sectional approach to examining interconnectedness in the complex as well as our commodity futures asset pricing framework together seem able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seem to have delivered an exogenous shock across the entire cross-section of liquid commodities and thereby potentially triggering a reversion to pre-financialisation dynamics.
+Commodity price dynamics appear to have altered substantially in quite different ways over the financialisation and the financial crisis periods and both our cross-sectional approach to examining interconnectedness in the complex as well as our commodity futures asset pricing framework together seem able to provide new insights into the nature of these changes: financialisation was a phenomenon endogenous to the commodity markets transmitted via the commodity futures markets and which effects were particularly strong for the metals sector while the crisis and its aftermath seem to have delivered an exogenous shock across the entire cross-section of liquid commodities, further altering the cross-sectional dynamics, and potentially triggering a reversion to pre-financialisation dynamics in the most recent period.
 
@@
 With the benefit of hindsight, this focus appears to have been too narrow.
-As our results suggests, financialisation was a phenomenon global in nature and studying the direct effects of increased market participation in single markets thus seems amiss in this context.
+As our results suggests, financialisation was a phenomenon global in nature and studying the direct effects of increased market participation in single markets thus seems limited in this context.
 The results of our analysis further suggest that financialisation had cross-sectional effects on market fundamentals across the commodity complex beyond energy and agricultural commodities and in fact strongest for the metals sector at the global level; an aspect largely overlooked in the original approach that we believe the existing literature has not fully analysed.
 The onset of the financial crisis and the monetary policy regimes that followed, on the other hand, also appear to have induced significant changes in commodity pricing dynamics.
-In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities and seem to have triggered a motion of reversion to legacy pre-financialisation fundamentals.
+In contrast with financialisation, our results suggest that the crisis and its aftermath have delivered an exogenous shock across the entire cross-section of liquid commodities which appears to have further altered the cross-sectional dynamics and eventually triggered a motion of reversion to legacy, pre-financialisation, fundamentals.
 
@@
 ```{r}
+#| label: tbl-regime-diference-tests
+#| tbl-cap: "This table shows the results for tests of difference in mean (t-test) and variance (F-test) between phases of aggregate backwardation and contango for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+1%, 5% and 10% p-value levels are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively in the significance column.
+Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
+
+colnames <- c("asset", "period", "moment", "dominant regime", "p-value", "significance")
+align <- make_series_of_repeated_chars(list(l = 4L, r = 2L))
+
+make_table("regime difference tests", colnames, align, 1L:4L, 5L:6L)
+```
+
+\newpage
+
+```{r}
 #| label: tbl-time-reg-US-CHP
 #| tbl-cap: "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in \\@sec-methods.
-Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and subsectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
 The results are discussed in \\@sec-results while \\@sec-taxonomy details the taxonomy for the commodity assets considered."
 
-colnames <- c("regressor", "sector", "subsector", periods)
+colnames <- c("regressor", "sector", "sub-sector", periods)
 align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))

### 2024-11-14 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@43da43602eb23751ec866d4c23bd220e312f26e0 🚀

@@
 uses a bespoke asset pricing factors based framework to study the issue
-through the lens of co-movement and find that the phenomenon had
+through the lens of co-movement. We find that the phenomenon had
 ontological consequences for the commodity complex with its impact
@@
 long-standing paradigm of commercial risk transfer with the entry of
-long only commodity index traders (CITs) with very different hedging and
-volume demands from traditional participants. This change could have
-altered the hedging ontology in these markets and our asset pricing
-framework is tailored to detect these more subtle effects driven by
-changes in the nature of market participation.\\
+long only commodity index traders (CITs) with very different demands
+from traditional participants. This change could have altered the
+hedging ontology in these markets and our asset pricing framework is
+tailored to detect these more subtle effects driven by changes in the
+nature of market participation.\\
 Factor model techniques are well suited to isolating common driving
@@
 These entered the commodity spectrum en masse with across-the-board
-index type positions propping the transition of the complex from a
-collection of idiosyncratic markets towards a more congruent ensemble
+index type positions prompting the transition of the complex from a
+collection of idiosyncratic markets towards a more cohesive ensemble
 akin to an asset class. In this context of heightened cross-asset market
@@
 converging, the pricing performance of CHP and \textbf{CHP} now part
-way, seemingly reverting to the Keynesian paradigm observed
+ways, seemingly reverting to the Keynesian paradigm observed
 pre-financialisation, further suggesting a reversion to legacy commodity
@@
 delivered an exogenous shock across the entire cross-section of liquid
-commodities and thereby potentially triggering a reversion to
-pre-financialisation dynamics.
+commodities, further altering the cross-sectional dynamics, and
+potentially triggering a reversion to pre-financialisation dynamics in
+the most recent period.
 
@@
 \citep{masters_testimony_2008, masters_accidental_2008}. This contention
-has since come to be known as the Masters' hypothesis and was largely
-endorsed by the final US Senate report on the issue
+has since come to be known as the ``Masters' hypothesis'' and was
+largely endorsed by the final US Senate report on the issue
 \citep{senate_excessive_2009}.\\
 At this stage, the question thrust on the academic sphere was whether
-``excessive speculation'' (understood as the market activity peculiar to
-index type investors) was linked to escalating energy and agricultural
-commodity prices. A number of ensuing academic studies, most of which
-used commodity specific correlation and causality based analysis have
-since disproved this contention: \citet{irwin_devil_2009},
+``excessive speculation''\footnote{Understood as the market activity
+  peculiar to index type investors.} was linked to escalating energy and
+agricultural commodity prices. A number of ensuing academic studies,
+most of which used commodity specific correlation and causality based
+analysis have since disproved this contention: \citet{irwin_devil_2009},
 \citet{sanders_adequacy_2010}, \citet{sanders_impact_2011},
@@
 
-For each commodity asset we compute the weekly front futures return and
-commercial hedging pressure (CHP) time series with the CHP calculated as
-the ratio of the number of long commercial positions to the total number
-of commercial positions for the considered asset-week combination. For
-each asset-period combination we compute the average return and
-corresponding volatility over the entire period as well as over phases
-of cross-sectional low and high CHP\footnote{Aggregate CHP or
-  \textbf{CHP}: see below for a formal definition and description of the
-  phase construction process.}. These statistics are also computed for
-equally weighted portfolios of the US and GB traded commodity assets
-independently.
-
-For each period, the return series for the individual US-traded assets
-are regressed on both the relative change on their respective CHP series
-and that on the cross-sectional CHP independently. The resulting
-\(R^{2}\) values are then averaged by sector and subsector.
-Additionally, pairwise correlations are computed for each combination of
-assets across the periods of interest and for each individual year
-within the full sample period. These correlation coefficients are
-subsequently averaged across the entire cross-section of assets, as well
-as by country, sector, and subsector. For each period, the coefficients
-are also calculated and averaged across phases of low and high
-cross-sectional CHP.
+For each commodity asset we compute the daily and weekly front futures
+return as well as weekly commercial hedging pressure (CHP) time series
+with the CHP calculated as the ratio of the number of long commercial
+positions to the total number of commercial positions for the considered
+asset-week combination. For each asset-period combination we compute the
+average annual daily return and corresponding volatility over the entire
+period as well as over phases of cross-sectional low and high
+CHP\footnote{Aggregate CHP or \textbf{CHP}: see below for a formal
+  definition and description of the phase construction process.} and
+further test for significance in difference between the two regimes
+using t-tests for mean returns and F-test for corresponding variances.
+These statistics are also computed, and their difference between regimes
+tested, for equally weighted portfolios of the US and GB traded
+commodity assets independently.
+
+For each period, the weekly return series for the individual US-traded
+assets are regressed on both the relative change on their respective CHP
+series and that on the cross-sectional CHP independently. The resulting
+\(R^{2}\) values are then averaged by sector and sub-sector.
+Additionally, pairwise daily return correlations are computed for each
+combination of assets across the periods of interest and for each
+individual year within the full sample period. These correlation
+coefficients are then averaged across the entire cross-section of
+assets, as well as by country, sector, and sub-sector. For each period,
+the coefficients are also calculated and averaged across phases of low
+and high cross-sectional CHP.
 
@@
 investment it simultaneously influenced the entire spectrum of liquid
-commodities; this sweeping impact spurred the transformation of
-commodity markets from a collection of idiosyncratic markets into a
-unified asset class with interconnectedness emerging as a crucial aspect
-that warrants thorough examination.\\
-We strive to address this issue by first examining the average of weekly
-returns pairwise correlations between commodities across the entire
+commodities, eventually spurring the transformation of commodity markets
+from a collection of idiosyncratic markets into a more cohesive
+collection akin to an asset class. In this context, interconnectedness
+emerges as a crucial aspect that warrants thorough examination.\\
+We strive to address this issue by first examining the average returns
+pairwise correlations between commodities across the entire
 cross-section of the commodity assets considered in the study as well as
@@
 returns are, as demonstrated in Table~\ref{tbl-stats-combined}.\\
-We further examine these correlations by year in
-Table~\ref{tbl-correlations-years} to uncover any distinct breakpoints.
-For the full sample of assets, the average pairwise correlations
-increase from 0.08 to 0.12 from 2003 to 2004 seemingly driven by US
-metals average pairwise correlations, more than doubling from 0.22 to
-0.49, suggesting 2004 as the onset of financialization as noted in
-several studies \citep{baker_financialization_2021, tang_index_2012} and
-our contribution is to observe that the US metals sub-sector seems to
-have played a major role in this.
+We break down these average correlations by years in
+Table~\ref{tbl-correlations-years}. For the full sample of assets, the
+average pairwise correlations remain in the 0.06--0.08 range from 1998
+through 2003, before suddenly increasing to 0.12 from 2003 to 2004. This
+suggests 2004 as a distinct break point for the onset of
+financialisation, as noted in several studies
+\citep{baker_financialization_2021, tang_index_2012}. We further observe
+that the US metals appear to have played a major role in this as the
+increase seems driven by the sector which average pairwise correlation
+more than doubles (0.49 vs 0.22) over the period.
 
@@
 market factor mimicking portfolio constituted of the twenty-four US
-traded commodities considered in the study with equal weighting. This
-portfolio enables a refined examination of cross correlations across
-sectors as the numerator of the beta of the regression of the returns
-for an individual commodity against those for the market factor is
-driven by covariances while the denominator is driven by the individual
-commodity variance. Thus, an increase in a commodity's correlation with
-other commodities should lead to an increase in its beta relative to the
-market factor portfolio. We accordingly regress the weekly individual
-commodity front futures returns against those for our market factor
-portfolio and average the resulting betas across the entire set of
-commodity assets considered as well as by country, sector and sub-sector
-for each of the four periods of interest with the results shown in
-Table~\ref{tbl-regressions-index}. The average beta for the US metals
-sector jumps sharply to 1.12 over financialisation from 0.63 over the
-previous period; the increase is even more dramatic for the base metals
-sub-sector (GB traded assets) in a relative sense. The group had a much
-lower beta of 0.27 over the past period, suggesting a low level of
-correlation with US commodities; this figure increases to 0.85 over the
-financialisation period, even beyond that for the US agricultural sector
-of 0.80. In contrast, the corresponding figure for the energy sector
-show a substantial decrease, down to 1.61 during financialisation from
-2.33 over the past period.\\
+traded commodities with equal weighting. This portfolio enables a
+refined examination of cross-correlations across sectors as the
+numerator of the beta of the regression of the returns for an individual
+commodity against those for the market factor is driven by covariances
+while the denominator is driven by the individual commodity variance.
+Thus, an increase in a commodity's correlation with other commodities
+should lead to an increase in its beta relative to the market factor
+portfolio. We accordingly regress the individual commodity front futures
+returns against those for our market factor portfolio and average the
+resulting betas across the entire set of commodity assets considered as
+well as by country, sector and sub-sector for each of the four periods
+of interest with the results shown in Table~\ref{tbl-regressions-index}.
+The average beta for the US metals sector jumps sharply to 1.12 over
+financialisation from 0.63 over the previous period; the increase is
+even more dramatic for the base metals sub-sector (GB traded assets) in
+a relative sense. The group had a much lower average beta of 0.27 over
+the past period, suggesting a low level of correlation with US
+commodities; this figure increases to 0.85 over the financialisation
+period, even beyond that for the US agricultural sector of 0.80. In
+contrast, the corresponding figure for the energy sector shows a
+substantial decrease, down to 1.61 during financialisation from 2.33
+over the past period.\\
 The corresponding pricing performance displays a similar pattern as
@@
 \textbf{backwardation}. The average \(R^{2}\) for the market factor
-across the entire cross-section of commodity assets considered in the
-study, including the GB traded base metals, increases to around 20\%
-during financialisation compared to around 10\% over the previous period
-with the rise driven by the metals sector at large. The sector average
-for the US traded assets jumps to 31\% during financialisation from
-7.5\% over the past period while for the GB traded assets the
-corresponding figure increases from less than 2\%, or virtually no
-explanatory power for the (US based) market factor, to almost 12\% over
-the financialisation period. The results for our other risk factor
-mimicking portfolios show a similar pattern and provide a deeper
-insights into co-movement dynamics in this context. All three
-factors---CHP, open interest and term structure---performed poorly in
-the first period, indicating that the commodities with extreme factor
-attributes (high or low CHP for example) were uncorrelated with the rest
-of the commodity cross-section, and the overall performance consistent
-across periods of \textbf{contango} and \textbf{backwardation}. The
-onset of financialisation leads to a substantial improvement in the
-performance of the CHP factor with its average \(R^{2}\), albeit still
-small at 5.4\%, almost tripling from the past to the financialisation
-period in contrast to the other factors that show weaker dynamics with a
-slight decrease and a much smaller increase for the open interest and
-term structure factors respectively. Here again the increase in pricing
-performance for the CHP factor is driven by the metals sector,
-particularly the precious sub-sector with the average \(R^{2}\) for the
-group jumping to almost 26\% during financialisation from 1.2\% over the
-past period. The corresponding figures of 22\% and 1.1\% for the entire
-US metals sector stand in sharp contrast with the agricultural sector,
-which exhibits no notable change, and the energy sector, where pricing
-performance drops substantially from 9.2\% down to 1.6\%. The
-improvement in the CHP factor's pricing performance remarkably comes
-predominantly from the long leg (low CHP assets: Keynesian ``normal
-backwardation'') of the factor\^{}\{Results available from the authors
-upon request.\} with the corresponding mimicking portfolio's performance
-itself driven by the metals, the precious sub-sector in particular. The
-average \(R^{2}\) for the group jumps to 55\% during financialisation
-from less than 12\% over the past period while the short leg sees a far
-smaller increase, up to 8.9\% from 3.3\% over the past period.
-Interestingly, although the term structure factor itself only sees a
-very modest increase, its short leg (low roll-yield assets: Working's
-backwardation) shows a sizeable rise in pricing performance, yet again
-driven the metals sector, with the average \(R^{2}\) for the group's US
-traded assets jumping to 28.2\% during financialisation from 6.2\% over
-the past period. The pattern of results for both factors extends to the
-GB trade assets and suggest a convergence of Keneysian and Working's
-term structure perspective over the financialisation period.\\
+across the entire cross-section of commodity assets, including the GB
+traded base metals, increases to around 20\% during financialisation
+compared to around 10\% over the previous period with the rise driven by
+the metals sector at large. The sector average for the US traded assets
+jumps to 31\% during financialisation from 7.5\% over the past period
+while for the GB traded assets the corresponding figure increases from
+less than 2\%, or virtually no explanatory power for the (US based)
+market factor, to almost 12\% over the financialisation period. The
+results for our other risk factor mimicking portfolios show a similar
+pattern and provide a deeper insights into co-movement dynamics in this
+context. All three factors---CHP, open interest and term
+structure---performed poorly in the first period, indicating that the
+commodities with extreme factor attributes (high or low CHP for example)
+were uncorrelated with the rest of the commodity cross-section, and the
+overall performance consistent across periods of \textbf{contango} and
+\textbf{backwardation}. The onset of financialisation leads to a
+substantial improvement in the performance of the CHP factor with its
+average \(R^{2}\), albeit still small at 5.4\%, almost tripling from the
+past to the financialisation period in contrast to the other factors
+that show weaker dynamics with a slight decrease and a much smaller
+increase for the open interest and term structure factors respectively.
+Here again the increase in pricing performance for the CHP factor is
+driven by the metals sector, particularly the precious sub-sector with
+the average \(R^{2}\) for the group jumping to almost 26\% during
+financialisation from 1.2\% over the past period. The corresponding
+figures of 22\% and 1.1\% for the entire US metals sector stand in sharp
+contrast with the agricultural sector, which exhibits no notable change,
+and the energy sector, where pricing performance drops substantially
+from 9.2\% down to 1.6\%. The improvement in the CHP factor's pricing
+performance remarkably comes predominantly from the long leg (low CHP
+assets: Keynesian ``normal backwardation'') of the factor\footnote{Results
+  available from the authors upon request.} with the corresponding
+mimicking portfolio's performance itself driven by the metals, the
+precious sub-sector in particular. Interestingly, although the term
+structure factor itself only sees a very modest increase, its short leg
+(low roll-yield assets: Working's backwardation) shows a sizeable rise
+in pricing performance, yet again driven the metals sector. The pattern
+of results for both factors extends to the GB traded assets and suggest
+a convergence of Keneysian and Working's term structure perspective over
+the financialisation period.\\
 Taken together these results emphasise the global nature of the impact
-of financialisation on the metals complex and provide further evidence
-that global metals co-movement could be detected by US based factor
-models that combine the Keynesian and Working's term structure
-paradigms. There seems thus to be information in the factor constructed
-from hedging pressure based on the Keynesian paradigm relevant to the
-term structure factor built on the Working paradigm and these findings
-therefore appear to complement the results of \citet{kang_tale_2020} who
-find that hedging pressure both conveys information about liquidity
-provision in the short term (Working paradigm) and risk transfer in the
-longer term (Keynesian paradigm).
+of financialisation on the metals complex suggest that there is
+information in the factor constructed from hedging pressure based on the
+Keynesian paradigm relevant to the term structure factor built on the
+Working paradigm. These findings therefore appear to complement the
+results of \citet{kang_tale_2020} who find that hedging pressure both
+conveys information about liquidity provision in the short term (Working
+paradigm) and risk transfer in the longer term (Keynesian paradigm).
 
@@
 the crisis period with seventeen US commodities showing higher mean
-returns over \textbf{backwardation} phases. The difference is
-significant at the 5\% level for Lumber (XCME) and at the 10\% level for
-Palladium (XNYM) while no difference is significant for the assets
-showing higher figures over phases of \textbf{contango}. The pattern is
-more pronounced for the GB traded subset with all six assets showing
-higher mean returns in \textbf{backwardation} with the difference
-significant at the 1\% level for Nickel-primary (XLME), 5\% level for
-Aluminium (XLME) and 10\% level for Zinc (XLME). It also extends to
-equally weighted portfolios of US and GB traded assets that both show
-higher mean returns during \textbf{backwardation} with the difference
-significant at the 5\% level for the GB portfolio and the figure close
-to the 10\% level significance threshold for the portfolio of US assets.
-Volatilities are overall higher in \textbf{contango} although less so
-than over the previous period with seventeen US commodities showing
-higher figures over \textbf{contango} against twenty-three in the crisis
-period. The pattern extends to three of the six GB traded metals with
-the difference significant at the 1\% level for Copper (XLME) and Tin
-(XLME) and at the 5\% level for Zinc (XLME) while differences are not
-significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME)
-that exhibit higher volatility over \textbf{backwardation} phases.
-Equally weighted portfolios of US and GB traded assets on the other hand
-both show higher volatility in \textbf{contango} with the difference
-significant at the 1\% level for both. Over the financialisation period
-in contrast volatilities were predominantly higher in
-\textbf{backwardation} for US traded assets with fourteen commodities
-showing higher volatility figures in these phases; the post-crisis
-pattern of results for volatilities thus likewise shows signs of
-reversion to pre-financialisation standards. After showing signs of
-convergence in the crisis period the dynamics of the explanatory power
-of CHP and \textbf{CHP} part ways (Table~\ref{tbl-time-reg-US-CHP}),
-seemingly reverting to the Keynesian paradigm observed
-pre-financialisation, further suggesting a return to legacy commodity
-specific dynamics. The recovery initiated in the crisis period for that
-of CHP is confirmed with a stronger increase in the post-crisis period,
-27.2\% vs.~22.5\%, strongest for the metals sector, 37.3\% vs.~23.7\%,
-while the energy sector shows the opposite pattern: 11\% vs.~16\%. In
-contrast, after increasing stronger in the crisis, that for \textbf{CHP}
-falls overall in the post-crisis period, 7.5\% vs 14.7\%, with the
-decrease strongest for the energy sector in a relative sense: 2.5\%
-vs.~14.8\%.
+returns over \textbf{backwardation} phases. The difference
+(Table~\ref{tbl-regime-diference-tests}) is significant at the 5\% level
+for Lumber (XCME) and at the 10\% level for Palladium (XNYM) while no
+difference is significant for the assets showing higher figures over
+phases of \textbf{contango}. The pattern is more pronounced for the GB
+traded subset with all six assets showing higher mean returns in
+\textbf{backwardation} with the difference significant at the 1\% level
+for Nickel-primary (XLME), 5\% level for Aluminium (XLME) and 10\% level
+for Zinc (XLME). It also extends to equally weighted portfolios of US
+and GB traded assets that both show higher mean returns during
+\textbf{backwardation} with the difference significant at the 5\% level
+for the GB portfolio and the figure close to the 10\% level significance
+threshold for the portfolio of US assets. Volatilities are overall
+higher in \textbf{contango} although less so than over the previous
+period with seventeen US commodities showing higher figures over
+\textbf{contango} against twenty-three in the crisis period. The pattern
+extends to three of the six GB traded metals with the difference
+significant at the 1\% level for Copper (XLME) and Tin (XLME) and at the
+5\% level for Zinc (XLME) while differences are not significant for
+Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit
+higher volatility over \textbf{backwardation} phases. Equally weighted
+portfolios of US and GB traded assets on the other hand both show higher
+volatility in \textbf{contango} with the difference significant at the
+1\% level for both. Over the financialisation period in contrast
+volatilities were predominantly higher in \textbf{backwardation} for US
+traded assets with fourteen commodities showing higher volatility
+figures in these phases; the post-crisis pattern of results for
+volatilities thus likewise shows signs of reversion to
+pre-financialisation standards. After showing signs of convergence in
+the crisis period the dynamics of the explanatory power of CHP and
+\textbf{CHP} part ways (Table~\ref{tbl-time-reg-US-CHP}), seemingly
+reverting to the Keynesian paradigm observed pre-financialisation,
+further suggesting a return to legacy commodity specific dynamics. The
+recovery initiated in the crisis period for that of CHP is confirmed
+with a stronger increase, 27.2\% vs.~22.5\%, strongest for the metals
+sector, 37.3\% vs.~23.7\%, while the energy sector shows the opposite
+pattern: 11\% vs.~16\%. In contrast, after increasing stronger in the
+crisis, that for \textbf{CHP} falls overall post-crisis, 7.5\% vs
+14.7\%, with the decrease strongest for the energy sector in a relative
+sense: 2.5\% vs.~14.8\%.
 
@@
 global in nature and studying the direct effects of increased market
-participation in single markets thus seems amiss in this context.\\
+participation in single markets thus seems limited in this context.\\
 The results of our analysis further suggest that financialisation had
@@
 have delivered an exogenous shock across the entire cross-section of
-liquid commodities and seem to have triggered a motion of reversion to
-legacy pre-financialisation fundamentals.
+liquid commodities which appears to have further altered the
+cross-sectional dynamics and eventually triggered a motion of reversion
+to legacy, pre-financialisation, fundamentals.
 

### 2024-11-18 others/sandbox.R
Add various sandbox scripts

@@ -1,0 +1,32 @@
+library(magrittr)
+library(slituR)
+library(kableExtra)
+
+
+tables_directory_path <- here::here("explore", "tables", "revision-jfm")
+tables <- readr::read_rds(paste_forward_slash(tables_directory_path, "tables-formatted.rds"))
+sectors <- c("country", "sector", "sub-sector")
+periods <- c("past", "financialisation", "crisis", "post-crisis")
+
+
+
+collapse_rows <- function(df, columns){
+  dplyr::mutate(df, row = dplyr::row_number(), .by = columns) %>%
+    dplyr::mutate(dplyr::across(columns, ~ifelse(row == 1L, ., "")))
+}
+
+make_table <- function(table_name, columns_to_collapse_rows_for, colnames, align, bold_columns, coloured_columns){
+  get_results(tables, table_name) %>% collapse_rows(columns_to_collapse_rows_for) %>%
+    kbl(booktabs = T, longtable = T, col.names = colnames, align = align) %>%
+    kable_styling(latex_options = "striped", font_size = 7L) %>%
+    row_spec(0L, bold = TRUE, color = "black") %>%
+    column_spec(bold_columns, bold = TRUE) %>% column_spec(coloured_columns, color = "#4285f4")
+}
+
+colnames <- c("asset", "regime", "estimate", periods)
+align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+
+make_table("stats - combined", c("asset", "regime"), colnames, align, 1L:7L, 4L:7L)
+
+
+

### 2024-11-18 docs/paper.qmd
collapse rows in tables

@@
 
-library(kableExtra); library(slituR)
+pacman::p_load(kableExtra, magrittr, slituR)
 
@@
 
-make_table <- function(table_name, colnames, align, bold_columns, coloured_columns){
-  get_results(tables, table_name) %>%
+make_table <- function(table_name, columns_to_collapse_rows_for, colnames, align, bold_columns, coloured_columns){
+  get_results(tables, table_name) %>% dplyr::mutate(dplyr::across(dplyr::where(is.factor), as.character)) %>%
+  collapse_rows(columns_to_collapse_rows_for) %>%
   kbl(booktabs = T, longtable = T, col.names = colnames, align = align) %>%
@@
 However, the fundamental question of the nature of the impact of financialisation across the entire cross-section of commodity futures markets has not yet been completely answered.
-We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2014, @ekeland_speculation_2016, @goldstein_commodity_2022, @ekeland_hedging_2019, @isleimeyyeh_role_2020.] and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in @tang_index_2012 and @basak_model_2016.
+We provide an empirical complement to a new stream of theoretical studies that try to model the impact of financialisation on various aspects of commodity futures markets^[@etula_broker-dealer_2013, @acharya_limits_2013, @cheng_convective_2014, @leclercq_equilibrium_2014, @sockin_informational_2015, @goldstein_speculation_2014, @ekeland_speculation_2014, @goldstein_commodity_2022, @ekeland_hedging_2019, @isleimeyyeh_role_2020.] and demonstrate that the effects of financialisation extend beyond the mechanical effects induced by indexation as outlined in @tang_index_2012 and @basak_model_2016.
 
@@
 
-make_table("stats - combined", colnames, align, 1L:7L, 4L:7L)
+make_table("stats - combined", c("asset", "regime"), colnames, align, 1L:7L, 4L:7L)
 ```
@@
 
-make_table("regime difference tests", colnames, align, 1L:4L, 5L:6L)
+make_table("regime difference tests", c("asset", "period"), colnames, align, 1L:4L, 5L:6L)
 ```
@@
 
-make_table("regressions - US returns ~ US CHP", colnames, align, 1L:7L, 4L:7L)
+make_table("regressions - US returns ~ US CHP", c("regressor", "sector"), colnames, align, 1L:7L, 4L:7L)
 ```
@@
 
-make_table("correlations - periods", colnames, align, 1L:8L, 5L:8L)
+make_table("correlations - periods", c("country", "sector", "subsector"), colnames, align, 1L:8L, 5L:8L)
 ```
@@
 
-make_table("correlations - years", colnames, align, 1L:14L, 5L:14L) %>%
+make_table("correlations - years", c("country", "sector", "subsector"), colnames, align, 1L:14L, 5L:14L) %>%
   landscape()
@@
 
-make_table("regressions - all returns ~ market index", colnames, align, 1L:7L, 4L:7L)
+make_table(
+  "regressions - all returns ~ market index", c("country", "sector", "subsector"), 
+  colnames, align, 1L:7L, 4L:7L
+  )
 ```
@@
 
-make_table("regressions - all returns ~ factors", colnames, align, 1L:9L, 6L:9L) %>%
-  landscape()
+make_table(
+  "regressions - all returns ~ factors", c("country", "sector", "subsector", "factor"), 
+  colnames, align, 1L:9L, 6L:9L
+  ) %>% landscape()
 ```
@@
 
-make_table("assets taxonomy", colnames, align, 1L, 2L:4L)
+make_table("assets taxonomy", c("country", "sector", "subsector"), colnames, align, 1L, 2L:4L)
 ```

### 2024-11-18 docs/paper.tex
collapse rows in tables

@@
   \citet{leclercq_equilibrium_2014}, \citet{sockin_informational_2015},
-  \citet{goldstein_speculation_2014}, \citet{ekeland_speculation_2016},
+  \citet{goldstein_speculation_2014}, \citet{ekeland_speculation_2014},
   \citet{goldstein_commodity_2022}, \citet{ekeland_hedging_2019},
@@
 \textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.74\%}}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.07\%}} & \textcolor[HTML]{4285f4}{\textbf{29.14\%}} & \textcolor[HTML]{4285f4}{\textbf{31.59\%}} & \textcolor[HTML]{4285f4}{\textbf{21\%}}\\
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.78\%}}}\\
-\addlinespace
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.74\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.07\%}} & \textcolor[HTML]{4285f4}{\textbf{29.14\%}} & \textcolor[HTML]{4285f4}{\textbf{31.59\%}} & \textcolor[HTML]{4285f4}{\textbf{21\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.78\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
 \textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.17\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.17\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
 \textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.52\%}}}\\
-\addlinespace
-\textbf{Soybean meal (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.52\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
 \textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.44\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.35\%}} & \textcolor[HTML]{4285f4}{\textbf{28.94\%}} & \textcolor[HTML]{4285f4}{\textbf{22.33\%}} & \textcolor[HTML]{4285f4}{\textbf{18.19\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.12\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.44\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.35\%}} & \textcolor[HTML]{4285f4}{\textbf{28.94\%}} & \textcolor[HTML]{4285f4}{\textbf{22.33\%}} & \textcolor[HTML]{4285f4}{\textbf{18.19\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.12\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
 \textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
 \addlinespace
-\textbf{Soybeans (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.45\%}}}\\
-\textbf{Soybeans (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.93\%}} & \textcolor[HTML]{4285f4}{\textbf{34.58\%}} & \textcolor[HTML]{4285f4}{\textbf{24.39\%}} & \textcolor[HTML]{4285f4}{\textbf{22.04\%}}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}}\\
-\textbf{Soybeans (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.09\%}} & \textcolor[HTML]{4285f4}{\textbf{24.74\%}} & \textcolor[HTML]{4285f4}{\textbf{31.11\%}} & \textcolor[HTML]{4285f4}{\textbf{20.56\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.45\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.93\%}} & \textcolor[HTML]{4285f4}{\textbf{34.58\%}} & \textcolor[HTML]{4285f4}{\textbf{24.39\%}} & \textcolor[HTML]{4285f4}{\textbf{22.04\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.09\%}} & \textcolor[HTML]{4285f4}{\textbf{24.74\%}} & \textcolor[HTML]{4285f4}{\textbf{31.11\%}} & \textcolor[HTML]{4285f4}{\textbf{20.56\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.44\%}}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{36\%}} & \textcolor[HTML]{4285f4}{\textbf{37.53\%}} & \textcolor[HTML]{4285f4}{\textbf{26.57\%}}\\
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.77\%}}}\\
-\addlinespace
-\textbf{Wheat-SRW (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.04\%}} & \textcolor[HTML]{4285f4}{\textbf{29.84\%}} & \textcolor[HTML]{4285f4}{\textbf{37.73\%}} & \textcolor[HTML]{4285f4}{\textbf{26.72\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.44\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{36\%}} & \textcolor[HTML]{4285f4}{\textbf{37.53\%}} & \textcolor[HTML]{4285f4}{\textbf{26.57\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.77\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.04\%}} & \textcolor[HTML]{4285f4}{\textbf{29.84\%}} & \textcolor[HTML]{4285f4}{\textbf{37.73\%}} & \textcolor[HTML]{4285f4}{\textbf{26.72\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**20.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.58\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}} & \textcolor[HTML]{4285f4}{\textbf{14.93\%}} & \textcolor[HTML]{4285f4}{\textbf{13.39\%}} & \textcolor[HTML]{4285f4}{\textbf{20.14\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.12\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.67\%}} & \textcolor[HTML]{4285f4}{\textbf{15.35\%}} & \textcolor[HTML]{4285f4}{\textbf{16.91\%}} & \textcolor[HTML]{4285f4}{\textbf{17.23\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**20.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.58\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}} & \textcolor[HTML]{4285f4}{\textbf{14.93\%}} & \textcolor[HTML]{4285f4}{\textbf{13.39\%}} & \textcolor[HTML]{4285f4}{\textbf{20.14\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.12\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.67\%}} & \textcolor[HTML]{4285f4}{\textbf{15.35\%}} & \textcolor[HTML]{4285f4}{\textbf{16.91\%}} & \textcolor[HTML]{4285f4}{\textbf{17.23\%}}\\
 \textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}}\\
-\textbf{Cattle-live (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.07\%}}}\\
-\addlinespace
-\textbf{Cattle-live (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.65\%}} & \textcolor[HTML]{4285f4}{\textbf{17.91\%}} & \textcolor[HTML]{4285f4}{\textbf{14.97\%}} & \textcolor[HTML]{4285f4}{\textbf{19.9\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
-\textbf{Cattle-live (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.49\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}} & \textcolor[HTML]{4285f4}{\textbf{17.57\%}} & \textcolor[HTML]{4285f4}{\textbf{16.66\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.07\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.65\%}} & \textcolor[HTML]{4285f4}{\textbf{17.91\%}} & \textcolor[HTML]{4285f4}{\textbf{14.97\%}} & \textcolor[HTML]{4285f4}{\textbf{19.9\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.49\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}} & \textcolor[HTML]{4285f4}{\textbf{17.57\%}} & \textcolor[HTML]{4285f4}{\textbf{16.66\%}}\\
 \textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.23\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.24\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{37.6\%}} & \textcolor[HTML]{4285f4}{\textbf{35.73\%}} & \textcolor[HTML]{4285f4}{\textbf{27.83\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.66\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.22\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}} & \textcolor[HTML]{4285f4}{\textbf{32.78\%}} & \textcolor[HTML]{4285f4}{\textbf{38.28\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.23\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.24\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{37.6\%}} & \textcolor[HTML]{4285f4}{\textbf{35.73\%}} & \textcolor[HTML]{4285f4}{\textbf{27.83\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.66\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.22\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}} & \textcolor[HTML]{4285f4}{\textbf{32.78\%}} & \textcolor[HTML]{4285f4}{\textbf{38.28\%}}\\
 \textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.65\%}}}\\
 \addlinespace
-\textbf{Cocoa (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.98\%}}}\\
-\textbf{Cocoa (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.57\%}} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.29\%}}}\\
-\textbf{Cocoa (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.91\%}} & \textcolor[HTML]{4285f4}{\textbf{34.66\%}} & \textcolor[HTML]{4285f4}{\textbf{23.57\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.98\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.57\%}} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.29\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.91\%}} & \textcolor[HTML]{4285f4}{\textbf{34.66\%}} & \textcolor[HTML]{4285f4}{\textbf{23.57\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.99\%}}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.36\%}}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{48.82\%}} & \textcolor[HTML]{4285f4}{\textbf{32.6\%}} & \textcolor[HTML]{4285f4}{\textbf{29.92\%}} & \textcolor[HTML]{4285f4}{\textbf{31.52\%}}\\
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.24\%}}}\\
-\addlinespace
-\textbf{Coffee-C (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.22\%}} & \textcolor[HTML]{4285f4}{\textbf{32.24\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.36\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{48.82\%}} & \textcolor[HTML]{4285f4}{\textbf{32.6\%}} & \textcolor[HTML]{4285f4}{\textbf{29.92\%}} & \textcolor[HTML]{4285f4}{\textbf{31.52\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.24\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.22\%}} & \textcolor[HTML]{4285f4}{\textbf{32.24\%}}\\
 \textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.84\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.02\%}} & \textcolor[HTML]{4285f4}{\textbf{29.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.94\%}} & \textcolor[HTML]{4285f4}{\textbf{21.33\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.91\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.77\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.59\%}} & \textcolor[HTML]{4285f4}{\textbf{19.95\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.84\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.02\%}} & \textcolor[HTML]{4285f4}{\textbf{29.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.94\%}} & \textcolor[HTML]{4285f4}{\textbf{21.33\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.91\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.77\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.59\%}} & \textcolor[HTML]{4285f4}{\textbf{19.95\%}}\\
 \textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.06\%}}}\\
-\textbf{Lumber (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
-\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**26.99\%}}}\\
-\addlinespace
-\textbf{Lumber (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.43\%}} & \textcolor[HTML]{4285f4}{\textbf{30.72\%}} & \textcolor[HTML]{4285f4}{\textbf{35.45\%}} & \textcolor[HTML]{4285f4}{\textbf{21.26\%}}\\
-\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.14\%}}}\\
-\textbf{Lumber (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}} & \textcolor[HTML]{4285f4}{\textbf{28.2\%}} & \textcolor[HTML]{4285f4}{\textbf{37.23\%}} & \textcolor[HTML]{4285f4}{\textbf{28.45\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**26.99\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.43\%}} & \textcolor[HTML]{4285f4}{\textbf{30.72\%}} & \textcolor[HTML]{4285f4}{\textbf{35.45\%}} & \textcolor[HTML]{4285f4}{\textbf{21.26\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.14\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}} & \textcolor[HTML]{4285f4}{\textbf{28.2\%}} & \textcolor[HTML]{4285f4}{\textbf{37.23\%}} & \textcolor[HTML]{4285f4}{\textbf{28.45\%}}\\
 \textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.8\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.64\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{30.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.64\%}}\\
-\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.64\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{38.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.11\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.64\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{30.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.64\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.64\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{38.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.11\%}}\\
 \textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.16\%}}}\\
 \addlinespace
-\textbf{Sugar-\#11 (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.07\%}}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.6\%}} & \textcolor[HTML]{4285f4}{\textbf{41.29\%}} & \textcolor[HTML]{4285f4}{\textbf{27.69\%}}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.7\%}}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.48\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.09\%}} & \textcolor[HTML]{4285f4}{\textbf{29.83\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.07\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.6\%}} & \textcolor[HTML]{4285f4}{\textbf{41.29\%}} & \textcolor[HTML]{4285f4}{\textbf{27.69\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.7\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.48\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.09\%}} & \textcolor[HTML]{4285f4}{\textbf{29.83\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.33\%}}}\\
-\textbf{Natural gas (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**85.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.76\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.33\%}}}\\
-\textbf{Natural gas (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{63.46\%}} & \textcolor[HTML]{4285f4}{\textbf{47.3\%}} & \textcolor[HTML]{4285f4}{\textbf{48.85\%}} & \textcolor[HTML]{4285f4}{\textbf{42.59\%}}\\
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.25\%}}}\\
-\addlinespace
-\textbf{Natural gas (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{59.76\%}} & \textcolor[HTML]{4285f4}{\textbf{61.3\%}} & \textcolor[HTML]{4285f4}{\textbf{58.18\%}} & \textcolor[HTML]{4285f4}{\textbf{46.41\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**85.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.76\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.33\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{63.46\%}} & \textcolor[HTML]{4285f4}{\textbf{47.3\%}} & \textcolor[HTML]{4285f4}{\textbf{48.85\%}} & \textcolor[HTML]{4285f4}{\textbf{42.59\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.25\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{59.76\%}} & \textcolor[HTML]{4285f4}{\textbf{61.3\%}} & \textcolor[HTML]{4285f4}{\textbf{58.18\%}} & \textcolor[HTML]{4285f4}{\textbf{46.41\%}}\\
 \textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.64\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.24\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.74\%}} & \textcolor[HTML]{4285f4}{\textbf{32.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.19\%}} & \textcolor[HTML]{4285f4}{\textbf{26.94\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-24.85\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.74\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{53.7\%}} & \textcolor[HTML]{4285f4}{\textbf{41.08\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.24\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.74\%}} & \textcolor[HTML]{4285f4}{\textbf{32.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.19\%}} & \textcolor[HTML]{4285f4}{\textbf{26.94\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-24.85\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.74\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{53.7\%}} & \textcolor[HTML]{4285f4}{\textbf{41.08\%}}\\
 \textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.37\%}}}\\
-\textbf{Gasoline (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}}\\
-\addlinespace
-\textbf{Gasoline (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.47\%}} & \textcolor[HTML]{4285f4}{\textbf{39.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.1\%}}\\
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-19.47\%}}}\\
-\textbf{Gasoline (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.14\%}} & \textcolor[HTML]{4285f4}{\textbf{44.13\%}} & \textcolor[HTML]{4285f4}{\textbf{47.11\%}} & \textcolor[HTML]{4285f4}{\textbf{41.71\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.47\%}} & \textcolor[HTML]{4285f4}{\textbf{39.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.1\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-19.47\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.14\%}} & \textcolor[HTML]{4285f4}{\textbf{44.13\%}} & \textcolor[HTML]{4285f4}{\textbf{47.11\%}} & \textcolor[HTML]{4285f4}{\textbf{41.71\%}}\\
 \textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.44\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.16\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.37\%}} & \textcolor[HTML]{4285f4}{\textbf{33.33\%}} & \textcolor[HTML]{4285f4}{\textbf{25.95\%}} & \textcolor[HTML]{4285f4}{\textbf{24.62\%}}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-21.62\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.98\%}} & \textcolor[HTML]{4285f4}{\textbf{39.16\%}} & \textcolor[HTML]{4285f4}{\textbf{35.69\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.16\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.37\%}} & \textcolor[HTML]{4285f4}{\textbf{33.33\%}} & \textcolor[HTML]{4285f4}{\textbf{25.95\%}} & \textcolor[HTML]{4285f4}{\textbf{24.62\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-21.62\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.98\%}} & \textcolor[HTML]{4285f4}{\textbf{39.16\%}} & \textcolor[HTML]{4285f4}{\textbf{35.69\%}}\\
 \textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.1\%}}}\\
 \addlinespace
-\textbf{Copper (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.1\%}}}\\
-\textbf{Copper (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{30.05\%}} & \textcolor[HTML]{4285f4}{\textbf{25.73\%}} & \textcolor[HTML]{4285f4}{\textbf{18.16\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-12.15\%}}}\\
-\textbf{Copper (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.78\%}} & \textcolor[HTML]{4285f4}{\textbf{33.69\%}} & \textcolor[HTML]{4285f4}{\textbf{42.28\%}} & \textcolor[HTML]{4285f4}{\textbf{20.87\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.1\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{30.05\%}} & \textcolor[HTML]{4285f4}{\textbf{25.73\%}} & \textcolor[HTML]{4285f4}{\textbf{18.16\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-12.15\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.78\%}} & \textcolor[HTML]{4285f4}{\textbf{33.69\%}} & \textcolor[HTML]{4285f4}{\textbf{42.28\%}} & \textcolor[HTML]{4285f4}{\textbf{20.87\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.53\%}}}\\
-\textbf{Gold (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.21\%}}}\\
-\textbf{Gold (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.89\%}} & \textcolor[HTML]{4285f4}{\textbf{19.2\%}} & \textcolor[HTML]{4285f4}{\textbf{17.03\%}} & \textcolor[HTML]{4285f4}{\textbf{12.36\%}}\\
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.1\%}}}\\
-\addlinespace
-\textbf{Gold (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}} & \textcolor[HTML]{4285f4}{\textbf{25.21\%}} & \textcolor[HTML]{4285f4}{\textbf{16.23\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.21\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.89\%}} & \textcolor[HTML]{4285f4}{\textbf{19.2\%}} & \textcolor[HTML]{4285f4}{\textbf{17.03\%}} & \textcolor[HTML]{4285f4}{\textbf{12.36\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.1\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}} & \textcolor[HTML]{4285f4}{\textbf{25.21\%}} & \textcolor[HTML]{4285f4}{\textbf{16.23\%}}\\
 \textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.75\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**49.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**31.93\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.49\%}} & \textcolor[HTML]{4285f4}{\textbf{23.82\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.88\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.2\%}} & \textcolor[HTML]{4285f4}{\textbf{38.71\%}} & \textcolor[HTML]{4285f4}{\textbf{26.8\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**49.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**31.93\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.49\%}} & \textcolor[HTML]{4285f4}{\textbf{23.82\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.88\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.2\%}} & \textcolor[HTML]{4285f4}{\textbf{38.71\%}} & \textcolor[HTML]{4285f4}{\textbf{26.8\%}}\\
 \textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.92\%}}}\\
-\textbf{Platinum (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*25.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.17\%}}}\\
-\addlinespace
-\textbf{Platinum (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.1\%}} & \textcolor[HTML]{4285f4}{\textbf{22.51\%}} & \textcolor[HTML]{4285f4}{\textbf{21.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.04\%}}\\
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.28\%}}}\\
-\textbf{Platinum (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.12\%}} & \textcolor[HTML]{4285f4}{\textbf{22.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.75\%}} & \textcolor[HTML]{4285f4}{\textbf{20.8\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*25.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.17\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.1\%}} & \textcolor[HTML]{4285f4}{\textbf{22.51\%}} & \textcolor[HTML]{4285f4}{\textbf{21.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.04\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.28\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.12\%}} & \textcolor[HTML]{4285f4}{\textbf{22.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.75\%}} & \textcolor[HTML]{4285f4}{\textbf{20.8\%}}\\
 \textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.43\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.44\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.07\%}} & \textcolor[HTML]{4285f4}{\textbf{32.5\%}} & \textcolor[HTML]{4285f4}{\textbf{37.17\%}} & \textcolor[HTML]{4285f4}{\textbf{20.3\%}}\\
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.09\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.93\%}} & \textcolor[HTML]{4285f4}{\textbf{35.34\%}} & \textcolor[HTML]{4285f4}{\textbf{42.44\%}} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.44\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.07\%}} & \textcolor[HTML]{4285f4}{\textbf{32.5\%}} & \textcolor[HTML]{4285f4}{\textbf{37.17\%}} & \textcolor[HTML]{4285f4}{\textbf{20.3\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.09\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.93\%}} & \textcolor[HTML]{4285f4}{\textbf{35.34\%}} & \textcolor[HTML]{4285f4}{\textbf{42.44\%}} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}}\\
 \textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.15\%}}}\\
 \addlinespace
-\textbf{Aluminium (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
-\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**23.68\%}}}\\
-\textbf{Aluminium (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.57\%}} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{18.94\%}}\\
-\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-23.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.74\%}}}\\
-\textbf{Aluminium (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.13\%}} & \textcolor[HTML]{4285f4}{\textbf{27.29\%}} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{18.23\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**23.68\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.57\%}} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{18.94\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-23.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.74\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.13\%}} & \textcolor[HTML]{4285f4}{\textbf{27.29\%}} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{18.23\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**28.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.03\%}}}\\
-\textbf{Copper (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.99\%}}}\\
-\textbf{Copper (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.98\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{17.92\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.89\%}}}\\
-\addlinespace
-\textbf{Copper (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{41.31\%}} & \textcolor[HTML]{4285f4}{\textbf{19.86\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.99\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.98\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{17.92\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.89\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{41.31\%}} & \textcolor[HTML]{4285f4}{\textbf{19.86\%}}\\
 \textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}}\\
-\textbf{Lead (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
-\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.05\%}}}\\
-\textbf{Lead (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.16\%}} & \textcolor[HTML]{4285f4}{\textbf{39.91\%}} & \textcolor[HTML]{4285f4}{\textbf{35.35\%}} & \textcolor[HTML]{4285f4}{\textbf{23.37\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*46.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-13.41\%}}}\\
-\textbf{Lead (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.12\%}} & \textcolor[HTML]{4285f4}{\textbf{43.16\%}} & \textcolor[HTML]{4285f4}{\textbf{46.22\%}} & \textcolor[HTML]{4285f4}{\textbf{23.09\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.05\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.16\%}} & \textcolor[HTML]{4285f4}{\textbf{39.91\%}} & \textcolor[HTML]{4285f4}{\textbf{35.35\%}} & \textcolor[HTML]{4285f4}{\textbf{23.37\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*46.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-13.41\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.12\%}} & \textcolor[HTML]{4285f4}{\textbf{43.16\%}} & \textcolor[HTML]{4285f4}{\textbf{46.22\%}} & \textcolor[HTML]{4285f4}{\textbf{23.09\%}}\\
 \textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.31\%}}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-39.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**35.09\%}}}\\
-\addlinespace
-\textbf{Nickel-primary (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.23\%}} & \textcolor[HTML]{4285f4}{\textbf{41.62\%}} & \textcolor[HTML]{4285f4}{\textbf{34.48\%}} & \textcolor[HTML]{4285f4}{\textbf{29.13\%}}\\
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**63.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**-34.64\%}}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.28\%}} & \textcolor[HTML]{4285f4}{\textbf{46.72\%}} & \textcolor[HTML]{4285f4}{\textbf{47.44\%}} & \textcolor[HTML]{4285f4}{\textbf{28.6\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-39.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**35.09\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.23\%}} & \textcolor[HTML]{4285f4}{\textbf{41.62\%}} & \textcolor[HTML]{4285f4}{\textbf{34.48\%}} & \textcolor[HTML]{4285f4}{\textbf{29.13\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**63.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**-34.64\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.28\%}} & \textcolor[HTML]{4285f4}{\textbf{46.72\%}} & \textcolor[HTML]{4285f4}{\textbf{47.44\%}} & \textcolor[HTML]{4285f4}{\textbf{28.6\%}}\\
 \textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.68\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.48\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.4\%}} & \textcolor[HTML]{4285f4}{\textbf{29.09\%}} & \textcolor[HTML]{4285f4}{\textbf{15.27\%}}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.69\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.77\%}} & \textcolor[HTML]{4285f4}{\textbf{32.08\%}} & \textcolor[HTML]{4285f4}{\textbf{41.13\%}} & \textcolor[HTML]{4285f4}{\textbf{21.68\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.48\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.4\%}} & \textcolor[HTML]{4285f4}{\textbf{29.09\%}} & \textcolor[HTML]{4285f4}{\textbf{15.27\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.69\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.77\%}} & \textcolor[HTML]{4285f4}{\textbf{32.08\%}} & \textcolor[HTML]{4285f4}{\textbf{41.13\%}} & \textcolor[HTML]{4285f4}{\textbf{21.68\%}}\\
 \textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.07\%}}}\\
 \addlinespace
-\textbf{Zinc (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.05\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.42\%}}}\\
-\textbf{Zinc (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.86\%}} & \textcolor[HTML]{4285f4}{\textbf{33.28\%}} & \textcolor[HTML]{4285f4}{\textbf{22.12\%}}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.31\%}}}\\
-\textbf{Zinc (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.38\%}} & \textcolor[HTML]{4285f4}{\textbf{40.51\%}} & \textcolor[HTML]{4285f4}{\textbf{39.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.32\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.05\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.42\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.86\%}} & \textcolor[HTML]{4285f4}{\textbf{33.28\%}} & \textcolor[HTML]{4285f4}{\textbf{22.12\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.31\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.38\%}} & \textcolor[HTML]{4285f4}{\textbf{40.51\%}} & \textcolor[HTML]{4285f4}{\textbf{39.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.32\%}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**15.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.18\%}}}\\
-\textbf{US commodities} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{***15.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.82\%}}}\\
-\textbf{US commodities} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*16.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.33\%}}}\\
-\addlinespace
-\textbf{US commodities} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{***15.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.82\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*16.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.33\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
 \textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*21.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.72\%}}}\\
-\textbf{GB commodities} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**19.95\%}}}\\
-\textbf{GB commodities} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-14.05\%}}}\\
-\textbf{GB commodities} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**19.95\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-14.05\%}}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
 \bottomrule
@@
 \textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{34.26\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{89.69\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.01\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{47.46\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{40.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{57.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.02\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{89.69\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.01\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{47.46\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{40.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{34} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{57.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.02\%} & \textcolor[HTML]{4285f4}{*}\\
 \textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{38.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Oats (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{35.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Oats (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.66\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Oats (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{82.72\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Oats (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{33} ***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{35.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{8} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.66\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{32} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{82.72\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
 \textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{66.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{81.2\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.83\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.57\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{75.13\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.31\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{81.2\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.83\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.57\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{31} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{75.13\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.31\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{31.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
 \addlinespace
-\textbf{Soybean oil (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{81.72\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{92.18\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.2\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{18.64\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{69.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.36\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{81.72\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{92.18\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.2\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{18.64\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{30} ***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{69.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.36\%} & \textcolor[HTML]{4285f4}{**}\\
 \textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{48.92\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Soybeans (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{17.18\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{38.74\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Soybeans (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{57.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Soybeans (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{37.95\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Soybeans (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.05\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{17.18\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{38.74\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{7} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{57.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{29} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{37.95\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.05\%} & \textcolor[HTML]{4285f4}{*}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{44.86\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.79\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{83.21\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{76.2\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Wheat-SRW (XCBT)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.81\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{94.9\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.79\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{83.21\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{6} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{76.2\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.51\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.81\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{94.9\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{76.82\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.34\%} & \textcolor[HTML]{4285f4}{*}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{6.35\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{62.38\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{99.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{50.04\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Cattle-feeder (XCME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.34\%} & \textcolor[HTML]{4285f4}{*}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{6.35\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{62.38\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{99.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{28} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{50.04\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{5} ***}\\
 \textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{51.11\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Cattle-live (XCME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{15.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{51.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Cattle-live (XCME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{20.96\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{82.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Cattle-live (XCME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{63.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Cattle-live (XCME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{15.26\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{51.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{20.96\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{82.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{63.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{4} ***}\\
 \textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{45.71\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
 \addlinespace
-\textbf{Lean hogs (XCME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{24.77\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{55.51\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Lean hogs (XCME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{68.46\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Lean hogs (XCME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{21.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Lean hogs (XCME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{6.81\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{24.77\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{55.51\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{3} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{68.46\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{21.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{6.81\%} & \textcolor[HTML]{4285f4}{*}\\
 \textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{99.36\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Cocoa (IFUS)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{12.33\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.85\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Cocoa (IFUS)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{7.73\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{42.98\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Cocoa (IFUS)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{51.48\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Cocoa (IFUS)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.17\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{12.33\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.85\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{7.73\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{42.98\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{27} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{51.48\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.17\%} & \textcolor[HTML]{4285f4}{**}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{53.38\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{69.3\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.63\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{95.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Coffee-C (IFUS)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{82.84\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{35.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{52.86\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{69.3\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.63\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{95.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{82.84\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{35.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{52.86\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{6.02\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{41.38\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.06\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{26.81\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{14.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{33.04\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{32.06\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Cotton-\#2 (IFUS)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.67\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{41.38\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.06\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{26.81\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{14.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{33.04\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{32.06\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.67\%} & \textcolor[HTML]{4285f4}{*}\\
 \textbf{\cellcolor{gray!10}{Lumber-random length (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{37.56\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Lumber-random length (XCME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{75.67\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Lumber-random length (XCME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{84.3\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Lumber-random length (XCME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.36\%} & \textcolor[HTML]{4285f4}{**}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Lumber-random length (XCME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{28.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Lumber-random length (XCME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{22.82\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Lumber-random length (XCME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{4.31\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
-\textbf{Lumber-random length (XCME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{75.67\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{84.3\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.36\%} & \textcolor[HTML]{4285f4}{**}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{28.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{22.82\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{4.31\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{26} ***}\\
 \textbf{\cellcolor{gray!10}{Orange juice-frozen concentrated (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{66.85\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
 \addlinespace
-\textbf{Orange juice-frozen concentrated (IFUS)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Orange juice-frozen concentrated (IFUS)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{28.81\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Orange juice-frozen concentrated (IFUS)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{92.47\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Orange juice-frozen concentrated (IFUS)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{67.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Orange juice-frozen concentrated (IFUS)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Orange juice-frozen concentrated (IFUS)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{25.72\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Orange juice-frozen concentrated (IFUS)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.01\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{28.81\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{92.47\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{67.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{25} ***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{25.72\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.01\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{24.1\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.76\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{75.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Sugar-\#11 (IFUS)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.89\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.08\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.22\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.76\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{75.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.89\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.08\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.22\%} & \textcolor[HTML]{4285f4}{*}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{4.66\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
-\textbf{Natural gas (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.01\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{68.1\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Natural gas (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.28\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Natural gas (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{67.04\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Natural gas (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.08\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.01\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{68.1\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{24} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.28\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{23} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{67.04\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.08\%} & \textcolor[HTML]{4285f4}{**}\\
 \textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{38.33\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{61.91\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{49.38\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{95.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{18.99\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Crude oil-WTI (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{22} ***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{61.91\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{49.38\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{95.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{21} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{18.99\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{20} ***}\\
 \textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{18.96\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Gasoline (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{66.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{58.35\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Gasoline (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.58\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{49.08\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Gasoline (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{34.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Gasoline (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{66.51\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{58.35\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.58\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{49.08\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{19} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{34.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{18} ***}\\
 \textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{21.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
 \addlinespace
-\textbf{Heating oil (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.45\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{99.52\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Heating oil (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.52\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{23.31\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Heating oil (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{15.71\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Heating oil (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.45\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{99.52\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.52\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{23.31\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{17} ***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{15.71\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{16} ***}\\
 \textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{90.64\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Copper (XCEC)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{17.88\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{74.37\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Copper (XCEC)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.71\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{55.78\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Copper (XCEC)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{17.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Copper (XCEC)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{17.88\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{74.37\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.71\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{55.78\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{15} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{17.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{43.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Gold (XCEC)} & \textbf{past} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{96.63\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Gold (XCEC)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.92\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{60.22\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Gold (XCEC)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.58\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Gold (XCEC)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{96.63\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.92\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{60.22\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{14} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.58\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{13} ***}\\
 \textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.77\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{***}}\\
-\textbf{Palladium (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{30.26\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Palladium (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.38\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{96.05\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Palladium (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{9.4\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
-\addlinespace
-\textbf{Palladium (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{12} ***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{30.26\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.38\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{96.05\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{9.4\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
 \textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{6.08\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
-\textbf{Platinum (XNYM)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{14.41\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Platinum (XNYM)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.86\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{85.5\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Platinum (XNYM)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{27.26\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Platinum (XNYM)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{14.41\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.86\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{85.5\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{11} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{27.26\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{***}\\
 \textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{96.07\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
 \addlinespace
-\textbf{Silver (XCEC)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.09\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{88.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Silver (XCEC)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.01\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{87.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Silver (XCEC)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.08\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{61.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Silver (XCEC)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.09\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{88.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.01\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{87.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.08\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{61.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{10} ***}\\
 \textbf{\cellcolor{gray!10}{Aluminium-primary (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{86.1\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Aluminium-primary (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Aluminium-primary (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Aluminium-primary (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.33\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Aluminium-primary (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{10.79\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Aluminium-primary (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.41\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Aluminium-primary (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.33\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
-\textbf{Aluminium-primary (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{25.99\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{9} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.33\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{10.79\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.41\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.33\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{25.99\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{88.51\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Copper (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{87.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Copper (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.15\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{43.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Copper (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{16.36\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Copper (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{87.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.15\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{43.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{8} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{16.36\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{***}\\
 \textbf{\cellcolor{gray!10}{Lead-refined pig (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{58.96\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Lead-refined pig (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.81\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Lead-refined pig (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{40.11\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Lead-refined pig (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.11\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{Lead-refined pig (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.17\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Lead-refined pig (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Lead-refined pig (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{15.62\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Lead-refined pig (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{85.45\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.81\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{40.11\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.11\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.17\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{7} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{15.62\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{85.45\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{76.56\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.04\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.24\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.62\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{49.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.46\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{***}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{69.15\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.04\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.24\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.62\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{49.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{6} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.46\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{***}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{69.15\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{5.22\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
 \addlinespace
-\textbf{Tin-refined (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{14.94\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{70.17\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Tin-refined (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{58.14\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{34.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Tin-refined (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{73.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Tin-refined (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{14.94\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{70.17\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{58.14\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{34.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{5} ***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{73.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{4} ***}\\
 \textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Zinc (XLME)} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.75\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{37.67\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{Zinc (XLME)} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.29\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.89\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{Zinc (XLME)} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{5.05\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
-\textbf{Zinc (XLME)} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{1.77\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.75\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{37.67\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.29\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.89\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{5.05\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{1.77\%} & \textcolor[HTML]{4285f4}{**}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{3.63\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
-\textbf{US commodities} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{54.29\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.09\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{US commodities} & \textbf{financialisation} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.22\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{58.92\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\addlinespace
-\textbf{US commodities} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{11.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{US commodities} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{54.29\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.09\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.22\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{58.92\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{3} ***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{11.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
 \textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{78.74\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{GB commodities} & \textbf{past} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{27.95\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{GB commodities} & \textbf{financialisation} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.65\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{46.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
-\textbf{GB commodities} & \textbf{crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.37\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
-\addlinespace
-\textbf{GB commodities} & \textbf{post-crisis} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.13\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{27.95\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.65\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{46.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.37\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.13\%} & \textcolor[HTML]{4285f4}{***}\\
 \bottomrule
@@
 \textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.17\%}}}\\
-\textbf{Δ\% commodity CHP} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.19\%}} & \textcolor[HTML]{4285f4}{\textbf{21.6\%}} & \textcolor[HTML]{4285f4}{\textbf{23.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.12\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.24\%}}}\\
-\textbf{Δ\% commodity CHP} & \textbf{agriculturals} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{6.23\%}} & \textcolor[HTML]{4285f4}{\textbf{10.53\%}} & \textcolor[HTML]{4285f4}{\textbf{6.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.88\%}}}\\
-\addlinespace
-\textbf{Δ\% commodity CHP} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.12\%}} & \textcolor[HTML]{4285f4}{\textbf{19.45\%}} & \textcolor[HTML]{4285f4}{\textbf{16\%}} & \textcolor[HTML]{4285f4}{\textbf{10.96\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
-\textbf{Δ\% commodity CHP} & \textbf{energy} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{18.87\%}} & \textcolor[HTML]{4285f4}{\textbf{12.85\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.32\%}}}\\
-\textbf{Δ\% commodity CHP} & \textbf{metals} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{47.38\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}} & \textcolor[HTML]{4285f4}{\textbf{18.07\%}} & \textcolor[HTML]{4285f4}{\textbf{34.9\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.93\%}}}\\
+\textbf{} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.19\%}} & \textcolor[HTML]{4285f4}{\textbf{21.6\%}} & \textcolor[HTML]{4285f4}{\textbf{23.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.12\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.24\%}}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{6.23\%}} & \textcolor[HTML]{4285f4}{\textbf{10.53\%}} & \textcolor[HTML]{4285f4}{\textbf{6.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.88\%}}}\\
+\addlinespace
+\textbf{} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.12\%}} & \textcolor[HTML]{4285f4}{\textbf{19.45\%}} & \textcolor[HTML]{4285f4}{\textbf{16\%}} & \textcolor[HTML]{4285f4}{\textbf{10.96\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{18.87\%}} & \textcolor[HTML]{4285f4}{\textbf{12.85\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.32\%}}}\\
+\textbf{} & \textbf{} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{47.38\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}} & \textcolor[HTML]{4285f4}{\textbf{18.07\%}} & \textcolor[HTML]{4285f4}{\textbf{34.9\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.93\%}}}\\
 \textbf{Δ\% aggregate CHP} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{5.37\%}} & \textcolor[HTML]{4285f4}{\textbf{7.12\%}} & \textcolor[HTML]{4285f4}{\textbf{14.72\%}} & \textcolor[HTML]{4285f4}{\textbf{7.49\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.23\%}}}\\
-\textbf{Δ\% aggregate CHP} & \textbf{agriculturals} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{7.25\%}} & \textcolor[HTML]{4285f4}{\textbf{5.4\%}} & \textcolor[HTML]{4285f4}{\textbf{19.75\%}} & \textcolor[HTML]{4285f4}{\textbf{8.45\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.26\%}}}\\
-\addlinespace
-\textbf{Δ\% aggregate CHP} & \textbf{agriculturals} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{5.64\%}} & \textcolor[HTML]{4285f4}{\textbf{10.35\%}} & \textcolor[HTML]{4285f4}{\textbf{6.98\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.45\%}}}\\
-\textbf{Δ\% aggregate CHP} & \textbf{energy} & \textbf{gas} & \textcolor[HTML]{4285f4}{\textbf{2.65\%}} & \textcolor[HTML]{4285f4}{\textbf{2.58\%}} & \textcolor[HTML]{4285f4}{\textbf{2.6\%}} & \textcolor[HTML]{4285f4}{\textbf{0.27\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.17\%}}}\\
-\textbf{Δ\% aggregate CHP} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{8.36\%}} & \textcolor[HTML]{4285f4}{\textbf{15.67\%}} & \textcolor[HTML]{4285f4}{\textbf{22.37\%}} & \textcolor[HTML]{4285f4}{\textbf{15.33\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.67\%}}}\\
-\textbf{Δ\% aggregate CHP} & \textbf{metals} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{7.92\%}} & \textcolor[HTML]{4285f4}{\textbf{16.4\%}} & \textcolor[HTML]{4285f4}{\textbf{21.98\%}} & \textcolor[HTML]{4285f4}{\textbf{17.25\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.23\%}}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{7.25\%}} & \textcolor[HTML]{4285f4}{\textbf{5.4\%}} & \textcolor[HTML]{4285f4}{\textbf{19.75\%}} & \textcolor[HTML]{4285f4}{\textbf{8.45\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{livestock}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.26\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{5.64\%}} & \textcolor[HTML]{4285f4}{\textbf{10.35\%}} & \textcolor[HTML]{4285f4}{\textbf{6.98\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.45\%}}}\\
+\textbf{} & \textbf{} & \textbf{gas} & \textcolor[HTML]{4285f4}{\textbf{2.65\%}} & \textcolor[HTML]{4285f4}{\textbf{2.58\%}} & \textcolor[HTML]{4285f4}{\textbf{2.6\%}} & \textcolor[HTML]{4285f4}{\textbf{0.27\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.17\%}}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{8.36\%}} & \textcolor[HTML]{4285f4}{\textbf{15.67\%}} & \textcolor[HTML]{4285f4}{\textbf{22.37\%}} & \textcolor[HTML]{4285f4}{\textbf{15.33\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{base}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.67\%}}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{7.92\%}} & \textcolor[HTML]{4285f4}{\textbf{16.4\%}} & \textcolor[HTML]{4285f4}{\textbf{21.98\%}} & \textcolor[HTML]{4285f4}{\textbf{17.25\%}}\\
 \bottomrule
@@
 \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0737}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1638}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2849}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1282}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0724}} & \textcolor[HTML]{4285f4}{\textbf{0.1790}} & \textcolor[HTML]{4285f4}{\textbf{0.2709}} & \textcolor[HTML]{4285f4}{\textbf{0.1001}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0748}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1501}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2985}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1495}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0724}} & \textcolor[HTML]{4285f4}{\textbf{0.1790}} & \textcolor[HTML]{4285f4}{\textbf{0.2709}} & \textcolor[HTML]{4285f4}{\textbf{0.1001}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0748}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1501}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2985}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1495}}}\\
 \textbf{US} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0684}} & \textcolor[HTML]{4285f4}{\textbf{0.1545}} & \textcolor[HTML]{4285f4}{\textbf{0.2526}} & \textcolor[HTML]{4285f4}{\textbf{0.1096}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0642}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1697}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2323}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0859}}}\\
-\addlinespace
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0720}} & \textcolor[HTML]{4285f4}{\textbf{0.1402}} & \textcolor[HTML]{4285f4}{\textbf{0.2706}} & \textcolor[HTML]{4285f4}{\textbf{0.1268}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0910}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1305}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2322}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1075}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0799}} & \textcolor[HTML]{4285f4}{\textbf{0.1421}} & \textcolor[HTML]{4285f4}{\textbf{0.1975}} & \textcolor[HTML]{4285f4}{\textbf{0.0955}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1018}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2611}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1186}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4421}} & \textcolor[HTML]{4285f4}{\textbf{0.4898}} & \textcolor[HTML]{4285f4}{\textbf{0.5673}} & \textcolor[HTML]{4285f4}{\textbf{0.3728}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4312}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5283}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5749}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3289}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4570}} & \textcolor[HTML]{4285f4}{\textbf{0.4510}} & \textcolor[HTML]{4285f4}{\textbf{0.5675}} & \textcolor[HTML]{4285f4}{\textbf{0.4161}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3340}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2868}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3707}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3333}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3053}} & \textcolor[HTML]{4285f4}{\textbf{0.2652}} & \textcolor[HTML]{4285f4}{\textbf{0.3906}} & \textcolor[HTML]{4285f4}{\textbf{0.3220}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3605}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3150}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3557}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3483}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0391}} & \textcolor[HTML]{4285f4}{\textbf{0.0853}} & \textcolor[HTML]{4285f4}{\textbf{0.1584}} & \textcolor[HTML]{4285f4}{\textbf{0.0764}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0437}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0845}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1210}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0685}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0334}} & \textcolor[HTML]{4285f4}{\textbf{0.0874}} & \textcolor[HTML]{4285f4}{\textbf{0.1937}} & \textcolor[HTML]{4285f4}{\textbf{0.0833}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4908}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5892}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4687}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4203}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.4844}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}} & \textcolor[HTML]{4285f4}{\textbf{0.4601}} & \textcolor[HTML]{4285f4}{\textbf{0.4179}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4957}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5869}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4779}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4210}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.7278}} & \textcolor[HTML]{4285f4}{\textbf{0.7846}} & \textcolor[HTML]{4285f4}{\textbf{0.7692}} & \textcolor[HTML]{4285f4}{\textbf{0.7175}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6962}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7854}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7282}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7606}} & \textcolor[HTML]{4285f4}{\textbf{0.7856}} & \textcolor[HTML]{4285f4}{\textbf{0.7716}} & \textcolor[HTML]{4285f4}{\textbf{0.7134}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2167}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5553}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4721}}}\\
-\addlinespace
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.2201}} & \textcolor[HTML]{4285f4}{\textbf{0.5418}} & \textcolor[HTML]{4285f4}{\textbf{0.6353}} & \textcolor[HTML]{4285f4}{\textbf{0.4155}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2145}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5709}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5035}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.2883}} & \textcolor[HTML]{4285f4}{\textbf{0.6305}} & \textcolor[HTML]{4285f4}{\textbf{0.6704}} & \textcolor[HTML]{4285f4}{\textbf{0.5762}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3070}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6061}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6991}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5386}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.6591}} & \textcolor[HTML]{4285f4}{\textbf{0.6615}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0642}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1697}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2323}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0859}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0720}} & \textcolor[HTML]{4285f4}{\textbf{0.1402}} & \textcolor[HTML]{4285f4}{\textbf{0.2706}} & \textcolor[HTML]{4285f4}{\textbf{0.1268}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0910}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1305}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2322}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1075}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0799}} & \textcolor[HTML]{4285f4}{\textbf{0.1421}} & \textcolor[HTML]{4285f4}{\textbf{0.1975}} & \textcolor[HTML]{4285f4}{\textbf{0.0955}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1018}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2611}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1186}}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4421}} & \textcolor[HTML]{4285f4}{\textbf{0.4898}} & \textcolor[HTML]{4285f4}{\textbf{0.5673}} & \textcolor[HTML]{4285f4}{\textbf{0.3728}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4312}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5283}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5749}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3289}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4570}} & \textcolor[HTML]{4285f4}{\textbf{0.4510}} & \textcolor[HTML]{4285f4}{\textbf{0.5675}} & \textcolor[HTML]{4285f4}{\textbf{0.4161}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3340}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2868}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3707}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3333}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3053}} & \textcolor[HTML]{4285f4}{\textbf{0.2652}} & \textcolor[HTML]{4285f4}{\textbf{0.3906}} & \textcolor[HTML]{4285f4}{\textbf{0.3220}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3605}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3150}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3557}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3483}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{softs} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0391}} & \textcolor[HTML]{4285f4}{\textbf{0.0853}} & \textcolor[HTML]{4285f4}{\textbf{0.1584}} & \textcolor[HTML]{4285f4}{\textbf{0.0764}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0437}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0845}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1210}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0685}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0334}} & \textcolor[HTML]{4285f4}{\textbf{0.0874}} & \textcolor[HTML]{4285f4}{\textbf{0.1937}} & \textcolor[HTML]{4285f4}{\textbf{0.0833}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4908}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5892}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4687}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4203}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.4844}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}} & \textcolor[HTML]{4285f4}{\textbf{0.4601}} & \textcolor[HTML]{4285f4}{\textbf{0.4179}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4957}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5869}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4779}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4210}}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.7278}} & \textcolor[HTML]{4285f4}{\textbf{0.7846}} & \textcolor[HTML]{4285f4}{\textbf{0.7692}} & \textcolor[HTML]{4285f4}{\textbf{0.7175}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6962}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7854}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7282}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7606}} & \textcolor[HTML]{4285f4}{\textbf{0.7856}} & \textcolor[HTML]{4285f4}{\textbf{0.7716}} & \textcolor[HTML]{4285f4}{\textbf{0.7134}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2167}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5553}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4721}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.2201}} & \textcolor[HTML]{4285f4}{\textbf{0.5418}} & \textcolor[HTML]{4285f4}{\textbf{0.6353}} & \textcolor[HTML]{4285f4}{\textbf{0.4155}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2145}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5709}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5035}}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.2883}} & \textcolor[HTML]{4285f4}{\textbf{0.6305}} & \textcolor[HTML]{4285f4}{\textbf{0.6704}} & \textcolor[HTML]{4285f4}{\textbf{0.5762}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3070}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6061}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6991}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5386}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.6591}} & \textcolor[HTML]{4285f4}{\textbf{0.6615}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4047}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4691}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6536}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4412}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3987}} & \textcolor[HTML]{4285f4}{\textbf{0.4753}} & \textcolor[HTML]{4285f4}{\textbf{0.6729}} & \textcolor[HTML]{4285f4}{\textbf{0.3954}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4108}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6456}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4797}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3987}} & \textcolor[HTML]{4285f4}{\textbf{0.4753}} & \textcolor[HTML]{4285f4}{\textbf{0.6729}} & \textcolor[HTML]{4285f4}{\textbf{0.3954}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4108}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6456}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4797}}}\\
 \bottomrule
@@
 \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0401}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0812}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0822}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0652}} & \textcolor[HTML]{4285f4}{\textbf{0.0719}} & \textcolor[HTML]{4285f4}{\textbf{0.0796}} & \textcolor[HTML]{4285f4}{\textbf{0.0848}} & \textcolor[HTML]{4285f4}{\textbf{0.1242}} & \textcolor[HTML]{4285f4}{\textbf{0.1247}} & \textcolor[HTML]{4285f4}{\textbf{0.1650}} & \textcolor[HTML]{4285f4}{\textbf{0.1541}} & \textcolor[HTML]{4285f4}{\textbf{0.3334}} & \textcolor[HTML]{4285f4}{\textbf{0.2913}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2743}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2837}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2235}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1432}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1139}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1547}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1339}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0963}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1374}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0652}} & \textcolor[HTML]{4285f4}{\textbf{0.0719}} & \textcolor[HTML]{4285f4}{\textbf{0.0796}} & \textcolor[HTML]{4285f4}{\textbf{0.0848}} & \textcolor[HTML]{4285f4}{\textbf{0.1242}} & \textcolor[HTML]{4285f4}{\textbf{0.1247}} & \textcolor[HTML]{4285f4}{\textbf{0.1650}} & \textcolor[HTML]{4285f4}{\textbf{0.1541}} & \textcolor[HTML]{4285f4}{\textbf{0.3334}} & \textcolor[HTML]{4285f4}{\textbf{0.2913}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2743}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2837}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2235}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1432}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1139}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1547}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1339}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0963}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1374}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
 \textbf{US} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0536}} & \textcolor[HTML]{4285f4}{\textbf{0.0811}} & \textcolor[HTML]{4285f4}{\textbf{0.0803}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0597}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0600}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0723}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1073}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1164}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1502}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1479}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3284}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2621}}}\\
-\addlinespace
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2275}} & \textcolor[HTML]{4285f4}{\textbf{0.2541}} & \textcolor[HTML]{4285f4}{\textbf{0.1850}} & \textcolor[HTML]{4285f4}{\textbf{0.1018}} & \textcolor[HTML]{4285f4}{\textbf{0.0986}} & \textcolor[HTML]{4285f4}{\textbf{0.1371}} & \textcolor[HTML]{4285f4}{\textbf{0.1064}} & \textcolor[HTML]{4285f4}{\textbf{0.0905}} & \textcolor[HTML]{4285f4}{\textbf{0.1197}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0827}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0916}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0918}} & \textcolor[HTML]{4285f4}{\textbf{0.0967}} & \textcolor[HTML]{4285f4}{\textbf{0.0734}} & \textcolor[HTML]{4285f4}{\textbf{0.0827}} & \textcolor[HTML]{4285f4}{\textbf{0.1111}} & \textcolor[HTML]{4285f4}{\textbf{0.1090}} & \textcolor[HTML]{4285f4}{\textbf{0.1125}} & \textcolor[HTML]{4285f4}{\textbf{0.1131}} & \textcolor[HTML]{4285f4}{\textbf{0.3034}} & \textcolor[HTML]{4285f4}{\textbf{0.2507}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2038}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2304}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1583}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0716}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0846}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1360}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1148}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1181}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.5243}} & \textcolor[HTML]{4285f4}{\textbf{0.4882}} & \textcolor[HTML]{4285f4}{\textbf{0.5650}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4870}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3851}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3402}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4473}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5335}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4594}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5040}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6325}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5681}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.5389}} & \textcolor[HTML]{4285f4}{\textbf{0.6424}} & \textcolor[HTML]{4285f4}{\textbf{0.5592}} & \textcolor[HTML]{4285f4}{\textbf{0.3199}} & \textcolor[HTML]{4285f4}{\textbf{0.3134}} & \textcolor[HTML]{4285f4}{\textbf{0.4390}} & \textcolor[HTML]{4285f4}{\textbf{0.3872}} & \textcolor[HTML]{4285f4}{\textbf{0.4123}} & \textcolor[HTML]{4285f4}{\textbf{0.3618}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2192}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3724}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3453}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.2762}} & \textcolor[HTML]{4285f4}{\textbf{0.3315}} & \textcolor[HTML]{4285f4}{\textbf{0.3243}} & \textcolor[HTML]{4285f4}{\textbf{0.3497}} & \textcolor[HTML]{4285f4}{\textbf{0.2937}} & \textcolor[HTML]{4285f4}{\textbf{0.4170}} & \textcolor[HTML]{4285f4}{\textbf{0.2784}} & \textcolor[HTML]{4285f4}{\textbf{0.2744}} & \textcolor[HTML]{4285f4}{\textbf{0.2822}} & \textcolor[HTML]{4285f4}{\textbf{0.3365}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3568}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4772}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3585}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1783}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3532}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4246}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3445}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2994}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{-0.0042}} & \textcolor[HTML]{4285f4}{\textbf{-0.0001}} & \textcolor[HTML]{4285f4}{\textbf{0.0128}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0603}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0289}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0470}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0807}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0577}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0624}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0765}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0485}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2484}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1710}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.1273}} & \textcolor[HTML]{4285f4}{\textbf{0.1400}} & \textcolor[HTML]{4285f4}{\textbf{0.1038}} & \textcolor[HTML]{4285f4}{\textbf{0.0568}} & \textcolor[HTML]{4285f4}{\textbf{0.0413}} & \textcolor[HTML]{4285f4}{\textbf{0.0983}} & \textcolor[HTML]{4285f4}{\textbf{0.1280}} & \textcolor[HTML]{4285f4}{\textbf{0.0825}} & \textcolor[HTML]{4285f4}{\textbf{0.0565}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4060}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4552}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5256}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.4362}} & \textcolor[HTML]{4285f4}{\textbf{0.5186}} & \textcolor[HTML]{4285f4}{\textbf{0.5682}} & \textcolor[HTML]{4285f4}{\textbf{0.5248}} & \textcolor[HTML]{4285f4}{\textbf{0.6212}} & \textcolor[HTML]{4285f4}{\textbf{0.6402}} & \textcolor[HTML]{4285f4}{\textbf{0.5082}} & \textcolor[HTML]{4285f4}{\textbf{0.5530}} & \textcolor[HTML]{4285f4}{\textbf{0.6278}} & \textcolor[HTML]{4285f4}{\textbf{0.4840}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4549}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4752}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3796}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2889}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4103}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4282}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4442}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3890}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4270}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.7207}} & \textcolor[HTML]{4285f4}{\textbf{0.7946}} & \textcolor[HTML]{4285f4}{\textbf{0.8527}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7632}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8072}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8321}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7377}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7703}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7895}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7460}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.8835}} & \textcolor[HTML]{4285f4}{\textbf{0.7867}} & \textcolor[HTML]{4285f4}{\textbf{0.6692}} & \textcolor[HTML]{4285f4}{\textbf{0.6075}} & \textcolor[HTML]{4285f4}{\textbf{0.6710}} & \textcolor[HTML]{4285f4}{\textbf{0.7069}} & \textcolor[HTML]{4285f4}{\textbf{0.7547}} & \textcolor[HTML]{4285f4}{\textbf{0.6672}} & \textcolor[HTML]{4285f4}{\textbf{0.7786}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2296}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2449}}}\\
-\addlinespace
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.1860}} & \textcolor[HTML]{4285f4}{\textbf{0.1832}} & \textcolor[HTML]{4285f4}{\textbf{0.1992}} & \textcolor[HTML]{4285f4}{\textbf{0.2290}} & \textcolor[HTML]{4285f4}{\textbf{0.4923}} & \textcolor[HTML]{4285f4}{\textbf{0.4480}} & \textcolor[HTML]{4285f4}{\textbf{0.6328}} & \textcolor[HTML]{4285f4}{\textbf{0.5426}} & \textcolor[HTML]{4285f4}{\textbf{0.5664}} & \textcolor[HTML]{4285f4}{\textbf{0.5547}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6297}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6458}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6649}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6160}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4531}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4850}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4269}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3584}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5259}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.3063}} & \textcolor[HTML]{4285f4}{\textbf{0.3451}} & \textcolor[HTML]{4285f4}{\textbf{0.3308}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2934}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3053}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2959}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5688}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6969}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6143}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6428}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6713}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.7004}} & \textcolor[HTML]{4285f4}{\textbf{0.7107}} & \textcolor[HTML]{4285f4}{\textbf{0.7089}} & \textcolor[HTML]{4285f4}{\textbf{0.6988}} & \textcolor[HTML]{4285f4}{\textbf{0.5620}} & \textcolor[HTML]{4285f4}{\textbf{0.6088}} & \textcolor[HTML]{4285f4}{\textbf{0.5652}} & \textcolor[HTML]{4285f4}{\textbf{0.4746}} & \textcolor[HTML]{4285f4}{\textbf{0.5716}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0597}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0600}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0723}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1073}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1164}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1502}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1479}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3284}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2621}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2275}} & \textcolor[HTML]{4285f4}{\textbf{0.2541}} & \textcolor[HTML]{4285f4}{\textbf{0.1850}} & \textcolor[HTML]{4285f4}{\textbf{0.1018}} & \textcolor[HTML]{4285f4}{\textbf{0.0986}} & \textcolor[HTML]{4285f4}{\textbf{0.1371}} & \textcolor[HTML]{4285f4}{\textbf{0.1064}} & \textcolor[HTML]{4285f4}{\textbf{0.0905}} & \textcolor[HTML]{4285f4}{\textbf{0.1197}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0827}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0916}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0918}} & \textcolor[HTML]{4285f4}{\textbf{0.0967}} & \textcolor[HTML]{4285f4}{\textbf{0.0734}} & \textcolor[HTML]{4285f4}{\textbf{0.0827}} & \textcolor[HTML]{4285f4}{\textbf{0.1111}} & \textcolor[HTML]{4285f4}{\textbf{0.1090}} & \textcolor[HTML]{4285f4}{\textbf{0.1125}} & \textcolor[HTML]{4285f4}{\textbf{0.1131}} & \textcolor[HTML]{4285f4}{\textbf{0.3034}} & \textcolor[HTML]{4285f4}{\textbf{0.2507}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2038}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2304}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1583}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0716}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0846}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1360}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1148}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1181}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.5243}} & \textcolor[HTML]{4285f4}{\textbf{0.4882}} & \textcolor[HTML]{4285f4}{\textbf{0.5650}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4870}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3851}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3402}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4473}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5335}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4594}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5040}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6325}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5681}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.5389}} & \textcolor[HTML]{4285f4}{\textbf{0.6424}} & \textcolor[HTML]{4285f4}{\textbf{0.5592}} & \textcolor[HTML]{4285f4}{\textbf{0.3199}} & \textcolor[HTML]{4285f4}{\textbf{0.3134}} & \textcolor[HTML]{4285f4}{\textbf{0.4390}} & \textcolor[HTML]{4285f4}{\textbf{0.3872}} & \textcolor[HTML]{4285f4}{\textbf{0.4123}} & \textcolor[HTML]{4285f4}{\textbf{0.3618}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2192}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3724}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3453}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.2762}} & \textcolor[HTML]{4285f4}{\textbf{0.3315}} & \textcolor[HTML]{4285f4}{\textbf{0.3243}} & \textcolor[HTML]{4285f4}{\textbf{0.3497}} & \textcolor[HTML]{4285f4}{\textbf{0.2937}} & \textcolor[HTML]{4285f4}{\textbf{0.4170}} & \textcolor[HTML]{4285f4}{\textbf{0.2784}} & \textcolor[HTML]{4285f4}{\textbf{0.2744}} & \textcolor[HTML]{4285f4}{\textbf{0.2822}} & \textcolor[HTML]{4285f4}{\textbf{0.3365}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3568}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4772}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3585}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1783}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3532}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4246}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3445}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2994}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{softs} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{-0.0042}} & \textcolor[HTML]{4285f4}{\textbf{-0.0001}} & \textcolor[HTML]{4285f4}{\textbf{0.0128}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0603}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0289}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0470}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0807}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0577}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0624}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0765}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0485}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2484}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1710}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.1273}} & \textcolor[HTML]{4285f4}{\textbf{0.1400}} & \textcolor[HTML]{4285f4}{\textbf{0.1038}} & \textcolor[HTML]{4285f4}{\textbf{0.0568}} & \textcolor[HTML]{4285f4}{\textbf{0.0413}} & \textcolor[HTML]{4285f4}{\textbf{0.0983}} & \textcolor[HTML]{4285f4}{\textbf{0.1280}} & \textcolor[HTML]{4285f4}{\textbf{0.0825}} & \textcolor[HTML]{4285f4}{\textbf{0.0565}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4060}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4552}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5256}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.4362}} & \textcolor[HTML]{4285f4}{\textbf{0.5186}} & \textcolor[HTML]{4285f4}{\textbf{0.5682}} & \textcolor[HTML]{4285f4}{\textbf{0.5248}} & \textcolor[HTML]{4285f4}{\textbf{0.6212}} & \textcolor[HTML]{4285f4}{\textbf{0.6402}} & \textcolor[HTML]{4285f4}{\textbf{0.5082}} & \textcolor[HTML]{4285f4}{\textbf{0.5530}} & \textcolor[HTML]{4285f4}{\textbf{0.6278}} & \textcolor[HTML]{4285f4}{\textbf{0.4840}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4549}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4752}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3796}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2889}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4103}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4282}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4442}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3890}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4270}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.7207}} & \textcolor[HTML]{4285f4}{\textbf{0.7946}} & \textcolor[HTML]{4285f4}{\textbf{0.8527}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7632}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8072}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8321}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7377}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7703}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7895}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7460}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.8835}} & \textcolor[HTML]{4285f4}{\textbf{0.7867}} & \textcolor[HTML]{4285f4}{\textbf{0.6692}} & \textcolor[HTML]{4285f4}{\textbf{0.6075}} & \textcolor[HTML]{4285f4}{\textbf{0.6710}} & \textcolor[HTML]{4285f4}{\textbf{0.7069}} & \textcolor[HTML]{4285f4}{\textbf{0.7547}} & \textcolor[HTML]{4285f4}{\textbf{0.6672}} & \textcolor[HTML]{4285f4}{\textbf{0.7786}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2296}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2449}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.1860}} & \textcolor[HTML]{4285f4}{\textbf{0.1832}} & \textcolor[HTML]{4285f4}{\textbf{0.1992}} & \textcolor[HTML]{4285f4}{\textbf{0.2290}} & \textcolor[HTML]{4285f4}{\textbf{0.4923}} & \textcolor[HTML]{4285f4}{\textbf{0.4480}} & \textcolor[HTML]{4285f4}{\textbf{0.6328}} & \textcolor[HTML]{4285f4}{\textbf{0.5426}} & \textcolor[HTML]{4285f4}{\textbf{0.5664}} & \textcolor[HTML]{4285f4}{\textbf{0.5547}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6297}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6458}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6649}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6160}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4531}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4850}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4269}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3584}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5259}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.3063}} & \textcolor[HTML]{4285f4}{\textbf{0.3451}} & \textcolor[HTML]{4285f4}{\textbf{0.3308}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2934}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3053}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2959}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5688}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6969}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6143}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6428}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6713}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.7004}} & \textcolor[HTML]{4285f4}{\textbf{0.7107}} & \textcolor[HTML]{4285f4}{\textbf{0.7089}} & \textcolor[HTML]{4285f4}{\textbf{0.6988}} & \textcolor[HTML]{4285f4}{\textbf{0.5620}} & \textcolor[HTML]{4285f4}{\textbf{0.6088}} & \textcolor[HTML]{4285f4}{\textbf{0.5652}} & \textcolor[HTML]{4285f4}{\textbf{0.4746}} & \textcolor[HTML]{4285f4}{\textbf{0.5716}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
 \addlinespace
 \textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2289}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3601}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4487}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.3550}} & \textcolor[HTML]{4285f4}{\textbf{0.4082}} & \textcolor[HTML]{4285f4}{\textbf{0.4775}} & \textcolor[HTML]{4285f4}{\textbf{0.5526}} & \textcolor[HTML]{4285f4}{\textbf{0.5068}} & \textcolor[HTML]{4285f4}{\textbf{0.4792}} & \textcolor[HTML]{4285f4}{\textbf{0.4340}} & \textcolor[HTML]{4285f4}{\textbf{0.4653}} & \textcolor[HTML]{4285f4}{\textbf{0.5795}} & \textcolor[HTML]{4285f4}{\textbf{0.6647}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6886}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6742}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6606}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4700}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5003}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4636}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3810}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3598}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.3550}} & \textcolor[HTML]{4285f4}{\textbf{0.4082}} & \textcolor[HTML]{4285f4}{\textbf{0.4775}} & \textcolor[HTML]{4285f4}{\textbf{0.5526}} & \textcolor[HTML]{4285f4}{\textbf{0.5068}} & \textcolor[HTML]{4285f4}{\textbf{0.4792}} & \textcolor[HTML]{4285f4}{\textbf{0.4340}} & \textcolor[HTML]{4285f4}{\textbf{0.4653}} & \textcolor[HTML]{4285f4}{\textbf{0.5795}} & \textcolor[HTML]{4285f4}{\textbf{0.6647}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6886}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6742}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6606}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4700}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5003}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4636}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3810}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3598}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
 \bottomrule
@@
 \textbf{US} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.7706}} & \textcolor[HTML]{4285f4}{\textbf{0.7965}} & \textcolor[HTML]{4285f4}{\textbf{0.8535}} & \textcolor[HTML]{4285f4}{\textbf{0.8252}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9891}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1982}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0301}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{0.4320}} & \textcolor[HTML]{4285f4}{\textbf{0.2059}} & \textcolor[HTML]{4285f4}{\textbf{0.3317}} & \textcolor[HTML]{4285f4}{\textbf{0.5484}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7213}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6900}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7953}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7589}}}\\
-\addlinespace
-\textbf{US} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{2.3308}} & \textcolor[HTML]{4285f4}{\textbf{1.6106}} & \textcolor[HTML]{4285f4}{\textbf{1.3977}} & \textcolor[HTML]{4285f4}{\textbf{1.7639}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6992}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.7090}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0044}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2585}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{2.2080}} & \textcolor[HTML]{4285f4}{\textbf{1.5778}} & \textcolor[HTML]{4285f4}{\textbf{1.5288}} & \textcolor[HTML]{4285f4}{\textbf{1.9324}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6320}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1252}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1212}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9131}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{0.4902}} & \textcolor[HTML]{4285f4}{\textbf{1.1178}} & \textcolor[HTML]{4285f4}{\textbf{1.4140}} & \textcolor[HTML]{4285f4}{\textbf{0.8780}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1271}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0480}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9219}}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9891}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1982}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0301}}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{0.4320}} & \textcolor[HTML]{4285f4}{\textbf{0.2059}} & \textcolor[HTML]{4285f4}{\textbf{0.3317}} & \textcolor[HTML]{4285f4}{\textbf{0.5484}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7213}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6900}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7953}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7589}}}\\
+\addlinespace
+\textbf{} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{2.3308}} & \textcolor[HTML]{4285f4}{\textbf{1.6106}} & \textcolor[HTML]{4285f4}{\textbf{1.3977}} & \textcolor[HTML]{4285f4}{\textbf{1.7639}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6992}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.7090}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0044}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2585}}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{2.2080}} & \textcolor[HTML]{4285f4}{\textbf{1.5778}} & \textcolor[HTML]{4285f4}{\textbf{1.5288}} & \textcolor[HTML]{4285f4}{\textbf{1.9324}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6320}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1252}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1212}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9131}}}\\
+\textbf{} & \textbf{} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{0.4902}} & \textcolor[HTML]{4285f4}{\textbf{1.1178}} & \textcolor[HTML]{4285f4}{\textbf{1.4140}} & \textcolor[HTML]{4285f4}{\textbf{0.8780}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1271}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0480}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9219}}}\\
 \textbf{GB} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.8520}} & \textcolor[HTML]{4285f4}{\textbf{1.1761}} & \textcolor[HTML]{4285f4}{\textbf{0.7192}}\\
@@
 \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.73\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.44\%}} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{11.82\%}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.99\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.92\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.43\%}} & \textcolor[HTML]{4285f4}{\textbf{3.78\%}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}}\\
-\addlinespace
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{5.55\%}} & \textcolor[HTML]{4285f4}{\textbf{4.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.69\%}} & \textcolor[HTML]{4285f4}{\textbf{5.47\%}} & \textcolor[HTML]{4285f4}{\textbf{3.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.12\%}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.74\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{2.95\%}} & \textcolor[HTML]{4285f4}{\textbf{5.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.39\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{3.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.44\%}} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{11.82\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.99\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.92\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.43\%}} & \textcolor[HTML]{4285f4}{\textbf{3.78\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{5.55\%}} & \textcolor[HTML]{4285f4}{\textbf{4.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.69\%}} & \textcolor[HTML]{4285f4}{\textbf{5.47\%}} & \textcolor[HTML]{4285f4}{\textbf{3.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.12\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.74\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{2.95\%}} & \textcolor[HTML]{4285f4}{\textbf{5.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.39\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{3.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}}\\
 \textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.73\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{11.26\%}} & \textcolor[HTML]{4285f4}{\textbf{23.68\%}} & \textcolor[HTML]{4285f4}{\textbf{28.95\%}} & \textcolor[HTML]{4285f4}{\textbf{13.12\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.66\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.38\%}} & \textcolor[HTML]{4285f4}{\textbf{5.8\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.54\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{6.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.14\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.79\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{5\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{2.87\%}} & \textcolor[HTML]{4285f4}{\textbf{5.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.85\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{5.73\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.07\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.57\%}} & \textcolor[HTML]{4285f4}{\textbf{18.68\%}} & \textcolor[HTML]{4285f4}{\textbf{23.01\%}} & \textcolor[HTML]{4285f4}{\textbf{11.56\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.91\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.11\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}} & \textcolor[HTML]{4285f4}{\textbf{1.56\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.85\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.73\%}} & \textcolor[HTML]{4285f4}{\textbf{2.16\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.55\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.69\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.27\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{14.54\%}} & \textcolor[HTML]{4285f4}{\textbf{34.68\%}} & \textcolor[HTML]{4285f4}{\textbf{38.84\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{44.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.71\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{0.78\%}} & \textcolor[HTML]{4285f4}{\textbf{2.98\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.46\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.06\%}} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.04\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{7.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.5\%}} & \textcolor[HTML]{4285f4}{\textbf{3.8\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.24\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}} & \textcolor[HTML]{4285f4}{\textbf{2.08\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.56\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.25\%}} & \textcolor[HTML]{4285f4}{\textbf{2.18\%}} & \textcolor[HTML]{4285f4}{\textbf{3.3\%}} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.84\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{6.2\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.63\%}} & \textcolor[HTML]{4285f4}{\textbf{2.06\%}} & \textcolor[HTML]{4285f4}{\textbf{3.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.94\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{1.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.71\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.47\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.48\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.82\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}} & \textcolor[HTML]{4285f4}{\textbf{15.58\%}} & \textcolor[HTML]{4285f4}{\textbf{8.44\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.6\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.51\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}} & \textcolor[HTML]{4285f4}{\textbf{0.9\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.41\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}} & \textcolor[HTML]{4285f4}{\textbf{2.42\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.08\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.9\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{26.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{33.74\%}} & \textcolor[HTML]{4285f4}{\textbf{20.94\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.77\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{3.5\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.68\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{5.95\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{7.91\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.67\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{38.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.93\%}} & \textcolor[HTML]{4285f4}{\textbf{17.59\%}} & \textcolor[HTML]{4285f4}{\textbf{22.07\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{41.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.13\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.99\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{1.86\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.16\%}} & \textcolor[HTML]{4285f4}{\textbf{2.76\%}} & \textcolor[HTML]{4285f4}{\textbf{5.88\%}} & \textcolor[HTML]{4285f4}{\textbf{1.26\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.86\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{21.36\%}} & \textcolor[HTML]{4285f4}{\textbf{17.54\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{7.17\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.96\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.62\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{16.2\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.3\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.46\%}} & \textcolor[HTML]{4285f4}{\textbf{5.26\%}} & \textcolor[HTML]{4285f4}{\textbf{13.46\%}} & \textcolor[HTML]{4285f4}{\textbf{13.84\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.03\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{23.23\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{14.53\%}} & \textcolor[HTML]{4285f4}{\textbf{16.64\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.41\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{4.24\%}} & \textcolor[HTML]{4285f4}{\textbf{7.16\%}} & \textcolor[HTML]{4285f4}{\textbf{5.22\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.9\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.48\%}} & \textcolor[HTML]{4285f4}{\textbf{6.51\%}} & \textcolor[HTML]{4285f4}{\textbf{4.6\%}} & \textcolor[HTML]{4285f4}{\textbf{4.55\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{48.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.91\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{27.65\%}} & \textcolor[HTML]{4285f4}{\textbf{37.22\%}} & \textcolor[HTML]{4285f4}{\textbf{40.79\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.71\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10.41\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.99\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.45\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}} & \textcolor[HTML]{4285f4}{\textbf{0.96\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{45.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.56\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{44.02\%}} & \textcolor[HTML]{4285f4}{\textbf{27.52\%}} & \textcolor[HTML]{4285f4}{\textbf{18.61\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{47.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{43.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.7\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.57\%}} & \textcolor[HTML]{4285f4}{\textbf{4.95\%}} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{6.3\%}} & \textcolor[HTML]{4285f4}{\textbf{0.16\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.58\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.5\%}} & \textcolor[HTML]{4285f4}{\textbf{31.77\%}} & \textcolor[HTML]{4285f4}{\textbf{42.95\%}} & \textcolor[HTML]{4285f4}{\textbf{11.54\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.76\%}} & \textcolor[HTML]{4285f4}{\textbf{18.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.33\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.71\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{23.49\%}} & \textcolor[HTML]{4285f4}{\textbf{21.5\%}} & \textcolor[HTML]{4285f4}{\textbf{13.38\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.27\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{2.83\%}} & \textcolor[HTML]{4285f4}{\textbf{0.32\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.48\%}} & \textcolor[HTML]{4285f4}{\textbf{7.31\%}} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.33\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.57\%}} & \textcolor[HTML]{4285f4}{\textbf{8.4\%}} & \textcolor[HTML]{4285f4}{\textbf{16.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{50.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.74\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{4.96\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}} & \textcolor[HTML]{4285f4}{\textbf{48.58\%}} & \textcolor[HTML]{4285f4}{\textbf{10.15\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.5\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{5.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}} & \textcolor[HTML]{4285f4}{\textbf{6.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.46\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{1.84\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.06\%}} & \textcolor[HTML]{4285f4}{\textbf{9.72\%}} & \textcolor[HTML]{4285f4}{\textbf{9.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.12\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{11.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.3\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.13\%}} & \textcolor[HTML]{4285f4}{\textbf{33.37\%}} & \textcolor[HTML]{4285f4}{\textbf{41.54\%}} & \textcolor[HTML]{4285f4}{\textbf{11.89\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.88\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{25.76\%}} & \textcolor[HTML]{4285f4}{\textbf{23.19\%}} & \textcolor[HTML]{4285f4}{\textbf{15.84\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.81\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.86\%}} & \textcolor[HTML]{4285f4}{\textbf{27.76\%}} & \textcolor[HTML]{4285f4}{\textbf{26.82\%}} & \textcolor[HTML]{4285f4}{\textbf{16.5\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.56\%}} & \textcolor[HTML]{4285f4}{\textbf{0.68\%}} & \textcolor[HTML]{4285f4}{\textbf{3.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.21\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}} & \textcolor[HTML]{4285f4}{\textbf{6.71\%}} & \textcolor[HTML]{4285f4}{\textbf{16.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{4.46\%}} & \textcolor[HTML]{4285f4}{\textbf{7.58\%}} & \textcolor[HTML]{4285f4}{\textbf{17.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.31\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{11.26\%}} & \textcolor[HTML]{4285f4}{\textbf{23.68\%}} & \textcolor[HTML]{4285f4}{\textbf{28.95\%}} & \textcolor[HTML]{4285f4}{\textbf{13.12\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.66\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.38\%}} & \textcolor[HTML]{4285f4}{\textbf{5.8\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.54\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{6.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.14\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.79\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{5\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{2.87\%}} & \textcolor[HTML]{4285f4}{\textbf{5.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.85\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{5.73\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.07\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.57\%}} & \textcolor[HTML]{4285f4}{\textbf{18.68\%}} & \textcolor[HTML]{4285f4}{\textbf{23.01\%}} & \textcolor[HTML]{4285f4}{\textbf{11.56\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.91\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.11\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}} & \textcolor[HTML]{4285f4}{\textbf{1.56\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.85\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.73\%}} & \textcolor[HTML]{4285f4}{\textbf{2.16\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.55\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.69\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.27\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{14.54\%}} & \textcolor[HTML]{4285f4}{\textbf{34.68\%}} & \textcolor[HTML]{4285f4}{\textbf{38.84\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{44.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.71\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{0.78\%}} & \textcolor[HTML]{4285f4}{\textbf{2.98\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.46\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.06\%}} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.04\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{7.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.5\%}} & \textcolor[HTML]{4285f4}{\textbf{3.8\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.24\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}} & \textcolor[HTML]{4285f4}{\textbf{2.08\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.56\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.25\%}} & \textcolor[HTML]{4285f4}{\textbf{2.18\%}} & \textcolor[HTML]{4285f4}{\textbf{3.3\%}} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.84\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{6.2\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.63\%}} & \textcolor[HTML]{4285f4}{\textbf{2.06\%}} & \textcolor[HTML]{4285f4}{\textbf{3.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.94\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{1.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.71\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.47\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.48\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.82\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}} & \textcolor[HTML]{4285f4}{\textbf{15.58\%}} & \textcolor[HTML]{4285f4}{\textbf{8.44\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.6\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.51\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}} & \textcolor[HTML]{4285f4}{\textbf{0.9\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.41\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}} & \textcolor[HTML]{4285f4}{\textbf{2.42\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.08\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.9\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{26.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{33.74\%}} & \textcolor[HTML]{4285f4}{\textbf{20.94\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.77\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{3.5\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.68\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{5.95\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{7.91\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.67\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{38.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.93\%}} & \textcolor[HTML]{4285f4}{\textbf{17.59\%}} & \textcolor[HTML]{4285f4}{\textbf{22.07\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{41.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.13\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.99\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{1.86\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.16\%}} & \textcolor[HTML]{4285f4}{\textbf{2.76\%}} & \textcolor[HTML]{4285f4}{\textbf{5.88\%}} & \textcolor[HTML]{4285f4}{\textbf{1.26\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.86\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{21.36\%}} & \textcolor[HTML]{4285f4}{\textbf{17.54\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{7.17\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.96\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.62\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{16.2\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.3\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.46\%}} & \textcolor[HTML]{4285f4}{\textbf{5.26\%}} & \textcolor[HTML]{4285f4}{\textbf{13.46\%}} & \textcolor[HTML]{4285f4}{\textbf{13.84\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.03\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{23.23\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{14.53\%}} & \textcolor[HTML]{4285f4}{\textbf{16.64\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.41\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{4.24\%}} & \textcolor[HTML]{4285f4}{\textbf{7.16\%}} & \textcolor[HTML]{4285f4}{\textbf{5.22\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.9\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.48\%}} & \textcolor[HTML]{4285f4}{\textbf{6.51\%}} & \textcolor[HTML]{4285f4}{\textbf{4.6\%}} & \textcolor[HTML]{4285f4}{\textbf{4.55\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{48.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.91\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{27.65\%}} & \textcolor[HTML]{4285f4}{\textbf{37.22\%}} & \textcolor[HTML]{4285f4}{\textbf{40.79\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.71\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10.41\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.99\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.45\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}} & \textcolor[HTML]{4285f4}{\textbf{0.96\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{45.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.56\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{44.02\%}} & \textcolor[HTML]{4285f4}{\textbf{27.52\%}} & \textcolor[HTML]{4285f4}{\textbf{18.61\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{47.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{43.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.7\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.57\%}} & \textcolor[HTML]{4285f4}{\textbf{4.95\%}} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{6.3\%}} & \textcolor[HTML]{4285f4}{\textbf{0.16\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.58\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.5\%}} & \textcolor[HTML]{4285f4}{\textbf{31.77\%}} & \textcolor[HTML]{4285f4}{\textbf{42.95\%}} & \textcolor[HTML]{4285f4}{\textbf{11.54\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.76\%}} & \textcolor[HTML]{4285f4}{\textbf{18.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.33\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.71\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{23.49\%}} & \textcolor[HTML]{4285f4}{\textbf{21.5\%}} & \textcolor[HTML]{4285f4}{\textbf{13.38\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.27\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{2.83\%}} & \textcolor[HTML]{4285f4}{\textbf{0.32\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.48\%}} & \textcolor[HTML]{4285f4}{\textbf{7.31\%}} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.33\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.57\%}} & \textcolor[HTML]{4285f4}{\textbf{8.4\%}} & \textcolor[HTML]{4285f4}{\textbf{16.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{50.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.74\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{4.96\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}} & \textcolor[HTML]{4285f4}{\textbf{48.58\%}} & \textcolor[HTML]{4285f4}{\textbf{10.15\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.5\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{5.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}} & \textcolor[HTML]{4285f4}{\textbf{6.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.46\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{1.84\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.06\%}} & \textcolor[HTML]{4285f4}{\textbf{9.72\%}} & \textcolor[HTML]{4285f4}{\textbf{9.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.12\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{11.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.3\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.13\%}} & \textcolor[HTML]{4285f4}{\textbf{33.37\%}} & \textcolor[HTML]{4285f4}{\textbf{41.54\%}} & \textcolor[HTML]{4285f4}{\textbf{11.89\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.88\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{25.76\%}} & \textcolor[HTML]{4285f4}{\textbf{23.19\%}} & \textcolor[HTML]{4285f4}{\textbf{15.84\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.81\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.86\%}} & \textcolor[HTML]{4285f4}{\textbf{27.76\%}} & \textcolor[HTML]{4285f4}{\textbf{26.82\%}} & \textcolor[HTML]{4285f4}{\textbf{16.5\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.56\%}} & \textcolor[HTML]{4285f4}{\textbf{0.68\%}} & \textcolor[HTML]{4285f4}{\textbf{3.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.21\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}} & \textcolor[HTML]{4285f4}{\textbf{6.71\%}} & \textcolor[HTML]{4285f4}{\textbf{16.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{4.46\%}} & \textcolor[HTML]{4285f4}{\textbf{7.58\%}} & \textcolor[HTML]{4285f4}{\textbf{17.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.31\%}}\\
 \textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.75\%}}}\\
 \addlinespace
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{13.03\%}} & \textcolor[HTML]{4285f4}{\textbf{34.39\%}} & \textcolor[HTML]{4285f4}{\textbf{6.62\%}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.72\%}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.42\%}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.28\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.09\%}}}\\
-\addlinespace
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{6.72\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{13.03\%}} & \textcolor[HTML]{4285f4}{\textbf{34.39\%}} & \textcolor[HTML]{4285f4}{\textbf{6.62\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.72\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.42\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.28\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.09\%}}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{6.72\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
 \bottomrule
@@
 \textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{grains}}\\
-\textbf{Oats (XCBT)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{grains}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{grains}}\\
-\textbf{Soybean oil (XCBT)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{grains}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{grains}}\\
-\addlinespace
-\textbf{Wheat-SRW (XCBT)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{grains}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{livestock}}\\
-\textbf{Cattle-live (XCME)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{livestock}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{livestock}}\\
-\textbf{Cocoa (IFUS)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{softs}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{softs}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{softs}\\
-\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{softs}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{softs}\\
-\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{softs}}\\
-\addlinespace
-\textbf{Natural gas (XNYM)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{energy} & \textcolor[HTML]{4285f4}{gas}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{energy}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{petroleum}}\\
-\textbf{Gasoline (XNYM)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{energy} & \textcolor[HTML]{4285f4}{petroleum}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{energy}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{petroleum}}\\
-\textbf{Copper (XCEC)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{precious}}\\
-\textbf{Silver (XCEC)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{precious}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{precious}}\\
-\textbf{Platinum (XNYM)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{precious}\\
+\textbf{Oats (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybean oil (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Wheat-SRW (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{livestock}}\\
+\textbf{Cattle-live (XCME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cocoa (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{softs}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\addlinespace
+\textbf{Natural gas (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{energy} & \textcolor[HTML]{4285f4}{gas}\\
+\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{petroleum}}\\
+\textbf{Gasoline (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Copper (XCEC)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
+\addlinespace
+\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{precious}}\\
+\textbf{Silver (XCEC)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Platinum (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{GB}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{base}}\\
 \addlinespace
-\textbf{Copper (XLME)} & \textcolor[HTML]{4285f4}{GB} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
-\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{GB}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{base}}\\
-\textbf{Nickel-primary (XLME)} & \textcolor[HTML]{4285f4}{GB} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{GB}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{base}}\\
-\textbf{Zinc (XLME)} & \textcolor[HTML]{4285f4}{GB} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
+\textbf{Copper (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Nickel-primary (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Zinc (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \bottomrule

### 2024-11-18 others/sandbox.R

@@ -1,32 +1,37 @@
-library(magrittr)
-library(slituR)
-library(kableExtra)
+
+pacman::p_load(kableExtra, magrittr, slituR)
+
+urls <- c(
+  "https://www.dropbox.com/scl/fi/n7t8g3hn32d8e5gf2rcti/references.bib?rlkey=xy251n44q3y0t3omxpqk0dvyf&dl=1",
+  "https://www.dropbox.com/scl/fi/c46nb5xpxwgvjdspla9p5/style.css?rlkey=d666hnaxod2stvkxel33or0cg&dl=1"
+)
+file_names <- c("bibliography.bib", "style.css")
+purrr::walk2(urls, file_names, function(url, file_name) download.file(url, file_name))
 
 
 tables_directory_path <- here::here("explore", "tables", "revision-jfm")
+
+
+tables_collapse_rows_align <- "top"
+tables_cut <- TRUE
+tables_hline <- "major"
+
 tables <- readr::read_rds(paste_forward_slash(tables_directory_path, "tables-formatted.rds"))
 sectors <- c("country", "sector", "sub-sector")
 periods <- c("past", "financialisation", "crisis", "post-crisis")
 
-
-
-collapse_rows <- function(df, columns){
-  dplyr::mutate(df, row = dplyr::row_number(), .by = columns) %>%
-    dplyr::mutate(dplyr::across(columns, ~ifelse(row == 1L, ., "")))
-}
-
 make_table <- function(table_name, columns_to_collapse_rows_for, colnames, align, bold_columns, coloured_columns){
   get_results(tables, table_name) %>% collapse_rows(columns_to_collapse_rows_for) %>%
-    kbl(booktabs = T, longtable = T, col.names = colnames, align = align) %>%
-    kable_styling(latex_options = "striped", font_size = 7L) %>%
-    row_spec(0L, bold = TRUE, color = "black") %>%
-    column_spec(bold_columns, bold = TRUE) %>% column_spec(coloured_columns, color = "#4285f4")
+  kbl(booktabs = T, longtable = T, col.names = colnames, align = align) %>%
+  kable_styling(latex_options = "striped", font_size = 7L) %>%
+  row_spec(0L, bold = TRUE, color = "black") %>%
+  column_spec(bold_columns, bold = TRUE) %>% column_spec(coloured_columns, color = "#4285f4")
 }
 
 colnames <- c("asset", "regime", "estimate", periods)
[…]

### 2024-11-19 docs/paper.qmd
Refactor correlations analysis
to accommodate for cross-correlation analysis

@@
 
-make_table("correlations - periods", c("country", "sector", "subsector"), colnames, align, 1L:8L, 5L:8L)
+make_table("correlations - inner - periods", c("country", "sector", "subsector"), colnames, align, 1L:8L, 5L:8L)
 ```
@@
 
-make_table("correlations - years", c("country", "sector", "subsector"), colnames, align, 1L:14L, 5L:14L) %>%
+make_table("correlations - inner - years", c("country", "sector", "subsector"), colnames, align, 1L:14L, 5L:14L) %>%
   landscape()

### 2024-11-19 explore/scripts/revision-jfm/analysis.r

@@ -1,4 +1,4 @@
-library(finRes); library(magrittr)
+pacman::p_load(finRes, magrittr)
 
 # source functions #############################################################
 source(here::here("explore", "scripts", "revision-jfm", "functions.r"))
@@ -40,29 +40,30 @@ commodity_pool_tickers <- make_commodity_pool_tickers_dataframe(
   commodity_futures_tickers, analysis = "correlations"
   )
 
-### raw ####
-correlations_raw <- make_pairwise_correlations_for_ticker_combinations_dataframe(
+### inner ####
+#### raw ####
+correlations_inner_raw <- make_inner_correlations_for_ticker_combinations_dataframe(
   commodity_pool_tickers, commodity_futures_data, aggregate_CHP_regimes, period_dates
 )
 
-### summary ####
-#### load raw dataset (optional) ####
-# path_correlations_raw_file <- paste_forward_slash(results_directory_path, "correlations-raw.rds")
-# correlations_raw <- readr::read_rds(path_correlations_raw_file)
+#### summary ####
+##### load raw dataset (optional) ####
+# path_correlations_inner_raw_file <- paste_forward_slash(results_directory_path, "correlations-inner-raw.rds")
+# correlations_inner_raw <- readr::read_rds(path_correlations_inner_raw_file)
 
-#### summarise ####
-correlations_summary <- 
-  add_top_3_and_average_to_pairwise_correlations_for_ticker_combinations_dataframe(correlations_raw)
+##### summarise ####
+correlations_inner_summary <- 
+  add_top_3_and_average_to_inner_correlations_for_ticker_combinations_dataframe(correlations_inner_raw)
 
-### formatted ####
-#### load summary dataset (optional) ####
-# path_correlations_summary_file <- 
-#   paste_forward_slash(results_directory_path, "correlations-summary.rds")
-# correlations_summary <- readr::read_rds(path_correlations_summary_file)
+#### formatted ####
+##### load summary dataset (optional) ####
+# path_correlations_inner_summary_file <- 
+#   paste_forward_slash(results_directory_path, "correlations-inner-summary.rds")
+# correlations_inner_summary <- readr::read_rds(path_correlations_inner_summary_file)
 
-#### format ####
-correlations_formatted <- 
-  format_correlation_summary_statistics_into_table(correlations_summary)
+##### format ####
+correlations_inner_formatted <- 
+  format_inner_correlations_summary_statistics_into_table(correlations_inner_summary)
 
[…]

### 2024-11-19 explore/scripts/revision-jfm/functions.r

@@ -1005,7 +1005,7 @@ compute_correlations <- function(df) {
   cor( dplyr::select(df, -date), use = "pairwise.complete.obs")
 }
 
-make_pairwise_correlations_for_ticker_combinations_dataframe <- function(
+make_inner_correlations_for_ticker_combinations_dataframe <- function(
     combinations, commodity_futures_data, aggregate_CHP_regimes, period_dates
     ){
   
@@ -1234,7 +1234,7 @@ compute_average_pairwise_correlations_from_correlation_matrix <- function(correl
   mean(pairwise_correlations$correlation, na.rm = T)
 }
 
-add_top_3_and_average_to_pairwise_correlations_for_ticker_combinations_dataframe <- function(
+add_top_3_and_average_to_inner_correlations_for_ticker_combinations_dataframe <- function(
     pairwise_correlations_for_ticker_combinations_dataframe
 ){
   
@@ -1407,7 +1407,7 @@ map_solution_to_problem_domain_jargon_in_correlation_top_3_unnested_results_summ
 }
 ####
 
-format_correlation_summary_statistics_into_table <- function(correlations_summary){
+format_inner_correlations_summary_statistics_into_table <- function(correlations_summary){
   
   top_3 <- unnest_analysis_statistic_results_summary(correlations_summary, "top 3") %>%
     dplyr::mutate(`top-bottom 3` = factor(`top-bottom 3`, levels = c("top", "bottom"))) %>%

### 2024-11-19 explore/scripts/revision-jfm/tables.r

@@ -1,6 +1,6 @@
 library(magrittr)
 
-# Globals ####
+# Globals ######################################################################
 ## datasets ####
 data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
 data("exchanges", package = "fewISOs")
@@ -53,7 +53,7 @@ sort_table_by_country_sector_subsector <- function(tb, sort_levels){
   ) %>% dplyr::arrange(sort) %>% dplyr::select(-sort)
 }
 
-# assets taxonomy ####
+# assets taxonomy ##############################################################
 `assets taxonomy` <- 
   make_asset_name_country_sector_subsector_dataframe(commodity_futures_tickers) %>%
   dplyr::mutate(
@@ -71,7 +71,7 @@ sort_table_by_country_sector_subsector <- function(tb, sort_levels){
     TRUE ~ asset
   ))
 
-# descriptive stats ####
+# descriptive stats ############################################################
 stats <- readr::read_rds(
   slituR::paste_forward_slash(results_directory_path, "descriptive-statistics-clean.rds")
   )
@@ -188,7 +188,7 @@ descriptive_stats_combined <- dplyr::bind_rows(commodities, countries) %>%
     estimate = ifelse(estimate == "mean", estimate, "volatility")
     )
 
-# regime difference tests ####
+# regime difference tests ######################################################
 regime_difference_tests <- readr::read_rds(
   slituR::paste_forward_slash(results_directory_path, "regime-difference-tests.rds")
 )
@@ -229,14 +229,15 @@ countries = dplyr::filter(
 
 regime_difference_tests <- dplyr::bind_rows(individuals, countries)
 
-# correlations ####
-correlations <- readr::read_rds(
-  slituR::paste_forward_slash(results_directory_path, "correlations.rds")
+# correlations #################################################################
+## inner ####
+correlations_inner <- readr::read_rds(
+  slituR::paste_forward_slash(results_directory_path, "correlations-inner.rds")
 )
 
-## By period ####
-correlations_periods <- dplyr::filter(
-  correlations, field == "close price", type == "return", frequency == "day", timespan == "period"
+### By period ####
+correlations_inner_periods <- dplyr::filter(
+  correlations_inner, field == "close price", type == "return", frequency == "day", timespan == "period"
 ) %>%
   dplyr::select(country, sector, subsector, period, regime, average) %>%
   dplyr::group_by(country, sector, subsector, period, regime) %>%
@@ -244,9 +245,9 @@ correlations_periods <- dplyr::filter(
[…]

### 2024-11-19 explore/scripts/revision-jfm/analysis.r
construct equally weighted portfolio returns
for countries, sectors and subsectors

@@ -1,10 +1,9 @@
 pacman::p_load(finRes, magrittr)
 
-# source functions #############################################################
-source(here::here("explore", "scripts", "revision-jfm", "functions.r"))
-
 # load global variables ########################################################
-load_global_variables()
+# source(here::here("explore", "scripts", "revision-jfm", "functions.r"))
+# load_global_variables()
+load(here::here("explore", "scripts", "revision-jfm", "globals.RData"))
 
 # analysis #####################################################################
 
@@ -64,6 +63,12 @@ correlations_inner_summary <-
 ##### format ####
 correlations_inner_formatted <- 
   format_inner_correlations_summary_statistics_into_table(correlations_inner_summary)
+
+### cross ####
+#### raw ####
+correlations_cross_raw <- make_cross_correlations_for_ticker_combinations_dataframe(
+  commodity_pool_tickers, commodity_futures_data, aggregate_CHP_regimes, period_dates
+)
 
 ## regressions #################################################################
 commodity_pool_tickers <- make_commodity_pool_tickers_dataframe(

### 2024-11-19 explore/scripts/revision-jfm/functions.r

@@ -154,7 +154,8 @@ make_US_commodity_pool_combinations_for_regressions_analysis <- function(){
   )
 }
 
-make_commodity_pool_tickers_dataframe_for_country_sectors_subsectors_combinations <- function(combinations, all_tickers){
+make_commodity_pool_tickers_dataframe_for_country_sectors_subsectors_combinations <- 
+  function(combinations, all_tickers){
   
   dplyr::rowwise(combinations) %>% 
     dplyr::mutate(
@@ -162,7 +163,8 @@ make_commodity_pool_tickers_dataframe_for_country_sectors_subsectors_combination
     )
 }
 
-make_commodity_pool_tickers_dataframe <- function(all_tickers, analysis = c("correlations", "regressions")){
+make_commodity_pool_tickers_dataframe <- 
+  function(all_tickers, analysis = c("correlations", "regressions")){
   
   all_all_all <- tibble::tibble(
     country = "all", sector = "all", subsector = "all", 
@@ -641,7 +643,6 @@ load_commodity_factor_returns <- function(){
   )
 } 
 
-
 load_data <- function(){
   ## time boundaries ####
   date_start <<- "1996-01-01"; date_end <<- "2018-12-14"
@@ -1005,6 +1006,7 @@ compute_correlations <- function(df) {
   cor( dplyr::select(df, -date), use = "pairwise.complete.obs")
 }
 
+## inner #######################################################################
 make_inner_correlations_for_ticker_combinations_dataframe <- function(
     combinations, commodity_futures_data, aggregate_CHP_regimes, period_dates
     ){
@@ -1015,6 +1017,41 @@ make_inner_correlations_for_ticker_combinations_dataframe <- function(
   )
   
   dplyr::mutate(combinations, results = analysis)
+}
+
+## cross #######################################################################
+extract_relative_change_for_field_frequency_tickerscombination <- function(
+    commodity_futures_data, field, frequency, tickers
+){
+  dplyr::filter(
+    commodity_futures_data, type == "return", field == field, frequency == frequency,
+    `active contract ticker` %in% tickers
+  ) %>% dplyr::select(ticker = `active contract ticker`, date, value)
+}
+
+make_EW_portfolio_for_tickers <- function(tickers, commodity_futures_data){
+  extract_relative_change_for_field_frequency_tickerscombination(
+    commodity_futures_data, "PX_LAST", "day", tickers
[…]

### 2024-11-21 explore/scripts/revision-jfm/functions.r
cross correlation tables minor edits

@@ -1632,20 +1632,9 @@ format_inner_correlations_summary_statistics_into_table <- function(correlations
 ### cross ######################################################################
 format_cross_correlation_averages <- function(correlations_cross_summary){
   
-  periods <- dplyr::filter(correlations_cross_summary, timespan == "period") %>% 
-    dplyr::mutate(summary = purrr::map(summary, function(summary){
-        dplyr::mutate(summary, average = purrr::map_dbl(average, ~round(., digits = 4L))) %>%
-          tidyr::pivot_wider(names_from = period, values_from = average)
-      }) 
-    )
-  
-  years <- dplyr::filter(correlations_cross_summary, timespan == "year") %>%
-    dplyr::mutate(summary = purrr::map(summary, function(summary){
-      dplyr::mutate(summary, average = purrr::map_dbl(average, ~round(., digits = 4L)))
-      }) 
-    )
-  
-  dplyr::bind_rows(periods, years)
+  dplyr::mutate(correlations_cross_summary, summary = purrr::map(summary, function(summary){
+    dplyr::mutate(summary, average = purrr::map_dbl(average, ~round(., digits = 4L)))
+  })) 
 }
 
 

### 2024-11-21 explore/scripts/revision-jfm/tables.r

@@ -278,9 +278,13 @@ correlations_cross_periods <- dplyr::filter(correlations_cross, timespan == "per
   dplyr::mutate(
     portfolios = ifelse(pool == "country", "countries", paste0(pool, "s")),
     regime = factor(regime, levels = regime_levels),
-    ) %>%
-  dplyr::select(-pool) %>% dplyr::relocate(portfolios, .before = 1L) %>%
-  dplyr::arrange(portfolios, regime)
+    period = ifelse(period == "financialization", "financialisation", period),
+    period = ifelse(period == "present", "post-crisis", period),
+    period = factor(period, levels = period_levels)
+    ) %>% dplyr::select(-pool) %>% 
+  dplyr::relocate(portfolios, .before = 1L) %>%
+  dplyr::arrange(portfolios, period, regime) %>%
+  tidyr::pivot_wider(names_from = "period", values_from = "average")
 
 ### By year ####
 correlations_cross_years <- dplyr::filter(correlations_cross, timespan == "year") %>%

### 2024-11-21 docs/paper.qmd
refine captions for tbl-correlations-inner-periods and tbl-correlations-inner-years

@@
 #| label: tbl-correlations-periods
-#| tbl-cap: "This table shows the average return pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+#| tbl-cap: "This table shows the average return pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as within countries and commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
 For each period, the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
@@
 #| label: tbl-correlations-years
-#| tbl-cap: "This table shows the average return pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and sub-sectors by year for the whole period of interest (1997-2018).
+#| tbl-cap: "While \\@tbl-correlations-periods shows results calculated independently for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018), this stable shows the results of the same analysis calculated by year over the entire sample period (1997-2018).
 The results are discussed in \\@sec-results while \\@sec-taxonomy details the taxonomy for the commodity assets considered."

### 2024-11-21 docs/paper.tex
refine captions for tbl-correlations-inner-periods and tbl-correlations-inner-years

@@
 the whole cross-section of commodity assets considered in the study as
-well as across countries and commodity sectors and sub-sectors for the
+well as within countries and commodity sectors and sub-sectors for the
 four periods of interest (past: 1997-2003; financialisation: 2004-2008;
@@
 
-\caption{\label{tbl-correlations-years}This table shows the average
-return pairwise correlation coefficients calculated independently across
-the whole cross-section of commodity assets considered in the study as
-well as across countries and commodity sectors and sub-sectors by year
-for the whole period of interest (1997-2018). The results are discussed
-in Section~\ref{sec-results} while Section~\ref{sec-taxonomy} details
-the taxonomy for the commodity assets considered.}
+\caption{\label{tbl-correlations-years}While
+Table~\ref{tbl-correlations-periods} shows results calculated
+independently for the four periods of interest (past: 1997-2003;
+financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018),
+this stable shows the results of the same analysis calculated by year
+over the entire sample period (1997-2018). The results are discussed in
+Section~\ref{sec-results} while Section~\ref{sec-taxonomy} details the
+taxonomy for the commodity assets considered.}
 

### 2024-11-21 docs/paper.qmd
include new cross correlations by period table

--- 2024-11-19 docs/paper.qmd
@@
 We strive to address this issue by first examining the average returns pairwise correlations between commodities across the entire cross-section of the commodity assets considered in the study as well as by country, sector and sub-sector.
-@tbl-correlations-periods shows the results for the four periods of interest with the results reported for the entire period as well as for periods of **backwardation** and **contango**.
+@tbl-correlations-inner-periods shows the results for the four periods of interest with the results reported for the entire period as well as for periods of **backwardation** and **contango**.
 For the entire sample the average pairwise correlation jumps from 0.07 in the first period to 0.16 over financialisation.
@@
 The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods which indicates that increased commodity interdependence over financialisation was not a phase driven phenomenon in the same way that individual commodity returns are, as demonstrated in @tbl-stats-combined.
-We break down these average correlations by years in @tbl-correlations-years.
+We break down these average correlations by years in @tbl-correlations-inner-years.
 For the full sample of assets, the average pairwise correlations remain in the 0.06–0.08 range from 1998 through 2003, before suddenly increasing to 0.12 from 2003 to 2004.
@@
 
-The average pairwise correlation for the entire set of sample assets increases further to 0.28 (@tbl-correlations-periods) indicating an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation.
+The average pairwise correlation for the entire set of sample assets increases further to 0.28 (@tbl-correlations-inner-periods) indicating an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation.
 The result is consistent with the greater interdependence between equity and commodity markets over this period documented in @silvennoinen_financialisation_2013.
-The figure for the US traded section of the metals sector only progresses modestly to 0.59 after peaking at 0.63 in 2006 (@tbl-correlations-years).
+The figure for the US traded section of the metals sector only progresses modestly to 0.59 after peaking at 0.63 in 2006 (@tbl-correlations-inner-years).
 In contrast, the GB traded assets see a sharp increase to over 0.65  starting in 2007 up to a peak of 0.69 in 2010, and so does the agricultural sector with the sharpest increase in 2008 when the average pairwise correlation for the sector jumps to 0.30.
@@
 
-The average pairwise correlations fall across the board, below the levels observed during financialisation, with the figure for the entire cross-section (@tbl-correlations-periods) dropping down to 0.12 from 0.28 over the crisis.
-This substantial decline, that does not seem to have been widely noted, appears to begin in the latter part of the crisis period, around 2012 (@tbl-correlations-years), before levelling down over the whole post-crisis period.
+The average pairwise correlations fall across the board, below the levels observed during financialisation, with the figure for the entire cross-section (@tbl-correlations-inner-periods) dropping down to 0.12 from 0.28 over the crisis.
+This substantial decline, that does not seem to have been widely noted, appears to begin in the latter part of the crisis period, around 2012 (@tbl-correlations-inner-years), before levelling down over the whole post-crisis period.
 
@@
 ```{r}
-#| label: tbl-correlations-periods
-#| tbl-cap: "This table shows the average return pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+#| label: tbl-correlations-inner-periods
+#| tbl-cap: "This table shows the average return pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as within countries and commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
 For each period, the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
@@
 ```{r}
-#| label: tbl-correlations-years
-#| tbl-cap: "This table shows the average return pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and sub-sectors by year for the whole period of interest (1997-2018).
+#| label: tbl-correlations-cross-periods
+#| tbl-cap: "This table shows the return pairwise correlation coefficients between two equally weighted country portfolios (US, GB) with the first formed from the twenty four US commodities and the second from the six GB traded assets.
+The table further shows the average return pairwise correlation coefficients between equally weighted US sector portfolios (agriculturals, energy, metals) as well as between equally weighted US sub-sector portfolios (agriculturals: gains, livestock, softs; energy: gas, petroleum; metals: base, precious).
+The results are independently calculated for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+For each period, the results are further calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
+Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the taxonomy for the commodity assets considered is detailed in \\@sec-taxonomy."
+
+colnames <- c("portfolios", "regime", periods)
+align <- make_series_of_repeated_chars(list(l = 1L, r = 5L))
+
+make_table("correlations - cross - periods", c("portfolios", "regime"), colnames, align, 1L:2L, 3L:6L)
+```
+
+\newpage
+
+```{r}
+#| label: tbl-correlations-inner-years
+#| tbl-cap: "While \\@tbl-correlations-inner-periods shows results calculated independently for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018), this stable shows the results of the same analysis calculated by year over the entire sample period (1997-2018).
 The results are discussed in \\@sec-results while \\@sec-taxonomy details the taxonomy for the commodity assets considered."

### 2024-11-21 docs/paper.tex
include new cross correlations by period table

--- 2024-11-18 docs/paper.tex
@@
 cross-section of the commodity assets considered in the study as well as
-by country, sector and sub-sector. Table~\ref{tbl-correlations-periods}
-shows the results for the four periods of interest with the results
-reported for the entire period as well as for periods of
-\textbf{backwardation} and \textbf{contango}. For the entire sample the
-average pairwise correlation jumps from 0.07 in the first period to 0.16
-over financialisation. This finding indicates higher interdependence
-within the full cross-section of commodities starting with the
-financialisation period, consistent with the empirical findings in
-\citet{fryMcKibbin_evolution_2023} and
+by country, sector and sub-sector.
+Table~\ref{tbl-correlations-inner-periods} shows the results for the
+four periods of interest with the results reported for the entire period
+as well as for periods of \textbf{backwardation} and \textbf{contango}.
+For the entire sample the average pairwise correlation jumps from 0.07
+in the first period to 0.16 over financialisation. This finding
+indicates higher interdependence within the full cross-section of
+commodities starting with the financialisation period, consistent with
+the empirical findings in \citet{fryMcKibbin_evolution_2023} and
 \citet{mayer_financialization_2017} as well as with the theoretical
@@
 We break down these average correlations by years in
-Table~\ref{tbl-correlations-years}. For the full sample of assets, the
-average pairwise correlations remain in the 0.06--0.08 range from 1998
-through 2003, before suddenly increasing to 0.12 from 2003 to 2004. This
-suggests 2004 as a distinct break point for the onset of
+Table~\ref{tbl-correlations-inner-years}. For the full sample of assets,
+the average pairwise correlations remain in the 0.06--0.08 range from
+1998 through 2003, before suddenly increasing to 0.12 from 2003 to 2004.
+This suggests 2004 as a distinct break point for the onset of
 financialisation, as noted in several studies
@@
 The average pairwise correlation for the entire set of sample assets
-increases further to 0.28 (Table~\ref{tbl-correlations-periods})
+increases further to 0.28 (Table~\ref{tbl-correlations-inner-periods})
 indicating an intensification of the higher interdependence within the
@@
 section of the metals sector only progresses modestly to 0.59 after
-peaking at 0.63 in 2006 (Table~\ref{tbl-correlations-years}). In
+peaking at 0.63 in 2006 (Table~\ref{tbl-correlations-inner-years}). In
 contrast, the GB traded assets see a sharp increase to over 0.65
@@
 levels observed during financialisation, with the figure for the entire
-cross-section (Table~\ref{tbl-correlations-periods}) dropping down to
-0.12 from 0.28 over the crisis. This substantial decline, that does not
-seem to have been widely noted, appears to begin in the latter part of
-the crisis period, around 2012 (Table~\ref{tbl-correlations-years}),
-before levelling down over the whole post-crisis period.
+cross-section (Table~\ref{tbl-correlations-inner-periods}) dropping down
+to 0.12 from 0.28 over the crisis. This substantial decline, that does
+not seem to have been widely noted, appears to begin in the latter part
+of the crisis period, around 2012
+(Table~\ref{tbl-correlations-inner-years}), before levelling down over
+the whole post-crisis period.
 
@@
 
-\caption{\label{tbl-correlations-periods}This table shows the average
-return pairwise correlation coefficients calculated independently across
-the whole cross-section of commodity assets considered in the study as
-well as across countries and commodity sectors and sub-sectors for the
-four periods of interest (past: 1997-2003; financialisation: 2004-2008;
-crisis: 2008-2013; post-crisis: 2013-2018). For each period, the results
-are calculated independently over the entire period as well as over
-phases of aggregate backwardation and contango. Aggregate CHP
-construction and corresponding regime definitions are discussed in
-Section~\ref{sec-methods} while the results are discussed in
-Section~\ref{sec-results} and the taxonomy for the commodity assets
-considered is detailed in Section~\ref{sec-taxonomy}.}
+\caption{\label{tbl-correlations-inner-periods}This table shows the
+average return pairwise correlation coefficients calculated
+independently across the whole cross-section of commodity assets
+considered in the study as well as within countries and commodity
+sectors and sub-sectors for the four periods of interest (past:
+1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
+2013-2018). For each period, the results are calculated independently
+over the entire period as well as over phases of aggregate backwardation
+and contango. Aggregate CHP construction and corresponding regime
+definitions are discussed in Section~\ref{sec-methods} while the results
+are discussed in Section~\ref{sec-results} and the taxonomy for the
+commodity assets considered is detailed in Section~\ref{sec-taxonomy}.}
 
@@
 
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}r>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-correlations-cross-periods}This table shows the
+return pairwise correlation coefficients between two equally weighted
+country portfolios (US, GB) with the first formed from the twenty four
+US commodities and the second from the six GB traded assets. The table
+further shows the average return pairwise correlation coefficients
+between equally weighted US sector portfolios (agriculturals, energy,
+metals) as well as between equally weighted US sub-sector portfolios
+(agriculturals: gains, livestock, softs; energy: gas, petroleum; metals:
+base, precious). The results are independently calculated for the four
+periods of interest (past: 1997-2003; financialisation: 2004-2008;
+crisis: 2008-2013; post-crisis: 2013-2018). For each period, the results
+are further calculated independently over the entire period as well as
+over phases of aggregate backwardation and contango. Aggregate CHP
+construction and corresponding regime definitions are discussed in
+Section~\ref{sec-methods} while the results are discussed in
+Section~\ref{sec-results} and the taxonomy for the commodity assets
+considered is detailed in Section~\ref{sec-taxonomy}.}
+
+\tabularnewline
+
+\toprule
+\textcolor{black}{\textbf{portfolios}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\midrule
+\textbf{\cellcolor{gray!10}{countries}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0053}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0024}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0024}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0028}}\\
+\textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.0157} & \textcolor[HTML]{4285f4}{-0.0041} & \textcolor[HTML]{4285f4}{0.0106} & \textcolor[HTML]{4285f4}{-0.0127}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0100}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0078}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0183}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0050}}\\
+\textbf{sectors} & \textbf{whole period} & \textcolor[HTML]{4285f4}{0.0496} & \textcolor[HTML]{4285f4}{0.0073} & \textcolor[HTML]{4285f4}{0.0637} & \textcolor[HTML]{4285f4}{0.0116}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.1527}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0183}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.2099}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0902}}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.0223} & \textcolor[HTML]{4285f4}{0.0240} & \textcolor[HTML]{4285f4}{-0.0141} & \textcolor[HTML]{4285f4}{0.0024}\\
+\textbf{\cellcolor{gray!10}{subsectors}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0421}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0631}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0799}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0778}}\\
+\textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.1166} & \textcolor[HTML]{4285f4}{0.0201} & \textcolor[HTML]{4285f4}{0.0633} & \textcolor[HTML]{4285f4}{0.0727}\\
+\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0297}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.1164}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0889}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0812}}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
+\newpage
+
 \begin{landscape}\begingroup\fontsize{7}{9}\selectfont
@@
 
-\caption{\label{tbl-correlations-years}This table shows the average
-return pairwise correlation coefficients calculated independently across
-the whole cross-section of commodity assets considered in the study as
-well as across countries and commodity sectors and sub-sectors by year
-for the whole period of interest (1997-2018). The results are discussed
-in Section~\ref{sec-results} while Section~\ref{sec-taxonomy} details
-the taxonomy for the commodity assets considered.}
+\caption{\label{tbl-correlations-inner-years}While
+Table~\ref{tbl-correlations-inner-periods} shows results calculated
+independently for the four periods of interest (past: 1997-2003;
+financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018),
+this stable shows the results of the same analysis calculated by year
+over the entire sample period (1997-2018). The results are discussed in
+Section~\ref{sec-results} while Section~\ref{sec-taxonomy} details the
+taxonomy for the commodity assets considered.}
 

### 2024-12-04 explore/scripts/revision-jfm/tables.r
Cache some elements of paper rendering process

@@ -1,12 +1,11 @@
-pacman::p_load(magrittr)
-
 # Globals ######################################################################
 ## datasets ####
 data("tickers_futures", "tickers_cftc", package = "BBGsymbols")
 data("exchanges", package = "fewISOs")
 
 ## variables ####
-factors <- c("market", "CHP", "open interest nearby", "open interest aggregate", "term structure")
+factors <- 
+  c("market", "CHP", "open interest nearby", "open interest aggregate", "term structure")
 period_levels <- c("past", "financialisation", "crisis", "post-crisis")
 results_directory_path <- here::here("explore", "results", "revision-jfm")
 sector_levels <- c("all", "agriculturals", "energy", "metals")
@@ -17,7 +16,8 @@ sort_levels <- c(
   "US-metals-precious", "GB-all-all"
 )
 portfolio_levels <- c("countries", "sectors", "subsectors")
-subsector_levels <- c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")
+subsector_levels <- 
+  c("all", "grains", "livestock", "softs", "gas", "petroleum", "base", "precious")
 regime_levels <- c("whole period", "backwardation", "contango")
 tables_directory_path <- here::here("explore", "tables", "revision-jfm")
 commodity_futures_tickers <- c(
@@ -35,11 +35,11 @@ commodity_futures_tickers <- c(
 make_asset_name_country_sector_subsector_dataframe <- function(tickers){
   
   dplyr::left_join(
-    dplyr::filter(tickers_futures, ticker %in% tickers) %>% 
+    dplyr::filter(tickers_futures, ticker %in% tickers) |> 
       dplyr::select(ticker, name, sector, subsector, MIC), 
     dplyr::select(exchanges, MIC, country), 
     by = "MIC"
-  ) %>% dplyr::select(-ticker)
+  ) |> dplyr::select(-ticker)
 }
 significance <- function(p.value, estimate){
   if(p.value <= 0.01) paste0("***", estimate)
@@ -52,143 +52,150 @@ sort_table_by_country_sector_subsector <- function(tb, sort_levels){
     tb,
     sort = paste(country, sector, subsector, sep = "-"),
     sort = factor(sort, levels = sort_levels)
-  ) %>% dplyr::arrange(sort) %>% dplyr::select(-sort)
[…]

### 2024-12-04 docs/paper.qmd
paper edits
refactor make_table function + introduce cross correlation analysis in methods section.

@@
       cite-style: authoryear
+
   html:
@@
 ```{r}
-#| label: globals
+#| label: fetch
 #| include: false
-
-pacman::p_load(kableExtra, magrittr, slituR)
-
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+#| cache: true
 
@@
 purrr::walk2(urls, file_names, function(url, file_name) download.file(url, file_name))
+```
+
+```{r}
+#| label: globals
+#| include: false
+#| cache: false
+
+knitr::opts_chunk$set(cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE)
+
+pacman::p_load(kableExtra, magrittr, slituR)
 
@@
 
-make_table <- function(table_name, columns_to_collapse_rows_for, colnames, align, bold_columns, coloured_columns){
+make_table <- function(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns){
   get_results(tables, table_name) %>% dplyr::mutate(dplyr::across(dplyr::where(is.factor), as.character)) %>%
     collapse_rows(columns_to_collapse_rows_for) %>%
-  kbl(booktabs = T, longtable = T, col.names = colnames, align = align) %>%
-  kable_styling(latex_options = "striped", font_size = 7L) %>%
+    kbl(booktabs = T, longtable = longtable, col.names = colnames, align = align) %>%
+    kable_styling(latex_options = "basic", font_size = 7L) %>%
     row_spec(0L, bold = TRUE, color = "black") %>%
@@
 These correlation coefficients are then averaged across the entire cross-section of assets, as well as by country, sector, and sub-sector.
-For each period, the coefficients are also calculated and averaged across phases of low and high cross-sectional CHP.
-
+For each period, the coefficients are also calculated and averaged independently over phases of low and high cross-sectional CHP.
+We further form equally weighted portfolios by country, by grouping together the US and GB traded assets independently, as well a
+by sector and sub-sector for the US traded assets.
+For each period we compute the correlation coefficient between the two country portfolios as well as the average pairwise correlation coefficients between the sector and sub-sector portfolios; these are computed over the entire period as well as over phases of low and high cross-sectional CHP.
 This approach sheds light on the evolving interconnectedness among commodity assets as the complex transitions from traditional market dynamics---where commodity producers and speculators had distinct roles---to a more intricate landscape shaped by the influx of financial investors.
@@
 The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods which indicates that increased commodity interdependence over financialisation was not a phase driven phenomenon in the same way that individual commodity returns are, as demonstrated in @tbl-stats-combined.
-We break down these average correlations by years in @tbl-correlations-inner-years.
+We break down these average correlations by year in @tbl-correlations-inner-years.
 For the full sample of assets, the average pairwise correlations remain in the 0.06–0.08 range from 1998 through 2003, before suddenly increasing to 0.12 from 2003 to 2004.
@@
 
+\newgeometry{margin=.75in}
+
 \newpage
@@
 
+table_name <- "stats - combined"
+columns_to_collapse_rows_for <- c("asset", "regime")
 colnames <- c("asset", "regime", "estimate", periods)
 align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+longtable <- TRUE
+bold_columns <- 1L:3L
+coloured_columns <- 4L:7L
 
-make_table("stats - combined", c("asset", "regime"), colnames, align, 1L:7L, 4L:7L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```
@@
 
+table_name <- "regime difference tests"
+columns_to_collapse_rows_for <- c("asset", "period")
 colnames <- c("asset", "period", "moment", "dominant regime", "p-value", "significance")
 align <- make_series_of_repeated_chars(list(l = 4L, r = 2L))
+longtable <- TRUE
+bold_columns <- 1L:4L 
+coloured_columns <- 5L:6L
 
-make_table("regime difference tests", c("asset", "period"), colnames, align, 1L:4L, 5L:6L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```
@@
 
+table_name <- "regressions - US returns ~ US CHP"
+columns_to_collapse_rows_for <- c("regressor", "sector")
 colnames <- c("regressor", "sector", "sub-sector", periods)
 align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+longtable <- TRUE
+bold_columns <- 1L:7L
+coloured_columns <- 4L:7L
 
-make_table("regressions - US returns ~ US CHP", c("regressor", "sector"), colnames, align, 1L:7L, 4L:7L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```
@@
 
+table_name <- "correlations - inner - periods"
+columns_to_collapse_rows_for <- c("country", "sector", "subsector")
 colnames <- c(sectors, "regime", periods)
 align <- make_series_of_repeated_chars(list(l = 3L, r = 5L))
+longtable <- TRUE
+bold_columns <- 1L:8L 
+coloured_columns <- 5L:8L
 
-make_table("correlations - inner - periods", c("country", "sector", "subsector"), colnames, align, 1L:8L, 5L:8L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```
-
-\newpage
 
@@
 
+table_name <- "correlations - cross - periods"
+columns_to_collapse_rows_for <- c("portfolios", "regime")
 colnames <- c("portfolios", "regime", periods)
 align <- make_series_of_repeated_chars(list(l = 1L, r = 5L))
+longtable <- TRUE
+bold_columns <- 1L:2L
+coloured_columns <- 3L:6L
 
-make_table("correlations - cross - periods", c("portfolios", "regime"), colnames, align, 1L:2L, 3L:6L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
+```
+
+\newpage
+
+```{r}
+#| eval: false
+#| label: tbl-experimental
+#| tbl-cap: "lorem ipsum dolor sit amet consectetur adipiscing elit sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident sunt in culpa qui officia deserunt mollit anim id est laborum.
+Lorem ipsum dolor sit amet consectetur adipiscing elit sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident sunt in culpa qui officia deserunt mollit anim id est laborum."
+#| tbl-subcap: 
+#|     - "Average pairwise inner correlations"
+#|     - "Average pairwise cross correlations"
+#| layout-nrows: 2
+
+table1_format <- list(
+  table_name = "correlations - inner - periods",
+  columns_to_collapse_rows_for = c("country", "sector", "subsector"),
+  longtable = FALSE,
+  colnames = c(sectors, "regime", periods),
+  align = make_series_of_repeated_chars(list(l = 3L, r = 5L)),
+  bold_columns = 1L:8L, 
+  coloured_columns = 5L:8L
+  )
+table2_format <- list(
+  table_name = "correlations - cross - periods",
+  columns_to_collapse_rows_for = c("portfolios", "regime"),
+  longtable = TRUE,
+  colnames = c("portfolios", "regime", periods),
+  align = make_series_of_repeated_chars(list(l = 1L, r = 5L)),
+  bold_columns = 1L:2L, 
+  coloured_columns = 3L:6L
+)
+formats <- list(table1_format, table2_format)
+
+get_results(tables, table1_format$table_name) %>% dplyr::mutate(dplyr::across(dplyr::where(is.factor), as.character)) %>%
+    collapse_rows(table1_format$columns_to_collapse_rows_for) %>%
+    kable(booktabs = T, longtable = table1_format$longtable, col.names = table1_format$colnames, align = table1_format$align, escape = FALSE) %>%
+    kable_styling(font_size = 7L) %>%
+    row_spec(0L, bold = TRUE, color = "black") %>%
+    column_spec(table1_format$bold_columns, bold = TRUE) %>% column_spec(table1_format$coloured_columns, color = "#4285f4")
+
+get_results(tables, table2_format$table_name) %>% dplyr::mutate(dplyr::across(dplyr::where(is.factor), as.character)) %>%
+    collapse_rows(table2_format$columns_to_collapse_rows_for) %>%
+    kable(booktabs = T, longtable = table2_format$longtable, col.names = table2_format$colnames, align = table2_format$align, escape = FALSE) %>%
+    kable_styling(font_size = 7L) %>%
+    row_spec(0L, bold = TRUE, color = "black") %>%
+    column_spec(table2_format$bold_columns, bold = TRUE) %>% column_spec(table2_format$coloured_columns, color = "#4285f4")
 ```
@@
 
+table_name <- "correlations - inner - years"
+columns_to_collapse_rows_for <- c("country", "sector", "subsector")
 colnames <- c(sectors, "decade", 0L:9L)
 align <- make_series_of_repeated_chars(list(l = 4L, r = 10L))
+longtable <- TRUE
+bold_columns <- 1L:14L
+coloured_columns <- 5L:14L
 
-make_table("correlations - inner - years", c("country", "sector", "subsector"), colnames, align, 1L:14L, 5L:14L) %>%
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns) %>%
   landscape()
@@
 
+table_name <- "regressions - all returns ~ market index"
+columns_to_collapse_rows_for <- c("country", "sector", "subsector")
 colnames <- c(sectors, periods)
 align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+longtable <- TRUE
+bold_columns <- 1L:7L
+coloured_columns <- 4L:7L
 
-make_table(
-  "regressions - all returns ~ market index", c("country", "sector", "subsector"), 
-  colnames, align, 1L:7L, 4L:7L
-  )
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```
@@
 
+table_name <- "regressions - all returns ~ factors"
+columns_to_collapse_rows_for <- c("country", "sector", "subsector", "factor")
 colnames <- c(sectors, "factor", "regime", periods)
 align <- make_series_of_repeated_chars(list(l = 5L, r = 4L))
+longtable <- TRUE
+bold_columns <- 1L:9L
+coloured_columns <- 6L:9L
 
-make_table(
-  "regressions - all returns ~ factors", c("country", "sector", "subsector", "factor"), 
-  colnames, align, 1L:9L, 6L:9L
-  ) %>% landscape()
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns) 
 ```
+
+\restoregeometry
 
@@
 
+table_name <- "assets taxonomy"
+columns_to_collapse_rows_for <- c("country", "sector", "subsector")
 colnames <- c("asset", "country", "sector", "sub-sector")
 align <- make_series_of_repeated_chars(list(l = 4L))
+longtable <- TRUE
+bold_columns <- 1L
+coloured_columns <- 2L:4L
 
-make_table("assets taxonomy", c("country", "sector", "subsector"), colnames, align, 1L, 2L:4L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```

### 2024-12-04 docs/paper.tex
paper edits
refactor make_table function + introduce cross correlation analysis in methods section.

@@
 assets, as well as by country, sector, and sub-sector. For each period,
-the coefficients are also calculated and averaged across phases of low
-and high cross-sectional CHP.
-
+the coefficients are also calculated and averaged independently over
+phases of low and high cross-sectional CHP. We further form equally
+weighted portfolios by country, by grouping together the US and GB
+traded assets independently, as well a by sector and sub-sector for the
+US traded assets. For each period we compute the correlation coefficient
+between the two country portfolios as well as the average pairwise
+correlation coefficients between the sector and sub-sector portfolios;
+these are computed over the entire period as well as over phases of low
+and high cross-sectional CHP.\\
 This approach sheds light on the evolving interconnectedness among
@@
 returns are, as demonstrated in Table~\ref{tbl-stats-combined}.\\
-We break down these average correlations by years in
+We break down these average correlations by year in
 Table~\ref{tbl-correlations-inner-years}. For the full sample of assets,
@@
 \midrule
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.74\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.07\%}} & \textcolor[HTML]{4285f4}{\textbf{29.14\%}} & \textcolor[HTML]{4285f4}{\textbf{31.59\%}} & \textcolor[HTML]{4285f4}{\textbf{21\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.78\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.17\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.52\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.44\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.35\%}} & \textcolor[HTML]{4285f4}{\textbf{28.94\%}} & \textcolor[HTML]{4285f4}{\textbf{22.33\%}} & \textcolor[HTML]{4285f4}{\textbf{18.19\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.12\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.45\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.93\%}} & \textcolor[HTML]{4285f4}{\textbf{34.58\%}} & \textcolor[HTML]{4285f4}{\textbf{24.39\%}} & \textcolor[HTML]{4285f4}{\textbf{22.04\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.09\%}} & \textcolor[HTML]{4285f4}{\textbf{24.74\%}} & \textcolor[HTML]{4285f4}{\textbf{31.11\%}} & \textcolor[HTML]{4285f4}{\textbf{20.56\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.44\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{36\%}} & \textcolor[HTML]{4285f4}{\textbf{37.53\%}} & \textcolor[HTML]{4285f4}{\textbf{26.57\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.77\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.04\%}} & \textcolor[HTML]{4285f4}{\textbf{29.84\%}} & \textcolor[HTML]{4285f4}{\textbf{37.73\%}} & \textcolor[HTML]{4285f4}{\textbf{26.72\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**20.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.58\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}} & \textcolor[HTML]{4285f4}{\textbf{14.93\%}} & \textcolor[HTML]{4285f4}{\textbf{13.39\%}} & \textcolor[HTML]{4285f4}{\textbf{20.14\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.12\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.67\%}} & \textcolor[HTML]{4285f4}{\textbf{15.35\%}} & \textcolor[HTML]{4285f4}{\textbf{16.91\%}} & \textcolor[HTML]{4285f4}{\textbf{17.23\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.07\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.65\%}} & \textcolor[HTML]{4285f4}{\textbf{17.91\%}} & \textcolor[HTML]{4285f4}{\textbf{14.97\%}} & \textcolor[HTML]{4285f4}{\textbf{19.9\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.49\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}} & \textcolor[HTML]{4285f4}{\textbf{17.57\%}} & \textcolor[HTML]{4285f4}{\textbf{16.66\%}}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.23\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.24\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{37.6\%}} & \textcolor[HTML]{4285f4}{\textbf{35.73\%}} & \textcolor[HTML]{4285f4}{\textbf{27.83\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.66\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.22\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}} & \textcolor[HTML]{4285f4}{\textbf{32.78\%}} & \textcolor[HTML]{4285f4}{\textbf{38.28\%}}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.65\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.98\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.57\%}} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.29\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.91\%}} & \textcolor[HTML]{4285f4}{\textbf{34.66\%}} & \textcolor[HTML]{4285f4}{\textbf{23.57\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.99\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.36\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{48.82\%}} & \textcolor[HTML]{4285f4}{\textbf{32.6\%}} & \textcolor[HTML]{4285f4}{\textbf{29.92\%}} & \textcolor[HTML]{4285f4}{\textbf{31.52\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.24\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.22\%}} & \textcolor[HTML]{4285f4}{\textbf{32.24\%}}\\
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.84\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.02\%}} & \textcolor[HTML]{4285f4}{\textbf{29.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.94\%}} & \textcolor[HTML]{4285f4}{\textbf{21.33\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.91\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.77\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.59\%}} & \textcolor[HTML]{4285f4}{\textbf{19.95\%}}\\
-\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.06\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**26.99\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.43\%}} & \textcolor[HTML]{4285f4}{\textbf{30.72\%}} & \textcolor[HTML]{4285f4}{\textbf{35.45\%}} & \textcolor[HTML]{4285f4}{\textbf{21.26\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.14\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}} & \textcolor[HTML]{4285f4}{\textbf{28.2\%}} & \textcolor[HTML]{4285f4}{\textbf{37.23\%}} & \textcolor[HTML]{4285f4}{\textbf{28.45\%}}\\
-\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.8\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.64\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{30.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.64\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.64\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{38.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.11\%}}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.16\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.07\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.6\%}} & \textcolor[HTML]{4285f4}{\textbf{41.29\%}} & \textcolor[HTML]{4285f4}{\textbf{27.69\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.7\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.48\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.09\%}} & \textcolor[HTML]{4285f4}{\textbf{29.83\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.33\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**85.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.76\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.33\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{63.46\%}} & \textcolor[HTML]{4285f4}{\textbf{47.3\%}} & \textcolor[HTML]{4285f4}{\textbf{48.85\%}} & \textcolor[HTML]{4285f4}{\textbf{42.59\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.25\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{59.76\%}} & \textcolor[HTML]{4285f4}{\textbf{61.3\%}} & \textcolor[HTML]{4285f4}{\textbf{58.18\%}} & \textcolor[HTML]{4285f4}{\textbf{46.41\%}}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.64\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.24\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.74\%}} & \textcolor[HTML]{4285f4}{\textbf{32.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.19\%}} & \textcolor[HTML]{4285f4}{\textbf{26.94\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-24.85\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.74\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{53.7\%}} & \textcolor[HTML]{4285f4}{\textbf{41.08\%}}\\
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.37\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.47\%}} & \textcolor[HTML]{4285f4}{\textbf{39.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.1\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-19.47\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.14\%}} & \textcolor[HTML]{4285f4}{\textbf{44.13\%}} & \textcolor[HTML]{4285f4}{\textbf{47.11\%}} & \textcolor[HTML]{4285f4}{\textbf{41.71\%}}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.44\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.16\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.37\%}} & \textcolor[HTML]{4285f4}{\textbf{33.33\%}} & \textcolor[HTML]{4285f4}{\textbf{25.95\%}} & \textcolor[HTML]{4285f4}{\textbf{24.62\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-21.62\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.98\%}} & \textcolor[HTML]{4285f4}{\textbf{39.16\%}} & \textcolor[HTML]{4285f4}{\textbf{35.69\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.1\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.1\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{30.05\%}} & \textcolor[HTML]{4285f4}{\textbf{25.73\%}} & \textcolor[HTML]{4285f4}{\textbf{18.16\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-12.15\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.78\%}} & \textcolor[HTML]{4285f4}{\textbf{33.69\%}} & \textcolor[HTML]{4285f4}{\textbf{42.28\%}} & \textcolor[HTML]{4285f4}{\textbf{20.87\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.53\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.21\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.89\%}} & \textcolor[HTML]{4285f4}{\textbf{19.2\%}} & \textcolor[HTML]{4285f4}{\textbf{17.03\%}} & \textcolor[HTML]{4285f4}{\textbf{12.36\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.1\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}} & \textcolor[HTML]{4285f4}{\textbf{25.21\%}} & \textcolor[HTML]{4285f4}{\textbf{16.23\%}}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.75\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**49.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**31.93\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.49\%}} & \textcolor[HTML]{4285f4}{\textbf{23.82\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.88\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.2\%}} & \textcolor[HTML]{4285f4}{\textbf{38.71\%}} & \textcolor[HTML]{4285f4}{\textbf{26.8\%}}\\
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.92\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*25.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.17\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.1\%}} & \textcolor[HTML]{4285f4}{\textbf{22.51\%}} & \textcolor[HTML]{4285f4}{\textbf{21.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.04\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.28\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.12\%}} & \textcolor[HTML]{4285f4}{\textbf{22.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.75\%}} & \textcolor[HTML]{4285f4}{\textbf{20.8\%}}\\
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.43\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.44\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.07\%}} & \textcolor[HTML]{4285f4}{\textbf{32.5\%}} & \textcolor[HTML]{4285f4}{\textbf{37.17\%}} & \textcolor[HTML]{4285f4}{\textbf{20.3\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.09\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.93\%}} & \textcolor[HTML]{4285f4}{\textbf{35.34\%}} & \textcolor[HTML]{4285f4}{\textbf{42.44\%}} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}}\\
-\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.15\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**23.68\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.57\%}} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{18.94\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-23.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.74\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.13\%}} & \textcolor[HTML]{4285f4}{\textbf{27.29\%}} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{18.23\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**28.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.03\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.99\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.98\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{17.92\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.89\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{41.31\%}} & \textcolor[HTML]{4285f4}{\textbf{19.86\%}}\\
-\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.05\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.16\%}} & \textcolor[HTML]{4285f4}{\textbf{39.91\%}} & \textcolor[HTML]{4285f4}{\textbf{35.35\%}} & \textcolor[HTML]{4285f4}{\textbf{23.37\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*46.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-13.41\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.12\%}} & \textcolor[HTML]{4285f4}{\textbf{43.16\%}} & \textcolor[HTML]{4285f4}{\textbf{46.22\%}} & \textcolor[HTML]{4285f4}{\textbf{23.09\%}}\\
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.31\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-39.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**35.09\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.23\%}} & \textcolor[HTML]{4285f4}{\textbf{41.62\%}} & \textcolor[HTML]{4285f4}{\textbf{34.48\%}} & \textcolor[HTML]{4285f4}{\textbf{29.13\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**63.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**-34.64\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.28\%}} & \textcolor[HTML]{4285f4}{\textbf{46.72\%}} & \textcolor[HTML]{4285f4}{\textbf{47.44\%}} & \textcolor[HTML]{4285f4}{\textbf{28.6\%}}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.68\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.48\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.4\%}} & \textcolor[HTML]{4285f4}{\textbf{29.09\%}} & \textcolor[HTML]{4285f4}{\textbf{15.27\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.69\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.77\%}} & \textcolor[HTML]{4285f4}{\textbf{32.08\%}} & \textcolor[HTML]{4285f4}{\textbf{41.13\%}} & \textcolor[HTML]{4285f4}{\textbf{21.68\%}}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.07\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.05\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.42\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.86\%}} & \textcolor[HTML]{4285f4}{\textbf{33.28\%}} & \textcolor[HTML]{4285f4}{\textbf{22.12\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.31\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.38\%}} & \textcolor[HTML]{4285f4}{\textbf{40.51\%}} & \textcolor[HTML]{4285f4}{\textbf{39.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.32\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**15.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.18\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{***15.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.82\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*16.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.33\%}}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*21.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.72\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**19.95\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-14.05\%}}}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.48\%} & \textcolor[HTML]{4285f4}{21.37\%} & \textcolor[HTML]{4285f4}{6.89\%} & \textcolor[HTML]{4285f4}{-4.51\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23\%} & \textcolor[HTML]{4285f4}{29.54\%} & \textcolor[HTML]{4285f4}{36.15\%} & \textcolor[HTML]{4285f4}{21.8\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.86\%} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{20.48\%} & \textcolor[HTML]{4285f4}{-8.74\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23.07\%} & \textcolor[HTML]{4285f4}{29.14\%} & \textcolor[HTML]{4285f4}{31.59\%} & \textcolor[HTML]{4285f4}{21\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.3\%} & \textcolor[HTML]{4285f4}{23.54\%} & \textcolor[HTML]{4285f4}{-4.43\%} & \textcolor[HTML]{4285f4}{0.78\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23\%} & \textcolor[HTML]{4285f4}{30.01\%} & \textcolor[HTML]{4285f4}{40.14\%} & \textcolor[HTML]{4285f4}{22.68\%}\\
+\textbf{Oats (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.49\%} & \textcolor[HTML]{4285f4}{21.62\%} & \textcolor[HTML]{4285f4}{8.89\%} & \textcolor[HTML]{4285f4}{-0.87\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.22\%} & \textcolor[HTML]{4285f4}{31.04\%} & \textcolor[HTML]{4285f4}{34.67\%} & \textcolor[HTML]{4285f4}{29.5\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.39\%} & \textcolor[HTML]{4285f4}{7.82\%} & \textcolor[HTML]{4285f4}{7.85\%} & \textcolor[HTML]{4285f4}{2.56\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{29.02\%} & \textcolor[HTML]{4285f4}{33.82\%} & \textcolor[HTML]{4285f4}{31.43\%} & \textcolor[HTML]{4285f4}{31.55\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.95\%} & \textcolor[HTML]{4285f4}{*35.38\%} & \textcolor[HTML]{4285f4}{11.68\%} & \textcolor[HTML]{4285f4}{-3.17\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{35.22\%} & \textcolor[HTML]{4285f4}{28.1\%} & \textcolor[HTML]{4285f4}{37.7\%} & \textcolor[HTML]{4285f4}{27.5\%}\\
+\textbf{Soybean meal (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{7.29\%} & \textcolor[HTML]{4285f4}{12.06\%} & \textcolor[HTML]{4285f4}{8.12\%} & \textcolor[HTML]{4285f4}{-0.33\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.34\%} & \textcolor[HTML]{4285f4}{32.55\%} & \textcolor[HTML]{4285f4}{31.78\%} & \textcolor[HTML]{4285f4}{25.11\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{13.15\%} & \textcolor[HTML]{4285f4}{8.22\%} & \textcolor[HTML]{4285f4}{16.04\%} & \textcolor[HTML]{4285f4}{-3.52\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{27.77\%} & \textcolor[HTML]{4285f4}{33.06\%} & \textcolor[HTML]{4285f4}{25.7\%} & \textcolor[HTML]{4285f4}{25.1\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.52\%} & \textcolor[HTML]{4285f4}{15.91\%} & \textcolor[HTML]{4285f4}{2.32\%} & \textcolor[HTML]{4285f4}{2.22\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.94\%} & \textcolor[HTML]{4285f4}{32.13\%} & \textcolor[HTML]{4285f4}{36.85\%} & \textcolor[HTML]{4285f4}{25.32\%}\\
+\textbf{Soybean oil (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.21\%} & \textcolor[HTML]{4285f4}{15.57\%} & \textcolor[HTML]{4285f4}{4.04\%} & \textcolor[HTML]{4285f4}{-7.39\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.43\%} & \textcolor[HTML]{4285f4}{28.35\%} & \textcolor[HTML]{4285f4}{25.75\%} & \textcolor[HTML]{4285f4}{18.95\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{14.79\%} & \textcolor[HTML]{4285f4}{14.62\%} & \textcolor[HTML]{4285f4}{20.34\%} & \textcolor[HTML]{4285f4}{-9.44\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.35\%} & \textcolor[HTML]{4285f4}{28.94\%} & \textcolor[HTML]{4285f4}{22.33\%} & \textcolor[HTML]{4285f4}{18.19\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.68\%} & \textcolor[HTML]{4285f4}{16.62\%} & \textcolor[HTML]{4285f4}{-10.01\%} & \textcolor[HTML]{4285f4}{-4.12\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.55\%} & \textcolor[HTML]{4285f4}{27.91\%} & \textcolor[HTML]{4285f4}{28.65\%} & \textcolor[HTML]{4285f4}{19.79\%}\\
+\textbf{Soybeans (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.89\%} & \textcolor[HTML]{4285f4}{13.36\%} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{-3.82\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.47\%} & \textcolor[HTML]{4285f4}{30.04\%} & \textcolor[HTML]{4285f4}{28\%} & \textcolor[HTML]{4285f4}{21.22\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{13.69\%} & \textcolor[HTML]{4285f4}{0.93\%} & \textcolor[HTML]{4285f4}{13.42\%} & \textcolor[HTML]{4285f4}{-11.45\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.93\%} & \textcolor[HTML]{4285f4}{34.58\%} & \textcolor[HTML]{4285f4}{24.39\%} & \textcolor[HTML]{4285f4}{22.04\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.16\%} & \textcolor[HTML]{4285f4}{25.71\%} & \textcolor[HTML]{4285f4}{0.96\%} & \textcolor[HTML]{4285f4}{3.75\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.09\%} & \textcolor[HTML]{4285f4}{24.74\%} & \textcolor[HTML]{4285f4}{31.11\%} & \textcolor[HTML]{4285f4}{20.56\%}\\
+\addlinespace
+\textbf{Wheat-SRW (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.07\%} & \textcolor[HTML]{4285f4}{17.63\%} & \textcolor[HTML]{4285f4}{6.68\%} & \textcolor[HTML]{4285f4}{-1.58\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.93\%} & \textcolor[HTML]{4285f4}{33.03\%} & \textcolor[HTML]{4285f4}{37.62\%} & \textcolor[HTML]{4285f4}{26.58\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.7\%} & \textcolor[HTML]{4285f4}{19.02\%} & \textcolor[HTML]{4285f4}{0.98\%} & \textcolor[HTML]{4285f4}{0.44\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{25.79\%} & \textcolor[HTML]{4285f4}{36\%} & \textcolor[HTML]{4285f4}{37.53\%} & \textcolor[HTML]{4285f4}{26.57\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.78\%} & \textcolor[HTML]{4285f4}{16.29\%} & \textcolor[HTML]{4285f4}{14.57\%} & \textcolor[HTML]{4285f4}{-2.77\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.04\%} & \textcolor[HTML]{4285f4}{29.84\%} & \textcolor[HTML]{4285f4}{37.73\%} & \textcolor[HTML]{4285f4}{26.72\%}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{7.43\%} & \textcolor[HTML]{4285f4}{7.13\%} & \textcolor[HTML]{4285f4}{1.87\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.23\%} & \textcolor[HTML]{4285f4}{15.16\%} & \textcolor[HTML]{4285f4}{15.24\%} & \textcolor[HTML]{4285f4}{18.69\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.31\%} & \textcolor[HTML]{4285f4}{**20.52\%} & \textcolor[HTML]{4285f4}{7.51\%} & \textcolor[HTML]{4285f4}{6.58\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{12.79\%} & \textcolor[HTML]{4285f4}{14.93\%} & \textcolor[HTML]{4285f4}{13.39\%} & \textcolor[HTML]{4285f4}{20.14\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.81\%} & \textcolor[HTML]{4285f4}{-5.49\%} & \textcolor[HTML]{4285f4}{7.28\%} & \textcolor[HTML]{4285f4}{-3.12\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.67\%} & \textcolor[HTML]{4285f4}{15.35\%} & \textcolor[HTML]{4285f4}{16.91\%} & \textcolor[HTML]{4285f4}{17.23\%}\\
+\textbf{Cattle-live (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.45\%} & \textcolor[HTML]{4285f4}{8.77\%} & \textcolor[HTML]{4285f4}{4.13\%} & \textcolor[HTML]{4285f4}{1.92\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.1\%} & \textcolor[HTML]{4285f4}{17.43\%} & \textcolor[HTML]{4285f4}{16.32\%} & \textcolor[HTML]{4285f4}{18.3\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{8.39\%} & \textcolor[HTML]{4285f4}{14.2\%} & \textcolor[HTML]{4285f4}{5.87\%} & \textcolor[HTML]{4285f4}{-2.07\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.65\%} & \textcolor[HTML]{4285f4}{17.91\%} & \textcolor[HTML]{4285f4}{14.97\%} & \textcolor[HTML]{4285f4}{19.9\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.34\%} & \textcolor[HTML]{4285f4}{3.43\%} & \textcolor[HTML]{4285f4}{2.7\%} & \textcolor[HTML]{4285f4}{5.82\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.49\%} & \textcolor[HTML]{4285f4}{16.99\%} & \textcolor[HTML]{4285f4}{17.57\%} & \textcolor[HTML]{4285f4}{16.66\%}\\
+\textbf{Lean hogs (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{8.4\%} & \textcolor[HTML]{4285f4}{12.69\%} & \textcolor[HTML]{4285f4}{-1.09\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.33\%} & \textcolor[HTML]{4285f4}{31.89\%} & \textcolor[HTML]{4285f4}{30.37\%} & \textcolor[HTML]{4285f4}{36.94\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{12.34\%} & \textcolor[HTML]{4285f4}{16.3\%} & \textcolor[HTML]{4285f4}{18.23\%} & \textcolor[HTML]{4285f4}{19.24\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{37.6\%} & \textcolor[HTML]{4285f4}{35.73\%} & \textcolor[HTML]{4285f4}{27.83\%} & \textcolor[HTML]{4285f4}{35.61\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-10.5\%} & \textcolor[HTML]{4285f4}{0.6\%} & \textcolor[HTML]{4285f4}{7.5\%} & \textcolor[HTML]{4285f4}{-20.66\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{39.22\%} & \textcolor[HTML]{4285f4}{27.67\%} & \textcolor[HTML]{4285f4}{32.78\%} & \textcolor[HTML]{4285f4}{38.28\%}\\
+\textbf{Cocoa (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.66\%} & \textcolor[HTML]{4285f4}{16.35\%} & \textcolor[HTML]{4285f4}{1.39\%} & \textcolor[HTML]{4285f4}{3.65\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.66\%} & \textcolor[HTML]{4285f4}{29.99\%} & \textcolor[HTML]{4285f4}{31.03\%} & \textcolor[HTML]{4285f4}{24.69\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.12\%} & \textcolor[HTML]{4285f4}{9.25\%} & \textcolor[HTML]{4285f4}{-9.56\%} & \textcolor[HTML]{4285f4}{-2.98\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{33.57\%} & \textcolor[HTML]{4285f4}{31.05\%} & \textcolor[HTML]{4285f4}{26.93\%} & \textcolor[HTML]{4285f4}{25.86\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.67\%} & \textcolor[HTML]{4285f4}{23.43\%} & \textcolor[HTML]{4285f4}{12.92\%} & \textcolor[HTML]{4285f4}{10.29\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{31.81\%} & \textcolor[HTML]{4285f4}{28.91\%} & \textcolor[HTML]{4285f4}{34.66\%} & \textcolor[HTML]{4285f4}{23.57\%}\\
+\addlinespace
+\textbf{Coffee-C (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.91\%} & \textcolor[HTML]{4285f4}{20.38\%} & \textcolor[HTML]{4285f4}{2.2\%} & \textcolor[HTML]{4285f4}{1.99\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{43.84\%} & \textcolor[HTML]{4285f4}{32.3\%} & \textcolor[HTML]{4285f4}{30.17\%} & \textcolor[HTML]{4285f4}{31.86\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.51\%} & \textcolor[HTML]{4285f4}{26.49\%} & \textcolor[HTML]{4285f4}{2.66\%} & \textcolor[HTML]{4285f4}{14.36\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{48.82\%} & \textcolor[HTML]{4285f4}{32.6\%} & \textcolor[HTML]{4285f4}{29.92\%} & \textcolor[HTML]{4285f4}{31.52\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-16.87\%} & \textcolor[HTML]{4285f4}{14.38\%} & \textcolor[HTML]{4285f4}{3.4\%} & \textcolor[HTML]{4285f4}{-10.24\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.35\%} & \textcolor[HTML]{4285f4}{32.06\%} & \textcolor[HTML]{4285f4}{30.22\%} & \textcolor[HTML]{4285f4}{32.24\%}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.24\%} & \textcolor[HTML]{4285f4}{0.95\%} & \textcolor[HTML]{4285f4}{12.53\%} & \textcolor[HTML]{4285f4}{0.5\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.38\%} & \textcolor[HTML]{4285f4}{29.01\%} & \textcolor[HTML]{4285f4}{33.26\%} & \textcolor[HTML]{4285f4}{20.61\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{22.64\%} & \textcolor[HTML]{4285f4}{7.85\%} & \textcolor[HTML]{4285f4}{35.53\%} & \textcolor[HTML]{4285f4}{10.84\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.02\%} & \textcolor[HTML]{4285f4}{29.71\%} & \textcolor[HTML]{4285f4}{33.94\%} & \textcolor[HTML]{4285f4}{21.33\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-16.46\%} & \textcolor[HTML]{4285f4}{-5.92\%} & \textcolor[HTML]{4285f4}{-9.36\%} & \textcolor[HTML]{4285f4}{-8.91\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.77\%} & \textcolor[HTML]{4285f4}{28.35\%} & \textcolor[HTML]{4285f4}{32.59\%} & \textcolor[HTML]{4285f4}{19.95\%}\\
+\textbf{Lumber (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.9\%} & \textcolor[HTML]{4285f4}{-3.58\%} & \textcolor[HTML]{4285f4}{11.74\%} & \textcolor[HTML]{4285f4}{5.06\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.58\%} & \textcolor[HTML]{4285f4}{29.39\%} & \textcolor[HTML]{4285f4}{36.31\%} & \textcolor[HTML]{4285f4}{25.1\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-8.48\%} & \textcolor[HTML]{4285f4}{-2.37\%} & \textcolor[HTML]{4285f4}{29.11\%} & \textcolor[HTML]{4285f4}{**26.99\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.43\%} & \textcolor[HTML]{4285f4}{30.72\%} & \textcolor[HTML]{4285f4}{35.45\%} & \textcolor[HTML]{4285f4}{21.26\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.68\%} & \textcolor[HTML]{4285f4}{-4.77\%} & \textcolor[HTML]{4285f4}{-5.04\%} & \textcolor[HTML]{4285f4}{-17.14\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.56\%} & \textcolor[HTML]{4285f4}{28.2\%} & \textcolor[HTML]{4285f4}{37.23\%} & \textcolor[HTML]{4285f4}{28.45\%}\\
+\textbf{Orange juice (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.67\%} & \textcolor[HTML]{4285f4}{13.87\%} & \textcolor[HTML]{4285f4}{14.4\%} & \textcolor[HTML]{4285f4}{3.8\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{29.5\%} & \textcolor[HTML]{4285f4}{33.01\%} & \textcolor[HTML]{4285f4}{34.43\%} & \textcolor[HTML]{4285f4}{29.37\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.38\%} & \textcolor[HTML]{4285f4}{-2.22\%} & \textcolor[HTML]{4285f4}{18.24\%} & \textcolor[HTML]{4285f4}{18.64\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{28.01\%} & \textcolor[HTML]{4285f4}{33.01\%} & \textcolor[HTML]{4285f4}{30.09\%} & \textcolor[HTML]{4285f4}{28.64\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.83\%} & \textcolor[HTML]{4285f4}{29.93\%} & \textcolor[HTML]{4285f4}{12.29\%} & \textcolor[HTML]{4285f4}{-8.64\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{31.05\%} & \textcolor[HTML]{4285f4}{33.1\%} & \textcolor[HTML]{4285f4}{38.06\%} & \textcolor[HTML]{4285f4}{30.11\%}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.56\%} & \textcolor[HTML]{4285f4}{24.87\%} & \textcolor[HTML]{4285f4}{11.82\%} & \textcolor[HTML]{4285f4}{-1.16\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.88\%} & \textcolor[HTML]{4285f4}{33.25\%} & \textcolor[HTML]{4285f4}{37.9\%} & \textcolor[HTML]{4285f4}{28.72\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.98\%} & \textcolor[HTML]{4285f4}{29.51\%} & \textcolor[HTML]{4285f4}{2.7\%} & \textcolor[HTML]{4285f4}{-8.07\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{33.23\%} & \textcolor[HTML]{4285f4}{33.6\%} & \textcolor[HTML]{4285f4}{41.29\%} & \textcolor[HTML]{4285f4}{27.69\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-20.49\%} & \textcolor[HTML]{4285f4}{20.35\%} & \textcolor[HTML]{4285f4}{21.47\%} & \textcolor[HTML]{4285f4}{4.7\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{36.48\%} & \textcolor[HTML]{4285f4}{32.98\%} & \textcolor[HTML]{4285f4}{34.09\%} & \textcolor[HTML]{4285f4}{29.83\%}\\
+\addlinespace
+\textbf{Natural gas (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{35.38\%} & \textcolor[HTML]{4285f4}{16.25\%} & \textcolor[HTML]{4285f4}{0.93\%} & \textcolor[HTML]{4285f4}{8.33\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{61.55\%} & \textcolor[HTML]{4285f4}{54.6\%} & \textcolor[HTML]{4285f4}{53.58\%} & \textcolor[HTML]{4285f4}{44.58\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**85.84\%} & \textcolor[HTML]{4285f4}{4.76\%} & \textcolor[HTML]{4285f4}{-2.32\%} & \textcolor[HTML]{4285f4}{18.33\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{63.46\%} & \textcolor[HTML]{4285f4}{47.3\%} & \textcolor[HTML]{4285f4}{48.85\%} & \textcolor[HTML]{4285f4}{42.59\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-11.98\%} & \textcolor[HTML]{4285f4}{27.84\%} & \textcolor[HTML]{4285f4}{4.77\%} & \textcolor[HTML]{4285f4}{3.25\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{59.76\%} & \textcolor[HTML]{4285f4}{61.3\%} & \textcolor[HTML]{4285f4}{58.18\%} & \textcolor[HTML]{4285f4}{46.41\%}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{15.43\%} & \textcolor[HTML]{4285f4}{*28.74\%} & \textcolor[HTML]{4285f4}{9.67\%} & \textcolor[HTML]{4285f4}{-5.64\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{39.87\%} & \textcolor[HTML]{4285f4}{32.56\%} & \textcolor[HTML]{4285f4}{42.84\%} & \textcolor[HTML]{4285f4}{34.69\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{29.17\%} & \textcolor[HTML]{4285f4}{*35.61\%} & \textcolor[HTML]{4285f4}{11.47\%} & \textcolor[HTML]{4285f4}{14.24\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{36.74\%} & \textcolor[HTML]{4285f4}{32.09\%} & \textcolor[HTML]{4285f4}{28.19\%} & \textcolor[HTML]{4285f4}{26.94\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.21\%} & \textcolor[HTML]{4285f4}{22.04\%} & \textcolor[HTML]{4285f4}{9.95\%} & \textcolor[HTML]{4285f4}{-24.85\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.74\%} & \textcolor[HTML]{4285f4}{33.1\%} & \textcolor[HTML]{4285f4}{53.7\%} & \textcolor[HTML]{4285f4}{41.08\%}\\
+\textbf{Gasoline (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.65\%} & \textcolor[HTML]{4285f4}{30.95\%} & \textcolor[HTML]{4285f4}{10.59\%} & \textcolor[HTML]{4285f4}{-5.37\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.77\%} & \textcolor[HTML]{4285f4}{41.76\%} & \textcolor[HTML]{4285f4}{40.07\%} & \textcolor[HTML]{4285f4}{37.09\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{39\%} & \textcolor[HTML]{4285f4}{19.82\%} & \textcolor[HTML]{4285f4}{23.98\%} & \textcolor[HTML]{4285f4}{9.69\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.47\%} & \textcolor[HTML]{4285f4}{39.38\%} & \textcolor[HTML]{4285f4}{31.41\%} & \textcolor[HTML]{4285f4}{32.1\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.22\%} & \textcolor[HTML]{4285f4}{42.13\%} & \textcolor[HTML]{4285f4}{-0.09\%} & \textcolor[HTML]{4285f4}{-19.47\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{43.14\%} & \textcolor[HTML]{4285f4}{44.13\%} & \textcolor[HTML]{4285f4}{47.11\%} & \textcolor[HTML]{4285f4}{41.71\%}\\
+\textbf{Heating oil (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.31\%} & \textcolor[HTML]{4285f4}{*29.88\%} & \textcolor[HTML]{4285f4}{6.83\%} & \textcolor[HTML]{4285f4}{-3.44\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{40.75\%} & \textcolor[HTML]{4285f4}{35.09\%} & \textcolor[HTML]{4285f4}{33.17\%} & \textcolor[HTML]{4285f4}{30.56\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{36.32\%} & \textcolor[HTML]{4285f4}{29.41\%} & \textcolor[HTML]{4285f4}{25.56\%} & \textcolor[HTML]{4285f4}{15.16\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{41.37\%} & \textcolor[HTML]{4285f4}{33.33\%} & \textcolor[HTML]{4285f4}{25.95\%} & \textcolor[HTML]{4285f4}{24.62\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.74\%} & \textcolor[HTML]{4285f4}{30.5\%} & \textcolor[HTML]{4285f4}{-10.77\%} & \textcolor[HTML]{4285f4}{-21.62\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{40.19\%} & \textcolor[HTML]{4285f4}{36.98\%} & \textcolor[HTML]{4285f4}{39.16\%} & \textcolor[HTML]{4285f4}{35.69\%}\\
+\textbf{Copper (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.45\%} & \textcolor[HTML]{4285f4}{*28.15\%} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{-0.1\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.23\%} & \textcolor[HTML]{4285f4}{31.89\%} & \textcolor[HTML]{4285f4}{34.91\%} & \textcolor[HTML]{4285f4}{19.56\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.14\%} & \textcolor[HTML]{4285f4}{22.17\%} & \textcolor[HTML]{4285f4}{16.53\%} & \textcolor[HTML]{4285f4}{12.1\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.71\%} & \textcolor[HTML]{4285f4}{30.05\%} & \textcolor[HTML]{4285f4}{25.73\%} & \textcolor[HTML]{4285f4}{18.16\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.28\%} & \textcolor[HTML]{4285f4}{34.17\%} & \textcolor[HTML]{4285f4}{-3.46\%} & \textcolor[HTML]{4285f4}{-12.15\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.78\%} & \textcolor[HTML]{4285f4}{33.69\%} & \textcolor[HTML]{4285f4}{42.28\%} & \textcolor[HTML]{4285f4}{20.87\%}\\
+\addlinespace
+\textbf{Gold (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.5\%} & \textcolor[HTML]{4285f4}{14.35\%} & \textcolor[HTML]{4285f4}{14.01\%} & \textcolor[HTML]{4285f4}{0.53\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.14\%} & \textcolor[HTML]{4285f4}{18.89\%} & \textcolor[HTML]{4285f4}{21.46\%} & \textcolor[HTML]{4285f4}{14.41\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{9.19\%} & \textcolor[HTML]{4285f4}{13.37\%} & \textcolor[HTML]{4285f4}{9.37\%} & \textcolor[HTML]{4285f4}{4.21\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.89\%} & \textcolor[HTML]{4285f4}{19.2\%} & \textcolor[HTML]{4285f4}{17.03\%} & \textcolor[HTML]{4285f4}{12.36\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.01\%} & \textcolor[HTML]{4285f4}{15.37\%} & \textcolor[HTML]{4285f4}{19.1\%} & \textcolor[HTML]{4285f4}{-3.1\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.24\%} & \textcolor[HTML]{4285f4}{18.58\%} & \textcolor[HTML]{4285f4}{25.21\%} & \textcolor[HTML]{4285f4}{16.23\%}\\
+\textbf{Palladium (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{9.12\%} & \textcolor[HTML]{4285f4}{9.03\%} & \textcolor[HTML]{4285f4}{*29.12\%} & \textcolor[HTML]{4285f4}{13.75\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.27\%} & \textcolor[HTML]{4285f4}{32.71\%} & \textcolor[HTML]{4285f4}{36.14\%} & \textcolor[HTML]{4285f4}{25.38\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**49.79\%} & \textcolor[HTML]{4285f4}{24.47\%} & \textcolor[HTML]{4285f4}{30.01\%} & \textcolor[HTML]{4285f4}{**31.93\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.98\%} & \textcolor[HTML]{4285f4}{34.23\%} & \textcolor[HTML]{4285f4}{33.49\%} & \textcolor[HTML]{4285f4}{23.82\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-30.19\%} & \textcolor[HTML]{4285f4}{-6.3\%} & \textcolor[HTML]{4285f4}{30.58\%} & \textcolor[HTML]{4285f4}{-4.88\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{41.22\%} & \textcolor[HTML]{4285f4}{31.2\%} & \textcolor[HTML]{4285f4}{38.71\%} & \textcolor[HTML]{4285f4}{26.8\%}\\
+\textbf{Platinum (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{12.93\%} & \textcolor[HTML]{4285f4}{10.56\%} & \textcolor[HTML]{4285f4}{7.29\%} & \textcolor[HTML]{4285f4}{-7.92\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.62\%} & \textcolor[HTML]{4285f4}{22.66\%} & \textcolor[HTML]{4285f4}{25.53\%} & \textcolor[HTML]{4285f4}{19.48\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**29.46\%} & \textcolor[HTML]{4285f4}{*25.07\%} & \textcolor[HTML]{4285f4}{10.46\%} & \textcolor[HTML]{4285f4}{1.17\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.1\%} & \textcolor[HTML]{4285f4}{22.51\%} & \textcolor[HTML]{4285f4}{21.24\%} & \textcolor[HTML]{4285f4}{18.04\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-3.22\%} & \textcolor[HTML]{4285f4}{-3.81\%} & \textcolor[HTML]{4285f4}{8.04\%} & \textcolor[HTML]{4285f4}{-17.28\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23.12\%} & \textcolor[HTML]{4285f4}{22.81\%} & \textcolor[HTML]{4285f4}{28.75\%} & \textcolor[HTML]{4285f4}{20.8\%}\\
+\textbf{Silver (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{17.54\%} & \textcolor[HTML]{4285f4}{21.96\%} & \textcolor[HTML]{4285f4}{-2.43\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22\%} & \textcolor[HTML]{4285f4}{33.92\%} & \textcolor[HTML]{4285f4}{39.87\%} & \textcolor[HTML]{4285f4}{24.35\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.98\%} & \textcolor[HTML]{4285f4}{14.29\%} & \textcolor[HTML]{4285f4}{19.66\%} & \textcolor[HTML]{4285f4}{3.44\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.07\%} & \textcolor[HTML]{4285f4}{32.5\%} & \textcolor[HTML]{4285f4}{37.17\%} & \textcolor[HTML]{4285f4}{20.3\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.57\%} & \textcolor[HTML]{4285f4}{20.83\%} & \textcolor[HTML]{4285f4}{26.77\%} & \textcolor[HTML]{4285f4}{-8.09\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.93\%} & \textcolor[HTML]{4285f4}{35.34\%} & \textcolor[HTML]{4285f4}{42.44\%} & \textcolor[HTML]{4285f4}{27.77\%}\\
+\textbf{Aluminium (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.13\%} & \textcolor[HTML]{4285f4}{13.78\%} & \textcolor[HTML]{4285f4}{-3.58\%} & \textcolor[HTML]{4285f4}{3.15\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.6\%} & \textcolor[HTML]{4285f4}{26.41\%} & \textcolor[HTML]{4285f4}{26.48\%} & \textcolor[HTML]{4285f4}{18.56\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.56\%} & \textcolor[HTML]{4285f4}{14.78\%} & \textcolor[HTML]{4285f4}{16.25\%} & \textcolor[HTML]{4285f4}{**23.68\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.82\%} & \textcolor[HTML]{4285f4}{25.57\%} & \textcolor[HTML]{4285f4}{24.94\%} & \textcolor[HTML]{4285f4}{18.94\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.38\%} & \textcolor[HTML]{4285f4}{12.86\%} & \textcolor[HTML]{4285f4}{-23.04\%} & \textcolor[HTML]{4285f4}{-16.74\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.13\%} & \textcolor[HTML]{4285f4}{27.29\%} & \textcolor[HTML]{4285f4}{28.01\%} & \textcolor[HTML]{4285f4}{18.23\%}\\
+\addlinespace
+\textbf{Copper (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.45\%} & \textcolor[HTML]{4285f4}{**28.59\%} & \textcolor[HTML]{4285f4}{5.74\%} & \textcolor[HTML]{4285f4}{0.03\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.25\%} & \textcolor[HTML]{4285f4}{31.09\%} & \textcolor[HTML]{4285f4}{34.27\%} & \textcolor[HTML]{4285f4}{18.92\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.54\%} & \textcolor[HTML]{4285f4}{25.22\%} & \textcolor[HTML]{4285f4}{18.66\%} & \textcolor[HTML]{4285f4}{11.99\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.98\%} & \textcolor[HTML]{4285f4}{29.01\%} & \textcolor[HTML]{4285f4}{25.53\%} & \textcolor[HTML]{4285f4}{17.92\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.95\%} & \textcolor[HTML]{4285f4}{32\%} & \textcolor[HTML]{4285f4}{-6.78\%} & \textcolor[HTML]{4285f4}{-11.89\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.41\%} & \textcolor[HTML]{4285f4}{32.98\%} & \textcolor[HTML]{4285f4}{41.31\%} & \textcolor[HTML]{4285f4}{19.86\%}\\
+\textbf{Lead (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.83\%} & \textcolor[HTML]{4285f4}{28.99\%} & \textcolor[HTML]{4285f4}{10.74\%} & \textcolor[HTML]{4285f4}{2.07\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.64\%} & \textcolor[HTML]{4285f4}{41.74\%} & \textcolor[HTML]{4285f4}{41.05\%} & \textcolor[HTML]{4285f4}{23.26\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{7.59\%} & \textcolor[HTML]{4285f4}{11.21\%} & \textcolor[HTML]{4285f4}{9.87\%} & \textcolor[HTML]{4285f4}{17.05\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.16\%} & \textcolor[HTML]{4285f4}{39.91\%} & \textcolor[HTML]{4285f4}{35.35\%} & \textcolor[HTML]{4285f4}{23.37\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.09\%} & \textcolor[HTML]{4285f4}{*46.48\%} & \textcolor[HTML]{4285f4}{12.65\%} & \textcolor[HTML]{4285f4}{-13.41\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.12\%} & \textcolor[HTML]{4285f4}{43.16\%} & \textcolor[HTML]{4285f4}{46.22\%} & \textcolor[HTML]{4285f4}{23.09\%}\\
+\textbf{Nickel (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{19.31\%} & \textcolor[HTML]{4285f4}{12.5\%} & \textcolor[HTML]{4285f4}{3.52\%} & \textcolor[HTML]{4285f4}{0.31\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.26\%} & \textcolor[HTML]{4285f4}{44.27\%} & \textcolor[HTML]{4285f4}{41.45\%} & \textcolor[HTML]{4285f4}{28.98\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{23.25\%} & \textcolor[HTML]{4285f4}{-39.24\%} & \textcolor[HTML]{4285f4}{16.3\%} & \textcolor[HTML]{4285f4}{**35.09\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.23\%} & \textcolor[HTML]{4285f4}{41.62\%} & \textcolor[HTML]{4285f4}{34.48\%} & \textcolor[HTML]{4285f4}{29.13\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{15.46\%} & \textcolor[HTML]{4285f4}{**63.47\%} & \textcolor[HTML]{4285f4}{-7.67\%} & \textcolor[HTML]{4285f4}{**-34.64\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.28\%} & \textcolor[HTML]{4285f4}{46.72\%} & \textcolor[HTML]{4285f4}{47.44\%} & \textcolor[HTML]{4285f4}{28.6\%}\\
+\textbf{Tin (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.07\%} & \textcolor[HTML]{4285f4}{*29.1\%} & \textcolor[HTML]{4285f4}{7.46\%} & \textcolor[HTML]{4285f4}{1.68\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.38\%} & \textcolor[HTML]{4285f4}{31.71\%} & \textcolor[HTML]{4285f4}{35.61\%} & \textcolor[HTML]{4285f4}{18.79\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{*15.83\%} & \textcolor[HTML]{4285f4}{34.62\%} & \textcolor[HTML]{4285f4}{23.7\%} & \textcolor[HTML]{4285f4}{4.48\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.99\%} & \textcolor[HTML]{4285f4}{31.4\%} & \textcolor[HTML]{4285f4}{29.09\%} & \textcolor[HTML]{4285f4}{15.27\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-7.78\%} & \textcolor[HTML]{4285f4}{23.88\%} & \textcolor[HTML]{4285f4}{-6.82\%} & \textcolor[HTML]{4285f4}{-1.69\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.77\%} & \textcolor[HTML]{4285f4}{32.08\%} & \textcolor[HTML]{4285f4}{41.13\%} & \textcolor[HTML]{4285f4}{21.68\%}\\
+\textbf{Zinc (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.52\%} & \textcolor[HTML]{4285f4}{20.13\%} & \textcolor[HTML]{4285f4}{7.62\%} & \textcolor[HTML]{4285f4}{9.07\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.73\%} & \textcolor[HTML]{4285f4}{38.77\%} & \textcolor[HTML]{4285f4}{36.17\%} & \textcolor[HTML]{4285f4}{23.25\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-9.06\%} & \textcolor[HTML]{4285f4}{2.95\%} & \textcolor[HTML]{4285f4}{10.05\%} & \textcolor[HTML]{4285f4}{**29.42\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.15\%} & \textcolor[HTML]{4285f4}{36.86\%} & \textcolor[HTML]{4285f4}{33.28\%} & \textcolor[HTML]{4285f4}{22.12\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.13\%} & \textcolor[HTML]{4285f4}{37.11\%} & \textcolor[HTML]{4285f4}{5.43\%} & \textcolor[HTML]{4285f4}{-11.31\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.38\%} & \textcolor[HTML]{4285f4}{40.51\%} & \textcolor[HTML]{4285f4}{39.03\%} & \textcolor[HTML]{4285f4}{24.32\%}\\
+\addlinespace
+\textbf{US commodities} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{*6.89\%} & \textcolor[HTML]{4285f4}{**15.89\%} & \textcolor[HTML]{4285f4}{9.39\%} & \textcolor[HTML]{4285f4}{-0.18\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{10\%} & \textcolor[HTML]{4285f4}{13.62\%} & \textcolor[HTML]{4285f4}{17.58\%} & \textcolor[HTML]{4285f4}{9.86\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{***15.44\%} & \textcolor[HTML]{4285f4}{*15.66\%} & \textcolor[HTML]{4285f4}{13.4\%} & \textcolor[HTML]{4285f4}{6.82\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{9.88\%} & \textcolor[HTML]{4285f4}{14.21\%} & \textcolor[HTML]{4285f4}{14.83\%} & \textcolor[HTML]{4285f4}{8.59\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-1.09\%} & \textcolor[HTML]{4285f4}{*16.16\%} & \textcolor[HTML]{4285f4}{4.9\%} & \textcolor[HTML]{4285f4}{-6.33\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{10.09\%} & \textcolor[HTML]{4285f4}{13.05\%} & \textcolor[HTML]{4285f4}{19.98\%} & \textcolor[HTML]{4285f4}{10.95\%}\\
+\textbf{GB commodities} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.47\%} & \textcolor[HTML]{4285f4}{*21.77\%} & \textcolor[HTML]{4285f4}{5.25\%} & \textcolor[HTML]{4285f4}{2.72\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.66\%} & \textcolor[HTML]{4285f4}{26.91\%} & \textcolor[HTML]{4285f4}{30.24\%} & \textcolor[HTML]{4285f4}{16.19\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.41\%} & \textcolor[HTML]{4285f4}{8.01\%} & \textcolor[HTML]{4285f4}{15.06\%} & \textcolor[HTML]{4285f4}{**19.95\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.39\%} & \textcolor[HTML]{4285f4}{25.92\%} & \textcolor[HTML]{4285f4}{25.94\%} & \textcolor[HTML]{4285f4}{15.13\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.34\%} & \textcolor[HTML]{4285f4}{*35.56\%} & \textcolor[HTML]{4285f4}{-5.24\%} & \textcolor[HTML]{4285f4}{-14.05\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.87\%} & \textcolor[HTML]{4285f4}{27.88\%} & \textcolor[HTML]{4285f4}{34.06\%} & \textcolor[HTML]{4285f4}{17.1\%}\\
 \bottomrule
@@
 \midrule
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{34.26\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{34.26\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{89.69\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.01\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{91.01\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{47.46\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{40.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{40.83\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{34} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{57.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{57.39\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.02\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{38.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Oats (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{38.12\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{33} ***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{35.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{35.29\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{8} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.66\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.66\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{32} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{82.72\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{82.72\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{66.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{66.39\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{81.2\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{81.2\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.83\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.57\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{56.57\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{31} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{75.13\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{75.13\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.31\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{31.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{31.59\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{81.72\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{92.18\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{92.18\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.2\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{18.64\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.64\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{30} ***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{69.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{69.59\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.36\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{48.92\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybeans (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{48.92\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{17.18\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{38.74\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{38.74\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{7} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{57.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{57.61\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{29} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{37.95\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.95\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.05\%} & \textcolor[HTML]{4285f4}{*}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{44.86\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Wheat-SRW (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{44.86\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.79\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{83.21\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{83.21\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{6} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{76.2\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{76.2\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.81\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.81\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{94.9\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{76.82\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{76.82\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.34\%} & \textcolor[HTML]{4285f4}{*}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{6.35\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.35\%} & \textcolor[HTML]{4285f4}{*}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{62.38\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{99.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{99.19\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{28} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{50.04\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{50.04\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{5} ***}\\
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{51.11\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cattle-live (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.11\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{15.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{51.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.61\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{20.96\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{82.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{82.12\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{63.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{63.19\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{4} ***}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{45.71\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lean hogs (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{45.71\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{24.77\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{55.51\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{55.51\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{3} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{68.46\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{68.46\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{21.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{21.55\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{6.81\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{99.36\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Cocoa (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{99.36\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{12.33\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.85\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.85\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{7.73\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{42.98\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{42.98\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{27} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{51.48\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{51.48\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.17\%} & \textcolor[HTML]{4285f4}{**}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{53.38\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Coffee-C (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{53.38\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{69.3\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{69.3\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.63\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{95.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{95.23\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{82.84\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{35.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{35.39\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{52.86\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{6.02\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.02\%} & \textcolor[HTML]{4285f4}{*}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{41.38\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.06\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{59.06\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{26.81\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{14.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{14.44\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{33.04\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{32.06\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{32.06\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.67\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{\cellcolor{gray!10}{Lumber-random length (XCME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{37.56\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lumber (XCME)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.56\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{75.67\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{84.3\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{84.3\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.36\%} & \textcolor[HTML]{4285f4}{**}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{28.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{28.12\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{22.82\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{4.31\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.31\%} & \textcolor[HTML]{4285f4}{**}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{26} ***}\\
-\textbf{\cellcolor{gray!10}{Orange juice-frozen concentrated (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{66.85\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Orange juice (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{66.85\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{28.81\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{28.81\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{92.47\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{67.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.55\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{25} ***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{25.72\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{25.72\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.01\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{24.1\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{24.1\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.76\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{75.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{75.29\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.89\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{56.23\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.08\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.08\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.22\%} & \textcolor[HTML]{4285f4}{*}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{4.66\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{Natural gas (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.66\%} & \textcolor[HTML]{4285f4}{**}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.01\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{68.1\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{68.1\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{24} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.28\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.28\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{23} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{67.04\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.04\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.08\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{38.33\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{38.33\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{22} ***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{61.91\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{61.91\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{49.38\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{95.55\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{95.55\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{21} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{18.99\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.99\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{20} ***}\\
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{18.96\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Gasoline (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.96\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{66.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{58.35\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{58.35\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.58\%} & \textcolor[HTML]{4285f4}{***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{49.08\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{49.08\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{19} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{34.23\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.23\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{18} ***}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{21.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Heating oil (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{21.83\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.45\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{99.52\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{99.52\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.52\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{23.31\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{23.31\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{17} ***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{15.71\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{15.71\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{16} ***}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{90.64\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Copper (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{90.64\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{17.88\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{74.37\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{74.37\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.71\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{55.78\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{55.78\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{15} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{17.19\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{17.19\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{43.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Gold (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{43.44\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{96.63\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.63\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.92\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{60.22\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{60.22\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{14} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{56.58\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{56.58\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{13} ***}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.77\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{***}}\\
+\textbf{Palladium (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.77\%} & \textcolor[HTML]{4285f4}{***}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{12} ***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{30.26\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{30.26\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.38\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{96.05\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.05\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{9.4\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{9.4\%} & \textcolor[HTML]{4285f4}{*}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{6.08\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{Platinum (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.08\%} & \textcolor[HTML]{4285f4}{*}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{14.41\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{14.41\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.86\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{85.5\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{85.5\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{11} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{27.26\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{27.26\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{96.07\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Silver (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.07\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.09\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{88.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{88.44\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.01\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{87.12\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.12\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.08\%} & \textcolor[HTML]{4285f4}{***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{61.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{61.83\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{10} ***}\\
-\textbf{\cellcolor{gray!10}{Aluminium-primary (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{86.1\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Aluminium (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{86.1\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{9} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.59\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.33\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{10.79\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{10.79\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.41\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.33\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.33\%} & \textcolor[HTML]{4285f4}{**}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{25.99\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{88.51\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Copper (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{88.51\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{87.59\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.59\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.15\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{43.61\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{43.61\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{8} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{16.36\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{16.36\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{Lead-refined pig (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{58.96\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lead (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{58.96\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.81\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{40.11\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{40.11\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.11\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.17\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.17\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{7} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{15.62\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{15.62\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{85.45\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{76.56\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Nickel (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{76.56\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.04\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.24\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{1.24\%} & \textcolor[HTML]{4285f4}{**}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.62\%} & \textcolor[HTML]{4285f4}{***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{49.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{49.29\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{6} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.46\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{***}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.46\%} & \textcolor[HTML]{4285f4}{***}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{69.15\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{5.22\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{Tin (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.22\%} & \textcolor[HTML]{4285f4}{*}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{14.94\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{70.17\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{70.17\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{58.14\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{34.29\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.29\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{5} ***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{73.44\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{73.44\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{4} ***}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{59.39\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Zinc (XLME)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.39\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.75\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{37.67\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.67\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.29\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{91.89\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.89\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{5.05\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{*}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.05\%} & \textcolor[HTML]{4285f4}{*}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{1.77\%} & \textcolor[HTML]{4285f4}{**}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{3.63\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{US commodities} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{3.63\%} & \textcolor[HTML]{4285f4}{**}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{54.29\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{93.09\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{93.09\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.22\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{58.92\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{58.92\%} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{3} ***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{11.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{11.83\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{past}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{78.74\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{GB commodities} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{78.74\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{financialisation}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{27.95\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{27.95\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.65\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{46.83\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{46.83\%} & \textcolor[HTML]{4285f4}{}\\
 \textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{post-crisis}} & \textbf{\cellcolor{gray!10}{mean}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{1.37\%}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{**}}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.37\%} & \textcolor[HTML]{4285f4}{**}\\
 \addlinespace
@@
 \midrule
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.17\%}}}\\
+\textbf{Δ\% commodity CHP} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{20.72\%}} & \textcolor[HTML]{4285f4}{\textbf{22.46\%}} & \textcolor[HTML]{4285f4}{\textbf{27.17\%}}\\
 \textbf{} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.19\%}} & \textcolor[HTML]{4285f4}{\textbf{21.6\%}} & \textcolor[HTML]{4285f4}{\textbf{23.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.12\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.24\%}}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{33.18\%}} & \textcolor[HTML]{4285f4}{\textbf{27.86\%}} & \textcolor[HTML]{4285f4}{\textbf{29.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.24\%}}\\
 \textbf{} & \textbf{} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{6.23\%}} & \textcolor[HTML]{4285f4}{\textbf{10.53\%}} & \textcolor[HTML]{4285f4}{\textbf{6.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.88\%}}}\\
+\textbf{} & \textbf{} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{26.68\%}} & \textcolor[HTML]{4285f4}{\textbf{20.89\%}} & \textcolor[HTML]{4285f4}{\textbf{27.19\%}} & \textcolor[HTML]{4285f4}{\textbf{31.88\%}}\\
 \addlinespace
 \textbf{} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.12\%}} & \textcolor[HTML]{4285f4}{\textbf{19.45\%}} & \textcolor[HTML]{4285f4}{\textbf{16\%}} & \textcolor[HTML]{4285f4}{\textbf{10.96\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
+\textbf{} & \textbf{} & \textbf{gas} & \textcolor[HTML]{4285f4}{\textbf{19.69\%}} & \textcolor[HTML]{4285f4}{\textbf{15.65\%}} & \textcolor[HTML]{4285f4}{\textbf{7.36\%}} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}}\\
 \textbf{} & \textbf{} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{18.87\%}} & \textcolor[HTML]{4285f4}{\textbf{12.85\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.32\%}}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{28.12\%}} & \textcolor[HTML]{4285f4}{\textbf{19.1\%}} & \textcolor[HTML]{4285f4}{\textbf{23.27\%}} & \textcolor[HTML]{4285f4}{\textbf{37.32\%}}\\
 \textbf{} & \textbf{} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{47.38\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}} & \textcolor[HTML]{4285f4}{\textbf{18.07\%}} & \textcolor[HTML]{4285f4}{\textbf{34.9\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.93\%}}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{23.3\%}} & \textcolor[HTML]{4285f4}{\textbf{17.41\%}} & \textcolor[HTML]{4285f4}{\textbf{24.57\%}} & \textcolor[HTML]{4285f4}{\textbf{37.93\%}}\\
 \textbf{Δ\% aggregate CHP} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{5.37\%}} & \textcolor[HTML]{4285f4}{\textbf{7.12\%}} & \textcolor[HTML]{4285f4}{\textbf{14.72\%}} & \textcolor[HTML]{4285f4}{\textbf{7.49\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.23\%}}}\\
+\textbf{} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{4.91\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{12.14\%}} & \textcolor[HTML]{4285f4}{\textbf{6.23\%}}\\
 \textbf{} & \textbf{} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{7.25\%}} & \textcolor[HTML]{4285f4}{\textbf{5.4\%}} & \textcolor[HTML]{4285f4}{\textbf{19.75\%}} & \textcolor[HTML]{4285f4}{\textbf{8.45\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{livestock}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.26\%}}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{1.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{0.52\%}} & \textcolor[HTML]{4285f4}{\textbf{0.26\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{5.64\%}} & \textcolor[HTML]{4285f4}{\textbf{10.35\%}} & \textcolor[HTML]{4285f4}{\textbf{6.98\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.45\%}}}\\
+\textbf{} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{3.35\%}} & \textcolor[HTML]{4285f4}{\textbf{6.27\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{2.45\%}}\\
 \textbf{} & \textbf{} & \textbf{gas} & \textcolor[HTML]{4285f4}{\textbf{2.65\%}} & \textcolor[HTML]{4285f4}{\textbf{2.58\%}} & \textcolor[HTML]{4285f4}{\textbf{2.6\%}} & \textcolor[HTML]{4285f4}{\textbf{0.27\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.17\%}}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{3.59\%}} & \textcolor[HTML]{4285f4}{\textbf{7.49\%}} & \textcolor[HTML]{4285f4}{\textbf{18.9\%}} & \textcolor[HTML]{4285f4}{\textbf{3.17\%}}\\
 \textbf{} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{8.36\%}} & \textcolor[HTML]{4285f4}{\textbf{15.67\%}} & \textcolor[HTML]{4285f4}{\textbf{22.37\%}} & \textcolor[HTML]{4285f4}{\textbf{15.33\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{base}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.67\%}}}\\
+\textbf{} & \textbf{} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{10.12\%}} & \textcolor[HTML]{4285f4}{\textbf{12.74\%}} & \textcolor[HTML]{4285f4}{\textbf{23.94\%}} & \textcolor[HTML]{4285f4}{\textbf{7.67\%}}\\
 \textbf{} & \textbf{} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{7.92\%}} & \textcolor[HTML]{4285f4}{\textbf{16.4\%}} & \textcolor[HTML]{4285f4}{\textbf{21.98\%}} & \textcolor[HTML]{4285f4}{\textbf{17.25\%}}\\
@@
 \midrule
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0737}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1638}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2849}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1282}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0737}} & \textcolor[HTML]{4285f4}{\textbf{0.1638}} & \textcolor[HTML]{4285f4}{\textbf{0.2849}} & \textcolor[HTML]{4285f4}{\textbf{0.1282}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0724}} & \textcolor[HTML]{4285f4}{\textbf{0.1790}} & \textcolor[HTML]{4285f4}{\textbf{0.2709}} & \textcolor[HTML]{4285f4}{\textbf{0.1001}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0748}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1501}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2985}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1495}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0748}} & \textcolor[HTML]{4285f4}{\textbf{0.1501}} & \textcolor[HTML]{4285f4}{\textbf{0.2985}} & \textcolor[HTML]{4285f4}{\textbf{0.1495}}\\
 \textbf{US} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0684}} & \textcolor[HTML]{4285f4}{\textbf{0.1545}} & \textcolor[HTML]{4285f4}{\textbf{0.2526}} & \textcolor[HTML]{4285f4}{\textbf{0.1096}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0642}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1697}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2323}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0859}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0642}} & \textcolor[HTML]{4285f4}{\textbf{0.1697}} & \textcolor[HTML]{4285f4}{\textbf{0.2323}} & \textcolor[HTML]{4285f4}{\textbf{0.0859}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0720}} & \textcolor[HTML]{4285f4}{\textbf{0.1402}} & \textcolor[HTML]{4285f4}{\textbf{0.2706}} & \textcolor[HTML]{4285f4}{\textbf{0.1268}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0910}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1305}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2322}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1075}}}\\
+\textbf{} & \textbf{agriculturals} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0910}} & \textcolor[HTML]{4285f4}{\textbf{0.1305}} & \textcolor[HTML]{4285f4}{\textbf{0.2322}} & \textcolor[HTML]{4285f4}{\textbf{0.1075}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0799}} & \textcolor[HTML]{4285f4}{\textbf{0.1421}} & \textcolor[HTML]{4285f4}{\textbf{0.1975}} & \textcolor[HTML]{4285f4}{\textbf{0.0955}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1018}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2611}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1186}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.1018}} & \textcolor[HTML]{4285f4}{\textbf{0.1184}} & \textcolor[HTML]{4285f4}{\textbf{0.2611}} & \textcolor[HTML]{4285f4}{\textbf{0.1186}}\\
 \textbf{} & \textbf{} & \textbf{grains} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4421}} & \textcolor[HTML]{4285f4}{\textbf{0.4898}} & \textcolor[HTML]{4285f4}{\textbf{0.5673}} & \textcolor[HTML]{4285f4}{\textbf{0.3728}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4312}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5283}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5749}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3289}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.4312}} & \textcolor[HTML]{4285f4}{\textbf{0.5283}} & \textcolor[HTML]{4285f4}{\textbf{0.5749}} & \textcolor[HTML]{4285f4}{\textbf{0.3289}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4570}} & \textcolor[HTML]{4285f4}{\textbf{0.4510}} & \textcolor[HTML]{4285f4}{\textbf{0.5675}} & \textcolor[HTML]{4285f4}{\textbf{0.4161}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3340}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2868}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3707}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3333}}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.3340}} & \textcolor[HTML]{4285f4}{\textbf{0.2868}} & \textcolor[HTML]{4285f4}{\textbf{0.3707}} & \textcolor[HTML]{4285f4}{\textbf{0.3333}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3053}} & \textcolor[HTML]{4285f4}{\textbf{0.2652}} & \textcolor[HTML]{4285f4}{\textbf{0.3906}} & \textcolor[HTML]{4285f4}{\textbf{0.3220}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3605}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3150}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3557}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3483}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.3605}} & \textcolor[HTML]{4285f4}{\textbf{0.3150}} & \textcolor[HTML]{4285f4}{\textbf{0.3557}} & \textcolor[HTML]{4285f4}{\textbf{0.3483}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{softs} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0391}} & \textcolor[HTML]{4285f4}{\textbf{0.0853}} & \textcolor[HTML]{4285f4}{\textbf{0.1584}} & \textcolor[HTML]{4285f4}{\textbf{0.0764}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0437}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0845}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1210}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0685}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0437}} & \textcolor[HTML]{4285f4}{\textbf{0.0845}} & \textcolor[HTML]{4285f4}{\textbf{0.1210}} & \textcolor[HTML]{4285f4}{\textbf{0.0685}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0334}} & \textcolor[HTML]{4285f4}{\textbf{0.0874}} & \textcolor[HTML]{4285f4}{\textbf{0.1937}} & \textcolor[HTML]{4285f4}{\textbf{0.0833}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4908}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5892}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4687}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4203}}}\\
+\textbf{} & \textbf{energy} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4908}} & \textcolor[HTML]{4285f4}{\textbf{0.5892}} & \textcolor[HTML]{4285f4}{\textbf{0.4687}} & \textcolor[HTML]{4285f4}{\textbf{0.4203}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.4844}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}} & \textcolor[HTML]{4285f4}{\textbf{0.4601}} & \textcolor[HTML]{4285f4}{\textbf{0.4179}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4957}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5869}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4779}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4210}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4957}} & \textcolor[HTML]{4285f4}{\textbf{0.5869}} & \textcolor[HTML]{4285f4}{\textbf{0.4779}} & \textcolor[HTML]{4285f4}{\textbf{0.4210}}\\
 \textbf{} & \textbf{} & \textbf{petroleum} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.7278}} & \textcolor[HTML]{4285f4}{\textbf{0.7846}} & \textcolor[HTML]{4285f4}{\textbf{0.7692}} & \textcolor[HTML]{4285f4}{\textbf{0.7175}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6962}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7854}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7282}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.6962}} & \textcolor[HTML]{4285f4}{\textbf{0.7854}} & \textcolor[HTML]{4285f4}{\textbf{0.7727}} & \textcolor[HTML]{4285f4}{\textbf{0.7282}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7606}} & \textcolor[HTML]{4285f4}{\textbf{0.7856}} & \textcolor[HTML]{4285f4}{\textbf{0.7716}} & \textcolor[HTML]{4285f4}{\textbf{0.7134}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2167}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5553}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4721}}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.2167}} & \textcolor[HTML]{4285f4}{\textbf{0.5553}} & \textcolor[HTML]{4285f4}{\textbf{0.5877}} & \textcolor[HTML]{4285f4}{\textbf{0.4721}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.2201}} & \textcolor[HTML]{4285f4}{\textbf{0.5418}} & \textcolor[HTML]{4285f4}{\textbf{0.6353}} & \textcolor[HTML]{4285f4}{\textbf{0.4155}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2145}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5709}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5035}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.2145}} & \textcolor[HTML]{4285f4}{\textbf{0.5727}} & \textcolor[HTML]{4285f4}{\textbf{0.5709}} & \textcolor[HTML]{4285f4}{\textbf{0.5035}}\\
 \textbf{} & \textbf{} & \textbf{precious} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.2883}} & \textcolor[HTML]{4285f4}{\textbf{0.6305}} & \textcolor[HTML]{4285f4}{\textbf{0.6704}} & \textcolor[HTML]{4285f4}{\textbf{0.5762}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3070}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6061}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6991}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5386}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3070}} & \textcolor[HTML]{4285f4}{\textbf{0.6061}} & \textcolor[HTML]{4285f4}{\textbf{0.6991}} & \textcolor[HTML]{4285f4}{\textbf{0.5386}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.6591}} & \textcolor[HTML]{4285f4}{\textbf{0.6615}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4047}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4691}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6536}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4412}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4047}} & \textcolor[HTML]{4285f4}{\textbf{0.4691}} & \textcolor[HTML]{4285f4}{\textbf{0.6536}} & \textcolor[HTML]{4285f4}{\textbf{0.4412}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3987}} & \textcolor[HTML]{4285f4}{\textbf{0.4753}} & \textcolor[HTML]{4285f4}{\textbf{0.6729}} & \textcolor[HTML]{4285f4}{\textbf{0.3954}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4108}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6456}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4797}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4108}} & \textcolor[HTML]{4285f4}{\textbf{0.4652}} & \textcolor[HTML]{4285f4}{\textbf{0.6456}} & \textcolor[HTML]{4285f4}{\textbf{0.4797}}\\
 \bottomrule
@@
 \midrule
-\textbf{\cellcolor{gray!10}{countries}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0053}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0024}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0024}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0028}}\\
+\textbf{countries} & \textbf{whole period} & \textcolor[HTML]{4285f4}{-0.0053} & \textcolor[HTML]{4285f4}{-0.0024} & \textcolor[HTML]{4285f4}{0.0024} & \textcolor[HTML]{4285f4}{-0.0028}\\
 \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.0157} & \textcolor[HTML]{4285f4}{-0.0041} & \textcolor[HTML]{4285f4}{0.0106} & \textcolor[HTML]{4285f4}{-0.0127}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0100}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0078}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0183}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{-0.0050}}\\
+\textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{-0.0100} & \textcolor[HTML]{4285f4}{0.0078} & \textcolor[HTML]{4285f4}{-0.0183} & \textcolor[HTML]{4285f4}{-0.0050}\\
 \textbf{sectors} & \textbf{whole period} & \textcolor[HTML]{4285f4}{0.0496} & \textcolor[HTML]{4285f4}{0.0073} & \textcolor[HTML]{4285f4}{0.0637} & \textcolor[HTML]{4285f4}{0.0116}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.1527}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0183}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.2099}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0902}}\\
+\textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.1527} & \textcolor[HTML]{4285f4}{0.0183} & \textcolor[HTML]{4285f4}{0.2099} & \textcolor[HTML]{4285f4}{0.0902}\\
 \addlinespace
 \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.0223} & \textcolor[HTML]{4285f4}{0.0240} & \textcolor[HTML]{4285f4}{-0.0141} & \textcolor[HTML]{4285f4}{0.0024}\\
-\textbf{\cellcolor{gray!10}{subsectors}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0421}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0631}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0799}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0778}}\\
+\textbf{subsectors} & \textbf{whole period} & \textcolor[HTML]{4285f4}{0.0421} & \textcolor[HTML]{4285f4}{0.0631} & \textcolor[HTML]{4285f4}{0.0799} & \textcolor[HTML]{4285f4}{0.0778}\\
 \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.1166} & \textcolor[HTML]{4285f4}{0.0201} & \textcolor[HTML]{4285f4}{0.0633} & \textcolor[HTML]{4285f4}{0.0727}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0297}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.1164}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0889}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{0.0812}}\\
+\textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.0297} & \textcolor[HTML]{4285f4}{0.1164} & \textcolor[HTML]{4285f4}{0.0889} & \textcolor[HTML]{4285f4}{0.0812}\\
 \bottomrule
@@
 \midrule
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0401}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0812}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0822}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0401}} & \textcolor[HTML]{4285f4}{\textbf{0.0812}} & \textcolor[HTML]{4285f4}{\textbf{0.0822}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0652}} & \textcolor[HTML]{4285f4}{\textbf{0.0719}} & \textcolor[HTML]{4285f4}{\textbf{0.0796}} & \textcolor[HTML]{4285f4}{\textbf{0.0848}} & \textcolor[HTML]{4285f4}{\textbf{0.1242}} & \textcolor[HTML]{4285f4}{\textbf{0.1247}} & \textcolor[HTML]{4285f4}{\textbf{0.1650}} & \textcolor[HTML]{4285f4}{\textbf{0.1541}} & \textcolor[HTML]{4285f4}{\textbf{0.3334}} & \textcolor[HTML]{4285f4}{\textbf{0.2913}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2743}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2837}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2235}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1432}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1139}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1547}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1339}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0963}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1374}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2743}} & \textcolor[HTML]{4285f4}{\textbf{0.2837}} & \textcolor[HTML]{4285f4}{\textbf{0.2235}} & \textcolor[HTML]{4285f4}{\textbf{0.1432}} & \textcolor[HTML]{4285f4}{\textbf{0.1139}} & \textcolor[HTML]{4285f4}{\textbf{0.1547}} & \textcolor[HTML]{4285f4}{\textbf{0.1339}} & \textcolor[HTML]{4285f4}{\textbf{0.0963}} & \textcolor[HTML]{4285f4}{\textbf{0.1374}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
 \textbf{US} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0536}} & \textcolor[HTML]{4285f4}{\textbf{0.0811}} & \textcolor[HTML]{4285f4}{\textbf{0.0803}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0597}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0600}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0723}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1073}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1164}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1502}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1479}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3284}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2621}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0597}} & \textcolor[HTML]{4285f4}{\textbf{0.0652}} & \textcolor[HTML]{4285f4}{\textbf{0.0600}} & \textcolor[HTML]{4285f4}{\textbf{0.0723}} & \textcolor[HTML]{4285f4}{\textbf{0.1073}} & \textcolor[HTML]{4285f4}{\textbf{0.1164}} & \textcolor[HTML]{4285f4}{\textbf{0.1502}} & \textcolor[HTML]{4285f4}{\textbf{0.1479}} & \textcolor[HTML]{4285f4}{\textbf{0.3284}} & \textcolor[HTML]{4285f4}{\textbf{0.2621}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2275}} & \textcolor[HTML]{4285f4}{\textbf{0.2541}} & \textcolor[HTML]{4285f4}{\textbf{0.1850}} & \textcolor[HTML]{4285f4}{\textbf{0.1018}} & \textcolor[HTML]{4285f4}{\textbf{0.0986}} & \textcolor[HTML]{4285f4}{\textbf{0.1371}} & \textcolor[HTML]{4285f4}{\textbf{0.1064}} & \textcolor[HTML]{4285f4}{\textbf{0.0905}} & \textcolor[HTML]{4285f4}{\textbf{0.1197}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0827}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0916}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}}\\
+\textbf{} & \textbf{agriculturals} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0827}} & \textcolor[HTML]{4285f4}{\textbf{0.0916}} & \textcolor[HTML]{4285f4}{\textbf{0.1121}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0918}} & \textcolor[HTML]{4285f4}{\textbf{0.0967}} & \textcolor[HTML]{4285f4}{\textbf{0.0734}} & \textcolor[HTML]{4285f4}{\textbf{0.0827}} & \textcolor[HTML]{4285f4}{\textbf{0.1111}} & \textcolor[HTML]{4285f4}{\textbf{0.1090}} & \textcolor[HTML]{4285f4}{\textbf{0.1125}} & \textcolor[HTML]{4285f4}{\textbf{0.1131}} & \textcolor[HTML]{4285f4}{\textbf{0.3034}} & \textcolor[HTML]{4285f4}{\textbf{0.2507}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2038}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2304}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1583}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0716}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0846}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1360}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1148}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1181}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2038}} & \textcolor[HTML]{4285f4}{\textbf{0.2304}} & \textcolor[HTML]{4285f4}{\textbf{0.1583}} & \textcolor[HTML]{4285f4}{\textbf{0.0716}} & \textcolor[HTML]{4285f4}{\textbf{0.0846}} & \textcolor[HTML]{4285f4}{\textbf{0.1360}} & \textcolor[HTML]{4285f4}{\textbf{0.1121}} & \textcolor[HTML]{4285f4}{\textbf{0.1148}} & \textcolor[HTML]{4285f4}{\textbf{0.1181}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
 \textbf{} & \textbf{} & \textbf{grains} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.5243}} & \textcolor[HTML]{4285f4}{\textbf{0.4882}} & \textcolor[HTML]{4285f4}{\textbf{0.5650}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4870}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3851}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3402}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4473}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5335}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4594}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5040}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6325}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5681}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.4870}} & \textcolor[HTML]{4285f4}{\textbf{0.4337}} & \textcolor[HTML]{4285f4}{\textbf{0.3851}} & \textcolor[HTML]{4285f4}{\textbf{0.3402}} & \textcolor[HTML]{4285f4}{\textbf{0.4473}} & \textcolor[HTML]{4285f4}{\textbf{0.5335}} & \textcolor[HTML]{4285f4}{\textbf{0.4594}} & \textcolor[HTML]{4285f4}{\textbf{0.5040}} & \textcolor[HTML]{4285f4}{\textbf{0.6325}} & \textcolor[HTML]{4285f4}{\textbf{0.5681}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.5389}} & \textcolor[HTML]{4285f4}{\textbf{0.6424}} & \textcolor[HTML]{4285f4}{\textbf{0.5592}} & \textcolor[HTML]{4285f4}{\textbf{0.3199}} & \textcolor[HTML]{4285f4}{\textbf{0.3134}} & \textcolor[HTML]{4285f4}{\textbf{0.4390}} & \textcolor[HTML]{4285f4}{\textbf{0.3872}} & \textcolor[HTML]{4285f4}{\textbf{0.4123}} & \textcolor[HTML]{4285f4}{\textbf{0.3618}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2192}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3724}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3453}}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.2192}} & \textcolor[HTML]{4285f4}{\textbf{0.3724}} & \textcolor[HTML]{4285f4}{\textbf{0.3453}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.2762}} & \textcolor[HTML]{4285f4}{\textbf{0.3315}} & \textcolor[HTML]{4285f4}{\textbf{0.3243}} & \textcolor[HTML]{4285f4}{\textbf{0.3497}} & \textcolor[HTML]{4285f4}{\textbf{0.2937}} & \textcolor[HTML]{4285f4}{\textbf{0.4170}} & \textcolor[HTML]{4285f4}{\textbf{0.2784}} & \textcolor[HTML]{4285f4}{\textbf{0.2744}} & \textcolor[HTML]{4285f4}{\textbf{0.2822}} & \textcolor[HTML]{4285f4}{\textbf{0.3365}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3568}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4772}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3585}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1783}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3532}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4246}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3445}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2994}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.3568}} & \textcolor[HTML]{4285f4}{\textbf{0.4772}} & \textcolor[HTML]{4285f4}{\textbf{0.3585}} & \textcolor[HTML]{4285f4}{\textbf{0.1783}} & \textcolor[HTML]{4285f4}{\textbf{0.3532}} & \textcolor[HTML]{4285f4}{\textbf{0.4246}} & \textcolor[HTML]{4285f4}{\textbf{0.3445}} & \textcolor[HTML]{4285f4}{\textbf{0.2948}} & \textcolor[HTML]{4285f4}{\textbf{0.2994}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{softs} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{-0.0042}} & \textcolor[HTML]{4285f4}{\textbf{-0.0001}} & \textcolor[HTML]{4285f4}{\textbf{0.0128}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0603}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0289}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0470}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0807}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0577}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0624}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0765}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0485}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2484}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1710}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0603}} & \textcolor[HTML]{4285f4}{\textbf{0.0289}} & \textcolor[HTML]{4285f4}{\textbf{0.0470}} & \textcolor[HTML]{4285f4}{\textbf{0.0807}} & \textcolor[HTML]{4285f4}{\textbf{0.0577}} & \textcolor[HTML]{4285f4}{\textbf{0.0624}} & \textcolor[HTML]{4285f4}{\textbf{0.0765}} & \textcolor[HTML]{4285f4}{\textbf{0.0485}} & \textcolor[HTML]{4285f4}{\textbf{0.2484}} & \textcolor[HTML]{4285f4}{\textbf{0.1710}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.1273}} & \textcolor[HTML]{4285f4}{\textbf{0.1400}} & \textcolor[HTML]{4285f4}{\textbf{0.1038}} & \textcolor[HTML]{4285f4}{\textbf{0.0568}} & \textcolor[HTML]{4285f4}{\textbf{0.0413}} & \textcolor[HTML]{4285f4}{\textbf{0.0983}} & \textcolor[HTML]{4285f4}{\textbf{0.1280}} & \textcolor[HTML]{4285f4}{\textbf{0.0825}} & \textcolor[HTML]{4285f4}{\textbf{0.0565}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4060}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4552}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5256}}}\\
+\textbf{} & \textbf{energy} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.4060}} & \textcolor[HTML]{4285f4}{\textbf{0.4552}} & \textcolor[HTML]{4285f4}{\textbf{0.5256}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.4362}} & \textcolor[HTML]{4285f4}{\textbf{0.5186}} & \textcolor[HTML]{4285f4}{\textbf{0.5682}} & \textcolor[HTML]{4285f4}{\textbf{0.5248}} & \textcolor[HTML]{4285f4}{\textbf{0.6212}} & \textcolor[HTML]{4285f4}{\textbf{0.6402}} & \textcolor[HTML]{4285f4}{\textbf{0.5082}} & \textcolor[HTML]{4285f4}{\textbf{0.5530}} & \textcolor[HTML]{4285f4}{\textbf{0.6278}} & \textcolor[HTML]{4285f4}{\textbf{0.4840}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4549}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4752}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3796}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2889}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4103}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4282}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4442}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3890}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4270}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.4549}} & \textcolor[HTML]{4285f4}{\textbf{0.4752}} & \textcolor[HTML]{4285f4}{\textbf{0.3796}} & \textcolor[HTML]{4285f4}{\textbf{0.2889}} & \textcolor[HTML]{4285f4}{\textbf{0.4103}} & \textcolor[HTML]{4285f4}{\textbf{0.4282}} & \textcolor[HTML]{4285f4}{\textbf{0.4442}} & \textcolor[HTML]{4285f4}{\textbf{0.3890}} & \textcolor[HTML]{4285f4}{\textbf{0.4270}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
 \textbf{} & \textbf{} & \textbf{petroleum} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.7207}} & \textcolor[HTML]{4285f4}{\textbf{0.7946}} & \textcolor[HTML]{4285f4}{\textbf{0.8527}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7632}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8072}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8321}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7377}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7703}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7895}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7460}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.6122}} & \textcolor[HTML]{4285f4}{\textbf{0.7632}} & \textcolor[HTML]{4285f4}{\textbf{0.8072}} & \textcolor[HTML]{4285f4}{\textbf{0.6948}} & \textcolor[HTML]{4285f4}{\textbf{0.8321}} & \textcolor[HTML]{4285f4}{\textbf{0.7377}} & \textcolor[HTML]{4285f4}{\textbf{0.7703}} & \textcolor[HTML]{4285f4}{\textbf{0.7895}} & \textcolor[HTML]{4285f4}{\textbf{0.8184}} & \textcolor[HTML]{4285f4}{\textbf{0.7460}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.8835}} & \textcolor[HTML]{4285f4}{\textbf{0.7867}} & \textcolor[HTML]{4285f4}{\textbf{0.6692}} & \textcolor[HTML]{4285f4}{\textbf{0.6075}} & \textcolor[HTML]{4285f4}{\textbf{0.6710}} & \textcolor[HTML]{4285f4}{\textbf{0.7069}} & \textcolor[HTML]{4285f4}{\textbf{0.7547}} & \textcolor[HTML]{4285f4}{\textbf{0.6672}} & \textcolor[HTML]{4285f4}{\textbf{0.7786}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2296}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2449}}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.2296}} & \textcolor[HTML]{4285f4}{\textbf{0.2877}} & \textcolor[HTML]{4285f4}{\textbf{0.2449}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.1860}} & \textcolor[HTML]{4285f4}{\textbf{0.1832}} & \textcolor[HTML]{4285f4}{\textbf{0.1992}} & \textcolor[HTML]{4285f4}{\textbf{0.2290}} & \textcolor[HTML]{4285f4}{\textbf{0.4923}} & \textcolor[HTML]{4285f4}{\textbf{0.4480}} & \textcolor[HTML]{4285f4}{\textbf{0.6328}} & \textcolor[HTML]{4285f4}{\textbf{0.5426}} & \textcolor[HTML]{4285f4}{\textbf{0.5664}} & \textcolor[HTML]{4285f4}{\textbf{0.5547}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6297}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6458}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6649}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6160}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4531}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4850}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4269}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3584}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5259}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.6297}} & \textcolor[HTML]{4285f4}{\textbf{0.6458}} & \textcolor[HTML]{4285f4}{\textbf{0.6649}} & \textcolor[HTML]{4285f4}{\textbf{0.6160}} & \textcolor[HTML]{4285f4}{\textbf{0.4531}} & \textcolor[HTML]{4285f4}{\textbf{0.4850}} & \textcolor[HTML]{4285f4}{\textbf{0.4269}} & \textcolor[HTML]{4285f4}{\textbf{0.3584}} & \textcolor[HTML]{4285f4}{\textbf{0.5259}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
 \textbf{} & \textbf{} & \textbf{precious} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.3063}} & \textcolor[HTML]{4285f4}{\textbf{0.3451}} & \textcolor[HTML]{4285f4}{\textbf{0.3308}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2934}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3053}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2959}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5688}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6969}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6143}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6428}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6713}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.2934}} & \textcolor[HTML]{4285f4}{\textbf{0.2337}} & \textcolor[HTML]{4285f4}{\textbf{0.3053}} & \textcolor[HTML]{4285f4}{\textbf{0.2959}} & \textcolor[HTML]{4285f4}{\textbf{0.5688}} & \textcolor[HTML]{4285f4}{\textbf{0.5674}} & \textcolor[HTML]{4285f4}{\textbf{0.6969}} & \textcolor[HTML]{4285f4}{\textbf{0.6143}} & \textcolor[HTML]{4285f4}{\textbf{0.6428}} & \textcolor[HTML]{4285f4}{\textbf{0.6713}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.7004}} & \textcolor[HTML]{4285f4}{\textbf{0.7107}} & \textcolor[HTML]{4285f4}{\textbf{0.7089}} & \textcolor[HTML]{4285f4}{\textbf{0.6988}} & \textcolor[HTML]{4285f4}{\textbf{0.5620}} & \textcolor[HTML]{4285f4}{\textbf{0.6088}} & \textcolor[HTML]{4285f4}{\textbf{0.5652}} & \textcolor[HTML]{4285f4}{\textbf{0.4746}} & \textcolor[HTML]{4285f4}{\textbf{0.5716}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2289}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3601}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4487}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.2289}} & \textcolor[HTML]{4285f4}{\textbf{0.3601}} & \textcolor[HTML]{4285f4}{\textbf{0.4487}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.3550}} & \textcolor[HTML]{4285f4}{\textbf{0.4082}} & \textcolor[HTML]{4285f4}{\textbf{0.4775}} & \textcolor[HTML]{4285f4}{\textbf{0.5526}} & \textcolor[HTML]{4285f4}{\textbf{0.5068}} & \textcolor[HTML]{4285f4}{\textbf{0.4792}} & \textcolor[HTML]{4285f4}{\textbf{0.4340}} & \textcolor[HTML]{4285f4}{\textbf{0.4653}} & \textcolor[HTML]{4285f4}{\textbf{0.5795}} & \textcolor[HTML]{4285f4}{\textbf{0.6647}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6886}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6742}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6606}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4700}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5003}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4636}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3810}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3598}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.6886}} & \textcolor[HTML]{4285f4}{\textbf{0.6742}} & \textcolor[HTML]{4285f4}{\textbf{0.6122}} & \textcolor[HTML]{4285f4}{\textbf{0.6606}} & \textcolor[HTML]{4285f4}{\textbf{0.4700}} & \textcolor[HTML]{4285f4}{\textbf{0.5003}} & \textcolor[HTML]{4285f4}{\textbf{0.4636}} & \textcolor[HTML]{4285f4}{\textbf{0.3810}} & \textcolor[HTML]{4285f4}{\textbf{0.3598}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
 \bottomrule
@@
 \midrule
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8556}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9709}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0352}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9438}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.8556}} & \textcolor[HTML]{4285f4}{\textbf{0.9709}} & \textcolor[HTML]{4285f4}{\textbf{1.0352}} & \textcolor[HTML]{4285f4}{\textbf{0.9438}}\\
 \textbf{US} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.7706}} & \textcolor[HTML]{4285f4}{\textbf{0.7965}} & \textcolor[HTML]{4285f4}{\textbf{0.8535}} & \textcolor[HTML]{4285f4}{\textbf{0.8252}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9891}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1982}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0301}}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{0.9891}} & \textcolor[HTML]{4285f4}{\textbf{1.1982}} & \textcolor[HTML]{4285f4}{\textbf{1.1727}} & \textcolor[HTML]{4285f4}{\textbf{1.0301}}\\
 \textbf{} & \textbf{} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{0.4320}} & \textcolor[HTML]{4285f4}{\textbf{0.2059}} & \textcolor[HTML]{4285f4}{\textbf{0.3317}} & \textcolor[HTML]{4285f4}{\textbf{0.5484}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7213}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6900}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7953}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7589}}}\\
+\textbf{} & \textbf{} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{0.7213}} & \textcolor[HTML]{4285f4}{\textbf{0.6900}} & \textcolor[HTML]{4285f4}{\textbf{0.7953}} & \textcolor[HTML]{4285f4}{\textbf{0.7589}}\\
 \addlinespace
 \textbf{} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{2.3308}} & \textcolor[HTML]{4285f4}{\textbf{1.6106}} & \textcolor[HTML]{4285f4}{\textbf{1.3977}} & \textcolor[HTML]{4285f4}{\textbf{1.7639}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6992}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.7090}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0044}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2585}}}\\
+\textbf{} & \textbf{} & \textbf{gas} & \textcolor[HTML]{4285f4}{\textbf{2.6992}} & \textcolor[HTML]{4285f4}{\textbf{1.7090}} & \textcolor[HTML]{4285f4}{\textbf{1.0044}} & \textcolor[HTML]{4285f4}{\textbf{1.2585}}\\
 \textbf{} & \textbf{} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{2.2080}} & \textcolor[HTML]{4285f4}{\textbf{1.5778}} & \textcolor[HTML]{4285f4}{\textbf{1.5288}} & \textcolor[HTML]{4285f4}{\textbf{1.9324}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6320}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1252}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1212}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9131}}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.6320}} & \textcolor[HTML]{4285f4}{\textbf{1.1252}} & \textcolor[HTML]{4285f4}{\textbf{1.1212}} & \textcolor[HTML]{4285f4}{\textbf{0.9131}}\\
 \textbf{} & \textbf{} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{0.4902}} & \textcolor[HTML]{4285f4}{\textbf{1.1178}} & \textcolor[HTML]{4285f4}{\textbf{1.4140}} & \textcolor[HTML]{4285f4}{\textbf{0.8780}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1271}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0480}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9219}}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{0.6674}} & \textcolor[HTML]{4285f4}{\textbf{1.1271}} & \textcolor[HTML]{4285f4}{\textbf{1.0480}} & \textcolor[HTML]{4285f4}{\textbf{0.9219}}\\
 \textbf{GB} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.8520}} & \textcolor[HTML]{4285f4}{\textbf{1.1761}} & \textcolor[HTML]{4285f4}{\textbf{0.7192}}\\
@@
 
-\begin{landscape}\begingroup\fontsize{7}{9}\selectfont
+\begingroup\fontsize{7}{9}\selectfont
 
@@
 \midrule
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.73\%}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.69\%}} & \textcolor[HTML]{4285f4}{\textbf{19.7\%}} & \textcolor[HTML]{4285f4}{\textbf{31.3\%}} & \textcolor[HTML]{4285f4}{\textbf{14.73\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.44\%}} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{11.82\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.99\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{10.07\%}} & \textcolor[HTML]{4285f4}{\textbf{18.15\%}} & \textcolor[HTML]{4285f4}{\textbf{32.67\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.92\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.43\%}} & \textcolor[HTML]{4285f4}{\textbf{3.78\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.6\%}} & \textcolor[HTML]{4285f4}{\textbf{5.61\%}} & \textcolor[HTML]{4285f4}{\textbf{4\%}} & \textcolor[HTML]{4285f4}{\textbf{4.57\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{5.55\%}} & \textcolor[HTML]{4285f4}{\textbf{4.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.98\%}} & \textcolor[HTML]{4285f4}{\textbf{5.63\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.69\%}} & \textcolor[HTML]{4285f4}{\textbf{5.47\%}} & \textcolor[HTML]{4285f4}{\textbf{3.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.12\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.74\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{6.41\%}} & \textcolor[HTML]{4285f4}{\textbf{6.21\%}} & \textcolor[HTML]{4285f4}{\textbf{4.73\%}} & \textcolor[HTML]{4285f4}{\textbf{4.74\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{2.95\%}} & \textcolor[HTML]{4285f4}{\textbf{5.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.39\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.7\%}} & \textcolor[HTML]{4285f4}{\textbf{4.56\%}} & \textcolor[HTML]{4285f4}{\textbf{2.3\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{3.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.73\%}}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{21.7\%}} & \textcolor[HTML]{4285f4}{\textbf{30.69\%}} & \textcolor[HTML]{4285f4}{\textbf{15.73\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{11.26\%}} & \textcolor[HTML]{4285f4}{\textbf{23.68\%}} & \textcolor[HTML]{4285f4}{\textbf{28.95\%}} & \textcolor[HTML]{4285f4}{\textbf{13.12\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.66\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{12.22\%}} & \textcolor[HTML]{4285f4}{\textbf{19.97\%}} & \textcolor[HTML]{4285f4}{\textbf{32.48\%}} & \textcolor[HTML]{4285f4}{\textbf{17.66\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.38\%}} & \textcolor[HTML]{4285f4}{\textbf{5.8\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.54\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{3.19\%}} & \textcolor[HTML]{4285f4}{\textbf{5.94\%}} & \textcolor[HTML]{4285f4}{\textbf{4.72\%}} & \textcolor[HTML]{4285f4}{\textbf{5.54\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{6.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.14\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{7.45\%}} & \textcolor[HTML]{4285f4}{\textbf{6.95\%}} & \textcolor[HTML]{4285f4}{\textbf{4.57\%}} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.79\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{5\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.95\%}} & \textcolor[HTML]{4285f4}{\textbf{7.61\%}} & \textcolor[HTML]{4285f4}{\textbf{5.24\%}} & \textcolor[HTML]{4285f4}{\textbf{5.82\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{2.87\%}} & \textcolor[HTML]{4285f4}{\textbf{5.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.85\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.3\%}} & \textcolor[HTML]{4285f4}{\textbf{2.78\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}} & \textcolor[HTML]{4285f4}{\textbf{2.85\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{5.73\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.07\%}}}\\
+\textbf{} & \textbf{agriculturals} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.08\%}} & \textcolor[HTML]{4285f4}{\textbf{16.04\%}} & \textcolor[HTML]{4285f4}{\textbf{25.99\%}} & \textcolor[HTML]{4285f4}{\textbf{12.07\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.57\%}} & \textcolor[HTML]{4285f4}{\textbf{18.68\%}} & \textcolor[HTML]{4285f4}{\textbf{23.01\%}} & \textcolor[HTML]{4285f4}{\textbf{11.56\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.91\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{9.85\%}} & \textcolor[HTML]{4285f4}{\textbf{13.5\%}} & \textcolor[HTML]{4285f4}{\textbf{28.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.91\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.11\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.14\%}} & \textcolor[HTML]{4285f4}{\textbf{2.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{3.11\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}} & \textcolor[HTML]{4285f4}{\textbf{1.56\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{1.9\%}} & \textcolor[HTML]{4285f4}{\textbf{0.45\%}} & \textcolor[HTML]{4285f4}{\textbf{1\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.85\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.58\%}} & \textcolor[HTML]{4285f4}{\textbf{0.97\%}} & \textcolor[HTML]{4285f4}{\textbf{0.58\%}} & \textcolor[HTML]{4285f4}{\textbf{0.67\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.73\%}} & \textcolor[HTML]{4285f4}{\textbf{2.16\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.55\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.27\%}} & \textcolor[HTML]{4285f4}{\textbf{1.93\%}} & \textcolor[HTML]{4285f4}{\textbf{3.55\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.69\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.27\%}}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{16.44\%}} & \textcolor[HTML]{4285f4}{\textbf{29.28\%}} & \textcolor[HTML]{4285f4}{\textbf{42.09\%}} & \textcolor[HTML]{4285f4}{\textbf{19.27\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{14.54\%}} & \textcolor[HTML]{4285f4}{\textbf{34.68\%}} & \textcolor[HTML]{4285f4}{\textbf{38.84\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{44.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.71\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{18.73\%}} & \textcolor[HTML]{4285f4}{\textbf{23.95\%}} & \textcolor[HTML]{4285f4}{\textbf{44.4\%}} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{0.78\%}} & \textcolor[HTML]{4285f4}{\textbf{2.98\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.46\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.77\%}} & \textcolor[HTML]{4285f4}{\textbf{2.63\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{5.46\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.06\%}} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.04\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.22\%}} & \textcolor[HTML]{4285f4}{\textbf{4.18\%}} & \textcolor[HTML]{4285f4}{\textbf{0.67\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{7.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.5\%}} & \textcolor[HTML]{4285f4}{\textbf{3.8\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.24\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.3\%}} & \textcolor[HTML]{4285f4}{\textbf{1.92\%}} & \textcolor[HTML]{4285f4}{\textbf{0.69\%}} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}} & \textcolor[HTML]{4285f4}{\textbf{2.08\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.56\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.19\%}} & \textcolor[HTML]{4285f4}{\textbf{1.87\%}} & \textcolor[HTML]{4285f4}{\textbf{3.56\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.25\%}} & \textcolor[HTML]{4285f4}{\textbf{2.18\%}} & \textcolor[HTML]{4285f4}{\textbf{3.3\%}} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.84\%}}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.96\%}} & \textcolor[HTML]{4285f4}{\textbf{1.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.84\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{6.2\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{4.03\%}} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{11.26\%}} & \textcolor[HTML]{4285f4}{\textbf{5.94\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.63\%}} & \textcolor[HTML]{4285f4}{\textbf{2.06\%}} & \textcolor[HTML]{4285f4}{\textbf{3.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.94\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.95\%}} & \textcolor[HTML]{4285f4}{\textbf{2.94\%}} & \textcolor[HTML]{4285f4}{\textbf{3.54\%}} & \textcolor[HTML]{4285f4}{\textbf{1.94\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{1.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.71\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.3\%}} & \textcolor[HTML]{4285f4}{\textbf{0.19\%}} & \textcolor[HTML]{4285f4}{\textbf{0.28\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.47\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{1.43\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.48\%}}}\\
+\textbf{} & \textbf{} & \textbf{softs} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{4.78\%}} & \textcolor[HTML]{4285f4}{\textbf{9.9\%}} & \textcolor[HTML]{4285f4}{\textbf{18.39\%}} & \textcolor[HTML]{4285f4}{\textbf{8.48\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.82\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}} & \textcolor[HTML]{4285f4}{\textbf{15.58\%}} & \textcolor[HTML]{4285f4}{\textbf{8.44\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.6\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.87\%}} & \textcolor[HTML]{4285f4}{\textbf{9.02\%}} & \textcolor[HTML]{4285f4}{\textbf{21.64\%}} & \textcolor[HTML]{4285f4}{\textbf{8.6\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.11\%}} & \textcolor[HTML]{4285f4}{\textbf{2.07\%}} & \textcolor[HTML]{4285f4}{\textbf{1.49\%}} & \textcolor[HTML]{4285f4}{\textbf{1.35\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.29\%}} & \textcolor[HTML]{4285f4}{\textbf{0.28\%}} & \textcolor[HTML]{4285f4}{\textbf{0.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.28\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.51\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}} & \textcolor[HTML]{4285f4}{\textbf{0.9\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{0.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}} & \textcolor[HTML]{4285f4}{\textbf{0.3\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.41\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}} & \textcolor[HTML]{4285f4}{\textbf{2.42\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.08\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{2.25\%}} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.9\%}}}\\
+\textbf{} & \textbf{energy} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}} & \textcolor[HTML]{4285f4}{\textbf{31.57\%}} & \textcolor[HTML]{4285f4}{\textbf{38.94\%}} & \textcolor[HTML]{4285f4}{\textbf{25.9\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{26.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{33.74\%}} & \textcolor[HTML]{4285f4}{\textbf{20.94\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.77\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{26.84\%}} & \textcolor[HTML]{4285f4}{\textbf{31.47\%}} & \textcolor[HTML]{4285f4}{\textbf{42.16\%}} & \textcolor[HTML]{4285f4}{\textbf{28.77\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{3.5\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.68\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{12.81\%}} & \textcolor[HTML]{4285f4}{\textbf{1.01\%}} & \textcolor[HTML]{4285f4}{\textbf{2.97\%}} & \textcolor[HTML]{4285f4}{\textbf{5.68\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{5.95\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{7.91\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.67\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{40\%}} & \textcolor[HTML]{4285f4}{\textbf{33.46\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{38.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.93\%}} & \textcolor[HTML]{4285f4}{\textbf{17.59\%}} & \textcolor[HTML]{4285f4}{\textbf{22.07\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{41.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.13\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{41.02\%}} & \textcolor[HTML]{4285f4}{\textbf{40.42\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.99\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{1.86\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.4\%}} & \textcolor[HTML]{4285f4}{\textbf{3.75\%}} & \textcolor[HTML]{4285f4}{\textbf{4.93\%}} & \textcolor[HTML]{4285f4}{\textbf{3.4\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.16\%}} & \textcolor[HTML]{4285f4}{\textbf{2.76\%}} & \textcolor[HTML]{4285f4}{\textbf{5.88\%}} & \textcolor[HTML]{4285f4}{\textbf{1.26\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.86\%}}}\\
+\textbf{} & \textbf{} & \textbf{gas} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{19.37\%}} & \textcolor[HTML]{4285f4}{\textbf{18.38\%}} & \textcolor[HTML]{4285f4}{\textbf{10.88\%}} & \textcolor[HTML]{4285f4}{\textbf{7.86\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{21.36\%}} & \textcolor[HTML]{4285f4}{\textbf{17.54\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{7.17\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.96\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{17.12\%}} & \textcolor[HTML]{4285f4}{\textbf{20.07\%}} & \textcolor[HTML]{4285f4}{\textbf{9.92\%}} & \textcolor[HTML]{4285f4}{\textbf{7.96\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.62\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{16.2\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.3\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{10.16\%}} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{11.42\%}} & \textcolor[HTML]{4285f4}{\textbf{19.3\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.46\%}} & \textcolor[HTML]{4285f4}{\textbf{5.26\%}} & \textcolor[HTML]{4285f4}{\textbf{13.46\%}} & \textcolor[HTML]{4285f4}{\textbf{13.84\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.03\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{22.08\%}} & \textcolor[HTML]{4285f4}{\textbf{27.47\%}} & \textcolor[HTML]{4285f4}{\textbf{15.46\%}} & \textcolor[HTML]{4285f4}{\textbf{16.03\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{23.23\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{14.53\%}} & \textcolor[HTML]{4285f4}{\textbf{16.64\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.41\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{20.54\%}} & \textcolor[HTML]{4285f4}{\textbf{32.65\%}} & \textcolor[HTML]{4285f4}{\textbf{16.18\%}} & \textcolor[HTML]{4285f4}{\textbf{15.41\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{4.24\%}} & \textcolor[HTML]{4285f4}{\textbf{7.16\%}} & \textcolor[HTML]{4285f4}{\textbf{5.22\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.9\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.36\%}} & \textcolor[HTML]{4285f4}{\textbf{2.03\%}} & \textcolor[HTML]{4285f4}{\textbf{11.66\%}} & \textcolor[HTML]{4285f4}{\textbf{5.9\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.48\%}} & \textcolor[HTML]{4285f4}{\textbf{6.51\%}} & \textcolor[HTML]{4285f4}{\textbf{4.6\%}} & \textcolor[HTML]{4285f4}{\textbf{4.55\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{48.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.91\%}}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}} & \textcolor[HTML]{4285f4}{\textbf{35.97\%}} & \textcolor[HTML]{4285f4}{\textbf{48.3\%}} & \textcolor[HTML]{4285f4}{\textbf{31.91\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{27.65\%}} & \textcolor[HTML]{4285f4}{\textbf{37.22\%}} & \textcolor[HTML]{4285f4}{\textbf{40.79\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.71\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{30.08\%}} & \textcolor[HTML]{4285f4}{\textbf{35.26\%}} & \textcolor[HTML]{4285f4}{\textbf{52.9\%}} & \textcolor[HTML]{4285f4}{\textbf{35.71\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10.41\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.99\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{13.69\%}} & \textcolor[HTML]{4285f4}{\textbf{0.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.14\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.45\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}} & \textcolor[HTML]{4285f4}{\textbf{0.96\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{45.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.56\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{45.97\%}} & \textcolor[HTML]{4285f4}{\textbf{35.46\%}} & \textcolor[HTML]{4285f4}{\textbf{23.06\%}} & \textcolor[HTML]{4285f4}{\textbf{31.56\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{44.02\%}} & \textcolor[HTML]{4285f4}{\textbf{27.52\%}} & \textcolor[HTML]{4285f4}{\textbf{18.61\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{47.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{43.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.7\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{47.85\%}} & \textcolor[HTML]{4285f4}{\textbf{43.02\%}} & \textcolor[HTML]{4285f4}{\textbf{26.44\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.57\%}} & \textcolor[HTML]{4285f4}{\textbf{4.95\%}} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.74\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}} & \textcolor[HTML]{4285f4}{\textbf{2.68\%}} & \textcolor[HTML]{4285f4}{\textbf{2.56\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{6.3\%}} & \textcolor[HTML]{4285f4}{\textbf{0.16\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.58\%}}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{7.54\%}} & \textcolor[HTML]{4285f4}{\textbf{30.79\%}} & \textcolor[HTML]{4285f4}{\textbf{38.2\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.5\%}} & \textcolor[HTML]{4285f4}{\textbf{31.77\%}} & \textcolor[HTML]{4285f4}{\textbf{42.95\%}} & \textcolor[HTML]{4285f4}{\textbf{11.54\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.63\%}} & \textcolor[HTML]{4285f4}{\textbf{30.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{23\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.76\%}} & \textcolor[HTML]{4285f4}{\textbf{18.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.33\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.71\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.66\%}} & \textcolor[HTML]{4285f4}{\textbf{20.33\%}} & \textcolor[HTML]{4285f4}{\textbf{15.15\%}} & \textcolor[HTML]{4285f4}{\textbf{12.71\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{23.49\%}} & \textcolor[HTML]{4285f4}{\textbf{21.5\%}} & \textcolor[HTML]{4285f4}{\textbf{13.38\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.27\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.91\%}} & \textcolor[HTML]{4285f4}{\textbf{3.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.27\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{2.83\%}} & \textcolor[HTML]{4285f4}{\textbf{0.32\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{4.31\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.48\%}} & \textcolor[HTML]{4285f4}{\textbf{7.31\%}} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.33\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.5\%}} & \textcolor[HTML]{4285f4}{\textbf{6.51\%}} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{0.33\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.57\%}} & \textcolor[HTML]{4285f4}{\textbf{8.4\%}} & \textcolor[HTML]{4285f4}{\textbf{16.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{50.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.74\%}}}\\
+\textbf{} & \textbf{} & \textbf{base} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{23.13\%}} & \textcolor[HTML]{4285f4}{\textbf{50.77\%}} & \textcolor[HTML]{4285f4}{\textbf{19.74\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{4.96\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}} & \textcolor[HTML]{4285f4}{\textbf{48.58\%}} & \textcolor[HTML]{4285f4}{\textbf{10.15\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.5\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{5.66\%}} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{52.45\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{5.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.4\%}} & \textcolor[HTML]{4285f4}{\textbf{5.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{0.29\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}} & \textcolor[HTML]{4285f4}{\textbf{6.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.46\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.01\%}} & \textcolor[HTML]{4285f4}{\textbf{2.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.46\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{1.84\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.82\%}} & \textcolor[HTML]{4285f4}{\textbf{3.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.06\%}} & \textcolor[HTML]{4285f4}{\textbf{9.72\%}} & \textcolor[HTML]{4285f4}{\textbf{9.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.12\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}} & \textcolor[HTML]{4285f4}{\textbf{7.74\%}} & \textcolor[HTML]{4285f4}{\textbf{7.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.12\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{11.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.3\%}}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{8.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.7\%}} & \textcolor[HTML]{4285f4}{\textbf{35.06\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.13\%}} & \textcolor[HTML]{4285f4}{\textbf{33.37\%}} & \textcolor[HTML]{4285f4}{\textbf{41.54\%}} & \textcolor[HTML]{4285f4}{\textbf{11.89\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.88\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{8.12\%}} & \textcolor[HTML]{4285f4}{\textbf{32.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.88\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{25.76\%}} & \textcolor[HTML]{4285f4}{\textbf{23.19\%}} & \textcolor[HTML]{4285f4}{\textbf{15.84\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.81\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{24.12\%}} & \textcolor[HTML]{4285f4}{\textbf{18.46\%}} & \textcolor[HTML]{4285f4}{\textbf{15.81\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.86\%}} & \textcolor[HTML]{4285f4}{\textbf{27.76\%}} & \textcolor[HTML]{4285f4}{\textbf{26.82\%}} & \textcolor[HTML]{4285f4}{\textbf{16.5\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}} & \textcolor[HTML]{4285f4}{\textbf{3.9\%}} & \textcolor[HTML]{4285f4}{\textbf{0.22\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.56\%}} & \textcolor[HTML]{4285f4}{\textbf{0.68\%}} & \textcolor[HTML]{4285f4}{\textbf{3.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.21\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.71\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{4.53\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}} & \textcolor[HTML]{4285f4}{\textbf{6.71\%}} & \textcolor[HTML]{4285f4}{\textbf{16.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}} & \textcolor[HTML]{4285f4}{\textbf{6.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.69\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{4.46\%}} & \textcolor[HTML]{4285f4}{\textbf{7.58\%}} & \textcolor[HTML]{4285f4}{\textbf{17.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.31\%}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.75\%}}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.74\%}} & \textcolor[HTML]{4285f4}{\textbf{11.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.71\%}} & \textcolor[HTML]{4285f4}{\textbf{10.75\%}}\\
 \addlinespace
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{13.03\%}} & \textcolor[HTML]{4285f4}{\textbf{34.39\%}} & \textcolor[HTML]{4285f4}{\textbf{6.62\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.48\%}} & \textcolor[HTML]{4285f4}{\textbf{10.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.45\%}} & \textcolor[HTML]{4285f4}{\textbf{14.35\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.72\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}} & \textcolor[HTML]{4285f4}{\textbf{4.26\%}} & \textcolor[HTML]{4285f4}{\textbf{1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{0.72\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.42\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{0.42\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.59\%}} & \textcolor[HTML]{4285f4}{\textbf{2.7\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}}\\
 \textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.28\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
-\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.09\%}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.17\%}} & \textcolor[HTML]{4285f4}{\textbf{2.37\%}} & \textcolor[HTML]{4285f4}{\textbf{3.67\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
 \addlinespace
@@
 \endgroup{}
-\end{landscape}
+
+\restoregeometry
 
@@
 \midrule
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{grains}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{grains}\\
 \textbf{Oats (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybean meal (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \textbf{Soybean oil (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Soybeans (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{Wheat-SRW (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{livestock}}\\
+\textbf{Cattle-feeder (XCME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{livestock}\\
 \textbf{Cattle-live (XCME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lean hogs (XCME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \textbf{Cocoa (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{softs}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Coffee-C (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \textbf{Cotton-\#2 (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Orange juice-frozen concentrated (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \textbf{Sugar-\#11 (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lumber-random length (XCME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \addlinespace
 \textbf{Natural gas (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{energy} & \textcolor[HTML]{4285f4}{gas}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{petroleum}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{petroleum}\\
 \textbf{Gasoline (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Heating oil (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \textbf{Copper (XCEC)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
 \addlinespace
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{precious}}\\
+\textbf{Gold (XCEC)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{precious}\\
 \textbf{Silver (XCEC)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Palladium (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \textbf{Platinum (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{GB}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{base}}\\
+\textbf{Aluminium-primary (XLME)} & \textcolor[HTML]{4285f4}{GB} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
 \addlinespace
 \textbf{Copper (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Lead-refined pig (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \textbf{Nickel-primary (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{}}\\
+\textbf{Tin-refined (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \textbf{Zinc (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\

### 2024-12-04 docs/paper.qmd
Refactor
make_commodity_pool_tickers_dataframe() and cross correlations analysis

@@
 
-table_name <- "correlations - cross - periods"
+table_name <- "correlations - cross - US - periods"
 columns_to_collapse_rows_for <- c("portfolios", "regime")

### 2024-12-04 explore/scripts/revision-jfm/analysis.r

@@ -1,4 +1,4 @@
-pacman::p_load(finRes, magrittr)
+pacman::p_load(finRes)
 
 # load global variables ########################################################
 # load_global_variables()
@@ -67,27 +67,28 @@ correlations_inner_formatted <-
 commodity_pool_tickers <- make_commodity_pool_tickers_dataframe(
   commodity_futures_tickers, analysis = "correlations - cross"
 )
-#### raw ####
-correlations_cross_raw <- make_cross_correlations_for_ticker_combinations_dataframe(
+#### US ####
+##### raw ####
+correlations_cross_US_raw <- make_cross_US_correlations_for_ticker_combinations_dataframe(
   commodity_pool_tickers, commodity_futures_data, aggregate_CHP_regimes, period_dates
 )
 
-#### summary ####
-##### load raw dataset (optional) ####
-# path_correlations_cross_raw_file <- paste_forward_slash(results_directory_path, "correlations-cross-raw.rds")
-# correlations_cross_raw <- readr::read_rds(path_correlations_cross_raw_file)
+##### summary ####
+###### load raw dataset (optional) ####
+# path_correlations_cross_US_raw_file <- paste_forward_slash(results_directory_path, "correlations-cross-US-raw.rds")
+# correlations_cross_US_raw <- readr::read_rds(path_correlations_cross_US_raw_file)
 
-##### summarise ####
-correlations_cross_summary <- summarise_cross_correlations(correlations_cross_raw)
+###### summarise ####
+correlations_cross_US_summary <- summarise_cross_US_correlations(correlations_cross_US_raw)
 
-#### formatted ####
-##### load summary dataset (optional) ####
-path_correlations_cross_summary_file <-
-  paste_forward_slash(results_directory_path, "correlations-cross-summary.rds")
-correlations_cross_summary <- readr::read_rds(path_correlations_cross_summary_file)
+##### formatted ####
+###### load summary dataset (optional) ####
+# path_correlations_cross_US_summary_file <-
+#   paste_forward_slash(results_directory_path, "correlations-cross-US-summary.rds")
+# correlations_cross_US_summary <- readr::read_rds(path_correlations_cross_US_summary_file)
 
-##### format ####
-correlations_cross_formatted <- format_cross_correlations_summary(correlations_cross_summary)
+###### format ####
+correlations_cross_US_formatted <- format_cross_US_correlations_summary(correlations_cross_US_summary)
 
 
[…]

### 2024-12-04 explore/scripts/revision-jfm/functions.r

@@ -132,7 +132,7 @@ filter_commodity_futures_tickers <- function(
   tickers$ticker
 }
 
-make_US_commodity_pool_combinations_for_correlations_analysis <- function(){
+make_US_commodity_pool_combinations_for_correlations_inner_analysis <- function(){
   
   tibble::tibble(
     country = rep("US", 8L),
@@ -143,7 +143,7 @@ make_US_commodity_pool_combinations_for_correlations_analysis <- function(){
   )
 }
 
-make_US_commodity_pool_combinations_for_regressions_analysis <- function(){
+make_US_commodity_pool_combinations_for_correlations_cross_analysis <- function(){
   
   tibble::tibble(
     country = rep("US", 10L),
@@ -152,6 +152,10 @@ make_US_commodity_pool_combinations_for_regressions_analysis <- function(){
       "all", "grains", "livestock", "softs", "all", "gas", "petroleum", "all", "base", "precious"
       )
   )
+}
+
+make_US_commodity_pool_combinations_for_regressions_analysis <- function(){
+  make_US_commodity_pool_combinations_for_correlations_cross_analysis()
 }
 
 make_commodity_pool_tickers_dataframe_for_country_sectors_subsectors_combinations <- 
@@ -163,36 +167,112 @@ make_commodity_pool_tickers_dataframe_for_country_sectors_subsectors_combination
     )
 }
 
-make_commodity_pool_tickers_dataframe <- function(
-    all_tickers, analysis = c("correlations - inner", correlations - inner, "regressions")
-    ){
-  
-  all_all_all <- tibble::tibble(
-    country = "all", sector = "all", subsector = "all", 
-    tickers = list(filter_commodity_futures_tickers(all_tickers))
-    )
-  
-  US_all_all <- tibble::tibble(
-    country = "US", sector = "all", subsector = "all", 
-    tickers = list(filter_commodity_futures_tickers(all_tickers, "US"))
+make_commodity_pool_tickers_dataframe_entry <- function(country, sector, subsector, tickers){
+  tibble::tibble(
+    country = country, sector = sector, subsector = subsector, tickers = list(tickers)
   )
+}
 
-  US_combinations <- if(analysis == "correlations - inner"){
-    make_US_commodity_pool_combinations_for_correlations_analysis()
-  } else {
-    make_US_commodity_pool_combinations_for_regressions_analysis()
-  }
[…]

### 2024-12-04 explore/scripts/revision-jfm/tables.r

@@ -278,12 +278,13 @@ correlations_inner_years <- dplyr::filter(
     )
 
 ## cross ####
-correlations_cross <- readr::read_rds(
-  slituR::paste_forward_slash(results_directory_path, "correlations-cross.rds")
+### US ####
+correlations_cross_US <- readr::read_rds(
+  slituR::paste_forward_slash(results_directory_path, "correlations-cross-US.rds")
 )
 
 ### By period ####
-correlations_cross_periods <- dplyr::filter(correlations_cross, timespan == "period") |>
+correlations_cross_US_periods <- dplyr::filter(correlations_cross_US, timespan == "period") |>
   tidyr::unnest(summary) |> dplyr::select(-timespan) |> 
   dplyr::mutate(
     portfolios = ifelse(pool == "country", "countries", paste0(pool, "s")),
@@ -297,7 +298,7 @@ correlations_cross_periods <- dplyr::filter(correlations_cross, timespan == "per
   tidyr::pivot_wider(names_from = "period", values_from = "average")
 
 ### By year ####
-correlations_cross_years <- dplyr::filter(correlations_cross, timespan == "year") |>
+correlations_cross_US_years <- dplyr::filter(correlations_cross_US, timespan == "year") |>
   tidyr::unnest(summary) |> dplyr::filter(regime == "whole period") |> 
   dplyr::mutate(
     portfolios = ifelse(pool == "country", "countries", paste0(pool, "s")),
@@ -443,8 +444,8 @@ tables <- tibble::tribble(
     "regressions - US returns ~ US CHP",        `US commodity returns ~ CHP`,
     "correlations - inner - periods",           correlations_inner_periods,
     "correlations - inner - years",             correlations_inner_years,
-    "correlations - cross - periods",           correlations_cross_periods,
-    "correlations - cross - years",             correlations_cross_years,
+    "correlations - cross - US - periods",      correlations_cross_US_periods,
+    "correlations - cross - US - years",        correlations_cross_US_years,
     "regressions - all returns ~ market index", `all commodity returns ~ market index`,
     "regressions - all returns ~ factors",      `all commodity returns ~ factors`,
     "assets taxonomy",                          `assets taxonomy`

### 2024-12-04 explore/scripts/revision-jfm/analysis.r
Refactor cross correlation analysis

@@ -64,10 +64,11 @@ correlations_inner_formatted <-
   format_inner_correlations_summary_statistics_into_table(correlations_inner_summary)
 
 ### cross ####
-commodity_pool_tickers <- make_commodity_pool_tickers_dataframe(
-  commodity_futures_tickers, analysis = "correlations - cross"
-)
 #### US ####
+commodity_pool_tickers <- make_commodity_pool_tickers_dataframe(
+  commodity_futures_tickers, analysis = "correlations - cross - US"
+)
+
 ##### raw ####
 correlations_cross_US_raw <- make_cross_US_correlations_for_ticker_combinations_dataframe(
   commodity_pool_tickers, commodity_futures_data, aggregate_CHP_regimes, period_dates
@@ -90,6 +91,15 @@ correlations_cross_US_summary <- summarise_cross_US_correlations(correlations_cr
 ###### format ####
 correlations_cross_US_formatted <- format_cross_US_correlations_summary(correlations_cross_US_summary)
 
+#### global ####
+commodity_pool_tickers <- make_commodity_pool_tickers_dataframe(
+  commodity_futures_tickers, analysis = "correlations - cross - global"
+)
+
+##### raw ####
+correlations_cross_global <- make_cross_US_correlations_for_ticker_combinations_dataframe(
+  commodity_pool_tickers, commodity_futures_data, aggregate_CHP_regimes, period_dates
+)
 
 ## regressions #################################################################
 commodity_pool_tickers <- make_commodity_pool_tickers_dataframe(

### 2024-12-04 explore/scripts/revision-jfm/functions.r
Update make_commodity_country_tickers_dataframe
for global cross correlation analysis

@@ -213,7 +213,7 @@ make_commodity_pool_tickers_dataframe_for_correlations_inner_analysis <- functio
   include_US_combinations_in_commodity_pool_tickers_dataframe_for_country_sectors_subsectors_combinations(skeleton, US_combinations)
 }
 
-make_commodity_pool_tickers_dataframe_for_correlations_cross_analysis <- function(all_tickers){
+make_commodity_pool_tickers_dataframe_for_correlations_cross_US_analysis <- function(all_tickers){
 
   skeleton <- make_commodity_pool_tickers_dataframe_skeleton_for_country_sectors_subsectors_combinations(all_tickers)
 
@@ -224,6 +224,62 @@ make_commodity_pool_tickers_dataframe_for_correlations_cross_analysis <- functio
     )
   
   include_US_combinations_in_commodity_pool_tickers_dataframe_for_country_sectors_subsectors_combinations(skeleton, US_combinations)
+}
+
+make_commodity_country_tickers_dataframe_for_correlations_cross_global_analysis <- function(all_tickers){
+  
+  US <- filter_commodity_futures_tickers(all_tickers, "US")
+  GB <- filter_commodity_futures_tickers(all_tickers, "GB")
+  tibble::tibble(portfolio = c("US", "GB"), tickers = list(US, GB))
+}
+
+make_commodity_sector_tickers_dataframe_for_correlations_cross_global_analysis <- function(all_tickers){
+  
+  agriculturals_US <- filter_commodity_futures_tickers(all_tickers, "US", "agriculturals")
+  energy_US <- filter_commodity_futures_tickers(all_tickers, "US", "energy")
+  metals_US <- filter_commodity_futures_tickers(all_tickers, "US", "metals")
+  metals_GB <- filter_commodity_futures_tickers(all_tickers, "GB", "metals")
+  
+  tibble::tibble(
+    portfolio = c("agriculturals (US)", "energy (US)", "metals (US)", "metals (GB)"),
+    tickers = list(agriculturals_US, energy_US, metals_US, metals_GB)
+    )
+}
+
+make_commodity_subsector_tickers_dataframe_for_correlations_cross_global_analysis <- function(all_tickers){
+  
+  grains_US <- filter_commodity_futures_tickers(all_tickers, "US", "agriculturals", "grains")
+  livestock_US <- filter_commodity_futures_tickers(all_tickers, "US", "agriculturals", "livestock")
[…]

### 2024-12-04 explore/scripts/revision-jfm/functions.r
Refactor
make_EW_portfolios_returns_for_ticker_combinations_dataframe to accommodate for global cross correlation analysis

@@ -278,7 +278,7 @@ make_commodity_pool_tickers_dataframe_for_correlations_cross_global_analysis <- 
 
   pool <- c(rep("countries", nrow(countries)), rep("sectors", nrow(sectors)), rep("subsectors", nrow(subsectors)))
   
-  dplyr::rbind(countries, sectors, subsectors) |> dplyr::mutate(pool = pool) |>
+  dplyr::bind_rows(countries, sectors, subsectors) |> dplyr::mutate(pool = pool) |>
     dplyr::select(pool, dplyr::everything())
 }
 
@@ -1148,13 +1148,17 @@ make_EW_portfolio_for_tickers <- function(tickers, commodity_futures_data){
 }
 
 make_EW_portfolios_returns_for_ticker_combinations_dataframe <- 
-  function(combinations, commodity_futures_data){
-
-    dplyr::group_by(combinations, country, sector, subsector) %>%
+  function(combinations, commodity_futures_data) {
+    
+    group_vars <- names(combinations) %>% setdiff("tickers")
+    
+    dplyr::group_by(combinations, dplyr::across(dplyr::all_of(group_vars))) %>%
       dplyr::mutate(
-        returns = purrr::map(tickers, ~make_EW_portfolio_for_tickers(., commodity_futures_data)), 
-      ) %>% dplyr::ungroup()
-  }
+        returns = purrr::map(tickers, ~make_EW_portfolio_for_tickers(., commodity_futures_data))
+      ) %>%
+      dplyr::ungroup()
+}
+
 
 extract_aggregate_CHP_regimes_by_timespan <- function(aggregate_CHP_regimes, timespan){
   dplyr::filter(aggregate_CHP_regimes, timespan == !!timespan) %>% 
@@ -1182,7 +1186,7 @@ make_cross_US_correlations_for_ticker_combinations_dataframe_by_period_no_regime
         dplyr::mutate(pool = rlang::as_string(group), regime = "whole period") %>%
         dplyr::relocate(pool, .before = 1L) %>% dplyr::relocate(regime, .after = period)
     })
-  }
+}
 
 make_cross_US_correlations_for_ticker_combinations_dataframe_by_period_regimes <-
   function(EW_portfolio_returns, aggregate_CHP_regimes_by_period){
@@ -1282,6 +1286,27 @@ make_cross_US_correlations_for_ticker_combinations_dataframe_by_year <-
   }
 
[…]

### 2024-12-05 explore/scripts/revision-jfm/functions.r
Compute raw global cross correlations

@@ -1188,102 +1188,193 @@ make_cross_US_correlations_for_ticker_combinations_dataframe_by_period_no_regime
     })
 }
 
+make_cross_global_correlations_for_ticker_combinations_dataframe_by_period_no_regimes <-
+  function(EW_portfolio_returns, period_dates){
+    
+  dplyr::select(EW_portfolio_returns, -tickers) |> tidyr::unnest(returns) |> 
+    dplyr::left_join(period_dates, by = "date") |> dplyr::filter(!is.na(period)) |>
+    dplyr::group_by(pool) |> tidyr::nest() |> 
+    dplyr::mutate(results = purrr::map(data, function(df){
+      tidyr::pivot_wider(df, names_from = portfolio, values_from = return) |>
+        dplyr::arrange(period, date) |> 
+        dplyr::filter(complete.cases(dplyr::across(dplyr::everything()))) |>
+        dplyr::group_by(period) |> tidyr::nest() |>
+        dplyr::mutate(results = purrr::map(data, compute_correlations)) |> dplyr::ungroup() |> 
+        dplyr::mutate(regime = "whole period") |> dplyr::relocate(regime, .after = period)
+    })) |> dplyr::ungroup() |> dplyr::select(-data) |> tidyr::unnest(results) 
+}
+
 make_cross_US_correlations_for_ticker_combinations_dataframe_by_period_regimes <-
   function(EW_portfolio_returns, aggregate_CHP_regimes_by_period){
     
-    groups <- c("country", "sector", "subsector")
-    purrr::map_df(groups, function(group){
-      
-      right_groups <- groups[match(group, groups):length(groups)][-1] 
-      
-      group <- rlang::ensym(group)
-      dplyr::select(EW_portfolio_returns, !!group, dplyr::all_of(right_groups), returns) %>% 
-        dplyr::filter(
-          !!group != "all" & dplyr::if_all(dplyr::all_of(right_groups), ~ . == "all") 
-        ) %>% dplyr::select(-dplyr::any_of(right_groups)) %>% tidyr::unnest(returns) %>%
-        dplyr::left_join(aggregate_CHP_regimes_by_period, by = "date") %>% 
-        dplyr::filter(!is.na(period)) %>%
-        tidyr::pivot_wider(names_from = group, values_from = return) %>%
-        dplyr::arrange(period, date) %>% dplyr::filter(complete.cases(.)) %>%
[…]

### 2024-12-12 explore/scripts/revision-jfm/functions.r
Limit yearly analysis to post 1996
for cross-correlations

@@ -1286,8 +1286,9 @@ make_cross_US_correlations_for_ticker_combinations_dataframe_by_year_no_regimes 
       ) %>% dplyr::select(-dplyr::any_of(right_groups)) %>% tidyr::unnest(returns) %>%
       tidyr::pivot_wider(names_from = group, values_from = return) %>%
       dplyr::arrange(date) %>% dplyr::filter(complete.cases(.)) %>%
-      dplyr::mutate(year = lubridate::year(date)) %>% dplyr::group_by(year) %>%
-      tidyr::nest() %>% dplyr::mutate(results = purrr::map(data, compute_correlations)) %>% 
+      dplyr::mutate(year = lubridate::year(date)) %>% dplyr::filter(year >= 1997L) %>%
+      dplyr::group_by(year) %>% tidyr::nest() %>% 
+        dplyr::mutate(results = purrr::map(data, compute_correlations)) %>% 
       dplyr::ungroup() %>% 
       dplyr::mutate(pool = rlang::as_string(group), regime = "whole period") %>%
       dplyr::relocate(pool, .before = 1L) %>% dplyr::relocate(regime, .after = year)
@@ -1303,7 +1304,8 @@ make_cross_global_correlations_for_ticker_combinations_dataframe_by_year_no_regi
       tidyr::pivot_wider(df, names_from = portfolio, values_from = return) |>
         dplyr::arrange(date) |> 
         dplyr::filter(complete.cases(dplyr::across(dplyr::everything()))) |>
-        dplyr::mutate(year = lubridate::year(date)) |> dplyr::group_by(year) |> 
+        dplyr::mutate(year = lubridate::year(date)) |> dplyr::filter(year >= 1997L) |> 
+        dplyr::group_by(year) |> 
         tidyr::nest() |> dplyr::mutate(results = purrr::map(data, compute_correlations)) |> 
         dplyr::ungroup() |> dplyr::mutate(regime = "whole period") |> 
         dplyr::relocate(regime, .after = year)

### 2024-12-12 explore/scripts/revision-jfm/tables.r
Refactor
to include table with all pools and sub-sectors separately, Only showing sub-sectors in the paper at the moment.

@@ -278,42 +278,88 @@ correlations_inner_years <- dplyr::filter(
     )
 
 ## cross ####
+format_correlations_cross_by_period <- function(correlations_cross){
+  
+  dplyr::filter(correlations_cross, timespan == "period") |>
+    tidyr::unnest(summary) |> dplyr::select(-timespan) |> 
+    dplyr::mutate(
+      portfolios = ifelse(
+        pool == "country", "countries", ifelse(stringr::str_ends(pool, "s"), pool, paste0(pool, "s"))
+      ),
+      regime = factor(regime, levels = regime_levels),
+      period = ifelse(period == "financialization", "financialisation", period),
+      period = ifelse(period == "present", "post-crisis", period),
+      period = factor(period, levels = period_levels)
+    ) |> dplyr::select(-pool) |> 
+    dplyr::relocate(portfolios, .before = 1L) |>
+    dplyr::arrange(portfolios, period, regime) |>
+    tidyr::pivot_wider(names_from = "period", values_from = "average")
+}
+
+format_correlations_cross_by_year <- function(correlations_cross){
+  
+  dplyr::filter(correlations_cross, timespan == "year") |>
+    tidyr::unnest(summary) |> dplyr::filter(regime == "whole period") |> 
+    dplyr::mutate(
+      portfolios = ifelse(
+        pool == "country", "countries", ifelse(stringr::str_ends(pool, "s"), pool, paste0(pool, "s"))
+      ),
+      decade = slituR::floor_year_to_nearest_decade(year),
+      year = slituR::remove_decade_from_year(year)
+    ) |>
+    dplyr::select(-c(timespan, regime, pool)) |> 
+    dplyr::arrange(portfolios, decade, year) |>
+    tidyr::pivot_wider(names_from = "year", values_from = "average") |>
+    dplyr::relocate(`0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, .after = dplyr::last_col()) |>
+    dplyr::mutate(
+      dplyr::across(c(`0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`), ~ format(.x, scientific = FALSE)),
+      dplyr::across(c(`0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`), ~ stringr::str_replace_all(.x, "    NA", ""))
+    )
+}
+
 ### US ####
 correlations_cross_US <- readr::read_rds(
[…]

### 2024-12-12 docs/paper.qmd
Update
to include only sub-sectors in cross correlation analysis.

--- 2024-12-04 docs/paper.qmd
@@
 For each period, the coefficients are also calculated and averaged independently over phases of low and high cross-sectional CHP.
-We further form equally weighted portfolios by country, by grouping together the US and GB traded assets independently, as well a
-by sector and sub-sector for the US traded assets.
-For each period we compute the correlation coefficient between the two country portfolios as well as the average pairwise correlation coefficients between the sector and sub-sector portfolios; these are computed over the entire period as well as over phases of low and high cross-sectional CHP.
+We further form equally weighted portfolios from the US traded commodity assets grouped by sub-sector.
+For each period we compute the average pairwise return correlation coefficients between these portfolios over the entire period as well as over phases of low and high cross-sectional CHP independently.
 This approach sheds light on the evolving interconnectedness among commodity assets as the complex transitions from traditional market dynamics---where commodity producers and speculators had distinct roles---to a more intricate landscape shaped by the influx of financial investors.
@@
 These results thus suggest that the US metals sector was the driving force behind increased average pairwise correlations during financialisation, a new observation to the best of our knowledge.
-The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods which indicates that increased commodity interdependence over financialisation was not a phase driven phenomenon in the same way that individual commodity returns are, as demonstrated in @tbl-stats-combined.
-We break down these average correlations by year in @tbl-correlations-inner-years.
+The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods.
+In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector.
+Although modest in magnitude, these exhibit a telling pattern, mirroring that shown by the individual commodity returns in @tbl-stats-combined, with a substantially higher average coefficient over **backwardation** phases in the first period (0.12 vs.
+0.03) and the pattern reversed over financilisation with an average coefficient substantially higher in **contango** (0.12 vs.
+0.02).
+We break down @tbl-correlations-inner-periods's average correlations by year in @tbl-correlations-inner-years.
 For the full sample of assets, the average pairwise correlations remain in the 0.06–0.08 range from 1998 through 2003, before suddenly increasing to 0.12 from 2003 to 2004.
@@
 
-The average pairwise correlation for the entire set of sample assets increases further to 0.28 (@tbl-correlations-inner-periods) indicating an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation.
-The result is consistent with the greater interdependence between equity and commodity markets over this period documented in @silvennoinen_financialisation_2013.
+The average pairwise return correlation for the entire set of sample assets increases further (up to 0.28: @tbl-correlations-inner-periods) and so does the average pairwise sub-sector portfolio correlation, albeit to a smaller level and in a smaller proportion (up to 0.08: @tbl-correlations-cross-periods).
+This indicates an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation consistent with the greater interdependence between equity and commodity markets over this period documented in @silvennoinen_financialisation_2013.
 The figure for the US traded section of the metals sector only progresses modestly to 0.59 after peaking at 0.63 in 2006 (@tbl-correlations-inner-years).
 In contrast, the GB traded assets see a sharp increase to over 0.65  starting in 2007 up to a peak of 0.69 in 2010, and so does the agricultural sector with the sharpest increase in 2008 when the average pairwise correlation for the sector jumps to 0.30.
-The energy sector also shows a substantial progression starting in 2007 and peaking at 0.63 in 2008 before levelling back down over the rest of the period.
+The energy sector also shows a substantial progression starting in 2007 and peaking at 0.63 in 2008 before leveling back down over the rest of the period.
 The onset of the financial crisis seems therefore to have had an across the board impact on the interdependence of commodities in contrast with financialisation, much more closely related to the metals sector.
@@
 
-The average pairwise correlations fall across the board, below the levels observed during financialisation, with the figure for the entire cross-section (@tbl-correlations-inner-periods) dropping down to 0.12 from 0.28 over the crisis.
-This substantial decline, that does not seem to have been widely noted, appears to begin in the latter part of the crisis period, around 2012 (@tbl-correlations-inner-years), before levelling down over the whole post-crisis period.
+While the average sub-sector portfolio return correlation remain stable (@tbl-correlations-cross-periods), the average individual asset pairwise correlations fall across the board, below the levels observed during financialisation, with the figure for the entire cross-section (@tbl-correlations-inner-periods) dropping down to 0.12 from 0.28 over the crisis.
+This substantial decline, that does not seem to have been widely noted, appears to begin in the latter part of the crisis period, around 2012 (@tbl-correlations-inner-years), before leveling down over the whole post-crisis period.
 
@@
 #| label: tbl-correlations-cross-periods
-#| tbl-cap: "This table shows the return pairwise correlation coefficients between two equally weighted country portfolios (US, GB) with the first formed from the twenty four US commodities and the second from the six GB traded assets.
-The table further shows the average return pairwise correlation coefficients between equally weighted US sector portfolios (agriculturals, energy, metals) as well as between equally weighted US sub-sector portfolios (agriculturals: gains, livestock, softs; energy: gas, petroleum; metals: base, precious).
+#| tbl-cap: "This table shows the average return pairwise correlation coefficients between equally weighted US sub-sector portfolios (agriculturals: gains, livestock, softs; energy: gas, petroleum; metals: base, precious).
 The results are independently calculated for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
@@
 
-table_name <- "correlations - cross - periods"
-columns_to_collapse_rows_for <- c("portfolios", "regime")
-colnames <- c("portfolios", "regime", periods)
-align <- make_series_of_repeated_chars(list(l = 1L, r = 5L))
+table_name <- "correlations - cross - US - periods - subsectors"
+columns_to_collapse_rows_for <- c("regime")
+colnames <- c("regime", periods)
+align <- make_series_of_repeated_chars(list(l = 1L, r = 4L))
 longtable <- TRUE
-bold_columns <- 1L:2L
-coloured_columns <- 3L:6L
+bold_columns <- 1L
+coloured_columns <- 2L:5L
 

### 2024-12-12 docs/paper.tex
Update
to include only sub-sectors in cross correlation analysis.

@@
 phases of low and high cross-sectional CHP. We further form equally
-weighted portfolios by country, by grouping together the US and GB
-traded assets independently, as well a by sector and sub-sector for the
-US traded assets. For each period we compute the correlation coefficient
-between the two country portfolios as well as the average pairwise
-correlation coefficients between the sector and sub-sector portfolios;
-these are computed over the entire period as well as over phases of low
-and high cross-sectional CHP.\\
+weighted portfolios from the US traded commodity assets grouped by
+sub-sector. For each period we compute the average pairwise return
+correlation coefficients between these portfolios over the entire period
+as well as over phases of low and high cross-sectional CHP
+independently.\\
 This approach sheds light on the evolving interconnectedness among
@@
 \textbf{backwardation} and \textbf{contango} for all the sectors and
-sub-sectors over the past and financialisation periods which indicates
-that increased commodity interdependence over financialisation was not a
-phase driven phenomenon in the same way that individual commodity
-returns are, as demonstrated in Table~\ref{tbl-stats-combined}.\\
-We break down these average correlations by year in
-Table~\ref{tbl-correlations-inner-years}. For the full sample of assets,
-the average pairwise correlations remain in the 0.06--0.08 range from
-1998 through 2003, before suddenly increasing to 0.12 from 2003 to 2004.
-This suggests 2004 as a distinct break point for the onset of
-financialisation, as noted in several studies
+sub-sectors over the past and financialisation periods. In this context,
+the ontological consequences of financialisation are better observed
+from an investment perspective as illustrated in
+Table~\ref{tbl-correlations-cross-periods} where we observe average
+pairwise correlation coefficients between equally weighted portfolios of
+US traded commodity assets grouped by sub-sector. Although modest in
+magnitude, these exhibit a telling pattern, mirroring that shown by the
+individual commodity returns in Table~\ref{tbl-stats-combined}, with a
+substantially higher average coefficient over \textbf{backwardation}
+phases in the first period (0.12 vs.~0.03) and the pattern reversed over
+financilisation with an average coefficient substantially higher in
+\textbf{contango} (0.12 vs.~0.02).\\
+We break down Table~\ref{tbl-correlations-inner-periods}'s average
+correlations by year in Table~\ref{tbl-correlations-inner-years}. For
+the full sample of assets, the average pairwise correlations remain in
+the 0.06--0.08 range from 1998 through 2003, before suddenly increasing
+to 0.12 from 2003 to 2004. This suggests 2004 as a distinct break point
+for the onset of financialisation, as noted in several studies
 \citep{baker_financialization_2021, tang_index_2012}. We further observe
@@
 
-The average pairwise correlation for the entire set of sample assets
-increases further to 0.28 (Table~\ref{tbl-correlations-inner-periods})
-indicating an intensification of the higher interdependence within the
-full cross-section of commodities prompted by financialisation. The
-result is consistent with the greater interdependence between equity and
-commodity markets over this period documented in
+The average pairwise return correlation for the entire set of sample
+assets increases further (up to 0.28:
+Table~\ref{tbl-correlations-inner-periods}) and so does the average
+pairwise sub-sector portfolio correlation, albeit to a smaller level and
+in a smaller proportion (up to 0.08:
+Table~\ref{tbl-correlations-cross-periods}). This indicates an
+intensification of the higher interdependence within the full
+cross-section of commodities prompted by financialisation consistent
+with the greater interdependence between equity and commodity markets
+over this period documented in
 \citet{silvennoinen_financialisation_2013}. The figure for the US traded
@@
 also shows a substantial progression starting in 2007 and peaking at
-0.63 in 2008 before levelling back down over the rest of the period. The
+0.63 in 2008 before leveling back down over the rest of the period. The
 onset of the financial crisis seems therefore to have had an across the
@@
 
-The average pairwise correlations fall across the board, below the
-levels observed during financialisation, with the figure for the entire
+While the average sub-sector portfolio return correlation remain stable
+(Table~\ref{tbl-correlations-cross-periods}), the average individual
+asset pairwise correlations fall across the board, below the levels
+observed during financialisation, with the figure for the entire
 cross-section (Table~\ref{tbl-correlations-inner-periods}) dropping down
@@
 of the crisis period, around 2012
-(Table~\ref{tbl-correlations-inner-years}), before levelling down over
+(Table~\ref{tbl-correlations-inner-years}), before leveling down over
 the whole post-crisis period.
@@
 
-\begin{longtable}[t]{>{}l>{}r>{}r>{}r>{}r>{}r}
+\begin{longtable}[t]{>{}l>{}r>{}r>{}r>{}r}
 
 \caption{\label{tbl-correlations-cross-periods}This table shows the
-return pairwise correlation coefficients between two equally weighted
-country portfolios (US, GB) with the first formed from the twenty four
-US commodities and the second from the six GB traded assets. The table
-further shows the average return pairwise correlation coefficients
-between equally weighted US sector portfolios (agriculturals, energy,
-metals) as well as between equally weighted US sub-sector portfolios
-(agriculturals: gains, livestock, softs; energy: gas, petroleum; metals:
-base, precious). The results are independently calculated for the four
-periods of interest (past: 1997-2003; financialisation: 2004-2008;
-crisis: 2008-2013; post-crisis: 2013-2018). For each period, the results
-are further calculated independently over the entire period as well as
-over phases of aggregate backwardation and contango. Aggregate CHP
-construction and corresponding regime definitions are discussed in
-Section~\ref{sec-methods} while the results are discussed in
-Section~\ref{sec-results} and the taxonomy for the commodity assets
-considered is detailed in Section~\ref{sec-taxonomy}.}
+average return pairwise correlation coefficients between equally
+weighted US sub-sector portfolios (agriculturals: gains, livestock,
+softs; energy: gas, petroleum; metals: base, precious). The results are
+independently calculated for the four periods of interest (past:
+1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
+2013-2018). For each period, the results are further calculated
+independently over the entire period as well as over phases of aggregate
+backwardation and contango. Aggregate CHP construction and corresponding
+regime definitions are discussed in Section~\ref{sec-methods} while the
+results are discussed in Section~\ref{sec-results} and the taxonomy for
+the commodity assets considered is detailed in
+Section~\ref{sec-taxonomy}.}
 
@@
 \toprule
-\textcolor{black}{\textbf{portfolios}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\textbf{countries} & \textbf{whole period} & \textcolor[HTML]{4285f4}{-0.0053} & \textcolor[HTML]{4285f4}{-0.0024} & \textcolor[HTML]{4285f4}{0.0024} & \textcolor[HTML]{4285f4}{-0.0028}\\
-\textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.0157} & \textcolor[HTML]{4285f4}{-0.0041} & \textcolor[HTML]{4285f4}{0.0106} & \textcolor[HTML]{4285f4}{-0.0127}\\
-\textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{-0.0100} & \textcolor[HTML]{4285f4}{0.0078} & \textcolor[HTML]{4285f4}{-0.0183} & \textcolor[HTML]{4285f4}{-0.0050}\\
-\textbf{sectors} & \textbf{whole period} & \textcolor[HTML]{4285f4}{0.0496} & \textcolor[HTML]{4285f4}{0.0073} & \textcolor[HTML]{4285f4}{0.0637} & \textcolor[HTML]{4285f4}{0.0116}\\
-\textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.1527} & \textcolor[HTML]{4285f4}{0.0183} & \textcolor[HTML]{4285f4}{0.2099} & \textcolor[HTML]{4285f4}{0.0902}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.0223} & \textcolor[HTML]{4285f4}{0.0240} & \textcolor[HTML]{4285f4}{-0.0141} & \textcolor[HTML]{4285f4}{0.0024}\\
-\textbf{subsectors} & \textbf{whole period} & \textcolor[HTML]{4285f4}{0.0421} & \textcolor[HTML]{4285f4}{0.0631} & \textcolor[HTML]{4285f4}{0.0799} & \textcolor[HTML]{4285f4}{0.0778}\\
-\textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.1166} & \textcolor[HTML]{4285f4}{0.0201} & \textcolor[HTML]{4285f4}{0.0633} & \textcolor[HTML]{4285f4}{0.0727}\\
-\textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.0297} & \textcolor[HTML]{4285f4}{0.1164} & \textcolor[HTML]{4285f4}{0.0889} & \textcolor[HTML]{4285f4}{0.0812}\\
+\textbf{whole period} & \textcolor[HTML]{4285f4}{0.0421} & \textcolor[HTML]{4285f4}{0.0631} & \textcolor[HTML]{4285f4}{0.0799} & \textcolor[HTML]{4285f4}{0.0778}\\
+\textbf{backwardation} & \textcolor[HTML]{4285f4}{0.1166} & \textcolor[HTML]{4285f4}{0.0201} & \textcolor[HTML]{4285f4}{0.0633} & \textcolor[HTML]{4285f4}{0.0727}\\
+\textbf{contango} & \textcolor[HTML]{4285f4}{0.0297} & \textcolor[HTML]{4285f4}{0.1164} & \textcolor[HTML]{4285f4}{0.0889} & \textcolor[HTML]{4285f4}{0.0812}\\
 \bottomrule

### 2025-01-07 paper.qmd
Deploying to gh-pages from @ bautheac/financialisation-co-movement@ad9b2b68b7faba85629ccca9fc9d0313b4da226c 🚀

@@
 ```{r}
-#| label: globals
+#| label: fetch
 #| include: false
-
-library(kableExtra); library(slituR)
-
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+#| cache: true
 
@@
 
-make_table <- function(table_name, colnames, align, bold_columns, coloured_columns){
-  get_results(tables, table_name) %>%
-  kbl(booktabs = T, longtable = T, col.names = colnames, align = align) %>%
-  kable_styling(latex_options = "striped", font_size = 7L) %>%
+make_table <- function(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns){
+  get_results(tables, table_name) %>% dplyr::mutate(dplyr::across(dplyr::where(is.factor), as.character)) %>%
+    collapse_rows(columns_to_collapse_rows_for) %>%
+    kbl(booktabs = T, longtable = longtable, col.names = colnames, align = align) %>%
+    kable_styling(latex_options = "basic", font_size = 7L) %>%
     row_spec(0L, bold = TRUE, color = "black") %>%
@@
 These correlation coefficients are then averaged across the entire cross-section of assets, as well as by country, sector, and sub-sector.
-For each period, the coefficients are also calculated and averaged across phases of low and high cross-sectional CHP.
-
+For each period, the coefficients are also calculated and averaged independently over phases of low and high cross-sectional CHP.
+We further form equally weighted portfolios from the US traded commodity assets grouped by sub-sector.
+For each period we compute the average pairwise return correlation coefficients between these portfolios over the entire period as well as over phases of low and high cross-sectional CHP independently.
 This approach sheds light on the evolving interconnectedness among commodity assets as the complex transitions from traditional market dynamics---where commodity producers and speculators had distinct roles---to a more intricate landscape shaped by the influx of financial investors.
@@
 These results thus suggest that the US metals sector was the driving force behind increased average pairwise correlations during financialisation, a new observation to the best of our knowledge.
-The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods which indicates that increased commodity interdependence over financialisation was not a phase driven phenomenon in the same way that individual commodity returns are, as demonstrated in @tbl-stats-combined.
-We break down these average correlations by years in @tbl-correlations-years.
+The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods.
+In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector.
+Although modest in magnitude, these exhibit a telling pattern, mirroring that shown by the individual commodity returns in @tbl-stats-combined, with a substantially higher average coefficient over **backwardation** phases in the first period (0.12 vs.
+0.03) and the pattern reversed over financilisation with an average coefficient substantially higher in **contango** (0.12 vs.
+0.02).
+We break down @tbl-correlations-inner-periods's average correlations by year in @tbl-correlations-inner-years.
 For the full sample of assets, the average pairwise correlations remain in the 0.06–0.08 range from 1998 through 2003, before suddenly increasing to 0.12 from 2003 to 2004.
@@
 
-The average pairwise correlation for the entire set of sample assets increases further to 0.28 (@tbl-correlations-periods) indicating an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation.
-The result is consistent with the greater interdependence between equity and commodity markets over this period documented in @silvennoinen_financialisation_2013.
-The figure for the US traded section of the metals sector only progresses modestly to 0.59 after peaking at 0.63 in 2006 (@tbl-correlations-years).
+The average pairwise return correlation for the entire set of sample assets increases further (up to 0.28: @tbl-correlations-inner-periods) and so does the average pairwise sub-sector portfolio correlation, albeit to a smaller level and in a smaller proportion (up to 0.08: @tbl-correlations-cross-periods).
+This indicates an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation consistent with the greater interdependence between equity and commodity markets over this period documented in @silvennoinen_financialisation_2013.
+The figure for the US traded section of the metals sector only progresses modestly to 0.59 after peaking at 0.63 in 2006 (@tbl-correlations-inner-years).
 In contrast, the GB traded assets see a sharp increase to over 0.65  starting in 2007 up to a peak of 0.69 in 2010, and so does the agricultural sector with the sharpest increase in 2008 when the average pairwise correlation for the sector jumps to 0.30.
-The energy sector also shows a substantial progression starting in 2007 and peaking at 0.63 in 2008 before levelling back down over the rest of the period.
+The energy sector also shows a substantial progression starting in 2007 and peaking at 0.63 in 2008 before leveling back down over the rest of the period.
 The onset of the financial crisis seems therefore to have had an across the board impact on the interdependence of commodities in contrast with financialisation, much more closely related to the metals sector.
@@
 
-The average pairwise correlations fall across the board, below the levels observed during financialisation, with the figure for the entire cross-section (@tbl-correlations-periods) dropping down to 0.12 from 0.28 over the crisis.
-This substantial decline, that does not seem to have been widely noted, appears to begin in the latter part of the crisis period, around 2012 (@tbl-correlations-years), before levelling down over the whole post-crisis period.
+While the average sub-sector portfolio return correlation remain stable (@tbl-correlations-cross-periods), the average individual asset pairwise correlations fall across the board, below the levels observed during financialisation, with the figure for the entire cross-section (@tbl-correlations-inner-periods) dropping down to 0.12 from 0.28 over the crisis.
+This substantial decline, that does not seem to have been widely noted, appears to begin in the latter part of the crisis period, around 2012 (@tbl-correlations-inner-years), before leveling down over the whole post-crisis period.
 
@@
 
+table_name <- "stats - combined"
+columns_to_collapse_rows_for <- c("asset", "regime")
 colnames <- c("asset", "regime", "estimate", periods)
 align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+longtable <- TRUE
+bold_columns <- 1L:3L
+coloured_columns <- 4L:7L
 
-make_table("stats - combined", colnames, align, 1L:7L, 4L:7L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```
@@
 
+table_name <- "regime difference tests"
+columns_to_collapse_rows_for <- c("asset", "period")
 colnames <- c("asset", "period", "moment", "dominant regime", "p-value", "significance")
 align <- make_series_of_repeated_chars(list(l = 4L, r = 2L))
+longtable <- TRUE
+bold_columns <- 1L:4L 
+coloured_columns <- 5L:6L
 
-make_table("regime difference tests", colnames, align, 1L:4L, 5L:6L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```
@@
 
+table_name <- "regressions - US returns ~ US CHP"
+columns_to_collapse_rows_for <- c("regressor", "sector")
 colnames <- c("regressor", "sector", "sub-sector", periods)
 align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+longtable <- TRUE
+bold_columns <- 1L:7L
+coloured_columns <- 4L:7L
 
-make_table("regressions - US returns ~ US CHP", colnames, align, 1L:7L, 4L:7L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```
@@
 
+table_name <- "correlations - inner - periods"
+columns_to_collapse_rows_for <- c("country", "sector", "subsector")
 colnames <- c(sectors, "regime", periods)
 align <- make_series_of_repeated_chars(list(l = 3L, r = 5L))
+longtable <- TRUE
+bold_columns <- 1L:8L 
+coloured_columns <- 5L:8L
 
-make_table("correlations - periods", colnames, align, 1L:8L, 5L:8L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```
@@
 ```{r}
-#| label: tbl-correlations-years
-#| tbl-cap: "This table shows the average return pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as across countries and commodity sectors and sub-sectors by year for the whole period of interest (1997-2018).
+#| label: tbl-correlations-cross-periods
+#| tbl-cap: "This table shows the average return pairwise correlation coefficients between equally weighted US sub-sector portfolios (agriculturals: gains, livestock, softs; energy: gas, petroleum; metals: base, precious).
+The results are independently calculated for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
+For each period, the results are further calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
+Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the taxonomy for the commodity assets considered is detailed in \\@sec-taxonomy."
+
+table_name <- "correlations - cross - US - periods - subsectors"
+columns_to_collapse_rows_for <- c("regime")
+colnames <- c("regime", periods)
+align <- make_series_of_repeated_chars(list(l = 1L, r = 4L))
+longtable <- TRUE
+bold_columns <- 1L
+coloured_columns <- 2L:5L
+
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
+```
+
+\newpage
+
+```{r}
+#| eval: false
+#| label: tbl-experimental
+#| tbl-cap: "lorem ipsum dolor sit amet consectetur adipiscing elit sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident sunt in culpa qui officia deserunt mollit anim id est laborum.
+Lorem ipsum dolor sit amet consectetur adipiscing elit sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident sunt in culpa qui officia deserunt mollit anim id est laborum."
+#| tbl-subcap: 
+#|     - "Average pairwise inner correlations"
+#|     - "Average pairwise cross correlations"
+#| layout-nrows: 2
+
+table1_format <- list(
+  table_name = "correlations - inner - periods",
+  columns_to_collapse_rows_for = c("country", "sector", "subsector"),
+  longtable = FALSE,
+  colnames = c(sectors, "regime", periods),
+  align = make_series_of_repeated_chars(list(l = 3L, r = 5L)),
+  bold_columns = 1L:8L, 
+  coloured_columns = 5L:8L
+  )
+table2_format <- list(
+  table_name = "correlations - cross - periods",
+  columns_to_collapse_rows_for = c("portfolios", "regime"),
+  longtable = TRUE,
+  colnames = c("portfolios", "regime", periods),
+  align = make_series_of_repeated_chars(list(l = 1L, r = 5L)),
+  bold_columns = 1L:2L, 
+  coloured_columns = 3L:6L
+)
+formats <- list(table1_format, table2_format)
+
+get_results(tables, table1_format$table_name) %>% dplyr::mutate(dplyr::across(dplyr::where(is.factor), as.character)) %>%
+    collapse_rows(table1_format$columns_to_collapse_rows_for) %>%
+    kable(booktabs = T, longtable = table1_format$longtable, col.names = table1_format$colnames, align = table1_format$align, escape = FALSE) %>%
+    kable_styling(font_size = 7L) %>%
+    row_spec(0L, bold = TRUE, color = "black") %>%
+    column_spec(table1_format$bold_columns, bold = TRUE) %>% column_spec(table1_format$coloured_columns, color = "#4285f4")
+
+get_results(tables, table2_format$table_name) %>% dplyr::mutate(dplyr::across(dplyr::where(is.factor), as.character)) %>%
+    collapse_rows(table2_format$columns_to_collapse_rows_for) %>%
+    kable(booktabs = T, longtable = table2_format$longtable, col.names = table2_format$colnames, align = table2_format$align, escape = FALSE) %>%
+    kable_styling(font_size = 7L) %>%
+    row_spec(0L, bold = TRUE, color = "black") %>%
+    column_spec(table2_format$bold_columns, bold = TRUE) %>% column_spec(table2_format$coloured_columns, color = "#4285f4")
+```
+
+\newpage
+
+```{r}
+#| label: tbl-correlations-inner-years
+#| tbl-cap: "While \\@tbl-correlations-inner-periods shows results calculated independently for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018), this stable shows the results of the same analysis calculated by year over the entire sample period (1997-2018).
 The results are discussed in \\@sec-results while \\@sec-taxonomy details the taxonomy for the commodity assets considered."
 
+table_name <- "correlations - inner - years"
+columns_to_collapse_rows_for <- c("country", "sector", "subsector")
 colnames <- c(sectors, "decade", 0L:9L)
 align <- make_series_of_repeated_chars(list(l = 4L, r = 10L))
+longtable <- TRUE
+bold_columns <- 1L:14L
+coloured_columns <- 5L:14L
 
-make_table("correlations - years", colnames, align, 1L:14L, 5L:14L) %>%
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns) %>%
   landscape()
@@
 
+table_name <- "regressions - all returns ~ market index"
+columns_to_collapse_rows_for <- c("country", "sector", "subsector")
 colnames <- c(sectors, periods)
 align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+longtable <- TRUE
+bold_columns <- 1L:7L
+coloured_columns <- 4L:7L
 
-make_table("regressions - all returns ~ market index", colnames, align, 1L:7L, 4L:7L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```
@@
 
+table_name <- "regressions - all returns ~ factors"
+columns_to_collapse_rows_for <- c("country", "sector", "subsector", "factor")
 colnames <- c(sectors, "factor", "regime", periods)
 align <- make_series_of_repeated_chars(list(l = 5L, r = 4L))
+longtable <- TRUE
+bold_columns <- 1L:9L
+coloured_columns <- 6L:9L
 
-make_table("regressions - all returns ~ factors", colnames, align, 1L:9L, 6L:9L) %>%
-  landscape()
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns) 
 ```
+
+\restoregeometry
 
@@
 
+table_name <- "assets taxonomy"
+columns_to_collapse_rows_for <- c("country", "sector", "subsector")
 colnames <- c("asset", "country", "sector", "sub-sector")
 align <- make_series_of_repeated_chars(list(l = 4L))
+longtable <- TRUE
+bold_columns <- 1L
+coloured_columns <- 2L:4L
 
-make_table("assets taxonomy", colnames, align, 1L, 2L:4L)
+make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
 ```

### 2025-01-07 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@ad9b2b68b7faba85629ccca9fc9d0313b4da226c 🚀

--- 2024-10-03 paper.tex
@@
 
-For each commodity asset we compute the weekly front futures return and
-commercial hedging pressure (CHP) time series with the CHP calculated as
-the ratio of the number of long commercial positions to the total number
-of commercial positions for the considered asset-week combination. For
-each asset-period combination we compute the average return and
-corresponding volatility over the entire period as well as over phases
-of cross-sectional low and high CHP\footnote{Aggregate CHP or
-  \textbf{CHP}: see below for a formal definition and description of the
-  phase construction process.}. These statistics are also computed for
-equally weighted portfolios of the US and GB traded commodity assets
-independently.
-
-For each period, the return series for the individual US-traded assets
-are regressed on both the relative change on their respective CHP series
-and that on the cross-sectional CHP independently. The resulting
-\(R^{2}\) values are then averaged by sector and subsector.
-Additionally, pairwise correlations are computed for each combination of
-assets across the periods of interest and for each individual year
-within the full sample period. These correlation coefficients are
-subsequently averaged across the entire cross-section of assets, as well
-as by country, sector, and subsector. For each period, the coefficients
-are also calculated and averaged across phases of low and high
-cross-sectional CHP.
-
+For each commodity asset we compute the daily and weekly front futures
+return as well as weekly commercial hedging pressure (CHP) time series
+with the CHP calculated as the ratio of the number of long commercial
+positions to the total number of commercial positions for the considered
+asset-week combination. For each asset-period combination we compute the
+average annual daily return and corresponding volatility over the entire
+period as well as over phases of cross-sectional low and high
+CHP\footnote{Aggregate CHP or \textbf{CHP}: see below for a formal
+  definition and description of the phase construction process.} and
+further test for significance in difference between the two regimes
+using t-tests for mean returns and F-test for corresponding variances.
+These statistics are also computed, and their difference between regimes
+tested, for equally weighted portfolios of the US and GB traded
+commodity assets independently.
+
+For each period, the weekly return series for the individual US-traded
+assets are regressed on both the relative change on their respective CHP
+series and that on the cross-sectional CHP independently. The resulting
+\(R^{2}\) values are then averaged by sector and sub-sector.
+Additionally, pairwise daily return correlations are computed for each
+combination of assets across the periods of interest and for each
+individual year within the full sample period. These correlation
+coefficients are then averaged across the entire cross-section of
+assets, as well as by country, sector, and sub-sector. For each period,
+the coefficients are also calculated and averaged independently over
+phases of low and high cross-sectional CHP. We further form equally
+weighted portfolios from the US traded commodity assets grouped by
+sub-sector. For each period we compute the average pairwise return
+correlation coefficients between these portfolios over the entire period
+as well as over phases of low and high cross-sectional CHP
+independently.\\
 This approach sheds light on the evolving interconnectedness among
@@
 investment it simultaneously influenced the entire spectrum of liquid
-commodities; this sweeping impact spurred the transformation of
-commodity markets from a collection of idiosyncratic markets into a
-unified asset class with interconnectedness emerging as a crucial aspect
-that warrants thorough examination.\\
-We strive to address this issue by first examining the average of weekly
-returns pairwise correlations between commodities across the entire
+commodities, eventually spurring the transformation of commodity markets
+from a collection of idiosyncratic markets into a more cohesive
+collection akin to an asset class. In this context, interconnectedness
+emerges as a crucial aspect that warrants thorough examination.\\
+We strive to address this issue by first examining the average returns
+pairwise correlations between commodities across the entire
 cross-section of the commodity assets considered in the study as well as
-by country, sector and sub-sector. Table~\ref{tbl-correlations-periods}
-shows the results for the four periods of interest with the results
-reported for the entire period as well as for periods of
-\textbf{backwardation} and \textbf{contango}. For the entire sample the
-average pairwise correlation jumps from 0.07 in the first period to 0.16
-over financialisation. This finding indicate higher interdependence
-within the full cross-section of commodities starting with the
-financialisation period, consistent with the empirical findings in
-\citet{fryMcKibbin_evolution_2023} and
+by country, sector and sub-sector.
+Table~\ref{tbl-correlations-inner-periods} shows the results for the
+four periods of interest with the results reported for the entire period
+as well as for periods of \textbf{backwardation} and \textbf{contango}.
+For the entire sample the average pairwise correlation jumps from 0.07
+in the first period to 0.16 over financialisation. This finding
+indicates higher interdependence within the full cross-section of
+commodities starting with the financialisation period, consistent with
+the empirical findings in \citet{fryMcKibbin_evolution_2023} and
 \citet{mayer_financialization_2017} as well as with the theoretical
@@
 \textbf{backwardation} and \textbf{contango} for all the sectors and
-sub-sectors over the past and financialisation periods which indicates
-that increased commodity interdependence over financialisation was not a
-phase driven phenomenon in the same way that individual commodity
-returns are, as demonstrated in Table~\ref{tbl-stats-combined}.\\
-We further examine these correlations by year in
-Table~\ref{tbl-correlations-years} to uncover any distinct breakpoints.
-For the full sample of assets, the average pairwise correlations
-increase from 0.08 to 0.12 from 2003 to 2004 seemingly driven by US
-metals average pairwise correlations, more than doubling from 0.22 to
-0.49, suggesting 2004 as the onset of financialization as noted in
-several studies \citep{baker_financialization_2021, tang_index_2012} and
-our contribution is to observe that the US metals sub-sector seems to
-have played a major role in this.
+sub-sectors over the past and financialisation periods. In this context,
+the ontological consequences of financialisation are better observed
+from an investment perspective as illustrated in
+Table~\ref{tbl-correlations-cross-periods} where we observe average
+pairwise correlation coefficients between equally weighted portfolios of
+US traded commodity assets grouped by sub-sector. Although modest in
+magnitude, these exhibit a telling pattern, mirroring that shown by the
+individual commodity returns in Table~\ref{tbl-stats-combined}, with a
+substantially higher average coefficient over \textbf{backwardation}
+phases in the first period (0.12 vs.~0.03) and the pattern reversed over
+financilisation with an average coefficient substantially higher in
+\textbf{contango} (0.12 vs.~0.02).\\
+We break down Table~\ref{tbl-correlations-inner-periods}'s average
+correlations by year in Table~\ref{tbl-correlations-inner-years}. For
+the full sample of assets, the average pairwise correlations remain in
+the 0.06--0.08 range from 1998 through 2003, before suddenly increasing
+to 0.12 from 2003 to 2004. This suggests 2004 as a distinct break point
+for the onset of financialisation, as noted in several studies
+\citep{baker_financialization_2021, tang_index_2012}. We further observe
+that the US metals appear to have played a major role in this as the
+increase seems driven by the sector which average pairwise correlation
+more than doubles (0.49 vs 0.22) over the period.
 
@@
 
-The average pairwise correlation for the entire set of sample assets
-increases further into the crisis to 0.28
-(Table~\ref{tbl-correlations-periods}) indicating an intensification of
-the higher interdependence within the full cross-section of commodities
-prompted by financialisation. The result is consistent with the greater
-interdependence between equity and commodity markets over this period
-documented in \citet{silvennoinen_financialisation_2013}. The figure for
-the US traded section of the metals sector only progresses modestly to
-0.59 after peaking at 0.63 in 2006 (Table~\ref{tbl-correlations-years}).
-In contrast, the GB traded assets see a sharp increase to over 0.65 in
-the crisis starting in 2007 up to a peak of 0.69 in 2010, and so does
-the agricultural sector with the sharpest increase in 2008 when the
-average pairwise correlation for the sector jumps to 0.30. The energy
-sector also shows a substantial progression starting in 2007 and peaking
-at 0.63 in 2008 before levelling back down over the rest of the period.
-The onset of the financial crisis seems therefore to have had an across
-the board impact on the interdependence of commodities in contrast with
+The average pairwise return correlation for the entire set of sample
+assets increases further (up to 0.28:
+Table~\ref{tbl-correlations-inner-periods}) and so does the average
+pairwise sub-sector portfolio correlation, albeit to a smaller level and
+in a smaller proportion (up to 0.08:
+Table~\ref{tbl-correlations-cross-periods}). This indicates an
+intensification of the higher interdependence within the full
+cross-section of commodities prompted by financialisation consistent
+with the greater interdependence between equity and commodity markets
+over this period documented in
+\citet{silvennoinen_financialisation_2013}. The figure for the US traded
+section of the metals sector only progresses modestly to 0.59 after
+peaking at 0.63 in 2006 (Table~\ref{tbl-correlations-inner-years}). In
+contrast, the GB traded assets see a sharp increase to over 0.65
+starting in 2007 up to a peak of 0.69 in 2010, and so does the
+agricultural sector with the sharpest increase in 2008 when the average
+pairwise correlation for the sector jumps to 0.30. The energy sector
+also shows a substantial progression starting in 2007 and peaking at
+0.63 in 2008 before leveling back down over the rest of the period. The
+onset of the financial crisis seems therefore to have had an across the
+board impact on the interdependence of commodities in contrast with
 financialisation, much more closely related to the metals sector.
@@
 
-The average pairwise correlations fall across the board in the
-post-crisis period, below the levels observed during financialisation,
-with the figure for the entire cross-section
-(Table~\ref{tbl-correlations-periods}) dropping down to 0.12 from 0.28
-over the crisis. This substantial decline, that does not appear to have
-been widely noted, appears to begin in the latter part of the crisis
-period, around 2012 (Table~\ref{tbl-correlations-years}), before
-levelling down over the whole post-crisis period.
+While the average sub-sector portfolio return correlation remain stable
+(Table~\ref{tbl-correlations-cross-periods}), the average individual
+asset pairwise correlations fall across the board, below the levels
+observed during financialisation, with the figure for the entire
+cross-section (Table~\ref{tbl-correlations-inner-periods}) dropping down
+to 0.12 from 0.28 over the crisis. This substantial decline, that does
+not seem to have been widely noted, appears to begin in the latter part
+of the crisis period, around 2012
+(Table~\ref{tbl-correlations-inner-years}), before leveling down over
+the whole post-crisis period.
 
@@
 have delivered an exogenous shock across the entire cross-section of
-liquid commodities and seem to have triggered a motion of reversion to
-legacy pre-financialisation fundamentals.
+liquid commodities which appears to have further altered the
+cross-sectional dynamics and eventually triggered a motion of reversion
+to legacy, pre-financialisation, fundamentals.
+
+\newgeometry{margin=.75in}
 
@@
 \midrule
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.74\%}}}\\
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.07\%}} & \textcolor[HTML]{4285f4}{\textbf{29.14\%}} & \textcolor[HTML]{4285f4}{\textbf{31.59\%}} & \textcolor[HTML]{4285f4}{\textbf{21\%}}\\
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.78\%}}}\\
-\addlinespace
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.17\%}}}\\
-\textbf{Oats (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.52\%}}}\\
-\addlinespace
-\textbf{Soybean meal (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.44\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.35\%}} & \textcolor[HTML]{4285f4}{\textbf{28.94\%}} & \textcolor[HTML]{4285f4}{\textbf{22.33\%}} & \textcolor[HTML]{4285f4}{\textbf{18.19\%}}\\
-\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.12\%}}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
-\addlinespace
-\textbf{Soybeans (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.45\%}}}\\
-\textbf{Soybeans (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.93\%}} & \textcolor[HTML]{4285f4}{\textbf{34.58\%}} & \textcolor[HTML]{4285f4}{\textbf{24.39\%}} & \textcolor[HTML]{4285f4}{\textbf{22.04\%}}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}}\\
-\textbf{Soybeans (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.09\%}} & \textcolor[HTML]{4285f4}{\textbf{24.74\%}} & \textcolor[HTML]{4285f4}{\textbf{31.11\%}} & \textcolor[HTML]{4285f4}{\textbf{20.56\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.44\%}}}\\
-\textbf{Wheat-SRW (XCBT)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{36\%}} & \textcolor[HTML]{4285f4}{\textbf{37.53\%}} & \textcolor[HTML]{4285f4}{\textbf{26.57\%}}\\
-\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.77\%}}}\\
-\addlinespace
-\textbf{Wheat-SRW (XCBT)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.04\%}} & \textcolor[HTML]{4285f4}{\textbf{29.84\%}} & \textcolor[HTML]{4285f4}{\textbf{37.73\%}} & \textcolor[HTML]{4285f4}{\textbf{26.72\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**20.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.58\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}} & \textcolor[HTML]{4285f4}{\textbf{14.93\%}} & \textcolor[HTML]{4285f4}{\textbf{13.39\%}} & \textcolor[HTML]{4285f4}{\textbf{20.14\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.12\%}}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.67\%}} & \textcolor[HTML]{4285f4}{\textbf{15.35\%}} & \textcolor[HTML]{4285f4}{\textbf{16.91\%}} & \textcolor[HTML]{4285f4}{\textbf{17.23\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}}\\
-\textbf{Cattle-live (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.07\%}}}\\
-\addlinespace
-\textbf{Cattle-live (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.65\%}} & \textcolor[HTML]{4285f4}{\textbf{17.91\%}} & \textcolor[HTML]{4285f4}{\textbf{14.97\%}} & \textcolor[HTML]{4285f4}{\textbf{19.9\%}}\\
-\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
-\textbf{Cattle-live (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.49\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}} & \textcolor[HTML]{4285f4}{\textbf{17.57\%}} & \textcolor[HTML]{4285f4}{\textbf{16.66\%}}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.23\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.24\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{37.6\%}} & \textcolor[HTML]{4285f4}{\textbf{35.73\%}} & \textcolor[HTML]{4285f4}{\textbf{27.83\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.66\%}}}\\
-\textbf{Lean hogs (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.22\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}} & \textcolor[HTML]{4285f4}{\textbf{32.78\%}} & \textcolor[HTML]{4285f4}{\textbf{38.28\%}}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.65\%}}}\\
-\addlinespace
-\textbf{Cocoa (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.98\%}}}\\
-\textbf{Cocoa (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.57\%}} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}}\\
-\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.29\%}}}\\
-\textbf{Cocoa (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.91\%}} & \textcolor[HTML]{4285f4}{\textbf{34.66\%}} & \textcolor[HTML]{4285f4}{\textbf{23.57\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.99\%}}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.36\%}}}\\
-\textbf{Coffee-C (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{48.82\%}} & \textcolor[HTML]{4285f4}{\textbf{32.6\%}} & \textcolor[HTML]{4285f4}{\textbf{29.92\%}} & \textcolor[HTML]{4285f4}{\textbf{31.52\%}}\\
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.24\%}}}\\
-\addlinespace
-\textbf{Coffee-C (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.22\%}} & \textcolor[HTML]{4285f4}{\textbf{32.24\%}}\\
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.84\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.02\%}} & \textcolor[HTML]{4285f4}{\textbf{29.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.94\%}} & \textcolor[HTML]{4285f4}{\textbf{21.33\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.91\%}}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.77\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.59\%}} & \textcolor[HTML]{4285f4}{\textbf{19.95\%}}\\
-\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.06\%}}}\\
-\textbf{Lumber (XCME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
-\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**26.99\%}}}\\
-\addlinespace
-\textbf{Lumber (XCME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.43\%}} & \textcolor[HTML]{4285f4}{\textbf{30.72\%}} & \textcolor[HTML]{4285f4}{\textbf{35.45\%}} & \textcolor[HTML]{4285f4}{\textbf{21.26\%}}\\
-\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.14\%}}}\\
-\textbf{Lumber (XCME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}} & \textcolor[HTML]{4285f4}{\textbf{28.2\%}} & \textcolor[HTML]{4285f4}{\textbf{37.23\%}} & \textcolor[HTML]{4285f4}{\textbf{28.45\%}}\\
-\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.8\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.64\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{30.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.64\%}}\\
-\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.64\%}}}\\
-\textbf{Orange juice (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{31.05\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{38.06\%}} & \textcolor[HTML]{4285f4}{\textbf{30.11\%}}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.16\%}}}\\
-\addlinespace
-\textbf{Sugar-\#11 (IFUS)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.07\%}}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{33.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.6\%}} & \textcolor[HTML]{4285f4}{\textbf{41.29\%}} & \textcolor[HTML]{4285f4}{\textbf{27.69\%}}\\
-\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-20.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.7\%}}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.48\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.09\%}} & \textcolor[HTML]{4285f4}{\textbf{29.83\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.33\%}}}\\
-\textbf{Natural gas (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**85.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.76\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.33\%}}}\\
-\textbf{Natural gas (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{63.46\%}} & \textcolor[HTML]{4285f4}{\textbf{47.3\%}} & \textcolor[HTML]{4285f4}{\textbf{48.85\%}} & \textcolor[HTML]{4285f4}{\textbf{42.59\%}}\\
-\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.25\%}}}\\
-\addlinespace
-\textbf{Natural gas (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{59.76\%}} & \textcolor[HTML]{4285f4}{\textbf{61.3\%}} & \textcolor[HTML]{4285f4}{\textbf{58.18\%}} & \textcolor[HTML]{4285f4}{\textbf{46.41\%}}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.64\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.24\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{36.74\%}} & \textcolor[HTML]{4285f4}{\textbf{32.09\%}} & \textcolor[HTML]{4285f4}{\textbf{28.19\%}} & \textcolor[HTML]{4285f4}{\textbf{26.94\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-24.85\%}}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.74\%}} & \textcolor[HTML]{4285f4}{\textbf{33.1\%}} & \textcolor[HTML]{4285f4}{\textbf{53.7\%}} & \textcolor[HTML]{4285f4}{\textbf{41.08\%}}\\
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.37\%}}}\\
-\textbf{Gasoline (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}}\\
-\addlinespace
-\textbf{Gasoline (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.47\%}} & \textcolor[HTML]{4285f4}{\textbf{39.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.1\%}}\\
-\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-19.47\%}}}\\
-\textbf{Gasoline (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.14\%}} & \textcolor[HTML]{4285f4}{\textbf{44.13\%}} & \textcolor[HTML]{4285f4}{\textbf{47.11\%}} & \textcolor[HTML]{4285f4}{\textbf{41.71\%}}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.44\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.16\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.37\%}} & \textcolor[HTML]{4285f4}{\textbf{33.33\%}} & \textcolor[HTML]{4285f4}{\textbf{25.95\%}} & \textcolor[HTML]{4285f4}{\textbf{24.62\%}}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-21.62\%}}}\\
-\textbf{Heating oil (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.98\%}} & \textcolor[HTML]{4285f4}{\textbf{39.16\%}} & \textcolor[HTML]{4285f4}{\textbf{35.69\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.1\%}}}\\
-\addlinespace
-\textbf{Copper (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.1\%}}}\\
-\textbf{Copper (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{30.05\%}} & \textcolor[HTML]{4285f4}{\textbf{25.73\%}} & \textcolor[HTML]{4285f4}{\textbf{18.16\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-12.15\%}}}\\
-\textbf{Copper (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.78\%}} & \textcolor[HTML]{4285f4}{\textbf{33.69\%}} & \textcolor[HTML]{4285f4}{\textbf{42.28\%}} & \textcolor[HTML]{4285f4}{\textbf{20.87\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.53\%}}}\\
-\textbf{Gold (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.21\%}}}\\
-\textbf{Gold (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.89\%}} & \textcolor[HTML]{4285f4}{\textbf{19.2\%}} & \textcolor[HTML]{4285f4}{\textbf{17.03\%}} & \textcolor[HTML]{4285f4}{\textbf{12.36\%}}\\
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.1\%}}}\\
-\addlinespace
-\textbf{Gold (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}} & \textcolor[HTML]{4285f4}{\textbf{25.21\%}} & \textcolor[HTML]{4285f4}{\textbf{16.23\%}}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.75\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**49.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**31.93\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.98\%}} & \textcolor[HTML]{4285f4}{\textbf{34.23\%}} & \textcolor[HTML]{4285f4}{\textbf{33.49\%}} & \textcolor[HTML]{4285f4}{\textbf{23.82\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.88\%}}}\\
-\textbf{Palladium (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{41.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.2\%}} & \textcolor[HTML]{4285f4}{\textbf{38.71\%}} & \textcolor[HTML]{4285f4}{\textbf{26.8\%}}\\
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.92\%}}}\\
-\textbf{Platinum (XNYM)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*25.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.17\%}}}\\
-\addlinespace
-\textbf{Platinum (XNYM)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.1\%}} & \textcolor[HTML]{4285f4}{\textbf{22.51\%}} & \textcolor[HTML]{4285f4}{\textbf{21.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.04\%}}\\
-\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-17.28\%}}}\\
-\textbf{Platinum (XNYM)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.12\%}} & \textcolor[HTML]{4285f4}{\textbf{22.81\%}} & \textcolor[HTML]{4285f4}{\textbf{28.75\%}} & \textcolor[HTML]{4285f4}{\textbf{20.8\%}}\\
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.43\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.44\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.07\%}} & \textcolor[HTML]{4285f4}{\textbf{32.5\%}} & \textcolor[HTML]{4285f4}{\textbf{37.17\%}} & \textcolor[HTML]{4285f4}{\textbf{20.3\%}}\\
-\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.09\%}}}\\
-\textbf{Silver (XCEC)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.93\%}} & \textcolor[HTML]{4285f4}{\textbf{35.34\%}} & \textcolor[HTML]{4285f4}{\textbf{42.44\%}} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}}\\
-\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.15\%}}}\\
-\addlinespace
-\textbf{Aluminium (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
-\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**23.68\%}}}\\
-\textbf{Aluminium (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.57\%}} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{18.94\%}}\\
-\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-23.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-16.74\%}}}\\
-\textbf{Aluminium (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.13\%}} & \textcolor[HTML]{4285f4}{\textbf{27.29\%}} & \textcolor[HTML]{4285f4}{\textbf{28.01\%}} & \textcolor[HTML]{4285f4}{\textbf{18.23\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**28.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.03\%}}}\\
-\textbf{Copper (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.99\%}}}\\
-\textbf{Copper (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.98\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{17.92\%}}\\
-\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.89\%}}}\\
-\addlinespace
-\textbf{Copper (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.41\%}} & \textcolor[HTML]{4285f4}{\textbf{32.98\%}} & \textcolor[HTML]{4285f4}{\textbf{41.31\%}} & \textcolor[HTML]{4285f4}{\textbf{19.86\%}}\\
-\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}}\\
-\textbf{Lead (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
-\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.05\%}}}\\
-\textbf{Lead (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.16\%}} & \textcolor[HTML]{4285f4}{\textbf{39.91\%}} & \textcolor[HTML]{4285f4}{\textbf{35.35\%}} & \textcolor[HTML]{4285f4}{\textbf{23.37\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*46.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-13.41\%}}}\\
-\textbf{Lead (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{20.12\%}} & \textcolor[HTML]{4285f4}{\textbf{43.16\%}} & \textcolor[HTML]{4285f4}{\textbf{46.22\%}} & \textcolor[HTML]{4285f4}{\textbf{23.09\%}}\\
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.31\%}}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-39.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**35.09\%}}}\\
-\addlinespace
-\textbf{Nickel-primary (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.23\%}} & \textcolor[HTML]{4285f4}{\textbf{41.62\%}} & \textcolor[HTML]{4285f4}{\textbf{34.48\%}} & \textcolor[HTML]{4285f4}{\textbf{29.13\%}}\\
-\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**63.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**-34.64\%}}}\\
-\textbf{Nickel-primary (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.28\%}} & \textcolor[HTML]{4285f4}{\textbf{46.72\%}} & \textcolor[HTML]{4285f4}{\textbf{47.44\%}} & \textcolor[HTML]{4285f4}{\textbf{28.6\%}}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.68\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{34.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.48\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.4\%}} & \textcolor[HTML]{4285f4}{\textbf{29.09\%}} & \textcolor[HTML]{4285f4}{\textbf{15.27\%}}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.69\%}}}\\
-\textbf{Tin-refined (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.77\%}} & \textcolor[HTML]{4285f4}{\textbf{32.08\%}} & \textcolor[HTML]{4285f4}{\textbf{41.13\%}} & \textcolor[HTML]{4285f4}{\textbf{21.68\%}}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.07\%}}}\\
-\addlinespace
-\textbf{Zinc (XLME)} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.05\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**29.42\%}}}\\
-\textbf{Zinc (XLME)} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.86\%}} & \textcolor[HTML]{4285f4}{\textbf{33.28\%}} & \textcolor[HTML]{4285f4}{\textbf{22.12\%}}\\
-\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.31\%}}}\\
-\textbf{Zinc (XLME)} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.38\%}} & \textcolor[HTML]{4285f4}{\textbf{40.51\%}} & \textcolor[HTML]{4285f4}{\textbf{39.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.32\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**15.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.18\%}}}\\
-\textbf{US commodities} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{***15.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*15.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.82\%}}}\\
-\textbf{US commodities} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
-\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*16.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-6.33\%}}}\\
-\addlinespace
-\textbf{US commodities} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*21.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.72\%}}}\\
-\textbf{GB commodities} & \textbf{whole period} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**19.95\%}}}\\
-\textbf{GB commodities} & \textbf{backwardation} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-14.05\%}}}\\
-\textbf{GB commodities} & \textbf{contango} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.48\%} & \textcolor[HTML]{4285f4}{21.37\%} & \textcolor[HTML]{4285f4}{6.89\%} & \textcolor[HTML]{4285f4}{-4.51\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23\%} & \textcolor[HTML]{4285f4}{29.54\%} & \textcolor[HTML]{4285f4}{36.15\%} & \textcolor[HTML]{4285f4}{21.8\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.86\%} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{20.48\%} & \textcolor[HTML]{4285f4}{-8.74\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23.07\%} & \textcolor[HTML]{4285f4}{29.14\%} & \textcolor[HTML]{4285f4}{31.59\%} & \textcolor[HTML]{4285f4}{21\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.3\%} & \textcolor[HTML]{4285f4}{23.54\%} & \textcolor[HTML]{4285f4}{-4.43\%} & \textcolor[HTML]{4285f4}{0.78\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23\%} & \textcolor[HTML]{4285f4}{30.01\%} & \textcolor[HTML]{4285f4}{40.14\%} & \textcolor[HTML]{4285f4}{22.68\%}\\
+\textbf{Oats (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.49\%} & \textcolor[HTML]{4285f4}{21.62\%} & \textcolor[HTML]{4285f4}{8.89\%} & \textcolor[HTML]{4285f4}{-0.87\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.22\%} & \textcolor[HTML]{4285f4}{31.04\%} & \textcolor[HTML]{4285f4}{34.67\%} & \textcolor[HTML]{4285f4}{29.5\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.39\%} & \textcolor[HTML]{4285f4}{7.82\%} & \textcolor[HTML]{4285f4}{7.85\%} & \textcolor[HTML]{4285f4}{2.56\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{29.02\%} & \textcolor[HTML]{4285f4}{33.82\%} & \textcolor[HTML]{4285f4}{31.43\%} & \textcolor[HTML]{4285f4}{31.55\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.95\%} & \textcolor[HTML]{4285f4}{*35.38\%} & \textcolor[HTML]{4285f4}{11.68\%} & \textcolor[HTML]{4285f4}{-3.17\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{35.22\%} & \textcolor[HTML]{4285f4}{28.1\%} & \textcolor[HTML]{4285f4}{37.7\%} & \textcolor[HTML]{4285f4}{27.5\%}\\
+\textbf{Soybean meal (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{7.29\%} & \textcolor[HTML]{4285f4}{12.06\%} & \textcolor[HTML]{4285f4}{8.12\%} & \textcolor[HTML]{4285f4}{-0.33\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.34\%} & \textcolor[HTML]{4285f4}{32.55\%} & \textcolor[HTML]{4285f4}{31.78\%} & \textcolor[HTML]{4285f4}{25.11\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{13.15\%} & \textcolor[HTML]{4285f4}{8.22\%} & \textcolor[HTML]{4285f4}{16.04\%} & \textcolor[HTML]{4285f4}{-3.52\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{27.77\%} & \textcolor[HTML]{4285f4}{33.06\%} & \textcolor[HTML]{4285f4}{25.7\%} & \textcolor[HTML]{4285f4}{25.1\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.52\%} & \textcolor[HTML]{4285f4}{15.91\%} & \textcolor[HTML]{4285f4}{2.32\%} & \textcolor[HTML]{4285f4}{2.22\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.94\%} & \textcolor[HTML]{4285f4}{32.13\%} & \textcolor[HTML]{4285f4}{36.85\%} & \textcolor[HTML]{4285f4}{25.32\%}\\
+\textbf{Soybean oil (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.21\%} & \textcolor[HTML]{4285f4}{15.57\%} & \textcolor[HTML]{4285f4}{4.04\%} & \textcolor[HTML]{4285f4}{-7.39\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.43\%} & \textcolor[HTML]{4285f4}{28.35\%} & \textcolor[HTML]{4285f4}{25.75\%} & \textcolor[HTML]{4285f4}{18.95\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{14.79\%} & \textcolor[HTML]{4285f4}{14.62\%} & \textcolor[HTML]{4285f4}{20.34\%} & \textcolor[HTML]{4285f4}{-9.44\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.35\%} & \textcolor[HTML]{4285f4}{28.94\%} & \textcolor[HTML]{4285f4}{22.33\%} & \textcolor[HTML]{4285f4}{18.19\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.68\%} & \textcolor[HTML]{4285f4}{16.62\%} & \textcolor[HTML]{4285f4}{-10.01\%} & \textcolor[HTML]{4285f4}{-4.12\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.55\%} & \textcolor[HTML]{4285f4}{27.91\%} & \textcolor[HTML]{4285f4}{28.65\%} & \textcolor[HTML]{4285f4}{19.79\%}\\
+\textbf{Soybeans (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.89\%} & \textcolor[HTML]{4285f4}{13.36\%} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{-3.82\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.47\%} & \textcolor[HTML]{4285f4}{30.04\%} & \textcolor[HTML]{4285f4}{28\%} & \textcolor[HTML]{4285f4}{21.22\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{13.69\%} & \textcolor[HTML]{4285f4}{0.93\%} & \textcolor[HTML]{4285f4}{13.42\%} & \textcolor[HTML]{4285f4}{-11.45\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.93\%} & \textcolor[HTML]{4285f4}{34.58\%} & \textcolor[HTML]{4285f4}{24.39\%} & \textcolor[HTML]{4285f4}{22.04\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.16\%} & \textcolor[HTML]{4285f4}{25.71\%} & \textcolor[HTML]{4285f4}{0.96\%} & \textcolor[HTML]{4285f4}{3.75\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.09\%} & \textcolor[HTML]{4285f4}{24.74\%} & \textcolor[HTML]{4285f4}{31.11\%} & \textcolor[HTML]{4285f4}{20.56\%}\\
+\addlinespace
+\textbf{Wheat-SRW (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.07\%} & \textcolor[HTML]{4285f4}{17.63\%} & \textcolor[HTML]{4285f4}{6.68\%} & \textcolor[HTML]{4285f4}{-1.58\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.93\%} & \textcolor[HTML]{4285f4}{33.03\%} & \textcolor[HTML]{4285f4}{37.62\%} & \textcolor[HTML]{4285f4}{26.58\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.7\%} & \textcolor[HTML]{4285f4}{19.02\%} & \textcolor[HTML]{4285f4}{0.98\%} & \textcolor[HTML]{4285f4}{0.44\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{25.79\%} & \textcolor[HTML]{4285f4}{36\%} & \textcolor[HTML]{4285f4}{37.53\%} & \textcolor[HTML]{4285f4}{26.57\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.78\%} & \textcolor[HTML]{4285f4}{16.29\%} & \textcolor[HTML]{4285f4}{14.57\%} & \textcolor[HTML]{4285f4}{-2.77\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.04\%} & \textcolor[HTML]{4285f4}{29.84\%} & \textcolor[HTML]{4285f4}{37.73\%} & \textcolor[HTML]{4285f4}{26.72\%}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{7.43\%} & \textcolor[HTML]{4285f4}{7.13\%} & \textcolor[HTML]{4285f4}{1.87\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.23\%} & \textcolor[HTML]{4285f4}{15.16\%} & \textcolor[HTML]{4285f4}{15.24\%} & \textcolor[HTML]{4285f4}{18.69\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.31\%} & \textcolor[HTML]{4285f4}{**20.52\%} & \textcolor[HTML]{4285f4}{7.51\%} & \textcolor[HTML]{4285f4}{6.58\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{12.79\%} & \textcolor[HTML]{4285f4}{14.93\%} & \textcolor[HTML]{4285f4}{13.39\%} & \textcolor[HTML]{4285f4}{20.14\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.81\%} & \textcolor[HTML]{4285f4}{-5.49\%} & \textcolor[HTML]{4285f4}{7.28\%} & \textcolor[HTML]{4285f4}{-3.12\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.67\%} & \textcolor[HTML]{4285f4}{15.35\%} & \textcolor[HTML]{4285f4}{16.91\%} & \textcolor[HTML]{4285f4}{17.23\%}\\
+\textbf{Cattle-live (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.45\%} & \textcolor[HTML]{4285f4}{8.77\%} & \textcolor[HTML]{4285f4}{4.13\%} & \textcolor[HTML]{4285f4}{1.92\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.1\%} & \textcolor[HTML]{4285f4}{17.43\%} & \textcolor[HTML]{4285f4}{16.32\%} & \textcolor[HTML]{4285f4}{18.3\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{8.39\%} & \textcolor[HTML]{4285f4}{14.2\%} & \textcolor[HTML]{4285f4}{5.87\%} & \textcolor[HTML]{4285f4}{-2.07\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.65\%} & \textcolor[HTML]{4285f4}{17.91\%} & \textcolor[HTML]{4285f4}{14.97\%} & \textcolor[HTML]{4285f4}{19.9\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.34\%} & \textcolor[HTML]{4285f4}{3.43\%} & \textcolor[HTML]{4285f4}{2.7\%} & \textcolor[HTML]{4285f4}{5.82\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.49\%} & \textcolor[HTML]{4285f4}{16.99\%} & \textcolor[HTML]{4285f4}{17.57\%} & \textcolor[HTML]{4285f4}{16.66\%}\\
+\textbf{Lean hogs (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{8.4\%} & \textcolor[HTML]{4285f4}{12.69\%} & \textcolor[HTML]{4285f4}{-1.09\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.33\%} & \textcolor[HTML]{4285f4}{31.89\%} & \textcolor[HTML]{4285f4}{30.37\%} & \textcolor[HTML]{4285f4}{36.94\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{12.34\%} & \textcolor[HTML]{4285f4}{16.3\%} & \textcolor[HTML]{4285f4}{18.23\%} & \textcolor[HTML]{4285f4}{19.24\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{37.6\%} & \textcolor[HTML]{4285f4}{35.73\%} & \textcolor[HTML]{4285f4}{27.83\%} & \textcolor[HTML]{4285f4}{35.61\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-10.5\%} & \textcolor[HTML]{4285f4}{0.6\%} & \textcolor[HTML]{4285f4}{7.5\%} & \textcolor[HTML]{4285f4}{-20.66\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{39.22\%} & \textcolor[HTML]{4285f4}{27.67\%} & \textcolor[HTML]{4285f4}{32.78\%} & \textcolor[HTML]{4285f4}{38.28\%}\\
+\textbf{Cocoa (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.66\%} & \textcolor[HTML]{4285f4}{16.35\%} & \textcolor[HTML]{4285f4}{1.39\%} & \textcolor[HTML]{4285f4}{3.65\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.66\%} & \textcolor[HTML]{4285f4}{29.99\%} & \textcolor[HTML]{4285f4}{31.03\%} & \textcolor[HTML]{4285f4}{24.69\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.12\%} & \textcolor[HTML]{4285f4}{9.25\%} & \textcolor[HTML]{4285f4}{-9.56\%} & \textcolor[HTML]{4285f4}{-2.98\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{33.57\%} & \textcolor[HTML]{4285f4}{31.05\%} & \textcolor[HTML]{4285f4}{26.93\%} & \textcolor[HTML]{4285f4}{25.86\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.67\%} & \textcolor[HTML]{4285f4}{23.43\%} & \textcolor[HTML]{4285f4}{12.92\%} & \textcolor[HTML]{4285f4}{10.29\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{31.81\%} & \textcolor[HTML]{4285f4}{28.91\%} & \textcolor[HTML]{4285f4}{34.66\%} & \textcolor[HTML]{4285f4}{23.57\%}\\
+\addlinespace
+\textbf{Coffee-C (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.91\%} & \textcolor[HTML]{4285f4}{20.38\%} & \textcolor[HTML]{4285f4}{2.2\%} & \textcolor[HTML]{4285f4}{1.99\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{43.84\%} & \textcolor[HTML]{4285f4}{32.3\%} & \textcolor[HTML]{4285f4}{30.17\%} & \textcolor[HTML]{4285f4}{31.86\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.51\%} & \textcolor[HTML]{4285f4}{26.49\%} & \textcolor[HTML]{4285f4}{2.66\%} & \textcolor[HTML]{4285f4}{14.36\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{48.82\%} & \textcolor[HTML]{4285f4}{32.6\%} & \textcolor[HTML]{4285f4}{29.92\%} & \textcolor[HTML]{4285f4}{31.52\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-16.87\%} & \textcolor[HTML]{4285f4}{14.38\%} & \textcolor[HTML]{4285f4}{3.4\%} & \textcolor[HTML]{4285f4}{-10.24\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.35\%} & \textcolor[HTML]{4285f4}{32.06\%} & \textcolor[HTML]{4285f4}{30.22\%} & \textcolor[HTML]{4285f4}{32.24\%}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.24\%} & \textcolor[HTML]{4285f4}{0.95\%} & \textcolor[HTML]{4285f4}{12.53\%} & \textcolor[HTML]{4285f4}{0.5\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.38\%} & \textcolor[HTML]{4285f4}{29.01\%} & \textcolor[HTML]{4285f4}{33.26\%} & \textcolor[HTML]{4285f4}{20.61\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{22.64\%} & \textcolor[HTML]{4285f4}{7.85\%} & \textcolor[HTML]{4285f4}{35.53\%} & \textcolor[HTML]{4285f4}{10.84\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.02\%} & \textcolor[HTML]{4285f4}{29.71\%} & \textcolor[HTML]{4285f4}{33.94\%} & \textcolor[HTML]{4285f4}{21.33\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-16.46\%} & \textcolor[HTML]{4285f4}{-5.92\%} & \textcolor[HTML]{4285f4}{-9.36\%} & \textcolor[HTML]{4285f4}{-8.91\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.77\%} & \textcolor[HTML]{4285f4}{28.35\%} & \textcolor[HTML]{4285f4}{32.59\%} & \textcolor[HTML]{4285f4}{19.95\%}\\
+\textbf{Lumber (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.9\%} & \textcolor[HTML]{4285f4}{-3.58\%} & \textcolor[HTML]{4285f4}{11.74\%} & \textcolor[HTML]{4285f4}{5.06\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.58\%} & \textcolor[HTML]{4285f4}{29.39\%} & \textcolor[HTML]{4285f4}{36.31\%} & \textcolor[HTML]{4285f4}{25.1\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-8.48\%} & \textcolor[HTML]{4285f4}{-2.37\%} & \textcolor[HTML]{4285f4}{29.11\%} & \textcolor[HTML]{4285f4}{**26.99\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.43\%} & \textcolor[HTML]{4285f4}{30.72\%} & \textcolor[HTML]{4285f4}{35.45\%} & \textcolor[HTML]{4285f4}{21.26\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.68\%} & \textcolor[HTML]{4285f4}{-4.77\%} & \textcolor[HTML]{4285f4}{-5.04\%} & \textcolor[HTML]{4285f4}{-17.14\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.56\%} & \textcolor[HTML]{4285f4}{28.2\%} & \textcolor[HTML]{4285f4}{37.23\%} & \textcolor[HTML]{4285f4}{28.45\%}\\
+\textbf{Orange juice (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.67\%} & \textcolor[HTML]{4285f4}{13.87\%} & \textcolor[HTML]{4285f4}{14.4\%} & \textcolor[HTML]{4285f4}{3.8\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{29.5\%} & \textcolor[HTML]{4285f4}{33.01\%} & \textcolor[HTML]{4285f4}{34.43\%} & \textcolor[HTML]{4285f4}{29.37\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.38\%} & \textcolor[HTML]{4285f4}{-2.22\%} & \textcolor[HTML]{4285f4}{18.24\%} & \textcolor[HTML]{4285f4}{18.64\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{28.01\%} & \textcolor[HTML]{4285f4}{33.01\%} & \textcolor[HTML]{4285f4}{30.09\%} & \textcolor[HTML]{4285f4}{28.64\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.83\%} & \textcolor[HTML]{4285f4}{29.93\%} & \textcolor[HTML]{4285f4}{12.29\%} & \textcolor[HTML]{4285f4}{-8.64\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{31.05\%} & \textcolor[HTML]{4285f4}{33.1\%} & \textcolor[HTML]{4285f4}{38.06\%} & \textcolor[HTML]{4285f4}{30.11\%}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.56\%} & \textcolor[HTML]{4285f4}{24.87\%} & \textcolor[HTML]{4285f4}{11.82\%} & \textcolor[HTML]{4285f4}{-1.16\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.88\%} & \textcolor[HTML]{4285f4}{33.25\%} & \textcolor[HTML]{4285f4}{37.9\%} & \textcolor[HTML]{4285f4}{28.72\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.98\%} & \textcolor[HTML]{4285f4}{29.51\%} & \textcolor[HTML]{4285f4}{2.7\%} & \textcolor[HTML]{4285f4}{-8.07\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{33.23\%} & \textcolor[HTML]{4285f4}{33.6\%} & \textcolor[HTML]{4285f4}{41.29\%} & \textcolor[HTML]{4285f4}{27.69\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-20.49\%} & \textcolor[HTML]{4285f4}{20.35\%} & \textcolor[HTML]{4285f4}{21.47\%} & \textcolor[HTML]{4285f4}{4.7\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{36.48\%} & \textcolor[HTML]{4285f4}{32.98\%} & \textcolor[HTML]{4285f4}{34.09\%} & \textcolor[HTML]{4285f4}{29.83\%}\\
+\addlinespace
+\textbf{Natural gas (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{35.38\%} & \textcolor[HTML]{4285f4}{16.25\%} & \textcolor[HTML]{4285f4}{0.93\%} & \textcolor[HTML]{4285f4}{8.33\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{61.55\%} & \textcolor[HTML]{4285f4}{54.6\%} & \textcolor[HTML]{4285f4}{53.58\%} & \textcolor[HTML]{4285f4}{44.58\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**85.84\%} & \textcolor[HTML]{4285f4}{4.76\%} & \textcolor[HTML]{4285f4}{-2.32\%} & \textcolor[HTML]{4285f4}{18.33\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{63.46\%} & \textcolor[HTML]{4285f4}{47.3\%} & \textcolor[HTML]{4285f4}{48.85\%} & \textcolor[HTML]{4285f4}{42.59\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-11.98\%} & \textcolor[HTML]{4285f4}{27.84\%} & \textcolor[HTML]{4285f4}{4.77\%} & \textcolor[HTML]{4285f4}{3.25\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{59.76\%} & \textcolor[HTML]{4285f4}{61.3\%} & \textcolor[HTML]{4285f4}{58.18\%} & \textcolor[HTML]{4285f4}{46.41\%}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{15.43\%} & \textcolor[HTML]{4285f4}{*28.74\%} & \textcolor[HTML]{4285f4}{9.67\%} & \textcolor[HTML]{4285f4}{-5.64\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{39.87\%} & \textcolor[HTML]{4285f4}{32.56\%} & \textcolor[HTML]{4285f4}{42.84\%} & \textcolor[HTML]{4285f4}{34.69\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{29.17\%} & \textcolor[HTML]{4285f4}{*35.61\%} & \textcolor[HTML]{4285f4}{11.47\%} & \textcolor[HTML]{4285f4}{14.24\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{36.74\%} & \textcolor[HTML]{4285f4}{32.09\%} & \textcolor[HTML]{4285f4}{28.19\%} & \textcolor[HTML]{4285f4}{26.94\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.21\%} & \textcolor[HTML]{4285f4}{22.04\%} & \textcolor[HTML]{4285f4}{9.95\%} & \textcolor[HTML]{4285f4}{-24.85\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.74\%} & \textcolor[HTML]{4285f4}{33.1\%} & \textcolor[HTML]{4285f4}{53.7\%} & \textcolor[HTML]{4285f4}{41.08\%}\\
+\textbf{Gasoline (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.65\%} & \textcolor[HTML]{4285f4}{30.95\%} & \textcolor[HTML]{4285f4}{10.59\%} & \textcolor[HTML]{4285f4}{-5.37\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.77\%} & \textcolor[HTML]{4285f4}{41.76\%} & \textcolor[HTML]{4285f4}{40.07\%} & \textcolor[HTML]{4285f4}{37.09\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{39\%} & \textcolor[HTML]{4285f4}{19.82\%} & \textcolor[HTML]{4285f4}{23.98\%} & \textcolor[HTML]{4285f4}{9.69\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.47\%} & \textcolor[HTML]{4285f4}{39.38\%} & \textcolor[HTML]{4285f4}{31.41\%} & \textcolor[HTML]{4285f4}{32.1\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.22\%} & \textcolor[HTML]{4285f4}{42.13\%} & \textcolor[HTML]{4285f4}{-0.09\%} & \textcolor[HTML]{4285f4}{-19.47\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{43.14\%} & \textcolor[HTML]{4285f4}{44.13\%} & \textcolor[HTML]{4285f4}{47.11\%} & \textcolor[HTML]{4285f4}{41.71\%}\\
+\textbf{Heating oil (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.31\%} & \textcolor[HTML]{4285f4}{*29.88\%} & \textcolor[HTML]{4285f4}{6.83\%} & \textcolor[HTML]{4285f4}{-3.44\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{40.75\%} & \textcolor[HTML]{4285f4}{35.09\%} & \textcolor[HTML]{4285f4}{33.17\%} & \textcolor[HTML]{4285f4}{30.56\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{36.32\%} & \textcolor[HTML]{4285f4}{29.41\%} & \textcolor[HTML]{4285f4}{25.56\%} & \textcolor[HTML]{4285f4}{15.16\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{41.37\%} & \textcolor[HTML]{4285f4}{33.33\%} & \textcolor[HTML]{4285f4}{25.95\%} & \textcolor[HTML]{4285f4}{24.62\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.74\%} & \textcolor[HTML]{4285f4}{30.5\%} & \textcolor[HTML]{4285f4}{-10.77\%} & \textcolor[HTML]{4285f4}{-21.62\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{40.19\%} & \textcolor[HTML]{4285f4}{36.98\%} & \textcolor[HTML]{4285f4}{39.16\%} & \textcolor[HTML]{4285f4}{35.69\%}\\
+\textbf{Copper (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.45\%} & \textcolor[HTML]{4285f4}{*28.15\%} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{-0.1\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.23\%} & \textcolor[HTML]{4285f4}{31.89\%} & \textcolor[HTML]{4285f4}{34.91\%} & \textcolor[HTML]{4285f4}{19.56\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.14\%} & \textcolor[HTML]{4285f4}{22.17\%} & \textcolor[HTML]{4285f4}{16.53\%} & \textcolor[HTML]{4285f4}{12.1\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.71\%} & \textcolor[HTML]{4285f4}{30.05\%} & \textcolor[HTML]{4285f4}{25.73\%} & \textcolor[HTML]{4285f4}{18.16\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.28\%} & \textcolor[HTML]{4285f4}{34.17\%} & \textcolor[HTML]{4285f4}{-3.46\%} & \textcolor[HTML]{4285f4}{-12.15\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.78\%} & \textcolor[HTML]{4285f4}{33.69\%} & \textcolor[HTML]{4285f4}{42.28\%} & \textcolor[HTML]{4285f4}{20.87\%}\\
+\addlinespace
+\textbf{Gold (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.5\%} & \textcolor[HTML]{4285f4}{14.35\%} & \textcolor[HTML]{4285f4}{14.01\%} & \textcolor[HTML]{4285f4}{0.53\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.14\%} & \textcolor[HTML]{4285f4}{18.89\%} & \textcolor[HTML]{4285f4}{21.46\%} & \textcolor[HTML]{4285f4}{14.41\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{9.19\%} & \textcolor[HTML]{4285f4}{13.37\%} & \textcolor[HTML]{4285f4}{9.37\%} & \textcolor[HTML]{4285f4}{4.21\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.89\%} & \textcolor[HTML]{4285f4}{19.2\%} & \textcolor[HTML]{4285f4}{17.03\%} & \textcolor[HTML]{4285f4}{12.36\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.01\%} & \textcolor[HTML]{4285f4}{15.37\%} & \textcolor[HTML]{4285f4}{19.1\%} & \textcolor[HTML]{4285f4}{-3.1\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.24\%} & \textcolor[HTML]{4285f4}{18.58\%} & \textcolor[HTML]{4285f4}{25.21\%} & \textcolor[HTML]{4285f4}{16.23\%}\\
+\textbf{Palladium (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{9.12\%} & \textcolor[HTML]{4285f4}{9.03\%} & \textcolor[HTML]{4285f4}{*29.12\%} & \textcolor[HTML]{4285f4}{13.75\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.27\%} & \textcolor[HTML]{4285f4}{32.71\%} & \textcolor[HTML]{4285f4}{36.14\%} & \textcolor[HTML]{4285f4}{25.38\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**49.79\%} & \textcolor[HTML]{4285f4}{24.47\%} & \textcolor[HTML]{4285f4}{30.01\%} & \textcolor[HTML]{4285f4}{**31.93\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.98\%} & \textcolor[HTML]{4285f4}{34.23\%} & \textcolor[HTML]{4285f4}{33.49\%} & \textcolor[HTML]{4285f4}{23.82\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-30.19\%} & \textcolor[HTML]{4285f4}{-6.3\%} & \textcolor[HTML]{4285f4}{30.58\%} & \textcolor[HTML]{4285f4}{-4.88\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{41.22\%} & \textcolor[HTML]{4285f4}{31.2\%} & \textcolor[HTML]{4285f4}{38.71\%} & \textcolor[HTML]{4285f4}{26.8\%}\\
+\textbf{Platinum (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{12.93\%} & \textcolor[HTML]{4285f4}{10.56\%} & \textcolor[HTML]{4285f4}{7.29\%} & \textcolor[HTML]{4285f4}{-7.92\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.62\%} & \textcolor[HTML]{4285f4}{22.66\%} & \textcolor[HTML]{4285f4}{25.53\%} & \textcolor[HTML]{4285f4}{19.48\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**29.46\%} & \textcolor[HTML]{4285f4}{*25.07\%} & \textcolor[HTML]{4285f4}{10.46\%} & \textcolor[HTML]{4285f4}{1.17\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.1\%} & \textcolor[HTML]{4285f4}{22.51\%} & \textcolor[HTML]{4285f4}{21.24\%} & \textcolor[HTML]{4285f4}{18.04\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-3.22\%} & \textcolor[HTML]{4285f4}{-3.81\%} & \textcolor[HTML]{4285f4}{8.04\%} & \textcolor[HTML]{4285f4}{-17.28\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23.12\%} & \textcolor[HTML]{4285f4}{22.81\%} & \textcolor[HTML]{4285f4}{28.75\%} & \textcolor[HTML]{4285f4}{20.8\%}\\
+\textbf{Silver (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{17.54\%} & \textcolor[HTML]{4285f4}{21.96\%} & \textcolor[HTML]{4285f4}{-2.43\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22\%} & \textcolor[HTML]{4285f4}{33.92\%} & \textcolor[HTML]{4285f4}{39.87\%} & \textcolor[HTML]{4285f4}{24.35\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.98\%} & \textcolor[HTML]{4285f4}{14.29\%} & \textcolor[HTML]{4285f4}{19.66\%} & \textcolor[HTML]{4285f4}{3.44\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.07\%} & \textcolor[HTML]{4285f4}{32.5\%} & \textcolor[HTML]{4285f4}{37.17\%} & \textcolor[HTML]{4285f4}{20.3\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.57\%} & \textcolor[HTML]{4285f4}{20.83\%} & \textcolor[HTML]{4285f4}{26.77\%} & \textcolor[HTML]{4285f4}{-8.09\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.93\%} & \textcolor[HTML]{4285f4}{35.34\%} & \textcolor[HTML]{4285f4}{42.44\%} & \textcolor[HTML]{4285f4}{27.77\%}\\
+\textbf{Aluminium (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.13\%} & \textcolor[HTML]{4285f4}{13.78\%} & \textcolor[HTML]{4285f4}{-3.58\%} & \textcolor[HTML]{4285f4}{3.15\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.6\%} & \textcolor[HTML]{4285f4}{26.41\%} & \textcolor[HTML]{4285f4}{26.48\%} & \textcolor[HTML]{4285f4}{18.56\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.56\%} & \textcolor[HTML]{4285f4}{14.78\%} & \textcolor[HTML]{4285f4}{16.25\%} & \textcolor[HTML]{4285f4}{**23.68\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.82\%} & \textcolor[HTML]{4285f4}{25.57\%} & \textcolor[HTML]{4285f4}{24.94\%} & \textcolor[HTML]{4285f4}{18.94\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.38\%} & \textcolor[HTML]{4285f4}{12.86\%} & \textcolor[HTML]{4285f4}{-23.04\%} & \textcolor[HTML]{4285f4}{-16.74\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.13\%} & \textcolor[HTML]{4285f4}{27.29\%} & \textcolor[HTML]{4285f4}{28.01\%} & \textcolor[HTML]{4285f4}{18.23\%}\\
+\addlinespace
+\textbf{Copper (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.45\%} & \textcolor[HTML]{4285f4}{**28.59\%} & \textcolor[HTML]{4285f4}{5.74\%} & \textcolor[HTML]{4285f4}{0.03\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.25\%} & \textcolor[HTML]{4285f4}{31.09\%} & \textcolor[HTML]{4285f4}{34.27\%} & \textcolor[HTML]{4285f4}{18.92\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.54\%} & \textcolor[HTML]{4285f4}{25.22\%} & \textcolor[HTML]{4285f4}{18.66\%} & \textcolor[HTML]{4285f4}{11.99\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.98\%} & \textcolor[HTML]{4285f4}{29.01\%} & \textcolor[HTML]{4285f4}{25.53\%} & \textcolor[HTML]{4285f4}{17.92\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.95\%} & \textcolor[HTML]{4285f4}{32\%} & \textcolor[HTML]{4285f4}{-6.78\%} & \textcolor[HTML]{4285f4}{-11.89\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.41\%} & \textcolor[HTML]{4285f4}{32.98\%} & \textcolor[HTML]{4285f4}{41.31\%} & \textcolor[HTML]{4285f4}{19.86\%}\\
+\textbf{Lead (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.83\%} & \textcolor[HTML]{4285f4}{28.99\%} & \textcolor[HTML]{4285f4}{10.74\%} & \textcolor[HTML]{4285f4}{2.07\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.64\%} & \textcolor[HTML]{4285f4}{41.74\%} & \textcolor[HTML]{4285f4}{41.05\%} & \textcolor[HTML]{4285f4}{23.26\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{7.59\%} & \textcolor[HTML]{4285f4}{11.21\%} & \textcolor[HTML]{4285f4}{9.87\%} & \textcolor[HTML]{4285f4}{17.05\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.16\%} & \textcolor[HTML]{4285f4}{39.91\%} & \textcolor[HTML]{4285f4}{35.35\%} & \textcolor[HTML]{4285f4}{23.37\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.09\%} & \textcolor[HTML]{4285f4}{*46.48\%} & \textcolor[HTML]{4285f4}{12.65\%} & \textcolor[HTML]{4285f4}{-13.41\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.12\%} & \textcolor[HTML]{4285f4}{43.16\%} & \textcolor[HTML]{4285f4}{46.22\%} & \textcolor[HTML]{4285f4}{23.09\%}\\
+\textbf{Nickel (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{19.31\%} & \textcolor[HTML]{4285f4}{12.5\%} & \textcolor[HTML]{4285f4}{3.52\%} & \textcolor[HTML]{4285f4}{0.31\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.26\%} & \textcolor[HTML]{4285f4}{44.27\%} & \textcolor[HTML]{4285f4}{41.45\%} & \textcolor[HTML]{4285f4}{28.98\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{23.25\%} & \textcolor[HTML]{4285f4}{-39.24\%} & \textcolor[HTML]{4285f4}{16.3\%} & \textcolor[HTML]{4285f4}{**35.09\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.23\%} & \textcolor[HTML]{4285f4}{41.62\%} & \textcolor[HTML]{4285f4}{34.48\%} & \textcolor[HTML]{4285f4}{29.13\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{15.46\%} & \textcolor[HTML]{4285f4}{**63.47\%} & \textcolor[HTML]{4285f4}{-7.67\%} & \textcolor[HTML]{4285f4}{**-34.64\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.28\%} & \textcolor[HTML]{4285f4}{46.72\%} & \textcolor[HTML]{4285f4}{47.44\%} & \textcolor[HTML]{4285f4}{28.6\%}\\
+\textbf{Tin (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.07\%} & \textcolor[HTML]{4285f4}{*29.1\%} & \textcolor[HTML]{4285f4}{7.46\%} & \textcolor[HTML]{4285f4}{1.68\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.38\%} & \textcolor[HTML]{4285f4}{31.71\%} & \textcolor[HTML]{4285f4}{35.61\%} & \textcolor[HTML]{4285f4}{18.79\%}\\
+\addlinespace
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{*15.83\%} & \textcolor[HTML]{4285f4}{34.62\%} & \textcolor[HTML]{4285f4}{23.7\%} & \textcolor[HTML]{4285f4}{4.48\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.99\%} & \textcolor[HTML]{4285f4}{31.4\%} & \textcolor[HTML]{4285f4}{29.09\%} & \textcolor[HTML]{4285f4}{15.27\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-7.78\%} & \textcolor[HTML]{4285f4}{23.88\%} & \textcolor[HTML]{4285f4}{-6.82\%} & \textcolor[HTML]{4285f4}{-1.69\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.77\%} & \textcolor[HTML]{4285f4}{32.08\%} & \textcolor[HTML]{4285f4}{41.13\%} & \textcolor[HTML]{4285f4}{21.68\%}\\
+\textbf{Zinc (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.52\%} & \textcolor[HTML]{4285f4}{20.13\%} & \textcolor[HTML]{4285f4}{7.62\%} & \textcolor[HTML]{4285f4}{9.07\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.73\%} & \textcolor[HTML]{4285f4}{38.77\%} & \textcolor[HTML]{4285f4}{36.17\%} & \textcolor[HTML]{4285f4}{23.25\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-9.06\%} & \textcolor[HTML]{4285f4}{2.95\%} & \textcolor[HTML]{4285f4}{10.05\%} & \textcolor[HTML]{4285f4}{**29.42\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.15\%} & \textcolor[HTML]{4285f4}{36.86\%} & \textcolor[HTML]{4285f4}{33.28\%} & \textcolor[HTML]{4285f4}{22.12\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.13\%} & \textcolor[HTML]{4285f4}{37.11\%} & \textcolor[HTML]{4285f4}{5.43\%} & \textcolor[HTML]{4285f4}{-11.31\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.38\%} & \textcolor[HTML]{4285f4}{40.51\%} & \textcolor[HTML]{4285f4}{39.03\%} & \textcolor[HTML]{4285f4}{24.32\%}\\
+\addlinespace
+\textbf{US commodities} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{*6.89\%} & \textcolor[HTML]{4285f4}{**15.89\%} & \textcolor[HTML]{4285f4}{9.39\%} & \textcolor[HTML]{4285f4}{-0.18\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{10\%} & \textcolor[HTML]{4285f4}{13.62\%} & \textcolor[HTML]{4285f4}{17.58\%} & \textcolor[HTML]{4285f4}{9.86\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{***15.44\%} & \textcolor[HTML]{4285f4}{*15.66\%} & \textcolor[HTML]{4285f4}{13.4\%} & \textcolor[HTML]{4285f4}{6.82\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{9.88\%} & \textcolor[HTML]{4285f4}{14.21\%} & \textcolor[HTML]{4285f4}{14.83\%} & \textcolor[HTML]{4285f4}{8.59\%}\\
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-1.09\%} & \textcolor[HTML]{4285f4}{*16.16\%} & \textcolor[HTML]{4285f4}{4.9\%} & \textcolor[HTML]{4285f4}{-6.33\%}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{10.09\%} & \textcolor[HTML]{4285f4}{13.05\%} & \textcolor[HTML]{4285f4}{19.98\%} & \textcolor[HTML]{4285f4}{10.95\%}\\
+\textbf{GB commodities} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.47\%} & \textcolor[HTML]{4285f4}{*21.77\%} & \textcolor[HTML]{4285f4}{5.25\%} & \textcolor[HTML]{4285f4}{2.72\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.66\%} & \textcolor[HTML]{4285f4}{26.91\%} & \textcolor[HTML]{4285f4}{30.24\%} & \textcolor[HTML]{4285f4}{16.19\%}\\
+\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.41\%} & \textcolor[HTML]{4285f4}{8.01\%} & \textcolor[HTML]{4285f4}{15.06\%} & \textcolor[HTML]{4285f4}{**19.95\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.39\%} & \textcolor[HTML]{4285f4}{25.92\%} & \textcolor[HTML]{4285f4}{25.94\%} & \textcolor[HTML]{4285f4}{15.13\%}\\
+\addlinespace
+\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.34\%} & \textcolor[HTML]{4285f4}{*35.56\%} & \textcolor[HTML]{4285f4}{-5.24\%} & \textcolor[HTML]{4285f4}{-14.05\%}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.87\%} & \textcolor[HTML]{4285f4}{27.88\%} & \textcolor[HTML]{4285f4}{34.06\%} & \textcolor[HTML]{4285f4}{17.1\%}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
+\newpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}l>{}r>{}r}
+
+\caption{\label{tbl-regime-diference-tests}This table shows the results
+for tests of difference in mean (t-test) and variance (F-test) between
+phases of aggregate backwardation and contango for the twenty four
+individual US commodities and the six GB metals considered in the study
+as well as for two equally weighted portfolios formed from the US
+commodities and the GB metals respectively across the four periods of
+interest (past: 1997-2003; financialisation: 2004-2008; crisis:
+2008-2013; post-crisis: 2013-2018). 1\%, 5\% and 10\% p-value levels are
+marked with ***, ** and * respectively in the significance column.
+Aggregate CHP construction and corresponding regime definitions are
+discussed in Section~\ref{sec-methods} while the results are discussed
+in Section~\ref{sec-results}.}
+
+\tabularnewline
+
+\toprule
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{period}} & \textcolor{black}{\textbf{moment}} & \textcolor{black}{\textbf{dominant regime}} & \textcolor{black}{\textbf{p-value}} & \textcolor{black}{\textbf{significance}}\\
+\midrule
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{34.26\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{89.69\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{91.01\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{47.46\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{40.83\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{34} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{57.39\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.02\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{Oats (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{38.12\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{33} ***}\\
+\addlinespace
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{35.29\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{8} ***}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.66\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{32} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{82.72\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{Soybean meal (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{66.39\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{81.2\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.83\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{56.57\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{31} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{75.13\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.31\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Soybean oil (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{31.59\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{81.72\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{92.18\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.2\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.64\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{30} ***}\\
+\addlinespace
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{69.59\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.36\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{Soybeans (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{48.92\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{17.18\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{38.74\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{7} ***}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{57.61\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{29} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.95\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.05\%} & \textcolor[HTML]{4285f4}{*}\\
+\addlinespace
+\textbf{Wheat-SRW (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{44.86\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.79\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{83.21\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{6} ***}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{76.2\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.51\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.81\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{94.9\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{76.82\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.34\%} & \textcolor[HTML]{4285f4}{*}\\
+\addlinespace
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.35\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{62.38\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{99.19\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{28} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{50.04\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{5} ***}\\
+\textbf{Cattle-live (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.11\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{15.26\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.61\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{20.96\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{82.12\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{63.19\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{4} ***}\\
+\textbf{Lean hogs (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{45.71\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{24.77\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{55.51\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{3} ***}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{68.46\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
+\addlinespace
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{21.55\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{6.81\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{Cocoa (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{99.36\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{12.33\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.85\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{7.73\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{42.98\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{27} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{51.48\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.17\%} & \textcolor[HTML]{4285f4}{**}\\
+\addlinespace
+\textbf{Coffee-C (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{53.38\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{69.3\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.63\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{95.23\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{82.84\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{35.39\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{52.86\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.02\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{41.38\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{59.06\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{26.81\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{14.44\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{33.04\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{32.06\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.67\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{Lumber (XCME)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.56\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{75.67\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{84.3\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.36\%} & \textcolor[HTML]{4285f4}{**}\\
+\addlinespace
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{28.12\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{22.82\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.31\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{26} ***}\\
+\textbf{Orange juice (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{66.85\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{28.81\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{92.47\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.55\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{25} ***}\\
+\addlinespace
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{25.72\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.01\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{24.1\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.76\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{75.29\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.89\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{56.23\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.08\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.22\%} & \textcolor[HTML]{4285f4}{*}\\
+\addlinespace
+\textbf{Natural gas (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.66\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.01\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{68.1\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{24} ***}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.28\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{23} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.04\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.08\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{38.33\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{22} ***}\\
+\addlinespace
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{61.91\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{49.38\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{95.55\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{21} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.99\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{20} ***}\\
+\textbf{Gasoline (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.96\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{66.51\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{58.35\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.58\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{49.08\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{19} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.23\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{18} ***}\\
+\textbf{Heating oil (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{21.83\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.45\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{99.52\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.52\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{23.31\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{17} ***}\\
+\addlinespace
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{15.71\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{16} ***}\\
+\textbf{Copper (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{90.64\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{17.88\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{74.37\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.71\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{55.78\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{15} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{17.19\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
+\addlinespace
+\textbf{Gold (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{43.44\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.63\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.92\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{60.22\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{14} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{56.58\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{13} ***}\\
+\textbf{Palladium (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.77\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{12} ***}\\
+\addlinespace
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{30.26\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.38\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.05\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{9.4\%} & \textcolor[HTML]{4285f4}{*}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{Platinum (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.08\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{14.41\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.86\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{85.5\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{11} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{27.26\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{Silver (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.07\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.09\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{88.44\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.01\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.12\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.08\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{61.83\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{10} ***}\\
+\textbf{Aluminium (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{86.1\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{9} ***}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.59\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.33\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{10.79\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.41\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.33\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{25.99\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{Copper (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{88.51\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.59\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.15\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{43.61\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{8} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{16.36\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{Lead (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{58.96\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.81\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{40.11\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.11\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.17\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{7} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{15.62\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{85.45\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Nickel (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{76.56\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.04\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{1.24\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.62\%} & \textcolor[HTML]{4285f4}{***}\\
+\addlinespace
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{49.29\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{6} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.46\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{69.15\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Tin (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.22\%} & \textcolor[HTML]{4285f4}{*}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{14.94\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{70.17\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{58.14\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.29\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{5} ***}\\
+\addlinespace
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{73.44\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{4} ***}\\
+\textbf{Zinc (XLME)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.39\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.75\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.67\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.29\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.89\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.05\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{1.77\%} & \textcolor[HTML]{4285f4}{**}\\
+\addlinespace
+\textbf{US commodities} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{3.63\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{54.29\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{93.09\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.22\%} & \textcolor[HTML]{4285f4}{**}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{58.92\%} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{3} ***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{11.83\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
+\textbf{GB commodities} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{78.74\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
+\addlinespace
+\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{27.95\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.65\%} & \textcolor[HTML]{4285f4}{*}\\
+\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{46.83\%} & \textcolor[HTML]{4285f4}{}\\
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
+\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.37\%} & \textcolor[HTML]{4285f4}{**}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.13\%} & \textcolor[HTML]{4285f4}{***}\\
 \bottomrule
@@
 \toprule
-\textcolor{black}{\textbf{regressor}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{regressor}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.17\%}}}\\
-\textbf{Δ\% commodity CHP} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.19\%}} & \textcolor[HTML]{4285f4}{\textbf{21.6\%}} & \textcolor[HTML]{4285f4}{\textbf{23.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.12\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.24\%}}}\\
-\textbf{Δ\% commodity CHP} & \textbf{agriculturals} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{6.23\%}} & \textcolor[HTML]{4285f4}{\textbf{10.53\%}} & \textcolor[HTML]{4285f4}{\textbf{6.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.88\%}}}\\
-\addlinespace
-\textbf{Δ\% commodity CHP} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.12\%}} & \textcolor[HTML]{4285f4}{\textbf{19.45\%}} & \textcolor[HTML]{4285f4}{\textbf{16\%}} & \textcolor[HTML]{4285f4}{\textbf{10.96\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
-\textbf{Δ\% commodity CHP} & \textbf{energy} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{18.87\%}} & \textcolor[HTML]{4285f4}{\textbf{12.85\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.32\%}}}\\
-\textbf{Δ\% commodity CHP} & \textbf{metals} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{47.38\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}} & \textcolor[HTML]{4285f4}{\textbf{18.07\%}} & \textcolor[HTML]{4285f4}{\textbf{34.9\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Δ\% commodity CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.93\%}}}\\
+\textbf{Δ\% commodity CHP} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.79\%}} & \textcolor[HTML]{4285f4}{\textbf{20.72\%}} & \textcolor[HTML]{4285f4}{\textbf{22.46\%}} & \textcolor[HTML]{4285f4}{\textbf{27.17\%}}\\
+\textbf{} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.19\%}} & \textcolor[HTML]{4285f4}{\textbf{21.6\%}} & \textcolor[HTML]{4285f4}{\textbf{23.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.12\%}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{33.18\%}} & \textcolor[HTML]{4285f4}{\textbf{27.86\%}} & \textcolor[HTML]{4285f4}{\textbf{29.15\%}} & \textcolor[HTML]{4285f4}{\textbf{36.24\%}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{6.23\%}} & \textcolor[HTML]{4285f4}{\textbf{10.53\%}} & \textcolor[HTML]{4285f4}{\textbf{6.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}}\\
+\textbf{} & \textbf{} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{26.68\%}} & \textcolor[HTML]{4285f4}{\textbf{20.89\%}} & \textcolor[HTML]{4285f4}{\textbf{27.19\%}} & \textcolor[HTML]{4285f4}{\textbf{31.88\%}}\\
+\addlinespace
+\textbf{} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{25.12\%}} & \textcolor[HTML]{4285f4}{\textbf{19.45\%}} & \textcolor[HTML]{4285f4}{\textbf{16\%}} & \textcolor[HTML]{4285f4}{\textbf{10.96\%}}\\
+\textbf{} & \textbf{} & \textbf{gas} & \textcolor[HTML]{4285f4}{\textbf{19.69\%}} & \textcolor[HTML]{4285f4}{\textbf{15.65\%}} & \textcolor[HTML]{4285f4}{\textbf{7.36\%}} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{26.93\%}} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}} & \textcolor[HTML]{4285f4}{\textbf{18.87\%}} & \textcolor[HTML]{4285f4}{\textbf{12.85\%}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{28.12\%}} & \textcolor[HTML]{4285f4}{\textbf{19.1\%}} & \textcolor[HTML]{4285f4}{\textbf{23.27\%}} & \textcolor[HTML]{4285f4}{\textbf{37.32\%}}\\
+\textbf{} & \textbf{} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{47.38\%}} & \textcolor[HTML]{4285f4}{\textbf{25.86\%}} & \textcolor[HTML]{4285f4}{\textbf{18.07\%}} & \textcolor[HTML]{4285f4}{\textbf{34.9\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{23.3\%}} & \textcolor[HTML]{4285f4}{\textbf{17.41\%}} & \textcolor[HTML]{4285f4}{\textbf{24.57\%}} & \textcolor[HTML]{4285f4}{\textbf{37.93\%}}\\
 \textbf{Δ\% aggregate CHP} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{5.37\%}} & \textcolor[HTML]{4285f4}{\textbf{7.12\%}} & \textcolor[HTML]{4285f4}{\textbf{14.72\%}} & \textcolor[HTML]{4285f4}{\textbf{7.49\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.23\%}}}\\
-\textbf{Δ\% aggregate CHP} & \textbf{agriculturals} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{7.25\%}} & \textcolor[HTML]{4285f4}{\textbf{5.4\%}} & \textcolor[HTML]{4285f4}{\textbf{19.75\%}} & \textcolor[HTML]{4285f4}{\textbf{8.45\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.26\%}}}\\
-\addlinespace
-\textbf{Δ\% aggregate CHP} & \textbf{agriculturals} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{5.64\%}} & \textcolor[HTML]{4285f4}{\textbf{10.35\%}} & \textcolor[HTML]{4285f4}{\textbf{6.98\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.45\%}}}\\
-\textbf{Δ\% aggregate CHP} & \textbf{energy} & \textbf{gas} & \textcolor[HTML]{4285f4}{\textbf{2.65\%}} & \textcolor[HTML]{4285f4}{\textbf{2.58\%}} & \textcolor[HTML]{4285f4}{\textbf{2.6\%}} & \textcolor[HTML]{4285f4}{\textbf{0.27\%}}\\
-\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.17\%}}}\\
-\textbf{Δ\% aggregate CHP} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{8.36\%}} & \textcolor[HTML]{4285f4}{\textbf{15.67\%}} & \textcolor[HTML]{4285f4}{\textbf{22.37\%}} & \textcolor[HTML]{4285f4}{\textbf{15.33\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Δ\% aggregate CHP}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.67\%}}}\\
-\textbf{Δ\% aggregate CHP} & \textbf{metals} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{7.92\%}} & \textcolor[HTML]{4285f4}{\textbf{16.4\%}} & \textcolor[HTML]{4285f4}{\textbf{21.98\%}} & \textcolor[HTML]{4285f4}{\textbf{17.25\%}}\\
+\textbf{} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{4.91\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{12.14\%}} & \textcolor[HTML]{4285f4}{\textbf{6.23\%}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{7.25\%}} & \textcolor[HTML]{4285f4}{\textbf{5.4\%}} & \textcolor[HTML]{4285f4}{\textbf{19.75\%}} & \textcolor[HTML]{4285f4}{\textbf{8.45\%}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{1.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{0.52\%}} & \textcolor[HTML]{4285f4}{\textbf{0.26\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{5.64\%}} & \textcolor[HTML]{4285f4}{\textbf{10.35\%}} & \textcolor[HTML]{4285f4}{\textbf{6.98\%}}\\
+\textbf{} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{3.35\%}} & \textcolor[HTML]{4285f4}{\textbf{6.27\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{2.45\%}}\\
+\textbf{} & \textbf{} & \textbf{gas} & \textcolor[HTML]{4285f4}{\textbf{2.65\%}} & \textcolor[HTML]{4285f4}{\textbf{2.58\%}} & \textcolor[HTML]{4285f4}{\textbf{2.6\%}} & \textcolor[HTML]{4285f4}{\textbf{0.27\%}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{3.59\%}} & \textcolor[HTML]{4285f4}{\textbf{7.49\%}} & \textcolor[HTML]{4285f4}{\textbf{18.9\%}} & \textcolor[HTML]{4285f4}{\textbf{3.17\%}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{8.36\%}} & \textcolor[HTML]{4285f4}{\textbf{15.67\%}} & \textcolor[HTML]{4285f4}{\textbf{22.37\%}} & \textcolor[HTML]{4285f4}{\textbf{15.33\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{10.12\%}} & \textcolor[HTML]{4285f4}{\textbf{12.74\%}} & \textcolor[HTML]{4285f4}{\textbf{23.94\%}} & \textcolor[HTML]{4285f4}{\textbf{7.67\%}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{7.92\%}} & \textcolor[HTML]{4285f4}{\textbf{16.4\%}} & \textcolor[HTML]{4285f4}{\textbf{21.98\%}} & \textcolor[HTML]{4285f4}{\textbf{17.25\%}}\\
 \bottomrule
@@
 
-\caption{\label{tbl-correlations-periods}This table shows the average
-pairwise correlation coefficients calculated independently across the
-whole cross-section of commodity assets considered in the study as well
-as across countries and commodity sectors and subsectors for the four
-periods of interest (past: 1997-2003; financialisation: 2004-2008;
-crisis: 2008-2013; post-crisis: 2013-2018). For each period, the results
-are calculated independently over the entire period as well as over
-phases of aggregate backwardation and contango. Aggregate CHP
-construction and corresponding regime definitions are discussed in
-Section~\ref{sec-methods} while the results are discussed in
-Section~\ref{sec-results} and the taxonomy for the commodity assets
-considered is detailed in Section~\ref{sec-taxonomy}.}
+\caption{\label{tbl-correlations-inner-periods}This table shows the
+average return pairwise correlation coefficients calculated
+independently across the whole cross-section of commodity assets
+considered in the study as well as within countries and commodity
+sectors and sub-sectors for the four periods of interest (past:
+1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
+2013-2018). For each period, the results are calculated independently
+over the entire period as well as over phases of aggregate backwardation
+and contango. Aggregate CHP construction and corresponding regime
+definitions are discussed in Section~\ref{sec-methods} while the results
+are discussed in Section~\ref{sec-results} and the taxonomy for the
+commodity assets considered is detailed in Section~\ref{sec-taxonomy}.}
 
@@
 \toprule
-\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0737}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1638}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2849}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1282}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0724}} & \textcolor[HTML]{4285f4}{\textbf{0.1790}} & \textcolor[HTML]{4285f4}{\textbf{0.2709}} & \textcolor[HTML]{4285f4}{\textbf{0.1001}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0748}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1501}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2985}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1495}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0737}} & \textcolor[HTML]{4285f4}{\textbf{0.1638}} & \textcolor[HTML]{4285f4}{\textbf{0.2849}} & \textcolor[HTML]{4285f4}{\textbf{0.1282}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0724}} & \textcolor[HTML]{4285f4}{\textbf{0.1790}} & \textcolor[HTML]{4285f4}{\textbf{0.2709}} & \textcolor[HTML]{4285f4}{\textbf{0.1001}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0748}} & \textcolor[HTML]{4285f4}{\textbf{0.1501}} & \textcolor[HTML]{4285f4}{\textbf{0.2985}} & \textcolor[HTML]{4285f4}{\textbf{0.1495}}\\
 \textbf{US} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0684}} & \textcolor[HTML]{4285f4}{\textbf{0.1545}} & \textcolor[HTML]{4285f4}{\textbf{0.2526}} & \textcolor[HTML]{4285f4}{\textbf{0.1096}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0642}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1697}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2323}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0859}}}\\
-\addlinespace
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0720}} & \textcolor[HTML]{4285f4}{\textbf{0.1402}} & \textcolor[HTML]{4285f4}{\textbf{0.2706}} & \textcolor[HTML]{4285f4}{\textbf{0.1268}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0910}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1305}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2322}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1075}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0799}} & \textcolor[HTML]{4285f4}{\textbf{0.1421}} & \textcolor[HTML]{4285f4}{\textbf{0.1975}} & \textcolor[HTML]{4285f4}{\textbf{0.0955}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1018}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2611}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1186}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4421}} & \textcolor[HTML]{4285f4}{\textbf{0.4898}} & \textcolor[HTML]{4285f4}{\textbf{0.5673}} & \textcolor[HTML]{4285f4}{\textbf{0.3728}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4312}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5283}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5749}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3289}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4570}} & \textcolor[HTML]{4285f4}{\textbf{0.4510}} & \textcolor[HTML]{4285f4}{\textbf{0.5675}} & \textcolor[HTML]{4285f4}{\textbf{0.4161}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3340}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2868}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3707}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3333}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3053}} & \textcolor[HTML]{4285f4}{\textbf{0.2652}} & \textcolor[HTML]{4285f4}{\textbf{0.3906}} & \textcolor[HTML]{4285f4}{\textbf{0.3220}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3605}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3150}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3557}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3483}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0391}} & \textcolor[HTML]{4285f4}{\textbf{0.0853}} & \textcolor[HTML]{4285f4}{\textbf{0.1584}} & \textcolor[HTML]{4285f4}{\textbf{0.0764}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0437}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0845}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1210}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0685}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0334}} & \textcolor[HTML]{4285f4}{\textbf{0.0874}} & \textcolor[HTML]{4285f4}{\textbf{0.1937}} & \textcolor[HTML]{4285f4}{\textbf{0.0833}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4908}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5892}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4687}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4203}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.4844}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}} & \textcolor[HTML]{4285f4}{\textbf{0.4601}} & \textcolor[HTML]{4285f4}{\textbf{0.4179}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4957}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5869}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4779}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4210}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.7278}} & \textcolor[HTML]{4285f4}{\textbf{0.7846}} & \textcolor[HTML]{4285f4}{\textbf{0.7692}} & \textcolor[HTML]{4285f4}{\textbf{0.7175}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6962}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7854}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7282}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7606}} & \textcolor[HTML]{4285f4}{\textbf{0.7856}} & \textcolor[HTML]{4285f4}{\textbf{0.7716}} & \textcolor[HTML]{4285f4}{\textbf{0.7134}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2167}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5553}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4721}}}\\
-\addlinespace
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.2201}} & \textcolor[HTML]{4285f4}{\textbf{0.5418}} & \textcolor[HTML]{4285f4}{\textbf{0.6353}} & \textcolor[HTML]{4285f4}{\textbf{0.4155}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2145}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5709}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5035}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.2883}} & \textcolor[HTML]{4285f4}{\textbf{0.6305}} & \textcolor[HTML]{4285f4}{\textbf{0.6704}} & \textcolor[HTML]{4285f4}{\textbf{0.5762}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3070}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6061}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6991}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5386}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.6591}} & \textcolor[HTML]{4285f4}{\textbf{0.6615}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4047}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4691}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6536}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4412}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3987}} & \textcolor[HTML]{4285f4}{\textbf{0.4753}} & \textcolor[HTML]{4285f4}{\textbf{0.6729}} & \textcolor[HTML]{4285f4}{\textbf{0.3954}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4108}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6456}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4797}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0642}} & \textcolor[HTML]{4285f4}{\textbf{0.1697}} & \textcolor[HTML]{4285f4}{\textbf{0.2323}} & \textcolor[HTML]{4285f4}{\textbf{0.0859}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0720}} & \textcolor[HTML]{4285f4}{\textbf{0.1402}} & \textcolor[HTML]{4285f4}{\textbf{0.2706}} & \textcolor[HTML]{4285f4}{\textbf{0.1268}}\\
+\textbf{} & \textbf{agriculturals} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0910}} & \textcolor[HTML]{4285f4}{\textbf{0.1305}} & \textcolor[HTML]{4285f4}{\textbf{0.2322}} & \textcolor[HTML]{4285f4}{\textbf{0.1075}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0799}} & \textcolor[HTML]{4285f4}{\textbf{0.1421}} & \textcolor[HTML]{4285f4}{\textbf{0.1975}} & \textcolor[HTML]{4285f4}{\textbf{0.0955}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.1018}} & \textcolor[HTML]{4285f4}{\textbf{0.1184}} & \textcolor[HTML]{4285f4}{\textbf{0.2611}} & \textcolor[HTML]{4285f4}{\textbf{0.1186}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4421}} & \textcolor[HTML]{4285f4}{\textbf{0.4898}} & \textcolor[HTML]{4285f4}{\textbf{0.5673}} & \textcolor[HTML]{4285f4}{\textbf{0.3728}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.4312}} & \textcolor[HTML]{4285f4}{\textbf{0.5283}} & \textcolor[HTML]{4285f4}{\textbf{0.5749}} & \textcolor[HTML]{4285f4}{\textbf{0.3289}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4570}} & \textcolor[HTML]{4285f4}{\textbf{0.4510}} & \textcolor[HTML]{4285f4}{\textbf{0.5675}} & \textcolor[HTML]{4285f4}{\textbf{0.4161}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.3340}} & \textcolor[HTML]{4285f4}{\textbf{0.2868}} & \textcolor[HTML]{4285f4}{\textbf{0.3707}} & \textcolor[HTML]{4285f4}{\textbf{0.3333}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3053}} & \textcolor[HTML]{4285f4}{\textbf{0.2652}} & \textcolor[HTML]{4285f4}{\textbf{0.3906}} & \textcolor[HTML]{4285f4}{\textbf{0.3220}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.3605}} & \textcolor[HTML]{4285f4}{\textbf{0.3150}} & \textcolor[HTML]{4285f4}{\textbf{0.3557}} & \textcolor[HTML]{4285f4}{\textbf{0.3483}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{softs} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0391}} & \textcolor[HTML]{4285f4}{\textbf{0.0853}} & \textcolor[HTML]{4285f4}{\textbf{0.1584}} & \textcolor[HTML]{4285f4}{\textbf{0.0764}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0437}} & \textcolor[HTML]{4285f4}{\textbf{0.0845}} & \textcolor[HTML]{4285f4}{\textbf{0.1210}} & \textcolor[HTML]{4285f4}{\textbf{0.0685}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0334}} & \textcolor[HTML]{4285f4}{\textbf{0.0874}} & \textcolor[HTML]{4285f4}{\textbf{0.1937}} & \textcolor[HTML]{4285f4}{\textbf{0.0833}}\\
+\textbf{} & \textbf{energy} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4908}} & \textcolor[HTML]{4285f4}{\textbf{0.5892}} & \textcolor[HTML]{4285f4}{\textbf{0.4687}} & \textcolor[HTML]{4285f4}{\textbf{0.4203}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.4844}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}} & \textcolor[HTML]{4285f4}{\textbf{0.4601}} & \textcolor[HTML]{4285f4}{\textbf{0.4179}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4957}} & \textcolor[HTML]{4285f4}{\textbf{0.5869}} & \textcolor[HTML]{4285f4}{\textbf{0.4779}} & \textcolor[HTML]{4285f4}{\textbf{0.4210}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.7278}} & \textcolor[HTML]{4285f4}{\textbf{0.7846}} & \textcolor[HTML]{4285f4}{\textbf{0.7692}} & \textcolor[HTML]{4285f4}{\textbf{0.7175}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.6962}} & \textcolor[HTML]{4285f4}{\textbf{0.7854}} & \textcolor[HTML]{4285f4}{\textbf{0.7727}} & \textcolor[HTML]{4285f4}{\textbf{0.7282}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7606}} & \textcolor[HTML]{4285f4}{\textbf{0.7856}} & \textcolor[HTML]{4285f4}{\textbf{0.7716}} & \textcolor[HTML]{4285f4}{\textbf{0.7134}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.2167}} & \textcolor[HTML]{4285f4}{\textbf{0.5553}} & \textcolor[HTML]{4285f4}{\textbf{0.5877}} & \textcolor[HTML]{4285f4}{\textbf{0.4721}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.2201}} & \textcolor[HTML]{4285f4}{\textbf{0.5418}} & \textcolor[HTML]{4285f4}{\textbf{0.6353}} & \textcolor[HTML]{4285f4}{\textbf{0.4155}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.2145}} & \textcolor[HTML]{4285f4}{\textbf{0.5727}} & \textcolor[HTML]{4285f4}{\textbf{0.5709}} & \textcolor[HTML]{4285f4}{\textbf{0.5035}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.2883}} & \textcolor[HTML]{4285f4}{\textbf{0.6305}} & \textcolor[HTML]{4285f4}{\textbf{0.6704}} & \textcolor[HTML]{4285f4}{\textbf{0.5762}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3070}} & \textcolor[HTML]{4285f4}{\textbf{0.6061}} & \textcolor[HTML]{4285f4}{\textbf{0.6991}} & \textcolor[HTML]{4285f4}{\textbf{0.5386}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.6591}} & \textcolor[HTML]{4285f4}{\textbf{0.6615}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}}\\
+\addlinespace
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4047}} & \textcolor[HTML]{4285f4}{\textbf{0.4691}} & \textcolor[HTML]{4285f4}{\textbf{0.6536}} & \textcolor[HTML]{4285f4}{\textbf{0.4412}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3987}} & \textcolor[HTML]{4285f4}{\textbf{0.4753}} & \textcolor[HTML]{4285f4}{\textbf{0.6729}} & \textcolor[HTML]{4285f4}{\textbf{0.3954}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4108}} & \textcolor[HTML]{4285f4}{\textbf{0.4652}} & \textcolor[HTML]{4285f4}{\textbf{0.6456}} & \textcolor[HTML]{4285f4}{\textbf{0.4797}}\\
 \bottomrule
@@
 
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-correlations-cross-periods}This table shows the
+average return pairwise correlation coefficients between equally
+weighted US sub-sector portfolios (agriculturals: gains, livestock,
+softs; energy: gas, petroleum; metals: base, precious). The results are
+independently calculated for the four periods of interest (past:
+1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
+2013-2018). For each period, the results are further calculated
+independently over the entire period as well as over phases of aggregate
+backwardation and contango. Aggregate CHP construction and corresponding
+regime definitions are discussed in Section~\ref{sec-methods} while the
+results are discussed in Section~\ref{sec-results} and the taxonomy for
+the commodity assets considered is detailed in
+Section~\ref{sec-taxonomy}.}
+
+\tabularnewline
+
+\toprule
+\textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\midrule
+\textbf{whole period} & \textcolor[HTML]{4285f4}{0.0421} & \textcolor[HTML]{4285f4}{0.0631} & \textcolor[HTML]{4285f4}{0.0799} & \textcolor[HTML]{4285f4}{0.0778}\\
+\textbf{backwardation} & \textcolor[HTML]{4285f4}{0.1166} & \textcolor[HTML]{4285f4}{0.0201} & \textcolor[HTML]{4285f4}{0.0633} & \textcolor[HTML]{4285f4}{0.0727}\\
+\textbf{contango} & \textcolor[HTML]{4285f4}{0.0297} & \textcolor[HTML]{4285f4}{0.1164} & \textcolor[HTML]{4285f4}{0.0889} & \textcolor[HTML]{4285f4}{0.0812}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
+\newpage
+
+\newpage
+
 \begin{landscape}\begingroup\fontsize{7}{9}\selectfont
@@
 
-\caption{\label{tbl-correlations-years}This table shows the average
-pairwise correlation coefficients calculated independently across the
-whole cross-section of commodity assets considered in the study as well
-as across countries and commodity sectors and subsectors by year for the
-whole period of interest (1997-2018). The results are discussed in
+\caption{\label{tbl-correlations-inner-years}While
+Table~\ref{tbl-correlations-inner-periods} shows results calculated
+independently for the four periods of interest (past: 1997-2003;
+financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018),
+this stable shows the results of the same analysis calculated by year
+over the entire sample period (1997-2018). The results are discussed in
 Section~\ref{sec-results} while Section~\ref{sec-taxonomy} details the
@@
 \toprule
-\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{decade}} & \textcolor{black}{\textbf{0}} & \textcolor{black}{\textbf{1}} & \textcolor{black}{\textbf{2}} & \textcolor{black}{\textbf{3}} & \textcolor{black}{\textbf{4}} & \textcolor{black}{\textbf{5}} & \textcolor{black}{\textbf{6}} & \textcolor{black}{\textbf{7}} & \textcolor{black}{\textbf{8}} & \textcolor{black}{\textbf{9}}\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{decade}} & \textcolor{black}{\textbf{0}} & \textcolor{black}{\textbf{1}} & \textcolor{black}{\textbf{2}} & \textcolor{black}{\textbf{3}} & \textcolor{black}{\textbf{4}} & \textcolor{black}{\textbf{5}} & \textcolor{black}{\textbf{6}} & \textcolor{black}{\textbf{7}} & \textcolor{black}{\textbf{8}} & \textcolor{black}{\textbf{9}}\\
 \midrule
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0401}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0812}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0822}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0652}} & \textcolor[HTML]{4285f4}{\textbf{0.0719}} & \textcolor[HTML]{4285f4}{\textbf{0.0796}} & \textcolor[HTML]{4285f4}{\textbf{0.0848}} & \textcolor[HTML]{4285f4}{\textbf{0.1242}} & \textcolor[HTML]{4285f4}{\textbf{0.1247}} & \textcolor[HTML]{4285f4}{\textbf{0.1650}} & \textcolor[HTML]{4285f4}{\textbf{0.1541}} & \textcolor[HTML]{4285f4}{\textbf{0.3334}} & \textcolor[HTML]{4285f4}{\textbf{0.2913}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2743}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2837}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2235}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1432}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1139}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1547}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1339}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0963}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1374}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0401}} & \textcolor[HTML]{4285f4}{\textbf{0.0812}} & \textcolor[HTML]{4285f4}{\textbf{0.0822}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0652}} & \textcolor[HTML]{4285f4}{\textbf{0.0719}} & \textcolor[HTML]{4285f4}{\textbf{0.0796}} & \textcolor[HTML]{4285f4}{\textbf{0.0848}} & \textcolor[HTML]{4285f4}{\textbf{0.1242}} & \textcolor[HTML]{4285f4}{\textbf{0.1247}} & \textcolor[HTML]{4285f4}{\textbf{0.1650}} & \textcolor[HTML]{4285f4}{\textbf{0.1541}} & \textcolor[HTML]{4285f4}{\textbf{0.3334}} & \textcolor[HTML]{4285f4}{\textbf{0.2913}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2743}} & \textcolor[HTML]{4285f4}{\textbf{0.2837}} & \textcolor[HTML]{4285f4}{\textbf{0.2235}} & \textcolor[HTML]{4285f4}{\textbf{0.1432}} & \textcolor[HTML]{4285f4}{\textbf{0.1139}} & \textcolor[HTML]{4285f4}{\textbf{0.1547}} & \textcolor[HTML]{4285f4}{\textbf{0.1339}} & \textcolor[HTML]{4285f4}{\textbf{0.0963}} & \textcolor[HTML]{4285f4}{\textbf{0.1374}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
 \textbf{US} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0536}} & \textcolor[HTML]{4285f4}{\textbf{0.0811}} & \textcolor[HTML]{4285f4}{\textbf{0.0803}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0597}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0652}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0600}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0723}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1073}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1164}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1502}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1479}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3284}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2621}}}\\
-\addlinespace
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2275}} & \textcolor[HTML]{4285f4}{\textbf{0.2541}} & \textcolor[HTML]{4285f4}{\textbf{0.1850}} & \textcolor[HTML]{4285f4}{\textbf{0.1018}} & \textcolor[HTML]{4285f4}{\textbf{0.0986}} & \textcolor[HTML]{4285f4}{\textbf{0.1371}} & \textcolor[HTML]{4285f4}{\textbf{0.1064}} & \textcolor[HTML]{4285f4}{\textbf{0.0905}} & \textcolor[HTML]{4285f4}{\textbf{0.1197}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0827}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0916}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0918}} & \textcolor[HTML]{4285f4}{\textbf{0.0967}} & \textcolor[HTML]{4285f4}{\textbf{0.0734}} & \textcolor[HTML]{4285f4}{\textbf{0.0827}} & \textcolor[HTML]{4285f4}{\textbf{0.1111}} & \textcolor[HTML]{4285f4}{\textbf{0.1090}} & \textcolor[HTML]{4285f4}{\textbf{0.1125}} & \textcolor[HTML]{4285f4}{\textbf{0.1131}} & \textcolor[HTML]{4285f4}{\textbf{0.3034}} & \textcolor[HTML]{4285f4}{\textbf{0.2507}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2038}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2304}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1583}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0716}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0846}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1360}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1121}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1148}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1181}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.5243}} & \textcolor[HTML]{4285f4}{\textbf{0.4882}} & \textcolor[HTML]{4285f4}{\textbf{0.5650}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4870}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3851}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3402}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4473}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5335}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4594}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5040}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6325}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5681}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.5389}} & \textcolor[HTML]{4285f4}{\textbf{0.6424}} & \textcolor[HTML]{4285f4}{\textbf{0.5592}} & \textcolor[HTML]{4285f4}{\textbf{0.3199}} & \textcolor[HTML]{4285f4}{\textbf{0.3134}} & \textcolor[HTML]{4285f4}{\textbf{0.4390}} & \textcolor[HTML]{4285f4}{\textbf{0.3872}} & \textcolor[HTML]{4285f4}{\textbf{0.4123}} & \textcolor[HTML]{4285f4}{\textbf{0.3618}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2192}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3724}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3453}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.2762}} & \textcolor[HTML]{4285f4}{\textbf{0.3315}} & \textcolor[HTML]{4285f4}{\textbf{0.3243}} & \textcolor[HTML]{4285f4}{\textbf{0.3497}} & \textcolor[HTML]{4285f4}{\textbf{0.2937}} & \textcolor[HTML]{4285f4}{\textbf{0.4170}} & \textcolor[HTML]{4285f4}{\textbf{0.2784}} & \textcolor[HTML]{4285f4}{\textbf{0.2744}} & \textcolor[HTML]{4285f4}{\textbf{0.2822}} & \textcolor[HTML]{4285f4}{\textbf{0.3365}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3568}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4772}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3585}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1783}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3532}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4246}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3445}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2994}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{-0.0042}} & \textcolor[HTML]{4285f4}{\textbf{-0.0001}} & \textcolor[HTML]{4285f4}{\textbf{0.0128}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0603}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0289}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0470}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0807}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0577}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0624}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0765}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.0485}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2484}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.1710}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.1273}} & \textcolor[HTML]{4285f4}{\textbf{0.1400}} & \textcolor[HTML]{4285f4}{\textbf{0.1038}} & \textcolor[HTML]{4285f4}{\textbf{0.0568}} & \textcolor[HTML]{4285f4}{\textbf{0.0413}} & \textcolor[HTML]{4285f4}{\textbf{0.0983}} & \textcolor[HTML]{4285f4}{\textbf{0.1280}} & \textcolor[HTML]{4285f4}{\textbf{0.0825}} & \textcolor[HTML]{4285f4}{\textbf{0.0565}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4060}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4552}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5256}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.4362}} & \textcolor[HTML]{4285f4}{\textbf{0.5186}} & \textcolor[HTML]{4285f4}{\textbf{0.5682}} & \textcolor[HTML]{4285f4}{\textbf{0.5248}} & \textcolor[HTML]{4285f4}{\textbf{0.6212}} & \textcolor[HTML]{4285f4}{\textbf{0.6402}} & \textcolor[HTML]{4285f4}{\textbf{0.5082}} & \textcolor[HTML]{4285f4}{\textbf{0.5530}} & \textcolor[HTML]{4285f4}{\textbf{0.6278}} & \textcolor[HTML]{4285f4}{\textbf{0.4840}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4549}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4752}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3796}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2889}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4103}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4282}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4442}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3890}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4270}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.7207}} & \textcolor[HTML]{4285f4}{\textbf{0.7946}} & \textcolor[HTML]{4285f4}{\textbf{0.8527}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7632}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8072}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6948}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8321}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7377}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7703}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7895}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8184}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7460}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.8835}} & \textcolor[HTML]{4285f4}{\textbf{0.7867}} & \textcolor[HTML]{4285f4}{\textbf{0.6692}} & \textcolor[HTML]{4285f4}{\textbf{0.6075}} & \textcolor[HTML]{4285f4}{\textbf{0.6710}} & \textcolor[HTML]{4285f4}{\textbf{0.7069}} & \textcolor[HTML]{4285f4}{\textbf{0.7547}} & \textcolor[HTML]{4285f4}{\textbf{0.6672}} & \textcolor[HTML]{4285f4}{\textbf{0.7786}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2296}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2877}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2449}}}\\
-\addlinespace
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.1860}} & \textcolor[HTML]{4285f4}{\textbf{0.1832}} & \textcolor[HTML]{4285f4}{\textbf{0.1992}} & \textcolor[HTML]{4285f4}{\textbf{0.2290}} & \textcolor[HTML]{4285f4}{\textbf{0.4923}} & \textcolor[HTML]{4285f4}{\textbf{0.4480}} & \textcolor[HTML]{4285f4}{\textbf{0.6328}} & \textcolor[HTML]{4285f4}{\textbf{0.5426}} & \textcolor[HTML]{4285f4}{\textbf{0.5664}} & \textcolor[HTML]{4285f4}{\textbf{0.5547}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6297}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6458}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6649}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6160}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4531}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4850}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4269}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3584}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5259}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.3063}} & \textcolor[HTML]{4285f4}{\textbf{0.3451}} & \textcolor[HTML]{4285f4}{\textbf{0.3308}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{2000}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2934}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2337}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3053}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2959}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5688}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6969}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6143}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6428}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6713}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.7004}} & \textcolor[HTML]{4285f4}{\textbf{0.7107}} & \textcolor[HTML]{4285f4}{\textbf{0.7089}} & \textcolor[HTML]{4285f4}{\textbf{0.6988}} & \textcolor[HTML]{4285f4}{\textbf{0.5620}} & \textcolor[HTML]{4285f4}{\textbf{0.6088}} & \textcolor[HTML]{4285f4}{\textbf{0.5652}} & \textcolor[HTML]{4285f4}{\textbf{0.4746}} & \textcolor[HTML]{4285f4}{\textbf{0.5716}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{1990}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.2289}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3601}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4487}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.3550}} & \textcolor[HTML]{4285f4}{\textbf{0.4082}} & \textcolor[HTML]{4285f4}{\textbf{0.4775}} & \textcolor[HTML]{4285f4}{\textbf{0.5526}} & \textcolor[HTML]{4285f4}{\textbf{0.5068}} & \textcolor[HTML]{4285f4}{\textbf{0.4792}} & \textcolor[HTML]{4285f4}{\textbf{0.4340}} & \textcolor[HTML]{4285f4}{\textbf{0.4653}} & \textcolor[HTML]{4285f4}{\textbf{0.5795}} & \textcolor[HTML]{4285f4}{\textbf{0.6647}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{2010}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6886}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6742}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6122}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6606}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4700}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5003}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4636}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3810}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3598}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{}}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0597}} & \textcolor[HTML]{4285f4}{\textbf{0.0652}} & \textcolor[HTML]{4285f4}{\textbf{0.0600}} & \textcolor[HTML]{4285f4}{\textbf{0.0723}} & \textcolor[HTML]{4285f4}{\textbf{0.1073}} & \textcolor[HTML]{4285f4}{\textbf{0.1164}} & \textcolor[HTML]{4285f4}{\textbf{0.1502}} & \textcolor[HTML]{4285f4}{\textbf{0.1479}} & \textcolor[HTML]{4285f4}{\textbf{0.3284}} & \textcolor[HTML]{4285f4}{\textbf{0.2621}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2275}} & \textcolor[HTML]{4285f4}{\textbf{0.2541}} & \textcolor[HTML]{4285f4}{\textbf{0.1850}} & \textcolor[HTML]{4285f4}{\textbf{0.1018}} & \textcolor[HTML]{4285f4}{\textbf{0.0986}} & \textcolor[HTML]{4285f4}{\textbf{0.1371}} & \textcolor[HTML]{4285f4}{\textbf{0.1064}} & \textcolor[HTML]{4285f4}{\textbf{0.0905}} & \textcolor[HTML]{4285f4}{\textbf{0.1197}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{} & \textbf{agriculturals} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0827}} & \textcolor[HTML]{4285f4}{\textbf{0.0916}} & \textcolor[HTML]{4285f4}{\textbf{0.1121}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0918}} & \textcolor[HTML]{4285f4}{\textbf{0.0967}} & \textcolor[HTML]{4285f4}{\textbf{0.0734}} & \textcolor[HTML]{4285f4}{\textbf{0.0827}} & \textcolor[HTML]{4285f4}{\textbf{0.1111}} & \textcolor[HTML]{4285f4}{\textbf{0.1090}} & \textcolor[HTML]{4285f4}{\textbf{0.1125}} & \textcolor[HTML]{4285f4}{\textbf{0.1131}} & \textcolor[HTML]{4285f4}{\textbf{0.3034}} & \textcolor[HTML]{4285f4}{\textbf{0.2507}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2038}} & \textcolor[HTML]{4285f4}{\textbf{0.2304}} & \textcolor[HTML]{4285f4}{\textbf{0.1583}} & \textcolor[HTML]{4285f4}{\textbf{0.0716}} & \textcolor[HTML]{4285f4}{\textbf{0.0846}} & \textcolor[HTML]{4285f4}{\textbf{0.1360}} & \textcolor[HTML]{4285f4}{\textbf{0.1121}} & \textcolor[HTML]{4285f4}{\textbf{0.1148}} & \textcolor[HTML]{4285f4}{\textbf{0.1181}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.5243}} & \textcolor[HTML]{4285f4}{\textbf{0.4882}} & \textcolor[HTML]{4285f4}{\textbf{0.5650}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.4870}} & \textcolor[HTML]{4285f4}{\textbf{0.4337}} & \textcolor[HTML]{4285f4}{\textbf{0.3851}} & \textcolor[HTML]{4285f4}{\textbf{0.3402}} & \textcolor[HTML]{4285f4}{\textbf{0.4473}} & \textcolor[HTML]{4285f4}{\textbf{0.5335}} & \textcolor[HTML]{4285f4}{\textbf{0.4594}} & \textcolor[HTML]{4285f4}{\textbf{0.5040}} & \textcolor[HTML]{4285f4}{\textbf{0.6325}} & \textcolor[HTML]{4285f4}{\textbf{0.5681}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.5389}} & \textcolor[HTML]{4285f4}{\textbf{0.6424}} & \textcolor[HTML]{4285f4}{\textbf{0.5592}} & \textcolor[HTML]{4285f4}{\textbf{0.3199}} & \textcolor[HTML]{4285f4}{\textbf{0.3134}} & \textcolor[HTML]{4285f4}{\textbf{0.4390}} & \textcolor[HTML]{4285f4}{\textbf{0.3872}} & \textcolor[HTML]{4285f4}{\textbf{0.4123}} & \textcolor[HTML]{4285f4}{\textbf{0.3618}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.2192}} & \textcolor[HTML]{4285f4}{\textbf{0.3724}} & \textcolor[HTML]{4285f4}{\textbf{0.3453}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.2762}} & \textcolor[HTML]{4285f4}{\textbf{0.3315}} & \textcolor[HTML]{4285f4}{\textbf{0.3243}} & \textcolor[HTML]{4285f4}{\textbf{0.3497}} & \textcolor[HTML]{4285f4}{\textbf{0.2937}} & \textcolor[HTML]{4285f4}{\textbf{0.4170}} & \textcolor[HTML]{4285f4}{\textbf{0.2784}} & \textcolor[HTML]{4285f4}{\textbf{0.2744}} & \textcolor[HTML]{4285f4}{\textbf{0.2822}} & \textcolor[HTML]{4285f4}{\textbf{0.3365}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.3568}} & \textcolor[HTML]{4285f4}{\textbf{0.4772}} & \textcolor[HTML]{4285f4}{\textbf{0.3585}} & \textcolor[HTML]{4285f4}{\textbf{0.1783}} & \textcolor[HTML]{4285f4}{\textbf{0.3532}} & \textcolor[HTML]{4285f4}{\textbf{0.4246}} & \textcolor[HTML]{4285f4}{\textbf{0.3445}} & \textcolor[HTML]{4285f4}{\textbf{0.2948}} & \textcolor[HTML]{4285f4}{\textbf{0.2994}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{softs} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{-0.0042}} & \textcolor[HTML]{4285f4}{\textbf{-0.0001}} & \textcolor[HTML]{4285f4}{\textbf{0.0128}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0603}} & \textcolor[HTML]{4285f4}{\textbf{0.0289}} & \textcolor[HTML]{4285f4}{\textbf{0.0470}} & \textcolor[HTML]{4285f4}{\textbf{0.0807}} & \textcolor[HTML]{4285f4}{\textbf{0.0577}} & \textcolor[HTML]{4285f4}{\textbf{0.0624}} & \textcolor[HTML]{4285f4}{\textbf{0.0765}} & \textcolor[HTML]{4285f4}{\textbf{0.0485}} & \textcolor[HTML]{4285f4}{\textbf{0.2484}} & \textcolor[HTML]{4285f4}{\textbf{0.1710}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.1273}} & \textcolor[HTML]{4285f4}{\textbf{0.1400}} & \textcolor[HTML]{4285f4}{\textbf{0.1038}} & \textcolor[HTML]{4285f4}{\textbf{0.0568}} & \textcolor[HTML]{4285f4}{\textbf{0.0413}} & \textcolor[HTML]{4285f4}{\textbf{0.0983}} & \textcolor[HTML]{4285f4}{\textbf{0.1280}} & \textcolor[HTML]{4285f4}{\textbf{0.0825}} & \textcolor[HTML]{4285f4}{\textbf{0.0565}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{} & \textbf{energy} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.4060}} & \textcolor[HTML]{4285f4}{\textbf{0.4552}} & \textcolor[HTML]{4285f4}{\textbf{0.5256}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.4362}} & \textcolor[HTML]{4285f4}{\textbf{0.5186}} & \textcolor[HTML]{4285f4}{\textbf{0.5682}} & \textcolor[HTML]{4285f4}{\textbf{0.5248}} & \textcolor[HTML]{4285f4}{\textbf{0.6212}} & \textcolor[HTML]{4285f4}{\textbf{0.6402}} & \textcolor[HTML]{4285f4}{\textbf{0.5082}} & \textcolor[HTML]{4285f4}{\textbf{0.5530}} & \textcolor[HTML]{4285f4}{\textbf{0.6278}} & \textcolor[HTML]{4285f4}{\textbf{0.4840}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.4549}} & \textcolor[HTML]{4285f4}{\textbf{0.4752}} & \textcolor[HTML]{4285f4}{\textbf{0.3796}} & \textcolor[HTML]{4285f4}{\textbf{0.2889}} & \textcolor[HTML]{4285f4}{\textbf{0.4103}} & \textcolor[HTML]{4285f4}{\textbf{0.4282}} & \textcolor[HTML]{4285f4}{\textbf{0.4442}} & \textcolor[HTML]{4285f4}{\textbf{0.3890}} & \textcolor[HTML]{4285f4}{\textbf{0.4270}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.7207}} & \textcolor[HTML]{4285f4}{\textbf{0.7946}} & \textcolor[HTML]{4285f4}{\textbf{0.8527}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.6122}} & \textcolor[HTML]{4285f4}{\textbf{0.7632}} & \textcolor[HTML]{4285f4}{\textbf{0.8072}} & \textcolor[HTML]{4285f4}{\textbf{0.6948}} & \textcolor[HTML]{4285f4}{\textbf{0.8321}} & \textcolor[HTML]{4285f4}{\textbf{0.7377}} & \textcolor[HTML]{4285f4}{\textbf{0.7703}} & \textcolor[HTML]{4285f4}{\textbf{0.7895}} & \textcolor[HTML]{4285f4}{\textbf{0.8184}} & \textcolor[HTML]{4285f4}{\textbf{0.7460}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.8835}} & \textcolor[HTML]{4285f4}{\textbf{0.7867}} & \textcolor[HTML]{4285f4}{\textbf{0.6692}} & \textcolor[HTML]{4285f4}{\textbf{0.6075}} & \textcolor[HTML]{4285f4}{\textbf{0.6710}} & \textcolor[HTML]{4285f4}{\textbf{0.7069}} & \textcolor[HTML]{4285f4}{\textbf{0.7547}} & \textcolor[HTML]{4285f4}{\textbf{0.6672}} & \textcolor[HTML]{4285f4}{\textbf{0.7786}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.2296}} & \textcolor[HTML]{4285f4}{\textbf{0.2877}} & \textcolor[HTML]{4285f4}{\textbf{0.2449}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.1860}} & \textcolor[HTML]{4285f4}{\textbf{0.1832}} & \textcolor[HTML]{4285f4}{\textbf{0.1992}} & \textcolor[HTML]{4285f4}{\textbf{0.2290}} & \textcolor[HTML]{4285f4}{\textbf{0.4923}} & \textcolor[HTML]{4285f4}{\textbf{0.4480}} & \textcolor[HTML]{4285f4}{\textbf{0.6328}} & \textcolor[HTML]{4285f4}{\textbf{0.5426}} & \textcolor[HTML]{4285f4}{\textbf{0.5664}} & \textcolor[HTML]{4285f4}{\textbf{0.5547}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.6297}} & \textcolor[HTML]{4285f4}{\textbf{0.6458}} & \textcolor[HTML]{4285f4}{\textbf{0.6649}} & \textcolor[HTML]{4285f4}{\textbf{0.6160}} & \textcolor[HTML]{4285f4}{\textbf{0.4531}} & \textcolor[HTML]{4285f4}{\textbf{0.4850}} & \textcolor[HTML]{4285f4}{\textbf{0.4269}} & \textcolor[HTML]{4285f4}{\textbf{0.3584}} & \textcolor[HTML]{4285f4}{\textbf{0.5259}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.3063}} & \textcolor[HTML]{4285f4}{\textbf{0.3451}} & \textcolor[HTML]{4285f4}{\textbf{0.3308}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.2934}} & \textcolor[HTML]{4285f4}{\textbf{0.2337}} & \textcolor[HTML]{4285f4}{\textbf{0.3053}} & \textcolor[HTML]{4285f4}{\textbf{0.2959}} & \textcolor[HTML]{4285f4}{\textbf{0.5688}} & \textcolor[HTML]{4285f4}{\textbf{0.5674}} & \textcolor[HTML]{4285f4}{\textbf{0.6969}} & \textcolor[HTML]{4285f4}{\textbf{0.6143}} & \textcolor[HTML]{4285f4}{\textbf{0.6428}} & \textcolor[HTML]{4285f4}{\textbf{0.6713}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.7004}} & \textcolor[HTML]{4285f4}{\textbf{0.7107}} & \textcolor[HTML]{4285f4}{\textbf{0.7089}} & \textcolor[HTML]{4285f4}{\textbf{0.6988}} & \textcolor[HTML]{4285f4}{\textbf{0.5620}} & \textcolor[HTML]{4285f4}{\textbf{0.6088}} & \textcolor[HTML]{4285f4}{\textbf{0.5652}} & \textcolor[HTML]{4285f4}{\textbf{0.4746}} & \textcolor[HTML]{4285f4}{\textbf{0.5716}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\addlinespace
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.2289}} & \textcolor[HTML]{4285f4}{\textbf{0.3601}} & \textcolor[HTML]{4285f4}{\textbf{0.4487}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.3550}} & \textcolor[HTML]{4285f4}{\textbf{0.4082}} & \textcolor[HTML]{4285f4}{\textbf{0.4775}} & \textcolor[HTML]{4285f4}{\textbf{0.5526}} & \textcolor[HTML]{4285f4}{\textbf{0.5068}} & \textcolor[HTML]{4285f4}{\textbf{0.4792}} & \textcolor[HTML]{4285f4}{\textbf{0.4340}} & \textcolor[HTML]{4285f4}{\textbf{0.4653}} & \textcolor[HTML]{4285f4}{\textbf{0.5795}} & \textcolor[HTML]{4285f4}{\textbf{0.6647}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.6886}} & \textcolor[HTML]{4285f4}{\textbf{0.6742}} & \textcolor[HTML]{4285f4}{\textbf{0.6122}} & \textcolor[HTML]{4285f4}{\textbf{0.6606}} & \textcolor[HTML]{4285f4}{\textbf{0.4700}} & \textcolor[HTML]{4285f4}{\textbf{0.5003}} & \textcolor[HTML]{4285f4}{\textbf{0.4636}} & \textcolor[HTML]{4285f4}{\textbf{0.3810}} & \textcolor[HTML]{4285f4}{\textbf{0.3598}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
 \bottomrule
@@
 \toprule
-\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.8556}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9709}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0352}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9438}}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.8556}} & \textcolor[HTML]{4285f4}{\textbf{0.9709}} & \textcolor[HTML]{4285f4}{\textbf{1.0352}} & \textcolor[HTML]{4285f4}{\textbf{0.9438}}\\
 \textbf{US} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.7706}} & \textcolor[HTML]{4285f4}{\textbf{0.7965}} & \textcolor[HTML]{4285f4}{\textbf{0.8535}} & \textcolor[HTML]{4285f4}{\textbf{0.8252}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9891}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1982}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1727}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0301}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{0.4320}} & \textcolor[HTML]{4285f4}{\textbf{0.2059}} & \textcolor[HTML]{4285f4}{\textbf{0.3317}} & \textcolor[HTML]{4285f4}{\textbf{0.5484}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7213}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6900}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7953}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.7589}}}\\
-\addlinespace
-\textbf{US} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{2.3308}} & \textcolor[HTML]{4285f4}{\textbf{1.6106}} & \textcolor[HTML]{4285f4}{\textbf{1.3977}} & \textcolor[HTML]{4285f4}{\textbf{1.7639}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6992}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.7090}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0044}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2585}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{2.2080}} & \textcolor[HTML]{4285f4}{\textbf{1.5778}} & \textcolor[HTML]{4285f4}{\textbf{1.5288}} & \textcolor[HTML]{4285f4}{\textbf{1.9324}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6320}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1252}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1212}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9131}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{0.4902}} & \textcolor[HTML]{4285f4}{\textbf{1.1178}} & \textcolor[HTML]{4285f4}{\textbf{1.4140}} & \textcolor[HTML]{4285f4}{\textbf{0.8780}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.6674}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.1271}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.0480}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.9219}}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{0.9891}} & \textcolor[HTML]{4285f4}{\textbf{1.1982}} & \textcolor[HTML]{4285f4}{\textbf{1.1727}} & \textcolor[HTML]{4285f4}{\textbf{1.0301}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{0.4320}} & \textcolor[HTML]{4285f4}{\textbf{0.2059}} & \textcolor[HTML]{4285f4}{\textbf{0.3317}} & \textcolor[HTML]{4285f4}{\textbf{0.5484}}\\
+\textbf{} & \textbf{} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{0.7213}} & \textcolor[HTML]{4285f4}{\textbf{0.6900}} & \textcolor[HTML]{4285f4}{\textbf{0.7953}} & \textcolor[HTML]{4285f4}{\textbf{0.7589}}\\
+\addlinespace
+\textbf{} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{2.3308}} & \textcolor[HTML]{4285f4}{\textbf{1.6106}} & \textcolor[HTML]{4285f4}{\textbf{1.3977}} & \textcolor[HTML]{4285f4}{\textbf{1.7639}}\\
+\textbf{} & \textbf{} & \textbf{gas} & \textcolor[HTML]{4285f4}{\textbf{2.6992}} & \textcolor[HTML]{4285f4}{\textbf{1.7090}} & \textcolor[HTML]{4285f4}{\textbf{1.0044}} & \textcolor[HTML]{4285f4}{\textbf{1.2585}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{2.2080}} & \textcolor[HTML]{4285f4}{\textbf{1.5778}} & \textcolor[HTML]{4285f4}{\textbf{1.5288}} & \textcolor[HTML]{4285f4}{\textbf{1.9324}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.6320}} & \textcolor[HTML]{4285f4}{\textbf{1.1252}} & \textcolor[HTML]{4285f4}{\textbf{1.1212}} & \textcolor[HTML]{4285f4}{\textbf{0.9131}}\\
+\textbf{} & \textbf{} & \textbf{base} & \textcolor[HTML]{4285f4}{\textbf{0.4902}} & \textcolor[HTML]{4285f4}{\textbf{1.1178}} & \textcolor[HTML]{4285f4}{\textbf{1.4140}} & \textcolor[HTML]{4285f4}{\textbf{0.8780}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{0.6674}} & \textcolor[HTML]{4285f4}{\textbf{1.1271}} & \textcolor[HTML]{4285f4}{\textbf{1.0480}} & \textcolor[HTML]{4285f4}{\textbf{0.9219}}\\
 \textbf{GB} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.8520}} & \textcolor[HTML]{4285f4}{\textbf{1.1761}} & \textcolor[HTML]{4285f4}{\textbf{0.7192}}\\
@@
 \toprule
-\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}} & \textcolor{black}{\textbf{factor}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{factor}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.73\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.44\%}} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{11.82\%}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.99\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.93\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.43\%}} & \textcolor[HTML]{4285f4}{\textbf{3.78\%}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.6\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}}\\
-\addlinespace
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.54\%}} & \textcolor[HTML]{4285f4}{\textbf{5.55\%}} & \textcolor[HTML]{4285f4}{\textbf{4.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.69\%}} & \textcolor[HTML]{4285f4}{\textbf{5.47\%}} & \textcolor[HTML]{4285f4}{\textbf{3.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.12\%}}\\
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.41\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.74\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{2.95\%}} & \textcolor[HTML]{4285f4}{\textbf{5.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.39\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}}\\
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{3.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.73\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{11.26\%}} & \textcolor[HTML]{4285f4}{\textbf{23.68\%}} & \textcolor[HTML]{4285f4}{\textbf{28.95\%}} & \textcolor[HTML]{4285f4}{\textbf{13.12\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.66\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.4\%}} & \textcolor[HTML]{4285f4}{\textbf{5.8\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.54\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{6.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.14\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.29\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.79\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{5\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.82\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{2.87\%}} & \textcolor[HTML]{4285f4}{\textbf{5.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.85\%}}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{5.73\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.07\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.57\%}} & \textcolor[HTML]{4285f4}{\textbf{18.68\%}} & \textcolor[HTML]{4285f4}{\textbf{23.01\%}} & \textcolor[HTML]{4285f4}{\textbf{11.56\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.91\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.03\%}} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.11\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.21\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}} & \textcolor[HTML]{4285f4}{\textbf{1.56\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.85\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.73\%}} & \textcolor[HTML]{4285f4}{\textbf{2.16\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.27\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.55\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.69\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{29.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.27\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{14.54\%}} & \textcolor[HTML]{4285f4}{\textbf{34.68\%}} & \textcolor[HTML]{4285f4}{\textbf{38.84\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{44.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.71\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.64\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{0.78\%}} & \textcolor[HTML]{4285f4}{\textbf{2.98\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.46\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.06\%}} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.04\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{7.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.5\%}} & \textcolor[HTML]{4285f4}{\textbf{3.8\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.24\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}} & \textcolor[HTML]{4285f4}{\textbf{2.08\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{grains}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.56\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{grains} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.25\%}} & \textcolor[HTML]{4285f4}{\textbf{2.18\%}} & \textcolor[HTML]{4285f4}{\textbf{3.3\%}} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.84\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{6.2\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.94\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{2.06\%}} & \textcolor[HTML]{4285f4}{\textbf{3.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.94\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.35\%}} & \textcolor[HTML]{4285f4}{\textbf{1.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.71\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{livestock}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.47\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{livestock} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.48\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.82\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}} & \textcolor[HTML]{4285f4}{\textbf{15.58\%}} & \textcolor[HTML]{4285f4}{\textbf{8.44\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.64\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.6\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.11\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.35\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.28\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.51\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}} & \textcolor[HTML]{4285f4}{\textbf{0.9\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.3\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.41\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}} & \textcolor[HTML]{4285f4}{\textbf{2.42\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{agriculturals}} & \textbf{\cellcolor{gray!10}{softs}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.08\%}}}\\
-\textbf{US} & \textbf{agriculturals} & \textbf{softs} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.94\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.9\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{26.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{33.74\%}} & \textcolor[HTML]{4285f4}{\textbf{20.94\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.84\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{42.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.77\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{3.5\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.81\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.68\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{6.05\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{7.91\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.67\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{38.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.93\%}} & \textcolor[HTML]{4285f4}{\textbf{17.59\%}} & \textcolor[HTML]{4285f4}{\textbf{22.07\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{41.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{40.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.13\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.99\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{1.86\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.4\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.16\%}} & \textcolor[HTML]{4285f4}{\textbf{2.76\%}} & \textcolor[HTML]{4285f4}{\textbf{5.88\%}} & \textcolor[HTML]{4285f4}{\textbf{1.26\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.86\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{21.36\%}} & \textcolor[HTML]{4285f4}{\textbf{17.54\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{7.17\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.92\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.96\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.37\%}} & \textcolor[HTML]{4285f4}{\textbf{3.62\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{16.2\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.14\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.3\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.26\%}} & \textcolor[HTML]{4285f4}{\textbf{13.46\%}} & \textcolor[HTML]{4285f4}{\textbf{13.84\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{22.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.03\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{23.23\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{14.53\%}} & \textcolor[HTML]{4285f4}{\textbf{16.64\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.41\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{4.24\%}} & \textcolor[HTML]{4285f4}{\textbf{7.16\%}} & \textcolor[HTML]{4285f4}{\textbf{5.22\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{gas}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.9\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{energy} & \textbf{gas} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.48\%}} & \textcolor[HTML]{4285f4}{\textbf{6.51\%}} & \textcolor[HTML]{4285f4}{\textbf{4.6\%}} & \textcolor[HTML]{4285f4}{\textbf{4.55\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.98\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{48.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.91\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{27.65\%}} & \textcolor[HTML]{4285f4}{\textbf{37.22\%}} & \textcolor[HTML]{4285f4}{\textbf{40.79\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.71\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.99\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.14\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}} & \textcolor[HTML]{4285f4}{\textbf{0.96\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{45.97\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{31.56\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{44.02\%}} & \textcolor[HTML]{4285f4}{\textbf{27.52\%}} & \textcolor[HTML]{4285f4}{\textbf{18.61\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{47.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{43.02\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{26.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{37.7\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.57\%}} & \textcolor[HTML]{4285f4}{\textbf{4.95\%}} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{energy}} & \textbf{\cellcolor{gray!10}{petroleum}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
-\textbf{US} & \textbf{energy} & \textbf{petroleum} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{6.3\%}} & \textcolor[HTML]{4285f4}{\textbf{0.16\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{38.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.58\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.5\%}} & \textcolor[HTML]{4285f4}{\textbf{31.77\%}} & \textcolor[HTML]{4285f4}{\textbf{42.95\%}} & \textcolor[HTML]{4285f4}{\textbf{11.54\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{36.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.76\%}} & \textcolor[HTML]{4285f4}{\textbf{18.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.33\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.71\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.72\%}} & \textcolor[HTML]{4285f4}{\textbf{23.49\%}} & \textcolor[HTML]{4285f4}{\textbf{21.5\%}} & \textcolor[HTML]{4285f4}{\textbf{13.38\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.27\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{2.83\%}} & \textcolor[HTML]{4285f4}{\textbf{0.32\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.61\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.28\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.48\%}} & \textcolor[HTML]{4285f4}{\textbf{7.31\%}} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.51\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.33\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.57\%}} & \textcolor[HTML]{4285f4}{\textbf{8.4\%}} & \textcolor[HTML]{4285f4}{\textbf{16.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{50.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.74\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{4.96\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}} & \textcolor[HTML]{4285f4}{\textbf{48.58\%}} & \textcolor[HTML]{4285f4}{\textbf{10.15\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.55\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{52.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{27.5\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.58\%}} & \textcolor[HTML]{4285f4}{\textbf{5.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.29\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.18\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.46\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{1.84\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.06\%}} & \textcolor[HTML]{4285f4}{\textbf{9.72\%}} & \textcolor[HTML]{4285f4}{\textbf{9.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{base}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.44\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.12\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{base} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{11.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.08\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.3\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.13\%}} & \textcolor[HTML]{4285f4}{\textbf{33.37\%}} & \textcolor[HTML]{4285f4}{\textbf{41.54\%}} & \textcolor[HTML]{4285f4}{\textbf{11.89\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{32.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.88\%}}}\\
-\addlinespace
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{25.76\%}} & \textcolor[HTML]{4285f4}{\textbf{23.19\%}} & \textcolor[HTML]{4285f4}{\textbf{15.84\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.72\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{18.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.81\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.76\%}} & \textcolor[HTML]{4285f4}{\textbf{26.82\%}} & \textcolor[HTML]{4285f4}{\textbf{16.5\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.56\%}} & \textcolor[HTML]{4285f4}{\textbf{0.68\%}} & \textcolor[HTML]{4285f4}{\textbf{3.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.21\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}} & \textcolor[HTML]{4285f4}{\textbf{6.71\%}} & \textcolor[HTML]{4285f4}{\textbf{16.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\textbf{\cellcolor{gray!10}{US}} & \textbf{\cellcolor{gray!10}{metals}} & \textbf{\cellcolor{gray!10}{precious}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
-\textbf{US} & \textbf{metals} & \textbf{precious} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{4.46\%}} & \textcolor[HTML]{4285f4}{\textbf{7.58\%}} & \textcolor[HTML]{4285f4}{\textbf{17.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.31\%}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.75\%}}}\\
-\addlinespace
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{13.03\%}} & \textcolor[HTML]{4285f4}{\textbf{34.39\%}} & \textcolor[HTML]{4285f4}{\textbf{6.62\%}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{market}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{33.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{CHP}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.09\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.72\%}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{CHP} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.03\%}} & \textcolor[HTML]{4285f4}{\textbf{3.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{whole period}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.42\%}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{open interest} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{open interest}} & \textbf{\cellcolor{gray!10}{contango}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.7\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.28\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
-\textbf{\cellcolor{gray!10}{GB}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{all}} & \textbf{\cellcolor{gray!10}{term structure}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.17\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.09\%}}}\\
-\addlinespace
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{term structure} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{6.72\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.69\%}} & \textcolor[HTML]{4285f4}{\textbf{19.7\%}} & \textcolor[HTML]{4285f4}{\textbf{31.3\%}} & \textcolor[HTML]{4285f4}{\textbf{14.73\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.44\%}} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{11.82\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{10.07\%}} & \textcolor[HTML]{4285f4}{\textbf{18.15\%}} & \textcolor[HTML]{4285f4}{\textbf{32.67\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.92\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.43\%}} & \textcolor[HTML]{4285f4}{\textbf{3.78\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.6\%}} & \textcolor[HTML]{4285f4}{\textbf{5.61\%}} & \textcolor[HTML]{4285f4}{\textbf{4\%}} & \textcolor[HTML]{4285f4}{\textbf{4.57\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{5.55\%}} & \textcolor[HTML]{4285f4}{\textbf{4.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.98\%}} & \textcolor[HTML]{4285f4}{\textbf{5.63\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.69\%}} & \textcolor[HTML]{4285f4}{\textbf{5.47\%}} & \textcolor[HTML]{4285f4}{\textbf{3.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.12\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{6.41\%}} & \textcolor[HTML]{4285f4}{\textbf{6.21\%}} & \textcolor[HTML]{4285f4}{\textbf{4.73\%}} & \textcolor[HTML]{4285f4}{\textbf{4.74\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{2.95\%}} & \textcolor[HTML]{4285f4}{\textbf{5.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.39\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.7\%}} & \textcolor[HTML]{4285f4}{\textbf{4.56\%}} & \textcolor[HTML]{4285f4}{\textbf{2.3\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{3.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{21.7\%}} & \textcolor[HTML]{4285f4}{\textbf{30.69\%}} & \textcolor[HTML]{4285f4}{\textbf{15.73\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{11.26\%}} & \textcolor[HTML]{4285f4}{\textbf{23.68\%}} & \textcolor[HTML]{4285f4}{\textbf{28.95\%}} & \textcolor[HTML]{4285f4}{\textbf{13.12\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{12.22\%}} & \textcolor[HTML]{4285f4}{\textbf{19.97\%}} & \textcolor[HTML]{4285f4}{\textbf{32.48\%}} & \textcolor[HTML]{4285f4}{\textbf{17.66\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.38\%}} & \textcolor[HTML]{4285f4}{\textbf{5.8\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{3.19\%}} & \textcolor[HTML]{4285f4}{\textbf{5.94\%}} & \textcolor[HTML]{4285f4}{\textbf{4.72\%}} & \textcolor[HTML]{4285f4}{\textbf{5.54\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{6.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.14\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{7.45\%}} & \textcolor[HTML]{4285f4}{\textbf{6.95\%}} & \textcolor[HTML]{4285f4}{\textbf{4.57\%}} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.79\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{5\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.95\%}} & \textcolor[HTML]{4285f4}{\textbf{7.61\%}} & \textcolor[HTML]{4285f4}{\textbf{5.24\%}} & \textcolor[HTML]{4285f4}{\textbf{5.82\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{2.87\%}} & \textcolor[HTML]{4285f4}{\textbf{5.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.3\%}} & \textcolor[HTML]{4285f4}{\textbf{2.78\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}} & \textcolor[HTML]{4285f4}{\textbf{2.85\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{5.73\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}}\\
+\textbf{} & \textbf{agriculturals} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.08\%}} & \textcolor[HTML]{4285f4}{\textbf{16.04\%}} & \textcolor[HTML]{4285f4}{\textbf{25.99\%}} & \textcolor[HTML]{4285f4}{\textbf{12.07\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.57\%}} & \textcolor[HTML]{4285f4}{\textbf{18.68\%}} & \textcolor[HTML]{4285f4}{\textbf{23.01\%}} & \textcolor[HTML]{4285f4}{\textbf{11.56\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{9.85\%}} & \textcolor[HTML]{4285f4}{\textbf{13.5\%}} & \textcolor[HTML]{4285f4}{\textbf{28.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.91\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.14\%}} & \textcolor[HTML]{4285f4}{\textbf{2.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{3.11\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}} & \textcolor[HTML]{4285f4}{\textbf{1.56\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{1.9\%}} & \textcolor[HTML]{4285f4}{\textbf{0.45\%}} & \textcolor[HTML]{4285f4}{\textbf{1\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.85\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.58\%}} & \textcolor[HTML]{4285f4}{\textbf{0.97\%}} & \textcolor[HTML]{4285f4}{\textbf{0.58\%}} & \textcolor[HTML]{4285f4}{\textbf{0.67\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.73\%}} & \textcolor[HTML]{4285f4}{\textbf{2.16\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.27\%}} & \textcolor[HTML]{4285f4}{\textbf{1.93\%}} & \textcolor[HTML]{4285f4}{\textbf{3.55\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.69\%}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{16.44\%}} & \textcolor[HTML]{4285f4}{\textbf{29.28\%}} & \textcolor[HTML]{4285f4}{\textbf{42.09\%}} & \textcolor[HTML]{4285f4}{\textbf{19.27\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{14.54\%}} & \textcolor[HTML]{4285f4}{\textbf{34.68\%}} & \textcolor[HTML]{4285f4}{\textbf{38.84\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{18.73\%}} & \textcolor[HTML]{4285f4}{\textbf{23.95\%}} & \textcolor[HTML]{4285f4}{\textbf{44.4\%}} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{0.78\%}} & \textcolor[HTML]{4285f4}{\textbf{2.98\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.77\%}} & \textcolor[HTML]{4285f4}{\textbf{2.63\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{5.46\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.06\%}} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.22\%}} & \textcolor[HTML]{4285f4}{\textbf{4.18\%}} & \textcolor[HTML]{4285f4}{\textbf{0.67\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{7.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.5\%}} & \textcolor[HTML]{4285f4}{\textbf{3.8\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.3\%}} & \textcolor[HTML]{4285f4}{\textbf{1.92\%}} & \textcolor[HTML]{4285f4}{\textbf{0.69\%}} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}} & \textcolor[HTML]{4285f4}{\textbf{2.08\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.19\%}} & \textcolor[HTML]{4285f4}{\textbf{1.87\%}} & \textcolor[HTML]{4285f4}{\textbf{3.56\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.25\%}} & \textcolor[HTML]{4285f4}{\textbf{2.18\%}} & \textcolor[HTML]{4285f4}{\textbf{3.3\%}} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.96\%}} & \textcolor[HTML]{4285f4}{\textbf{1.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.84\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{6.2\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{4.03\%}} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{11.26\%}} & \textcolor[HTML]{4285f4}{\textbf{5.94\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.63\%}} & \textcolor[HTML]{4285f4}{\textbf{2.06\%}} & \textcolor[HTML]{4285f4}{\textbf{3.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.95\%}} & \textcolor[HTML]{4285f4}{\textbf{2.94\%}} & \textcolor[HTML]{4285f4}{\textbf{3.54\%}} & \textcolor[HTML]{4285f4}{\textbf{1.94\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{1.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.71\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.3\%}} & \textcolor[HTML]{4285f4}{\textbf{0.19\%}} & \textcolor[HTML]{4285f4}{\textbf{0.28\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{1.43\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{softs} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{4.78\%}} & \textcolor[HTML]{4285f4}{\textbf{9.9\%}} & \textcolor[HTML]{4285f4}{\textbf{18.39\%}} & \textcolor[HTML]{4285f4}{\textbf{8.48\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.82\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}} & \textcolor[HTML]{4285f4}{\textbf{15.58\%}} & \textcolor[HTML]{4285f4}{\textbf{8.44\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.87\%}} & \textcolor[HTML]{4285f4}{\textbf{9.02\%}} & \textcolor[HTML]{4285f4}{\textbf{21.64\%}} & \textcolor[HTML]{4285f4}{\textbf{8.6\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.11\%}} & \textcolor[HTML]{4285f4}{\textbf{2.07\%}} & \textcolor[HTML]{4285f4}{\textbf{1.49\%}} & \textcolor[HTML]{4285f4}{\textbf{1.35\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.29\%}} & \textcolor[HTML]{4285f4}{\textbf{0.28\%}} & \textcolor[HTML]{4285f4}{\textbf{0.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.28\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.51\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}} & \textcolor[HTML]{4285f4}{\textbf{0.9\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{0.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}} & \textcolor[HTML]{4285f4}{\textbf{0.3\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.41\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}} & \textcolor[HTML]{4285f4}{\textbf{2.42\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{2.25\%}} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}}\\
+\textbf{} & \textbf{energy} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}} & \textcolor[HTML]{4285f4}{\textbf{31.57\%}} & \textcolor[HTML]{4285f4}{\textbf{38.94\%}} & \textcolor[HTML]{4285f4}{\textbf{25.9\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{26.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{33.74\%}} & \textcolor[HTML]{4285f4}{\textbf{20.94\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{26.84\%}} & \textcolor[HTML]{4285f4}{\textbf{31.47\%}} & \textcolor[HTML]{4285f4}{\textbf{42.16\%}} & \textcolor[HTML]{4285f4}{\textbf{28.77\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{3.5\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{12.81\%}} & \textcolor[HTML]{4285f4}{\textbf{1.01\%}} & \textcolor[HTML]{4285f4}{\textbf{2.97\%}} & \textcolor[HTML]{4285f4}{\textbf{5.68\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{5.95\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{7.91\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{40\%}} & \textcolor[HTML]{4285f4}{\textbf{33.46\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{38.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.93\%}} & \textcolor[HTML]{4285f4}{\textbf{17.59\%}} & \textcolor[HTML]{4285f4}{\textbf{22.07\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{41.02\%}} & \textcolor[HTML]{4285f4}{\textbf{40.42\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.99\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{1.86\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.4\%}} & \textcolor[HTML]{4285f4}{\textbf{3.75\%}} & \textcolor[HTML]{4285f4}{\textbf{4.93\%}} & \textcolor[HTML]{4285f4}{\textbf{3.4\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.16\%}} & \textcolor[HTML]{4285f4}{\textbf{2.76\%}} & \textcolor[HTML]{4285f4}{\textbf{5.88\%}} & \textcolor[HTML]{4285f4}{\textbf{1.26\%}}\\
+\textbf{} & \textbf{} & \textbf{gas} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{19.37\%}} & \textcolor[HTML]{4285f4}{\textbf{18.38\%}} & \textcolor[HTML]{4285f4}{\textbf{10.88\%}} & \textcolor[HTML]{4285f4}{\textbf{7.86\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{21.36\%}} & \textcolor[HTML]{4285f4}{\textbf{17.54\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{7.17\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{17.12\%}} & \textcolor[HTML]{4285f4}{\textbf{20.07\%}} & \textcolor[HTML]{4285f4}{\textbf{9.92\%}} & \textcolor[HTML]{4285f4}{\textbf{7.96\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.62\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{16.2\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{10.16\%}} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{11.42\%}} & \textcolor[HTML]{4285f4}{\textbf{19.3\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.46\%}} & \textcolor[HTML]{4285f4}{\textbf{5.26\%}} & \textcolor[HTML]{4285f4}{\textbf{13.46\%}} & \textcolor[HTML]{4285f4}{\textbf{13.84\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{22.08\%}} & \textcolor[HTML]{4285f4}{\textbf{27.47\%}} & \textcolor[HTML]{4285f4}{\textbf{15.46\%}} & \textcolor[HTML]{4285f4}{\textbf{16.03\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{23.23\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{14.53\%}} & \textcolor[HTML]{4285f4}{\textbf{16.64\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{20.54\%}} & \textcolor[HTML]{4285f4}{\textbf{32.65\%}} & \textcolor[HTML]{4285f4}{\textbf{16.18\%}} & \textcolor[HTML]{4285f4}{\textbf{15.41\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{4.24\%}} & \textcolor[HTML]{4285f4}{\textbf{7.16\%}} & \textcolor[HTML]{4285f4}{\textbf{5.22\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.36\%}} & \textcolor[HTML]{4285f4}{\textbf{2.03\%}} & \textcolor[HTML]{4285f4}{\textbf{11.66\%}} & \textcolor[HTML]{4285f4}{\textbf{5.9\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.48\%}} & \textcolor[HTML]{4285f4}{\textbf{6.51\%}} & \textcolor[HTML]{4285f4}{\textbf{4.6\%}} & \textcolor[HTML]{4285f4}{\textbf{4.55\%}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}} & \textcolor[HTML]{4285f4}{\textbf{35.97\%}} & \textcolor[HTML]{4285f4}{\textbf{48.3\%}} & \textcolor[HTML]{4285f4}{\textbf{31.91\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{27.65\%}} & \textcolor[HTML]{4285f4}{\textbf{37.22\%}} & \textcolor[HTML]{4285f4}{\textbf{40.79\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{30.08\%}} & \textcolor[HTML]{4285f4}{\textbf{35.26\%}} & \textcolor[HTML]{4285f4}{\textbf{52.9\%}} & \textcolor[HTML]{4285f4}{\textbf{35.71\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10.41\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.99\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{13.69\%}} & \textcolor[HTML]{4285f4}{\textbf{0.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.14\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.45\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}} & \textcolor[HTML]{4285f4}{\textbf{0.96\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{45.97\%}} & \textcolor[HTML]{4285f4}{\textbf{35.46\%}} & \textcolor[HTML]{4285f4}{\textbf{23.06\%}} & \textcolor[HTML]{4285f4}{\textbf{31.56\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{44.02\%}} & \textcolor[HTML]{4285f4}{\textbf{27.52\%}} & \textcolor[HTML]{4285f4}{\textbf{18.61\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{47.85\%}} & \textcolor[HTML]{4285f4}{\textbf{43.02\%}} & \textcolor[HTML]{4285f4}{\textbf{26.44\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.57\%}} & \textcolor[HTML]{4285f4}{\textbf{4.95\%}} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.74\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}} & \textcolor[HTML]{4285f4}{\textbf{2.68\%}} & \textcolor[HTML]{4285f4}{\textbf{2.56\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{6.3\%}} & \textcolor[HTML]{4285f4}{\textbf{0.16\%}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{7.54\%}} & \textcolor[HTML]{4285f4}{\textbf{30.79\%}} & \textcolor[HTML]{4285f4}{\textbf{38.2\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.5\%}} & \textcolor[HTML]{4285f4}{\textbf{31.77\%}} & \textcolor[HTML]{4285f4}{\textbf{42.95\%}} & \textcolor[HTML]{4285f4}{\textbf{11.54\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.63\%}} & \textcolor[HTML]{4285f4}{\textbf{30.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{23\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.76\%}} & \textcolor[HTML]{4285f4}{\textbf{18.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.66\%}} & \textcolor[HTML]{4285f4}{\textbf{20.33\%}} & \textcolor[HTML]{4285f4}{\textbf{15.15\%}} & \textcolor[HTML]{4285f4}{\textbf{12.71\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{23.49\%}} & \textcolor[HTML]{4285f4}{\textbf{21.5\%}} & \textcolor[HTML]{4285f4}{\textbf{13.38\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.91\%}} & \textcolor[HTML]{4285f4}{\textbf{3.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.27\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{2.83\%}} & \textcolor[HTML]{4285f4}{\textbf{0.32\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{4.31\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.48\%}} & \textcolor[HTML]{4285f4}{\textbf{7.31\%}} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.5\%}} & \textcolor[HTML]{4285f4}{\textbf{6.51\%}} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{0.33\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.57\%}} & \textcolor[HTML]{4285f4}{\textbf{8.4\%}} & \textcolor[HTML]{4285f4}{\textbf{16.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{base} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{23.13\%}} & \textcolor[HTML]{4285f4}{\textbf{50.77\%}} & \textcolor[HTML]{4285f4}{\textbf{19.74\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{4.96\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}} & \textcolor[HTML]{4285f4}{\textbf{48.58\%}} & \textcolor[HTML]{4285f4}{\textbf{10.15\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{5.66\%}} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{52.45\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{5.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.4\%}} & \textcolor[HTML]{4285f4}{\textbf{5.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{0.29\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}} & \textcolor[HTML]{4285f4}{\textbf{6.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.01\%}} & \textcolor[HTML]{4285f4}{\textbf{2.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.46\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{1.84\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.82\%}} & \textcolor[HTML]{4285f4}{\textbf{3.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.06\%}} & \textcolor[HTML]{4285f4}{\textbf{9.72\%}} & \textcolor[HTML]{4285f4}{\textbf{9.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}} & \textcolor[HTML]{4285f4}{\textbf{7.74\%}} & \textcolor[HTML]{4285f4}{\textbf{7.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.12\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{11.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{8.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.7\%}} & \textcolor[HTML]{4285f4}{\textbf{35.06\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.13\%}} & \textcolor[HTML]{4285f4}{\textbf{33.37\%}} & \textcolor[HTML]{4285f4}{\textbf{41.54\%}} & \textcolor[HTML]{4285f4}{\textbf{11.89\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{8.12\%}} & \textcolor[HTML]{4285f4}{\textbf{32.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.88\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{25.76\%}} & \textcolor[HTML]{4285f4}{\textbf{23.19\%}} & \textcolor[HTML]{4285f4}{\textbf{15.84\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{24.12\%}} & \textcolor[HTML]{4285f4}{\textbf{18.46\%}} & \textcolor[HTML]{4285f4}{\textbf{15.81\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.86\%}} & \textcolor[HTML]{4285f4}{\textbf{27.76\%}} & \textcolor[HTML]{4285f4}{\textbf{26.82\%}} & \textcolor[HTML]{4285f4}{\textbf{16.5\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}} & \textcolor[HTML]{4285f4}{\textbf{3.9\%}} & \textcolor[HTML]{4285f4}{\textbf{0.22\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.56\%}} & \textcolor[HTML]{4285f4}{\textbf{0.68\%}} & \textcolor[HTML]{4285f4}{\textbf{3.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.71\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{4.53\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}} & \textcolor[HTML]{4285f4}{\textbf{6.71\%}} & \textcolor[HTML]{4285f4}{\textbf{16.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}} & \textcolor[HTML]{4285f4}{\textbf{6.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.69\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{4.46\%}} & \textcolor[HTML]{4285f4}{\textbf{7.58\%}} & \textcolor[HTML]{4285f4}{\textbf{17.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.31\%}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.74\%}} & \textcolor[HTML]{4285f4}{\textbf{11.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.71\%}} & \textcolor[HTML]{4285f4}{\textbf{10.75\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{13.03\%}} & \textcolor[HTML]{4285f4}{\textbf{34.39\%}} & \textcolor[HTML]{4285f4}{\textbf{6.62\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.48\%}} & \textcolor[HTML]{4285f4}{\textbf{10.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.45\%}} & \textcolor[HTML]{4285f4}{\textbf{14.35\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}} & \textcolor[HTML]{4285f4}{\textbf{4.26\%}} & \textcolor[HTML]{4285f4}{\textbf{1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{0.72\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{0.42\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.59\%}} & \textcolor[HTML]{4285f4}{\textbf{2.7\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.28\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.17\%}} & \textcolor[HTML]{4285f4}{\textbf{2.37\%}} & \textcolor[HTML]{4285f4}{\textbf{3.67\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{6.72\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
 \bottomrule
@@
 \toprule
-\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{subsector}}\\
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}}\\
 \midrule
-\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{grains}}\\
-\textbf{Oats (XCBT)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{grains}\\
-\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{grains}}\\
-\textbf{Soybean oil (XCBT)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{grains}\\
-\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{grains}}\\
-\addlinespace
-\textbf{Wheat-SRW (XCBT)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{grains}\\
-\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{livestock}}\\
-\textbf{Cattle-live (XCME)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{livestock}\\
-\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{livestock}}\\
-\textbf{Cocoa (IFUS)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{softs}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{softs}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{softs}\\
-\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{softs}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{softs}\\
-\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{agriculturals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{softs}}\\
-\addlinespace
-\textbf{Natural gas (XNYM)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{energy} & \textcolor[HTML]{4285f4}{gas}\\
-\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{energy}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{petroleum}}\\
-\textbf{Gasoline (XNYM)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{energy} & \textcolor[HTML]{4285f4}{petroleum}\\
-\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{energy}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{petroleum}}\\
-\textbf{Copper (XCEC)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
-\addlinespace
-\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{precious}}\\
-\textbf{Silver (XCEC)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{precious}\\
-\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{US}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{precious}}\\
-\textbf{Platinum (XNYM)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{precious}\\
-\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{GB}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{base}}\\
-\addlinespace
-\textbf{Copper (XLME)} & \textcolor[HTML]{4285f4}{GB} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
-\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{GB}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{base}}\\
-\textbf{Nickel-primary (XLME)} & \textcolor[HTML]{4285f4}{GB} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
-\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{GB}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{metals}} & \textcolor[HTML]{4285f4}{\cellcolor{gray!10}{base}}\\
-\textbf{Zinc (XLME)} & \textcolor[HTML]{4285f4}{GB} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
+\textbf{Corn-\#2 yellow (XCBT)} & \textcolor[HTML]{4285f4}{US} & \textcolor[HTML]{4285f4}{agriculturals} & \textcolor[HTML]{4285f4}{grains}\\
+\textbf{Oats (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Soybean meal (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Soybean oil (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Soybeans (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{Wheat-SRW (XCBT)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Cattle-feeder (XCME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{livestock}\\
+\textbf{Cattle-live (XCME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Lean hogs (XCME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Cocoa (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{softs}\\
+\addlinespace
+\textbf{Coffee-C (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Cotton-\#2 (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Orange juice-frozen concentrated (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Sugar-\#11 (IFUS)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Lumber-random length (XCME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\addlinespace
+\textbf{Natural gas (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{energy} & \textcolor[HTML]{4285f4}{gas}\\
+\textbf{Crude oil-WTI (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{petroleum}\\
+\textbf{Gasoline (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Heating oil (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Copper (XCEC)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
+\addlinespace
+\textbf{Gold (XCEC)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{precious}\\
+\textbf{Silver (XCEC)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Palladium (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Platinum (XNYM)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Aluminium-primary (XLME)} & \textcolor[HTML]{4285f4}{GB} & \textcolor[HTML]{4285f4}{metals} & \textcolor[HTML]{4285f4}{base}\\
+\addlinespace
+\textbf{Copper (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Lead-refined pig (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Nickel-primary (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Tin-refined (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
+\textbf{Zinc (XLME)} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{} & \textcolor[HTML]{4285f4}{}\\
 \bottomrule

### 2025-01-07 explore/shiny/revision-jfm/app.r
Introduce dropdown menu for correlations
Move current correlation page to new "inner" tab in dropdown menu.

@@ -21,7 +21,10 @@ source(file.path(path_directory, "modules", "results_summary.r"))
 
 sidebar <- dashboardSidebar(
   sidebarMenu(
-    menuItem("Correlations", tabName = "correlations", icon = icon("table")),
+    menuItem("Correlations", tabName = "correlations", icon = icon("table"),
+             menuSubItem("Inner", tabName = "correlations-inner")
+    
+    ),
     menuItem("Regressions", icon = icon("table"),
              menuSubItem("Index", tabName = "regressions-index"),
              menuSubItem("Factors", tabName = "regressions-factors")
@@ -31,7 +34,7 @@ sidebar <- dashboardSidebar(
 
 body <- dashboardBody(
   tabItems(
-    tabItem(tabName = "correlations", results_summary_UI("correlations", list(
+    tabItem(tabName = "correlations-inner", results_summary_UI("correlations-inner", list(
       period = results$correlations$inner$period, year = results$correlations$inner$year
     ))),
     tabItem(tabName = "regressions-index", results_summary_UI("regressions-index", list(
@@ -48,7 +51,7 @@ ui <- dashboardPage(
 )
 
 server <- function(input, output) {
-  results_summary_Server("correlations", list(
+  results_summary_Server("correlations-inner", list(
     period = results$correlations$inner$period, year = results$correlations$inner$year
   ))
   

### 2025-01-08 explore/shiny/revision-jfm/app.r
Made EW portfolio correlations page
and included corresponding link to dropdown menu.
Closes #84, closes #85.

@@ -21,13 +21,17 @@ source(file.path(path_directory, "modules", "results_summary.r"))
 
 sidebar <- dashboardSidebar(
   sidebarMenu(
-    menuItem("Correlations", tabName = "correlations", icon = icon("table"),
-             menuSubItem("Inner", tabName = "correlations-inner")
+    menuItem("Correlations", tabName = "correlations",
+             menuItem("Inner", tabName = "correlations-inner"),
+             menuItem("Cross", tabName = "correlations-cross", 
+                      menuItem("US", tabName = "correlations-cross-US"),
+                      menuItem("Global", tabName = "correlations-cross-global")
+            )
     
     ),
-    menuItem("Regressions", icon = icon("table"),
-             menuSubItem("Index", tabName = "regressions-index"),
-             menuSubItem("Factors", tabName = "regressions-factors")
+    menuItem("Regressions",
+             menuItem("Index", tabName = "regressions-index"),
+             menuItem("Factors", tabName = "regressions-factors")
     )
   )
 )
@@ -37,6 +41,13 @@ body <- dashboardBody(
     tabItem(tabName = "correlations-inner", results_summary_UI("correlations-inner", list(
       period = results$correlations$inner$period, year = results$correlations$inner$year
     ))),
+    tabItem(tabName = "correlations-cross-US", results_summary_UI("correlations-cross-US", list(
+      period = results$correlations$cross$US$period, year = results$correlations$cross$US$year
+    ))),
+    tabItem(tabName = "correlations-cross-global", results_summary_UI("correlations-cross-global", list(
+      period = results$correlations$cross$global$period, year = results$correlations$cross$global$year
+    ))),
+    tabItem(tabName = "correlations-cross", h2("Cross")),
     tabItem(tabName = "regressions-index", results_summary_UI("regressions-index", list(
       period = results$regressions$index$period, year = results$regressions$index$year
     ))),
@@ -53,6 +64,13 @@ ui <- dashboardPage(
 server <- function(input, output) {
   results_summary_Server("correlations-inner", list(
     period = results$correlations$inner$period, year = results$correlations$inner$year
+  ))
+  
+  results_summary_Server("correlations-cross-US", list(
+    period = results$correlations$cross$US$period, year = results$correlations$cross$US$year
+  ))
+  results_summary_Server("correlations-cross-global", list(
+    period = results$correlations$cross$global$period, year = results$correlations$cross$global$year
   ))
   
   results_summary_Server("regressions-index", list(

### 2025-01-08 explore/shiny/revision-jfm/datasets.r

@@ -100,6 +100,17 @@ correlations_inner_split <- split_analysis_summary_results_into_category_datafra
   correlations_inner_raw, correlations_inner_helpers
   )
 
+correlations_cross_split <- purrr::map(c("US", "global"), function(x){
+  file_name <- paste0("correlations-cross-", x, ".rds")
+  results <- readr::read_rds(file.path(path_directory, "results", file_name))
+  periods <- results$summary[[1L]] |> tidyr::pivot_wider(names_from = period, values_from = average)
+  years <- results$summary[[2L]] |> tidyr::pivot_wider(names_from = year, values_from = average)
+  
+  list(period = list(Average = periods), year = list(Average = years))
+  }
+) |> setNames(c("US", "global"))
+
+
 regressions_index_raw <- readr::read_rds(file.path(path_directory, "results", "regressions-index.rds"))
 regressions_index_helpers <- list(
   period = list(
@@ -140,6 +151,6 @@ regressions_factors_split <- split_analysis_summary_results_into_category_datafr
 
 
 results <- list(
-  correlations = list(inner = correlations_inner_split), 
+  correlations = list(inner = correlations_inner_split, cross = correlations_cross_split), 
   regressions = list(index = regressions_index_split, factors = regressions_factors_split)
 )

### 2025-01-08 docs/paper.tex
Introduced reference to updated dashboard in paper
as "internet appendix". Closes #86.

@@
 \makeatother
-\journal{Journal of Futures Markets}
+\journal{the Journal of Futures Markets}
 
@@
 pairwise correlation coefficients between equally weighted portfolios of
-US traded commodity assets grouped by sub-sector. Although modest in
-magnitude, these exhibit a telling pattern, mirroring that shown by the
-individual commodity returns in Table~\ref{tbl-stats-combined}, with a
-substantially higher average coefficient over \textbf{backwardation}
-phases in the first period (0.12 vs.~0.03) and the pattern reversed over
-financilisation with an average coefficient substantially higher in
-\textbf{contango} (0.12 vs.~0.02).\\
+US traded commodity assets grouped by sub-sector\footnote{A more
+  detailed breakdown of country, sector and subsector average pairwise
+  correlations is provided in the attached
+  \href{http://bautheac.duckdns.org:3838/bautheac/revision-jfm/}{Internet
+  Appendix}.}. Although modest in magnitude, these exhibit a telling
+pattern, mirroring that shown by the individual commodity returns in
+Table~\ref{tbl-stats-combined}, with a substantially higher average
+coefficient over \textbf{backwardation} phases in the first period (0.12
+vs.~0.03) and the pattern reversed over financilisation with an average
+coefficient substantially higher in \textbf{contango} (0.12 vs.~0.02).\\
 We break down Table~\ref{tbl-correlations-inner-periods}'s average
@@
 
+\newpage
+
 \begingroup\fontsize{7}{9}\selectfont

### 2025-01-08 docs/paper.qmd

@@
     journal:  
-      name: Journal of Futures Markets
+      name: the Journal of Futures Markets
       formatting: preprint
@@
 The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods.
-In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector.
+In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector^[A more detailed breakdown of country, sector and subsector average pairwise correlations is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/revision-jfm/).].
 Although modest in magnitude, these exhibit a telling pattern, mirroring that shown by the individual commodity returns in @tbl-stats-combined, with a substantially higher average coefficient over **backwardation** phases in the first period (0.12 vs.
@@
 
+\newpage
+
 ```{r}
@@
 make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
-```
-
-\newpage
-
-```{r}
-#| eval: false
-#| label: tbl-experimental
-#| tbl-cap: "lorem ipsum dolor sit amet consectetur adipiscing elit sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident sunt in culpa qui officia deserunt mollit anim id est laborum.
-Lorem ipsum dolor sit amet consectetur adipiscing elit sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident sunt in culpa qui officia deserunt mollit anim id est laborum."
-#| tbl-subcap: 
-#|     - "Average pairwise inner correlations"
-#|     - "Average pairwise cross correlations"
-#| layout-nrows: 2
-
-table1_format <- list(
-  table_name = "correlations - inner - periods",
-  columns_to_collapse_rows_for = c("country", "sector", "subsector"),
-  longtable = FALSE,
-  colnames = c(sectors, "regime", periods),
-  align = make_series_of_repeated_chars(list(l = 3L, r = 5L)),
-  bold_columns = 1L:8L, 
-  coloured_columns = 5L:8L
-  )
-table2_format <- list(
-  table_name = "correlations - cross - periods",
-  columns_to_collapse_rows_for = c("portfolios", "regime"),
-  longtable = TRUE,
-  colnames = c("portfolios", "regime", periods),
-  align = make_series_of_repeated_chars(list(l = 1L, r = 5L)),
-  bold_columns = 1L:2L, 
-  coloured_columns = 3L:6L
-)
-formats <- list(table1_format, table2_format)
-
-get_results(tables, table1_format$table_name) %>% dplyr::mutate(dplyr::across(dplyr::where(is.factor), as.character)) %>%
-    collapse_rows(table1_format$columns_to_collapse_rows_for) %>%
-    kable(booktabs = T, longtable = table1_format$longtable, col.names = table1_format$colnames, align = table1_format$align, escape = FALSE) %>%
-    kable_styling(font_size = 7L) %>%
-    row_spec(0L, bold = TRUE, color = "black") %>%
-    column_spec(table1_format$bold_columns, bold = TRUE) %>% column_spec(table1_format$coloured_columns, color = "#4285f4")
-
-get_results(tables, table2_format$table_name) %>% dplyr::mutate(dplyr::across(dplyr::where(is.factor), as.character)) %>%
-    collapse_rows(table2_format$columns_to_collapse_rows_for) %>%
-    kable(booktabs = T, longtable = table2_format$longtable, col.names = table2_format$colnames, align = table2_format$align, escape = FALSE) %>%
-    kable_styling(font_size = 7L) %>%
-    row_spec(0L, bold = TRUE, color = "black") %>%
-    column_spec(table2_format$bold_columns, bold = TRUE) %>% column_spec(table2_format$coloured_columns, color = "#4285f4")
 ```

### 2025-04-04 docs/paper.qmd
Recompile for resubmission

@@
 Data for DCOT and SCOT date back to 2006 and 2007 respectively.
-We examine the period from 1997 to 2018, during which we utilize futures-only position data from the COT report---the only CFTC report providing data for the entire duration of interest---as well as futures term structure price and open interest data sourced from Bloomberg.
+We examine the period from 1997 to 2018, during which we utilise futures-only position data from the COT report---the only CFTC report providing data for the entire duration of interest---as well as futures term structure price and open interest data sourced from Bloomberg.
 The sample period is further divided into four distinct intervals.
@@
 
+\newpage
+
 \newgeometry{margin=.75in}
 
-\newpage
-
-# Tables
+# Tables {.unnumbered}
 
@@
 
-# Appendix
+# Appendix {.unnumbered}
 

### 2025-04-04 docs/paper.tex
Recompile for resubmission

@@
 DCOT and SCOT date back to 2006 and 2007 respectively.\\
-We examine the period from 1997 to 2018, during which we utilize
+We examine the period from 1997 to 2018, during which we utilise
 futures-only position data from the COT report---the only CFTC report
@@
 
+\newpage
+
 \newgeometry{margin=.75in}
 
-\newpage
-
-\section{Tables}\label{tables}
+\section*{Tables}\label{tables}
+\addcontentsline{toc}{section}{Tables}
 
@@
 
-\section{Appendix}\label{appendix}
+\section*{Appendix}\label{appendix}
+\addcontentsline{toc}{section}{Appendix}
 

### 2025-06-30 docs/paper.qmd
Correct typos

@@
 The increase is even more pronounced for an equally weighted portfolio of GB traded assets (metals), 2.47% (not significant) to 21.8% (significant at the 10% level), which sets out the global nature of the phenomenon.
-Most commodities show a higher mean return while five---Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)---show a lower figure with five og them significant---Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)---against none pre-financialisation.
+Most commodities show a higher mean return while five---Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)---show a lower figure with five of them significant---Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)---against none pre-financialisation.
 Sugar-#11 wins the race with a mean return increasing from -4.6% to 24.9% followed by copper with sizeable increases for both markets: 1.5% to 28.2% (XCEC) and 0.5% to 28.6% (XLME).

### 2025-06-30 explore/scripts/revision-jfm/functions.r
Compute ew sector portfolio returns

@@ -4,19 +4,21 @@ paste_forward_slash <- function(...) paste(..., sep = "/")
 # load environment variables ###################################################
 ## variables ###################################################################
 ### local function #############################################################
-make_path_to_storethat_database <- function(){
+make_path_to_storethat_database <- function() {
   paste0(here::here(), "/data/storethat.sqlite")
 }
 
-make_periods_data_frame <- function(period_bounds){
-  purrr::imap_dfr(period_bounds, function(bounds, name){
-    purrr::imap_dfr(bounds, function(date, bound){
+make_periods_data_frame <- function(period_bounds) {
+  purrr::imap_dfr(period_bounds, function(bounds, name) {
+    purrr::imap_dfr(bounds, function(date, bound) {
       tibble::tibble(bound = bound, date = date)
-    }) %>% dplyr::mutate(period = name) %>% dplyr::select(period, dplyr::everything())
+    }) %>%
+      dplyr::mutate(period = name) %>%
+      dplyr::select(period, dplyr::everything())
   })
 }
 
-load_variables <- function(){
+load_variables <- function() {
   ## variables ####
   storethat_db_path <<- make_path_to_storethat_database() # assign to parent environment.
   results_directory_path <<- here::here("explore", "results", "revision-jfm")
@@ -30,178 +32,174 @@ load_variables <- function(){
 
   periods <<- make_periods_data_frame(period_bounds)
   assign(
-    "rf", readr::read_rds(here::here("data", "risk-free-rate.rds")), envir = parent.frame()
+    "rf", readr::read_rds(here::here("data", "risk-free-rate.rds")),
+    envir = parent.frame()
   ) # conflict with stat::rf if parent environment; can't use <<- here.
 }
 
 ## load data ###################################################################
 ### functions ##################################################################
 get_commodity_futures_individual_data_levels <- function(
-    commodity_futures_tickers, start, end, storethat_db_path
-    ){
-  
+    commodity_futures_tickers, start, end, storethat_db_path) {
   raw_data_object <- pullit::pull_futures_market(
-    source = "storethat", type = "term structure", 
[…]

### 2025-07-01 explore/scripts/revision-jfm/analysis.r
Compute raw ew portfolio stats

@@ -10,6 +10,14 @@ source(here::here("explore", "scripts", "revision-jfm", "functions.r"))
 pacman::p_load(furrr)
 plan(multisession, workers = parallel::detectCores())
 
+
+## descriptive stats ###########################################################
+### equally weighted portfolios ################################################
+#### raw ####
+descriptive_stats_ew_portfolios_raw <- make_ew_portfolios_stats()
+
+
+
 ## regime difference tests #####################################################
 ### raw ####
 regime_difference_tests_raw <- make_regime_difference_tests()
@@ -179,7 +187,32 @@ regressions_factors_formatted <-
   format_regression_factor_summary_statistics_into_table(regressions_factors_summary)
 
 
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
 # export #######################################################################
+## descriptive stats ###########################################################
+### raw ####
+path_descriptive_stats_ew_portfolios_raw_file <- 
+  paste_forward_slash(results_directory_path, "descriptive-stats-ew-portfolios-raw.rds")
+saveRDS(descriptive_stats_ew_portfolios_raw, path_descriptive_stats_ew_portfolios_raw_file)
+
 ## regime difference tests #####################################################
 ### raw ####
 path_regime_difference_tests_raw_file <- 

### 2025-07-01 explore/scripts/revision-jfm/functions.r

@@ -980,6 +980,21 @@ make_ticker_pools_for_stats <- function() {
     dplyr::arrange(country, sector, subsector)
 }
 
+compute_ew_sector_portfolio_returns <- function(ticker_pools) {
+  dplyr::mutate(
+    ticker_pools,
+    returns = purrr::map(tickers, function(tickers) {
+      dplyr::filter(
+        commodity_futures_data,
+        type == "return", frequency == "day", field == "PX_LAST",
+        `active contract ticker` %in% tickers
+      ) |> 
+        dplyr::select(ticker = `active contract ticker`, date, return = value) |>
+        dplyr::summarise(return = mean(return, na.rm = TRUE), .by = date)
+    })
+  )
+}
+
 make_aggregate_CHP_regimes_for_stats <- function() {
   regimes <- dplyr::mutate(
     aggregate_CHP_regimes,
@@ -997,22 +1012,40 @@ make_aggregate_CHP_regimes_for_stats <- function() {
   )
 }
 
-make_ew_sector_portfolios <- function(ticker_pools) {
+compute_ew_sector_portfolio_stats <- function(ew_sector_portfolio_returns, aggregate_CHP_regimes) {
+
   dplyr::mutate(
-    ticker_pools,
-    returns = purrr::map(tickers, function(tickers) {
-      dplyr::filter(
-        commodity_futures_data,
-        type == "return", frequency == "day", field == "PX_LAST",
-        `active contract ticker` %in% tickers
-      ) |> 
-        dplyr::select(ticker = `active contract ticker`, date, return = value) |>
-        dplyr::summarise(return = mean(return, na.rm = TRUE), .by = date)
-    })
-  )
+    ew_sector_portfolio_returns,
+    stats = purrr::map(returns, function(returns){
+      dplyr::mutate(
+        aggregate_CHP_regimes,
+        stats = purrr::map(regimes, function(regimes){
+          dplyr::left_join(regimes, returns, by = "date") |>
+            dplyr::filter(!is.na(return)) |>
+            dplyr::summarise(
+              mean = list(t.test(return, na.rm = TRUE)), volatility = sd(return, na.rm = TRUE), 
+              .by = c("regime", "period")
+            ) |> 
+            tibble::as_tibble() |>
+            dplyr::select(period, regime, mean, volatility) |> 
+            dplyr::arrange(period, regime)
+        }) 
+      ) |> dplyr::select(-regimes)
+    }) 
[…]

### 2025-07-04 explore/scripts/revision-jfm/analysis.r
Include individual asset stats in revision analysis

@@ -6,15 +6,26 @@ load(here::here("explore", "scripts", "revision-jfm", "globals.RData"))
 source(here::here("explore", "scripts", "revision-jfm", "functions.r"))
 
 # analysis #####################################################################
-
 pacman::p_load(furrr)
 plan(multisession, workers = parallel::detectCores())
 
 
 ## descriptive stats ###########################################################
+### individual assets ##########################################################
+#### formatted ####
+##### load summary dataset (optional) ####
+path_descriptive_stats_assets_summary_file <-
+  paste_forward_slash(results_directory_path, "descriptive-statistics-clean.rds")
+descriptive_stats_assets_summary <- extract_descriptive_stats_assets_summary()
+
+##### format ####
+descriptive_stats_assets_formatted <- format_asset_stats(descriptive_stats_assets_summary)
+
+
+
 ### equally weighted portfolios ################################################
 #### raw ####
-descriptive_stats_ew_portfolios_raw <- make_ew_portfolios_stats_raw()
+descriptive_stats_ew_portfolios_raw <- compute_ew_portfolios_stats_raw()
 
 #### summary ####
 ##### load raw dataset (optional) ####
@@ -23,7 +34,19 @@ descriptive_stats_ew_portfolios_raw <- make_ew_portfolios_stats_raw()
 # descriptive_stats_ew_portfolios_raw <- readr::read_rds(path_descriptive_stats_ew_portfolios_raw_file)
 
 ##### summarise ####
-descriptive_stats_ew_portfolios_summary <- make_ew_portfolios_stats_summary(descriptive_stats_ew_portfolios_raw)
+descriptive_stats_ew_portfolios_summary <- 
+  summarise_ew_portfolios_stats(descriptive_stats_ew_portfolios_raw)
+
+#### formatted ####
+##### load summary dataset (optional) ####
+# path_descriptive_stats_ew_portfolios_summary_file <- 
+#   paste_forward_slash(results_directory_path, "descriptive-stats-ew-portfolios-summary.rds")
+# descriptive_stats_ew_portfolios_summary <- 
+#   readr::read_rds(path_descriptive_stats_ew_portfolios_summary_file)
+
+##### format ####
+descriptive_stats_ew_portfolios_formatted <- 
+  format_ew_portfolios_stats(descriptive_stats_ew_portfolios_summary)
 
 
 
@@ -42,9 +65,9 @@ regime_difference_tests_summary <- extract_pvalues_from_test_objects(regime_diff
 
 ### formatted ####
[…]

### 2025-07-04 explore/scripts/revision-jfm/functions.r

@@ -943,6 +943,54 @@ make_analysis_for_ticker_combinations_dataframe <- function(
   })
 }
 
+## descriptive stats for individual assets #####################################
+
+extract_descriptive_stats_assets_summary <- function(){
+  readr::read_rds(path_descriptive_stats_assets_summary_file) |>
+    dplyr::filter(analysis == "commodity futures") |> dplyr::select(results) |>
+    tidyr::unnest(results) |> dplyr::filter(analysis == "market variables") |>
+    dplyr::select(results) |> tidyr::unnest(results) |> 
+    dplyr::filter(assets == "individual commodities") |> dplyr::select(results) |>
+    tidyr::unnest(results)
+}
+
+format_asset_stats <- function(stats_assets_summary) {
+  sort_levels <- c(
+    "all-all-all", "US-all-all", "US-agriculturals-all", "US-agriculturals-grains",
+    "US-agriculturals-livestock", "US-agriculturals-softs", "US-energy-all", 
+    "US-energy-gas", "US-energy-petroleum", "US-metals-all", "US-metals-base", 
+    "US-metals-precious", "GB-all-all"
+  )
+  
+  subset <- dplyr::filter(
+    stats_assets_summary, type == "returns", frequency == "daily", field == "close price"
+  ) |>
+    dplyr::mutate(
+      sort = paste0(country, "-", sector, "-", subsector) |> factor(levels = sort_levels)
+    ) |>
+    dplyr::arrange(sort, commodity) |>
+    dplyr::select(commodity, period, year, regime, mean, p.value, volatility = sd) |>
+    dplyr::mutate(
+      regime = ifelse(regime == "all", "whole period", regime),
+      regime = factor(regime, levels = c("whole period", "backwardation", "contango")),
+      period = as.character(period),
+      period = ifelse(period == "financialization", "financialisation", period),
+      period = ifelse(period == "present", "post-crisis", period),
+      period = factor(period, levels = c("past", "financialisation", "crisis", "post-crisis", "year")),
+      dplyr::across(c(mean, volatility), ~ slituR::percentize(.x)),
+      significance = slituR::significance(unlist(p.value)),
+      mean = paste0(significance, mean)
+    ) |> dplyr::select(-c(p.value, significance)) |>
+    tidyr::pivot_longer(cols = c(mean, volatility), names_to = "statistic", values_to = "value")
+  
+  periods <- dplyr::filter(subset, period != "year") |> dplyr::select(-year) |>
[…]

### 2025-07-04 explore/scripts/revision-jfm/tables.r
Update tables layout
Streamline and combine table 1 and 2; streamline table 8 (now 7)

@@ -76,8 +76,10 @@ long_to_short_asset_name_map <- tibble::tribble(
   dplyr::relocate(country, .after = asset) |>
   dplyr::arrange(country, sector, subsector) 
 
+readr::write_rds(`assets taxonomy`, slituR::paste_forward_slash(tables_directory_path, "assets-taxonomy.rds"))
 
 # descriptive stats ############################################################
+## individual assets ###########################################################
 stats <- readr::read_rds(
   slituR::paste_forward_slash(results_directory_path, "descriptive-statistics-clean.rds")
   )
@@ -106,7 +108,7 @@ commodities_market_countries <- dplyr::filter(stats, analysis == "commodity futu
   ) |> dplyr::select(-c(type, frequency, field, year)) |>
   dplyr::mutate_if(.predicate = is.list, .funs = unlist)
 
-## whole ####
+### whole ####
 commodities <- dplyr::filter(commodities_market_individuals, regime == "all") |>
   dplyr::select(-c(regime, min, max)) |> 
   dplyr::mutate(
@@ -132,9 +134,9 @@ countries <- dplyr::filter(commodities_market_countries, regime == "all") |>
     cols = c("mean", "sd"), names_to = "estimate", values_to = "value"
   ) |> tidyr::pivot_wider(names_from = "period", values_from = "value")
 
-descriptive_stats_whole <- dplyr::bind_rows(commodities, countries)
+descriptive_stats_individuals_whole <- dplyr::bind_rows(commodities, countries)
 
-## regimes ####
+### regimes ####
 commodities <- dplyr::filter(commodities_market_individuals, regime != "all") |>
   dplyr::select(-c(min, max)) |> 
   dplyr::mutate(
@@ -160,9 +162,9 @@ countries <- dplyr::filter(commodities_market_countries, regime != "all") |>
     cols = c("mean", "sd"), names_to = "estimate", values_to = "value"
   ) |> tidyr::pivot_wider(names_from = "period", values_from = "value")
 
-descriptive_stats_regimes <- dplyr::bind_rows(commodities, countries)
+descriptive_stats_individuals_regimes <- dplyr::bind_rows(commodities, countries)
 
-## combined ####
+### combined ####
 commodities <- dplyr::select(commodities_market_individuals, -c(min, max)) |> 
   dplyr::mutate(
     mean = slituR::percentize(mean), sd = slituR::percentize(sd),
[…]

### 2025-07-04 explore/shiny/revision-jfm/app.r
Updated Shiny app
Include individual asset stats and tests of difference

@@ -21,6 +21,10 @@ source(file.path(path_directory, "modules", "results_summary.r"))
 
 sidebar <- dashboardSidebar(
   sidebarMenu(
+    menuItem("Stats", tabName = "stats",
+             menuItem("Descriptive", tabName = "stats-descriptive"),
+             menuItem("Regime ≠ tests", tabName = "stats-difference-tests")
+             ),
     menuItem("Correlations", tabName = "correlations",
              menuItem("Inner", tabName = "correlations-inner"),
              menuItem("Cross", tabName = "correlations-cross", 
@@ -38,6 +42,12 @@ sidebar <- dashboardSidebar(
 
 body <- dashboardBody(
   tabItems(
+    tabItem(tabName = "stats-descriptive", results_summary_UI("stats-descriptive", list(
+      period = results$stats$descriptive$period, year = results$stats$descriptive$year
+    ))),
+    tabItem(tabName = "stats-difference-tests", results_summary_UI("stats-difference-tests", list(
+      period = results$stats$regime_tests$period
+    ))),
     tabItem(tabName = "correlations-inner", results_summary_UI("correlations-inner", list(
       period = results$correlations$inner$period, year = results$correlations$inner$year
     ))),
@@ -62,6 +72,13 @@ ui <- dashboardPage(
 )
 
 server <- function(input, output) {
+  
+  results_summary_Server("stats-descriptive", list(
+    period = results$stats$descriptive$period, year = results$stats$descriptive$year
+  ))
+  
+  results_summary_Server("stats-difference-tests", list(period = results$stats$regime_tests$period))
+  
   results_summary_Server("correlations-inner", list(
     period = results$correlations$inner$period, year = results$correlations$inner$year
   ))

### 2025-07-04 explore/shiny/revision-jfm/datasets.r

@@ -79,7 +79,46 @@ construct_path <- function() {
 path_directory <- construct_path()
 
 
-correlations_inner_raw <- readr::read_rds(file.path(path_directory, "results", "correlations-inner.rds"))
+period_levels <- c("past", "financialisation", "crisis", "post-crisis")
+
+
+
+
+
+
+# stats ########################################################################
+## descriptive #################################################################
+descriptive <- readr::read_rds(file.path(path_directory, "results", "descriptive-statistics.rds")) |>
+  lapply(function(x) list(`Individual assets` = x))
+
+
+## regime tests ################################################################
+regime_tests_raw <- readr::read_rds(file.path(path_directory, "results", "regime-difference-tests.rds")) 
+
+descriptive_periods <- tidyr::pivot_longer(
+  descriptive$periods$`Individual assets`, c(past, financialisation, crisis, `post-crisis`), names_to = "period", values_to = "value"
+) |> dplyr::filter(regime != "whole period") |>
+  tidyr::pivot_wider(names_from = regime, values_from = value)
+
+regime_tests <- dplyr::left_join(
+  descriptive_periods,
+  dplyr::select(regime_tests_raw, commodity = asset, period, statistic = moment, `≠ p-value` = `p-value`),
+  by = c("commodity", "period", "statistic")
+) |> dplyr::rename(estimate = statistic) |> dplyr::relocate(estimate, .after = period) |>
+  dplyr::mutate(
+    commodity = factor(commodity, levels = unique(commodity)), period = factor(period, levels = unique(period)),
+  ) |>
+  dplyr::arrange(commodity, period, estimate, .by_group = TRUE)
+
+
+
+
+
+
+# correlations #################################################################
+
+correlations_inner_raw <- readr::read_rds(file.path(path_directory, "results", "correlations-inner.rds")) 
+
 correlations_inner_helpers <- list(
   period = list(
     calls = c("average", "top_3"), 
@@ -110,6 +149,25 @@ correlations_cross_split <- purrr::map(c("US", "global"), function(x){
   }
 ) |> setNames(c("US", "global"))
 
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+# regressions ##################################################################
 
 regressions_index_raw <- readr::read_rds(file.path(path_directory, "results", "regressions-index.rds"))
 regressions_index_helpers <- list(
[…]

### 2025-07-04 explore/shiny/revision-jfm/modules/results_summary.r

@@ -16,7 +16,7 @@ results_summary_Server <- function(id, results) {
   moduleServer(id, function(input, output, session) {
     
     ns <- session$ns
-    
+    # browser()
     lapply(seq_along(results), function(i) {
       results_summary_category_Server(names(results)[i], results[[i]])
     })

### 2025-07-04 docs/paper.qmd
Update paper
Replace old tables with new; update body of text and captions accordingly

@@
 
-@tbl-stats-combined displays descriptive statistics for the commodity series considered in the study; the results show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
+@tbl-stats-regime-tests displays descriptive statistics for the commodity series considered in the study; the results show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
 6.9% with a 10% significance in the pre-financialisation period.
@@
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
-@tbl-stats-combined further shows the mean returns and volatilities for high (**contango**) and low (**backwardation**) **CHP** regimes for each time period while @tbl-regime-diference-tests shows the results of difference tests for returns mean and variance between the two regimes.
+@tbl-stats-regime-tests further reports the dominating regime for each asset-period-moment combination along with the corresponding results of difference tests for returns mean and variance between the two regimes^[The estimate values per regime as well as the p-values for the corresponding difference tests are available in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).].
 Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another.
@@
 The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods.
-In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector^[A more detailed breakdown of country, sector and subsector average pairwise correlations is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/revision-jfm/).].
-Although modest in magnitude, these exhibit a telling pattern, mirroring that shown by the individual commodity returns in @tbl-stats-combined, with a substantially higher average coefficient over **backwardation** phases in the first period (0.12 vs.
+In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector^[A more detailed breakdown of country, sector and subsector average pairwise correlations is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).].
+Although modest in magnitude, these exhibit a telling pattern, mirroring that shown by the individual commodity returns in @tbl-stats-regime-tests, with a substantially higher average coefficient over **backwardation** phases in the first period (0.12 vs.
 0.03) and the pattern reversed over financilisation with an average coefficient substantially higher in **contango** (0.12 vs.
@@
 The results for our other risk factor mimicking portfolios show a similar pattern and provide a deeper insights into co-movement dynamics in this context.
-All three factors---CHP, open interest and term structure---performed poorly in the first period, indicating that the commodities with extreme factor attributes (high or low CHP for example) were uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of **contango** and **backwardation**.
+All three factors---CHP, open interest and term structure---performed poorly in the first period, indicating that the commodities with extreme factor attributes (high or low CHP for example) were uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of **contango** and **backwardation**^[A breakdown of the performance by regime is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).].
 The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average $R^{2}$, albeit still small at 5.4%, almost tripling from the past to the financialisation period in contrast to the other factors that show weaker dynamics with a slight decrease and a much smaller increase for the open interest and term structure factors respectively.
@@
 The corresponding figures of 22% and 1.1% for the entire US metals sector stand in sharp contrast with the agricultural sector, which exhibits no notable change, and the energy sector, where pricing performance drops substantially from 9.2% down to 1.6%.
-The improvement in the CHP factor's pricing performance remarkably comes predominantly from the long leg (low CHP assets: Keynesian "normal backwardation") of the factor^[Results available from the authors upon request.] with the corresponding mimicking portfolio's performance itself driven by the metals, the precious sub-sector in particular.
+The improvement in the CHP factor's pricing performance remarkably comes predominantly from the long leg (low CHP assets: Keynesian "normal backwardation") of the factor^[A breakdown of the performance by factor leg is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).] with the corresponding mimicking portfolio's performance itself driven by the metals, the precious sub-sector in particular.
 Interestingly, although the term structure factor itself only sees a very modest increase, its short leg (low roll-yield assets: Working's backwardation) shows a sizeable rise in pricing performance, yet again driven the metals sector.
@@
 The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results.
-Returns fall sharply relative to the financialisation period (@tbl-stats-combined) with eighteen US commodities along with all six GB traded metals showing lower mean returns.
+Returns fall sharply relative to the financialisation period (@tbl-stats-regime-tests) with eighteen US commodities along with all six GB traded metals showing lower mean returns.
 Returns for equally weighted portfolios of both sets of assets fall down to 9.4% and 5.3% from 15.9% and 21.8% respectively.
@@
 
-The returns pull-back continues into the post-crisis period (@tbl-stats-combined) with twenty-two US and four GB traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all GB metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and GB assets drop down to -0.2% and 2.7% respectively.
+The returns pull-back continues into the post-crisis period (@tbl-stats-regime-tests) with twenty-two US and four GB traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all GB metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and GB assets drop down to -0.2% and 2.7% respectively.
 Interestingly volatility also recedes substantially with twenty US assets and all GB metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
@@
 The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of **backwardation** relative to **contango**, more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
-The difference (@tbl-regime-diference-tests) is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
+The difference (@tbl-stats-regime-tests) is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
 The pattern is more pronounced for the GB traded subset with all six assets showing higher mean returns in **backwardation** with the difference significant at the 1% level for Nickel-primary (XLME), 5% level for Aluminium (XLME) and 10% level for Zinc (XLME).
@@
 ```{r}
-#| label: tbl-stats-combined
-#| tbl-cap: "This table shows mean returns and corresponding volatility for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-for each period the figures are shown independently for the entire period as well as for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Mean values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
-Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
+#| label: tbl-stats-regime-tests
+#| tbl-cap: "This table shows mean returns and volatilities for the individual commodities as well as for two equally weighted portfolios of US and GB traded assets across the four periods.
+For each period, estimates are computed independently over the whole period (figure shown) as well as over phases of **backwardation** (b) and **contango** (c) with corresponding comparison results reported in brackets.
+The table further shows the results of t-tests of significance for the mean returns computed over the whole periods as well as t-tests of difference between these when computed over the two phases independently along with F-tests of difference for the corresponding variances.
+Values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
+The estimate values per regime as well as the p-values for the corresponding difference tests are available in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).
+**Backwardation** and **contango** regimes as well as period definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
 
-table_name <- "stats - combined"
-columns_to_collapse_rows_for <- c("asset", "regime")
-colnames <- c("asset", "regime", "estimate", periods)
-align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
+table_name <- "stats-individuals - regime difference tests"
+columns_to_collapse_rows_for <- c("asset")
+colnames <- c("asset", "estimate", "past", "financialisation", "crisis", "post-crisis")
+align <- make_series_of_repeated_chars(list(l = 1L, r = 5L))
 longtable <- TRUE
-bold_columns <- 1L:3L
-coloured_columns <- 4L:7L
-
-make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
-```
-
-\newpage
-
-```{r}
-#| label: tbl-regime-diference-tests
-#| tbl-cap: "This table shows the results for tests of difference in mean (t-test) and variance (F-test) between phases of aggregate backwardation and contango for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-1%, 5% and 10% p-value levels are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively in the significance column.
-Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
-
-table_name <- "regime difference tests"
-columns_to_collapse_rows_for <- c("asset", "period")
-colnames <- c("asset", "period", "moment", "dominant regime", "p-value", "significance")
-align <- make_series_of_repeated_chars(list(l = 4L, r = 2L))
-longtable <- TRUE
-bold_columns <- 1L:4L 
-coloured_columns <- 5L:6L
+bold_columns <- 1L:6L 
+coloured_columns <- 3L:6L
 
@@
 #| label: tbl-time-reg-US-CHP
-#| tbl-cap: "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in aggregate CHP, a market wide measure of CHP which calculation method is discussed in \\@sec-methods.
-Averages are calculated independently across the whole cross-section of US traded commodity assets considered in the study as well as across commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The results are discussed in \\@sec-results while \\@sec-taxonomy details the taxonomy for the commodity assets considered."
+#| tbl-cap: "This table shows the average time series $R^{2}$ for models where the returns series for the individual US traded commodities are independently regressed against relative change in their own commercial hedging pressure (CHP) series as well as against that in **CHP**, a market wide measure of CHP which calculation method is discussed in \\@sec-methods.
+Averages are computed independently across the whole cross-section of US traded commodity assets as well as across commodity sectors and sub-sectors for the four periods.
+Period definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the commodity assets taxonomy is detailed in \\@sec-taxonomy."
 
@@
 #| label: tbl-correlations-inner-periods
-#| tbl-cap: "This table shows the average return pairwise correlation coefficients calculated independently across the whole cross-section of commodity assets considered in the study as well as within countries and commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-For each period, the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
-Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the taxonomy for the commodity assets considered is detailed in \\@sec-taxonomy."
+#| tbl-cap: "This table shows the average return pairwise correlation coefficients computed independently across the whole cross-section of individual commodity assets as well as within countries and commodity sectors and sub-sectors for the four periods.
+For each period, the results are computed independently over the entire period as well as over phases of **backwardation** and **contango**.
+**Backwardation** and **contango** regimes as well as period definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the commodity assets taxonomy is detailed in \\@sec-taxonomy."
 
@@
 #| label: tbl-correlations-cross-periods
-#| tbl-cap: "This table shows the average return pairwise correlation coefficients between equally weighted US sub-sector portfolios (agriculturals: gains, livestock, softs; energy: gas, petroleum; metals: base, precious).
-The results are independently calculated for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-For each period, the results are further calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
-Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the taxonomy for the commodity assets considered is detailed in \\@sec-taxonomy."
+#| tbl-cap: "This table shows the average return pairwise correlation coefficients between equally weighted US sub-sector portfolios (agriculturals: gains, livestock, softs; energy: gas, petroleum; metals: base, precious) independently computed for the four periods.
+For each period, the results are further computed independently over the entire period as well as over phases **backwardation** and **contango**.
+**Backwardation** and **contango** regimes as well as period definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the commodity assets taxonomy is detailed in \\@sec-taxonomy."
 
@@
 longtable <- TRUE
-bold_columns <- 1L
+bold_columns <- 1L:5L
 coloured_columns <- 2L:5L
@@
 #| label: tbl-correlations-inner-years
-#| tbl-cap: "While \\@tbl-correlations-inner-periods shows results calculated independently for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018), this stable shows the results of the same analysis calculated by year over the entire sample period (1997-2018).
-The results are discussed in \\@sec-results while \\@sec-taxonomy details the taxonomy for the commodity assets considered."
+#| tbl-cap: "While \\@tbl-correlations-inner-periods shows results computed independently for the four periods, this table shows the results of the same analysis implemented for each year over the entire sample period.
+The results are discussed in \\@sec-results while \\@sec-taxonomy details the commodity assets taxonomy."
 
@@
 #| label: tbl-regressions-index
-#| tbl-cap: "This table shows the average time series regression coefficients for models where the returns series for all the commodity assets considered in the study are independently regressed against the return series for our market factor, an equally weighted portfolio of the 24 US commodities considered in the study.
-The results are calculated independently across countries as well as commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-The market factor construction is discussed in \\@sec-methods while the results are discussed in \\@sec-results and the taxonomy for the commodity assets considered is detailed in \\@sec-taxonomy."
+#| tbl-cap: "This table shows the average time series regression coefficients for models where the returns series for all the commodity assets are independently regressed against the return series for our market factor, an equally weighted portfolio of the US traded commodities.
+The results are computed independently across countries as well as commodity sectors and sub-sectors for the four periods.
+Period definitions along with the market factor construction method are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the commodity assets taxonomy is detailed in \\@sec-taxonomy."
 
@@
 #| label: tbl-regressions-factors
-#| tbl-cap: "This table shows the average time series regression $R^{2}$ for models where the returns series for all the commodity assets considered in the study are independently regressed against the return series for our mimicking portfolios for risk factors in returns, including the market, CHP, open interest and term structure factors.
-The results are calculated independently across countries and commodity sectors and sub-sectors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018); for each period the results are calculated independently over the entire period as well as over phases of aggregate backwardation and contango.
-Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the taxonomy for the commodity assets considered is detailed in \\@sec-taxonomy."
+#| tbl-cap: "This table shows the average time series regression $R^{2}$ for models where the returns series for all the commodity assets are independently regressed against the return series for our mimicking portfolios for risk factors in returns, including the market, CHP, open interest and term structure factors.
+The results are computed independently across countries and commodity sectors and sub-sectors for the four periods.
+A breakdown of the estimates computed independently over the whole periods as well as over phases of **backwardation** and **contango** is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).
+Factor construction methods along with **backwardation** and **contango** regimes as well as period definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the commodity assets taxonomy is detailed in \\@sec-taxonomy."
 
-table_name <- "regressions - all returns ~ factors"
+table_name <- "regressions - all returns ~ factors - short"
 columns_to_collapse_rows_for <- c("country", "sector", "subsector", "factor")
-colnames <- c(sectors, "factor", "regime", periods)
-align <- make_series_of_repeated_chars(list(l = 5L, r = 4L))
+colnames <- c(sectors, "factor", periods)
+align <- make_series_of_repeated_chars(list(l = 4L, r = 4L))
 longtable <- TRUE
-bold_columns <- 1L:9L
-coloured_columns <- 6L:9L
+bold_columns <- 1L:8L
+coloured_columns <- 5L:8L
 
@@
 #| tbl-cap: "This table shows the detailed taxonomy for the thirty commodity assets considered in the study.
-The assets are classified by the country of residence of the exchange where they are traded as well as by sector and sub-sector according to the nature of the asset."
+The assets are classified by the country of residence of the exchange where they are traded at the time of writing as well as by sector and sub-sector according to the nature of the asset."
 

### 2025-07-04 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@342e653499d97540ee93e29b1a6bb8dbd4a5f3c9 🚀

@@
 
-Table~\ref{tbl-stats-combined} displays descriptive statistics for the
-commodity series considered in the study; the results show a clear
+Table~\ref{tbl-stats-regime-tests} displays descriptive statistics for
+the commodity series considered in the study; the results show a clear
 pattern of increase in average return during financialisation with an
@@
 Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary
-(XLME)---show a lower figure with five og them significant---Crude
+(XLME)---show a lower figure with five of them significant---Crude
 oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and
@@
 that returns for individual commodities should be high in periods where
-\textbf{CHP} is low and vice et versa. Table~\ref{tbl-stats-combined}
-further shows the mean returns and volatilities for high
-(\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP}
-regimes for each time period while
-Table~\ref{tbl-regime-diference-tests} shows the results of difference
-tests for returns mean and variance between the two regimes.\\
+\textbf{CHP} is low and vice et versa.
+Table~\ref{tbl-stats-regime-tests} further reports the dominating regime
+for each asset-period-moment combination along with the corresponding
+results of difference tests for returns mean and variance between the
+two regimes\footnote{The estimate values per regime as well as the
+  p-values for the corresponding difference tests are available in the
+  attached
+  \href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
+  Appendix}.}.\\
 Over the first period eighteen of the twenty-four US commodities have
@@
 pairwise correlation coefficients between equally weighted portfolios of
-US traded commodity assets grouped by sub-sector. Although modest in
-magnitude, these exhibit a telling pattern, mirroring that shown by the
-individual commodity returns in Table~\ref{tbl-stats-combined}, with a
-substantially higher average coefficient over \textbf{backwardation}
-phases in the first period (0.12 vs.~0.03) and the pattern reversed over
-financilisation with an average coefficient substantially higher in
-\textbf{contango} (0.12 vs.~0.02).\\
+US traded commodity assets grouped by sub-sector\footnote{A more
+  detailed breakdown of country, sector and subsector average pairwise
+  correlations is provided in the attached
+  \href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
+  Appendix}.}. Although modest in magnitude, these exhibit a telling
+pattern, mirroring that shown by the individual commodity returns in
+Table~\ref{tbl-stats-regime-tests}, with a substantially higher average
+coefficient over \textbf{backwardation} phases in the first period (0.12
+vs.~0.03) and the pattern reversed over financilisation with an average
+coefficient substantially higher in \textbf{contango} (0.12 vs.~0.02).\\
 We break down Table~\ref{tbl-correlations-inner-periods}'s average
@@
 overall performance consistent across periods of \textbf{contango} and
-\textbf{backwardation}. The onset of financialisation leads to a
-substantial improvement in the performance of the CHP factor with its
-average \(R^{2}\), albeit still small at 5.4\%, almost tripling from the
-past to the financialisation period in contrast to the other factors
-that show weaker dynamics with a slight decrease and a much smaller
-increase for the open interest and term structure factors respectively.
-Here again the increase in pricing performance for the CHP factor is
-driven by the metals sector, particularly the precious sub-sector with
-the average \(R^{2}\) for the group jumping to almost 26\% during
-financialisation from 1.2\% over the past period. The corresponding
-figures of 22\% and 1.1\% for the entire US metals sector stand in sharp
-contrast with the agricultural sector, which exhibits no notable change,
-and the energy sector, where pricing performance drops substantially
-from 9.2\% down to 1.6\%. The improvement in the CHP factor's pricing
-performance remarkably comes predominantly from the long leg (low CHP
-assets: Keynesian ``normal backwardation'') of the factor\footnote{Results
-  available from the authors upon request.} with the corresponding
-mimicking portfolio's performance itself driven by the metals, the
-precious sub-sector in particular. Interestingly, although the term
-structure factor itself only sees a very modest increase, its short leg
-(low roll-yield assets: Working's backwardation) shows a sizeable rise
-in pricing performance, yet again driven the metals sector. The pattern
-of results for both factors extends to the GB traded assets and suggest
-a convergence of Keneysian and Working's term structure perspective over
-the financialisation period.\\
+\textbf{backwardation}\footnote{A breakdown of the performance by regime
+  is provided in the attached
+  \href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
+  Appendix}.}. The onset of financialisation leads to a substantial
+improvement in the performance of the CHP factor with its average
+\(R^{2}\), albeit still small at 5.4\%, almost tripling from the past to
+the financialisation period in contrast to the other factors that show
+weaker dynamics with a slight decrease and a much smaller increase for
+the open interest and term structure factors respectively. Here again
+the increase in pricing performance for the CHP factor is driven by the
+metals sector, particularly the precious sub-sector with the average
+\(R^{2}\) for the group jumping to almost 26\% during financialisation
+from 1.2\% over the past period. The corresponding figures of 22\% and
+1.1\% for the entire US metals sector stand in sharp contrast with the
+agricultural sector, which exhibits no notable change, and the energy
+sector, where pricing performance drops substantially from 9.2\% down to
+1.6\%. The improvement in the CHP factor's pricing performance
+remarkably comes predominantly from the long leg (low CHP assets:
+Keynesian ``normal backwardation'') of the factor\footnote{A breakdown
+  of the performance by factor leg is provided in the attached
+  \href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
+  Appendix}.} with the corresponding mimicking portfolio's performance
+itself driven by the metals, the precious sub-sector in particular.
+Interestingly, although the term structure factor itself only sees a
+very modest increase, its short leg (low roll-yield assets: Working's
+backwardation) shows a sizeable rise in pricing performance, yet again
+driven the metals sector. The pattern of results for both factors
+extends to the GB traded assets and suggest a convergence of Keneysian
+and Working's term structure perspective over the financialisation
+period.\\
 Taken together these results emphasise the global nature of the impact
@@
 results. Returns fall sharply relative to the financialisation period
-(Table~\ref{tbl-stats-combined}) with eighteen US commodities along with
-all six GB traded metals showing lower mean returns. Returns for equally
-weighted portfolios of both sets of assets fall down to 9.4\% and 5.3\%
-from 15.9\% and 21.8\% respectively. Returns are mostly higher during
-phases of \textbf{backwardation} relative to \textbf{contango} with
-fifteen US assets and five of the GB traded metals showing higher mean
-returns in \textbf{backwardation} and the pattern extending to equally
-weighted portfolios of the two sets of assets. Volatility is moderately
-higher for both sets with fifteen US commodities and three GB metals
-showing higher figures and interestingly eminently higher over phases of
-\textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none
-of the GB traded metals show higher volatility figures over
-\textbf{backwardation} phases. The symmetry between the dynamics of CHP
-and \textbf{CHP}'s explanatory power on individual commodity returns
+(Table~\ref{tbl-stats-regime-tests}) with eighteen US commodities along
+with all six GB traded metals showing lower mean returns. Returns for
+equally weighted portfolios of both sets of assets fall down to 9.4\%
+and 5.3\% from 15.9\% and 21.8\% respectively. Returns are mostly higher
+during phases of \textbf{backwardation} relative to \textbf{contango}
+with fifteen US assets and five of the GB traded metals showing higher
+mean returns in \textbf{backwardation} and the pattern extending to
+equally weighted portfolios of the two sets of assets. Volatility is
+moderately higher for both sets with fifteen US commodities and three GB
+metals showing higher figures and interestingly eminently higher over
+phases of \textbf{contango}; out of the US complex only Sugar-\#11
+(IFUS) and none of the GB traded metals show higher volatility figures
+over \textbf{backwardation} phases. The symmetry between the dynamics of
+CHP and \textbf{CHP}'s explanatory power on individual commodity returns
 breaks (Table~\ref{tbl-time-reg-US-CHP}) with both now seemingly
@@
 The returns pull-back continues into the post-crisis period
-(Table~\ref{tbl-stats-combined}) with twenty-two US and four GB traded
-assets showing lower mean returns relative to the crisis while the same
-number of US commodities and all GB metals show lower figures relative
-to the financialisation period; mean returns for equally weighted
-portfolios of US and GB assets drop down to -0.2\% and 2.7\%
+(Table~\ref{tbl-stats-regime-tests}) with twenty-two US and four GB
+traded assets showing lower mean returns relative to the crisis while
+the same number of US commodities and all GB metals show lower figures
+relative to the financialisation period; mean returns for equally
+weighted portfolios of US and GB assets drop down to -0.2\% and 2.7\%
 respectively. Interestingly volatility also recedes substantially with
@@
 returns over \textbf{backwardation} phases. The difference
-(Table~\ref{tbl-regime-diference-tests}) is significant at the 5\% level
-for Lumber (XCME) and at the 10\% level for Palladium (XNYM) while no
+(Table~\ref{tbl-stats-regime-tests}) is significant at the 5\% level for
+Lumber (XCME) and at the 10\% level for Palladium (XNYM) while no
 difference is significant for the assets showing higher figures over
@@
 
+\newpage
+
 \newgeometry{margin=.75in}
 
+\section*{Tables}\label{tables}
+\addcontentsline{toc}{section}{Tables}
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}r>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-stats-regime-tests}This table shows mean returns and
+volatilities for the individual commodities as well as for two equally
+weighted portfolios of US and GB traded assets across the four periods.
+For each period, estimates are computed independently over the whole
+period (figure shown) as well as over phases of \textbf{backwardation}
+(b) and \textbf{contango} (c) with corresponding comparison results
+reported in brackets. The table further shows the results of t-tests of
+significance for the mean returns computed over the whole periods as
+well as t-tests of difference between these when computed over the two
+phases independently along with F-tests of difference for the
+corresponding variances. Values significant at the 1\%, 5\% and 10\%
+level are marked with ***, ** and * respectively. The estimate values
+per regime as well as the p-values for the corresponding difference
+tests are available in the attached
+\href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
+Appendix}. \textbf{Backwardation} and \textbf{contango} regimes as well
+as period definitions are discussed in Section~\ref{sec-methods} while
+the results are discussed in Section~\ref{sec-results}.}
+
+\tabularnewline
+
+\toprule
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\midrule
+\textbf{Corn-\#2 yellow (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.48\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{21.37\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-4.51\% (b<c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{29.54\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{36.15\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{21.8\% (b<c*)}}\\
+\textbf{Oats (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{5.49\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{21.62\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{8.89\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.87\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.22\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{31.04\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.67\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{29.5\% (b>c***)}}\\
+\textbf{Soybean meal (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{7.29\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.06\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{8.12\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.33\% (b<c)}}\\
+\addlinespace
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.34\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.55\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{31.78\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{25.11\% (b<c)}}\\
+\textbf{Soybean oil (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{6.21\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{15.57\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{4.04\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-7.39\% (b<c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.43\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{28.35\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{25.75\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.95\% (b<c**)}}\\
+\textbf{Soybeans (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{6.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{13.36\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.19\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.82\% (b<c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.47\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{30.04\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{28\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{21.22\% (b>c*)}}\\
+\addlinespace
+\textbf{Wheat-SRW (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{5.07\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{17.63\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{6.68\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-1.58\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.93\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{33.03\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{37.62\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{26.58\% (b<c)}}\\
+\textbf{Cattle-feeder (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{0.39\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{7.43\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{7.13\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.87\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.23\% (b<c*)}} & \textcolor[HTML]{4285f4}{\textbf{15.16\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{15.24\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.69\% (b>c***)}}\\
+\textbf{Cattle-live (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.45\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{8.77\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{4.13\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.92\% (b<c)}}\\
+\addlinespace
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.1\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{17.43\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{16.32\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.3\% (b>c***)}}\\
+\textbf{Lean hogs (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{0.73\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{8.4\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.69\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-1.09\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.33\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.89\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{30.37\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{36.94\% (b<c*)}}\\
+\textbf{Cocoa (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.66\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{16.35\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{1.39\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{3.65\% (b<c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.66\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{29.99\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{31.03\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{24.69\% (b>c**)}}\\
+\addlinespace
+\textbf{Coffee-C (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{-5.91\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{20.38\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{2.2\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.99\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.84\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.3\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{30.17\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.86\% (b<c)}}\\
+\textbf{Cotton-\#2 (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.24\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{0.95\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.53\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{0.5\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.38\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{29.01\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{33.26\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{20.61\% (b>c*)}}\\
+\textbf{Lumber (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.9\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.58\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{11.74\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{5.06\% (b>c**)}}\\
+\addlinespace
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.58\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{29.39\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{36.31\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{25.1\% (b<c***)}}\\
+\textbf{Orange juice (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.67\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{13.87\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{14.4\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{3.8\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.5\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{33.01\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{34.43\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{29.37\% (b<c)}}\\
+\textbf{Sugar-\#11 (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{-4.56\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{24.87\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{11.82\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-1.16\% (b<c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.88\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{33.25\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{37.9\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{28.72\% (b<c*)}}\\
+\addlinespace
+\textbf{Natural gas (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{35.38\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{16.25\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{0.93\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{8.33\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{61.55\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{54.6\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{53.58\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{44.58\% (b<c**)}}\\
+\textbf{Crude oil-WTI (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{15.43\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*28.74\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{9.67\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-5.64\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.87\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.56\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{42.84\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.69\% (b<c***)}}\\
+\textbf{Gasoline (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{16.65\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{30.95\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{10.59\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-5.37\% (b>c)}}\\
+\addlinespace
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.77\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{41.76\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{40.07\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{37.09\% (b<c***)}}\\
+\textbf{Heating oil (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{16.31\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*29.88\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.83\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.44\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.75\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{35.09\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{33.17\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{30.56\% (b<c***)}}\\
+\textbf{Copper (XCEC)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.45\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*28.15\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.19\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.1\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.23\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.89\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.91\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{19.56\% (b<c***)}}\\
+\addlinespace
+\textbf{Gold (XCEC)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{4.5\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{14.35\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{14.01\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{0.53\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.14\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{21.46\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{14.41\% (b<c***)}}\\
+\textbf{Palladium (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{9.12\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{9.03\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*29.12\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{13.75\% (b>c*)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.27\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.71\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{36.14\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{25.38\% (b<c***)}}\\
+\textbf{Platinum (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{12.93\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{10.56\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{7.29\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-7.92\% (b>c)}}\\
+\addlinespace
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.62\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{22.66\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{25.53\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{19.48\% (b<c***)}}\\
+\textbf{Silver (XCEC)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{6.19\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{17.54\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{21.96\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-2.43\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{33.92\% (b<c*)}} & \textcolor[HTML]{4285f4}{\textbf{39.87\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{24.35\% (b<c***)}}\\
+\textbf{Aluminium (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.13\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{13.78\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.58\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{3.15\% (b>c**)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.6\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{26.41\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{26.48\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.56\% (b>c)}}\\
+\addlinespace
+\textbf{Copper (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{0.45\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{**28.59\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{5.74\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{0.03\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.25\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{31.09\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.27\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.92\% (b<c***)}}\\
+\textbf{Lead (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.83\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{28.99\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{10.74\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{2.07\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.64\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{41.74\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{41.05\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{23.26\% (b>c)}}\\
+\textbf{Nickel (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{19.31\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.5\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{3.52\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{0.31\% (b>c***)}}\\
+\addlinespace
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.26\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{44.27\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{41.45\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{28.98\% (b>c)}}\\
+\textbf{Tin (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{4.07\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{*29.1\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{7.46\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.68\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.38\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.71\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{35.61\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.79\% (b<c***)}}\\
+\textbf{Zinc (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{-4.52\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{20.13\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{7.62\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{9.07\% (b>c*)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.73\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{38.77\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{36.17\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{23.25\% (b<c**)}}\\
+\addlinespace
+\textbf{US commodities} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{*6.89\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{**15.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{9.39\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.18\% (b>c)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{13.62\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{17.58\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{9.86\% (b<c***)}}\\
+\textbf{GB commodities} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{2.47\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*21.77\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{5.25\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{2.72\% (b>c**)}}\\
+\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.66\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{26.91\% (b<c*)}} & \textcolor[HTML]{4285f4}{\textbf{30.24\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{16.19\% (b<c***)}}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
 \newpage
 
-\section{Tables}\label{tables}
-
 \begingroup\fontsize{7}{9}\selectfont
@@
 
-\caption{\label{tbl-stats-combined}This table shows mean returns and
-corresponding volatility for the twenty four individual US commodities
-and the six GB metals considered in the study as well as for two equally
-weighted portfolios formed from the US commodities and the GB metals
-respectively across the four periods of interest (past: 1997-2003;
-financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-for each period the figures are shown independently for the entire
-period as well as for phases of aggregate backwardation (aggregate CHP
-\(\leq\) period median) and aggregate contango (aggregate CHP
-\textgreater{} period median). Mean values significant at the 1\%, 5\%
-and 10\% level are marked with ***, ** and * respectively. Aggregate CHP
-construction and corresponding regime definitions are discussed in
+\caption{\label{tbl-time-reg-US-CHP}This table shows the average time
+series \(R^{2}\) for models where the returns series for the individual
+US traded commodities are independently regressed against relative
+change in their own commercial hedging pressure (CHP) series as well as
+against that in \textbf{CHP}, a market wide measure of CHP which
+calculation method is discussed in Section~\ref{sec-methods}. Averages
+are computed independently across the whole cross-section of US traded
+commodity assets as well as across commodity sectors and sub-sectors for
+the four periods. Period definitions are discussed in
 Section~\ref{sec-methods} while the results are discussed in
-Section~\ref{sec-results}.}
-
-\tabularnewline
-
-\toprule
-\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
-\midrule
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.48\%} & \textcolor[HTML]{4285f4}{21.37\%} & \textcolor[HTML]{4285f4}{6.89\%} & \textcolor[HTML]{4285f4}{-4.51\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23\%} & \textcolor[HTML]{4285f4}{29.54\%} & \textcolor[HTML]{4285f4}{36.15\%} & \textcolor[HTML]{4285f4}{21.8\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.86\%} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{20.48\%} & \textcolor[HTML]{4285f4}{-8.74\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23.07\%} & \textcolor[HTML]{4285f4}{29.14\%} & \textcolor[HTML]{4285f4}{31.59\%} & \textcolor[HTML]{4285f4}{21\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.3\%} & \textcolor[HTML]{4285f4}{23.54\%} & \textcolor[HTML]{4285f4}{-4.43\%} & \textcolor[HTML]{4285f4}{0.78\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23\%} & \textcolor[HTML]{4285f4}{30.01\%} & \textcolor[HTML]{4285f4}{40.14\%} & \textcolor[HTML]{4285f4}{22.68\%}\\
-\textbf{Oats (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.49\%} & \textcolor[HTML]{4285f4}{21.62\%} & \textcolor[HTML]{4285f4}{8.89\%} & \textcolor[HTML]{4285f4}{-0.87\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.22\%} & \textcolor[HTML]{4285f4}{31.04\%} & \textcolor[HTML]{4285f4}{34.67\%} & \textcolor[HTML]{4285f4}{29.5\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.39\%} & \textcolor[HTML]{4285f4}{7.82\%} & \textcolor[HTML]{4285f4}{7.85\%} & \textcolor[HTML]{4285f4}{2.56\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{29.02\%} & \textcolor[HTML]{4285f4}{33.82\%} & \textcolor[HTML]{4285f4}{31.43\%} & \textcolor[HTML]{4285f4}{31.55\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.95\%} & \textcolor[HTML]{4285f4}{*35.38\%} & \textcolor[HTML]{4285f4}{11.68\%} & \textcolor[HTML]{4285f4}{-3.17\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{35.22\%} & \textcolor[HTML]{4285f4}{28.1\%} & \textcolor[HTML]{4285f4}{37.7\%} & \textcolor[HTML]{4285f4}{27.5\%}\\
-\textbf{Soybean meal (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{7.29\%} & \textcolor[HTML]{4285f4}{12.06\%} & \textcolor[HTML]{4285f4}{8.12\%} & \textcolor[HTML]{4285f4}{-0.33\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.34\%} & \textcolor[HTML]{4285f4}{32.55\%} & \textcolor[HTML]{4285f4}{31.78\%} & \textcolor[HTML]{4285f4}{25.11\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{13.15\%} & \textcolor[HTML]{4285f4}{8.22\%} & \textcolor[HTML]{4285f4}{16.04\%} & \textcolor[HTML]{4285f4}{-3.52\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{27.77\%} & \textcolor[HTML]{4285f4}{33.06\%} & \textcolor[HTML]{4285f4}{25.7\%} & \textcolor[HTML]{4285f4}{25.1\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.52\%} & \textcolor[HTML]{4285f4}{15.91\%} & \textcolor[HTML]{4285f4}{2.32\%} & \textcolor[HTML]{4285f4}{2.22\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.94\%} & \textcolor[HTML]{4285f4}{32.13\%} & \textcolor[HTML]{4285f4}{36.85\%} & \textcolor[HTML]{4285f4}{25.32\%}\\
-\textbf{Soybean oil (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.21\%} & \textcolor[HTML]{4285f4}{15.57\%} & \textcolor[HTML]{4285f4}{4.04\%} & \textcolor[HTML]{4285f4}{-7.39\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.43\%} & \textcolor[HTML]{4285f4}{28.35\%} & \textcolor[HTML]{4285f4}{25.75\%} & \textcolor[HTML]{4285f4}{18.95\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{14.79\%} & \textcolor[HTML]{4285f4}{14.62\%} & \textcolor[HTML]{4285f4}{20.34\%} & \textcolor[HTML]{4285f4}{-9.44\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.35\%} & \textcolor[HTML]{4285f4}{28.94\%} & \textcolor[HTML]{4285f4}{22.33\%} & \textcolor[HTML]{4285f4}{18.19\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.68\%} & \textcolor[HTML]{4285f4}{16.62\%} & \textcolor[HTML]{4285f4}{-10.01\%} & \textcolor[HTML]{4285f4}{-4.12\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.55\%} & \textcolor[HTML]{4285f4}{27.91\%} & \textcolor[HTML]{4285f4}{28.65\%} & \textcolor[HTML]{4285f4}{19.79\%}\\
-\textbf{Soybeans (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.89\%} & \textcolor[HTML]{4285f4}{13.36\%} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{-3.82\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.47\%} & \textcolor[HTML]{4285f4}{30.04\%} & \textcolor[HTML]{4285f4}{28\%} & \textcolor[HTML]{4285f4}{21.22\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{13.69\%} & \textcolor[HTML]{4285f4}{0.93\%} & \textcolor[HTML]{4285f4}{13.42\%} & \textcolor[HTML]{4285f4}{-11.45\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.93\%} & \textcolor[HTML]{4285f4}{34.58\%} & \textcolor[HTML]{4285f4}{24.39\%} & \textcolor[HTML]{4285f4}{22.04\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.16\%} & \textcolor[HTML]{4285f4}{25.71\%} & \textcolor[HTML]{4285f4}{0.96\%} & \textcolor[HTML]{4285f4}{3.75\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.09\%} & \textcolor[HTML]{4285f4}{24.74\%} & \textcolor[HTML]{4285f4}{31.11\%} & \textcolor[HTML]{4285f4}{20.56\%}\\
-\addlinespace
-\textbf{Wheat-SRW (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.07\%} & \textcolor[HTML]{4285f4}{17.63\%} & \textcolor[HTML]{4285f4}{6.68\%} & \textcolor[HTML]{4285f4}{-1.58\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.93\%} & \textcolor[HTML]{4285f4}{33.03\%} & \textcolor[HTML]{4285f4}{37.62\%} & \textcolor[HTML]{4285f4}{26.58\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.7\%} & \textcolor[HTML]{4285f4}{19.02\%} & \textcolor[HTML]{4285f4}{0.98\%} & \textcolor[HTML]{4285f4}{0.44\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{25.79\%} & \textcolor[HTML]{4285f4}{36\%} & \textcolor[HTML]{4285f4}{37.53\%} & \textcolor[HTML]{4285f4}{26.57\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.78\%} & \textcolor[HTML]{4285f4}{16.29\%} & \textcolor[HTML]{4285f4}{14.57\%} & \textcolor[HTML]{4285f4}{-2.77\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.04\%} & \textcolor[HTML]{4285f4}{29.84\%} & \textcolor[HTML]{4285f4}{37.73\%} & \textcolor[HTML]{4285f4}{26.72\%}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{7.43\%} & \textcolor[HTML]{4285f4}{7.13\%} & \textcolor[HTML]{4285f4}{1.87\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.23\%} & \textcolor[HTML]{4285f4}{15.16\%} & \textcolor[HTML]{4285f4}{15.24\%} & \textcolor[HTML]{4285f4}{18.69\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.31\%} & \textcolor[HTML]{4285f4}{**20.52\%} & \textcolor[HTML]{4285f4}{7.51\%} & \textcolor[HTML]{4285f4}{6.58\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{12.79\%} & \textcolor[HTML]{4285f4}{14.93\%} & \textcolor[HTML]{4285f4}{13.39\%} & \textcolor[HTML]{4285f4}{20.14\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.81\%} & \textcolor[HTML]{4285f4}{-5.49\%} & \textcolor[HTML]{4285f4}{7.28\%} & \textcolor[HTML]{4285f4}{-3.12\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.67\%} & \textcolor[HTML]{4285f4}{15.35\%} & \textcolor[HTML]{4285f4}{16.91\%} & \textcolor[HTML]{4285f4}{17.23\%}\\
-\textbf{Cattle-live (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.45\%} & \textcolor[HTML]{4285f4}{8.77\%} & \textcolor[HTML]{4285f4}{4.13\%} & \textcolor[HTML]{4285f4}{1.92\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.1\%} & \textcolor[HTML]{4285f4}{17.43\%} & \textcolor[HTML]{4285f4}{16.32\%} & \textcolor[HTML]{4285f4}{18.3\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{8.39\%} & \textcolor[HTML]{4285f4}{14.2\%} & \textcolor[HTML]{4285f4}{5.87\%} & \textcolor[HTML]{4285f4}{-2.07\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.65\%} & \textcolor[HTML]{4285f4}{17.91\%} & \textcolor[HTML]{4285f4}{14.97\%} & \textcolor[HTML]{4285f4}{19.9\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.34\%} & \textcolor[HTML]{4285f4}{3.43\%} & \textcolor[HTML]{4285f4}{2.7\%} & \textcolor[HTML]{4285f4}{5.82\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.49\%} & \textcolor[HTML]{4285f4}{16.99\%} & \textcolor[HTML]{4285f4}{17.57\%} & \textcolor[HTML]{4285f4}{16.66\%}\\
-\textbf{Lean hogs (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{8.4\%} & \textcolor[HTML]{4285f4}{12.69\%} & \textcolor[HTML]{4285f4}{-1.09\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.33\%} & \textcolor[HTML]{4285f4}{31.89\%} & \textcolor[HTML]{4285f4}{30.37\%} & \textcolor[HTML]{4285f4}{36.94\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{12.34\%} & \textcolor[HTML]{4285f4}{16.3\%} & \textcolor[HTML]{4285f4}{18.23\%} & \textcolor[HTML]{4285f4}{19.24\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{37.6\%} & \textcolor[HTML]{4285f4}{35.73\%} & \textcolor[HTML]{4285f4}{27.83\%} & \textcolor[HTML]{4285f4}{35.61\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-10.5\%} & \textcolor[HTML]{4285f4}{0.6\%} & \textcolor[HTML]{4285f4}{7.5\%} & \textcolor[HTML]{4285f4}{-20.66\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{39.22\%} & \textcolor[HTML]{4285f4}{27.67\%} & \textcolor[HTML]{4285f4}{32.78\%} & \textcolor[HTML]{4285f4}{38.28\%}\\
-\textbf{Cocoa (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.66\%} & \textcolor[HTML]{4285f4}{16.35\%} & \textcolor[HTML]{4285f4}{1.39\%} & \textcolor[HTML]{4285f4}{3.65\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.66\%} & \textcolor[HTML]{4285f4}{29.99\%} & \textcolor[HTML]{4285f4}{31.03\%} & \textcolor[HTML]{4285f4}{24.69\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.12\%} & \textcolor[HTML]{4285f4}{9.25\%} & \textcolor[HTML]{4285f4}{-9.56\%} & \textcolor[HTML]{4285f4}{-2.98\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{33.57\%} & \textcolor[HTML]{4285f4}{31.05\%} & \textcolor[HTML]{4285f4}{26.93\%} & \textcolor[HTML]{4285f4}{25.86\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.67\%} & \textcolor[HTML]{4285f4}{23.43\%} & \textcolor[HTML]{4285f4}{12.92\%} & \textcolor[HTML]{4285f4}{10.29\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{31.81\%} & \textcolor[HTML]{4285f4}{28.91\%} & \textcolor[HTML]{4285f4}{34.66\%} & \textcolor[HTML]{4285f4}{23.57\%}\\
-\addlinespace
-\textbf{Coffee-C (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.91\%} & \textcolor[HTML]{4285f4}{20.38\%} & \textcolor[HTML]{4285f4}{2.2\%} & \textcolor[HTML]{4285f4}{1.99\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{43.84\%} & \textcolor[HTML]{4285f4}{32.3\%} & \textcolor[HTML]{4285f4}{30.17\%} & \textcolor[HTML]{4285f4}{31.86\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.51\%} & \textcolor[HTML]{4285f4}{26.49\%} & \textcolor[HTML]{4285f4}{2.66\%} & \textcolor[HTML]{4285f4}{14.36\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{48.82\%} & \textcolor[HTML]{4285f4}{32.6\%} & \textcolor[HTML]{4285f4}{29.92\%} & \textcolor[HTML]{4285f4}{31.52\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-16.87\%} & \textcolor[HTML]{4285f4}{14.38\%} & \textcolor[HTML]{4285f4}{3.4\%} & \textcolor[HTML]{4285f4}{-10.24\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.35\%} & \textcolor[HTML]{4285f4}{32.06\%} & \textcolor[HTML]{4285f4}{30.22\%} & \textcolor[HTML]{4285f4}{32.24\%}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.24\%} & \textcolor[HTML]{4285f4}{0.95\%} & \textcolor[HTML]{4285f4}{12.53\%} & \textcolor[HTML]{4285f4}{0.5\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.38\%} & \textcolor[HTML]{4285f4}{29.01\%} & \textcolor[HTML]{4285f4}{33.26\%} & \textcolor[HTML]{4285f4}{20.61\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{22.64\%} & \textcolor[HTML]{4285f4}{7.85\%} & \textcolor[HTML]{4285f4}{35.53\%} & \textcolor[HTML]{4285f4}{10.84\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.02\%} & \textcolor[HTML]{4285f4}{29.71\%} & \textcolor[HTML]{4285f4}{33.94\%} & \textcolor[HTML]{4285f4}{21.33\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-16.46\%} & \textcolor[HTML]{4285f4}{-5.92\%} & \textcolor[HTML]{4285f4}{-9.36\%} & \textcolor[HTML]{4285f4}{-8.91\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.77\%} & \textcolor[HTML]{4285f4}{28.35\%} & \textcolor[HTML]{4285f4}{32.59\%} & \textcolor[HTML]{4285f4}{19.95\%}\\
-\textbf{Lumber (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.9\%} & \textcolor[HTML]{4285f4}{-3.58\%} & \textcolor[HTML]{4285f4}{11.74\%} & \textcolor[HTML]{4285f4}{5.06\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.58\%} & \textcolor[HTML]{4285f4}{29.39\%} & \textcolor[HTML]{4285f4}{36.31\%} & \textcolor[HTML]{4285f4}{25.1\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-8.48\%} & \textcolor[HTML]{4285f4}{-2.37\%} & \textcolor[HTML]{4285f4}{29.11\%} & \textcolor[HTML]{4285f4}{**26.99\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.43\%} & \textcolor[HTML]{4285f4}{30.72\%} & \textcolor[HTML]{4285f4}{35.45\%} & \textcolor[HTML]{4285f4}{21.26\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.68\%} & \textcolor[HTML]{4285f4}{-4.77\%} & \textcolor[HTML]{4285f4}{-5.04\%} & \textcolor[HTML]{4285f4}{-17.14\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.56\%} & \textcolor[HTML]{4285f4}{28.2\%} & \textcolor[HTML]{4285f4}{37.23\%} & \textcolor[HTML]{4285f4}{28.45\%}\\
-\textbf{Orange juice (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.67\%} & \textcolor[HTML]{4285f4}{13.87\%} & \textcolor[HTML]{4285f4}{14.4\%} & \textcolor[HTML]{4285f4}{3.8\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{29.5\%} & \textcolor[HTML]{4285f4}{33.01\%} & \textcolor[HTML]{4285f4}{34.43\%} & \textcolor[HTML]{4285f4}{29.37\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.38\%} & \textcolor[HTML]{4285f4}{-2.22\%} & \textcolor[HTML]{4285f4}{18.24\%} & \textcolor[HTML]{4285f4}{18.64\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{28.01\%} & \textcolor[HTML]{4285f4}{33.01\%} & \textcolor[HTML]{4285f4}{30.09\%} & \textcolor[HTML]{4285f4}{28.64\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.83\%} & \textcolor[HTML]{4285f4}{29.93\%} & \textcolor[HTML]{4285f4}{12.29\%} & \textcolor[HTML]{4285f4}{-8.64\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{31.05\%} & \textcolor[HTML]{4285f4}{33.1\%} & \textcolor[HTML]{4285f4}{38.06\%} & \textcolor[HTML]{4285f4}{30.11\%}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.56\%} & \textcolor[HTML]{4285f4}{24.87\%} & \textcolor[HTML]{4285f4}{11.82\%} & \textcolor[HTML]{4285f4}{-1.16\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.88\%} & \textcolor[HTML]{4285f4}{33.25\%} & \textcolor[HTML]{4285f4}{37.9\%} & \textcolor[HTML]{4285f4}{28.72\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.98\%} & \textcolor[HTML]{4285f4}{29.51\%} & \textcolor[HTML]{4285f4}{2.7\%} & \textcolor[HTML]{4285f4}{-8.07\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{33.23\%} & \textcolor[HTML]{4285f4}{33.6\%} & \textcolor[HTML]{4285f4}{41.29\%} & \textcolor[HTML]{4285f4}{27.69\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-20.49\%} & \textcolor[HTML]{4285f4}{20.35\%} & \textcolor[HTML]{4285f4}{21.47\%} & \textcolor[HTML]{4285f4}{4.7\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{36.48\%} & \textcolor[HTML]{4285f4}{32.98\%} & \textcolor[HTML]{4285f4}{34.09\%} & \textcolor[HTML]{4285f4}{29.83\%}\\
-\addlinespace
-\textbf{Natural gas (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{35.38\%} & \textcolor[HTML]{4285f4}{16.25\%} & \textcolor[HTML]{4285f4}{0.93\%} & \textcolor[HTML]{4285f4}{8.33\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{61.55\%} & \textcolor[HTML]{4285f4}{54.6\%} & \textcolor[HTML]{4285f4}{53.58\%} & \textcolor[HTML]{4285f4}{44.58\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**85.84\%} & \textcolor[HTML]{4285f4}{4.76\%} & \textcolor[HTML]{4285f4}{-2.32\%} & \textcolor[HTML]{4285f4}{18.33\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{63.46\%} & \textcolor[HTML]{4285f4}{47.3\%} & \textcolor[HTML]{4285f4}{48.85\%} & \textcolor[HTML]{4285f4}{42.59\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-11.98\%} & \textcolor[HTML]{4285f4}{27.84\%} & \textcolor[HTML]{4285f4}{4.77\%} & \textcolor[HTML]{4285f4}{3.25\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{59.76\%} & \textcolor[HTML]{4285f4}{61.3\%} & \textcolor[HTML]{4285f4}{58.18\%} & \textcolor[HTML]{4285f4}{46.41\%}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{15.43\%} & \textcolor[HTML]{4285f4}{*28.74\%} & \textcolor[HTML]{4285f4}{9.67\%} & \textcolor[HTML]{4285f4}{-5.64\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{39.87\%} & \textcolor[HTML]{4285f4}{32.56\%} & \textcolor[HTML]{4285f4}{42.84\%} & \textcolor[HTML]{4285f4}{34.69\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{29.17\%} & \textcolor[HTML]{4285f4}{*35.61\%} & \textcolor[HTML]{4285f4}{11.47\%} & \textcolor[HTML]{4285f4}{14.24\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{36.74\%} & \textcolor[HTML]{4285f4}{32.09\%} & \textcolor[HTML]{4285f4}{28.19\%} & \textcolor[HTML]{4285f4}{26.94\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.21\%} & \textcolor[HTML]{4285f4}{22.04\%} & \textcolor[HTML]{4285f4}{9.95\%} & \textcolor[HTML]{4285f4}{-24.85\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.74\%} & \textcolor[HTML]{4285f4}{33.1\%} & \textcolor[HTML]{4285f4}{53.7\%} & \textcolor[HTML]{4285f4}{41.08\%}\\
-\textbf{Gasoline (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.65\%} & \textcolor[HTML]{4285f4}{30.95\%} & \textcolor[HTML]{4285f4}{10.59\%} & \textcolor[HTML]{4285f4}{-5.37\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.77\%} & \textcolor[HTML]{4285f4}{41.76\%} & \textcolor[HTML]{4285f4}{40.07\%} & \textcolor[HTML]{4285f4}{37.09\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{39\%} & \textcolor[HTML]{4285f4}{19.82\%} & \textcolor[HTML]{4285f4}{23.98\%} & \textcolor[HTML]{4285f4}{9.69\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.47\%} & \textcolor[HTML]{4285f4}{39.38\%} & \textcolor[HTML]{4285f4}{31.41\%} & \textcolor[HTML]{4285f4}{32.1\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.22\%} & \textcolor[HTML]{4285f4}{42.13\%} & \textcolor[HTML]{4285f4}{-0.09\%} & \textcolor[HTML]{4285f4}{-19.47\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{43.14\%} & \textcolor[HTML]{4285f4}{44.13\%} & \textcolor[HTML]{4285f4}{47.11\%} & \textcolor[HTML]{4285f4}{41.71\%}\\
-\textbf{Heating oil (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.31\%} & \textcolor[HTML]{4285f4}{*29.88\%} & \textcolor[HTML]{4285f4}{6.83\%} & \textcolor[HTML]{4285f4}{-3.44\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{40.75\%} & \textcolor[HTML]{4285f4}{35.09\%} & \textcolor[HTML]{4285f4}{33.17\%} & \textcolor[HTML]{4285f4}{30.56\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{36.32\%} & \textcolor[HTML]{4285f4}{29.41\%} & \textcolor[HTML]{4285f4}{25.56\%} & \textcolor[HTML]{4285f4}{15.16\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{41.37\%} & \textcolor[HTML]{4285f4}{33.33\%} & \textcolor[HTML]{4285f4}{25.95\%} & \textcolor[HTML]{4285f4}{24.62\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.74\%} & \textcolor[HTML]{4285f4}{30.5\%} & \textcolor[HTML]{4285f4}{-10.77\%} & \textcolor[HTML]{4285f4}{-21.62\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{40.19\%} & \textcolor[HTML]{4285f4}{36.98\%} & \textcolor[HTML]{4285f4}{39.16\%} & \textcolor[HTML]{4285f4}{35.69\%}\\
-\textbf{Copper (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.45\%} & \textcolor[HTML]{4285f4}{*28.15\%} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{-0.1\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.23\%} & \textcolor[HTML]{4285f4}{31.89\%} & \textcolor[HTML]{4285f4}{34.91\%} & \textcolor[HTML]{4285f4}{19.56\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.14\%} & \textcolor[HTML]{4285f4}{22.17\%} & \textcolor[HTML]{4285f4}{16.53\%} & \textcolor[HTML]{4285f4}{12.1\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.71\%} & \textcolor[HTML]{4285f4}{30.05\%} & \textcolor[HTML]{4285f4}{25.73\%} & \textcolor[HTML]{4285f4}{18.16\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.28\%} & \textcolor[HTML]{4285f4}{34.17\%} & \textcolor[HTML]{4285f4}{-3.46\%} & \textcolor[HTML]{4285f4}{-12.15\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.78\%} & \textcolor[HTML]{4285f4}{33.69\%} & \textcolor[HTML]{4285f4}{42.28\%} & \textcolor[HTML]{4285f4}{20.87\%}\\
-\addlinespace
-\textbf{Gold (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.5\%} & \textcolor[HTML]{4285f4}{14.35\%} & \textcolor[HTML]{4285f4}{14.01\%} & \textcolor[HTML]{4285f4}{0.53\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.14\%} & \textcolor[HTML]{4285f4}{18.89\%} & \textcolor[HTML]{4285f4}{21.46\%} & \textcolor[HTML]{4285f4}{14.41\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{9.19\%} & \textcolor[HTML]{4285f4}{13.37\%} & \textcolor[HTML]{4285f4}{9.37\%} & \textcolor[HTML]{4285f4}{4.21\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.89\%} & \textcolor[HTML]{4285f4}{19.2\%} & \textcolor[HTML]{4285f4}{17.03\%} & \textcolor[HTML]{4285f4}{12.36\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.01\%} & \textcolor[HTML]{4285f4}{15.37\%} & \textcolor[HTML]{4285f4}{19.1\%} & \textcolor[HTML]{4285f4}{-3.1\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.24\%} & \textcolor[HTML]{4285f4}{18.58\%} & \textcolor[HTML]{4285f4}{25.21\%} & \textcolor[HTML]{4285f4}{16.23\%}\\
-\textbf{Palladium (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{9.12\%} & \textcolor[HTML]{4285f4}{9.03\%} & \textcolor[HTML]{4285f4}{*29.12\%} & \textcolor[HTML]{4285f4}{13.75\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.27\%} & \textcolor[HTML]{4285f4}{32.71\%} & \textcolor[HTML]{4285f4}{36.14\%} & \textcolor[HTML]{4285f4}{25.38\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**49.79\%} & \textcolor[HTML]{4285f4}{24.47\%} & \textcolor[HTML]{4285f4}{30.01\%} & \textcolor[HTML]{4285f4}{**31.93\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.98\%} & \textcolor[HTML]{4285f4}{34.23\%} & \textcolor[HTML]{4285f4}{33.49\%} & \textcolor[HTML]{4285f4}{23.82\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-30.19\%} & \textcolor[HTML]{4285f4}{-6.3\%} & \textcolor[HTML]{4285f4}{30.58\%} & \textcolor[HTML]{4285f4}{-4.88\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{41.22\%} & \textcolor[HTML]{4285f4}{31.2\%} & \textcolor[HTML]{4285f4}{38.71\%} & \textcolor[HTML]{4285f4}{26.8\%}\\
-\textbf{Platinum (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{12.93\%} & \textcolor[HTML]{4285f4}{10.56\%} & \textcolor[HTML]{4285f4}{7.29\%} & \textcolor[HTML]{4285f4}{-7.92\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.62\%} & \textcolor[HTML]{4285f4}{22.66\%} & \textcolor[HTML]{4285f4}{25.53\%} & \textcolor[HTML]{4285f4}{19.48\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**29.46\%} & \textcolor[HTML]{4285f4}{*25.07\%} & \textcolor[HTML]{4285f4}{10.46\%} & \textcolor[HTML]{4285f4}{1.17\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.1\%} & \textcolor[HTML]{4285f4}{22.51\%} & \textcolor[HTML]{4285f4}{21.24\%} & \textcolor[HTML]{4285f4}{18.04\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-3.22\%} & \textcolor[HTML]{4285f4}{-3.81\%} & \textcolor[HTML]{4285f4}{8.04\%} & \textcolor[HTML]{4285f4}{-17.28\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23.12\%} & \textcolor[HTML]{4285f4}{22.81\%} & \textcolor[HTML]{4285f4}{28.75\%} & \textcolor[HTML]{4285f4}{20.8\%}\\
-\textbf{Silver (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{17.54\%} & \textcolor[HTML]{4285f4}{21.96\%} & \textcolor[HTML]{4285f4}{-2.43\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22\%} & \textcolor[HTML]{4285f4}{33.92\%} & \textcolor[HTML]{4285f4}{39.87\%} & \textcolor[HTML]{4285f4}{24.35\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.98\%} & \textcolor[HTML]{4285f4}{14.29\%} & \textcolor[HTML]{4285f4}{19.66\%} & \textcolor[HTML]{4285f4}{3.44\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.07\%} & \textcolor[HTML]{4285f4}{32.5\%} & \textcolor[HTML]{4285f4}{37.17\%} & \textcolor[HTML]{4285f4}{20.3\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.57\%} & \textcolor[HTML]{4285f4}{20.83\%} & \textcolor[HTML]{4285f4}{26.77\%} & \textcolor[HTML]{4285f4}{-8.09\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.93\%} & \textcolor[HTML]{4285f4}{35.34\%} & \textcolor[HTML]{4285f4}{42.44\%} & \textcolor[HTML]{4285f4}{27.77\%}\\
-\textbf{Aluminium (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.13\%} & \textcolor[HTML]{4285f4}{13.78\%} & \textcolor[HTML]{4285f4}{-3.58\%} & \textcolor[HTML]{4285f4}{3.15\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.6\%} & \textcolor[HTML]{4285f4}{26.41\%} & \textcolor[HTML]{4285f4}{26.48\%} & \textcolor[HTML]{4285f4}{18.56\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.56\%} & \textcolor[HTML]{4285f4}{14.78\%} & \textcolor[HTML]{4285f4}{16.25\%} & \textcolor[HTML]{4285f4}{**23.68\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.82\%} & \textcolor[HTML]{4285f4}{25.57\%} & \textcolor[HTML]{4285f4}{24.94\%} & \textcolor[HTML]{4285f4}{18.94\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.38\%} & \textcolor[HTML]{4285f4}{12.86\%} & \textcolor[HTML]{4285f4}{-23.04\%} & \textcolor[HTML]{4285f4}{-16.74\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.13\%} & \textcolor[HTML]{4285f4}{27.29\%} & \textcolor[HTML]{4285f4}{28.01\%} & \textcolor[HTML]{4285f4}{18.23\%}\\
-\addlinespace
-\textbf{Copper (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.45\%} & \textcolor[HTML]{4285f4}{**28.59\%} & \textcolor[HTML]{4285f4}{5.74\%} & \textcolor[HTML]{4285f4}{0.03\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.25\%} & \textcolor[HTML]{4285f4}{31.09\%} & \textcolor[HTML]{4285f4}{34.27\%} & \textcolor[HTML]{4285f4}{18.92\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.54\%} & \textcolor[HTML]{4285f4}{25.22\%} & \textcolor[HTML]{4285f4}{18.66\%} & \textcolor[HTML]{4285f4}{11.99\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.98\%} & \textcolor[HTML]{4285f4}{29.01\%} & \textcolor[HTML]{4285f4}{25.53\%} & \textcolor[HTML]{4285f4}{17.92\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.95\%} & \textcolor[HTML]{4285f4}{32\%} & \textcolor[HTML]{4285f4}{-6.78\%} & \textcolor[HTML]{4285f4}{-11.89\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.41\%} & \textcolor[HTML]{4285f4}{32.98\%} & \textcolor[HTML]{4285f4}{41.31\%} & \textcolor[HTML]{4285f4}{19.86\%}\\
-\textbf{Lead (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.83\%} & \textcolor[HTML]{4285f4}{28.99\%} & \textcolor[HTML]{4285f4}{10.74\%} & \textcolor[HTML]{4285f4}{2.07\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.64\%} & \textcolor[HTML]{4285f4}{41.74\%} & \textcolor[HTML]{4285f4}{41.05\%} & \textcolor[HTML]{4285f4}{23.26\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{7.59\%} & \textcolor[HTML]{4285f4}{11.21\%} & \textcolor[HTML]{4285f4}{9.87\%} & \textcolor[HTML]{4285f4}{17.05\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.16\%} & \textcolor[HTML]{4285f4}{39.91\%} & \textcolor[HTML]{4285f4}{35.35\%} & \textcolor[HTML]{4285f4}{23.37\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.09\%} & \textcolor[HTML]{4285f4}{*46.48\%} & \textcolor[HTML]{4285f4}{12.65\%} & \textcolor[HTML]{4285f4}{-13.41\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.12\%} & \textcolor[HTML]{4285f4}{43.16\%} & \textcolor[HTML]{4285f4}{46.22\%} & \textcolor[HTML]{4285f4}{23.09\%}\\
-\textbf{Nickel (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{19.31\%} & \textcolor[HTML]{4285f4}{12.5\%} & \textcolor[HTML]{4285f4}{3.52\%} & \textcolor[HTML]{4285f4}{0.31\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.26\%} & \textcolor[HTML]{4285f4}{44.27\%} & \textcolor[HTML]{4285f4}{41.45\%} & \textcolor[HTML]{4285f4}{28.98\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{23.25\%} & \textcolor[HTML]{4285f4}{-39.24\%} & \textcolor[HTML]{4285f4}{16.3\%} & \textcolor[HTML]{4285f4}{**35.09\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.23\%} & \textcolor[HTML]{4285f4}{41.62\%} & \textcolor[HTML]{4285f4}{34.48\%} & \textcolor[HTML]{4285f4}{29.13\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{15.46\%} & \textcolor[HTML]{4285f4}{**63.47\%} & \textcolor[HTML]{4285f4}{-7.67\%} & \textcolor[HTML]{4285f4}{**-34.64\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.28\%} & \textcolor[HTML]{4285f4}{46.72\%} & \textcolor[HTML]{4285f4}{47.44\%} & \textcolor[HTML]{4285f4}{28.6\%}\\
-\textbf{Tin (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.07\%} & \textcolor[HTML]{4285f4}{*29.1\%} & \textcolor[HTML]{4285f4}{7.46\%} & \textcolor[HTML]{4285f4}{1.68\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.38\%} & \textcolor[HTML]{4285f4}{31.71\%} & \textcolor[HTML]{4285f4}{35.61\%} & \textcolor[HTML]{4285f4}{18.79\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{*15.83\%} & \textcolor[HTML]{4285f4}{34.62\%} & \textcolor[HTML]{4285f4}{23.7\%} & \textcolor[HTML]{4285f4}{4.48\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.99\%} & \textcolor[HTML]{4285f4}{31.4\%} & \textcolor[HTML]{4285f4}{29.09\%} & \textcolor[HTML]{4285f4}{15.27\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-7.78\%} & \textcolor[HTML]{4285f4}{23.88\%} & \textcolor[HTML]{4285f4}{-6.82\%} & \textcolor[HTML]{4285f4}{-1.69\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.77\%} & \textcolor[HTML]{4285f4}{32.08\%} & \textcolor[HTML]{4285f4}{41.13\%} & \textcolor[HTML]{4285f4}{21.68\%}\\
-\textbf{Zinc (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.52\%} & \textcolor[HTML]{4285f4}{20.13\%} & \textcolor[HTML]{4285f4}{7.62\%} & \textcolor[HTML]{4285f4}{9.07\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.73\%} & \textcolor[HTML]{4285f4}{38.77\%} & \textcolor[HTML]{4285f4}{36.17\%} & \textcolor[HTML]{4285f4}{23.25\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-9.06\%} & \textcolor[HTML]{4285f4}{2.95\%} & \textcolor[HTML]{4285f4}{10.05\%} & \textcolor[HTML]{4285f4}{**29.42\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.15\%} & \textcolor[HTML]{4285f4}{36.86\%} & \textcolor[HTML]{4285f4}{33.28\%} & \textcolor[HTML]{4285f4}{22.12\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.13\%} & \textcolor[HTML]{4285f4}{37.11\%} & \textcolor[HTML]{4285f4}{5.43\%} & \textcolor[HTML]{4285f4}{-11.31\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.38\%} & \textcolor[HTML]{4285f4}{40.51\%} & \textcolor[HTML]{4285f4}{39.03\%} & \textcolor[HTML]{4285f4}{24.32\%}\\
-\addlinespace
-\textbf{US commodities} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{*6.89\%} & \textcolor[HTML]{4285f4}{**15.89\%} & \textcolor[HTML]{4285f4}{9.39\%} & \textcolor[HTML]{4285f4}{-0.18\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{10\%} & \textcolor[HTML]{4285f4}{13.62\%} & \textcolor[HTML]{4285f4}{17.58\%} & \textcolor[HTML]{4285f4}{9.86\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{***15.44\%} & \textcolor[HTML]{4285f4}{*15.66\%} & \textcolor[HTML]{4285f4}{13.4\%} & \textcolor[HTML]{4285f4}{6.82\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{9.88\%} & \textcolor[HTML]{4285f4}{14.21\%} & \textcolor[HTML]{4285f4}{14.83\%} & \textcolor[HTML]{4285f4}{8.59\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-1.09\%} & \textcolor[HTML]{4285f4}{*16.16\%} & \textcolor[HTML]{4285f4}{4.9\%} & \textcolor[HTML]{4285f4}{-6.33\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{10.09\%} & \textcolor[HTML]{4285f4}{13.05\%} & \textcolor[HTML]{4285f4}{19.98\%} & \textcolor[HTML]{4285f4}{10.95\%}\\
-\textbf{GB commodities} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.47\%} & \textcolor[HTML]{4285f4}{*21.77\%} & \textcolor[HTML]{4285f4}{5.25\%} & \textcolor[HTML]{4285f4}{2.72\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.66\%} & \textcolor[HTML]{4285f4}{26.91\%} & \textcolor[HTML]{4285f4}{30.24\%} & \textcolor[HTML]{4285f4}{16.19\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.41\%} & \textcolor[HTML]{4285f4}{8.01\%} & \textcolor[HTML]{4285f4}{15.06\%} & \textcolor[HTML]{4285f4}{**19.95\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.39\%} & \textcolor[HTML]{4285f4}{25.92\%} & \textcolor[HTML]{4285f4}{25.94\%} & \textcolor[HTML]{4285f4}{15.13\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.34\%} & \textcolor[HTML]{4285f4}{*35.56\%} & \textcolor[HTML]{4285f4}{-5.24\%} & \textcolor[HTML]{4285f4}{-14.05\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.87\%} & \textcolor[HTML]{4285f4}{27.88\%} & \textcolor[HTML]{4285f4}{34.06\%} & \textcolor[HTML]{4285f4}{17.1\%}\\
-\bottomrule
-
-\end{longtable}
-
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{7}{9}\selectfont
-
-\begin{longtable}[t]{>{}l>{}l>{}l>{}l>{}r>{}r}
-
-\caption{\label{tbl-regime-diference-tests}This table shows the results
-for tests of difference in mean (t-test) and variance (F-test) between
-phases of aggregate backwardation and contango for the twenty four
-individual US commodities and the six GB metals considered in the study
-as well as for two equally weighted portfolios formed from the US
-commodities and the GB metals respectively across the four periods of
-interest (past: 1997-2003; financialisation: 2004-2008; crisis:
-2008-2013; post-crisis: 2013-2018). 1\%, 5\% and 10\% p-value levels are
-marked with ***, ** and * respectively in the significance column.
-Aggregate CHP construction and corresponding regime definitions are
-discussed in Section~\ref{sec-methods} while the results are discussed
-in Section~\ref{sec-results}.}
-
-\tabularnewline
-
-\toprule
-\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{period}} & \textcolor{black}{\textbf{moment}} & \textcolor{black}{\textbf{dominant regime}} & \textcolor{black}{\textbf{p-value}} & \textcolor{black}{\textbf{significance}}\\
-\midrule
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{34.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{89.69\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{91.01\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{47.46\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{40.83\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{34} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{57.39\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.02\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{Oats (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{38.12\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{33} ***}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{35.29\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{8} ***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.66\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{32} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{82.72\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{Soybean meal (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{66.39\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{81.2\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.83\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{56.57\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{31} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{75.13\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.31\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Soybean oil (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{31.59\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{81.72\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{92.18\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.2\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.64\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{30} ***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{69.59\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.36\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{Soybeans (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{48.92\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{17.18\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{38.74\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{7} ***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{57.61\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{29} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.95\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.05\%} & \textcolor[HTML]{4285f4}{*}\\
-\addlinespace
-\textbf{Wheat-SRW (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{44.86\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.79\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{83.21\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{6} ***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{76.2\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.81\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{94.9\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{76.82\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.34\%} & \textcolor[HTML]{4285f4}{*}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.35\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{62.38\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{99.19\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{28} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{50.04\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{5} ***}\\
-\textbf{Cattle-live (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.11\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{15.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.61\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{20.96\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{82.12\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{63.19\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{4} ***}\\
-\textbf{Lean hogs (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{45.71\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{24.77\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{55.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{3} ***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{68.46\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{21.55\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{6.81\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{Cocoa (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{99.36\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{12.33\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.85\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{7.73\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{42.98\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{27} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{51.48\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.17\%} & \textcolor[HTML]{4285f4}{**}\\
-\addlinespace
-\textbf{Coffee-C (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{53.38\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{69.3\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.63\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{95.23\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{82.84\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{35.39\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{52.86\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.02\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{41.38\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{59.06\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{26.81\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{14.44\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{33.04\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{32.06\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.67\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{Lumber (XCME)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.56\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{75.67\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{84.3\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.36\%} & \textcolor[HTML]{4285f4}{**}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{28.12\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{22.82\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.31\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{26} ***}\\
-\textbf{Orange juice (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{66.85\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{28.81\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{92.47\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.55\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{25} ***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{25.72\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.01\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{24.1\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.76\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{75.29\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.89\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{56.23\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.08\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.22\%} & \textcolor[HTML]{4285f4}{*}\\
-\addlinespace
-\textbf{Natural gas (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.66\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.01\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{68.1\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{24} ***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.28\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{23} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.04\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.08\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{38.33\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{22} ***}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{61.91\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{49.38\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{95.55\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{21} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.99\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{20} ***}\\
-\textbf{Gasoline (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.96\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{66.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{58.35\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.58\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{49.08\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{19} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.23\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{18} ***}\\
-\textbf{Heating oil (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{21.83\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.45\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{99.52\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.52\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{23.31\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{17} ***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{15.71\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{16} ***}\\
-\textbf{Copper (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{90.64\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{17.88\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{74.37\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.71\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{55.78\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{15} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{17.19\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\addlinespace
-\textbf{Gold (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{43.44\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.63\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.92\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{60.22\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{14} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{56.58\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{13} ***}\\
-\textbf{Palladium (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.77\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{12} ***}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{30.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.38\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.05\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{9.4\%} & \textcolor[HTML]{4285f4}{*}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{Platinum (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.08\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{14.41\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.86\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{85.5\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{11} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{27.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{Silver (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.07\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.09\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{88.44\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.01\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.12\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.08\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{61.83\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{10} ***}\\
-\textbf{Aluminium (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{86.1\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{9} ***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.59\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.33\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{10.79\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.41\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.33\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{25.99\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{Copper (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{88.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.59\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.15\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{43.61\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{8} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{16.36\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{Lead (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{58.96\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.81\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{40.11\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.11\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.17\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{7} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{15.62\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{85.45\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Nickel (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{76.56\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.04\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{1.24\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.62\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{49.29\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{6} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.46\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{69.15\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Tin (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.22\%} & \textcolor[HTML]{4285f4}{*}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{14.94\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{70.17\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{58.14\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.29\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{5} ***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{73.44\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{4} ***}\\
-\textbf{Zinc (XLME)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.39\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.75\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.67\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.29\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.89\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.05\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{1.77\%} & \textcolor[HTML]{4285f4}{**}\\
-\addlinespace
-\textbf{US commodities} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{3.63\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{54.29\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{93.09\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.22\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{58.92\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{3} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{11.83\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
-\textbf{GB commodities} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{78.74\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{27.95\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.65\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{46.83\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.37\%} & \textcolor[HTML]{4285f4}{**}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.13\%} & \textcolor[HTML]{4285f4}{***}\\
-\bottomrule
-
-\end{longtable}
-
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{7}{9}\selectfont
-
-\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
-
-\caption{\label{tbl-time-reg-US-CHP}This table shows the average time
-series \(R^{2}\) for models where the returns series for the twenty four
-individual US commodities are independently regressed against relative
-change in their own commercial hedging pressure (CHP) series as well as
-against that in aggregate CHP, a market wide measure of CHP which
-calculation method is discussed in Section~\ref{sec-methods}. Averages
-are calculated independently across the whole cross-section of US traded
-commodity assets considered in the study as well as across commodity
-sectors and sub-sectors for the four periods of interest (past:
-1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
-2013-2018). The results are discussed in Section~\ref{sec-results} while
-Section~\ref{sec-taxonomy} details the taxonomy for the commodity assets
-considered.}
+Section~\ref{sec-results} and the commodity assets taxonomy is detailed
+in Section~\ref{sec-taxonomy}.}
 
@@
 \caption{\label{tbl-correlations-inner-periods}This table shows the
-average return pairwise correlation coefficients calculated
-independently across the whole cross-section of commodity assets
-considered in the study as well as within countries and commodity
-sectors and sub-sectors for the four periods of interest (past:
-1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
-2013-2018). For each period, the results are calculated independently
-over the entire period as well as over phases of aggregate backwardation
-and contango. Aggregate CHP construction and corresponding regime
-definitions are discussed in Section~\ref{sec-methods} while the results
-are discussed in Section~\ref{sec-results} and the taxonomy for the
-commodity assets considered is detailed in Section~\ref{sec-taxonomy}.}
+average return pairwise correlation coefficients computed independently
+across the whole cross-section of individual commodity assets as well as
+within countries and commodity sectors and sub-sectors for the four
+periods. For each period, the results are computed independently over
+the entire period as well as over phases of \textbf{backwardation} and
+\textbf{contango}. \textbf{Backwardation} and \textbf{contango} regimes
+as well as period definitions are discussed in Section~\ref{sec-methods}
+while the results are discussed in Section~\ref{sec-results} and the
+commodity assets taxonomy is detailed in Section~\ref{sec-taxonomy}.}
 
@@
 weighted US sub-sector portfolios (agriculturals: gains, livestock,
-softs; energy: gas, petroleum; metals: base, precious). The results are
-independently calculated for the four periods of interest (past:
-1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
-2013-2018). For each period, the results are further calculated
-independently over the entire period as well as over phases of aggregate
-backwardation and contango. Aggregate CHP construction and corresponding
-regime definitions are discussed in Section~\ref{sec-methods} while the
-results are discussed in Section~\ref{sec-results} and the taxonomy for
-the commodity assets considered is detailed in
-Section~\ref{sec-taxonomy}.}
+softs; energy: gas, petroleum; metals: base, precious) independently
+computed for the four periods. For each period, the results are further
+computed independently over the entire period as well as over phases
+\textbf{backwardation} and \textbf{contango}. \textbf{Backwardation} and
+\textbf{contango} regimes as well as period definitions are discussed in
+Section~\ref{sec-methods} while the results are discussed in
+Section~\ref{sec-results} and the commodity assets taxonomy is detailed
+in Section~\ref{sec-taxonomy}.}
 
@@
 \midrule
-\textbf{whole period} & \textcolor[HTML]{4285f4}{0.0421} & \textcolor[HTML]{4285f4}{0.0631} & \textcolor[HTML]{4285f4}{0.0799} & \textcolor[HTML]{4285f4}{0.0778}\\
-\textbf{backwardation} & \textcolor[HTML]{4285f4}{0.1166} & \textcolor[HTML]{4285f4}{0.0201} & \textcolor[HTML]{4285f4}{0.0633} & \textcolor[HTML]{4285f4}{0.0727}\\
-\textbf{contango} & \textcolor[HTML]{4285f4}{0.0297} & \textcolor[HTML]{4285f4}{0.1164} & \textcolor[HTML]{4285f4}{0.0889} & \textcolor[HTML]{4285f4}{0.0812}\\
+\textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0421}} & \textcolor[HTML]{4285f4}{\textbf{0.0631}} & \textcolor[HTML]{4285f4}{\textbf{0.0799}} & \textcolor[HTML]{4285f4}{\textbf{0.0778}}\\
+\textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.1166}} & \textcolor[HTML]{4285f4}{\textbf{0.0201}} & \textcolor[HTML]{4285f4}{\textbf{0.0633}} & \textcolor[HTML]{4285f4}{\textbf{0.0727}}\\
+\textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0297}} & \textcolor[HTML]{4285f4}{\textbf{0.1164}} & \textcolor[HTML]{4285f4}{\textbf{0.0889}} & \textcolor[HTML]{4285f4}{\textbf{0.0812}}\\
 \bottomrule
@@
 
-\newpage
-
 \begin{landscape}\begingroup\fontsize{7}{9}\selectfont
@@
 \caption{\label{tbl-correlations-inner-years}While
-Table~\ref{tbl-correlations-inner-periods} shows results calculated
-independently for the four periods of interest (past: 1997-2003;
-financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018),
-this stable shows the results of the same analysis calculated by year
-over the entire sample period (1997-2018). The results are discussed in
-Section~\ref{sec-results} while Section~\ref{sec-taxonomy} details the
-taxonomy for the commodity assets considered.}
+Table~\ref{tbl-correlations-inner-periods} shows results computed
+independently for the four periods, this table shows the results of the
+same analysis implemented for each year over the entire sample period.
+The results are discussed in Section~\ref{sec-results} while
+Section~\ref{sec-taxonomy} details the commodity assets taxonomy.}
 
@@
 series regression coefficients for models where the returns series for
-all the commodity assets considered in the study are independently
-regressed against the return series for our market factor, an equally
-weighted portfolio of the 24 US commodities considered in the study. The
-results are calculated independently across countries as well as
-commodity sectors and sub-sectors for the four periods of interest
-(past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013;
-post-crisis: 2013-2018). The market factor construction is discussed in
-Section~\ref{sec-methods} while the results are discussed in
-Section~\ref{sec-results} and the taxonomy for the commodity assets
-considered is detailed in Section~\ref{sec-taxonomy}.}
+all the commodity assets are independently regressed against the return
+series for our market factor, an equally weighted portfolio of the US
+traded commodities. The results are computed independently across
+countries as well as commodity sectors and sub-sectors for the four
+periods. Period definitions along with the market factor construction
+method are discussed in Section~\ref{sec-methods} while the results are
+discussed in Section~\ref{sec-results} and the commodity assets taxonomy
+is detailed in Section~\ref{sec-taxonomy}.}
 
@@
 
-\begin{longtable}[t]{>{}l>{}l>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+\begin{longtable}[t]{>{}l>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
 
@@
 time series regression \(R^{2}\) for models where the returns series for
-all the commodity assets considered in the study are independently
-regressed against the return series for our mimicking portfolios for
-risk factors in returns, including the market, CHP, open interest and
-term structure factors. The results are calculated independently across
-countries and commodity sectors and sub-sectors for the four periods of
-interest (past: 1997-2003; financialisation: 2004-2008; crisis:
-2008-2013; post-crisis: 2013-2018); for each period the results are
-calculated independently over the entire period as well as over phases
-of aggregate backwardation and contango. Factors as well as aggregate
-CHP construction and corresponding regime definitions are discussed in
-Section~\ref{sec-methods} while the results are discussed in
-Section~\ref{sec-results} and the taxonomy for the commodity assets
-considered is detailed in Section~\ref{sec-taxonomy}.}
+all the commodity assets are independently regressed against the return
+series for our mimicking portfolios for risk factors in returns,
+including the market, CHP, open interest and term structure factors. The
+results are computed independently across countries and commodity
+sectors and sub-sectors for the four periods. A breakdown of the
+estimates computed independently over the whole periods as well as over
+phases of \textbf{backwardation} and \textbf{contango} is provided in
+the attached
+\href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
+Appendix}. Factor construction methods along with \textbf{backwardation}
+and \textbf{contango} regimes as well as period definitions are
+discussed in Section~\ref{sec-methods} while the results are discussed
+in Section~\ref{sec-results} and the commodity assets taxonomy is
+detailed in Section~\ref{sec-taxonomy}.}
 
@@
 \toprule
-\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{factor}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{factor}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.69\%}} & \textcolor[HTML]{4285f4}{\textbf{19.7\%}} & \textcolor[HTML]{4285f4}{\textbf{31.3\%}} & \textcolor[HTML]{4285f4}{\textbf{14.73\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.44\%}} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{11.82\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{10.07\%}} & \textcolor[HTML]{4285f4}{\textbf{18.15\%}} & \textcolor[HTML]{4285f4}{\textbf{32.67\%}} & \textcolor[HTML]{4285f4}{\textbf{16.99\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.92\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.43\%}} & \textcolor[HTML]{4285f4}{\textbf{3.78\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.6\%}} & \textcolor[HTML]{4285f4}{\textbf{5.61\%}} & \textcolor[HTML]{4285f4}{\textbf{4\%}} & \textcolor[HTML]{4285f4}{\textbf{4.57\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{5.55\%}} & \textcolor[HTML]{4285f4}{\textbf{4.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.98\%}} & \textcolor[HTML]{4285f4}{\textbf{5.63\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.69\%}} & \textcolor[HTML]{4285f4}{\textbf{5.47\%}} & \textcolor[HTML]{4285f4}{\textbf{3.89\%}} & \textcolor[HTML]{4285f4}{\textbf{4.12\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{6.41\%}} & \textcolor[HTML]{4285f4}{\textbf{6.21\%}} & \textcolor[HTML]{4285f4}{\textbf{4.73\%}} & \textcolor[HTML]{4285f4}{\textbf{4.74\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{2.95\%}} & \textcolor[HTML]{4285f4}{\textbf{5.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.39\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.7\%}} & \textcolor[HTML]{4285f4}{\textbf{4.56\%}} & \textcolor[HTML]{4285f4}{\textbf{2.3\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.62\%}} & \textcolor[HTML]{4285f4}{\textbf{3.59\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}} & \textcolor[HTML]{4285f4}{\textbf{1.12\%}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{21.7\%}} & \textcolor[HTML]{4285f4}{\textbf{30.69\%}} & \textcolor[HTML]{4285f4}{\textbf{15.73\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{11.26\%}} & \textcolor[HTML]{4285f4}{\textbf{23.68\%}} & \textcolor[HTML]{4285f4}{\textbf{28.95\%}} & \textcolor[HTML]{4285f4}{\textbf{13.12\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{12.22\%}} & \textcolor[HTML]{4285f4}{\textbf{19.97\%}} & \textcolor[HTML]{4285f4}{\textbf{32.48\%}} & \textcolor[HTML]{4285f4}{\textbf{17.66\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.38\%}} & \textcolor[HTML]{4285f4}{\textbf{5.8\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{3.19\%}} & \textcolor[HTML]{4285f4}{\textbf{5.94\%}} & \textcolor[HTML]{4285f4}{\textbf{4.72\%}} & \textcolor[HTML]{4285f4}{\textbf{5.54\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{6.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.14\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{7.45\%}} & \textcolor[HTML]{4285f4}{\textbf{6.95\%}} & \textcolor[HTML]{4285f4}{\textbf{4.57\%}} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.1\%}} & \textcolor[HTML]{4285f4}{\textbf{6.79\%}} & \textcolor[HTML]{4285f4}{\textbf{4.5\%}} & \textcolor[HTML]{4285f4}{\textbf{5\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.95\%}} & \textcolor[HTML]{4285f4}{\textbf{7.61\%}} & \textcolor[HTML]{4285f4}{\textbf{5.24\%}} & \textcolor[HTML]{4285f4}{\textbf{5.82\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{2.87\%}} & \textcolor[HTML]{4285f4}{\textbf{5.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.3\%}} & \textcolor[HTML]{4285f4}{\textbf{2.78\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}} & \textcolor[HTML]{4285f4}{\textbf{2.85\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{5.73\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}}\\
-\textbf{} & \textbf{agriculturals} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.08\%}} & \textcolor[HTML]{4285f4}{\textbf{16.04\%}} & \textcolor[HTML]{4285f4}{\textbf{25.99\%}} & \textcolor[HTML]{4285f4}{\textbf{12.07\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.57\%}} & \textcolor[HTML]{4285f4}{\textbf{18.68\%}} & \textcolor[HTML]{4285f4}{\textbf{23.01\%}} & \textcolor[HTML]{4285f4}{\textbf{11.56\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{9.85\%}} & \textcolor[HTML]{4285f4}{\textbf{13.5\%}} & \textcolor[HTML]{4285f4}{\textbf{28.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.91\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.14\%}} & \textcolor[HTML]{4285f4}{\textbf{2.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{3.11\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}} & \textcolor[HTML]{4285f4}{\textbf{1.56\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{1.9\%}} & \textcolor[HTML]{4285f4}{\textbf{0.45\%}} & \textcolor[HTML]{4285f4}{\textbf{1\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.85\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{2.01\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.58\%}} & \textcolor[HTML]{4285f4}{\textbf{0.97\%}} & \textcolor[HTML]{4285f4}{\textbf{0.58\%}} & \textcolor[HTML]{4285f4}{\textbf{0.67\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.73\%}} & \textcolor[HTML]{4285f4}{\textbf{2.16\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.27\%}} & \textcolor[HTML]{4285f4}{\textbf{1.93\%}} & \textcolor[HTML]{4285f4}{\textbf{3.55\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.69\%}}\\
-\textbf{} & \textbf{} & \textbf{grains} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{16.44\%}} & \textcolor[HTML]{4285f4}{\textbf{29.28\%}} & \textcolor[HTML]{4285f4}{\textbf{42.09\%}} & \textcolor[HTML]{4285f4}{\textbf{19.27\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{14.54\%}} & \textcolor[HTML]{4285f4}{\textbf{34.68\%}} & \textcolor[HTML]{4285f4}{\textbf{38.84\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{18.73\%}} & \textcolor[HTML]{4285f4}{\textbf{23.95\%}} & \textcolor[HTML]{4285f4}{\textbf{44.4\%}} & \textcolor[HTML]{4285f4}{\textbf{20.71\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{0.78\%}} & \textcolor[HTML]{4285f4}{\textbf{2.98\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.77\%}} & \textcolor[HTML]{4285f4}{\textbf{2.63\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{5.46\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.06\%}} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.22\%}} & \textcolor[HTML]{4285f4}{\textbf{4.18\%}} & \textcolor[HTML]{4285f4}{\textbf{0.67\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{7.87\%}} & \textcolor[HTML]{4285f4}{\textbf{2.5\%}} & \textcolor[HTML]{4285f4}{\textbf{3.8\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.3\%}} & \textcolor[HTML]{4285f4}{\textbf{1.92\%}} & \textcolor[HTML]{4285f4}{\textbf{0.69\%}} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}} & \textcolor[HTML]{4285f4}{\textbf{2.08\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.19\%}} & \textcolor[HTML]{4285f4}{\textbf{1.87\%}} & \textcolor[HTML]{4285f4}{\textbf{3.56\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{2.25\%}} & \textcolor[HTML]{4285f4}{\textbf{2.18\%}} & \textcolor[HTML]{4285f4}{\textbf{3.3\%}} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}}\\
-\textbf{} & \textbf{} & \textbf{livestock} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.96\%}} & \textcolor[HTML]{4285f4}{\textbf{1.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.84\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{2.15\%}} & \textcolor[HTML]{4285f4}{\textbf{6.2\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{4.03\%}} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{11.26\%}} & \textcolor[HTML]{4285f4}{\textbf{5.94\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.63\%}} & \textcolor[HTML]{4285f4}{\textbf{2.06\%}} & \textcolor[HTML]{4285f4}{\textbf{3.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.95\%}} & \textcolor[HTML]{4285f4}{\textbf{2.94\%}} & \textcolor[HTML]{4285f4}{\textbf{3.54\%}} & \textcolor[HTML]{4285f4}{\textbf{1.94\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{1.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.71\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.3\%}} & \textcolor[HTML]{4285f4}{\textbf{0.19\%}} & \textcolor[HTML]{4285f4}{\textbf{0.28\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{1.43\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{1.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{softs} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{4.78\%}} & \textcolor[HTML]{4285f4}{\textbf{9.9\%}} & \textcolor[HTML]{4285f4}{\textbf{18.39\%}} & \textcolor[HTML]{4285f4}{\textbf{8.48\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{5.82\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}} & \textcolor[HTML]{4285f4}{\textbf{15.58\%}} & \textcolor[HTML]{4285f4}{\textbf{8.44\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.87\%}} & \textcolor[HTML]{4285f4}{\textbf{9.02\%}} & \textcolor[HTML]{4285f4}{\textbf{21.64\%}} & \textcolor[HTML]{4285f4}{\textbf{8.6\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.11\%}} & \textcolor[HTML]{4285f4}{\textbf{2.07\%}} & \textcolor[HTML]{4285f4}{\textbf{1.49\%}} & \textcolor[HTML]{4285f4}{\textbf{1.35\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{1.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.29\%}} & \textcolor[HTML]{4285f4}{\textbf{0.28\%}} & \textcolor[HTML]{4285f4}{\textbf{0.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.28\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.51\%}} & \textcolor[HTML]{4285f4}{\textbf{1.04\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}} & \textcolor[HTML]{4285f4}{\textbf{0.9\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{0.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.66\%}} & \textcolor[HTML]{4285f4}{\textbf{0.3\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.41\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}} & \textcolor[HTML]{4285f4}{\textbf{2.42\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{2.25\%}} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.53\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}}\\
-\textbf{} & \textbf{energy} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}} & \textcolor[HTML]{4285f4}{\textbf{31.57\%}} & \textcolor[HTML]{4285f4}{\textbf{38.94\%}} & \textcolor[HTML]{4285f4}{\textbf{25.9\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{26.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{33.74\%}} & \textcolor[HTML]{4285f4}{\textbf{20.94\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{26.84\%}} & \textcolor[HTML]{4285f4}{\textbf{31.47\%}} & \textcolor[HTML]{4285f4}{\textbf{42.16\%}} & \textcolor[HTML]{4285f4}{\textbf{28.77\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{9.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{3.5\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{12.81\%}} & \textcolor[HTML]{4285f4}{\textbf{1.01\%}} & \textcolor[HTML]{4285f4}{\textbf{2.97\%}} & \textcolor[HTML]{4285f4}{\textbf{5.68\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{5.95\%}} & \textcolor[HTML]{4285f4}{\textbf{2.32\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{7.91\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{40\%}} & \textcolor[HTML]{4285f4}{\textbf{33.46\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{38.82\%}} & \textcolor[HTML]{4285f4}{\textbf{25.93\%}} & \textcolor[HTML]{4285f4}{\textbf{17.59\%}} & \textcolor[HTML]{4285f4}{\textbf{22.07\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{41.02\%}} & \textcolor[HTML]{4285f4}{\textbf{40.42\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.99\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{1.86\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.4\%}} & \textcolor[HTML]{4285f4}{\textbf{3.75\%}} & \textcolor[HTML]{4285f4}{\textbf{4.93\%}} & \textcolor[HTML]{4285f4}{\textbf{3.4\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.16\%}} & \textcolor[HTML]{4285f4}{\textbf{2.76\%}} & \textcolor[HTML]{4285f4}{\textbf{5.88\%}} & \textcolor[HTML]{4285f4}{\textbf{1.26\%}}\\
-\textbf{} & \textbf{} & \textbf{gas} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{19.37\%}} & \textcolor[HTML]{4285f4}{\textbf{18.38\%}} & \textcolor[HTML]{4285f4}{\textbf{10.88\%}} & \textcolor[HTML]{4285f4}{\textbf{7.86\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{21.36\%}} & \textcolor[HTML]{4285f4}{\textbf{17.54\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{7.17\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{17.12\%}} & \textcolor[HTML]{4285f4}{\textbf{20.07\%}} & \textcolor[HTML]{4285f4}{\textbf{9.92\%}} & \textcolor[HTML]{4285f4}{\textbf{7.96\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.62\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{16.2\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{10.16\%}} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{11.42\%}} & \textcolor[HTML]{4285f4}{\textbf{19.3\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.46\%}} & \textcolor[HTML]{4285f4}{\textbf{5.26\%}} & \textcolor[HTML]{4285f4}{\textbf{13.46\%}} & \textcolor[HTML]{4285f4}{\textbf{13.84\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{22.08\%}} & \textcolor[HTML]{4285f4}{\textbf{27.47\%}} & \textcolor[HTML]{4285f4}{\textbf{15.46\%}} & \textcolor[HTML]{4285f4}{\textbf{16.03\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{23.23\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{14.53\%}} & \textcolor[HTML]{4285f4}{\textbf{16.64\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{20.54\%}} & \textcolor[HTML]{4285f4}{\textbf{32.65\%}} & \textcolor[HTML]{4285f4}{\textbf{16.18\%}} & \textcolor[HTML]{4285f4}{\textbf{15.41\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{4.24\%}} & \textcolor[HTML]{4285f4}{\textbf{7.16\%}} & \textcolor[HTML]{4285f4}{\textbf{5.22\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.36\%}} & \textcolor[HTML]{4285f4}{\textbf{2.03\%}} & \textcolor[HTML]{4285f4}{\textbf{11.66\%}} & \textcolor[HTML]{4285f4}{\textbf{5.9\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.48\%}} & \textcolor[HTML]{4285f4}{\textbf{6.51\%}} & \textcolor[HTML]{4285f4}{\textbf{4.6\%}} & \textcolor[HTML]{4285f4}{\textbf{4.55\%}}\\
-\textbf{} & \textbf{} & \textbf{petroleum} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}} & \textcolor[HTML]{4285f4}{\textbf{35.97\%}} & \textcolor[HTML]{4285f4}{\textbf{48.3\%}} & \textcolor[HTML]{4285f4}{\textbf{31.91\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{27.65\%}} & \textcolor[HTML]{4285f4}{\textbf{37.22\%}} & \textcolor[HTML]{4285f4}{\textbf{40.79\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{30.08\%}} & \textcolor[HTML]{4285f4}{\textbf{35.26\%}} & \textcolor[HTML]{4285f4}{\textbf{52.9\%}} & \textcolor[HTML]{4285f4}{\textbf{35.71\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10.41\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.99\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{13.69\%}} & \textcolor[HTML]{4285f4}{\textbf{0.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.14\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.45\%}} & \textcolor[HTML]{4285f4}{\textbf{1.34\%}} & \textcolor[HTML]{4285f4}{\textbf{0.96\%}} & \textcolor[HTML]{4285f4}{\textbf{5.93\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{45.97\%}} & \textcolor[HTML]{4285f4}{\textbf{35.46\%}} & \textcolor[HTML]{4285f4}{\textbf{23.06\%}} & \textcolor[HTML]{4285f4}{\textbf{31.56\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{44.02\%}} & \textcolor[HTML]{4285f4}{\textbf{27.52\%}} & \textcolor[HTML]{4285f4}{\textbf{18.61\%}} & \textcolor[HTML]{4285f4}{\textbf{23.88\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{47.85\%}} & \textcolor[HTML]{4285f4}{\textbf{43.02\%}} & \textcolor[HTML]{4285f4}{\textbf{26.44\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.57\%}} & \textcolor[HTML]{4285f4}{\textbf{4.95\%}} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.74\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}} & \textcolor[HTML]{4285f4}{\textbf{2.68\%}} & \textcolor[HTML]{4285f4}{\textbf{2.56\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.51\%}} & \textcolor[HTML]{4285f4}{\textbf{6.3\%}} & \textcolor[HTML]{4285f4}{\textbf{0.16\%}}\\
-\textbf{} & \textbf{metals} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{7.54\%}} & \textcolor[HTML]{4285f4}{\textbf{30.79\%}} & \textcolor[HTML]{4285f4}{\textbf{38.2\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{7.5\%}} & \textcolor[HTML]{4285f4}{\textbf{31.77\%}} & \textcolor[HTML]{4285f4}{\textbf{42.95\%}} & \textcolor[HTML]{4285f4}{\textbf{11.54\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{7.63\%}} & \textcolor[HTML]{4285f4}{\textbf{30.19\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{23\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.76\%}} & \textcolor[HTML]{4285f4}{\textbf{18.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.66\%}} & \textcolor[HTML]{4285f4}{\textbf{20.33\%}} & \textcolor[HTML]{4285f4}{\textbf{15.15\%}} & \textcolor[HTML]{4285f4}{\textbf{12.71\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7\%}} & \textcolor[HTML]{4285f4}{\textbf{23.49\%}} & \textcolor[HTML]{4285f4}{\textbf{21.5\%}} & \textcolor[HTML]{4285f4}{\textbf{13.38\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.91\%}} & \textcolor[HTML]{4285f4}{\textbf{3.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.27\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{2.83\%}} & \textcolor[HTML]{4285f4}{\textbf{0.32\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{4.31\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.48\%}} & \textcolor[HTML]{4285f4}{\textbf{7.31\%}} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.5\%}} & \textcolor[HTML]{4285f4}{\textbf{6.51\%}} & \textcolor[HTML]{4285f4}{\textbf{13.24\%}} & \textcolor[HTML]{4285f4}{\textbf{0.33\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{3.57\%}} & \textcolor[HTML]{4285f4}{\textbf{8.4\%}} & \textcolor[HTML]{4285f4}{\textbf{16.35\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{base} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{23.13\%}} & \textcolor[HTML]{4285f4}{\textbf{50.77\%}} & \textcolor[HTML]{4285f4}{\textbf{19.74\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{4.96\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}} & \textcolor[HTML]{4285f4}{\textbf{48.58\%}} & \textcolor[HTML]{4285f4}{\textbf{10.15\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{5.66\%}} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{52.45\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{5.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.4\%}} & \textcolor[HTML]{4285f4}{\textbf{5.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.91\%}} & \textcolor[HTML]{4285f4}{\textbf{0.29\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}} & \textcolor[HTML]{4285f4}{\textbf{6.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}} & \textcolor[HTML]{4285f4}{\textbf{0.88\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.01\%}} & \textcolor[HTML]{4285f4}{\textbf{2.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.46\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.1\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{1.84\%}} & \textcolor[HTML]{4285f4}{\textbf{0.61\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.82\%}} & \textcolor[HTML]{4285f4}{\textbf{3.42\%}} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.06\%}} & \textcolor[HTML]{4285f4}{\textbf{9.72\%}} & \textcolor[HTML]{4285f4}{\textbf{9.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.37\%}} & \textcolor[HTML]{4285f4}{\textbf{7.74\%}} & \textcolor[HTML]{4285f4}{\textbf{7.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.12\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{11.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}}\\
-\textbf{} & \textbf{} & \textbf{precious} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{8.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.7\%}} & \textcolor[HTML]{4285f4}{\textbf{35.06\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{8.13\%}} & \textcolor[HTML]{4285f4}{\textbf{33.37\%}} & \textcolor[HTML]{4285f4}{\textbf{41.54\%}} & \textcolor[HTML]{4285f4}{\textbf{11.89\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{8.12\%}} & \textcolor[HTML]{4285f4}{\textbf{32.35\%}} & \textcolor[HTML]{4285f4}{\textbf{32.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.88\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{25.76\%}} & \textcolor[HTML]{4285f4}{\textbf{23.19\%}} & \textcolor[HTML]{4285f4}{\textbf{15.84\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.72\%}} & \textcolor[HTML]{4285f4}{\textbf{24.12\%}} & \textcolor[HTML]{4285f4}{\textbf{18.46\%}} & \textcolor[HTML]{4285f4}{\textbf{15.81\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.86\%}} & \textcolor[HTML]{4285f4}{\textbf{27.76\%}} & \textcolor[HTML]{4285f4}{\textbf{26.82\%}} & \textcolor[HTML]{4285f4}{\textbf{16.5\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}} & \textcolor[HTML]{4285f4}{\textbf{3.9\%}} & \textcolor[HTML]{4285f4}{\textbf{0.22\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.56\%}} & \textcolor[HTML]{4285f4}{\textbf{0.68\%}} & \textcolor[HTML]{4285f4}{\textbf{3.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.71\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{4.53\%}} & \textcolor[HTML]{4285f4}{\textbf{0.21\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}} & \textcolor[HTML]{4285f4}{\textbf{6.71\%}} & \textcolor[HTML]{4285f4}{\textbf{16.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}} & \textcolor[HTML]{4285f4}{\textbf{6.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.69\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{4.46\%}} & \textcolor[HTML]{4285f4}{\textbf{7.58\%}} & \textcolor[HTML]{4285f4}{\textbf{17.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.31\%}}\\
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{market} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{1.74\%}} & \textcolor[HTML]{4285f4}{\textbf{11.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.71\%}} & \textcolor[HTML]{4285f4}{\textbf{10.75\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{2.14\%}} & \textcolor[HTML]{4285f4}{\textbf{13.03\%}} & \textcolor[HTML]{4285f4}{\textbf{34.39\%}} & \textcolor[HTML]{4285f4}{\textbf{6.62\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{1.48\%}} & \textcolor[HTML]{4285f4}{\textbf{10.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.45\%}} & \textcolor[HTML]{4285f4}{\textbf{14.35\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}} & \textcolor[HTML]{4285f4}{\textbf{4.26\%}} & \textcolor[HTML]{4285f4}{\textbf{1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{0.72\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.4\%}} & \textcolor[HTML]{4285f4}{\textbf{1.31\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{0.42\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.44\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.59\%}} & \textcolor[HTML]{4285f4}{\textbf{2.7\%}} & \textcolor[HTML]{4285f4}{\textbf{0.39\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.28\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.17\%}} & \textcolor[HTML]{4285f4}{\textbf{2.37\%}} & \textcolor[HTML]{4285f4}{\textbf{3.67\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.02\%}} & \textcolor[HTML]{4285f4}{\textbf{4.34\%}} & \textcolor[HTML]{4285f4}{\textbf{6.72\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{9.69\%}} & \textcolor[HTML]{4285f4}{\textbf{19.7\%}} & \textcolor[HTML]{4285f4}{\textbf{31.3\%}} & \textcolor[HTML]{4285f4}{\textbf{14.73\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{1.92\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.43\%}} & \textcolor[HTML]{4285f4}{\textbf{3.78\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{5.98\%}} & \textcolor[HTML]{4285f4}{\textbf{5.63\%}} & \textcolor[HTML]{4285f4}{\textbf{4.09\%}} & \textcolor[HTML]{4285f4}{\textbf{4.32\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{1.52\%}} & \textcolor[HTML]{4285f4}{\textbf{2.95\%}} & \textcolor[HTML]{4285f4}{\textbf{5.2\%}} & \textcolor[HTML]{4285f4}{\textbf{1.39\%}}\\
+\textbf{US} & \textbf{agriculturals} & \textbf{all} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{9.08\%}} & \textcolor[HTML]{4285f4}{\textbf{16.04\%}} & \textcolor[HTML]{4285f4}{\textbf{25.99\%}} & \textcolor[HTML]{4285f4}{\textbf{12.07\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}} & \textcolor[HTML]{4285f4}{\textbf{1.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.47\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{1.9\%}} & \textcolor[HTML]{4285f4}{\textbf{0.45\%}} & \textcolor[HTML]{4285f4}{\textbf{1\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{1.28\%}} & \textcolor[HTML]{4285f4}{\textbf{1.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.73\%}} & \textcolor[HTML]{4285f4}{\textbf{2.16\%}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{16.44\%}} & \textcolor[HTML]{4285f4}{\textbf{29.28\%}} & \textcolor[HTML]{4285f4}{\textbf{42.09\%}} & \textcolor[HTML]{4285f4}{\textbf{19.27\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{0.78\%}} & \textcolor[HTML]{4285f4}{\textbf{2.98\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{2.22\%}} & \textcolor[HTML]{4285f4}{\textbf{4.18\%}} & \textcolor[HTML]{4285f4}{\textbf{0.67\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{1.78\%}} & \textcolor[HTML]{4285f4}{\textbf{1.37\%}} & \textcolor[HTML]{4285f4}{\textbf{2.04\%}} & \textcolor[HTML]{4285f4}{\textbf{2.08\%}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{2.96\%}} & \textcolor[HTML]{4285f4}{\textbf{1.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.99\%}} & \textcolor[HTML]{4285f4}{\textbf{4.84\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{1.63\%}} & \textcolor[HTML]{4285f4}{\textbf{2.06\%}} & \textcolor[HTML]{4285f4}{\textbf{3.36\%}} & \textcolor[HTML]{4285f4}{\textbf{1.23\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{0.43\%}} & \textcolor[HTML]{4285f4}{\textbf{0.55\%}} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{0.38\%}} & \textcolor[HTML]{4285f4}{\textbf{1.25\%}} & \textcolor[HTML]{4285f4}{\textbf{1.15\%}} & \textcolor[HTML]{4285f4}{\textbf{1.79\%}}\\
+\textbf{} & \textbf{} & \textbf{softs} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{4.78\%}} & \textcolor[HTML]{4285f4}{\textbf{9.9\%}} & \textcolor[HTML]{4285f4}{\textbf{18.39\%}} & \textcolor[HTML]{4285f4}{\textbf{8.48\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{1.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.59\%}} & \textcolor[HTML]{4285f4}{\textbf{1.22\%}} & \textcolor[HTML]{4285f4}{\textbf{0.44\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{0.29\%}} & \textcolor[HTML]{4285f4}{\textbf{0.28\%}} & \textcolor[HTML]{4285f4}{\textbf{0.36\%}} & \textcolor[HTML]{4285f4}{\textbf{0.28\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{1.24\%}} & \textcolor[HTML]{4285f4}{\textbf{1.41\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}} & \textcolor[HTML]{4285f4}{\textbf{2.42\%}}\\
+\addlinespace
+\textbf{} & \textbf{all} & \textbf{all} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{11.67\%}} & \textcolor[HTML]{4285f4}{\textbf{21.7\%}} & \textcolor[HTML]{4285f4}{\textbf{30.69\%}} & \textcolor[HTML]{4285f4}{\textbf{15.73\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{2.38\%}} & \textcolor[HTML]{4285f4}{\textbf{5.8\%}} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{4.47\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{7.45\%}} & \textcolor[HTML]{4285f4}{\textbf{6.95\%}} & \textcolor[HTML]{4285f4}{\textbf{4.57\%}} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{1.89\%}} & \textcolor[HTML]{4285f4}{\textbf{2.87\%}} & \textcolor[HTML]{4285f4}{\textbf{5.12\%}} & \textcolor[HTML]{4285f4}{\textbf{1.71\%}}\\
+\textbf{} & \textbf{energy} & \textbf{all} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}} & \textcolor[HTML]{4285f4}{\textbf{31.57\%}} & \textcolor[HTML]{4285f4}{\textbf{38.94\%}} & \textcolor[HTML]{4285f4}{\textbf{25.9\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{9.13\%}} & \textcolor[HTML]{4285f4}{\textbf{1.61\%}} & \textcolor[HTML]{4285f4}{\textbf{3.5\%}} & \textcolor[HTML]{4285f4}{\textbf{4.79\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{40\%}} & \textcolor[HTML]{4285f4}{\textbf{33.46\%}} & \textcolor[HTML]{4285f4}{\textbf{21.16\%}} & \textcolor[HTML]{4285f4}{\textbf{27.67\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{3.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.99\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{1.86\%}}\\
+\textbf{} & \textbf{} & \textbf{gas} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{19.37\%}} & \textcolor[HTML]{4285f4}{\textbf{18.38\%}} & \textcolor[HTML]{4285f4}{\textbf{10.88\%}} & \textcolor[HTML]{4285f4}{\textbf{7.86\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{5.29\%}} & \textcolor[HTML]{4285f4}{\textbf{3.62\%}} & \textcolor[HTML]{4285f4}{\textbf{12.6\%}} & \textcolor[HTML]{4285f4}{\textbf{16.2\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{22.08\%}} & \textcolor[HTML]{4285f4}{\textbf{27.47\%}} & \textcolor[HTML]{4285f4}{\textbf{15.46\%}} & \textcolor[HTML]{4285f4}{\textbf{16.03\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{0.41\%}} & \textcolor[HTML]{4285f4}{\textbf{4.24\%}} & \textcolor[HTML]{4285f4}{\textbf{7.16\%}} & \textcolor[HTML]{4285f4}{\textbf{5.22\%}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}} & \textcolor[HTML]{4285f4}{\textbf{35.97\%}} & \textcolor[HTML]{4285f4}{\textbf{48.3\%}} & \textcolor[HTML]{4285f4}{\textbf{31.91\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{10.41\%}} & \textcolor[HTML]{4285f4}{\textbf{0.94\%}} & \textcolor[HTML]{4285f4}{\textbf{0.47\%}} & \textcolor[HTML]{4285f4}{\textbf{0.99\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{45.97\%}} & \textcolor[HTML]{4285f4}{\textbf{35.46\%}} & \textcolor[HTML]{4285f4}{\textbf{23.06\%}} & \textcolor[HTML]{4285f4}{\textbf{31.56\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{2.57\%}} & \textcolor[HTML]{4285f4}{\textbf{4.95\%}} & \textcolor[HTML]{4285f4}{\textbf{0.74\%}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{7.54\%}} & \textcolor[HTML]{4285f4}{\textbf{30.79\%}} & \textcolor[HTML]{4285f4}{\textbf{38.2\%}} & \textcolor[HTML]{4285f4}{\textbf{18.58\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{1.07\%}} & \textcolor[HTML]{4285f4}{\textbf{21.76\%}} & \textcolor[HTML]{4285f4}{\textbf{18.67\%}} & \textcolor[HTML]{4285f4}{\textbf{12.79\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{0.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.91\%}} & \textcolor[HTML]{4285f4}{\textbf{3.68\%}} & \textcolor[HTML]{4285f4}{\textbf{0.27\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{2.48\%}} & \textcolor[HTML]{4285f4}{\textbf{7.31\%}} & \textcolor[HTML]{4285f4}{\textbf{14.99\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{base} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{5.39\%}} & \textcolor[HTML]{4285f4}{\textbf{23.13\%}} & \textcolor[HTML]{4285f4}{\textbf{50.77\%}} & \textcolor[HTML]{4285f4}{\textbf{19.74\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{5.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.6\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{0.18\%}} & \textcolor[HTML]{4285f4}{\textbf{1.01\%}} & \textcolor[HTML]{4285f4}{\textbf{2.78\%}} & \textcolor[HTML]{4285f4}{\textbf{0.46\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{0.06\%}} & \textcolor[HTML]{4285f4}{\textbf{9.72\%}} & \textcolor[HTML]{4285f4}{\textbf{9.63\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{8.08\%}} & \textcolor[HTML]{4285f4}{\textbf{32.7\%}} & \textcolor[HTML]{4285f4}{\textbf{35.06\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{1.2\%}} & \textcolor[HTML]{4285f4}{\textbf{25.76\%}} & \textcolor[HTML]{4285f4}{\textbf{23.19\%}} & \textcolor[HTML]{4285f4}{\textbf{15.84\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{0.89\%}} & \textcolor[HTML]{4285f4}{\textbf{3.9\%}} & \textcolor[HTML]{4285f4}{\textbf{0.22\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{3.08\%}} & \textcolor[HTML]{4285f4}{\textbf{6.71\%}} & \textcolor[HTML]{4285f4}{\textbf{16.33\%}} & \textcolor[HTML]{4285f4}{\textbf{0.24\%}}\\
+\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{market} & \textcolor[HTML]{4285f4}{\textbf{1.74\%}} & \textcolor[HTML]{4285f4}{\textbf{11.71\%}} & \textcolor[HTML]{4285f4}{\textbf{33.71\%}} & \textcolor[HTML]{4285f4}{\textbf{10.75\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{CHP} & \textcolor[HTML]{4285f4}{\textbf{0.08\%}} & \textcolor[HTML]{4285f4}{\textbf{3.74\%}} & \textcolor[HTML]{4285f4}{\textbf{0.57\%}} & \textcolor[HTML]{4285f4}{\textbf{1.02\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{} & \textbf{open interest} & \textcolor[HTML]{4285f4}{\textbf{0.07\%}} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{2.17\%}} & \textcolor[HTML]{4285f4}{\textbf{0.42\%}}\\
+\textbf{} & \textbf{} & \textbf{} & \textbf{term structure} & \textcolor[HTML]{4285f4}{\textbf{0.04\%}} & \textcolor[HTML]{4285f4}{\textbf{3.28\%}} & \textcolor[HTML]{4285f4}{\textbf{5.5\%}} & \textcolor[HTML]{4285f4}{\textbf{0.09\%}}\\
 \bottomrule
@@
 assets are classified by the country of residence of the exchange where
-they are traded as well as by sector and sub-sector according to the
-nature of the asset.}
+they are traded at the time of writing as well as by sector and
+sub-sector according to the nature of the asset.}
 

### 2025-07-04 docs/paper.qmd
Update paper online version

@@
       cite-style: authoryear
-
   html:

### 2025-07-16 docs/blind.qmd
Minor revision before reresubmission

--- 2025-07-04 docs/paper.qmd
@@
 subtitle: Co-movement Behind-the-Scenes
-author:
-  - name: Devraj Basu
-    email: devraj.basu@strath.ac.uk
-    affiliations: 
-        - id: strathclyde
-          name: University of Strathclyde Business School
-          department: Accounting & Finance
-          address: 199 Cathedral Street
-          city: Glasgow
-          state: Scotland
-          postal-code: G4 0QU
-    attributes:
-        corresponding: true
-  - name: Olivier Bauthéac
-    email: olivier.bautheac@strath.ac.uk
-    affiliations:
-        - ref: strathclyde
 abstract: |
@@
 
-The returns pull-back continues into the post-crisis period, interestingly amidst a lower volatility environment, suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed during financialisation.
+The returns pull-back continues into the post-crisis period, interestingly amidst a lower volatility environment, suggesting that the underlying contributing factors--including investment outflows from the commodity futures complex as well as perhaps the evolving nature of global oil demand over the period--have had a lower impact on volatility than witnessed during financialisation.
 The pattern of reversion toward the pre-financialisation Keynesian paradigm continues stronger with mean returns higher during phases of **backwardation** relative to **contango** and the difference more pronounced than over the crisis period.
@@
 
-@tbl-stats-regime-tests displays descriptive statistics for the commodity series considered in the study; the results show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
+@tbl-stats-regime-tests displays descriptive statistics for the commodity series considered in the study; the results show a clear pattern of increase in average return during financialisation with most individual commodities showing a higher mean return and an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
 6.9% with a 10% significance in the pre-financialisation period.
 The increase is even more pronounced for an equally weighted portfolio of GB traded assets (metals), 2.47% (not significant) to 21.8% (significant at the 10% level), which sets out the global nature of the phenomenon.
-Most commodities show a higher mean return while five---Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)---show a lower figure with five of them significant---Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)---against none pre-financialisation.
-Sugar-#11 wins the race with a mean return increasing from -4.6% to 24.9% followed by copper with sizeable increases for both markets: 1.5% to 28.2% (XCEC) and 0.5% to 28.6% (XLME).
-The pattern of results for volatilities is similar although the increase is less pronounced.
-Both equally weighted portfolios shows an increase, more pronounced for the GB assets, 10% to 13.6% (US) vs.
-15.7% to 26.9% (GB), while out of the thirty assets, eleven show a drop in volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C (IFUS), Lumber (XCME), Sugar-#11 (IFUS), Natural gas (XNYM), Crude oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
-Financialisation seems however to have impacted the commodity complex beyond these mechanical effects of increased long participation ensuing from the entry on index type investments as our results suggest next.
+The pattern of results for volatilities is similar although the increase is less pronounced with a weaker majority of individual commodities showing heightened volatility and both equally weighted portfolios showing an increase, more pronounced for the GB assets.
+Financialisation seems however to have impacted the commodity complex beyond these mechanical effects of increased long participation ensuing from the entry of index type investments as our results suggest next.
 The cross-sectional nature of financialisation naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure.
@@
 
+\newpage
+
 ```{r}
 #| label: tbl-stats-regime-tests
-#| tbl-cap: "This table shows mean returns and volatilities for the individual commodities as well as for two equally weighted portfolios of US and GB traded assets across the four periods.
-For each period, estimates are computed independently over the whole period (figure shown) as well as over phases of **backwardation** (b) and **contango** (c) with corresponding comparison results reported in brackets.
-The table further shows the results of t-tests of significance for the mean returns computed over the whole periods as well as t-tests of difference between these when computed over the two phases independently along with F-tests of difference for the corresponding variances.
+#| tbl-cap: "This table shows mean returns and volatilities for the individual commodities and two equally weighted portfolios of US and GB traded assets for the four periods.
+For each period, estimates are computed independently over the whole period--figure shown--as well as over phases of **backwardation** (b) and **contango** (c)--results in brackets.
+The table further shows the results of t-tests of significance for the mean returns computed over the whole periods and t-tests of difference between these when computed over the two phases independently along with F-tests of difference for the corresponding variances.
 Values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
-The estimate values per regime as well as the p-values for the corresponding difference tests are available in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).
+Detailed results are available in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).
 **Backwardation** and **contango** regimes as well as period definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."

### 2025-07-16 blind.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@83fc75059bf36178bab2418157f7606c553b8174 🚀

--- 2025-07-04 paper.tex
@@
   pdftitle={Financialisation of Commodity Markets},
-  pdfauthor={Devraj Basu; Olivier Bauthéac},
   pdfkeywords={Commodity markets, Financialisation, Co-movement, Asset
@@
 Behind-the-Scenes} }
-\author[1]{Devraj Basu%
-\corref{cor1}%
-}
- \ead{devraj.basu@strath.ac.uk} 
-\author[1]{Olivier Bauthéac%
-%
-}
- \ead{olivier.bautheac@strath.ac.uk}
-
-\affiliation[1]{organization={University of Strathclyde Business
-School, Accounting \& Finance},addressline={199 Cathedral
-Street},city={Glasgow},postcode={G4 0QU},postcodesep={}}
 
@@
 The returns pull-back continues into the post-crisis period,
-interestingly amidst a lower volatility environment, suggesting that
-investment outflows from the commodity futures complex have had a lower
-impact on volatility than the corresponding inflows witnessed during
-financialisation. The pattern of reversion toward the
-pre-financialisation Keynesian paradigm continues stronger with mean
+interestingly amidst a lower volatility environment, suggesting that the
+underlying contributing factors--including investment outflows from the
+commodity futures complex as well as perhaps the evolving nature of
+global oil demand over the period--have had a lower impact on volatility
+than witnessed during financialisation. The pattern of reversion toward
+the pre-financialisation Keynesian paradigm continues stronger with mean
 returns higher during phases of \textbf{backwardation} relative to
@@
 the commodity series considered in the study; the results show a clear
-pattern of increase in average return during financialisation with an
-equally weighted portfolio of the US traded assets showing a mean
-returns of 15.9\% significant at the 5\% level vs.~6.9\% with a 10\%
-significance in the pre-financialisation period. The increase is even
-more pronounced for an equally weighted portfolio of GB traded assets
-(metals), 2.47\% (not significant) to 21.8\% (significant at the 10\%
-level), which sets out the global nature of the phenomenon. Most
-commodities show a higher mean return while five---Lumber (XCME),
-Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary
-(XLME)---show a lower figure with five of them significant---Crude
-oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and
-Tin-refined (XLME)---against none pre-financialisation. Sugar-\#11 wins
-the race with a mean return increasing from -4.6\% to 24.9\% followed by
-copper with sizeable increases for both markets: 1.5\% to 28.2\% (XCEC)
-and 0.5\% to 28.6\% (XLME).\\
-The pattern of results for volatilities is similar although the increase
-is less pronounced. Both equally weighted portfolios shows an increase,
-more pronounced for the GB assets, 10\% to 13.6\% (US) vs.~15.7\% to
-26.9\% (GB), while out of the thirty assets, eleven show a drop in
-volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C
-(IFUS), Lumber (XCME), Sugar-\#11 (IFUS), Natural gas (XNYM), Crude
-oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
-Financialisation seems however to have impacted the commodity complex
-beyond these mechanical effects of increased long participation ensuing
-from the entry on index type investments as our results suggest next.\\
+pattern of increase in average return during financialisation with most
+individual commodities showing a higher mean return and an equally
+weighted portfolio of the US traded assets showing a mean returns of
+15.9\% significant at the 5\% level vs.~6.9\% with a 10\% significance
+in the pre-financialisation period. The increase is even more pronounced
+for an equally weighted portfolio of GB traded assets (metals), 2.47\%
+(not significant) to 21.8\% (significant at the 10\% level), which sets
+out the global nature of the phenomenon. The pattern of results for
+volatilities is similar although the increase is less pronounced with a
+weaker majority of individual commodities showing heightened volatility
+and both equally weighted portfolios showing an increase, more
+pronounced for the GB assets. Financialisation seems however to have
+impacted the commodity complex beyond these mechanical effects of
+increased long participation ensuing from the entry of index type
+investments as our results suggest next.\\
 The cross-sectional nature of financialisation naturally leads us to
@@
 \caption{\label{tbl-stats-regime-tests}This table shows mean returns and
-volatilities for the individual commodities as well as for two equally
-weighted portfolios of US and GB traded assets across the four periods.
-For each period, estimates are computed independently over the whole
-period (figure shown) as well as over phases of \textbf{backwardation}
-(b) and \textbf{contango} (c) with corresponding comparison results
-reported in brackets. The table further shows the results of t-tests of
-significance for the mean returns computed over the whole periods as
-well as t-tests of difference between these when computed over the two
-phases independently along with F-tests of difference for the
-corresponding variances. Values significant at the 1\%, 5\% and 10\%
-level are marked with ***, ** and * respectively. The estimate values
-per regime as well as the p-values for the corresponding difference
-tests are available in the attached
+volatilities for the individual commodities and two equally weighted
+portfolios of US and GB traded assets for the four periods. For each
+period, estimates are computed independently over the whole
+period--figure shown--as well as over phases of \textbf{backwardation}
+(b) and \textbf{contango} (c)--results in brackets. The table further
+shows the results of t-tests of significance for the mean returns
+computed over the whole periods and t-tests of difference between these
+when computed over the two phases independently along with F-tests of
+difference for the corresponding variances. Values significant at the
+1\%, 5\% and 10\% level are marked with ***, ** and * respectively.
+Detailed results are available in the attached
 \href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet

### 2025-07-16 paper.qmd
Deploying to gh-pages from @ bautheac/financialisation-co-movement@83fc75059bf36178bab2418157f7606c553b8174 🚀

@@
 
-@tbl-stats-combined displays descriptive statistics for the commodity series considered in the study; the results show a clear pattern of increase in average return during financialisation with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
+@tbl-stats-regime-tests displays descriptive statistics for the commodity series considered in the study; the results show a clear pattern of increase in average return during financialisation with most individual commodities showing a higher mean return and an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
 6.9% with a 10% significance in the pre-financialisation period.
 The increase is even more pronounced for an equally weighted portfolio of GB traded assets (metals), 2.47% (not significant) to 21.8% (significant at the 10% level), which sets out the global nature of the phenomenon.
-Most commodities show a higher mean return while five---Lumber (XCME), Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary (XLME)---show a lower figure with five og them significant---Crude oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and Tin-refined (XLME)---against none pre-financialisation.
-Sugar-#11 wins the race with a mean return increasing from -4.6% to 24.9% followed by copper with sizeable increases for both markets: 1.5% to 28.2% (XCEC) and 0.5% to 28.6% (XLME).
-The pattern of results for volatilities is similar although the increase is less pronounced.
-Both equally weighted portfolios shows an increase, more pronounced for the GB assets, 10% to 13.6% (US) vs.
-15.7% to 26.9% (GB), while out of the thirty assets, eleven show a drop in volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C (IFUS), Lumber (XCME), Sugar-#11 (IFUS), Natural gas (XNYM), Crude oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
-Financialisation seems however to have impacted the commodity complex beyond these mechanical effects of increased long participation ensuing from the entry on index type investments as our results suggest next.
+The pattern of results for volatilities is similar although the increase is less pronounced with a weaker majority of individual commodities showing heightened volatility and both equally weighted portfolios showing an increase, more pronounced for the GB assets.
+Financialisation seems however to have impacted the commodity complex beyond these mechanical effects of increased long participation ensuing from the entry of index type investments as our results suggest next.
 The cross-sectional nature of financialisation naturally leads us to extend the individual hedging pressure paradigm by incorporating aggregate CHP (**CHP**), a market wide measure of hedging pressure.
@@
 The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods.
-In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector.
-Although modest in magnitude, these exhibit a telling pattern, mirroring that shown by the individual commodity returns in @tbl-stats-combined, with a substantially higher average coefficient over **backwardation** phases in the first period (0.12 vs.
+In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector^[A more detailed breakdown of country, sector and subsector average pairwise correlations is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).].
+Although modest in magnitude, these exhibit a telling pattern, mirroring that shown by the individual commodity returns in @tbl-stats-regime-tests, with a substantially higher average coefficient over **backwardation** phases in the first period (0.12 vs.
 0.03) and the pattern reversed over financilisation with an average coefficient substantially higher in **contango** (0.12 vs.
@@
 
+\newpage
+
 \newgeometry{margin=.75in}
 
-\newpage
-
-# Tables
-
-```{r}
-#| label: tbl-stats-combined
-#| tbl-cap: "This table shows mean returns and corresponding volatility for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-for each period the figures are shown independently for the entire period as well as for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median).
-Mean values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
-Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
-
-table_name <- "stats - combined"
-columns_to_collapse_rows_for <- c("asset", "regime")
-colnames <- c("asset", "regime", "estimate", periods)
-align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
-longtable <- TRUE
-bold_columns <- 1L:3L
-coloured_columns <- 4L:7L
-
-make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
-```
+# Tables {.unnumbered}
 
@@
 ```{r}
-#| label: tbl-regime-diference-tests
-#| tbl-cap: "This table shows the results for tests of difference in mean (t-test) and variance (F-test) between phases of aggregate backwardation and contango for the twenty four individual US commodities and the six GB metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the GB metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-1%, 5% and 10% p-value levels are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively in the significance column.
-Aggregate CHP construction and corresponding regime definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
+#| label: tbl-stats-regime-tests
+#| tbl-cap: "This table shows mean returns and volatilities for the individual commodities and two equally weighted portfolios of US and GB traded assets for the four periods.
+For each period, estimates are computed independently over the whole period--figure shown--as well as over phases of **backwardation** (b) and **contango** (c)--results in brackets.
+The table further shows the results of t-tests of significance for the mean returns computed over the whole periods and t-tests of difference between these when computed over the two phases independently along with F-tests of difference for the corresponding variances.
+Values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
+Detailed results are available in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).
+**Backwardation** and **contango** regimes as well as period definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
 
-table_name <- "regime difference tests"
-columns_to_collapse_rows_for <- c("asset", "period")
-colnames <- c("asset", "period", "moment", "dominant regime", "p-value", "significance")
-align <- make_series_of_repeated_chars(list(l = 4L, r = 2L))
+table_name <- "stats-individuals - regime difference tests"
+columns_to_collapse_rows_for <- c("asset")
+colnames <- c("asset", "estimate", "past", "financialisation", "crisis", "post-crisis")
+align <- make_series_of_repeated_chars(list(l = 1L, r = 5L))
 longtable <- TRUE
-bold_columns <- 1L:4L 
-coloured_columns <- 5L:6L
+bold_columns <- 1L:6L 
+coloured_columns <- 3L:6L
 
@@
 ```{r}
-#| eval: false
-#| label: tbl-experimental
-#| tbl-cap: "lorem ipsum dolor sit amet consectetur adipiscing elit sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident sunt in culpa qui officia deserunt mollit anim id est laborum.
-Lorem ipsum dolor sit amet consectetur adipiscing elit sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident sunt in culpa qui officia deserunt mollit anim id est laborum."
-#| tbl-subcap: 
-#|     - "Average pairwise inner correlations"
-#|     - "Average pairwise cross correlations"
-#| layout-nrows: 2
-
-table1_format <- list(
-  table_name = "correlations - inner - periods",
-  columns_to_collapse_rows_for = c("country", "sector", "subsector"),
-  longtable = FALSE,
-  colnames = c(sectors, "regime", periods),
-  align = make_series_of_repeated_chars(list(l = 3L, r = 5L)),
-  bold_columns = 1L:8L, 
-  coloured_columns = 5L:8L
-  )
-table2_format <- list(
-  table_name = "correlations - cross - periods",
-  columns_to_collapse_rows_for = c("portfolios", "regime"),
-  longtable = TRUE,
-  colnames = c("portfolios", "regime", periods),
-  align = make_series_of_repeated_chars(list(l = 1L, r = 5L)),
-  bold_columns = 1L:2L, 
-  coloured_columns = 3L:6L
-)
-formats <- list(table1_format, table2_format)
-
-get_results(tables, table1_format$table_name) %>% dplyr::mutate(dplyr::across(dplyr::where(is.factor), as.character)) %>%
-    collapse_rows(table1_format$columns_to_collapse_rows_for) %>%
-    kable(booktabs = T, longtable = table1_format$longtable, col.names = table1_format$colnames, align = table1_format$align, escape = FALSE) %>%
-    kable_styling(font_size = 7L) %>%
-    row_spec(0L, bold = TRUE, color = "black") %>%
-    column_spec(table1_format$bold_columns, bold = TRUE) %>% column_spec(table1_format$coloured_columns, color = "#4285f4")
-
-get_results(tables, table2_format$table_name) %>% dplyr::mutate(dplyr::across(dplyr::where(is.factor), as.character)) %>%
-    collapse_rows(table2_format$columns_to_collapse_rows_for) %>%
-    kable(booktabs = T, longtable = table2_format$longtable, col.names = table2_format$colnames, align = table2_format$align, escape = FALSE) %>%
-    kable_styling(font_size = 7L) %>%
-    row_spec(0L, bold = TRUE, color = "black") %>%
-    column_spec(table2_format$bold_columns, bold = TRUE) %>% column_spec(table2_format$coloured_columns, color = "#4285f4")
-```
-
-\newpage
-
-```{r}
 #| label: tbl-correlations-inner-years
-#| tbl-cap: "While \\@tbl-correlations-inner-periods shows results calculated independently for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018), this stable shows the results of the same analysis calculated by year over the entire sample period (1997-2018).
-The results are discussed in \\@sec-results while \\@sec-taxonomy details the taxonomy for the commodity assets considered."
+#| tbl-cap: "While \\@tbl-correlations-inner-periods shows results computed independently for the four periods, this table shows the results of the same analysis implemented for each year over the entire sample period.
+The results are discussed in \\@sec-results while \\@sec-taxonomy details the commodity assets taxonomy."
 

### 2025-08-19 docs/paper.qmd
Include reference to table 8 + update url
of internet appendix

@@
 We also consider the GB metal complex with aluminium (XLME), copper (XLME), lead (XLME), nickel-primary (XLME), tin-refined (XLME) and zinc (XLME).
-This sample cross-section of assets is further divided into groups for the purpose of the analysis by country (US, GB), sector (agriculturals, energy, metals) and by sub-sector (agriculturals: grains, livestock, softs; energy: gas, petroleum; metals: base, precious)^[See @sec-taxonomy for a detailed taxonomy of the commodity assets considered in the study.].
+This sample cross-section of assets is further divided into groups for the purpose of the analysis by country (US, GB), sector (agriculturals, energy, metals) and by sub-sector (agriculturals: grains, livestock, softs; energy: gas, petroleum; metals: base, precious)^[See @tbl-assets-taxonomy for a detailed taxonomy of the commodity assets considered in the study.].
 
@@
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
-@tbl-stats-regime-tests further reports the dominating regime for each asset-period-moment combination along with the corresponding results of difference tests for returns mean and variance between the two regimes^[The estimate values per regime as well as the p-values for the corresponding difference tests are available in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).].
+@tbl-stats-regime-tests further reports the dominating regime for each asset-period-moment combination along with the corresponding results of difference tests for returns mean and variance between the two regimes^[The estimate values per regime as well as the p-values for the corresponding difference tests are available in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).].
 Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another.
@@
 The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods.
-In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector^[A more detailed breakdown of country, sector and subsector average pairwise correlations is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).].
+In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector^[A more detailed breakdown of country, sector and subsector average pairwise correlations is provided in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).].
 Although modest in magnitude, these exhibit a telling pattern, mirroring that shown by the individual commodity returns in @tbl-stats-regime-tests, with a substantially higher average coefficient over **backwardation** phases in the first period (0.12 vs.
@@
 The results for our other risk factor mimicking portfolios show a similar pattern and provide a deeper insights into co-movement dynamics in this context.
-All three factors---CHP, open interest and term structure---performed poorly in the first period, indicating that the commodities with extreme factor attributes (high or low CHP for example) were uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of **contango** and **backwardation**^[A breakdown of the performance by regime is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).].
+All three factors---CHP, open interest and term structure---performed poorly in the first period, indicating that the commodities with extreme factor attributes (high or low CHP for example) were uncorrelated with the rest of the commodity cross-section, and the overall performance consistent across periods of **contango** and **backwardation**^[A breakdown of the performance by regime is provided in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).].
 The onset of financialisation leads to a substantial improvement in the performance of the CHP factor with its average $R^{2}$, albeit still small at 5.4%, almost tripling from the past to the financialisation period in contrast to the other factors that show weaker dynamics with a slight decrease and a much smaller increase for the open interest and term structure factors respectively.
@@
 The corresponding figures of 22% and 1.1% for the entire US metals sector stand in sharp contrast with the agricultural sector, which exhibits no notable change, and the energy sector, where pricing performance drops substantially from 9.2% down to 1.6%.
-The improvement in the CHP factor's pricing performance remarkably comes predominantly from the long leg (low CHP assets: Keynesian "normal backwardation") of the factor^[A breakdown of the performance by factor leg is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).] with the corresponding mimicking portfolio's performance itself driven by the metals, the precious sub-sector in particular.
+The improvement in the CHP factor's pricing performance remarkably comes predominantly from the long leg (low CHP assets: Keynesian "normal backwardation") of the factor^[A breakdown of the performance by factor leg is provided in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).] with the corresponding mimicking portfolio's performance itself driven by the metals, the precious sub-sector in particular.
 Interestingly, although the term structure factor itself only sees a very modest increase, its short leg (low roll-yield assets: Working's backwardation) shows a sizeable rise in pricing performance, yet again driven the metals sector.
@@
 
+\newpage
+
 ```{r}
 #| label: tbl-stats-regime-tests
-#| tbl-cap: "This table shows mean returns and volatilities for the individual commodities as well as for two equally weighted portfolios of US and GB traded assets across the four periods.
-For each period, estimates are computed independently over the whole period (figure shown) as well as over phases of **backwardation** (b) and **contango** (c) with corresponding comparison results reported in brackets.
-The table further shows the results of t-tests of significance for the mean returns computed over the whole periods as well as t-tests of difference between these when computed over the two phases independently along with F-tests of difference for the corresponding variances.
+#| tbl-cap: "This table shows mean returns and volatilities for the individual commodities and two equally weighted portfolios of US and GB traded assets for the four periods.
+For each period, estimates are computed independently over the whole period--figure shown--as well as over phases of **backwardation** (b) and **contango** (c)--results in brackets.
+The table further shows the results of t-tests of significance for the mean returns computed over the whole periods and t-tests of difference between these when computed over the two phases independently along with F-tests of difference for the corresponding variances.
 Values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
-The estimate values per regime as well as the p-values for the corresponding difference tests are available in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).
+Detailed results are available in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).
 **Backwardation** and **contango** regimes as well as period definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
@@
 The results are computed independently across countries and commodity sectors and sub-sectors for the four periods.
-A breakdown of the estimates computed independently over the whole periods as well as over phases of **backwardation** and **contango** is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).
+A breakdown of the estimates computed independently over the whole periods as well as over phases of **backwardation** and **contango** is provided in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).
 Factor construction methods along with **backwardation** and **contango** regimes as well as period definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the commodity assets taxonomy is detailed in \\@sec-taxonomy."

### 2025-08-19 explore/shiny/co-movement/app.r
Shiny app directory name change

@@ -1,0 +1,105 @@
+library(dplyr)
+library(DT)
+library(here) 
+library(magrittr)
+library(purrr)
+library(readr)
+library(rlang)
+library(shiny) 
+library(shinydashboard)
+library(tidyr)
+
+
+
+app_dir <- normalizePath(".", winslash = "/", mustWork = TRUE)
+if (identical(Sys.getenv("SHINY_ENV"), "local")) {
+  app_dir <- here::here("explore", "shiny", "revision-jfm")
+}
+
+source(file.path(app_dir, "datasets.r"))
+source(file.path(app_dir, "functions.r"))
+source(file.path(app_dir, "modules", "results_summary_table.r"))
+source(file.path(app_dir, "modules", "results_summary_category.r"))
+source(file.path(app_dir, "modules", "results_summary.r"))
+
+sidebar <- dashboardSidebar(
+  sidebarMenu(
+    menuItem("Stats", tabName = "stats",
+             menuItem("Descriptive", tabName = "stats-descriptive"),
+             menuItem("Regime ≠ tests", tabName = "stats-difference-tests")
+             ),
+    menuItem("Correlations", tabName = "correlations",
+             menuItem("Inner", tabName = "correlations-inner"),
+             menuItem("Cross", tabName = "correlations-cross", 
+                      menuItem("US", tabName = "correlations-cross-US"),
+                      menuItem("Global", tabName = "correlations-cross-global")
+            )
+    
+    ),
+    menuItem("Regressions",
+             menuItem("Index", tabName = "regressions-index"),
+             menuItem("Factors", tabName = "regressions-factors")
+    )
+  )
+)
+
+body <- dashboardBody(
+  tabItems(
+    tabItem(tabName = "stats-descriptive", results_summary_UI("stats-descriptive", list(
+      period = results$stats$descriptive$period, year = results$stats$descriptive$year
+    ))),
+    tabItem(tabName = "stats-difference-tests", results_summary_UI("stats-difference-tests", list(
+      period = results$stats$regime_tests$period
+    ))),
+    tabItem(tabName = "correlations-inner", results_summary_UI("correlations-inner", list(
+      period = results$correlations$inner$period, year = results$correlations$inner$year
+    ))),
+    tabItem(tabName = "correlations-cross-US", results_summary_UI("correlations-cross-US", list(
+      period = results$correlations$cross$US$period, year = results$correlations$cross$US$year
+    ))),
+    tabItem(tabName = "correlations-cross-global", results_summary_UI("correlations-cross-global", list(
[…]

### 2025-08-19 explore/shiny/co-movement/datasets.r

@@ -1,0 +1,226 @@
+
+extract_analysis_summary_results_average_table <- function(
+    analysis_summary_results_category, category, summary_group_variables = c(), 
+    summary_analysis_variables
+    ){
+  
+  category_sym <- rlang::sym(category)
+  group_vars <- rlang::syms(summary_group_variables)
+  analysis_vars <- rlang::syms(summary_analysis_variables)
+  
+  dplyr::select(
+    analysis_summary_results_category,
+    field, type, frequency, country, sector, subsector, !!category_sym, 
+    !!!group_vars, regime, !!!analysis_vars
+  ) %>% 
+    dplyr::group_by(
+      field, type, frequency, country, sector, subsector, !!category_sym, 
+      !!!group_vars, regime
+      ) %>%
+    dplyr::filter(dplyr::row_number() == dplyr::n()) %>% dplyr::ungroup()
+}
+
+
+extract_analysis_summary_results_top_3_table <- function(
+    analysis_summary_results_category, category, summary_group_variables = c(), 
+    summary_analysis_variables
+    ){
+  
+  dplyr::select(analysis_summary_results_category, -average)
+}
+
+
+extract_analysis_summary_results_by_category <- function(
+    analysis_summary_results, category, variables
+    ){
+  
+  analysis <- dplyr::filter(analysis_summary_results, timespan == category) %>%
+    dplyr::select(-c("timespan", ifelse(category == "period", "year", "period")))
+  
+  lapply(seq_along(variables$calls), function(i){
+    fun <- paste0("extract_analysis_summary_results_", variables$calls[[i]],  "_table")
+    args <- list(
+      analysis, category, 
+      variables$variables[[i]]$summary_group_variables, variables$variables[[i]]$summary_analysis_variables
+      )
+    do.call(fun, args = args)
+  }) %>% setNames(names(variables$variables))
+}
+
+
+
+split_analysis_summary_results_into_category_dataframes <- function(
+    analysis_summary_results, helpers
+    ){
+  
+  lapply(seq_along(helpers), function(i){
+    fun <- extract_analysis_summary_results_by_category
+    args <- list(
+      analysis_summary_results, names(helpers)[i], helpers[[i]]
+      )
+    do.call(fun, args = args)
+  }) %>% setNames(names(helpers))
+}
+
+
+app_dir <- normalizePath(".", winslash = "/", mustWork = TRUE)
[…]

### 2025-08-19 explore/shiny/co-movement/modules/results_summary.r

@@ -1,0 +1,22 @@
+
+results_summary_UI <- function(id, categories) {
+  
+  ns <- NS(id)
+  
+  tagList(
+    lapply(seq_along(categories), function(i) {
+      results_summary_category_UI(ns(names(categories)[i]), names(categories)[i], categories[[i]])
+    })
+  )
+}
+
+results_summary_Server <- function(id, results) {
+  moduleServer(id, function(input, output, session) {
+    
+    ns <- session$ns
+    # browser()
+    lapply(seq_along(results), function(i) {
+      results_summary_category_Server(names(results)[i], results[[i]])
+    })
+  })
+}

### 2025-08-19 explore/shiny/co-movement/modules/results_summary_category.r

@@ -1,0 +1,24 @@
+
+results_summary_category_UI <- function(id, category_name, table_list){
+  
+  ns <- NS(id)
+  
+  tagList(
+    h2(paste("By", category_name)),
+    p(linebreaks(3L)),
+    lapply(seq_along(table_list), function(i) {
+      results_summary_table_UI(ns(names(table_list)[i]), names(table_list)[i])
+    }),
+  )
+}
+
+results_summary_category_Server <- function(id, table_list) {
+  moduleServer(id, function(input, output, session) {
+    
+    ns <- session$ns
+    
+    lapply(seq_along(table_list), function(i) {
+      results_summary_table_Server(names(table_list)[i], table_list[[i]])
+    })
+  })
+}

### 2025-08-19 explore/shiny/co-movement/modules/results_summary_table.r

@@ -1,0 +1,37 @@
+
+results_summary_table_UI <- function(id, table_name){
+  
+  ns <- NS(id)
+  
+  tagList(
+    fluidRow(
+      column(6, align = "left", h3(table_name)),
+      column(6, align = "right", downloadButton(ns('download'), 'Download .csv')
+      )
+    ),
+    fluidRow(DT::dataTableOutput(ns("table")), width = "100%", height = "auto", fill = TRUE),
+    p(linebreaks(3L))
+  )
+}
+
+
+results_summary_table_Server <- function(id, table) {
+  moduleServer(id, function(input, output, session) {
+    
+    ns <- session$ns
+    
+    table_reactive <- reactive(table)
+    
+    output$table <- DT::renderDataTable(
+      table_reactive(), filter = 'top', options = list(scrollX = TRUE)
+    )
+    output$download <- downloadHandler(
+      filename = function() {
+        paste0("results-", Sys.time(), ".csv")
+      },
+      content = function(file) {
+        readr::write_csv(table_reactive(), file)
+      }
+    )
+  })
+}

### 2025-08-19 explore/shiny/revision-jfm/app.r

@@ -1,102 +1,0 @@
-library(shinydashboard)
-library(shiny)
-
-construct_path <- function() {
-  shiny_env <- Sys.getenv("SHINY_ENV")
-  if (shiny_env == "local") {
-    path_directory <- here::here("explore", "shiny", "revision-jfm")
-  } else {
-    path_directory <- here::here()
-  }
-  
-  return(path_directory)
-}
-path_directory <- construct_path()
-
-source(file.path(path_directory, "datasets.r"))
-source(file.path(path_directory, "functions.r"))
-source(file.path(path_directory, "modules", "results_summary_table.r"))
-source(file.path(path_directory, "modules", "results_summary_category.r"))
-source(file.path(path_directory, "modules", "results_summary.r"))
-
-sidebar <- dashboardSidebar(
-  sidebarMenu(
-    menuItem("Stats", tabName = "stats",
-             menuItem("Descriptive", tabName = "stats-descriptive"),
-             menuItem("Regime ≠ tests", tabName = "stats-difference-tests")
-             ),
-    menuItem("Correlations", tabName = "correlations",
-             menuItem("Inner", tabName = "correlations-inner"),
-             menuItem("Cross", tabName = "correlations-cross", 
-                      menuItem("US", tabName = "correlations-cross-US"),
-                      menuItem("Global", tabName = "correlations-cross-global")
-            )
-    
-    ),
-    menuItem("Regressions",
-             menuItem("Index", tabName = "regressions-index"),
-             menuItem("Factors", tabName = "regressions-factors")
-    )
-  )
-)
-
-body <- dashboardBody(
-  tabItems(
-    tabItem(tabName = "stats-descriptive", results_summary_UI("stats-descriptive", list(
-      period = results$stats$descriptive$period, year = results$stats$descriptive$year
-    ))),
-    tabItem(tabName = "stats-difference-tests", results_summary_UI("stats-difference-tests", list(
-      period = results$stats$regime_tests$period
-    ))),
-    tabItem(tabName = "correlations-inner", results_summary_UI("correlations-inner", list(
-      period = results$correlations$inner$period, year = results$correlations$inner$year
-    ))),
-    tabItem(tabName = "correlations-cross-US", results_summary_UI("correlations-cross-US", list(
-      period = results$correlations$cross$US$period, year = results$correlations$cross$US$year
-    ))),
-    tabItem(tabName = "correlations-cross-global", results_summary_UI("correlations-cross-global", list(
[…]

### 2025-08-19 explore/shiny/revision-jfm/datasets.r

@@ -1,236 +1,0 @@
-library(magrittr)
-
-extract_analysis_summary_results_average_table <- function(
-    analysis_summary_results_category, category, summary_group_variables = c(), 
-    summary_analysis_variables
-    ){
-  
-  category_sym <- rlang::sym(category)
-  group_vars <- rlang::syms(summary_group_variables)
-  analysis_vars <- rlang::syms(summary_analysis_variables)
-  
-  dplyr::select(
-    analysis_summary_results_category,
-    field, type, frequency, country, sector, subsector, !!category_sym, 
-    !!!group_vars, regime, !!!analysis_vars
-  ) %>% 
-    dplyr::group_by(
-      field, type, frequency, country, sector, subsector, !!category_sym, 
-      !!!group_vars, regime
-      ) %>%
-    dplyr::filter(dplyr::row_number() == dplyr::n()) %>% dplyr::ungroup()
-}
-
-
-extract_analysis_summary_results_top_3_table <- function(
-    analysis_summary_results_category, category, summary_group_variables = c(), 
-    summary_analysis_variables
-    ){
-  
-  dplyr::select(analysis_summary_results_category, -average)
-}
-
-
-extract_analysis_summary_results_by_category <- function(
-    analysis_summary_results, category, variables
-    ){
-  
-  analysis <- dplyr::filter(analysis_summary_results, timespan == category) %>%
-    dplyr::select(-c("timespan", ifelse(category == "period", "year", "period")))
-  
-  lapply(seq_along(variables$calls), function(i){
-    fun <- paste0("extract_analysis_summary_results_", variables$calls[[i]],  "_table")
-    args <- list(
-      analysis, category, 
-      variables$variables[[i]]$summary_group_variables, variables$variables[[i]]$summary_analysis_variables
-      )
-    do.call(fun, args = args)
-  }) %>% setNames(names(variables$variables))
-}
-
-
-
-split_analysis_summary_results_into_category_dataframes <- function(
-    analysis_summary_results, helpers
-    ){
-  
-  lapply(seq_along(helpers), function(i){
-    fun <- extract_analysis_summary_results_by_category
-    args <- list(
-      analysis_summary_results, names(helpers)[i], helpers[[i]]
-      )
-    do.call(fun, args = args)
-  }) %>% setNames(names(helpers))
-}
-
-
-construct_path <- function() {
-  shiny_env <- Sys.getenv("SHINY_ENV")
-  if (shiny_env == "local") {
[…]

### 2025-08-19 explore/shiny/revision-jfm/modules/results_summary.r

@@ -1,24 +1,0 @@
-library(shinydashboard)
-library(shiny)
-
-results_summary_UI <- function(id, categories) {
-  
-  ns <- NS(id)
-  
-  tagList(
-    lapply(seq_along(categories), function(i) {
-      results_summary_category_UI(ns(names(categories)[i]), names(categories)[i], categories[[i]])
-    })
-  )
-}
-
-results_summary_Server <- function(id, results) {
-  moduleServer(id, function(input, output, session) {
-    
-    ns <- session$ns
-    # browser()
-    lapply(seq_along(results), function(i) {
-      results_summary_category_Server(names(results)[i], results[[i]])
-    })
-  })
-}

### 2025-08-19 explore/shiny/revision-jfm/modules/results_summary_category.r

@@ -1,26 +1,0 @@
-library(shinydashboard)
-library(shiny)
-
-results_summary_category_UI <- function(id, category_name, table_list){
-  
-  ns <- NS(id)
-  
-  tagList(
-    h2(paste("By", category_name)),
-    p(linebreaks(3L)),
-    lapply(seq_along(table_list), function(i) {
-      results_summary_table_UI(ns(names(table_list)[i]), names(table_list)[i])
-    }),
-  )
-}
-
-results_summary_category_Server <- function(id, table_list) {
-  moduleServer(id, function(input, output, session) {
-    
-    ns <- session$ns
-    
-    lapply(seq_along(table_list), function(i) {
-      results_summary_table_Server(names(table_list)[i], table_list[[i]])
-    })
-  })
-}

### 2025-08-19 explore/shiny/revision-jfm/modules/results_summary_table.r

@@ -1,39 +1,0 @@
-library(shinydashboard)
-library(shiny)
-
-results_summary_table_UI <- function(id, table_name){
-  
-  ns <- NS(id)
-  
-  tagList(
-    fluidRow(
-      column(6, align = "left", h3(table_name)),
-      column(6, align = "right", downloadButton(ns('download'), 'Download .csv')
-      )
-    ),
-    fluidRow(DT::dataTableOutput(ns("table")), width = "100%", height = "auto", fill = TRUE),
-    p(linebreaks(3L))
-  )
-}
-
-
-results_summary_table_Server <- function(id, table) {
-  moduleServer(id, function(input, output, session) {
-    
-    ns <- session$ns
-    
-    table_reactive <- reactive(table)
-    
-    output$table <- DT::renderDataTable(
-      table_reactive(), filter = 'top', options = list(scrollX = TRUE)
-    )
-    output$download <- downloadHandler(
-      filename = function() {
-        paste0("results-", Sys.time(), ".csv")
-      },
-      content = function(file) {
-        readr::write_csv(table_reactive(), file)
-      }
-    )
-  })
-}

### 2025-08-19 blind.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@fba5d0f4311c2970234a42c3d1515050b6d463c6 🚀

@@
 grains, livestock, softs; energy: gas, petroleum; metals: base,
-precious)\footnote{See Section~\ref{sec-taxonomy} for a detailed
+precious)\footnote{See Table~\ref{tbl-assets-taxonomy} for a detailed
   taxonomy of the commodity assets considered in the study.}.
@@
   p-values for the corresponding difference tests are available in the
-  attached
-  \href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
+  attached \href{https://bautheac.shinyapps.io/co-movement/}{Internet
   Appendix}.}.\\
@@
   correlations is provided in the attached
-  \href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
-  Appendix}.}. Although modest in magnitude, these exhibit a telling
-pattern, mirroring that shown by the individual commodity returns in
+  \href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.}.
+Although modest in magnitude, these exhibit a telling pattern, mirroring
+that shown by the individual commodity returns in
 Table~\ref{tbl-stats-regime-tests}, with a substantially higher average
@@
   is provided in the attached
-  \href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
-  Appendix}.}. The onset of financialisation leads to a substantial
-improvement in the performance of the CHP factor with its average
-\(R^{2}\), albeit still small at 5.4\%, almost tripling from the past to
-the financialisation period in contrast to the other factors that show
-weaker dynamics with a slight decrease and a much smaller increase for
-the open interest and term structure factors respectively. Here again
-the increase in pricing performance for the CHP factor is driven by the
-metals sector, particularly the precious sub-sector with the average
-\(R^{2}\) for the group jumping to almost 26\% during financialisation
-from 1.2\% over the past period. The corresponding figures of 22\% and
-1.1\% for the entire US metals sector stand in sharp contrast with the
-agricultural sector, which exhibits no notable change, and the energy
-sector, where pricing performance drops substantially from 9.2\% down to
-1.6\%. The improvement in the CHP factor's pricing performance
-remarkably comes predominantly from the long leg (low CHP assets:
-Keynesian ``normal backwardation'') of the factor\footnote{A breakdown
-  of the performance by factor leg is provided in the attached
-  \href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
-  Appendix}.} with the corresponding mimicking portfolio's performance
-itself driven by the metals, the precious sub-sector in particular.
-Interestingly, although the term structure factor itself only sees a
-very modest increase, its short leg (low roll-yield assets: Working's
-backwardation) shows a sizeable rise in pricing performance, yet again
-driven the metals sector. The pattern of results for both factors
-extends to the GB traded assets and suggest a convergence of Keneysian
-and Working's term structure perspective over the financialisation
-period.\\
+  \href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.}.
+The onset of financialisation leads to a substantial improvement in the
+performance of the CHP factor with its average \(R^{2}\), albeit still
+small at 5.4\%, almost tripling from the past to the financialisation
+period in contrast to the other factors that show weaker dynamics with a
+slight decrease and a much smaller increase for the open interest and
+term structure factors respectively. Here again the increase in pricing
+performance for the CHP factor is driven by the metals sector,
+particularly the precious sub-sector with the average \(R^{2}\) for the
+group jumping to almost 26\% during financialisation from 1.2\% over the
+past period. The corresponding figures of 22\% and 1.1\% for the entire
+US metals sector stand in sharp contrast with the agricultural sector,
+which exhibits no notable change, and the energy sector, where pricing
+performance drops substantially from 9.2\% down to 1.6\%. The
+improvement in the CHP factor's pricing performance remarkably comes
+predominantly from the long leg (low CHP assets: Keynesian ``normal
+backwardation'') of the factor\footnote{A breakdown of the performance
+  by factor leg is provided in the attached
+  \href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.}
+with the corresponding mimicking portfolio's performance itself driven
+by the metals, the precious sub-sector in particular. Interestingly,
+although the term structure factor itself only sees a very modest
+increase, its short leg (low roll-yield assets: Working's backwardation)
+shows a sizeable rise in pricing performance, yet again driven the
+metals sector. The pattern of results for both factors extends to the GB
+traded assets and suggest a convergence of Keneysian and Working's term
+structure perspective over the financialisation period.\\
 Taken together these results emphasise the global nature of the impact
@@
 Detailed results are available in the attached
-\href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
-Appendix}. \textbf{Backwardation} and \textbf{contango} regimes as well
-as period definitions are discussed in Section~\ref{sec-methods} while
-the results are discussed in Section~\ref{sec-results}.}
+\href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.
+\textbf{Backwardation} and \textbf{contango} regimes as well as period
+definitions are discussed in Section~\ref{sec-methods} while the results
+are discussed in Section~\ref{sec-results}.}
 
@@
 phases of \textbf{backwardation} and \textbf{contango} is provided in
-the attached
-\href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
+the attached \href{https://bautheac.shinyapps.io/co-movement/}{Internet
 Appendix}. Factor construction methods along with \textbf{backwardation}

### 2025-08-19 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@fba5d0f4311c2970234a42c3d1515050b6d463c6 🚀

@@
 \caption{\label{tbl-stats-regime-tests}This table shows mean returns and
-volatilities for the individual commodities as well as for two equally
-weighted portfolios of US and GB traded assets across the four periods.
-For each period, estimates are computed independently over the whole
-period (figure shown) as well as over phases of \textbf{backwardation}
-(b) and \textbf{contango} (c) with corresponding comparison results
-reported in brackets. The table further shows the results of t-tests of
-significance for the mean returns computed over the whole periods as
-well as t-tests of difference between these when computed over the two
-phases independently along with F-tests of difference for the
-corresponding variances. Values significant at the 1\%, 5\% and 10\%
-level are marked with ***, ** and * respectively. The estimate values
-per regime as well as the p-values for the corresponding difference
-tests are available in the attached
-\href{http://bautheac.duckdns.org:3838/bautheac/co-movement/}{Internet
-Appendix}. \textbf{Backwardation} and \textbf{contango} regimes as well
-as period definitions are discussed in Section~\ref{sec-methods} while
-the results are discussed in Section~\ref{sec-results}.}
+volatilities for the individual commodities and two equally weighted
+portfolios of US and GB traded assets for the four periods. For each
+period, estimates are computed independently over the whole
+period--figure shown--as well as over phases of \textbf{backwardation}
+(b) and \textbf{contango} (c)--results in brackets. The table further
+shows the results of t-tests of significance for the mean returns
+computed over the whole periods and t-tests of difference between these
+when computed over the two phases independently along with F-tests of
+difference for the corresponding variances. Values significant at the
+1\%, 5\% and 10\% level are marked with ***, ** and * respectively.
+Detailed results are available in the attached
+\href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.
+\textbf{Backwardation} and \textbf{contango} regimes as well as period
+definitions are discussed in Section~\ref{sec-methods} while the results
+are discussed in Section~\ref{sec-results}.}
 

### 2025-08-20 explore/scripts/revision-jfm/bar-charts.r
Make bar charts
Closes #93, closes #94.

@@ -1,0 +1,75 @@
+library(dplyr)
+library(ggplot2)
+library(here)
+library(MetBrewer)
+library(readr)
+library(slituR)
+library(tidyr)
+
+
+
+tables_directory_path <- here("explore", "tables", "revision-jfm")
+figures_directory_path <- here("explore", "results", "figures")
+
+table_stats_individuals_path <- paste_forward_slash(tables_directory_path, "stats-individual-assets.rds")
+stats_individuals <- read_rds(table_stats_individuals_path) |>
+  mutate(across(past:present, ~ as.numeric(gsub("[%*]", "", .)) / 100L))
+
+
+
+table_estimates <- filter(stats_individuals, !stringr::str_detect(asset, "commodities"), regime == "whole period") |> group_by(estimate) |>
+  summarise(
+    `past vs. financialisation <` = sum(past < financialization, na.rm = TRUE),
+    `past vs. financialisation >` = sum(past > financialization, na.rm = TRUE),
+    `financialisation vs. crisis <` = sum(financialization < crisis, na.rm = TRUE),
+    `financialisation vs. crisis >` = sum(financialization > crisis, na.rm = TRUE),
+    `crisis vs. post-crisis <` = sum(crisis < present, na.rm = TRUE),
+    `crisis vs. post-crisis >` = sum(crisis > present, na.rm = TRUE)
+  ) |>
+  pivot_longer(
+    cols = -estimate, names_to = c("period", "operator"), names_pattern = "(.*)\\s([<>])", values_to = "count"
+  ) |>
+  pivot_wider(names_from = period, values_from = count) |>
+  select(estimate, operator, `past vs. financialisation`, `financialisation vs. crisis`, `crisis vs. post-crisis`)  |>
+  pivot_longer(
+    cols = c(`past vs. financialisation`, `financialisation vs. crisis`, `crisis vs. post-crisis`),
+    names_to = "period", values_to = "value"
+  ) |>
+  dplyr::mutate(period = factor(period, levels = c("past vs. financialisation", "financialisation vs. crisis", "crisis vs. post-crisis")))
+
+figures_estimates <- ggplot(table_estimates, aes(x = period, y = value, fill = operator)) +
+  geom_bar(stat = "identity") +
+  geom_text(aes(label = value), position = position_stack(vjust = 0.5), color = "white", size = 4, fontface = "bold") +
+  facet_wrap(~estimate, ncol = 1) +
[…]

### 2025-08-25 docs/paper.qmd
Made captions for bar charts

@@
 #| cache: true
+library(dplyr)
+library(ggplot2)
+library(here)
+library(MetBrewer)
+library(readr)
+library(slituR)
+library(tidyr)
 
@@
 
+figures_directory_path <- here::here("explore", "results", "figures")
 tables_directory_path <- here::here("explore", "tables", "revision-jfm")
@@
 
+# Figures {.unnumbered}
+
+```{r}
+#| label: fig-estimates
+#| fig-cap: "This figure compares the evolution of estimates for mean (top panel) and volatility (bottom panel) for individual commodity returns across three period transitions: past → financialisation, financialisation → crisis and crisis → post-crisis.
+Each stacked bar shows how many cases fall into two categories: yellow (the estimate in the previous period is smaller than in the next period) and blue (the estimate in the previous period is larger than in the next period); numbers inside the bars indicate the count of observations in each category.
+Detailed results are available in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).
+Period definitions are discussed in @sec-methods while the results are discussed in @sec-results."
+#| fig-height: 6
+#| fig-width: 5
+
+estimates <- readr::read_rds(here::here(figures_directory_path, "estimates.rds"))
+estimates
+```
+
+\newpage
+
+```{r}
+#| label: fig-regimes
+#| fig-cap: "This figure compares estimates for mean (top panel) and volatility (bottom panel) for individual commodity returns between **CHP** regime phases (**backwardation** vs.
+**contango**) for the four periods.
+Each stacked bar shows how many cases fall into two categories: yellow (the estimate for the **backwardation phase** is smaller than for the **contango** phase) and blue (the estimate for the **backwardation phase** is greater than for the **contango** phase); numbers inside the bars indicate the count of observations in each category.
+**Backwardation** and **contango** regimes as well as period definitions are discussed in @sec-methods while the results are discussed in @sec-results."
+#| fig-height: 6
+#| fig-width: 5
+
+regimes <- readr::read_rds(here::here(figures_directory_path, "regimes.rds"))
+regimes
+```
+
+\newpage
+
 # Tables {.unnumbered}

### 2025-08-25 explore/scripts/revision-jfm/bar-charts.r

@@ -35,15 +35,24 @@ table_estimates <- filter(stats_individuals, !stringr::str_detect(asset, "commod
     cols = c(`past vs. financialisation`, `financialisation vs. crisis`, `crisis vs. post-crisis`),
     names_to = "period", values_to = "value"
   ) |>
-  dplyr::mutate(period = factor(period, levels = c("past vs. financialisation", "financialisation vs. crisis", "crisis vs. post-crisis")))
+  # dplyr::mutate(period = factor(period, levels = c("past vs. financialisation", "financialisation vs. crisis", "crisis vs. post-crisis")))
+  dplyr::mutate(
+    period = factor(period, levels = unique(period)), operator = paste("previous", operator, "next", sep = " ")
+  ) 
+
 
 figures_estimates <- ggplot(table_estimates, aes(x = period, y = value, fill = operator)) +
   geom_bar(stat = "identity") +
-  geom_text(aes(label = value), position = position_stack(vjust = 0.5), color = "white", size = 4, fontface = "bold") +
+  geom_text(aes(label = value), position = position_stack(vjust = 0.5), color = "white", size = 3, fontface = "bold") +
   facet_wrap(~estimate, ncol = 1) +
-  labs(x = "", y = "", fill = "") +
+  labs(title = "Estimate comparison from one period to the next", x = "", y = "", fill = "") +
   theme_minimal() +
-  theme(strip.text = element_text(size = 16)) +
+  theme(
+    strip.text = element_text(size = 10), plot.title = element_text(size = 12, hjust = 0.5),
+    legend.position = "bottom", legend.justification = "left", 
+    legend.direction = "horizontal", legend.box = "horizontal",
+    legend.margin = margin(t = -10, b = 20, unit = "pt")
+    ) +
   scale_fill_manual(values = met.brewer("Isfahan2", 2))
 
 figure_estimates_path <- paste_forward_slash(figures_directory_path, "estimates.rds")
@@ -53,20 +62,29 @@ write_rds(figures_estimates, figure_estimates_path)
 
 table_regimes <- filter(stats_individuals, !stringr::str_detect(asset, "commodities"), regime != "whole period") |> 
   pivot_longer(cols = past:present, names_to = "period", values_to = "value") |>
+    dplyr::mutate(period = stringr::str_replace_all(period, c("financialization" = "financialisation", "present" = "post-crisis"))) |>
[…]

### 2025-08-25 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@16a22e3a403c14e67bce5a71fdf7b2e77fde2afa 🚀

@@
 
+\section*{Figures}\label{figures}
+\addcontentsline{toc}{section}{Figures}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-estimates-1.pdf}
+
+}
+
+\caption{\label{fig-estimates}This figure compares the evolution of
+estimates for mean (top panel) and volatility (bottom panel) for
+individual commodity returns across three period transitions: past →
+financialisation, financialisation → crisis and crisis → post-crisis.
+Each stacked bar shows how many cases fall into two categories: yellow
+(the estimate in the previous period is smaller than in the next period)
+and blue (the estimate in the previous period is larger than in the next
+period); numbers inside the bars indicate the count of observations in
+each category. Detailed results are available in the attached
+\href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.
+Period definitions are discussed in Section~\ref{sec-methods} while the
+results are discussed in Section~\ref{sec-results}.}
+
+\end{figure}%
+
+\newpage
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-regimes-1.pdf}
+
+}
+
+\caption{\label{fig-regimes}This figure compares estimates for mean (top
+panel) and volatility (bottom panel) for individual commodity returns
+between \textbf{CHP} regime phases (\textbf{backwardation}
+vs.~\textbf{contango}) for the four periods. Each stacked bar shows how
+many cases fall into two categories: yellow (the estimate for the
+\textbf{backwardation phase} is smaller than for the \textbf{contango}
+phase) and blue (the estimate for the \textbf{backwardation phase} is
+greater than for the \textbf{contango} phase); numbers inside the bars
+indicate the count of observations in each category.
+\textbf{Backwardation} and \textbf{contango} regimes as well as period
+definitions are discussed in @sec-methods while the results are
+discussed in @sec-results.}
+
+\end{figure}%
+
+\newpage
+
 \section*{Tables}\label{tables}

### 2025-08-25 docs/paper.qmd

@@
 
-\newgeometry{margin=.75in}
+<!-- \newgeometry{margin=.75in} -->
 
@@
 
-\newpage
-
 ```{r}
 #| label: tbl-stats-regime-tests
-#| tbl-cap: "This table shows mean returns and volatilities for the individual commodities and two equally weighted portfolios of US and GB traded assets for the four periods.
-For each period, estimates are computed independently over the whole period--figure shown--as well as over phases of **backwardation** (b) and **contango** (c)--results in brackets.
-The table further shows the results of t-tests of significance for the mean returns computed over the whole periods and t-tests of difference between these when computed over the two phases independently along with F-tests of difference for the corresponding variances.
+#| tbl-cap: "This table shows mean returns and volatilities for two equally weighted portfolios of US and GB traded assets for the four periods.
+For each period, estimates are computed independently over the whole period as well as over phases of **backwardation** and **contango**.
+The table further shows the results of t-tests of significance for the mean returns as well as t-tests of difference between these when computed over the two phases independently along with F-tests of difference for the corresponding variances.
 Values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
@@
 
-table_name <- "stats-individuals - regime difference tests"
-columns_to_collapse_rows_for <- c("asset")
-colnames <- c("asset", "estimate", "past", "financialisation", "crisis", "post-crisis")
-align <- make_series_of_repeated_chars(list(l = 1L, r = 5L))
+table_name <- "stats-ew - regime difference tests"
+columns_to_collapse_rows_for <- c("asset", "estimate")
+colnames <- c("asset", "estimate", "regime", "past", "financialisation", "crisis", "post-crisis")
+align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
 longtable <- TRUE
-bold_columns <- 1L:6L 
-coloured_columns <- 3L:6L
+bold_columns <- 1L:7L 
+coloured_columns <- 4L:7L
 
@@
 
-\restoregeometry
+<!-- \restoregeometry -->
 

### 2025-08-25 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@44a69cd7b8d55bcede84743b6529d25e5e1d6a41 🚀

@@
 
-\newgeometry{margin=.75in}
-
 \section*{Figures}\label{figures}
@@
 \textbf{Backwardation} and \textbf{contango} regimes as well as period
-definitions are discussed in @sec-methods while the results are
-discussed in @sec-results.}
+definitions are discussed in Section~\ref{sec-methods} while the results
+are discussed in Section~\ref{sec-results}.}
 
@@
 
-\newpage
-
 \begingroup\fontsize{7}{9}\selectfont
 
-\begin{longtable}[t]{>{}l>{}r>{}r>{}r>{}r>{}r}
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
 
 \caption{\label{tbl-stats-regime-tests}This table shows mean returns and
-volatilities for the individual commodities and two equally weighted
-portfolios of US and GB traded assets for the four periods. For each
-period, estimates are computed independently over the whole
-period--figure shown--as well as over phases of \textbf{backwardation}
-(b) and \textbf{contango} (c)--results in brackets. The table further
-shows the results of t-tests of significance for the mean returns
-computed over the whole periods and t-tests of difference between these
-when computed over the two phases independently along with F-tests of
-difference for the corresponding variances. Values significant at the
-1\%, 5\% and 10\% level are marked with ***, ** and * respectively.
-Detailed results are available in the attached
-\href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.
-\textbf{Backwardation} and \textbf{contango} regimes as well as period
-definitions are discussed in Section~\ref{sec-methods} while the results
-are discussed in Section~\ref{sec-results}.}
+volatilities for two equally weighted portfolios of US and GB traded
+assets for the four periods. For each period, estimates are computed
+independently over the whole period as well as over phases of
+\textbf{backwardation} and \textbf{contango}. The table further shows
+the results of t-tests of significance for the mean returns as well as
+t-tests of difference between these when computed over the two phases
+independently along with F-tests of difference for the corresponding
+variances. Values significant at the 1\%, 5\% and 10\% level are marked
+with ***, ** and * respectively. Detailed results are available in the
+attached \href{https://bautheac.shinyapps.io/co-movement/}{Internet
+Appendix}. \textbf{Backwardation} and \textbf{contango} regimes as well
+as period definitions are discussed in Section~\ref{sec-methods} while
+the results are discussed in Section~\ref{sec-results}.}
 
@@
 \toprule
-\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.48\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{21.37\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-4.51\% (b<c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{29.54\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{36.15\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{21.8\% (b<c*)}}\\
-\textbf{Oats (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{5.49\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{21.62\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{8.89\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.87\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.22\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{31.04\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.67\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{29.5\% (b>c***)}}\\
-\textbf{Soybean meal (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{7.29\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.06\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{8.12\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.33\% (b<c)}}\\
-\addlinespace
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.34\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.55\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{31.78\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{25.11\% (b<c)}}\\
-\textbf{Soybean oil (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{6.21\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{15.57\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{4.04\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-7.39\% (b<c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.43\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{28.35\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{25.75\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.95\% (b<c**)}}\\
-\textbf{Soybeans (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{6.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{13.36\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.19\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.82\% (b<c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.47\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{30.04\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{28\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{21.22\% (b>c*)}}\\
-\addlinespace
-\textbf{Wheat-SRW (XCBT)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{5.07\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{17.63\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{6.68\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-1.58\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.93\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{33.03\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{37.62\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{26.58\% (b<c)}}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{0.39\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{7.43\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{7.13\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.87\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{13.23\% (b<c*)}} & \textcolor[HTML]{4285f4}{\textbf{15.16\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{15.24\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.69\% (b>c***)}}\\
-\textbf{Cattle-live (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.45\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{8.77\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{4.13\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.92\% (b<c)}}\\
-\addlinespace
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.1\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{17.43\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{16.32\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.3\% (b>c***)}}\\
-\textbf{Lean hogs (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{0.73\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{8.4\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.69\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-1.09\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.33\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.89\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{30.37\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{36.94\% (b<c*)}}\\
-\textbf{Cocoa (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.66\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{16.35\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{1.39\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{3.65\% (b<c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.66\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{29.99\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{31.03\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{24.69\% (b>c**)}}\\
-\addlinespace
-\textbf{Coffee-C (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{-5.91\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{20.38\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{2.2\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.99\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{43.84\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.3\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{30.17\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.86\% (b<c)}}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.24\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{0.95\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.53\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{0.5\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.38\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{29.01\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{33.26\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{20.61\% (b>c*)}}\\
-\textbf{Lumber (XCME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.9\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.58\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{11.74\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{5.06\% (b>c**)}}\\
-\addlinespace
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{30.58\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{29.39\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{36.31\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{25.1\% (b<c***)}}\\
-\textbf{Orange juice (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.67\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{13.87\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{14.4\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{3.8\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.5\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{33.01\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{34.43\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{29.37\% (b<c)}}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{-4.56\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{24.87\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{11.82\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-1.16\% (b<c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{34.88\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{33.25\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{37.9\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{28.72\% (b<c*)}}\\
-\addlinespace
-\textbf{Natural gas (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{35.38\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{16.25\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{0.93\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{8.33\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{61.55\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{54.6\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{53.58\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{44.58\% (b<c**)}}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{15.43\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*28.74\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{9.67\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-5.64\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{39.87\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.56\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{42.84\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.69\% (b<c***)}}\\
-\textbf{Gasoline (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{16.65\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{30.95\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{10.59\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-5.37\% (b>c)}}\\
-\addlinespace
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{42.77\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{41.76\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{40.07\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{37.09\% (b<c***)}}\\
-\textbf{Heating oil (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{16.31\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*29.88\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.83\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.44\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{40.75\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{35.09\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{33.17\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{30.56\% (b<c***)}}\\
-\textbf{Copper (XCEC)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.45\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*28.15\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{6.19\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.1\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.23\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.89\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.91\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{19.56\% (b<c***)}}\\
-\addlinespace
-\textbf{Gold (XCEC)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{4.5\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{14.35\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{14.01\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{0.53\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.14\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{21.46\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{14.41\% (b<c***)}}\\
-\textbf{Palladium (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{9.12\% (b>c***)}} & \textcolor[HTML]{4285f4}{\textbf{9.03\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*29.12\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{13.75\% (b>c*)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{38.27\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{32.71\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{36.14\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{25.38\% (b<c***)}}\\
-\textbf{Platinum (XNYM)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{12.93\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{10.56\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{7.29\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-7.92\% (b>c)}}\\
-\addlinespace
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22.62\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{22.66\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{25.53\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{19.48\% (b<c***)}}\\
-\textbf{Silver (XCEC)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{6.19\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{17.54\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{21.96\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{-2.43\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{22\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{33.92\% (b<c*)}} & \textcolor[HTML]{4285f4}{\textbf{39.87\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{24.35\% (b<c***)}}\\
-\textbf{Aluminium (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{1.13\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{13.78\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-3.58\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{3.15\% (b>c**)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{17.6\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{26.41\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{26.48\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.56\% (b>c)}}\\
-\addlinespace
-\textbf{Copper (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{0.45\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{**28.59\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{5.74\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{0.03\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.25\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{31.09\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{34.27\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.92\% (b<c***)}}\\
-\textbf{Lead (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{3.83\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{28.99\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{10.74\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{2.07\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{19.64\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{41.74\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{41.05\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{23.26\% (b>c)}}\\
-\textbf{Nickel (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{19.31\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{12.5\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{3.52\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{0.31\% (b>c***)}}\\
-\addlinespace
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.26\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{44.27\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{41.45\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{28.98\% (b>c)}}\\
-\textbf{Tin (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{4.07\% (b>c*)}} & \textcolor[HTML]{4285f4}{\textbf{*29.1\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{7.46\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{1.68\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.38\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{31.71\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{35.61\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{18.79\% (b<c***)}}\\
-\textbf{Zinc (XLME)} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{-4.52\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{20.13\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{7.62\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{9.07\% (b>c*)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.73\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{38.77\% (b<c**)}} & \textcolor[HTML]{4285f4}{\textbf{36.17\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{23.25\% (b<c**)}}\\
-\addlinespace
-\textbf{US commodities} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{*6.89\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{**15.89\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{9.39\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{-0.18\% (b>c)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{10\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{13.62\% (b>c**)}} & \textcolor[HTML]{4285f4}{\textbf{17.58\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{9.86\% (b<c***)}}\\
-\textbf{GB commodities} & \textbf{mean} & \textcolor[HTML]{4285f4}{\textbf{2.47\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{*21.77\% (b<c)}} & \textcolor[HTML]{4285f4}{\textbf{5.25\% (b>c)}} & \textcolor[HTML]{4285f4}{\textbf{2.72\% (b>c**)}}\\
-\textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{15.66\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{26.91\% (b<c*)}} & \textcolor[HTML]{4285f4}{\textbf{30.24\% (b<c***)}} & \textcolor[HTML]{4285f4}{\textbf{16.19\% (b<c***)}}\\
+\textbf{US commodities} & \textbf{mean} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{*6.89\%}} & \textcolor[HTML]{4285f4}{\textbf{**15.89\%}} & \textcolor[HTML]{4285f4}{\textbf{9.39\%}} & \textcolor[HTML]{4285f4}{\textbf{-0.18\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{***15.44\%}} & \textcolor[HTML]{4285f4}{\textbf{*15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{13.4\%}} & \textcolor[HTML]{4285f4}{\textbf{6.82\%}}\\
+\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{-1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{*16.16\%}} & \textcolor[HTML]{4285f4}{\textbf{4.9\%}} & \textcolor[HTML]{4285f4}{\textbf{-6.33\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation vs.
+contango} & \textcolor[HTML]{4285f4}{\textbf{**}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{} & \textbf{volatility} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
+\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation vs.
+contango} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{**}} & \textcolor[HTML]{4285f4}{\textbf{***}} & \textcolor[HTML]{4285f4}{\textbf{***}}\\
+\textbf{GB commodities} & \textbf{mean} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.47\%}} & \textcolor[HTML]{4285f4}{\textbf{*21.77\%}} & \textcolor[HTML]{4285f4}{\textbf{5.25\%}} & \textcolor[HTML]{4285f4}{\textbf{2.72\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{8.01\%}} & \textcolor[HTML]{4285f4}{\textbf{15.06\%}} & \textcolor[HTML]{4285f4}{\textbf{**19.95\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{*35.56\%}} & \textcolor[HTML]{4285f4}{\textbf{-5.24\%}} & \textcolor[HTML]{4285f4}{\textbf{-14.05\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation vs.
+contango} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{**}}\\
+\textbf{} & \textbf{volatility} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
+\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{backwardation vs.
+contango} & \textcolor[HTML]{4285f4}{\textbf{***}} & \textcolor[HTML]{4285f4}{\textbf{*}} & \textcolor[HTML]{4285f4}{\textbf{***}} & \textcolor[HTML]{4285f4}{\textbf{***}}\\
 \bottomrule
@@
 
-\restoregeometry
-
 \newpage

### 2025-08-25 docs/paper.tex
Update body of text
for bar charts and EW portfolios table.

@@
 
-Table~\ref{tbl-stats-combined} displays descriptive statistics for the
-commodity series considered in the study; the results show a clear
-pattern of increase in average return during financialisation with an
-equally weighted portfolio of the US traded assets showing a mean
-returns of 15.9\% significant at the 5\% level vs.~6.9\% with a 10\%
-significance in the pre-financialisation period. The increase is even
-more pronounced for an equally weighted portfolio of GB traded assets
-(metals), 2.47\% (not significant) to 21.8\% (significant at the 10\%
-level), which sets out the global nature of the phenomenon. Most
-commodities show a higher mean return while five---Lumber (XCME),
-Natural gas (XNYM), Palladium (XNYM), Platinum (XNYM) and Nickel-primary
-(XLME)---show a lower figure with five og them significant---Crude
-oil-WTI (XNYM), Heating oil (XNYM), Copper (XCEC), Copper (XLME) and
-Tin-refined (XLME)---against none pre-financialisation. Sugar-\#11 wins
-the race with a mean return increasing from -4.6\% to 24.9\% followed by
-copper with sizeable increases for both markets: 1.5\% to 28.2\% (XCEC)
-and 0.5\% to 28.6\% (XLME).\\
-The pattern of results for volatilities is similar although the increase
-is less pronounced. Both equally weighted portfolios shows an increase,
-more pronounced for the GB assets, 10\% to 13.6\% (US) vs.~15.7\% to
-26.9\% (GB), while out of the thirty assets, eleven show a drop in
-volatility: Oats (XCBT), Lean hogs (XCME), Cocoa (IFUS), Coffee-C
-(IFUS), Lumber (XCME), Sugar-\#11 (IFUS), Natural gas (XNYM), Crude
-oil-WTI (XNYM), Gasoline (XNYM), Heating oil (XNYM), Palladium (XNYM).
-Financialisation seems however to have impacted the commodity complex
-beyond these mechanical effects of increased long participation ensuing
-from the entry on index type investments as our results suggest next.\\
+The results show a clear pattern of increase in average return during
+financialisation as illustrated by Figure~\ref{fig-estimates}, with most
+individual commodities showing a higher mean return, and
+Table~\ref{tbl-stats-regime-tests} with an equally weighted portfolio of
+the US traded assets showing a mean returns of 15.9\% significant at the
+5\% level vs.~6.9\% with a 10\% significance in the pre-financialisation
+period. The increase is even more pronounced for an equally weighted
+portfolio of GB traded assets (metals), 2.47\% (not significant) to
+21.8\% (significant at the 10\% level), which sets out the global nature
+of the phenomenon. The pattern of results for volatilities is similar
+although the increase is less pronounced with a weaker majority of
+individual commodities showing heightened volatility and both equally
+weighted portfolios showing an increase, more pronounced for the GB
+assets. Financialisation seems however to have impacted the commodity
+complex beyond these mechanical effects of increased long participation
+ensuing from the entry of index type investments as our results suggest
+next.\\
 The cross-sectional nature of financialisation naturally leads us to
@@
 that returns for individual commodities should be high in periods where
-\textbf{CHP} is low and vice et versa. Table~\ref{tbl-stats-combined}
-further shows the mean returns and volatilities for high
-(\textbf{contango}) and low (\textbf{backwardation}) \textbf{CHP}
-regimes for each time period while
-Table~\ref{tbl-regime-diference-tests} shows the results of difference
-tests for returns mean and variance between the two regimes.\\
-Over the first period eighteen of the twenty-four US commodities have
-higher mean returns during periods of \textbf{backwardation} as compared
-to \textbf{contango}, with the difference being statistically
-significant at the 10\% level for two commodities, at the 5\% level for
-one and at the 1\% level for another. For the remaining six commodities
-the higher mean return during \textbf{contango} is not statistically
-significant for any of them. For the six GB commodities, all metals,
-five of them had higher mean returns during phases of
-\textbf{backwardation} as compared to \textbf{contango} in the first
-period, with one of these differences being statistically significant at
-the 10\% level while for the remaining asset (Zinc (XLME)) the higher
-mean return during \textbf{contango} is not statistically significant.
-An equally weighted portfolio of the twenty-four US commodities had a
-mean return of 15.4\% during \textbf{backwardation} phases,
-statistically significant at the 1\% level, and a mean return of -1.1\%
-during \textbf{contango}, both in the first period, with the difference
-between them statistically significant at the 5\% level. The
-corresponding figures for an equally weighted portfolio of the GB metals
-were 4.4\% and 0.3\% respectively. These results provide broad support
-for an aggregate version of the Keynesian hedging pressure hypothesis
-and suggest that hedgers in the aggregate were engaged in risk transfer
-during this period.\\
-Over the second period the pattern essentially reverses. For the
-twenty-four US commodities over this period, fourteen have higher mean
-returns during phases of \textbf{contango} over \textbf{backwardation}.
-Four of the six GB metals achieved higher mean returns over
-\textbf{contango} relative to \textbf{backwardation} phases with the
-difference being statistically significant at the 5\% level for one
-commodity (Nickel-primary (XLME)). The equally weighted US portfolio had
-a mean return of 15.7\% over \textbf{backwardation} against 16.2\%
-during phases of \textbf{contango}, both statistically significant at
-the 10\% level. The difference was considerably more pronounced for the
-equally weighted GB metals portfolio with a mean return of 8\% during
-\textbf{backwardation} rising to 35.6\% during \textbf{contango}.
+\textbf{CHP} is low and vice et versa.\\
+Over the first period twenty three of the thirty commodity assets
+considered have a higher mean returns during periods of
+\textbf{backwardation} as compared to \textbf{contango}
+(Figure~\ref{fig-regimes}) including eighteen US and five GB traded
+assets. For the US commodities the difference is statistically
+significant at the 10\% level for two assets, at the 5\% level for one
+and at the 1\% level for another; for the remaining six commodities the
+higher mean return during \textbf{contango} is not statistically
+significant for any of them. For the GB commodities, the difference is
+significant at the 10\% level for one asset while for the remaining
+asset the higher mean return during \textbf{contango} is not
+statistically significant. An equally weighted portfolio of the
+twenty-four US commodities had a mean return of 15.4\% during
+\textbf{backwardation} phases, statistically significant at the 1\%
+level, and a mean return of -1.1\% during \textbf{contango}, both in the
+first period, with the difference between them statistically significant
+at the 5\% level. The corresponding figures for an equally weighted
+portfolio of the GB metals were 4.4\% and 0.3\% respectively. These
+results provide broad support for an aggregate version of the Keynesian
+hedging pressure hypothesis and suggest that hedgers in the aggregate
+were engaged in risk transfer during this period.\\
+Over the second period the pattern essentially reverses with seventeen
+of the thirty commodities having higher mean returns during phases of
+\textbf{contango} over \textbf{backwardation} including fourteen US and
+four GB traded assets with the difference being statistically
+significant at the 5\% level for one commodity. The equally weighted US
+portfolio had a mean return of 15.7\% over \textbf{backwardation}
+against 16.2\% during phases of \textbf{contango}, both statistically
+significant at the 10\% level. The difference was considerably more
+pronounced for the equally weighted GB metals portfolio with a mean
+return of 8\% during \textbf{backwardation} rising to 35.6\% during
+\textbf{contango}.
 
@@
   correlations is provided in the attached
-  \href{http://bautheac.duckdns.org:3838/bautheac/revision-jfm/}{Internet
-  Appendix}.}. Although modest in magnitude, these exhibit a telling
-pattern, mirroring that shown by the individual commodity returns in
-Table~\ref{tbl-stats-combined}, with a substantially higher average
+  \href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.}.
+Although modest in magnitude, these exhibit a telling pattern, mirroring
+that shown by the individual commodity returns in
+Table~\ref{tbl-stats-regime-tests}, with a substantially higher average
 coefficient over \textbf{backwardation} phases in the first period (0.12
@@
 overall performance consistent across periods of \textbf{contango} and
-\textbf{backwardation}. The onset of financialisation leads to a
-substantial improvement in the performance of the CHP factor with its
-average \(R^{2}\), albeit still small at 5.4\%, almost tripling from the
-past to the financialisation period in contrast to the other factors
-that show weaker dynamics with a slight decrease and a much smaller
-increase for the open interest and term structure factors respectively.
-Here again the increase in pricing performance for the CHP factor is
-driven by the metals sector, particularly the precious sub-sector with
-the average \(R^{2}\) for the group jumping to almost 26\% during
-financialisation from 1.2\% over the past period. The corresponding
-figures of 22\% and 1.1\% for the entire US metals sector stand in sharp
-contrast with the agricultural sector, which exhibits no notable change,
-and the energy sector, where pricing performance drops substantially
-from 9.2\% down to 1.6\%. The improvement in the CHP factor's pricing
-performance remarkably comes predominantly from the long leg (low CHP
-assets: Keynesian ``normal backwardation'') of the factor\footnote{Results
-  available from the authors upon request.} with the corresponding
-mimicking portfolio's performance itself driven by the metals, the
-precious sub-sector in particular. Interestingly, although the term
-structure factor itself only sees a very modest increase, its short leg
-(low roll-yield assets: Working's backwardation) shows a sizeable rise
-in pricing performance, yet again driven the metals sector. The pattern
-of results for both factors extends to the GB traded assets and suggest
-a convergence of Keneysian and Working's term structure perspective over
-the financialisation period.\\
+\textbf{backwardation}\footnote{A breakdown of the performance by regime
+  is provided in the attached
+  \href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.}.
+The onset of financialisation leads to a substantial improvement in the
+performance of the CHP factor with its average \(R^{2}\), albeit still
+small at 5.4\%, almost tripling from the past to the financialisation
+period in contrast to the other factors that show weaker dynamics with a
+slight decrease and a much smaller increase for the open interest and
+term structure factors respectively. Here again the increase in pricing
+performance for the CHP factor is driven by the metals sector,
+particularly the precious sub-sector with the average \(R^{2}\) for the
+group jumping to almost 26\% during financialisation from 1.2\% over the
+past period. The corresponding figures of 22\% and 1.1\% for the entire
+US metals sector stand in sharp contrast with the agricultural sector,
+which exhibits no notable change, and the energy sector, where pricing
+performance drops substantially from 9.2\% down to 1.6\%. The
+improvement in the CHP factor's pricing performance remarkably comes
+predominantly from the long leg (low CHP assets: Keynesian ``normal
+backwardation'') of the factor\footnote{A breakdown of the performance
+  by factor leg is provided in the attached
+  \href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.}
+with the corresponding mimicking portfolio's performance itself driven
+by the metals, the precious sub-sector in particular. Interestingly,
+although the term structure factor itself only sees a very modest
+increase, its short leg (low roll-yield assets: Working's backwardation)
+shows a sizeable rise in pricing performance, yet again driven the
+metals sector. The pattern of results for both factors extends to the GB
+traded assets and suggest a convergence of Keneysian and Working's term
+structure perspective over the financialisation period.\\
 Taken together these results emphasise the global nature of the impact
@@
 results. Returns fall sharply relative to the financialisation period
-(Table~\ref{tbl-stats-combined}) with eighteen US commodities along with
-all six GB traded metals showing lower mean returns. Returns for equally
-weighted portfolios of both sets of assets fall down to 9.4\% and 5.3\%
-from 15.9\% and 21.8\% respectively. Returns are mostly higher during
-phases of \textbf{backwardation} relative to \textbf{contango} with
-fifteen US assets and five of the GB traded metals showing higher mean
-returns in \textbf{backwardation} and the pattern extending to equally
-weighted portfolios of the two sets of assets. Volatility is moderately
-higher for both sets with fifteen US commodities and three GB metals
-showing higher figures and interestingly eminently higher over phases of
+(Figure~\ref{fig-estimates}) with twenty-four commodities showing lower
+mean returns, including eighteen US and six GB traded assets. Returns
+for equally weighted portfolios of both sets of assets
+(Table~\ref{tbl-stats-regime-tests}) fall down to 9.4\% and 5.3\% from
+15.9\% and 21.8\% respectively. Returns are mostly higher during phases
+of \textbf{backwardation} relative to \textbf{contango}
+(Figure~\ref{fig-regimes}) with twenty commodities showing higher mean
+returns in \textbf{backwardation}, including fifteen US and five of the
+GB traded assets, and the pattern extending to equally weighted
+portfolios of the two sets of assets. Volatility is moderately higher
+with eighteen assets showing higher figures, fifteen US commodities and
+three GB metals; and interestingly eminently higher over phases of
 \textbf{contango}; out of the US complex only Sugar-\#11 (IFUS) and none
@@
 
-The returns pull-back continues into the post-crisis period
-(Table~\ref{tbl-stats-combined}) with twenty-two US and four GB traded
-assets showing lower mean returns relative to the crisis while the same
-number of US commodities and all GB metals show lower figures relative
-to the financialisation period; mean returns for equally weighted
-portfolios of US and GB assets drop down to -0.2\% and 2.7\%
+The returns pull-back continues into the post-crisis period with twenty
+six commodities (Figure~\ref{fig-estimates}), including twenty-two US
+and four GB traded assets, showing lower mean returns relative to the
+crisis while the same number of US commodities and all GB metals show
+lower figures relative to the financialisation period; mean returns for
+equally weighted portfolios of US and GB assets
+(@Table~\ref{tbl-stats-regime-tests}) drop down to -0.2\% and 2.7\%
 respectively. Interestingly volatility also recedes substantially with
-twenty US assets and all GB metals showing lower volatility figures
-relative to both the crisis and financialisation periods suggesting that
-investment outflows from the commodity futures complex have had a lower
-impact on volatility than the corresponding inflows witnessed over the
-financialisation period. The figures for the equally weighted portfolios
-of US and GB assets drop to 9.9\% and 16.2\% respectively, very close to
-pre-financialisation levels.\\
+twenty six commodities, including twenty US assets and all GB metals,
+showing lower volatility figures relative to both the crisis and
+financialisation periods suggesting that investment outflows from the
+commodity futures complex have had a lower impact on volatility than the
+corresponding inflows witnessed over the financialisation period. The
+figures for the equally weighted portfolios of US and GB assets drop to
+9.9\% and 16.2\% respectively, very close to pre-financialisation
+levels.\\
 The pattern of reversion toward the pre-financialisation Keynesian
@@
 post-crisis period with mean returns higher during phases of
-\textbf{backwardation} relative to \textbf{contango}, more so than over
-the crisis period with seventeen US commodities showing higher mean
-returns over \textbf{backwardation} phases. The difference
-(Table~\ref{tbl-regime-diference-tests}) is significant at the 5\% level
-for Lumber (XCME) and at the 10\% level for Palladium (XNYM) while no
-difference is significant for the assets showing higher figures over
-phases of \textbf{contango}. The pattern is more pronounced for the GB
-traded subset with all six assets showing higher mean returns in
+\textbf{backwardation} relative to \textbf{contango}
+(Figure~\ref{fig-regimes}), more so than over the crisis period with
+twenty three commodities showing higher mean returns over
+\textbf{backwardation} phases. Seventeen of those are US traded assets
+with the difference significant at the 5\% level for Lumber (XCME) and
+at the 10\% level for Palladium (XNYM) while no difference is
+significant for the assets showing higher figures over phases of
+\textbf{contango}. The pattern is more pronounced for the GB traded
+subset with all six assets showing higher mean returns in
 \textbf{backwardation} with the difference significant at the 1\% level
@@
 higher in \textbf{contango} although less so than over the previous
-period with seventeen US commodities showing higher figures over
-\textbf{contango} against twenty-three in the crisis period. The pattern
-extends to three of the six GB traded metals with the difference
-significant at the 1\% level for Copper (XLME) and Tin (XLME) and at the
-5\% level for Zinc (XLME) while differences are not significant for
-Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit
-higher volatility over \textbf{backwardation} phases. Equally weighted
-portfolios of US and GB traded assets on the other hand both show higher
-volatility in \textbf{contango} with the difference significant at the
-1\% level for both. Over the financialisation period in contrast
-volatilities were predominantly higher in \textbf{backwardation} for US
-traded assets with fourteen commodities showing higher volatility
-figures in these phases; the post-crisis pattern of results for
-volatilities thus likewise shows signs of reversion to
-pre-financialisation standards. After showing signs of convergence in
-the crisis period the dynamics of the explanatory power of CHP and
-\textbf{CHP} part ways (Table~\ref{tbl-time-reg-US-CHP}), seemingly
-reverting to the Keynesian paradigm observed pre-financialisation,
-further suggesting a return to legacy commodity specific dynamics. The
-recovery initiated in the crisis period for that of CHP is confirmed
-with a stronger increase, 27.2\% vs.~22.5\%, strongest for the metals
-sector, 37.3\% vs.~23.7\%, while the energy sector shows the opposite
-pattern: 11\% vs.~16\%. In contrast, after increasing stronger in the
-crisis, that for \textbf{CHP} falls overall post-crisis, 7.5\% vs
-14.7\%, with the decrease strongest for the energy sector in a relative
-sense: 2.5\% vs.~14.8\%.
+period with twenty one commodities showing higher figures over
+\textbf{contango} against twenty-eight in the crisis period, including
+seventeen US traded assets. The pattern extends to three of the six GB
+traded metals with the difference significant at the 1\% level for
+Copper (XLME) and Tin (XLME) and at the 5\% level for Zinc (XLME) while
+differences are not significant for Aluminium (XLME), Lead (XLME) and
+Nickel-primary (XLME) that exhibit higher volatility over
+\textbf{backwardation} phases. Equally weighted portfolios of US and GB
+traded assets on the other hand both show higher volatility in
+\textbf{contango} with the difference significant at the 1\% level for
+both. Over the financialisation period in contrast volatilities were
+predominantly higher in \textbf{backwardation} for US traded assets with
+fourteen commodities showing higher volatility figures in these phases;
+the post-crisis pattern of results for volatilities thus likewise shows
+signs of reversion to pre-financialisation standards. After showing
+signs of convergence in the crisis period the dynamics of the
+explanatory power of CHP and \textbf{CHP} part ways
+(Table~\ref{tbl-time-reg-US-CHP}), seemingly reverting to the Keynesian
+paradigm observed pre-financialisation, further suggesting a return to
+legacy commodity specific dynamics. The recovery initiated in the crisis
+period for that of CHP is confirmed with a stronger increase, 27.2\%
+vs.~22.5\%, strongest for the metals sector, 37.3\% vs.~23.7\%, while
+the energy sector shows the opposite pattern: 11\% vs.~16\%. In
+contrast, after increasing stronger in the crisis, that for \textbf{CHP}
+falls overall post-crisis, 7.5\% vs 14.7\%, with the decrease strongest
+for the energy sector in a relative sense: 2.5\% vs.~14.8\%.
 
@@
 
-\newgeometry{margin=.75in}
+\section*{Figures}\label{figures}
+\addcontentsline{toc}{section}{Figures}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-estimates-1.pdf}
+
+}
+
+\caption{\label{fig-estimates}This figure compares the evolution of
+estimates for mean (top panel) and volatility (bottom panel) for
+individual commodity returns across three period transitions: past →
+financialisation, financialisation → crisis and crisis → post-crisis.
+Each stacked bar shows how many cases fall into two categories: yellow
+(the estimate in the previous period is smaller than in the next period)
+and blue (the estimate in the previous period is larger than in the next
+period); numbers inside the bars indicate the count of observations in
+each category. Detailed results are available in the attached
+\href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.
+Period definitions are discussed in Section~\ref{sec-methods} while the
+results are discussed in Section~\ref{sec-results}.}
+
+\end{figure}%
+
+\newpage
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-regimes-1.pdf}
+
+}
+
+\caption{\label{fig-regimes}This figure compares estimates for mean (top
+panel) and volatility (bottom panel) for individual commodity returns
+between \textbf{CHP} regime phases (\textbf{backwardation}
+vs.~\textbf{contango}) for the four periods. Each stacked bar shows how
+many cases fall into two categories: yellow (the estimate for the
+\textbf{backwardation phase} is smaller than for the \textbf{contango}
+phase) and blue (the estimate for the \textbf{backwardation phase} is
+greater than for the \textbf{contango} phase); numbers inside the bars
+indicate the count of observations in each category.
+\textbf{Backwardation} and \textbf{contango} regimes as well as period
+definitions are discussed in Section~\ref{sec-methods} while the results
+are discussed in Section~\ref{sec-results}.}
+
+\end{figure}%
+
+\newpage
 
@@
 
-\caption{\label{tbl-stats-combined}This table shows mean returns and
-corresponding volatility for the twenty four individual US commodities
-and the six GB metals considered in the study as well as for two equally
-weighted portfolios formed from the US commodities and the GB metals
-respectively across the four periods of interest (past: 1997-2003;
-financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
-for each period the figures are shown independently for the entire
-period as well as for phases of aggregate backwardation (aggregate CHP
-\(\leq\) period median) and aggregate contango (aggregate CHP
-\textgreater{} period median). Mean values significant at the 1\%, 5\%
-and 10\% level are marked with ***, ** and * respectively. Aggregate CHP
-construction and corresponding regime definitions are discussed in
+\caption{\label{tbl-stats-regime-tests}This table shows mean returns and
+volatilities for two equally weighted portfolios of US and GB traded
+assets for the four periods. For each period, estimates are computed
+independently over the whole period as well as over phases of
+\textbf{backwardation} and \textbf{contango}. The table further shows
+the results of t-tests of significance for the mean returns as well as
+t-tests of difference between these when computed over the two phases
+independently along with F-tests of difference for the corresponding
+variances. Values significant at the 1\%, 5\% and 10\% level are marked
+with ***, ** and * respectively. Detailed results are available in the
+attached \href{https://bautheac.shinyapps.io/co-movement/}{Internet
+Appendix}. \textbf{Backwardation} and \textbf{contango} regimes as well
+as period definitions are discussed in Section~\ref{sec-methods} while
+the results are discussed in Section~\ref{sec-results}.}
+
+\tabularnewline
+
+\toprule
+\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\midrule
+\textbf{US commodities} & \textbf{mean} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{*6.89\%}} & \textcolor[HTML]{4285f4}{\textbf{**15.89\%}} & \textcolor[HTML]{4285f4}{\textbf{9.39\%}} & \textcolor[HTML]{4285f4}{\textbf{-0.18\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{***15.44\%}} & \textcolor[HTML]{4285f4}{\textbf{*15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{13.4\%}} & \textcolor[HTML]{4285f4}{\textbf{6.82\%}}\\
+\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{-1.09\%}} & \textcolor[HTML]{4285f4}{\textbf{*16.16\%}} & \textcolor[HTML]{4285f4}{\textbf{4.9\%}} & \textcolor[HTML]{4285f4}{\textbf{-6.33\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation vs.
+contango} & \textcolor[HTML]{4285f4}{\textbf{**}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
+\textbf{} & \textbf{volatility} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{9.88\%}} & \textcolor[HTML]{4285f4}{\textbf{14.21\%}} & \textcolor[HTML]{4285f4}{\textbf{14.83\%}} & \textcolor[HTML]{4285f4}{\textbf{8.59\%}}\\
+\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{10.09\%}} & \textcolor[HTML]{4285f4}{\textbf{13.05\%}} & \textcolor[HTML]{4285f4}{\textbf{19.98\%}} & \textcolor[HTML]{4285f4}{\textbf{10.95\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation vs.
+contango} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{**}} & \textcolor[HTML]{4285f4}{\textbf{***}} & \textcolor[HTML]{4285f4}{\textbf{***}}\\
+\textbf{GB commodities} & \textbf{mean} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{2.47\%}} & \textcolor[HTML]{4285f4}{\textbf{*21.77\%}} & \textcolor[HTML]{4285f4}{\textbf{5.25\%}} & \textcolor[HTML]{4285f4}{\textbf{2.72\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{4.41\%}} & \textcolor[HTML]{4285f4}{\textbf{8.01\%}} & \textcolor[HTML]{4285f4}{\textbf{15.06\%}} & \textcolor[HTML]{4285f4}{\textbf{**19.95\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.34\%}} & \textcolor[HTML]{4285f4}{\textbf{*35.56\%}} & \textcolor[HTML]{4285f4}{\textbf{-5.24\%}} & \textcolor[HTML]{4285f4}{\textbf{-14.05\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation vs.
+contango} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{**}}\\
+\textbf{} & \textbf{volatility} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\
+\textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{14.39\%}} & \textcolor[HTML]{4285f4}{\textbf{25.92\%}} & \textcolor[HTML]{4285f4}{\textbf{25.94\%}} & \textcolor[HTML]{4285f4}{\textbf{15.13\%}}\\
+\textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{16.87\%}} & \textcolor[HTML]{4285f4}{\textbf{27.88\%}} & \textcolor[HTML]{4285f4}{\textbf{34.06\%}} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{backwardation vs.
+contango} & \textcolor[HTML]{4285f4}{\textbf{***}} & \textcolor[HTML]{4285f4}{\textbf{*}} & \textcolor[HTML]{4285f4}{\textbf{***}} & \textcolor[HTML]{4285f4}{\textbf{***}}\\
+\bottomrule
+
+\end{longtable}
+
+\endgroup{}
+
+\newpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
+
+\caption{\label{tbl-time-reg-US-CHP}This table shows the average time
+series \(R^{2}\) for models where the returns series for the individual
+US traded commodities are independently regressed against relative
+change in their own commercial hedging pressure (CHP) series as well as
+against that in \textbf{CHP}, a market wide measure of CHP which
+calculation method is discussed in Section~\ref{sec-methods}. Averages
+are computed independently across the whole cross-section of US traded
+commodity assets as well as across commodity sectors and sub-sectors for
+the four periods. Period definitions are discussed in
 Section~\ref{sec-methods} while the results are discussed in
-Section~\ref{sec-results}.}
-
-\tabularnewline
-
-\toprule
-\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
-\midrule
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.48\%} & \textcolor[HTML]{4285f4}{21.37\%} & \textcolor[HTML]{4285f4}{6.89\%} & \textcolor[HTML]{4285f4}{-4.51\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23\%} & \textcolor[HTML]{4285f4}{29.54\%} & \textcolor[HTML]{4285f4}{36.15\%} & \textcolor[HTML]{4285f4}{21.8\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.86\%} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{20.48\%} & \textcolor[HTML]{4285f4}{-8.74\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23.07\%} & \textcolor[HTML]{4285f4}{29.14\%} & \textcolor[HTML]{4285f4}{31.59\%} & \textcolor[HTML]{4285f4}{21\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.3\%} & \textcolor[HTML]{4285f4}{23.54\%} & \textcolor[HTML]{4285f4}{-4.43\%} & \textcolor[HTML]{4285f4}{0.78\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23\%} & \textcolor[HTML]{4285f4}{30.01\%} & \textcolor[HTML]{4285f4}{40.14\%} & \textcolor[HTML]{4285f4}{22.68\%}\\
-\textbf{Oats (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.49\%} & \textcolor[HTML]{4285f4}{21.62\%} & \textcolor[HTML]{4285f4}{8.89\%} & \textcolor[HTML]{4285f4}{-0.87\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.22\%} & \textcolor[HTML]{4285f4}{31.04\%} & \textcolor[HTML]{4285f4}{34.67\%} & \textcolor[HTML]{4285f4}{29.5\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.39\%} & \textcolor[HTML]{4285f4}{7.82\%} & \textcolor[HTML]{4285f4}{7.85\%} & \textcolor[HTML]{4285f4}{2.56\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{29.02\%} & \textcolor[HTML]{4285f4}{33.82\%} & \textcolor[HTML]{4285f4}{31.43\%} & \textcolor[HTML]{4285f4}{31.55\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.95\%} & \textcolor[HTML]{4285f4}{*35.38\%} & \textcolor[HTML]{4285f4}{11.68\%} & \textcolor[HTML]{4285f4}{-3.17\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{35.22\%} & \textcolor[HTML]{4285f4}{28.1\%} & \textcolor[HTML]{4285f4}{37.7\%} & \textcolor[HTML]{4285f4}{27.5\%}\\
-\textbf{Soybean meal (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{7.29\%} & \textcolor[HTML]{4285f4}{12.06\%} & \textcolor[HTML]{4285f4}{8.12\%} & \textcolor[HTML]{4285f4}{-0.33\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.34\%} & \textcolor[HTML]{4285f4}{32.55\%} & \textcolor[HTML]{4285f4}{31.78\%} & \textcolor[HTML]{4285f4}{25.11\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{13.15\%} & \textcolor[HTML]{4285f4}{8.22\%} & \textcolor[HTML]{4285f4}{16.04\%} & \textcolor[HTML]{4285f4}{-3.52\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{27.77\%} & \textcolor[HTML]{4285f4}{33.06\%} & \textcolor[HTML]{4285f4}{25.7\%} & \textcolor[HTML]{4285f4}{25.1\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.52\%} & \textcolor[HTML]{4285f4}{15.91\%} & \textcolor[HTML]{4285f4}{2.32\%} & \textcolor[HTML]{4285f4}{2.22\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.94\%} & \textcolor[HTML]{4285f4}{32.13\%} & \textcolor[HTML]{4285f4}{36.85\%} & \textcolor[HTML]{4285f4}{25.32\%}\\
-\textbf{Soybean oil (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.21\%} & \textcolor[HTML]{4285f4}{15.57\%} & \textcolor[HTML]{4285f4}{4.04\%} & \textcolor[HTML]{4285f4}{-7.39\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.43\%} & \textcolor[HTML]{4285f4}{28.35\%} & \textcolor[HTML]{4285f4}{25.75\%} & \textcolor[HTML]{4285f4}{18.95\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{14.79\%} & \textcolor[HTML]{4285f4}{14.62\%} & \textcolor[HTML]{4285f4}{20.34\%} & \textcolor[HTML]{4285f4}{-9.44\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.35\%} & \textcolor[HTML]{4285f4}{28.94\%} & \textcolor[HTML]{4285f4}{22.33\%} & \textcolor[HTML]{4285f4}{18.19\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.68\%} & \textcolor[HTML]{4285f4}{16.62\%} & \textcolor[HTML]{4285f4}{-10.01\%} & \textcolor[HTML]{4285f4}{-4.12\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.55\%} & \textcolor[HTML]{4285f4}{27.91\%} & \textcolor[HTML]{4285f4}{28.65\%} & \textcolor[HTML]{4285f4}{19.79\%}\\
-\textbf{Soybeans (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.89\%} & \textcolor[HTML]{4285f4}{13.36\%} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{-3.82\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.47\%} & \textcolor[HTML]{4285f4}{30.04\%} & \textcolor[HTML]{4285f4}{28\%} & \textcolor[HTML]{4285f4}{21.22\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{13.69\%} & \textcolor[HTML]{4285f4}{0.93\%} & \textcolor[HTML]{4285f4}{13.42\%} & \textcolor[HTML]{4285f4}{-11.45\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.93\%} & \textcolor[HTML]{4285f4}{34.58\%} & \textcolor[HTML]{4285f4}{24.39\%} & \textcolor[HTML]{4285f4}{22.04\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.16\%} & \textcolor[HTML]{4285f4}{25.71\%} & \textcolor[HTML]{4285f4}{0.96\%} & \textcolor[HTML]{4285f4}{3.75\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.09\%} & \textcolor[HTML]{4285f4}{24.74\%} & \textcolor[HTML]{4285f4}{31.11\%} & \textcolor[HTML]{4285f4}{20.56\%}\\
-\addlinespace
-\textbf{Wheat-SRW (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.07\%} & \textcolor[HTML]{4285f4}{17.63\%} & \textcolor[HTML]{4285f4}{6.68\%} & \textcolor[HTML]{4285f4}{-1.58\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.93\%} & \textcolor[HTML]{4285f4}{33.03\%} & \textcolor[HTML]{4285f4}{37.62\%} & \textcolor[HTML]{4285f4}{26.58\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.7\%} & \textcolor[HTML]{4285f4}{19.02\%} & \textcolor[HTML]{4285f4}{0.98\%} & \textcolor[HTML]{4285f4}{0.44\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{25.79\%} & \textcolor[HTML]{4285f4}{36\%} & \textcolor[HTML]{4285f4}{37.53\%} & \textcolor[HTML]{4285f4}{26.57\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.78\%} & \textcolor[HTML]{4285f4}{16.29\%} & \textcolor[HTML]{4285f4}{14.57\%} & \textcolor[HTML]{4285f4}{-2.77\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.04\%} & \textcolor[HTML]{4285f4}{29.84\%} & \textcolor[HTML]{4285f4}{37.73\%} & \textcolor[HTML]{4285f4}{26.72\%}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{7.43\%} & \textcolor[HTML]{4285f4}{7.13\%} & \textcolor[HTML]{4285f4}{1.87\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.23\%} & \textcolor[HTML]{4285f4}{15.16\%} & \textcolor[HTML]{4285f4}{15.24\%} & \textcolor[HTML]{4285f4}{18.69\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.31\%} & \textcolor[HTML]{4285f4}{**20.52\%} & \textcolor[HTML]{4285f4}{7.51\%} & \textcolor[HTML]{4285f4}{6.58\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{12.79\%} & \textcolor[HTML]{4285f4}{14.93\%} & \textcolor[HTML]{4285f4}{13.39\%} & \textcolor[HTML]{4285f4}{20.14\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.81\%} & \textcolor[HTML]{4285f4}{-5.49\%} & \textcolor[HTML]{4285f4}{7.28\%} & \textcolor[HTML]{4285f4}{-3.12\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.67\%} & \textcolor[HTML]{4285f4}{15.35\%} & \textcolor[HTML]{4285f4}{16.91\%} & \textcolor[HTML]{4285f4}{17.23\%}\\
-\textbf{Cattle-live (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.45\%} & \textcolor[HTML]{4285f4}{8.77\%} & \textcolor[HTML]{4285f4}{4.13\%} & \textcolor[HTML]{4285f4}{1.92\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.1\%} & \textcolor[HTML]{4285f4}{17.43\%} & \textcolor[HTML]{4285f4}{16.32\%} & \textcolor[HTML]{4285f4}{18.3\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{8.39\%} & \textcolor[HTML]{4285f4}{14.2\%} & \textcolor[HTML]{4285f4}{5.87\%} & \textcolor[HTML]{4285f4}{-2.07\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.65\%} & \textcolor[HTML]{4285f4}{17.91\%} & \textcolor[HTML]{4285f4}{14.97\%} & \textcolor[HTML]{4285f4}{19.9\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.34\%} & \textcolor[HTML]{4285f4}{3.43\%} & \textcolor[HTML]{4285f4}{2.7\%} & \textcolor[HTML]{4285f4}{5.82\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.49\%} & \textcolor[HTML]{4285f4}{16.99\%} & \textcolor[HTML]{4285f4}{17.57\%} & \textcolor[HTML]{4285f4}{16.66\%}\\
-\textbf{Lean hogs (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{8.4\%} & \textcolor[HTML]{4285f4}{12.69\%} & \textcolor[HTML]{4285f4}{-1.09\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.33\%} & \textcolor[HTML]{4285f4}{31.89\%} & \textcolor[HTML]{4285f4}{30.37\%} & \textcolor[HTML]{4285f4}{36.94\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{12.34\%} & \textcolor[HTML]{4285f4}{16.3\%} & \textcolor[HTML]{4285f4}{18.23\%} & \textcolor[HTML]{4285f4}{19.24\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{37.6\%} & \textcolor[HTML]{4285f4}{35.73\%} & \textcolor[HTML]{4285f4}{27.83\%} & \textcolor[HTML]{4285f4}{35.61\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-10.5\%} & \textcolor[HTML]{4285f4}{0.6\%} & \textcolor[HTML]{4285f4}{7.5\%} & \textcolor[HTML]{4285f4}{-20.66\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{39.22\%} & \textcolor[HTML]{4285f4}{27.67\%} & \textcolor[HTML]{4285f4}{32.78\%} & \textcolor[HTML]{4285f4}{38.28\%}\\
-\textbf{Cocoa (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.66\%} & \textcolor[HTML]{4285f4}{16.35\%} & \textcolor[HTML]{4285f4}{1.39\%} & \textcolor[HTML]{4285f4}{3.65\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.66\%} & \textcolor[HTML]{4285f4}{29.99\%} & \textcolor[HTML]{4285f4}{31.03\%} & \textcolor[HTML]{4285f4}{24.69\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.12\%} & \textcolor[HTML]{4285f4}{9.25\%} & \textcolor[HTML]{4285f4}{-9.56\%} & \textcolor[HTML]{4285f4}{-2.98\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{33.57\%} & \textcolor[HTML]{4285f4}{31.05\%} & \textcolor[HTML]{4285f4}{26.93\%} & \textcolor[HTML]{4285f4}{25.86\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.67\%} & \textcolor[HTML]{4285f4}{23.43\%} & \textcolor[HTML]{4285f4}{12.92\%} & \textcolor[HTML]{4285f4}{10.29\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{31.81\%} & \textcolor[HTML]{4285f4}{28.91\%} & \textcolor[HTML]{4285f4}{34.66\%} & \textcolor[HTML]{4285f4}{23.57\%}\\
-\addlinespace
-\textbf{Coffee-C (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.91\%} & \textcolor[HTML]{4285f4}{20.38\%} & \textcolor[HTML]{4285f4}{2.2\%} & \textcolor[HTML]{4285f4}{1.99\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{43.84\%} & \textcolor[HTML]{4285f4}{32.3\%} & \textcolor[HTML]{4285f4}{30.17\%} & \textcolor[HTML]{4285f4}{31.86\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.51\%} & \textcolor[HTML]{4285f4}{26.49\%} & \textcolor[HTML]{4285f4}{2.66\%} & \textcolor[HTML]{4285f4}{14.36\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{48.82\%} & \textcolor[HTML]{4285f4}{32.6\%} & \textcolor[HTML]{4285f4}{29.92\%} & \textcolor[HTML]{4285f4}{31.52\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-16.87\%} & \textcolor[HTML]{4285f4}{14.38\%} & \textcolor[HTML]{4285f4}{3.4\%} & \textcolor[HTML]{4285f4}{-10.24\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.35\%} & \textcolor[HTML]{4285f4}{32.06\%} & \textcolor[HTML]{4285f4}{30.22\%} & \textcolor[HTML]{4285f4}{32.24\%}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.24\%} & \textcolor[HTML]{4285f4}{0.95\%} & \textcolor[HTML]{4285f4}{12.53\%} & \textcolor[HTML]{4285f4}{0.5\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.38\%} & \textcolor[HTML]{4285f4}{29.01\%} & \textcolor[HTML]{4285f4}{33.26\%} & \textcolor[HTML]{4285f4}{20.61\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{22.64\%} & \textcolor[HTML]{4285f4}{7.85\%} & \textcolor[HTML]{4285f4}{35.53\%} & \textcolor[HTML]{4285f4}{10.84\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.02\%} & \textcolor[HTML]{4285f4}{29.71\%} & \textcolor[HTML]{4285f4}{33.94\%} & \textcolor[HTML]{4285f4}{21.33\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-16.46\%} & \textcolor[HTML]{4285f4}{-5.92\%} & \textcolor[HTML]{4285f4}{-9.36\%} & \textcolor[HTML]{4285f4}{-8.91\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.77\%} & \textcolor[HTML]{4285f4}{28.35\%} & \textcolor[HTML]{4285f4}{32.59\%} & \textcolor[HTML]{4285f4}{19.95\%}\\
-\textbf{Lumber (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.9\%} & \textcolor[HTML]{4285f4}{-3.58\%} & \textcolor[HTML]{4285f4}{11.74\%} & \textcolor[HTML]{4285f4}{5.06\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.58\%} & \textcolor[HTML]{4285f4}{29.39\%} & \textcolor[HTML]{4285f4}{36.31\%} & \textcolor[HTML]{4285f4}{25.1\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-8.48\%} & \textcolor[HTML]{4285f4}{-2.37\%} & \textcolor[HTML]{4285f4}{29.11\%} & \textcolor[HTML]{4285f4}{**26.99\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.43\%} & \textcolor[HTML]{4285f4}{30.72\%} & \textcolor[HTML]{4285f4}{35.45\%} & \textcolor[HTML]{4285f4}{21.26\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.68\%} & \textcolor[HTML]{4285f4}{-4.77\%} & \textcolor[HTML]{4285f4}{-5.04\%} & \textcolor[HTML]{4285f4}{-17.14\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.56\%} & \textcolor[HTML]{4285f4}{28.2\%} & \textcolor[HTML]{4285f4}{37.23\%} & \textcolor[HTML]{4285f4}{28.45\%}\\
-\textbf{Orange juice (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.67\%} & \textcolor[HTML]{4285f4}{13.87\%} & \textcolor[HTML]{4285f4}{14.4\%} & \textcolor[HTML]{4285f4}{3.8\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{29.5\%} & \textcolor[HTML]{4285f4}{33.01\%} & \textcolor[HTML]{4285f4}{34.43\%} & \textcolor[HTML]{4285f4}{29.37\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.38\%} & \textcolor[HTML]{4285f4}{-2.22\%} & \textcolor[HTML]{4285f4}{18.24\%} & \textcolor[HTML]{4285f4}{18.64\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{28.01\%} & \textcolor[HTML]{4285f4}{33.01\%} & \textcolor[HTML]{4285f4}{30.09\%} & \textcolor[HTML]{4285f4}{28.64\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.83\%} & \textcolor[HTML]{4285f4}{29.93\%} & \textcolor[HTML]{4285f4}{12.29\%} & \textcolor[HTML]{4285f4}{-8.64\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{31.05\%} & \textcolor[HTML]{4285f4}{33.1\%} & \textcolor[HTML]{4285f4}{38.06\%} & \textcolor[HTML]{4285f4}{30.11\%}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.56\%} & \textcolor[HTML]{4285f4}{24.87\%} & \textcolor[HTML]{4285f4}{11.82\%} & \textcolor[HTML]{4285f4}{-1.16\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.88\%} & \textcolor[HTML]{4285f4}{33.25\%} & \textcolor[HTML]{4285f4}{37.9\%} & \textcolor[HTML]{4285f4}{28.72\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.98\%} & \textcolor[HTML]{4285f4}{29.51\%} & \textcolor[HTML]{4285f4}{2.7\%} & \textcolor[HTML]{4285f4}{-8.07\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{33.23\%} & \textcolor[HTML]{4285f4}{33.6\%} & \textcolor[HTML]{4285f4}{41.29\%} & \textcolor[HTML]{4285f4}{27.69\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-20.49\%} & \textcolor[HTML]{4285f4}{20.35\%} & \textcolor[HTML]{4285f4}{21.47\%} & \textcolor[HTML]{4285f4}{4.7\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{36.48\%} & \textcolor[HTML]{4285f4}{32.98\%} & \textcolor[HTML]{4285f4}{34.09\%} & \textcolor[HTML]{4285f4}{29.83\%}\\
-\addlinespace
-\textbf{Natural gas (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{35.38\%} & \textcolor[HTML]{4285f4}{16.25\%} & \textcolor[HTML]{4285f4}{0.93\%} & \textcolor[HTML]{4285f4}{8.33\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{61.55\%} & \textcolor[HTML]{4285f4}{54.6\%} & \textcolor[HTML]{4285f4}{53.58\%} & \textcolor[HTML]{4285f4}{44.58\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**85.84\%} & \textcolor[HTML]{4285f4}{4.76\%} & \textcolor[HTML]{4285f4}{-2.32\%} & \textcolor[HTML]{4285f4}{18.33\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{63.46\%} & \textcolor[HTML]{4285f4}{47.3\%} & \textcolor[HTML]{4285f4}{48.85\%} & \textcolor[HTML]{4285f4}{42.59\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-11.98\%} & \textcolor[HTML]{4285f4}{27.84\%} & \textcolor[HTML]{4285f4}{4.77\%} & \textcolor[HTML]{4285f4}{3.25\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{59.76\%} & \textcolor[HTML]{4285f4}{61.3\%} & \textcolor[HTML]{4285f4}{58.18\%} & \textcolor[HTML]{4285f4}{46.41\%}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{15.43\%} & \textcolor[HTML]{4285f4}{*28.74\%} & \textcolor[HTML]{4285f4}{9.67\%} & \textcolor[HTML]{4285f4}{-5.64\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{39.87\%} & \textcolor[HTML]{4285f4}{32.56\%} & \textcolor[HTML]{4285f4}{42.84\%} & \textcolor[HTML]{4285f4}{34.69\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{29.17\%} & \textcolor[HTML]{4285f4}{*35.61\%} & \textcolor[HTML]{4285f4}{11.47\%} & \textcolor[HTML]{4285f4}{14.24\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{36.74\%} & \textcolor[HTML]{4285f4}{32.09\%} & \textcolor[HTML]{4285f4}{28.19\%} & \textcolor[HTML]{4285f4}{26.94\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.21\%} & \textcolor[HTML]{4285f4}{22.04\%} & \textcolor[HTML]{4285f4}{9.95\%} & \textcolor[HTML]{4285f4}{-24.85\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.74\%} & \textcolor[HTML]{4285f4}{33.1\%} & \textcolor[HTML]{4285f4}{53.7\%} & \textcolor[HTML]{4285f4}{41.08\%}\\
-\textbf{Gasoline (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.65\%} & \textcolor[HTML]{4285f4}{30.95\%} & \textcolor[HTML]{4285f4}{10.59\%} & \textcolor[HTML]{4285f4}{-5.37\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.77\%} & \textcolor[HTML]{4285f4}{41.76\%} & \textcolor[HTML]{4285f4}{40.07\%} & \textcolor[HTML]{4285f4}{37.09\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{39\%} & \textcolor[HTML]{4285f4}{19.82\%} & \textcolor[HTML]{4285f4}{23.98\%} & \textcolor[HTML]{4285f4}{9.69\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{42.47\%} & \textcolor[HTML]{4285f4}{39.38\%} & \textcolor[HTML]{4285f4}{31.41\%} & \textcolor[HTML]{4285f4}{32.1\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.22\%} & \textcolor[HTML]{4285f4}{42.13\%} & \textcolor[HTML]{4285f4}{-0.09\%} & \textcolor[HTML]{4285f4}{-19.47\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{43.14\%} & \textcolor[HTML]{4285f4}{44.13\%} & \textcolor[HTML]{4285f4}{47.11\%} & \textcolor[HTML]{4285f4}{41.71\%}\\
-\textbf{Heating oil (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.31\%} & \textcolor[HTML]{4285f4}{*29.88\%} & \textcolor[HTML]{4285f4}{6.83\%} & \textcolor[HTML]{4285f4}{-3.44\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{40.75\%} & \textcolor[HTML]{4285f4}{35.09\%} & \textcolor[HTML]{4285f4}{33.17\%} & \textcolor[HTML]{4285f4}{30.56\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{36.32\%} & \textcolor[HTML]{4285f4}{29.41\%} & \textcolor[HTML]{4285f4}{25.56\%} & \textcolor[HTML]{4285f4}{15.16\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{41.37\%} & \textcolor[HTML]{4285f4}{33.33\%} & \textcolor[HTML]{4285f4}{25.95\%} & \textcolor[HTML]{4285f4}{24.62\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.74\%} & \textcolor[HTML]{4285f4}{30.5\%} & \textcolor[HTML]{4285f4}{-10.77\%} & \textcolor[HTML]{4285f4}{-21.62\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{40.19\%} & \textcolor[HTML]{4285f4}{36.98\%} & \textcolor[HTML]{4285f4}{39.16\%} & \textcolor[HTML]{4285f4}{35.69\%}\\
-\textbf{Copper (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.45\%} & \textcolor[HTML]{4285f4}{*28.15\%} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{-0.1\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.23\%} & \textcolor[HTML]{4285f4}{31.89\%} & \textcolor[HTML]{4285f4}{34.91\%} & \textcolor[HTML]{4285f4}{19.56\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.14\%} & \textcolor[HTML]{4285f4}{22.17\%} & \textcolor[HTML]{4285f4}{16.53\%} & \textcolor[HTML]{4285f4}{12.1\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.71\%} & \textcolor[HTML]{4285f4}{30.05\%} & \textcolor[HTML]{4285f4}{25.73\%} & \textcolor[HTML]{4285f4}{18.16\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.28\%} & \textcolor[HTML]{4285f4}{34.17\%} & \textcolor[HTML]{4285f4}{-3.46\%} & \textcolor[HTML]{4285f4}{-12.15\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.78\%} & \textcolor[HTML]{4285f4}{33.69\%} & \textcolor[HTML]{4285f4}{42.28\%} & \textcolor[HTML]{4285f4}{20.87\%}\\
-\addlinespace
-\textbf{Gold (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.5\%} & \textcolor[HTML]{4285f4}{14.35\%} & \textcolor[HTML]{4285f4}{14.01\%} & \textcolor[HTML]{4285f4}{0.53\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.14\%} & \textcolor[HTML]{4285f4}{18.89\%} & \textcolor[HTML]{4285f4}{21.46\%} & \textcolor[HTML]{4285f4}{14.41\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{9.19\%} & \textcolor[HTML]{4285f4}{13.37\%} & \textcolor[HTML]{4285f4}{9.37\%} & \textcolor[HTML]{4285f4}{4.21\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.89\%} & \textcolor[HTML]{4285f4}{19.2\%} & \textcolor[HTML]{4285f4}{17.03\%} & \textcolor[HTML]{4285f4}{12.36\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.01\%} & \textcolor[HTML]{4285f4}{15.37\%} & \textcolor[HTML]{4285f4}{19.1\%} & \textcolor[HTML]{4285f4}{-3.1\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.24\%} & \textcolor[HTML]{4285f4}{18.58\%} & \textcolor[HTML]{4285f4}{25.21\%} & \textcolor[HTML]{4285f4}{16.23\%}\\
-\textbf{Palladium (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{9.12\%} & \textcolor[HTML]{4285f4}{9.03\%} & \textcolor[HTML]{4285f4}{*29.12\%} & \textcolor[HTML]{4285f4}{13.75\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{38.27\%} & \textcolor[HTML]{4285f4}{32.71\%} & \textcolor[HTML]{4285f4}{36.14\%} & \textcolor[HTML]{4285f4}{25.38\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**49.79\%} & \textcolor[HTML]{4285f4}{24.47\%} & \textcolor[HTML]{4285f4}{30.01\%} & \textcolor[HTML]{4285f4}{**31.93\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.98\%} & \textcolor[HTML]{4285f4}{34.23\%} & \textcolor[HTML]{4285f4}{33.49\%} & \textcolor[HTML]{4285f4}{23.82\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-30.19\%} & \textcolor[HTML]{4285f4}{-6.3\%} & \textcolor[HTML]{4285f4}{30.58\%} & \textcolor[HTML]{4285f4}{-4.88\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{41.22\%} & \textcolor[HTML]{4285f4}{31.2\%} & \textcolor[HTML]{4285f4}{38.71\%} & \textcolor[HTML]{4285f4}{26.8\%}\\
-\textbf{Platinum (XNYM)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{12.93\%} & \textcolor[HTML]{4285f4}{10.56\%} & \textcolor[HTML]{4285f4}{7.29\%} & \textcolor[HTML]{4285f4}{-7.92\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.62\%} & \textcolor[HTML]{4285f4}{22.66\%} & \textcolor[HTML]{4285f4}{25.53\%} & \textcolor[HTML]{4285f4}{19.48\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{**29.46\%} & \textcolor[HTML]{4285f4}{*25.07\%} & \textcolor[HTML]{4285f4}{10.46\%} & \textcolor[HTML]{4285f4}{1.17\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.1\%} & \textcolor[HTML]{4285f4}{22.51\%} & \textcolor[HTML]{4285f4}{21.24\%} & \textcolor[HTML]{4285f4}{18.04\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-3.22\%} & \textcolor[HTML]{4285f4}{-3.81\%} & \textcolor[HTML]{4285f4}{8.04\%} & \textcolor[HTML]{4285f4}{-17.28\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23.12\%} & \textcolor[HTML]{4285f4}{22.81\%} & \textcolor[HTML]{4285f4}{28.75\%} & \textcolor[HTML]{4285f4}{20.8\%}\\
-\textbf{Silver (XCEC)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{17.54\%} & \textcolor[HTML]{4285f4}{21.96\%} & \textcolor[HTML]{4285f4}{-2.43\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22\%} & \textcolor[HTML]{4285f4}{33.92\%} & \textcolor[HTML]{4285f4}{39.87\%} & \textcolor[HTML]{4285f4}{24.35\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.98\%} & \textcolor[HTML]{4285f4}{14.29\%} & \textcolor[HTML]{4285f4}{19.66\%} & \textcolor[HTML]{4285f4}{3.44\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.07\%} & \textcolor[HTML]{4285f4}{32.5\%} & \textcolor[HTML]{4285f4}{37.17\%} & \textcolor[HTML]{4285f4}{20.3\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.57\%} & \textcolor[HTML]{4285f4}{20.83\%} & \textcolor[HTML]{4285f4}{26.77\%} & \textcolor[HTML]{4285f4}{-8.09\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.93\%} & \textcolor[HTML]{4285f4}{35.34\%} & \textcolor[HTML]{4285f4}{42.44\%} & \textcolor[HTML]{4285f4}{27.77\%}\\
-\textbf{Aluminium (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.13\%} & \textcolor[HTML]{4285f4}{13.78\%} & \textcolor[HTML]{4285f4}{-3.58\%} & \textcolor[HTML]{4285f4}{3.15\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.6\%} & \textcolor[HTML]{4285f4}{26.41\%} & \textcolor[HTML]{4285f4}{26.48\%} & \textcolor[HTML]{4285f4}{18.56\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.56\%} & \textcolor[HTML]{4285f4}{14.78\%} & \textcolor[HTML]{4285f4}{16.25\%} & \textcolor[HTML]{4285f4}{**23.68\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.82\%} & \textcolor[HTML]{4285f4}{25.57\%} & \textcolor[HTML]{4285f4}{24.94\%} & \textcolor[HTML]{4285f4}{18.94\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.38\%} & \textcolor[HTML]{4285f4}{12.86\%} & \textcolor[HTML]{4285f4}{-23.04\%} & \textcolor[HTML]{4285f4}{-16.74\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.13\%} & \textcolor[HTML]{4285f4}{27.29\%} & \textcolor[HTML]{4285f4}{28.01\%} & \textcolor[HTML]{4285f4}{18.23\%}\\
-\addlinespace
-\textbf{Copper (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.45\%} & \textcolor[HTML]{4285f4}{**28.59\%} & \textcolor[HTML]{4285f4}{5.74\%} & \textcolor[HTML]{4285f4}{0.03\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.25\%} & \textcolor[HTML]{4285f4}{31.09\%} & \textcolor[HTML]{4285f4}{34.27\%} & \textcolor[HTML]{4285f4}{18.92\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.54\%} & \textcolor[HTML]{4285f4}{25.22\%} & \textcolor[HTML]{4285f4}{18.66\%} & \textcolor[HTML]{4285f4}{11.99\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.98\%} & \textcolor[HTML]{4285f4}{29.01\%} & \textcolor[HTML]{4285f4}{25.53\%} & \textcolor[HTML]{4285f4}{17.92\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.95\%} & \textcolor[HTML]{4285f4}{32\%} & \textcolor[HTML]{4285f4}{-6.78\%} & \textcolor[HTML]{4285f4}{-11.89\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.41\%} & \textcolor[HTML]{4285f4}{32.98\%} & \textcolor[HTML]{4285f4}{41.31\%} & \textcolor[HTML]{4285f4}{19.86\%}\\
-\textbf{Lead (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.83\%} & \textcolor[HTML]{4285f4}{28.99\%} & \textcolor[HTML]{4285f4}{10.74\%} & \textcolor[HTML]{4285f4}{2.07\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.64\%} & \textcolor[HTML]{4285f4}{41.74\%} & \textcolor[HTML]{4285f4}{41.05\%} & \textcolor[HTML]{4285f4}{23.26\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{7.59\%} & \textcolor[HTML]{4285f4}{11.21\%} & \textcolor[HTML]{4285f4}{9.87\%} & \textcolor[HTML]{4285f4}{17.05\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{19.16\%} & \textcolor[HTML]{4285f4}{39.91\%} & \textcolor[HTML]{4285f4}{35.35\%} & \textcolor[HTML]{4285f4}{23.37\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.09\%} & \textcolor[HTML]{4285f4}{*46.48\%} & \textcolor[HTML]{4285f4}{12.65\%} & \textcolor[HTML]{4285f4}{-13.41\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{20.12\%} & \textcolor[HTML]{4285f4}{43.16\%} & \textcolor[HTML]{4285f4}{46.22\%} & \textcolor[HTML]{4285f4}{23.09\%}\\
-\textbf{Nickel (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{19.31\%} & \textcolor[HTML]{4285f4}{12.5\%} & \textcolor[HTML]{4285f4}{3.52\%} & \textcolor[HTML]{4285f4}{0.31\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.26\%} & \textcolor[HTML]{4285f4}{44.27\%} & \textcolor[HTML]{4285f4}{41.45\%} & \textcolor[HTML]{4285f4}{28.98\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{23.25\%} & \textcolor[HTML]{4285f4}{-39.24\%} & \textcolor[HTML]{4285f4}{16.3\%} & \textcolor[HTML]{4285f4}{**35.09\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{30.23\%} & \textcolor[HTML]{4285f4}{41.62\%} & \textcolor[HTML]{4285f4}{34.48\%} & \textcolor[HTML]{4285f4}{29.13\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{15.46\%} & \textcolor[HTML]{4285f4}{**63.47\%} & \textcolor[HTML]{4285f4}{-7.67\%} & \textcolor[HTML]{4285f4}{**-34.64\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{34.28\%} & \textcolor[HTML]{4285f4}{46.72\%} & \textcolor[HTML]{4285f4}{47.44\%} & \textcolor[HTML]{4285f4}{28.6\%}\\
-\textbf{Tin (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.07\%} & \textcolor[HTML]{4285f4}{*29.1\%} & \textcolor[HTML]{4285f4}{7.46\%} & \textcolor[HTML]{4285f4}{1.68\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.38\%} & \textcolor[HTML]{4285f4}{31.71\%} & \textcolor[HTML]{4285f4}{35.61\%} & \textcolor[HTML]{4285f4}{18.79\%}\\
-\addlinespace
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{*15.83\%} & \textcolor[HTML]{4285f4}{34.62\%} & \textcolor[HTML]{4285f4}{23.7\%} & \textcolor[HTML]{4285f4}{4.48\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.99\%} & \textcolor[HTML]{4285f4}{31.4\%} & \textcolor[HTML]{4285f4}{29.09\%} & \textcolor[HTML]{4285f4}{15.27\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-7.78\%} & \textcolor[HTML]{4285f4}{23.88\%} & \textcolor[HTML]{4285f4}{-6.82\%} & \textcolor[HTML]{4285f4}{-1.69\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.77\%} & \textcolor[HTML]{4285f4}{32.08\%} & \textcolor[HTML]{4285f4}{41.13\%} & \textcolor[HTML]{4285f4}{21.68\%}\\
-\textbf{Zinc (XLME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.52\%} & \textcolor[HTML]{4285f4}{20.13\%} & \textcolor[HTML]{4285f4}{7.62\%} & \textcolor[HTML]{4285f4}{9.07\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.73\%} & \textcolor[HTML]{4285f4}{38.77\%} & \textcolor[HTML]{4285f4}{36.17\%} & \textcolor[HTML]{4285f4}{23.25\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-9.06\%} & \textcolor[HTML]{4285f4}{2.95\%} & \textcolor[HTML]{4285f4}{10.05\%} & \textcolor[HTML]{4285f4}{**29.42\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.15\%} & \textcolor[HTML]{4285f4}{36.86\%} & \textcolor[HTML]{4285f4}{33.28\%} & \textcolor[HTML]{4285f4}{22.12\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.13\%} & \textcolor[HTML]{4285f4}{37.11\%} & \textcolor[HTML]{4285f4}{5.43\%} & \textcolor[HTML]{4285f4}{-11.31\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{22.38\%} & \textcolor[HTML]{4285f4}{40.51\%} & \textcolor[HTML]{4285f4}{39.03\%} & \textcolor[HTML]{4285f4}{24.32\%}\\
-\addlinespace
-\textbf{US commodities} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{*6.89\%} & \textcolor[HTML]{4285f4}{**15.89\%} & \textcolor[HTML]{4285f4}{9.39\%} & \textcolor[HTML]{4285f4}{-0.18\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{10\%} & \textcolor[HTML]{4285f4}{13.62\%} & \textcolor[HTML]{4285f4}{17.58\%} & \textcolor[HTML]{4285f4}{9.86\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{***15.44\%} & \textcolor[HTML]{4285f4}{*15.66\%} & \textcolor[HTML]{4285f4}{13.4\%} & \textcolor[HTML]{4285f4}{6.82\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{9.88\%} & \textcolor[HTML]{4285f4}{14.21\%} & \textcolor[HTML]{4285f4}{14.83\%} & \textcolor[HTML]{4285f4}{8.59\%}\\
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-1.09\%} & \textcolor[HTML]{4285f4}{*16.16\%} & \textcolor[HTML]{4285f4}{4.9\%} & \textcolor[HTML]{4285f4}{-6.33\%}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{10.09\%} & \textcolor[HTML]{4285f4}{13.05\%} & \textcolor[HTML]{4285f4}{19.98\%} & \textcolor[HTML]{4285f4}{10.95\%}\\
-\textbf{GB commodities} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.47\%} & \textcolor[HTML]{4285f4}{*21.77\%} & \textcolor[HTML]{4285f4}{5.25\%} & \textcolor[HTML]{4285f4}{2.72\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{15.66\%} & \textcolor[HTML]{4285f4}{26.91\%} & \textcolor[HTML]{4285f4}{30.24\%} & \textcolor[HTML]{4285f4}{16.19\%}\\
-\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{4.41\%} & \textcolor[HTML]{4285f4}{8.01\%} & \textcolor[HTML]{4285f4}{15.06\%} & \textcolor[HTML]{4285f4}{**19.95\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{14.39\%} & \textcolor[HTML]{4285f4}{25.92\%} & \textcolor[HTML]{4285f4}{25.94\%} & \textcolor[HTML]{4285f4}{15.13\%}\\
-\addlinespace
-\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.34\%} & \textcolor[HTML]{4285f4}{*35.56\%} & \textcolor[HTML]{4285f4}{-5.24\%} & \textcolor[HTML]{4285f4}{-14.05\%}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.87\%} & \textcolor[HTML]{4285f4}{27.88\%} & \textcolor[HTML]{4285f4}{34.06\%} & \textcolor[HTML]{4285f4}{17.1\%}\\
-\bottomrule
-
-\end{longtable}
-
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{7}{9}\selectfont
-
-\begin{longtable}[t]{>{}l>{}l>{}l>{}l>{}r>{}r}
-
-\caption{\label{tbl-regime-diference-tests}This table shows the results
-for tests of difference in mean (t-test) and variance (F-test) between
-phases of aggregate backwardation and contango for the twenty four
-individual US commodities and the six GB metals considered in the study
-as well as for two equally weighted portfolios formed from the US
-commodities and the GB metals respectively across the four periods of
-interest (past: 1997-2003; financialisation: 2004-2008; crisis:
-2008-2013; post-crisis: 2013-2018). 1\%, 5\% and 10\% p-value levels are
-marked with ***, ** and * respectively in the significance column.
-Aggregate CHP construction and corresponding regime definitions are
-discussed in Section~\ref{sec-methods} while the results are discussed
-in Section~\ref{sec-results}.}
-
-\tabularnewline
-
-\toprule
-\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{period}} & \textcolor{black}{\textbf{moment}} & \textcolor{black}{\textbf{dominant regime}} & \textcolor{black}{\textbf{p-value}} & \textcolor{black}{\textbf{significance}}\\
-\midrule
-\textbf{Corn-\#2 yellow (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{34.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{89.69\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{91.01\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{47.46\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{40.83\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{34} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{57.39\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.02\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{Oats (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{38.12\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{33} ***}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{35.29\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{8} ***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.66\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{32} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{82.72\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{Soybean meal (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{66.39\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{81.2\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.83\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{56.57\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{31} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{75.13\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.31\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Soybean oil (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{31.59\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{81.72\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{92.18\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.2\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.64\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{30} ***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{69.59\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.36\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{Soybeans (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{48.92\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{17.18\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{38.74\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{7} ***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{57.61\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{29} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.95\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.05\%} & \textcolor[HTML]{4285f4}{*}\\
-\addlinespace
-\textbf{Wheat-SRW (XCBT)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{44.86\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.79\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{83.21\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{6} ***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{76.2\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.81\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{94.9\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Cattle-feeder (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{76.82\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.34\%} & \textcolor[HTML]{4285f4}{*}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.35\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{62.38\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{99.19\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{28} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{50.04\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{5} ***}\\
-\textbf{Cattle-live (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.11\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{15.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.61\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{20.96\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{82.12\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{63.19\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{4} ***}\\
-\textbf{Lean hogs (XCME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{45.71\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{24.77\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{55.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{3} ***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{68.46\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{21.55\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{6.81\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{Cocoa (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{99.36\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{12.33\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.85\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{7.73\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{42.98\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{27} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{51.48\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.17\%} & \textcolor[HTML]{4285f4}{**}\\
-\addlinespace
-\textbf{Coffee-C (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{53.38\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{69.3\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{51.63\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{95.23\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{82.84\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{35.39\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{52.86\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Cotton-\#2 (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.02\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{41.38\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{59.06\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{26.81\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{14.44\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{33.04\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{32.06\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.67\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{Lumber (XCME)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.56\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{75.67\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{84.3\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.36\%} & \textcolor[HTML]{4285f4}{**}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{28.12\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{22.82\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.31\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{26} ***}\\
-\textbf{Orange juice (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{66.85\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{28.81\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{92.47\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.55\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{25} ***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{25.72\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.01\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Sugar-\#11 (IFUS)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{24.1\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.76\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{75.29\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.89\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{56.23\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.08\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.22\%} & \textcolor[HTML]{4285f4}{*}\\
-\addlinespace
-\textbf{Natural gas (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{4.66\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.01\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{68.1\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{24} ***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.28\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{23} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{67.04\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.08\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{Crude oil-WTI (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{38.33\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{22} ***}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{61.91\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{49.38\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{95.55\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{21} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.99\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{20} ***}\\
-\textbf{Gasoline (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{18.96\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{66.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{58.35\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.58\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{49.08\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{19} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.23\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{18} ***}\\
-\textbf{Heating oil (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{21.83\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.45\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{99.52\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.52\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{23.31\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{17} ***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{15.71\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{16} ***}\\
-\textbf{Copper (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{90.64\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{17.88\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{74.37\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.71\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{55.78\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{15} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{17.19\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\addlinespace
-\textbf{Gold (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{43.44\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.63\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{39.92\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{60.22\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{14} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{56.58\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{13} ***}\\
-\textbf{Palladium (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.77\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{12} ***}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{30.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.38\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.05\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{9.4\%} & \textcolor[HTML]{4285f4}{*}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.12\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{Platinum (XNYM)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{6.08\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{14.41\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{83.86\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{85.5\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{11} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{27.26\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.02\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{Silver (XCEC)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{96.07\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.09\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{88.44\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{5.01\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.12\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.08\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{61.83\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{10} ***}\\
-\textbf{Aluminium (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{86.1\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{9} ***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.59\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.33\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{10.79\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.41\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.33\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{25.99\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{Copper (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{88.51\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.03\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{87.59\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.15\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{43.61\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{8} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{16.36\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{Lead (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{58.96\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{16.81\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{40.11\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{4.11\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{93.17\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{7} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{15.62\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{85.45\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Nickel (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{76.56\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.04\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{1.24\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.62\%} & \textcolor[HTML]{4285f4}{***}\\
-\addlinespace
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{49.29\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{6} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{0.46\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{69.15\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{Tin (XLME)} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.22\%} & \textcolor[HTML]{4285f4}{*}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{14.94\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{70.17\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{58.14\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{34.29\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{5} ***}\\
-\addlinespace
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{73.44\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{4} ***}\\
-\textbf{Zinc (XLME)} & \textbf{past} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{59.39\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{11.75\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{37.67\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{2.29\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{91.89\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.01\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{5.05\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{1.77\%} & \textcolor[HTML]{4285f4}{**}\\
-\addlinespace
-\textbf{US commodities} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{3.63\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{54.29\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{93.09\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{2.22\%} & \textcolor[HTML]{4285f4}{**}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{58.92\%} & \textcolor[HTML]{4285f4}{}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{3} ***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{11.83\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{2} ***}\\
-\textbf{GB commodities} & \textbf{past} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{78.74\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{\vphantom{1} ***}\\
-\addlinespace
-\textbf{} & \textbf{financialisation} & \textbf{mean} & \textbf{contango} & \textcolor[HTML]{4285f4}{27.95\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{7.65\%} & \textcolor[HTML]{4285f4}{*}\\
-\textbf{} & \textbf{crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{46.83\%} & \textcolor[HTML]{4285f4}{}\\
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0\%} & \textcolor[HTML]{4285f4}{***}\\
-\textbf{} & \textbf{post-crisis} & \textbf{mean} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{1.37\%} & \textcolor[HTML]{4285f4}{**}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{volatility} & \textbf{contango} & \textcolor[HTML]{4285f4}{0.13\%} & \textcolor[HTML]{4285f4}{***}\\
-\bottomrule
-
-\end{longtable}
-
-\endgroup{}
-
-\newpage
-
-\begingroup\fontsize{7}{9}\selectfont
-
-\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
-
-\caption{\label{tbl-time-reg-US-CHP}This table shows the average time
-series \(R^{2}\) for models where the returns series for the twenty four
-individual US commodities are independently regressed against relative
-change in their own commercial hedging pressure (CHP) series as well as
-against that in aggregate CHP, a market wide measure of CHP which
-calculation method is discussed in Section~\ref{sec-methods}. Averages
-are calculated independently across the whole cross-section of US traded
-commodity assets considered in the study as well as across commodity
-sectors and sub-sectors for the four periods of interest (past:
-1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis:
-2013-2018). The results are discussed in Section~\ref{sec-results} while
-Section~\ref{sec-taxonomy} details the taxonomy for the commodity assets
-considered.}
+Section~\ref{sec-results} and the commodity assets taxonomy is detailed
+in Section~\ref{sec-taxonomy}.}
 
@@
 time series regression \(R^{2}\) for models where the returns series for
-all the commodity assets considered in the study are independently
-regressed against the return series for our mimicking portfolios for
-risk factors in returns, including the market, CHP, open interest and
-term structure factors. The results are calculated independently across
-countries and commodity sectors and sub-sectors for the four periods of
-interest (past: 1997-2003; financialisation: 2004-2008; crisis:
-2008-2013; post-crisis: 2013-2018); for each period the results are
-calculated independently over the entire period as well as over phases
-of aggregate backwardation and contango. Factors as well as aggregate
-CHP construction and corresponding regime definitions are discussed in
-Section~\ref{sec-methods} while the results are discussed in
-Section~\ref{sec-results} and the taxonomy for the commodity assets
-considered is detailed in Section~\ref{sec-taxonomy}.}
+all the commodity assets are independently regressed against the return
+series for our mimicking portfolios for risk factors in returns,
+including the market, CHP, open interest and term structure factors. The
+results are computed independently across countries and commodity
+sectors and sub-sectors for the four periods. A breakdown of the
+estimates computed independently over the whole periods as well as over
+phases of \textbf{backwardation} and \textbf{contango} is provided in
+the attached \href{https://bautheac.shinyapps.io/co-movement/}{Internet
+Appendix}. Factor construction methods along with \textbf{backwardation}
+and \textbf{contango} regimes as well as period definitions are
+discussed in Section~\ref{sec-methods} while the results are discussed
+in Section~\ref{sec-results} and the commodity assets taxonomy is
+detailed in Section~\ref{sec-taxonomy}.}
 
@@
 \endgroup{}
-
-\restoregeometry
 

### 2025-08-25 docs/paper.qmd

@@
 
-@tbl-stats-regime-tests displays descriptive statistics for the commodity series considered in the study; the results show a clear pattern of increase in average return during financialisation with most individual commodities showing a higher mean return and an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
+The results show a clear pattern of increase in average return during financialisation as illustrated by @fig-estimates, with most individual commodities showing a higher mean return, and @tbl-stats-regime-tests with an equally weighted portfolio of the US traded assets showing a mean returns of 15.9% significant at the 5% level vs.
 6.9% with a 10% significance in the pre-financialisation period.
@@
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
-@tbl-stats-regime-tests further reports the dominating regime for each asset-period-moment combination along with the corresponding results of difference tests for returns mean and variance between the two regimes^[The estimate values per regime as well as the p-values for the corresponding difference tests are available in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).].
-Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another.
-For the remaining six commodities the higher mean return during **contango** is not statistically significant for any of them.
-For the six GB commodities, all metals, five of them had higher mean returns during phases of **backwardation** as compared to **contango** in the first period, with one of these differences being statistically significant at the 10% level while for the remaining asset (Zinc (XLME)) the higher mean return during **contango** is not statistically significant.
+Over the first period twenty three of the thirty commodity assets considered have a higher mean returns during periods of **backwardation** as compared to **contango** (@fig-regimes) including eighteen US and five GB traded assets.
+For the US commodities the difference is statistically significant at the 10% level for two assets, at the 5% level for one and at the 1% level for another; for the remaining six commodities the higher mean return during **contango** is not statistically significant for any of them.
+For the GB commodities, the difference is significant at the 10% level for one asset while for the remaining asset the higher mean return during **contango** is not statistically significant.
 An equally weighted portfolio of the twenty-four US commodities had a mean return of 15.4% during **backwardation** phases, statistically significant at the 1% level, and a mean return of -1.1% during **contango**, both in the first period, with the difference between them statistically significant at the 5% level.
@@
 These results provide broad support for an aggregate version of the Keynesian hedging pressure hypothesis and suggest that hedgers in the aggregate were engaged in risk transfer during this period.
-Over the second period the pattern essentially reverses.
-For the twenty-four US commodities over this period, fourteen have higher mean returns during phases of **contango** over **backwardation**.
-Four of the six GB metals achieved higher mean returns over **contango** relative to **backwardation** phases with the difference being statistically significant at the 5% level for one commodity (Nickel-primary (XLME)).
+Over the second period the pattern essentially reverses with seventeen of the thirty commodities having higher mean returns during phases of **contango** over **backwardation** including fourteen US and four GB traded assets with the difference being statistically significant at the 5% level for one commodity.
 The equally weighted US portfolio had a mean return of 15.7% over **backwardation** against 16.2% during phases of **contango**, both statistically significant at the 10% level.
@@
 The crisis period (late 2008 to mid-2013) shows a contrasting pattern of results.
-Returns fall sharply relative to the financialisation period (@tbl-stats-regime-tests) with eighteen US commodities along with all six GB traded metals showing lower mean returns.
-Returns for equally weighted portfolios of both sets of assets fall down to 9.4% and 5.3% from 15.9% and 21.8% respectively.
-Returns are mostly higher during phases of **backwardation** relative to **contango** with fifteen US assets and five of the GB traded metals showing higher mean returns in **backwardation** and the pattern extending to equally weighted portfolios of the two sets of assets.
-Volatility is moderately higher for both sets with fifteen US commodities and three GB metals showing higher figures and interestingly eminently higher over phases of **contango**; out of the US complex only Sugar-#11 (IFUS) and none of the GB traded metals show higher volatility figures over **backwardation** phases.
+Returns fall sharply relative to the financialisation period (@fig-estimates) with twenty-four commodities showing lower mean returns, including eighteen US and six GB traded assets.
+Returns for equally weighted portfolios of both sets of assets (@tbl-stats-regime-tests) fall down to 9.4% and 5.3% from 15.9% and 21.8% respectively.
+Returns are mostly higher during phases of **backwardation** relative to **contango** (@fig-regimes) with twenty commodities showing higher mean returns in **backwardation**, including fifteen US and five of the GB traded assets, and the pattern extending to equally weighted portfolios of the two sets of assets.
+Volatility is moderately higher with eighteen assets showing higher figures, fifteen US commodities and three GB metals; and interestingly eminently higher over phases of **contango**; out of the US complex only Sugar-#11 (IFUS) and none of the GB traded metals show higher volatility figures over **backwardation** phases.
 The symmetry between the dynamics of CHP and **CHP**'s explanatory power on individual commodity returns breaks (@tbl-time-reg-US-CHP) with both now seemingly converging; the US cross-sectional average $R^{2}$ at the individual level bouncing back up (22.5% vs 20.8%) while that at the aggregate level rises further (14.7% vs 7.1%).
@@
 
-The returns pull-back continues into the post-crisis period (@tbl-stats-regime-tests) with twenty-two US and four GB traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all GB metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and GB assets drop down to -0.2% and 2.7% respectively.
-Interestingly volatility also recedes substantially with twenty US assets and all GB metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
+The returns pull-back continues into the post-crisis period with twenty six commodities (@fig-estimates), including twenty-two US and four GB traded assets, showing lower mean returns relative to the crisis while the same number of US commodities and all GB metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and GB assets (@@tbl-stats-regime-tests) drop down to -0.2% and 2.7% respectively.
+Interestingly volatility also recedes substantially with twenty six commodities, including twenty US assets and all GB metals, showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
 The figures for the equally weighted portfolios of US and GB assets drop to 9.9% and 16.2% respectively, very close to pre-financialisation levels.
-The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of **backwardation** relative to **contango**, more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
-The difference (@tbl-stats-regime-tests) is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
+The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of **backwardation** relative to **contango** (@fig-regimes), more so than over the crisis period with twenty three commodities showing higher mean returns over **backwardation** phases.
+Seventeen of those are US traded assets with the difference significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
 The pattern is more pronounced for the GB traded subset with all six assets showing higher mean returns in **backwardation** with the difference significant at the 1% level for Nickel-primary (XLME), 5% level for Aluminium (XLME) and 10% level for Zinc (XLME).
 It also extends to equally weighted portfolios of US and GB traded assets that both show higher mean returns during **backwardation** with the difference significant at the 5% level for the GB portfolio and the figure close to the 10% level significance threshold for the portfolio of US assets.
-Volatilities are overall higher in **contango** although less so than over the previous period with seventeen US commodities showing higher figures over **contango** against twenty-three in the crisis period.
+Volatilities are overall higher in **contango** although less so than over the previous period with twenty one commodities showing higher figures over **contango** against twenty-eight in the crisis period, including seventeen US traded assets.
 The pattern extends to three of the six GB traded metals with the difference significant at the 1% level for Copper (XLME) and Tin (XLME) and at the 5% level for Zinc (XLME) while differences are not significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit higher volatility over **backwardation** phases.

### 2025-08-26 explore/scripts/revision-jfm/figures.r
Make inner yearly correlations figure
Insert in figures section and update body of text accordingly.

@@ -9,6 +9,7 @@ library(tidyr)
 
 
 tables_directory_path <- here("explore", "tables", "revision-jfm")
+results_directory_path <- here::here("explore", "results", "revision-jfm")
 figures_directory_path <- here("explore", "results", "figures")
 
 table_stats_individuals_path <- paste_forward_slash(tables_directory_path, "stats-individual-assets.rds")
@@ -88,6 +89,53 @@ figure_regimes <- ggplot(table_regimes, aes(x = period, y = value, fill = operat
   scale_fill_manual(values = met.brewer("Isfahan2", 2))
 
 
-
 figure_regimes_path <- paste_forward_slash(figures_directory_path, "regimes.rds")
 write_rds(figure_regimes, figure_regimes_path)
+
+
+
+
+
+table_correlations_path <- paste_forward_slash(tables_directory_path, "correlations-inner-years.rds")
+correlations <- read_rds(table_correlations_path) 
+
+
+table_correlations <- readr::read_rds(
+  slituR::paste_forward_slash(results_directory_path, "correlations-inner.rds")
+) |> dplyr::filter(
+    field == "close price", type == "return", frequency == "day", 
+    timespan == "year", regime == "whole period", subsector == "all"
+  ) |>
+    dplyr::select(country, sector, year, average) |>
+    dplyr::slice_tail(n = 1L, by = c("country", "sector", "year")) |>
+    dplyr::mutate(
+       `asset pool` = paste(country, sector, sep = "-"),
+      `asset pool` = factor(
+        `asset pool`, levels = c("all-all", "US-all", "US-agriculturals", "US-energy", "US-metals", "GB-all")
+      )
+    ) |>
+    dplyr::select(`asset pool`, year, average)
+
+
+# Create a line chart for correlations
+figure_correlations <- ggplot(table_correlations, aes(x = year, y = average, color = `asset pool`, group = `asset pool`)) +
+  geom_line(linewidth = 1.2) +
+  geom_point(size = 2, show.legend = FALSE) +
+  # geom_text(aes(label = round(average, 2)), vjust = -1, size = 5, fontface = "bold", show.legend = FALSE) +
+  labs(title = "Average returns pairwise correlations", x = "", y = "", color = "Asset Pool") +
+  theme_minimal() +
+  theme(
+    strip.text = element_text(size = 10),
+    plot.title = element_text(size = 12, hjust = 0.5),
+    legend.position = "bottom",
[…]

### 2025-08-26 explore/scripts/revision-jfm/tables.r
Remove regime breakdown
from inner correlations table (table 3).

@@ -362,13 +362,19 @@ correlations_inner <- readr::read_rds(
 
 ### By period ####
 correlations_inner_periods <- dplyr::filter(
-  correlations_inner, field == "close price", type == "return", frequency == "day", timespan == "period"
+  correlations_inner, field == "close price", type == "return", frequency == "day", 
+  timespan == "period", regime == "whole period"
 ) |>
-  dplyr::select(country, sector, subsector, period, regime, average) |>
-  dplyr::group_by(country, sector, subsector, period, regime) |>
+  dplyr::select(country, sector, subsector, period, average) |>
+  dplyr::group_by(country, sector, subsector, period) |>
   dplyr::slice_tail(n = 1L) |> dplyr::ungroup() |>
   tidyr::pivot_wider(names_from = "period", values_from = "average") |>
   sort_table_by_country_sector_subsector(sort_levels)
+
+readr::write_rds(
+  correlations_inner_periods, 
+  slituR::paste_forward_slash(tables_directory_path, "correlations-inner-periods.rds")
+)
 
 ### By year ####
 correlations_inner_years <- dplyr::filter(
@@ -389,6 +395,11 @@ correlations_inner_years <- dplyr::filter(
     dplyr::across(c(`0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`), ~ format(.x, scientific = FALSE)),
     dplyr::across(c(`0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`), ~ stringr::str_replace_all(.x, "    NA", ""))
     )
+
+readr::write_rds(
+  correlations_inner_years, 
+  slituR::paste_forward_slash(tables_directory_path, "correlations-inner-years.rds")
+)
 
 ## cross ####
 format_correlations_cross_by_period <- function(correlations_cross){

### 2025-08-26 docs/paper.tex
Update body of text, figures and tables sections
to accommodate new figure 3 and restructured table 3.

@@
 
+\usepackage{rotating}
 \usepackage{booktabs}
@@
 \(\beta\)s and \(R^{2}\)s are computed for models where the regressor is
-the factor itself as well as both its long and short legs independently
-(results available upon request).
+the factor itself as well as both its long and short legs
+independently\footnote{A detailed breakdown of these results is provided
+  in the attached
+  \href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.}.
 
@@
 cross-section of the commodity assets considered in the study as well as
-by country, sector and sub-sector.
-Table~\ref{tbl-correlations-inner-periods} shows the results for the
-four periods of interest with the results reported for the entire period
-as well as for periods of \textbf{backwardation} and \textbf{contango}.
-For the entire sample the average pairwise correlation jumps from 0.07
-in the first period to 0.16 over financialisation. This finding
-indicates higher interdependence within the full cross-section of
-commodities starting with the financialisation period, consistent with
-the empirical findings in \citet{fryMcKibbin_evolution_2023} and
+by country, sector and sub-sector with the results shown in
+Table~\ref{tbl-correlations-inner-periods}. For the entire sample the
+average pairwise correlation jumps from 0.07 in the first period to 0.16
+over financialisation. This finding indicates higher interdependence
+within the full cross-section of commodities starting with the
+financialisation period, consistent with the empirical findings in
+\citet{fryMcKibbin_evolution_2023} and
 \citet{mayer_financialization_2017} as well as with the theoretical
@@
 \textbf{backwardation} and \textbf{contango} for all the sectors and
-sub-sectors over the past and financialisation periods. In this context,
-the ontological consequences of financialisation are better observed
-from an investment perspective as illustrated in
+sub-sectors over the past and financialisation periods\footnote{A
+  breakdown of the average pairwise correlations by regime is provided
+  in the attached
+  \href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.}.
+In this context, the ontological consequences of financialisation are
+better observed from an investment perspective as illustrated in
 Table~\ref{tbl-correlations-cross-periods} where we observe average
@@
 We break down Table~\ref{tbl-correlations-inner-periods}'s average
-correlations by year in Table~\ref{tbl-correlations-inner-years}. For
-the full sample of assets, the average pairwise correlations remain in
-the 0.06--0.08 range from 1998 through 2003, before suddenly increasing
-to 0.12 from 2003 to 2004. This suggests 2004 as a distinct break point
-for the onset of financialisation, as noted in several studies
+correlations by year in Figure~\ref{fig-correlations}. For the full
+sample of assets, the average pairwise correlations remain in the
+0.06--0.08 range from 1998 through 2003, before suddenly increasing to
+0.12 from 2003 to 2004. This suggests 2004 as a distinct break point for
+the onset of financialisation, as noted in several studies
 \citep{baker_financialization_2021, tang_index_2012}. We further observe
@@
 The corresponding pricing performance displays a similar pattern as
-shown in Table~\ref{tbl-regressions-factors} where for each period the
-corresponding \(R^{2}\) values are independently averaged over the
-entire period as well as over periods of \textbf{contango} and
-\textbf{backwardation}. The average \(R^{2}\) for the market factor
-across the entire cross-section of commodity assets, including the GB
-traded base metals, increases to around 20\% during financialisation
-compared to around 10\% over the previous period with the rise driven by
-the metals sector at large. The sector average for the US traded assets
-jumps to 31\% during financialisation from 7.5\% over the past period
-while for the GB traded assets the corresponding figure increases from
-less than 2\%, or virtually no explanatory power for the (US based)
-market factor, to almost 12\% over the financialisation period. The
-results for our other risk factor mimicking portfolios show a similar
-pattern and provide a deeper insights into co-movement dynamics in this
-context. All three factors---CHP, open interest and term
-structure---performed poorly in the first period, indicating that the
-commodities with extreme factor attributes (high or low CHP for example)
-were uncorrelated with the rest of the commodity cross-section, and the
-overall performance consistent across periods of \textbf{contango} and
-\textbf{backwardation}\footnote{A breakdown of the performance by regime
-  is provided in the attached
+shown in Table~\ref{tbl-regressions-factors}. The average \(R^{2}\) for
+the market factor across the entire cross-section of commodity assets,
+including the GB traded base metals, increases to around 20\% during
+financialisation compared to around 10\% over the previous period with
+the rise driven by the metals sector at large. The sector average for
+the US traded assets jumps to 31\% during financialisation from 7.5\%
+over the past period while for the GB traded assets the corresponding
+figure increases from less than 2\%, or virtually no explanatory power
+for the (US based) market factor, to almost 12\% over the
+financialisation period. The results for our other risk factor mimicking
+portfolios show a similar pattern and provide a deeper insights into
+co-movement dynamics in this context. All three factors---CHP, open
+interest and term structure---performed poorly in the first period,
+indicating that the commodities with extreme factor attributes (high or
+low CHP for example) were uncorrelated with the rest of the commodity
+cross-section, and the overall performance consistent across periods of
+\textbf{contango} and \textbf{backwardation}\footnote{A breakdown of the
+  performance by regime is provided in the attached
   \href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.}.
@@
 section of the metals sector only progresses modestly to 0.59 after
-peaking at 0.63 in 2006 (Table~\ref{tbl-correlations-inner-years}). In
-contrast, the GB traded assets see a sharp increase to over 0.65
-starting in 2007 up to a peak of 0.69 in 2010, and so does the
-agricultural sector with the sharpest increase in 2008 when the average
-pairwise correlation for the sector jumps to 0.30. The energy sector
-also shows a substantial progression starting in 2007 and peaking at
-0.63 in 2008 before leveling back down over the rest of the period. The
-onset of the financial crisis seems therefore to have had an across the
-board impact on the interdependence of commodities in contrast with
-financialisation, much more closely related to the metals sector.
+peaking at 0.63 in 2006 (Figure~\ref{fig-correlations}). In contrast,
+the GB traded assets see a sharp increase to over 0.65 starting in 2007
+up to a peak of 0.69 in 2010, and so does the agricultural sector with
+the sharpest increase in 2008 when the average pairwise correlation for
+the sector jumps to 0.30. The energy sector also shows a substantial
+progression starting in 2007 and peaking at 0.63 in 2008 before leveling
+back down over the rest of the period. The onset of the financial crisis
+seems therefore to have had an across the board impact on the
+interdependence of commodities in contrast with financialisation, much
+more closely related to the metals sector.
 
@@
 equally weighted portfolios of US and GB assets
-(@Table~\ref{tbl-stats-regime-tests}) drop down to -0.2\% and 2.7\%
+(Table~\ref{tbl-stats-regime-tests}) drop down to -0.2\% and 2.7\%
 respectively. Interestingly volatility also recedes substantially with
@@
 not seem to have been widely noted, appears to begin in the latter part
-of the crisis period, around 2012
-(Table~\ref{tbl-correlations-inner-years}), before leveling down over
-the whole post-crisis period.
+of the crisis period, around 2012 (Figure~\ref{fig-correlations}),
+before leveling down over the whole post-crisis period.
 
@@
 widely discussed in the existing literature.\\
-The phases analysis further documents the emerging role/dominance of the
-\textbf{contango} regime post-crisis with average correlations higher
-during those phases and the pattern stronger for the metal assets both
-US and GB traded. Similarly, for the latter the pricing performance of
-the market factor is considerably better during phase of
-\textbf{contango} in contrast with the previous periods that showed no
-substantial difference between phase of \textbf{contango} and
-\textbf{backwardation}. The figures for the US and GB traded segments of
-the sector are 23\% (\textbf{contango}) vs 11.5\%
-(\textbf{backwardation}) against 36.2\% vs 43\% during financialisation
-and 14.4\% (\textbf{contango}) vs 6.6\% (\textbf{backwardation}) against
-33.5\% vs 34.4\% during financialisation respectively. Taken together,
-these results indicate some recent changes in the correlation structure
-within the sector and provide additional evidence that the
-interdependence effects of financialization seems to have been strongest
-for the entire cross-section of the metals sector with a lesser impact
-for the other sectors. This observation, along with the decline in
-interdependence in the commodity sector at large documented above, could
-form a valuable basis for future research.
+The phases analysis\footnote{Results available in the attached
+  \href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.}
+further documents the emerging role/dominance of the \textbf{contango}
+regime post-crisis with average correlations higher during those phases
+and the pattern stronger for the metal assets both US and GB traded.
+Similarly, for the latter the pricing performance of the market factor
+is considerably better during phase of \textbf{contango} in contrast
+with the previous periods that showed no substantial difference between
+phase of \textbf{contango} and \textbf{backwardation}. The figures for
+the US and GB traded segments of the sector are 23\% (\textbf{contango})
+vs 11.5\% (\textbf{backwardation}) against 36.2\% vs 43\% during
+financialisation and 14.4\% (\textbf{contango}) vs 6.6\%
+(\textbf{backwardation}) against 33.5\% vs 34.4\% during
+financialisation respectively. Taken together, these results indicate
+some recent changes in the correlation structure within the sector and
+provide additional evidence that the interdependence effects of
+financialization seems to have been strongest for the entire
+cross-section of the metals sector with a lesser impact for the other
+sectors. This observation, along with the decline in interdependence in
+the commodity sector at large documented above, could form a valuable
+basis for future research.
 
@@
 
+\newgeometry{margin=2.5cm}
+
+\begin{sidewaysfigure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-correlations-1.pdf}
+
+}
+
+\caption{\label{fig-correlations}While
+Table~\ref{tbl-correlations-inner-periods} shows results computed
+independently for the four periods, this figure shows the results of the
+same analysis implemented for each year over the entire sample period.
+The corresponding figures along with a breakdown by sub-sector are
+provided in the attached
+\href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.
+The results are discussed in Section~\ref{sec-results} while
+Section~\ref{sec-taxonomy} details the commodity assets taxonomy.}
+
+\end{sidewaysfigure}%
+
+\restoregeometry
+
+\newpage
+
 \section*{Tables}\label{tables}
@@
 variances. Values significant at the 1\%, 5\% and 10\% level are marked
-with ***, ** and * respectively. Detailed results are available in the
-attached \href{https://bautheac.shinyapps.io/co-movement/}{Internet
-Appendix}. \textbf{Backwardation} and \textbf{contango} regimes as well
-as period definitions are discussed in Section~\ref{sec-methods} while
-the results are discussed in Section~\ref{sec-results}.}
+with ***, ** and * respectively. Results for individual commodity assets
+are available in the attached
+\href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.
+\textbf{Backwardation} and \textbf{contango} regimes as well as period
+definitions are discussed in Section~\ref{sec-methods} while the results
+are discussed in Section~\ref{sec-results}.}
 
@@
 
-\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r>{}r}
+\begin{longtable}[t]{>{}l>{}l>{}l>{}r>{}r>{}r>{}r}
 
@@
 within countries and commodity sectors and sub-sectors for the four
-periods. For each period, the results are computed independently over
-the entire period as well as over phases of \textbf{backwardation} and
-\textbf{contango}. \textbf{Backwardation} and \textbf{contango} regimes
-as well as period definitions are discussed in Section~\ref{sec-methods}
-while the results are discussed in Section~\ref{sec-results} and the
-commodity assets taxonomy is detailed in Section~\ref{sec-taxonomy}.}
+periods. A breakdown of the average pairwise correlations by
+\textbf{CHP} regime (\textbf{backwardation} vs.~\textbf{contango}) is
+provided in the attached
+\href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.
+\textbf{Backwardation} and \textbf{contango} regimes as well as period
+definitions are discussed in Section~\ref{sec-methods} while the results
+are discussed in Section~\ref{sec-results} and the commodity assets
+taxonomy is detailed in Section~\ref{sec-taxonomy}.}
 
@@
 \toprule
-\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{regime}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
+\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
 \midrule
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0737}} & \textcolor[HTML]{4285f4}{\textbf{0.1638}} & \textcolor[HTML]{4285f4}{\textbf{0.2849}} & \textcolor[HTML]{4285f4}{\textbf{0.1282}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0724}} & \textcolor[HTML]{4285f4}{\textbf{0.1790}} & \textcolor[HTML]{4285f4}{\textbf{0.2709}} & \textcolor[HTML]{4285f4}{\textbf{0.1001}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0748}} & \textcolor[HTML]{4285f4}{\textbf{0.1501}} & \textcolor[HTML]{4285f4}{\textbf{0.2985}} & \textcolor[HTML]{4285f4}{\textbf{0.1495}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0684}} & \textcolor[HTML]{4285f4}{\textbf{0.1545}} & \textcolor[HTML]{4285f4}{\textbf{0.2526}} & \textcolor[HTML]{4285f4}{\textbf{0.1096}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0642}} & \textcolor[HTML]{4285f4}{\textbf{0.1697}} & \textcolor[HTML]{4285f4}{\textbf{0.2323}} & \textcolor[HTML]{4285f4}{\textbf{0.0859}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0720}} & \textcolor[HTML]{4285f4}{\textbf{0.1402}} & \textcolor[HTML]{4285f4}{\textbf{0.2706}} & \textcolor[HTML]{4285f4}{\textbf{0.1268}}\\
-\textbf{} & \textbf{agriculturals} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0910}} & \textcolor[HTML]{4285f4}{\textbf{0.1305}} & \textcolor[HTML]{4285f4}{\textbf{0.2322}} & \textcolor[HTML]{4285f4}{\textbf{0.1075}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0799}} & \textcolor[HTML]{4285f4}{\textbf{0.1421}} & \textcolor[HTML]{4285f4}{\textbf{0.1975}} & \textcolor[HTML]{4285f4}{\textbf{0.0955}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.1018}} & \textcolor[HTML]{4285f4}{\textbf{0.1184}} & \textcolor[HTML]{4285f4}{\textbf{0.2611}} & \textcolor[HTML]{4285f4}{\textbf{0.1186}}\\
-\textbf{} & \textbf{} & \textbf{grains} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4421}} & \textcolor[HTML]{4285f4}{\textbf{0.4898}} & \textcolor[HTML]{4285f4}{\textbf{0.5673}} & \textcolor[HTML]{4285f4}{\textbf{0.3728}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.4312}} & \textcolor[HTML]{4285f4}{\textbf{0.5283}} & \textcolor[HTML]{4285f4}{\textbf{0.5749}} & \textcolor[HTML]{4285f4}{\textbf{0.3289}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4570}} & \textcolor[HTML]{4285f4}{\textbf{0.4510}} & \textcolor[HTML]{4285f4}{\textbf{0.5675}} & \textcolor[HTML]{4285f4}{\textbf{0.4161}}\\
-\textbf{} & \textbf{} & \textbf{livestock} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.3340}} & \textcolor[HTML]{4285f4}{\textbf{0.2868}} & \textcolor[HTML]{4285f4}{\textbf{0.3707}} & \textcolor[HTML]{4285f4}{\textbf{0.3333}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3053}} & \textcolor[HTML]{4285f4}{\textbf{0.2652}} & \textcolor[HTML]{4285f4}{\textbf{0.3906}} & \textcolor[HTML]{4285f4}{\textbf{0.3220}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.3605}} & \textcolor[HTML]{4285f4}{\textbf{0.3150}} & \textcolor[HTML]{4285f4}{\textbf{0.3557}} & \textcolor[HTML]{4285f4}{\textbf{0.3483}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{softs} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.0391}} & \textcolor[HTML]{4285f4}{\textbf{0.0853}} & \textcolor[HTML]{4285f4}{\textbf{0.1584}} & \textcolor[HTML]{4285f4}{\textbf{0.0764}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.0437}} & \textcolor[HTML]{4285f4}{\textbf{0.0845}} & \textcolor[HTML]{4285f4}{\textbf{0.1210}} & \textcolor[HTML]{4285f4}{\textbf{0.0685}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.0334}} & \textcolor[HTML]{4285f4}{\textbf{0.0874}} & \textcolor[HTML]{4285f4}{\textbf{0.1937}} & \textcolor[HTML]{4285f4}{\textbf{0.0833}}\\
-\textbf{} & \textbf{energy} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4908}} & \textcolor[HTML]{4285f4}{\textbf{0.5892}} & \textcolor[HTML]{4285f4}{\textbf{0.4687}} & \textcolor[HTML]{4285f4}{\textbf{0.4203}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.4844}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}} & \textcolor[HTML]{4285f4}{\textbf{0.4601}} & \textcolor[HTML]{4285f4}{\textbf{0.4179}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4957}} & \textcolor[HTML]{4285f4}{\textbf{0.5869}} & \textcolor[HTML]{4285f4}{\textbf{0.4779}} & \textcolor[HTML]{4285f4}{\textbf{0.4210}}\\
-\textbf{} & \textbf{} & \textbf{petroleum} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.7278}} & \textcolor[HTML]{4285f4}{\textbf{0.7846}} & \textcolor[HTML]{4285f4}{\textbf{0.7692}} & \textcolor[HTML]{4285f4}{\textbf{0.7175}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.6962}} & \textcolor[HTML]{4285f4}{\textbf{0.7854}} & \textcolor[HTML]{4285f4}{\textbf{0.7727}} & \textcolor[HTML]{4285f4}{\textbf{0.7282}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.7606}} & \textcolor[HTML]{4285f4}{\textbf{0.7856}} & \textcolor[HTML]{4285f4}{\textbf{0.7716}} & \textcolor[HTML]{4285f4}{\textbf{0.7134}}\\
-\textbf{} & \textbf{metals} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.2167}} & \textcolor[HTML]{4285f4}{\textbf{0.5553}} & \textcolor[HTML]{4285f4}{\textbf{0.5877}} & \textcolor[HTML]{4285f4}{\textbf{0.4721}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.2201}} & \textcolor[HTML]{4285f4}{\textbf{0.5418}} & \textcolor[HTML]{4285f4}{\textbf{0.6353}} & \textcolor[HTML]{4285f4}{\textbf{0.4155}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.2145}} & \textcolor[HTML]{4285f4}{\textbf{0.5727}} & \textcolor[HTML]{4285f4}{\textbf{0.5709}} & \textcolor[HTML]{4285f4}{\textbf{0.5035}}\\
-\textbf{} & \textbf{} & \textbf{precious} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.2883}} & \textcolor[HTML]{4285f4}{\textbf{0.6305}} & \textcolor[HTML]{4285f4}{\textbf{0.6704}} & \textcolor[HTML]{4285f4}{\textbf{0.5762}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3070}} & \textcolor[HTML]{4285f4}{\textbf{0.6061}} & \textcolor[HTML]{4285f4}{\textbf{0.6991}} & \textcolor[HTML]{4285f4}{\textbf{0.5386}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.2713}} & \textcolor[HTML]{4285f4}{\textbf{0.6591}} & \textcolor[HTML]{4285f4}{\textbf{0.6615}} & \textcolor[HTML]{4285f4}{\textbf{0.5949}}\\
-\addlinespace
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{whole period} & \textcolor[HTML]{4285f4}{\textbf{0.4047}} & \textcolor[HTML]{4285f4}{\textbf{0.4691}} & \textcolor[HTML]{4285f4}{\textbf{0.6536}} & \textcolor[HTML]{4285f4}{\textbf{0.4412}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{backwardation} & \textcolor[HTML]{4285f4}{\textbf{0.3987}} & \textcolor[HTML]{4285f4}{\textbf{0.4753}} & \textcolor[HTML]{4285f4}{\textbf{0.6729}} & \textcolor[HTML]{4285f4}{\textbf{0.3954}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{contango} & \textcolor[HTML]{4285f4}{\textbf{0.4108}} & \textcolor[HTML]{4285f4}{\textbf{0.4652}} & \textcolor[HTML]{4285f4}{\textbf{0.6456}} & \textcolor[HTML]{4285f4}{\textbf{0.4797}}\\
+\textbf{all} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.0737}} & \textcolor[HTML]{4285f4}{\textbf{0.1638}} & \textcolor[HTML]{4285f4}{\textbf{0.2849}} & \textcolor[HTML]{4285f4}{\textbf{0.1282}}\\
+\textbf{US} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.0684}} & \textcolor[HTML]{4285f4}{\textbf{0.1545}} & \textcolor[HTML]{4285f4}{\textbf{0.2526}} & \textcolor[HTML]{4285f4}{\textbf{0.1096}}\\
+\textbf{} & \textbf{agriculturals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.0910}} & \textcolor[HTML]{4285f4}{\textbf{0.1305}} & \textcolor[HTML]{4285f4}{\textbf{0.2322}} & \textcolor[HTML]{4285f4}{\textbf{0.1075}}\\
+\textbf{} & \textbf{} & \textbf{grains} & \textcolor[HTML]{4285f4}{\textbf{0.4421}} & \textcolor[HTML]{4285f4}{\textbf{0.4898}} & \textcolor[HTML]{4285f4}{\textbf{0.5673}} & \textcolor[HTML]{4285f4}{\textbf{0.3728}}\\
+\textbf{} & \textbf{} & \textbf{livestock} & \textcolor[HTML]{4285f4}{\textbf{0.3340}} & \textcolor[HTML]{4285f4}{\textbf{0.2868}} & \textcolor[HTML]{4285f4}{\textbf{0.3707}} & \textcolor[HTML]{4285f4}{\textbf{0.3333}}\\
+\addlinespace
+\textbf{} & \textbf{} & \textbf{softs} & \textcolor[HTML]{4285f4}{\textbf{0.0391}} & \textcolor[HTML]{4285f4}{\textbf{0.0853}} & \textcolor[HTML]{4285f4}{\textbf{0.1584}} & \textcolor[HTML]{4285f4}{\textbf{0.0764}}\\
+\textbf{} & \textbf{energy} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.4908}} & \textcolor[HTML]{4285f4}{\textbf{0.5892}} & \textcolor[HTML]{4285f4}{\textbf{0.4687}} & \textcolor[HTML]{4285f4}{\textbf{0.4203}}\\
+\textbf{} & \textbf{} & \textbf{petroleum} & \textcolor[HTML]{4285f4}{\textbf{0.7278}} & \textcolor[HTML]{4285f4}{\textbf{0.7846}} & \textcolor[HTML]{4285f4}{\textbf{0.7692}} & \textcolor[HTML]{4285f4}{\textbf{0.7175}}\\
+\textbf{} & \textbf{metals} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.2167}} & \textcolor[HTML]{4285f4}{\textbf{0.5553}} & \textcolor[HTML]{4285f4}{\textbf{0.5877}} & \textcolor[HTML]{4285f4}{\textbf{0.4721}}\\
+\textbf{} & \textbf{} & \textbf{precious} & \textcolor[HTML]{4285f4}{\textbf{0.2883}} & \textcolor[HTML]{4285f4}{\textbf{0.6305}} & \textcolor[HTML]{4285f4}{\textbf{0.6704}} & \textcolor[HTML]{4285f4}{\textbf{0.5762}}\\
+\addlinespace
+\textbf{GB} & \textbf{all} & \textbf{all} & \textcolor[HTML]{4285f4}{\textbf{0.4047}} & \textcolor[HTML]{4285f4}{\textbf{0.4691}} & \textcolor[HTML]{4285f4}{\textbf{0.6536}} & \textcolor[HTML]{4285f4}{\textbf{0.4412}}\\
 \bottomrule
@@
 \endgroup{}
-
-\newpage
-
-\begin{landscape}\begingroup\fontsize{7}{9}\selectfont
-
-\begin{longtable}[t]{>{}l>{}l>{}l>{}l>{}r>{}r>{}r>{}r>{}r>{}r>{}r>{}r>{}r>{}r}
-
-\caption{\label{tbl-correlations-inner-years}While
-Table~\ref{tbl-correlations-inner-periods} shows results computed
-independently for the four periods, this table shows the results of the
-same analysis implemented for each year over the entire sample period.
-The results are discussed in Section~\ref{sec-results} while
-Section~\ref{sec-taxonomy} details the commodity assets taxonomy.}
-
-\tabularnewline
-
-\toprule
-\textcolor{black}{\textbf{country}} & \textcolor{black}{\textbf{sector}} & \textcolor{black}{\textbf{sub-sector}} & \textcolor{black}{\textbf{decade}} & \textcolor{black}{\textbf{0}} & \textcolor{black}{\textbf{1}} & \textcolor{black}{\textbf{2}} & \textcolor{black}{\textbf{3}} & \textcolor{black}{\textbf{4}} & \textcolor{black}{\textbf{5}} & \textcolor{black}{\textbf{6}} & \textcolor{black}{\textbf{7}} & \textcolor{black}{\textbf{8}} & \textcolor{black}{\textbf{9}}\\
-\midrule
-\textbf{all} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0401}} & \textcolor[HTML]{4285f4}{\textbf{0.0812}} & \textcolor[HTML]{4285f4}{\textbf{0.0822}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0652}} & \textcolor[HTML]{4285f4}{\textbf{0.0719}} & \textcolor[HTML]{4285f4}{\textbf{0.0796}} & \textcolor[HTML]{4285f4}{\textbf{0.0848}} & \textcolor[HTML]{4285f4}{\textbf{0.1242}} & \textcolor[HTML]{4285f4}{\textbf{0.1247}} & \textcolor[HTML]{4285f4}{\textbf{0.1650}} & \textcolor[HTML]{4285f4}{\textbf{0.1541}} & \textcolor[HTML]{4285f4}{\textbf{0.3334}} & \textcolor[HTML]{4285f4}{\textbf{0.2913}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2743}} & \textcolor[HTML]{4285f4}{\textbf{0.2837}} & \textcolor[HTML]{4285f4}{\textbf{0.2235}} & \textcolor[HTML]{4285f4}{\textbf{0.1432}} & \textcolor[HTML]{4285f4}{\textbf{0.1139}} & \textcolor[HTML]{4285f4}{\textbf{0.1547}} & \textcolor[HTML]{4285f4}{\textbf{0.1339}} & \textcolor[HTML]{4285f4}{\textbf{0.0963}} & \textcolor[HTML]{4285f4}{\textbf{0.1374}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{US} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0536}} & \textcolor[HTML]{4285f4}{\textbf{0.0811}} & \textcolor[HTML]{4285f4}{\textbf{0.0803}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0597}} & \textcolor[HTML]{4285f4}{\textbf{0.0652}} & \textcolor[HTML]{4285f4}{\textbf{0.0600}} & \textcolor[HTML]{4285f4}{\textbf{0.0723}} & \textcolor[HTML]{4285f4}{\textbf{0.1073}} & \textcolor[HTML]{4285f4}{\textbf{0.1164}} & \textcolor[HTML]{4285f4}{\textbf{0.1502}} & \textcolor[HTML]{4285f4}{\textbf{0.1479}} & \textcolor[HTML]{4285f4}{\textbf{0.3284}} & \textcolor[HTML]{4285f4}{\textbf{0.2621}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2275}} & \textcolor[HTML]{4285f4}{\textbf{0.2541}} & \textcolor[HTML]{4285f4}{\textbf{0.1850}} & \textcolor[HTML]{4285f4}{\textbf{0.1018}} & \textcolor[HTML]{4285f4}{\textbf{0.0986}} & \textcolor[HTML]{4285f4}{\textbf{0.1371}} & \textcolor[HTML]{4285f4}{\textbf{0.1064}} & \textcolor[HTML]{4285f4}{\textbf{0.0905}} & \textcolor[HTML]{4285f4}{\textbf{0.1197}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{} & \textbf{agriculturals} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.0827}} & \textcolor[HTML]{4285f4}{\textbf{0.0916}} & \textcolor[HTML]{4285f4}{\textbf{0.1121}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0918}} & \textcolor[HTML]{4285f4}{\textbf{0.0967}} & \textcolor[HTML]{4285f4}{\textbf{0.0734}} & \textcolor[HTML]{4285f4}{\textbf{0.0827}} & \textcolor[HTML]{4285f4}{\textbf{0.1111}} & \textcolor[HTML]{4285f4}{\textbf{0.1090}} & \textcolor[HTML]{4285f4}{\textbf{0.1125}} & \textcolor[HTML]{4285f4}{\textbf{0.1131}} & \textcolor[HTML]{4285f4}{\textbf{0.3034}} & \textcolor[HTML]{4285f4}{\textbf{0.2507}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.2038}} & \textcolor[HTML]{4285f4}{\textbf{0.2304}} & \textcolor[HTML]{4285f4}{\textbf{0.1583}} & \textcolor[HTML]{4285f4}{\textbf{0.0716}} & \textcolor[HTML]{4285f4}{\textbf{0.0846}} & \textcolor[HTML]{4285f4}{\textbf{0.1360}} & \textcolor[HTML]{4285f4}{\textbf{0.1121}} & \textcolor[HTML]{4285f4}{\textbf{0.1148}} & \textcolor[HTML]{4285f4}{\textbf{0.1181}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{} & \textbf{} & \textbf{grains} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.5243}} & \textcolor[HTML]{4285f4}{\textbf{0.4882}} & \textcolor[HTML]{4285f4}{\textbf{0.5650}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.4870}} & \textcolor[HTML]{4285f4}{\textbf{0.4337}} & \textcolor[HTML]{4285f4}{\textbf{0.3851}} & \textcolor[HTML]{4285f4}{\textbf{0.3402}} & \textcolor[HTML]{4285f4}{\textbf{0.4473}} & \textcolor[HTML]{4285f4}{\textbf{0.5335}} & \textcolor[HTML]{4285f4}{\textbf{0.4594}} & \textcolor[HTML]{4285f4}{\textbf{0.5040}} & \textcolor[HTML]{4285f4}{\textbf{0.6325}} & \textcolor[HTML]{4285f4}{\textbf{0.5681}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.5389}} & \textcolor[HTML]{4285f4}{\textbf{0.6424}} & \textcolor[HTML]{4285f4}{\textbf{0.5592}} & \textcolor[HTML]{4285f4}{\textbf{0.3199}} & \textcolor[HTML]{4285f4}{\textbf{0.3134}} & \textcolor[HTML]{4285f4}{\textbf{0.4390}} & \textcolor[HTML]{4285f4}{\textbf{0.3872}} & \textcolor[HTML]{4285f4}{\textbf{0.4123}} & \textcolor[HTML]{4285f4}{\textbf{0.3618}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{} & \textbf{} & \textbf{livestock} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.2192}} & \textcolor[HTML]{4285f4}{\textbf{0.3724}} & \textcolor[HTML]{4285f4}{\textbf{0.3453}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.2762}} & \textcolor[HTML]{4285f4}{\textbf{0.3315}} & \textcolor[HTML]{4285f4}{\textbf{0.3243}} & \textcolor[HTML]{4285f4}{\textbf{0.3497}} & \textcolor[HTML]{4285f4}{\textbf{0.2937}} & \textcolor[HTML]{4285f4}{\textbf{0.4170}} & \textcolor[HTML]{4285f4}{\textbf{0.2784}} & \textcolor[HTML]{4285f4}{\textbf{0.2744}} & \textcolor[HTML]{4285f4}{\textbf{0.2822}} & \textcolor[HTML]{4285f4}{\textbf{0.3365}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.3568}} & \textcolor[HTML]{4285f4}{\textbf{0.4772}} & \textcolor[HTML]{4285f4}{\textbf{0.3585}} & \textcolor[HTML]{4285f4}{\textbf{0.1783}} & \textcolor[HTML]{4285f4}{\textbf{0.3532}} & \textcolor[HTML]{4285f4}{\textbf{0.4246}} & \textcolor[HTML]{4285f4}{\textbf{0.3445}} & \textcolor[HTML]{4285f4}{\textbf{0.2948}} & \textcolor[HTML]{4285f4}{\textbf{0.2994}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{softs} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{-0.0042}} & \textcolor[HTML]{4285f4}{\textbf{-0.0001}} & \textcolor[HTML]{4285f4}{\textbf{0.0128}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.0603}} & \textcolor[HTML]{4285f4}{\textbf{0.0289}} & \textcolor[HTML]{4285f4}{\textbf{0.0470}} & \textcolor[HTML]{4285f4}{\textbf{0.0807}} & \textcolor[HTML]{4285f4}{\textbf{0.0577}} & \textcolor[HTML]{4285f4}{\textbf{0.0624}} & \textcolor[HTML]{4285f4}{\textbf{0.0765}} & \textcolor[HTML]{4285f4}{\textbf{0.0485}} & \textcolor[HTML]{4285f4}{\textbf{0.2484}} & \textcolor[HTML]{4285f4}{\textbf{0.1710}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.1273}} & \textcolor[HTML]{4285f4}{\textbf{0.1400}} & \textcolor[HTML]{4285f4}{\textbf{0.1038}} & \textcolor[HTML]{4285f4}{\textbf{0.0568}} & \textcolor[HTML]{4285f4}{\textbf{0.0413}} & \textcolor[HTML]{4285f4}{\textbf{0.0983}} & \textcolor[HTML]{4285f4}{\textbf{0.1280}} & \textcolor[HTML]{4285f4}{\textbf{0.0825}} & \textcolor[HTML]{4285f4}{\textbf{0.0565}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{} & \textbf{energy} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.4060}} & \textcolor[HTML]{4285f4}{\textbf{0.4552}} & \textcolor[HTML]{4285f4}{\textbf{0.5256}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.4362}} & \textcolor[HTML]{4285f4}{\textbf{0.5186}} & \textcolor[HTML]{4285f4}{\textbf{0.5682}} & \textcolor[HTML]{4285f4}{\textbf{0.5248}} & \textcolor[HTML]{4285f4}{\textbf{0.6212}} & \textcolor[HTML]{4285f4}{\textbf{0.6402}} & \textcolor[HTML]{4285f4}{\textbf{0.5082}} & \textcolor[HTML]{4285f4}{\textbf{0.5530}} & \textcolor[HTML]{4285f4}{\textbf{0.6278}} & \textcolor[HTML]{4285f4}{\textbf{0.4840}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.4549}} & \textcolor[HTML]{4285f4}{\textbf{0.4752}} & \textcolor[HTML]{4285f4}{\textbf{0.3796}} & \textcolor[HTML]{4285f4}{\textbf{0.2889}} & \textcolor[HTML]{4285f4}{\textbf{0.4103}} & \textcolor[HTML]{4285f4}{\textbf{0.4282}} & \textcolor[HTML]{4285f4}{\textbf{0.4442}} & \textcolor[HTML]{4285f4}{\textbf{0.3890}} & \textcolor[HTML]{4285f4}{\textbf{0.4270}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{} & \textbf{} & \textbf{petroleum} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.7207}} & \textcolor[HTML]{4285f4}{\textbf{0.7946}} & \textcolor[HTML]{4285f4}{\textbf{0.8527}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.6122}} & \textcolor[HTML]{4285f4}{\textbf{0.7632}} & \textcolor[HTML]{4285f4}{\textbf{0.8072}} & \textcolor[HTML]{4285f4}{\textbf{0.6948}} & \textcolor[HTML]{4285f4}{\textbf{0.8321}} & \textcolor[HTML]{4285f4}{\textbf{0.7377}} & \textcolor[HTML]{4285f4}{\textbf{0.7703}} & \textcolor[HTML]{4285f4}{\textbf{0.7895}} & \textcolor[HTML]{4285f4}{\textbf{0.8184}} & \textcolor[HTML]{4285f4}{\textbf{0.7460}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.8835}} & \textcolor[HTML]{4285f4}{\textbf{0.7867}} & \textcolor[HTML]{4285f4}{\textbf{0.6692}} & \textcolor[HTML]{4285f4}{\textbf{0.6075}} & \textcolor[HTML]{4285f4}{\textbf{0.6710}} & \textcolor[HTML]{4285f4}{\textbf{0.7069}} & \textcolor[HTML]{4285f4}{\textbf{0.7547}} & \textcolor[HTML]{4285f4}{\textbf{0.6672}} & \textcolor[HTML]{4285f4}{\textbf{0.7786}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{} & \textbf{metals} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.2296}} & \textcolor[HTML]{4285f4}{\textbf{0.2877}} & \textcolor[HTML]{4285f4}{\textbf{0.2449}}\\
-\addlinespace
-\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.1860}} & \textcolor[HTML]{4285f4}{\textbf{0.1832}} & \textcolor[HTML]{4285f4}{\textbf{0.1992}} & \textcolor[HTML]{4285f4}{\textbf{0.2290}} & \textcolor[HTML]{4285f4}{\textbf{0.4923}} & \textcolor[HTML]{4285f4}{\textbf{0.4480}} & \textcolor[HTML]{4285f4}{\textbf{0.6328}} & \textcolor[HTML]{4285f4}{\textbf{0.5426}} & \textcolor[HTML]{4285f4}{\textbf{0.5664}} & \textcolor[HTML]{4285f4}{\textbf{0.5547}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.6297}} & \textcolor[HTML]{4285f4}{\textbf{0.6458}} & \textcolor[HTML]{4285f4}{\textbf{0.6649}} & \textcolor[HTML]{4285f4}{\textbf{0.6160}} & \textcolor[HTML]{4285f4}{\textbf{0.4531}} & \textcolor[HTML]{4285f4}{\textbf{0.4850}} & \textcolor[HTML]{4285f4}{\textbf{0.4269}} & \textcolor[HTML]{4285f4}{\textbf{0.3584}} & \textcolor[HTML]{4285f4}{\textbf{0.5259}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\textbf{} & \textbf{} & \textbf{precious} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.3063}} & \textcolor[HTML]{4285f4}{\textbf{0.3451}} & \textcolor[HTML]{4285f4}{\textbf{0.3308}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.2934}} & \textcolor[HTML]{4285f4}{\textbf{0.2337}} & \textcolor[HTML]{4285f4}{\textbf{0.3053}} & \textcolor[HTML]{4285f4}{\textbf{0.2959}} & \textcolor[HTML]{4285f4}{\textbf{0.5688}} & \textcolor[HTML]{4285f4}{\textbf{0.5674}} & \textcolor[HTML]{4285f4}{\textbf{0.6969}} & \textcolor[HTML]{4285f4}{\textbf{0.6143}} & \textcolor[HTML]{4285f4}{\textbf{0.6428}} & \textcolor[HTML]{4285f4}{\textbf{0.6713}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.7004}} & \textcolor[HTML]{4285f4}{\textbf{0.7107}} & \textcolor[HTML]{4285f4}{\textbf{0.7089}} & \textcolor[HTML]{4285f4}{\textbf{0.6988}} & \textcolor[HTML]{4285f4}{\textbf{0.5620}} & \textcolor[HTML]{4285f4}{\textbf{0.6088}} & \textcolor[HTML]{4285f4}{\textbf{0.5652}} & \textcolor[HTML]{4285f4}{\textbf{0.4746}} & \textcolor[HTML]{4285f4}{\textbf{0.5716}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\addlinespace
-\textbf{GB} & \textbf{all} & \textbf{all} & \textbf{1990} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{}} & \textcolor[HTML]{4285f4}{\textbf{0.2289}} & \textcolor[HTML]{4285f4}{\textbf{0.3601}} & \textcolor[HTML]{4285f4}{\textbf{0.4487}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2000} & \textcolor[HTML]{4285f4}{\textbf{0.3550}} & \textcolor[HTML]{4285f4}{\textbf{0.4082}} & \textcolor[HTML]{4285f4}{\textbf{0.4775}} & \textcolor[HTML]{4285f4}{\textbf{0.5526}} & \textcolor[HTML]{4285f4}{\textbf{0.5068}} & \textcolor[HTML]{4285f4}{\textbf{0.4792}} & \textcolor[HTML]{4285f4}{\textbf{0.4340}} & \textcolor[HTML]{4285f4}{\textbf{0.4653}} & \textcolor[HTML]{4285f4}{\textbf{0.5795}} & \textcolor[HTML]{4285f4}{\textbf{0.6647}}\\
-\textbf{} & \textbf{} & \textbf{} & \textbf{2010} & \textcolor[HTML]{4285f4}{\textbf{0.6886}} & \textcolor[HTML]{4285f4}{\textbf{0.6742}} & \textcolor[HTML]{4285f4}{\textbf{0.6122}} & \textcolor[HTML]{4285f4}{\textbf{0.6606}} & \textcolor[HTML]{4285f4}{\textbf{0.4700}} & \textcolor[HTML]{4285f4}{\textbf{0.5003}} & \textcolor[HTML]{4285f4}{\textbf{0.4636}} & \textcolor[HTML]{4285f4}{\textbf{0.3810}} & \textcolor[HTML]{4285f4}{\textbf{0.3598}} & \textcolor[HTML]{4285f4}{\textbf{}}\\
-\bottomrule
-
-\end{longtable}
-
-\endgroup{}
-\end{landscape}
 

### 2025-08-26 paper.qmd
Deploying to gh-pages from @ bautheac/financialisation-co-movement@377dcc6c018cb3465e026ff7d1ce6f986440a47f 🚀

@@
       cite-style: authoryear
+    include-in-header: preamble.tex
   html:
@@
 We use a time series regression approach where individual commodity front futures contract daily returns are regressed on returns to the mimicking portfolio for a particular risk factor with the corresponding $\beta$s and $R^{2}$s averaged.
-For the long-short factors the $\beta$s and $R^{2}$s are computed for models where the regressor is the factor itself as well as both its long and short legs independently (results available upon request).
+For the long-short factors the $\beta$s and $R^{2}$s are computed for models where the regressor is the factor itself as well as both its long and short legs independently^[A detailed breakdown of these results is provided in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).].
 
@@
 The extended Keynesian hedging pressure paradigm, in the context of financialisation, should also imply that returns for individual commodities should be high in periods where **CHP** is low and vice et versa.
-@tbl-stats-regime-tests further reports the dominating regime for each asset-period-moment combination along with the corresponding results of difference tests for returns mean and variance between the two regimes^[The estimate values per regime as well as the p-values for the corresponding difference tests are available in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).].
-Over the first period eighteen of the twenty-four US commodities have higher mean returns during periods of **backwardation** as compared to **contango**, with the difference being statistically significant at the 10% level for two commodities, at the 5% level for one and at the 1% level for another.
-For the remaining six commodities the higher mean return during **contango** is not statistically significant for any of them.
-For the six GB commodities, all metals, five of them had higher mean returns during phases of **backwardation** as compared to **contango** in the first period, with one of these differences being statistically significant at the 10% level while for the remaining asset (Zinc (XLME)) the higher mean return during **contango** is not statistically significant.
+Over the first period twenty three of the thirty commodity assets considered have a higher mean returns during periods of **backwardation** as compared to **contango** (@fig-regimes) including eighteen US and five GB traded assets.
+For the US commodities the difference is statistically significant at the 10% level for two assets, at the 5% level for one and at the 1% level for another; for the remaining six commodities the higher mean return during **contango** is not statistically significant for any of them.
+For the GB commodities, the difference is significant at the 10% level for one asset while for the remaining asset the higher mean return during **contango** is not statistically significant.
 An equally weighted portfolio of the twenty-four US commodities had a mean return of 15.4% during **backwardation** phases, statistically significant at the 1% level, and a mean return of -1.1% during **contango**, both in the first period, with the difference between them statistically significant at the 5% level.
@@
 In this context, interconnectedness emerges as a crucial aspect that warrants thorough examination.
-We strive to address this issue by first examining the average returns pairwise correlations between commodities across the entire cross-section of the commodity assets considered in the study as well as by country, sector and sub-sector.
-@tbl-correlations-inner-periods shows the results for the four periods of interest with the results reported for the entire period as well as for periods of **backwardation** and **contango**.
+We strive to address this issue by first examining the average returns pairwise correlations between commodities across the entire cross-section of the commodity assets considered in the study as well as by country, sector and sub-sector with the results shown in @tbl-correlations-inner-periods.
 For the entire sample the average pairwise correlation jumps from 0.07 in the first period to 0.16 over financialisation.
@@
 These results thus suggest that the US metals sector was the driving force behind increased average pairwise correlations during financialisation, a new observation to the best of our knowledge.
-The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods.
-In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector^[A more detailed breakdown of country, sector and subsector average pairwise correlations is provided in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).].
+The pattern of correlations is very similar across phases of **backwardation** and **contango** for all the sectors and sub-sectors over the past and financialisation periods^[A breakdown of the average pairwise correlations by regime is provided in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).].
+In this context, the ontological consequences of financialisation are better observed from an investment perspective as illustrated in @tbl-correlations-cross-periods where we observe average pairwise correlation coefficients between equally weighted portfolios of US traded commodity assets grouped by sub-sector^[A more detailed breakdown of country, sector and subsector average pairwise correlations is provided in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).].
 Although modest in magnitude, these exhibit a telling pattern, mirroring that shown by the individual commodity returns in @tbl-stats-regime-tests, with a substantially higher average coefficient over **backwardation** phases in the first period (0.12 vs.
@@
 0.02).
-We break down @tbl-correlations-inner-periods's average correlations by year in @tbl-correlations-inner-years.
+We break down @tbl-correlations-inner-periods's average correlations by year in @fig-correlations.
 For the full sample of assets, the average pairwise correlations remain in the 0.06–0.08 range from 1998 through 2003, before suddenly increasing to 0.12 from 2003 to 2004.
@@
 In contrast, the corresponding figure for the energy sector shows a substantial decrease, down to 1.61 during financialisation from 2.33 over the past period.
-The corresponding pricing performance displays a similar pattern as shown in @tbl-regressions-factors where for each period the corresponding $R^{2}$ values are independently averaged over the entire period as well as over periods of **contango** and **backwardation**.
+The corresponding pricing performance displays a similar pattern as shown in @tbl-regressions-factors.
 The average $R^{2}$ for the market factor across the entire cross-section of commodity assets, including the GB traded base metals, increases to around 20% during financialisation compared to around 10% over the previous period with the rise driven by the metals sector at large.
@@
 This indicates an intensification of the higher interdependence within the full cross-section of commodities prompted by financialisation consistent with the greater interdependence between equity and commodity markets over this period documented in @silvennoinen_financialisation_2013.
-The figure for the US traded section of the metals sector only progresses modestly to 0.59 after peaking at 0.63 in 2006 (@tbl-correlations-inner-years).
+The figure for the US traded section of the metals sector only progresses modestly to 0.59 after peaking at 0.63 in 2006 (@fig-correlations).
 In contrast, the GB traded assets see a sharp increase to over 0.65 starting in 2007 up to a peak of 0.69 in 2010, and so does the agricultural sector with the sharpest increase in 2008 when the average pairwise correlation for the sector jumps to 0.30.
@@
 
-The returns pull-back continues into the post-crisis period (@tbl-stats-regime-tests) with twenty-two US and four GB traded assets showing lower mean returns relative to the crisis while the same number of US commodities and all GB metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and GB assets drop down to -0.2% and 2.7% respectively.
-Interestingly volatility also recedes substantially with twenty US assets and all GB metals showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
+The returns pull-back continues into the post-crisis period with twenty six commodities (@fig-estimates), including twenty-two US and four GB traded assets, showing lower mean returns relative to the crisis while the same number of US commodities and all GB metals show lower figures relative to the financialisation period; mean returns for equally weighted portfolios of US and GB assets (@tbl-stats-regime-tests) drop down to -0.2% and 2.7% respectively.
+Interestingly volatility also recedes substantially with twenty six commodities, including twenty US assets and all GB metals, showing lower volatility figures relative to both the crisis and financialisation periods suggesting that investment outflows from the commodity futures complex have had a lower impact on volatility than the corresponding inflows witnessed over the financialisation period.
 The figures for the equally weighted portfolios of US and GB assets drop to 9.9% and 16.2% respectively, very close to pre-financialisation levels.
-The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of **backwardation** relative to **contango**, more so than over the crisis period with seventeen US commodities showing higher mean returns over **backwardation** phases.
-The difference (@tbl-stats-regime-tests) is significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
+The pattern of reversion toward the pre-financialisation Keynesian paradigm initiated during the crisis continues stronger into the post-crisis period with mean returns higher during phases of **backwardation** relative to **contango** (@fig-regimes), more so than over the crisis period with twenty three commodities showing higher mean returns over **backwardation** phases.
+Seventeen of those are US traded assets with the difference significant at the 5% level for Lumber (XCME) and at the 10% level for Palladium (XNYM) while no difference is significant for the assets showing higher figures over phases of **contango**.
 The pattern is more pronounced for the GB traded subset with all six assets showing higher mean returns in **backwardation** with the difference significant at the 1% level for Nickel-primary (XLME), 5% level for Aluminium (XLME) and 10% level for Zinc (XLME).
 It also extends to equally weighted portfolios of US and GB traded assets that both show higher mean returns during **backwardation** with the difference significant at the 5% level for the GB portfolio and the figure close to the 10% level significance threshold for the portfolio of US assets.
-Volatilities are overall higher in **contango** although less so than over the previous period with seventeen US commodities showing higher figures over **contango** against twenty-three in the crisis period.
+Volatilities are overall higher in **contango** although less so than over the previous period with twenty one commodities showing higher figures over **contango** against twenty-eight in the crisis period, including seventeen US traded assets.
 The pattern extends to three of the six GB traded metals with the difference significant at the 1% level for Copper (XLME) and Tin (XLME) and at the 5% level for Zinc (XLME) while differences are not significant for Aluminium (XLME), Lead (XLME) and Nickel-primary (XLME) that exhibit higher volatility over **backwardation** phases.
@@
 While the average sub-sector portfolio return correlation remain stable (@tbl-correlations-cross-periods), the average individual asset pairwise correlations fall across the board, below the levels observed during financialisation, with the figure for the entire cross-section (@tbl-correlations-inner-periods) dropping down to 0.12 from 0.28 over the crisis.
-This substantial decline, that does not seem to have been widely noted, appears to begin in the latter part of the crisis period, around 2012 (@tbl-correlations-inner-years), before leveling down over the whole post-crisis period.
+This substantial decline, that does not seem to have been widely noted, appears to begin in the latter part of the crisis period, around 2012 (@fig-correlations), before leveling down over the whole post-crisis period.
 
@@
 These results, along with those from the crisis period, suggest that the exogenous shock of the financial crisis, combined with the subsequent accommodative monetary policy, may have triggered a reversion toward pre-financialization fundamentals in the commodity futures complex; an issue that, to our knowledge, has not been widely discussed in the existing literature.
-The phases analysis further documents the emerging role/dominance of the **contango** regime post-crisis with average correlations higher during those phases and the pattern stronger for the metal assets both US and GB traded.
+The phases analysis^[Results available in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).] further documents the emerging role/dominance of the **contango** regime post-crisis with average correlations higher during those phases and the pattern stronger for the metal assets both US and GB traded.
 Similarly, for the latter the pricing performance of the market factor is considerably better during phase of **contango** in contrast with the previous periods that showed no substantial difference between phase of **contango** and **backwardation**.
@@
 
-\newgeometry{margin=.75in}
+<!-- \newgeometry{margin=.75in} -->
 
-# Tables {.unnumbered}
+# Figures {.unnumbered}
+
+```{r}
+#| label: fig-estimates
+#| fig-cap: "This figure compares the evolution of estimates for mean (top panel) and volatility (bottom panel) for individual commodity returns across three period transitions: past → financialisation, financialisation → crisis and crisis → post-crisis.
+Each stacked bar shows how many cases fall into two categories: yellow (the estimate in the previous period is smaller than in the next period) and blue (the estimate in the previous period is larger than in the next period); numbers inside the bars indicate the count of observations in each category.
+Detailed results are available in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).
+Period definitions are discussed in @sec-methods while the results are discussed in @sec-results."
+#| fig-height: 6
+#| fig-width: 5
+
+estimates <- readr::read_rds(here::here(figures_directory_path, "estimates.rds"))
+estimates
+```
 
@@
 ```{r}
+#| label: fig-regimes
+#| fig-cap: "This figure compares estimates for mean (top panel) and volatility (bottom panel) for individual commodity returns between **CHP** regime phases (**backwardation** vs.
+**contango**) for the four periods.
+Each stacked bar shows how many cases fall into two categories: yellow (the estimate for the **backwardation phase** is smaller than for the **contango** phase) and blue (the estimate for the **backwardation phase** is greater than for the **contango** phase); numbers inside the bars indicate the count of observations in each category.
+**Backwardation** and **contango** regimes as well as period definitions are discussed in @sec-methods while the results are discussed in @sec-results."
+#| fig-height: 6
+#| fig-width: 5
+
+regimes <- readr::read_rds(here::here(figures_directory_path, "regimes.rds"))
+regimes
+```
+
+\newpage
+
+\newgeometry{margin=2.5cm}
+
+```{r}
+#| label: fig-correlations
+#| fig-cap: "While @tbl-correlations-inner-periods shows results computed independently for the four periods, this figure shows the results of the same analysis implemented for each year over the entire sample period.
+The corresponding figures along with a breakdown by sub-sector are provided in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).
+The results are discussed in @sec-results while @sec-taxonomy details the commodity assets taxonomy."
+#| fig-env: sidewaysfigure 
+#| fig-width: 11
+#| fig-height: 7
+
+correlations <- readr::read_rds(here::here(figures_directory_path, "correlations.rds"))
+correlations
+```
+
+\restoregeometry
+
+\newpage
+
+# Tables {.unnumbered}
+
+```{r}
 #| label: tbl-stats-regime-tests
-#| tbl-cap: "This table shows mean returns and volatilities for the individual commodities and two equally weighted portfolios of US and GB traded assets for the four periods.
-For each period, estimates are computed independently over the whole period--figure shown--as well as over phases of **backwardation** (b) and **contango** (c)--results in brackets.
-The table further shows the results of t-tests of significance for the mean returns computed over the whole periods and t-tests of difference between these when computed over the two phases independently along with F-tests of difference for the corresponding variances.
+#| tbl-cap: "This table shows mean returns and volatilities for two equally weighted portfolios of US and GB traded assets for the four periods.
+For each period, estimates are computed independently over the whole period as well as over phases of **backwardation** and **contango**.
+The table further shows the results of t-tests of significance for the mean returns as well as t-tests of difference between these when computed over the two phases independently along with F-tests of difference for the corresponding variances.
 Values significant at the 1%, 5% and 10% level are marked with \\\\*\\\\*\\\\*, \\\\*\\\\* and \\\\* respectively.
-Detailed results are available in the attached [Internet Appendix](http://bautheac.duckdns.org:3838/bautheac/co-movement/).
+Results for individual commodity assets are available in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).
 **Backwardation** and **contango** regimes as well as period definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results."
 
-table_name <- "stats-individuals - regime difference tests"
-columns_to_collapse_rows_for <- c("asset")
-colnames <- c("asset", "estimate", "past", "financialisation", "crisis", "post-crisis")
-align <- make_series_of_repeated_chars(list(l = 1L, r = 5L))
+table_name <- "stats-ew - regime difference tests"
+columns_to_collapse_rows_for <- c("asset", "estimate")
+colnames <- c("asset", "estimate", "regime", "past", "financialisation", "crisis", "post-crisis")
+align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
 longtable <- TRUE
-bold_columns <- 1L:6L 
-coloured_columns <- 3L:6L
+bold_columns <- 1L:7L 
+coloured_columns <- 4L:7L
 
@@
 #| tbl-cap: "This table shows the average return pairwise correlation coefficients computed independently across the whole cross-section of individual commodity assets as well as within countries and commodity sectors and sub-sectors for the four periods.
-For each period, the results are computed independently over the entire period as well as over phases of **backwardation** and **contango**.
+A breakdown of the average pairwise correlations by **CHP** regime (**backwardation** vs.
+**contango**) is provided in the attached [Internet Appendix](https://bautheac.shinyapps.io/co-movement/).
 **Backwardation** and **contango** regimes as well as period definitions are discussed in \\@sec-methods while the results are discussed in \\@sec-results and the commodity assets taxonomy is detailed in \\@sec-taxonomy."
@@
 table_name <- "correlations - inner - periods"
-columns_to_collapse_rows_for <- c("country", "sector", "subsector")
-colnames <- c(sectors, "regime", periods)
-align <- make_series_of_repeated_chars(list(l = 3L, r = 5L))
+columns_to_collapse_rows_for <- c("country", "sector")
+colnames <- c(sectors, periods)
+align <- make_series_of_repeated_chars(list(l = 3L, r = 4L))
 longtable <- TRUE
-bold_columns <- 1L:8L 
-coloured_columns <- 5L:8L
+bold_columns <- 1L:7L 
+coloured_columns <- 4L:7L
 
@@
 make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns)
-```
-
-\newpage
-
-```{r}
-#| label: tbl-correlations-inner-years
-#| tbl-cap: "While \\@tbl-correlations-inner-periods shows results computed independently for the four periods, this table shows the results of the same analysis implemented for each year over the entire sample period.
-The results are discussed in \\@sec-results while \\@sec-taxonomy details the commodity assets taxonomy."
-
-table_name <- "correlations - inner - years"
-columns_to_collapse_rows_for <- c("country", "sector", "subsector")
-colnames <- c(sectors, "decade", 0L:9L)
-align <- make_series_of_repeated_chars(list(l = 4L, r = 10L))
-longtable <- TRUE
-bold_columns <- 1L:14L
-coloured_columns <- 5L:14L
-
-make_table(table_name, columns_to_collapse_rows_for, colnames, align, longtable, bold_columns, coloured_columns) %>%
-  landscape()
 ```
